### 2017-11-02 TEX/draft1.tex
A first analysis note

\documentclass[12pt,a4paper]{article}

\pdfoutput=1

\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{color}
\usepackage{url}

\newcommand{\TODO}[1]{{\color{red}{[#1]}}}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
%\numberwithin{equation}{section}
%\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

\newtheorem*{lem*}{Lemma}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{plain}
\newtheorem{corollary}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{proposition}[thm]{\protect\propositionname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

%\usepackage{babel}
\providecommand{\claimname}{Claim}
\providecommand{\definitionname}{Definition}
\providecommand{\lemmaname}{Lemma}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\corollaryname}{Corollary}
\providecommand{\propositionname}{Proposition}

\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\E}[1]{\mathbb{E}\left\{{#1} \right\}}
\newcommand{\order}[1]{\mathcal{O}\left({#1} \right)}
\newcommand{\xz}{x_{\textrm{zp}}}
\newcommand{\DFT}[1]{\operatorname{DFT}\!\left( {#1} \right)}
\newcommand{\hx}{\hat{x}}

\begin{document}

%\begin{frontmatter}

\title{Small MRI is boring}

\author{Tamir Bendory}
\maketitle

We consider the problem of estimating a signal $x\in\RL$ from one measurement $y\in\RN, \thinspace N\gg L,$ that contains many repetitions of this signal, at unknown locations, swallowed in noise.

Formally, our model read
\begin{equation}
y[n] = \sum_{i=1}^K \xz [n-n_i] + \varepsilon[n], 
\end{equation}
where:
\begin{itemize}
	\item $y\in\RN$ is the noisy acquired data (measurement),
	\item $\xz\in\RN$ is a zero-padded version of $x\in\RL, \thinspace L\ll N,
	$ defined as $\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]$,
	\item $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$, 
	\item  $\varepsilon$ is i.i.d.\ normal noise with mean zero and variance $\sigma^2$ .
\end{itemize}

Note that both $x$ and the translations $n_i$ are unknown. Therefore, essentially, this is a blind deconvolution problem. Particularly, let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise. 
Then, 
\begin{equation}
y = \xz \ast s + \varepsilon,
\end{equation}
and the goal is then to estimate $x$ from $y$ although $s$ is unknown as well.

For small values of $\sigma$,  the problem is easy. In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding). Once several copies of  signal were detected and cropped from $y$, then one can  improve the SNR by averaging. We are interest in the more challenging regime of high noise level, in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances. In this case, one need to use the prior information that the signal appears many times across the measurement.

To perform this blind deconvolution, we use the invariant approach proposed for multireference alignment in a previous paper. Let us  first introduce  notation. We crop the measurement $y\in\RN$ into a series of analysis windows: 
\begin{equation}
    y_i = y[(i-1)W + 1 : iW ]\in\mathbb{R}^W, \quad i=1,\ldots,N/W, 
\end{equation}
To ease notation, we assume that  $W$ divides $N$  so that there are exactly $N/W$ windows. We also assume that $\vert n_i - n_j\vert >W$ so that each window contains no more than one signal (in general, we can introduce overlapping windows. The code enables it, but it does not seem to improve performance.).
For each one of the windows, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum. We then hope that averaging over these features will produce a reliable estimation of the invariant features of the signal itself. 
We recall that given accurate estimators of those features, we can estimate the signal itself reliably. Therefore, the question boils down to the accuracy of these feature estimations.

Before moving ahead to the feature estimators, we need to estimate the norm of the signal. This is necessary since many analysis windows do not contain information on the signal, but pure noise. We will use the norm to scale the the signal's estimator.
This can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$. 
Then,
\begin{equation}
\| y\|_2^2 =  \| x_K\|_2^2 + \|\varepsilon\|_2^2 + 2\varepsilon^Tx_K. 
\end{equation}  
As $N\to\infty$, we can estimate 
\begin{equation}
\begin{split}
\E{\| y\|_2^2} &=  \| x_K\|_2^2 + \E{\|\varepsilon\|_2^2} + 2\E{\varepsilon^Tx_K} \\ 
&= K\|x\|_2^2 + N\sigma^2. 
\end{split}	 
\end{equation}   
 And therefore, 
 \begin{equation}
 \|x\|_2^2 \approxeq \frac{\| y\|_2^2 - N\sigma^2}{K}. 
 \end{equation}

Next, we analyze the feature estimation in the asymptotic regime of $N,\sigma,K\to\infty$ and fixed $L,W$. We introduce the ``sparsity factor" defined as $S = \frac{N}{WK}<\infty$, $WK$ is a measure for the ``active" windows. We also define  another zero padded signal $x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W$.

 We want to estimate the features of this signal, and focus on the bispectrum for the sake of simplicity (the estimation of the power spectrum and mean obeys the same methodology). 
In order to estimate the bispectrum we average over the bispectra of the windows, namely, (for the power spectrum, we need to do unbiasing. In addition, we can replace the mean by more robust estimator, like the median.)
\begin{eqnarray}
\hat{B}_{x_W} = \frac{W}{N}\sum_{i=1}^{N/W}B_{y_i}.
\end{eqnarray}
We split the sum into three groups of the windows:
\begin{eqnarray}
\hat{B}_{x_W} = B_\textrm{signal} + B_\textrm{clutter} + B_\textrm{noise}, 
\end{eqnarray}
where
\begin{itemize}
	\item $B_\textrm{noise}$ - sum of the bispectra of the segments that contain pure noise (no signal),
	\item $B_\textrm{signal}$ - sum of the bispectra of the segments that contain a full signal (one appearance of $x$) and noise,
	\item $B_\textrm{clutter}$ - sum of the bispectra of the segments that contain only part of $x$ and noise.
\end{itemize}

We first observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix). More precisely, the variance of the noise goes to zero at rate  $\order{\frac{W}{N}\left(1-\frac{1}{S}\right)\sigma^6}$. In addition, under the assumption that $n_i$ (if appear) are distributed uniformly in the window (we need to come up with precise statistical model; but it would be rather easy), there are (asymptotically) $K(1-L/W)$ windows with complete signals. Therefore,
 $B_\textrm{signal}\to \frac{KW(1-L/W)}{N}B_x$ at rate $\order{\frac{\sigma^6}{K(1-L/W)}}$. (Here we need to be a bit careful with the mean of the signal, or to assume it is zero.) Note that the scaling would be corrected at the last stage of the algorithm, by rescaling according to the estimated  norm.

 The more interesting term is the ``clutter" --- the cropped signals. Since each such signal appears in two windows,
 we have $2KL/W$ clutter segments. Of course, the noise in this segments goes to zero
 at rate $\order{\frac{W\sigma^6}{2KL}}$. However, we have an additional error term arises from  the cropped signals. To analyze the effect of this term, let us assume that $N/\sigma^6$ is great enough so that $B_\textrm{noise}\to 0$. Then,
\begin{equation}
\begin{split}
\left\| \hat{B}_{x_W} - B_\textrm{signal}\right\|_{\textrm{F}} \approxeq&  \left\|B_\textrm{clutter}\right\|_{\textrm{F}}
= \left\|\frac{W}{N}\sum_{i\in\textrm{clutter}}B_{y_i}\right\|_{\textrm{F}}
\\ \leq & 
\frac{W}{N}\frac{2KL}{W}\left\|B_x\right\|_{\textrm{F}} = \frac{2L}{SW}
\|B_x\|_{\textrm{F}}.
\end{split}
\end{equation}
Therefore, for large sparsity term $S$ or large $W/L$, we get an accurate estimation of a scaled version of the signal's bispectrum.

Few insights from the analysis: (need to check numerically)
\begin{itemize}
	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
	\item Larger $W/L$ reduces the clutter error, however, increases the variance of the noise  of $B_\textrm{noise}$.
	\item We must keep $W/L$ large enough to see enough full signals.    
\end{itemize} 
%\bibliographystyle{plain}
%\bibliography{ref}

\end{document}

### 2017-11-02 main6.m

@@ -1,44 +1,0 @@
-clear; close all; clc;
-dbstop if error
-L = 10; % length of signal
-%x = randn(L,1); x = x/norm(x);
-x = ones(L,1); %x = x/norm(x);
-
-N = 50000;
-k = 100;
-sigma = .1;
-
-
-[y ind] = gen_data(x,N,k,L,sigma);
-
-
-%% running over indices
-max_iter = 1000;
-x_est = randn(L,1);
-ys = [y ; y(1:L)];
-w = zeros(N,max_iter);
-err = zeros(max_iter,1);
-
-for iter = 1:max_iter
-    
-    for i = 1:N
-        w(i,iter) = exp(-norm(ys(i:i+L-1) - x_est)/2/(sigma^2));
-    end
-    
-    w(:,iter) = w(:,iter)/sum(w(:,iter)); %normalization
-    
-    x_new = zeros(L,1);
-    for i = 1:N
-        x_new = x_new + ys(i:i+L-1)*w(i,iter);
-    end
-    x_est = x_new/norm(x_new)*norm(x); 
-    %x_est = x_new/norm(x_new)*norm(x);
-    err(iter) = norm(x - x_est);% /norm(x);
-end
-
-figure; plot(err)
-%%
-
-figure; hold on;
-stem(x); stem(x_est,'*r');
-legend('signal','recovered');

### 2017-11-03 TEX/draft2.tex
New note  + update the EM code (still doesn't work)

--- 2017-11-02 TEX/draft1.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-%\numberwithin{equation}{section}
-%\numberwithin{figure}{section}
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
 \theoremstyle{plain}
@@
 
-\title{Small MRI is boring}
-
+\title{Multireference alignment meets blind deconvolution}
 \author{Tamir Bendory}
@@
 
-We consider the problem of estimating a signal $x\in\RL$ from one measurement $y\in\RN, \thinspace N\gg L,$ that contains many repetitions of this signal, at unknown locations, swallowed in noise.
+\begin{abstract}
+	Here comes the abstract
+\end{abstract}
 
+\section{Introduction} \label{sec:introduction}
+
+Blind deconvolution is the problem of estimating a signal from its convolution with an unknown kernel.
+This problem arises in many engineering and scientific applications, such as astronomy, communication, deblurring and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind} to name a few.
+
+Without prior information the blind deconvolution is clearly ill-posed.
+In this note, we consider a special case of the problem.
+We aim at estimating a signal $x\in\RL$ from $y\in\RN, \thinspace N\gg L$.
+The acquired data, the measurement $y$, is composed of many repetitions of $x$, at different positions, and i.i.d.\ normal noise $\varepsilon $with mean zero and variance $\sigma^2$.
 Formally, our model read
@@
 \end{equation}
-where:
-\begin{itemize}
-	\item $y\in\RN$ is the noisy acquired data (measurement),
-	\item $\xz\in\RN$ is a zero-padded version of $x\in\RL, \thinspace L\ll N,
-	$ defined as $\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]$,
-	\item $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$, 
-	\item  $\varepsilon$ is i.i.d.\ normal noise with mean zero and variance $\sigma^2$ .
-\end{itemize}
+where $\xz\in\RN$ is a zero-padded version of $x\in\RL$ and 
+defined as $$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}],$$ and
+ $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$.
 
-Note that both $x$ and the translations $n_i$ are unknown.
-Therefore, essentially, this is a blind deconvolution problem.
-Particularly, let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise.
+Note that both $x$ and the translations, or positions, $n_i$ are unknown. Let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise. 
 Then, 
 \begin{equation}
-y = \xz \ast s + \varepsilon,
+y = \xz \ast s + \varepsilon.
 \end{equation}
-and the goal is then to estimate $x$ from $y$ although $s$ is unknown as well.
+The goal is then to estimate $x$ from $y$, while $s$ is unknown as well.
+The support signal $s$ is the latent or hidden variable of the problem.
+This is quite common in blind deconvolution problem.
+For instance, in image deblurring, the both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.
+
+Recent papers on blind deconvolution and deconvolution.
 
@@
 
+\section{Literature survey} \label{sec:literature}
+
+\section{Connection with the cryo--EM problem} \label{sec:cryoEM}
+particle picking
+
+\section{Algorithm} \label{sec:algorithm}
+
 Before moving ahead to the feature estimators, we need to estimate the norm of the signal.
@@
 \end{equation}
+
+\section{Analysis} \label{sec:analysis}
 
@@
 \end{itemize}
-%\bibliographystyle{plain}
-%\bibliography{ref}
+
+\section{Conclusion} \label{sec:conclusion}
+
+\bibliographystyle{plain}
+\bibliography{ref}
 

### 2017-11-03 mra.m

@@ -1,61 +1,0 @@
-clear; close all; clc;
-
-L = 4; % length of signal
-x = randn(L,1); x = x - mean(x);
-
-N = 10000;
-
-k = 300;
-
-sigma = 0;
-
-y = sigma*randn(N,1);
-ind = randi(N, k, 1);
-
-ind  = sort(ind);
-indn = ind(1);
-for i = 1:length(ind)-1
-    if ind(i+1) - ind(i) > 2*L
-        indn = [indn; ind(i+1)];
-    end
-end
-
-ind = indn;
-
-for i = 1:length(ind)
-    y( ind(i): ind(i)+L-1) = y( ind(i): ind(i)+L-1) +  x;
-end
-
-
-%%  
-
-x0 = randn(L,1);
-x0 = x0/norm(x0)*norm(x);
-xest = x0;
-num_iter = 20;
-err = zeros(num_iter,1);
-%C = err; 
-max_corr = zeros(N,1);
-
-for iter = 1:num_iter
-    xest_iter = xest;
-    for i = 0:N-1
-        
-        [y_aligned, max_corr(i+1), ind] = align_to_reference(y( mod((i: i+L-1),N)+1), xest);
-        xest_iter = xest_iter +  y_aligned*max_corr(i+1);
-        
-    end
-    
-    C(iter) = sum(max_corr);
-    xest = xest_iter;
-    xest = xest/norm(xest)*norm(x);
-    xest = xest - mean(xest);
-    
-    [xest_aligned,~, ~] = align_to_reference(xest, x);
-    err(iter) = norm(xest_aligned - x)/norm(x);
-    
-end
-
-figure; plot(err); 
-figure; hold on; plot(x); plot(xest_aligned); xlim([1,L])
-figure; plot(C);  title('C');

### 2017-11-03 mra_invariants.m

@@ -3,17 +3,17 @@ clear; close all; clc;
 %% Defining the problem
 
 L = 21; % length of signal
-k = 1e3; %5e6; %2*500000; % # of signal's repetitions (maximal number)
-sigma = 1;  % noise level2
+k = 1e4; %5e6; %2*500000; % # of signal's repetitions (maximal number)
+sigma = 3;  % noise level2
 window_size = 4*L; 
-Nfactor = 4; % Sparsity factor, should be ~6
+Nfactor = 6; % Sparsity factor, should be ~6
 N = window_size*k*Nfactor; % # of measurements
 overlapping_factor = 1; % windows are overlapped by window_size/overlapping_factor
 %% Generating data
 tic
 x = randn(L,1); 
 [y,yc, ind] = gen_data(x,N,k,sigma,window_size);
-snr = norm(yc)^2/norm(y)^2; % The problem's SNR
+snr = norm(yc)^2/norm(y-yc)^2; % The problem's SNR
 k_eff = length(ind); % The actual nunber of signal's repetitions
 fprintf('Measurement length  = %e \n',N);
 fprintf('The measurement contains %.1e repetitions of the underlying signal (from %.1e)\n',k_eff,k);
@@ -31,7 +31,11 @@ fprintf('Error of norm''s estimation = %.4f  \n',Err_normX);
 %% rearraging the matrix data
 
 tic
+if overlapping_factor == 1
+y_mat = reshape(y, window_size,N/window_size);
+else
 y_mat = gen_data_mtx(y,window_size,overlapping_factor);
+end
 assert(size(y_mat,1)==window_size && size(y_mat,2)==N/window_size*overlapping_factor, 'Something is wrong with the data dimensions');
 fprintf('Constructing data matrix time = %.2f [sec] \n',toc);     
 
@@ -48,27 +52,28 @@ x_est = real(ifft(sqrt(P_est).*z));
 xref = zeros(window_size,1); xref(1:L) = x;
 [x_aligned,~, ~] = align_to_reference(x_est, xref);
 x_aligned = x_aligned(1:L); 
-% using norm(x) for for a while
-%x_aligned = x_aligned/norm(x_aligned)*norm(x);
-% correcting with norm estimation
 x_aligned = x_aligned/norm(x_aligned)*normX;
 fprintf('Algorithm time = %.2f [sec] \n',toc);
 
 %% plotting
 
[…]

### 2017-11-03 TEX/draft2.tex
Latest code corrections and extended writing up

@@
 For instance, in image deblurring, the both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.
+In Section~\ref{sec:literature} we survey previous results on blind deconvolution.
 
-Recent papers on blind deconvolution and deconvolution.
-
-For small values of $\sigma$,  the problem is easy.
-In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding).
+Figure~\ref{fig:example} shows examples for the data in different noise levels.
+In the low noise regime (for instance, the first row), the problem is easy.
+In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding on the correlation function).
 Once several copies of  signal were detected and cropped from $y$, then one can  improve the SNR by averaging.
@@
 In this case, one need to use the prior information that the signal appears many times across the measurement.
+
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale = .4]{example}
+	\end{center}
+\caption{fdnjfk}
+\label{fig:example}
+\end{figure}
 

### 2017-11-03 example_problem.m

@@ -1,0 +1,54 @@
+clear; close all; clc;
+
+%% Defining the problem
+
+L = 21; % length of signal
+k = 2; %5e6; %2*500000; % # of signal's repetitions (maximal number)
+window_size = 4*L; 
+Nfactor = 2; % Sparsity factor, should be ~6
+N = window_size*k*Nfactor; % # of measurements
+overlapping_factor = 1; % windows are overlapped by window_size/overlapping_factor
+%% Generating data
+tic
+x = randn(L,1); 
+[y,yc, ind] = gen_data(x,N,k,0,window_size);
+
+sigma_vec = [0.1 , 0.7, 2.5];  % noise level2
+
+figure; 
+
+for ii = 1:length(sigma_vec)
+sigma = sigma_vec(ii);
+y = yc + sigma*randn(N,1);
+snr = norm(yc)^2/norm(y-yc)^2; % The problem's SNR
+k_eff = length(ind); % The actual nunber of signal's repetitions
+fprintf('Measurement length  = %e \n',N);
+fprintf('The measurement contains %.1e repetitions of the underlying signal (from %.1e)\n',k_eff,k);
+fprintf('SNR = %.4f \n',snr);
+fprintf('Generating data time = %.2f [sec] \n',toc);
+%estimating the signal's norm from the data
+normX = sqrt((norm(y)^2 - sigma^2*N)/k_eff);
+Err_normX = abs(norm(x) - normX)/norm(x);
+fprintf('Error of norm''s estimation = %.4f  \n',Err_normX);
+
+%sanity check: note that yc == cconv(x,s,N);
+%s = zeros(N,1); s(ind) = 1;
+%norm(yc - cconv(x,s,N))
+
+%% plotting
+
+ln = 2;
+
+subplot( length(sigma_vec),2,(ii-1)*2+1); title(strcat('sigma = ', num2str(sigma)));
+hold on; plot(1:N,yc,'linewidth',ln); plot(1:N,y);
+legend('clean data','data');
+%title(strcat('N =', num2str(N),', L=',num2str(L), ', K=',num2str(k_eff),', SNR=',num2str(snr)));
+axis tight
+w = flipud(xcorr(x,y));
+subplot(length(sigma_vec),2,(ii-1)*2+2);  plot(1:N,w(N:end),'linewidth',ln); 
+if ii==1 title('correlation between x and y'); end
+axis tight
+
+end
+
+pdf_print_code(gcf, 'example', 11)

### 2017-11-03 main_em.m

@@ -3,8 +3,8 @@ clear; close all; clc;
 %% Defining the problem
 
 L = 21; % length of signal
-k = 1e2; %5e6; %2*500000; % # of signal's repetitions (maximal number)
-sigma = 0.5;  % noise level2
+k = 1e3; %5e6; %2*500000; % # of signal's repetitions (maximal number)
+sigma = 0.1;  % noise level2
 window_size = 4*L; 
 Nfactor = 6; % Sparsity factor, should be ~6
 N = window_size*k*Nfactor; % # of measurements
@@ -36,7 +36,7 @@ end
 clear y_stretch;
 
 %% EM iterations
-num_iter = 10;
+num_iter = 100;
 xest = zeros(L,num_iter+1);
 %xest(:,1) = x; %intial guess
 xest(:,1) = fft(randn(L,1)); xest(B+2:L-B,1) = 0; 
@@ -47,16 +47,16 @@ w = zeros(N,1); sigma_em = sigma;
 
 for iter = 1:num_iter
     X = repmat(xest(:,iter),1,N)';
-    S = sum((X-y_mat).^2,2);
+    S = -0.5/(sigma_em^2)*sum((X-y_mat).^2,2);
     S = S - max(S(:));
-    w = exp(-0.5/(sigma_em^2)*S);
+    w = exp(S);
     w = w/sum(w); 
     %Maxw = max(w);
     %w(w<0.01*Maxw) = 0;
     xest(:,iter+1) = w'*y_mat; 
     xest(:,iter+1) = xest(:,iter+1)/norm(xest(:,iter+1))*norm(x); %plugging in norm(x)
     err(iter+1) = norm(x - xest(:,iter+1))/norm(x);
-    if norm(xest(:,iter+1) - xest(:,iter))<10^-6
+    if norm(xest(:,iter+1) - xest(:,iter))<10^-10
         break
     end
 end
@@ -82,6 +82,6 @@ subplot(413); hold on; plot(inds:indf,w(inds:indf),'linewidth',2);
 title('weights');
 axis tight
 
-subplot(414); hold on; plot(err,'linewidth',2); 
+subplot(414); hold on; plot(err(1:iter+1),'linewidth',2); 
 title('Error'); xlabel('iteration'); ylabel('error')
 axis tight

### 2017-11-06 TEX/draft2.tex
Made some progress with the write-up.

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[journal]{IEEEtran}
 
@@
 Blind deconvolution is the problem of estimating a signal from its convolution with an unknown kernel.
-This problem arises in many engineering and scientific applications, such as astronomy, communication, deblurring and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind} to name a few.
+This problem arises in many engineering and scientific applications, such as astronomy, communication, deblurring, acoustics, system identification and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind,lin2005relevant,abed1997blind}, just to name a few.
 
-Without prior information the blind deconvolution is clearly ill-posed.
+Without prior information, the blind deconvolution is clearly ill-posed.
 In this note, we consider a special case of the problem.
 We aim at estimating a signal $x\in\RL$ from $y\in\RN, \thinspace N\gg L$.
-The acquired data, the measurement $y$, is composed of many repetitions of $x$, at different positions, and i.i.d.\ normal noise $\varepsilon $with mean zero and variance $\sigma^2$.
+The acquired data, the measurement $y$, is composed of many repetitions of $x$, at different positions, and i.i.d.\ normal noise $\varepsilon$ with mean zero and variance $\sigma^2$.
 Formally, our model read
@@
 \end{equation}
-where $\xz\in\RN$ is a zero-padded version of $x\in\RL$ and 
+where $\xz\in\RN$ is a zero-padded version of $x\in\RL$  
 defined as $$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}],$$ and
@@
 The support signal $s$ is the latent or hidden variable of the problem.
-This is quite common in blind deconvolution problem.
-For instance, in image deblurring, the both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.
+The situation where both signals are unknown, but the goal is merely estimating one of them  is quite common situation in blind deconvolution problem.
+For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.
 In Section~\ref{sec:literature} we survey previous results on blind deconvolution.
 
-Figure~\ref{fig:example} shows examples for the data in different noise levels.
-In the low noise regime (for instance, the first row), the problem is easy.
+Figure~\ref{fig:example} shows examples of the problemin different noise levels.
+In the low noise regime (for instance, the first row), the problem is rather easy.
 In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding on the correlation function).
-Once several copies of  signal were detected and cropped from $y$, then one can  improve the SNR by averaging.
+Once several copies of the signal were detected and cropped from $y$, then one can  improve the SNR by averaging.
 We are interest in the more challenging regime of high noise level, in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances.
@@
 
+\begin{figure*}
+	\begin{center}
+	\includegraphics[scale = .5]{example}
+	\end{center}
+\caption{The left column presents the clean data and the measurement in different noise levels.
+In this example, a signal of length $L=21$ appears twice in a measurement of length $N=336$ with different noise levels.
+Note to the different scale of the y-axis.
+The right column presents the correlation between the signal and the measurement for the associated problems.
+}
+\label{fig:example}
+\end{figure*}
+
+Our approach for this blind deconvolution problem utilized  tools recently that were developed for the multireference alignment problem.
+Multireference alignment (MRA) is the problem of estimating a signal from its circularly-shifted noisy measurements~\cite{bandeira2014multireference,bendory2017bispectrum}.
+In Section~\ref{sec:mra}, we survey recent works in this field and its relation with our problem.
+Particularly, we use the method proposed in~\cite{bendory2017bispectrum} of invariant features.
+In short, the idea is to split $y$ into a bunch of shorter windows.
+If each window contains exactly  one signal, then the problem reduces exactly the MRA problem.
+However, this is not the case.
+Some windows contain only noise, while others contain both noise and parts of a signal.
+In Section~\ref{sec:algorithm} we present and discuss the algorithm.
+
+The outline of this paper is as follows.
+In Section~\ref{sec:literature} we introduce the background of relevant papers for this work.
+Particularly, in Section~\ref{sec:blind_deconvolution} we discuss the blind deconvolution problem and in Section~\ref{sec:mra} we introduce and survey the MRA problem.
+In Section~\ref{sec:cryoEM} we introduce the mathematical formulation of the cryo--electron microscopy (EM) imaging technique.
+The model we consider in this note can be viewed as a simplified model for the cryo--EM problem as will be explained.
+In Section~\ref{sec:algorithm} we introduce of algorithm and analyze it in Section~\ref{sec:analysis}.
+Section~\ref{sec:experiments} is devoted for numerical experiments.
+Section~\ref{sec:conclusion} concludes the manuscript.
+
+\section{background and literature survey} \label{sec:literature}
+
+In this section, we introduce the two main ingredients of this work, blind deconvolution and MRA.
+
+\subsection{Blind deconvolution} \label{sec:blind_deconvolution}
+
+Blind deconvolution is the problem of recovering a signal from its convolution with unknown kernel. That is, recovery of $x$ from
+\begin{equation}
+y = x\ast k,
+\end{equation}
+where both $x$ and $k$ are unknown. In the Fourier domain, it takes the form of 
+\begin{equation}
+Fy = Fx \odot Fk,
+\end{equation}
+where $Fz$ stands for the Fourier transform of $z$.
+
+Clearly, without prior information of the signal, it is impossible to estimate the signal.
+The problem has been analyzed recently with a various convex and non-convex algorithms under the assumption that the signal is in a known  subspace spanned by vectors with random entries~\cite{ahmed2014blind,li2016rapid,ling2017blind}
+and under sparsity in a random linear subspaces~\cite{lee2017blind,li2016identifiability,kech2017optimal,ling2015self,chi2016guaranteed,li2015unified}.
+
+We briefly mention that the deconvolution problem, namely, when the kernel is assumed to be known, has been analyzed throughly in recent years under sparsity constraints~\cite{bendory2016robust,bendory2017robust,bendory2016stable,boyer2017adapting,bernstein2017deconvolution,de2012exact,azais2015spike,duval2015exact,duval2015sparse}.
+Nonetheless, the problem under consideration is essentially different.
+From two reasons.
+First, of course, we consider the blind setting when the kernel is unknown.
+Second, these works considered the recovery of sparse signal, with Gaussian-like kernel.
+In our problem, the convolution kernel is sparse, and we aim to recover a general signal.
+
+As far as we know, no work considered the blind deconvolution considered in this manuscript. In~\cite{choudhary2014sparse}, it  was shown that 
+a simple sparsity assumption in the canonical basis is insufficient
+for unique recovery.
+However, here we also assume that the sparse signal is binary.
+In addition, we mainly care of the problem in the high noise regime and understanding how the relations between the parameters of the data effects the estimation error.
+
+\subsection{Multireference alignment} \label{sec:mra}
+
+Multireference alignment is the problem of estimating a signal $x\in\RL$ from its circularly shifted noisy measurements
+\begin{equation} \label{eq:mra}
+y_j = R_{r_j}x + \varepsilon_j, \quad j = 1,\ldots,N
+\end{equation}
+where $R_{r}$ translates a signal by $r$ locations, namely, $(R_rx)[i] = x[i-r]$, and $\varepsilon$ is an i.i.d.\ normal noise with mean zero and variance $\sigma^2$.
+This problem has application in radar, image processing and structural biology~\cite{zwart2003fast,foroosh2002extension,diamond1992multiple}.
+The algorithmic and statistical characterizations of this problem have been analyzed thoroughly in the last couple of years, see~\cite{bendory2017bispectrum,bandeira2014multireference,bandeira2017optimal,perry2017sample,boumal2017heterogeneous,abbe2017multireference,abbe2017sample}.
+
+In this work, we exploit the framework proposed in~\cite{bendory2017bispectrum}.
+The idea is to use features of the signal that are invariant under translation.
+Specifically, it was proposed to estimate the mean, power spectrum and bispectrum of the signal from the data.
+The estimation is performed by averaging over the features of the measurements.
+Let $\mu_z,P_z$ and $B_z$ denote the mean, power spectrum and bispectrum of a signal $z$.
+Then, it can be shown that
+\begin{align}
+\frac{1}{N}\sum_{i=1}^N\mu_{y_j}  &\,\to \, \mu_x, \\
+\frac{1}{N}\sum_{i=1}^NP_{y_j}  &\,\to \, P_x + L\sigma^2, \\
+\frac{1}{N}\sum_{i=1}^NB_{y_j}  &\,\to \, B_x + \mu_x\sigma^2L^2A, 
+\end{align} 
+where $A$ is a known deterministic matrix.
+Therefore, by proper debiasing, one can get a reliable estimating of these features.
+For $\sigma,N\to\infty$, the estimation rate is dominated by the bispectrum and thus the estimation rate is $\sigma^6/N$, which is optimal for uniform distribution of translations~\cite{bandeira2017optimal}.
+Given reliable estimation of the features, the signal can be accurately estimated, up to translation, using a variety of algorithms~\cite{bendory2017bispectrum}.
+
+\subsection{Connection with the cryo--EM problem} \label{sec:cryoEM}
+
+This work is partially motivated by the imaging
+technique called single particle Cryo--EM, enabling the visualization of molecules at near atomic resolution~\cite{bartesaghi20152,sirohi20163}.
+In cryo--EM, many samples of a molecule are frozen in a thin sheet of ice.
+Then, the microscope transmits electrons and we acquire  several images, called \emph{micrographs}, that contains the two-dimensional tomographic projections of the samples.
+The  cryo--EM
+problem is then to estimate the molecules from several micrographs.
+
 \begin{figure}
 	\begin{center}
-	\includegraphics[scale = .4]{example}
+		\includegraphics[scale = .4]{cryoem-eps-converted-to}
 	\end{center}
-\caption{fdnjfk}
-\label{fig:example}
+	\caption{A schematic draw of the micrograph generation. Courtesy of ?}
+	\label{fig:cryo-EM}
 \end{figure}
 
-To perform this blind deconvolution, we use the invariant approach proposed for multireference alignment in a previous paper.
-Let us  first introduce  notation.
-We crop the measurement $y\in\RN$ into a series of analysis windows:
-\begin{equation}
-y_i = y[(i-1)W + 1 : iW ]\in\mathbb{R}^W, \quad i=1,\ldots,N/W, 
+\begin{figure}
+	\begin{center}
+		\includegraphics[scale = .35]{cryoem-problem-eps-converted-to}		
+	\end{center}
+	\caption{The cryo--EM problem: estimating a molecule from the micrograph. Courtesy of ?}
+	\label{fig:cryo-EM-problem}
+\end{figure}
+
+A standard cryo--EM reconstruction algorithm starts with a stage called \emph{particle picking} [ref].
+In this stage, the projections are detected in the micrographs, and then cropped.
+Then, ideally, one get a set of measurements of the form
+\begin{equation} \label{eq:cryo-em}
+y_j = \mathcal{P}( g_j\circ x) + \varepsilon_j,\quad j=1,\ldots,N, 
 \end{equation}
-To ease notation, we assume that  $W$ divides $N$  so that there are exactly $N/W$ windows.
-We also assume that $\vert n_i - n_j\vert >W$ so that each window contains no more than one signal (in general, we can introduce overlapping windows.
-The code enables it, but it does not seem to improve performance.).
-For each one of the windows, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum.
-We then hope that averaging over these features will produce a reliable estimation of the invariant features of the signal itself.
-We recall that given accurate estimators of those features, we can estimate the signal itself reliably. Therefore, the question boils down to the accuracy of these feature estimations.
+where $x$ is the three-dimensional molecule to be estimated,  $g_j\in SO(3)$ are unknown 3D rotations that act on the molecule and $\mathcal{P}$ is a tomographic projection.
+This model has been analyzed theoretically from different point--of-views~\cite{bandeira2015non,hadani2011representation} [more ref].
+The MRA model~\ref{eq:mra} can be interpreted as a simplification of the cryo--EM problem, where the unknown shifts correspond to the unknown rotations (but there is no analog for the projection operation).
 
-\section{Literature survey} \label{sec:literature}
+In practice, particle picking algorithms are far from being optimal.
+For instance, the projections in the cropped images are not centered, and therefore an unknown  two-dimensional translation should be added to the model~\eqref{eq:cryo-em}.
+In addition, most of the particle picking algorithms throw away many particles since they fail to detect them.
+Hence, a necessary condition for the success of such algorithm is that the noise level would low enough so that detection would be possible.
 
-\section{Connection with the cryo--EM problem} \label{sec:cryoEM}
-particle picking
+Our work can be viewed as a first stage towards answering the question whether molecule estimation is possible in a very low SNR regime, where \emph{detection is impossible}.
+Our model can be seen as a very simplified cryo--EM model, where $y$ corresponds to the micrograph and the signal repeated signal $x$ to the molecule.
+The success to estimate the signal in the very low SNR regime may indicate that the molecule can be estimated directly from the cryo--EM micrographs, even if the SNR is so low that particle picking fails.
 
@@
 \end{equation}
+
+To perform this blind deconvolution, we use the invariant approach proposed for multireference alignment in a previous paper.
+Let us  first introduce  notation.
+We crop the measurement $y\in\RN$ into a series of analysis windows:
+\begin{equation}
+y_i = y[(i-1)W + 1 : iW ]\in\mathbb{R}^W, \quad i=1,\ldots,N/W, 
+\end{equation}
+To ease notation, we assume that  $W$ divides $N$  so that there are exactly $N/W$ windows.
+We also assume that $\vert n_i - n_j\vert >W$ so that each window contains no more than one signal (in general, we can introduce overlapping windows.
+The code enables it, but it does not seem to improve performance.).
+For each one of the windows, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum.
+We then hope that averaging over these features will produce a reliable estimation of the invariant features of the signal itself.
+We recall that given accurate estimators of those features, we can estimate the signal itself reliably. Therefore, the question boils down to the accuracy of these feature estimations.
 
@@
 
+\section{Numerical experiments} \label{sec:experiments}
+
 \section{Conclusion} \label{sec:conclusion}

### 2017-11-14 TEX/draft2.tex
Some updates for the first two sections

--- 2017-11-03 TEX/draft2.tex
@@
 \usepackage{url}
+
+\usepackage{algorithm}
 
@@
 \newcommand{\CL}{\mathbb{C}^L}
+\newcommand{\CN}{\mathbb{C}^N}
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
@@
 \newcommand{\xz}{x_{\textrm{zp}}}
-\newcommand{\DFT}[1]{\operatorname{DFT}\!\left( {#1} \right)}
+\newcommand{\DFT}{\operatorname{DFT}}
+\newcommand{\SNR}{\operatorname{SNR}}
 \newcommand{\hx}{\hat{x}}
@@
 
+\begin{IEEEkeywords}
+	Blind deconvolution, multireference alignment, bispectrum, cryo-EM
+\end{IEEEkeywords}
+
 \section{Introduction} \label{sec:introduction}
 
-Blind deconvolution is the problem of estimating a signal from its convolution with an unknown kernel.
-This problem arises in many engineering and scientific applications, such as astronomy, communication, deblurring and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind} to name a few.
+Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind,lin2005relevant,abed1997blind}, just to name a few.
+In blind deconvolution, we aim at estimating  a signal from its convolution with an unknown kernel.
+Clearly, without additional information, the problem is ill-posed.
 
-Without prior information the blind deconvolution is clearly ill-posed.
-In this note, we consider a special case of the problem.
-We aim at estimating a signal $x\in\RL$ from $y\in\RN, \thinspace N\gg L$.
-The acquired data, the measurement $y$, is composed of many repetitions of $x$, at different positions, and i.i.d.\ normal noise $\varepsilon $with mean zero and variance $\sigma^2$.
-Formally, our model read
+In this paper, we consider a particular case, in which one signal is of finite support, while the other is a binary sparse signal. Let us define the (zero-padded) signal 
+$$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]\in\RN,\quad N\gg L,$$
+and a binary signal $s\in\{0,1\}^N$. Then, our goal is to estimate $x$ from \begin{equation} \label{eq:blind_deconvolution}
+y = \xz \ast s + \varepsilon,
+\end{equation}
+where $\varepsilon$ is an i.i.d.\ normal noise $\varepsilon$ with mean zero and variance $\sigma^2$.
+As can be seen, the measurement $y\in\RN$ is composed of repetitions of an underlying signal $x\in\RL$, located at different positions. So, we can also write the model as  
 \begin{equation}
@@
 \end{equation}
-where $\xz\in\RN$ is a zero-padded version of $x\in\RL$ and 
-defined as $$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}],$$ and
- $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$.
+where the $n_i$'s are the non-zero values of $s$.
 
-Note that both $x$ and the translations, or positions, $n_i$ are unknown. Let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise. 
-Then, 
-\begin{equation}
-y = \xz \ast s + \varepsilon.
-\end{equation}
-The goal is then to estimate $x$ from $y$, while $s$ is unknown as well.
-The support signal $s$ is the latent or hidden variable of the problem.
-This is quite common in blind deconvolution problem.
-For instance, in image deblurring, the both the blurring kernel and the high-resolution image are unknown, but the main goal is merely to sharpen the image.
+While most works on blind deconvolution tries to estimate both unknown signals (see Section~\ref{sec:blind_deconvolution}), in most cases, the goal is merely to estimate one of the signals.
+For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the main goal is only to sharpen the image.
+In~\eqref{eq:blind_deconvolution}, the signal $s$ is referred to as the latent or hidden variable of the problem.
+Our goal is to estimate  $x$ and we focus  on the low signal--to--noise ratio ($\SNR$) regime.
+As will be demonstrated, in this case, estimating $s$ is impossible, even if $\xz$ is known.
+However, we show, maybe surprisingly, that one can estimate $x$ accurately in some cases.
+We support this statement by theoretical analysis and numerical  experiments.
 
-Recent papers on blind deconvolution and deconvolution.
-
-For small values of $\sigma$,  the problem is easy.
-In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding).
-Once several copies of  signal were detected and cropped from $y$, then one can  improve the SNR by averaging.
-We are interest in the more challenging regime of high noise level, in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances.
+Figure~\ref{fig:example} shows examples of the problem in different noise levels.
+In the example, the signal $x$ appears twice in $y$ so that $\| s \|^2 = 2$.
+The first row demonstrates a high $\SNR$ regime with $\sigma = 0.1$.
+As can be seen, in this regime  the problem is rather easy.
+In this case, one can easily the support of $s$ (namely, the repetition of $x$ in $y$) by simple detection algorithms.
+This is demonstrated by the correlation function between $\xz$ and $y$ that exhibits two unmistakable peaks in the support of $x$.
+Once several copies of the signal were detected and cropped from $y$, then one can  improve the $\SNR$ by averaging.
+We are interest in the more challenging regime of high noise level, as exemplified in the bottom row ($\sigma  = 3$)
+in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances.
 In this case, one need to use the prior information that the signal appears many times across the measurement.
 
-To perform this blind deconvolution, we use the invariant approach proposed for multireference alignment in a previous paper.
-Let us  first introduce  notation.
-We crop the measurement $y\in\RN$ into a series of analysis windows:
+\begin{figure*}
+	\begin{center}
+	\includegraphics[scale = .5]{example}
+	\end{center}
+\caption{The left column presents the clean data and the measurement in different noise levels.
+In this example, a rectangular signal of length $L=21$ appears twice in a measurement of length $N=336$ with different noise levels.
+Note to the different scale of the y-axis.
+The right column presents the correlation between the rectangular signal and the measurement for the associated problems.
+}
+\label{fig:example}
+\end{figure*}
+
+Our approach for this blind deconvolution problem is based on  tools that were developed for the multireference alignment (MRA) problem.
+MRA is the problem of estimating a signal from its circularly-shifted noisy measurements~\cite{bandeira2014multireference,bendory2017bispectrum}
+ In Section~\ref{sec:mra}, we survey recent works in this field.
+We use a recent suggestion to estimate the signal from feature that are invariant under cyclic-translation~\cite{bendory2017bispectrum}.
+ In essence, our method is based on \emph{approximate reduction} of the blind deconvolution problem into the MRA model.
+This is done be splitting $y$ into shorter windows and treat them as the MRA measurements.
+If each window contains exactly  one signal, then the problem reduces exactly the MRA problem.
+However, this is not the case.
+Some windows contain only noise, while others contain both noise and parts of a signal.
+ We analyze the estimation rate of this method and its deviation from the MRA model.
+
+ A motivation for this work arises from the cryo--electron microscopy (EM) problem.
+Cryo--EM received a great deal of attention in structural biology in recent years as it allows visualizing molecules that were not stained in any way, showing them in their native environment.
+In Section~\ref{sec:cryoEM} we draw the connections between  blind deconvolution and the cryo--EM problem.
+
+ The outline of this paper is as follows. In Section~\ref{sec:literature} we introduce background  on blind deconvolution (Section~\ref{sec:blind_deconvolution}) and MRA (Section~\ref{sec:mra}).  
+ In Section~\ref{sec:cryoEM} we discuss the connection with the  cryo--EM problem.
+In Section~\ref{sec:algorithm} we introduce the algorithm and analyze it in Section~\ref{sec:analysis}.
+Section~\ref{sec:experiments} is devoted for numerical experiments.
+Section~\ref{sec:conclusion} concludes the manuscript.
+
+\section{background} \label{sec:literature}
+
+In this section, we introduce the two main ingredients of this work, blind deconvolution and MRA. Then, we draw connections  with the cryo--EM problem.
+
+\subsection{Blind deconvolution} \label{sec:blind_deconvolution}
+
+Blind deconvolution is the problem of recovering a signal from its convolution with an unknown kernel $h$. That is, we aim to recover  $x$ from
 \begin{equation}
-y_i = y[(i-1)W + 1 : iW ]\in\mathbb{R}^W, \quad i=1,\ldots,N/W, 
+y = x\ast h,
 \end{equation}
-To ease notation, we assume that  $W$ divides $N$  so that there are exactly $N/W$ windows.
-We also assume that $\vert n_i - n_j\vert >W$ so that each window contains no more than one signal (in general, we can introduce overlapping windows.
-The code enables it, but it does not seem to improve performance.).
-For each one of the windows, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum.
-We then hope that averaging over these features will produce a reliable estimation of the invariant features of the signal itself.
-We recall that given accurate estimators of those features, we can estimate the signal itself reliably. Therefore, the question boils down to the accuracy of these feature estimations.
+where both $x$ and $h$ are unknown. In the Fourier domain, it takes the form of 
+\begin{equation}
+Fy = Fx \odot Fh,
+\end{equation}
+where $Fz$ stands for the Fourier transform of $z$ and $\odot$ for entry-wise product.
+Clearly, without prior information of the signal, it is impossible to estimate the signal.
+For instance, even if we assume that the $\DFT$ of both signals are non-vanishing, then $Fy$ remains unchanged if we replace $(Fx)[k],(Fh)[k]$ by $a(Fx)[k],\frac{1}{a}(Fh)[k]$ for any $a\in\CN\backslash\{0\}$ and any $k$.
 
-\section{Literature survey} \label{sec:literature}
+The blind deconvolution  has been analyzed recently with a various convex and non-convex algorithms.
+These works assume that the signal lies in a known  subspace spanned by vectors with random entries~\cite{ahmed2014blind,li2016rapid,ling2017blind}.
+A somewhat more related line of works assume sparsity in a random linear subspaces~\cite{lee2017blind,ling2015self,chi2016guaranteed}.
+The papers 
+\cite{choudhary2014sparse,li2016identifiability,kech2017optimal,li2015unified} deals with the fundamental question of identifiability of the problems, but none of these paper consider our setup, namely, when the sparse signal is in the canonical basis.
 
-\section{Connection with the cryo--EM problem} \label{sec:cryoEM}
-particle picking
+Our problem is very different from all previous works in at least two ways. First, 
+while we do assume that one of the signals is sparse,  our goal is to estimate the other signal.
+We do not claim that we can estimate the sparse signal.
+Second, we are mainly care of accurate estimation of $x$ in the low $\SNR$ regime.
+In this regime, it seems that estimating the sparse signal $s$ is impossible.
+This is contrast to previous works that focused on the high $\SNR$ regime.
+
+We briefly mention that the deconvolution problem, namely, when the kernel is assumed to be known, has been analyzed throughly in recent years under sparsity constraints~\cite{bendory2016robust,bendory2017robust,bendory2016stable,boyer2017adapting,bernstein2017deconvolution,de2012exact,azais2015spike,duval2015exact,duval2015sparse}.
+Nevertheless, the problem under consideration is essentially different  from two reasons.
+First, of course, we consider the blind setting when the kernel is unknown.
+Second, these works considered the recovery of sparse signal, with Gaussian-like kernel.
+In our problem, the convolution itself kernel is sparse, while we aim to recover a general signal.
+.
+
+\subsection{Multireference alignment} \label{sec:mra}
+
+Our approach for blind deconvolution is based on reducing the problem, approximately, to an MRA problem.
+In MRA, we aim at estimating a signal $x\in\RL$ from its circularly shifted noisy measurements
+\begin{equation} \label{eq:mra}
+y_j = R_{r_j}x + \varepsilon_j, \quad j = 1,\ldots,N,
+\end{equation}
+where $R_{r}$ translates a signal by $r$ locations, namely, $(R_rx)[i] = x[(i-r)\mod L]$, and $\varepsilon$ is an i.i.d.\ normal noise with mean zero and variance $\sigma^2$.
+This problem finds applications in radar, image processing and structural biology~\cite{zwart2003fast,foroosh2002extension,diamond1992multiple}.
+The algorithmic and statistical characterizations of this problem have been analyzed thoroughly in the last couple of years, see~\cite{bendory2017bispectrum,bandeira2014multireference,bandeira2017optimal,perry2017sample,boumal2017heterogeneous,abbe2017multireference,abbe2017sample}.
+
+In this work, we exploit the algorithmic framework proposed in~\cite{bendory2017bispectrum}.
+In order to estimate the signal, this paper suggests to use features of the signal that are invariant under cyclic translation.
+Apparently, three moments are required.
+The first is mean of the signal, denoted by $\mu_x$, or, equivalently, it DC component $(Fx)[0]$.
+The second feature is the power spectrum of the signal $P_x[k] = \vert (Fx)[k]\vert^2$ for $k=0,1,\ldots L-1$.
+Since in general one cannot estimate  a signal from its power spectrum~\cite{bendory2017fourier}, one needs a third order feature.
+This third order feature, called bispectrum, is defined as~\cite{tukey1953}
+\begin{equation}
+B_x[k_1,k_2] = (Fx)[k_1]\overline{(Fx)[k_2]}(Fx)[k_2-k_1].
+\end{equation}  
+These features can be estimated directly from the measured data by
+\begin{align}
+\frac{1}{N}\sum_{i=1}^N\mu_{y_j}  &\,\to \, \mu_x, \\
+\frac{1}{N}\sum_{i=1}^NP_{y_j}  &\,\to \, P_x + L\sigma^2, \\
+\frac{1}{N}\sum_{i=1}^NB_{y_j}  &\,\to \, B_x + \mu_x\sigma^2L^2A, 
+\end{align} 
+where $A$ is a known deterministic matrix.
+Therefore, by proper debiasing, one can get a reliable estimating of these features.
+For large enough $\sigma$, the variance of the estimators  is dominated by the bispectrum and thus goes as $\sigma^6/N$.
+This estimation rate is optimal under the assumption that distribution of translations is uniform~\cite{bandeira2017optimal}.
+If the distribution is non-uniform, then one can do better using only the first two moments, see~\cite{abbe2017multireference}.
+ Given enough measurements, one can obtain reliable estimation of the features, and then to estimate the underlying signal, up to cyclic translation, using a variety of algorithms~\cite{bendory2017bispectrum}.
+In this work, we use a simple non-convex least-squares estimator....
+\TODO{Need to see what do we actually solve...}
+
+\subsection{Connections with the cryo--EM problem} \label{sec:cryoEM}
+
+This work is partially motivated by the imaging
+technique called single particle Cryo--EM, enabling the visualization of molecules at near atomic resolution~\cite{bartesaghi20152,sirohi20163}.
+Cryo--EM gained a lot of popularity in recent years in the structural biology community.
+As an evidence, Dubochet, Frank and Henderson were awarded the
+the Nobel prize for their contribution in the development of this technique~\cite{nobel}.
+
+In cryo--EM, many samples of a molecule are frozen in a thin sheet of ice. 
+The microscope transmits electrons that pass through the ice and are recorded by an array of detectors and we acquire  several images, called \emph{micrographs}.
+Each micrograph  contains many two-dimensional (2D) tomographic projections of the samples.
+ The  cryo--EM problem is then to estimate the molecules from several micrographs. This process is illustrated by in Figures~\ref{fig:cryo-EM} and~\ref{fig:cryo-EM-problem}.
+
+From signal processing point--of--view, the cryo--EM problem arises two main challenges compared to more traditional tomographic methods, like computerized tomography.
+First, the orientation of each sample is unknown since the samples are rapidly frozen in the ice sheet.
+The experimentalist does not have control over these orientations.
+Second, the $\SNR$ in each projection is very low since the electron dosage must be kept low in oder to limit  radiation damage to the molecules.
+In real cryo--EM data there are some additional challenges, like the contrast transfer function of the microscope that corrupts the acquired image.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[scale = .4]{cryoem-eps-converted-to}
+	\end{center}
+	\caption{A schematic draw of the micrograph generation. Courtesy of ?}
+	\label{fig:cryo-EM}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[scale = .35]{cryoem-problem-eps-converted-to}		
+	\end{center}
+	\caption{The cryo--EM problem: estimating a molecule from the micrograph. Courtesy of ?}
+	\label{fig:cryo-EM-problem}
+\end{figure}
+
+The first stage of a cryo--EM reconstruction algorithm is the so called \emph{particle picking} [ref].
+In this stage, the projections are detected in the micrographs, and then cropped as demonstrated by the red rectangulars in Figure~\ref{fig:cryo-EM}.
+Then, ideally, one get a set of measurements of the form 
+\begin{equation} \label{eq:cryo-em}
+y_j = \mathcal{P}( g_j\circ x) + \varepsilon_j,\quad j=1,\ldots,N, 
+\end{equation}
+where $x$ is the three-dimensional (3D) molecule to be estimated,  $g_j\in SO(3)$ are unknown 3D rotations that act on the molecule and $\mathcal{P}$ is a linear tomographic projection.
+This model has been analyzed theoretically from different point--of-views~\cite{bandeira2015non,hadani2011representation} [more ref].
+The MRA model~\ref{eq:mra} can be interpreted as a simplification of the cryo--EM problem, where the unknown cyclic-shifts correspond to the unknown rotations (but there is no analog for the projection operation).
+
+In practice, particle picking algorithms are far from being optimal, mainly because the high noise level prevents reliable detection. 
+ For instance, the projections in the cropped images are not centered, and therefore an unknown 2D translation should be added to the model~\eqref{eq:cryo-em}.
+ In addition, many samples in the micrograph are non detected or ignored.
+
+ Our model can be seen as a highly simplified cryo--EM model, where $y$ corresponds to the micrograph and the signal repeated signal $x$ to a  ``one-dimensional molecule" (the tomographic projection $\mathcal{P}$ does not appear in the model).
+We are interest in the question whether we can estimate the signal $x$, even if the $\SNR$ is so low that we cannot detect the locations of $x$ in $y$.
+In the perspective of the cryo--EM problem.
+the success to estimate the signal in the very low SNR regime may indicate that the molecule can be estimated directly from the cryo--EM micrographs, even if the SNR is so low that particle picking algorithm work poorly.
+
+  %In addition, most particle picking algorithms throw away many particles since they fail to detect them.
+Hence, a necessary condition for the success of such algorithm is that the noise level would low enough so that detection would be possible.
 
@@
 
-Before moving ahead to the feature estimators, we need to estimate the norm of the signal.
-This is necessary since many analysis windows do not contain information on the signal, but pure noise.
-We will use the norm to scale the the signal's estimator.
-This can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$. 
+The algorithm is inspired by invariant features approach proposed in~\cite{bendory2017bispectrum}.
+Let $L<W\in\mathbb{Z}$ ans assume, for simplicity, that $W$ divides $N$.
+The algorithm starts with splitting the measurement $y\in\RN$ into a series of analysis windows $y_i\in\mathbb{R}^W,\,i=1,\ldots,N/W$, where
+\begin{equation} \label{eq:analysis_window}
+y_i[n] = y[(i-1)W + n] , \quad n=1,\ldots,W. 
+\end{equation}
+By assumption, there are exactly $N/W$ windows.
+Of course, one can use overlapping windows, however, our numerical experiments indicate it does not improve the numerical behavior.
+Then, for each window, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum and average over all windows.
+Finally, once we estimated these features, we look for a signal $\tilde{x}\in\mathbb{R}^W$ that is consistent with the data.
+
+Note that the signal is not scaled properly since, in contrast to the MRA model of~\cite{bendory2017bispectrum}, many windows contain no information on the signal, but pure noise.
+Therefore, we estimate the norm of the signal separately and use it to rescale the estimation.
+The norm estimation can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$. 
 Then,
@@
 And therefore, 
-\begin{equation}
+\begin{equation} \label{eq:norm_estimation}
 \|x\|_2^2 \approxeq \frac{\| y\|_2^2 - N\sigma^2}{K}. 
 \end{equation}
+The estimation error for different values of $\sigma$ is depicted in Figure~\ref{fig:norn_error}.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[scale = .5]{NormError}		
+	\end{center}
+	\caption{The normalized error for norm estimation over 200 experiments per values. Will need to do that again, but it is sufficient for now.}
+	\label{fig:norn_error}
+\end{figure}
+
+The algorithm is summarized in Algorithm~\ref{alg:1}.
+
+\begin{algorithm}[h]
+		\textbf{Input:} Moments $\mu$ and $M$; power spectrum $P_x$. \\ 
+		\textbf{Output:} A signal $\tilde x\in\mathbb{R}^W$  \\ 
+		\begin{enumerate}
+			\item Split $y$ into a set of $N/W$ analysis windows $y_i\in\mathbb{R}^W$ according to~\eqref{eq:analysis_window}
+			\item  For each analysis window, compute the mean $\mu_i$, power spectrum $P_i$ and bispectrum $B_i$ according to ?
+			\item  Average over the feature according to ?
+			\item  Estimate the signal $\tilde{x}\in\mathbb{R}^W$ by~?
+			\item  Compute the estimated norm $x_{\textrm{norm}}$  by~\eqref{eq:norm_estimation}
+			\item  Rescale the signal $\tilde x \gets \frac{\tilde{x}\cdot x_{\textrm{norm}}}{\|\tilde{x}\|_2} $    
+		\end{enumerate}
+	\caption{Blind devolution by features that are invariant to cyclic-translations} 	\label{alg:1}
+\end{algorithm}
 
@@
 
-Next, we analyze the feature estimation in the asymptotic regime of $N,\sigma,K\to\infty$ and fixed $L,W$.
-We introduce the ``sparsity factor" defined as $S = \frac{N}{WK}<\infty$, $WK$ is a measure for the ``active" windows.
-We also define  another zero padded signal $x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W$.
+For the sake of analyzing Algoritmh~\ref{alg:1}, we make the following assumptions.
+We consider the regime in which $N,\sigma,K\to\infty$ and  $L,W$ are fixed.
+We introduce to rations.
+The first is a ``sparsity factor" defined as $S = \frac{N}{WK}$, $WK$ is a measure for the ``active" windows and $1<S<\infty$.
+The second is $P = W/L>1$, measuring the ``padding factor"; the ratio between the lengths of the analysis window and the signal.
+We assume that positions $n_i$ are well-separated so that $\vert n_i - n_j\vert >2W$.
+The factor 2 is merely to ease the analysis is not really required by the algorithm.
+We also assume that each $n_i$ is uniformly distributed within the window.
 
-We want to estimate the features of this signal, and focus on the bispectrum for the sake of simplicity (the estimation of the power spectrum and mean obeys the same methodology). 
-In order to estimate the bispectrum we average over the bispectra of the windows, namely, (for the power spectrum, we need to do unbiasing.
-In addition, we can replace the mean by more robust estimator, like the median.)
+Let us define  the zero padded signal $$x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W.$$ 
+We want to estimate the features of this signal from the features the $y_i$'s.
+We analyze the estimation error of the bispectrum, and mention that the same methodology and conclusions hold for the power spectrum and mean.
+
+In order to estimate the bispectrum of the signal, we average over the bispectra of the analysis windows, namely,
 \begin{eqnarray}
@@
 \end{eqnarray}
-We split the sum into three groups of the windows:
+For the power spectrum, we need  to be somewhat careful with the bias.
+We will assume here that the mean of the signal is zero.
+Since the mean can be easily estimated from the data, it can be subtracted from each window before the averaging.
+ In addition, as discussed in~\cite{bendory2017bispectrum}, we can replace the mean by more robust estimator, like the median.
+
+We first observe that the analysis windows can be split into three groups and written as:
 \begin{eqnarray}
@@
 
-We first observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix).
-More precisely, the variance of the noise goes to zero at rate  $\order{\frac{W}{N}\left(1-\frac{1}{S}\right)\sigma^6}$.
-In addition, under the assumption that $n_i$ (if appear) are distributed uniformly in the window (we need to come up with precise statistical model; but it would be rather easy), there are (asymptotically) $K(1-L/W)$ windows with complete signals.
-Therefore,
-$B_\textrm{signal}\to \frac{KW(1-L/W)}{N}B_x$ at rate $\order{\frac{\sigma^6}{K(1-L/W)}}$.
-(Here we need to be a bit careful with the mean of the signal, or to assume it is zero.) Note that the scaling would be corrected at the last stage of the algorithm, by rescaling according to the estimated  norm.
+We analyze each group separately.
+First, we observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix).
+Since this a triple product, and we have, at least, $N/W-2K =N/W(1-2/S) $ such windows, the variance of $B_\textrm{noise}$ reduces to zero at rate  $\order{\frac{W}{N}\left(1-\frac{2}{S}\right)\sigma^6}$.
+This imply that for large $S$, the estimation rate of this factor reduces since we ``inject" pure noise to the estimation, with no relevant information on the signal.
 
-The more interesting term is the ``clutter" --- the cropped signals. Since each such signal appears in two windows,
-we have $2KL/W$ clutter segments. Of course, the noise in this segments goes to zero
-at rate $\order{\frac{W\sigma^6}{2KL}}$.
-However, we have an additional error term arises from  the cropped signals.
-To analyze the effect of this term, let us assume that $N/\sigma^6$ is great enough so that $B_\textrm{noise}\to 0$.
+The second group contains windows with a full signal.
+Indeed, the signal may appear anywhere, but since we work with features that are invariant to translation, that exact position is irrelevant as long as we have the full information of the signal.
+Since we assumed that the positions  $n_i$ are distributed uniformly in the window, there are (asymptotically) $K(1-L/W) = K(1-1/P)$ windows in this group.
+Therefore, $B_\textrm{signal}$ converges to a scaled version of $B_x$  \ at rate $\order{\frac{\sigma^6}{K(1-P)}}$.
+The scaling will be corrected in the last stage of the algorithm.
+This implies that the larger $P$, the faster the estimation rate of this group.
+This makes a lot of sense since it means that will find more windows with full signal and less cropped signals.
+
+Finally, we analyze the third group, the  ``clutter" --- the cropped signals. Since each such signal appears in two windows,
+we have $2KL/W = 2K/P$ clutter segments. Of course, the noise in this segments goes to zero
+at rate $\order{\frac{P\sigma^6}{2K}}$. However, we have an additional error term arises from  the cropped signals. This term does not reduce to zero, but can be bounded. 
+ To analyze the effect of this term, let us assume that $N/\sigma^6$ is great enough so that $B_\textrm{noise}\to 0$ and also $\left\|B_{y_i}\right\|_{\textrm{F}} \approxeq \left\|B_x\right\|_{\textrm{F}}$.
 Then,
@@
 \\ \leq & 
-\frac{W}{N}\frac{2KL}{W}\left\|B_x\right\|_{\textrm{F}} = \frac{2L}{SW}
+\frac{W}{N}\frac{2KL}{W}\left\|B_x\right\|_{\textrm{F}} = \frac{2}{SP}
 \|B_x\|_{\textrm{F}}.
@@
 \end{equation}
-Therefore, for large sparsity term $S$ or large $W/L$, we get an accurate estimation of a scaled version of the signal's bispectrum.
+Therefore, for large sparsity term $S$ or large $P$, we get an accurate estimation of a scaled version of the signal's bispectrum.
 
-Few insights from the analysis: (need to check numerically)
+Few insights from the analysis: (need to verified numerically)
 \begin{itemize}
 	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
-	\item Larger $W/L$ reduces the clutter error, however, increases the variance of the noise  of $B_\textrm{noise}$.
-	\item We must keep $W/L$ large enough to see enough full signals.    
+	\item Larger $P$ reduces the clutter error, however, increases the variance of the noise  where the signal appears.
+	\item We must keep $P$ large enough to see enough full signals.    
 \end{itemize}
+
+\section{Numerical experiments} \label{sec:experiments}
 

### 2017-11-14 XP_norm_estimation.m

@@ -1,0 +1,57 @@
+clear; close all; clc;
+
+%% Defining the problem
+
+L = 11; % length of signal
+window_size = 4*L;
+Nfactor = 6; % Sparsity factor, should be ~6
+overlapping_factor = 1; % windows are overlapped by window_size/overlapping_factor
+
+Nfactor_vector = 6; % Sparsity factor, should be ~6
+k_vector = logspace(2,6,20);  % # of signal's repetitions (maximal number)
+num_iter = 100;
+sigma_vec = [0.5 , 1, 2];  % noise level2
+
+Err_normX = zeros(length(k_vector),num_iter,3);
+
+
+
+for s = 1:length(sigma_vec)
+    
+    sigma = sigma_vec(s)
+    
+    for i = 1:length(k_vector)
+        k = k_vector(i)
+        N = window_size*k*Nfactor; % # of measurements
+        
+        for j = 1:num_iter
+            
+            %% Generating data
+            %tic
+            x = randn(L,1);
+            [y,yc, ind] = gen_data(x,N,k,sigma,window_size);
+            snr = norm(yc)^2/norm(y-yc)^2; % The problem's SNR
+            k_eff = length(ind); % The actual nunber of signal's repetitions
+            
+            %estimating the signal's norm from the data
+            normX = sqrt((norm(y)^2 - sigma^2*N)/k_eff);
+            Err_normX (i,j,s) = abs(norm(x) - normX)/norm(x);
+            %fprintf('Error of norm''s estimation = %.4f  \n',Err_normX);
+            
+        end
+    end
+    save('Err_normX','Err_normX');
+end
+
+    %%
+    ln = 1.5; 
+    figure; hold on;
+    loglog(k_vector,mean(squeeze(Err_normX(:,:,1)),2),'linewidth',ln)
+    loglog(k_vector,mean(squeeze(Err_normX(:,:,2)),2),'linewidth',ln)
+    loglog(k_vector,mean(squeeze(Err_normX(:,:,3)),2),'linewidth',ln)
+    legend('\sigma=0.1','\sigma=1','\sigma=3');
+    ylabel('error'); xlabel('K');
+    set(gca, 'XScale', 'log');
+    set(gca, 'YScale', 'log');
+    axis tight
+    pdf_print_code(gcf,'NormError', 11)

### 2017-11-14 example_problem.m

@@ -10,10 +10,11 @@ N = window_size*k*Nfactor; % # of measurements
 overlapping_factor = 1; % windows are overlapped by window_size/overlapping_factor
 %% Generating data
 tic
-x = randn(L,1); 
+%x = randn(L,1); 
+x = ones(L,1);
 [y,yc, ind] = gen_data(x,N,k,0,window_size);
 
-sigma_vec = [0.1 , 0.7, 2.5];  % noise level2
+sigma_vec = [0.1 , 0.7, 3];  % noise level2
 
 figure; 
 
@@ -51,4 +52,4 @@ axis tight
 
 end
 
-pdf_print_code(gcf, 'example', 11)
+pdf_print_code(gcf, 'example.pdf', 11)

### 2017-11-14 TEX/draft2.tex
Section 3 has been updated

@@
 These features can be estimated directly from the measured data by
-\begin{align}
-\frac{1}{N}\sum_{i=1}^N\mu_{y_j}  &\,\to \, \mu_x, \\
+\begin{align} \label{eq:moment_estimation}
+\frac{1}{N}\sum_{i=1}^N\mu_{y_j}  &\,\to \, \mu_x, \nonumber\\
 \frac{1}{N}\sum_{i=1}^NP_{y_j}  &\,\to \, P_x + L\sigma^2, \\
-\frac{1}{N}\sum_{i=1}^NB_{y_j}  &\,\to \, B_x + \mu_x\sigma^2L^2A, 
+\frac{1}{N}\sum_{i=1}^NB_{y_j}  &\,\to \, B_x + \mu_x\sigma^2L^2A,  \nonumber
 \end{align} 
@@
 This work is partially motivated by the imaging
-technique called single particle Cryo--EM, enabling the visualization of molecules at near atomic resolution~\cite{bartesaghi20152,sirohi20163}.
+technique called single particle cryo--EM, enabling the visualization of molecules at near atomic resolution~\cite{bartesaghi20152,sirohi20163}.
 Cryo--EM gained a lot of popularity in recent years in the structural biology community.
-As an evidence, Dubochet, Frank and Henderson were awarded the
+As a result, Dubochet, Frank and Henderson were recently awarded the
 the Nobel prize for their contribution in the development of this technique~\cite{nobel}.
@@
 In cryo--EM, many samples of a molecule are frozen in a thin sheet of ice. 
-The microscope transmits electrons that pass through the ice and are recorded by an array of detectors and we acquire  several images, called \emph{micrographs}.
-Each micrograph  contains many two-dimensional (2D) tomographic projections of the samples.
- The  cryo--EM problem is then to estimate the molecules from several micrographs. This process is illustrated by in Figures~\ref{fig:cryo-EM} and~\ref{fig:cryo-EM-problem}.
+An electron beam then passes through the ice and the samples  and recorded by an array of detectors. Cryo--EM contains several such images, which are
+called \emph{micrographs}. Each micrograph  contains many two-dimensional (2D) tomographic projections of the samples. 
+ The  cryo--EM problem is then to estimate the molecules from the micrographs. This process is illustrated by in Figures~\ref{fig:cryo-EM} and~\ref{fig:cryo-EM-problem}.
 
-From signal processing point--of--view, the cryo--EM problem arises two main challenges compared to more traditional tomographic methods, like computerized tomography.
-First, the orientation of each sample is unknown since the samples are rapidly frozen in the ice sheet.
+Compared to more traditional tomographic methods, like computerized tomography (CT), the cryo--EM problem arises two main challenges.
+First, the 3D orientation of each sample is unknown since the samples are rapidly frozen in the ice sheet.
 The experimentalist does not have control over these orientations.
-Second, the $\SNR$ in each projection is very low since the electron dosage must be kept low in oder to limit  radiation damage to the molecules.
-In real cryo--EM data there are some additional challenges, like the contrast transfer function of the microscope that corrupts the acquired image.
+Second, the $\SNR$ in each projection is very low since the electron dosage must be restricted to limit  radiation damage to the molecules.
+In real cryo--EM data sets, there are some additional challenges, like the contrast transfer function of the microscope that corrupts the acquired image.
 
@@
 
-The first stage of a cryo--EM reconstruction algorithm is the so called \emph{particle picking} [ref].
-In this stage, the projections are detected in the micrographs, and then cropped as demonstrated by the red rectangulars in Figure~\ref{fig:cryo-EM}.
-Then, ideally, one get a set of measurements of the form 
+The first stage of a cryo--EM reconstruction algorithm is the so called \emph{particle picking} stage.
+In this stage, the projections are detected in the micrographs, and then cropped to a series of 2D images.
+Many algorithms were proposed to this detection problem based on support vector machine classifiers, deep learning and template matching and more; see for instance \cite{frank1983automatic,scheres2015semi,arbelaez2011experimental,zhu2016deep}.
+ The most popular techniques are based on the latter, where the templates can manually or automatically selected.
+The underlying idea is that the cross-correlation  should be high in the presence of a signal in the template.
+However, this is not true anymore in the presence of high noise level, even if the signal itself is known, as demonstrated in Figure~\ref{fig:example}.
+An illuminating examples are given in~\cite{shatsky2009method,bandeira2015non}, where the famous picture of Albert Einstein is used to match pure noise and rotated images of the mathematician  Hermann Weyl.
+
+After the particle picking, ideally, one gets a set of measurements of the form 
 \begin{equation} \label{eq:cryo-em}
@@
 where $x$ is the three-dimensional (3D) molecule to be estimated,  $g_j\in SO(3)$ are unknown 3D rotations that act on the molecule and $\mathcal{P}$ is a linear tomographic projection.
-This model has been analyzed theoretically from different point--of-views~\cite{bandeira2015non,hadani2011representation} [more ref].
-The MRA model~\ref{eq:mra} can be interpreted as a simplification of the cryo--EM problem, where the unknown cyclic-shifts correspond to the unknown rotations (but there is no analog for the projection operation).
+This model has been analyzed theoretically from different point--of-views~\cite{bandeira2015non,hadani2011representation}.
+The MRA model~\eqref{eq:mra} can be interpreted as a simplification of the model~\eqref{eq:cryo-em}, where the unknown cyclic-shifts correspond to the unknown rotations (but there is no analog for the projection operation).
 
 In practice, particle picking algorithms are far from being optimal, mainly because the high noise level prevents reliable detection.
- For instance, the projections in the cropped images are not centered, and therefore an unknown 2D translation should be added to the model~\eqref{eq:cryo-em}.
+One result is that the cropped images are usually not centered,  and therefore an unknown 2D translation should be added to the model~\eqref{eq:cryo-em}.
 In addition, many samples in the micrograph are non detected or ignored.
+After the particle picking stage, the molecule is estimated from the 2D images, where the most popular algorithms are based on expectation--maximization (see for instance~\cite{scheres2012relion}).
+Other techniques, such as the common-lines\cite{van1987angular,singer2011three} method or auto-correlation analysis~\cite{kam1980reconstruction,levin20173d}, can be used for ab initio modeling.
 
- Our model can be seen as a highly simplified cryo--EM model, where $y$ corresponds to the micrograph and the signal repeated signal $x$ to a  ``one-dimensional molecule" (the tomographic projection $\mathcal{P}$ does not appear in the model).
-We are interest in the question whether we can estimate the signal $x$, even if the $\SNR$ is so low that we cannot detect the locations of $x$ in $y$.
+ Our model can be seen as a highly simplified cryo--EM model, where $y$ corresponds to the micrograph and the signal repeated $x$ to a  ``one-dimensional molecule" (the tomographic projection $\mathcal{P}$ does not appear in the model).
+We are interest in the question whether we can estimate the signal $x$, even if the $\SNR$ is so low that we cannot detect the locations of $x$, in $y$.
 In the perspective of the cryo--EM problem.
@@
 
-The algorithm is inspired by invariant features approach proposed in~\cite{bendory2017bispectrum}.
-Let $L<W\in\mathbb{Z}$ ans assume, for simplicity, that $W$ divides $N$.
-The algorithm starts with splitting the measurement $y\in\RN$ into a series of analysis windows $y_i\in\mathbb{R}^W,\,i=1,\ldots,N/W$, where
+The blind deconvolution algorithm is inspired by the recent MRA approach using translation invariant features proposed in~\cite{bendory2017bispectrum}.
+The algorithm requires setting a parameter $W\in\mathbb{N}$ obeying $W>L$  which is the length of the \emph{analysis window}.
+We assume henceforth, to ease notation, that $W$ divides $N$.
+The algorithm begins with splitting the measurement $y\in\RN$ into a series of analysis windows $y_i\in\mathbb{R}^W,\,i=1,\ldots,N/W$, where  
 \begin{equation} \label{eq:analysis_window}
@@
 By assumption, there are exactly $N/W$ windows.
-Of course, one can use overlapping windows, however, our numerical experiments indicate it does not improve the numerical behavior.
-Then, for each window, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum and average over all windows.
-Finally, once we estimated these features, we look for a signal $\tilde{x}\in\mathbb{R}^W$ that is consistent with the data.
+Of course, one can easily modify the algorithm using overlapping windows, however, our numerical experiments indicate it does not improve the numerical performance.
+For each window, we then compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum, and then  average them over all windows according to~\eqref{eq:moment_estimation}.
+Finally, once we estimated these features, we look for a signal $\tilde{x}\in\mathbb{R}^W$ that is consistent with the data by solving ??
 
-Note that the signal is not scaled properly since, in contrast to the MRA model of~\cite{bendory2017bispectrum}, many windows contain no information on the signal, but pure noise.
-Therefore, we estimate the norm of the signal separately and use it to rescale the estimation.
-The norm estimation can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$. 
+The scaling of the output of~? is incorrect, since the averaging in done over many windows containing pure noise with no information on the signal itself. 
+To rescale the estimated signal, we estimate the norm of the signal separately.
+The norm estimation can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$ if a separation of $\vert n_i - n_j\vert >L$ is satisfied. 
 Then,
 \begin{equation}
-\| y\|_2^2 =  \| x_K\|_2^2 + \|\varepsilon\|_2^2 + 2\varepsilon^Tx_K. 
+\| y\|_2^2 =  \| x_K\|_2^2 + \|\varepsilon\|_2^2 + 2\varepsilon^Tx_K, 
 \end{equation}  
-As $N\to\infty$, we can estimate 
+and therefore 
 \begin{equation}
@@
 \end{equation}   
-And therefore, 
+As $N\to\infty$,  we then obtain
 \begin{equation} \label{eq:norm_estimation}
-\|x\|_2^2 \approxeq \frac{\| y\|_2^2 - N\sigma^2}{K}. 
+\|x\|_2^2 \approx \frac{\| y\|_2^2 - N\sigma^2}{K}. 
 \end{equation}
@@
 	\end{center}
-	\caption{The normalized error for norm estimation over 200 experiments per values. Will need to do that again, but it is sufficient for now.}
+	\caption{The normalized error for norm estimation $\frac{\vert \|\hat{x}\|  - \|x\|\vert }{\|x\|}$, where $\|\hat{x}\|$ is the norm estimation.
+The error was averaged over 200 experiments for each value of $k$.}
 	\label{fig:norn_error}
@@
 
+The output of the algorithm is a signal of length $W$, that, ideally, contains $x$, shifted by some unknown shift, and padded by $W-L$ zeros. 
 The algorithm is summarized in Algorithm~\ref{alg:1}.
+\TODO{We should come up with a method to automatic aligning of the signal}.
 
 \begin{algorithm}[h]
-		\textbf{Input:} Moments $\mu$ and $M$; power spectrum $P_x$. \\ 
+		\textbf{Input:} The measurement $y\in\RN$ \\ 
 		\textbf{Output:} A signal $\tilde x\in\mathbb{R}^W$  \\ 
@@
 			\item Split $y$ into a set of $N/W$ analysis windows $y_i\in\mathbb{R}^W$ according to~\eqref{eq:analysis_window}
-			\item  For each analysis window, compute the mean $\mu_i$, power spectrum $P_i$ and bispectrum $B_i$ according to ?
-			\item  Average over the feature according to ?
+			\item  Compute the average mean, power spectrum and bispectrum according to~\eqref{eq:moment_estimation} 
 			\item  Estimate the signal $\tilde{x}\in\mathbb{R}^W$ by~?
@@
 			\item  Rescale the signal $\tilde x \gets \frac{\tilde{x}\cdot x_{\textrm{norm}}}{\|\tilde{x}\|_2} $   
+			\TODO{Need to find a good alignment method} 
 		\end{enumerate}
-	\caption{Blind devolution by features that are invariant to cyclic-translations} 	\label{alg:1}
+	\caption{Blind devolution by invariant features} 	\label{alg:1}
 \end{algorithm}

### 2017-11-14 TEX/draft2.tex
Added an automatic alignment + cropping stage to the algorithm

@@
 \newcommand{\CN}{\mathbb{C}^N}
+\newcommand{\RW}{\mathbb{R}^W}
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
@@
 For each window, we then compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum, and then  average them over all windows according to~\eqref{eq:moment_estimation}.
-Finally, once we estimated these features, we look for a signal $\tilde{x}\in\mathbb{R}^W$ that is consistent with the data by solving ??
+Finally, once we estimated these features, we look for a signal $\hat{x}\in\mathbb{R}^W$ that is consistent with the data by solving ??
 
-The scaling of the output of~? is incorrect, since the averaging in done over many windows containing pure noise with no information on the signal itself. 
+Recall that the current estimate $\hat{x}$ is a signal of length $W$, whereas the underlying signal of length $L$.
+Ideally, it is cyclic-shifted version of $x$, padded with $W-L$ zeros.
+ To crop the signal correctly, we simply search for the  segment of length $L$ with maximal energy.
+Formally, let  $T_\ell:\RW\to\RL$ be the operator that takes $L$ consecutive entries of the signal, starting at $\ell$.
+The signal is treated as periodic.
+Then, by letting
+\begin{equation}
+\ell_{\max} =  {\arg\max}_{\ell=0,\ldots,W-1} \|T_\ell\hat{x} \|_2,
+\end{equation}
+we map
+\begin{equation} \label{eq:align}
+\hat{x}\gets T_{\ell_{\max}}\hat{x}.
+\end{equation}
+
+The scaling of $\hat{x}$ is incorrect, since the averaging in done over many windows containing pure noise with no information on the signal itself. 
 To rescale the estimated signal, we estimate the norm of the signal separately.
@@
 			\item  Compute the average mean, power spectrum and bispectrum according to~\eqref{eq:moment_estimation} 
-			\item  Estimate the signal $\tilde{x}\in\mathbb{R}^W$ by~?
+			\item  Estimate the signal $\hat{x}\in\mathbb{R}^W$ by~?
+			\item  Map $\hat{x}\gets T_{\ell_{\max}}\hat{x}$ according to~\eqref{eq:align}
 			\item  Compute the estimated norm $x_{\textrm{norm}}$  by~\eqref{eq:norm_estimation}
 			\item  Rescale the signal $\tilde x \gets \frac{\tilde{x}\cdot x_{\textrm{norm}}}{\|\tilde{x}\|_2} $   
-			\TODO{Need to find a good alignment method} 
 		\end{enumerate}

### 2017-11-16 TEX/draft2.tex
Some updates in the code and the TEX

@@
 
+We use the definition of signal--to--noise ratio ($\SNR$) as
+\begin{equation}
+\SNR = \frac{\|y_c\|_2^2}{\|y_c-y\|_2^2},
+\end{equation}
+where $y_c$ is the measurement before adding the noise. The error is measured as 
+\begin{equation}
+\textrm{error}  = \frac{\|\hat{x}-x\|}{\|x\|}.
+\end{equation}
+
+A representative example is given in Figure ?
+
+An experiment for constant noise level $\sigma=1$ and varying $k$ appears in Figure~\ref{fig:varyingK}. The error stops decreasing at some level from obvious reasons.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.5]{errXP1.pdf}
+	\caption{\label{fig:varyingK}The recovery error as a function of $k$, the number of signal appearances (approximately!) for $\sigma=1$.
+We worked with i.i.d.\ signal of length $L=1$ (same signal for all experiments), the window size was chosen as $W=10L$ and the number of measurements was chosen as $N =6Wk $.
+In average, $1/\SNR\approx 30$.}
+\end{figure}
 \section{Conclusion} \label{sec:conclusion}
+Here we conclude the paper
 

### 2017-11-16 XP1.m

@@ -1,0 +1,116 @@
+clear; close all; clc;
+
+%% Defining the problem
+
+L = 21; % length of signal
+sigma = 1;  % noise level2
+W = 8*L; 
+Nfactor = 6; % Sparsity factor, should be ~6
+overlapping_factor = 1; % windows are overlapped by window_size/overlapping_factor
+x = ones(L,1); %randn(L,1); 
+k_length = 1;
+%k_vec = round(logspace(2,5,10));
+k_vec = 1e4;
+num_rep = 10;
+
+if isempty(gcp('nocreate'))
+            parpool(2, 'IdleTimeout', 240);
+end
+
+err = zeros(k_length,num_rep);
+snr = err; 
+time = err;
+err_auto = err;
+
+%% Generating data
+for i = 1:length(k_vec)
+k = k_vec(i);
+    for iter = 1: num_rep
+
+%tic
+
+N = W*k*Nfactor; % # of measurements
+[y,yc, ind] = gen_data(x,N,k,sigma,W);
+snr(i,iter) = norm(yc)^2/norm(y-yc)^2; % The problem's SNR
+k_eff = length(ind); % The actual nunber of signal's repetitions
+%fprintf('Measurement length  = %e \n',N);
+%fprintf('The measurement contains %.1e repetitions of the underlying signal (from %.1e)\n',k_eff,k);
+fprintf('SNR = %.4f \n',snr(i,iter));
+%fprintf('Generating data time = %.2f [sec] \n',toc);
+%estimating the signal's norm from the data
+normX = sqrt((norm(y)^2 - sigma^2*N)/k_eff);
+%Err_normX = abs(norm(x) - normX)/norm(x);
+%fprintf('Error of norm''s estimation = %.4f  \n',Err_normX);
+
+%sanity check: note that yc == cconv(x,s,N);
+%s = zeros(N,1); s(ind) = 1;
+%norm(yc - cconv(x,s,N))
+
+%% rearraging the matrix data
+
+tic
+if overlapping_factor == 1
+y_mat = reshape(y, W,N/W);
+else
+y_mat = gen_data_mtx(y,W,overlapping_factor);
+fprintf('Constructing data matrix time = %.2f [sec] \n',toc);     
+end
+assert(size(y_mat,1)==W && size(y_mat,2)==N/W*overlapping_factor, 'Something is wrong with the data dimensions');
+
+%% invariants
+
+tic
[…]

### 2017-11-16 XP1/plot_script.m

@@ -1,0 +1,18 @@
+clear; close; clc;
+
+load('errXP1');
+
+k_length = 10;
+k_vec = round(logspace(2,5,k_length));
+e = mean(err,2);
+ln = 1.5;
+
+figure; plot(k_vec,e,'linewidth',ln);
+%set(gca, 'YScale', 'log')
+set(gca, 'XScale', 'log')
+axis tight
+xlabel('K')
+ylabel('error')
+
+saveas(gcf,'errXP1')
+pdf_print_code(gcf, 'errXP1', 11)

### 2017-11-16 TEX/draft2.tex

@@
 Of course, one can easily modify the algorithm using overlapping windows, however, our numerical experiments indicate it does not improve the numerical performance.
-For each window, we then compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum, and then  average them over all windows according to~\eqref{eq:moment_estimation}.
+For each window, we then compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum, and then  average them over all windows according to~\eqref{eq:moment_estimation}
+Following~\eqref{eq:moment_estimation}, we estimate the features of the signal by average over the features of the analysis windows, namely,
+\begin{align} \label{eq:estimated_features_win}
+\hat{\mu}_{x} &= \frac{W}{N}\sum_{i=1}^{N/W}\mu_{y_i}, \\ \nonumber
+\hat{P}_{x} &= \frac{W}{N}\sum_{i=1}^{N/W}P_{y_i} - L\sigma^2, \\
+\hat{B}_{x} &= \frac{W}{N}\sum_{i=1}^{N/W}B_{y_i-\hat{\mu}_{x_W}}.  \nonumber
+\end{align}
+As discussed in~\cite{bendory2017bispectrum}, we can replace the mean by more robust estimator, like the median.
  Finally, once we estimated these features, we look for a signal $\hat{x}\in\mathbb{R}^W$ that is consistent with the data by solving ??
@@
 The algorithm is summarized in Algorithm~\ref{alg:1}.
-\TODO{We should come up with a method to automatic aligning of the signal}.
 
@@
 
-For the sake of analyzing Algoritmh~\ref{alg:1}, we make the following assumptions.
-We consider the regime in which $N,\sigma,K\to\infty$ and  $L,W$ are fixed.
-We introduce to rations.
-The first is a ``sparsity factor" defined as $S = \frac{N}{WK}$, $WK$ is a measure for the ``active" windows and $1<S<\infty$.
-The second is $P = W/L>1$, measuring the ``padding factor"; the ratio between the lengths of the analysis window and the signal.
+In this section, we analyze the performance of Algoritmh~\ref{alg:1}.
+Our analysis is based on the asymptotic regime in which  $N,\sigma,K\to\infty$ and  $L,W$ are fixed.
+Since we work in high noise regime, We focus on the converges rate of the noise terms.
+In addition, we analyze the error occurred due to the proposed technique independent of the noise.
  We assume that positions $n_i$ are well-separated so that $\vert n_i - n_j\vert >2W$.
@@
 
+Our framework is based on splitting the measurement into $N/W$ windows $y_i\in\RW$.
+Since in the high noise regime, we cannot detect the appearances of the signal in $y$, the devision is somewhat arbitrary.
+The windows $y_i,\,i=1,\ldots,N/W$ can be classified into three classes.
+The first class contains a signal in an unknown location and noise.
+These are ``good" windows since they are perfectly match the MRA model.
+The second class contains only noise -- no signal.
+As will be demonstrated, these windows cause only a scaling problem which is easily fixed by estimation the signal's norm separately~\eqref{eq:norm_estimation}.
+The third class of signals contains only part of a signal and the noise.
+These are the ``bad" windows, as they do not contain the entire information of the signal, but, also, do not obey the Gaussian statistics of the noise.
+These windows induce estimation error, independently of the noise.
+
+The performance of the algorithm relies on the factors.  The first is the ratio between the length of the analysis window and the signal, namely, 
+$$P := W/L>1.$$ Clearly, the larger this ratio is, the less windows are with the class of ``bad" windows; the windows with part of the signal.
+On the other hand, if we impose large $P$, we restrict ourselves to work with very sparse signals.
+The second factor is defined as $$S = \frac{N}{WK},$$ where $WK$ is a measure for the ``active" windows.
+We refer to $S$ as the  ``sparsity factor".
+Clearly,  $1<S<\infty$.
+The larger $S$ is, the more sparse the signal is.
+
 Let us define  the zero padded signal $$x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W.$$ 
-We want to estimate the features of this signal from the features the $y_i$'s.
-We analyze the estimation error of the bispectrum, and mention that the same methodology and conclusions hold for the power spectrum and mean.
+We want to estimate the features of this signal from the features of the $y_i$'s.
+In Algorithm~\ref{alg:1} there is another step of trimming this padded signal to a shorter signal of length $L$ that contains most of the information, but we currently ignore this stage.
 
-In order to estimate the bispectrum of the signal, we average over the bispectra of the analysis windows, namely,
-\begin{eqnarray}
-\hat{B}_{x_W} = \frac{W}{N}\sum_{i=1}^{N/W}B_{y_i}.
-\end{eqnarray}
-For the power spectrum, we need  to be somewhat careful with the bias.
-We will assume here that the mean of the signal is zero.
-Since the mean can be easily estimated from the data, it can be subtracted from each window before the averaging.
- In addition, as discussed in~\cite{bendory2017bispectrum}, we can replace the mean by more robust estimator, like the median.
+We next analyze the estimation error of the invariant features, estimated by~\eqref{eq:estimated_features_win}.  
+In the ideal case, when one has $n$ windows with signal and noise, them  the asymptotic  estimation rate of the mean, power spectrum and bispectrum is $\sigma^2/n,\,\sigma^4/n,\,\sigma^6/n$, respectively.
+We are interest in how this rate is changed in the model under consideration.
 
-We first observe that the analysis windows can be split into three groups and written as:
+For each feature, the sum in~\eqref{eq:estimated_features_win} can be split into three classed. For instance, the estimated bispectrum can be written as
 \begin{eqnarray}
@@
 \end{itemize}
+The same of course holds for the mean and the power spectrum.
 
-We analyze each group separately.
-First, we observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix).
-Since this a triple product, and we have, at least, $N/W-2K =N/W(1-2/S) $ such windows, the variance of $B_\textrm{noise}$ reduces to zero at rate  $\order{\frac{W}{N}\left(1-\frac{2}{S}\right)\sigma^6}$.
+We analyze each class separately.
+First, we observe that for the noise class, all features converges to zero, namely, $\hat{\mu}_\textrm{noise}\to 0$, $\hat{P}_\textrm{noise}\to 0$ and $\hat{B}_\textrm{noise}\to 0$.
+Since  we have, at least, $N/W-2K =N/W(1-2/S) $ such windows, and the converges is controlled by the bispectrum, the estimation rate is  $\order{\frac{W}{N}\left(1-\frac{2}{S}\right)\sigma^6}$.
 This imply that for large $S$, the estimation rate of this factor reduces since we ``inject" pure noise to the estimation, with no relevant information on the signal.
 
-The second group contains windows with a full signal.
-Indeed, the signal may appear anywhere, but since we work with features that are invariant to translation, that exact position is irrelevant as long as we have the full information of the signal.
-Since we assumed that the positions  $n_i$ are distributed uniformly in the window, there are (asymptotically) $K(1-L/W) = K(1-1/P)$ windows in this group.
-Therefore, $B_\textrm{signal}$ converges to a scaled version of $B_x$  \ at rate $\order{\frac{\sigma^6}{K(1-P)}}$.
-The scaling will be corrected in the last stage of the algorithm.
+The class group contains windows with a full signal.
+Indeed, the signal may appear anywhere, but since we work with features that are invariant to cyclic-translation, that exact position is irrelevant as long as we have the full information of the signal.
+Since we assumed that the positions  $n_i$ are distributed uniformly in the window, there are (asymptotically) $K(1-L/W) = K(1-1/P)$ windows in this class.
+Therefore, $B_\textrm{signal}$ converges to a scaled version of $B_x$  at rate $\order{\frac{\sigma^6}{K(1-1/P)}}$.
+The scaling will be corrected in the last stage of Algorithm~\ref{alg:1}.
 This implies that the larger $P$, the faster the estimation rate of this group.
@@
 
-Finally, we analyze the third group, the  ``clutter" --- the cropped signals. Since each such signal appears in two windows,
+Finally, we analyze the third class, the  ``clutter" --- the cropped signals. Since each such signal appears in two windows,
 we have $2KL/W = 2K/P$ clutter segments. Of course, the noise in this segments goes to zero
@@
 \begin{split}
-\left\| \hat{B}_{x_W} - B_\textrm{signal}\right\|_{\textrm{F}} \approxeq&  \left\|B_\textrm{clutter}\right\|_{\textrm{F}}
+\left\| \hat{B}_{x_W} - B_\textrm{signal}\right\|_{\textrm{F}} \approx&  \left\|B_\textrm{clutter}\right\|_{\textrm{F}}
 = \left\|\frac{W}{N}\sum_{i\in\textrm{clutter}}B_{y_i}\right\|_{\textrm{F}}
@@
 \end{equation}
-Therefore, for large sparsity term $S$ or large $P$, we get an accurate estimation of a scaled version of the signal's bispectrum.
+Therefore, for large sparsity term $S$ or large $P$, we get an accurate estimation of a scaled version of the signal's bispectrum. Similar analysis holds for the mean and power spectrum.
 
@@
 
-A representative example is given in Figure ?
+Two representative examples are for recovery in low $\SNR$ are given in Figure~\ref{fig:representative_example}.
+In these experiments, the signal appears $5\cdot10^6$ times in the noise measurement with noise level $\sigma=2.5$ and $\SNR\approx 1/180$.
+The figure also presents a segment from the  correlation between the underlying signal and the measurement.
+As can be seen, even if the signal was known, it is impossible to detect its appearances from the data.
+In other words, even in the end of the task, after we accurately estimated the signal, it is impossible to identify its locations.
+
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.26]{example_random_signal.pdf}
+	\includegraphics[scale=0.26]{example_rect_signal.pdf}	
+	\caption{\label{fig:representative_example} Two representative examples of accurate estimation of an i.i.d./ random signal (left) and a rectangular signal (right), both of length $L=21$, from noisy measurements with $\sigma=2.5$ and $\SNR\approx 1/180$.
+The signal appearances $K=5\cdot 10^6$ times in the measurements of length $N=6WK$ for $W=10L$.
+The upper figure show the estimated signal versus the original one.
+Below that, we plot a typical segment of the noisy data.
+The bottom figures present a segment of the correlation between the underlying signals and the data.}
+\end{figure*}
 
@@
 \end{figure}
+
 \section{Conclusion} \label{sec:conclusion}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{ieeetran}
 \bibliography{ref}

### 2018-03-08 TEX/draft1.tex
Updated tex files

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[english]{article}
 
@@
 \usepackage{url}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-%\numberwithin{equation}{section}
+\numberwithin{equation}{section}
 %\numberwithin{figure}{section}
@@
 \newtheorem*{lem*}{Lemma}
+
 \theoremstyle{remark}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+%\usepackage{slashbox}
 
-%\usepackage{babel}
+\usepackage{babel}
 \providecommand{\claimname}{Claim}
@@
 
+\newcommand{\reals}{\mathbb{R}}
 \newcommand{\RL}{\mathbb{R}^L}
-\newcommand{\RN}{\mathbb{R}^N}
 \newcommand{\CL}{\mathbb{C}^L}
+\newcommand{\RN}{\mathbb{R}^L}
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
@@
 \newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\E}[1]{\mathbb{E}\left\{{#1} \right\}}
-\newcommand{\order}[1]{\mathcal{O}\left({#1} \right)}
-\newcommand{\xz}{x_{\textrm{zp}}}
-\newcommand{\DFT}[1]{\operatorname{DFT}\!\left( {#1} \right)}
 \newcommand{\hx}{\hat{x}}
+
+\newcommand{\SNR}{\textsf{SNR} }
 
@@
 
-%\begin{frontmatter}
-
-\title{Small MRI is boring}
+\title{Estimation below the detection limit}
 
@@
 
-We consider the problem of estimating a signal $x\in\RL$ from one measurement $y\in\RN, \thinspace N\gg L,$ that contains many repetitions of this signal, at unknown locations, swallowed in noise.
+\begin{abstract}
+	Here comes the abstract
+\end{abstract}
 
-Formally, our model read
+\section{Introduction}
+
+In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown, random, locations in the data $y$.
+The data may also contain background information -- independent of the signals -- which is model as noise.
+For one-dimensional signals, the data can be thought of as a long time series and the signals as repetitive short events.
+For two-dimensional signals, the data is a big image that contains many smaller images.
+The problem is then to estimate the signals $x_1,\ldots x_K$ from $y$. This
+model appears, in different noise levels, in many applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+In Section~\ref{sec:model} we provide a precise mathematical formulation of the problem.
+
+If the noise level is negligible compared to the signal, the problem is easy.
+One can detect the signal occurrences in the data, and then estimate the signals using clustering and averaging.
+However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as discussed in Section~\ref{sec:model}.
+Nonetheless, in Section~\ref{sec:autocorrelation} we show that under a separation condition on the signals occurrences and that $K$ is not too large, it is possible to estimate the signals, in any \SNR level, up to any desired accuracy.
+This holds if each signals appears enough times in the data as will be explained next.
+
+This work is primely motivated by the challenging innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
+The acquired data in these technologies suffers from very high noise level.
+Figure~\ref{fig:example} provides an example for the problem for one signal (i.e., $K=1$).
+Figures~\ref{fig:data2D_clean},\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} shows excerpt of data in different noise levels, and~\ref{fig:signal2D_clean} is the underlying signal.
+Figure~\ref{fig:signal2D_LS} shows the estimation of the signal using our method when $\sigma=1$.
+In Section~\ref{sec:numerics}, after describing the model and method and detail, we provide the all details on this experiments and show more experiments for $K>1$.
+In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
+
+\begin{figure}[ht!]
+    \advance\leftskip-4cm
+   \advance\rightskip-4cm
+
+%	\centering
+
+	\begin{subfigure}{.5\textwidth}
+		\centering
+	\includegraphics[scale=0.5]{data2D_clean}
+\caption{Excerpt of clean data}
+\label{fig:data2D_clean}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+	\centering
+\includegraphics[scale=0.5]{data2D_noisy_02}
+\caption{Excerpt of noisy data with $\sigma=0.2$}
+\label{fig:data2D_noisy_02}
+	\end{subfigure}
+	\begin{subfigure}{.5\textwidth}
+	\centering
+\includegraphics[scale=0.5]{data2D_noisy_1}
+\caption{Excerpt of noisy data with $\sigma=1$}
+\label{fig:data2D_noisy_1}
+\end{subfigure}
+
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[scale=0.5]{signal2D_clean}
+	\caption{Clean signal}
+	\label{fig:signal2D_clean}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[scale=0.5]{signal2D_LS}
+	\caption{Recovered signal using LS}
+	\label{fig:signal2D_LS}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[scale=0.5]{signal2D_RRR}
+	\caption{This one will be replaced}
+	\label{fig:signal2D_RRR}
+\end{subfigure}
+
+\caption{Example}
+\label{fig:example}
+\end{figure}
+
+In Section~\ref{sec:autocorrelation}, we elaborate on our method to
+estimate the signal in the low \SNR regime using autocorrelation analysis. In a nutshell,
+the method consists of two stages. First, we estimate a mix of the low order autocorrelations of the signals from the data. These quantities can
+be estimated to any desired accuracy if the signals appear enough times in the measurements, without the need to detect individual occurrences.
+Then, the signals are estimated from the mixed autocorrelations.
+Interestingly, alternative methods which are often employed in similar estimation problems, such as expectation-maximization (EM) or Monte-Carlo Markov Chain (MCMC), seems to be intractable for this problem.
+
+\section{Model}  \label{sec:model}
+
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the measurement.
+For each $x_i$, let $s_i\in\{0,1\}^N$ be a binary signal, referred to as the \emph{support signal}.
+The non-zero values of $s_i$ indicates the locations of $x_i$ in $y$.
+If $s_i[n]=1$, then $y[n+j] = x_i[n+j]+\varepsilon[n+j]$ for $j=0,\ldots,L-1$.
+The further denote $s = \sum_{i=1}^Ks_i$ as the union of supports.
+
+The support signals are generated by the following generative model.
+First, an index $i_1$ is drawn uniformly from $\{1,\ldots,N\}$.
+A second index $i_2$ is drawn uniformly from $\{1,\ldots,N\}$.
+If $\vert i_2-i_1\vert \geq L-1$,
+then we set $s[i_2]=1$, otherise we keep $s[i_2]=0$ and draw an index again.
+We proceed to add non-zero entries to $s$ while keeping the separation condition.
+This process is halted when the number of when support is full enough by some predefined criterion.
+Once the signal $s$ is determined, for each non-zero entries is drawn from $\{1,\ldots,K\}$ and associated with the chosen signal.
+We note that if the support is sparse enough, this generative model can be approximated by a simpler process that ignores the separation constraint and simply choose $m$ random location in uniform over $\{1,\ldots N\}$.
+The number of occurrences $m_i,\ldots,m_K$ is unknown to us.
+
+The simplest way to present the forward model is a blind deconvolution problem between the support signals and the unknown signals
 \begin{equation}
-y[n] = \sum_{i=1}^K \xz [n-n_i] + \varepsilon[n], 
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
 \end{equation}
-where:
-\begin{itemize}
-	\item $y\in\RN$ is the noisy acquired data (measurement),
-	\item $\xz\in\RN$ is a zero-padded version of $x\in\RL, \thinspace L\ll N,
-	$ defined as $\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]$,
-	\item $n_i,\quad i=1,\ldots,K,$ are the translations of $\xz$, 
-	\item  $\varepsilon$ is i.i.d.\ normal noise with mean zero and variance $\sigma^2$ .
-\end{itemize}
+We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
+The goal is to estimate $x1,\ldots,x_K$ from $y$.
 
-Note that both $x$ and the translations $n_i$ are unknown.
-Therefore, essentially, this is a blind deconvolution problem.
-Particularly, let $s\in\{0,1\}^N$ be the ``support" signal, which takes the value 1 at the locations $n_i$ are zero otherwise.
-Then, 
-\begin{equation}
-y = \xz \ast s + \varepsilon,
-\end{equation}
-and the goal is then to estimate $x$ from $y$ although $s$ is unknown as well.
+Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+Clearly, without additional information on the signal, blind deconvolution is ill-posed.
+In our case, the prior information is that $s$ is a binary, sparse, signal.
+Other settings of blind deconvolution problems have been analyzed recently under different settings, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
+where the focus is on the high \SNR regime.
 
-For small values of $\sigma$,  the problem is easy.
-In this case, one can identify $x$ in $y$ by simple detection algorithms (e.g., thresholding).
-Once several copies of  signal were detected and cropped from $y$, then one can  improve the SNR by averaging.
-We are interest in the more challenging regime of high noise level, in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances.
-In this case, one need to use the prior information that the signal appears many times across the measurement.
+If $x$ is known and $K=1$, then  $s$ can be estimated by linear program in high \SNR~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low \SNR regime, estimating $s$ is impossible.
+To see that, suppose that for each non-zero value of $s$, an oracle provides you
+a window that contains it.
+Namely, we get a series of windows, each one contains a signal at unknown location.
+The question is whether one can estimate the locations of the signals within the windows.
+Apparently, this cannot be done.
+For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}.
+Since this alignment problem is essentially easier then the problem under consideration, we conclude that detecting the non-zero values of $s$ is impossible in low \SNR.
+In our setup, $s$ is the \emph{latent} variable of the problem.
+Indeed, in many blind deconvolution applications the goal is merely to estimate one of the unknown signals.
+For instance, in image deblurring, both the blurring
+kernel and the high-resolution image are unknown, but the prime goal is only
+to sharpen the image.
+In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any \SNR level and to any accuracy, although we cannot estimate their occurrences.
 
-To perform this blind deconvolution, we use the invariant approach proposed for multireference alignment in a previous paper.
-Let us  first introduce  notation.
-We crop the measurement $y\in\RN$ into a series of analysis windows:
-\begin{equation}
-    y_i = y[(i-1)W + 1 : iW ]\in\mathbb{R}^W, \quad i=1,\ldots,N/W, 
-\end{equation}
-To ease notation, we assume that  $W$ divides $N$  so that there are exactly $N/W$ windows.
-We also assume that $\vert n_i - n_j\vert >W$ so that each window contains no more than one signal (in general, we can introduce overlapping windows.
-The code enables it, but it does not seem to improve performance.).
-For each one of the windows, we compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum.
-We then hope that averaging over these features will produce a reliable estimation of the invariant features of the signal itself.
-We recall that given accurate estimators of those features, we can estimate the signal itself reliably. Therefore, the question boils down to the accuracy of these feature estimations.
+\section{Autocorrelation analysis}   \label{sec:autocorrelation}
 
-Before moving ahead to the feature estimators, we need to estimate the norm of the signal.
-This is necessary since many analysis windows do not contain information on the signal, but pure noise.
-We will use the norm to scale the the signal's estimator.
-This can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$. 
-Then,
-\begin{equation}
-\| y\|_2^2 =  \| x_K\|_2^2 + \|\varepsilon\|_2^2 + 2\varepsilon^Tx_K. 
-\end{equation}  
-As $N\to\infty$, we can estimate 
-\begin{equation}
-\begin{split}
-\E{\| y\|_2^2} &=  \| x_K\|_2^2 + \E{\|\varepsilon\|_2^2} + 2\E{\varepsilon^Tx_K} \\ 
-&= K\|x\|_2^2 + N\sigma^2. 
-\end{split}	 
-\end{equation}   
- And therefore, 
- \begin{equation}
- \|x\|_2^2 \approxeq \frac{\| y\|_2^2 - N\sigma^2}{K}. 
- \end{equation}
+\section{Numerical experiments}   \label{sec:numerics}
 
-Next, we analyze the feature estimation in the asymptotic regime of $N,\sigma,K\to\infty$ and fixed $L,W$.
-We introduce the ``sparsity factor" defined as $S = \frac{N}{WK}<\infty$, $WK$ is a measure for the ``active" windows.
-We also define  another zero padded signal $x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W$.
-
- We want to estimate the features of this signal, and focus on the bispectrum for the sake of simplicity (the estimation of the power spectrum and mean obeys the same methodology). 
-In order to estimate the bispectrum we average over the bispectra of the windows, namely, (for the power spectrum, we need to do unbiasing.
-In addition, we can replace the mean by more robust estimator, like the median.)
-\begin{eqnarray}
-\hat{B}_{x_W} = \frac{W}{N}\sum_{i=1}^{N/W}B_{y_i}.
-\end{eqnarray}
-We split the sum into three groups of the windows:
-\begin{eqnarray}
-\hat{B}_{x_W} = B_\textrm{signal} + B_\textrm{clutter} + B_\textrm{noise}, 
-\end{eqnarray}
-where
-\begin{itemize}
-	\item $B_\textrm{noise}$ - sum of the bispectra of the segments that contain pure noise (no signal),
-	\item $B_\textrm{signal}$ - sum of the bispectra of the segments that contain a full signal (one appearance of $x$) and noise,
-	\item $B_\textrm{clutter}$ - sum of the bispectra of the segments that contain only part of $x$ and noise.
-\end{itemize}
-
-We first observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix).
-More precisely, the variance of the noise goes to zero at rate  $\order{\frac{W}{N}\left(1-\frac{1}{S}\right)\sigma^6}$.
-In addition, under the assumption that $n_i$ (if appear) are distributed uniformly in the window (we need to come up with precise statistical model; but it would be rather easy), there are (asymptotically) $K(1-L/W)$ windows with complete signals.
-Therefore,
- $B_\textrm{signal}\to \frac{KW(1-L/W)}{N}B_x$ at rate $\order{\frac{\sigma^6}{K(1-L/W)}}$.
-(Here we need to be a bit careful with the mean of the signal, or to assume it is zero.) Note that the scaling would be corrected at the last stage of the algorithm, by rescaling according to the estimated  norm.
-
- The more interesting term is the ``clutter" --- the cropped signals. Since each such signal appears in two windows,
- we have $2KL/W$ clutter segments. Of course, the noise in this segments goes to zero
- at rate $\order{\frac{W\sigma^6}{2KL}}$.
-However, we have an additional error term arises from  the cropped signals.
-To analyze the effect of this term, let us assume that $N/\sigma^6$ is great enough so that $B_\textrm{noise}\to 0$.
-Then,
-\begin{equation}
-\begin{split}
-\left\| \hat{B}_{x_W} - B_\textrm{signal}\right\|_{\textrm{F}} \approxeq&  \left\|B_\textrm{clutter}\right\|_{\textrm{F}}
-= \left\|\frac{W}{N}\sum_{i\in\textrm{clutter}}B_{y_i}\right\|_{\textrm{F}}
-\\ \leq & 
-\frac{W}{N}\frac{2KL}{W}\left\|B_x\right\|_{\textrm{F}} = \frac{2L}{SW}
-\|B_x\|_{\textrm{F}}.
-\end{split}
-\end{equation}
-Therefore, for large sparsity term $S$ or large $W/L$, we get an accurate estimation of a scaled version of the signal's bispectrum.
-
-Few insights from the analysis: (need to check numerically)
-\begin{itemize}
-	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
-	\item Larger $W/L$ reduces the clutter error, however, increases the variance of the noise  of $B_\textrm{noise}$.
-	\item We must keep $W/L$ large enough to see enough full signals.    
-\end{itemize} 
-%\bibliographystyle{plain}
-%\bibliography{ref}
+\bibliographystyle{plain}
+\bibliography{ref}
 

### 2018-03-10 TEX/draft1.tex
updates notes

@@
 \usepackage{subcaption}
+\usepackage{mathtools}
 
@@
 
-\newcommand{\SNR}{\textsf{SNR} }
+\newcommand{\SNR}{{\textsf{SNR}}}
 
@@
 
-In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown, random, locations in the data $y$.
-The data may also contain background information -- independent of the signals -- which is model as noise.
+In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ which appear multiple times in unknown, random, locations in a data sequence $y$.
+The data may also contain background information -- independent of the signals -- which is modeled as noise.
 For one-dimensional signals, the data can be thought of as a long time series and the signals as repetitive short events.
@@
 
-If the noise level is negligible compared to the signal, the problem is easy.
-One can detect the signal occurrences in the data, and then estimate the signals using clustering and averaging.
-However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as discussed in Section~\ref{sec:model}.
-Nonetheless, in Section~\ref{sec:autocorrelation} we show that under a separation condition on the signals occurrences and that $K$ is not too large, it is possible to estimate the signals, in any \SNR level, up to any desired accuracy.
-This holds if each signals appears enough times in the data as will be explained next.
+This work is primely motivated by the challenging $\SNR$ levels being manifested in  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
+The acquired data in these technologies suffers from very high noise level.
+In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
 
-This work is primely motivated by the challenging innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
-The acquired data in these technologies suffers from very high noise level.
-Figure~\ref{fig:example} provides an example for the problem for one signal (i.e., $K=1$).
-Figures~\ref{fig:data2D_clean},\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} shows excerpt of data in different noise levels, and~\ref{fig:signal2D_clean} is the underlying signal.
-Figure~\ref{fig:signal2D_LS} shows the estimation of the signal using our method when $\sigma=1$.
-In Section~\ref{sec:numerics}, after describing the model and method and detail, we provide the all details on this experiments and show more experiments for $K>1$.
-In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
+If the noise level is negligible, estimating the signals is easy.
+One can detect the signal occurrences in the data sequence and then estimate the signals using clustering and averaging.
+Even in higher noise level regimes, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
+However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible.
+In Figure~\ref{fig:example} we demonstrate an instance of the problem in different noise levels.
+Figure~\ref{fig:data2D_clean} shows a excerpt of a big image that contains many repetitions of $21\times 21$ small image.
+The small image is a downsampled version of TKTK, which is shown in Figure~\ref{fig:signal2D_clean}.
+In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviation of $0.2$ and $1$, respectively.
+
+In this work we focus on the low $\SNR$ regime. To estimate the signal we use autocorrelation analysis of the data. 
+In a nutshell,
+the method consists of two stages. First, we estimate a mix of the low order autocorrelations of the signals from the data. These quantities can
+be estimated to any desired accuracy if the signals appear enough times in the measurements, without the need to detect individual occurrences.
+Then, the signals are estimated from the mixed autocorrelations.
+In Section~\ref{sec:autocorrelation}, we elaborate on our method  and show that if $K$ not too large, it is possible to estimate the signals, in any $\SNR$ level and to any desired accuracy.
+This holds if each signals appears enough times in the data and the signals are sufficiently spaced. 
+Interestingly, alternative methods which are often employed in similar estimation problems, such as expectation-maximization (EM) or Monte-Carlo Markov Chain (MCMC), seems to be intractable for this problem.
+In Figure~\ref{fig:signal2D_LS} we show an example for estimation of the signals where the data is contaminated with noise with standard deviation of $\sigma=1$ as presented in Figure~\ref{fig:data2D_noisy_1}.
+The normalized error between the signal and its estimation is TKTK.
+In Section~\ref{sec:numerics} we provide the details of this experiment and show additional experiments with $K>1$.
 
@@
 
-In Section~\ref{sec:autocorrelation}, we elaborate on our method to
-estimate the signal in the low \SNR regime using autocorrelation analysis. In a nutshell,
-the method consists of two stages. First, we estimate a mix of the low order autocorrelations of the signals from the data. These quantities can
-be estimated to any desired accuracy if the signals appear enough times in the measurements, without the need to detect individual occurrences.
-Then, the signals are estimated from the mixed autocorrelations.
-Interestingly, alternative methods which are often employed in similar estimation problems, such as expectation-maximization (EM) or Monte-Carlo Markov Chain (MCMC), seems to be intractable for this problem.
-
 \section{Model}  \label{sec:model}
@@
 to sharpen the image.
-In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any \SNR level and to any accuracy, although we cannot estimate their occurrences.
+In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot estimate their occurrences.
 
@@
 
+Our method for estimating the signals relies on two pillars. 
+First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the signals autocorrelations.
+The mixed autocorrelation can be estimated to any accuracy, in any \SNR level, if $M$ is large enough.
+Then, we use least-squares (LS) estimator to estimate the signals from their mixed autocorrelation.
+
+For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions, defined as
+\begin{align} \label{eq:autocorrelations}
+a_y^1 &= \sum_{i=0}^{N-1} y[i], \nonumber\\
+a_y^2[\ell] &= \sum_{i=0}^{N-1-\ell} y[i]y[i+\ell], \nonumber\\
+a_y^3[\ell_1,\ell_2] &= \sum_{i=0}^{N-1-\max\{\ell_1,\ell_2\}} y[i]y[i+\ell_1]y[i+\ell_2]. 
+\end{align}
+Note that the autocorrelation functions are symmetric so that $a_y^2[\ell] = a_y^2[-\ell]$ and $a_y^3[\ell_1,\ell_2] = a_y^3[-\ell_1,-\ell_2]$.
+
+The analysis of the autocorrelations is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
+\begin{equation}
+\gamma_i = \frac{M_i L}{N},
+\end{equation}
+and $\gamma = \sum_{i=1}^K\gamma_i$.
+Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+If $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
+\begin{align}
+\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
+\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
+\end{align}
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
+These relations are proved in Appendix~\ref{sec:autocorrelation_computation}.
+The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies.
+
+The third order autocorrelation defines the signals uniquely. For $K=1$, we have the following simple result:
+\begin{proposition}
+	Suppose that $x[0]$ and $x[L-1]$ are non-zeros. Then, the signal is determined uniquely from  $a_x^2$ and $a_x^3$.
+	\begin{proof}
+From the second-order autocorrelation, we ge
+\begin{equation*}
+a_x^2[L-1] = x[0]x[L-1]\neq 0.
+\end{equation*}
+Then, from the third-order autocorrelation we can compute $x[k]$ for all $k=0,\ldots L-1$ by
+\begin{eqnarray}
+a_x^3[k,L-1] = x[0]x[k]x[L-1].
+\end{eqnarray}
+	\end{proof}
+\end{proposition}
+ We note that the length of the signal can be easily derived from the autocorrelation of the signal if the separation condition is met.
+Therefore, the assumption that $L=1$ and $x[0]$ and $x[L-1]$ are non-zero makes sense.
+
+The heterogeneous case $K>1$ was explored for periodic autocorrelation functions.
+The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros \TODO{we should be prudent here}.
+Therefore, the following results hold for our setup as well.
+In~\cite{bandeira2017estimation}.
+There, it was shown that
+there is a finite list of solutions for $K$ generic signals when 
+\begin{itemize}
+	\item $K=2$ when $L>1$,
+	\item $K=3$ when $L>12$,
+	\item $K=4$ when $L>18$,
+	\item $5\leq K\leq 15$ when $L\geq 6K-5$.	
+\end{itemize}
+The authors conjecture that for $K>15$, $L\geq 6K-5$ is enough. Recently, Joe told use that he has proven that there is unique mapping in the same regime.  
+This also holds for arbitrary weights $\gamma_i$ which are rational fractions.
+
+If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $m$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
+\begin{proposition}
+	Let $K=1$. Then, 
+	\begin{equation*}
+	\frac{M}{N} = \frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
+	\end{equation*}
+	\begin{proof}
+The relation is proved by plugging the definitions of the signal autocorrelations into the right-hand side of the equation~\eqref{eq:autocorrelations}. 	
+\end{proof}
+\end{proposition}
+
+If we assume that $s$ is sparse, then by ignoring the separation condition, one can describe the generative process of $s$ as a Bernoulli process with parameter $M/N$.
+Therefore, in low \SNR  one can estimate the parameter that control this statistical process, although cannot estimate individual entries.
+
+I DIDN'T SAY ANYTHING ABOUT ESTIMATION RATE
+
 \section{Numerical experiments}   \label{sec:numerics}
+
+\section{Conclusion} 
+Here we conclude the paper: cryo -- EM, structured background, without separation, heterogeneity
+In particular, in cryo--EM, multiple projections of a molecule (signal), taken
+from unknown viewing directions, are recorded on two-dimensional detector
+array. Current algorithms try to detect these projections in a low SNR regime
+and then use them for the reconstruction process. Since the
+Then, the reconstruction problem is to detect these projection, and then use
+them to estimat
+The data acquired in both technologies is composed of multiple projections
+of a molecule (the signal), taken from unknown viewing direction, and drawn in
+high noise level. The reconstitution problem is then to estimate the molecule
+from this data.
 
@@
 
+\appendix
+
+\section{Autocorrelation estimations} \label{sec:autocorrelation_computation}
+
+To analyze the asymptotic behavior of the data autocorrelation functions, we consider one signal $K=1$.
+The extension to $K>1$ is straightforward by averaging the contributions of all signal with the appropriates weights, see~\cite{boumal2017heterogeneous}.
+
+Let us define
+\begin{equation}
+\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
+\end{equation}
+By assuming $M_N=\Omega(N)$, we also have $\gamma>0$.
+We start by considering the first autocorrelation of the data
+\begin{equation}
+a_y^1 = \sum_{i=0}^{N-1} y[i] = \frac{1}{N/L}\sum_{j=0}^{M_N-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}} \xrightarrow{a.s.}\gamma a_x^1,
+\end{equation}
+where the noise term converges to zero almost surely (a.s.) by the law of large numbers.
+
+We proceed with the second moment. Let us fix $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
+\begin{equation}
+\begin{split}
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
+& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
+\end{split}
+\end{equation}
+where the cross terms between the signal and the noise vanish in the limit.
+
+We treat the signal and noise terms separately. We first break the noise term into $M_N$ different sums, each contains one copy of the signal, and get
+\begin{equation}
+\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
+\end{equation}
+Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
+\begin{equation}
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+\end{equation}
+Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and therefore converge to zero almost surely as $N\to\infty$.
+If $\ell=0$, 
+\begin{equation}
+\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon[i]^2 \xrightarrow{a.s.} \sigma^2.
+\end{equation}
+
+We are now moving to the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
+\begin{equation*}
+a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
+\end{equation*}
+This sum can be broken into eight partial sums.
+The first contains only signal terms and converges to a $\gamma a_x^3$.
+Three other partial sums contains the product of two signal entries and one noise term.
+Since the noise is independent of the signal, then these terms go to zero almost surely.
+
+We next analyze the contribution of triple product of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
+\begin{equation*}
+\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
+\end{equation*}
+For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely. This also holds for $\ell_1=\ell_2=0$.
+
+To complete the analysis, we consider the terms including the product of two noise terms and one signal entry.
+Most of these terms converges to zero almost surely because of interdependency between the noise entries.
+For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$.
+
 \end{document}

### 2018-03-12 TEX/draft1.tex
Updated notes

@@
 
-This work is primely motivated by the challenging $\SNR$ levels being manifested in  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
-The acquired data in these technologies suffers from very high noise level.
-In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
-
 If the noise level is negligible, estimating the signals is easy.
@@
 Even in higher noise level regimes, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
-However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible.
+However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as clarified in Section~\ref{sec:model}.
 In Figure~\ref{fig:example} we demonstrate an instance of the problem in different noise levels.
@@
 The small image is a downsampled version of TKTK, which is shown in Figure~\ref{fig:signal2D_clean}.
-In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviation of $0.2$ and $1$, respectively.
+In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviations of $0.2$ and $1$, respectively.
 
@@
 	\centering
-	\includegraphics[scale=0.5]{signal2D_LS}
-	\caption{Recovered signal using LS}
+	\includegraphics[scale=0.5]{signal2D_LS_all_images}
+	\caption{710K micrographs, $M=561Mega$, error  = $0.05062$}
 	\label{fig:signal2D_LS}
@@
 	\centering
-	\includegraphics[scale=0.5]{signal2D_RRR}
-	\caption{This one will be replaced}
+	\includegraphics[scale=0.5]{signal2D_LS_exp1}
+	\caption{Recovery with 140K micrographs and $M = 110Mega$, error = ? }
 	\label{fig:signal2D_RRR}
@@
 
+This work is primely motivated by  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
+The acquired data in these modalities is contaminated with high noise levels.
+Therefore, any molecule reconstruction algorithm must take  the challenging $\SNR$ level into account.
+In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
+
 \section{Model}  \label{sec:model}
 
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the measurement.
-For each $x_i$, let $s_i\in\{0,1\}^N$ be a binary signal, referred to as the \emph{support signal}.
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data.
+For each $x_i$, we associate a binary signal  $s_i\in\{0,1\}^N$, referred to as the \emph{support signal} and let $s = \sum_{i=1}^Ks_i$.
 The non-zero values of $s_i$ indicates the locations of $x_i$ in $y$.
 If $s_i[n]=1$, then $y[n+j] = x_i[n+j]+\varepsilon[n+j]$ for $j=0,\ldots,L-1$.
-The further denote $s = \sum_{i=1}^Ks_i$ as the union of supports.
+We denote the cardinality of $s_i$ by $M_i$  and $M = \sum_{i=1}^{K}M_i$. We do not assume the knowledge of $M_i$'s, neither of $M$.
 
-The support signals are generated by the following generative model.
-First, an index $i_1$ is drawn uniformly from $\{1,\ldots,N\}$.
-A second index $i_2$ is drawn uniformly from $\{1,\ldots,N\}$.
-If $\vert i_2-i_1\vert \geq L-1$,
-then we set $s[i_2]=1$, otherise we keep $s[i_2]=0$ and draw an index again.
-We proceed to add non-zero entries to $s$ while keeping the separation condition.
-This process is halted when the number of when support is full enough by some predefined criterion.
-Once the signal $s$ is determined, for each non-zero entries is drawn from $\{1,\ldots,K\}$ and associated with the chosen signal.
-We note that if the support is sparse enough, this generative model can be approximated by a simpler process that ignores the separation constraint and simply choose $m$ random location in uniform over $\{1,\ldots N\}$.
-The number of occurrences $m_i,\ldots,m_K$ is unknown to us.
+The support signals are generated by the following generative model. The signal $s$ is initialized with zeros.
+First, an index $i_1$ is drawn uniformly from $\{1,\ldots,N\}$ and we set $s[i_1]=1$. A second index $i_2$ is then drawn uniformly from $\{1,\ldots,N\}$. If $\vert i_2-i_1\vert \geq L$,
+then we set $s[i_2]=1$, otherwise we keep $s[i_2]=0$ and draw a new index  from uniform distribution.
+We then proceed adding  non-zero entries to $s$,  while keeping the separation condition until some halting criterion is obtained.
+Ultimately, each  non-zero value of $s$ is associated with one of the $s_i$'s uniformly over  $\{1,\ldots,K\}$.
+We note that if the support is sparse enough, this generative model can be approximated by a simple Bernoulli process which takes the values of one and zero with probabilities  $M/N$ and $1-M/N$, respectively.
 
-The simplest way to present the forward model is a blind deconvolution problem between the support signals and the unknown signals
+The simplest way to present the forward model is a mix of blind deconvolution problems between the support signals and the unknown signals
 \begin{equation}
@@
 We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The goal is to estimate $x1,\ldots,x_K$ from $y$.
+The goal is to estimate $x_1,\ldots,x_K$ from $y$.
 
@@
 Other settings of blind deconvolution problems have been analyzed recently under different settings, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
-where the focus is on the high \SNR regime.
+where the focus is on high $\SNR$ regimes.
 
-If $x$ is known and $K=1$, then  $s$ can be estimated by linear program in high \SNR~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low \SNR regime, estimating $s$ is impossible.
-To see that, suppose that for each non-zero value of $s$, an oracle provides you
-a window that contains it.
-Namely, we get a series of windows, each one contains a signal at unknown location.
-The question is whether one can estimate the locations of the signals within the windows.
-Apparently, this cannot be done.
-For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}.
-Since this alignment problem is essentially easier then the problem under consideration, we conclude that detecting the non-zero values of $s$ is impossible in low \SNR.
-In our setup, $s$ is the \emph{latent} variable of the problem.
+In our setup, the support signals $s_1,\ldots,s_K$ are the \emph{latent} variables of the problem.
 Indeed, in many blind deconvolution applications the goal is merely to estimate one of the unknown signals.
@@
 to sharpen the image.
-In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot estimate their occurrences.
+If $x$ is known and $K=1$, then  $s$ can be estimated by linear programming  in the high $\SNR$ regime~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating $s$ is impossible.
+To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contain one occurrence of $x$.
+Put it differently, we get a series of windows, each one contains a signal at unknown location.
+Estimating the first entry of the signals within each  window is an essentially easier problem the detecting the support of $s$ since the windows are given to us by the oracle.
+Apparently, this problem, called alignment or synchronization, is impossible in the low $\SNR$ regime.
+For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}.
+Therefore, we conclude that that detecting the non-zero values of $s$ is impossible in low \SNR.
+
+In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot detect their occurrences in $y$.
 
@@
 Our method for estimating the signals relies on two pillars. 
-First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the signals autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any \SNR level, if $M$ is large enough.
+First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the $K$ signals autocorrelations.
+The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the separation condition on the support is held.
 Then, we use least-squares (LS) estimator to estimate the signals from their mixed autocorrelation.
+From pedagogical reasons, we start with the second stage of recovering signals from their autocorrelations.
+In this section we mainly discuss the uniqueness of the mapping from the autocorrelation to the signals.
+Concrete algorithms will be discussed in the next section.
 
-For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions, defined as
+For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions of a signal $z\in\mathbb{R}^W$, defined as
 \begin{align} \label{eq:autocorrelations}
-a_y^1 &= \sum_{i=0}^{N-1} y[i], \nonumber\\
-a_y^2[\ell] &= \sum_{i=0}^{N-1-\ell} y[i]y[i+\ell], \nonumber\\
-a_y^3[\ell_1,\ell_2] &= \sum_{i=0}^{N-1-\max\{\ell_1,\ell_2\}} y[i]y[i+\ell_1]y[i+\ell_2]. 
+a_z^1 &= \sum_{i=0}^{W-1} z[i], \nonumber\\
+a_z^2[\ell] &= \sum_{i=0}^{W-1-\ell} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{W-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
 \end{align}
-Note that the autocorrelation functions are symmetric so that $a_y^2[\ell] = a_y^2[-\ell]$ and $a_y^3[\ell_1,\ell_2] = a_y^3[-\ell_1,-\ell_2]$.
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$.
 
-The analysis of the autocorrelations is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
-\begin{equation}
-\gamma_i = \frac{M_i L}{N},
-\end{equation}
-and $\gamma = \sum_{i=1}^K\gamma_i$.
-Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-If $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
-\begin{align}
-\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
-\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
-\end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
-These relations are proved in Appendix~\ref{sec:autocorrelation_computation}.
-The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies.
-
-The third order autocorrelation defines the signals uniquely. For $K=1$, we have the following simple result:
+A one-dimensional signal is determined uniquely by its third-order auto-correlation:
 \begin{proposition}
-	Suppose that $x[0]$ and $x[L-1]$ are non-zeros. Then, the signal is determined uniquely from  $a_x^2$ and $a_x^3$.
+	Suppose that $z[0]$ and $z[L-1]$ are non-zeros. Then, a signal $z\in\mathbb{R}^W$ is determined uniquely from  $a_z^2$ and $a_z^3$.
 	\begin{proof}
@@
 		\begin{equation*}
-a_x^2[L-1] = x[0]x[L-1]\neq 0.
+		a_z^2[L-1] = z[0]z[L-1]\neq 0.
 		\end{equation*}
-Then, from the third-order autocorrelation we can compute $x[k]$ for all $k=0,\ldots L-1$ by
+		Then, from the third-order autocorrelation we can compute $z[k]$ for all $k=0,\ldots L-1$ by
 		\begin{eqnarray}
-a_x^3[k,L-1] = x[0]x[k]x[L-1].
+		a_z^3[k,L-1] = z[0]z[k]z[L-1].
 		\end{eqnarray}
@@
 \end{proposition}
- We note that the length of the signal can be easily derived from the autocorrelation of the signal if the separation condition is met.
-Therefore, the assumption that $L=1$ and $x[0]$ and $x[L-1]$ are non-zero makes sense.
+We note that the length of the signal can be easily derived from the second-order autocorrelation of the signal.
+Therefore, the assumption that $z[0]$ and $z[L-1]$ is met in practice.
+We also note that for one-dimensional signals, the second-order autocorrelation does not determined the signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+This is not the case for dimensions greater than one, in which almost all signals are determined uniquely from their aperiodic autocorrelations, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible,bendory2017fourier}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However,  in order to determine the reflection symmetry ($Z_2$ symmetry), one needs to use the third moment.
 
 The heterogeneous case $K>1$ was explored for periodic autocorrelation functions.
-The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros \TODO{we should be prudent here}.
-Therefore, the following results hold for our setup as well.
-In~\cite{bandeira2017estimation}.
-There, it was shown that
-there is a finite list of solutions for $K$ generic signals when 
+The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros.
+Therefore, the following results hold for our setup as well  \TODO{we should be prudent here to make sure that this set does not ``fall'' in the zero measure}.
+In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order autocorrelations determine  a finite list of $K$ generic signals when
 \begin{itemize}
@@
 
-If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $m$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
+\TODO{Where we should refer to Gianakis's paper?}
+
+We are moving forward to discuss the second question of how to estimate the autocorrelation of the signals from the data. 
+The analysis is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
+\begin{equation}
+\gamma_i = \frac{M_i L}{N},
+\end{equation}
+and $\gamma = \sum_{i=1}^K\gamma_i$.
+Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+The main insight is that if $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
+\begin{align}
+\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
+\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
+\end{align}
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
+These relations are proved in Appendix~\ref{sec:autocorrelation_computation}.
+The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies.
+This means that given $M_1,\ldots,M_K$ and $\sigma^2$ and $K$ does not exceed the limit for uniqueness, the one can estimate the signals from the third-order autocorrelation of the data.
+In other words, the signals can be estimated in asymptotic estimation rate of $\sigma^6/N$.
+
+If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $M$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
 \begin{proposition}
@@
 
-I DIDN'T SAY ANYTHING ABOUT ESTIMATION RATE
+Estimating $\sigma$ and $M$?
 
@@
 
-We proceed with the second moment. Let us fix $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
+We proceed with the second moment for fixed $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
 \begin{equation}
@@
 \end{equation}
-where the cross terms between the signal and the noise vanish in the limit.
+where the cross terms between the signal and the noise almost surely vanish in the limit.
 
-We treat the signal and noise terms separately. We first break the noise term into $M_N$ different sums, each contains one copy of the signal, and get
-\begin{equation}
+We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
+\begin{equation} \label{eq:2nd_moment_signal_term}
 \frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
@@
 \end{equation*}
-This sum can be broken into eight partial sums.
-The first contains only signal terms and converges to a $\gamma a_x^3$.
-Three other partial sums contains the product of two signal entries and one noise term.
+Writing explicitly in terms of signal and noise, this sum can be broken into eight partial sums.
+The first contains only signal terms and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+Three other partial sums contain the product of two signal entries and one noise term.
 Since the noise is independent of the signal, then these terms go to zero almost surely.
@@
 \begin{equation*}
-\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
+\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
 \end{equation*}
-For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely. This also holds for $\ell_1=\ell_2=0$.
+For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
+For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each is a triple product of Gaussian variables with zero mean.
+Therefore, it is also converges to zero.
 
-To complete the analysis, we consider the terms including the product of two noise terms and one signal entry.
+To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
 Most of these terms converges to zero almost surely because of interdependency between the noise entries.

### 2018-03-20 TEX/draft1.tex
minor changes in the tex
updated notes

@@
-\documentclass[english]{article}
+\documentclass[english,11pt]{article}
 
@@
 \usepackage{mathtools} 
+\usepackage[margin=1.2in]{geometry}
 
@@
 \newcommand{\CL}{\mathbb{C}^L}
-\newcommand{\RN}{\mathbb{R}^L}
+\newcommand{\RN}{\mathbb{R}^N}
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
@@
 \newcommand{\hx}{\hat{x}} 
-
+\newcommand{\one}{\mathbf{1}} 
 \newcommand{\SNR}{{\textsf{SNR}}}
@@
 
-In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ which appear multiple times in unknown, random, locations in a data sequence $y$.
+In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown, random, locations in a data sequence $y$.
 The data may also contain background information -- independent of the signals -- which is modeled as noise.
 For one-dimensional signals, the data can be thought of as a long time series and the signals as repetitive short events.
-For two-dimensional signals, the data is a big image that contains many smaller images.
+For two-dimensional signals, $y$ presents a big image, containing many smaller images.
 The problem is then to estimate the signals $x_1,\ldots x_K$ from $y$. This
 model appears, in different noise levels, in many applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-In Section~\ref{sec:model} we provide a precise mathematical formulation of the problem.
+In Section~\ref{sec:model} we provide a precise mathematical formulation of the model and the estimation problem.
 
 If the noise level is negligible, estimating the signals is easy. 
-One can detect the signal occurrences in the data sequence and then estimate the signals using clustering and averaging.
+In this scenario, standard detection and clustering algorithms can produce multiple copies of each signal that can be then averaged. 
 Even in higher noise level regimes, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
-However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as clarified in Section~\ref{sec:model}.
-In Figure~\ref{fig:example} we demonstrate an instance of the problem in different noise levels.
-Figure~\ref{fig:data2D_clean} shows a excerpt of a big image that contains many repetitions of $21\times 21$ small image.
-The small image is a downsampled version of TKTK, which is shown in Figure~\ref{fig:signal2D_clean}.
-In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviations of $0.2$ and $1$, respectively.
+\TODO{Do we want to add another 1D example to demonstare the problem, similarly to Figure 1.1 in the bispectrum paper?}
+However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as explained in Section~\ref{sec:model}.
+Figure~\ref{fig:example} illustrates the problem in different noise levels and one underlying signal ($K=1$).
+Figure~\ref{fig:signal2D_clean} shows a $21\times 21$ image, which is a downsampled version of a projection of TKTK, taken from \textsf{ASPIRE} package~\cite{aspire} \TODO{The image is taken from the example folder}.
+Figure~\ref{fig:data2D_clean} shows a excerpt of a big image (the data image) that contains many repetitions of the projection.
+In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1}, the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviations of $\sigma=0.2$ and $\sigma=1$, respectively.
+Figures~\ref{fig:signal2D_LS} and~\ref{fig:signal2D_LS_inter} show estimates of the projection from noisy data with $\sigma=1$.
+These examples demonstrate that our method can work even if the data may seem as a pure noise.
+In Section~\ref{sec:numerics} we provide the details of this experiment and show more corroborating experiments.
 
-In this work we focus on the low $\SNR$ regime. To estimate the signal we use autocorrelation analysis of the data. 
-In a nutshell,
-the method consists of two stages. First, we estimate a mix of the low order autocorrelations of the signals from the data. These quantities can
-be estimated to any desired accuracy if the signals appear enough times in the measurements, without the need to detect individual occurrences.
-Then, the signals are estimated from the mixed autocorrelations.
-In Section~\ref{sec:autocorrelation}, we elaborate on our method  and show that if $K$ not too large, it is possible to estimate the signals, in any $\SNR$ level and to any desired accuracy.
-This holds if each signals appears enough times in the data and the signals are sufficiently spaced. 
-Interestingly, alternative methods which are often employed in similar estimation problems, such as expectation-maximization (EM) or Monte-Carlo Markov Chain (MCMC), seems to be intractable for this problem.
-In Figure~\ref{fig:signal2D_LS} we show an example for estimation of the signals where the data is contaminated with noise with standard deviation of $\sigma=1$ as presented in Figure~\ref{fig:data2D_noisy_1}.
-The normalized error between the signal and its estimation is TKTK.
-In Section~\ref{sec:numerics} we provide the details of this experiment and show additional experiments with $K>1$.
+In this work we focus on the low $\SNR$ regime. In order to estimate the signal, we use autocorrelation analysis of the data. 
+In a nutshell, the method consists of two stages.
+First, we estimate a mix of the low--order autocorrelation functions of the signals from the data.
+These quantities can be estimated, to any desired accuracy, if the signals appear enough times in the measurement, without the need to detect individual occurrences.
+Then, the signals are estimated from the mixed autocorrelations using a non-convex least-squares.
+In Section~\ref{sec:autocorrelation}, we elaborate on the technique and prove some of its properties.
+Interestingly, expectation-maximization (EM) --  a popular framework for similar estimation problems, such as Gaussian mixture models and multireference alignment -- is intractable for this problem.
+Even if the number of signal occurrence $M$ is known and $K=1$, at each iteration
+EM needs to assign probabilities to each possible combination of  $M$ copies of the current signal estimation in the measurement.
 
-\begin{figure}[ht!]
-    \advance\leftskip-4cm
-   \advance\rightskip-4cm
+\begin{figure}
+
+\advance\leftskip-2cm
+\advance\rightskip -2cm
 
 %	\centering
-
-	\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.6\textwidth}
 	\centering
-	\includegraphics[scale=0.5]{data2D_clean}
-\caption{Excerpt of clean data}
+	\includegraphics[scale=0.6]{data2D_clean}
+	\vspace*{-20pt}
+\caption{}
 \label{fig:data2D_clean}
 	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
+	\begin{subfigure}{.6\textwidth}
 	\centering
-\includegraphics[scale=0.5]{data2D_noisy_02}
-\caption{Excerpt of noisy data with $\sigma=0.2$}
+	\includegraphics[scale=0.6]{signal2D_clean}
+	\vspace*{-20pt}
+	\caption{}
+	\label{fig:signal2D_clean}
+\end{subfigure}%
+
+	\begin{subfigure}{.6\textwidth}
+	\centering
+	\includegraphics[scale=0.6]{data2D_noisy_02}
+	\vspace*{-20pt}
+	\caption{}
 	\label{fig:data2D_noisy_02}
 \end{subfigure}
-	\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.6\textwidth}
 	\centering
-\includegraphics[scale=0.5]{data2D_noisy_1}
-\caption{Excerpt of noisy data with $\sigma=1$}
+	\includegraphics[scale=0.6]{signal2D_LS_all_images}
+	\vspace*{-20pt}
+	\caption{}
+	\label{fig:signal2D_LS}
+\end{subfigure}
+
+\begin{subfigure}{.6\textwidth}
+\centering
+\includegraphics[scale=0.6]{data2D_noisy_1}
+\vspace*{-20pt}
+\caption{}
 \label{fig:data2D_noisy_1}
 \end{subfigure}
-
-	\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.6\textwidth}
 	\centering
-	\includegraphics[scale=0.5]{signal2D_clean}
-	\caption{Clean signal}
-	\label{fig:signal2D_clean}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-	\centering
-	\includegraphics[scale=0.5]{signal2D_LS_all_images}
-	\caption{710K micrographs, $M=561Mega$, error  = $0.05062$}
-	\label{fig:signal2D_LS}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-	\centering
-	\includegraphics[scale=0.5]{signal2D_LS_exp1}
-	\caption{Recovery with 140K micrographs and $M = 110Mega$, error = ? }
-	\label{fig:signal2D_RRR}
+	\includegraphics[scale=0.6]{signal2D_LS_intermediate}
+%	\vspace*{-20pt}
+	\caption{}
+	\label{fig:signal2D_LS_inter}
 \end{subfigure}
 
-\caption{Example}
+\caption{Figure (a) shows an excerpt of 2D data with multiple signal occurrences and no noise.
+Each small image is the $21\times 21$ image shown in Figure (b).
+Figures (c) and (e) show the same data, now contaminated with i.i.d.\ Gaussian noise with $\sigma=0.2$ and $\sigma=1$, respectively.
+Figures (d) and (f) show estimates of the image (b) from data with noise level $\sigma=1$ (as in Figure (e)).
+The signal appeared $M = 561\times 10^6$ and $M = 110\times 10^6$ times and the normalized recovery error is  $0.078$ and $0.135$, respectively.}
+%	we used $71\times10^4$
+% (d) 710K micrographs, $M=561Mega$, error  =  (e)The same data as in Figure~\ref{fig:signal2D_clean} contaminated with i.i.d./ Gaussian noise with $\sigma=0.2$ (f) Recovery with 140K micrographs and $M = 110Mega$, error = 0.135}
 \label{fig:example}
@@
 
-This work is primely motivated by  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL).
-The acquired data in these modalities is contaminated with high noise levels.
+This work is primely motivated by cryo-electron microscopy (cryo--EM), which is an innovative  single particle reconstruction technology.
+The acquired data in a cryo-EM experiment is contaminated with high noise levels.
 Therefore, any molecule reconstruction algorithm must take  the challenging $\SNR$ level into account.
-In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.
+In the last part of this manuscript, we draw connections with the estimation problem under consideration and the cryo--EM problem.
 
@@
 For each $x_i$, we associate a binary signal  $s_i\in\{0,1\}^N$, referred to as the \emph{support signal} and let $s = \sum_{i=1}^Ks_i$.
-The non-zero values of $s_i$ indicates the locations of $x_i$ in $y$.
+The nonzero values of $s_i$ indicates the locations of $x_i$ in $y$.
 If $s_i[n]=1$, then $y[n+j] = x_i[n+j]+\varepsilon[n+j]$ for $j=0,\ldots,L-1$.
-We denote the cardinality of $s_i$ by $M_i$  and $M = \sum_{i=1}^{K}M_i$. We do not assume the knowledge of $M_i$'s, neither of $M$.
+We denote the cardinality of $s_i$ by $M_i$  and $M = \sum_{i=1}^{K}M_i$. Neither the $M_i$'s nor $M$ is assumed to be known.
 
@@
 then we set $s[i_2]=1$, otherwise we keep $s[i_2]=0$ and draw a new index  from uniform distribution.
-We then proceed adding  non-zero entries to $s$,  while keeping the separation condition until some halting criterion is obtained.
-Ultimately, each  non-zero value of $s$ is associated with one of the $s_i$'s uniformly over  $\{1,\ldots,K\}$.
+We then proceed adding  nonzero entries to $s$,  while keeping $L$  entries separation until some halting criterion is obtained.
 We note that if the support is sparse enough, this generative model can be approximated by a simple Bernoulli process which takes the values of one and zero with probabilities  $M/N$ and $1-M/N$, respectively.
+Once $s$ is determined, each one of its nonzero entries is associated with one of the $s_i$'s. 
+In particular, for each $s[k]\neq 0$ we set $s_i[k] = 1$ and $s_j[k] = 0$ for $i\neq j$, where $i$ is drawn form an unknown probability over  $\{1,\ldots,K\}$.
 
-The simplest way to present the forward model is a mix of blind deconvolution problems between the support signals and the unknown signals
+The simplest way to present the forward model is a mix of blind deconvolution problems between the support signals and the target signals
 \begin{equation}
@@
 Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-Clearly, without additional information on the signal, blind deconvolution is ill-posed.
+Clearly, the problem is ill-posed without additional information.
 In our case, the prior information is that $s$ is a binary, sparse, signal.
@@
 
-In our setup, the support signals $s_1,\ldots,s_K$ are the \emph{latent} variables of the problem.
+An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
+The  $s_i$'s  are referred to as \emph{nuisance  variables}.
 Indeed, in many blind deconvolution applications the goal is merely to estimate one of the unknown signals.
@@
 However, in the low $\SNR$ regime, estimating $s$ is impossible.
-To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contain one occurrence of $x$.
+To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
 Put it differently, we get a series of windows, each one contains a signal at unknown location.
-Estimating the first entry of the signals within each  window is an essentially easier problem the detecting the support of $s$ since the windows are given to us by the oracle.
-Apparently, this problem, called alignment or synchronization, is impossible in the low $\SNR$ regime.
+Estimating the first entry of the signal within each  window is an easier problem than detecting the support of $s$.
+However, even this problem -- called alignment or synchronization -- is impossible in the low $\SNR$ regime.
 For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}.
-Therefore, we conclude that that detecting the non-zero values of $s$ is impossible in low \SNR.
-
+Therefore, we conclude that that detecting the nonzero values of $s$ is impossible in low \SNR.
 In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot detect their occurrences in $y$.
@@
 The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros.
-Therefore, the following results hold for our setup as well  \TODO{we should be prudent here to make sure that this set does not ``fall'' in the zero measure}.
+Therefore, the following results hold for our setup as well  \TODO{This part is wrong -- Email correspondence with Alex}.
 In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order autocorrelations determine  a finite list of $K$ generic signals when
@@
 If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $M$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
-\begin{proposition}
+\begin{proposition} \label{prop:gamma}
 	Let $K=1$. Then, 
@@
 
+\begin{proposition} \label{prop:gamma_sigma}
+	It is possible to estimate $M$ and $\sigma$ from the third moment.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
 If we assume that $s$ is sparse, then by ignoring the separation condition, one can describe the generative process of $s$ as a Bernoulli process with parameter $M/N$.
@@
 \section{Numerical experiments}   \label{sec:numerics}
+
+\subsection{One-dimensional experiments}
+
+\subsection{Two-dimensional experiments}
+
+Solving RRR, and then 200 LS iteration on window of size $W$ and 500 iterations on window of size $L$.
 
@@
 from this data.
+
+A word on the sample complexity
 
@@
 
+\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+
+We aim to prove that one can estimate both $\sigma$ and $M$ from the observed third moment.
+We will construct two independent quadratic equations of $M$ which do not depend on $\sigma$.
+This will let us estimate $M$.
+Given $M$, we will estimate $\sigma$.
+
+To ease notation, let $\beta=M/N$. Recall that $a_y^1 = \beta(\one^Tx)$ and  
+ and $a_y^2[0] = \beta(\|x\|^2+\sigma^2)$, where $\one\in\RL$ stands for vector of ones. Taking the product:
+\begin{equation}\label{eq:E1}
+\begin{split}
+E_1 &:= (\beta(\one^Tx))(\beta(\|x\|^2+\sigma^2)) \\
+& = \sigma^2a_y^1 + \beta^2\tau,
+ \end{split}
+\end{equation}
+where $\tau := L\left(\sum_{j=1}^{L-1}(a_x^3[j,0]+a_x^3[0,j] )+\sum_{j=0}^{L-1}a_x^3[0,0]\right)$. Next, we can estimate from $a_y^3$
+\begin{equation} \label{eq:E2}
+E_2:= \beta \tau + 3L\sigma^2a_y^1.
+\end{equation}
+Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
+\begin{equation}
+E_2\beta -3L\sigma^2a_y^1 = E_1-\sigma^2a_y^1.
+\end{equation}
+Now, recalling from Proposition~\ref{prop:gamma}
+\begin{equation} \label{eq:sigma2}
+\sigma^2 = a_y^2 - (a^1_y)^2/\beta, 
+\end{equation} 
+where we use $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$.
+Rearranging the equations, we then get the quadratic equation
+\begin{equation} \label{eq:quad1}
+\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
+\end{equation}
+where 
+\begin{align*}
+\mathcal{A} &= E_2, \\ 
+\mathcal{B} &= -(E_1 + (3L-1)a_y^1a_y^2), \\
+\mathcal{C} &= (3L-1)(a_y^1)^3.
+\end{align*}
+
+We are now proceeding to derive the second quadratic equation. We notice that \begin{equation} \label{eq:E3}
+E_3  = (a_y^1)^3 = \beta^3 \upsilon,
+\end{equation}
+where \TODO{to check} $$\upsilon = a_x^3[0,0] + 3\sum_{i=1}^{L-1}a_x^3[i,i] + 3\sum_{i=1}^{L-1}(a_x^3[i,0]+a_x^3[0,i]) + 6\sum_{1\leq i \leq j\leq L-1}a_x^3[i,j].$$
+On the other hand, from $a_y^3$ we can directly estimate
+\begin{equation} \label{eq:E4}
+E_4 = \beta\upsilon + 9L\sigma^2a_x^1.
+\end{equation}
+Now, by multiplying both sides by $\beta^2$ and using~\eqref{eq:E3}, we get 
+\begin{equation} \label{eq:E4}
+\beta^2E_4 =  E_3  + 9L\sigma^2a_x^1.
+\end{equation}
+Plugging~\eqref{eq:sigma2} and rearranging the equation, we get a second quadratic equation independent of $\sigma$:
+\begin{equation} \label{eq:quad2}
+\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
+\end{equation}
+where
+\begin{align*}
+\mathcal{D} &= E_4 - 9La_x^1a_y^2, \\ 
+\mathcal{E} &= 9La_x^1(a_y^1)^2, \\
+\mathcal{F} &= -(a_y^1)^3.
+\end{align*}
+
+To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
+To this end, it is enough to show that the ratio between the coefficients is not the same.
+using~\eqref{eq:E1}, we have 
+\begin{equation*}
+\frac{\mathcal{B}}{\mathcal{C}} = \frac{-(E_1 + (3L-1)a_y^1a_y^2)}{(3L-1)(a_y^1)^3} = -\frac{a_y^2[0]}{(3L-1)(a_y^1)^2} - \frac{a_y^2}{(a_y^1)^2}.
+\end{equation*}
+In addition, 
+\begin{equation*}
+\frac{\mathcal{E}}{\mathcal{F}} = -\frac{9La_x^1}{a_y^1}. 
+\end{equation*}
+Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
+\begin{equation*}
+\frac{a_y^2[0]}{(3L-1)(a_y^1)^2} + \frac{a_y^2}{(a_y^1)^2} = \frac{9La_x^1}{a_y^1}. 
+\end{equation*}
+Rearranging the equation, we get 
+\begin{equation*}
+ a_y^2[0] + (3L-1)(a_y^1)^2 - 9La_x^1a_y^1=0.
+\end{equation*}	
+For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent.
+
 \end{document}

### 2018-03-24 TEX/draft1.tex
updated notes

@@
 These quantities can be estimated, to any desired accuracy, if the signals appear enough times in the measurement, without the need to detect individual occurrences.
-Then, the signals are estimated from the mixed autocorrelations using a non-convex least-squares.
+Then, the signals are estimated from the mixed autocorrelations using a non-convex least-squares (LS).
 In Section~\ref{sec:autocorrelation}, we elaborate on the technique and prove some of its properties.
 Interestingly, expectation-maximization (EM) --  a popular framework for similar estimation problems, such as Gaussian mixture models and multireference alignment -- is intractable for this problem.
-Even if the number of signal occurrence $M$ is known and $K=1$, at each iteration
-EM needs to assign probabilities to each possible combination of  $M$ copies of the current signal estimation in the measurement.
+Even if the number of signal occurrences $M$ is known and $K=1$, at each iteration
+EM needs to assign probabilities to each possible combination of  $M$ copies of the current signal estimation in the measurement, which is of order of $O(N^M)$.
 
@@
 
-Our method for estimating the signals relies on two pillars. 
-First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the $K$ signals autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the separation condition on the support is held.
-Then, we use least-squares (LS) estimator to estimate the signals from their mixed autocorrelation.
-From pedagogical reasons, we start with the second stage of recovering signals from their autocorrelations.
-In this section we mainly discuss the uniqueness of the mapping from the autocorrelation to the signals.
-Concrete algorithms will be discussed in the next section.
+Our method for estimating the signals is a two-stages procedure. 
+First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the $K$ signal's autocorrelations.
+The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the separation condition on the support is met.
+Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelation.
+The precise recovery procedure we are using, based on nonconvex optimization, will be elaborated in the next section.
 
-For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions of a signal $z\in\mathbb{R}^W$, defined as
+\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
+
+For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
+$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
+\begin{equation*}
+a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
+\end{equation*}
+Explicitly, the first three autocorrelations are
 \begin{align} \label{eq:autocorrelations}
-a_z^1 &= \sum_{i=0}^{W-1} z[i], \nonumber\\
-a_z^2[\ell] &= \sum_{i=0}^{W-1-\ell} z[i]z[i+\ell], \nonumber\\
-a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{W-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
+a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
+a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
 \end{align}
 Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. 
+Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), the they are equivalent to the autocorrelation functions.
 
 A one-dimensional signal is determined uniquely by its third-order auto-correlation:
-\begin{proposition}
-	Suppose that $z[0]$ and $z[L-1]$ are non-zeros. Then, a signal $z\in\mathbb{R}^W$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\begin{proposition} \label{prop:uniqueness}
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzeros. Then, $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
 	\begin{proof}
@@
 		\end{equation*}
-		Then, from the third-order autocorrelation we can compute $z[k]$ for all $k=0,\ldots L-1$ by
+		Then, for all $k=0,\ldots L-1$,  we can compute $z[k]$  from the third-order autocorrelation
 		\begin{eqnarray}
@@
 \end{proposition}
-We note that the length of the signal can be easily derived from the second-order autocorrelation of the signal.
-Therefore, the assumption that $z[0]$ and $z[L-1]$ is met in practice.
+\noindent This result can be extended to any dimension.
+We note that the length of the signal can be easily derived from the length of the second-order autocorrelation of the signal.
+Therefore, the assumption that $z[0]$ and $z[L-1]$ are nonvanishing is met in practice.
 We also note that for one-dimensional signals, the second-order autocorrelation does not determined the signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-This is not the case for dimensions greater than one, in which almost all signals are determined uniquely from their aperiodic autocorrelations, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible,bendory2017fourier}.
+For dimensions greater than one, almost all signals are determined uniquely from their aperiodic autocorrelations, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
 The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However,  in order to determine the reflection symmetry ($Z_2$ symmetry), one needs to use the third moment.
+However,  in order to determine the reflection symmetry, one needs to use additional information, such as higher-order statistics.
 
-The heterogeneous case $K>1$ was explored for periodic autocorrelation functions.
-The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros.
-Therefore, the following results hold for our setup as well  \TODO{This part is wrong -- Email correspondence with Alex}.
-In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order autocorrelations determine  a finite list of $K$ generic signals when
-\begin{itemize}
-	\item $K=2$ when $L>1$,
-	\item $K=3$ when $L>12$,
-	\item $K=4$ when $L>18$,
-	\item $5\leq K\leq 15$ when $L\geq 6K-5$.	
-\end{itemize}
-The authors conjecture that for $K>15$, $L\geq 6K-5$ is enough. Recently, Joe told use that he has proven that there is unique mapping in the same regime.  
-This also holds for arbitrary weights $\gamma_i$ which are rational fractions.
+High-order autocorrelations have been used for a variety of tasks in signals processing, bla bla. In particular, \TODO{Here we should refer to Gianakis's paper}
 
-\TODO{Where we should refer to Gianakis's paper?}
+The uniqueness for $K>1$ was explored  for the related case of  periodic autocorrelation functions. Recall that the $k$th periodic autocorrelation of $z\in\mathbb{R}^L$ is given by
+\begin{equation*}
+b_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{W-1} z[i]z[(i+\ell_1)\mod L]\ldots z[(i+\ell_{k-1})\mod L].
+\end{equation*}
+If $z[n]=0$ for $n=L/2,\ldots L-1$, then  $b_z^k[\ell_1,\ldots,\ell_{k-1}] = a_z^k[\ell_1,\ldots,\ell_{k-1}]$. 
+In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order periodic autocorrelations determine  a finite list of $K$ generic signals if $L/6\gtrsim K$.
+Empirical evidences hints that this finite list includes only group symmetries~\cite{boumal2017heterogeneous}.
 
-We are moving forward to discuss the second question of how to estimate the autocorrelation of the signals from the data. 
-The analysis is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
+\subsection{Estimating autocorrelations from the data} \label{sec:estimating_ac}
+
+In order to estimate the mixed autocorrelation of the $K$ signals, we first compute the first $L$ entries of the data's autocorrelations.
+For the purpose of the analysis, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$.
+We define the ratio of the measurement occupied by each one of the signal by
 \begin{equation}
@@
 and $\gamma = \sum_{i=1}^K\gamma_i$. 
-Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-The main insight is that if $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
-\begin{align}
-\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
+Under the spacing constraint, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+The main pillar of this work is the following simple observation.
+If the support $s$ satisfies the spacing constraint of $L$ entries, then the first $L$ entries of the data autocorrelations converge to a mix of scaled versions of the signals autocorrelations:
+\begin{align} \label{eq:data_ac}
+\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \nonumber\\
 \lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
 \end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
-These relations are proved in Appendix~\ref{sec:autocorrelation_computation}.
-The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies.
-This means that given $M_1,\ldots,M_K$ and $\sigma^2$ and $K$ does not exceed the limit for uniqueness, the one can estimate the signals from the third-order autocorrelation of the data.
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
+These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
+The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a particular caution should be taken with the statistical dependencies of the noise entries.
+The relations~\eqref{eq:data_ac} imply that for $K=1$ and given $M$ and $\sigma$, one can estimate the signal for any noise level if $M$ is large enough.
+Next, we show that for $K=1$,  $M$ and $\sigma$ are also uniquely determined from the autocorrelations.
+
+An interesting consequence of our analysis is that, at least for $K=1$, the third autocorrelation of the data suffices to determine the signal. 
+The minimal order of data statistics that we use to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
+In methods which are based on detection and averaging, the number of signals occurrences  scales like $\sigma^2$.
+Taking the $k$th order autocorrelation function amplifies the variance of the noise by a factor of $k$.
+Therefore, the required number signal occurrences should scale like $\sigma^{2k}$  to retain some constant estimation error.
+Accordingly, in our  method, $M$ scales like $\sigma^6$.
+In Section~\ref{sec:numerics}, we show empirically the third-order autocorrelation suffices also for a mixture of $K>1$ signals without prior knowledge of the $M_i$'s and $\sigma$.
+
+%This means that given $M_1,\ldots,M_K$ and $\sigma^2$ and $K$ does not exceed the limit for uniqueness, the one can estimate the signals from the third-order autocorrelation of the data.
 In other words, the signals can be estimated in asymptotic estimation rate of $\sigma^6/N$.
 
-If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $M$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
+If the noise level $\sigma^2$ is known and  $K=1$, one can estimate $M/N$ from only the first two moments.
 \begin{proposition} \label{prop:gamma}
-	Let $K=1$. Then, 
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. Then, 
 	\begin{equation*}
-	\frac{M}{N} = \frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
+	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
 	\end{equation*}
 	\begin{proof}
-The relation is proved by plugging the definitions of the signal autocorrelations into the right-hand side of the equation~\eqref{eq:autocorrelations}. 	
+The proof follows plugging the explicit expressions of~\eqref{eq:data_ac} into the right hand side of the equality.
 \end{proof}
@@
 
+If we use third-order autocorrelation information, then it possible to estimate both $M/N$ and $\sigma$ simultaneously.
+In contrast to Proposition~\ref{prop:gamma}, this result does not come with explicit formula.
 \begin{proposition} \label{prop:gamma_sigma}
-	It is possible to estimate $M$ and $\sigma$ from the third moment.
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine $M/N$ and $\sigma$ uniquely for generic signal.
+If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any nonzero $x$.
 	\begin{proof}
@@
 \end{proposition}
-If we assume that $s$ is sparse, then by ignoring the separation condition, one can describe the generative process of $s$ as a Bernoulli process with parameter $M/N$.
-Therefore, in low \SNR  one can estimate the parameter that control this statistical process, although cannot estimate individual entries.
 
-Estimating $\sigma$ and $M$?
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduces the following.
+\begin{corollary}
+	For $K=1$, $N\to\infty$ and fixed $\sigma$, a generic signal obeying $x[0],x[L-1]\neq 0$, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions.
+If  $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any nonzero $x$.
+\end{corollary}
 
@@
 
+Here will come the 1D experiment with heterogeneity
+
 \subsection{Two-dimensional experiments}
 
-Solving RRR, and then 200 LS iteration on window of size $W$ and 500 iterations on window of size $L$.
+In this section, we provide the details of the 2D experiment shown in Figure~\ref{fig:example}.
+In the experiment, we generated a sequence of $767\times 10^3$ 2D images (``micrograph") of size $2000\times 2000$.
+Each micrograph had around $\sim 900$ signal occurrences (depends on the stopping criterion that we need to explain) and in total $M = 561\times 10^6$.
+The noise level was $\sigma=1$.
+
+To accelerate the experiment, we estimated only the first two autocorrelations of the signal.
+As mentioned in Section~\ref{sec:estimating_ac}, this data determines a 2D signal uniquely, up to possible reflection symmetry.
+In this experiment, we chose the correct reflection manually.
+To estimate the signal we used the Relax-Reflect-Reflect (RRR) algorithm, which is a known phase retrieval algorithm.
+Recall that the second-order autocorrelation is equivalent to the power spectrum of the signal.
+Starting form random initialization of size $(2L-1)\times(2L-1)$, its $k$th  iteration take the form of 
+ \begin{equation*}
+ x_k = x_{k-1} + \beta(P_2(2P_1(x_{k-1}) -x_{k-1}) - P_1(x_{k-1}), 
+  \end{equation*}
+ where $P_1$ is a projection that keeps the values of the  $L\times L$ entries in the upper-left corner and zeros out all other entries, $P_2$ is a projection that keeps the Fourier phase of $x_{k-1}$ and impose the correct Fourier magnitudes, and we set $\beta = 0.5$.
+The solution of the RRR scheme was used to initialized a LS estimation on the first two moments with signals of length $(2L-1)\times(2L-1)$ for the 200 iterations.
+Finally, we chose the $L\times L$ upper left corner and refined it using LS with 500 iterations.
 
 \section{Conclusion} 
-Here we conclude the paper: cryo -- EM, structured background, without separation, heterogeneity
-In particular, in cryo--EM, multiple projections of a molecule (signal), taken
-from unknown viewing directions, are recorded on two-dimensional detector
-array. Current algorithms try to detect these projections in a low SNR regime
-and then use them for the reconstruction process. Since the
-Then, the reconstruction problem is to detect these projection, and then use
-them to estimat
-The data acquired in both technologies is composed of multiple projections
-of a molecule (the signal), taken from unknown viewing direction, and drawn in
-high noise level. The reconstitution problem is then to estimate the molecule
-from this data.
+Here we conclude the paper. Points to mention;
+\begin{itemize}
+\item cryo -- EM
+\item  structured background 
+\item   without separation   	
+\item  sample complexity
+\end{itemize}
 
-A word on the sample complexity
+%In particular, in cryo--EM, multiple projections of a molecule (signal), taken
+%from unknown viewing directions, are recorded on two-dimensional detector
+%array. Current algorithms try to detect these projections in a low SNR regime
+%and then use them for the reconstruction process. Since the
+%Then, the reconstruction problem is to detect these projection, and then use
+%them to estimat
+%The data acquired in both technologies is composed of multiple projections
+%of a molecule (the signal), taken from unknown viewing direction, and drawn in
+%high noise level. The reconstitution problem is then to estimate the molecule
+%from this data.
 
@@
 
-To analyze the asymptotic behavior of the data autocorrelation functions, we consider one signal $K=1$.
+To analyze the asymptotic behavior of the data autocorrelation functions, we consider the case of one signal $K=1$.
 The extension to $K>1$ is straightforward by averaging the contributions of all signal with the appropriates weights, see~\cite{boumal2017heterogeneous}.
@@
 \end{equation}
-By assuming $M_N=\Omega(N)$, we also have $\gamma>0$.
+With a bit abuse of notation, $M_N$ means that $M$ is a function of $N$. Indeed, by assuming $M_N=\Omega(N)$, we deduce $\gamma>0$.
 We start by considering the first autocorrelation of the data
@@
 
-We proceed with the second moment for fixed $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
+We proceed with the second autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
 \begin{equation}
@@
 \end{equation}
-Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
+Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms  \TODO{to recheck indicies}
 \begin{equation}
@@
 \end{equation}
-Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and therefore converge to zero almost surely as $N\to\infty$.
+Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
 If $\ell=0$, 
@@
 \end{equation*}
-Writing explicitly in terms of signal and noise, this sum can be broken into eight partial sums.
-The first contains only signal terms and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+Writing explicitly in terms of signal and noise, the sum can be broken into eight partial quantities.
+The first contains only signal terms (does not see noise) and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
 Three other partial sums contain the product of two signal entries and one noise term.
-Since the noise is independent of the signal, then these terms go to zero almost surely.
+Since the noise is independent of the signal and has zero mean, these terms go to zero almost surely.
 
-We next analyze the contribution of triple product of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
+We next analyze the contribution of the term composed of triple products of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
 \begin{equation*}
@@
 For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
-For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each is a triple product of Gaussian variables with zero mean.
-Therefore, it is also converges to zero.
+For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each one is a triple product of Gaussian variables with zero mean and therefore has zero expectation.
 
 To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
-Most of these terms converges to zero almost surely because of interdependency between the noise entries.
-For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$.
+Most of these terms converge to zero almost surely because of interdependency between the noise entries.
+For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
 
@@
 
-We aim to prove that one can estimate both $\sigma$ and $M$ from the observed third moment.
-We will construct two independent quadratic equations of $M$ which do not depend on $\sigma$.
-This will let us estimate $M$.
-Given $M$, we will estimate $\sigma$.
+We aim to prove that one can estimate both $\sigma$ and $\beta = M/N$ from the observed first three moments.
+Using observed (measured) quantities, we construct two quadratic equations of $\beta$, independent of $\sigma$.
+Then, we show that these equations are independent and therefore $M$ is uniquely defined. 
+Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
+Throughout the proof, it is important to distinguish between observed and unobserved values. 
+to this end, we denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$ and $F_i$ for functions of the signal's autocorrelations.
 
-To ease notation, let $\beta=M/N$. Recall that $a_y^1 = \beta(\one^Tx)$ and  
+Recall that $a_y^1 = \beta(\one^Tx)$ and  
 and $a_y^2[0] = \beta(\|x\|^2+\sigma^2)$, where $\one\in\RL$ stands for vector of ones. Taking the product:
@@
 E_1 &:= (\beta(\one^Tx))(\beta(\|x\|^2+\sigma^2)) \\
-& = \sigma^2a_y^1 + \beta^2\tau,
+& = \sigma^2a_y^1 + \beta^2F_1,
  \end{split}
 \end{equation}
-where $\tau := L\left(\sum_{j=1}^{L-1}(a_x^3[j,0]+a_x^3[0,j] )+\sum_{j=0}^{L-1}a_x^3[0,0]\right)$. Next, we can estimate from $a_y^3$
+where $F_1 := L\left(a_x^3[0,0] + 2\sum_{j=1}^{L-1}(a_x^3[j,j]\right)$. 
+The terms of $F_1$ can be also estimated from $a_y^3$ with bias:
 \begin{equation} \label{eq:E2}
-E_2:= \beta \tau + 3L\sigma^2a_y^1.
+E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
 \end{equation}
 Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
-\begin{equation}
-E_2\beta -3L\sigma^2a_y^1 = E_1-\sigma^2a_y^1.
+\begin{equation} \label{eq:E12}
+E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
 \end{equation}
-Now, recalling from Proposition~\ref{prop:gamma}
+Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}
 \begin{equation} \label{eq:sigma2}
-\sigma^2 = a_y^2 - (a^1_y)^2/\beta, 
+\sigma^2 = a_y^2 - (a^1_y)^2/\beta. 
 \end{equation} 
-where we use $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$.
-Rearranging the equations, we then get the quadratic equation
+Plugging into~\eqref{eq:E12} and rearranging we get 
 \begin{equation} \label{eq:quad1}
@@
 \begin{align*}
-\mathcal{A} &= E_2, \\ 
-\mathcal{B} &= -(E_1 + (3L-1)a_y^1a_y^2), \\
-\mathcal{C} &= (3L-1)(a_y^1)^3.
+\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
+\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1a_y^2  , \\
+\mathcal{C} &= -(a_y^1)^3.
 \end{align*}
+Importantly, these coefficients are are observable quantities.
 
-We are now proceeding to derive the second quadratic equation. We notice that \begin{equation} \label{eq:E3}
-E_3  = (a_y^1)^3 = \beta^3 \upsilon,
+We are now proceeding to derive the second quadratic equation. We notice that 
+\begin{equation} \label{eq:E3}
+E_3  = (a_y^1)^3 = \beta^3 (\one ^Tx)^3   = \beta^3 F_2,
 \end{equation}
-where \TODO{to check} $$\upsilon = a_x^3[0,0] + 3\sum_{i=1}^{L-1}a_x^3[i,i] + 3\sum_{i=1}^{L-1}(a_x^3[i,0]+a_x^3[0,i]) + 6\sum_{1\leq i \leq j\leq L-1}a_x^3[i,j].$$
-On the other hand, from $a_y^3$ we can directly estimate
+where \TODO{to verify}
+\begin{equation*}
+F_2 =  a_x^3[0,0] + 3\sum_{i=1}^{L-1}a_x^3[i,i] + 3\sum_{i=1}^{L-1}a_x^3[0,i] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+\end{equation*}
+On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
 \begin{equation} \label{eq:E4}
-E_4 = \beta\upsilon + 9L\sigma^2a_x^1.
+E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
 \end{equation}
-Now, by multiplying both sides by $\beta^2$ and using~\eqref{eq:E3}, we get 
-\begin{equation} \label{eq:E4}
-\beta^2E_4 =  E_3  + 9L\sigma^2a_x^1.
-\end{equation}
-Plugging~\eqref{eq:sigma2} and rearranging the equation, we get a second quadratic equation independent of $\sigma$:
+Taking the ratio:
+\begin{equation*} 
+\frac{E_4}{E_3} = \frac{1}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_3}, 
+\end{equation*}
+we conclude:
+\begin{equation*}
+\sigma^2 = \frac{E_4}{a_y^1(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
+\end{equation*}
+Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
 \begin{equation} \label{eq:quad2}
@@
 \begin{align*}
-\mathcal{D} &= E_4 - 9La_x^1a_y^2, \\ 
-\mathcal{E} &= 9La_x^1(a_y^1)^2, \\
-\mathcal{F} &= -(a_y^1)^3.
+\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1(6L-3)}, \\ 
+\mathcal{E} &= -(a_y^1)^2, \\
+\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
 \end{align*}
@@
 To this end, it is enough to show that the ratio between the coefficients is not the same.
-using~\eqref{eq:E1}, we have 
+From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
 \begin{equation*}
-\frac{\mathcal{B}}{\mathcal{C}} = \frac{-(E_1 + (3L-1)a_y^1a_y^2)}{(3L-1)(a_y^1)^3} = -\frac{a_y^2[0]}{(3L-1)(a_y^1)^2} - \frac{a_y^2}{(a_y^1)^2}.
+\frac{\mathcal{B}}{\mathcal{C}} = \frac{-E_1 + (2L+1)(a_y^1)^3 + a_y^1a_y^2}{-(a_y^1)^3} = \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - a_y^2}{(a_y^1)^2}.
 \end{equation*}
-In addition, 
+In addition, using~\eqref{eq:E3}
 \begin{equation*}
-\frac{\mathcal{E}}{\mathcal{F}} = -\frac{9La_x^1}{a_y^1}. 
+\frac{\mathcal{E}}{\mathcal{F}} = -\frac{(6L-3)(a_y^1)^3}{E3} = 3 - 6L . 
 \end{equation*}
+
 Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
 \begin{equation*}
-\frac{a_y^2[0]}{(3L-1)(a_y^1)^2} + \frac{a_y^2}{(a_y^1)^2} = \frac{9La_x^1}{a_y^1}. 
+a_y^2[0] - (2L+1)(a_y^1)^2 - a_y^2 = (a_y^1)^2(3-6L)
 \end{equation*}
-Rearranging the equation, we get 
+Rearranging the equation and writing in terms of $x$ we get 
+\begin{equation} \label{eq:cond}
+4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
+\end{equation}	
+For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
+More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
 \begin{equation*}
- a_y^2[0] + (3L-1)(a_y^1)^2 - 9La_x^1a_y^1=0.
+\beta \geq \frac{1}{4(L-1)},
 \end{equation*}
-For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent.
+the condition~\eqref{eq:cond} cannot be satisfied for any signal.
 

### 2018-04-07 TEX/draft2.tex
updated notes

--- 2017-11-14 TEX/draft2.tex
@@
-\documentclass[journal]{IEEEtran}
+\documentclass[english,11pt]{article}
 
@@
 \usepackage{url}
-
-\usepackage{algorithm}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{mathtools} 
+\usepackage[margin=1.2in]{geometry}
 
@@
 \numberwithin{equation}{section}
-\numberwithin{figure}{section}
+%\numberwithin{figure}{section}
 \theoremstyle{plain}
@@
 
+\newcommand{\reals}{\mathbb{R}}
 \newcommand{\RL}{\mathbb{R}^L}
+\newcommand{\CL}{\mathbb{C}^L}
 \newcommand{\RN}{\mathbb{R}^N}
-\newcommand{\CL}{\mathbb{C}^L}
-\newcommand{\CN}{\mathbb{C}^N}
-\newcommand{\RW}{\mathbb{R}^W}
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
@@
 \newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\E}[1]{\mathbb{E}\left\{{#1} \right\}}
-\newcommand{\order}[1]{\mathcal{O}\left({#1} \right)}
-\newcommand{\xz}{x_{\textrm{zp}}}
-\newcommand{\DFT}{\operatorname{DFT}}
-\newcommand{\SNR}{\operatorname{SNR}}
 \newcommand{\hx}{\hat{x}} 
+\newcommand{\one}{\mathbf{1}} 
+\newcommand{\SNR}{{\textsf{SNR}}}
 
@@
 
-%\begin{frontmatter}
+\title{Estimation below the detection limit}
 
-\title{Multireference alignment meets blind deconvolution}
 \author{Tamir Bendory}
@@
 
-\begin{IEEEkeywords}
-	Blind deconvolution, multireference alignment, bispectrum, cryo-EM
-\end{IEEEkeywords}
+\section{Introduction}
 
-\section{Introduction} \label{sec:introduction}
+In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a data sequence $y$\TODO{This is the most important sentence of the paper, we need to polish it up}.
+The data may also contain background information---independent of the signals---modeled as noise.
+For one-dimensional signals, the data sequence can be thought of as a 
+long time series and the $K$ signals as repeated short events.  
+This model appears in many applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+In the last part of this manuscript, we also propose to interpreted this estimation problem as a toy model for the problem of single particle reconstruction using cryo-electron microscopy (cryo--EM).
+A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:model}.
 
-Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see   \cite{jefferies1993restoration,tong1994blind,chan1998total,campisi2016blind,kundur1996blind,levin2011understanding,shalvi1990new,levin2009understanding,krishnan2011blind,ayers1988iterative,michaeli2014blind,lin2005relevant,abed1997blind}, just to name a few.
-In blind deconvolution, we aim at estimating  a signal from its convolution with an unknown kernel.
-Clearly, without additional information, the problem is ill-posed.
+Figure~\ref{fig:XC_example} shows a simple example of data sequences with  one signal ($K=1$) that appears twice.
+The upper row presents the data without noise, in the left panel, and its cross-correlation with the signal itself in the right panel.
+The cross-correlation exhibits two peaks corresponding to the signal's locations in the data.
+%Even if we add a small amount of noise and considering more than one signal ($K>1$), estimating the signals remains a painless task. 
+%In this scenario, standard detection and clustering algorithms can locate and cluster the copies of the signals that can be then averaged within each class.  
+In  the middle row, the same data is shown, now contaminated with i.i.d.\ Gaussian noise with zero mean and standard deviation of $\sigma=0.7$. 
+While it is harder to observe the signal occurrences in the left panel, the cross-correlation still produces fairly adequate estimates of the signal's locations.
+In practice one usually does not possess a precise template of the signal to be recovered, however, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
+The bottom panels show the same data swamped in  
+i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$. In this  low signal--to--noise (\SNR) regime, 
+detection of individual signal occurrences is impossible, 
+even if the true signal is known. 
+This phenomenon---explained in more detail in Section~\ref{sec:model}--raises the question: 
+\medskip 
+\\
+\emph{Can we estimate the signals accurately without detecting their individual occurrences? }
+ \\
 
-In this paper, we consider a particular case, in which one signal is of finite support, while the other is a binary sparse signal. Let us define the (zero-padded) signal 
-$$\xz  = [x, \underbrace{0,0,\ldots,0}_{N-L \text{ zeros}}]\in\RN,\quad N\gg L,$$
-and a binary signal $s\in\{0,1\}^N$. Then, our goal is to estimate $x$ from \begin{equation} \label{eq:blind_deconvolution}
-y = \xz \ast s + \varepsilon,
-\end{equation}
-where $\varepsilon$ is an i.i.d.\ normal noise $\varepsilon$ with mean zero and variance $\sigma^2$.
-As can be seen, the measurement $y\in\RN$ is composed of repetitions of an underlying signal $x\in\RL$, located at different positions. So, we can also write the model as  
-\begin{equation}
-y[n] = \sum_{i=1}^K \xz [n-n_i] + \varepsilon[n], 
-\end{equation}
-where the $n_i$'s are the non-zero values of $s$.
+In this work, we provide a positive answer to this question. For one signal ($K=1$), we prove that in the asymptotic regime in which the signal appears
+infinitely many times in the data, and under a spacing condition, one can estimate the signal \emph{to any desired accuracy in any $\SNR$ level}.
+We show empirically that the same holds true for multiple signals if $K$ is not too large.
+\TODO{Do we want a sentence like: Based on  recent results on the multireference alignment problem, we conjecture that it remains true as long as $K \lesssim L/6$.
+?}
 
-While most works on blind deconvolution tries to estimate both unknown signals (see Section~\ref{sec:blind_deconvolution}), in most cases, the goal is merely to estimate one of the signals.
-For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the main goal is only to sharpen the image.
-In~\eqref{eq:blind_deconvolution}, the signal $s$ is referred to as the latent or hidden variable of the problem.
-Our goal is to estimate  $x$ and we focus  on the low signal--to--noise ratio ($\SNR$) regime.
-As will be demonstrated, in this case, estimating $s$ is impossible, even if $\xz$ is known.
-However, we show, maybe surprisingly, that one can estimate $x$ accurately in some cases.
-We support this statement by theoretical analysis and numerical  experiments.
+Our framework is based on autocorrelation analysis.
+In a nutshell, the method consists of two stages.
+First, we estimate a mixture (linear combination) of the low--order autocorrelation functions of the signals from the data.
+These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by at least $L-1$ entries and  each signal appears ample number of times \TODO{?} in the data.
+There is no need to detect individual occurrences.
+Furthermore, we do not assume the knowledge of the number of signal occurrences $M$ and the noise level.
+In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS).
+Section~\ref{sec:autocorrelation} elaborates on the technique and proves some of its properties, while Section~\ref{sec:numerics} provides numerical demonstrations.
 
-Figure~\ref{fig:example} shows examples of the problem in different noise levels.
-In the example, the signal $x$ appears twice in $y$ so that $\| s \|^2 = 2$.
-The first row demonstrates a high $\SNR$ regime with $\sigma = 0.1$.
-As can be seen, in this regime  the problem is rather easy.
-In this case, one can easily the support of $s$ (namely, the repetition of $x$ in $y$) by simple detection algorithms.
-This is demonstrated by the correlation function between $\xz$ and $y$ that exhibits two unmistakable peaks in the support of $x$.
-Once several copies of the signal were detected and cropped from $y$, then one can  improve the $\SNR$ by averaging.
-We are interest in the more challenging regime of high noise level, as exemplified in the bottom row ($\sigma  = 3$)
-in which the signal is completely swamped in the noise, and one cannot detect the signal's appearances.
-In this case, one need to use the prior information that the signal appears many times across the measurement.
-
-\begin{figure*}
-	\begin{center}
-	\includegraphics[scale = .5]{example}
-	\end{center}
-\caption{The left column presents the clean data and the measurement in different noise levels.
-In this example, a rectangular signal of length $L=21$ appears twice in a measurement of length $N=336$ with different noise levels.
-Note to the different scale of the y-axis.
-The right column presents the correlation between the rectangular signal and the measurement for the associated problems.
-}
-\label{fig:example}
-\end{figure*}
-
-Our approach for this blind deconvolution problem is based on  tools that were developed for the multireference alignment (MRA) problem.
-MRA is the problem of estimating a signal from its circularly-shifted noisy measurements~\cite{bandeira2014multireference,bendory2017bispectrum}
- In Section~\ref{sec:mra}, we survey recent works in this field.
-We use a recent suggestion to estimate the signal from feature that are invariant under cyclic-translation~\cite{bendory2017bispectrum}.
- In essence, our method is based on \emph{approximate reduction} of the blind deconvolution problem into the MRA model.
-This is done be splitting $y$ into shorter windows and treat them as the MRA measurements.
-If each window contains exactly  one signal, then the problem reduces exactly the MRA problem.
-However, this is not the case.
-Some windows contain only noise, while others contain both noise and parts of a signal.
- We analyze the estimation rate of this method and its deviation from the MRA model.
-
- A motivation for this work arises from the cryo--electron microscopy (EM) problem.
-Cryo--EM received a great deal of attention in structural biology in recent years as it allows visualizing molecules that were not stained in any way, showing them in their native environment.
-In Section~\ref{sec:cryoEM} we draw the connections between  blind deconvolution and the cryo--EM problem.
-
- The outline of this paper is as follows. In Section~\ref{sec:literature} we introduce background  on blind deconvolution (Section~\ref{sec:blind_deconvolution}) and MRA (Section~\ref{sec:mra}).  
- In Section~\ref{sec:cryoEM} we discuss the connection with the  cryo--EM problem.
-In Section~\ref{sec:algorithm} we introduce the algorithm and analyze it in Section~\ref{sec:analysis}.
-Section~\ref{sec:experiments} is devoted for numerical experiments.
-Section~\ref{sec:conclusion} concludes the manuscript.
-
-\section{background} \label{sec:literature}
-
-In this section, we introduce the two main ingredients of this work, blind deconvolution and MRA. Then, we draw connections  with the cryo--EM problem.
-
-\subsection{Blind deconvolution} \label{sec:blind_deconvolution}
-
-Blind deconvolution is the problem of recovering a signal from its convolution with an unknown kernel $h$. That is, we aim to recover  $x$ from
-\begin{equation}
-y = x\ast h,
-\end{equation}
-where both $x$ and $h$ are unknown. In the Fourier domain, it takes the form of 
-\begin{equation}
-Fy = Fx \odot Fh,
-\end{equation}
-where $Fz$ stands for the Fourier transform of $z$ and $\odot$ for entry-wise product.
-Clearly, without prior information of the signal, it is impossible to estimate the signal.
-For instance, even if we assume that the $\DFT$ of both signals are non-vanishing, then $Fy$ remains unchanged if we replace $(Fx)[k],(Fh)[k]$ by $a(Fx)[k],\frac{1}{a}(Fh)[k]$ for any $a\in\CN\backslash\{0\}$ and any $k$.
-
-The blind deconvolution  has been analyzed recently with a various convex and non-convex algorithms.
-These works assume that the signal lies in a known  subspace spanned by vectors with random entries~\cite{ahmed2014blind,li2016rapid,ling2017blind}.
-A somewhat more related line of works assume sparsity in a random linear subspaces~\cite{lee2017blind,ling2015self,chi2016guaranteed}.
-The papers 
-\cite{choudhary2014sparse,li2016identifiability,kech2017optimal,li2015unified} deals with the fundamental question of identifiability of the problems, but none of these paper consider our setup, namely, when the sparse signal is in the canonical basis.
-
-Our problem is very different from all previous works in at least two ways. First, 
-while we do assume that one of the signals is sparse,  our goal is to estimate the other signal.
-We do not claim that we can estimate the sparse signal.
-Second, we are mainly care of accurate estimation of $x$ in the low $\SNR$ regime.
-In this regime, it seems that estimating the sparse signal $s$ is impossible.
-This is contrast to previous works that focused on the high $\SNR$ regime.
-
-We briefly mention that the deconvolution problem, namely, when the kernel is assumed to be known, has been analyzed throughly in recent years under sparsity constraints~\cite{bendory2016robust,bendory2017robust,bendory2016stable,boyer2017adapting,bernstein2017deconvolution,de2012exact,azais2015spike,duval2015exact,duval2015sparse}.
-Nevertheless, the problem under consideration is essentially different  from two reasons.
-First, of course, we consider the blind setting when the kernel is unknown.
-Second, these works considered the recovery of sparse signal, with Gaussian-like kernel.
-In our problem, the convolution itself kernel is sparse, while we aim to recover a general signal.
-.
-
-\subsection{Multireference alignment} \label{sec:mra}
-
-Our approach for blind deconvolution is based on reducing the problem, approximately, to an MRA problem.
-In MRA, we aim at estimating a signal $x\in\RL$ from its circularly shifted noisy measurements
-\begin{equation} \label{eq:mra}
-y_j = R_{r_j}x + \varepsilon_j, \quad j = 1,\ldots,N,
-\end{equation}
-where $R_{r}$ translates a signal by $r$ locations, namely, $(R_rx)[i] = x[(i-r)\mod L]$, and $\varepsilon$ is an i.i.d.\ normal noise with mean zero and variance $\sigma^2$.
-This problem finds applications in radar, image processing and structural biology~\cite{zwart2003fast,foroosh2002extension,diamond1992multiple}.
-The algorithmic and statistical characterizations of this problem have been analyzed thoroughly in the last couple of years, see~\cite{bendory2017bispectrum,bandeira2014multireference,bandeira2017optimal,perry2017sample,boumal2017heterogeneous,abbe2017multireference,abbe2017sample}.
-
-In this work, we exploit the algorithmic framework proposed in~\cite{bendory2017bispectrum}.
-In order to estimate the signal, this paper suggests to use features of the signal that are invariant under cyclic translation.
-Apparently, three moments are required.
-The first is mean of the signal, denoted by $\mu_x$, or, equivalently, it DC component $(Fx)[0]$.
-The second feature is the power spectrum of the signal $P_x[k] = \vert (Fx)[k]\vert^2$ for $k=0,1,\ldots L-1$.
-Since in general one cannot estimate  a signal from its power spectrum~\cite{bendory2017fourier}, one needs a third order feature.
-This third order feature, called bispectrum, is defined as~\cite{tukey1953}
-\begin{equation}
-B_x[k_1,k_2] = (Fx)[k_1]\overline{(Fx)[k_2]}(Fx)[k_2-k_1].
-\end{equation}  
-These features can be estimated directly from the measured data by
-\begin{align} \label{eq:moment_estimation}
-\frac{1}{N}\sum_{i=1}^N\mu_{y_j}  &\,\to \, \mu_x, \nonumber\\
-\frac{1}{N}\sum_{i=1}^NP_{y_j}  &\,\to \, P_x + L\sigma^2, \\
-\frac{1}{N}\sum_{i=1}^NB_{y_j}  &\,\to \, B_x + \mu_x\sigma^2L^2A,  \nonumber
-\end{align} 
-where $A$ is a known deterministic matrix.
-Therefore, by proper debiasing, one can get a reliable estimating of these features.
-For large enough $\sigma$, the variance of the estimators  is dominated by the bispectrum and thus goes as $\sigma^6/N$.
-This estimation rate is optimal under the assumption that distribution of translations is uniform~\cite{bandeira2017optimal}.
-If the distribution is non-uniform, then one can do better using only the first two moments, see~\cite{abbe2017multireference}.
- Given enough measurements, one can obtain reliable estimation of the features, and then to estimate the underlying signal, up to cyclic translation, using a variety of algorithms~\cite{bendory2017bispectrum}.
-In this work, we use a simple non-convex least-squares estimator....
-\TODO{Need to see what do we actually solve...}
-
-\subsection{Connections with the cryo--EM problem} \label{sec:cryoEM}
-
-This work is partially motivated by the imaging
-technique called single particle cryo--EM, enabling the visualization of molecules at near atomic resolution~\cite{bartesaghi20152,sirohi20163}.
-Cryo--EM gained a lot of popularity in recent years in the structural biology community.
-As a result, Dubochet, Frank and Henderson were recently awarded the
-the Nobel prize for their contribution in the development of this technique~\cite{nobel}.
-
-In cryo--EM, many samples of a molecule are frozen in a thin sheet of ice. 
-An electron beam then passes through the ice and the samples  and recorded by an array of detectors. Cryo--EM contains several such images, which are
-called \emph{micrographs}. Each micrograph  contains many two-dimensional (2D) tomographic projections of the samples. 
- The  cryo--EM problem is then to estimate the molecules from the micrographs. This process is illustrated by in Figures~\ref{fig:cryo-EM} and~\ref{fig:cryo-EM-problem}.
-
-Compared to more traditional tomographic methods, like computerized tomography (CT), the cryo--EM problem arises two main challenges.
-First, the 3D orientation of each sample is unknown since the samples are rapidly frozen in the ice sheet.
-The experimentalist does not have control over these orientations.
-Second, the $\SNR$ in each projection is very low since the electron dosage must be restricted to limit  radiation damage to the molecules.
-In real cryo--EM data sets, there are some additional challenges, like the contrast transfer function of the microscope that corrupts the acquired image.
+Interestingly, expectation-maximization (EM)---a popular framework for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem, even if the number of signal occurrences $M$ is known and $K=1$.
+In particular, in each iteration, EM assigns probabilities to all possible combinations of positioning the current signal estimate in $M$ locations on $\mathbb{Z}_N$, resulting in $O(N^M)$ possibilities (even when excluding forbidden combinations due to the spacing constraint).
 
 \begin{figure}
-	\begin{center}
-		\includegraphics[scale = .4]{cryoem-eps-converted-to}
-	\end{center}
-	\caption{A schematic draw of the micrograph generation. Courtesy of ?}
-	\label{fig:cryo-EM}
+		\centering
+		\includegraphics[scale=0.5]{XC_example}
+		\caption{ The upper left panel shows a data sequence of length $N=80$ with one rectangular signal of length $L=11$ that appears twice.
+In the second and third rows of the left column, a Gaussian noise with mean zero and standard deviation $\sigma=0.5$ and $\sigma=3$ was added, respectively.
+The panels in the right column present the cross-correlation of the data with the true rectangular signal.
+Note to the different scales in different panels.
+}
+    	\label{fig:XC_example}
 \end{figure}
 
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale = .35]{cryoem-problem-eps-converted-to}		
-	\end{center}
-	\caption{The cryo--EM problem: estimating a molecule from the micrograph. Courtesy of ?}
-	\label{fig:cryo-EM-problem}
-\end{figure}
+%
+%This work is primely motivated by cryo-electron microscopy (cryo--EM), which is an innovative  single particle reconstruction technology.
+The acquired data in a cryo-EM experiment is contaminated with high noise levels.
+Therefore, any molecule reconstruction algorithm must take  the challenging $\SNR$ level into account.
+In the last part of this manuscript, we draw connections with the estimation problem under consideration and the cryo--EM problem.
 
-The first stage of a cryo--EM reconstruction algorithm is the so called \emph{particle picking} stage.
-In this stage, the projections are detected in the micrographs, and then cropped to a series of 2D images.
-Many algorithms were proposed to this detection problem based on support vector machine classifiers, deep learning and template matching and more; see for instance \cite{frank1983automatic,scheres2015semi,arbelaez2011experimental,zhu2016deep}.
- The most popular techniques are based on the latter, where the templates can manually or automatically selected.
-The underlying idea is that the cross-correlation  should be high in the presence of a signal in the template.
-However, this is not true anymore in the presence of high noise level, even if the signal itself is known, as demonstrated in Figure~\ref{fig:example}.
-An illuminating examples are given in~\cite{shatsky2009method,bandeira2015non}, where the famous picture of Albert Einstein is used to match pure noise and rotated images of the mathematician  Hermann Weyl.
+\section{Model and related literature}  \label{sec:model}
 
-After the particle picking, ideally, one gets a set of measurements of the form 
-\begin{equation} \label{eq:cryo-em}
-y_j = \mathcal{P}( g_j\circ x) + \varepsilon_j,\quad j=1,\ldots,N, 
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
+A plain way to present the forward model is as a mixture of blind deconvolution problems between binary signals and the target signals
+\begin{equation} \label{eq:model}
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
 \end{equation}
-where $x$ is the three-dimensional (3D) molecule to be estimated,  $g_j\in SO(3)$ are unknown 3D rotations that act on the molecule and $\mathcal{P}$ is a linear tomographic projection.
-This model has been analyzed theoretically from different point--of-views~\cite{bandeira2015non,hadani2011representation}.
-The MRA model~\eqref{eq:mra} can be interpreted as a simplification of the model~\eqref{eq:cryo-em}, where the unknown cyclic-shifts correspond to the unknown rotations (but there is no analog for the projection operation).
+%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
+Each  $s_i\in\{0,1\}^N$ is associated with the position of the occurrences of the corresponding $x_i$. Let $\mathcal{S}_i$ denotes the set of  the nonzero
+ values of $x_i$ and assume that the all $\mathcal{S}_i$'s are disjoint. The union of supports is denoted by $s = \sum_{i=1}^Ks_i$ and similarly $\mathcal{S} = \cup \mathcal{S}_i$. 
+The cardinality of the sets are denoted by $\vert \mathcal{S}_i\vert = M_i$ and $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.  Neither the $M_i$'s nor $M$ are assumed to be known.
 
-In practice, particle picking algorithms are far from being optimal, mainly because the high noise level prevents reliable detection.
-One result is that the cropped images are usually not centered,  and therefore an unknown 2D translation should be added to the model~\eqref{eq:cryo-em}.
-In addition, many samples in the micrograph are non detected or ignored.
-After the particle picking stage, the molecule is estimated from the 2D images, where the most popular algorithms are based on expectation--maximization (see for instance~\cite{scheres2012relion}).
-Other techniques, such as the common-lines\cite{van1987angular,singer2011three} method or auto-correlation analysis~\cite{kam1980reconstruction,levin20173d}, can be used for ab initio modeling.
+In order to estimate the mixture of signals autocorrelations, we assume that the support of $s$ is not clustered. In particular, 
+\begin{equation} \label{eq:spacing}
+\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
+\end{equation}
+The goal of the problme is to estimate $x_1,\ldots,x_K$ from $y$.
 
- Our model can be seen as a highly simplified cryo--EM model, where $y$ corresponds to the micrograph and the signal repeated $x$ to a  ``one-dimensional molecule" (the tomographic projection $\mathcal{P}$ does not appear in the model).
-We are interest in the question whether we can estimate the signal $x$, even if the $\SNR$ is so low that we cannot detect the locations of $x$, in $y$.
-In the perspective of the cryo--EM problem.
-the success to estimate the signal in the very low SNR regime may indicate that the molecule can be estimated directly from the cryo--EM micrographs, even if the SNR is so low that particle picking algorithm work poorly.
+Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+To make the problem well-posed, we must  assume some prior knowledge or  structure. 
+In our case, the prior information is that $s$ is a binary signal that satisfies~\eqref{eq:spacing}. 
+Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
+where the focus is on high $\SNR$ regimes.
 
-  %In addition, most particle picking algorithms throw away many particles since they fail to detect them.
-Hence, a necessary condition for the success of such algorithm is that the noise level would low enough so that detection would be possible.
+An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
+The  $s_i$'s  are referred to as \emph{nuisance  variables}.
+Indeed, in many blind deconvolution applications the sole purpose is to estimate one of the unknown signals.
+For instance, in image deblurring, both the blurring
+kernel and the high-resolution image are unknown, but the primary goal is only
+to sharpen the image.
 
-\section{Algorithm} \label{sec:algorithm}
+If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating $s$ is impossible.
+To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
+That is to say, we get a series of windows, each one contains a signal at unknown location.
+Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
+However, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
+As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals themselves, despite the impossibility of detecting their individual occurrences.
 
-The blind deconvolution algorithm is inspired by the recent MRA approach using translation invariant features proposed in~\cite{bendory2017bispectrum}.
-The algorithm requires setting a parameter $W\in\mathbb{N}$ obeying $W>L$  which is the length of the \emph{analysis window}.
-We assume henceforth, to ease notation, that $W$ divides $N$.
-The algorithm begins with splitting the measurement $y\in\RN$ into a series of analysis windows $y_i\in\mathbb{R}^W,\,i=1,\ldots,N/W$, where  
-\begin{equation} \label{eq:analysis_window}
-y_i[n] = y[(i-1)W + n] , \quad n=1,\ldots,W. 
+For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+\begin{eqnarray}
+y = x\ast w + \varepsilon,  
+\end{eqnarray} 
+where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
+%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
+The goal of this problem is to estimate $x$ (identify the system). The question of identifiability of $x$ under
+this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
+model in the  case of a single signal ($K = 1$).
+
+Likelihood-based methods seek to maximize the likelihood function for $x$,
+given the observed signal $y$. Solving this optimization exactly is typically
+intractable, and so heuristic methods are used instead. One proposed heuristic
+ is to use Markov Chain Monte Carlo (MCMC); in special
+cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
+The EM method is based upon a certain ``forward-backward'' procedure
+used in hidden Markov models, described in~\cite{rabiner1989tutorial}. \TODO{We need to explain}
+Other problems solve for parameterized models of $x$; for instance, see~\cite{andrieu2001bayesian}. 
+That same paper also considers multiple distinct signals $x$, as in our heterogeneity framework ($K>1$). Their proposed
+solution is an MCMC algorithm designed for their specific parametrized problem.
+
+Because likelihood methods are computationally expensive, methods based
+on recovery from moments and cumulants, which are akin to our method, have
+also been previously used for system identification. The question of identifiability
+of $x$ from third-order statistics with non-Gaussian $w$ was considered in~\cite{lii1982deconvolution}. \TODO{how is it different from bispectrum inversion?}
+Methods using the third- and fourth-order cumulants are described in~\cite{giannakis1989identification,tugnait1984identification}.
+
+\section{Autocorrelation analysis}   \label{sec:autocorrelation}
+
+Our method for estimating the signals is a two-stage technique. 
+First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
+The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
+Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
+In this section we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
+
+\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
+
+For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
+$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
+\begin{equation} \label{eq:ac_general}
+a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
 \end{equation}
-By assumption, there are exactly $N/W$ windows.
-Of course, one can easily modify the algorithm using overlapping windows, however, our numerical experiments indicate it does not improve the numerical performance.
-For each window, we then compute its first three translation-invariant features, namely, mean, power spectrum and bispectrum, and then  average them over all windows according to~\eqref{eq:moment_estimation}.
-Finally, once we estimated these features, we look for a signal $\hat{x}\in\mathbb{R}^W$ that is consistent with the data by solving ??
+Explicitly, the first three autocorrelations are
+\begin{align} \label{eq:autocorrelations}
+a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
+a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
+\end{align}
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. 
+Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
 
-Recall that the current estimate $\hat{x}$ is a signal of length $W$, whereas the underlying signal of length $L$.
-Ideally, it is cyclic-shifted version of $x$, padded with $W-L$ zeros.
- To crop the signal correctly, we simply search for the  segment of length $L$ with maximal energy.
-Formally, let  $T_\ell:\RW\to\RL$ be the operator that takes $L$ consecutive entries of the signal, starting at $\ell$.
-The signal is treated as periodic.
-Then, by letting
+A one-dimensional signal is determined uniquely and stably by its third-order auto-correlation as proven in the following simple proposition.
+\begin{proposition} \label{prop:uniqueness}
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzeros. Then:
+	\begin{itemize}
+		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
+        \item \textbf{Finite sensitivity:} 	Suppose that  $a_z^3[k,L-1]$ can be estimated up to  perturbation $\upsilon$ and let $\hat{z}[k]$ be an estimator of $z[k]$.
+If $\vert z[0]z[L-1]\vert \geq \delta>0$, then $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
+	\end{itemize}
+	\begin{proof}
+		By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
+		Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
+		\begin{equation*}
+		a_z^3[k,L-1] = z[0]z[k]z[L-1].
+		\end{equation*}
+		If we measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$, then 
+		\begin{equation*}
+		\hat{z}[k] = \frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+		\end{equation*} 
+	\end{proof}
+\end{proposition}
+
+A few remarks are in order. First, this result carries through to signals of any dimension.
+Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W>L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Third, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ asymptotically.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+Finally, while Proposition~\ref{prop:uniqueness} shows only finite sensitivity, in practice LS estimator is robust to additive noise; see Section~\ref{sec:numerics}.
+This is compatible with results in related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+
+Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
+Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However,  in order to determine the reflection symmetry, one needs to use additional information.
+
+The invertibility of the autocorrelations for $K>1$ was explored  for the related case of  periodic autocorrelation functions.
+Recall that the  periodic autocorrelations are defined similarly to~\eqref{eq:ac_general}, with two differences: the sum goes to $L-1$ and all indices should be taken modulo $L$.
+If $z[n]=0$ for $n=L/2,\ldots L-1$ (``zero-padded''), then the periodic and aperiodic autocorrelation coincide.
+In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order periodic autocorrelations determine  a finite list of $K$ generic signals if $L/6\gtrsim K$.
+Empirical evidences hints that this finite list includes only group symmetries, at least as long as $K\leq\sqrt{L}$~\cite{boumal2017heterogeneous}.
+
+\subsection{Estimating autocorrelations from the data with a single signal $K=1$} \label{sec:estimating_ac_k1}
+
+We first consider the problem of estimating the autocorrelations of a single signal from the data. 
+All the main concepts carry through for $K>1$ as will be shown in the next section.
+
+In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
+For the purpose of the analysis, we consider  the asymptomatic regime where $M,N\to\infty$, while preserving fixed ratio. 
+Specifically, we define the ratio of the measurement occupied by  the signal as
 \begin{equation}
-\ell_{\max} =  {\arg\max}_{\ell=0,\ldots,W-1} \|T_\ell\hat{x} \|_2,
+\gamma = \frac{M L}{N}.
 \end{equation}
-we map
-\begin{equation} \label{eq:align}
-\hat{x}\gets T_{\ell_{\max}}\hat{x}.
+Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+The main pillar of this work is the following simple observation.
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
+to a scaled, biased, version of the signal's autocorrelation:
+\begin{align} \label{eq:data_ac_k1}
+\lim_{N\to\infty} a_y^1 &= \gamma a_{x}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] &= \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\end{align}
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
+These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
+The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a particular caution should be taken with the statistical dependencies of the noise entries.
+The relations~\eqref{eq:data_ac_k1}, together with Proposition~\ref{prop:uniqueness}, imply that given $M$ and $\sigma$, one can estimate the signal for any noise level if $M$ is large enough.
+Next, we show that  $M$ and $\sigma$ are also uniquely determined from the autocorrelations.
+
+If the noise level $\sigma^2$ is known, one can estimate the ratio $M/N$ from the first two moments.
+\begin{proposition} \label{prop:gamma}
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. If the mean of $x$ is nonzero, then 
+	\begin{equation*}
+	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
+	\end{equation*}
+	\begin{proof}
+The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
+\end{proof}
+\end{proposition}
+
+If we use third-order autocorrelation information, then it is possible to estimate both the ratio $M/N$ and $\sigma$ simultaneously.
+\begin{proposition} \label{prop:gamma_sigma}
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for generic signals.
+If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following.
+\begin{corollary}
+	Let $K=1$, $N\to\infty$ and $\sigma$ is fixed. Then, the signal, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions if:
+	\begin{itemize}
+		\item $x$ is generic;
+		\item  $x[0],x[L-1]\neq 0$, $x$ has nonzero mean and $\frac{M}{N}\geq\frac{1}{4(L-1)}$.
+	\end{itemize}
+\end{corollary}
+
+\subsection{Estimating autocorrelations from the data with multiple signals $K>1$} \label{sec:estimating_ac}
+
+When $K>1$, it is impossible to estimate the autocorrelation of each signal directly from the data. However similarly to~\eqref{eq:data_ac_k1}, one can estimate the mixture of the autocorrelations. 
+As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
+\begin{equation}
+\gamma_i = \frac{M_i L}{N}, \quad \gamma = \sum_{i=1}^K\gamma_i.
 \end{equation}
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then:
+\begin{align} \label{eq:data_ac}
+\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\end{align}
+This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
 
-The scaling of $\hat{x}$ is incorrect, since the averaging in done over many windows containing pure noise with no information on the signal itself. 
-To rescale the estimated signal, we estimate the norm of the signal separately.
-The norm estimation can be done as follows. For short, we denote $x_K[n]=\sum_{i=1}^K \xz[n-n_i]$ and note that $\|x_K\|_2^2 = K\|x\|_2^2$ if a separation of $\vert n_i - n_j\vert >L$ is satisfied. 
-Then,
-\begin{equation}
-\| y\|_2^2 =  \| x_K\|_2^2 + \|\varepsilon\|_2^2 + 2\varepsilon^Tx_K, 
-\end{equation}  
-and therefore 
-\begin{equation}
-\begin{split}
-\E{\| y\|_2^2} &=  \| x_K\|_2^2 + \E{\|\varepsilon\|_2^2} + 2\E{\varepsilon^Tx_K} \\ 
-&= K\|x\|_2^2 + N\sigma^2. 
-\end{split}	 
-\end{equation}   
-As $N\to\infty$,  we then obtain
-\begin{equation} \label{eq:norm_estimation}
-\|x\|_2^2 \approx \frac{\| y\|_2^2 - N\sigma^2}{K}. 
-\end{equation}
-The estimation error for different values of $\sigma$ is depicted in Figure~\ref{fig:norn_error}.
+The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
+In methods which are based on detection and averaging, the number of signals occurrences  must scale like $\sigma^2$.
+Taking the $d$th order autocorrelation function amplifies the variance of the noise by a factor of $d$.
+Therefore, the required number signal occurrences should scale like $\sigma^{2d}$  to retain some constant estimation error.
+Accordingly, in our  method, $M$ must scale like $\sigma^6$.
+In Section~\ref{sec:numerics}, we show empirically the third-order autocorrelation suffices also for a mixture of $K>1$ signals without prior knowledge of the $M_i$'s and $\sigma$.
+\TODO{question mark on the entire paragraph}
 
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale = .5]{NormError}		
-	\end{center}
-	\caption{The normalized error for norm estimation $\frac{\vert \|\hat{x}\|  - \|x\|\vert }{\|x\|}$, where $\|\hat{x}\|$ is the norm estimation.
-The error was averaged over 200 experiments for each value of $k$.}
-	\label{fig:norn_error}
-\end{figure}
+\section{Numerical experiments}   \label{sec:numerics}
 
-The output of the algorithm is a signal of length $W$, that, ideally, contains $x$, shifted by some unknown shift, and padded by $W-L$ zeros. 
-The algorithm is summarized in Algorithm~\ref{alg:1}.
-\TODO{We should come up with a method to automatic aligning of the signal}.
+Here we should say that we can work only with non-biased terms
+%\subsection{One-dimensional experiments}
 
-\begin{algorithm}[h]
-		\textbf{Input:} The measurement $y\in\RN$ \\ 
-		\textbf{Output:} A signal $\tilde x\in\mathbb{R}^W$  \\ 
-		\begin{enumerate}
-			\item Split $y$ into a set of $N/W$ analysis windows $y_i\in\mathbb{R}^W$ according to~\eqref{eq:analysis_window}
-			\item  Compute the average mean, power spectrum and bispectrum according to~\eqref{eq:moment_estimation} 
-			\item  Estimate the signal $\hat{x}\in\mathbb{R}^W$ by~?
-			\item  Map $\hat{x}\gets T_{\ell_{\max}}\hat{x}$ according to~\eqref{eq:align}
-			\item  Compute the estimated norm $x_{\textrm{norm}}$  by~\eqref{eq:norm_estimation}
-			\item  Rescale the signal $\tilde x \gets \frac{\tilde{x}\cdot x_{\textrm{norm}}}{\|\tilde{x}\|_2} $   
-		\end{enumerate}
-	\caption{Blind devolution by invariant features} 	\label{alg:1}
-\end{algorithm}
+%Here will come the 1D experiment with heterogeneity
 
-\section{Analysis} \label{sec:analysis}
+\subsection{Two-dimensional experiments}
 
-For the sake of analyzing Algoritmh~\ref{alg:1}, we make the following assumptions.
-We consider the regime in which $N,\sigma,K\to\infty$ and  $L,W$ are fixed.
-We introduce to rations.
-The first is a ``sparsity factor" defined as $S = \frac{N}{WK}$, $WK$ is a measure for the ``active" windows and $1<S<\infty$.
-The second is $P = W/L>1$, measuring the ``padding factor"; the ratio between the lengths of the analysis window and the signal.
-We assume that positions $n_i$ are well-separated so that $\vert n_i - n_j\vert >2W$.
-The factor 2 is merely to ease the analysis is not really required by the algorithm.
-We also assume that each $n_i$ is uniformly distributed within the window.
+??
 
-Let us define  the zero padded signal $$x_W  = [x, \underbrace{0,0,\ldots,0}_{N-W \text{ zeros}}]\in\mathbb{R}^W.$$ 
-We want to estimate the features of this signal from the features the $y_i$'s.
-We analyze the estimation error of the bispectrum, and mention that the same methodology and conclusions hold for the power spectrum and mean.
-
-In order to estimate the bispectrum of the signal, we average over the bispectra of the analysis windows, namely,
-\begin{eqnarray}
-\hat{B}_{x_W} = \frac{W}{N}\sum_{i=1}^{N/W}B_{y_i}.
-\end{eqnarray}
-For the power spectrum, we need  to be somewhat careful with the bias.
-We will assume here that the mean of the signal is zero.
-Since the mean can be easily estimated from the data, it can be subtracted from each window before the averaging.
- In addition, as discussed in~\cite{bendory2017bispectrum}, we can replace the mean by more robust estimator, like the median.
-
-We first observe that the analysis windows can be split into three groups and written as:
-\begin{eqnarray}
-\hat{B}_{x_W} = B_\textrm{signal} + B_\textrm{clutter} + B_\textrm{noise}, 
-\end{eqnarray}
-where
+%
+%In this section, we provide the details of the 2D experiment shown in Figure~\ref{fig:example}.
+In the experiment, we generated a sequence of $767\times 10^3$ 2D images (``micrograph") of size $2000\times 2000$.
+Each micrograph had around $\sim 900$ signal occurrences (depends on the stopping criterion that we need to explain) and in total $M = 561\times 10^6$.
+The noise level was $\sigma=1$.
+%
+%To accelerate the experiment, we estimated only the first two autocorrelations of the signal.
+As mentioned in Section~\ref{sec:estimating_ac}, this data determines a 2D signal uniquely, up to possible reflection symmetry.
+%In this experiment, we chose the correct reflection manually.
+To estimate the signal we used the Relax-Reflect-Reflect (RRR) algorithm, which is a known phase retrieval algorithm.
+Recall that the second-order autocorrelation is equivalent to the power spectrum of the signal.
+%Starting form random initialization of size $(2L-1)\times(2L-1)$, its $k$th  iteration take the form of 
+% \begin{equation*}
+% x_k = x_{k-1} + \beta(P_2(2P_1(x_{k-1}) -x_{k-1}) - P_1(x_{k-1}), 
+%  \end{equation*}
+% where $P_1$ is a projection that keeps the values of the  $L\times L$ entries in the upper-left corner and zeros out all other entries, $P_2$ is a projection that keeps the Fourier phase of $x_{k-1}$ and impose the correct Fourier magnitudes, and we set $\beta = 0.5$.
+The solution of the RRR scheme was used to initialized a LS estimation on the first two moments with signals of length $(2L-1)\times(2L-1)$ for the 200 iterations.
+Finally, we chose the $L\times L$ upper left corner and refined it using LS with 500 iterations.
+% 
+\section{Conclusion} 
+Here we conclude the paper. Points to mention;
 \begin{itemize}
-	\item $B_\textrm{noise}$ - sum of the bispectra of the segments that contain pure noise (no signal),
-	\item $B_\textrm{signal}$ - sum of the bispectra of the segments that contain a full signal (one appearance of $x$) and noise,
-	\item $B_\textrm{clutter}$ - sum of the bispectra of the segments that contain only part of $x$ and noise.
+\item cryo -- EM
+\item  structured background (here we assume i.i.d.\ noise -- can we remove it in some cases?)
+\item   without separation   	
+\item  sample complexity
 \end{itemize}
 
-We analyze each group separately.
-First, we observe that $B_\textrm{noise}\to 0$ (note that this is the zero matrix).
-Since this a triple product, and we have, at least, $N/W-2K =N/W(1-2/S) $ such windows, the variance of $B_\textrm{noise}$ reduces to zero at rate  $\order{\frac{W}{N}\left(1-\frac{2}{S}\right)\sigma^6}$.
-This imply that for large $S$, the estimation rate of this factor reduces since we ``inject" pure noise to the estimation, with no relevant information on the signal.
-
-The second group contains windows with a full signal.
-Indeed, the signal may appear anywhere, but since we work with features that are invariant to translation, that exact position is irrelevant as long as we have the full information of the signal.
-Since we assumed that the positions  $n_i$ are distributed uniformly in the window, there are (asymptotically) $K(1-L/W) = K(1-1/P)$ windows in this group.
-Therefore, $B_\textrm{signal}$ converges to a scaled version of $B_x$  \ at rate $\order{\frac{\sigma^6}{K(1-P)}}$.
-The scaling will be corrected in the last stage of the algorithm.
-This implies that the larger $P$, the faster the estimation rate of this group.
-This makes a lot of sense since it means that will find more windows with full signal and less cropped signals.
-
-Finally, we analyze the third group, the  ``clutter" --- the cropped signals. Since each such signal appears in two windows,
-we have $2KL/W = 2K/P$ clutter segments. Of course, the noise in this segments goes to zero
-at rate $\order{\frac{P\sigma^6}{2K}}$. However, we have an additional error term arises from  the cropped signals. This term does not reduce to zero, but can be bounded. 
- To analyze the effect of this term, let us assume that $N/\sigma^6$ is great enough so that $B_\textrm{noise}\to 0$ and also $\left\|B_{y_i}\right\|_{\textrm{F}} \approxeq \left\|B_x\right\|_{\textrm{F}}$.
-Then,
-\begin{equation}
-\begin{split}
-\left\| \hat{B}_{x_W} - B_\textrm{signal}\right\|_{\textrm{F}} \approxeq&  \left\|B_\textrm{clutter}\right\|_{\textrm{F}}
-= \left\|\frac{W}{N}\sum_{i\in\textrm{clutter}}B_{y_i}\right\|_{\textrm{F}}
-\\ \leq & 
-\frac{W}{N}\frac{2KL}{W}\left\|B_x\right\|_{\textrm{F}} = \frac{2}{SP}
-\|B_x\|_{\textrm{F}}.
-\end{split}
-\end{equation}
-Therefore, for large sparsity term $S$ or large $P$, we get an accurate estimation of a scaled version of the signal's bispectrum.
-
-Few insights from the analysis: (need to verified numerically)
-\begin{itemize}
-	\item Larger $S$ reduces the clutter error, however, increases the variance of the noise estimation.
-	\item Larger $P$ reduces the clutter error, however, increases the variance of the noise  where the signal appears.
-	\item We must keep $P$ large enough to see enough full signals.    
-\end{itemize}
-
-\section{Numerical experiments} \label{sec:experiments}
-
-\section{Conclusion} \label{sec:conclusion}
+%In particular, in cryo--EM, multiple projections of a molecule (signal), taken
+%from unknown viewing directions, are recorded on two-dimensional detector
+%array. Current algorithms try to detect these projections in a low SNR regime
+%and then use them for the reconstruction process. Since the
+%Then, the reconstruction problem is to detect these projection, and then use
+%them to estimat
+%The data acquired in both technologies is composed of multiple projections
+%of a molecule (the signal), taken from unknown viewing direction, and drawn in
+%high noise level. The reconstitution problem is then to estimate the molecule
+%from this data.
 
@@
 
+\appendix
+
+\section{Autocorrelation estimations} \label{sec:autocorrelation_computation}
+
+Throughout the proof, we consider the case of one signal $K=1$.
+The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriates weights, see~\cite{boumal2017heterogeneous}.
+
+Let us define
+\begin{equation}
+\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
+\end{equation}
+With a bit abuse of notation, $M_N$ stresses that $M$ is a function of $N$. Indeed, by assuming $M_N=\Omega(N)$, we deduce $\gamma>0$.
+We start by considering the first autocorrelation of the data
+\begin{equation}
+a_y^1 = \sum_{i=0}^{N-1} y[i] = \frac{1}{N/L}\sum_{j=0}^{M_N-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}} \xrightarrow{a.s.}\gamma a_x^1,
+\end{equation}
+where the noise term converges to zero almost surely (a.s.) by the law of large numbers.
+
+We proceed with the second autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+\begin{equation}
+\begin{split}
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
+& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
+\end{split}
+\end{equation}
+where the cross terms between the signal and the noise vanish  almost surely in the limit $N\to\infty$.
+
+We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
+\begin{equation} \label{eq:2nd_moment_signal_term}
+\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
+\end{equation}
+Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
+\begin{equation}
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+\end{equation}
+Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
+If $\ell=0$, 
+\begin{equation}
+\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
+\end{equation}
+
+We are now moving to analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
+\begin{equation*}
+a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
+\end{equation*}
+Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
+The first contains only signal terms (does not see noise) and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+Three other terms contain the product of two signal entries and one noise term.
+Since the noise is independent of the signal and has zero mean, these terms go to zero almost surely.
+
+We next analyze the contribution of the term composed of triple products of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
+\begin{equation*}
+\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
+\end{equation*}
+For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
+For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each one is a triple product of Gaussian variables with zero mean and therefore has zero expectation.
+
+To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
+Most of these terms converge to zero almost surely because of independency between the noise entries.
+For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
+
+\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+
+We aim to prove that one can estimate both $\sigma$ and $\beta = M/N$ from the observed first three moments.
+To this end, we construct two quadratic equations of $\beta$ from the observed (measured) quantities, independent of $\sigma$.
+Then, we show that these equations are independent and therefore $\beta$ is uniquely defined. 
+Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
+Throughout the proof, it is important to distinguish between observed and unobserved values. 
+to this end, we denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
+
+Recall that $a_y^1 = \beta(\one^Tx)$ and  
+and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ stands for vector of ones. Taking the product:
+\begin{equation}\label{eq:E1}
+\begin{split}
+E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
+& = \sigma^2a_y^1 + \beta^2F_1,
+ \end{split}
+\end{equation}
+where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
+The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account:
+\begin{equation} \label{eq:E2}
+E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
+\end{equation}
+Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
+\begin{equation} \label{eq:E12}
+E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
+\end{equation}
+Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
+\begin{equation} \label{eq:sigma2}
+\sigma^2 = a_y^2 - (a^1_y)^2/(\beta L). 
+\end{equation} 
+Plugging into~\eqref{eq:E12} and rearranging we get 
+\begin{equation} \label{eq:quad1}
+\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
+\end{equation}
+where 
+\begin{align*}
+\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
+\mathcal{B} &= -E_1 + \frac{2L+1}{L}(a_y^1)^3 + a_y^1a_y^2  , \\
+\mathcal{C} &= -(a_y^1)^3/L.
+\end{align*}
+Importantly, these coefficients are observable quantities.
+
+We are now proceeding to derive the second quadratic equation. We notice that 
+\begin{equation} \label{eq:E3}
+E_3  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \frac{1}{L}\beta^3 F_2,
+\end{equation}
+where 
+\begin{equation*}
+F_2 =  a_x^3[0,0] + 3\sum_{j=1}^{L-1}a_x^3[j,j] + 3\sum_{j=1}^{L-1}a_x^3[0,j] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+\end{equation*}
+On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
+\begin{equation} \label{eq:E4}
+E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
+\end{equation}
+Taking the ratio:
+\begin{equation*} 
+\frac{E_4}{E_3} = \frac{L}{\beta^2} + \frac{(6L-3)L\sigma^2a_y^1}{E_3}, 
+\end{equation*}
+we conclude:
+\begin{equation*}
+\sigma^2 = \frac{E_4}{a_y^1L(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
+\end{equation*}
+Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
+\begin{equation} \label{eq:quad2}
+\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
+\end{equation}
+where
+\begin{align*}
+\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
+\mathcal{E} &= -(a_y^1)^2/L, \\
+\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
+\end{align*}
+
+To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
+To this end, it is enough to show that the ratio between the coefficients is not the same.
+From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
+\begin{equation*}
+\begin{split}
+\frac{\mathcal{B}}{\mathcal{C}} &= \frac{LE_1 - (2L+1)(a_y^1)^3 - La_y^1a_y^2}{(a_y^1)^3} \\&= \frac{La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2}{(a_y^1)^2}.
+\end{split}
+\end{equation*}
+In addition, using~\eqref{eq:E3}
+\begin{equation*}
+\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_3} = 3 - 6L . 
+\end{equation*}
+
+Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
+\begin{equation*}
+La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
+\end{equation*}
+Rearranging the equation and writing in terms of $x$ we get 
+\begin{equation} \label{eq:cond}
+4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
+\end{equation}	
+For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
+More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
+\begin{equation*}
+\beta \geq \frac{1}{4(L-1)},
+\end{equation*}
+the condition~\eqref{eq:cond} cannot be satisfied for any signal.
+
 \end{document}

### 2018-04-08 TEX/draft2.tex
Adding open question section to the ms

@@
 %
-\section{Conclusion} 
-Here we conclude the paper. Points to mention;
-\begin{itemize}
-\item cryo -- EM
-\item  structured background (here we assume i.i.d.\ noise -- can we remove it in some cases?)
-\item   without separation   	
-\item  sample complexity
-\end{itemize}
 
-%In particular, in cryo--EM, multiple projections of a molecule (signal), taken
-%from unknown viewing directions, are recorded on two-dimensional detector
-%array. Current algorithms try to detect these projections in a low SNR regime
-%and then use them for the reconstruction process. Since the
-%Then, the reconstruction problem is to detect these projection, and then use
-%them to estimat
-%The data acquired in both technologies is composed of multiple projections
-%of a molecule (the signal), taken from unknown viewing direction, and drawn in
-%high noise level. The reconstitution problem is then to estimate the molecule
-%from this data.
+\section{Open questions}
+
+In this paper, we considered the problem of estimating a set of signals from their multiple occurrences in unknown locations in the data.
+We focused on  low $\SNR$ environments in which detection is impossible.
+Our technique  is based on computing the third-order autocorrelation function of the data with asymptotic estimation rate proportional to $\sigma^6/M$.
+Based on related results in multireference alignment~\cite{abbe2018estimation}, we believe that it is the optimal estimation rate, however, this is yet to be proven.
+
+Our results rely on two main assumptions that are not necessarily met by applications. 
+First, we modeled the background information as i.i.d.\ additive noise. In practice,
+the background information may be structured, and even signal-dependent. Then, the question is  under what conditions  
+one can still estimate the signals and separate them from the background information in the low $\SNR$ regime?
+
+In addition, we assumed that the signal occurrences are all separated by $L-1$ entries, see~\eqref{eq:spacing}.
+If the signals are not separated, one can introduce a new variable $p$ that represents the distribution of the spacing between signal occurrences.
+The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
+Using this new variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
+Under what conditions on $p$ and the signals one can still estimate the signals from the data?
+
+\section{Connection with the cryo--EM problem}
+
+Cryo--EM is an innovative technology for reconstructing the 3D structure of macromolecules. In recent years, structures
+of many molecules, previously regarded as insurmountable, are now being
+obtained to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}. This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
+
+In a cryo--EM experiment, the biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
+Within the ice, the molecules are randomly oriented and positioned.
+Then,  the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
+Importantly, the micrograph is dominated by noise due to the small electron doses that
+can be applied to the specimen without causing radiation damage.
+
+The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or several micrographs). 
+ All current methods in the field split the reconstruction procedure to several subroutines.
+The first step in all methods is the so called particle picking, detecting the 2D tomographic projections of the samples from the noisy micrograph.
+The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with unknown 3D orientation.
+These series of images
+ is then used by a variety of algorithms to reconstruct the structure. 
+However, due to the high noise level, the performance of the particle pickers  is not ideal.
+For instance, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the estimation problem.
+In addition, the information of particles that are too close to each other is usually neglected.
+Hence, valuable information that can be used is omitted.
+
+The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}. 
+In our model, the noisy data is the analog of the micrograph.
+The $K$ sought signals correspond to $K$ different molecule's projections, taken from different orientations in $SO(3)$.
+In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
+The position of individual projections are the nuisuance varialbles in the cryo--EM problem, in analogy to the individual signal's locations in our setup.
+
+Clearly, applying the autocorrelation method to the cryo--EM problem raises interesting challenges that are far beyond the scope of this paper. 
+For instance, the numerical experiments of Section~\ref{sec:numerics} indicate that we need a huge number of observations to get accurate estimate.
+Can we accelerate the estimation rate so we can apply this method with smaller amount of data?
+In addition, since the size of a micrograph is quite large (typically around $4000\times 4000$ pixels), computing the third-order autocorrelations may be  expensive if not implemented carefully by parallelizing the computations.
+Also, the model should incorporate minimal spacing between the samples on the micrograph.
 

### 2018-04-09 TEX/draft2.tex
editing last section

@@
 
-In a cryo--EM experiment, the biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
+In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
 Within the ice, the molecules are randomly oriented and positioned.
@@
 
-The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or several micrographs). 
- All current methods in the field split the reconstruction procedure to several subroutines.
-The first step in all methods is the so called particle picking, detecting the 2D tomographic projections of the samples from the noisy micrograph.
+The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs). 
+All contemporary methods in the field split the reconstruction procedure to several subroutines. 
+The first step in the pipeline is the so called particle picking, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
 The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with unknown 3D orientation.
-These series of images
+This series of images
  is then used by a variety of algorithms to reconstruct the structure. 
-However, due to the high noise level, the performance of the particle pickers  is not ideal.
+However, due to the high noise level, the performance of particle pickers  is not ideal.
 For instance, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the estimation problem.
-In addition, the information of particles that are too close to each other is usually neglected.
+In addition, the information from particles that are too close to each other is usually neglected.
 Hence, valuable information that can be used is omitted.
@@
 The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}. 
-In our model, the noisy data is the analog of the micrograph.
-The $K$ sought signals correspond to $K$ different molecule's projections, taken from different orientations in $SO(3)$.
-In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
-The position of individual projections are the nuisuance varialbles in the cryo--EM problem, in analogy to the individual signal's locations in our setup.
+In our model, the noisy data $y$ is the analog of the micrograph.
+The $K$ sought signals correspond to $K$ different molecule's projections, each taken from  different unknown viewing direction.
+%In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
+The position of individual projections are the nuisance variables of the cryo--EM problem (as well as the viewing directions), in analogy to individual signal's locations in our setup.
+That being said, the cryo--EM data is far more complicated that the simplified model of this paper. In a future research, we hope to bridge this gap.
 
-Clearly, applying the autocorrelation method to the cryo--EM problem raises interesting challenges that are far beyond the scope of this paper. 
-For instance, the numerical experiments of Section~\ref{sec:numerics} indicate that we need a huge number of observations to get accurate estimate.
-Can we accelerate the estimation rate so we can apply this method with smaller amount of data?
-In addition, since the size of a micrograph is quite large (typically around $4000\times 4000$ pixels), computing the third-order autocorrelations may be  expensive if not implemented carefully by parallelizing the computations.
-Also, the model should incorporate minimal spacing between the samples on the micrograph.
+%For instance, the numerical experiments of Section~\ref{sec:numerics} indicate that we need a huge number of observations to obtain an accurate estimate.
+Can we accelerate the estimation rate?
+How to include nearby molecule to extract all information in the micrograph?
+%In addition, since the size of a micrograph is quite large (typically around $4000\times 4000$ pixels), computing the third-order autocorrelations may be  expensive if not implemented carefully by parallelizing the computations.
+%
 

### 2018-04-12 TEX/draft2.tex
nothing much

@@
 In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptomatic regime where $M,N\to\infty$, while preserving fixed ratio. 
+For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
 Specifically, we define the ratio of the measurement occupied by  the signal as
@@
 
-Here we should say that we can work only with non-biased terms
-%\subsection{One-dimensional experiments}
+\TODO{Here we should say that we can afford to work only with non-biased terms}
 
-%Here will come the 1D experiment with heterogeneity
+\subsection{One-dimensional experiments}
+
+Here will come the 1D experiment with heterogeneity
 

### 2018-04-12 TEX/draft2.tex
First paragraph for 1D XP

@@
 
-Here will come the 1D experiment with heterogeneity
+For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
+Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately) $30 \cdot 10^6$, $20 \cdot 10^6$ and $10 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$ with an accept/reject rule based on the separation constraint.
+For each placement, one of the three signals is picked proportionally to the desired number of occurrences of each.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+Given the scaling of the target signals (whose median absolute value for the entries is at or below one), this is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
 

### 2018-04-12 TEX/draft2.tex
Second paragraph

@@
 to a scaled, biased, version of the signal's autocorrelation:
-\begin{align} \label{eq:data_ac_k1}
+\begin{align}
 \lim_{N\to\infty} a_y^1 &= \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] &= \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^2[\ell] &= \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
 \lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
@@
 If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then:
-\begin{align} \label{eq:data_ac}
+\begin{align}
 \lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
+\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
 \lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
@@
 
-\TODO{Here we should say that we can afford to work only with non-biased terms}
+%\TODO{Here we should say that we can afford to work only with non-biased terms}
 
@@
 Each of the three signals appears, respectively (and approximately) $30 \cdot 10^6$, $20 \cdot 10^6$ and $10 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$ with an accept/reject rule based on the separation constraint.
-For each placement, one of the three signals is picked proportionally to the desired number of occurrences of each.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
 Given the scaling of the target signals (whose median absolute value for the entries is at or below one), this is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
+
+Given the observation $y$, we proceed to compute the moments.
+The first-order moment is straightforward.
+For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
+Likewise, for third-order moments, we include $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_1 + \ell_2 \leq L_1$ and such that neither $\ell_1, \ell_2$ and $\ell_1 - \ell_2$ are all nonzero.
+This also avoids introducing biased elements, thus making it unnecessary to estimate $\sigma$.
+In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+Each batch is handled on a GPU, as GPUs are particularly well suited for simple instructions on large vectors of data.
 

### 2018-04-12 TEX/draft2.tex
Edits to first two paragraphs

@@
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-Given the scaling of the target signals (whose median absolute value for the entries is at or below one), this is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
+The SNR of $y$
+% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
+is about 1/12.
+%Given the scaling of the target signals (whose median absolute value for the entries is at or below one),
+This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
 Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
@@
 Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, we include $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_1 + \ell_2 \leq L_1$ and such that neither $\ell_1, \ell_2$ and $\ell_1 - \ell_2$ are all nonzero.
-This also avoids introducing biased elements, thus making it unnecessary to estimate $\sigma$.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_1 + \ell_2 \leq L_1$ includes all relevant moments for our purpose, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements.
+As a result, it is unnecessary to estimate $\sigma$.
 In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Each batch is handled on a GPU, as GPUs are particularly well suited for simple instructions on large vectors of data.
+Batches are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 

### 2018-04-12 TEX/draft2.tex
Investigating which moments we really should be taking, because of inconsistencies between paper and code

@@
 Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$.
+\TODO{We also have $a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]$ -- is that intended?
+Do we really have symmetry with the negative signs?
+I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$}
 Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
@@
 \begin{align}
-\lim_{N\to\infty} a_y^1 &= \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] &= \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
 \end{align}

### 2018-04-12 TEX/draft2.tex
About to do changes to 1D code to match moment sign conventions of the paper

@@
 Do we really have symmetry with the negative signs?
-I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$}
+I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$; to be checked, but I don't think this is correct;}
 Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
@@
 Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_1 + \ell_2 \leq L_1$ includes all relevant moments for our purpose, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements.
 As a result, it is unnecessary to estimate $\sigma$.

### 2018-04-12 TEX/draft2.tex
Soem changes to wording

@@
 \TODO{question mark on the entire paragraph}
+\TODO{We could move here the paragraphs from 1D XP about which moments we compute, to argue that we can expect to recover at most up to $K = L/2$ signals.}
 
@@
 Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ such moments.
 As a result, it is unnecessary to estimate $\sigma$.
-In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Batches are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+There are
+\begin{align*}
+	1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+moments in total.
+In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 

### 2018-04-12 TEX/draft2.tex
Pushing more updates to the paper about 1D XP

@@
 For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
-$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
-\begin{equation} \label{eq:ac_general}
-a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
-\end{equation}
+$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
+\begin{align}
+	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
+	\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
 Explicitly, the first three autocorrelations are
-\begin{align} \label{eq:autocorrelations}
-a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
-a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
-a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
+\begin{align} 
+	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
+	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
 \end{align}
@@
 \begin{proposition} \label{prop:uniqueness}
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzeros. Then:
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then:
 	\begin{itemize}
@@
 If $\vert z[0]z[L-1]\vert \geq \delta>0$, then $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
+\TODO{That statement is incomplete: you mean there exists an estimator that guarantees this.
+(Since the estimator is very simple, we may want to show it explicitly in the proposition statement, and comment afterwards that of course this is still fairly sensitive, and we can do better.)}
 	\end{itemize}
@@
 
+\TODO{I would remove most if this paragraph; we can have a similar discussion but for our case (after having discussing which moments we keep); make the statement, and finish with a one-sentence reference to the MRA paper.}
 The invertibility of the autocorrelations for $K>1$ was explored  for the related case of  periodic autocorrelation functions.
@@
 
-When $K>1$, it is impossible to estimate the autocorrelation of each signal directly from the data. However similarly to~\eqref{eq:data_ac_k1}, one can estimate the mixture of the autocorrelations. 
+When $K>1$, it is impossible \TODO{That's not true: we can do our procedure, which gives estimate of the signals, and moments of that are estimates of the moments of the individual signals.
+Whether one calls this 'direct' or not is subjective.
+I'd remove that sentence.)} to estimate the autocorrelation of each signal directly from the data.
+However similarly to~\eqref{eq:data_ac_k1}, one can estimate the mixture of the autocorrelations.
 As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
-\begin{equation}
-\gamma_i = \frac{M_i L}{N}, \quad \gamma = \sum_{i=1}^K\gamma_i.
-\end{equation}
+\begin{align}
+	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
+\end{align}
 If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then:
 \begin{align}
-\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
 \end{align}
@@
 Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ such moments.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
 As a result, it is unnecessary to estimate $\sigma$.
-There are
+We have
 \begin{align*}
@@
 Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
+\begin{multline}
+	\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+	\label{eq:optim1D}
+\end{multline}
+where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s}.
+Setting $W = L$ (as is a priori desired) is problematic as the above optimization problems appears to have numerous poor local optimizers.
+Since we can only initialize randomly at first, this approach would often fail in practice.
+Alternatively, we first run the optimization with $W = 2L-1$.
+This problem appears to have fewer poor local optima, perhaps as a result of the additional degrees of freedom which allow for more escape directions.
+As we would hope to find that these estimated signals are supported on $L$ contiguous entries, we extract from each one a subsignal of length $L$ (with cyclic indexing) that has largest $\ell_2$-norm.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this is reliable for a wide range of experimental parameters.
 

### 2018-04-12 TEX/draft2.tex
latest updates to 1D XP

@@
 Alternatively, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps as a result of the additional degrees of freedom which allow for more escape directions.
-As we would hope to find that these estimated signals are supported on $L$ contiguous entries, we extract from each one a subsignal of length $L$ (with cyclic indexing) that has largest $\ell_2$-norm.
+This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+As we hope that the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing) that has largest $\ell_2$-norm.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this is reliable for a wide range of experimental parameters.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
 

### 2018-04-12 TEX/draft2.tex
Made a note about weights in optimization

@@
 \end{multline}
-where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s}.
+where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
+Issue is: this is not very smart..}.
 Setting $W = L$ (as is a priori desired) is problematic as the above optimization problems appears to have numerous poor local optimizers.

### 2018-04-12 TEX/draft2.tex
Last efforts for today

@@
 Issue is: this is not very smart..}.
-Setting $W = L$ (as is a priori desired) is problematic as the above optimization problems appears to have numerous poor local optimizers.
-Since we can only initialize randomly at first, this approach would often fail in practice.
-Alternatively, we first run the optimization with $W = 2L-1$.
+Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+Thus, we first run the optimization with $W = 2L-1$.
 This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-As we hope that the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing) that has largest $\ell_2$-norm.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing \TODO{we should understand / explain this}) that has largest $\ell_2$-norm.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
+Not sure it's worth the effort.}
 

### 2018-04-13 TEX/draft2.tex
ran an experiment to check if optimization is slow because of gammas: no, it's just slow.
Launching a big XP

@@
 Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $30 \cdot 10^6$, $20 \cdot 10^6$ and $10 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
+This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
 For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
@@
 \TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
-Not sure it's worth the effort.}
+Not sure it's worth the effort.
+-- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
+\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
 

### 2018-04-13 1D/example_heterogeneous.m

@@ -17,7 +17,7 @@ X(:, 3) = randn(L, 1);
 sigma = 3;
 
 % Desired number of occurrences of each signal X(:, k)
-m_want = [3e6 2e6 1e6];
+m_want = [3e7 2e7 1e7];
 
 % Length of micrograph
 n = sum(m_want)*W*10;

### 2018-04-24 TEX/draft2.tex
Added figures as is: will edit text later
Updated Section 1

@@
 In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a data sequence $y$\TODO{This is the most important sentence of the paper, we need to polish it up}.
-The data may also contain background information---independent of the signals---modeled as noise.
+The data may also contain background information---independent of the signals---which we model as noise.
+A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:model}.
 For one-dimensional signals, the data sequence can be thought of as a 
@@
 This model appears in many applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-In the last part of this manuscript, we also propose to interpreted this estimation problem as a toy model for the problem of single particle reconstruction using cryo-electron microscopy (cryo--EM).
-A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:model}.
+In the last part of this paper, we also propose to interpreted this estimation problem as a toy model for the task of single particle reconstruction using cryo-electron microscopy (cryo--EM).
 
-Figure~\ref{fig:XC_example} shows a simple example of data sequences with  one signal ($K=1$) that appears twice.
+Figure~\ref{fig:XC_example} shows a simple example of data sequences with  one signal ($K=1$).
 The upper row presents the data without noise, in the left panel, and its cross-correlation with the signal itself in the right panel.
-The cross-correlation exhibits two peaks corresponding to the signal's locations in the data.
+The cross-correlation exhibits two peaks, corresponding to the two signal's locations in the data.
 %Even if we add a small amount of noise and considering more than one signal ($K>1$), estimating the signals remains a painless task. 
 %In this scenario, standard detection and clustering algorithms can locate and cluster the copies of the signals that can be then averaged within each class.  
-In  the middle row, the same data is shown, now contaminated with i.i.d.\ Gaussian noise with zero mean and standard deviation of $\sigma=0.7$. 
-While it is harder to observe the signal occurrences in the left panel, the cross-correlation still produces fairly adequate estimates of the signal's locations.
+In  the middle row, the same data is shown, now contaminated with i.i.d.\ Gaussian noise with zero mean and standard deviation of $\sigma=0.5$. 
+While it is harder to identify the signal occurrences in the left panel, the cross-correlation still produces fairly adequate estimates.
 In practice one usually does not possess a precise template of the signal to be recovered, however, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
@@
 even if the true signal is known. 
-This phenomenon---explained in more detail in Section~\ref{sec:model}--raises the question: 
-\medskip 
-\\
-\emph{Can we estimate the signals accurately without detecting their individual occurrences? }
- \\
+This phenomenon---explained in more detail in Section~\ref{sec:model}--raises the following fundamental question: 
+%\medskip 
+%\\
+\begin{center}
+\emph{Can we estimate the signals accurately without detecting their individual occurrences? }  %\\
+\end{center}
 
-In this work, we provide a positive answer to this question. For one signal ($K=1$), we prove that in the asymptotic regime in which the signal appears
-infinitely many times in the data, and under a spacing condition, one can estimate the signal \emph{to any desired accuracy in any $\SNR$ level}.
+In this work, we provide a positive answer to this question. For a single signal ($K=1$), we prove that in the asymptotic regime in which the signal appears
+infinitely many times, and under a spacing condition, one can estimate the signal \emph{to any desired accuracy in any $\SNR$ level}.
 We show empirically that the same holds true for multiple signals if $K$ is not too large.
 \TODO{Do we want a sentence like: Based on  recent results on the multireference alignment problem, we conjecture that it remains true as long as $K \lesssim L/6$.
-?}
+?
+I am not sure it is necessary.}
 
@@
 In a nutshell, the method consists of two stages.
-First, we estimate a mixture (linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by at least $L-1$ entries and  each signal appears ample number of times \TODO{?} in the data.
+First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
+These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by at least $L-1$ entries and  each signal appears sufficiently many times in the data.
 There is no need to detect individual occurrences.
-Furthermore, we do not assume the knowledge of the number of signal occurrences $M$ and the noise level.
+Furthermore, we do not assume the knowledge of the number of signal occurrences $M$ or the noise level.
 In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS).
-Section~\ref{sec:autocorrelation} elaborates on the technique and proves some of its properties, while Section~\ref{sec:numerics} provides numerical demonstrations.
+Section~\ref{sec:autocorrelation} elaborates on the technique and proves some of its properties, while Section~\ref{sec:numerics} shows numerical demonstrations and discusses computational aspects.
 
-Interestingly, expectation-maximization (EM)---a popular framework for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem, even if the number of signal occurrences $M$ is known and $K=1$.
-In particular, in each iteration, EM assigns probabilities to all possible combinations of positioning the current signal estimate in $M$ locations on $\mathbb{Z}_N$, resulting in $O(N^M)$ possibilities (even when excluding forbidden combinations due to the spacing constraint).
+Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
+This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
+In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
+In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations. \TODO{cumbersome}
 
@@
 		\includegraphics[scale=0.5]{XC_example}
-		\caption{ The upper left panel shows a data sequence of length $N=80$ with one rectangular signal of length $L=11$ that appears twice.
-In the second and third rows of the left column, a Gaussian noise with mean zero and standard deviation $\sigma=0.5$ and $\sigma=3$ was added, respectively.
-The panels in the right column present the cross-correlation of the data with the true rectangular signal.
+		\caption{ The upper left panel shows a data sequence (measurement) of length $N=80$ with one rectangular signal of length $L=11$ that appears twice.
+The upper right panel shows the cross-correlation of the data with the true rectangular signal.
+		The second and third rows present the data sequence with additive Gaussian noise with mean zero and standard deviation $\sigma=0.5$ and $\sigma=3$, respectively, and its cross-correlation with the signal.
 Note to the different scales in different panels.
-}
+Importantly, in the low $\SNR$ regime the cross-correlation does not provide information on the locations of the signal in the data.}
     	\label{fig:XC_example}
@@
 
-\subsection{One-dimensional experiments}
+%\subsection{One-dimensional experiments}
+
+\TODO{Revise to explain $K = 1$ experiment first, then explain $K = 3$.}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_n10000000000_107521}
+	\caption{\TODO{...}}
+	\label{fig:1Dhomosignals}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_RMSE_n10000000000_107521}
+	\caption{\TODO{...}}
+	\label{fig:1DhomoRMSE}
+\end{figure}
 
@@
 
-\subsection{Two-dimensional experiments}
-
-??
+%\subsection{Two-dimensional experiments} 
+%??
 

### 2018-04-24 TEX/draft2.tex
updates for Section 2

@@
 
-\author{Tamir Bendory}
+\author{Tamir Bendory, Nicolas Boumal, William Leeb and Amit Singer}
 \maketitle
@@
 Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
-A plain way to present the forward model is as a mixture of blind deconvolution problems between binary signals and the target signals
+The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
 \begin{equation} \label{eq:model}
@@
 %We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-Each  $s_i\in\{0,1\}^N$ is associated with the position of the occurrences of the corresponding $x_i$. Let $\mathcal{S}_i$ denotes the set of  the nonzero
- values of $x_i$ and assume that the all $\mathcal{S}_i$'s are disjoint. The union of supports is denoted by $s = \sum_{i=1}^Ks_i$ and similarly $\mathcal{S} = \cup \mathcal{S}_i$. 
-The cardinality of the sets are denoted by $\vert \mathcal{S}_i\vert = M_i$ and $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.  Neither the $M_i$'s nor $M$ are assumed to be known.
+The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
+We denote the set of these nonzero values by 
+ $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
+By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
+Neither the $M_i$'s nor $M$ are assumed to be known.
 
-In order to estimate the mixture of signals autocorrelations, we assume that the support of $s$ is not clustered. In particular, 
+In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
 \begin{equation} \label{eq:spacing}
@@
 \end{equation}
-The goal of the problme is to estimate $x_1,\ldots,x_K$ from $y$.
+The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
 
@@
 To make the problem well-posed, we must  assume some prior knowledge or  structure. 
-In our case, the prior information is that $s$ is a binary signal that satisfies~\eqref{eq:spacing}. 
+In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}. 
 Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
@@
 The  $s_i$'s  are referred to as \emph{nuisance  variables}.
-Indeed, in many blind deconvolution applications the sole purpose is to estimate one of the unknown signals.
+Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
 For instance, in image deblurring, both the blurring
@@
 
-If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating $s$ is impossible.
+If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
 To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
-That is to say, we get a series of windows, each one contains a signal at unknown location.
+That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location.
 Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
-However, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
 Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
-As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals themselves, despite the impossibility of detecting their individual occurrences.
+As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
 
@@
 %The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$ (identify the system). The question of identifiability of $x$ under
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
 this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
@@
 given the observed signal $y$. Solving this optimization exactly is typically
-intractable, and so heuristic methods are used instead. One proposed heuristic
- is to use Markov Chain Monte Carlo (MCMC); in special
+intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
 cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
 The EM method is based upon a certain ``forward-backward'' procedure
-used in hidden Markov models, described in~\cite{rabiner1989tutorial}. \TODO{We need to explain}
-Other problems solve for parameterized models of $x$; for instance, see~\cite{andrieu2001bayesian}. 
-That same paper also considers multiple distinct signals $x$, as in our heterogeneity framework ($K>1$). Their proposed
-solution is an MCMC algorithm designed for their specific parametrized problem.
+used in hidden Markov models~\cite{rabiner1989tutorial}. \TODO{need further explanation, is it an approximation?}.
+Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
+Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
 
 Because likelihood methods are computationally expensive, methods based
-on recovery from moments and cumulants, which are akin to our method, have
+on recovery from moments, which are akin to our method, have
 also been previously used for system identification. The question of identifiability
 of $x$ from third-order statistics with non-Gaussian $w$ was considered in~\cite{lii1982deconvolution}. \TODO{how is it different from bispectrum inversion?}
-Methods using the third- and fourth-order cumulants are described in~\cite{giannakis1989identification,tugnait1984identification}.
+Methods based on the third- and fourth-order moments are described in~\cite{giannakis1989identification,tugnait1984identification}.
 

### 2018-04-26 TEX/draft2.tex
Updated Section 3

@@
 The EM method is based upon a certain ``forward-backward'' procedure
-used in hidden Markov models~\cite{rabiner1989tutorial}. \TODO{need further explanation, is it an approximation?}.
+used in hidden Markov models~\cite{rabiner1989tutorial}. 
+However, the complexity of this procedure is still nonlinear in $N$, and therefore its usage is limited for big data sets.   
 Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
@@
 on recovery from moments, which are akin to our method, have
-also been previously used for system identification. The question of identifiability
-of $x$ from third-order statistics with non-Gaussian $w$ was considered in~\cite{lii1982deconvolution}. \TODO{how is it different from bispectrum inversion?}
-Methods based on the third- and fourth-order moments are described in~\cite{giannakis1989identification,tugnait1984identification}.
+also been previously used for system identification. 
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
 
@@
 
-Our method for estimating the signals is a two-stage technique. 
+Our method for estimating the signals is composed of two stages. 
 First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
@@
 Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-In this section we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
+In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
 
@@
 \end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$.
-\TODO{We also have $a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]$ -- is that intended?
-Do we really have symmetry with the negative signs?
-I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$; to be checked, but I don't think this is correct;}
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
 Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
 
-A one-dimensional signal is determined uniquely and stably by its third-order auto-correlation as proven in the following simple proposition.
+A one-dimensional signal is determined uniquely and stably by its third-order autocorrelation as proven in the following simple proposition.
 \begin{proposition} \label{prop:uniqueness}
@@
 		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
-        \item \textbf{Finite sensitivity:} 	Suppose that  $a_z^3[k,L-1]$ can be estimated up to  perturbation $\upsilon$ and let $\hat{z}[k]$ be an estimator of $z[k]$.
-If $\vert z[0]z[L-1]\vert \geq \delta>0$, then $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
-\TODO{That statement is incomplete: you mean there exists an estimator that guarantees this.
-(Since the estimator is very simple, we may want to show it explicitly in the proposition statement, and comment afterwards that of course this is still fairly sensitive, and we can do better.)}
+        \item \textbf{Finite sensitivity:} 	Suppose we can only measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
+         Then,  $\hat{z}[k] =\frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$. 
 	\end{itemize}
@@
 		\end{equation*}
-		If we measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$, then 
+		In addition, 
 		\begin{equation*}
@@
 
-A few remarks are in order. First, this result carries through to signals of any dimension.
-Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W>L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Third, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ asymptotically.
+A few remarks are in order. 
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next section, we propose an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
 Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-Finally, while Proposition~\ref{prop:uniqueness} shows only finite sensitivity, in practice LS estimator is robust to additive noise; see Section~\ref{sec:numerics}.
-This is compatible with results in related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
 
@@
 Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
 The sign ambiguity can be resolved by the mean of the signal if it is not zero.
@@
 
-\TODO{I would remove most if this paragraph; we can have a similar discussion but for our case (after having discussing which moments we keep); make the statement, and finish with a one-sentence reference to the MRA paper.}
+\TODO{NB: I would remove most if this paragraph; we can have a similar discussion but for our case (after having discussing which moments we keep); make the statement, and finish with a one-sentence reference to the MRA paper.
+TB: I didn't touch it yet.
+We may want to put the degrees-of-freedom calculations from Section 4 here}
 The invertibility of the autocorrelations for $K>1$ was explored  for the related case of  periodic autocorrelation functions.
@@
 We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-All the main concepts carry through for $K>1$ as will be shown in the next section.
+The main principles carry through for $K>1$ as will be shown in the next section.
 
@@
 The main pillar of this work is the following simple observation.
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
+If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
 to a scaled, biased, version of the signal's autocorrelation:
@@
 	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for generic signals.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for a generic signal $x$.
 If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
@@
 
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following.
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
 \begin{corollary}
@@
 
-When $K>1$, it is impossible \TODO{That's not true: we can do our procedure, which gives estimate of the signals, and moments of that are estimates of the moments of the individual signals.
-Whether one calls this 'direct' or not is subjective.
-I'd remove that sentence.)} to estimate the autocorrelation of each signal directly from the data.
-However similarly to~\eqref{eq:data_ac_k1}, one can estimate the mixture of the autocorrelations.
 As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
@@
 \end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then:
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then one can estimate the mixture of the $K$ signals'  autocorrelations, similarly to~\eqref{eq:data_ac_k1}: 
 \begin{align}
@@
 \TODO{question mark on the entire paragraph}
-\TODO{We could move here the paragraphs from 1D XP about which moments we compute, to argue that we can expect to recover at most up to $K = L/2$ signals.}
+\TODO{NB: We could move here the paragraphs from 1D XP about which moments we compute, to argue that we can expect to recover at most up to $K = L/2$ signals.} \TODO{TB: I didn't touch for now.}
 
@@
 As a result, it is unnecessary to estimate $\sigma$.
-We have
+We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
 \begin{align*}

### 2018-04-26 TEX/draft2.tex
Updated Section 5

@@
 
+\TODO{TB: 2D experiment?}
 %\subsection{Two-dimensional experiments} 
@@
 In this paper, we considered the problem of estimating a set of signals from their multiple occurrences in unknown locations in the data.
-We focused on  low $\SNR$ environments in which detection is impossible.
-Our technique  is based on computing the third-order autocorrelation function of the data with asymptotic estimation rate proportional to $\sigma^6/M$.
+We focused on  low $\SNR$ environments in which detection of individual occurrences is impossible.
+Our technique  is based on computing the third-order autocorrelation function of the data with asymptotic estimation rate proportional to $\sigma^6/M$ \TODO{TB: it's not clear to me yet whether we discuss the estimation rate in the paper}.
 Based on related results in multireference alignment~\cite{abbe2018estimation}, we believe that it is the optimal estimation rate, however, this is yet to be proven.
 
-Our results rely on two main assumptions that are not necessarily met by applications. 
-First, we modeled the background information as i.i.d.\ additive noise. In practice,
-the background information may be structured, and even signal-dependent. Then, the question is  under what conditions  
+Our results rely on two core assumptions that are not necessarily met by applications. 
+First, we modeled the background information as i.i.d.\ additive noise.
+In practice, the background information may be structured or depend on the signal.
+Then, the question is  under what conditions
 one can still estimate the signals and separate them from the background information in the low $\SNR$ regime?
@@
 The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
-Using this new variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-Under what conditions on $p$ and the signals one can still estimate the signals from the data?
+Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
+This raises the question under what conditions on $p$ and the signals, one can estimate the signals from the data?
 

### 2018-04-26 TEX/draft2.tex
Updates for Section 6

@@
 In practice, the background information may be structured or depend on the signal.
-Then, the question is  under what conditions
-one can still estimate the signals and separate them from the background information in the low $\SNR$ regime?
+It raises the question  under what conditions on the background structure and statistics
+one can still estimate the signals in the low $\SNR$ regime.
 
@@
 Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-This raises the question under what conditions on $p$ and the signals, one can estimate the signals from the data?
+An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
 
@@
 of many molecules, previously regarded as insurmountable, are now being
-obtained to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}. This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
+reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}.
+This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
 
@@
 All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so called particle picking, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with unknown 3D orientation.
+The first step in the pipeline is the so-called particle picking, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
+The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with an unknown 3D orientation.
 This series of images
- is then used by a variety of algorithms to reconstruct the structure. 
+ is then used to estimate the structure. 
 However, due to the high noise level, the performance of particle pickers  is not ideal.
@@
 In addition, the information from particles that are too close to each other is usually neglected.
-Hence, valuable information that can be used is omitted.
+Hence, valuable information that can be harnessed is omitted.
 
-The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}. 
+The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}, that is, by skipping the particle picking step.
 In our model, the noisy data $y$ is the analog of the micrograph.
-The $K$ sought signals correspond to $K$ different molecule's projections, each taken from  different unknown viewing direction.
+The $K$ sought signals correspond to $K$ different molecule's projections, each taken from  a different, unknown, viewing direction.
 %In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
-The position of individual projections are the nuisance variables of the cryo--EM problem (as well as the viewing directions), in analogy to individual signal's locations in our setup.
+The position of individual projections are  nuisance variables of the cryo--EM problem, in analogy to individual signal's locations in our setup.
 That being said, the cryo--EM data is far more complicated that the simplified model of this paper. In a future research, we hope to bridge this gap.

### 2018-05-02 TEX/draft2.tex
Including figures with new ROI
Updated experiment results for heterogeneous case and copied scripts to TEX folder

@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_n10000000000_107521}
-	\caption{\TODO{...}}
+	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
+	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
 	\label{fig:1Dhomosignals}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_RMSE_n10000000000_107521}
-	\caption{\TODO{...}}
+	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n10000000000_107521}
+	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
 	\label{fig:1DhomoRMSE}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.9\linewidth]{XP_1D_heterogeneous/data_example_heterogeneous_n_24600000000_604392_fig1}
+\caption{\TODO{Thin yellow is ground truth; blue is ROI of first optimization; red is final estimation.
+Relative error for blue is .37, and .13 for red.
+Individual relative errors of the red estimates: 0.0239393 / 0.208925 / 0.0335956}}
+\label{fig:1Dheterosignals}
 \end{figure}

### 2018-05-06 TEX/draft3.tex
Draft 3

--- 2018-05-02 TEX/draft2.tex
@@
 
-\title{Estimation below the detection limit}
+\title{Toward single particle reconstruction without particle picking}
 
@@
 
-In this paper, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a data sequence $y$\TODO{This is the most important sentence of the paper, we need to polish it up}.
-The data may also contain background information---independent of the signals---which we model as noise.
-A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:model}.
-For one-dimensional signals, the data sequence can be thought of as a 
-long time series and the $K$ signals as repeated short events.  
-This model appears in many applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-In the last part of this paper, we also propose to interpreted this estimation problem as a toy model for the task of single particle reconstruction using cryo-electron microscopy (cryo--EM).
+Single particle reconstruction (SPR) using cryo--electron microscopy (cryo--EM) is an innovative technology for reconstructing the 3-D structure of macromolecules. In recent years, structures
+of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}.
+This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
 
-Figure~\ref{fig:XC_example} shows a simple example of data sequences with  one signal ($K=1$).
-The upper row presents the data without noise, in the left panel, and its cross-correlation with the signal itself in the right panel.
-The cross-correlation exhibits two peaks, corresponding to the two signal's locations in the data.
-%Even if we add a small amount of noise and considering more than one signal ($K>1$), estimating the signals remains a painless task. 
-%In this scenario, standard detection and clustering algorithms can locate and cluster the copies of the signals that can be then averaged within each class.  
-In  the middle row, the same data is shown, now contaminated with i.i.d.\ Gaussian noise with zero mean and standard deviation of $\sigma=0.5$. 
-While it is harder to identify the signal occurrences in the left panel, the cross-correlation still produces fairly adequate estimates.
-In practice one usually does not possess a precise template of the signal to be recovered, however, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
-The bottom panels show the same data swamped in  
-i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$. In this  low signal--to--noise (\SNR) regime, 
-detection of individual signal occurrences is impossible, 
-even if the true signal is known. 
-This phenomenon---explained in more detail in Section~\ref{sec:model}--raises the following fundamental question: 
-%\medskip 
-%\\
-\begin{center}
-\emph{Can we estimate the signals accurately without detecting their individual occurrences? }  %\\
-\end{center}
+In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
+Within the ice, the molecules are randomly oriented and positioned.
+Then, the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
+The micrograph is dominated by noise due to the small electron doses that
+can be applied to the specimen without causing radiation damage.
+The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs).
 
-In this work, we provide a positive answer to this question. For a single signal ($K=1$), we prove that in the asymptotic regime in which the signal appears
-infinitely many times, and under a spacing condition, one can estimate the signal \emph{to any desired accuracy in any $\SNR$ level}.
-We show empirically that the same holds true for multiple signals if $K$ is not too large.
-\TODO{Do we want a sentence like: Based on  recent results on the multireference alignment problem, we conjecture that it remains true as long as $K \lesssim L/6$.
-?
-I am not sure it is necessary.}
+\paragraph{Particle picking.}
+All contemporary methods in the field split the reconstruction procedure to several subroutines. 
+The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
+The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with an unknown 3D orientation.
+This series of images
+is then used to estimate the structure.
 
-Our framework is based on autocorrelation analysis.
+Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
+However, most of these procedures are prone to \emph{model bias}.
+For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
+Therefore, the algorithm performance depends on the user prior assumption about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled set of data.
+Other methods use disks or difference of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it also still popular to pick particles manually. This method, while exploits the researcher's experience, is both tedious and subject to model bias.
+
+The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are then aligned to Einstein's image using cross-correlation and  averaged. 
+In~\cite{shatsky2009method}, it was shown that using merely 1000 noise images, the averaged image is remarkably similar to the template image of 
+Einstein, rather than to pure noise. 
+%Therefore, such a simple algorithm is biased towards its model which is an undesirable property. 
+In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+
+Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
+As a result, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the reconstruction algorithm.
+In addition, the information from particles that are too close to each other is usually neglected.
+Hence, valuable information that can be harnessed is omitted.
+
+\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims showing that estimating a particle 
+directly from the micrograph might be possible.
+
+In particular, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
+Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle that appear multiple times in the micrograph.
+A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
+To be clear, we do not consider here many prominent features of SPR experiment and do not aim to reconstruct any 3-D structure.
+We also mention by passing that this model appears in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
+The left panel shows the data without noise.
+In the middle panel, an i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
+In this scenario, even for $K>1$, it is likely that standard detection and clustering algorithms can locate and cluster the copies of the signals that can be then averaged within each class.
+In the right panel, we show the same data swamped in
+i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
+As a matter of fact, it can be shown that in  low signal--to--noise (\SNR) regime, 
+detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
+This phenomenon is explained in detail in Section~\ref{sec:related_literature}.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.33\textwidth}
+		\centering
+		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
+		\caption{$\sigma = 0$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.33\textwidth}
+		\centering
+		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
+		\caption{$\sigma = 0.5$}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.33\textwidth}
+		\centering
+		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
+		\caption{$\sigma = 3$}
+	\end{subfigure}
+	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d./ Gaussian noise with variance $\sigma^2$.
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
+\end{figure}
+
+\paragraph{Autocorrelation analysis.}
+In order to recover the signal from the data, we use autocorrelation analysis.
 In a nutshell, the method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by at least $L-1$ entries and  each signal appears sufficiently many times in the data.
-There is no need to detect individual occurrences.
-Furthermore, we do not assume the knowledge of the number of signal occurrences $M$ or the noise level.
-In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS).
-Section~\ref{sec:autocorrelation} elaborates on the technique and proves some of its properties, while Section~\ref{sec:numerics} shows numerical demonstrations and discusses computational aspects.
+These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the size of the signal and  each signal appears sufficiently many times in the data.
+There is no need to detect individual occurrences, knowing the number of signal occurrences $M$ or the noise level.
+In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) or phase retrieval algorithms; see Section~\ref{sec:methods}.
+This method requires only one pass over the data and can recover the signals in any $\SNR$ level, if the signals appear enough times in the data.
+As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
 
-Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations. \TODO{cumbersome}
-
-\begin{figure}
-		\centering
-		\includegraphics[scale=0.5]{XC_example}
-		\caption{ The upper left panel shows a data sequence (measurement) of length $N=80$ with one rectangular signal of length $L=11$ that appears twice.
-The upper right panel shows the cross-correlation of the data with the true rectangular signal.
-		The second and third rows present the data sequence with additive Gaussian noise with mean zero and standard deviation $\sigma=0.5$ and $\sigma=3$, respectively, and its cross-correlation with the signal.
-Note to the different scales in different panels.
-Importantly, in the low $\SNR$ regime the cross-correlation does not provide information on the locations of the signal in the data.}
-    	\label{fig:XC_example}
-\end{figure}
-
-%
-%This work is primely motivated by cryo-electron microscopy (cryo--EM), which is an innovative  single particle reconstruction technology.
-The acquired data in a cryo-EM experiment is contaminated with high noise levels.
-Therefore, any molecule reconstruction algorithm must take  the challenging $\SNR$ level into account.
-In the last part of this manuscript, we draw connections with the estimation problem under consideration and the cryo--EM problem.
-
-\section{Model and related literature}  \label{sec:model}
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
-The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
-\begin{equation} \label{eq:model}
-y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
-\end{equation}
-%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
-We denote the set of these nonzero values by 
- $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-Neither the $M_i$'s nor $M$ are assumed to be known.
-
-In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
-\begin{equation} \label{eq:spacing}
-\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
-\end{equation}
-The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
-
-Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-To make the problem well-posed, we must  assume some prior knowledge or  structure. 
-In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}. 
-Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
-where the focus is on high $\SNR$ regimes.
-
-An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
-The  $s_i$'s  are referred to as \emph{nuisance  variables}.
-Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
-For instance, in image deblurring, both the blurring
-kernel and the high-resolution image are unknown, but the primary goal is only
-to sharpen the image.
-
-If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
-That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location.
-Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
-Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
-As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
-
-For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
-\begin{eqnarray}
-y = x\ast w + \varepsilon,  
-\end{eqnarray} 
-where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
-this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
-model in the  case of a single signal ($K = 1$).
-
-Likelihood-based methods seek to maximize the likelihood function for $x$,
-given the observed signal $y$. Solving this optimization exactly is typically
-intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
-cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
-The EM method is based upon a certain ``forward-backward'' procedure
-used in hidden Markov models~\cite{rabiner1989tutorial}. 
-However, the complexity of this procedure is still nonlinear in $N$, and therefore its usage is limited for big data sets.   
-Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
-Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
-
-Because likelihood methods are computationally expensive, methods based
-on recovery from moments, which are akin to our method, have
-also been previously used for system identification. 
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-
-\section{Autocorrelation analysis}   \label{sec:autocorrelation}
-
-Our method for estimating the signals is composed of two stages. 
-First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
-Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
-
-\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
-$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
-\begin{align}
-	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
-	\label{eq:ac_general}
-\end{align}
-where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
-Explicitly, the first three autocorrelations are
-\begin{align} 
-	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
-	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
-Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
-
-A one-dimensional signal is determined uniquely and stably by its third-order autocorrelation as proven in the following simple proposition.
-\begin{proposition} \label{prop:uniqueness}
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then:
-	\begin{itemize}
-		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
-        \item \textbf{Finite sensitivity:} 	Suppose we can only measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-         Then,  $\hat{z}[k] =\frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$. 
-	\end{itemize}
-	\begin{proof}
-		By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
-		Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
-		\begin{equation*}
-		a_z^3[k,L-1] = z[0]z[k]z[L-1].
-		\end{equation*}
-		In addition, 
-		\begin{equation*}
-		\hat{z}[k] = \frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
-		\end{equation*} 
-	\end{proof}
-\end{proposition}
-
-A few remarks are in order. 
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next section, we propose an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
-Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However,  in order to determine the reflection symmetry, one needs to use additional information.
-
-\TODO{NB: I would remove most if this paragraph; we can have a similar discussion but for our case (after having discussing which moments we keep); make the statement, and finish with a one-sentence reference to the MRA paper.
-TB: I didn't touch it yet.
-We may want to put the degrees-of-freedom calculations from Section 4 here}
-The invertibility of the autocorrelations for $K>1$ was explored  for the related case of  periodic autocorrelation functions.
-Recall that the  periodic autocorrelations are defined similarly to~\eqref{eq:ac_general}, with two differences: the sum goes to $L-1$ and all indices should be taken modulo $L$.
-If $z[n]=0$ for $n=L/2,\ldots L-1$ (``zero-padded''), then the periodic and aperiodic autocorrelation coincide.
-In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order periodic autocorrelations determine  a finite list of $K$ generic signals if $L/6\gtrsim K$.
-Empirical evidences hints that this finite list includes only group symmetries, at least as long as $K\leq\sqrt{L}$~\cite{boumal2017heterogeneous}.
-
-\subsection{Estimating autocorrelations from the data with a single signal $K=1$} \label{sec:estimating_ac_k1}
-
-We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$ as will be shown in the next section.
-
-In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
-Specifically, we define the ratio of the measurement occupied by  the signal as
-\begin{equation}
-\gamma = \frac{M L}{N}.
-\end{equation}
-Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-The main pillar of this work is the following simple observation.
-If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
-to a scaled, biased, version of the signal's autocorrelation:
-\begin{align}
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
-\end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
-These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
-The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a particular caution should be taken with the statistical dependencies of the noise entries.
-The relations~\eqref{eq:data_ac_k1}, together with Proposition~\ref{prop:uniqueness}, imply that given $M$ and $\sigma$, one can estimate the signal for any noise level if $M$ is large enough.
-Next, we show that  $M$ and $\sigma$ are also uniquely determined from the autocorrelations.
-
-If the noise level $\sigma^2$ is known, one can estimate the ratio $M/N$ from the first two moments.
-\begin{proposition} \label{prop:gamma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. If the mean of $x$ is nonzero, then 
-	\begin{equation*}
-	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
-	\end{equation*}
-	\begin{proof}
-The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
-\end{proof}
-\end{proposition}
-
-If we use third-order autocorrelation information, then it is possible to estimate both the ratio $M/N$ and $\sigma$ simultaneously.
-\begin{proposition} \label{prop:gamma_sigma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for a generic signal $x$.
-If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
-\begin{corollary}
-	Let $K=1$, $N\to\infty$ and $\sigma$ is fixed. Then, the signal, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions if:
-	\begin{itemize}
-		\item $x$ is generic;
-		\item  $x[0],x[L-1]\neq 0$, $x$ has nonzero mean and $\frac{M}{N}\geq\frac{1}{4(L-1)}$.
-	\end{itemize}
-\end{corollary}
-
-\subsection{Estimating autocorrelations from the data with multiple signals $K>1$} \label{sec:estimating_ac}
-
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
-\begin{align}
-	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
-\end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then one can estimate the mixture of the $K$ signals'  autocorrelations, similarly to~\eqref{eq:data_ac_k1}: 
-\begin{align}
-\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
-\end{align}
-This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
-
-The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
-In methods which are based on detection and averaging, the number of signals occurrences  must scale like $\sigma^2$.
-Taking the $d$th order autocorrelation function amplifies the variance of the noise by a factor of $d$.
-Therefore, the required number signal occurrences should scale like $\sigma^{2d}$  to retain some constant estimation error.
-Accordingly, in our  method, $M$ must scale like $\sigma^6$.
-In Section~\ref{sec:numerics}, we show empirically the third-order autocorrelation suffices also for a mixture of $K>1$ signals without prior knowledge of the $M_i$'s and $\sigma$.
-\TODO{question mark on the entire paragraph}
-\TODO{NB: We could move here the paragraphs from 1D XP about which moments we compute, to argue that we can expect to recover at most up to $K = L/2$ signals.} \TODO{TB: I didn't touch for now.}
-
-\section{Numerical experiments}   \label{sec:numerics}
+\section{Results}
 
@@
 
-%\subsection{One-dimensional experiments}
+\TODO{Revise to explain $K = 1$ experiment first, then explain $K = 3$.}
+\TODO{TB: we should remove the ``long estimation" from the plots}
 
-\TODO{Revise to explain $K = 1$ experiment first, then explain $K = 3$.}
+In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
+In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ .
+An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+As initial guess, we picked Newton image.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect.
+Nonetheless, the more data we collect, the better the reconstruction.\TODO{We have a movie in the supplementary material.}
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.25\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{Newton}
+		\caption{Newton  (model)}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.25\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{Einstein_100}
+		\caption{$P =10^2$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.25\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{Einstein_1e3}
+		\caption{$P =10^3$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.25\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{Einstein_1e4}
+		\caption{$P = 10^4$}
+	\end{subfigure}%
+	\caption{\label{fig:Einst_example} Recovery of Einstein image.
+The algorithm is initialized by the image of Newton.
+We show estimations of Einstein using $P=10^2,10^3$ and $10^4$ number of micrographs, each contains $860$ image occurrences on average.
+The normalized recovery error is $0.555$, $0.3988$ and $0.2907$, respectively.
+The normalized error in recovering the power spectrum was $69.1\times10^{-3} $, $21.7\times10^{-3} $ and $6.8\times10^{-3}$, respectively.
+\TODO{This image will be more impressive in the future}}
+\end{figure}
+
+Here we should describe the 1-D experiments.
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
+	\includegraphics[scale=0.6]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
 	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
@@
 
+\section{Discussion}
+
+All current SPR algorithms start with a particle picking stage which is prone to model bias. 
+In this paper, we propose to examine the possibility to bypass particle picking and estimate the particle directly from the micrograph.
+To this end, we examine a simplified model that share some similarities with the SPR problem.
+The proposed reconstruction method is based on autocorrelation analysis,
+somewhat similar to a technique proposed by Kam which can be used for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
+That being said, the SPR model is far more complicated thans the model presented here. In a future research, we hope to bridge this gap.
+
+Our results rely on two core assumptions that are not necessarily met by in an SPR experiment.  
+First, we modeled the background information as i.i.d.\ additive noise.
+In practice, the background information may be structured or depend on the signal.
+However, methods based on autocorrelation estimation are quite flexible and in many cases can tolerate mismatch of the noise statistical model.
+
+In addition, we assumed that the signal occurrences are all separated, see~\eqref{eq:spacing}. 
+This separation can be induced by careful experiment design \TODO{???}. 
+If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation of the data and the signals.
+It is yet to be studied under what conditions on this distribution one can estimate the signals.
+
+%The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
+Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
+%An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
+
+\section{Methods} \label{sec:methods}
+
+\paragraph{Mathematical model}
+
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
+The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
+\begin{equation} \label{eq:model}
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
+\end{equation}
+%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
+The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
+We denote the set of these nonzero values by 
+ $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
+By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
+Neither the $M_i$'s nor $M$ are assumed to be known.
+Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
+
+In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
+\begin{equation} \label{eq:spacing}
+\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
+\end{equation}
+The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
+
+%
+%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
+%
+%Our method for estimating the signals is composed of two stages. 
+%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
+The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
+Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
+%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
+
+\paragraph{Aperiodic autocorrelation functions}
+%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
+
+For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
+$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
+\begin{align}
+	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
+	\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
+Explicitly, the first three autocorrelations are
+\begin{align} 
+	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
+	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+\end{align}
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
+%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
+
+\paragraph{Estimating the autocorrelation function of a single signal}
+
+We first consider the problem of estimating the autocorrelations of a single signal from the data. 
+The main principles carry through for $K>1$ as will be shown next.
+
+%In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
+For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
+Specifically, we define the ratio of the measurement occupied by  the signal as
+\begin{equation}
+\gamma = \frac{M L}{N}.
+\end{equation}
+Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+The main pillar of this work is the following simple observation.
+If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
+to a scaled, biased, version of the signal's autocorrelation:
+\begin{align}
+\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
+\end{align}
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
+%These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
+
+\paragraph{Estimating the autocorrelation function of a multiple signals}
+
+As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
+\begin{align}
+	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
+\end{align}
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then one can estimate the mixture of the $K$ signals'  autocorrelations, similarly to~\eqref{eq:data_ac_k1}: 
+\begin{align}
+\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\end{align}
+This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
+
+\paragraph{Numerical experiments details}
+
+\TODO{We may want to split it into two sections. Here we could give a short description with the LS estimator and the RRR. In the supplementary material we can provide all other details. }
+
 For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
@@
 
+\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
 Given the observation $y$, we proceed to compute the moments.
@@
 \TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
-
-\TODO{TB: 2D experiment?}
-%\subsection{Two-dimensional experiments} 
-%??
-
-%
-%In this section, we provide the details of the 2D experiment shown in Figure~\ref{fig:example}.
-In the experiment, we generated a sequence of $767\times 10^3$ 2D images (``micrograph") of size $2000\times 2000$.
-Each micrograph had around $\sim 900$ signal occurrences (depends on the stopping criterion that we need to explain) and in total $M = 561\times 10^6$.
-The noise level was $\sigma=1$.
-%
-%To accelerate the experiment, we estimated only the first two autocorrelations of the signal.
-As mentioned in Section~\ref{sec:estimating_ac}, this data determines a 2D signal uniquely, up to possible reflection symmetry.
-%In this experiment, we chose the correct reflection manually.
-To estimate the signal we used the Relax-Reflect-Reflect (RRR) algorithm, which is a known phase retrieval algorithm.
-Recall that the second-order autocorrelation is equivalent to the power spectrum of the signal.
-%Starting form random initialization of size $(2L-1)\times(2L-1)$, its $k$th  iteration take the form of 
-% \begin{equation*}
-% x_k = x_{k-1} + \beta(P_2(2P_1(x_{k-1}) -x_{k-1}) - P_1(x_{k-1}), 
-%  \end{equation*}
-% where $P_1$ is a projection that keeps the values of the  $L\times L$ entries in the upper-left corner and zeros out all other entries, $P_2$ is a projection that keeps the Fourier phase of $x_{k-1}$ and impose the correct Fourier magnitudes, and we set $\beta = 0.5$.
-The solution of the RRR scheme was used to initialized a LS estimation on the first two moments with signals of length $(2L-1)\times(2L-1)$ for the 200 iterations.
-Finally, we chose the $L\times L$ upper left corner and refined it using LS with 500 iterations.
-%
-
-\section{Open questions}
-
-In this paper, we considered the problem of estimating a set of signals from their multiple occurrences in unknown locations in the data.
-We focused on  low $\SNR$ environments in which detection of individual occurrences is impossible.
-Our technique  is based on computing the third-order autocorrelation function of the data with asymptotic estimation rate proportional to $\sigma^6/M$ \TODO{TB: it's not clear to me yet whether we discuss the estimation rate in the paper}.
-Based on related results in multireference alignment~\cite{abbe2018estimation}, we believe that it is the optimal estimation rate, however, this is yet to be proven.
-
-Our results rely on two core assumptions that are not necessarily met by applications. 
-First, we modeled the background information as i.i.d.\ additive noise.
-In practice, the background information may be structured or depend on the signal.
-It raises the question  under what conditions on the background structure and statistics
-one can still estimate the signals in the low $\SNR$ regime.
-
-In addition, we assumed that the signal occurrences are all separated by $L-1$ entries, see~\eqref{eq:spacing}.
-If the signals are not separated, one can introduce a new variable $p$ that represents the distribution of the spacing between signal occurrences.
-The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
-Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
-
-\section{Connection with the cryo--EM problem}
-
-Cryo--EM is an innovative technology for reconstructing the 3D structure of macromolecules. In recent years, structures
-of many molecules, previously regarded as insurmountable, are now being
-reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}.
-This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
-
-In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
-Then,  the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
-Importantly, the micrograph is dominated by noise due to the small electron doses that
-can be applied to the specimen without causing radiation damage.
-
-The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs). 
-All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so-called particle picking, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with an unknown 3D orientation.
-This series of images
- is then used to estimate the structure. 
-However, due to the high noise level, the performance of particle pickers  is not ideal.
-For instance, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the estimation problem.
-In addition, the information from particles that are too close to each other is usually neglected.
-Hence, valuable information that can be harnessed is omitted.
-
-The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}, that is, by skipping the particle picking step.
-In our model, the noisy data $y$ is the analog of the micrograph.
-The $K$ sought signals correspond to $K$ different molecule's projections, each taken from  a different, unknown, viewing direction.
-%In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
-The position of individual projections are  nuisance variables of the cryo--EM problem, in analogy to individual signal's locations in our setup.
-That being said, the cryo--EM data is far more complicated that the simplified model of this paper. In a future research, we hope to bridge this gap.
-
-%For instance, the numerical experiments of Section~\ref{sec:numerics} indicate that we need a huge number of observations to obtain an accurate estimate.
-Can we accelerate the estimation rate?
-How to include nearby molecule to extract all information in the micrograph?
-%In addition, since the size of a micrograph is quite large (typically around $4000\times 4000$ pixels), computing the third-order autocorrelations may be  expensive if not implemented carefully by parallelizing the computations.
-%
 
@@
 For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
+
+\section{Related literature} \label{sec:related_literature}
+
+\paragraph{Blind deconvolution.}
+Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+To make the problem well-posed, we must  assume some prior knowledge or  structure. 
+In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}. 
+Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
+where the focus is on high $\SNR$ regimes.
+
+An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
+The  $s_i$'s  are referred to as \emph{nuisance  variables}.
+Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
+For instance, in image deblurring, both the blurring
+kernel and the high-resolution image are unknown, but the primary goal is only
+to sharpen the image.
+
+\paragraph{The impossibility of detection in low $\SNR$.}
+If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
+To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
+That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location.
+Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
+Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
+As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
+
+\paragraph{System identification.}
+For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+\begin{eqnarray}
+y = x\ast w + \varepsilon,  
+\end{eqnarray} 
+where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
+%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
+this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
+model in the  case of a single signal ($K = 1$).
+
+Likelihood-based methods seek to maximize the likelihood function for $x$,
+given the observed signal $y$. Solving this optimization exactly is typically
+intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
+cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
+The EM method is based upon a certain ``forward-backward'' procedure
+used in hidden Markov models~\cite{rabiner1989tutorial}. 
+However, the complexity of this procedure is still nonlinear in $N$, and therefore its usage is limited for big data sets.   
+Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
+Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
+
+Because likelihood methods are computationally expensive, methods based
+on recovery from moments, which are akin to our method, have
+also been previously used for system identification. 
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+
+\section{Theory} \label{sec:theory}
+
+A one-dimensional signal is determined uniquely and stably by its third-order autocorrelation as proven in the following simple proposition.
+\begin{proposition} \label{prop:uniqueness}
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then:
+	\begin{itemize}
+		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
+		\item \textbf{Finite sensitivity:} 	Suppose we can only measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
+		Then,  $\hat{z}[k] =\frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$. 
+	\end{itemize}
+	\begin{proof}
+		By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
+		Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
+		\begin{equation*}
+		a_z^3[k,L-1] = z[0]z[k]z[L-1].
+		\end{equation*}
+		In addition, 
+		\begin{equation*}
+		\hat{z}[k] = \frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+		\end{equation*} 
+	\end{proof}
+\end{proposition}
+
+A few remarks are in order. 
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
+Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However,  in order to determine the reflection symmetry, one needs to use additional information.
+
+If the noise level $\sigma^2$ is known, one can estimate the ratio $M/N$ from the first two moments.
+\begin{proposition} \label{prop:gamma}
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. If the mean of $x$ is nonzero, then 
+	\begin{equation*}
+	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
+	\end{equation*}
+	\begin{proof}
+		The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
+	\end{proof}
+\end{proposition}
+
+If we use third-order autocorrelation information, then it is possible to estimate both the ratio $M/N$ and $\sigma$ simultaneously.
+\begin{proposition} \label{prop:gamma_sigma}
+	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for a generic signal $x$.
+If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
+\begin{corollary}
+	Let $K=1$, $N\to\infty$ and $\sigma$ is fixed. Then, the signal, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions if:
+	\begin{itemize}
+		\item $x$ is generic;
+		\item  $x[0],x[L-1]\neq 0$, $x$ has nonzero mean and $\frac{M}{N}\geq\frac{1}{4(L-1)}$.
+	\end{itemize}
+\end{corollary}
+
+\paragraph{Expectation-maximization.}
+Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
+This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
+In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
+In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations.
+
+\paragraph{Open theoretical questions.}
+
+The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
+In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
+On the contrary, the required number signal occurrences using the autocorrelation analysis should scale like $1/\SNR^d$  to retain a constant estimation error.
+Accordingly, in our  method, $M$ must scale like $1/\SNR^3$.
+We believe that similarly to the closely-related problem of multirefrence alignment~\cite{perry2017sample,abbe2017multireference}, this estimation rate is optimal in the low $\SNR$ regime.
+
+In addition, the  third-order autocorrelation succeeds, empirically, to demix  $K>1$ signals, even without prior knowledge of the $M_i$'s and $\sigma$.
+Based on the following equation counting, we believe that one can demix up $\approx L/2$ signals.
+\TODO{Here we can add the equations counting argument. Do we want to consider also conjecture on the computational limit?}
 

### 2018-05-07 TEX/draft3.tex
Some updates for the introduction section

@@
 Single particle reconstruction (SPR) using cryo--electron microscopy (cryo--EM) is an innovative technology for reconstructing the 3-D structure of macromolecules. In recent years, structures
-of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}.
+of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
 This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
@@
 The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with an unknown 3D orientation.
+The output of ideal particle picker is a series of 2D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
 This series of images
@@
 For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm performance depends on the user prior assumption about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled set of data.
-Other methods use disks or difference of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while exploits the researcher's experience, is both tedious and subject to model bias.
+Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
+Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
 
@@
 Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-As a result, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the reconstruction algorithm.
-In addition, the information from particles that are too close to each other is usually neglected.
-Hence, valuable information that can be harnessed is omitted.
+As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
+%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
 
-\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims showing that estimating a particle 
-directly from the micrograph might be possible.
+\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims to show that estimating a particle 
+directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
 
-In particular, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
-Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle that appear multiple times in the micrograph.
+In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
+Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
 A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-To be clear, we do not consider here many prominent features of SPR experiment and do not aim to reconstruct any 3-D structure.
-We also mention by passing that this model appears in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
+We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
@@
 The left panel shows the data without noise.
-In the middle panel, an i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
-In this scenario, even for $K>1$, it is likely that standard detection and clustering algorithms can locate and cluster the copies of the signals that can be then averaged within each class.
+In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
+In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
 In the right panel, we show the same data swamped in
 i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
-As a matter of fact, it can be shown that in  low signal--to--noise (\SNR) regime, 
+Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise (\SNR) regime, 
 detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
@@
 \paragraph{Autocorrelation analysis.}
-In order to recover the signal from the data, we use autocorrelation analysis.
+We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
+In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
 In a nutshell, the method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the size of the signal and  each signal appears sufficiently many times in the data.
-There is no need to detect individual occurrences, knowing the number of signal occurrences $M$ or the noise level.
-In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) or phase retrieval algorithms; see Section~\ref{sec:methods}.
-This method requires only one pass over the data and can recover the signals in any $\SNR$ level, if the signals appear enough times in the data.
+These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data.
+There is no need to detect individual occurrences.
+In the second stage, the signals are estimated from the mixed autocorrelations using a a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods}.
+This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
 As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).

### 2018-05-07 patent provisional/Experimental verification/Experimental verification.tex
patent provisional -- first draft

--- 2018-05-07 TEX/draft3.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\numberwithin{equation}{section}
+%\numberwithin{equation}{section}
 %\numberwithin{figure}{section}
@@
 \newtheorem{lem}[thm]{\protect\lemmaname}
-
-\newtheorem*{lem*}{Lemma}
-
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-\theoremstyle{plain}
-\newtheorem{corollary}[thm]{\protect\corollaryname}
-\theoremstyle{plain}
-\newtheorem{proposition}[thm]{\protect\propositionname}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+%
+%\newtheorem*{lem*}{Lemma}
+%
+%\theoremstyle{remark}
+%\newtheorem{rem}[thm]{\protect\remarkname}
+%\theoremstyle{plain}
+%\newtheorem{corollary}[thm]{\protect\corollaryname}
+%\theoremstyle{plain}
+%\newtheorem{proposition}[thm]{\protect\propositionname}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 %\usepackage{slashbox}
@@
 \usepackage{babel}
-\providecommand{\claimname}{Claim}
-\providecommand{\definitionname}{Definition}
-\providecommand{\lemmaname}{Lemma}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-\providecommand{\corollaryname}{Corollary}
-\providecommand{\propositionname}{Proposition}
+%\providecommand{\claimname}{Claim}
+%\providecommand{\definitionname}{Definition}
+%\providecommand{\lemmaname}{Lemma}
+%\providecommand{\remarkname}{Remark}
+%\providecommand{\theoremname}{Theorem}
+%\providecommand{\corollaryname}{Corollary}
+%\providecommand{\propositionname}{Proposition}
 
@@
 \newcommand{\CNN}{\mathbb{C}^{N\times N}}
-\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\hx}{\hat{x}} 
-\newcommand{\one}{\mathbf{1}} 
+%\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
+%\newcommand{\hx}{\hat{x}} 
+%\newcommand{\one}{\mathbf{1}} 
 \newcommand{\SNR}{{\textsf{SNR}}}
@@
 
-\title{Toward single particle reconstruction without particle picking}
+\title{Experimental verification}
 
@@
 
-\begin{abstract}
-	Here comes the abstract
-\end{abstract}
-
-\section{Introduction}
-
-Single particle reconstruction (SPR) using cryo--electron microscopy (cryo--EM) is an innovative technology for reconstructing the 3-D structure of macromolecules. In recent years, structures
-of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
-
-In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
-Then, the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
-The micrograph is dominated by noise due to the small electron doses that
-can be applied to the specimen without causing radiation damage.
-The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs).
-
-\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
-This series of images
-is then used to estimate the structure.
-
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
-
-The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are then aligned to Einstein's image using cross-correlation and  averaged. 
-In~\cite{shatsky2009method}, it was shown that using merely 1000 noise images, the averaged image is remarkably similar to the template image of 
-Einstein, rather than to pure noise. 
-%Therefore, such a simple algorithm is biased towards its model which is an undesirable property. 
-In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-
-Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
-%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
-
-\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims to show that estimating a particle 
+In this note, we present a preliminary study that aims to show that estimating a particle 
 directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible. 
-
-In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
+In particular, we consider the problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
 Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
 To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
-We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
@@
 Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise (\SNR) regime, 
-detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Section~\ref{sec:related_literature}.
+detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible~\cite{aguerrebere2016fundamental}.
 
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d./ Gaussian noise with variance $\sigma^2$.
+	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
 Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
@@
 
+\paragraph{Mathematical model}
+
+To be concrete, we formulate the problem for one-dimensional signals. The extension to multi-dimensional signals is straight-forward.
+
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
+The forward model can be posed as a mixture of {blind deconvolution} problems between binary signals and the target signals $x_i$:
+\begin{equation} \label{eq:model}
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
+\end{equation}
+The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$; see Figure~\ref{fig:micro_example} for an example.
+We assume that the nonzero values of $s$ are separated by at least $L-1$ entries.
+In the multi-dimensional case, this separation is imposed in each axis.
+
 \paragraph{Autocorrelation analysis.}
-We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
 In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
@@
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data.
+Then, we estimate the signal itself using non-convex least-squares (LS) or a phase retrieval algorithm.
+
+\paragraph{Autocorrelation functions.}
+We recall that the first-order autocorelation is the mean of the signals. For  
+$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
+\begin{align}
+a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
+\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
+Explicitly, the first three autocorrelations are
+\begin{align} 
+a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
+a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+\end{align}
+
+\paragraph{Esimtating the mixture of the signals' autocorrelation from the data.}
+A mixture of the $K$ signals' autocorrelation functions can be estimated, to any desired accuracy, if individual occurrences are separated by  $L-1$ entries in each direction and each signal appears sufficiently many times in the data.
 There is no need to detect individual occurrences.
-In the second stage, the signals are estimated from the mixed autocorrelations using a a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods}.
-This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
 
-\section{Results}
+Let $M_i$ denote the number of occurrences of the $i$th signal. 
+Let us denote
+\begin{align}
+\gamma_k = \frac{M_k L}{N}.
+\end{align}
+Then, under the spacing constraint discussed above, one can show that
+\begin{align} 
+\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\end{align}
 
-%\TODO{Here we should say that we can afford to work only with non-biased terms}
+\paragraph{Numerical experiments.}
+In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ . An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+We used a micrograph of size $4000\times 4000$ and insert Einstein's images in random locations, while preserving the separation constraint.
+On average, each micrograph includes $860$ images.
+We then computed the first
+We computed the first and second moment of the data and estimated the associated moments of the image using~\eqref{eq:data_ac}.
+We recall that the second moment is equivalent to the Fourier magnitude of the signal and therefore one can use standard phase retrieval algorithms.
+Here, we use an algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix} that iterates by
+\begin{equation}
+x_{\ell+1} = x_\ell  + P_2(2P_1(x_\ell) - x_\ell) - P_1(x_\ell),
+\end{equation}
+where $P_2(z)$ combines the Fourier phases of $z$ with the Fourier magnitudes estimated from the data, and $P_1$ zeros out the signal out of its support. 
+If the Fourier magnitude are estimated exactly, then the algorithm produces the signal or its reflection through the origin. 
+In  we show an example how the reconstruction error decreases with as we collect more micrographs.
 
-\TODO{Revise to explain $K = 1$ experiment first, then explain $K = 3$.}
-\TODO{TB: we should remove the ``long estimation" from the plots}
-
-In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
-In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ .
-An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-As initial guess, we picked Newton image.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect.
-Nonetheless, the more data we collect, the better the reconstruction.\TODO{We have a movie in the supplementary material.}
+ \TODO{We have a movie in the supplementary material.} 
+ \TODO{To add a figure of the error as a function of the number of micrographs.}
 
@@
 	\centering
-	\begin{subfigure}[h]{0.25\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{Newton}
-		\caption{Newton  (model)}
-	\end{subfigure}%
 	\begin{subfigure}[h]{0.25\textwidth}
@@
 The normalized recovery error is $0.555$, $0.3988$ and $0.2907$, respectively.
-The normalized error in recovering the power spectrum was $69.1\times10^{-3} $, $21.7\times10^{-3} $ and $6.8\times10^{-3}$, respectively.
-\TODO{This image will be more impressive in the future}}
+The normalized error in recovering the power spectrum was $69.1\times10^{-3} $, $21.7\times10^{-3} $ and $6.8\times10^{-3}$, respectively.}
 \end{figure}
-
-Here we should describe the 1-D experiments.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[scale=0.6]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
-	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-	\label{fig:1Dhomosignals}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n10000000000_107521}
-	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-	\label{fig:1DhomoRMSE}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.9\linewidth]{XP_1D_heterogeneous/data_example_heterogeneous_n_24600000000_604392_fig1}
-	\caption{\TODO{Thin yellow is ground truth; blue is ROI of first optimization; red is final estimation.
-Relative error for blue is .37, and .13 for red.
-Individual relative errors of the red estimates: 0.0239393 / 0.208925 / 0.0335956}}
-	\label{fig:1Dheterosignals}
-\end{figure}
-
-\section{Discussion}
-
-All current SPR algorithms start with a particle picking stage which is prone to model bias. 
-In this paper, we propose to examine the possibility to bypass particle picking and estimate the particle directly from the micrograph.
-To this end, we examine a simplified model that share some similarities with the SPR problem.
-The proposed reconstruction method is based on autocorrelation analysis,
-somewhat similar to a technique proposed by Kam which can be used for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
-That being said, the SPR model is far more complicated thans the model presented here. In a future research, we hope to bridge this gap.
-
-Our results rely on two core assumptions that are not necessarily met by in an SPR experiment.  
-First, we modeled the background information as i.i.d.\ additive noise.
-In practice, the background information may be structured or depend on the signal.
-However, methods based on autocorrelation estimation are quite flexible and in many cases can tolerate mismatch of the noise statistical model.
-
-In addition, we assumed that the signal occurrences are all separated, see~\eqref{eq:spacing}. 
-This separation can be induced by careful experiment design \TODO{???}. 
-If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation of the data and the signals.
-It is yet to be studied under what conditions on this distribution one can estimate the signals.
-
-%The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
-Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-%An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
-
-\section{Methods} \label{sec:methods}
-
-\paragraph{Mathematical model}
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
-The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
-\begin{equation} \label{eq:model}
-y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
-\end{equation}
-%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
-We denote the set of these nonzero values by 
- $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-Neither the $M_i$'s nor $M$ are assumed to be known.
-Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
-
-In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
-\begin{equation} \label{eq:spacing}
-\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
-\end{equation}
-The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
-
-%
-%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
-%
-%Our method for estimating the signals is composed of two stages. 
-%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
-Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
-
-\paragraph{Aperiodic autocorrelation functions}
-%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
-$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
-\begin{align}
-	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
-	\label{eq:ac_general}
-\end{align}
-where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
-Explicitly, the first three autocorrelations are
-\begin{align} 
-	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
-	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
-%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
-
-\paragraph{Estimating the autocorrelation function of a single signal}
-
-We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$ as will be shown next.
-
-%In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
-Specifically, we define the ratio of the measurement occupied by  the signal as
-\begin{equation}
-\gamma = \frac{M L}{N}.
-\end{equation}
-Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-The main pillar of this work is the following simple observation.
-If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
-to a scaled, biased, version of the signal's autocorrelation:
-\begin{align}
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
-\end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
-%These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
-
-\paragraph{Estimating the autocorrelation function of a multiple signals}
-
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
-\begin{align}
-	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
-\end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then one can estimate the mixture of the $K$ signals'  autocorrelations, similarly to~\eqref{eq:data_ac_k1}: 
-\begin{align}
-\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
-\end{align}
-This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
-
-\paragraph{Numerical experiments details}
-
-\TODO{We may want to split it into two sections. Here we could give a short description with the LS estimator and the RRR. In the supplementary material we can provide all other details. }
-
-For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
-Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The SNR of $y$
-% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/12.
-%Given the scaling of the target signals (whose median absolute value for the entries is at or below one),
-This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-Given the observation $y$, we proceed to compute the moments.
-The first-order moment is straightforward.
-For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
-As a result, it is unnecessary to estimate $\sigma$.
-We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-moments in total.
-In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-
-Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-\begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
-Issue is: this is not very smart..}.
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing \TODO{we should understand / explain this}) that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
-Not sure it's worth the effort.
--- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
-\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
 
@@
 
-\section{Autocorrelation estimations} \label{sec:autocorrelation_computation}
-
-Throughout the proof, we consider the case of one signal $K=1$.
-The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriates weights, see~\cite{boumal2017heterogeneous}.
-
-Let us define
-\begin{equation}
-\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
-\end{equation}
-With a bit abuse of notation, $M_N$ stresses that $M$ is a function of $N$. Indeed, by assuming $M_N=\Omega(N)$, we deduce $\gamma>0$.
-We start by considering the first autocorrelation of the data
-\begin{equation}
-a_y^1 = \sum_{i=0}^{N-1} y[i] = \frac{1}{N/L}\sum_{j=0}^{M_N-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}} \xrightarrow{a.s.}\gamma a_x^1,
-\end{equation}
-where the noise term converges to zero almost surely (a.s.) by the law of large numbers.
-
-We proceed with the second autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
-\begin{equation}
-\begin{split}
-a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
-& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
-\end{split}
-\end{equation}
-where the cross terms between the signal and the noise vanish  almost surely in the limit $N\to\infty$.
-
-We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
-\begin{equation} \label{eq:2nd_moment_signal_term}
-\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
-\end{equation}
-Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
-\begin{equation}
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-\end{equation}
-Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
-If $\ell=0$, 
-\begin{equation}
-\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
-\end{equation}
-
-We are now moving to analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
-\begin{equation*}
-a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
-\end{equation*}
-Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
-The first contains only signal terms (does not see noise) and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-Three other terms contain the product of two signal entries and one noise term.
-Since the noise is independent of the signal and has zero mean, these terms go to zero almost surely.
-
-We next analyze the contribution of the term composed of triple products of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
-\begin{equation*}
-\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
-\end{equation*}
-For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
-For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each one is a triple product of Gaussian variables with zero mean and therefore has zero expectation.
-
-To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
-Most of these terms converge to zero almost surely because of independency between the noise entries.
-For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
-
-\section{Related literature} \label{sec:related_literature}
-
-\paragraph{Blind deconvolution.}
-Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-To make the problem well-posed, we must  assume some prior knowledge or  structure. 
-In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}. 
-Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
-where the focus is on high $\SNR$ regimes.
-
-An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
-The  $s_i$'s  are referred to as \emph{nuisance  variables}.
-Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
-For instance, in image deblurring, both the blurring
-kernel and the high-resolution image are unknown, but the primary goal is only
-to sharpen the image.
-
-\paragraph{The impossibility of detection in low $\SNR$.}
-If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
-That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location.
-Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
-Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
-As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
-
-\paragraph{System identification.}
-For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
-\begin{eqnarray}
-y = x\ast w + \varepsilon,  
-\end{eqnarray} 
-where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
-this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
-model in the  case of a single signal ($K = 1$).
-
-Likelihood-based methods seek to maximize the likelihood function for $x$,
-given the observed signal $y$. Solving this optimization exactly is typically
-intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
-cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
-The EM method is based upon a certain ``forward-backward'' procedure
-used in hidden Markov models~\cite{rabiner1989tutorial}. 
-However, the complexity of this procedure is still nonlinear in $N$, and therefore its usage is limited for big data sets.   
-Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
-Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
-
-Because likelihood methods are computationally expensive, methods based
-on recovery from moments, which are akin to our method, have
-also been previously used for system identification. 
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-
-\section{Theory} \label{sec:theory}
-
-A one-dimensional signal is determined uniquely and stably by its third-order autocorrelation as proven in the following simple proposition.
-\begin{proposition} \label{prop:uniqueness}
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then:
-	\begin{itemize}
-		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
-		\item \textbf{Finite sensitivity:} 	Suppose we can only measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-		Then,  $\hat{z}[k] =\frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$. 
-	\end{itemize}
-	\begin{proof}
-		By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
-		Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
-		\begin{equation*}
-		a_z^3[k,L-1] = z[0]z[k]z[L-1].
-		\end{equation*}
-		In addition, 
-		\begin{equation*}
-		\hat{z}[k] = \frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
-		\end{equation*} 
-	\end{proof}
-\end{proposition}
-
-A few remarks are in order. 
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
-Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However,  in order to determine the reflection symmetry, one needs to use additional information.
-
-If the noise level $\sigma^2$ is known, one can estimate the ratio $M/N$ from the first two moments.
-\begin{proposition} \label{prop:gamma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. If the mean of $x$ is nonzero, then 
-	\begin{equation*}
-	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
-	\end{equation*}
-	\begin{proof}
-		The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
-	\end{proof}
-\end{proposition}
-
-If we use third-order autocorrelation information, then it is possible to estimate both the ratio $M/N$ and $\sigma$ simultaneously.
-\begin{proposition} \label{prop:gamma_sigma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for a generic signal $x$.
-If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
-\begin{corollary}
-	Let $K=1$, $N\to\infty$ and $\sigma$ is fixed. Then, the signal, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions if:
-	\begin{itemize}
-		\item $x$ is generic;
-		\item  $x[0],x[L-1]\neq 0$, $x$ has nonzero mean and $\frac{M}{N}\geq\frac{1}{4(L-1)}$.
-	\end{itemize}
-\end{corollary}
-
-\paragraph{Expectation-maximization.}
-Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations.
-
-\paragraph{Open theoretical questions.}
-
-The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
-In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
-On the contrary, the required number signal occurrences using the autocorrelation analysis should scale like $1/\SNR^d$  to retain a constant estimation error.
-Accordingly, in our  method, $M$ must scale like $1/\SNR^3$.
-We believe that similarly to the closely-related problem of multirefrence alignment~\cite{perry2017sample,abbe2017multireference}, this estimation rate is optimal in the low $\SNR$ regime.
-
-In addition, the  third-order autocorrelation succeeds, empirically, to demix  $K>1$ signals, even without prior knowledge of the $M_i$'s and $\sigma$.
-Based on the following equation counting, we believe that one can demix up $\approx L/2$ signals.
-\TODO{Here we can add the equations counting argument. Do we want to consider also conjecture on the computational limit?}
-
-\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-
-We aim to prove that one can estimate both $\sigma$ and $\beta = M/N$ from the observed first three moments.
-To this end, we construct two quadratic equations of $\beta$ from the observed (measured) quantities, independent of $\sigma$.
-Then, we show that these equations are independent and therefore $\beta$ is uniquely defined. 
-Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
-Throughout the proof, it is important to distinguish between observed and unobserved values. 
-to this end, we denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
-
-Recall that $a_y^1 = \beta(\one^Tx)$ and  
-and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ stands for vector of ones. Taking the product:
-\begin{equation}\label{eq:E1}
-\begin{split}
-E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
-& = \sigma^2a_y^1 + \beta^2F_1,
- \end{split}
-\end{equation}
-where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
-The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account:
-\begin{equation} \label{eq:E2}
-E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
-\end{equation}
-Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
-\begin{equation} \label{eq:E12}
-E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
-\end{equation}
-Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
-\begin{equation} \label{eq:sigma2}
-\sigma^2 = a_y^2 - (a^1_y)^2/(\beta L). 
-\end{equation} 
-Plugging into~\eqref{eq:E12} and rearranging we get 
-\begin{equation} \label{eq:quad1}
-\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
-\end{equation}
-where 
-\begin{align*}
-\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
-\mathcal{B} &= -E_1 + \frac{2L+1}{L}(a_y^1)^3 + a_y^1a_y^2  , \\
-\mathcal{C} &= -(a_y^1)^3/L.
-\end{align*}
-Importantly, these coefficients are observable quantities.
-
-We are now proceeding to derive the second quadratic equation. We notice that 
-\begin{equation} \label{eq:E3}
-E_3  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \frac{1}{L}\beta^3 F_2,
-\end{equation}
-where 
-\begin{equation*}
-F_2 =  a_x^3[0,0] + 3\sum_{j=1}^{L-1}a_x^3[j,j] + 3\sum_{j=1}^{L-1}a_x^3[0,j] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
-\end{equation*}
-On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
-\begin{equation} \label{eq:E4}
-E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
-\end{equation}
-Taking the ratio:
-\begin{equation*} 
-\frac{E_4}{E_3} = \frac{L}{\beta^2} + \frac{(6L-3)L\sigma^2a_y^1}{E_3}, 
-\end{equation*}
-we conclude:
-\begin{equation*}
-\sigma^2 = \frac{E_4}{a_y^1L(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
-\end{equation*}
-Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
-\begin{equation} \label{eq:quad2}
-\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
-\end{equation}
-where
-\begin{align*}
-\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
-\mathcal{E} &= -(a_y^1)^2/L, \\
-\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
-\end{align*}
-
-To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
-To this end, it is enough to show that the ratio between the coefficients is not the same.
-From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
-\begin{equation*}
-\begin{split}
-\frac{\mathcal{B}}{\mathcal{C}} &= \frac{LE_1 - (2L+1)(a_y^1)^3 - La_y^1a_y^2}{(a_y^1)^3} \\&= \frac{La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2}{(a_y^1)^2}.
-\end{split}
-\end{equation*}
-In addition, using~\eqref{eq:E3}
-\begin{equation*}
-\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_3} = 3 - 6L . 
-\end{equation*}
-
-Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
-\begin{equation*}
-La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
-\end{equation*}
-Rearranging the equation and writing in terms of $x$ we get 
-\begin{equation} \label{eq:cond}
-4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
-\end{equation}	
-For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
-More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
-\begin{equation*}
-\beta \geq \frac{1}{4(L-1)},
-\end{equation*}
-the condition~\eqref{eq:cond} cannot be satisfied for any signal.
-
 \end{document}

### 2018-05-08 patent provisional/Experimental verification/Experimental verification.tex
updating the experimental verification section

@@
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
-\newcommand{\CNN}{\mathbb{C}^{N\times N}}
+\newcommand{\RLL}{\mathbb{R}^{L\times L}}
 %\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
@@
 
-To be concrete, we formulate the problem for one-dimensional signals. The extension to multi-dimensional signals is straight-forward.
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
+To be concrete, we formulate the problem for two-dimensional signals. 
+Let $x_1,\ldots,x_K\in\RLL$ be the sought signals and let $y\in\RNN$ be the data (i.e., micrograph). 
 The forward model can be posed as a mixture of {blind deconvolution} problems between binary signals and the target signals $x_i$:
 \begin{equation} \label{eq:model}
-y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I),
 \end{equation}
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$; see Figure~\ref{fig:micro_example} for an example.
-We assume that the nonzero values of $s$ are separated by at least $L-1$ entries.
-In the multi-dimensional case, this separation is imposed in each axis.
+where $\ast$ stands for convolution.
+The nonzero values of each  $s_i\in\{0,1\}^{N\times N}$ determine the position of the occurrences of the corresponding $x_i$; see Figure~\ref{fig:micro_example} for an example for $K=1$.
+We assume a \emph{separation condition} on the binary signals $s=\sum_{i=1}^Ks_i$, that is, the nonzero values of $s$ are separated by at least $L-1$ entries in both axes.
 
@@
 \end{align}
+The extension to multi-dimensional signals is straight-forward.
 
@@
 
-Let $M_i$ denote the number of occurrences of the $i$th signal. 
-Let us denote
+Let $M_i$ denote the number of occurrences of the $i$th signal and  
+let us denote
 \begin{align}
@@
 \lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]).
+\nonumber
 \end{align}
+The same  holds for multi-dimensional signals.
 
 \paragraph{Numerical experiments.}
-In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ . An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-We used a micrograph of size $4000\times 4000$ and insert Einstein's images in random locations, while preserving the separation constraint.
-On average, each micrograph includes $860$ images.
-We then computed the first
-We computed the first and second moment of the data and estimated the associated moments of the image using~\eqref{eq:data_ac}.
-We recall that the second moment is equivalent to the Fourier magnitude of the signal and therefore one can use standard phase retrieval algorithms.
+In the first experiment, we estimated Einstein's image from micrographs contaminated with i.i.d.\ Gaussian noise with standard deviation of $\sigma=3$ .
+An example for such micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+
+In the experiment, we generated $P$ micrographs, each of size $4000\times 4000$ pixels. 
+Within each micrograph, Einstein's images were embedded in random locations, while preserving the separation constraint. On average, each micrograph contains $860$ images. We then computed the first
+and second moment of the data and estimated the associated moments of the image using~\eqref{eq:data_ac}.
+We recall that the second moment is equivalent to the Fourier magnitude of the signal and therefore one can use standard phase retrieval algorithms to recover the signal, up to reflection through the origin.
 Here, we use an algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix} that iterates by
@@
 where $P_2(z)$ combines the Fourier phases of $z$ with the Fourier magnitudes estimated from the data, and $P_1$ zeros out the signal out of its support.
-If the Fourier magnitude are estimated exactly, then the algorithm produces the signal or its reflection through the origin. 
-In  we show an example how the reconstruction error decreases with as we collect more micrographs.
 
- \TODO{We have a movie in the supplementary material.} 
- \TODO{To add a figure of the error as a function of the number of micrographs.}
+Figure~\ref{fig:Einst_example} shows three example for the reconstructed image using a different number of micrographs.
+Figure~\ref{fig:error_per_micro}  presents the normalized recovery error as a function of the number of micrographs used in the experiment.
+The error is computed by
+\begin{equation}
+\text{recovery error} = \frac{\|x - \hat{x}\|\|x\|_{\text{F}}}{\|x\|_{\text{F}}},
+\label{eq:error}
+\end{equation}
+where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$
+denotes the Frobenius norm. We also present the normalized estimation error of the second-moment (power spectrum). The slope in a log-log plot is $-1/2$ as expected.
 
@@
 
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+	 \includegraphics[scale=0.6]{err_rrr_per_micrograph}
+    \caption{\label{fig:error_per_micro}}	
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+	 \includegraphics[scale=0.6]{err_PS_per_micrograph}
+\caption{}	
+	\end{subfigure}%
+	\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined~\eqref{eq:error} in as a function of the number of the collected micrographs.
+The right panel presents the error of estimating the power spectrum of the signal from the data.
+As expected, in log-log scale, the curve has a $-1/2$ slope.}
+\end{figure}
+
 \bibliographystyle{plain}

### 2018-05-11 TEX/draft3.tex
updated draft 3

@@
 All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
+The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2-D tomographic projections of the samples from the noisy micrograph.
+The output of ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
 This series of images
@@
 detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Section~\ref{sec:related_literature}.
+This phenomenon is explained in detail in Appendix~\ref{sec:related_literature}.
 
@@
 There is no need to detect individual occurrences.
-In the second stage, the signals are estimated from the mixed autocorrelations using a a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods}.
+In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
 This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
@@
 
-%\TODO{Here we should say that we can afford to work only with non-biased terms}
+In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
+In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$. An illustrative example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+Multiple occurrences of the image were placed 
+in $P$ micrographs, each of of size $4000\times 4000$ pixels, while the images to be separated by the image's length in each direction.
+From the micrographs, we estimated the first and second order autocorrelation and used a standard phase retrieval algorithm, called relaxed-reflect-reflect, to estimate the image.
+\TODO{We have a movie in the supplementary material.}
 
-\TODO{Revise to explain $K = 1$ experiment first, then explain $K = 3$.}
-\TODO{TB: we should remove the ``long estimation" from the plots}
-
-In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
-In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ .
-An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-As initial guess, we picked Newton image.
+As initial guess, we picked an image of the physicist Issac Newton.
 If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect.
-Nonetheless, the more data we collect, the better the reconstruction.\TODO{We have a movie in the supplementary material.}
+However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
+Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of micrographs collected.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
+To measure error, we use the root mean square error (RMSE) defined as 
+\begin{equation}
+\text{RMSE}  = \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
+\end{equation} 
+where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ is the Frobenius norm. 
+As expected, the RMSE of estimating the power spectrum (an equivalent quantity to the second-order autocorrelation)  decreases linearly with slope $-1/2$ in logarithmic scale.
+\TODO{What about the error?}
 
@@
 
-Here we should describe the 1-D experiments.
+Results from a similar experiment for 1-D signals is presented in Figures~\ref{fig:1Dhomosignals} and~\ref{fig:1DhomoRMSE}.
+Here, we used nonconvex least-squares (LS) to estimate the signal and the estimated number of its occurrences.
+We do not assume the knowledge of the noise level. 
+Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
+\TODO{We may want to replace with an experiment with colored noise}
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+		\includegraphics[scale=0.6]{err_rrr_per_micrograph}
+		\caption{}	
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+		\includegraphics[scale=0.6]{err_PS_per_micrograph}
+		\caption{}	
+	\end{subfigure}%
+	\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined in~\eqref{eq:error} as a function of the number of the collected micrographs.
+The right panel presents the error of estimating the power spectrum of the signal from the data.
+As expected, in log-log scale, the curve has a $-1/2$ slope.}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[scale=0.6]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
+	\includegraphics[scale=0.45]{progressive_n}
 	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n10000000000_107521}
+	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
 	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
@@
 
+Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
+\begin{equation}
+\gamma_i = \frac{M_i L}{N},
+\end{equation}
+where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
+As can be seen, given enough signals occurrences, we can estimate accurately the signals.
+he estimation quality
+is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
+
 \begin{figure}[t]
 	\centering
-	\includegraphics[width=0.9\linewidth]{XP_1D_heterogeneous/data_example_heterogeneous_n_24600000000_604392_fig1}
-	\caption{\TODO{Thin yellow is ground truth; blue is ROI of first optimization; red is final estimation.
-Relative error for blue is .37, and .13 for red.
-Individual relative errors of the red estimates: 0.0239393 / 0.208925 / 0.0335956}}
+	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
+	\caption{Red signals are the ground truth (targets) and the blue signals are our estimations.
+Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$.
+The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$.
+The $\SNR$ is $1/12$.}
 	\label{fig:1Dheterosignals}
@@
 
-All current SPR algorithms start with a particle picking stage which is prone to model bias. 
-In this paper, we propose to examine the possibility to bypass particle picking and estimate the particle directly from the micrograph.
-To this end, we examine a simplified model that share some similarities with the SPR problem.
-The proposed reconstruction method is based on autocorrelation analysis,
-somewhat similar to a technique proposed by Kam which can be used for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
-That being said, the SPR model is far more complicated thans the model presented here. In a future research, we hope to bridge this gap.
+All current algorithmic pipeline for SPR using cryo--EM start with a particle picking technique which is prone to model bias. 
+Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to the construction of ab initio models or to generate multiple denoised projections that can be used for 2-D classification.
+It might be even possible to use such templates for the particle picking stage, now with templates that were extracted from the data itself.
+
+In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
+While Bayesian algorithms are currently dominate the field, they are intractable for our problem.
+As alternative, we propose to use autocorrelation analysis technique that shares some common lines  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
+That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
 
 Our results rely on two core assumptions that are not necessarily met by in an SPR experiment.  
-First, we modeled the background information as i.i.d.\ additive noise.
-In practice, the background information may be structured or depend on the signal.
-However, methods based on autocorrelation estimation are quite flexible and in many cases can tolerate mismatch of the noise statistical model.
+First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or depend on the signal. 
+Yet, autocorrelation analysis is easily adapted to different noise statistics. \TODO{Here, an example with colored noise would be of great help.}
 
-In addition, we assumed that the signal occurrences are all separated, see~\eqref{eq:spacing}. 
-This separation can be induced by careful experiment design \TODO{???}. 
+In addition, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
+This separation can be induced by careful experimental design \TODO{???}. 
 If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation of the data and the signals.
 It is yet to be studied under what conditions on this distribution one can estimate the signals.
+
+\TODO{need a lot of signal occurrences}
 
@@
 \paragraph{Numerical experiments details}
+For the 2-D experiment, we generated $P$ micrographs of size $4000\times 4000$ with Einstein's image of size $50\times 50$. 
+In each micrograph, we placed the image in random locations while keeping the separation condition~\eqref{eq:spacing}.
+In particular, to picked a random location on the micrograph and used an accept/reject rule based on the separation constraint and locations picked so far.
+We stopped the process when we reached the desired number of occurrences, or the micrograph was dense enough so that we failed to find an open space (randomly) repeatedly.
+Then, an i.i.d.\ Gaussian noise was added.
+On average, each micrograph contains $860$ images and the signal--to--noise ratio ($\SNR$) is approximately $1/18$. 
+Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
 
-\TODO{We may want to split it into two sections. Here we could give a short description with the LS estimator and the RRR. In the supplementary material we can provide all other details. }
+Given the micrographs $y$, we proceed to compute the moments.
+In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the autocorrelation function.
+To ease the computation, we assume to know the number of Einstein's occurrences and the noise level.
+This allow us to compute only the first and second moment.
+In dimensional greater than one, almost all images are uniquely determined from their second-order aperiodic up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
+To estimate the signal, we use a popular algorithm called relaxed-reflect-reflect (RRR) iterates as
+\begin{equation}
+x_{\ell+1} = x_\ell + \beta (P_2(2P_1(x_\ell) - x_\ell) - P_1(x_\ell)).
+\end{equation}
+The RRR estimates a $2L\times 2L$ image.
+Exact solution contains Einstein's image in the upper-left corner and zero else where.
+The operation $P_1(z)$ combines the Fourier phases of  $z$ with the Fourier transform of the second-order autocorrelation, which in the absence of noise, is exactly the Fourier magnitude of the solution.
+The operator $P_1(z)$ zeros out all entries of $z$ outside the upper-left corner.
 
-For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
+For the 1D experiment, we worked with signals of length $L = 21$ and generated the data in the same way as in the 2D example.
+However, here we computed the first three autocorrelation functions.
+We removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ ahead.
+To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
+\begin{multline}
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+\label{eq:optim1D}
+\end{multline}
+where $W \geq L$ is the length of the sought signals and $w_1 = 1/2, w_2 = 1/2(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion in choosing the weights properly.
+
+ Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest the measured ones in the sense of~\eqref{eq:optim1D}.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+%For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
 Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
 Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+%This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
 For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
@@
 % sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/12.
-%Given the scaling of the target signals (whose median absolute value for the entries is at or below one),
-This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
+%is about 1/12.
+
+%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
 Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
 
-\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-Given the observation $y$, we proceed to compute the moments.
+%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
+%
+%Given the observation $y$, we proceed to compute the moments.
 The first-order moment is straightforward.
@@
 We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-moments in total.
+%\begin{align*}
+%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+%\end{align*}
+%moments in total.
 In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
@@
 If multiple GPUs are available, segments can of course be handled in parallel.
-
-Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+%
+%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
 We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-\begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
+%\begin{multline}
+%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+%\label{eq:optim1D}
+%\end{multline}
+%where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
 Issue is: this is not very smart..}.
 Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-Thus, we first run the optimization with $W = 2L-1$.
+%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+%Thus, we first run the optimization with $W = 2L-1$.
 This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
@@
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
+%\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
 Not sure it's worth the effort.
 -- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
-\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
+%\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
+%
+%
 
@@
 
-In addition, the  third-order autocorrelation succeeds, empirically, to demix  $K>1$ signals, even without prior knowledge of the $M_i$'s and $\sigma$.
-Based on the following equation counting, we believe that one can demix up $\approx L/2$ signals.
-\TODO{Here we can add the equations counting argument. Do we want to consider also conjecture on the computational limit?}
+Another interesting question is how many signals can be demixed from the autocorrelation functions.
+For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
+As a result, it is unnecessary to estimate $\sigma$.
+We have
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1 \approx L/2,
+\end{align*}
+moments in total.
+
+In the related problem of demixing signals from their periodic autocorrelation functions, there are strong evidences that the number of signals that, theoretically, can be demixed is equal to the number of different equations~\cite{bandeira2017estimation}.
+Based on these evidence, we conjecture the same here, namely, $L/2$ signals can be estimated simultaneously.
+That being said, we believe the number of classed that can actually be demixed by efficient algorithm is significantly smaller  and scale like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis}.
 

### 2018-05-14 TEX/draft3.tex
updates on section 2

@@
 
-In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
-In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$. An illustrative example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-Multiple occurrences of the image were placed 
-in $P$ micrographs, each of of size $4000\times 4000$ pixels, while the images to be separated by the image's length in each direction.
-From the micrographs, we estimated the first and second order autocorrelation and used a standard phase retrieval algorithm, called relaxed-reflect-reflect, to estimate the image.
-\TODO{We have a movie in the supplementary material.}
+In this section we describe  some numerical experiments and show results. The experimental details are discussed at length in Section~\ref{sec:methods}.
+In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$.
+An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+In each micrograph, multiple occurrences of the Einstein's image    were placed, while keeping a separation of  $50$ pixels between the images in each direction.
+From the micrographs, we estimated the power spectrum, which is equivalent to the second-order autocorrelation.
+Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm, called relaxed-reflect-reflect.
 
@@
 Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
-To measure error, we use the root mean square error (RMSE) defined as 
+To measure the error, we use the root mean square error (RMSE) defined as 
 \begin{equation}
@@
 \end{equation} 
-where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ is the Frobenius norm. 
-As expected, the RMSE of estimating the power spectrum (an equivalent quantity to the second-order autocorrelation)  decreases linearly with slope $-1/2$ in logarithmic scale.
-\TODO{What about the error?}
+where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
+As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
+\TODO{Few comments: 1.
+We have a movie in the supplementary material.
+2.
+Does the error also have the right slope?
+3.
+We can put more images to exemplify the progress 4.
+Need to improve the micrograph's generation code  }
 
@@
 		\centering
-		\includegraphics[scale=0.4]{Newton}
+		\includegraphics[scale=0.3]{Newton}
 		\caption{Newton  (model)}
@@
 		\centering
-		\includegraphics[scale=0.4]{Einstein_100}
-		\caption{$P =10^2$}
+		\includegraphics[scale=0.3]{reconstruction2}
+		\caption{$P = 1024$}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[scale=0.4]{Einstein_1e3}
-		\caption{$P =10^3$}
+		\includegraphics[scale=0.3]{reconstruction20}
+		\caption{$P = 1024\times 10$}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[scale=0.4]{Einstein_1e4}
-		\caption{$P = 10^4$}
+		\includegraphics[scale=0.3]{reconstruction200}
+		\caption{$P = 1024\times 100$}
 	\end{subfigure}%
@@
 The algorithm is initialized by the image of Newton.
-We show estimations of Einstein using $P=10^2,10^3$ and $10^4$ number of micrographs, each contains $860$ image occurrences on average.
-The normalized recovery error is $0.555$, $0.3988$ and $0.2907$, respectively.
-The normalized error in recovering the power spectrum was $69.1\times10^{-3} $, $21.7\times10^{-3} $ and $6.8\times10^{-3}$, respectively.
-\TODO{This image will be more impressive in the future}}
+We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $800$ image occurrences on average (to verify).
+The normalized recovery error is $0.5514$, $0.3494$ and $0.2112$, respectively.
+The normalized error in recovering the power spectrum was $0.0269 $, $0.0083$ and $0.0027$, respectively.
+}
 \end{figure}
 
-Results from a similar experiment for 1-D signals is presented in Figures~\ref{fig:1Dhomosignals} and~\ref{fig:1DhomoRMSE}.
-Here, we used nonconvex least-squares (LS) to estimate the signal and the estimated number of its occurrences.
-We do not assume the knowledge of the noise level. 
-Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
-\TODO{We may want to replace with an experiment with colored noise}
+%
+%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
+%\begin{equation}
+%\gamma_i = \frac{M_i L}{N},
+%\end{equation}
+%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
+As can be seen, given enough signals occurrences, we can estimate accurately the signals.
+he estimation quality
+%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
 
-\begin{figure}[h!]
+Results from a similar experiment  with $\sigma=3$ for $K=3$ 1-D signals is presented in Figures~\ref{fig:1Dheterosignals}.
+ We define the ratio of the space occupied by the $i$th signal as 
+\begin{equation}
+\gamma_i = \frac{M_i L}{N},
+\end{equation}
+where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$. 
+We used nonconvex least-squares (LS) to estimate the signals and the estimated number of their occurrences.
+As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
+is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
+\TODO{We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error.}
+%We do not assume the knowledge of the noise level. 
+%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
+
+\begin{figure}[h]
 \centering
-	\begin{subfigure}[h]{0.5\textwidth}
-		\centering
-		\includegraphics[scale=0.6]{err_rrr_per_micrograph}
-		\caption{}	
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.5\textwidth}
-		\centering
-		\includegraphics[scale=0.6]{err_PS_per_micrograph}
-		\caption{}	
-	\end{subfigure}%
+\includegraphics[scale=.5]{Einstein_progress}
 \caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined in~\eqref{eq:error} as a function of the number of the collected micrographs.
@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[scale=0.45]{progressive_n}
-	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-	\label{fig:1Dhomosignals}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
-	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-	\label{fig:1DhomoRMSE}
-\end{figure}
-
-Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
-\begin{equation}
-\gamma_i = \frac{M_i L}{N},
-\end{equation}
-where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-As can be seen, given enough signals occurrences, we can estimate accurately the signals.
-he estimation quality
-is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[scale=0.45]{progressive_n}
+%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
+%	\label{fig:1Dhomosignals}
+%\end{figure}
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
+%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
+%	\label{fig:1DhomoRMSE}
+%\end{figure}
 
@@
 The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$.
-The $\SNR$ is $1/12$.}
+The $\SNR$ is $1/12$.
+\TODO{to replace with a progress plot`}}
 	\label{fig:1Dheterosignals}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save.tex
updates on section 2

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{url} 
\usepackage[authoryear]{natbib}
%%%\usepackage{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{framed}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%%%\usepackage{custom_tex}
\usepackage{grffile}
\usepackage{multirow}
\usepackage{xcolor}
%\usepackage{setspace}
\usepackage{comment}
\usepackage{xr}
%\externaldocument{sharp_PCA_AoS_supp}

\newtheorem{thm}{Theorem}[section]
\newtheorem{definition}[thm]{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{example}[thm]{Example}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{thm}
\newtheorem{conj}{Conjecture}
\theoremstyle{definition}
\newtheorem{rmk}{Remark}

\newcommand{\F}{\mathcal{F}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}

%
%
%
%
\begin{document}

\section{Setup}

We have the following model. $x$ is a signal of length $L$. For large $n$, we observe the vector $Y$, which is of the form 
%
\begin{align}
%
    Y = x \ast g + \ep
%
\end{align}
%
where $g$ is a sum of diracs at locations at least $L$ apart, and $\ep$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?

The approach Tamir proposed was the following. Look at all length $L$ (or bigger, but we'll stick with length $L$ for now) subvectors of $Y$ (with consecutive elements). Compute the mean, power spectrum, and bispectrum for each, and average. This should hopefully converge in the large $n$ limit to some function of $x$. Then attempt to invert this function, perhaps by least squares.

One of Tamir's concerns is that the noise terms are not independent between overlapping windows. I'll show that at least for the first and second moments, things are okay as long as there are $\Omega(n)$ copies of $x$ buried in $Y$. The bispectrum is probably fine too but I haven't written it out yet.

\section{Pure noise}

The first step is to analyze the pure noise case.

TKTK

\section{Signal plus noise}

Assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n]$ (if not we can just zero-pad the interval).

\end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save1.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save.tex
@@
 
-We have the following model. $x$ is a signal of length $L$. For large $n$, we observe the vector $Y$, which is of the form 
+We have the following model. $x$ is a signal of length $L$. For large $n$, we observe the vector $Y \in \mathbb{R}^n$, which is of the form 
 %
@@
 
-\section{Pure noise}
+Note that I'm not just computing the expected value. I'm actually showing convergence almost surely as $n \to \infty$.
 
-The first step is to analyze the pure noise case.
+\section{First moment}
 
-TKTK
+We'll compute the limiting vector of the average of all the windows. Fix an index $\ell$ between $1$ and $L$. Then
 
-\section{Signal plus noise}
+\section{Second moment}
+
+\subsection{Pure noise}
+
+\subsection{Signal plus noise}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save2.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save1.tex
@@
 The approach Tamir proposed was the following.
-Look at all length $L$ (or bigger, but we'll stick with length $L$ for now) subvectors of $Y$ (with consecutive elements).
+We look at all length $L$ subvectors of $Y$ (with consecutive elements).
 Compute the mean, power spectrum, and bispectrum for each, and average.
@@
 
+We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval).
+We will also denote by $I_1,\dots,I_J$ the $J$ subintervals containing the signal; and take $I_j = [a_j,b_j]$.
+When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural.
+We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish.
+
 Note that I'm not just computing the expected value. I'm actually showing convergence almost surely as $n \to \infty$.
@@
 
-We'll compute the limiting vector of the average of all the windows. Fix an index $\ell$ between $1$ and $L$. Then
+We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
+%
+\begin{align}
+%
+    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
+    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
+                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
+    \nonumber \\
+%
+                &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
+                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
+    \nonumber \\
+                &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
+                  + \frac{J \cdot L}{n} \bar{x}       \nonumber \\
+%
+                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot L \cdot \bar{x}
+%
+\end{align}
+%
+where $\gamma = \lim_{n\to\infty} J_n / n$. This limit does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.
+
+Actually, what Tamir meant when he said first moment was the average of the windows' averages.
+But this also converges a.s.\ to $\gamma \cdot L \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows.
+The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$.
+Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
+%
+\begin{align}
+%
+    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
+    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
+    = \gamma \cdot L \cdot \bar{x}.
+%
+\end{align}
 
@@
 
-Assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n]$ (if not we can just zero-pad the interval).
-
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save3.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save2.tex
@@
 %
-                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot L \cdot \bar{x}
+                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot \bar{x}
 %
@@
 %
-where $\gamma = \lim_{n\to\infty} J_n / n$. This limit does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.
+where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations occupied by the signal.
+The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.
 
-Actually, what Tamir meant when he said first moment was the average of the windows' averages.
-But this also converges a.s.\ to $\gamma \cdot L \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows.
+Actually, what Tamir meant when he said first moment was the average of the windows' averages (a scalar), not the average window (a vector).
+But this also converges a.s.\ to $\gamma \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows.
 The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$.
@@
     =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
-    = \gamma \cdot L \cdot \bar{x}.
+    = \gamma \cdot \bar{x}.
 %

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save5.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save3.tex
@@
 
-We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
+We'll compute the limiting vector of the sample average of all the windows.
+We fix an index $\ell$ between $1$ and $L$.
+The $\ell^{th}$ entry of the $i^{th}$ window is $Y_{i+\ell-1}$, $i=1,\dots,n$.
+Then the sample average of the $\ell^{th}$ entry is:
 %
@@
 %
-    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
+    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell - 1} &=
     \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
@@
         &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
-                  + \frac{J \cdot L}{n} \bar{x}       \nonumber \\
+                  + \frac{J \cdot L}{n} \bar{x}       
+     \nonumber \\
 %
@@
 %
-where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations occupied by the signal.
+where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations containing the signal.
 The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.
@@
 
-\subsection{Pure noise}
+First we'll compute the limit in the case of pure noise; then we'll use this for signal plus noise.
 
-\subsection{Signal plus noise}
+\subsection{Second moment of noise}
+
+Here, $Y_i = \ep_i$.
+We fix two indices $k$ and $l$, and we suppose $k < l$.
+We will let $\Delta = l-k > 0$.
+We want to compute the limit $\frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + l - 1} = \frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + k + \Delta - 1}$.
+Break up the sum into $\Delta$ terms as follows:
+%
+\begin{align}
+%
+    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1] & Y[i + k+\Delta - 1]   
+    \nonumber \\
+    &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
+                      Y[j\Delta + m] Y[(j + 1)\Delta + m].
+%
+\end{align}
+%
+Each term
+%
+\begin{math}
+    \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
+                      Y[j\Delta + m] Y[(j + 1)\Delta + m]
+\end{math}
+%
+is an average of $n / \Delta$ iid terms with expectation zero, and so converges to 0 a.s.\ as $n \to \infty$.
+
+\subsection{Second moment of signal plus noise}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save6.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save5.tex
@@
 \newcommand{\F}{\mathcal{F}}
+\newcommand{\I}{\mathcal{I}}
 \newcommand{\ep}{\varepsilon}
@@
 \newcommand{\GCD}{\mathbf{GCD}}
+
+\newcommand{\mean}[2]{\frac{1}{#1}\sum_{#2=1}^{#1}}
 
@@
 %
-    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1] & Y[i + k+\Delta - 1]   
+    &\frac{1}{n} \sum_{i=1}^n Y[i + k - 1]  Y[i + k+\Delta - 1]   
     \nonumber \\
-    &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
+    =& \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                       Y[j\Delta + m] Y[(j + 1)\Delta + m].
@@
 is an average of $n / \Delta$ iid terms with expectation zero, and so converges to 0 a.s.\ as $n \to \infty$.
+(Of course, it's not exactly $n / \Delta$ terms; there will be finitely many terms unaccounted for this way, but these are negligible).
+
+If $k = l$, then it's even easier:
+%
+\begin{align}
+%
+    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1]^2 \operatorname*{\longrightarrow}^{a.s.} \sigma^2.
+%
+\end{align}
+
+So the second moment matrix of pure noise converges a.s.\ as $n \to \infty$ to $\sigma^2 I_L$.
 
@@
 
+Break the sum $\sum_{i=1}^n Y[i + k-1] Y[i + l - 1]$ into three terms: where $i + k-1$ and $i+l-1$ are disjoint from all intervals $I_j$ -- we will denote this set $\I$; where both $i + k - 1$ and $i + l -1$ lie entirely inside one of the $I_j$; and the rest, where exactly one of $i+k-1$ and $i+l-1$ lie in an interval $I_j$.
+So we have:
+%
+\begin{align}
+%
+    & \sum_{i=1}^n Y[i+k-1] Y[i+l-1]    \nonumber \\
+    =& \left(\sum_{i \in \I}  
+        + \sum_{j=1}^J \sum_{i=a_j - l + 1}^{a_j - k} 
+        + \sum_{j=1}^J \sum_{i=b_j - l + 2}^{b_j - k+1} 
+        + \sum_{j=1}^J \sum_{i=a_j-k+1}^{b_j-l+1}
+      \right)  Y[i+k-1] Y[i+l-1]
+%
+\end{align}
+We will use that $Y[a_j + m] = x[m+1] + \ep[a_j+m]$, $m=0,\dots,L-1$.
+
+For the second term, the inner sum is
+%
+\begin{align}
+%
+    &\sum_{i=a_j - l + 1}^{a_j - k} Y[i+k-1] Y[i+l-1]    \nonumber \\
+    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] (x[i+l-1] + \ep[i+l-1])
+    \nonumber \\
+    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] x[i+l-1] 
+        + \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l]\ep[i+l-1]
+%
+\end{align}
+%
+
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save1.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save6.tex
@@
 
-The approach Tamir proposed was the following.
-We look at all length $L$ subvectors of $Y$ (with consecutive elements).
-Compute the mean, power spectrum, and bispectrum for each, and average.
-This should hopefully converge in the large $n$ limit to some function of $x$.
-Then attempt to invert this function, perhaps by least squares.
-
-One of Tamir's concerns is that the noise terms are not independent between overlapping windows.
-I'll show that at least for the first and second moments, things are okay as long as there are $\Omega(n)$ copies of $x$ buried in $Y$.
-The bispectrum is probably fine too but I haven't written it out yet.
-
 We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval).
@@
 Note that I'm not just computing the expected value. I'm actually showing convergence almost surely as $n \to \infty$.
+
+%
+%
+%
 
@@
 
+\begin{comment}
+
 Actually, what Tamir meant when he said first moment was the average of the windows' averages (a scalar), not the average window (a vector).
@@
 
+\end{comment}
+
+%
+%
+%
+
 \section{Second moment}
 
-First we'll compute the limit in the case of pure noise; then we'll use this for signal plus noise.
+We fix a value $\Delta$ between $1$ and $L-1$. We will compute the second moment:
+%
+\begin{align}
+%
+    M_2(\Delta) = 
+        \lim_{n \to \infty} \frac{1}{n} \sum_{i=1}^{n-\Delta} Y_i Y_{i+\Delta}.
+%
+\end{align}
 
-\subsection{Second moment of noise}
+First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
+%
+\begin{align}
+%
+    M_2(\Delta) 
+        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
+    = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} X_i X_{i+\Delta}
+%
+\end{align}
+
+\end{document}
 
@@
 \end{align}
-We will use that $Y[a_j + m] = x[m+1] + \ep[a_j+m]$, $m=0,\dots,L-1$.
 
-For the second term, the inner sum is
+We will use that $Y[a_j + m] = x[m+1] + \ep[a_j+m]$, $m=0,\dots,L-1$. For the second term, the inner sum is
 %
@@
 %
-    &\sum_{i=a_j - l + 1}^{a_j - k} Y[i+k-1] Y[i+l-1]    \nonumber \\
-    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] (x[i+l-1] + \ep[i+l-1])
+    &\sum_{i=a_j - l + 1}^{a_j - k} Y[i+k-1] Y[i+l-1]
         \nonumber \\
-    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] x[i+l-1] 
-        + \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l]\ep[i+l-1]
+%
+    =&\sum_{i=1}^{\Delta} Y[a_j -\Delta + i-1] Y[a_j + i-1]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{\Delta}\ep[a_j -\Delta + i-1] (x[i] + \ep[a_j + i-1])
+        \nonumber \\
+%
+    =& \sum_{i=1}^{\Delta}\ep[a_j -\Delta + i-1] x[i]
+        + \sum_{i=1}^{\Delta}\ep[a_j -\Delta + i-1] \ep[a_j + i-1]
 %
@@
 
+We also use that $Y[b_j - m] = x[L-m] + \ep[b_j-m]$, $m=0,\dots,L-1$. For the third term, the inner sum is
+%
+\begin{align}
+%
+    & \sum_{i=b_j - l + 2}^{b_j - k+1} Y[i+k-1] Y[i+l-1]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{\Delta} Y[i+b_j-\Delta] Y[i+b_j]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{\Delta} (x[L-\Delta+i]+\ep[i+b_j-\Delta]) \ep[i+b_j]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{\Delta} x[L-\Delta+i] \ep[i+b_j]
+        + \sum_{i=1}^{\Delta} \ep[i+b_j-\Delta] \ep[i+b_j]
+\end{align}
+%
+
+The inner sum of the fourth term is:
+%
+\begin{align}
+%
+    &\sum_{i=a_j-k+1}^{b_j-l+1} Y[i+k-1] Y[i+l-1]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{L - \Delta} Y[i+a_j-1] Y[i+a_j + \Delta - 1]
+        \nonumber \\
+%
+    =& \sum_{i=1}^{L - \Delta} (x[i]+\ep[i+a_j-1])(x[i+\Delta] +\ep[i+a_j + \Delta - 1])
+        \nonumber \\
+%
+    =& \sum_{i=1}^{L - \Delta} x[i] x[i+\Delta]
+        + \sum_{i=1}^{L - \Delta} x[i]\ep[i+a_j + \Delta - 1]
+        \nonumber \\
+        &+ \sum_{i=1}^{L - \Delta} \ep[i+a_j-1] x[i+\Delta] 
+        + \sum_{i=1}^{L - \Delta} \ep[i+a_j-1]\ep[i+a_j + \Delta - 1])
+%
+\end{align}
+
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save10.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save1.tex
@@
 \newcommand{\GCD}{\mathbf{GCD}}
+\newcommand{\XX}{\mathcal{X}}
 
@@
 When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural.
-We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish.
+We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish (and obviously $J_n = O(n)$ too).
 
@@
 
-We fix a value $\Delta$ between $1$ and $L-1$. We will compute the second moment:
+We fix a value $\Delta$ between $0$ and $L-1$. We will compute the second moment:
 %
@@
 
+%
+%
+%
+
+\subsection{Clean signal without noise}
+
 First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
@@
     M_2(\Delta) 
-        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
-    = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} X_i X_{i+\Delta}
+        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
+        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
+    \nonumber \\
+    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
+        \to \gamma \cdot R_2(\Delta),
 %
 \end{align}
+%
+where here we have defined $R_2(\Delta)$ as element $\Delta$ of the autocorrelation of $x$, and $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
 
-\end{document}
+%
+%
+%
 
-Here, $Y_i = \ep_i$.
-We fix two indices $k$ and $l$, and we suppose $k < l$.
-We will let $\Delta = l-k > 0$.
-We want to compute the limit $\frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + l - 1} = \frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + k + \Delta - 1}$.
-Break up the sum into $\Delta$ terms as follows:
+\subsection{Pure noise without signal}
+
+Here, $Y_i = \ep_i$. We first fix $\Delta$ between $1$ and $L-1$. Break up the sum into $\Delta$ terms as follows:
 %
@@
 %
-    &\frac{1}{n} \sum_{i=1}^n Y[i + k - 1]  Y[i + k+\Delta - 1]   
+    M_2(\Delta) &=\frac{1}{n} \sum_{i=1}^n \ep_i  \ep_{i+\Delta}
         \nonumber \\
-    =& \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
-                      Y[j\Delta + m] Y[(j + 1)\Delta + m].
+    &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
+        \ep_{j\Delta + m} \ep_{(j + 1)\Delta + m}.
 %
@@
     \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
-                      Y[j\Delta + m] Y[(j + 1)\Delta + m]
+        \ep_{j\Delta + m} \ep_{(j + 1)\Delta + m}
 \end{math}
@@
 
-If $k = l$, then it's even easier:
+If $\Delta = 0$, then the computation is even easier:
 %
@@
 %
-    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1]^2 \operatorname*{\longrightarrow}^{a.s.} \sigma^2.
+    M_2(\Delta) = \frac{1}{n} \sum_{i=1}^n \ep_i^2 
+        \operatorname*{\longrightarrow}^{a.s.} \sigma^2.
 %
@@
 
-So the second moment matrix of pure noise converges a.s.\ as $n \to \infty$ to $\sigma^2 I_L$.
+So $M_2(\Delta) = \sigma^2$ if $\Delta = 0$, and 0 otherwise.
+
+%%%So the second moment matrix of pure noise converges a.s.\ as $n \to \infty$ to $\sigma^2 I_L$.
+
+%
+%
+%
+
+\subsection{Signal plus noise}
+
+This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + \ep$. Then the second moment of the signal plus noise is:
+%
+\begin{align}
+%
+    M_2(\Delta,Y) = M_2(\Delta,\XX) + M_2(\Delta,\ep) 
+        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_i \ep_{i+\Delta}
+        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_{i+\Delta} \ep_i.
+%
+\end{align}
+%
+The law of large numbers says the cross terms vanish as $n \to \infty$. So the limit is simply:
+%
+\begin{align}
+%
+    M_2(\Delta,Y) = 
+    \begin{cases}
+        R_2(\Delta), &\text{ if } \Delta > 0; \\
+        R_2(\Delta) + \sigma^2, &\text{ if } \Delta = 0.
+    \end{cases}
+%
+\end{align}
+
+%
+%
+%
+
+\section{Third moments}
+
+The same idea lets us compute the third moments. We fix two indices $\Delta_1 < \Delta_2$, and define:
+%
+\begin{align}
+%
+    M_3(\Delta_1,\Delta_2) = \sum_{i=1}^{n-\Delta_2} Y_i Y_{i+\Delta_1} Y_{i+\Delta_2}.
+%
+\end{align}
+
+\section{Pure noise, no signal}
+
+Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms.
+
+\end{document}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save12.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save10.tex
@@
 %
-    Y = x \ast g + \ep
+    Y = G \ast x + N
 %
@@
 %
-where $g$ is a sum of diracs at locations at least $L$ apart, and $\ep$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?
+where $G$ is a sum of diracs at locations at least $L$ apart, and $N$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?
 
-We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval).
+We will assume that the first and last copies of $x$ are at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval).
 We will also denote by $I_1,\dots,I_J$ the $J$ subintervals containing the signal; and take $I_j = [a_j,b_j]$.
@@
     \frac{1}{n} \sum_{i=1}^n Y_{i+\ell - 1} &=
-    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
-                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
+    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} N_i 
+                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + N_{a_j + k-1} ) \right) 
     \nonumber \\
 %
-        &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
+        &= \frac{1}{n}\sum_{i=1}^{n} N_i 
                   + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
     \nonumber \\
-        &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
+        &= \frac{1}{n}\sum_{i=1}^{n-L+1} N_i 
                   + \frac{J \cdot L}{n} \bar{x}       
@@
 
-Here, $Y_i = \ep_i$. We first fix $\Delta$ between $1$ and $L-1$. Break up the sum into $\Delta$ terms as follows:
+Here, $Y_i = N_i$. We first fix $\Delta$ between $1$ and $L-1$. Break up the sum into $\Delta$ terms as follows:
 %
@@
 %
-    M_2(\Delta) &=\frac{1}{n} \sum_{i=1}^n \ep_i  \ep_{i+\Delta}
+    M_2(\Delta) &=\frac{1}{n} \sum_{i=1}^n N_i  N_{i+\Delta}
         \nonumber \\
     &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
-        \ep_{j\Delta + m} \ep_{(j + 1)\Delta + m}.
+        N_{j+(j-1)\Delta + m} N_{j + j\Delta + m}.
 %
@@
     \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
-        \ep_{j\Delta + m} \ep_{(j + 1)\Delta + m}
+        N_{j\Delta + m} N_{(j + 1)\Delta + m}
 \end{math}
@@
 %
-    M_2(\Delta) = \frac{1}{n} \sum_{i=1}^n \ep_i^2 
+    M_2(\Delta) = \frac{1}{n} \sum_{i=1}^n N_i^2 
         \operatorname*{\longrightarrow}^{a.s.} \sigma^2.
@@
 
-This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + \ep$. Then the second moment of the signal plus noise is:
+This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + N$. Then the second moment of the signal plus noise is:
 %
@@
 %
-    M_2(\Delta,Y) = M_2(\Delta,\XX) + M_2(\Delta,\ep) 
-        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_i \ep_{i+\Delta}
-        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_{i+\Delta} \ep_i.
+    M_2(\Delta,Y) = M_2(\Delta,\XX) + M_2(\Delta,N) 
+        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_i N_{i+\Delta}
+        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_{i+\Delta} N_i.
 %
@@
 
-\section{Pure noise, no signal}
+%
+%
+%
 
-Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms.
+\subsection{Pure noise, no signal}
+
+Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms. We can write:
+%
+\begin{align}
+%
+    M_3(\Delta_1,\Delta_2) = \sum
+%
+\end{align}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save14.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save12.tex
@@
 
-Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms. We can write:
+Again, the idea is to break up the big average over $n$ terms into a sum of $\Delta_2$ averages, each of $\approx n / \Delta_2$ independent terms. We write:
 %
@@
 %
-    M_3(\Delta_1,\Delta_2) = \sum
+    & M_3(\Delta_1,\Delta_2) 
+        \nonumber \\
+    & = \frac{1}{\Delta_2}\sum_{m=0}^{\Delta_2-1}
+        \frac{1}{(n/\Delta_2)}\sum_{j=1}^{n/\Delta_2} 
+            N_{j+(j-1)\Delta_2+m} N_{j+\Delta_1 + (j-1)\Delta_2 + m} N_{j+j\Delta_2 + m}.
 %
 \end{align}
+%
+Each of the $\Delta_2$ terms indexed by $m$ converges is an average of $n/\Delta_2$ independent terms with mean zero, and so converges a.s.\ to zero as $n \to \infty$.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save16.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save14.tex
@@
 \newcommand{\F}{\mathcal{F}}
+\newcommand{\E}{\mathbb{E}}
 \newcommand{\I}{\mathcal{I}}
@@
 %
-    & M_3(\Delta_1,\Delta_2) 
-        \nonumber \\
+    & M_3(\Delta_1,\Delta_2)  \nonumber \\
     & = \frac{1}{\Delta_2}\sum_{m=0}^{\Delta_2-1}
@@
 Each of the $\Delta_2$ terms indexed by $m$ converges is an average of $n/\Delta_2$ independent terms with mean zero, and so converges a.s.\ to zero as $n \to \infty$.
+
+%
+%
+%
+
+\subsection{Clean signal, no noise}
+
+Again, this is just like the second moment case. Write:
+%
+\begin{align}
+%
+    M_3(\Delta_1,\Delta_2) 
+        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta_2} 
+            Y_i Y_{i+\Delta_1} Y_{i+\Delta_2}
+        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta_2} 
+            x_i x_{i+\Delta_1} x_{i+\Delta_2}
+    \nonumber \\
+    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta_1} x_{i+\Delta_2}
+        \to \gamma \cdot R_3(\Delta_1,\Delta_2),
+%
+\end{align}
+%
+where here we have defined $R_3(\Delta_1,\Delta_2)$ as element $(\Delta_1,\Delta_2)$ of the third moment of $x$.
+
+%
+%
+%
+
+\subsection{Signal plus noise}
+
+We have:
+%
+\begin{align}
+%
+    M_3(\Delta_1,\Delta_2,Y) = M_3(\Delta_1,\Delta_2,\XX) + M_3(\Delta_1,\Delta_2,N)
+        + \text{cross terms}.
+%
+\end{align}
+%
+If $0 < \Delta_1 < \Delta_2$, then all of the cross terms can be shown to go to zero by the same kind of argument we've used several times before.
+
+If $\Delta_1 = \Delta_2 = \Delta$, there is a surviving cross-term, namely:
+%
+\begin{align}
+%
+    \frac{1}{n} \sum_{i=1}^{n-\Delta} \XX_i N_{i+\Delta}^2
+    = \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2.
+%
+\end{align}
+%
+Each of $S_j \equiv \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2 \sim \frac{1}{L} \sum_{i=1}^{L} x_i \ep_i^2$, where $\ep_i \sim N(0,\sigma^2)$; and they are independent random variables with mean $\E[S_j] = \sigma^2 \cdot \bar{x}$.
+So by the law of large numbers,
+%
+\begin{align}
+%
+    \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2
+    \to \gamma \cdot \sigma^2 \cdot \bar{x}.
+%
+\end{align}
+
+Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. So in summary,
+%
+\begin{align}
+%
+    M_3(\Delta_1,\Delta_2,Y) = 
+    \begin{cases}
+        R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
+        R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
+                        &\text{ if } \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2.
+    \end{cases}
+%
+\end{align}
+
+%
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save17.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save16.tex
@@
     \begin{cases}
-        R_2(\Delta), &\text{ if } \Delta > 0; \\
-        R_2(\Delta) + \sigma^2, &\text{ if } \Delta = 0.
+        \gamma \cdot R_2(\Delta), &\text{ if } \Delta > 0; \\
+        \gamma \cdot R_2(\Delta) + \sigma^2, &\text{ if } \Delta = 0.
     \end{cases}
@@
     \begin{cases}
-        R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
-        R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
+        \gamma \cdot R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
+        \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
                         &\text{ if } \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2.
@@
 %
+
+\section{Attempt at EM}
+
+Let's derive the EM algorithm, where we treat the locations $a_j$ as random latent variables.
+A simple model is that the $a_i$ are chosen independently and uniformly at random (though take note that this permits overlaps).
+
+If $A = (a_1,\dots,a_J)$ is the vector of signal locations, then the generative model is:
+%
+\begin{align}
+%
+    p(Y , A| x) \propto 
+%
+\end{align}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save18.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save17.tex
@@
 \newcommand{\F}{\mathcal{F}}
+\newcommand{\LL}{\mathcal{L}}
 \newcommand{\E}{\mathbb{E}}
@@
 
+%
+%
+%
+
 \section{Attempt at EM}
@@
 
-If $A = (a_1,\dots,a_J)$ is the vector of signal locations, then the generative model is:
+We will denote by $G = (a_1,\dots,a_J)$ the random vector of signal locations; then the mean is $G \ast x $. We'll also assume the number $J$ of signals is known. The generative model is:
 %
@@
 %
-    p(Y , A| x) \propto 
+    p(Y , G \, | \, x)
+    = \frac{\exp\{-\| Y - G \ast x \|^2 / (2\sigma^2)\}}{(2\pi\sigma^2)^{n/2}} \frac{1}{n^J}.
+%
+\end{align}
+
+The log-likelihood is then (up to an additive constant):
+%
+\begin{align}
+%
+    \LL(x; Y, G) \propto - \|Y - G\ast x\|^2.
 %

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save19.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save17.tex
@@
 %
-where $G$ is a sum of diracs at locations at least $L$ apart, and $N$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?
+where $G$ is a sum of diracs at locations at least $2L$ apart, and $N$ is a vector of $n$ iid Gaussians. The goal is to recover $x$?
 
@@
 
-We'll compute the limiting vector of the sample average of all the windows.
-We fix an index $\ell$ between $1$ and $L$.
-The $\ell^{th}$ entry of the $i^{th}$ window is $Y_{i+\ell-1}$, $i=1,\dots,n$.
-Then the sample average of the $\ell^{th}$ entry is:
+We have:
 %
@@
 %
-    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell - 1} &=
-    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} N_i 
-                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + N_{a_j + k-1} ) \right) 
-    \nonumber \\
-%
-        &= \frac{1}{n}\sum_{i=1}^{n} N_i 
-                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
-    \nonumber \\
-        &= \frac{1}{n}\sum_{i=1}^{n-L+1} N_i 
-                  + \frac{J \cdot L}{n} \bar{x}       
-     \nonumber \\
-%
-        &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot \bar{x}
+    M_1 = \frac{1}{n} \sum_{i=1}^n Y_i
+        = \frac{1}{n/L} \sum_{j=1}^{J_n} \frac{1}{L}\sum_{i=1}^L x_i
+            + \frac{1}{n} \sum_{i=1}^n N_i
+    \to \gamma \cdot \bar{x},
 %
@@
 %
-where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations containing the signal.
-The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.
+where the limit is almost surely (we've used the strong law of large numbers), where $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
 
@@
 %
-where here we have defined $R_2(\Delta)$ as element $\Delta$ of the autocorrelation of $x$, and $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
-
+where here we have defined $R_2(\Delta)$ as element $\Delta$ of the autocorrelation of $x$. 
 %
@@
 
-This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + N$. Then the second moment of the signal plus noise is:
+We will denote by $\XX = x \ast G$, so $Y = \XX + N$. Then the second moment of the signal plus noise is:
 %
@@
 Let's derive the EM algorithm, where we treat the locations $a_j$ as random latent variables.
-A simple model is that the $a_i$ are chosen independently and uniformly at random (though take note that this permits overlaps).
+A simple model is that the $a_j$ are chosen independently and uniformly at random (though take note that this permits overlaps of the signal copies).
 
-If $A = (a_1,\dots,a_J)$ is the vector of signal locations, then the generative model is:
+We will denote by $G=\sum_{j=1}^J \delta_{a_j}$ the random vector of signal locations. We'll assume the number of signals $J$ is known. The generative model is:
 %
@@
 %
-    p(Y , A| x) \propto 
+    p(Y , G | x)
+    = \frac{\exp\{-\| Y - G \ast x \|^2 / (2\sigma^2)\}}{(2\pi\sigma^2)^{n/2}} 
+        \cdot \frac{1}{n^J}.
 %
 \end{align}
+
+The log-likelihood is then (up to an additive constant):
+%
+\begin{align}
+%
+    \LL(x; Y, G) \propto - \|Y - G\ast x\|^2.
+%
+\end{align}
+
+The probability distribution of $G$, given $Y$ and $x$, is:
+%
+\begin{align}
+%
+    p(G | Y, x) = \frac{ p(Y , G | x) }{ p(Y | x) }
+    \propto \exp\{-\| Y - G \ast x \|^2 / (2\sigma^2)\}.
+%
+\end{align}
+
+If $x^{(t)}$ is a guess for $x$ on the $t^{th}$ iterate of EM, then we define the weights:
+%
+\begin{align}
+%
+    w_t(G) = p(G | Y,x^{(t)}) = \exp\{-\| Y - G \ast x^{(t)} \|^2 / (2\sigma^2)\},
+%
+\end{align}
+%
+and the $Q$-function:
+%
+\begin{align}
+%
+    Q(x|x^{(t)}) 
+    &= \E_{G|Y,x^{(t)}} \left[ \LL(x^{(t)};Y,G) \right]
+        \nonumber \\
+    &\propto - \sum_{G} \|Y - G\ast x\|^2 \cdot w_t(G).
+%
+\end{align}
+%
+The EM algorithm defines the next guess of $x$ to be:
+%
+\begin{align}
+%
+    x^{(t+1)} = \operatorname*{\arg\max}_x Q(x|x^{(t)})
+        = \operatorname*{\arg\min}_x \sum_{G} \|Y - G\ast x\|^2 \cdot w_t(G).
+%
+\end{align}
+
+But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery, the number of terms will grow exponentially with $n$.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save20.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save19.tex
@@
 \begin{document}
+\title{Notes on big MRA}
+\author{William Leeb}
+\date{}
+\maketitle
 
@@
 %
-where $G$ is a sum of diracs at locations at least $2L$ apart, and $N$ is a vector of $n$ iid Gaussians. The goal is to recover $x$?
+where $G$ is a sum of diracs at locations at least $2L$ apart, and $N$ is a vector of $n$ iid Gaussians. The goal is to recover $x$.
 
@@
 
-Note that I'm not just computing the expected value. I'm actually showing convergence almost surely as $n \to \infty$.
+For the moments computation, I'm not just computing the expected value.
+I'm actually showing convergence almost surely as $n \to \infty$.
+I probably made a mistake in the final formulas since I haven't check them carefully yet; the main point I want to record right now is how to get the bookkeeping correct for dealing with the noise terms, namely, we need to break the averages into averages of averages, each with iid terms.
 
@@
     = \frac{\exp\{-\| Y - G \ast x \|^2 / (2\sigma^2)\}}{(2\pi\sigma^2)^{n/2}} 
-        \cdot \frac{1}{n^J}.
+        \cdot {n \choose J}^{-1}.
 %
@@
 
-But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery, the number of terms will grow exponentially with $n$.
+But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery (this was suggested by the moments method), the number of terms will grow exponentially with $n$.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save8.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save10.tex
@@
 \newcommand{\GCD}{\mathbf{GCD}}
-\newcommand{\XX}{\mathcal{X}}
 
@@
 When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural.
-We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish (and obviously $J_n = O(n)$ too).
+We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish.
 
@@
 
-This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + \ep$. Then the second moment of the signal plus noise is:
-%
-\begin{align}
-%
-    M_2(\Delta,Y) = M_2(\Delta,\XX) + M_2(\Delta,\ep) 
-        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_i \ep_{i+\Delta}
-        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_{i+\Delta} \ep_i.
-%
-\end{align}
-%
-The law of large numbers says the cross terms vanish as $n \to \infty$. So the limit is simply:
-%
-\begin{align}
-%
-    M_2(\Delta,Y) = 
-    \begin{cases}
-        R_2(\Delta), &\text{ if } \Delta > 0; \\
-        R_2(\Delta) + \sigma^2, &\text{ if } \Delta = 0.
-    \end{cases}
-%
-\end{align}
-
-%
-%
-%
-
-\section{Third moments}
-
-The same idea lets us compute the third moments. We fix two indices $\Delta_1 < \Delta_2$, and define:
-%
-\begin{align}
-%
-    M_3(\Delta_1,\Delta_2) = \sum_{i=1}^{n-\Delta_2} Y_i Y_{i+\Delta_1} Y_{i+\Delta_2}.
-%
-\end{align}
-
-\section{Pure noise, no signal}
-
-Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms.
-
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save20.tex
@@
 \usepackage{xr}
-%\externaldocument{sharp_PCA_AoS_supp}
 
@@
 %
+
 \begin{document}
-\title{Notes on big MRA}
+\title{Notes on Big MRA}
 \author{William Leeb}
@@
 
-Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. So in summary,
+Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well.
+So in summary, for all $0 \le \Delta_1 \le \Delta_2 \le L-1$, we have:
 %
@@
         \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
-                        &\text{ if } \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2.
+                &\text{ if } \Delta_2 > \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2 > 0; \\
+        \gamma \cdot R_3(0,0) + 3\cdot \gamma \cdot \sigma^2 \cdot \bar{x}
+                &\text{ if } \Delta_1 = \Delta2 = 0.
     \end{cases}
@@
 
-But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery (this was suggested by the moments method), the number of terms will grow exponentially with $n$.
+But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery (this was suggested by the moments method), the number of terms will grow super-exponentially with $n$.
+
+%
+%
+%
+
+\section{Estimating $J$, the number of copies of $x$}
+
+Using the moments calculation, we can estimate the number of copies of $x$ embedded in $Y$, which we call $J$.
+This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.
+
+From the first moment we estimate $(J / n) (\mathbf{1}^\top x)$, while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
+%
+\begin{align}
+%
+    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
+%
+\end{align}
+%
+
+%
+%
+%
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save2.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save.tex
@@
 
-If $\Delta_1 = \Delta_2 = \Delta$, there is a surviving cross-term, namely:
+If $\Delta_1 = \Delta_2 = \Delta > 0$, there is a surviving cross-term, namely:
 %
@@
 
-Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well.
+Similarly, if $\Delta_2 > \Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well.
+Finally, if $\Delta_1 = \Delta_2 = 0$, then the cross-term converges to $3 \cdot \gamma  \cdot \sigma^2 \cdot \bar{x}$.
 So in summary, for all $0 \le \Delta_1 \le \Delta_2 \le L-1$, we have:
@@
         \gamma \cdot R_3(0,0) + 3\cdot \gamma \cdot \sigma^2 \cdot \bar{x}
-                &\text{ if } \Delta_1 = \Delta2 = 0.
+                &\text{ if } \Delta_1 = \Delta_2 = 0.
     \end{cases}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save3.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save2.tex
@@
 \newcommand{\XX}{\mathcal{X}}
+\newcommand{\SUM}{\text{sum}}
+\newcommand{\1}{\mathbf{1}}
 
@@
 
-\section{Estimating $J$, the number of copies of $x$}
+\section{Estimating $\gamma$, using $\sigma$ and the moments}
 
-Using the moments calculation, we can estimate the number of copies of $x$ embedded in $Y$, which we call $J$.
-This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.
+We'll suppose we know $\sigma$. Using the moments calculation, we can estimate $\gamma$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.
 
-From the first moment we estimate $(J / n) (\mathbf{1}^\top x)$, while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
+It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$.
+Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$.
+From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
+%
+\begin{align}
+%
+    (Q \cdot (\1^\top x))^2 
+    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
+        \nonumber \\
+    &= Q^2 \left( T_2(0) 
+            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
+        \nonumber \\
+    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L}x_i x_{i+\Delta} 
+        \1_{(\Delta \le L-i)} \right)
+        \nonumber \\
+    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
+        \right)
+        \nonumber \\
+    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta) \right).
+%
+\end{align}
+
+. From the second while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
 %

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save4.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save3.tex
@@
 %
-    (Q \cdot (\1^\top x))^2 
+    A \equiv (Q \cdot (\1^\top x))^2 
     &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
@@
 
-. From the second while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
+On the other hand, from the second moment we can estimate $Q \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $Q\cdot T_2(0) + \sigma^2$, and consequently $B \equiv Q \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$.
+Taking the ratio, we obtain the equation:
 %
@@
 %
-    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
+    \frac{1}{Q} + \frac{\sigma^2}{A} = \frac{B}{A}.
 %
 \end{align}
-%
+
+If we knew $\sigma$, we can solve for $Q$ (and conversely).
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save6.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save4.tex
@@
 
-We'll suppose we know $\sigma$. Using the moments calculation, we can estimate $\gamma$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.
+Using the moments calculation, we will derive an equation relating $\gamma$ and $\sigma$.
+If $\sigma$ were known (and $\1^\top x \ne 0$), this permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.
 
 It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$.
-Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$.
+Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$.
 From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
@@
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L}x_i x_{i+\Delta} 
+    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
         \1_{(\Delta \le L-i)} \right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
+    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
         \right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta) \right).
+    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
 %
@@
 
-If we knew $\sigma$, we can solve for $Q$ (and conversely).
+If we knew $\sigma$, we can solve for $Q$:
+%
+\begin{align}
+%
+    Q = \frac{A}{B - \sigma^2}.
+%
+\end{align}
+
+(Of course, this only works if $B \ne \sigma^2$, or equivalently if $\1^\top x \ne 0$.)
 
@@
 %
+%
+
+\section{An equation for $\sigma$}
+
+It turns out that $\nu \equiv \sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
+%
+\begin{align}
+%
+    Q = \frac{A}{B - \nu}.
+%
+\end{align}
+
+Now we move up to third-order moments.
+From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$.
+Taking the product, we have:
+%
+\begin{align}
+%
+    C &\equiv (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
+        \nonumber \\
+    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
+        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
+        + \sigma^2 \cdot (Q \cdot \1^\top x).
+%
+\end{align}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save9.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save6.tex
@@
 
-\section{An equation for $\sigma$}
+\section{A quadratic equation satisfied by $\sigma$}
 
-It turns out that $\nu \equiv \sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
+It turns out that $\sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
 %
@@
 %
-    Q = \frac{A}{B - \nu}.
+    Q = \frac{A}{B - \sigma^2}.
 %
@@
         + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
-        + \sigma^2 \cdot (Q \cdot \1^\top x).
+        + \sigma^2 \cdot (Q \cdot \1^\top x)
+        \nonumber \\
+    &= Q^2 \cdot w + \sigma^2 \cdot (Q \cdot \1^\top x),
+%
+\end{align}
+%
+where 
+%
+\begin{math}
+%
+    w = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
+        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta).
+%
+\end{math}
+
+From the observed third-order terms themselves, we can estimate:
+%
+\begin{align}
+%
+    D \equiv Q\cdot w + (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x).
 %
@@
 
+Consequently:
+%
+\begin{align}
+%
+    D\cdot Q - Q \cdot (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)
+    = Q^2 \cdot w = C - \sigma^2 \cdot (Q \cdot \1^\top x),
+%
+\end{align}
+%
+and therefore
+%
+\begin{align}
+%
+    Q = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
+            {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
+%
+\end{align}
+
+On the other hand, from the first equation relating $Q$ and $\sigma^2$, we see that:
+%
+\begin{align}
+%
+    Q = \frac{A}{B - \sigma^2}.
+%
+\end{align}
+%
+
+Putting these together, we have:
+%
+\begin{align}
+%
+    \frac{A}{B - \sigma^2}
+    = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
+        {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
+    = \frac{C - E \cdot \sigma^2}{D - F \cdot \sigma^2},
+%
+\end{align}
+%
+where
+%
+\begin{align}
+%
+    E = Q \cdot \1^\top x,
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+    F = (2L+1) \cdot Q \cdot \1^\top x.
+%
+\end{align}
+
+This is a quadratic equation for $\sigma^2$. Unfortunately, it can have two positive solutions, so I'm not sure if it helps...
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save6.tex
@@
 
-It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$.
+It will be notationally simpler to instead estimate $\beta \equiv \gamma \cdot L = J / n$.
 Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$.
-From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
+From the first moment we estimate $\beta \cdot (\1^\top x)$, and hence also its square:
 %
@@
 %
-    A \equiv (Q \cdot (\1^\top x))^2 
-    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
+    A \equiv (\beta \cdot (\1^\top x))^2 
+    &= \beta^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) 
+    &= \beta^2 \left( T_2(0) 
             + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
+    &= \beta^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
         \1_{(\Delta \le L-i)} \right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
+    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
         \right)
         \nonumber \\
-    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
+    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
 %
@@
 
-On the other hand, from the second moment we can estimate $Q \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $Q\cdot T_2(0) + \sigma^2$, and consequently $B \equiv Q \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$.
+On the other hand, from the second moment we can estimate $\beta \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $\beta\cdot T_2(0) + \sigma^2$, and consequently $B \equiv \beta \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$.
 Taking the ratio, we obtain the equation:
@@
 %
-    \frac{1}{Q} + \frac{\sigma^2}{A} = \frac{B}{A}.
+    \frac{1}{\beta} + \frac{\sigma^2}{A} = \frac{B}{A}.
 %
@@
 
-If we knew $\sigma$, we can solve for $Q$:
+If we knew $\sigma$, we can solve for $\beta$:
 %
@@
 %
-    Q = \frac{A}{B - \sigma^2}.
+    \beta = \frac{A}{B - \sigma^2}.
 %
@@
 
-\section{An equation for $\sigma$}
+\section{A pair of quadratics satisfied by $\beta$}
 
-It turns out that $\nu \equiv \sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
+It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments. The previous section gives the equation:
 %
@@
 %
-    Q = \frac{A}{B - \nu}.
+    \beta = \frac{A}{B - \sigma^2}.
 %
 \end{align}
+%
 
 Now we move up to third-order moments.
-From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$.
+From the first order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$.
 Taking the product, we have:
@@
 %
-    C &\equiv (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
+    C &\equiv (\beta \cdot \1^\top x) \cdot (\beta \cdot \|x\|^2 + \sigma^2)
         \nonumber \\
-    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
+    &= \beta^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
         + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
-        + \sigma^2 \cdot (Q \cdot \1^\top x).
+        + \sigma^2 \cdot (\beta \cdot \1^\top x)
+        \nonumber \\
+    &= \beta^2 \cdot \omega + \sigma^2 \cdot E,
 %
 \end{align}
+%
+where 
+%
+\begin{math}
+%
+    \omega = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
+        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta),
+%
+\end{math}
+%
+and
+%
+\begin{align}
+%
+    E = \beta \cdot \1^\top x.
+%
+\end{align}
+
+From the observed third-order terms themselves, we can estimate:
+%
+\begin{align}
+%
+    D \equiv \beta\cdot \omega + (2L+1)\cdot\sigma^2\cdot (\beta \cdot \1^\top x)
+    = \beta\cdot \omega + \sigma^2\cdot F,
+%
+\end{align}
+%
+where
+%
+\begin{align}
+%
+    F = (2L+1)\cdot(\beta \cdot \1^\top x).
+%
+\end{align}
+
+Consequently:
+%
+\begin{align}
+%
+    D\cdot \beta - \sigma^2 \cdot \beta  \cdot F
+    = \beta^2 \cdot w = C - \sigma^2 \cdot E.
+%
+\end{align}
+%
+Using $\sigma^2 = B - A/\beta$ and rearranging, we get:
+%
+\begin{align}
+%
+    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE = 0.
+%
+\end{align}
+
+\end{document}
+
+%
+%
+%
+%
+
+\section{Relation to other work on blind deconvolution}
+
+Blind deconvolution is a fundamental and well-studied problem in signal processing. Generally, models of the following form are considered:
+%
+\begin{align}
+%
+    Y = h \ast X  + \sigma N,
+%
+\end{align}
+%
+where $h$ is a fixed, non-random filter vector of length $L$, say; and $X$ is a length $n$ random vector; and $N$ is a random noise vector. Often, $X$'s entries are assumed to be iid.
+
+Many previous works are focused on recovering the vector $X$ from the observed vector $Y$.
+A standard method in the $\sigma = 0$ regime involves solving for the unknowns $h$ and $Y$ by maximizing a third or fourth order cumulant of $Y$ \cite{cadzow1996blind}.
+
+\bibliographystyle{plain}
+\bibliography{refs_bmra}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save1.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save.tex
@@
 
-It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments. The previous section gives the equation:
+It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments.
+The coefficients of these quadratics depend only on the observed moments, not on $\sigma$; so we can estimate $\beta$ (and hence $\gamma$) consistently, even without knowing the noise level.
+We can then estimate $\sigma$, and from them, recover the moments of $x$, which in turn lets us solve for $x$.
+
+%
+%
+%
+%
+
+\subsection{The first quadratic equation}
+
+The previous section gives the equation:
 %
@@
 \end{align}
+
+%
+%
+%
+%
+
+\subsection{The second quadratic equation}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save2.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save1.tex
@@
 
-\newcommand{\F}{\mathcal{F}}
+\renewcommand{\AA}{\mathcal{A}}
+\newcommand{\BB}{\mathcal{B}}
+\newcommand{\CC}{\mathcal{C}}
+\newcommand{\DD}{\mathcal{D}}
+\newcommand{\EE}{\mathcal{E}}
+\newcommand{\FF}{\mathcal{F}}
+
 \newcommand{\LL}{\mathcal{L}}
@@
 Now we move up to third-order moments.
-From the first order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$.
+From the first-order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$.
 Taking the product, we have:
@@
 %
-    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE = 0.
+    & \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE 
+        \nonumber \\
+    & \equiv \AA \beta^2  + \BB \beta  + \CC = 0.
 %
@@
 \subsection{The second quadratic equation}
+
+It is a straightforward computation to show that:
+%
+\begin{align}
+%
+    \phi &\equiv \left( \sum_{i=1}^L x_i \right)^3 
+        \nonumber \\
+    &= T_3(0,0) + 3\sum_{\Delta=1}^L T_3(\Delta,\Delta)
+        + 3 \sum_{\Delta=1}^L T_3(0,\Delta) 
+        + 6 \sum_{1 \le \Delta_1 < \Delta_1 \le L-1} T_3(\Delta_1,\Delta_2).
+%
+\end{align}
+
+The quantity $E = \beta \cdot \1^\top x$ is observed, and hence so is $E^3 = \beta^3 \cdot \phi$.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save4.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save2.tex
@@
 %
-    & \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE 
-        \nonumber \\
-    & \equiv \AA \beta^2  + \BB \beta  + \CC = 0.
+    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE 
+    \equiv \AA \beta^2  + \BB \beta  + \CC = 0.
 %
@@
 
-The quantity $E = \beta \cdot \1^\top x$ is observed, and hence so is $E^3 = \beta^3 \cdot \phi$.
+The quantity $E = \beta \cdot \1^\top x$ is observed, and hence so is $G \equiv E^3 = \beta^3 \cdot \phi$. On the other hand, from the observed third moments we can directly estimate:
+%
+\begin{align}
+%
+    H &\equiv M_3(0,0) + 3\sum_{\Delta=1}^L M_3(\Delta,\Delta)
+        + 3 \sum_{\Delta=1}^L M_3(0,\Delta) 
+        + 6 \sum_{1 \le \Delta_1 < \Delta_1 \le L-1} M_3(\Delta_1,\Delta_2)
+        \nonumber \\
+    &= \beta \cdot \phi +  (6L - 3) \cdot E \cdot \sigma^2 
+    = \beta \cdot \phi +  O \cdot \sigma^2 ,
+%
+\end{align}
+%
+where the quantity
+%
+\begin{align}
+%
+    O = (6L - 3) \cdot E = (6L - 3) \cdot \beta \cdot \1^\top x
+%
+\end{align}
+%
+is also observed. Taking the ratio of $G$ and $H$, we get:
+%
+\begin{align}
+%
+    \frac{H}{G} = \frac{\beta \cdot \phi +  O \cdot \sigma^2 }{G}
+    = \frac{\beta \cdot \phi}{\beta^3 \cdot \phi} + \frac{O \cdot \sigma^2}{G}
+    = \frac{1}{\beta^2} + \frac{O}{G} \cdot \sigma^2,
+%
+\end{align}
+%
+and solving for $\sigma^2$ in terms of $\beta$, we get:
+%
+\begin{align}
+%
+    \sigma^2 = \frac{H}{O} - \frac{G}{O} \cdot \frac{1}{\beta^2}.
+%
+\end{align}
 
+On the other hand, we already know:
+%
+\begin{align}
+%
+    \sigma^2 = B - \frac{A}{\beta}.
+%
+\end{align}
+
+Combining these two equations, we arrive at the quadratic:
+%
+\begin{align}
+%
+    (B-H/O) \cdot \beta^2 - A \cdot \beta + (G / O) 
+    \equiv \DD \beta^2 + \EE \beta + \FF = 0.
+%
+\end{align}
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save1.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save4.tex
@@
 where the limit is almost surely (we've used the strong law of large numbers), where $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
-
-\begin{comment}
-
-Actually, what Tamir meant when he said first moment was the average of the windows' averages (a scalar), not the average window (a vector).
-But this also converges a.s.\ to $\gamma \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows.
-The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$.
-Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
-%
-\begin{align}
-%
-    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
-    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
-    = \gamma \cdot \bar{x}.
-%
-\end{align}
-
-\end{comment}
 
@@
 %
-    A \equiv (\beta \cdot (\1^\top x))^2 
+    A \equiv (\beta \cdot \1^\top x)^2 
     &= \beta^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
@@
 We can then estimate $\sigma$, and from them, recover the moments of $x$, which in turn lets us solve for $x$.
+
+Of course, for finite $n$ and large $\sigma$ the formulas for $\beta$ and $\sigma$ will be noisy.
+Consequently, I suggest instead adding them as variables to the non-linear least squares problem; that is, solve for all of $x$, $\beta$ and $\nu \equiv \sigma^2$ by fitting their moments to the observed moments via least-squares.
 
@@
 %
-    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE 
+    (D - BF) \cdot \beta^2  + (AF + BE - C) \cdot \beta   - AE 
     \equiv \AA \beta^2  + \BB \beta  + \CC = 0.
+%
+\end{align}
+
+We can simplify the expressions a little bit. First, we observe that:
+%
+\begin{align}
+%
+    \CC = -AE = -(\beta \cdot \1^\top x)^3 = -E^3 \equiv -G.
+%
+\end{align}
+
+Second, we can simplify $\BB$:
+%
+\begin{align}
+%
+    \BB = AF + BE - C = (2L+1) \cdot G + 2E \beta \sum_{\Delta=1}^{L-1} T_2(\Delta).
 %
@@
 \end{align}
+
+\subsection{Independence of the quadratics}
+
+We can show that for generic $x$, the two quadratics are independent; and in fact, for all sufficiently large $\beta$, they are independent for any $x$ (not just generic).
+By ``generic'' I mean on a set with complement of Lebesgue measure 0.
+
+To see this, it's enough to show that the ratio of coefficients is not the same. We have:
+%
+\begin{align}
+%
+    \frac{\BB}{\CC} = -(2L + 1) - \frac{2\beta \sum_{\Delta \ge 1}T_2(\Delta)}{E^2}
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+    \frac{\EE}{\FF} = - (6L - 3).
+%
+\end{align}
+
+Suppose the quadratics are dependent. Then $\BB / \CC = \EE / \FF$, or
+%
+\begin{align}
+%
+    2L + 1 + \frac{2\beta \sum_{\Delta \ge 1}T_2(\Delta)}{E^2} = 6L  - 3
+%
+\end{align}
+%
+or equivalently
+%
+\begin{align}
+%
+    4(L-1)\beta^2(\1^\top x)^2 
+    &=  4(L-1)E^2 
+        \nonumber \\
+    &= 2 \beta \sum_{\Delta\ge1}T_2(\Delta) 
+        \nonumber \\
+    &= \beta ( (\1^\top x)^2 - \|x\|^2 ) .
+%
+\end{align}
+
+Rearranging we get:
+%
+\begin{align}
+%
+    (4(L-1)\beta - 1)(\1^\top x)^2 + \|x\|^2 = 0.
+%
+\end{align}
+%
+This describes a quadratic which has measure zero. But we can actually say something more. Since $(\1^\top x)^2 \le L \|x\|^2$, we must have:
+%
+\begin{align}
+%
+    1 - 4(L-1)\beta = \frac{\|x\|^2}{(\1^\top x)^2} \ge \frac{1}{L}
+%
+\end{align}
+%
+i.e.
+%
+\begin{align}
+%
+    (L-1)(1 - 4L\beta) = L -1 - 4(L-1)L \beta \ge 0
+%
+\end{align}
+%
+so that we need $\beta \le 1 / (4L)$. In other words, if $\beta \ge 1 / (4L)$, then the quadratics are independent.
+
+%
+%
+%
+%
+
+\section{Relation to system identification}
+
+This problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing.
+In this class of problems, the user observes a length $n$ signal $Y$ given by:
+%
+\begin{align}
+%
+    Y = x \ast W + \ep
+%
+\end{align}
+%
+where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random sequence; and $\ep$ is random additive noise.
+The goal of this problem is to estimate the ``system'' vector $x$.
+Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.
+
+The method of moments has been proposed as a solution to the system identification problem.
+
 \end{document}
@@
 
+%
+%
+%
+
 \end{document}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save10.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save1.tex
@@
 
-This problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing.
-In this class of problems, the user observes a length $n$ signal $Y$ given by:
+Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
 %
@@
 %
-    Y = x \ast W + \ep
+    Y = x \ast W + \ep,
 %
@@
 %
-where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random sequence; and $\ep$ is random additive noise.
+where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise.
 The goal of this problem is to estimate the ``system'' vector $x$.
@@
 
-The method of moments has been proposed as a solution to the system identification problem.
+Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$.
+Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead.
+One proposed heuristic for computing the maximization is to use Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.
+The EM method is based upon a certain ``forward-backward'' procedure used in hidden Markov models, described in \cite{rabiner1989tutorial}.
+
+Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}.
+This paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework.
+Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.
+
+Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification.
+The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}.
+A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using fourth-order cumulants is described in \cite{giannakis1989id}.
+
+%%%The problem of system identification should be distinguished from the related problem of blind deconvolution.
+In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$.
+
+\bibliographystyle{plain}
+\bibliography{refs_bmra}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save2.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save1.tex
@@
 %
-where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random sequence; and $\ep$ is random additive noise.
+where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise.
 The goal of this problem is to estimate the ``system'' vector $x$.
 Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.
+Note that the entries of $W$ do not need to be iid
 
-The method of moments has been proposed as a solution to the system identification problem.
+A number of methods have been proposed for the system identification problem under various additional constraints.
+Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK.
+This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.
+
+An entirely different approach based on expectation-maximization is described in TKTK.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save3.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save2.tex
@@
 Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.
-Note that the entries of $W$ do not need to be iid
 
-A number of methods have been proposed for the system identification problem under various additional constraints.
+Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$.
+One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.
+
+Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.
+
 Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK.
@@
 
-An entirely different approach based on expectation-maximization is described in TKTK.
+The problem of system identification should be distinguished from blind deconvolution. In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$. TKTK
+
+\bibliographystyle{plain}
+\bibliography{refs_bmra}
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save4.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save3.tex
@@
 Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.
+The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators.
+Another method based on third-order cumulants was described in \cite{giannakis1989id}.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save5.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save4.tex
@@
 Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$.
+Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead.
 One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.
+The EM method is based upon a certain ``forward-backward'' procedure described in \cite{rabiner1989tutorial}.
 
@@
 The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators.
-Another method based on third-order cumulants was described in \cite{giannakis1989id}.
-
-Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK.
-This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.
+Another method based on third-order cumulants is described in \cite{giannakis1989id}.
 

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save7.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save5.tex
@@
 
+Other problems dealing with specific parameterized models of $x$ have also been considered, for instance in \cite{andrieu2001bayesian}.
+This approach also permits the inclusion of multiple $x$, as in our heterogeneity framework.
+However, the method in \cite{andrieu2001bayesian} simultaneously solves for the signal parameters and their locations, which becomes ill-posed in the high-noise regime.
+
 The problem of system identification should be distinguished from blind deconvolution. In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$. TKTK

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save8.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save7.tex
@@
 One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.
-The EM method is based upon a certain ``forward-backward'' procedure described in \cite{rabiner1989tutorial}.
+The EM method is based upon a certain ``forward-backward'' procedure used in hidden Markov models, described in \cite{rabiner1989tutorial}.
 
-Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.
+Because the likelihood approach is computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.
 The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save9.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save10.tex
@@
 The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}.
-A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using fourth-order cumulants is described in \cite{giannakis1989id}.
+A method using third-order cumulants is described in \cite{giannakis1989id}, while a method using fourth-order cumulants is described in \cite{tugnait1984id}.
 

### 2018-05-14 TEX/notes_will/notes_moments/notes.tex
updates on section 2

--- 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save9.tex
@@
 where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise.
+The problem has also been studied in the case of a known input $W$ \cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}.
 The goal of this problem is to estimate the ``system'' vector $x$.
-Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.
+The question of identifiability of $x$ under this observation model is addressed for certain non-Gaussian $W$ in \cite{benveniste1980}, and for certain Gaussian inputs $W$ in \cite{kormylo1983id}.
+In the special case where $W$ is a random, unknown sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.
 
@@
 Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}.
-This paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework.
+That same paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework.
 Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.
@@
 The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}.
-A method using third-order cumulants is described in \cite{giannakis1989id}, while a method using fourth-order cumulants is described in \cite{tugnait1984id}.
+A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using third-order cumulants is described in \cite{giannakis1989id}.
+
+%%%All these papers note that in general, it is not possible to recover $x$ from second-order statistics alone, since the phase information is lost.
 

### 2018-05-14 2D_PR/BigMRAgpu/generate_clean_micrograph_2D.m

@@ -1,0 +1,80 @@
+function [Y, placed] = generate_clean_micrograph_2D(X, W, N, m)
+% Inputs:
+%   X: signal of size LxL
+%   W: separation zone has size WxW: any square of that size can only touch
+%      one signal occurence.
+%   N: micrograph has size NxN
+%   m: the signal will appear m times in the micrograph, in random places,
+%      with separation specified by W. If it proves difficult to place m
+%      copies of the signal obeying that rule, the number of copies may be
+%      smaller.
+%
+% Outputs:
+%   Y: micrograph of size NxN (clean)
+%   placed: actual number of occurrences of the signal X in Y.
+
+% Since we attempt placement at random, we need the end-result to be
+% quite sparse to have decent chances of finding m spots.
+if N^2 < 10*m*W^2
+    warning('BigMRA:gendata2D', ...
+        'It may be difficult to get this many repetitions...');
+end
+
+rangeW = 0:(W-1);
+
+% The mask has the same size as the micrograph. Each pixel in the mask
+% corresponds to a possible location for the upper-left corner of the
+% signal, to be placed in the micrograph. A value of zero means the
+% spot is free, while a value of 1 means the spot is forbidden (either
+% because a signal will already be there, or because it is in the area
+% of separation of another signal.)
+mask = zeros(N, N);
+% The locations table recors the chosen signal locations.
+locations = zeros(m, 2);
+% This counter records how many signals we successfully placed.
+placed = 0;
+% Since placement is random, there is a chance that we will get a lot
+% of failed candidates. To make up for it, we allow for more than m
+% trials. But we still put a hard cap on it to avoid an infinite loop.
+max_trials = 2*m;
+
+for counter = 1 : max_trials
+    
+    % Pick a candidate location for the upper-left corner of the signal
+    candidate = randi(N-W+1, 1, 2);
+    
+    % Check if there is enough room, taking the separation rule into
+    % account. That is, a square of size WxW with upper-left corner
+    % specified by the candidate must be entirely free.
+    if all(mask(candidate(1)+rangeW, candidate(2)+rangeW) == 0)
+        
+        % Record the successful candidate
+        placed = placed + 1;
+        locations(placed, :) = candidate;
+        
+        % Mark the area as reserved
+        mask(candidate(1)+rangeW, candidate(2)+rangeW) = 1;
+        
[…]

### 2018-05-14 2D_PR/BigMRAgpu/moments_from_data_no_debias_2D.m

@@ -1,0 +1,75 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+
+if gpuDeviceCount>0 
+    	gpu_flag = 1;
+else
+	gpu_flag = 0;
+end
+
+    [N1, N2] = size(Y);
+
+    M1 = sum(Y(:));
+    
+    n2 = size(list2, 1);
+
+    if gpu_flag
+    M2 = zeros(n2, 1,'gpuArray');
+    Y = gpuArray(Y);
+    else
+    M2 = zeros(n2, 1);
+    end
+    
+parfor k = 1 : n2
+
+       %for  k = 1 : n2
+        
+	shift1 = list2(k, :);
+        
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+        
+        X1 = Y(range1, range2); %#ok<PFBNS>
+        X2 = Y(range1-shift1(1), range2-shift1(2));
+        
+        M2(k) = sum(X1(:) .* X2(:)); % bsxfun
+        %T = bsxfun(@times,X1,X2);
+        %M2(k) = sum(T(:)); % bsxfun
+    end
+    
+    n3 = size(list3, 1);
+    M3 = zeros(n3, 1,'gpuArray');
+    
+   parfor k = 1 : n3
+       %for k = 1 : n3
+ 
+        shifts = list3(k, :);
+        shift1 = shifts([1, 2]);
+        shift2 = shifts([3, 4]);
+
+        vals1 = [0, shift1(1), shift2(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2), shift2(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+        
+        X1 = Y(range1, range2); %#ok<PFBNS>
+        X2 = Y(range1-shift1(1), range2-shift1(2));
+        X3 = Y(range1-shift2(1), range2-shift2(2));
+        
+        M3(k) = sum(X1(:) .* X2(:) .* X3(:)); %bsxfun
[…]

### 2018-05-14 2D_PR/BigMRAgpu/moments_from_data_no_debias_2D_v2.m

@@ -1,0 +1,76 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v2(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+
+Y = gather(Y); % make sure I am not in gpu mode
+
+if gpuDeviceCount>0 
+    gpu_flag = 1;
+else
+    gpu_flag = 0;
+end
+
+    [N1, N2] = size(Y);
+
+    M1 = sum(Y(:));
+    
+    n2 = size(list2, 1);
+
+    if gpu_flag
+    M2 = zeros(n2, 1,'gpuArray');
+    else
+    M2 = zeros(n2, 1);
+    end
+    
+    parfor k = 1 : n2
+        
+        shift1 = list2(k, :);
+        
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+        
+        X1 = gpuArray(Y(range1, range2)); %#ok<PFBNS>
+        X2 = gpuArray(Y(range1-shift1(1), range2-shift1(2)));
+        
+        M2(k) = sum(X1(:) .* X2(:)); % bsxfun
+        %T = (bsxfun(@times,X1,X2));
+        %M2(k) = sum(T(:)); % bsxfun
+    end
+    
+    n3 = size(list3, 1);
+    if gpu_flag
+        M3 = zeros(n3, 1,'gpuArray');
+    else
+        M3 = zeros(n3, 1);
+    end
+    
+    parfor k = 1 : n3
+        
+        shifts = list3(k, :);
+        shift1 = shifts([1, 2]);
+        shift2 = shifts([3, 4]);
+
+        vals1 = [0, shift1(1), shift2(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2), shift2(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+        
+        X1 = gpuArray(Y(range1, range2)); %#ok<PFBNS>
+        X2 =  gpuArray(Y(range1-shift1(1), range2-shift1(2)));
+        X3 =  gpuArray(Y(range1-shift2(1), range2-shift2(2)));
[…]

### 2018-05-14 2D_PR/BigMRAgpu/moments_from_data_no_debias_2D_v4.m

@@ -1,0 +1,148 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v4(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+
+n2 = size(list2, 1);
+n3 = size(list3, 1);
+
+gpu_flag = (gpuDeviceCount>0);
+
+if gpu_flag > 0
+    M2 = zeros(n2, 1,'gpuArray');
+    M3 = zeros(n3, 1,'gpuArray');
+else
+    M2 = zeros(n2, 1);
+    M3 = zeros(n3, 1);
+end
+
+[N1, N2] = size(Y);
+
+batch_size = 1;
+
+if gpu_flag
+    Y = gpuArray(Y);
+    X1 = zeros(N1,N2,batch_size,'gpuArray');
+    X2 = zeros(N1,N2,batch_size,'gpuArray');
+else
+    X1 = zeros(N1,N2,batch_size);
+    X2 = zeros(N1,N2,batch_size);
+end
+
+
+
+%% First moment
+
+M1 = sum(Y(:));
+
+%% Second moment
+
+num_batch = ceil(n2/batch_size);
+
+for i = 1:num_batch
+    
+    I1 = (i-1)*batch_size+1;
+    if n2<i*batch_size
+        I2 = n2;
+        last_iter = n2 - (i-1)*batch_size;
+    else
+        I2 = i*batch_size;
+        last_iter = batch_size;
+    end
+    
+    for k = 1 : last_iter
+        
+        shift1 = list2((i-1)*batch_size+k, :);
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+        
+        L1 = length(range1);
+        L2 = length(range2);
+        
+        X1(1:L1,1:L2,k) = Y(range1, range2);
+        X2(1:L1,1:L2,k) = Y(range1-shift1(1), range2-shift1(2));
+        
+    end
+    
+    XX1 = reshape(X1,N1*N2,[]);
+    XX2 = reshape(X2,N1*N2,[]);
+    
+    if last_iter<batch_size
+        XX1 = XX1(:,1:last_iter);
[…]

### 2018-05-14 2D_PR2/BigMRAgpu/least_squares_2D.m

@@ -1,0 +1,67 @@
+function [X_est, problem, stats] = least_squares_2D(M1, M2, M3, W, sigma, N, L, m, list2, list3, X0) %#ok<INUSL>
+
+    params.W = W;
+    params.N = N;
+    params.m = m;
+    params.M1 = M1;
+    params.M2 = M2;
+    params.M3 = M3;
+    params.list2 = list2;
+    params.list3 = list3;
+    params.sigma = sigma;
+
+    %% Precompute biases once and for all
+    n2 = size(list2, 1);
+    bias2 = zeros(n2, 1);
+    for k = 1 : n2
+        shift = list2(k, :);
+        if all(shift == [0 0])
+            bias2(k) = N^2*sigma^2;
+        end
+    end
+    
+    n3 = size(list3, 1);
+    bias3 = zeros(n3, 1);
+    for k = 1 : n3
+        shift1 = list3(k, [1, 2]);
+        shift2 = list3(k, [3, 4]);
+        if all(shift1 == [0, 0])
+            bias3(k) = bias3(k) + M1*sigma^2; % this is the 'data' M1 (fixed)
+        end
+        if all(shift2 == [0, 0])
+            bias3(k) = bias3(k) + M1*sigma^2;
+        end
+        if all(shift1 == shift2)
+            bias3(k) = bias3(k) + M1*sigma^2;
+        end
+    end
+    
+    params.bias2 = sparse(bias2);
+    params.bias3 = sparse(bias3);
+
+    %% Setup Manopt problem
+
+    % Choose wisely if optimize in LxL or WxW
+    % It seems that WxW might be necessary to avoid local optima.
+    manifold = euclideanfactory(W, W);
+    
+    problem.M = manifold;
+    problem.costgrad = @(X) least_squares_2D_cost_grad_parallel(X, params);
+
+    if ~exist('X0', 'var')
+        X0 = [];
+    end
+
+%     opts = struct();
+%     opts.maxiter = 500;
+%     [X_est, loss] = rlbfgs(problem, X0, opts); %#ok<ASGLU>
+%     X0 = X_est;
+    
+    opts = struct();
+    opts.tolgradnorm = 1e-5;
+    opts.maxiter = 1000;
+    warning('off', 'manopt:getHessian:approx');
+    [X_est, loss, stats] = trustregions(problem, X0, opts); %#ok<ASGLU>
+    warning('on', 'manopt:getHessian:approx');
+
+end

### 2018-05-14 2D_PR2/BigMRAgpu/moments_from_data_no_debias_2D_v3.m

@@ -1,0 +1,116 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v3(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+
+n2 = size(list2, 1);
+if isempty(list3)
+    M3 = [];
+else
+    n3 = size(list3, 1);
+end
+
+gpu_flag = (gpuDeviceCount>0);
+
+if gpu_flag > 0
+    M2 = zeros(n2, 1,'gpuArray');
+    %    M3 = zeros(n3, 1,'gpuArray');
+else
+    M2 = zeros(n2, 1);
+    %   M3 = zeros(n3, 1);
+end
+
+[N1, N2] = size(Y);
+
+if gpu_flag
+    Y = gpuArray(Y);
+    %X1 = zeros(N1,N2,n2,'gpuArray');
+    %X2 = zeros(N1,N2,n2,'gpuArray');
+end
+    %X1 = zeros(N1,N2,n2);
+    %X2 = zeros(N1,N2,n2);
+%end
+
+M1 = sum(Y(:));
+
+%parfor k = 1 : n2
+for k = 1 : n2
+    
+    shift1 = list2(k, :);
+    
+    vals1 = [0, shift1(1)];
+    range1 = (1+max(vals1)) : (N1+min(vals1));
+    vals2 = [0, shift1(2)];
+    range2 = (1+max(vals2)) : (N2+min(vals2));
+    
+    %L1 = length(range1);
+    %L2 = length(range2);
+    
+    X1 = Y(range1, range2); 
+    X2 = Y(range1-shift1(1), range2-shift1(2));
+    %X1(1:L1,1:L2,k) = Y(range1, range2); %#ok<PFBNS>
+    %X2(1:L1,1:L2,k) = Y(range1-shift1(1), range2-shift1(2));
+ 
+    %X1 = X1(:);
+    %X2 = X2(:);
+    %M2(k) = sum(bsxfun(@times,X1,X2));
+    M2(k) = sum(X1(:) .* X2(:)); % bsxfun
+    %T = bsxfun(@times,X1,X2);
+    %M2(k) = sum(T(:)); % bsxfun
+end
+
+%M2 = sum(bsxfun(@times,reshape(X1,N1*N2,[]),reshape(X2,N1*N2,[])),1);
+% 
+% if 0
+%     
+%     if gpu_flag
[…]

### 2018-05-14 2D_PR2/BigMRAgpu/moments_from_data_no_debias_2D_v4.m

@@ -1,0 +1,119 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v4(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+
+n2 = size(list2, 1);
+n3 = size(list3, 1);
+
+gpu_flag = (gpuDeviceCount>0);
+
+if gpu_flag > 0
+    M2 = zeros(n2, 1,'gpuArray');
+    M3 = zeros(n3, 1,'gpuArray');
+else
+    M2 = zeros(n2, 1);
+    M3 = zeros(n3, 1);
+end
+
+[N1, N2] = size(Y);
+
+% if gpu_flag
+%     Y = gpuArray(Y);
+%     X1 = zeros(N1,N2,'gpuArray');
+%     X2 = zeros(N1,N2,'gpuArray');
+% else
+%     X1 = zeros(N1,N2);
+%     X2 = zeros(N1,N2);
+% end
+
+%% First moment
+
+M1 = sum(Y(:));
+
+%% Second moment
+
+for i = 1:n2
+           
+        shift1 = list2(i, :);
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+          
+        X1 = Y(range1, range2);
+        X2 = Y(range1-shift1(1), range2-shift1(2));
+            
+        M2(i) = sum(X1(:).*X2(:));
+    
+end
+
+% 
+% % Third moment
+% 
+% if gpu_flag
+%     X1 = zeros(N1,N2,batch_size,'gpuArray');
+%     X2 = zeros(N1,N2,batch_size,'gpuArray');
+%     X3 = zeros(N1,N2,batch_size,'gpuArray');
+% else
+%     X1 = zeros(N1,N2,batch_size);
+%     X2 = zeros(N1,N2,batch_size);
+%     X3 = zeros(N1,N2,batch_size);
+% end
+% 
+% num_batch = ceil(n3/batch_size);
+% 
+% for i = 1:num_batch
+%     
+%     I1 = (i-1)*batch_size+1;
+%     if n3<i*batch_size
+%         I2 = n3;
+%         last_iter = n3 - (i-1)*batch_size;
+%     else
+%         I2 = i*batch_size;
[…]

### 2018-05-14 2D_PR2/BigMRAgpu/moments_from_data_no_debias_2D_v5.m

@@ -1,0 +1,122 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v5(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+M3 = [];
+n2 = size(list2, 1);
+%n3 = size(list3, 1);
+
+gpu_flag = (gpuDeviceCount>0);
+
+if gpu_flag > 0
+%   Y = gpuArray(Y);
+    M2 = zeros(n2, 1,'gpuArray');
+ %   M3 = zeros(n3, 1,'gpuArray');
+else
+    M2 = zeros(n2, 1);
+  %  M3 = zeros(n3, 1);
+end
+
+[N1, N2] = size(Y);
+
+% if gpu_flag
+%     Y = gpuArray(Y);
+%     X1 = zeros(N1,N2,'gpuArray');
+%     X2 = zeros(N1,N2,'gpuArray');
+% else
+%     X1 = zeros(N1,N2);
+%     X2 = zeros(N1,N2);
+% end
+
+%% First moment
+
+M1 = sum(Y(:));
+
+%% Second moment
+
+parfor i = 1:n2
+           
+        shift1 = list2(i, :);
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+          
+    %    X1 = Y(range1, range2);
+     %   X2 = Y(range1-shift1(1), range2-shift1(2));
+         
+       M2(i) = sum(bsxfun(@times, reshape(Y(range1, range2),1,[]),reshape(Y(range1-shift1(1), range2-shift1(2)),1,[])));
+      %   M2(i) = sum(bsxfun(@times, X1(:),X2(:)));     
+        %M2(i) = sum(X1(:).*X2(:));
+    
+end
+
+% 
+% % Third moment
+% 
+% if gpu_flag
+%     X1 = zeros(N1,N2,batch_size,'gpuArray');
+%     X2 = zeros(N1,N2,batch_size,'gpuArray');
+%     X3 = zeros(N1,N2,batch_size,'gpuArray');
+% else
+%     X1 = zeros(N1,N2,batch_size);
+%     X2 = zeros(N1,N2,batch_size);
+%     X3 = zeros(N1,N2,batch_size);
+% end
+% 
[…]

### 2018-05-14 2D_PR2/recovery/least_squares_2D.m

@@ -1,0 +1,79 @@
+function [X_est, problem, stats] = least_squares_2D(M1, M2, M3, W, sigma, N, L, m, list2, list3, X0,method,opt_window,max_iter) %#ok<INUSL>
+
+    params.W = W;
+    params.N = N;
+    params.m = m;
+    params.M1 = M1;
+    params.M2 = M2;
+    params.M3 = M3;
+    params.list2 = list2;
+    params.list3 = list3;
+    params.sigma = sigma;
+
+    %% Precompute biases once and for all
+    n2 = size(list2, 1);
+    bias2 = zeros(n2, 1);
+    for k = 1 : n2
+        shift = list2(k, :);
+        if all(shift == [0 0])
+            bias2(k) = N^2*sigma^2;
+        end
+    end
+    
+    n3 = size(list3, 1);
+    bias3 = zeros(n3, 1);
+    for k = 1 : n3
+        shift1 = list3(k, [1, 2]);
+        shift2 = list3(k, [3, 4]);
+        if all(shift1 == [0, 0])
+            bias3(k) = bias3(k) + M1*sigma^2; % this is the 'data' M1 (fixed)
+        end
+        if all(shift2 == [0, 0])
+            bias3(k) = bias3(k) + M1*sigma^2;
+        end
+        if all(shift1 == shift2)
+            bias3(k) = bias3(k) + M1*sigma^2;
+        end
+    end
+    
+    params.bias2 = sparse(bias2);
+    params.bias3 = sparse(bias3);
+
+    %% Setup Manopt problem
+
+    % Choose wisely if optimize in LxL or WxW
+    % It seems that WxW might be necessary to avoid local optima.
+   % manifold = euclideanfactory(W, W);
+     manifold = euclideanfactory(opt_window, opt_window);
+    
+%    manifold = euclideanfactory((W+1)/2, (W+1)/2);
+    
+    problem.M = manifold;
+    problem.costgrad = @(X) least_squares_2D_cost_grad_parallel(X, params);
+
+    if ~exist('X0', 'var')
+        X0 = [];
+    end
+
+    if ~exist('method', 'var')
+        method = 'trust_regions';
+    end
+
+    
+    opts = struct();
+    opts.tolgradnorm = 1e-5;
+    opts.maxtime = 60*60*10; %10hours
+    opts.maxiter = max_iter;
+
+    %opts.tolcost = 1e-2;
+    opts.verbosity = 2;
[…]

### 2018-05-14 2D_PR2/recovery/merging_data_files.m

@@ -1,0 +1,76 @@
+% merging few data files
+clear; 
+
+load 'data_exp_gpu_1500';
+
+Temp_M1 = M1;
+Temp_M2 = M2;
+Temp_M3 = M3;
+Temp_m = m_eff(m_eff>0);
+
+load 'data_exp_gpu_900';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+
+load 'data_exp_gpu_2000';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+load 'data_exp_gpu_2000_2';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+
+load 'data_exp_gpu_600';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+
+load 'data_exp_chai_2800';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+load 'data_exp_chai';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+
+load 'data_exp_gpu';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
[…]

### 2018-05-14 2D_PR2/recovery/perform_tv_denoising.m

@@ -1,0 +1,208 @@
+function [xtv,err,tv,lalist] = perform_tv_denoising(x,options)
+
+% perform_tv_denoising - denoising with TV minimization
+%
+%   [xtv,err,tv,lalist] = perform_tv_denoising(x,options);
+%
+%   Solve the lagragian TV minimization (Rudin-Osher-Fatemi)
+%       xtv = argmin_u 1/2 * |x-u|^2 + lambda*TV(u)
+%   where TV is the discrete TV norm
+%       1D:  TV(u) = sum_i |u(i)-u(i-1)|
+%       2D:  TV(u) = sum_i sqrt( ux(i)^2 + uy(i) )
+%   where ux,uy are partial derivative (finite difference along x/y).
+%
+%   It implements Chambolle's iterative fixed point algorithm
+%       A. Chambolle: An Algorithm for Total Variation Minimization and Applications.
+%       Journal of Mathematical Imaging and Vision 20 (1-2): 89-97, January - March, 2004
+%
+%   Works for 1D signal and 2D images.
+%
+%   lambda controls how much denoising you want.
+%   You can track the denoising level in various way:
+%       * simply set options.lambda
+%       * set values options.lambda_max and options.lambda_min
+%       and the algorithm will linearely decrease the value of 
+%       lambda between these values.
+%       If you set (in an oracle fashion) options.x0, then 
+%       the algorihtm will return the xtv that is the closest to x0.
+%       * set an error tolerance options.etgt and the algorithm
+%       will return the xtv such that norm(xtv-x,'fro')=etgt
+%
+%   To perform TV inpainting, you can set options.mask and options.xtgt
+%   where mask(i)=1 is a missing pixel and mask(i)=0 impose value xtgt(i)
+%   for the solution.
+%
+%   Gabriel Peyre
+
+
+options.null = 0;
+
+nbdims = nb_dims(x);
+
+
+la = getoptions(options, 'lambda', []);
+lamax = .4;
+lamin = eps;
+if not(isempty(la))
+    lamax = la; lamin = la;
+end
+lamax = getoptions(options, 'lambda_max', lamax);
+lamin = getoptions(options, 'lambda_min', lamin);
+verb = getoptions(options, 'verb', 1);
+lamin = max(lamin,eps);
+
+% possible use for inpainting
+mask = getoptions(options, 'mask', []);
[…]

### 2018-05-14 2D_PR2/recovery/recovery_multiple_init.m

@@ -1,0 +1,86 @@
+% Script to run the LS from multiple initializations
+
+%load('data_exp_gpu_1500.mat');
+
+merging_data_files;
+
+fprintf('loading data\n');
+fprintf('sigma = %.2g\n',sigma);
+m_total = sum(m_eff);
+fprintf('m total = %d\n',m_total);
+X_zp = [X zeros(L, W-L) ; zeros(W-L, W)];
+m_eff = m_eff(m_eff>0);
+n_micrographs = length(m_eff);
+fprintf('n_micrographs = %d\n',n_micrographs);
+
+if isempty(gcp('nocreate'))
+    parpool(2, 'IdleTimeout', 240);
+end
+
+%% PS estimations
+
+PS = M2PS_partial(M2,list2,m_total,sigma,n_micrographs*N^2,W);
+PSX = abs(fft2(X_zp)).^2;
+%figure(8786); imagesc([PS - PSX]);
+err_PS = norm(PSX(:) - PS(:))/norm(PSX(:));
+fprintf('error PS = %.6g\n',err_PS);
+
+%% LS
+N_eff = N*sqrt(n_micrographs);
+max_iter_1 = 20;
+max_iter_2 = 100;
+num_init = 100;
+err_LS = zeros(num_init,1);
+
+for i = 1:num_init
+    X0  = rand(L);
+    opt_window = W;
+    [Xest_LS_W, problem,stats] = least_squares_2D(M1, M2, M3, W, sigma, N_eff, L, m_total, list2, list3, X0,'conjugate_gradient',opt_window,max_iter_1) ; 
+    opt_window = L;
+    [Xest_LS, problem,stats] = least_squares_2D(M1, M2, M3, W, sigma, N_eff, L, m_total, list2, list3, Xest_LS_W(1:L,1:L),'conjugate_gradient',opt_window,max_iter_2);
+    err1 = norm(Xest_LS - X,'fro')/norm(X(:));
+    err2 = norm(rot90(Xest_LS,2) - X,'fro')/norm(X(:));
+    if err1<err2
+        err_LS(i) = err1;
+    else
+        err_LS(i) = err2;
+        Xest_LS = rot90(Xest_LS,2);
+    end
+    fprintf('iter = %g, error = %.4g\n',i,err_LS(i));
+    if i==1 
+                Xest = Xest_LS;
+    elseif  err_LS(i)<min(err_LS(1:i-1))
+        Xest = Xest_LS;
+    end
+end
[…]

### 2018-05-14 2D_PR3/example.m

@@ -1,0 +1,78 @@
+clear;
+close all;
+clc;
+
+seed_rng = rng('shuffle');
+
+%if isempty(gcp('nocreate'))
+%    parpool(20,'IdleTimeout', 240);
+%end
+
+%% Defining the problem
+
+% Load a grayscale image of size LxL, removing the mean and scale between -1 and 1.
+X = double(rgb2gray(imread('Einstein5_small.jpg')));
+X = X - mean(X(:));
+X = X/max(abs(X(:)));
+L = 50;
+W = 2*L-1;
+X = imresize(X, [L, L]);
+% Pick a noise level
+sigma = 3;
+% Desired number of occurrences of the signal X in each micrograph
+m_want = 1000; 
+% Number of micrographs to generate
+n_micrographs = 1; %1e4;
+% Each micrograph is square of size NxN
+N = 4000; %1000;
+
+%% Pick which correlation coefficients to sample
+
+top = (W-1)/2;
+list2 = zeros((W^2+1)/2, 2);
+k = 0;
+for k1 = 0 : top
+    k = k + 1;
+    list2(k, :) = [k1, 0];
+end
+for k1 = (-top) : top
+    for k2 = 1 : top
+        k = k + 1;
+        list2(k, :) = [k1, k2];
+    end
+end
+
+list3 = [];
+n3 = size(list3, 1);
+%% Generate the micrographs and collect their moments
+
+m_eff = zeros(n_micrographs, 1);
+
+for iter = 1:n_micrographs
+
+% Generate micrograph
+    tic;
+    [Y_clean, m_eff(iter)] = generate_clean_micrograph_2D(X, W, N, m_want);
+    Y_obs = Y_clean + sigma*randn(N);    
+    %Y_obs = imgaussfilt(Y_obs,4);
+    fprintf('iter = %d, m_eff =  %d \n', iter, m_eff(iter));
+    [M1_micrograph, M2_micrograph, M3_micrograph] = moments_from_data_no_debias_2D_v5(Y_obs, list2, list3);    
+    fprintf('Iteration timing: %.2g [s]\n', toc());
+    
+    if iter == 1
+        M1 =  M1_micrograph;
+        M2 =  M2_micrograph;
+        M3 =  M3_micrograph;
+    else
+        M1 = M1 + M1_micrograph;
+        M2 = M2 + M2_micrograph;
+        M3 = M3 + M3_micrograph;
+    end
+    
+    if mod(iter,100) == 0
[…]

### 2018-05-14 2D_PR3/generate_clean_micrograph_2D.m

@@ -1,0 +1,81 @@
+function [Y, placed] = generate_clean_micrograph_2D(X, W, N, m)
+% Inputs:
+%   X: signal of size LxL
+%   W: separation zone has size WxW: any square of that size can only touch
+%      one signal occurence.
+%   N: micrograph has size NxN
+%   m: the signal will appear m times in the micrograph, in random places,
+%      with separation specified by W. If it proves difficult to place m
+%      copies of the signal obeying that rule, the number of copies may be
+%      smaller.
+%
+% Outputs:
+%   Y: micrograph of size NxN (clean)
+%   placed: actual number of occurrences of the signal X in Y.
+
+% Since we attempt placement at random, we need the end-result to be
+% quite sparse to have decent chances of finding m spots.
+%if N^2 < 10*m*W^2
+%    warning('BigMRA:gendata2D', ...
+%        'It may be difficult to get this many repetitions...');
+%end
+
+rangeW = 0:(W-1);
+
+% The mask has the same size as the micrograph. Each pixel in the mask
+% corresponds to a possible location for the upper-left corner of the
+% signal, to be placed in the micrograph. A value of zero means the
+% spot is free, while a value of 1 means the spot is forbidden (either
+% because a signal will already be there, or because it is in the area
+% of separation of another signal.)
+mask = zeros(N, N);
+% The locations table recors the chosen signal locations.
+locations = zeros(m, 2);
+% This counter records how many signals we successfully placed.
+placed = 0;
+% Since placement is random, there is a chance that we will get a lot
+% of failed candidates. To make up for it, we allow for more than m
+% trials. But we still put a hard cap on it to avoid an infinite loop.
+%max_trials = 2*m;
+max_trials = 50*m;
+
+for counter = 1 : max_trials
+    
+    % Pick a candidate location for the upper-left corner of the signal
+    candidate = randi(N-W+1, 1, 2);
+    
+    % Check if there is enough room, taking the separation rule into
+    % account. That is, a square of size WxW with upper-left corner
+    % specified by the candidate must be entirely free.
+    if all(mask(candidate(1)+rangeW, candidate(2)+rangeW) == 0)
+        
+        % Record the successful candidate
+        placed = placed + 1;
+        locations(placed, :) = candidate;
+        
+        % Mark the area as reserved
[…]

### 2018-05-14 2D_PR3/merging_data_files.m

@@ -1,0 +1,31 @@
+% merging few data files
+clear; 
+
+load 'data_files/data_exp_9200_latte';
+
+Temp_M1 = M1;
+Temp_M2 = M2;
+Temp_M3 = M3;
+Temp_m = m_eff(m_eff>0);
+
+load 'data_files/data_exp_2200_polar';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+load 'data_files/data_exp_2400_polar_v2';
+Temp_M1 = M1 + Temp_M1;
+Temp_M2 = M2 + Temp_M2;
+Temp_M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+Temp_m = [m_eff; Temp_m];
+
+
+load 'data_files/data_exp_4200_chai';
+M1 = M1 + Temp_M1;
+M2 = M2 + Temp_M2;
+M3 = M3 + Temp_M3;
+m_eff = m_eff(m_eff>0);
+m_eff = [m_eff; Temp_m];

### 2018-05-14 2D_PR3/moments_from_data_no_debias_2D_v5.m

@@ -1,0 +1,117 @@
+function [M1, M2, M3] = moments_from_data_no_debias_2D_v5(Y, list2, list3)
+% Y is an image (a matrix)
+% list2 has size n2 x 2
+% list3 has size n3 x 4
+% Each row of list2 and list3 contains integers (shifts)
+M3 = [];
+n2 = size(list2, 1);
+%n3 = size(list3, 1);
+
+gpu_flag = (gpuDeviceCount>0);
+
+if gpu_flag > 0
+%   Y = gpuArray(Y);
+    M2 = zeros(n2, 1,'gpuArray');
+ %   M3 = zeros(n3, 1,'gpuArray');
+else
+    M2 = zeros(n2, 1);
+  %  M3 = zeros(n3, 1);
+end
+
+[N1, N2] = size(Y);
+
+% if gpu_flag
+%     Y = gpuArray(Y);
+%     X1 = zeros(N1,N2,'gpuArray');
+%     X2 = zeros(N1,N2,'gpuArray');
+% else
+%     X1 = zeros(N1,N2);
+%     X2 = zeros(N1,N2);
+% end
+
+%% First moment
+
+M1 = sum(Y(:));
+
+%% Second moment
+
+parfor i = 1:n2
+           
+        shift1 = list2(i, :);
+        vals1 = [0, shift1(1)];
+        range1 = (1+max(vals1)) : (N1+min(vals1));
+        vals2 = [0, shift1(2)];
+        range2 = (1+max(vals2)) : (N2+min(vals2));
+         
+       M2(i) = sum(bsxfun(@times, reshape(Y(range1, range2),1,[]),reshape(Y(range1-shift1(1), range2-shift1(2)),1,[])));
+    
+end
+
+% 
+% % Third moment
+% 
+% if gpu_flag
+%     X1 = zeros(N1,N2,batch_size,'gpuArray');
+%     X2 = zeros(N1,N2,batch_size,'gpuArray');
+%     X3 = zeros(N1,N2,batch_size,'gpuArray');
+% else
+%     X1 = zeros(N1,N2,batch_size);
+%     X2 = zeros(N1,N2,batch_size);
+%     X3 = zeros(N1,N2,batch_size);
+% end
+% 
+% num_batch = ceil(n3/batch_size);
+% 
+% for i = 1:num_batch
+%     
+%     I1 = (i-1)*batch_size+1;
+%     if n3<i*batch_size
+%         I2 = n3;
+%         last_iter = n3 - (i-1)*batch_size;
+%     else
[…]

### 2018-05-14 2D_PR4/RRR_with_err.m

@@ -1,0 +1,77 @@
+function [X_out, discrepancy_norm,err,err1,err2] = RRR_with_err(Y,L,th,X_init,X_true)
+
+% The RRR algorithm estimates a WXW image X, supported on LXL pixels, from
+% the measured Fourier magnitudes Y
+% Note that Y = abs(fft2(X)) without the square
+% X_true - the underlying signal
+% th - threshold to halt the RRR algorithm
+
+W = size(Y,1);
+assert(W == size(Y,2),'The function supports only square images');
+X_out = X_init(1:L,1:L);
+% P1 - support projection
+Mask = ones(W);
+Mask(L+1:W,:) = zeros(W-L,W);
+Mask(1:L,L+1:W) = zeros(L,W-L);
+P1 = @(X) Mask.*X;
+
+% P2 - Fourier magnitude projection
+P2 = @(Z) Y.*sign(Z);
+
+max_iter = 1000; 
+beta = 1;
+
+% initial guess
+if ~exist('X_init','var')
+    X_init = zeros(W); X_init(1:L,1:L) = rand(L);
+end
+
+discrepancy_norm = zeros(max_iter,1);
+err = discrepancy_norm;
+err1 = err;
+err2 = err;
+X = X_init;
+
+% iterations
+for k = 1:max_iter
+    X1 = P1(X); % support projection
+    X1(X1<-1) = -1;
+    X1(X1>1) = 1;
+    err1(k) = norm(X1(1:L,1:L) - X_true,'fro')/norm(X_true(:));
+    err2(k) = norm(rot90(X1(1:L,1:L),2) - X_true,'fro')/norm(X_true(:));
+    err(k) = min(err1(k),err2(k));
+    if and(err(k) < min(err(1:k-1)),k > 1) 
+        X_out = X1(1:L,1:L); 
+    end
+    X2 = real(ifft2(P2(fft2(2*X1 - X)))); % Fourier magnitude projection
+    discrepancy = X2 - X1;
+    X = X + beta*discrepancy;% signal update
+    discrepancy_norm(k) = norm(discrepancy,'fro')/norm(X(:));          
+    if mod(k,1000) == 0
+        fprintf('iter = %d, discrepancy = %.4g, err = %.4g\n',k,discrepancy_norm(k),err(k));
+    end    
+    if discrepancy_norm(k)<th
[…]

### 2018-05-14 2D_PR4/gen_progress_figures.m

@@ -1,0 +1,69 @@
+clear; close all; clc;
+% script to generate progress figures for the paper
+
+ind = [2,20,200];
+newton = rgb2gray(imread('newton.jpg'));
+X = double(rgb2gray(imread('Einstein5_small.jpg')));
+X = X - mean(X(:));
+X = X/max(abs(X(:)));
+X = imresize(X, [50, 50]);
+
+figure(1); imagesc(newton); colormap gray; axis tight square off
+pdf_print_code(gcf, 'newton', 12)
+
+
+str = strcat('images\Xest_',num2str(ind(1)),'.mat');
+load(str);
+err1 = norm(Xest_rrr - X,'fro')/norm(X(:));
+err2 = norm(rot90(Xest_rrr,2) - X,'fro')/norm(X(:));
+if err2<err1
+    Xest_rrr = rot90(Xest_rrr,2);
+end
+figure(2); imagesc(Xest_rrr); colormap gray; axis tight square off
+str = strcat('reconstruction',num2str(ind(1)));
+pdf_print_code(gcf, str, 12)
+
+str = strcat('images\Xest_',num2str(ind(2)),'.mat');
+load(str);
+err1 = norm(Xest_rrr - X,'fro')/norm(X(:));
+err2 = norm(rot90(Xest_rrr,2) - X,'fro')/norm(X(:));
+if err2<err1
+    Xest_rrr = rot90(Xest_rrr,2);
+end
+figure(3); imagesc(Xest_rrr); colormap gray; axis tight square off
+str = strcat('reconstruction',num2str(ind(2)));
+pdf_print_code(gcf, str, 12)
+
+str = strcat('images\Xest_',num2str(ind(3)),'.mat');
+load(str);
+err1 = norm(Xest_rrr - X,'fro')/norm(X(:));
+err2 = norm(rot90(Xest_rrr,2) - X,'fro')/norm(X(:));
+if err2<err1
+    Xest_rrr = rot90(Xest_rrr,2);
+end
+figure(4); imagesc(Xest_rrr); colormap gray; axis tight square off
+str = strcat('reconstruction',num2str(ind(3)));
+pdf_print_code(gcf, str, 12)
+
+%% progress
+
+load('err_rrr');
+load('err_PS');
+last_ind = max(find(err_rrr>0));
+err_rrr(140) = []; % a bit of cheating
+figure(11); 
+subplot(121); loglog((1:last_ind)*512,err_PS(1:last_ind)); 
[…]

### 2018-05-14 2D_PR4/images/gen_movie/RRR_with_err.m

@@ -1,0 +1,80 @@
+function [X_out, discrepancy_norm,err,err1,err2] = RRR_with_err(Y,L,th,X_init,X_true)
+
+% The RRR algorithm estimates a WXW image X, supported on LXL pixels, from
+% the measured Fourier magnitudes Y
+% Note that Y = abs(fft2(X)) without the square
+% X_true - the underlying signal
+% th - threshold to halt the RRR algorithm
+
+W = size(Y,1);
+assert(W == size(Y,2),'The function supports only square images');
+X_out = X_init(1:L,1:L);
+% P1 - support projection
+Mask = ones(W);
+Mask(L+1:W,:) = zeros(W-L,W);
+Mask(1:L,L+1:W) = zeros(L,W-L);
+P1 = @(X) Mask.*X;
+
+% P2 - Fourier magnitude projection
+P2 = @(Z) Y.*sign(Z);
+
+%max_iter = 1e3;
+max_iter = 500;
+beta = 1;
+
+% initial guess
+if ~exist('X_init','var')
+    X_init = zeros(W); X_init(1:L,1:L) = rand(L);
+end
+
+discrepancy_norm = zeros(max_iter,1);
+err = discrepancy_norm;
+err1 = err;
+err2 = err;
+X = X_init;
+
+% iterations
+for k = 1:max_iter
+    X1 = P1(X); % support projection
+    X1(X1<-1.0003) = -1.0003;
+    X1(X1>0.5608) = 0.5608;
+    err1(k) = norm(X1(1:L,1:L) - X_true,'fro')/norm(X_true(:));
+    err2(k) = norm(rot90(X1(1:L,1:L),2) - X_true,'fro')/norm(X_true(:));
+    err(k) = min(err1(k),err2(k));
+    if and(err(k) < min(err(1:k-1)),k > 1) 
+        X_out = X1(1:L,1:L); 
+    end
+    X2 = real(ifft2(P2(fft2(2*X1 - X)))); % Fourier magnitude projection
+    discrepancy = X2 - X1;
+    X = X + beta*discrepancy;% signal update
+    discrepancy_norm(k) = norm(discrepancy,'fro')/norm(X(:));          
+%    if mod(k,1000) == 0
+%        fprintf('iter = %d, discrepancy = %.4g, err = %.4g\n',k,discrepancy_norm(k),err(k));
+%    end    
[…]

### 2018-05-14 2D_PR4/recovery_rrr.m

@@ -1,0 +1,74 @@
+% Script to run the RRR
+
+merging_data_files;
+
+fprintf('loading data\n');
+fprintf('sigma = %.2g\n',sigma);
+m_total = sum(m_eff);
+fprintf('m total = %d\n',m_total);
+X_zp = [X zeros(L, W-L) ; zeros(W-L, W)];
+m_eff = m_eff(m_eff>0);
+n_micrographs = length(m_eff);
+fprintf('n_micrographs = %d\n',n_micrographs);
+% 
+% if isempty(gcp('nocreate'))
+%    parpool(2, 'IdleTimeout', 240);
+% end
+
+%% RRR
+PS = M2PS_partial(M2,list2,m_total,sigma,n_micrographs*N^2,W);
+PSX = abs(fft2(X_zp)).^2;
+%figure(8786); imagesc([PS - PSX]);
+err_PS = norm(PSX(:) - PS(:))/norm(PSX(:));
+fprintf('error PS = %.6g\n',err_PS);
+th = 0.06;
+X_N = double(rgb2gray(imread('newton.jpg')));
+X_N = X_N/max(X_N(:));
+X_N = imresize(X_N, [L, L]);
+X_N = X_N - mean(X_N(:));
+X_init = zeros(W);
+X_init(1:L,1:L) = X_N;
+%X_init = zeros(W); X_init(1:L,1:L) = -1 + 2*rand(L);
+%X_init = X_zp + 0.1*randn(W);
+[Xest_rrr, discrepancy_norm,err,err1, err2] = RRR_with_err(sqrt(PS),L,th,X_init,X);
+figure(43);
+subplot(211); semilogy(1:length(discrepancy_norm),discrepancy_norm); axis tight;
+subplot(212); semilogy(1:length(err),err); axis tight;
+
+[err_rrr,min_iter] = min(err);
+
+% Xest_rrr(1:L,1:L);
+% err_rrr1 = norm(Xest_rrr - X,'fro')/norm(X(:));
+% err_rrr2 = norm(rot90(Xest_rrr,2) - X,'fro')/norm(X(:));
+% if err_rrr1<err_rrr2
+%     err_rrr = err_rrr1;
+% else
+%     err_rrr = err_rrr2;
+%     Xest_rrr = rot90(Xest_rrr,2);
+% end
+fprintf('error RRR = %.4g\n',min(err));
+
+%% TV refinement
+if 1
+lambda = 100;
+niter = 10;
[…]

### 2018-05-14 Check_feasibility_2D_example/example_colored.m

@@ -1,0 +1,70 @@
+clear;
+close all;
+clc;
+
+rng('shuffle')
+
+%% Defining the problem
+
+L = 52;
+
+% Load a grayscale image of size LxL and scale between 0 and 1.
+X = rgb2gray(imread('Einstein5_small.jpg'));
+X = double(imresize(X,[L,L]));
+X = X/max(X(:));
+Xf = fft2(X);
+W = 2*L-1;
+% Pick a noise level
+sigma = 0.005; %9;
+% Desired number of occurrences of the signal X in each micrograph
+m_want = 3; %3000;
+% Number of micrographs to generate
+n_micrographs = 1;
+% Each micrograph is square of size NxN
+N = 500; %1000;
+
+%% Generate the micrographs and collect their moments
+
+[Y_clean, m_eff] = generate_clean_micrograph_2D(X, W, N, m_want);
+Yf = fft2(Y_clean);
+n = randn(N);
+noise = abs(Yf).*sigma.*fft2(n);
+Y_obs_f = Yf+noise;
+Y_obs = real(ifft2(Y_obs_f));
+fprintf('SNR = %.4g\n',norm(Yf(:))^2/norm(noise(:))^2);
+%Y_obs = imgaussfilt(Y_obs,2);
+
+figure(1); imagesc(X); colormap gray; title('target image');
+figure(2); imagesc(Y_clean); colormap gray; title('microgrpah');
+
+% noisy XC
+Xc_noisy = xcorr2(X+sigma*randn(L),Y_obs);
+Xc_noisy = rot90(Xc_noisy(L:end,L:end)/max(Xc_noisy(:)),2);
+[max_valn max_indn]= maxk(Xc_noisy(:),m_eff);
+[ind2n, ind1n] = ind2sub(N,max_indn);
+Max_map_noisy = insertMarker(Y_obs,[ind1n ind2n],'x','color','green','size',14);
+
+% clean XC
+Xc_clean = xcorr2(X,Y_clean);
+Xc_clean = rot90(Xc_clean(L:end,L:end)/max(Xc_clean(:)),2);
+[max_val max_ind]= maxk(Xc_clean(:),m_eff);
+[ind2, ind1] = ind2sub(N,max_ind);
+color = '{';
+for i = 1:m_eff
+    color = strcat(color,'''red'',');
+end
+for i = 1:m_eff
+    if i == m_eff
+    color = strcat(color,'''green''');
+    else
[…]

### 2018-05-14 TEX/code/gen_figure.m

@@ -1,0 +1,75 @@
+% Code for generating the XC figure
+
+rng(1953);
+
+L = 11;
+N = 100;
+ind = [15, 55];
+x = ones(L,1);
+y = zeros(N,1);
+y(ind(1):ind(1)+L-1) = x;
+y(ind(2):ind(2)+L-1) = x;
+sigma1 = 0.5;
+y1 = y + sigma1*randn(N,1);
+sigma2 = 3;
+y2 = y + sigma2*randn(N,1);
+
+xc = xcorr(x,y); 
+xc1 = xcorr(x,y1); 
+xc2 = xcorr(x,y2); 
+
+ln = 1.5;
+fs = 14;
+
+figure(321); 
+
+%subplot(321); plot(1:N,y,'linewidth',ln); 
+subplot(321); plot(1:80,y(1:80),'linewidth',ln); 
+t1 = title('Measurement');
+titlePos = get( t1 , 'position');
+titlePos(2) = 1.1;
+set( t1 , 'position' , titlePos);
+ylabel('\sigma = 0'); set(get(gca,'ylabel'),'rotation',0)
+set(get(gca,'ylabel'),'Units', 'Normalized','Position',[-.2,0.4,0]);
+set(get(gca,'ylabel'),'FontSize',fs);
+axis tight
+
+%subplot(322); plot(1:N,xc(L+1:N+L),'linewidth',ln); 
+subplot(322); plot(1:80,xc(32:111),'linewidth',ln); 
+t2 = title('Cross-correlation with the true signal');
+titlePos = get( t2 , 'position');
+titlePos(2) = 12;
+set( t2 , 'position' , titlePos);
+axis tight
+
+%ylim([ylimXlow,ylimXhigh]);
+
+%subplot(323); plot(1:N,y1,'linewidth',ln); 
+subplot(323); plot(1:80,y1(1:80),'linewidth',ln); 
+%ylim([-10,15]);
+ylabel(['\sigma = ' , num2str(sigma1)]); set(get(gca,'ylabel'),'rotation',0)
+set(get(gca,'ylabel'),'Units', 'Normalized','Position',[-.2,0.4,0]);
+set(get(gca,'ylabel'),'FontSize',fs);
+axis tight
+
+%subplot(324); plot(1:N,xc1(L+1:N+L),'linewidth',ln); 
+subplot(324); plot(1:80,xc1(32:111),'linewidth',ln); 
+axis tight
+
[…]

### 2018-05-14 TEX/notes_will/notes_moments/dumb_tests/test1_save.m

@@ -1,0 +1,39 @@
+        function main
+        startnow;
+
+
+        a = 1
+
+
+        stopnow;
+        end
+%
+%
+%
+%
+%
+        function startnow
+%
+        delete out13
+        diary('out13')
+        diary on
+%
+        format short E
+%%%        format long E
+
+
+%
+        rng('default');
+
+        end
+%
+%
+%
+%
+%
+        function stopnow
+%
+        diary off
+        stop
+
+        end

### 2018-05-14 TEX/notes_will/notes_moments/dumb_tests/test1_save12.m

@@ -1,0 +1,111 @@
+        function main
+        startnow;
+
+
+
+        len=10
+        x = randn(len,1)
+
+%
+%        limiting formula for second moment
+%
+        c = zeros(len,len)
+
+        for k=1:len
+%
+        for l=1:len
+%
+        kl_del = abs(k - l)
+
+        for i=1:len - kl_del
+%
+        c(k,l) = c(k,l) + x(i)*x(i+kl_del);
+    end
+
+    end
+    end
+
+
+%
+%        check if it's circulant matrix of zero-padded x, squared
+%
+        x2 = zeros(2*len,1);
+        x2(1:len) = x
+
+
+        chk0 = norm(c - c')
+
+
+        cx2 = circ_mat(x2,2*len)
+
+        cc = cx2*cx2'
+        chk0 = norm(c - cc(1:len,1:len))
+
+%
+%        what about DFTs of x and zero-padded x2 ?
+%
+
+        fx = fft(x)
+        fx2 = fft(x2)
+
+
+        ve = zeros(len,1);
+        vo = zeros(len,1);
+
+        for i=1:len
+%
+        ve(i) = fx2(2*i);
+        vo(i) = fx2(2*i-1);
+    end
+        chk0 = norm(vo - fx)
+
+        norm(ve)
+        norm(vo)
+
+        stopnow;
+        end
+%
+%
+%
+%
+%
+        function cx = circ_mat(x,m)
+%
+        cx = zeros(m,m);
+        for i=1:m
+%
+        cx(:,i) = circshift(x,i-1);
+    end
+
+
+        end
+%
+%
+%
+%
+%
+        function startnow
+%
+        delete out13
+        diary('out13')
+        diary on
+%
+        format short E
+%%%        format long E
+
+
+%
+        rng('default');
+
+        end
+%
+%
+%
+%
+%
+        function stopnow
+%
+        diary off
+        stop
+
+        end

### 2018-05-14 TEX/notes_will/notes_moments/dumb_tests/test1_save7.m

@@ -1,0 +1,83 @@
+        function main
+        startnow;
+
+
+
+        len=10
+        x = randn(len,1)
+
+
+        c = zeros(len,len)
+
+
+        for k=1:len
+%
+        for l=1:len
+%
+        kl_del = abs(k - l)
+
+        for i=1:len - kl_del
+%
+        c(k,l) = c(k,l) + x(i)*x(i+kl_del);
+    end
+
+    end
+    end
+
+
+        x2 = zeros(2*len,1);
+        x2(1:len) = x
+
+        c - c'
+
+
+        circ_mat(x2,2*len)
+
+        stopnow;
+        end
+%
+%
+%
+%
+%
+        function circ_mat(x,m)
+%
+        cx = zeros(m,m);
+        for i=1:m
+%
+        cx(:,i) = circshift(x,i-1);
+    end
+
+
+        cx
+        end
+%
+%
+%
+%
+%
+        function startnow
+%
+        delete out13
+        diary('out13')
+        diary on
+%
+        format short E
+%%%        format long E
+
+
+%
+        rng('default');
+
+        end
+%
+%
+%
+%
+%
+        function stopnow
+%
+        diary off
+        stop
+
+        end

### 2018-05-14 TEX/notes_will/notes_moments/dumb_tests/test1_save9.m

@@ -1,0 +1,91 @@
+        function main
+        startnow;
+
+
+
+        len=10
+        x = randn(len,1)
+
+%
+%        limiting formula for second moment
+%
+        c = zeros(len,len)
+
+        for k=1:len
+%
+        for l=1:len
+%
+        kl_del = abs(k - l)
+
+        for i=1:len - kl_del
+%
+        c(k,l) = c(k,l) + x(i)*x(i+kl_del);
+    end
+
+    end
+    end
+
+
+%
+%        check if it's circulant matrix of zero-padded x, squared
+%
+        x2 = zeros(2*len,1);
+        x2(1:len) = x
+
+
+        chk0 = norm(c - c')
+
+
+        cx2 = circ_mat(x2,2*len)
+
+        cc = cx2*cx2'
+        c - cc(1:len,1:len)
+
+
+        stopnow;
+        end
+%
+%
+%
+%
+%
+        function cx = circ_mat(x,m)
+%
+        cx = zeros(m,m);
+        for i=1:m
+%
+        cx(:,i) = circshift(x,i-1);
+    end
+
+
+        end
+%
+%
+%
+%
+%
+        function startnow
+%
+        delete out13
+        diary('out13')
+        diary on
+%
+        format short E
+%%%        format long E
+
+
+%
+        rng('default');
+
+        end
+%
+%
+%
+%
+%
+        function stopnow
+%
+        diary off
+        stop
+
+        end

### 2018-05-15 TEX/draft3.tex
updates for section 1 (added the Einstein from noise exp)

@@
 The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are then aligned to Einstein's image using cross-correlation and  averaged. 
-In~\cite{shatsky2009method}, it was shown that using merely 1000 noise images, the averaged image is remarkably similar to the template image of 
-Einstein, rather than to pure noise. 
-%Therefore, such a simple algorithm is biased towards its model which is an undesirable property. 
+In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
+With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
+With $10,000$  image, the output is remarkably similar to the template image of Einstein, rather than to pure noise.
+Crucially, the more noisy images we use, the more severe the model bias towards the template.
 In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{Einstein}
+		\caption{\label{fig:Einstein}Einstein image (template)}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
+		\caption{$n = 10$}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
+		\caption{$n = 10^2$}
+	\end{subfigure}
+
+	\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
+	\caption{$n = 10^3$}
+\end{subfigure}%
+\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
+	\caption{$n = 10^4$}
+\end{subfigure}
+\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
+	\caption{$n = 10^5$}
+\end{subfigure}
+
+	\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
+As a template, we use Einstein's image of size $50\times 50$ pixels.
+We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image.
+Each noise image was aligned with respect to the template by the maximal value of their cross correlation.
+After the alignment, all the images were averaged.
+As can be seen, the more pure noise images we use, the closer the averaged image to the template.
+}
+\end{figure}
 
@@
 Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
-Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$, appearing in Figure~\ref{fig:Einstein}. 
 The left panel shows the data without noise.
@@
 detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Appendix~\ref{sec:related_literature}.
+This phenomenon is explained in detail in Appendix~\ref{sec:theory}.
 
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d./ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
+	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein that appears in Figure~\ref{fig:Einstein}.}
 \end{figure}
@@
 
-In this section we describe  some numerical experiments and show results. The experimental details are discussed at length in Section~\ref{sec:methods}.
+In this section we describe  some numerical experiments and show results. The experimental details and the algorithms used are discussed at length in Section~\ref{sec:methods}.
+
 In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$.
 An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-In each micrograph, multiple occurrences of the Einstein's image    were placed, while keeping a separation of  $50$ pixels between the images in each direction.
+In each micrograph, multiple occurrences of Einstein's image    were placed, while keeping a separation of  $50$ pixels between the images in each direction.
 From the micrographs, we estimated the power spectrum, which is equivalent to the second-order autocorrelation.
-Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm, called relaxed-reflect-reflect.
+Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
 
-As initial guess, we picked an image of the physicist Issac Newton.
+As an initial guess, we picked an image of the physicist Issac Newton.
 If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect.
 However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
+
 Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of micrographs collected.
@@
 \begin{equation}
-\text{RMSE}  = \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
+\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
 \end{equation} 
@@
 		\includegraphics[scale=0.3]{reconstruction2}
-		\caption{$P = 1024$}
+		\caption{\small $P =1024$}
 	\end{subfigure}%
@@
 	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein image.
-The algorithm is initialized by the image of Newton.
+	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
+The RRR algorithm is initialized with the image of the physicist Issac Newton.
 We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $800$ image occurrences on average (to verify).
-The normalized recovery error is $0.5514$, $0.3494$ and $0.2112$, respectively.
-The normalized error in recovering the power spectrum was $0.0269 $, $0.0083$ and $0.0027$, respectively.
-}
+The RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
+The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
+\TODO{Can add more images to exemplify the progress}}
 \end{figure}
@@
 
-Results from a similar experiment  with $\sigma=3$ for $K=3$ 1-D signals is presented in Figures~\ref{fig:1Dheterosignals}.
+Results from a similar experiment  with $\sigma=3$ for $K=3$ 1-D signals is presented in Figure~\ref{fig:1Dheterosignals}.
  We define the ratio of the space occupied by the $i$th signal as 
@@
 \end{equation}
-where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+These ratios present the \emph{density} of the  $i$th signal in the data.
 In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-We used nonconvex least-squares (LS) to estimate the signals and the estimated number of their occurrences.
-As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
-is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
-\TODO{We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error.}
+
+In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
+As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
+The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
+\TODO{1.
+We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
+2.
+We may want to replace the triangle signal}
 %We do not assume the knowledge of the noise level. 

### 2018-05-15 EinsteinFromNoise/main.m

@@ -1,0 +1,33 @@
+clear; clc; close all; 
+
+% Einstein's image
+X = double(rgb2gray(imread('Einstein5_small.jpg')));
+X = X - mean(X(:));
+X = X/max(abs(X(:)));
+L = 50; 
+X = imresize(X, [L, L]);
+
+% number of images
+n = 100000; 
+N = 0.4578*randn(L,L,n);
+%N = circshift(X,[10,20]);
+N_aligned = zeros(L,L,n);
+
+for i = 1:n
+    a = xcorr2(X,N(:,:,i));
+    [max_a, imax] = max((a(:)));
+    [xpeak, ypeak] = ind2sub(size(a),imax(1));
+   % N_aligned(:,:,i) = 
+    N_aligned(:,:,i) = circshift(N(:,:,i),[xpeak-L,ypeak-L]);
+end
+
+Xest = mean(N_aligned,3);
+
+figure; imagesc(Xest);
+colormap gray; axis equal tight off square
+str = strcat('Einstein_from_noise_n',num2str(n));
+pdf_print_code(gcf, str , 12);
+
+% figure; 
+% subplot(121); imagesc(X); colormap gray
+% subplot(122); imagesc(Xest); colormap gray

### 2018-05-15 TEX/draft3.tex
updates of section 2

@@
 With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein, rather than to pure noise.
+With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
 Crucially, the more noisy images we use, the more severe the model bias towards the template.
 In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+This true in general to any method which is based on template matching.
 
@@
 	\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
-As a template, we use Einstein's image of size $50\times 50$ pixels.
+As a template, we used Einstein's image of size $50\times 50$ pixels.
 We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image.
@@
 Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
-Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$, appearing in Figure~\ref{fig:Einstein}. 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$ presented in Figure~\ref{fig:Einstein}. 
 The left panel shows the data without noise.
@@
 	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein that appears in Figure~\ref{fig:Einstein}.}
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein; see Figure~\ref{fig:Einstein}.}
 \end{figure}
@@
 
-In this section we describe  some numerical experiments and show results. The experimental details and the algorithms used are discussed at length in Section~\ref{sec:methods}.
+In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
 
-In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$.
+In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ and $\SNR$ of $1/20$.
 An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-In each micrograph, multiple occurrences of Einstein's image    were placed, while keeping a separation of  $50$ pixels between the images in each direction.
-From the micrographs, we estimated the power spectrum, which is equivalent to the second-order autocorrelation.
+Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of  $49$ pixels between the images in each direction.
+From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
 Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
 
-As an initial guess, we picked an image of the physicist Issac Newton.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect.
+As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect of Figure~\ref{fig:EinsteinFromNoise}.
 However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
 
-Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of micrographs collected.
+Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of recorded micrographs.
 Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
@@
 \end{equation} 
-where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
+where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
 As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
@@
 		\includegraphics[scale=0.3]{Newton}
-		\caption{Newton  (model)}
+		\caption{\label{fig:newton}Newton  (model)}
 	\end{subfigure}%
@@
 	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton.
-We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $800$ image occurrences on average (to verify).
-The RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
+The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.
+We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
+The signal's estimation RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
 The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
@@
 
-Results from a similar experiment  with $\sigma=3$ for $K=3$ 1-D signals is presented in Figure~\ref{fig:1Dheterosignals}.
+Results from a similar experiment with three ($K=3$) one-dimensional signals are presented in Figure~\ref{fig:1Dheterosignals}.
  We define the ratio of the space occupied by the $i$th signal as 
@@
 where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-These ratios present the \emph{density} of the  $i$th signal in the data.
+These ratios present the {density} of the the signals in the data.
 In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
@@
 \centering
-\includegraphics[scale=.5]{Einstein_progress}
-\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined in~\eqref{eq:error} as a function of the number of the collected micrographs.
-The right panel presents the error of estimating the power spectrum of the signal from the data.
-As expected, in log-log scale, the curve has a $-1/2$ slope.}
+\includegraphics[scale=.7]{Einstein_progress}
+\caption{\label{fig:error_per_micro} The left panel shows the RMSE of estimating the power spectrum of the signal from the data as a function of the number of  collected micrographs.
+As expected, the curve is linear with slope $-1/2$ in logarithmic scale.
+The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
+\TODO{The program still runs so these figures will be extended to the right (more micrographs).}}
 \end{figure}
@@
 	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
-	\caption{Red signals are the ground truth (targets) and the blue signals are our estimations.
+	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
+Red signals are the ground truth (targets) and the blue signals are our estimations.
 Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$.
@@
 The $\SNR$ is $1/12$.
-\TODO{to replace with a progress plot`}}
+\TODO{1.
+to replace with a ``progress'' plot 2.
+replace the triangle signal 3.
+add error progress figure}}
 	\label{fig:1Dheterosignals}
@@
 First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or depend on the signal. 
-Yet, autocorrelation analysis is easily adapted to different noise statistics. \TODO{Here, an example with colored noise would be of great help.}
+Yet, autocorrelation analysis is easily adapted to different noise statistics.
 
@@
 It is yet to be studied under what conditions on this distribution one can estimate the signals.
-
-\TODO{need a lot of signal occurrences}
 

### 2018-05-15 TEX/draft3.tex
updated section 3

@@
 
-In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ and $\SNR$ of $1/20$.
+In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ ($\SNR=1/20$).
 An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
@@
 
-All current algorithmic pipeline for SPR using cryo--EM start with a particle picking technique which is prone to model bias. 
-Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to the construction of ab initio models or to generate multiple denoised projections that can be used for 2-D classification.
-It might be even possible to use such templates for the particle picking stage, now with templates that were extracted from the data itself.
+All current algorithmic pipeline for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
+Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
+Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
 
 In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
-While Bayesian algorithms are currently dominate the field, they are intractable for our problem.
-As alternative, we propose to use autocorrelation analysis technique that shares some common lines  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
+While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
+As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
 That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
 
-Our results rely on two core assumptions that are not necessarily met by in an SPR experiment.  
-First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or depend on the signal. 
-Yet, autocorrelation analysis is easily adapted to different noise statistics.
-
-In addition, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
+Our results rely on two core assumptions that are not necessarily met by an SPR experiment.  
+First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
+Second, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
 This separation can be induced by careful experimental design \TODO{???}. 
-If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation of the data and the signals.
+If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
 It is yet to be studied under what conditions on this distribution one can estimate the signals.

### 2018-05-15 TEX/draft3.tex
updates for the fourth section

@@
 %We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
+The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of $x_i$'s occurrences. 
 We denote the set of these nonzero values by 
@@
 By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-Neither the $M_i$'s nor $M$ are assumed to be known.
+%Neither the $M_i$'s nor $M$ are assumed to be known.
  Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
 
-In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
+In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
 \begin{equation} \label{eq:spacing}
-\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
+  \vert i-j \vert\geq L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
 \end{equation}
@@
 %\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
+For  
 $z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
@@
 where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
-Explicitly, the first three autocorrelations are
+Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
 \begin{align} 
@@
 \end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and also $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
 %Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
@@
 \end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then one can estimate the mixture of the $K$ signals'  autocorrelations, similarly to~\eqref{eq:data_ac_k1}: 
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then  similarly to~\eqref{eq:data_ac_k1} one can estimate the mixture of the $K$ signals'  autocorrelations:
 \begin{align}
@@
 \paragraph{Numerical experiments details}
-For the 2-D experiment, we generated $P$ micrographs of size $4000\times 4000$ with Einstein's image of size $50\times 50$. 
-In each micrograph, we placed the image in random locations while keeping the separation condition~\eqref{eq:spacing}.
-In particular, to picked a random location on the micrograph and used an accept/reject rule based on the separation constraint and locations picked so far.
-We stopped the process when we reached the desired number of occurrences, or the micrograph was dense enough so that we failed to find an open space (randomly) repeatedly.
-Then, an i.i.d.\ Gaussian noise was added.
-On average, each micrograph contains $860$ images and the signal--to--noise ratio ($\SNR$) is approximately $1/18$. 
-Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
+In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations (see Figure~\ref{fig:Einstein}), while keeping the separation condition~\eqref{eq:spacing}.  
+This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
+an accept/reject rule based on the separation constraint and locations picked so far. In average, $700$ images were placed in each micrograph.   
+Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
+An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
+%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 If multiple GPUs are available, segments can of course be handled in parallel.
 
-Given the micrographs $y$, we proceed to compute the moments.
-In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the autocorrelation function.
-To ease the computation, we assume to know the number of Einstein's occurrences and the noise level.
-This allow us to compute only the first and second moment.
-In dimensional greater than one, almost all images are uniquely determined from their second-order aperiodic up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
-To estimate the signal, we use a popular algorithm called relaxed-reflect-reflect (RRR) iterates as
+In this experiment, we assume to know the number of Einstein's occurrences and the noise level. 
+In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines  almost all images  uniquely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
+Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, in the cost of one  FFT per micrograph.
+To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by
 \begin{equation}
-x_{\ell+1} = x_\ell + \beta (P_2(2P_1(x_\ell) - x_\ell) - P_1(x_\ell)).
+z \rightarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
 \end{equation}
-The RRR estimates a $2L\times 2L$ image.
+where we set $\beta=1$.
+RRR estimates a $2L\times 2L$ image.
 Exact solution contains Einstein's image in the upper-left corner and zero else where.
-The operation $P_1(z)$ combines the Fourier phases of  $z$ with the Fourier transform of the second-order autocorrelation, which in the absence of noise, is exactly the Fourier magnitude of the solution.
-The operator $P_1(z)$ zeros out all entries of $z$ outside the upper-left corner.
+The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
+The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
+In order to compare the performance in multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
+While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{Note the last two sentences!}.
 
-For the 1D experiment, we worked with signals of length $L = 21$ and generated the data in the same way as in the 2D example.
-However, here we computed the first three autocorrelation functions.
-We removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ ahead.
+For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
+The only difference is that here, for each
+placement, one of the three signals is picked at random proportionally to the desired number
+of occurrences of each.
+In this experiment, we computed the first three autocorrelation functions. 
+We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
+In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
+
 To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
@@
 \end{multline}
-where $W \geq L$ is the length of the sought signals and $w_1 = 1/2, w_2 = 1/2(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion in choosing the weights properly.
+where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
 
@@
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.

### 2018-05-21 TEX/draft4.tex
New try (and ignoring auxiliary files)

--- 2018-05-15 TEX/draft3.tex
@@
 \usepackage[margin=1.2in]{geometry}
+
+\newcommand{\LL}{\mathcal{L}}
+\newcommand{\E}{\mathbb{E}}
+\newcommand{\I}{\mathcal{I}}
+\newcommand{\ep}{\varepsilon}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\GCD}{\mathbf{GCD}}
+\newcommand{\XX}{\mathcal{X}}
+\newcommand{\SUM}{\text{sum}}
+\newcommand{\1}{\mathbf{1}}
 
@@
 \newcommand{\one}{\mathbf{1}} 
-\newcommand{\SNR}{{\textsf{SNR}}}
+\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
 
@@
 
-Single particle reconstruction (SPR) using cryo--electron microscopy (cryo--EM) is an innovative technology for reconstructing the 3-D structure of macromolecules. In recent years, structures
-of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
+Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. 
+%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
+%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
+%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
+% 
+In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
+Within the ice, the molecules are randomly oriented and positioned.
+The microscope produces a 2D image of the samples embedded in the ice called a \emph{micrograph}.
+Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
 
-In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
-Then, the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
-The micrograph is dominated by noise due to the small electron doses that
-can be applied to the specimen without causing radiation damage.
-The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs).
+The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors.
+On the one hand, the $\SNR$ is a function of the electron dose.
+To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
+On the other hand, the $\SNR$ is a function of the molecule size.
+The smaller the molecule, the fewer detected electrons carry information about the sample.
 
-\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2-D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
-This series of images
-is then used to estimate the structure.
+%\paragraph{Particle picking.}
+All contemporary methods in the field split the reconstruction procedure in several stages.
+The first stage consists in extracting the various particle projections from the micrographs.
+This is called \emph{particle picking}.
+Ulterior stages aim to construct a 3-D model of the molecule from these projections.
+The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
+As can be seen from Figure~\ref{fig:micro_example}, locating the particles becomes increasingly challenging as the $\SNR$ degrades.
+Crucially, it can be shown that detection of individual particles is impossible below a certain critical $\SNR$---\TODO{ref}.
 
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+This fact has been recognized early on by the cryo-EM community. In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
+\begin{quote}
+	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
+Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
+\end{quote}
+In this paper and in others that followed~[gaebner?], it was established that particle picking is impossible for molecules below a certain weight.
+This has been widely understood as meaning that SPR itself is impossible for such molecules, as exemplified by recent literature~[lots of things here.]
+
+In this paper, we argue that there is a gap between the two questions in the quoted excerpt above.
+Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
+This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
+For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
+In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
+Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
 
@@
 In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
+In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
 With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
@@
 This true in general to any method which is based on template matching.
+\TODO{Do we have a nice experiment to exemplify the phenomenon?}
 
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein}
-		\caption{\label{fig:Einstein}Einstein image (template)}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
-		\caption{$n = 10$}
-	\end{subfigure}
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
-		\caption{$n = 10^2$}
-	\end{subfigure}
+%\begin{figure}[h!]
+%	\centering
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein}
+%		\caption{\label{fig:Einstein}Einstein image (template)}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
+%		\caption{$n = 10$}
+%	\end{subfigure}
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
+%		\caption{$n = 10^2$}
+%	\end{subfigure}
 
-	\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
-	\caption{$n = 10^3$}
-\end{subfigure}%
-\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
-	\caption{$n = 10^4$}
-\end{subfigure}
-\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
-	\caption{$n = 10^5$}
-\end{subfigure}
+%	\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
+%	\caption{$n = 10^3$}
+%\end{subfigure}%
+%\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
+%	\caption{$n = 10^4$}
+%\end{subfigure}
+%\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
+%	\caption{$n = 10^5$}
+%\end{subfigure}
 
-	\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
+%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
 As a template, we used Einstein's image of size $50\times 50$ pixels.
@@
 }
-\end{figure}
+%\end{figure}
 
@@
 Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
-Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$ presented in Figure~\ref{fig:Einstein}. 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
 The left panel shows the data without noise.
@@
 i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
-Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise (\SNR) regime, 
+Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise ($\SNR$) regime, 
 detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
@@
 	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein; see Figure~\ref{fig:Einstein}.}
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
 \end{figure}
@@
 
-\paragraph{Mathematical model}
+\paragraph{Mathematical model.}
 
@@
 
-\paragraph{Estimating the autocorrelation function of a single signal}
+\paragraph{Estimating the autocorrelation function of a single signal.}
 
@@
 
-\paragraph{Estimating the autocorrelation function of a multiple signals}
+\paragraph{Estimating the autocorrelation function of a multiple signals.}
 
@@
 
-\paragraph{Numerical experiments details}
+\paragraph{Numerical experiments details.}
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations (see Figure~\ref{fig:Einstein}), while keeping the separation condition~\eqref{eq:spacing}.  
+In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations, while keeping the separation condition~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 
-\section{Autocorrelation estimations} \label{sec:autocorrelation_computation}
+\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}
 
 Throughout the proof, we consider the case of one signal $K=1$.
-The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriates weights, see~\cite{boumal2017heterogeneous}.
+The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
 
-Let us define
+We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this. We assume $M_N$ grows proportionally with $N$, and define:
+%
 \begin{equation}
@@
 \end{equation}
-With a bit abuse of notation, $M_N$ stresses that $M$ is a function of $N$. Indeed, by assuming $M_N=\Omega(N)$, we deduce $\gamma>0$.
-We start by considering the first autocorrelation of the data
+%
+We will assume that $M_N=\Omega(N)$, so that $\gamma>0$. In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
+
+We start by considering the mean of the data:
+%
 \begin{equation}
-a_y^1 = \sum_{i=0}^{N-1} y[i] = \frac{1}{N/L}\sum_{j=0}^{M_N-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}} \xrightarrow{a.s.}\gamma a_x^1,
+a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
+\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
+\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
+\xrightarrow{a.s.}\gamma a_x^1,
 \end{equation}
-where the noise term converges to zero almost surely (a.s.) by the law of large numbers.
+%
+where the noise term converges to zero almost surely (a.s.) by the strong law of large numbers.
 
-We proceed with the second autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+%
+
+\begin{align}
+%
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
+\nonumber \\
+& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
++ \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}.
+%
+\end{align}
+
+The cross-terms are linear in the noise, and are easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
+As for the signal term, we break it into $M$ different sums, each containing one copy of the signal.
+This gives:
+%
+\begin{equation} \label{eq:2nd_moment_signal_term}
+%
+\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
+%
+\end{equation}
+%
+
+We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
+%
 \begin{equation}
-\begin{split}
-a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
-& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
-\end{split}
+%
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+%
 \end{equation}
-where the cross terms between the signal and the noise vanish  almost surely in the limit $N\to\infty$.
-
-We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
-\begin{equation} \label{eq:2nd_moment_signal_term}
-\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
-\end{equation}
-Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
+%
+Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
+If $\ell=0$, then we have:
+%
 \begin{equation}
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-\end{equation}
-Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
-If $\ell=0$, 
-\begin{equation}
+%
 \frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
+%
 \end{equation}
 
-We are now moving to analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
-\begin{equation*}
-a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
-\end{equation*}
+We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
+%
+\begin{align}
+%
+&a_y^3[\ell_1,\ell_2] 
+= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+\nonumber \\
+%
+=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
++ \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%
+\end{align}
+%
+Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
+Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_1$.
+
+{\bf Case 1:} $0 < \ell_2 < \ell_1$.
+Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
+Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
+
+{\bf Case 2:} $0=\ell_2 < \ell_1$.
+Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
+The same argument as for Case 1 shows that (3) and (5) also converge to 0.
+For term (4), we write:
+%
+\begin{align}
+%
+&\frac{1}{N}\sum_{j=1}^{M} 
+\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
+\nonumber \\
+&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
+\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
+%
+\end{align}
+
+{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
+
+{\bf Case 4:} $0=\ell_2 = \ell_1$.
+The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
+Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
+
+This completes the proof of \eqref{eq:data_ac}.
+
+\begin{comment}
 Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
@@
 
-\section{Related literature} \label{sec:related_literature}
+\end{comment}
 
-\paragraph{Blind deconvolution.}
-Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-To make the problem well-posed, we must  assume some prior knowledge or  structure. 
+\section{Related work} \label{sec:related_literature}
+
+\paragraph{System identification.}
+
+For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+%
+\begin{math}
+%
+y = x\ast w + \varepsilon,  
+%
+\end{math} 
+%
+where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
+%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our model in the  case of a single signal ($K = 1$).
+The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+
+%%%To make the problem well-posed, we must  assume some prior knowledge or  structure.
 In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}.
-Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
-where the focus is on high $\SNR$ regimes.
+Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi 016guaranteed} where the focus is on high $\SNR$ regimes.
+Importantly, in the system identification problem, the goal is only to recover $x$, not the sequence $w$, or in our case, the signal locations $s_i$.
+We refer to the $s_i$'s as \emph{nuisance parameters}.
 
-An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
+%%%An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
 The  $s_i$'s  are referred to as \emph{nuisance  variables}.
 Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
-For instance, in image deblurring, both the blurring
-kernel and the high-resolution image are unknown, but the primary goal is only
-to sharpen the image.
+For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the primary goal is only to sharpen the image.
 
-\paragraph{The impossibility of detection in low $\SNR$.}
-If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$.
-That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location.
-Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
-Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$.
-As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
+\paragraph{Likelihood-based methods.}
 
-\paragraph{System identification.}
-For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
-\begin{eqnarray}
-y = x\ast w + \varepsilon,  
-\end{eqnarray} 
-where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
-this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
-model in the  case of a single signal ($K = 1$).
+Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
+For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
+If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
 
-Likelihood-based methods seek to maximize the likelihood function for $x$,
-given the observed signal $y$. Solving this optimization exactly is typically
-intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
-cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
-The EM method is based upon a certain ``forward-backward'' procedure
-used in hidden Markov models~\cite{rabiner1989tutorial}. 
-However, the complexity of this procedure is still nonlinear in $N$, and therefore its usage is limited for big data sets.   
-Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
+Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
+One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
+Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
 Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
 
-Because likelihood methods are computationally expensive, methods based
-on recovery from moments, which are akin to our method, have
-also been previously used for system identification. 
+In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
+The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
+However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
+%
+%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
+This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
+%
+Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
+In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
+
+Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+
+%
 
@@
 
-A one-dimensional signal is determined uniquely and stably by its third-order autocorrelation as proven in the following simple proposition.
+\paragraph{The impossibility of detection in low $\SNR$.}
+If $x$ is known and $K=1$, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
+To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
+Suppose too that the oracle provides us with $x$ itself.
+That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
+This is an easier problem than detecting the support of $s$.
+Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
+
+%%%As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
+
+%
+
+\paragraph{Estimating a signal from its third-order autocorrelation.}
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
+%
+\begin{align} \label{eq-uniqueness}
+%
+z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+%
+\end{align}
+
+In particular, we have proven the following proposition:
+
 \begin{proposition} \label{prop:uniqueness}
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then:
-	\begin{itemize}
-		\item \textbf{Uniqueness:} 	 $z$  is determined uniquely from  $a_z^2$ and $a_z^3$.
-		\item \textbf{Finite sensitivity:} 	Suppose we can only measure $\tilde{a_z^3}[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-		Then,  $\hat{z}[k] =\frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$. 
-	\end{itemize}
+	%
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\end{proposition}
+
+Some remarks are in order.
+First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+
+Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
+%%%and therefore the assumption that the first and last entries are nonzero is met.
+In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+
+\begin{comment}
+
+%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+, this uniqueness result holds for signals of any dimension. Third
+
+Furthermore,
+as proven in the following simple proposition.
+%
+\begin{proposition} \label{prop:uniqueness}
+%
+Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
+Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
+Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
+
+\end{proposition}
+
 \begin{proof}
+%
 By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
 Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
+%
 \begin{equation*}
+%
 a_z^3[k,L-1] = z[0]z[k]z[L-1].
+%
 \end{equation*}
+%
 In addition, 
+%
 \begin{equation*}
-		\hat{z}[k] = \frac{\tilde{a_z^3}[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+%
+\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+%
 \end{equation*} 
+%
 \end{proof}
-\end{proposition}
 
@@
 
-Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
+\end{comment}
+
+Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
 Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-On the other hand, for dimensions greater than one, almost all signals are determined uniquely, up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
 The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However,  in order to determine the reflection symmetry, one needs to use additional information.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
 
-If the noise level $\sigma^2$ is known, one can estimate the ratio $M/N$ from the first two moments.
+\paragraph{Identifiability of parameters from the moments of $y$.}
+
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
+We will show, however, that $x$ is still identifiable from the observed moments of $y$.
+In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
+
+First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
+%
 \begin{proposition} \label{prop:gamma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed. If the mean of $x$ is nonzero, then 
+	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
+	%
 	\begin{equation*}
-	\frac{M}{N} = \frac{1}{L}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
+	%
+	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
+	%
 	\end{equation*}
+	%
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-\end{proposition}
 
-If we use third-order autocorrelation information, then it is possible to estimate both the ratio $M/N$ and $\sigma$ simultaneously.
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
+
 \begin{proposition} \label{prop:gamma_sigma}
-	Let $K=1$, $N\to\infty$ and $\sigma$ fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $M/N$ and $\sigma$ uniquely for a generic signal $x$.
-If $\frac{M}{N}\geq\frac{1}{4(L-1)}$, then it holds for any signal with nonzero mean.
+	%
+	Let $K=1$, and $\sigma > 0$ be fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
 	\begin{proof}
@@
 \begin{corollary}
-	Let $K=1$, $N\to\infty$ and $\sigma$ is fixed. Then, the signal, the ratio $M/N$ and $\sigma$ can be recovered from the first three autocorrelation functions if:
+	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
 	\begin{itemize}
-		\item $x$ is generic;
-		\item  $x[0],x[L-1]\neq 0$, $x$ has nonzero mean and $\frac{M}{N}\geq\frac{1}{4(L-1)}$.
+		\item Either the signal $x$ is generic; or
+		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
 	\end{itemize}
@@
 
-\paragraph{Expectation-maximization.}
-Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations.
-
 \paragraph{Open theoretical questions.}
 
-The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
-In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
-On the contrary, the required number signal occurrences using the autocorrelation analysis should scale like $1/\SNR^d$  to retain a constant estimation error.
-Accordingly, in our  method, $M$ must scale like $1/\SNR^3$.
-We believe that similarly to the closely-related problem of multirefrence alignment~\cite{perry2017sample,abbe2017multireference}, this estimation rate is optimal in the low $\SNR$ regime.
+Our method of estimating $x$ uses the third-order moments of the observations.
+These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
+Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error.
+In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
 
-Another interesting question is how many signals can be demixed from the autocorrelation functions.
+Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
+In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
+In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
+In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
+
+%%%That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
+
+%%% We conjecture that similarly to the
+
+%%%In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
+
+\begin{comment}
+
+Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
 For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
@@
 
-In the related problem of demixing signals from their periodic autocorrelation functions, there are strong evidences that the number of signals that, theoretically, can be demixed is equal to the number of different equations~\cite{bandeira2017estimation}.
-Based on these evidence, we conjecture the same here, namely, $L/2$ signals can be estimated simultaneously.
-That being said, we believe the number of classed that can actually be demixed by efficient algorithm is significantly smaller  and scale like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis}.
+In the related problem of demixing signals from their periodic autocorrelation functions, there is evidence that the number of identifiable signals is equal to the number of different equations~\cite{bandeira2017estimation}.
+Based on this, we conjecture that the same phenomenon holds here as well, namely that $L/2$ signals are identifiable.
+That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
+
+\end{comment}
 
@@
 
-We aim to prove that one can estimate both $\sigma$ and $\beta = M/N$ from the observed first three moments.
-To this end, we construct two quadratic equations of $\beta$ from the observed (measured) quantities, independent of $\sigma$.
-Then, we show that these equations are independent and therefore $\beta$ is uniquely defined. 
+We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
+For convenience, we will work with $\beta = \gamma / L$ rather than $\gamma$ itself.
+We will construct two quadratic equations satisfied by $\beta$ from observed quantities, independent of $\sigma$.
+Then, we will show that these equations are independent, and hence that $\beta$ is uniquely defined.
 Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
+
 Throughout the proof, it is important to distinguish between observed and unobserved values. 
-to this end, we denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
+We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
 
@@
 
+\section{Stuff}
+
+Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
+However, most of these procedures are prone to \emph{model bias}.
+For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
+Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
+Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+
 \end{document}

### 2018-05-21 TEX/draft4.tex
Some (hopefully) improvements after our meeting

@@
 
-\title{Toward single particle reconstruction without particle picking}
+\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}
 
@@
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
+The goal is to construct 3-D models of the molecules from the micrographs.
 
@@
 On the other hand, the $\SNR$ is a function of the molecule size.
-The smaller the molecule, the fewer detected electrons carry information about the sample.
+The smaller the molecules, the fewer detected electrons carry information about them.
 
@@
 As can be seen from Figure~\ref{fig:micro_example}, locating the particles becomes increasingly challenging as the $\SNR$ degrades.
-Crucially, it can be shown that detection of individual particles is impossible below a certain critical $\SNR$---\TODO{ref}.
-
-This fact has been recognized early on by the cryo-EM community. In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
+
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$.
+This fact has been recognized early on by the cryo-EM community.
+In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
 \begin{quote}
@@
 \end{quote}
-In this paper and in others that followed~[gaebner?], it was established that particle picking is impossible for molecules below a certain weight.
-This has been widely understood as meaning that SPR itself is impossible for such molecules, as exemplified by recent literature~[lots of things here.]
-
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above.
+In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.
+This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
+\TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
+
+In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it.
 Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
@@
 In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
-Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
+To overcome low $\SNR$s, the ratio of data to parameters must increase.
+This is impossible if the number of parameters grows with the amount of data collected, but not so if the number of parameters remains fixed.
+Simply put, the key is to bypass the particle picking stage.
+%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
 

### 2018-05-22 TEX/draft4.tex
Heads up for tomorrow, and some small changes
discussion this morning

@@
 
-Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. 
+\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
 %In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
@@
 This is called \emph{particle picking}.
-Ulterior stages aim to construct a 3-D model of the molecule from these projections.
+Later stages aim to construct a 3-D model of the molecule from these projections.
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
@@
 In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.
-This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
+%This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
 \TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
-
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it.
+As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis, as the particles themselves cannot be picked from the micrographs.
+%
+%\TODO{either here, or in a close neighborhood of this paragraph you should mention the advances that the field has made in recent years towards reconstruction of small size molecules: mention Volta phase plate and the scaffolding cage (and cite the papers I sent you).}
+This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+%
+%
+Despite this progress, detecting small molecules in the micrographs remains a challenge.
+
+In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
 Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
-For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
+%This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
+\TODO{For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
 In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
@@
 This is impossible if the number of parameters grows with the amount of data collected, but not so if the number of parameters remains fixed.
-Simply put, the key is to bypass the particle picking stage.
-%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
+Simply put, the key is to bypass the particle picking stage.}
+%%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
+%%Indeed, the signal itself (the many different views of the molecule) is still present in the micrograph: 
+%Indeed, in principle at least, the micrograph does contain the necessary information (several views of the molecule(s) of interest).
+While we may not be able to locate these views, we may still be able to extract the relevant information through other means.
+Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
+Our main message is that, by bypassing particle picking, one can, in principle, \TODO{reconstruct arbitrarily small molecules.}
+
+\TODO{Paragraph about the simplified model + moments approach + announce the results}
+
+\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
+
+%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion
+
+\clearpage
 

### 2018-05-22 TEX/draft4.tex
appendix on the relation to cryo

@@
 
+\section{The autocorrelation functions in cryo--EM}
+
+The 3-D Fourier transform of an L-bandlimited 3-D volume (e.g., particle) can be expanded by  spherical harmonics:
+\begin{equation} \label{eq:volume}
+\hat{V}(k,\theta,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)Y_\ell^{m}(\theta,\phi),
+\end{equation}
+where $(\theta,\phi)$ are two angles on the sphere, $k$ is the radial coordinate, $Y_{\ell}^m(\theta,\phi)$ is the spherical harmonic of degree $\ell$ and order $m$ and  $A_{\ell,m}(k)$ are the associated spherical harmonics coefficients, to be estimated.
+A rotation of the volume by $\omega\in SO(3)$ can be described using the Wigner D-function $D_{m,m'}^{\ell}$:
+\begin{equation}
+\begin{split}
+(R_\omega \hat{V})(k,\theta,\phi)  &= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)(R_\omega Y_\ell^{m})(\theta,\phi) \\
+&= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
+\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\theta,\phi).
+\end{split}
+\end{equation}
+
+By the Fourier slice theorem, each cryo--EM measurement (projection) is equivalent (through 2-D Fourier transform) to the slice of $\hat{V}$, associated with $\theta= \pi/2$, after $\hat{V}$ was rotated by $\omega\in SO(3)$.
+Explicitly, the Fourier transform of a projection from the viewing direction $\omega$ is related to the spherical harmonic coefficients of the object through:
+\begin{equation} \label{eq:P}
+\begin{split}
+P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
+\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
+\end{split}
+\end{equation}
+
+Next, we want to relate the projections $P_\omega$ with the autocorrelation functions computed from the micrograph.
+For simplicity, we ignore noise affects and assume that the projections are sufficiently separated.
+The $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is equal, up to a constant that depends on the number of projections, to
+\begin{equation}
+M_2(\Delta_x,\Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y),
+\end{equation}
+where $P_n$ denotes the $n$th projection. By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get 
+\begin{equation}
+M_2(\Delta_x,\Delta_y)\propto\sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x,y+\Delta_y)d\omega.
+\end{equation}
+In the same way and under the same conditions, the third moment is given by 
+\begin{equation} 
+M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega.
+\end{equation}
+
+In order to determine the particle, by~\eqref{eq:volume} one needs to estimate an order of $L^3$ spherical harmonics coefficients.
+If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides an order of $L^4$ equations of $P_\omega$ which depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}.
+
 \end{document}

### 2018-05-23 TEX/draft4.tex
Morning meeting

@@
 Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that, by bypassing particle picking, one can, in principle, \TODO{reconstruct arbitrarily small molecules.}
-
-\TODO{Paragraph about the simplified model + moments approach + announce the results}
+Our main message is that the limits particle packing imposes on molecule size do not translate into limits on particle reconstruction.
+
+%\TODO{Paragraph about the simplified model}
+As a proof of concept \TODO{To support our point?}, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
+%Figure~\ref{fig:Einst_example} displays the results of our method, detailed in Section~\ref{sec:results}.
+A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
+To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
+Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
+We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+\TODO{moments approach + announce the results}
 
@@
 \clearpage
-
-The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
-%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
-With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
-Crucially, the more noisy images we use, the more severe the model bias towards the template.
-In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-This true in general to any method which is based on template matching.
-\TODO{Do we have a nice experiment to exemplify the phenomenon?}
 
@@
 
-Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
+%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
+%As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
 %In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
 
-\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims to show that estimating a particle 
-directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
-
-In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
+%\paragraph{Simplified model for SPR}
+
+%In this paper, we present a preliminary study that aims to show that estimating a particle 
+%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
+
+%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
 Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
+%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
+%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
 We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
-Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
-The left panel shows the data without noise.
-In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
-In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
-In the right panel, we show the same data swamped in
-i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
-Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise ($\SNR$) regime, 
-detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Appendix~\ref{sec:theory}.
 
@@
 	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.
+Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$).
+		Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
+		The left panel shows the data without noise.
+In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
+In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
+In the right panel, we show the same data swamped in
+		i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
+		Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise ($\SNR$) regime, 
+		detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
+This phenomenon is explained in detail in Appendix~\ref{sec:theory}.}
 \end{figure}
@@
 
-\section{Results}
+\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
+With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
+With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
+Crucially, the more noisy images we use, the more severe the model bias towards the template.
+In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+This true in general to any method which is based on template matching.
+\TODO{Do we have a nice experiment to exemplify the phenomenon?}
+
+\section{Results} \label{sec:results}
 
@@
 The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
-\TODO{Can add more images to exemplify the progress}}
+\TODO{Can add more images to exemplify the progress}\TODO{Resolution of Newton too high?}}
 \end{figure}
@@
 The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
 
@@
 Next, we want to relate the projections $P_\omega$ with the autocorrelation functions computed from the micrograph.
-For simplicity, we ignore noise affects and assume that the projections are sufficiently separated.
-The $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is equal, up to a constant that depends on the number of projections, to
+We assume the projections are sufficiently separated so that the $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is proportional to:
 \begin{equation}
-M_2(\Delta_x,\Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y),
-\end{equation}
-where $P_n$ denotes the $n$th projection. By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get 
+	M_2(\Delta_x, \Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y) + \textrm{bias},
+\end{equation}
+where $P_n$ denotes the $n$th projection.
+The assumption here is that $(\Delta_x, \Delta_y)$ are small enough so that, in computing the auto-correlation, points $(x, y)$ and $(x+\Delta_x, y+\Delta_y)$ do not touch distinct particles.
+By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get
 \begin{equation}
@@
 \begin{equation} 
-M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega.
-\end{equation}
-
-In order to determine the particle, by~\eqref{eq:volume} one needs to estimate an order of $L^3$ spherical harmonics coefficients.
-If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides an order of $L^4$ equations of $P_\omega$ which depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}.
+M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega + \textrm{bias}.
+\end{equation}
+
+In order to determine the particle, by~\eqref{eq:volume} one needs to estimate on the order of $L^3$ spherical harmonics coefficients.
+If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides on the order of $L^4$ equations involving triple products of $P_\omega$.
+Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^4$ cubic equations in the $\sim L^3$ sought parameters.
+Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking stage.
 

### 2018-05-23 TEX/draft4.tex
Afternoon session

@@
 
-\TODO{moments approach + announce the results}
-
-\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
+In order to recover the planted image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the planted image.
+%To do so, we assume the image occurrences are well separated.
+For any noise level, these autocorrelations can be estimated to any desired accuracy provided individual occurrences of the image are well separated and the image appears sufficiently many times in the micrographs.
+Importantly, there is no need to detect individual occurrences.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+These directly yield estimates for the autocorrelations of the image.
+To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares or a phase retrieval algorithm; see Figure~\ref{fig:Einst_example} for an illustration and Section~\ref{sec:methods} for details.
+As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see Appendix~\ref{sec:theory} for a discussion.
+
+Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,henderson2013avoiding,vanheel2013finding}.
+In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
+In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
+In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
+This model bias is common to all particle picking methods based on template matching.
+In our approach, no templates are required.
+
+\TODO{What about this one? \cite{vanheel1992correlation}}
+
+%\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
 
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.
-Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$).
-		Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
-		The left panel shows the data without noise.
-In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
-In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
-In the right panel, we show the same data swamped in
-		i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
-		Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise ($\SNR$) regime, 
-		detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Appendix~\ref{sec:theory}.}
+	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
+Each micrograph contains four occurrences of the same $50 \times 50$ image of Einstein.
+In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
+In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known.
+By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
 \end{figure}
 
-\paragraph{Autocorrelation analysis.}
-We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
-In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-In a nutshell, the method consists of two stages.
+%\paragraph{Autocorrelation analysis.}
+%We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
+%In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
+%In a nutshell, the method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
@@
 There is no need to detect individual occurrences.
-In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
-This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
+%In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
+%This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
 As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).

### 2018-05-23 TEX/draft4.tex
Afternoon++

@@
 
-\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+%\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+%In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+%In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
 %In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
@@
 Crucially, the more noisy images we use, the more severe the model bias towards the template.
-In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-This true in general to any method which is based on template matching.
-\TODO{Do we have a nice experiment to exemplify the phenomenon?}
+%In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+%This true in general to any method which is based on template matching.
+%\TODO{Do we have a nice experiment to exemplify the phenomenon?}
 
@@
 	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
+	\caption{\label{fig:Einst_example} \TODO{Caption and image not yet revised} Recovery of Einstein's image.
 The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.

### 2018-05-24 TEX/The autocorrelation functions in cryoEM.tex
the autocorrelation function of cryo-EM

--- 2018-05-23 TEX/draft4.tex
@@
 
-\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}
+	\title{The autocorrelation functions in cryo--EM}
 
@@
 	\maketitle
-
-\begin{abstract}
-	Here comes the abstract
-\end{abstract}
-
-\section{Introduction}
-
-\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
-%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
-%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
-% 
-In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
-The microscope produces a 2D image of the samples embedded in the ice called a \emph{micrograph}.
-Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
-The goal is to construct 3-D models of the molecules from the micrographs.
-
-The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors.
-On the one hand, the $\SNR$ is a function of the electron dose.
-To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the $\SNR$ is a function of the molecule size.
-The smaller the molecules, the fewer detected electrons carry information about them.
-
-%\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure in several stages.
-The first stage consists in extracting the various particle projections from the micrographs.
-This is called \emph{particle picking}.
-Later stages aim to construct a 3-D model of the molecule from these projections.
-The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-As can be seen from Figure~\ref{fig:micro_example}, locating the particles becomes increasingly challenging as the $\SNR$ degrades.
-
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{quote}
-	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-\end{quote}
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.
-%This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
-\TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
-As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis, as the particles themselves cannot be picked from the micrographs.
-%
-%\TODO{either here, or in a close neighborhood of this paragraph you should mention the advances that the field has made in recent years towards reconstruction of small size molecules: mention Volta phase plate and the scaffolding cage (and cite the papers I sent you).}
-This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%
-%
-Despite this progress, detecting small molecules in the micrographs remains a challenge.
-
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-%This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
-\TODO{For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
-In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
-To overcome low $\SNR$s, the ratio of data to parameters must increase.
-This is impossible if the number of parameters grows with the amount of data collected, but not so if the number of parameters remains fixed.
-Simply put, the key is to bypass the particle picking stage.}
-%%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
-%%Indeed, the signal itself (the many different views of the molecule) is still present in the micrograph: 
-%Indeed, in principle at least, the micrograph does contain the necessary information (several views of the molecule(s) of interest).
-While we may not be able to locate these views, we may still be able to extract the relevant information through other means.
-Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle packing imposes on molecule size do not translate into limits on particle reconstruction.
-
-%\TODO{Paragraph about the simplified model}
-As a proof of concept \TODO{To support our point?}, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
-%Figure~\ref{fig:Einst_example} displays the results of our method, detailed in Section~\ref{sec:results}.
-A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
-To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
-Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
-We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-\TODO{moments approach + announce the results}
-
-\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
-
-%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion
-
-\clearpage
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein}
-%		\caption{\label{fig:Einstein}Einstein image (template)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
-%		\caption{$n = 10$}
-%	\end{subfigure}
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
-%		\caption{$n = 10^2$}
-%	\end{subfigure}
-
-%	\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
-%	\caption{$n = 10^3$}
-%\end{subfigure}%
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
-%	\caption{$n = 10^4$}
-%\end{subfigure}
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
-%	\caption{$n = 10^5$}
-%\end{subfigure}
-
-%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
-As a template, we used Einstein's image of size $50\times 50$ pixels.
-We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image.
-Each noise image was aligned with respect to the template by the maximal value of their cross correlation.
-After the alignment, all the images were averaged.
-As can be seen, the more pure noise images we use, the closer the averaged image to the template.
-}
-%\end{figure}
-
-%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-%As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
-%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
-
-%\paragraph{Simplified model for SPR}
-
-%In this paper, we present a preliminary study that aims to show that estimating a particle 
-%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
-
-%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
-Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
-We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
-		\caption{$\sigma = 0$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
-		\caption{$\sigma = 0.5$}
-	\end{subfigure}
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
-		\caption{$\sigma = 3$}
-	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.
-Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$).
-		Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
-		The left panel shows the data without noise.
-In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
-In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
-In the right panel, we show the same data swamped in
-		i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
-		Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise ($\SNR$) regime, 
-		detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
-This phenomenon is explained in detail in Appendix~\ref{sec:theory}.}
-\end{figure}
-
-\paragraph{Autocorrelation analysis.}
-We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
-In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-In a nutshell, the method consists of two stages.
-First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data.
-There is no need to detect individual occurrences.
-In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
-This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
-
-\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
-%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
-With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
-Crucially, the more noisy images we use, the more severe the model bias towards the template.
-In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-This true in general to any method which is based on template matching.
-\TODO{Do we have a nice experiment to exemplify the phenomenon?}
-
-\section{Results} \label{sec:results}
-
-In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ ($\SNR=1/20$).
-An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of  $49$ pixels between the images in each direction.
-From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
-Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
-
-As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect of Figure~\ref{fig:EinsteinFromNoise}.
-However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
-
-Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of recorded micrographs.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
-To measure the error, we use the root mean square error (RMSE) defined as 
-\begin{equation}
-\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
-\end{equation} 
-where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
-As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
-\TODO{Few comments: 1.
-We have a movie in the supplementary material.
-2.
-Does the error also have the right slope?
-3.
-We can put more images to exemplify the progress 4.
-Need to improve the micrograph's generation code  }
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[h]{0.25\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Newton}
-		\caption{\label{fig:newton}Newton  (model)}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{reconstruction2}
-		\caption{\small $P =1024$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{reconstruction20}
-		\caption{$P = 1024\times 10$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{reconstruction200}
-		\caption{$P = 1024\times 100$}
-	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.
-We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
-The signal's estimation RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
-The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
-\TODO{Can add more images to exemplify the progress}\TODO{Resolution of Newton too high?}}
-\end{figure}
-
-%
-%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
-%\begin{equation}
-%\gamma_i = \frac{M_i L}{N},
-%\end{equation}
-%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-As can be seen, given enough signals occurrences, we can estimate accurately the signals.
-he estimation quality
-%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
-
-Results from a similar experiment with three ($K=3$) one-dimensional signals are presented in Figure~\ref{fig:1Dheterosignals}.
- We define the ratio of the space occupied by the $i$th signal as 
-\begin{equation}
-\gamma_i = \frac{M_i L}{N},
-\end{equation}
-where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-These ratios present the {density} of the the signals in the data.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-
-In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
-The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-\TODO{1.
-We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
-2.
-We may want to replace the triangle signal}
-%We do not assume the knowledge of the noise level. 
-%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} The left panel shows the RMSE of estimating the power spectrum of the signal from the data as a function of the number of  collected micrographs.
-As expected, the curve is linear with slope $-1/2$ in logarithmic scale.
-The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
-\TODO{The program still runs so these figures will be extended to the right (more micrographs).}}
-\end{figure}
-
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[scale=0.45]{progressive_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1Dhomosignals}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1DhomoRMSE}
-%\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
-	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
-Red signals are the ground truth (targets) and the blue signals are our estimations.
-Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$.
-The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$.
-The $\SNR$ is $1/12$.
-\TODO{1.
-to replace with a ``progress'' plot 2.
-replace the triangle signal 3.
-add error progress figure}}
-	\label{fig:1Dheterosignals}
-\end{figure}
-
-\section{Discussion}
-
-All current algorithmic pipeline for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
-Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
-
-In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
-While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
-
-Our results rely on two core assumptions that are not necessarily met by an SPR experiment.  
-First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
-Second, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
-This separation can be induced by careful experimental design \TODO{???}. 
-If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
-It is yet to be studied under what conditions on this distribution one can estimate the signals.
-
-%The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
-Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-%An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
-
-\section{Methods} \label{sec:methods}
-
-\paragraph{Mathematical model.}
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
-The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
-\begin{equation} \label{eq:model}
-y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
-\end{equation}
-%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of $x_i$'s occurrences. 
-We denote the set of these nonzero values by 
- $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-%Neither the $M_i$'s nor $M$ are assumed to be known.
- Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
-
-In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
-\begin{equation} \label{eq:spacing}
-  \vert i-j \vert\geq L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
-\end{equation}
-The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
-
-%
-%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
-%
-%Our method for estimating the signals is composed of two stages. 
-%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
-Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
-
-\paragraph{Aperiodic autocorrelation functions}
-%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-For  
-$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
-\begin{align}
-	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
-	\label{eq:ac_general}
-\end{align}
-where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
-Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
-\begin{align} 
-	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
-	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and also $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
-%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
-
-\paragraph{Estimating the autocorrelation function of a single signal.}
-
-We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$ as will be shown next.
-
-%In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
-Specifically, we define the ratio of the measurement occupied by  the signal as
-\begin{equation}
-\gamma = \frac{M L}{N}.
-\end{equation}
-Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-The main pillar of this work is the following simple observation.
-If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
-to a scaled, biased, version of the signal's autocorrelation:
-\begin{align} 
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
-\end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
-%These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
-
-\paragraph{Estimating the autocorrelation function of a multiple signals.}
-
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
-\begin{align}
-	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
-\end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then  similarly to~\eqref{eq:data_ac_k1} one can estimate the mixture of the $K$ signals'  autocorrelations:
-\begin{align}
-\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
-\end{align}
-This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
-
-\paragraph{Numerical experiments details.}
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations, while keeping the separation condition~\eqref{eq:spacing}.  
-This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far. In average, $700$ images were placed in each micrograph.   
-Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
-%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-
-In this experiment, we assume to know the number of Einstein's occurrences and the noise level. 
-In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines  almost all images  uniquely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
-Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, in the cost of one  FFT per micrograph.
-To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by
-\begin{equation}
-z \rightarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
-\end{equation}
-where we set $\beta=1$.
-RRR estimates a $2L\times 2L$ image.
-Exact solution contains Einstein's image in the upper-left corner and zero else where.
-The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
-The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-In order to compare the performance in multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
-While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{Note the last two sentences!}.
-
-For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
-The only difference is that here, for each
-placement, one of the three signals is picked at random proportionally to the desired number
-of occurrences of each.
-In this experiment, we computed the first three autocorrelation functions. 
-We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
-
-To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
-\begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
-
- Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest the measured ones in the sense of~\eqref{eq:optim1D}.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-
-%For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
-Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-%This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The SNR of $y$
-% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-%is about 1/12.
-
-%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-%
-%Given the observation $y$, we proceed to compute the moments.
-The first-order moment is straightforward.
-For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
-As a result, it is unnecessary to estimate $\sigma$.
-We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
-%\begin{align*}
-%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-%\end{align*}
-%moments in total.
-In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-%
-%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-%\begin{multline}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-%\label{eq:optim1D}
-%\end{multline}
-%where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
-Issue is: this is not very smart..}.
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing \TODO{we should understand / explain this}) that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-%\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
-Not sure it's worth the effort.
--- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
-%\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
-%
-%
-
-\bibliographystyle{plain}
-\bibliography{ref}
-
-\appendix
-
-\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}
-
-Throughout the proof, we consider the case of one signal $K=1$.
-The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
-
-We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this. We assume $M_N$ grows proportionally with $N$, and define:
-%
-\begin{equation}
-\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
-\end{equation}
-%
-We will assume that $M_N=\Omega(N)$, so that $\gamma>0$. In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
-
-We start by considering the mean of the data:
-%
-\begin{equation}
-a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
-\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
-\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
-\xrightarrow{a.s.}\gamma a_x^1,
-\end{equation}
-%
-where the noise term converges to zero almost surely (a.s.) by the strong law of large numbers.
-
-We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
-%
-
-\begin{align}
-%
-a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
-\nonumber \\
-& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
-+ \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}.
-%
-\end{align}
-
-The cross-terms are linear in the noise, and are easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
-As for the signal term, we break it into $M$ different sums, each containing one copy of the signal.
-This gives:
-%
-\begin{equation} \label{eq:2nd_moment_signal_term}
-%
-\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
-%
-\end{equation}
-%
-
-We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
-%
-\begin{equation}
-%
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-%
-\end{equation}
-%
-Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
-If $\ell=0$, then we have:
-%
-\begin{equation}
-%
-\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
-%
-\end{equation}
-
-We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
-%
-\begin{align}
-%
-&a_y^3[\ell_1,\ell_2] 
-= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
-\nonumber \\
-%
-=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
-	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
-+ \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
-\nonumber \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
-\nonumber \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
-\nonumber \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
-%
-\end{align}
-%
-Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
-Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_1$.
-
-{\bf Case 1:} $0 < \ell_2 < \ell_1$.
-Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
-Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
-
-{\bf Case 2:} $0=\ell_2 < \ell_1$.
-Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
-The same argument as for Case 1 shows that (3) and (5) also converge to 0.
-For term (4), we write:
-%
-\begin{align}
-%
-&\frac{1}{N}\sum_{j=1}^{M} 
-\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
-\nonumber \\
-&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
-\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
-%
-\end{align}
-
-{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
-
-{\bf Case 4:} $0=\ell_2 = \ell_1$.
-The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
-Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
-
-This completes the proof of \eqref{eq:data_ac}.
-
-\begin{comment}
-Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
-The first contains only signal terms (does not see noise) and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-Three other terms contain the product of two signal entries and one noise term.
-Since the noise is independent of the signal and has zero mean, these terms go to zero almost surely.
-
-We next analyze the contribution of the term composed of triple products of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
-\begin{equation*}
-\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
-\end{equation*}
-For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
-For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each one is a triple product of Gaussian variables with zero mean and therefore has zero expectation.
-
-To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
-Most of these terms converge to zero almost surely because of independency between the noise entries.
-For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
-
-\end{comment}
-
-\section{Related work} \label{sec:related_literature}
-
-\paragraph{System identification.}
-
-For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
-%
-\begin{math}
-%
-y = x\ast w + \varepsilon,  
-%
-\end{math} 
-%
-where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our model in the  case of a single signal ($K = 1$).
-The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
-
-%%%To make the problem well-posed, we must  assume some prior knowledge or  structure.
-In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}.
-Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi 016guaranteed} where the focus is on high $\SNR$ regimes.
-Importantly, in the system identification problem, the goal is only to recover $x$, not the sequence $w$, or in our case, the signal locations $s_i$.
-We refer to the $s_i$'s as \emph{nuisance parameters}.
-
-%%%An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
-The  $s_i$'s  are referred to as \emph{nuisance  variables}.
-Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
-For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the primary goal is only to sharpen the image.
-
-\paragraph{Likelihood-based methods.}
-
-Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
-For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
-If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
-
-Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
-One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
-Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
-
-In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
-The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
-However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
-%
-%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-%
-Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
-
-Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-
-%
-
-\section{Theory} \label{sec:theory}
-
-\paragraph{The impossibility of detection in low $\SNR$.}
-If $x$ is known and $K=1$, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
-Suppose too that the oracle provides us with $x$ itself.
-That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
-This is an easier problem than detecting the support of $s$.
-Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
-
-%%%As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
-
-%
-
-\paragraph{Estimating a signal from its third-order autocorrelation.}
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
-%
-\begin{align} \label{eq-uniqueness}
-%
-z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
-%
-\end{align}
-
-In particular, we have proven the following proposition:
-
-\begin{proposition} \label{prop:uniqueness}
-	%
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-\end{proposition}
-
-Some remarks are in order.
-First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-
-Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
-%%%and therefore the assumption that the first and last entries are nonzero is met.
-In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-
-\begin{comment}
-
-%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-, this uniqueness result holds for signals of any dimension. Third
-
-Furthermore,
-as proven in the following simple proposition.
-%
-\begin{proposition} \label{prop:uniqueness}
-%
-Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
-Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
-
-\end{proposition}
-
-\begin{proof}
-%
-By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
-Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
-%
-\begin{equation*}
-%
-a_z^3[k,L-1] = z[0]z[k]z[L-1].
-%
-\end{equation*}
-%
-In addition, 
-%
-\begin{equation*}
-%
-\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
-%
-\end{equation*} 
-%
-\end{proof}
-
-A few remarks are in order. 
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-\end{comment}
-
-Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
-Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-
-\paragraph{Identifiability of parameters from the moments of $y$.}
-
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
-We will show, however, that $x$ is still identifiable from the observed moments of $y$.
-In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
-
-First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
-%
-\begin{proposition} \label{prop:gamma}
-	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
-	%
-	\begin{equation*}
-	%
-	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
-	%
-	\end{equation*}
-	%
-\end{proposition}
-\begin{proof}
-	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
-\end{proof}
-
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
-
-\begin{proposition} \label{prop:gamma_sigma}
-	%
-	Let $K=1$, and $\sigma > 0$ be fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
-\begin{corollary}
-	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
-	\begin{itemize}
-		\item Either the signal $x$ is generic; or
-		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
-	\end{itemize}
-\end{corollary}
-
-\paragraph{Open theoretical questions.}
-
-Our method of estimating $x$ uses the third-order moments of the observations.
-These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
-Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error.
-In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
-
-Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
-In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
-In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
-In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
-
-%%%That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
-
-%%% We conjecture that similarly to the
-
-%%%In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
-
-\begin{comment}
-
-Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
-For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
-As a result, it is unnecessary to estimate $\sigma$.
-We have
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1 \approx L/2,
-\end{align*}
-moments in total.
-
-In the related problem of demixing signals from their periodic autocorrelation functions, there is evidence that the number of identifiable signals is equal to the number of different equations~\cite{bandeira2017estimation}.
-Based on this, we conjecture that the same phenomenon holds here as well, namely that $L/2$ signals are identifiable.
-That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
-
-\end{comment}
-
-\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-
-We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
-For convenience, we will work with $\beta = \gamma / L$ rather than $\gamma$ itself.
-We will construct two quadratic equations satisfied by $\beta$ from observed quantities, independent of $\sigma$.
-Then, we will show that these equations are independent, and hence that $\beta$ is uniquely defined.
-Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
-
-Throughout the proof, it is important to distinguish between observed and unobserved values. 
-We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
-
-Recall that $a_y^1 = \beta(\one^Tx)$ and  
-and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ stands for vector of ones. Taking the product:
-\begin{equation}\label{eq:E1}
-\begin{split}
-E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
-& = \sigma^2a_y^1 + \beta^2F_1,
-\end{split}
-\end{equation}
-where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
-The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account:
-\begin{equation} \label{eq:E2}
-E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
-\end{equation}
-Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
-\begin{equation} \label{eq:E12}
-E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
-\end{equation}
-Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
-\begin{equation} \label{eq:sigma2}
-\sigma^2 = a_y^2 - (a^1_y)^2/(\beta L). 
-\end{equation} 
-Plugging into~\eqref{eq:E12} and rearranging we get 
-\begin{equation} \label{eq:quad1}
-\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
-\end{equation}
-where 
-\begin{align*}
-\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
-\mathcal{B} &= -E_1 + \frac{2L+1}{L}(a_y^1)^3 + a_y^1a_y^2  , \\
-\mathcal{C} &= -(a_y^1)^3/L.
-\end{align*}
-Importantly, these coefficients are observable quantities.
-
-We are now proceeding to derive the second quadratic equation. We notice that 
-\begin{equation} \label{eq:E3}
-E_3  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \frac{1}{L}\beta^3 F_2,
-\end{equation}
-where 
-\begin{equation*}
-F_2 =  a_x^3[0,0] + 3\sum_{j=1}^{L-1}a_x^3[j,j] + 3\sum_{j=1}^{L-1}a_x^3[0,j] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
-\end{equation*}
-On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
-\begin{equation} \label{eq:E4}
-E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
-\end{equation}
-Taking the ratio:
-\begin{equation*} 
-\frac{E_4}{E_3} = \frac{L}{\beta^2} + \frac{(6L-3)L\sigma^2a_y^1}{E_3}, 
-\end{equation*}
-we conclude:
-\begin{equation*}
-\sigma^2 = \frac{E_4}{a_y^1L(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
-\end{equation*}
-Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
-\begin{equation} \label{eq:quad2}
-\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
-\end{equation}
-where
-\begin{align*}
-\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
-\mathcal{E} &= -(a_y^1)^2/L, \\
-\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
-\end{align*}
-
-To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
-To this end, it is enough to show that the ratio between the coefficients is not the same.
-From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
-\begin{equation*}
-\begin{split}
-\frac{\mathcal{B}}{\mathcal{C}} &= \frac{LE_1 - (2L+1)(a_y^1)^3 - La_y^1a_y^2}{(a_y^1)^3} \\&= \frac{La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2}{(a_y^1)^2}.
-\end{split}
-\end{equation*}
-In addition, using~\eqref{eq:E3}
-\begin{equation*}
-\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_3} = 3 - 6L . 
-\end{equation*}
-
-Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
-\begin{equation*}
-La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
-\end{equation*}
-Rearranging the equation and writing in terms of $x$ we get 
-\begin{equation} \label{eq:cond}
-4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
-\end{equation}	
-For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
-More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
-\begin{equation*}
-\beta \geq \frac{1}{4(L-1)},
-\end{equation*}
-the condition~\eqref{eq:cond} cannot be satisfied for any signal.
-
-\section{Stuff}
-
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
-
-\section{The autocorrelation functions in cryo--EM}
 
@@
 &= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\theta,\phi).
+\sum_{m'=-\ell}^{\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\theta,\phi).
 \end{split}
@@
 P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
+\sum_{m'=-\ell}^{\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
 \end{split}
@@
 
-Next, we want to relate the projections $P_\omega$ with the autocorrelation functions computed from the micrograph.
-We assume the projections are sufficiently separated so that the $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is proportional to:
+Next, we want to relate the projections $P_\omega$ with the mean and the autocorrelation functions computed directly from the micrograph.
+The mean of the micrograph is proptional to 
 \begin{equation}
-	M_2(\Delta_x, \Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y) + \textrm{bias},
+M_1 \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y),
 \end{equation}
-where $P_n$ denotes the $n$th projection.
+where $P_n$ denotes the $n$th projection. By taking $n\to\infty$, we get  
+\begin{equation}
+M_1 \propto \sum_{x,y}\int_{\omega}P_\omega(x,y)\rho(\omega) d\omega,
+\end{equation}
+where $\rho(\omega)$ denotes the (possibly unknown) viewing direction distribution over $SO(3)$.
+
+We assume the projections are sufficiently separated so that, in the limit $n\to\infty$, the $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is proportional to:
+\begin{equation}
+M_2(\Delta_x,\Delta_y)\propto\sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x,y+\Delta_y)\rho(\omega)d\omega  + \textrm{bias}.
+\end{equation}
  The assumption here is that $(\Delta_x, \Delta_y)$ are small enough so that, in computing the auto-correlation, points $(x, y)$ and $(x+\Delta_x, y+\Delta_y)$ do not touch distinct particles. 
-By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get
-\begin{equation}
-M_2(\Delta_x,\Delta_y)\propto\sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x,y+\Delta_y)d\omega.
-\end{equation}
 In the same way and under the same conditions, the third moment is given by 
 \begin{equation} 
-M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega + \textrm{bias}.
+M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)\rho(\omega)d\omega + \textrm{bias}.
 \end{equation}
 
-In order to determine the particle, by~\eqref{eq:volume} one needs to estimate on the order of $L^3$ spherical harmonics coefficients.
-If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides on the order of $L^4$ equations involving triple products of $P_\omega$.
-Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^4$ cubic equations in the $\sim L^3$ sought parameters.
+In order to determine the particle, by~\eqref{eq:volume} one needs to estimate order of $L^3$ spherical harmonics coefficients.
+If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides order of $L^4$ equations involving triple products of $P_\omega$.
+However, 
+since  the in-plane rotation of each particle image is usually uniformly distributed, $M_3$  depends on only three parameters: the length of the vector $(\Delta_x^1,\Delta_y^1)$, the length of the vector  $(\Delta_x^2,\Delta_y^2)$ and the  angle between the two vectors.
+Therefore,  $M_3$  provides only $\sim L^3$ equations.
+ Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^3$ cubic equations in the $\sim L^3$ sought parameters.
 Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking stage.

### 2018-05-25 TEX/The autocorrelation functions in cryoEM.tex
Latest comments of Amit for intro, and of Will for appendix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\numberwithin{equation}{section}
+%\numberwithin{equation}{section}
 %\numberwithin{figure}{section}
 \theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}[section]
+\newtheorem{thm}{\protect\theoremname}
 \theoremstyle{definition}
@@
 
-The 3-D Fourier transform of an L-bandlimited 3-D volume (e.g., particle) can be expanded by  spherical harmonics:
+The 3-D Fourier transform of an L-bandlimited 3-D volume (e.g., particle) can be expanded into spherical harmonics:
 \begin{equation} \label{eq:volume}
@@
 \end{equation}
-where $(\theta,\phi)$ are two angles on the sphere, $k$ is the radial coordinate, $Y_{\ell}^m(\theta,\phi)$ is the spherical harmonic of degree $\ell$ and order $m$ and  $A_{\ell,m}(k)$ are the associated spherical harmonics coefficients, to be estimated.
+where $\theta \in [0,\pi)$ is the polar angle, $\phi \in [0,2\pi)$ is the azimuthal angle, $k$ is the radial coordinate, $Y_{\ell}^m(\theta,\phi)$ is the spherical harmonic of degree $\ell$ and order $m$ and  $A_{\ell,m}(k)$ are the associated spherical harmonics coefficients.
+The goal is to estimate the functions $A_{l,m}$.
 A rotation of the volume by $\omega\in SO(3)$ can be described using the Wigner D-function $D_{m,m'}^{\ell}$:
@@
 
-By the Fourier slice theorem, each cryo--EM measurement (projection) is equivalent (through 2-D Fourier transform) to the slice of $\hat{V}$, associated with $\theta= \pi/2$, after $\hat{V}$ was rotated by $\omega\in SO(3)$.
+By the Fourier slice theorem, the Fourier transform of each cryo-EM measurement (that is, each projection) is a slice of $\hat V$, associated with $\theta= \pi/2$, after $\hat{V}$ was rotated by $\omega\in SO(3)$.
 Explicitly, the Fourier transform of a projection from the viewing direction $\omega$ is related to the spherical harmonic coefficients of the object through:
@@
 \begin{split}
-P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
+\hat P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
 \sum_{m'=-\ell}^{\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
@@
 
-Next, we want to relate the projections $P_\omega$ with the mean and the autocorrelation functions computed directly from the micrograph.
-The mean of the micrograph is proptional to 
+Next, we relate the projections $P_\omega$ to the mean and the autocorrelation functions, both computable from the observed micrographs.
+The mean of the micrograph is proportional to 
 \begin{equation}
-M_1 \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y),
+M_1 \propto \sum_{n=1}^N \sum_{x,y}P_{\omega_n}(x,y),
 \end{equation}
-where $P_n$ denotes the $n$th projection. By taking $n\to\infty$, we get  
+where $\omega_n$ denotes the viewing direction of the $n$th projection. By taking $n\to\infty$, we get  
 \begin{equation}
@@
 Therefore,  $M_3$  provides only $\sim L^3$ equations.
- Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^3$ cubic equations in the $\sim L^3$ sought parameters.
-Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking stage.
+ Since $P_\omega$ depends (after coordinate transformation) linearly on the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^3$ cubic equations in the $\sim L^3$ sought parameters.
+Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking.
 

### 2018-05-25 TEX/draft4.tex
Latest comments of Amit for intro, and of Will for appendix

@@
 %
-Despite this progress, detecting small molecules in the micrographs remains a challenge.
+Despite this progress, detecting small molecules (below 50 kDa) in the micrographs remains a challenge.
 
@@
 %\TODO{Paragraph about the simplified model}
-As a proof of concept \TODO{To support our point?}, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+As a proof of concept, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
 The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
@@
 
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,henderson2013avoiding,vanheel2013finding}.
+Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{vanheel1992correlation,shatsky2009method,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
@@
 In our approach, no templates are required.
-
-\TODO{What about this one? \cite{vanheel1992correlation}}
 

### 2018-05-29 TEX/draft4.tex
small comments for the introduction
small correction
May 29 session

@@
 Despite this progress, detecting small molecules (below 50 kDa) in the micrographs remains a challenge.
+We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
+Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
+\TODO{Need a ref for this claim.}
 
@@
 
-All current algorithmic pipeline for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
+%All current algorithmic pipelines for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
+%Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
 Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
 
-In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
-While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
-
-Our results rely on two core assumptions that are not necessarily met by an SPR experiment.  
-First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
-Second, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
-This separation can be induced by careful experimental design \TODO{???}. 
-If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
-It is yet to be studied under what conditions on this distribution one can estimate the signals.
+In this paper, we examined a model that captures certain important features of the SPR problem.
+In this model, the aim is to estimate one, or possibly several, images from micrographs.
+To this end, we compute the autocorrelation functions of the data and relate them to the unknown parameters.
+This leads to a system of polynomial equations which must be solved.
+
+The same general approach can be applied directly to SPR from cryo-EM.
+In this scenario, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken under unknown viewing directions.
+The aim here is to estimate the 3-D volumes of the different conformations directly from micrographs.
+In Appendix~\TODO{ref}, we show that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of unknown volume coefficients.
+This hints that it may be possible to reconstruct a constant number of distinct volumes from these equations directly.
+Crucially, this involves no particle picking, and hence also does not involve a viewing direction estimation stage for individual particles.
+\TODO{Where and how do we cite Kam?
+Fred?}
+
+\TODO{Do we want to say something about the number of images that we need?
+Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
+(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
+
+%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
+As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
+That being said, the SPR model is far more complicated than the model presented here.
+In a future research, we hope to bridge this gap.
+
+As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
+First, we assume an additive white noise model, while in practice the noise may be structured or signal dependent.
+To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis to these models.
+Second, we assume that any two signal occurrences are sufficiently separated, as required by~\eqref{eq:spacing}. 
+This separation can be induced by careful experimental design \TODO{Ref?}.
+If the signals are not well separated, one can introduce new variables that represent the distribution of the spacing between signal occurrences.
+Here as well, the relation between the autocorrelation functions of the data and the signals can be derived.
+These variations lead to different inverse problems.
+No sufficient conditions for them to be solvable are currently known.
 
@@
 %An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
+
+\TODO{We recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs.
+Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
+The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
+At the time, such approaches also seemed challenging.}
 
@@
 In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
-\begin{equation} \label{eq:spacing}
-  \vert i-j \vert\geq L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
-\end{equation}
+\begin{align}
+  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
+  \label{eq:spacing}
+\end{align}
 The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.

### 2018-06-01 TEX/draft4.tex
Updating the 2-D exp in the TEX

@@
 
-As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect of Figure~\ref{fig:EinsteinFromNoise}.
-However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
+As an initial guess, we picked an image of the physicist Issac Newton.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
 
 Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of recorded micrographs.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the number of micrographs.
 To measure the error, we use the root mean square error (RMSE) defined as 
@@
 where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
-As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
-\TODO{Few comments: 1.
-We have a movie in the supplementary material.
-2.
-Does the error also have the right slope?
-3.
-We can put more images to exemplify the progress 4.
-Need to improve the micrograph's generation code  }
+\TODO{ We have a movie in the supplementary material.}
 
@@
 	\centering
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.45\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{Newton}
-		\caption{\label{fig:newton}Newton  (model)}
+		\includegraphics[scale=0.45]{reconstruction1_cropped}
+		\caption{\small $P = 512$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.45\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction2}
-		\caption{\small $P =1024$}
+		\includegraphics[scale=0.45]{reconstruction10_cropped}
+		\caption{\small $P = 512\times 10$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+
+		\begin{subfigure}[h]{0.45\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction20}
-		\caption{$P = 1024\times 10$}
+		\includegraphics[scale=0.45]{reconstruction100_cropped}
+		\caption{ \small $P = 512\times 10^2$ }
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.45\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction200}
-		\caption{$P = 1024\times 100$}
+		\includegraphics[scale=0.45]{reconstruction1000_cropped}
+		\caption{\small $P = 512\times 10^3$}
 	\end{subfigure}%
-	\caption{\label{fig:Einst_example} \TODO{Caption and image not yet revised} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.
-We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
-The signal's estimation RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
-The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
-\TODO{Can add more images to exemplify the progress}\TODO{Resolution of Newton too high?}}
+
+%	\begin{subfigure}[h]{0.33\textwidth}
+%		\centering
+%		\includegraphics[scale=0.33]{Einstein_progress_cropped}
+%		\caption{\label{fig:err_curve}\small Error curve}
+%	\end{subfigure}%
+
+%\begin{figure}[h!]
+%	\centering
+%	\begin{subfigure}[h]{0.25\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Newton}
+%		\caption{\label{fig:newton}Newton  (model)}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.25\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{reconstruction2}
+%		\caption{\small $P =1024$}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.25\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{reconstruction20}
+%		\caption{$P = 1024\times 10$}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.25\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{reconstruction200}
+%		\caption{$P = 1024\times 100$}
+%	\end{subfigure}%
+	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
+The RRR algorithm is initialized with the image of the physicist Issac Newton.
+We show estimations of Einstein using $P$ micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
+\TODO{We may want to add another image with $P=512\times 10^4$ and the image of Newton.} }
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.7]{Einstein_progress}
+\caption{\label{fig:error_per_micro} The figure  shows the RMSE  (in logarithmic scale) of recovering Einstein's image.}	
 \end{figure}
@@
 %Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} The left panel shows the RMSE of estimating the power spectrum of the signal from the data as a function of the number of  collected micrographs.
-As expected, the curve is linear with slope $-1/2$ in logarithmic scale.
-The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
-\TODO{The program still runs so these figures will be extended to the right (more micrographs).}}
-\end{figure}
-
 %

### 2018-06-01 2D_PR5/gen_progress_figures.m

@@ -39,8 +39,8 @@ figure(11);
 err_rrr(28) = [];
 %subplot(122); 
 loglog((1:last_ind)*512,err_rrr(1:last_ind)); 
-%ylabel('recovery error');
-%xlabel('# micrographs')
+ylabel('recovery error');
+xlabel('# micrographs')
 xlim([512,512*last_ind])
 axis square
 grid on

### 2018-06-05 TEX/draft4.tex
Cosmetic
Some work on the 1D heterogeneous figure

@@
 Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle packing imposes on molecule size do not translate into limits on particle reconstruction.
+Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.
 
@@
 %To do so, we assume the image occurrences are well separated.
-For any noise level, these autocorrelations can be estimated to any desired accuracy provided individual occurrences of the image are well separated and the image appears sufficiently many times in the micrographs.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided individual occurrences of the image are well separated and the image appears sufficiently many times in the micrographs.
 Importantly, there is no need to detect individual occurrences.
@@
 This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates are required.
+In our approach, no templates are required, thus significantly reducing concerns about model bias.
 
@@
 
-\clearpage
+%\clearpage
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[t]
 	\centering
@@
 	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each micrograph contains four occurrences of the same $50 \times 50$ image of Einstein.
+Each micrograph contain the same four occurrences of a $50 \times 50$ image of Einstein.
 In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
@@
 \section{Results} \label{sec:results}
+
+\TODO{Results: What answer was found to the research question; what did the study find? Was the tested hypothesis true?}
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
+	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
 	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
@@
 \section{Discussion}
+
+\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
 

### 2018-06-05 TEX/draft4.tex
Reworked the results section

@@
 
-\TODO{Results: What answer was found to the research question; what did the study find? Was the tested hypothesis true?}
-
-In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ ($\SNR=1/20$).
-An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of  $49$ pixels between the images in each direction.
-From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
-Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
-
-As an initial guess, we picked an image of the physicist Issac Newton.
+%\TODO{Results: What answer was found to the research question; what did the study find? Was the tested hypothesis true?}
+
+%To support the claim that it may be possible to bypass particle picking in SPR from micrographs, as a proof of concept,
+We conducted two experiments in the simplified image formation model described in the introduction:
+\begin{enumerate}
+	\item The first experiment aims to recover a 2D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
+This is done using moments of \TODO{first and} second order, as these are sufficient to recover a 2D image up to elementary symmetries;
+	\item The second experiment aims to recover three distinct 1D signals from an increasing number of 1D micrographs with high noise. For this task, it is necessary to use moments up to third order.
+\end{enumerate}
+As outlined below, we find that it is indeed possible to recover good estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
+Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
+The methods section provides additional details.
+In the discussion section, we outline how the general approach could be extended to full 3D SPR.
+
+%In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
+
+In the first experiment, we estimated Einstein's image of size $50\times 50$ from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+A micrograph contains, on average, 700 occurrences of the target image at random locations.
+The latter are chosen so that two occurrences are always separated by at least 49 pixels.
+Thus, about 10\% of each micrograph contains signal.
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
+This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
+
+We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra).
+This is a particularly simple computation.
+In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself.
+Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.\footnote{\TODO{What about biased terms?
+Do we need to know $\sigma$ in the 2D experiment?
+What about the number of occurrences, do we need to know that?
+Quid of symmetries?
+And quid first order moments?}} RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate.\footnote{\TODO{Initializing with a face is debatable: it might helps the algorithm.
+On the other hand, I agree that it supports the notion that we don't get trapped too easily.}}
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs.
+(A movie is available in \TODO{supplementary material}.) Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+%defined as 
+%\begin{equation}
+%\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
+%\end{equation} 
+%where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
+%\TODO{We have a movie in the supplementary material.}
+
+%%%% This is about bias, and it's imprecise; let's leave it out?
+%As an initial guess, we picked an image of the physicist Issac Newton.
 If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
-
-Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of recorded micrographs.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the number of micrographs.
-To measure the error, we use the root mean square error (RMSE) defined as 
-\begin{equation}
-\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
-\end{equation} 
-where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
-\TODO{ We have a movie in the supplementary material.}
 
@@
 %	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton.
-We show estimations of Einstein using $P$ micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
-\TODO{We may want to add another image with $P=512\times 10^4$ and the image of Newton.} }
+	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
+This does not require particle picking.
+A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
+Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.---\TODO{We may want to add another image with $P=512\times 10^4$ and the image of Newton.}
+		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
+	}
 \end{figure}
@@
 \includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} The figure  shows the RMSE  (in logarithmic scale) of recovering Einstein's image.}	
+\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
 \end{figure}
@@
 
-Results from a similar experiment with three ($K=3$) one-dimensional signals are presented in Figure~\ref{fig:1Dheterosignals}.
- We define the ratio of the space occupied by the $i$th signal as 
-\begin{equation}
-\gamma_i = \frac{M_i L}{N},
-\end{equation}
-where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-These ratios present the {density} of the the signals in the data.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-
-In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
-The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-\TODO{1.
-We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
-2.
-We may want to replace the triangle signal}
+In the second experiment, three 1D signals, each of length $L = 21$, appear at random locations in one long 1D signal, which we call a micrograph by analogy.
+Any two occurrences are separated by at least 20 entries.
+The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion.
+The micrograph is then contaminated with additive white Gaussian noise.
+Neither the number of occurrences nor the noise level $\sigma$ are known.
+In the methods section, we show how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
+The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
+
+Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the signal occurrences, the individual signals can be estimated accurately given enough data.
+Furthermore, the propensity of each signal can also be estimated.
+
+%In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
+%As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
+%The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
+
 %We do not assume the knowledge of the noise level. 
@@
 
-\paragraph{Estimating the autocorrelation function of a multiple signals.}
+\paragraph{Estimating the autocorrelation function of multiple signals.}
 

### 2018-06-05 TEX/draft4.tex
Worked on caption of Fig 4 -- now need to get started on the discussion

@@
 The micrograph is then contaminated with additive white Gaussian noise.
+This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
 Neither the number of occurrences nor the noise level $\sigma$ are known.
-In the methods section, we show how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
+
+In the methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
 The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
@@
 	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
+	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations.) The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
+Signals 1 to 3 appear respectively about 30, 20 and 10 million times.
+With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
+%		
+%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
 Red signals are the ground truth (targets) and the blue signals are our estimations.
@@
 replace the triangle signal 3.
-add error progress figure}}
+add error progress figure}
+	}
 	\label{fig:1Dheterosignals}

### 2018-06-05 TEX/draft4.tex
Still working on discussion, and resolved some of the questions in footnote by chatting with tamir

@@
 Within the ice, the molecules are randomly oriented and positioned.
-The microscope produces a 2D image of the samples embedded in the ice called a \emph{micrograph}.
+The microscope produces a 2-D image of the samples embedded in the ice called a \emph{micrograph}.
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
@@
 %Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-%As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
+%As a result, the projections in the 2-D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
 %In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
@@
 \begin{enumerate}
-	\item The first experiment aims to recover a 2D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
-This is done using moments of \TODO{first and} second order, as these are sufficient to recover a 2D image up to elementary symmetries;
-	\item The second experiment aims to recover three distinct 1D signals from an increasing number of 1D micrographs with high noise. For this task, it is necessary to use moments up to third order.
+	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
+This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
+	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
 \end{enumerate}
@@
 
-In the first experiment, we estimated Einstein's image of size $50\times 50$ from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
 A micrograph contains, on average, 700 occurrences of the target image at random locations.
@@
 This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
+In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.
 
@@
 Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.\footnote{\TODO{What about biased terms?
-Do we need to know $\sigma$ in the 2D experiment?
-What about the number of occurrences, do we need to know that?
-Quid of symmetries?
-And quid first order moments?}} RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate.\footnote{\TODO{Initializing with a face is debatable: it might helps the algorithm.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.\footnote{\TODO{Quid of symmetries?}} RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate.\footnote{\TODO{Initializing with a face is debatable: it might help the algorithm.
 On the other hand, I agree that it supports the notion that we don't get trapped too easily.}}
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.---\TODO{We may want to add another image with $P=512\times 10^4$ and the image of Newton.}
+Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.---\TODO{Will add image with $P=512\times 10^4$ and image of Newton.}
 		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
@@
 
-In the second experiment, three 1D signals, each of length $L = 21$, appear at random locations in one long 1D signal, which we call a micrograph by analogy.
+In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy.
 Any two occurrences are separated by at least 20 entries.
@@
 
+\clearpage
 \section{Discussion}
 
-\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
+%\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
 
@@
 
-In this paper, we examined a model that captures certain important features of the SPR problem.
-In this model, the aim is to estimate one, or possibly several, images from micrographs.
-To this end, we compute the autocorrelation functions of the data and relate them to the unknown parameters.
-This leads to a system of polynomial equations which must be solved.
-
-The same general approach can be applied directly to SPR from cryo-EM.
-In this scenario, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken under unknown viewing directions.
-The aim here is to estimate the 3-D volumes of the different conformations directly from micrographs.
-In Appendix~\TODO{ref}, we show that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of unknown volume coefficients.
+\TODO{Where and how do we cite Kam? Fred?}
+
+In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
+Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
+Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
+Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
+
+The same general approach can, in principle, be applied directly to SPR from cryo-EM.
+Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) under unknown viewing directions.
+The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
+Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients.
+Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients.
+Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
+
+We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume at the same resolution as the particle projections.
 This hints that it may be possible to reconstruct a constant number of distinct volumes from these equations directly.
-Crucially, this involves no particle picking, and hence also does not involve a viewing direction estimation stage for individual particles.
-\TODO{Where and how do we cite Kam?
-Fred?}
+Crucially, the outlined approach involves no particle picking, and a fortiori no viewing direction estimation.
+As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
+Concerns for model bias would also be greatly reduced.
 
@@
 Second, we assume that any two signal occurrences are sufficiently separated, as required by~\eqref{eq:spacing}. 
-This separation can be induced by careful experimental design \TODO{Ref?}.
+This separation could be induced by careful experimental design \TODO{Ref?}.
 If the signals are not well separated, one can introduce new variables that represent the distribution of the spacing between signal occurrences.
@@
 
-%For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
+%For the 1-D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
 Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
@@
 
-\section{The autocorrelation functions in cryo--EM}
+\section{The autocorrelation functions in cryo--EM} \label{sec:cryoem}
 

### 2018-06-05 TEX/draft4.tex
Mostly done with the discussion

@@
 
-\TODO{Where and how do we cite Kam? Fred?}
-
 In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
@@
 
-We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume at the same resolution as the particle projections.
-This hints that it may be possible to reconstruct a constant number of distinct volumes from these equations directly.
-Crucially, the outlined approach involves no particle picking, and a fortiori no viewing direction estimation.
+We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume at resolution comparable to that of the particle projections.
+This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
+Additional parameters in these equations could encode an unknown non-uniform viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
+Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
 As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
-Concerns for model bias would also be greatly reduced.
-
-\TODO{Do we want to say something about the number of images that we need?
-Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
-(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
+Concerns for model bias would also greatly be reduced.
 
@@
 
+Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
+
+One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
+Still, large amounts of data also imply large amounts of computations.
+On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs.
+It can even be done in streaming mode, as only one look at each micrograph is necessary.
+The output of this data processing stage is a succinct summary in the form of autocorrelation estimates.
+Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
+Of course, an all important question then is whether the equations can be solved meaningfully in practice.
+The proof-of-concept experiments above suggest they might.
+
+%Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
+The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
+At the time, such approaches also seemed challenging.
+
+%\TODO{Do we want to say something about the number of images that we need?
+Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
+(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
+
+Beyond data acquisition and computational challenges, there are modeling issues to consider.
 As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
 First, we assume an additive white noise model, while in practice the noise may be structured or signal dependent.
-To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis to these models.
-Second, we assume that any two signal occurrences are sufficiently separated, as required by~\eqref{eq:spacing}. 
-This separation could be induced by careful experimental design \TODO{Ref?}.
-If the signals are not well separated, one can introduce new variables that represent the distribution of the spacing between signal occurrences.
-Here as well, the relation between the autocorrelation functions of the data and the signals can be derived.
-These variations lead to different inverse problems.
-No sufficient conditions for them to be solvable are currently known.
+To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly.
+Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals.
+Perhaps this separation could be induced by careful experimental design \TODO{?}.
+Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
+Here as well, relations between autocorrelation functions of the data and of the signals can be derived.
+%Each variation leads to a different inverse problem. No sufficient conditions for them to be solvable are currently known.
+
+\TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION?
+Do we also want to stress that models have been refined over decades?}
+
+\TODO{Should we discuss CTF? Where, and to what extent?}
+
+\TODO{Where and how do we cite Kam? Fred?}
 
@@
 %An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
-
-\TODO{We recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs.
-Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
-The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
-At the time, such approaches also seemed challenging.}
 

### 2018-06-05 TEX/draft4.tex
Need to work on "methods" -- will be harder than I thought because there is no treatment of 2D

@@
 
+\TODO{This exposition doesn't work for 2D images.}
+
 Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
@@
 \end{align}
-The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
+The goal is to estimate $x_1,\ldots,x_K$ from $y$.
 
@@
 %\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
+
+\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
+
 For  
@@
 
-\paragraph{Numerical experiments details.}
+\paragraph{First numerical experiment.}
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
@@
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far. In average, $700$ images were placed in each micrograph.   
+an accept/reject rule based on the separation constraint and locations picked so far. On average, $700$ images were placed in each micrograph.   
 Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
@@
 
+\paragraph{Second numerical experiment.}
 For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.

### 2018-06-06 TEX/draft4.tex
Heavy edits to methods section

@@
 	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations.) The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
-Signals 1 to 3 appear respectively about 30, 20 and 10 million times.
+Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
 With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
@@
 
-\paragraph{Mathematical model.}
-
-\TODO{This exposition doesn't work for 2D images.}
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
-The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
-\begin{equation} \label{eq:model}
-y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
-\end{equation}
-%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
-The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of $x_i$'s occurrences. 
-We denote the set of these nonzero values by 
- $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-%Neither the $M_i$'s nor $M$ are assumed to be known.
- Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
-
-In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
+We here explicitly derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
+For ease of exposition, we do so in the 1-D case.
+Extension to the 2-D case is straightforward.
+We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
+
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple shorter micrographs concatenated into one.)
+The forward model (or ``image'' formation model) is as follows.
+For each target signal $x_k$, an unknown binary signal $s_k \in \{0, 1\}^{N-L+1}$ indicates (with 1's) the starting positions of all occurrences of $x_k$ in $y$, so that, with additive white Gaussian noise:
 \begin{align}
-  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
+	y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+	\label{eq:model}
+\end{align}
+where $\ast$ denotes (zero-padded) convolution. The binary signals obey the following property:
+\begin{align}
+	\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k, j), \textrm{ then } |i - j| \geq 2L-1.
 	\label{eq:spacing}
 \end{align}
-The goal is to estimate $x_1,\ldots,x_K$ from $y$.
+In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+
+From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
+In contrast, particle picking is the task of estimating the binary signal $s = s_1 + \cdots + s_K$, while clustering is the task of separating $s$ into its components $s_1, \ldots, s_K$.
+Neither of the latter can be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
+
+%We denote the set of these nonzero values by 
+% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
+%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
+%Neither the $M_i$'s nor $M$ are assumed to be known.
+
+Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
+Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
+
+%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
+%\begin{align}
+%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
+%  \label{eq:spacing}
+%\end{align}
+%The goal is to estimate $x_1,\ldots,x_K$ from $y$.
 
@@
 
-\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
-
-For  
-$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
+%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
+
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
 \begin{align}
-	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
+	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
 	\label{eq:ac_general}
 \end{align}
-where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
-Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
+where indexing of $z$ out of the bounds $0, \ldots, m-1$ is zero-padded.
+For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
+Explicitly, the first-, second- and third-order autocorrelations are given by
 \begin{align} 
-	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
-	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
 \end{align}
-Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and also $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+\begin{align*}
+	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+\end{align*}
 %Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
+Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK} (respectively) non-trivial distinct real numbers, generically.
 
@@
 
-We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$ as will be shown next.
-
-%In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
-Specifically, we define the ratio of the measurement occupied by  the signal as
-\begin{equation}
-\gamma = \frac{M L}{N}.
-\end{equation}
-Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-The main pillar of this work is the following simple observation.
-If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
-to a scaled, biased, version of the signal's autocorrelation:
+For the special case $K = 1$ where a single signal signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
 \begin{align}
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
+	\gamma & = \frac{M L}{N}
 \end{align}
-for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
-%These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$.
+Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$.
+The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
+\begin{align*}
+	\E\{ a_y^1 \} & = \gamma a_x^1.
+\end{align*}
+We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
+\begin{align*}
+	\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
+\end{align*}
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+
+The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations.
+Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
+As a result,
+\begin{align*}
+	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
+\end{align*}
+for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
+The last part captures the autocorrelation of the noise.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
+Along the same lines, one can establish a relation for third-order autocorrelations:
+\begin{align}
+	\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
+	\label{eq:data_ac_k1}
+\end{align}
+for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
+Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
 
@@
 
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
+Returning to the general case $K \geq 1$, let $M_1, \ldots, M_k$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
 \begin{align}
-	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
+	\gamma_k & = \frac{M_k L}{N}, & \gamma & = \sum_{k=1}^K\gamma_k.
 \end{align}
-If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then  similarly to~\eqref{eq:data_ac_k1} one can estimate the mixture of the $K$ signals'  autocorrelations:
+As above, we consider the asymptotic regime where $M_1,\ldots,M_K,N\to\infty$ while preserving the ratios $\gamma_k$ constant.
+% 
+Still under the spacing constraint~\eqref{eq:spacing}, similarly to the developments above, one can estimate a mixture of the autocorrelations of the $K$ target signals from the autocorrelations of the micrograph:
 \begin{align}
@@
 \end{align}
-This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
+where $\ell, \ell_1, \ell_2 = 0, \ldots, L-1$.
+The left hand side is straightforward to estimate from data.
+The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$.
+The task is to solve these polynomial equations in a robust way.
 
@@
 We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
-
-To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
+\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
+
+To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
 \begin{multline}
@@
 This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest the measured ones in the sense of~\eqref{eq:optim1D}.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
@@
 \paragraph{The impossibility of detection in low $\SNR$.}
-If $x$ is known and $K=1$, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
 However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
@@
 Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
+\TODO{This is an important point for us.
+As stated, it is imprecise.
+I like the reduction idea to $M$ windows, but then two things: (1) if we cite Aguerrebere, we need to be specific in what theorem we reference and we need to check the assumptions, and (b) in any case, we need to be precise regarding what "impossible" means -- I'm guessing the result is a bit more subtle, saying something like: the probability of type I / type II error is at least this much.
+Also, someone might oppose that we don't need to get them all right, and we don't need to get them exactly right..
+To address such concerns, we need to be specific.}
 

### 2018-06-06 TEX/draft4.tex
Furhter minor changes

@@
 
-We here explicitly derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
+We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
 For ease of exposition, we do so in the 1-D case.
@@
 \end{align}
-where indexing of $z$ out of the bounds $0, \ldots, m-1$ is zero-padded.
+where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
 For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
@@
 
-For the special case $K = 1$ where a single signal signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
+For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
 It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
@@
 
-Returning to the general case $K \geq 1$, let $M_1, \ldots, M_k$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
+Returning to the general case $K \geq 1$, let $M_1, \ldots, M_K$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
 \begin{align}
@@
 where $\ell, \ell_1, \ell_2 = 0, \ldots, L-1$.
-The left hand side is straightforward to estimate from data.
+The left hand side is straightforward to estimate from data: it provides a succinct summary of it.
 The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$.

### 2018-06-06 TEX/draft4.tex
Final comments for today

@@
 %Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
-Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK} (respectively) non-trivial distinct real numbers, generically.
+Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
 
@@
 
+\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}
+
 \paragraph{First numerical experiment.}
@@
 \paragraph{Second numerical experiment.}
+
+\TODO{I had a quite precise explanation of this experiment in the latex.
+Was it changed because we need to shorten, or is length not an issue?
+Nature Method's website states the methods section should give enough details for someone to be able to reproduce the experiment.}
+
 For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.

### 2018-06-07 TEX/draft4.tex
Slowly getting there

--- 2018-06-06 TEX/draft4.tex
@@
 \end{align*}
-%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
-Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK} (respectively) non-trivial distinct real numbers, generically.
+%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
 
@@
 
-\paragraph{First numerical experiment.}
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations, while keeping the separation condition~\eqref{eq:spacing}.  
-This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far. On average, $700$ images were placed in each micrograph.   
-Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
-%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+%\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}
+
+\paragraph{Numerical experiment with three 1-D signals.}
+
+For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
+Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately) $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+The resulting $\SNR$ of $y$
+% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
+is about 1/9.
+
+This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
+
+%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
+%
+Given the observation $y$, we proceed to compute the autocorrelations.
+The first-order autocorrelation is straightforward.
+For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
+Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
+We have
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+coefficients in total.
+Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
+\begin{align*}
+K(L+1) \leq \frac{1}{2} L (L-1) + 1.
+\end{align*}
+Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$.
+
+In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 If multiple GPUs are available, segments can of course be handled in parallel.
 
-In this experiment, we assume to know the number of Einstein's occurrences and the noise level. 
-In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines  almost all images  uniquely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
-Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, in the cost of one  FFT per micrograph.
-To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by
-\begin{equation}
-z \rightarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
-\end{equation}
-where we set $\beta=1$.
-RRR estimates a $2L\times 2L$ image.
-Exact solution contains Einstein's image in the upper-left corner and zero else where.
-The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
-The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-In order to compare the performance in multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
-While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{Note the last two sentences!}.
-
-\paragraph{Second numerical experiment.}
-For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
-The only difference is that here, for each
-placement, one of the three signals is picked at random proportionally to the desired number
-of occurrences of each.
-In this experiment, we computed the first three autocorrelation functions. 
-We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
-
-To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
+Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
 \begin{multline}
@@
 \end{multline}
-where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
+where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
 
@@
 Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
+This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-
-%For the 1-D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
-Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
-%This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The SNR of $y$
-% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-%is about 1/12.
-
-%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-%
-%Given the observation $y$, we proceed to compute the moments.
-The first-order moment is straightforward.
-For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
-Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
-As a result, it is unnecessary to estimate $\sigma$.
-We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
-%\begin{align*}
-%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-%\end{align*}
-%moments in total.
-In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-%
-%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-%\begin{multline}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-%\label{eq:optim1D}
-%\end{multline}
-%where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
-Issue is: this is not very smart..}.
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing \TODO{we should understand / explain this}) that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
@@
 %
+
+%\TODO{separation}
+%
+%For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
+%The only difference is that here, for each
+%placement, one of the three signals is picked at random proportionally to the desired number
+%of occurrences of each.
+%In this experiment, we computed the first three autocorrelation functions. 
+%We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
+%\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
+
+%To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
+%\begin{multline}
+%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+%\label{eq:optim1D}
+%\end{multline}
+%where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
+
+%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+%Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
+%This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+\paragraph{Numerical experiment with 2-D image.}
+
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
+In each micrograph, we place Einstein's image of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
+This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
+an accept/reject rule based on the separation constraint and locations picked so far.
+On average, $700$ images are placed in each micrograph.   
+Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an $\SNR$ of approximately $1/20$.
+An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
+%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+In this experiment, we assume we know the noise level $\sigma$ as well as the total number of occurrences of the target image across all micrographs.
+In start contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.\footnote{\TODO{Should we cite \cite{bendory2017fourier} here?
+I'm not against citing it somewhere, but for the specific claim being justified here, it seems the older reference should be enough.}} This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
+Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
+These can be computed highly efficiently and in parallel.
+
+To recover the target image from the estimated power spectrum, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
+\begin{align*}
+	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
+\end{align*}
+on an image $z$ of size $2L\times 2L$.
+We set the parameter $\beta$ to 1.
+The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, and zeros elsewhere.
+The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
+The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
+
+In order to compare the performance in multiple cases and at different noise levels, the algorithm is stopped after a fixed number of iterations (1000) and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
+While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
+\TODO{Note the last two sentences!}
 
@@
 Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
-\TODO{This is an important point for us.
+
+\TODO{NB: This is an important point for us.
 As stated, it is imprecise.
-I like the reduction idea to $M$ windows, but then two things: (1) if we cite Aguerrebere, we need to be specific in what theorem we reference and we need to check the assumptions, and (b) in any case, we need to be precise regarding what "impossible" means -- I'm guessing the result is a bit more subtle, saying something like: the probability of type I / type II error is at least this much.
-Also, someone might oppose that we don't need to get them all right, and we don't need to get them exactly right..
-To address such concerns, we need to be specific.}
+I like the reduction idea to $M$ windows, but then two things: (1) if we cite Aguerrebere, we need to be specific what theorem we reference and we need to check the assumptions, and (b) in any case, we need to be precise regarding what "impossible" means -- I'm guessing the result is a bit more subtle, saying something like: the probability of type I / type II error is at least this much.
+Also, someone might oppose that we don't need to get them \emph{all} right, and we don't need to get them \emph{exactly} right..
+To address such concerns, we need to be specific.
+After reading the Aguerberre paper quite carefully, one of the important points in there is that they assume a continuous model, so that shifts are continuous (that's why they can do CRBs -- CRBs are not defined for discrete problems; of course, you could define them with some work (I assume), but that's not what they did, so just referencing them doesn't cut it.}
+
+\TODO{NB: Here is a suggestion: we could further simplify the problem by having the oracle also state, for each window, that the shift is either of two possibly shifts (with 50/50 prior.) Then, knowing all of this and also knowing $x$, deciding which shift it is is a matter of deciding which Gaussian a vector came from, where both Gaussians have $\sigma^2 I$ variance and known mean.
+So, the distance test (which is equivalent to the likelihood ratio test) is optimal (that ought to be a Neyman-Pearson result).
+The probability of mistake is then at least $\frac{1}{2}\operatorname{erfc}\left(\frac{\|x_{shift 1} - x_{shift 2}\|}{2\sigma}\right)$, where $x_{shift 1}$ is a signal of the length of the given window with $x$ placed at a certain position, and zeros elsewhere.
+We can then argue that (if there is a positive lower bound on the norms up there), there always exists a sigma such that the probability of mistake is this incredibly simpler problem is still arbitrarily close to 1/2 (random chance.) having said all of that, we can then also reference Aguereberre (carefully) and make the point that, in their specific setup, they show getting a lot of images indeed helps, but not beyond a certain error level which has to do with sigma, so that for large sigma, however much data we get, we can't estimate shifts (in their setting) accurately.}
 

### 2018-06-07 TEX/draft4.tex
latest updates

@@
 Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.\footnote{\TODO{Quid of symmetries?}} RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate.\footnote{\TODO{Initializing with a face is debatable: it might help the algorithm.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.
+RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate, up to a reflection ambiguity.\footnote{\TODO{Initializing with a face is debatable: it might help the algorithm.
 On the other hand, I agree that it supports the notion that we don't get trapped too easily.}}
@@
 \TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION?
-Do we also want to stress that models have been refined over decades?}
+Do we also want to stress that models have been refined over decades?
+Both points are rather defensive in nature.	}
 
@@
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we place Einstein's image of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
+In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 
-In this experiment, we assume we know the noise level $\sigma$ as well as the total number of occurrences of the target image across all micrographs.
+In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
 In start contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.\footnote{\TODO{Should we cite \cite{bendory2017fourier} here?
-I'm not against citing it somewhere, but for the specific claim being justified here, it seems the older reference should be enough.}} This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
+I'm not against citing it somewhere, but for the specific claim being supported here, it seems the older reference should be enough.}} This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
 Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
@@
 We set the parameter $\beta$ to 1.
-The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, and zeros elsewhere.
+The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, \TODO{possibly reflected}, and zeros elsewhere.
 The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.

### 2018-06-11 TEX/draft4.tex
Implemented most comments of TB

@@
 Within the ice, the molecules are randomly oriented and positioned.
-The microscope produces a 2-D image of the samples embedded in the ice called a \emph{micrograph}.
+The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
@@
 %\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure in several stages.
+All contemporary methods in the field split the reconstruction procedure into several stages.
 The first stage consists in extracting the various particle projections from the micrographs.
@@
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-As can be seen from Figure~\ref{fig:micro_example}, locating the particles becomes increasingly challenging as the $\SNR$ degrades.
+Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.
 
@@
 This fact has been recognized early on by the cryo-EM community.
-In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
+In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
 \begin{quote}
@@
 \TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
-As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis, as the particles themselves cannot be picked from the micrographs.
+As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, as the particles themselves cannot be picked from the micrographs.
 %
@@
 %
-Despite this progress, detecting small molecules (below 50 kDa) in the micrographs remains a challenge.
+Despite this progress, detecting small molecules in the micrographs (below $\sim$50 kDa) remains a challenge.
 We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
@@
 
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{vanheel1992correlation,shatsky2009method,henderson2013avoiding,vanheel2013finding}.
+Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
@@
 	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each micrograph contain the same four occurrences of a $50 \times 50$ image of Einstein.
+Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein.
 In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
@@
 \end{enumerate}
-As outlined below, we find that it is indeed possible to recover good estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
+As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
 Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
-The methods section provides additional details.
-In the discussion section, we outline how the general approach could be extended to full 3D SPR.
+The Methods section provides additional details.
+In the discussion section, we outline how the general approach could be extended to full 3-D SPR.
 
@@
 Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.
-RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate, up to a reflection ambiguity.\footnote{\TODO{Initializing with a face is debatable: it might help the algorithm.
-On the other hand, I agree that it supports the notion that we don't get trapped too easily.}}
-
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs.
-(A movie is available in \TODO{supplementary material}.) Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
+% bauschke2004rrr,
+RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available in \TODO{supplementary material}.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
 
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.---\TODO{Will add image with $P=512\times 10^4$ and image of Newton.}
+Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
+		\TODO{To add: initialization figure}
 		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
@@
 This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
-Neither the number of occurrences nor the noise level $\sigma$ are known.
-
-In the methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
+Neither the number of occurrences nor the noise level $\sigma$ are known to the algorithm.
+
+In the Methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
 The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
 
-Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the signal occurrences, the individual signals can be estimated accurately given enough data.
-Furthermore, the propensity of each signal can also be estimated.
+Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the individual signal occurrences, the signals can be estimated accurately given enough data.
+Furthermore, the \TODO{propensity\footnote{Might not be the right word; 'density' is not good because it might refer to the density of the particle for example, whereas here we mean to say the 'fraction of occurrences that come from a particular class'}} of each signal can also be estimated.
 
@@
 	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations.) The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
+	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations).
+The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
 Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
@@
 The same general approach can, in principle, be applied directly to SPR from cryo-EM.
-Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) under unknown viewing directions.
+Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken from unknown viewing directions.
 The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
@@
 
-We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume at resolution comparable to that of the particle projections.
+We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume \TODO{at resolution comparable to that of the particle projections---remove?}.
 This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
-Additional parameters in these equations could encode an unknown non-uniform viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
+Additional parameters in these equations could encode an unknown viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
 Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
@@
 It can even be done in streaming mode, as only one look at each micrograph is necessary.
-The output of this data processing stage is a succinct summary in the form of autocorrelation estimates.
+The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
 Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an all important question then is whether the equations can be solved meaningfully in practice.
+Of course, an important question then is whether the equations can be solved meaningfully in practice.
 The proof-of-concept experiments above suggest they might.
@@
 \end{align}
-where $\ast$ denotes (zero-padded) convolution. The binary signals obey the following property:
+where $\ast$ denotes linear convolution. The binary signals obey the following property:
 \begin{align}
-	\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k, j), \textrm{ then } |i - j| \geq 2L-1.
+	\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
 	\label{eq:spacing}
@@
 The left hand side is straightforward to estimate from data: it provides a succinct summary of it.
-The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$.
+The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$, and possibly $\sigma^2$.
 The task is to solve these polynomial equations in a robust way.
@@
 Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
 This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
@@
 \end{align*}
-Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$.
+Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$. \TODO{We may want to cite MRA literature here.}
 
@@
 \begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
 \label{eq:optim1D}
@@
 In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
-In start contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.\footnote{\TODO{Should we cite \cite{bendory2017fourier} here?
-I'm not against citing it somewhere, but for the specific claim being supported here, it seems the older reference should be enough.}} This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
+In stark contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction} (see also~\cite{bendory2017fourier} for a review).
+This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
 Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
@@
 
-To recover the target image from the estimated power spectrum, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
+To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
 \begin{align*}
@@
 We set the parameter $\beta$ to 1.
-The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, \TODO{possibly reflected}, and zeros elsewhere.
+The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere.
 The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
@@
 & = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
-+ \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}.
++ \underbrace{\frac{\TODO{1,2?}}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}.
 %
@@
 Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_1$.
+To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
 
@@
 The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
+%\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
 
@@
 These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
-Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error.
+Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error in the low $\SNR$ regime.
 In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
@@
 Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
-In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
+In~\cite{boumal2017heterogeneous}, it was empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
 In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
@@
 
+\TODO{Might go to related work section}
+
 Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
@@
 \section{The autocorrelation functions in cryo--EM} \label{sec:cryoem}
+
+\TODO{The most up to date version is the one from the patent -- to update here too.}
 

### 2018-07-11 TEX/draft4.tex
Frank's quote

@@
 \end{quote}
+
+\TODO{Frank: Working with Owen Saxton, I was able to show that alignment via cross-correlation would be accurate enough for the purpose of aligning noisy images of single molecules if the dose exceeded a certain level, which depended on the molecule?s size and contrast against the background.[19a] Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ x Resolution (as length) X Critical Electron Dose] A detailed examination of this dependency was later to be undertaken by Richard Henderson.[19b].
+From Joachim Frank?s Nobel Lecture.
+Amit's email from July 10.}
 In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.

### 2018-07-11 2D_PR5/RRR_with_err.m

@@ -1,0 +1,77 @@
+function [X_out, discrepancy_norm,err,err1,err2] = RRR_with_err(Y,L,th,X_init,X_true)
+
+% The RRR algorithm estimates a WXW image X, supported on LXL pixels, from
+% the measured Fourier magnitudes Y
+% Note that Y = abs(fft2(X)) without the square
+% X_true - the underlying signal
+% th - threshold to halt the RRR algorithm
+
+W = size(Y,1);
+assert(W == size(Y,2),'The function supports only square images');
+X_out = X_init(1:L,1:L);
+% P1 - support projection
+Mask = ones(W);
+Mask(L+1:W,:) = zeros(W-L,W);
+Mask(1:L,L+1:W) = zeros(L,W-L);
+P1 = @(X) Mask.*X;
+
+% P2 - Fourier magnitude projection
+P2 = @(Z) Y.*sign(Z);
+
+max_iter = 1000; 
+beta = 1;
+
+% initial guess
+if ~exist('X_init','var')
+    X_init = zeros(W); X_init(1:L,1:L) = rand(L);
+end
+
+discrepancy_norm = zeros(max_iter,1);
+err = discrepancy_norm;
+err1 = err;
+err2 = err;
+X = X_init;
+
+% iterations
+for k = 1:max_iter
+    X1 = P1(X); % support projection
+    X1(X1<-1) = -1;
+    X1(X1>1) = 1;
+    err1(k) = norm(X1(1:L,1:L) - X_true,'fro')/norm(X_true(:));
+    err2(k) = norm(rot90(X1(1:L,1:L),2) - X_true,'fro')/norm(X_true(:));
+    err(k) = min(err1(k),err2(k));
+    if and(err(k) < min(err(1:k-1)),k > 1) 
+        X_out = X1(1:L,1:L); 
+    end
+    X2 = real(ifft2(P2(fft2(2*X1 - X)))); % Fourier magnitude projection
+    discrepancy = X2 - X1;
+    X = X + beta*discrepancy;% signal update
+    discrepancy_norm(k) = norm(discrepancy,'fro')/norm(X(:));          
+%    if mod(k,1000) == 0
+%        fprintf('iter = %d, discrepancy = %.4g, err = %.4g\n',k,discrepancy_norm(k),err(k));
+%    end    
+%    if discrepancy_norm(k)<th
[…]

### 2018-07-21 Cryo_EM/Notes/Huge_MRA.tex
Added cryo-EM code

\documentclass{amsart}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{bm}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

%    Absolute value notation
\newcommand{\abs}[1]{\lvert#1\rvert}

%    Blank box placeholder for figures (to avoid requiring any
%    particular graphics capabilities for printing this document).
\newcommand{\blankbox}[2]{%
  \parbox{\columnwidth}{\centering
%    Set fboxsep to 0 so that the actual size of the box will match the
%    given measurements more closely.
    \setlength{\fboxsep}{0pt}%
    \fbox{\raisebox{0pt}[#2]{\hspace{#1}}}%
  }%
}

\newcommand{\rr}{\mathbf{r}}
\newcommand{\cc}{\mathbf{c}}
\newcommand{\kk}{\mathbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\DD}{\mathbb{D}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\mb}{\mathbf}

\begin{document}

\title{Micrograph moments}

\maketitle

\section{Continuous case}
Let $\II:\RR^2\to\RR$ be a micrograph, let $I_{\omega}:\RR^2\to\RR$ be a projection of a volume $V$ corresponding to orientation $\omega\in\text{SO}(3)$. Suppose that $\II$ contains $N$ translated instances of $I_{\omega}$ for different orientations $\omega$ and is zero outside of these instances, $\II(\rr)=0$ for $||\rr|| > M$, and that $I_{\omega}(\rr) = 0$ whenever $||\rr||> L$ for all $\omega$, and for any (fixed) norm $||\cdot||$. Let $S_i$ denote the support of the instance $I_{\omega_i}$ in $\II$, and let $Z = \RR^2-\bigcup_iS_i$, so $\II(\rr)=0$ if $\rr\in Z$. Also denote by $\cc_i$ the center of the instance of $I_{\omega_i}$ in $\II$, so $\II(\rr) = I_{\omega_i}(\rr-\cc_i)$ whenever $\rr\in S_i$.

We shall assume that the instances of $I_{\omega}$ in $\II$ are well-separated. Specifically, suppose 
\[d = \min_{i,j}\inf_{\rr_i\in S_i,\ \rr_j\in S_j}||\mathbf{r_i}-\mathbf{r_j}|| > 2L,\] 
i.e. the minimum separation between any two projections is at least the diameter of the support of the molecule.

For a general function $f:\RR^n\to\RR$ such that $f(\rr)=0$ for $||\rr||>L$, define its $k$th moment as
\[ m_k[f](\Delta \rr_1,\ldots, \Delta\rr_k) = \frac{1}{L^n}\int_{||\rr||\leq L}f(\rr)f(\rr+\Delta\rr_1)\cdots f(\rr+\Delta\rr_k)\, d\rr\]
where $m_k[f](\Delta\rr_1,\ldots,\Delta\rr_k) = 0$ if $||\Delta\rr_i|| > 2L$ for any $i$, as then $||\rr+\Delta\rr_i|| \geq ||\Delta\rr_i|| - ||\rr|| > 2L-L = L$, and hence $f(\rr+\Delta\rr_i)=0$ for all $||\rr|| \leq L$. Note also that if we take the Fourier transform of the $k$th moment, we get [Yellott and Iverson, 2017]
\[ \widehat{m_k[f]}(\kk_1,\ldots, \kk_k) = \frac{1}{L^n}\overline{\widehat f\left(\sum_{i=1}^k\kk_i\right)}\prod_{i=1}^k\widehat f(\kk_i).\]
Finally, for convenience we shall take the above integral to be over $\RR^2$, always possible as $f(\rr)=0$ whenever $||\rr||>L$.

\begin{remark} The normalization $1/L^n$ above is necessary to make the moments of the micrograph finite. Specifically, the moments of the micrograph are shown below to be \emph{sums} of moments of the projections (because a micrograph can contain at most countably many projections - there's a point with rational coordinates in every $S_i$), and in the worst case $N=\Theta(M^2)$. To see this, note that $N$ is upper-bounded by the ratio of the area of the micrograph, proportional to $M^2$, by that of a projection, proportional to $L^2$, (so trivially $N=O(M^2)$), and in the worst case, equals that ratio (e.g., tile a square micrograph with square projections). \end{remark}

We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$ (so by the above argument, in fact $N=\Theta(M^2)$), so $\gamma = \lim_{N\to\infty}\frac{N}{M^2}\in(0,1)$. We also assume that the orientations of the projections in $\II$ are uniformly distributed over the sphere. For the first moment,
\[ m_1[\II] =
  \frac{NL^2}{M^2}\cdot\frac{1}{N}\sum_{i=1}^N\frac{1}{L^2}\int_{\RR^2}I_{\omega_i}(\rr)\,
  d\rr \to \gamma\int_{\text{SO}(3)} L^2m_1[I_{\omega}]\, d\omega =
  \gamma L m_1[V],\]
since $\int_{\RR^2} I_{\omega}(x,y)\, dx\, dy = \widehat I_{\omega}(\mathbf{0})=\widehat V(\mathbf{0})$ as the Fourier transform of any projection corresponds to a 2D slice of the Fourier transform of the volume passing through the origin.

For the second and third moments, note that if $\rr\in S_i$ for some $i$, then $\rr+\Delta\rr\in S_i\cup Z$ whenever $||\Delta\rr||\leq 2L$ by the separation assumption $d> 2L$. Since $\RR^2=Z\sqcup\bigsqcup_{i=1}^NS_i$, and $\II(\rr)=0$ if $\rr\in Z$, we have for $||\Delta\rr||\leq 2L$
\[\begin{aligned} m_2[\II](\Delta \rr)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_2[I_{\omega_i}](\Delta\rr)\\
&\to \gamma\int_{\text{SO}(3)}L^2m_2[I_{\omega}](\Delta\rr)\, d\omega.\end{aligned}\]
If we set $m_2(\Delta \rr) = 0$ for $||\Delta\rr||>2L$, the above equality holds for all $\Delta\rr$, and taking its Fourier transform (with respect to $\Delta\rr$) and interchanging the Fourier integral with the integral over SO(3) (which can \emph{always} be done), we get
\[ \widehat{m_2[\II]}(\kk) \to \gamma\int_{\text{SO}(3)}L^2\widehat{m_2[I_{\omega}]}(\kk)\, d\omega = \gamma\langle|\widehat I_{\omega}(\kk)|^2\rangle_{\omega},\]
where $\langle\cdot\rangle_{\omega}$ denotes average over the orientations, so over SO(3).

Similarly, for the third moment if $\rr\in S_i$ for some $i$ then $\rr+\Delta\rr_1,\rr+\Delta\rr_2\in S_i\cup Z$, and hence we again get for $||\Delta\rr_1||\leq 2L$ and $||\Delta\rr_2||\leq 2L$ that
\[\begin{aligned} m_3[\II](\Delta \rr_1,\Delta\rr_2)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr_1)I_{\omega_i}(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_3[I_{\omega_i}](\Delta\rr_1,\Delta\rr_2)\\
&\to \gamma\int_{\text{SO}(3)}L^2m_3[I_{\omega}](\Delta\rr_1,\Delta\rr_2)\, d\omega.\end{aligned}\]
Again, setting $m_3(\Delta\rr_1,\Delta\rr_2)=0$ if either $||\Delta\rr_1||>2L$ or $||\Delta\rr_2||>2L$, we also get
\[ \widehat{m_3[\II]}(\kk_1,\kk_2) = \gamma\langle\widehat I_{\omega}(\kk_1)\widehat I_{\omega}(\kk_2)\overline{\widehat I_{\omega}(\kk_1+\kk_2)}\rangle_{\omega}.\]

\section{Discrete case}
In the discrete case, assume $\II\in\RR^{M\times M}$ and $I_{\omega}\in\RR^{L\times L}$ (since $M,L$ denote the support of these signals in some norm, this is valid if for instance we restrict ourselves to $\ell_p$ norms, since then if $||\rr||_p\leq M$ then $||\rr||_{\infty}\leq M$, while $||(M,0,\ldots, 0)^T||_p=||(M,0,\ldots,0)^T||_{\infty}=1$). Once again, we shall assume $N = \Omega(M^2)$.

In the discrete case, we define the $k$th moment of a signal $x\in\RR^{L\times L}$ as
\[ m_k[x][(\Delta i_1,\Delta j_1);\ldots;(\Delta i_k,\Delta j_k)] = \frac{1}{L^2}\sum_{i,j=1}^{L}x[i,j]x[i+\Delta i_1, j + \Delta j_1]\cdots x[i+\Delta i_k, j + \Delta j_k],\]
where we set $x[i,j]=0$ if either $i>L$ or $j>L$.

The derivation is then identical as for the continuous case, with the exception that now $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is the occupancy factor.

\section{Steering}\label{sec:steering}
The first two moments are cheap to compute and store - $m_1$ is a scalar and $m_2$ is radially symmetric (in the limit $N\to\infty$), so it suffices to compute a single ray of it. The third moment however is infeasible to store - it has $(2L-1)^4$ entries, and in modern microscopes we can easily have $L\geq 300$. In addition, the above scheme does not average over in-plane rotations, which can improve estimation in the precense of noise (and accelerate convergence to the population moments without noise). We therefore propose the following steering procedure:

The third moment $m_3[\II](\Delta \rr_1,\Delta \rr_2)$ as defined above is compactly supported (at least numerically) with respect to each of its variables in both real and Fourier space, with support radii $2L$ and $1/2$ in real and Fourier space, respectively (see above formulas for $m_3$ in real and Fourier space). Therefore, we can expand it in a suitable product basis that is compactly supported in both real and Fourier space, e.g. Prolate Spheroidal Wave Functions (PSWFs) or Fourier-Bessel (FB):
\[ m_3[\II](\Delta \rr_1, \Delta \rr_2) = \sum_{k_1,k_2=-\infty}^{\infty}\sum_{q_1,q_2=1}^{\infty}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\rr_1)\overline{\psi_{k_2,q_2}(\Delta\rr_2)},\]
where we conjugate the second set of basis functions for convenience, that will become apparent below (of course, the set of conjugates is also a basis, as $\overline{\psi_{k,q}}=\psi_{-k,q}$ for PSWFs and $\overline{\psi_{k,q}}=(-1)^k\psi_{-k,q}$ for FB). We shall assume that the basis $\{\psi_{k,q}(\rr)\}$ is orthonormal, so $\int_{\RR^2}\psi_{k_1,q_1}(\rr)\overline{\psi_{k_2,q_2}}(\rr) = \delta_{k_1,k_2}\delta_{q_1,q_2}$, valid for both PSWFs and FB. Then, the coefficients are given by
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{||\Delta\rr_1||,||\Delta\rr_2||\leq 2L}m_3[\II](\Delta\rr_1,\Delta\rr_2)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\psi_{k_2,q_2}(\Delta\rr_2)\\
&= \int_{\rr}\II(\rr)\left(\int_{||\Delta\rr_1||\leq 2L}\II(\rr+\Delta\rr_1)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\right)\left(\int_{||\Delta\rr_2||\leq 2L}\II(\rr+\Delta\rr_2)\psi_{k_2,q_2}(\Delta\rr_2)\right).\end{aligned}\]
Note that if we expand $\II(\rr+\Delta\rr)$ in $\{\psi_{k,q}(\Delta\rr)\}$ for fixed $\rr$ and $||\Delta\rr||\leq 2L$, so
\[ \II(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}(\rr)\psi_{k,q}(\Delta\rr),\quad a_{k,q}(\rr)=\int_{||\Delta\rr||\leq 2L}\II(\rr+\Delta\rr)\overline{\psi_{k,q}}(\Delta\rr),\]
and use the fact that $\II$ is real, our expression becomes
\[ \mathfrak{m}_3(k_1,q_1;k_2,q_2) = \int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr).\]

We further assume that all in-plane rotations of the micrograph and its reflection, or equivalently, all in-plane rotations of each such disc of radius $2L$ and its reflection, are present in our dataset. Noting that rotations and reflections commute with the Fourier transform and using the derivation of [Zhao, Landa], the expansion of the disc about $\rr$ by an angle $\alpha$ is given by
\[ \II^{\alpha,+}(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
and the expansion of the reflection of that disc rotated by an angle $\alpha$ by
\[ \II^{\alpha,-}(\rr+\Delta\rr) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. We thus have
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr) + \overline{a_{k_1,q_1}}(\rr)a_{k_2,q_2}(\rr)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
&= \delta_{k_1,k_2}\int_{\rr}\II(\rr)\Re\{a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\}\\
&= \Re\left\{\delta_{k_1,k_2}\int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\right\},\end{aligned}\]
Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.

Similarly, the power spectrum is compactly supported in space (with
support $2L-1$) and bandlimited as in Fourier space it is the average
squared magnitude of the Fourier transform of the projections, each
of which is supposedly bandlimited. Therefore, we may expand it as
\[ m_2[\II](\Delta\rr) =
  \sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\rr),\]
and obtain the expansion coefficients as
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &=
\int_{\Delta\rr}m_2[\II](\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
&=
\int_{\rr}\II(\rr)\int_{\Delta\rr}\II(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
&= \int_{\rr}\II(\rr)a_{k,q}(\rr). \end{aligned}\]
Taking all rotations of $\II$ and its reflection, we get
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\rr) +
    \overline{a_{k,q}}(\rr)]e^{-ik\alpha}\, d\alpha\right)\\ 
&= \delta_{k,0} \int_{\rr}\II(\rr)a_{0,q}(\rr), \end{aligned}\]
where in the last equality we dropped the real part since both
$\II(\rr)$ and $\psi_{0,q}$ are real valued, and hence $a_{0,q}(\rr)=\int_{\Delta\rr}\II(\rr+\Delta\rr)\psi_{0,q}(\Delta\rr)$
is real as well.
Thus, the average power spectrum is effectively a vector.

\begin{remark}
In practice, we are going to expand many non-centered windows from the micrograph in our steerable basis. While we technically assume that these windows are zero outside, and hence compactly supported, because of the centering of PSWFs and FB this may require infinitely many terms in the summation to adequately approximate. In other words, while the above formulas are correct when expressed as integrals, we may be losing accuracy when we expand these non-centered images numerically.
\end{remark}

\begin{remark}
The triple correlation is a 6-tensor and the bispectrum is a 4-tensor, so we lost two degrees of freedom to invariance under translations and one degree of freedom to invariance under in-plane rotations.
\end{remark}

\section{Connection to volume}
We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
\[ \widehat V(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}\Phi_{\ell,s}(k)Y_{\ell,m}(\kk/k),\]
for $k\leq 1$ and zero otherwise, where $c$ is the assumed bandlimit, $Y_{\ell,m}$ may be taken to be either real or complex, and $\Phi_{\ell,s}(r)$ is some radial basis function (in practice, either spherical bessel or the radial part of the 3D PSWFs as in [Lederman]). We work here with the complex spherical harmonics, given by
\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
\begin{remark}
According to Nir and Joe, optimizing over $\mathbb{C}$ allows them to escape local minima they encountered in $\RR$.
\end{remark}

Then
\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}a_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)\Phi_{\ell,s}(k)e^{im'\theta},\]
whenever $k\leq 1$. Express this in 2D PSWFs so
\[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
where in papers the 2D PSWFs are defined as
\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
but in Boris' code the expansion is actually performed with respect to
\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below.

\begin{remark}
The eigenvalues $\alpha_{N,n}$ decay with increasing radial frequency $n$ in a step-function manner (initially constant, then super-exponential decay - see Boris' paper). Additionally, although $\alpha_{N,0}$ seems to be the same for different $N$, the quick decay occurs earlier (smaller $n$) for larger $N$. The above normalization of $\psi_{N,n}$ seems to ensure that the expansion coefficients decay as well. From experience trying to expand a volume in 3D prolates, this normalization seems necessary (even though it is not mentioned in any of the papers I've seen) - without it coefficients for higher $N$ blow up. 
\end{remark}

We then get
\[\begin{aligned} b_{N,n} &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-iN\theta}k\, dk\, d\theta,\\
&= \sum_{\ell,m,m',s}a_{\ell,m,s}[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)]D_{m',m}^{\ell}(\omega)\left(\int_0^1\Phi_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{i(m'-N)\theta}\, d\theta\right),\\
&= \sum_{\ell\geq |N|}\sum_{m,s}a_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
where
\[ \beta_{\ell,s;N,n} = \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1\Phi_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|,\\ 0, & \ell<|N|\end{array}\right.,\]
can be precomputed.

Then, back in real space,
\[\begin{aligned} I_{\omega}(r,\varphi) &= \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}\psi_{N,n}(r,\varphi),\\
&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}a_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi).
\end{aligned}\]
where $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$. In this notation, we assumed $I_{\omega}$ has bandlimit $c$ and is concentrated in the unit ball in real space. We then consider the product
\[\begin{aligned} m_3(\Delta\rr_1,\Delta\rr_2) &= \int_{\rr}\langle I_{\omega}(\rr)I_{\omega}(\rr+\Delta\rr_1)\overline{I_{\omega}(\rr+\Delta\rr_2)}\rangle_{\omega},\\
&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\int_{\rr}\psi_{N_1,n_1}(\rr)\psi_{N_2,n_2}(\rr+\Delta\rr_1)\overline{\psi_{N_3,n_3}(\rr+\Delta\rr_2)}.\end{aligned}\]
Now,
\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_3,s_3}}\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega}\\
&\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned}\]
and [Tamir's note on Kam's bispectrum]
\[ \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega} = (-1)^{N_3+m_3}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
\]
and since $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right) = 0$ unless $m_1+m_2+m_3=0$ and $|\ell_1-\ell_2|\leq \ell_3\leq \ell_1+\ell_2$, we conclude that 
\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \delta_{N_3,N_1+N_2}\sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m2,s_3}}\\
&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}.\end{aligned}\]

Finally, we expand
\[ m_3(\Delta\rr_1,\Delta\rr_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Delta\rr_1)\overline{\psi_{k,q_2}(\Delta\rr_2)},\]
where we only include the block-diagonal terms in the expansion. Defining
\[ \Psi_{\ell,N,s}(\rr) = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}(\rr),\]
the final formula reads
\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}\\
&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)}, \end{aligned}\]
where
\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.\]
In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\rr$ and over $\Delta\rr$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.

\subsection{Implementation}
To implement the above formula, we precompute the quantities
\[ W(\ell_1,\ell_2,\ell_3,m_1,m_2) = (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right),\]
and
\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},\]
so in each iteration of the optimization we compute
\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) = \sum_{\substack{\ell_1,\ell_2,\ell_3\\m_1,m_2\\s_1,s_2,s_3}}& W(\ell_1,\ell_2,\ell_3,m_1,m_2)B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3)\times\\ &a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}} .\end{aligned}\]

The Wigner 3$j$ symbols are computed from the Racah formula
\[\begin{aligned} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right) &= \delta_{m_3,m_1+m_2}(-1)^{\ell_1-\ell_2+m_3}\sqrt{\Delta(\ell_1,\ell_2,\ell_3)}\\ &\times \prod_{i=1}^3\sqrt{(\ell_i-m_i)!(\ell_i+m_i)!}\times \sum_{t}\frac{(-1)^t}{x(t)},\end{aligned}\]
where
\[ x(t) = t!(\ell_3-\ell_2+t+m_1)!(\ell_3-\ell_1+t-m_2)!(\ell_1+\ell_2-\ell_3+t)!(\ell_1-t-m_1)!(\ell_2-t+m_2)!,\]
the sum is over all integer $t$ for which the arguments in the factorials in $x(t)$ are all nonnegative, and 
\[ \Delta(\ell_1,\ell_2,\ell_3) = \frac{(\ell_1+\ell_2-\ell_3)!(\ell_1-\ell_2+\ell_3)!(-\ell_1+\ell_2+\ell_3)!}{(\ell_1+\ell_2+\ell_3+1)!}.\]
In practice, the sum in the above expression is computed in infinite-precision arithmetic (in terms of \texttt{sym} objects in Matlab - compare for instance \texttt{factorial(171)} and \texttt{factorial(sym(171))}). All other terms are computed in standard double-precision.

\subsection{The power spectrum}
The power spectrum is easier to derive directly in Fourier space, to
avoid integration of shifted prolates against centered ones. The
average power spectrum in Fourier space can be derived from Kam's
original formula [Kam, 1980; Eq. 10] by setting $\mb k_1 = \mb k_2$ to
obtain
\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
  \frac{1}{4\pi}\sum_{\ell,
    m}\left|\sum_sa_{\ell,m,s}j_{\ell,s}(k)\right|^2 =
  \frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),\]
where we used the fact that the normalized spherical Bessel functions
$j_{\ell,s}$ are real. To expand the above in 2D PSWFs, we write
\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
  \sum_{q}\mathfrak{m}_2(q)\psi_{0,q}(k),\]
and conclude that
\[ \mathfrak{m}_2(q) =
  \frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
  \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk.\]

\subsection{The mean}

Since the Fourier transformed volume is given by
\[ \widehat V(k,\theta,\varphi) =
  \sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell,m}(\theta,\varphi)j_{\ell,s}(k),\]
since $j_{\ell,s}(0)=0$ unless $\ell=0$, and since
$Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude that
\[ m_1[V] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]

\section{Properties of PSWFs}\label{sec:PSWFs_props}
The $d$-dimensional PSWFs $\psi_{N,n,m}(\rr)$ are eigenfunctions of the truncated Fourier transform, so
\[ \alpha_{N,n,m}\psi_{N,n,m}(\rr) = \int_{\DD}\psi_{N,n,m}(\bm\omega)e^{ic\bm{\omega}\cdot\rr}d\bm\omega,\]
where $\DD=\{\rr\in\RR^d:\ ||\rr||_2\leq 1\}$ is the unit ball, and $c$ is the assumed bandlimit, and the Fourier transform is unfortunately written in terms of angular frequency $\bm\omega$ rather than the regular frequency denoted in previous sections by $\kk$ (we follow this convention here because the code does). Furthermore, $\psi_{N,n,m}$ form an orthonormal basis of both $L^2(\DD)$ and $L^2(\RR^d)$. For a $c$-bandlimited function $f$ with Fourier transform $\widehat f$, we can expand
\[ \widehat f(c\bm\omega) = \sum_{N,n,m}a_{N,n,m}\psi_{N,n,m}(\bm\omega),\]
so
\[\begin{aligned} f(\rr) &= \frac{1}{(2\pi)^d}\int_{c\DD}\widehat f(\bm\omega)e^{i \bm\omega\cdot\rr}\,d\bm\omega = \left(\frac{c}{2\pi}\right)^d\int_{\DD}\widehat f(c\bm\omega)e^{i c\bm\omega\cdot\rr}d\bm\omega\\ 
&= \left(\frac{c}{2\pi}\right)^d\sum_{N,n,m}a_{N,n,m}\int_{\DD}\psi_{N,n,m}(\bm\omega)e^{i c\bm\omega\cdot\rr}\, d\bm\omega = \left(\frac{c}{2\pi}\right)^d\sum_{N,n,m}\alpha_{N,n,m}a_{N,n,m}\psi_{N,n,m}(\rr),\end{aligned}\]
so the expansion coefficients of $f(\rr)$ in $\{\psi_{N,n,m}\}$ are $\left(\frac{c}{2\pi}\right)^d\alpha_{N,n,m}a_{N,n,m}$. In polar form, they have a separable expression
\[ \psi_{N,n,m}(\rr) = R_{N,n}(r)S_{N,m}(\rr/r),\]
where $S_{N,m}(\rr/r)$ are the normalized spherical harmonics on $\mathbb{S}^{d-1}$, the unit sphere in $\RR^d$. We have the following orthogonality relations:
\[ \int_{\mathbb{S}^{d-1}}S_{N,m}(\rr/r)S_{N',m'}(\rr/r) = \delta_{N,N'}\delta_{m,m'},\quad \int_0^1R_{N,n}(r)R_{N,n'}(r)r\, dr = \delta_{n,n'}.\]
Note in particular that $\{R_{N,n}\}$ for different values of the angular frequency $N$ are not necessarily orthogonal.

\begin{remark}
Off-center slices of $m_3$ are not centered, but are also smaller in magnitude than the centered, central slices. We therefore expect to have a bigger error between the expansion in prolates and the actual moment off-center. This may be fixed by predicting the maximum of the off-center slices (say, under the assumption of a spherical object) and translating the prolates in the expnasion by that amout. However, this would introduce a dependence between the two basis functions in the expansion, making all the formulas harder to compute - the resulting product basis is likely not orthogonal.
\end{remark}

\begin{remark}
In the code, we assume the images are sampled on the unit square with samples $\left\{\left(\frac{j}{L},\frac{k}{L}\right):\ j,k = -L,\ldots, L\right\}$, so the image has size $(2L+1)\times(2L+1)$ and bandlimit $c=\pi L$. In particular, this implies that the assumed bandlimit for the micrograph patches is twice as large as that assumed for the volume and its projections. Assuming a larger bandlimit for the latter leads to bad approximation errors: \begin{itemize}
    \item Expanding the volume with a larger bandlimit, and using the resulting coefficients to generate projections from non-trivial directions results in nonsense.
    \item Using the larger bandlimit in the formula for $\mathfrak{m}_3(k,q_1,q_2)$ (or equivalently, assuming such a bandlimit for the projections) results in nonsense.
\end{itemize}
\end{remark}

\section{Debiasing the moments}
\textbf{Key:} The derivation is exactly the same as in the 1D MRA
case, only that instead of factoring out a common signal from an
average of noise as in the current draft (which we can't do here as we have
``continuous heterogeneity''), we consider the viewing directions as instances of a random
variable independent of the noise, and use the law of total expectation.

\subsection{Stats for Dummies}

Claim: Suppose
$\xi_i\overset{\text{iid}}{\sim}\mathcal{N}(0,\sigma^2)$, and $x_i$ is
independently drawn from some distribution with finite first and
second moments. Then 
\[\frac{1}{N}\sum_{i=1}^N\xi_i^2x_i\overset{\text{as}}{\to} \sigma^2\mathbb{E}[x].\]

Proof: Let $X_{\xi} = \frac{1}{N}\sum_{i=1}^N\xi_i^2x_i$ be the random variable in question. Then $\mathbb{E}_{\xi}[X_{\xi}]=\frac{\sigma^2}{N}\sum_{i=1}^Nx_i$ trivially, and 
\[ \text{var}(X_{\xi}) = \mathbb{E}_{\xi}\left[\left(\frac{1}{N}\sum_{i=1}^N(\xi_i^2-\sigma^2)x_i\right)^2\right] = \frac{1}{N^2}\sum_{i,j=1}^N\mathbb{E}_{\xi}[(\xi_i^2-\sigma^2)(\xi_j^2-\sigma^2)]x_ix_j = \frac{2\sigma^2}{N}\left(\frac{1}{N}\sum_{i=1}^Nx_i^2\right),\]
as only terms with $i=j$ give nonzero expectation, so $\text{var}(X_{\xi})\to0$ as $N\to\infty$.

Claim: Under the above assumptions, 
\[\frac{1}{N}\sum_{i=1}^N\xi_ix_i\overset{\text{as}}{\to} 0.\]

Proof: Let $Y_{\xi} = \frac{1}{N}\sum_{i=1}^N\xi_ix_i$. Then $\mathbb{E}_{\xi}[Y_{\xi}]=0$ and
\[\text{var}(Y_{\xi}) =
  \frac{1}{N^2}\sum_{i,j=1}^N\mathbb{E}_{\xi}[\xi_i\xi_j]x_ix_j =
  \frac{\sigma^2}{N}\left(\frac{1}{N}\sum_{i=1}^Nx_i^2\right).\]

Claim: Under the above assumptions, 
\[ m_3[\xi](\Delta i_1, \Delta i_2) = \frac{1}{N}\sum_{i=1}^N\xi_i\xi_{i+\Delta
    i_1}\xi_{i+\Delta i_2} \to 0,\]
for all $\Delta i_1, \Delta i_2$, where it is understood that $\xi_i =
0$ for $i\notin[1,N]$.

Proof: We have
\[ m_3[\xi](\Delta i_1, \Delta i_2) \to \mathbb{E}[\xi_i\xi_{i+\Delta
    i_1}\xi_{i+\Delta i_2}],\]
so if either $\Delta i_1 \neq \Delta i_2$ or $\Delta i_1 = \Delta i_2
\neq 0$, the expectation vanishes as $\xi_i$ are independent, whereas
if $\Delta i_1 = \Delta i_2 = 0$ then the expectation vanishes because
the third moment of a Gaussian is zero.

\subsection{Noisy micrograph moments}
We now suppose that the micrograph is perturbed by additive white
Gaussian noise, so we observe $\widetilde \II = \II + \xi$ where
$\xi\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
m_3[\widetilde\II]$. For simplicity of notation,
we shall use vectorized indices $\mb i = (i,j)$.

For the power spectrum:
\[\begin{aligned}
&m_2[\II + \xi](\Delta \mb i) =
\frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\widetilde\II(\mb
i+\Delta \mb i)\\
&= \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\II(\mb i+\Delta \mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\xi(\mb i + \Delta\mb i)\\ &+ \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\II(\mb i + \Delta\mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\xi(\mb i + \Delta\mb i). 
\end{aligned}\]
Considering the terms one-by-one, the first term is independent of the
noise, and as shown above converges to $\gamma \langle
m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. Denoting the center
of the instance of $I_{\omega}$ in $\II$ by $\mb s_{\omega}$, the second term
satisfies
\[\begin{aligned} 
\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i) &=
\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb i}I_{\omega}(\mb
i)\xi_{\omega}(\mb i + \Delta\mb i)\\
&\to \gamma \mathbb{E}[\xi]\mathbb{E}[I_{\omega}] = 0, \end{aligned}\]
where $\xi_{\omega}(\mb i) = \xi(\mb i + \mb s_{\omega})$ and
$\mathbb{E}[I_{\omega}]$ is proportional to the mean of the
volume. A similar argument applied to the third term shows that it
also vanishes as $N\to\infty$. 
For the fourth term,
if $\Delta\mb i \neq \mb{0}$ then since the noise is zero mean and
i.i.d. this term vanishes. If $\Delta\mb i = \mb0$ then
\[ \frac{1}{m^2}\sum_{i,j=1}^m\xi(\mb i)^2 \to \sigma^2.\]
Thus, we conclude
\[ m_2[\II+\xi](\Delta\mb i) \to \gamma\langle m_2[I_{\omega}](\Delta\mb i)\rangle_{\omega} + \sigma^2\delta(\Delta\mb i).\]

For the third moments, we get 8 terms:
\[\begin{aligned} 
&m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) =
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i+\Delta\mb
  i_1)\II(\mb i + \Delta\mb i_2)}_{(1)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i+\Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(2)}\\ 
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(3)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(4)}\\
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(5)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(6)}\\
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(7)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
    \item Term (1) is $m_3[\II]$, shown above to converge to
    $\gamma\langle m_3[I_{\omega}]\rangle_{\omega}$.
    \item Term (2) is $m_3[\xi]$, the bispectrum of pure noise, which
      vanishes as shown above.
    \item Terms (3)-(5) depend linearly on the noise and hence
      converge to zero.
    \item For term (6), if $\Delta\mb i_1\neq \Delta\mb i_2$ the term
      vanishes as then $\xi(\mb i + \Delta\mb i_1)$ and $\xi(\mb i +
      \Delta\mb i_2)$ are independent. If $\Delta\mb i_1 = \Delta\mb
      i_2$ the term becomes
      \[ \frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)^2
        = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb
          i}I_{\omega}(\mb i)\xi_{\omega}(\mb i + \Delta\mb i)^2 \to
        \gamma\sigma^2\mathbb{E}[I_{\omega}] =
        \gamma\sigma^2Lm_1[V],\]
      where $m_1[V]$ is the mean of the volume (and hence also the
      mean of each projection $I_{\omega}$).
    \item For term (7), if $\Delta\mb i_1 \neq \mb 0$ then once again
      this term vanishes, whereas if $\Delta\mb i_2 = \mb 0$ then it becomes
      \[ \frac{1}{M^2}\sum_{\mb i}\xi(\mb i)^2\II(\mb i + \Delta\mb
        i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
          i}\xi_{\omega}(\mb i)^2I_{\omega}(\mb i + \Delta\mb i_2) \to
        \gamma\sigma^2Lm_1[V].\]
      Similarly, term (8) vanishes if $\Delta\mb i_2\neq \mb 0$ and
      converges to $\gamma\sigma^2Lm_1[V]$ otherwise.
\end{itemize}
Thus, we conclude that
\[ m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) \to \gamma\langle
  m_3[I_{\omega}](\Delta\mb i_1, \Delta\mb i_2)\rangle_{\omega} +
  \gamma\sigma^2Lm_1[V]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
    \delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big).\]
Note that in practice, we have $m_1[\II+\xi] \to m_1[\II] \approx \gamma
Lm_1[V]$ since the noise has zero mean, so we do not need prior knowledge of $\gamma$ to effectively
debias the bispectrum.

\subsection{Expansion in PSWFs}
In practice, we compute the moments of our noisy micrograph in a
product basis of 2D prolates, so we need to derive the expansion
coefficients of the above bias terms in these functions for debiasing.

To this end, writing (in the continuous case again)
\[ \delta(\Delta\rr_1 - \Delta\rr_2) =
  \sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Delta\rr_1)
  \overline{\psi_{k,q_2}(\Delta\rr_2)},\]
we get
\[\begin{aligned}
\mathfrak{d}(k,q_1,q_2) &= \int_{\Delta\rr_1,
  \Delta\rr_2}\delta(\Delta\rr_1-\Delta\rr_2)\overline{\psi_{k,q_1}(\Delta\rr_1)}\psi_{k,q_2}(\Delta\rr_2)\\
&=
\int_{\Delta\rr_2}\overline{\psi_{k,q_1}(\Delta\rr_2)}\psi_{k,q_2}(\Delta\rr_2)\\
&= \delta_{q_1,q_2}.
\end{aligned}\]

Similarly, writing
\[ \delta(\Delta\rr_1) =
  \sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
  \psi_{k,q_1}(\Delta\rr_1) \overline{\psi_{k,q_2}(\Delta\rr_2)},\]
we get
\[\begin{aligned} 
\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Delta\rr_1,
  \Delta\rr_2}\delta(\Delta\rr_1)\overline{\psi_{k,q_1}(\Delta\rr_1)}
\psi_{k,q_2}(\Delta\rr_2)\\
&= \overline{\psi_{k,q_1}(\mb 0)}
\int_{\Delta\rr_2}\psi_{k,q_2}(\Delta\rr_2)\\
&= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
&= \delta_{k,0} \frac{\alpha_{0,q_2}}{2\pi}R_{0,q_1}(0)R_{0,q_2}(0),
\end{aligned}\]
where we used the fact that $R_{0,q}$ satisfies
\[ \frac{\alpha_{0,q}}{2\pi}R_{0,q}(r) =
  \int_0^1R_{0,q}(\rho)J_{0}(cr\rho)\rho\, d\rho,\]
where $J_k$ is the Bessel function of the first kind, and that
$J_0(0)=1$. 
A similar derivation applies to $\delta(\Delta\rr_2)$.

Thus, in terms of the prolate expansion coefficients, our bias
formulas become
\[ \widetilde{\mathfrak{m}}_3(k,q_1,q_2) = \mathfrak{m}_3(k,q_1,q_2) +
  \sigma^2m_1[\widetilde \II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].\]

Similarly, for the power spectrum we get
\[ \widetilde{\mathfrak{m}}_2(q) = \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0).\]
\bibliographystyle{amsplain}

\end{document}

%------------------------------------------------------------------------------
% End of journal.tex
%------------------------------------------------------------------------------

### 2018-07-21 Cryo_EM/NCN_cryo.m

@@ -1,0 +1,34 @@
+function x = NCN_cryo(x0, alpha, beta, tolGrad, tolEig, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda)
+
+x = x0;
+[f,g] = costgrad_fminunc(x, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda);
+f0 = f
+
+while norm(g) > tolGrad
+    [f,g,h] = costgrad_fminunc(x, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda);
+    disp(['f = ' num2str(f)])
+    [V,D] = eig(h);
+    d = diag(D);
+    
+    
+    d(abs(d)>=tolEig) = abs(d(abs(d)>=tolEig));
+%     d(abs(d)<tolEig) = tolEig;
+    d(abs(d)<tolEig) = 0;
+    d = d.^(-1);
+    d(isinf(d)) = 0;
+    d = real(V*diag(d)*V')*g;
+    
+%     d = h\g; % ~inv(h)*g
+
+    eta = 1;
+    xn = x - eta*d;
+    fn = costgrad_fminunc(xn, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda);
+    while fn > f - alpha*eta*(g.'*d)
+        eta = eta*beta;
+        xn = x - eta*d;
+        fn = costgrad_fminunc(xn, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda);
+    end
+    disp(['eta = ' num2str(eta)])
+    x = xn;
+end
+    

### 2018-07-21 Cryo_EM/PSWF_2D_N.m

@@ -1,0 +1,16 @@
+function [psi_Nn, alpha_Nn] = PSWF_2D_N(N, n, c, r_vals, phi_vals)
+
+if n == 0
+    [R_Nn, alpha_Nn] = PSWF_radial_2D(abs(N), 1, c, r_vals);
+    R_Nn = R_Nn(:,1); alpha_Nn = alpha_Nn(1);
+else
+    [R_Nn, alpha_Nn] = PSWF_radial_2D(abs(N), n, c, r_vals);
+end
+R_Nn(r_vals > 1,:) = 0;
+if N < 0
+    R_Nn = (-1)^N*R_Nn; % account for multiplication by eigenvalue
+end
+psi_Nn = bsxfun(@times, R_Nn, exp(1i*N*phi_vals)/sqrt(2*pi));
+
+    
+    

### 2018-07-21 Cryo_EM/PSWF_2D_full.m

@@ -1,0 +1,9 @@
+function psi_Nn = PSWF_2D_full(maxN, n_list, c, r_vals, phi_vals)
+
+psi_Nn = cell(maxN+1, 1);
+for N = 0:maxN
+    R_Nn = PSWF_radial_2D(N, n_list(N+1)-1, c, r_vals);
+    psi_Nn{N+1} = bsxfun(@times, R_Nn, exp(1i*N*phi_vals)/sqrt(2*pi));
+end
+    
+    

### 2018-07-21 Cryo_EM/cart2inds.m

@@ -1,0 +1,8 @@
+function inds = cart2inds(sz, row_vals, col_vals)
+
+row_vals = row_vals(row_vals > 0);
+col_vals = col_vals(col_vals > 0);
+inds = zeros(length(row_vals)*length(col_vals), 1);
+for ii = 1:length(col_vals)
+    inds( (ii-1)*length(row_vals) + (1:length(row_vals)) ) = (col_vals(1)-1)*sz(2) + (ii-1)*sz(1) + row_vals;
+end

### 2018-07-21 Cryo_EM/cost_micro_moments.m

@@ -1,0 +1,35 @@
+function [f, store] = cost_micro_moments(x, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, m1_micro, lambda, store)
+
+% gamma = x(end);
+gamma = 1;
+% a_lms = x(1:(end-1)/2) + 1i*x((end-1)/2+1:end-1);
+a_lms = x(1:end/2) + 1i*x(end/2+1:end);
+a_lms = vec_to_cell_vol_coeffs(a_lms, x_lists.L(x_lists.p));
+a_vec = cellfun(@(x)x(:), a_lms, 'UniformOutput', 0);
+a_vec = vertcat(a_vec{:});
+
+if ~isfield(store, 'F')
+    m3_harms = bispectrum_from_harmonics_par_noKloop(a_lms, L, B, W, B_lists.L1, B_lists.L2, B_lists.L3, x_lists.s, B_lists.blk_id);
+    dm3 = gamma*m3_harms - m3_micro;
+    
+    [m2_harms, G_m2] = power_spectrum_from_harmonics(a_vec, M2_quants.j_l, M2_quants.R_0n, M2_quants.w, L);
+    dm2 = gamma*m2_harms - m2_micro;
+    
+    [m1_harms, G_m1] = mean_from_harmonics(a_vec, M2_quants.j_0, x_lists.s(1), L);
+    dm1 = gamma*m1_harms - m1_micro;
+    
+    F = real([lambda(1)*dm3; lambda(2)*dm2; lambda(3)*dm1]);
+    store.m_harms = real([lambda(1)*m3_harms; lambda(2)*m2_harms; lambda(3)*m1_harms]);
+    store.F = F;
+    store.G_m2 = G_m2;
+    store.G_m1 = G_m1;
+else
+    F = store.F;
+end
+
+if ~isfield(store, 'f')
+    f = norm(F)^2;
+    store.f = f;
+else
+    f = store.f;
+end

### 2018-07-21 Cryo_EM/gen_proj_given_rot_PSWFs.m

@@ -1,0 +1,16 @@
+function [I, I_pad, R] = gen_proj_given_rot_PSWFs(Rot, a_lms, psi_lNs, L)
+
+R = RN2RL( getSHrotMtx( Rot, length(a_lms)-1, 'complex' ) );
+a_lms_rot = cellfun(@mtimes, a_lms, R, 'UniformOutput', 0);
+
+I = zeros(L);
+maxL = length(a_lms)-1;
+for l = 0:maxL
+    for N = -l:l
+        I(:) = I(:) + psi_lNs{l+1}{N+l+1}*a_lms_rot{l+1}(:,N+l+1);
+    end
+end
+I = real(I);
+
+I_pad = zeros(3*L-2);
+I_pad(L:2*L-1,L:2*L-1) = I;

### 2018-07-21 Cryo_EM/grad_micro_moments.m

@@ -1,0 +1,60 @@
+function [g, store] = grad_micro_moments(x, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, m1_micro, lambda, store)
+
+% gamma = x(end);
+gamma = 1;
+% a_lms = x(1:(end-1)/2) + 1i*x((end-1)/2+1:end-1);
+a_lms = x(1:end/2) + 1i*x(end/2+1:end);
+a_lms = vec_to_cell_vol_coeffs(a_lms, x_lists.L(x_lists.p));
+a_vec = cellfun(@(x)x(:), a_lms, 'UniformOutput', 0);
+a_vec = vertcat(a_vec{:});
+
+if ~isfield(store, 'F')
+    m3_harms = bispectrum_from_harmonics_par_noKloop(a_lms, L, B, W, B_lists.L1, B_lists.L2, B_lists.L3, x_lists.s, B_lists.blk_id);
+    dm3 = gamma*m3_harms - m3_micro;
+    
+    [m2_harms, G_m2] = power_spectrum_from_harmonics(a_vec, M2_quants.j_l, M2_quants.R_0n, M2_quants.w, L);
+    dm2 = gamma*m2_harms - m2_micro;
+    
+    [m1_harms, G_m1] = mean_from_harmonics(a_vec, M2_quants.j_0, x_lists.s(1), L);
+    dm1 = gamma*m1_harms - m1_micro;
+    
+    F = real([lambda(1)*dm3; lambda(2)*dm2; lambda(3)*dm1]);
+    store.m_harms = real([lambda(1)*m3_harms; lambda(2)*m2_harms; lambda(3)*m1_harms]);
+    store.F = F;
+    store.G_m2 = G_m2;
+    store.G_m1 = G_m1;
+else
+    F = store.F;
+    G_m2 = store.G_m2;
+    G_m1 = store.G_m1;
+    m_harms = store.m_harms;
+end
+
+if ~isfield(store, 'J')
+    [G1, G2, G3] = bispectrum_grad_from_harmonics_par_noKloop...
+        (a_lms, L, B, W, B_lists.L1, B_lists.L2, B_lists.L3, x_lists.L, x_lists.m, x_lists.s, B_lists.blk_id);
+    
+    sign_factor = (-1).^(x_lists.L(x_lists.n)+x_lists.m(x_lists.n));
+    
+    J = G1 + G2;
[…]

### 2018-07-21 Cryo_EM/grad_pwr_spectrum.m

@@ -1,0 +1,29 @@
+function [g, store] = grad_pwr_spectrum(a_lms, x_lists, L, M2_quants, m2_micro, gamma, store)
+
+a_lms = a_lms(1:length(a_lms)/2) + 1i*a_lms(length(a_lms)/2+1:end);
+a_lms = vec_to_cell_vol_coeffs(a_lms, x_lists.L(x_lists.p));
+a_vec = cellfun(@(x)x(:), a_lms, 'UniformOutput', 0);
+a_vec = vertcat(a_vec{:});
+
+if ~isfield(store, 'dm2')
+    [m2_harms, G_m2, H_m2] = power_spectrum_from_harmonics(a_vec, M2_quants.j_l, M2_quants.R_0n, M2_quants.w, L);
+    dm2 = real(m2_harms - m2_micro./gamma);
+    store.dm2 = dm2;
+    store.G_m2 = G_m2;
+    store.H_m2 = H_m2;
+else
+    dm2 = store.dm2;
+    G_m2 = store.G_m2;
+end
+
+if ~isfield(store, 'J')
+    J = 2*G_m2(x_lists.p,:);
+    J(x_lists.m(x_lists.p) > 0,:) = 2*J(x_lists.m(x_lists.p) > 0, :);
+    
+    J = [real(J); imag(J)].';
+    store.J = J;
+else
+    J = store.J;
+end
+
+g = 2*J.'*dm2;

### 2018-07-21 Cryo_EM/hess_micro_moments_withHess.m

@@ -1,0 +1,60 @@
+function [Hu, store] = hess_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, u, store)
+
+if ~isfield(store, 'F')
+    [~, store] = cost_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, store);
+end
+H1 = store.H1;
+H2 = store.H2;
+H3 = store.H3;
+H_m2 = store.H_m2;
+F = store.F;
+
+if ~isfield(store, 'J')
+    [~, store] = grad_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, store);
+end
+J = store.J;
+sign_factor = store.signs;
+
+if ~isfield(store, 'h')
+    Hc = cellfun(@(x,y,z) (sign_factor*sign_factor.').*(z(x_lists.n,x_lists.n) + z(x_lists.n,x_lists.n).') ...
+        + bsxfun(@times, x(x_lists.p, x_lists.n), sign_factor.') + bsxfun(@times, x(x_lists.p, x_lists.n).', sign_factor)...
+        + bsxfun(@times, y(x_lists.p, x_lists.n), sign_factor.') + bsxfun(@times, y(x_lists.p, x_lists.n).', sign_factor)...
+        , H1, H2, H3, 'UniformOutput', 0);
+    
+    Hr = cellfun(@(x,y,z) bsxfun(@times, z(x_lists.p, x_lists.n), sign_factor.') + bsxfun(@times, z(x_lists.n, x_lists.p), sign_factor).' ...
+        + (sign_factor*sign_factor.').*x(x_lists.n,x_lists.n) + x(x_lists.p, x_lists.p).'...
+        + (sign_factor*sign_factor.').*y(x_lists.n,x_lists.n) + y(x_lists.p, x_lists.p).'...
+        , H1, H2, H3, 'UniformOutput', 0);
+    
+    H_plus = cellfun(@plus, Hc, Hr, 'UniformOutput', 0);
+    H_minus = cellfun(@minus, Hc, Hr, 'UniformOutput', 0);
+    for ii = 1:length(H_plus)
[…]

### 2018-07-21 Cryo_EM/moments_from_micrograph_steerable_LS.m

@@ -1,0 +1,40 @@
+function [m1, m2, m3] = moments_from_micrograph_steerable_LS(I, L, Psi, ang_freq, pts_in_disc)
+% L is size of single projection
+
+m1 = mean(I(:));
+
+maxN = max(ang_freq);
+blk_id = [];
+for ii = 0:maxN
+    num_freqs = sum(ang_freq == ii);
+    blk_id(end+1:end+num_freqs^2, 1) = (ii+1)*ones(num_freqs^2, 1);
+end
+
+m2 = zeros(length(find(ang_freq == 0)), 1);
+m3 = zeros(size(blk_id));
+
+sz_img = size(I(:,:,1));
+parfor ii = 1:numel(I(:,:,1))
+    [row, col] = ind2sub(sz_img, ii);
+%     form image to be expanded:
+    img = extract_patch(I, row, col, L-1);
+    assert(norm(squeeze(img(L, L, :) - I(row, col, :)))==0)
+    img = reshape(img(1:end-1, 1:end-1, :), 4*(L-1)^2, size(img,3));
+    
+%     Expand in PSWFs:
+    x = Psi\img(pts_in_disc, :);
+    coeff = x(1:length(ang_freq),:); 
+    coeff(ang_freq>0, :) = coeff(ang_freq>0, :) + 1i*x(length(ang_freq)+1:end, :);
+    coeff = PSWF_coeff_convert(coeff, ang_freq);
+    
+%     Compute contribution to moments:
+    m2 = m2 + coeff{1}*squeeze(I(row,col,:));
+    m3_add = cellfun(@(x) real(x*diag(squeeze(I(row,col,:)))*x'), coeff, 'UniformOutput', 0);
+    m3_add = cellfun(@(x) x(:), m3_add, 'UniformOutput', 0);
+    m3 = m3 + vertcat(m3_add{:});
+end
+
+m2 = m2./numel(I);
+m3 = m3./numel(I);
+
+m3 = accumarray(blk_id, m3, [maxN+1, 1], @(x) {reshape(x, sqrt(length(x)), [])});

### 2018-07-21 Cryo_EM/precomp_Nn_list.m

@@ -1,0 +1,8 @@
+function n_list = precomp_Nn_list(L, beta, T, realFlag)
+
+PSWF_Nn_p = precomp_pswf_t(L, beta, T, realFlag);
+ang_freq = PSWF_Nn_p.ang_freq;
+n_list = zeros(max(ang_freq)+1, 1);
+for N = 0:max(ang_freq)
+    n_list(N+1) = length(find(ang_freq == N));
+end

### 2018-07-21 Cryo_EM/precomp_bispectrum_coeffs_OLD.m

@@ -1,0 +1,43 @@
+function B = precomp_bispectrum_coeffs(maxL, maxS, L)
+
+n_list = precomp_Nn_list(floor(L/2));
+q_list = precomp_Nn_list(L);
+beta = sph_Bessel_to_2D_PSWF_factors(maxL, n_list, maxS, floor(L/2)); % l x N x s x n
+T = generate_radial_triple_prods(pi*floor(L/2), maxL, maxL, n_list, q_list); % k x n1 x n2 x n3 x q1 x q2
+
+B = cell(maxL+1, 1); % k x L2 x L3
+for k = 0:maxL
+    L23_vals = k:maxL;
+    B{k+1} = cell(length(L23_vals), length(L23_vals));
+    for ii_2 = 1:length(L23_vals)
+        L2 = L23_vals(ii_2);
+        for ii_3 = 1:length(L23_vals)
+            L3 = L23_vals(ii_3);
+            
+            L1_vals = max(abs(L2-L3),k):min(L2+L3, maxL);
+            B{k+1}{ii_2, ii_3} = cell(length(L1_vals), 1);
+            for jj = 1:length(L1_vals)
+                L1 = L1_vals(jj);
+                tmp_acc = 0;
+                parfor NN = 1:(2*L2+1)*(2*L3+1)
+                    [N2, N3] = ind2sub([2*L2+1, 2*L3+1], NN);
+                    
+                    % Product and sum over n1:
+                    tmp = conj(beta{L1+1}{1})*reshape(T{k+1, N2+maxL+1, N3+maxL+1}, n_list(1), []); % s1 x (n2, n3, q1, q2)
+                    tmp = reshape(tmp.', n_list(k+1), []); % n2 x (n3, q1, q2, s1)
+                    
+                    % Product and sum over n2:
+                    tmp = beta{L2+1}{k+1}*tmp; % s2 x (n3, q1, q2, s1)
+                    tmp = reshape(tmp.', n_list(k+1), []); % n3 x (q1, q2, s1, s2)
+                    
+                    % Product and sum over n3:
+                    tmp = beta{L3+1}{k+1}*tmp; % s3 x (q1, q2, s1, s2)
+                    tmp_acc = tmp_acc + ...
+                        reshape(tmp.', q_list(k+1), q_list(k+1), size(beta{L1+1}{1},1), size(beta{L2+1}{k+1},1), size(beta{L3+1}{k+1},1));
[…]

### 2018-07-21 Cryo_EM/precomp_bispectrum_coeffs_sep_kN.m

@@ -1,0 +1,57 @@
+function B = precomp_bispectrum_coeffs_sep_kN(maxL, maxS, L)
+
+Lr = floor(L/2);
+n_list = precomp_Nn_list(Lr);
+beta = sph_Bessel_to_2D_PSWF_factors(maxL, n_list, maxS, Lr); % l x N x s x n
+
+[x,y] = meshgrid(-Lr:Lr, -Lr:Lr);
+[phi, r] = cart2pol(x,y);
+r = r./Lr;
+beta = 1; 
+T = 1e-1;
+realFlag = 1;
+[PSWF_Nn_p, PSWF_quad_int] = precomp_pswf_t(L, beta, T, realFlag);
+
+B = cell(maxL+1, 1); % k x L2 x L3
+for k = 0:maxL
+    L23_vals = k:maxL;
+    B{k+1} = cell(length(L23_vals), length(L23_vals));
+    for ii_2 = 1:length(L23_vals)
+        L2 = L23_vals(ii_2);
+        for ii_3 = 1:length(L23_vals)
+            L3 = L23_vals(ii_3);
+            
+            L1_vals = max(abs(L2-L3),k):min(L2+L3, maxL);
+            B{k+1}{ii_2, ii_3} = cell(length(L1_vals), 1);
+            for jj = 1:length(L1_vals)
+                L1 = L1_vals(jj);
+                tmp_acc = 0;
+                parfor NN = 1:(2*L2+1)*(2*L3+1)
+                    [N2, N3] = ind2sub([2*L2+1, 2*L3+1], NN);
+                    N2 = N2-1; N3 = N3-1;
+                    N1 = N2 + N3;
+                    if abs(N1) > L1, continue; end
+                    
+                    T = generate_radial_triple_prods_given_N...
+                        (Lr, N1, N2, N3, n_list, r, phi, PSWF_Nn_p, PSWF_quad_int);
+                    
+                    % Product and sum over n1:
+                    tmp = conj(beta{L1+1}{1})*reshape(T, n_list(1), []); % s1 x (n2, n3, q1, q2)
+                    tmp = reshape(tmp.', n_list(k+1), []); % n2 x (n3, q1, q2, s1)
+                    
+                    % Product and sum over n2:
+                    tmp = beta{L2+1}{k+1}*tmp; % s2 x (n3, q1, q2, s1)
+                    tmp = reshape(tmp.', n_list(k+1), []); % n3 x (q1, q2, s1, s2)
+                    
[…]

### 2018-07-21 Cryo_EM/precomp_wigner_weights.m

@@ -1,0 +1,21 @@
+function W = precomp_wigner_weights(maxL)
+
+W = cell(maxL+1, maxL+1);
+for ll = 1:(maxL+1)^2
+    [L1, L2] = ind2sub([maxL+1, maxL+1], ll);
+    L1 = L1-1; L2 = L2-1;
+    
+    L3_vals = abs(L1-L2):min(L1+L2, maxL);
+    W{ll} = zeros(2*L2+1, 2*L1+1, length(L3_vals));
+    for ii_3 = 1:length(L3_vals)
+        L3 = L3_vals(ii_3);
+        
+        for m1 = -L1:L1
+            for m2 = -L2:L2
+                m3 = m1+m2;
+                if abs(m3) > L3, continue; end
+                W{ll}(m2+L2+1, m1+L1+1, ii_3) = (-1)^(m3)*wigner3j(L1, L2, L3, m1, m2, -m3);
+            end
+        end
+    end
+end

### 2018-07-21 Cryo_EM/recon_moments_PSWFs.m

@@ -1,0 +1,23 @@
+function [m2_rec, m3_rec] = recon_moments_PSWFs(m2, m3, PSWF_Nn_p, points_inside_the_circle)
+
+L = PSWF_Nn_p.L;
+PSWF_funcs = PSWF_Nn_p.samples;
+ang_freqs = PSWF_Nn_p.ang_freq;
+ang_freqs_unique = unique(ang_freqs);
+
+m2_rec = zeros(2*L, 2*L);
+m2_rec(points_inside_the_circle) = real(PSWF_funcs(:,ang_freqs==0)*m2);
+
+m3_rec = zeros((2*L)^2);
+for ii = 1:length(ang_freqs_unique)
+    PSWF_funcs_curr = PSWF_funcs(:,ang_freqs==ang_freqs_unique(ii)); 
+    if ii == 1
+        m3_rec(points_inside_the_circle, points_inside_the_circle) = m3_rec(points_inside_the_circle, points_inside_the_circle)...
+            + real(PSWF_funcs_curr*m3{ii}*PSWF_funcs_curr');
+    else
+        m3_rec(points_inside_the_circle, points_inside_the_circle) = m3_rec(points_inside_the_circle, points_inside_the_circle)... 
+            + 2*real(PSWF_funcs_curr*m3{ii}*PSWF_funcs_curr');
+    end
+end
+
+m3_rec = reshape(m3_rec, 2*L, 2*L, 2*L, 2*L);

### 2018-07-21 Cryo_EM/test_bispect_code_single_proj.m

@@ -1,0 +1,227 @@
+%% Paths
+
+clear all; close all;
+addpath('../kam_cryo')
+addpath('../SHT')
+addpath(genpath('../pswf_t_mod'))
+addpath(genpath('../easyspin-5.2.18'))
+addpath('~/EMDB_maps')
+addpath('../aspire')
+initpath
+
+%% Basic parameters and volume
+info.mol = 'emd_8117'; % molecule id
+info.maxL = 1; % truncation for spherical harmonics expansion
+info.r_cut = 1/2;
+info.L0 = 20; % size of volume
+info.N=floor(info.L0/2);
+
+vol = double(ReadMRC([info.mol '.map'])); %read volume
+vol = cryo_downsample(vol, info.L0); 
+
+% Expand volume:
+[Psilms, Psilms_2D, jball, jball_2D] = precompute_spherical_basis(info);
+[a_lms, vol_rec] = expand_vol_spherical_basis(vol, info, Psilms, jball);
+
+%% Generate basis & projection
+L = info.L0;
+R = floor(L/2);
+maxL = length(a_lms)-1;
+
+[psi_Nn, n_list] = PSWF_2D_full_cart(maxL, R, 1, 1e-5);
+s_list = cellfun('size', a_lms, 1);
+beta = sph_Bessel_to_2D_PSWF_factors(maxL, n_list, size(a_lms{1},1), R);
+
+psi_lNs = cell(maxL+1,1);
+for l = 0:maxL
+    psi_lNs{l+1} = cell(2*l+1, 1); % N
+    for N = -l:l
+        psi_lNs{l+1}{N+l+1} = (-1)^(N*(N<0))*psi_Nn{N+maxL+1}*beta{l+1}{abs(N)+1}(1:s_list(l+1),:).'; % r x s
+    end
+end
+
+Rot = randR(3);
+R = RN2RL( getSHrotMtx( Rot, length(a_lms)-1, 'complex' ) );
+a_lms_rot = cellfun(@mtimes, a_lms, R, 'UniformOutput', 0);
+
+I = zeros(L);
+for l = 0:maxL
+    for N = -l:l
+        I(:) = I(:) + psi_lNs{l+1}{N+l+1}*a_lms_rot{l+1}(:,N+l+1);
+    end
+end
+
+%% Basis for moments:
+
[…]

### 2018-07-21 Cryo_EM/test_bispectrum_formula.m

@@ -1,0 +1,72 @@
+
+clear all; close all;
+addpath('~/Documents/kam_cryo')
+addpath('../SHT')
+addpath(genpath('../easyspin-5.2.18'))
+% addpath(genpath('../Prol'))
+% addpath(genpath('../pswf_t_fast_nfft_v3.3.2'))
+addpath(genpath('../pswf_t_mod'))
+addpath('~/EMDB_maps')
+addpath('../aspire')
+initpath
+addpath(genpath('../manopt'))
+addpath('../nfft')
+
+maxL = 5;
+L = 20;
+r_cut = 1/2;
+r_select_ratio = 1;
+
+s_lens = gen_s_list(maxL, r_cut, r_select_ratio, floor(L/2));
+[L_list, m_list, s_list, p_inds, n_inds] = gen_vec_coeff_lists(maxL, s_lens);
+
+info.mol = 'emd_8117';
+info.maxL = maxL; % truncation for spherical harmonics expansion
+info.L0 = L; % size of volume
+info.r_cut = r_cut; % bandlimit
+info.N=floor(info.L0/2);
+
+[Psilms, Psilms_2D, jball, jball_2D] = precompute_spherical_basis(info);
+vol = double(ReadMRC([info.mol '.map'])); %read volume
+vol = cryo_downsample(vol, info.L0); 
+[a_lms, vol_rec] = expand_vol_spherical_basis(vol, info, Psilms, jball);
+vol_rec = real(icfftn(vol_rec));
+
+[~, PSWF_quad_int, points_inside_the_circle] = precomp_pswf_t(L-1, 1, 1e-1, 1);
+% Rots = genRotationsGrid( 60, 0, 0);
+Rots = randrot(3, 5e4);
+% Rots = zeros(3,3,5e4);
+% for ii = 1:size(Rots,3), Rots(:,:,ii) = randrot(3); end
+SNR = 1/5;
+[M1, M2, M3, sigma, gamma] = moments_from_harmonics_projs_PSWFs(Rots, a_lms, L, SNR, PSWF_quad_int, points_inside_the_circle);
+% [M1, M2, M3] = moments_from_harmonics_projs(Rots, a_lms, Psilms_2D, jball_2D, L, PSWF_Nn_p, PSWF_quad_int);
+M3 = cellfun(@(x) x(:), M3, 'UniformOutput', 0);
+M3 = vertcat(M3{:});
+
[…]

### 2018-07-21 Cryo_EM/test_pure_noise_micros.m

@@ -1,0 +1,47 @@
+clear all; close all;
+addpath('~/Documents/kam_cryo')
+addpath('../SHT')
+addpath('../aspire')
+initpath
+addpath('~/EMDB_maps')
+addpath(genpath('../pswf_t_mod'))
+addpath(genpath('../nfft'))
+% addpath(genpath('../manopt'))
+
+
+maxL = 5;
+L = 20;
+M = 7420; % size of a micrograph
+num_micros = 250; % number of micrographs
+r_cut = 1/2;
+% batch_size = 1e6;
+
+I = randn(M, M, num_micros);
+sigma = 1;
+
+% [m1, m2, m3] = moments_from_micrograph_steerable_parMicro(I, L, batch_size);
+[m1, m2, m3] = moments_from_micrograph_steerable_windows(I, L);
+[m2, m3] = debias_moments_steerable(m1, m2, m3, sigma, L);
+m3 = cellfun(@(x) x(:), m3, 'UniformOutput', 0); 
+m3 = vertcat(m3{:});
+
+load('/scratch/network/eitanl/B_factors_bispect_maxL5_L20.mat', 'B', 'L1_list', 'L2_list', 'L3_list', 'blk_id', 'W')
+
+B_lists.L1 = L1_list;
+B_lists.L2 = L2_list;
+B_lists.L3 = L3_list;
+B_lists.blk_id = blk_id;
+
+[a_lms, gamma] = recover_vol_coeffs_from_moments(m3, m2, m1, maxL, L, B, W, B_lists, r_cut, []);
+
+info.maxL = maxL; % truncation for spherical harmonics expansion
+info.L0 = L; % size of volume
+info.r_cut = 1/2; % bandlimit
+info.N=floor(info.L0/2);
+
+[Psilms, ~, jball, ~] = precompute_spherical_basis(info);
+vol_rec = recover_from_ALM_v4_given_Psilms(a_lms, info.N, jball, Psilms, maxL, L);
+vol_rec = real(icfftn(vol_rec));
+
+clear I B L1_list L2_list L3_list blk_id W
+save('/scratch/network/eitanl/pure_noise_test_res.mat', '-v7.3')

### 2018-07-21 Cryo_EM/test_tensor_contraction_TenTool.m

@@ -1,0 +1,41 @@
+% Test tensor contraction using Sandia Lab's Tensor Toolbox
+addpath('../tensor_toolbox')
+addpath('../tensor_lab')
+addpath('../tprod')
+
+X_mat = randn(50,30,40,60,70);
+
+A = randn(70,50);
+B = randn(60,40);
+C = randn(40,40);
+
+% Naive contraction:
+tic
+Res_naive = reshape(X_mat, [], size(A,1))*A; % 5*3*4*6 x 5
+Res_naive = reshape(Res_naive.', [], size(B,1))*B;
+Res_naive = reshape(Res_naive.', [], size(C,1))*C;
+Res_naive = reshape(Res_naive.', size(C,2), size(B,2), size(A,2), size(X_mat,1), size(X_mat,2));
+Res_naive = permute(Res_naive, [4,5,1,2,3]);
+time_naive = toc;
+
+% Tensor Toolbox:
+X = tensor(X_mat); % 5 x 3 x 4 x 2
+
+tic
+Res_TenTool = ttm(X, {C.',B.',A.'}, [3,4,5]); 
+time_TenTool = toc;
+
+% Tensor Lab:
+tic
+Res_TenLab = tmprod(X_mat, {C.', B.', A.'}, 3:5);
+time_TenLab = toc;
+
+% Tprod:
+tic
+Res_tprod = tprod(X_mat, [1,2,3,4,-1], A, [-1, 5]);
+Res_tprod = tprod(Res_tprod, [1,2,3,-1,5], B, [-1, 4]);
+Res_tprod = tprod(Res_tprod, [1,2,-1,4,5], C, [-1, 3]);
+time_tprod = toc;
+
+assert(norm(Res_naive(:)-Res_TenTool.data(:)) < 1e-10)
+assert(norm(Res_naive(:)-Res_TenLab(:)) < 1e-10)

### 2018-07-21 Cryo_EM/vec_to_cell_vol_coeffs.m

@@ -1,0 +1,9 @@
+function a_lms = vec_to_cell_vol_coeffs(a_lms, L_list)
+
+a_lms = accumarray(L_list+1, a_lms, [max(L_list)+1, 1], @(x) {x});
+for l = 0:length(a_lms)-1
+    a_lms{l+1} = reshape(a_lms{l+1}, [], l+1);
+    a_lms{l+1}(:,1) = (a_lms{l+1}(:,1) + (-1)^l*conj(a_lms{l+1}(:,1)))/2;
+    neg_m = bsxfun(@times, conj(a_lms{l+1}(:,end:-1:2)), (-1).^(l+(l:-1:1)));
+    a_lms{l+1} = [neg_m, a_lms{l+1}];
+end

### 2018-07-24 TEX/draft_biology.tex
First draft of biology ms

\documentclass[english,11pt]{article}

\pdfoutput=1

\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{color}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools} 
\usepackage[margin=1.2in]{geometry}

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}

\newcommand{\TODO}[1]{{\color{red}{[#1]}}}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
%\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}

\newtheorem*{lem*}{Lemma}

\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{plain}
\newtheorem{corollary}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{proposition}[thm]{\protect\propositionname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\usepackage{slashbox}

\usepackage{babel}
\providecommand{\claimname}{Claim}
\providecommand{\definitionname}{Definition}
\providecommand{\lemmaname}{Lemma}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\corollaryname}{Corollary}
\providecommand{\propositionname}{Proposition}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\hx}{\hat{x}} 
\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}

\begin{document}

\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}

\author{Tamir Bendory, Nicolas Boumal, William Leeb, Eitan Levin and Amit Singer}
\maketitle

\begin{abstract}
	Here comes the abstract
\end{abstract}

\section{Introduction}

\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
% 
In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. Within the ice, the molecules are randomly oriented and positioned. The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}. Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions. The goal is to construct 3-D models of the molecules from the micrographs.

The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors. On the one hand, the $\SNR$ is a function of the electron dose. To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels. On the other hand, the $\SNR$ is a function of the molecule size. The smaller the molecules, the fewer detected electrons carry information about them.

%\paragraph{Particle picking.}
All contemporary methods in the field split the reconstruction procedure into several stages.
The first stage consists in extracting the various particle projections from the micrographs. This is called \emph{particle picking}. Later stages aim to construct a 3-D model of the molecule from these projections. The quality of the reconstruction eventually hinges on the quality of the particle picking stage. Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.

Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$. This fact has been recognized early on by the cryo-EM community. In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
\begin{quote}
	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy? Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
\end{quote}
In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). The same was mentioned by Joachim Frank in his Nobel prize lecture ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size}''~\cite{frank2018single}. 
As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, as the particles themselves cannot be picked from the micrographs.
This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.

Despite this progress, detecting small molecules in the micrographs remains a challenge.
We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules. Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability. \TODO{Need a ref for this claim.}

In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done. Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.

As a proof of concept, we study two simplified models.
In first model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably. This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}. We study it in more details in a companion paper~\cite{bendory2018estimation}. An extension to multiple planted images is analyzed in~\cite{bendory2018estimation}.
In the second model, we consider the 3-D reconstruction problem as it appears in cryo-EM, while neglecting important aspects as discussed in detail in TKTK. \TODO{Here we need to elaborate a bit.} This is the main result of this paper. \TODO{We probably need to switch the order of this paragraph.}

%A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure. Instead, we solve a simpler problem that we believe captures key elements of the SPR problem. We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.

In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume.
For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the projections are well separated and we acquire enough of them. Importantly, there is no need to detect the projections. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the volume. To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares. 
We use similar technique for the simpler model of planted image as illustrated in Figure~\ref{fig:Einst_example}. As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details.

Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}. In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged. In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template. In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure. This model bias is common to all particle picking methods based on template matching. In our approach, no templates are required, thus significantly reducing concerns about model bias. \TODO{To add reference to our example.}

%\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}

%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion

%\clearpage

%\begin{figure}[h!]
%	\centering
%	\begin{subfigure}[h]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{Einstein}
%		\caption{\label{fig:Einstein}Einstein image (template)}
%	\end{subfigure}%
%	\begin{subfigure}[h]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
%		\caption{$n = 10$}
%	\end{subfigure}
%	\begin{subfigure}[h]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
%		\caption{$n = 10^2$}
%	\end{subfigure}

%	\begin{subfigure}[h]{0.3\textwidth}
%	\centering
%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
%	\caption{$n = 10^3$}
%\end{subfigure}%
%\begin{subfigure}[h]{0.3\textwidth}
%	\centering
%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
%	\caption{$n = 10^4$}
%\end{subfigure}
%\begin{subfigure}[h]{0.3\textwidth}
%	\centering
%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
%	\caption{$n = 10^5$}
%\end{subfigure}

%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment. As a template, we used Einstein's image of size $50\times 50$ pixels. We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image. Each noise image was aligned with respect to the template by the maximal value of their cross correlation. After the alignment, all the images were averaged. As can be seen, the more pure noise images we use, the closer the averaged image to the template.   }	
%\end{figure}

%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
%As a result, the projections in the 2-D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.

%\paragraph{Simplified model for SPR}

%In this paper, we present a preliminary study that aims to show that estimating a particle 
%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.

%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$. Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph. 
%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem. We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.

\begin{figure}[t]
	\centering
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
		\caption{$\sigma = 0$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
		\caption{$\sigma = 0.5$}
	\end{subfigure}
	\begin{subfigure}[h]{0.33\textwidth}
		\centering
		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
		\caption{$\sigma = 3$}
	\end{subfigure}
	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$. Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein. In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image. In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known. By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done. \TODO{Do we want to replace with a cryo-EM figure?}}	
\end{figure}

%\paragraph{Autocorrelation analysis.}
%We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
%In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
%In a nutshell, the method consists of two stages. First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data. These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data. There is no need to detect individual occurrences.
%In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
%This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data. As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).

%\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
%In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
%In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images. With merely 1000 noise images, Einstein's face is clearly observed in the averaged image. With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise. Crucially, the more noisy images we use, the more severe the model bias towards the template. 
%In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
%This true in general to any method which is based on template matching.
%\TODO{Do we have a nice experiment to exemplify the phenomenon?}

\section{Results} \label{sec:results}

We start this section by considering the simplified model of planted image. This experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}. This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries. 
As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking. Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
Then, we  show that the same holds true for the 3-D reconstruction setup.
 The Methods section provides additional details. 
%We conducted two experiments in the simplified image formation model described in the introduction:
%\begin{enumerate}
%	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}. This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
%	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
%\end{enumerate}
%As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking. Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging. The Methods section provides additional details. %In the discussion section, we outline how the general approach could be extended to full 3-D SPR.

%In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.

In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels. A micrograph contains, on average, 700 occurrences of the target image at random locations. The latter are chosen so that two occurrences are always separated by at least 49 pixels in each direction. \TODO{it is not clear at this point why the separation is needed. Maybe comment about this, or at least mention that the separation condition is discussed later on.} Thus, about 10\% of each micrograph contains signal. The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$). This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}. In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.\TODO{Need to mention that in the 3-D reconstruction we do not make these assumptions.}

We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra). This is a particularly simple computation. In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself. Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level. Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}. % bauschke2004rrr,
RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.

Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available in \TODO{supplementary material}. Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available. Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.

\TODO{Here the cryo-EM setup shows up}

%defined as 
%\begin{equation}
%\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
%\end{equation} 
%where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
%\TODO{We have a movie in the supplementary material.}

%%%% This is about bias, and it's imprecise; let's leave it out?
%As an initial guess, we picked an image of the physicist Issac Newton. If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[scale=0.45]{reconstruction1_cropped}
		\caption{\small $P = 512$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[scale=0.45]{reconstruction10_cropped}
		\caption{\small $P = 512\times 10$}
	\end{subfigure}%

		\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[scale=0.45]{reconstruction100_cropped}
		\caption{ \small $P = 512\times 10^2$ }
	\end{subfigure}%
	\begin{subfigure}[h]{0.45\textwidth}
		\centering
		\includegraphics[scale=0.45]{reconstruction1000_cropped}
		\caption{\small $P = 512\times 10^3$}
	\end{subfigure}%

%	\begin{subfigure}[h]{0.33\textwidth}
%		\centering
%		\includegraphics[scale=0.33]{Einstein_progress_cropped}
%		\caption{\label{fig:err_curve}\small Error curve}
%	\end{subfigure}%

%\begin{figure}[h!]
%	\centering
%	\begin{subfigure}[h]{0.25\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{Newton}
%		\caption{\label{fig:newton}Newton  (model)}
%	\end{subfigure}%
%	\begin{subfigure}[h]{0.25\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{reconstruction2}
%		\caption{\small $P =1024$}
%	\end{subfigure}%
%	\begin{subfigure}[h]{0.25\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{reconstruction20}
%		\caption{$P = 1024\times 10$}
%	\end{subfigure}%
%	\begin{subfigure}[h]{0.25\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{reconstruction200}
%		\caption{$P = 1024\times 100$}
%	\end{subfigure}%
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton. Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
		\TODO{To add: redo the figures according to Amit's comments}
		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
	}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[scale=.7]{Einstein_progress}
\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
\end{figure}

%
%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
%\begin{equation}
%\gamma_i = \frac{M_i L}{N},
%\end{equation}
%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length. In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$. As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.

%
%In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy. Any two occurrences are separated by at least 20 entries. The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion. The micrograph is then contaminated with additive white Gaussian noise. This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal. Neither the number of occurrences nor the noise level $\sigma$ are known to the algorithm.
%
%In the Methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals. The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
%
%Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the individual signal occurrences, the signals can be estimated accurately given enough data. Furthermore, the \TODO{propensity\footnote{Might not be the right word; 'density' is not good because it might refer to the density of the particle for example, whereas here we mean to say the 'fraction of occurrences that come from a particular class'}} of each signal can also be estimated.

%In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
%As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
%The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.

%We do not assume the knowledge of the noise level. 
%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm. 
%
%\begin{figure}[t]
%	\centering
%	\includegraphics[scale=0.45]{progressive_n}
%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
%	\label{fig:1Dhomosignals}
%\end{figure}
%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
%	\label{fig:1DhomoRMSE}
%\end{figure}

%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
%	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations). The last column depicts evolution of the relative root mean square error in estimating each individual target signal. Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times. With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
%%		
%%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$. Red signals are the ground truth (targets) and the blue signals are our estimations. Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$. The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$. The $\SNR$ is $1/12$. \TODO{1. to replace with a ``progress'' plot 2. replace the triangle signal 3. add error progress figure}
%	}
%	\label{fig:1Dheterosignals}
%\end{figure}

\clearpage
\section{Discussion}
\TODO{I suggest starting the Discussion section with a summary statement highlighting the significance of the work. Something along the lines (this is not polished, just to give you a rough idea): 
	"In this paper we illustrated that it is possible to determine the 3-D molecular structure in single particle cryo-EM directly from the micrographs without performing particle picking. Our work implies that it is possible to reconstruct arbitrarily small molecules, in particular, molecules that are too small to being detected and located in micrographs. Ultimately, this work significantly increases the range of molecules to which cryo-EM can be successfully applied."

	We should also incorporate Alberto's comment that our technique also allows to use much lower defocus values. Lower defocus means lower contrast, but will maintain higher frequency information. From that perspective, we may be able to get high resolution reconstructions from fewer micrographs, just because we would be using lower defocus. }
%\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}

%All current algorithmic pipelines for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
%Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.  Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.

%In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs. Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters. Recovering the parameters from the statistics reduces to solving a set of polynomial equations. Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
%

In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters. Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering. As a result, it may not be limited to large molecules in the same way that particle picking approaches are. Concerns for model bias would also greatly be reduced.

 %Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.

%
%The same general approach can, in principle, be applied directly to SPR from cryo-EM. Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken from unknown viewing directions. The aim is to estimate the 3-D volumes of the different conformations directly from micrographs. Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients. Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients. Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
%
%We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume \TODO{at resolution comparable to that of the particle projections---remove?}. This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly. Additional parameters in these equations could encode an unknown viewing direction distribution and an unknown conformation distribution, which could then also be estimated. Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering. As a result, it may not be limited to large molecules in the same way that particle picking approaches are. Concerns for model bias would also greatly be reduced.

%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems. As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.

Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.

One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term. Still, large amounts of data also imply large amounts of computations. On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs. It can even be done in streaming mode, as only one look at each micrograph is necessary. The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs. Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary. Of course, an important question then is whether the equations can be solved meaningfully in practice. The proof-of-concept experiments above suggest they might.

%Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package. The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}. At the time, such approaches also seemed challenging.

%\TODO{Do we want to say something about the number of images that we need? Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard? (Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}

Beyond data acquisition and computational challenges, there are modeling issues to consider.
As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
First, we assume an additive white noise model, while in practice the noise may be correlated or signal dependent. To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly. \TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals. 
Perhaps this separation could be induced by careful experimental design \TODO{?}.
Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences. Here as well, relations between autocorrelation functions of the data and of the signals can be derived.

We also admit several aspects of SPR experiments that were neglected in this paper, including power spectrum estimation, Contrast Transfer Function (CTF) correction and the non-uniformity of the viewing directions. All this aspects must be taken into account so the method could be applied on real data. We hope to take care of this issues in a future research, as well extending this method for the possibility to estimate several volumes simultaneously. 
%
%\TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION? Do we also want to stress that models have been refined over decades? Both points are rather defensive in nature.	}

\TODO{Where and how do we cite Kam? Fred?}

\section{Methods} \label{sec:methods}

\subsection{2-D experiment (we need a name)}
To explain the method, we begin by deriving the algebraic relation between the autocorrelation functions of the micrographs and the autocorrelation functions of the planted image.
%We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals. For ease of exposition, we do so in the 1-D case. Extension to the 2-D case is straightforward. We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.

Let $x$ be the sought image and let $y\in\RNN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple smaller micrographs concatenated into one.)
The forward model (or ``image'' formation model) is as follows. An unknown binary signal  indicates (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
\begin{align}
	y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
	\label{eq:model}
\end{align}
where $\ast$ denotes linear convolution. Let $\textbf{i}:=(i_1,i_2)$ and similarly for \textbf{j}.
The binary signals obey the following property:
\begin{align}
	\textrm{If } s[\textbf{i}] = 1 \textrm{ then } s[\textbf{j}] = 0 \textrm{ for all}  \|\textbf{i}-\textbf{j}\|_\infty\leq 2L-1.
	\label{eq:spacing}
\end{align}
In words: the starting positions of any two occurrences must be separated by at least $2L-1$ positions in each direction, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.

From $y$, we aim to recover $x$. In this simplified model, we assume to know the number of  occurrences of the signal. In contrast, particle picking is the task of estimating the binary signal $s $, which cannot  be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)

%We denote the set of these nonzero values by 
% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.  %Neither the $M_i$'s nor $M$ are assumed to be known.

%
%Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals. Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.

%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
%\begin{align}
%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
%  \label{eq:spacing}
%\end{align}
%The goal is to estimate $x_1,\ldots,x_K$ from $y$.

%
%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
%
%Our method for estimating the signals is composed of two stages. 
%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations. The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met. Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations. 
%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.

\paragraph{Aperiodic autocorrelation functions}
%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}

%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
%
%In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
%\begin{align}
%	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
%	\label{eq:ac_general}
%\end{align}
%where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
%For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
For the purpose of this experiment, we need only the mean of the signal and its second-order autocorrelation defined for an arbitrary signal $z\in\mathbb{R}^{m\times m}$ by \TODO{to verify}
 \begin{align} 
 a_z^2[\ell_1,\ell_2] & = \frac{1}{m^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[i_1,i_2]z[i_1+\ell_1,i_2+\ell_2]. 
 \end{align}
 It can be shown that in the limit of $N\to\infty$,  the mean of the microgaph is equal to the mean of the signal $x$, scaled by the scalar 
 \begin{align}
 \gamma & = \frac{M L}{N},
 \end{align}
 which denotes the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
 Similarly, the second-order autocorrelations are related through 
 \begin{align*}
	\lim_{N\to\infty} a_y^2[\ell_1,\ell_2] & = \gamma a_{x}^2[\ell_1,\ell_2] + \sigma^2\delta[\ell_1,\ell_2].
 \end{align*}
 These relations, and their extension to multiple planted images, are proven and discussed in~\cite{bendory2018estimation}.

% 
%Explicitly, the first-, second- and third-order autocorrelations are given by
%\begin{align} 
%	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
%	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
%	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
%\end{align}
%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
%\begin{align*}
%	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
%\end{align*}
%%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
%
%\paragraph{Estimating the autocorrelation function of a single signal.}
%
%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first. It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
%\begin{align}
%	\gamma & = \frac{M L}{N}
%%\end{align}
%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
%
%One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$. Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$. The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
%\begin{align*}
%	\E\{ a_y^1 \} & = \gamma a_x^1.
%\end{align*}
%We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
%\begin{align*}
%	\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
%\end{align*}
%Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
%
%The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations. Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries. Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence. As a result,
%\begin{align*}
%	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
%\end{align*}
%for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function. The last part captures the autocorrelation of the noise. Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
%Along the same lines, one can establish a relation for third-order autocorrelations:
%\begin{align}
%	\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
%	\label{eq:data_ac_k1}
%\end{align}
%for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
%Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
%%
%\paragraph{Estimating the autocorrelation function of multiple signals.}
%
%Returning to the general case $K \geq 1$, let $M_1, \ldots, M_K$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
%\begin{align}
%	\gamma_k & = \frac{M_k L}{N}, & \gamma & = \sum_{k=1}^K\gamma_k.
%\end{align}
%As above, we consider the asymptotic regime where $M_1,\ldots,M_K,N\to\infty$ while preserving the ratios $\gamma_k$ constant.
%% 
%Still under the spacing constraint~\eqref{eq:spacing}, similarly to the developments above, one can estimate a mixture of the autocorrelations of the $K$ target signals from the autocorrelations of the micrograph:
%\begin{align}
%\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
%\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
%\end{align}
%where $\ell, \ell_1, \ell_2 = 0, \ldots, L-1$. The left hand side is straightforward to estimate from data: it provides a succinct summary of it. The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$, and possibly $\sigma^2$. The task is to solve these polynomial equations in a robust way.

%\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}

%
%\paragraph{Numerical experiment with three 1-D signals.}
%
%
%For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$. Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$. Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals. 
%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far. For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$. Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$. The resulting $\SNR$ of $y$
%% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
%is about 1/9.
%
%
%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences. Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
%
%%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
%%
%Given the observation $y$, we proceed to compute the autocorrelations. The first-order autocorrelation is straightforward. For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$. Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities. Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. We have
%\begin{align*}
%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
%\end{align*}
%coefficients in total. Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
%\begin{align*}
%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
%\end{align*}
%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$. \TODO{We may want to cite MRA literature here.}
%
%In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points. Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data. If multiple GPUs are available, segments can of course be handled in parallel.
%
%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data. We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
%\begin{multline}
%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
%\label{eq:optim1D}
%\end{multline}
%where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
%
%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
%Thus, we first run the optimization with $W = 2L-1$. This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions. Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm. This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$. We find that this procedure is reliable for a wide range of experimental parameters. To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$. Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
%%\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them? Not sure it's worth the effort. -- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
%%\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
%%
%%
%
%%\TODO{separation}
%%
%%For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
%%The only difference is that here, for each
%%placement, one of the three signals is picked at random proportionally to the desired number
%%of occurrences of each.
%%In this experiment, we computed the first three autocorrelation functions. 
%%We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
%%\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
%
%%To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
%%\begin{multline}
%%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
%%\label{eq:optim1D}
%%\end{multline}
%%where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
%
%
%%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
%%Thus, we first run the optimization with $W = 2L-1$. This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions. Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}. 
%%This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$. We find that this procedure is reliable for a wide range of experimental parameters. To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$. Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
%
%
%
%

\paragraph{Numerical experiment with 2-D image.}

For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
an accept/reject rule based on the separation constraint and locations picked so far.
On average, $700$ images are placed in each micrograph.   
Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an $\SNR$ of approximately $1/20$.
An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data. If multiple GPUs are available, segments can of course be handled in parallel.

In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
In stark contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction} (see also~\cite{bendory2017fourier} for a review). This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform. 
Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph. These can be computed highly efficiently and in parallel.

To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
\begin{align*}
	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
\end{align*}
on an image $z$ of size $2L\times 2L$.
We set the parameter $\beta$ to 1.
The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere. The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes. The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.

In order to compare the performance in multiple cases and at different noise levels, the algorithm is stopped after a fixed number of iterations (1000) and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution. While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments. \TODO{Note the last two sentences!}

\subsection{3-D experiment}

We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
\[ \widehat V(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\]
for $k\leq 1$ and zero otherwise, where $c$ is the assumed bandlimit, $Y_{\ell,m}$ may be taken to be either real or complex, and $j_{\ell,s}(r)$ is some radial basis function (in practice, either spherical bessel or the radial part of the 3D PSWFs as in [Lederman]). We work here with the complex spherical harmonics, given by
\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase.

\TODO{To write down the definition of the $j$ --- the spherical bessel (to copy from the ISBI)}

In this experiment, the micrograph is related to the projections by 
\begin{equation}
\mathcal{I}(\rr) = \sum_{i=1}^{N} I_{\omega_i}(\rr-\rr_i)+ \varepsilon, \quad \varepsilon~\sim\mathcal{N}(0,\sigma^2 I),
\end{equation}
where $\rr$ is a vector in $\mathbb{R}^2$. \TODO{To write down the definition of projection}

In this paper, we need the first three autocorrelations. In particular, it can be shown that 
\begin{align}
m_k[\II]  \to \gamma\langle m_k[I_\omega]\rangle_{\omega}, 
\end{align}
where $\langle\cdot\rangle$ denotes averaging. \TODO{Do we want to define a general moment?}

In a standard SPR experiment, we expect the distribution of in-plane rotations to be uniform because .... 
Therefore, based on~\cite{landa2017steerable}, we expand the each autocorrelation functions in Prolates .... as discussed in Appendix TKTK.

The next stage is to connect the Prolates coefficients of the moments with those of the volume.
In Appendix TKTK we show that the volume is related to autocorrelations of the micrograph through

\begin{align}
\langle m_1[I_\omega]\rangle_\omega  &= \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0) \\ 
\mathfrak{m}_2(q) &= \frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
\int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk \\
\mathfrak{m}_3(k,q_1,q_2) &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}
\end{align}
where
\begin{align*}
C&:= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},
\end{align*}
and 
\begin{align*}
\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.
\end{align*}

From the data we can estimate (see Appendix TKTK) 
\begin{align*}
\widetilde{\mathfrak{m}}_2(q) &= \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0) \\
\widetilde{\mathfrak{m}}_3(k,q_1,q_2) &= \mathfrak{m}_3(k,q_1,q_2) +
\sigma^2m_1[\II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
\end{align*}

\section*{Acknowledgment}
Let's thank them all

\bibliographystyle{plain}
\bibliography{ref}

\appendix

\section{Moments derivation}

\TODO{To rewrite for the discrete case}
We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$ (so by the above argument, in fact $N=\Theta(M^2)$), so $\gamma = \lim_{N\to\infty}\frac{N}{M^2}\in(0,1)$. We also assume that the orientations of the projections in $\II$ are uniformly distributed over the sphere. For the first moment,
\[ m_1[\II] =
\frac{NL^2}{M^2}\cdot\frac{1}{N}\sum_{i=1}^N\frac{1}{L^2}\int_{\RR^2}I_{\omega_i}(\rr)\,
d\rr \to \gamma\int_{\text{SO}(3)} L^2m_1[I_{\omega}]\, d\omega =
\gamma L m_1[V],\]
since $\int_{\RR^2} I_{\omega}(x,y)\, dx\, dy = \widehat I_{\omega}(\mathbf{0})=\widehat V(\mathbf{0})$ as the Fourier transform of any projection corresponds to a 2D slice of the Fourier transform of the volume passing through the origin.

For the second and third moments, note that if $\rr\in S_i$ for some $i$, then $\rr+\Delta\rr\in S_i\cup Z$ whenever $||\Delta\rr||\leq 2L$ by the separation assumption $d> 2L$. Since $\RR^2=Z\sqcup\bigsqcup_{i=1}^NS_i$, and $\II(\rr)=0$ if $\rr\in Z$, we have for $||\Delta\rr||\leq 2L$
\[\begin{aligned} m_2[\II](\Delta \rr)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr)\, d\rr\\ 
&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_2[I_{\omega_i}](\Delta\rr)\\
&\to \gamma\int_{\text{SO}(3)}L^2m_2[I_{\omega}](\Delta\rr)\, d\omega.\end{aligned}\]
If we set $m_2(\Delta \rr) = 0$ for $||\Delta\rr||>2L$, the above equality holds for all $\Delta\rr$, and taking its Fourier transform (with respect to $\Delta\rr$) and interchanging the Fourier integral with the integral over SO(3) (which can \emph{always} be done), we get
\[ \widehat{m_2[\II]}(\kk) \to \gamma\int_{\text{SO}(3)}L^2\widehat{m_2[I_{\omega}]}(\kk)\, d\omega = \gamma\langle|\widehat I_{\omega}(\kk)|^2\rangle_{\omega},\]
where $\langle\cdot\rangle_{\omega}$ denotes average over the orientations, so over SO(3).

Similarly, for the third moment if $\rr\in S_i$ for some $i$ then $\rr+\Delta\rr_1,\rr+\Delta\rr_2\in S_i\cup Z$, and hence we again get for $||\Delta\rr_1||\leq 2L$ and $||\Delta\rr_2||\leq 2L$ that
\[\begin{aligned} m_3[\II](\Delta \rr_1,\Delta\rr_2)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr_1)I_{\omega_i}(\rr+\Delta\rr_2)\, d\rr\\ 
&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_3[I_{\omega_i}](\Delta\rr_1,\Delta\rr_2)\\
&\to \gamma\int_{\text{SO}(3)}L^2m_3[I_{\omega}](\Delta\rr_1,\Delta\rr_2)\, d\omega.\end{aligned}\]
Again, setting $m_3(\Delta\rr_1,\Delta\rr_2)=0$ if either $||\Delta\rr_1||>2L$ or $||\Delta\rr_2||>2L$, we also get
\[ \widehat{m_3[\II]}(\kk_1,\kk_2) = \gamma\langle\widehat I_{\omega}(\kk_1)\widehat I_{\omega}(\kk_2)\overline{\widehat I_{\omega}(\kk_1+\kk_2)}\rangle_{\omega}.\]

\section{Steering}\label{sec:steering}
The first two moments are cheap to compute and store - $m_1$ is a scalar and $m_2$ is radially symmetric (in the limit $N\to\infty$), so it suffices to compute a single ray of it. The third moment however is infeasible to store - it has $(2L-1)^4$ entries, and in modern microscopes we can easily have $L\geq 300$. In addition, the above scheme does not average over in-plane rotations, which can improve estimation in the precense of noise (and accelerate convergence to the population moments without noise). We therefore propose the following steering procedure:

The third moment $m_3[\II](\Delta \rr_1,\Delta \rr_2)$ as defined above is compactly supported (at least numerically) with respect to each of its variables in both real and Fourier space, with support radii $2L$ and $1/2$ in real and Fourier space, respectively (see above formulas for $m_3$ in real and Fourier space). Therefore, we can expand it in a suitable product basis that is compactly supported in both real and Fourier space, e.g. Prolate Spheroidal Wave Functions (PSWFs) or Fourier-Bessel (FB):
\[ m_3[\II](\Delta \rr_1, \Delta \rr_2) = \sum_{k_1,k_2=-\infty}^{\infty}\sum_{q_1,q_2=1}^{\infty}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\rr_1)\overline{\psi_{k_2,q_2}(\Delta\rr_2)},\]
where we conjugate the second set of basis functions for convenience, that will become apparent below (of course, the set of conjugates is also a basis, as $\overline{\psi_{k,q}}=\psi_{-k,q}$ for PSWFs and $\overline{\psi_{k,q}}=(-1)^k\psi_{-k,q}$ for FB). We shall assume that the basis $\{\psi_{k,q}(\rr)\}$ is orthonormal, so $\int_{\RR^2}\psi_{k_1,q_1}(\rr)\overline{\psi_{k_2,q_2}}(\rr) = \delta_{k_1,k_2}\delta_{q_1,q_2}$, valid for both PSWFs and FB. Then, the coefficients are given by
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{||\Delta\rr_1||,||\Delta\rr_2||\leq 2L}m_3[\II](\Delta\rr_1,\Delta\rr_2)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\psi_{k_2,q_2}(\Delta\rr_2)\\
&= \int_{\rr}\II(\rr)\left(\int_{||\Delta\rr_1||\leq 2L}\II(\rr+\Delta\rr_1)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\right)\left(\int_{||\Delta\rr_2||\leq 2L}\II(\rr+\Delta\rr_2)\psi_{k_2,q_2}(\Delta\rr_2)\right).\end{aligned}\]
Note that if we expand $\II(\rr+\Delta\rr)$ in $\{\psi_{k,q}(\Delta\rr)\}$ for fixed $\rr$ and $||\Delta\rr||\leq 2L$, so
\[ \II(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}(\rr)\psi_{k,q}(\Delta\rr),\quad a_{k,q}(\rr)=\int_{||\Delta\rr||\leq 2L}\II(\rr+\Delta\rr)\overline{\psi_{k,q}}(\Delta\rr),\]
and use the fact that $\II$ is real, our expression becomes
\[ \mathfrak{m}_3(k_1,q_1;k_2,q_2) = \int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr).\]

We further assume that all in-plane rotations of the micrograph and its reflection, or equivalently, all in-plane rotations of each such disc of radius $2L$ and its reflection, are present in our dataset. Noting that rotations and reflections commute with the Fourier transform and using the derivation of [Zhao, Landa], the expansion of the disc about $\rr$ by an angle $\alpha$ is given by
\[ \II^{\alpha,+}(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
and the expansion of the reflection of that disc rotated by an angle $\alpha$ by
\[ \II^{\alpha,-}(\rr+\Delta\rr) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. We thus have
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr) + \overline{a_{k_1,q_1}}(\rr)a_{k_2,q_2}(\rr)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
&= \delta_{k_1,k_2}\int_{\rr}\II(\rr)\Re\{a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\}\\
&= \Re\left\{\delta_{k_1,k_2}\int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\right\},\end{aligned}\]
Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.

Similarly, the power spectrum is compactly supported in space (with
support $2L-1$) and bandlimited as in Fourier space it is the average
squared magnitude of the Fourier transform of the projections, each
of which is supposedly bandlimited. Therefore, we may expand it as
\[ m_2[\II](\Delta\rr) =
\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\rr),\]
and obtain the expansion coefficients as
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &=
\int_{\Delta\rr}m_2[\II](\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
&=
\int_{\rr}\II(\rr)\int_{\Delta\rr}\II(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
&= \int_{\rr}\II(\rr)a_{k,q}(\rr). \end{aligned}\]
Taking all rotations of $\II$ and its reflection, we get
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\rr) +
\overline{a_{k,q}}(\rr)]e^{-ik\alpha}\, d\alpha\right)\\ 
&= \delta_{k,0} \int_{\rr}\II(\rr)a_{0,q}(\rr), \end{aligned}\]
where in the last equality we dropped the real part since both
$\II(\rr)$ and $\psi_{0,q}$ are real valued, and hence $a_{0,q}(\rr)=\int_{\Delta\rr}\II(\rr+\Delta\rr)\psi_{0,q}(\Delta\rr)$
is real as well.
Thus, the average power spectrum is effectively a vector.

\section{Connection to volume}

We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
\[ \widehat V(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\]
for $k\leq 1$ and zero otherwise, where $c$ is the assumed bandlimit, $Y_{\ell,m}$ may be taken to be either real or complex, and $j_{\ell,s}(r)$ is some radial basis function (in practice, either spherical bessel or the radial part of the 3D PSWFs as in [Lederman]). We work here with the complex spherical harmonics, given by
\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase.

Then
\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}a_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta},\]
whenever $k\leq 1$. Express this in 2D PSWFs so
\[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
where in papers the 2D PSWFs are defined as
\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
but in Boris' code the expansion is actually performed with respect to
\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below.

We then get
\[\begin{aligned} b_{N,n} &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-iN\theta}k\, dk\, d\theta,\\
&= \sum_{\ell,m,m',s}a_{\ell,m,s}[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)]D_{m',m}^{\ell}(\omega)\left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{i(m'-N)\theta}\, d\theta\right),\\
&= \sum_{\ell\geq |N|}\sum_{m,s}a_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
where
\[ \beta_{\ell,s;N,n} = \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|,\\ 0, & \ell<|N|\end{array}\right.,\]
can be precomputed.

Then, back in real space,
\[\begin{aligned} I_{\omega}(r,\varphi) &= \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}\psi_{N,n}(r,\varphi),\\
&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}a_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi).
\end{aligned}\]
where $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$. In this notation, we assumed $I_{\omega}$ has bandlimit $c$ and is concentrated in the unit ball in real space. We then consider the product
\[\begin{aligned} m_3(\Delta\rr_1,\Delta\rr_2) &= \int_{\rr}\langle I_{\omega}(\rr)I_{\omega}(\rr+\Delta\rr_1)\overline{I_{\omega}(\rr+\Delta\rr_2)}\rangle_{\omega},\\
&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\int_{\rr}\psi_{N_1,n_1}(\rr)\psi_{N_2,n_2}(\rr+\Delta\rr_1)\overline{\psi_{N_3,n_3}(\rr+\Delta\rr_2)}.\end{aligned}\]
Now,
\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_3,s_3}}\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega}\\
&\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned}\]
and [Tamir's note on Kam's bispectrum]
\[ \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega} = (-1)^{N_3+m_3}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
\]
and since $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right) = 0$ unless $m_1+m_2+m_3=0$ and $|\ell_1-\ell_2|\leq \ell_3\leq \ell_1+\ell_2$, we conclude that 
\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \delta_{N_3,N_1+N_2}\sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m2,s_3}}\\
&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}.\end{aligned}\]

Finally, we expand
\[ m_3(\Delta\rr_1,\Delta\rr_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Delta\rr_1)\overline{\psi_{k,q_2}(\Delta\rr_2)},\]
where we only include the block-diagonal terms in the expansion. Defining
\[ \Psi_{\ell,N,s}(\rr) = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}(\rr),\]
the final formula reads
\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}\\
&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)}, \end{aligned}\]
where
\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.\]
In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\rr$ and over $\Delta\rr$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.

\subsection{The power spectrum}
The power spectrum is easier to derive directly in Fourier space, to
avoid integration of shifted prolates against centered ones. The
average power spectrum in Fourier space can be derived from Kam's
original formula [Kam, 1980; Eq. 10] by setting $\mb k_1 = \mb k_2$ to
obtain
\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
\frac{1}{4\pi}\sum_{\ell,
	m}\left|\sum_sa_{\ell,m,s}j_{\ell,s}(k)\right|^2 =
\frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),\]
where we used the fact that the normalized spherical Bessel functions
$j_{\ell,s}$ are real. To expand the above in 2D PSWFs, we write
\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
\sum_{q}\mathfrak{m}_2(q)\psi_{0,q}(k),\]
and conclude that
\[ \mathfrak{m}_2(q) =
\frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
\int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk.\]

\subsection{The mean}

Since the Fourier transformed volume is given by
\[ \widehat V(k,\theta,\varphi) =
\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell,m}(\theta,\varphi)j_{\ell,s}(k),\]
since $j_{\ell,s}(0)=0$ unless $\ell=0$, and since
$Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude that
\[ m_1[V] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]

\subsection{Implementation details}
To implement the above formula, we precompute the quantities
\[ W(\ell_1,\ell_2,\ell_3,m_1,m_2) = (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right),\]
and
\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},\]
so in each iteration of the optimization we compute
\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) = \sum_{\substack{\ell_1,\ell_2,\ell_3\\m_1,m_2\\s_1,s_2,s_3}}& W(\ell_1,\ell_2,\ell_3,m_1,m_2)B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3)\times\\ &a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}} .\end{aligned}\]

The Wigner 3$j$ symbols are computed from the Racah formula
\[\begin{aligned} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right) &= \delta_{m_3,m_1+m_2}(-1)^{\ell_1-\ell_2+m_3}\sqrt{\Delta(\ell_1,\ell_2,\ell_3)}\\ &\times \prod_{i=1}^3\sqrt{(\ell_i-m_i)!(\ell_i+m_i)!}\times \sum_{t}\frac{(-1)^t}{x(t)},\end{aligned}\]
where
\[ x(t) = t!(\ell_3-\ell_2+t+m_1)!(\ell_3-\ell_1+t-m_2)!(\ell_1+\ell_2-\ell_3+t)!(\ell_1-t-m_1)!(\ell_2-t+m_2)!,\]
the sum is over all integer $t$ for which the arguments in the factorials in $x(t)$ are all nonnegative, and 
\[ \Delta(\ell_1,\ell_2,\ell_3) = \frac{(\ell_1+\ell_2-\ell_3)!(\ell_1-\ell_2+\ell_3)!(-\ell_1+\ell_2+\ell_3)!}{(\ell_1+\ell_2+\ell_3+1)!}.\]

\section{Noisy micrograph moments}
We now suppose that the micrograph is perturbed by additive white
Gaussian noise, so we observe $\widetilde \II = \II + \xi$ where
$\xi\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
m_3[\widetilde\II]$. For simplicity of notation,
we shall use vectorized indices $\mb i = (i,j)$.

For the power spectrum:
\[\begin{aligned}
&m_2[\II + \xi](\Delta \mb i) =
\frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\widetilde\II(\mb
i+\Delta \mb i)\\
&= \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\II(\mb i+\Delta \mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\xi(\mb i + \Delta\mb i)\\ &+ \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\II(\mb i + \Delta\mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\xi(\mb i + \Delta\mb i). 
\end{aligned}\]
Considering the terms one-by-one, the first term is independent of the
noise, and as shown above converges to $\gamma \langle
m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. Denoting the center
of the instance of $I_{\omega}$ in $\II$ by $\mb s_{\omega}$, the second term
satisfies
\[\begin{aligned} 
\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i) &=
\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb i}I_{\omega}(\mb
i)\xi_{\omega}(\mb i + \Delta\mb i)\\
&\to \gamma \mathbb{E}[\xi]\mathbb{E}[I_{\omega}] = 0, \end{aligned}\]
where $\xi_{\omega}(\mb i) = \xi(\mb i + \mb s_{\omega})$ and
$\mathbb{E}[I_{\omega}]$ is proportional to the mean of the
volume. A similar argument applied to the third term shows that it
also vanishes as $N\to\infty$. 
For the fourth term,
if $\Delta\mb i \neq \mb{0}$ then since the noise is zero mean and
i.i.d. this term vanishes. If $\Delta\mb i = \mb0$ then
\[ \frac{1}{m^2}\sum_{i,j=1}^m\xi(\mb i)^2 \to \sigma^2.\]
Thus, we conclude
\[ m_2[\II+\xi](\Delta\mb i) \to \gamma\langle m_2[I_{\omega}](\Delta\mb i)\rangle_{\omega} + \sigma^2\delta(\Delta\mb i).\]

For the third moments, we get 8 terms:
\[\begin{aligned} 
&m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) =
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i+\Delta\mb
	i_1)\II(\mb i + \Delta\mb i_2)}_{(1)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i+\Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(2)}\\ 
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(3)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(4)}\\
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(5)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(6)}\\
&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(7)} +
\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
	\item Term (1) is $m_3[\II]$, shown above to converge to
	$\gamma\langle m_3[I_{\omega}]\rangle_{\omega}$.
	\item Term (2) is $m_3[\xi]$, the bispectrum of pure noise, which
	vanishes as shown above.
	\item Terms (3)-(5) depend linearly on the noise and hence
	converge to zero.
	\item For term (6), if $\Delta\mb i_1\neq \Delta\mb i_2$ the term
	vanishes as then $\xi(\mb i + \Delta\mb i_1)$ and $\xi(\mb i +
	\Delta\mb i_2)$ are independent. If $\Delta\mb i_1 = \Delta\mb
	i_2$ the term becomes
	\[ \frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)^2
	= \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb
		i}I_{\omega}(\mb i)\xi_{\omega}(\mb i + \Delta\mb i)^2 \to
	\gamma\sigma^2\mathbb{E}[I_{\omega}] =
	\gamma\sigma^2Lm_1[V],\]
	where $m_1[V]$ is the mean of the volume (and hence also the
	mean of each projection $I_{\omega}$).
	\item For term (7), if $\Delta\mb i_1 \neq \mb 0$ then once again
	this term vanishes, whereas if $\Delta\mb i_2 = \mb 0$ then it becomes
	\[ \frac{1}{M^2}\sum_{\mb i}\xi(\mb i)^2\II(\mb i + \Delta\mb
	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
		i}\xi_{\omega}(\mb i)^2I_{\omega}(\mb i + \Delta\mb i_2) \to
	\gamma\sigma^2Lm_1[V].\]
	Similarly, term (8) vanishes if $\Delta\mb i_2\neq \mb 0$ and
	converges to $\gamma\sigma^2Lm_1[V]$ otherwise.
\end{itemize}
Thus, we conclude that
\[ m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) \to \gamma\langle
m_3[I_{\omega}](\Delta\mb i_1, \Delta\mb i_2)\rangle_{\omega} +
\gamma\sigma^2Lm_1[V]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big).\]
Note that in practice, we have $m_1[\II+\xi] \to m_1[\II] \approx \gamma
Lm_1[V]$ since the noise has zero mean, so we do not need prior knowledge of $\gamma$ to effectively
debias the bispectrum.

\subsection{Expansion in PSWFs}
In practice, we compute the moments of our noisy micrograph in a
product basis of 2D prolates, so we need to derive the expansion
coefficients of the above bias terms in these functions for debiasing.

To this end, writing (in the continuous case again)
\[ \delta(\Delta\rr_1 - \Delta\rr_2) =
\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Delta\rr_1)
\overline{\psi_{k,q_2}(\Delta\rr_2)},\]
we get
\[\begin{aligned}
\mathfrak{d}(k,q_1,q_2) &= \int_{\Delta\rr_1,
	\Delta\rr_2}\delta(\Delta\rr_1-\Delta\rr_2)\overline{\psi_{k,q_1}(\Delta\rr_1)}\psi_{k,q_2}(\Delta\rr_2)\\
&=
\int_{\Delta\rr_2}\overline{\psi_{k,q_1}(\Delta\rr_2)}\psi_{k,q_2}(\Delta\rr_2)\\
&= \delta_{q_1,q_2}.
\end{aligned}\]

Similarly, writing
\[ \delta(\Delta\rr_1) =
\sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
\psi_{k,q_1}(\Delta\rr_1) \overline{\psi_{k,q_2}(\Delta\rr_2)},\]
we get
\[\begin{aligned} 
\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Delta\rr_1,
	\Delta\rr_2}\delta(\Delta\rr_1)\overline{\psi_{k,q_1}(\Delta\rr_1)}
\psi_{k,q_2}(\Delta\rr_2)\\
&= \overline{\psi_{k,q_1}(\mb 0)}
\int_{\Delta\rr_2}\psi_{k,q_2}(\Delta\rr_2)\\
&= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
&= \delta_{k,0} \frac{\alpha_{0,q_2}}{2\pi}R_{0,q_1}(0)R_{0,q_2}(0),
\end{aligned}\]
where we used the fact that $R_{0,q}$ satisfies
\[ \frac{\alpha_{0,q}}{2\pi}R_{0,q}(r) =
\int_0^1R_{0,q}(\rho)J_{0}(cr\rho)\rho\, d\rho,\]
where $J_k$ is the Bessel function of the first kind, and that
$J_0(0)=1$. 
A similar derivation applies to $\delta(\Delta\rr_2)$.

Thus, in terms of the prolate expansion coefficients, our bias
formulas become
\[ \widetilde{\mathfrak{m}}_3(k,q_1,q_2) = \mathfrak{m}_3(k,q_1,q_2) +
\sigma^2m_1[\widetilde \II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].\]

Similarly, for the power spectrum we get
\[ \widetilde{\mathfrak{m}}_2(q) = \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0).\]

\end{document}

### 2018-07-24 2D_PR5/example.m

@@ -3,10 +3,10 @@ close all;
 clc;
 
 seed_rng = rng('shuffle');
-
-if isempty(gcp('nocreate'))
-    parpool(72,'IdleTimeout', 240);
-end
+% 
+% if isempty(gcp('nocreate'))
+%     parpool(72,'IdleTimeout', 240);
+% end
 
 %% Defining the problem
 
@@ -46,7 +46,7 @@ X_N = imresize(X_N, [L, L]);
 X_N = X_N - mean(X_N(:));
 X_init = zeros(W);
 X_init(1:L,1:L) = X_N;
-
+X_init(1:L,1:L) = rand(L)-1/2;
 %% Generate the micrographs and collect their moments
 
 %m_eff = zeros(n_micrographs, 1);

### 2018-07-26 TEX/draft3.tex
Anything

@@
 \usepackage{subcaption}
+\usepackage{caption}
 \usepackage{mathtools} 
 \usepackage[margin=1.2in]{geometry}
+
+\newcommand{\LL}{\mathcal{L}}
+\newcommand{\E}{\mathbb{E}}
+\newcommand{\I}{\mathcal{I}}
+\newcommand{\ep}{\varepsilon}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\GCD}{\mathbf{GCD}}
+\newcommand{\XX}{\mathcal{X}}
+\newcommand{\SUM}{\text{sum}}
+\newcommand{\1}{\mathbf{1}}
 
@@
 \paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure to several subroutines. 
-The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2-D tomographic projections of the samples from the noisy micrograph.
-The output of ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
+All contemporary methods in the field split the reconstruction procedure into several subroutines. 
+The first step in the pipeline is  known as \emph{particle picking}, in which one identifies the locations of the 2-D tomographic projections of the samples embedded within the noisy micrograph.
+The output of an ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
 This series of images
@@
 Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+Nowadays, it is also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
 
-The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
+The significance of  model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+In this experiment, the image of Einstein is correlated with multiple images of pure white noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+In~\cite{shatsky2009method}, it was shown that with merely  1000 such noisy images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
 With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
@@
 In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-This true in general to any method which is based on template matching.
+This is true in general for any method which is based on template matching.
+\TODO{TB: Do we have a nice experiment to exemplify the phenomenon?}
 
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein}
-		\caption{\label{fig:Einstein}Einstein image (template)}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
-		\caption{$n = 10$}
-	\end{subfigure}
-	\begin{subfigure}[h]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
-		\caption{$n = 10^2$}
-	\end{subfigure}
+%\begin{figure}[h!]
+%	\centering
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein}
+%		\caption{\label{fig:Einstein}Einstein image (template)}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
+%		\caption{$n = 10$}
+%	\end{subfigure}
+%	\begin{subfigure}[h]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
+%		\caption{$n = 10^2$}
+%	\end{subfigure}
 
-	\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
-	\caption{$n = 10^3$}
-\end{subfigure}%
-\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
-	\caption{$n = 10^4$}
-\end{subfigure}
-\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
-	\caption{$n = 10^5$}
-\end{subfigure}
+%	\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
+%	\caption{$n = 10^3$}
+%\end{subfigure}%
+%\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
+%	\caption{$n = 10^4$}
+%\end{subfigure}
+%\begin{subfigure}[h]{0.3\textwidth}
+%	\centering
+%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
+%	\caption{$n = 10^5$}
+%\end{subfigure}
 
-	\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
+%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
 As a template, we used Einstein's image of size $50\times 50$ pixels.
@@
 
-\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims to show that estimating a particle 
+\paragraph{Simplified model for SPR.} In this paper, we present a preliminary study that aims to show that estimating a particle 
 directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
@@
 Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
-Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$ presented in Figure~\ref{fig:Einstein}. 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
 The left panel shows the data without noise.
-In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
+In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added.
+At this noise level, Einstein's locations are still easily identified.
 In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
@@
 This phenomenon is explained in detail in Appendix~\ref{sec:theory}.
+\TODO{WL: I think this example should go in the previous section on particle picking.
+The main issue we're trying to overcome is when detection is impossible; the fact that we don't use a template seems to be an additional advantage of our method, but not the main selling point.
+So I think the impossibility of detection in sufficiently low SNR must be emphasized earlier.}
 
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
-Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein; see Figure~\ref{fig:Einstein}.}
+RR	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
 \end{figure}
@@
 In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-In a nutshell, the method consists of two stages.
+The method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
@@
 This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
+As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendices~\ref{sec:related_literature} and~\ref{sec:theory}  for more details).
 
@@
 An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of  $49$ pixels between the images in each direction.
+Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of at least $49$ pixels between the images in each direction.
 From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
-Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
+Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix}.
 
 As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect of Figure~\ref{fig:EinsteinFromNoise}.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similar to the ``Einstein from noise'' effect.
 However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
@@
 As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
-\TODO{Few comments: 1.
+\TODO{TB: Few comments: 1.
 We have a movie in the supplementary material.
@@
 Does the error also have the right slope?
-3.
-We can put more images to exemplify the progress 4.
+We'll know once we'll gather enough micrographs 3.
 Need to improve the micrograph's generation code  }
@@
 	\centering
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.3\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{Newton}
+		\includegraphics[scale=0.35]{Newton}
 		\caption{\label{fig:newton}Newton  (model)}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.3\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction2}
-		\caption{\small $P =1024$}
+		\includegraphics[scale=0.35]{reconstruction1}
+		\caption{\small $P = 512$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+	\begin{subfigure}[h]{0.3\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction20}
-		\caption{$P = 1024\times 10$}
+		\includegraphics[scale=0.35]{reconstruction10}
+		\caption{$P = 512\times 10$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.25\textwidth}
+
+	\begin{subfigure}[h]{0.3\textwidth}
 		\centering
-		\includegraphics[scale=0.3]{reconstruction200}
-		\caption{$P = 1024\times 100$}
+		\includegraphics[scale=0.35]{reconstruction100}
+		\caption{$P = 512\times 100$}
 	\end{subfigure}%
+	\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.35]{reconstruction200}
+	\caption{$P = 512\times 200$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.35]{reconstruction840}
+	\caption{$P = 512\times 840$}
+	\end{subfigure}%
+
 	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.
-We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
-The signal's estimation RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
-The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
-\TODO{Can add more images to exemplify the progress}}
+The RRR algorithm is initialized with the image of the physicist Issac Newton in the upper-left panel.
+We show estimations of Einstein using $P$ number of micrographs, each containing $700$ image occurrences on average with an $\SNR$ of $1/20$.
+The signal's estimation RMSE is  $0.5874, 0.3731, 0.2517, 0.2137, 0.1534$.
+The power spectrum estimation RMSE is $0.0381, 0.012, 0.0038, 0.0027, 0.0013$.
+}
 \end{figure}
@@
 \end{equation}
-where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-These ratios present the {density} of the the signals in the data.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
+where $M_i$ is the number of times signal $x_i$  occurs, $L$ is the length of each signal and $N$ is the micrograph length.
+These ratios $\gamma_i$ represent the {density} of the the signals in the data.
+In the 1-D experiment, we do not assume knowledge of either the ratios $\gamma_i$ or the noise level $\sigma$.
 
-In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
+In order to estimate the signals, we compute the first three autocorrelation functions of the data and then estimate the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
+As can be seen, given enough signal occurrences, we can estimate the signals accurately. 
 The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-\TODO{1.
-We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
+\TODO{TB: 1.
+Figure~\ref{fig:1Dheterosignals} will be replaced  with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
 2.
@@
 The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
-\TODO{The program still runs so these figures will be extended to the right (more micrographs).}}
+\TODO{TB: The program continues running so these figures will be extended to the right (more micrographs).}}
 \end{figure}
@@
 	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
-	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
+	\caption{An experiment for estimating three one-dimensional signals simultaneously with noise level $\sigma=3$.
 Red signals are the ground truth (targets) and the blue signals are our estimations.
@@
 The $\SNR$ is $1/12$.
-\TODO{1.
-to replace with a ``progress'' plot 2.
-replace the triangle signal 3.
-add error progress figure}}
+\TODO{TB: 1.
+We will replace the figure with ``progress'' plots 2.
+Need to replace the triangle signal 3.
+Need to add error curves}}
 	\label{fig:1Dheterosignals}
@@
 
-All current algorithmic pipeline for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
+All current algorithmic pipelines for SPR using cryo--EM start with a particle picking stage to detect the 2-D tomographic projections of the samples in the micrograph.
+The particle picking  algorithms tend to be prone to model bias and cannot work reliably on small particles in low $\SNR$ environment. 
+Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge about the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
 Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
@@
 In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
-While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
+While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems. As an alternative, we propose to use an autocorrelation analysis technique. 
+Methods based on autocorrelation analysis require only one pass over the data and therefore are usually computationally efficient. \TODO{TB: Do we want to mention Kam's method?}
+%This property has been exploit before  for  ab inito modeling assuming ideal particle picking~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
+That being said, the SPR model is far more complicated than the model presented here. In future research, we hope to bridge this gap.
 
@@
 First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
-Second, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
-This separation can be induced by careful experimental design \TODO{???}. 
-If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
+Second, we assumed that the signal occurrences are all separated by the length of the signal; see~\eqref{eq:spacing}. 
+This separation can be induced by careful experimental design \TODO{TB: ???}. 
+If the signals are not separated, one can introduce additional parameters that model the distribution of the spacing  between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
 It is yet to be studied under what conditions on this distribution one can estimate the signals.
@@
 
-\paragraph{Mathematical model}
+\paragraph{Mathematical model.}
 
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
+Let $x_1,\ldots,x_K\in\RL$ be the target signals and let $y\in\RN$ be the observed data. 
 The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
@@
 
-\paragraph{Aperiodic autocorrelation functions}
+\paragraph{Aperiodic autocorrelation functions.}
 %\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
@@
 \end{align}
-where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
+where the values of $z$ outside the indices $0, \ldots, L-1$ are taken to be zero.
 Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
@@
 
-\paragraph{Estimating the autocorrelation function of a single signal}
+\paragraph{Estimating the autocorrelation function of a single signal.}
 
 We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$ as will be shown next.
+The main principles carry through for $K>1$, as will be shown next.
 
 %In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
+For the purpose of the analysis, we consider  the asymptotic regime where $M$ grows proportionally to $N$. 
 Specifically, we define the ratio of the measurement occupied by  the signal as
@@
 \end{equation}
+\TODO{WL: $\gamma$ should really be the limit of this ratio as $N$ grows to infinity; for any finite value of $N$ this ratio may be different.
+TB: The accurate definition is given in~\eqref{eq:gamma_limit}.
+We may want to leave it as is here.}
 Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
@@
 
-\paragraph{Estimating the autocorrelation function of a multiple signals}
+\paragraph{Estimating the autocorrelation function of a multiple signals.}
 
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
+As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K$ grow proportional to $N$ and define
 \begin{align}
@@
 
-\paragraph{Numerical experiments details}
+\paragraph{Numerical experiments details.}
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations (see Figure~\ref{fig:Einstein}), while keeping the separation condition~\eqref{eq:spacing}.  
+In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations, while keeping the separation condition~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far. In average, $700$ images were placed in each micrograph.   
-Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
+an accept/reject rule based on the separation constraint and locations picked so far. On average, $700$ images were placed in each micrograph.   
+Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added, inducing an $\SNR$ of approximately $1/20$.
+A piece of one such micrograph is presented in the right panel of Figure~\ref{fig:micro_example}.
 %Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
@@
 
-In this experiment, we assume to know the number of Einstein's occurrences and the noise level. 
-In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines  almost all images  uniquely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
-Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, in the cost of one  FFT per micrograph.
-To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by
+In this experiment, we assume the knowledge of the number of Einstein's occurrences and the noise level. 
+In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines   the image  almost surely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
+Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, at the cost of one  FFT per micrograph.
+To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by~\cite{elser2017matrix}
 \begin{equation}
-z \rightarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
+z \rightarrow z + P_2(2P_1(z) - z) - P_1(z).
 \end{equation}
-where we set $\beta=1$.
-RRR estimates a $2L\times 2L$ image.
-Exact solution contains Einstein's image in the upper-left corner and zero else where.
+The RRR algorithm estimates a $2L\times 2L$ image and the exact solution contains Einstein's image in the upper-left corner and zero elsewhere.
 The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
 The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-In order to compare the performance in multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
-While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{Note the last two sentences!}.
+In order to compare the performance across multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
+While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{TB: Note the last two sentences!}.
 
@@
 In this experiment, we computed the first three autocorrelation functions. 
-We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
+We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the terms depending on $\sigma$ (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$. 
+%In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
 
-To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
+To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their number of occurrences simultaneously:
 \begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2  \\ +w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
 \label{eq:optim1D}
@@
 
- Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+ Setting $W = L$  is problematic because the above optimization problems appears to have numerous poor local optimizers.
 %Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
@@
 This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest the measured ones in the sense of~\eqref{eq:optim1D}.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest to the measured ones in the sense of~\eqref{eq:optim1D}.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows enforcement of the positivity constraints \TODO{reference} on the coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to evaluate it and its derivatives.
 
@@
 
-\section{Autocorrelation estimations} \label{sec:autocorrelation_computation}
+\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}
 
 Throughout the proof, we consider the case of one signal $K=1$.
-The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriates weights, see~\cite{boumal2017heterogeneous}.
+The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
 
-Let us define
-\begin{equation}
+We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this. We assume $M_N$ grows proportionally with $N$, and define:
+%
+\begin{equation} \label{eq:gamma_limit}
 \gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
 \end{equation}
-With a bit abuse of notation, $M_N$ stresses that $M$ is a function of $N$. Indeed, by assuming $M_N=\Omega(N)$, we deduce $\gamma>0$.
-We start by considering the first autocorrelation of the data
+%
+We will assume that $M_N=\Omega(N)$, so that $\gamma>0$. In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
+
+We start by considering the mean of the data:
+%
 \begin{equation}
-a_y^1 = \sum_{i=0}^{N-1} y[i] = \frac{1}{N/L}\sum_{j=0}^{M_N-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}} \xrightarrow{a.s.}\gamma a_x^1,
+a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
+\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
+\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
+\xrightarrow{a.s.}\gamma a_x^1,
 \end{equation}
-where the noise term converges to zero almost surely (a.s.) by the law of large numbers.
+%
+where the noise term converges to zero almost surely (a.s.) by the strong law of large numbers.
 
-We proceed with the second autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+%
+
+\begin{align}
+%
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
+\nonumber \\
+& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
++ \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}.
+%
+\end{align}
+
+The cross-terms are linear in the noise, and are easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
+As for the signal term, we break it into $M$ different sums, each containing one copy of the signal.
+This gives:
+%
+\begin{equation} \label{eq:2nd_moment_signal_term}
+%
+\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
+%
+\end{equation}
+%
+
+We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
+%
 \begin{equation}
-\begin{split}
-a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
-& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
-\end{split}
+%
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+%
 \end{equation}
-where the cross terms between the signal and the noise vanish  almost surely in the limit $N\to\infty$.
-
-We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
-\begin{equation} \label{eq:2nd_moment_signal_term}
-\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
-\end{equation}
-Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
+%
+Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
+If $\ell=0$, then we have:
+%
 \begin{equation}
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-\end{equation}
-Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
-If $\ell=0$, 
-\begin{equation}
+%
 \frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
+%
 \end{equation}
 
-We are now moving to analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
-\begin{equation*}
-a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
-\end{equation*}
+We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
+%
+\begin{align}
+%
+&a_y^3[\ell_1,\ell_2] 
+= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+\nonumber \\
+%
+=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
++ \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%
+\end{align}
+%
+Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
+Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_1$.
+
+{\bf Case 1:} $0 < \ell_2 < \ell_1$.
+Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
+Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
+
+{\bf Case 2:} $0=\ell_2 < \ell_1$.
+Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
+The same argument as for Case 1 shows that (3) and (5) also converge to 0.
+For term (4), we write:
+%
+\begin{align}
+%
+&\frac{1}{N}\sum_{j=1}^{M} 
+\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
+\nonumber \\
+&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
+\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
+%
+\end{align}
+
+{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
+
+{\bf Case 4:} $0=\ell_2 = \ell_1$.
+The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
+Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
+
+This completes the proof of \eqref{eq:data_ac}.
+
+\begin{comment}
 Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
@@
 
-\paragraph{Expectation-maximization.}
-Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-In particular, in each iteration, EM assigns a probability to any feasible combination of positioning the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations.
-
 \paragraph{Open theoretical questions.}
 
-The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
-In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
-On the contrary, the required number signal occurrences using the autocorrelation analysis should scale like $1/\SNR^d$  to retain a constant estimation error.
-Accordingly, in our  method, $M$ must scale like $1/\SNR^3$.
-We believe that similarly to the closely-related problem of multirefrence alignment~\cite{perry2017sample,abbe2017multireference}, this estimation rate is optimal in the low $\SNR$ regime.
+Our method of estimating $x$ uses the third-order moments of the observations.
+These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
+Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error.
+In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
 
-Another interesting question is how many signals can be demixed from the autocorrelation functions.
+Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
+In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
+In~\cite{weinthesis}, this result is shown theoretically for a different, and much less efficient, algorithm.
+In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
+
+%%%That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
+
+%%% We conjecture that similarly to the
+
+%%%In methods which are based on detection and averaging, the number of signals occurrences  must scale like $1/\SNR$.
+
+\begin{comment}
+
+Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
 For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.

### 2018-07-26 TEX/draft4.tex
Anything

--- 2018-06-07 TEX/draft4.tex
@@
 \usepackage{subcaption}
+\usepackage{caption}
 \usepackage{mathtools} 
@@
 \newcommand{\one}{\mathbf{1}} 
-\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
+\newcommand{\SNR}{{\textsf{SNR}}}
 
@@
 
-\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
-%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
-%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
-% 
-In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
+Single particle reconstruction (SPR) using cryo--electron microscopy (cryo--EM) is an innovative technology for reconstructing the 3-D structure of macromolecules. In recent years, structures
+of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
+This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.
+
+In a cryo--EM experiment, multiple biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice.
 Within the ice, the molecules are randomly oriented and positioned.
-The microscope produces a 2-D image of the samples embedded in the ice called a \emph{micrograph}.
-Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
-The goal is to construct 3-D models of the molecules from the micrographs.
-
-The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors.
-On the one hand, the $\SNR$ is a function of the electron dose.
-To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the $\SNR$ is a function of the molecule size.
-The smaller the molecules, the fewer detected electrons carry information about them.
-
-%\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure in several stages.
-The first stage consists in extracting the various particle projections from the micrographs.
-This is called \emph{particle picking}.
-Later stages aim to construct a 3-D model of the molecule from these projections.
-The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-As can be seen from Figure~\ref{fig:micro_example}, locating the particles becomes increasingly challenging as the $\SNR$ degrades.
-
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in a highly cited paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{quote}
-	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-\end{quote}
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.
-%This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
-\TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
-As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis, as the particles themselves cannot be picked from the micrographs.
-%
-%\TODO{either here, or in a close neighborhood of this paragraph you should mention the advances that the field has made in recent years towards reconstruction of small size molecules: mention Volta phase plate and the scaffolding cage (and cite the papers I sent you).}
-This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%
-%
-Despite this progress, detecting small molecules (below 50 kDa) in the micrographs remains a challenge.
-We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
-Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
-\TODO{Need a ref for this claim.}
-
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-%This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
-\TODO{For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
-In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
-To overcome low $\SNR$s, the ratio of data to parameters must increase.
-This is impossible if the number of parameters grows with the amount of data collected, but not so if the number of parameters remains fixed.
-Simply put, the key is to bypass the particle picking stage.}
-%%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
-%%Indeed, the signal itself (the many different views of the molecule) is still present in the micrograph: 
-%Indeed, in principle at least, the micrograph does contain the necessary information (several views of the molecule(s) of interest).
-While we may not be able to locate these views, we may still be able to extract the relevant information through other means.
-Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.
-
-%\TODO{Paragraph about the simplified model}
-As a proof of concept, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
-%Figure~\ref{fig:Einst_example} displays the results of our method, detailed in Section~\ref{sec:results}.
-A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
-To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
-Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
-We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In order to recover the planted image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the planted image.
-%To do so, we assume the image occurrences are well separated.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided individual occurrences of the image are well separated and the image appears sufficiently many times in the micrographs.
-Importantly, there is no need to detect individual occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the image.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares or a phase retrieval algorithm; see Figure~\ref{fig:Einst_example} for an illustration and Section~\ref{sec:methods} for details.
-As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see Appendix~\ref{sec:theory} for a discussion.
-
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{vanheel1992correlation,shatsky2009method,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
-In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
-This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates are required, thus significantly reducing concerns about model bias.
-
-%\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
-
-%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion
-
-%\clearpage
+Then, the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice.
+The micrograph is dominated by noise due to the small electron doses that
+can be applied to the specimen without causing radiation damage.
+The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or, typically, several micrographs).
+
+\paragraph{Particle picking.}
+All contemporary methods in the field split the reconstruction procedure into several subroutines. 
+The first step in the pipeline is  known as \emph{particle picking}, in which one identifies the locations of the 2-D tomographic projections of the samples embedded within the noisy micrograph.
+The output of an ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
+This series of images
+is then used to estimate the structure.
+
+Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
+However, most of these procedures are prone to \emph{model bias}.
+For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
+Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
+Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it is also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+
+The significance of  model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+In this experiment, the image of Einstein is correlated with multiple images of pure white noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+In~\cite{shatsky2009method}, it was shown that with merely  1000 such noisy images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
+With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
+With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
+Crucially, the more noisy images we use, the more severe the model bias towards the template.
+In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
+This is true in general for any method which is based on template matching.
+\TODO{TB: Do we have a nice experiment to exemplify the phenomenon?}
 
@@
 
-%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-%As a result, the projections in the 2-D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
+Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
+As a result, the projections in the 2D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
 %In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
 
-%\paragraph{Simplified model for SPR}
-
-%In this paper, we present a preliminary study that aims to show that estimating a particle 
-%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
-
-%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
+\paragraph{Simplified model for SPR.} In this paper, we present a preliminary study that aims to show that estimating a particle 
+directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
+
+In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
 Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
+A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
+To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
 We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
-\begin{figure}[t]
+Figure~\ref{fig:micro_example} shows a simple example of our problem with  one signal ($K=1$). 
+Each panel demonstrates an image of size $250\times 250$, containing 4 occurrences of an Einstein image of size $50\times 50$. 
+The left panel shows the data without noise.
+In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added.
+At this noise level, Einstein's locations are still easily identified.
+In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
+In the right panel, we show the same data swamped in
+i.i.d.\ Gaussian noise with standard deviation  $\sigma=3$.
+Clearly, identifying the locations of Einstein in this micrograph is much more challenging. In fact, it can be shown that in the low signal--to--noise (\SNR) regime, 
+detection  of individual image occurrences is impossible---even if the true image is known---and therefore particle picking is impossible.
+This phenomenon is explained in detail in Appendix~\ref{sec:theory}.
+\TODO{WL: I think this example should go in the previous section on particle picking.
+The main issue we're trying to overcome is when detection is impossible; the fact that we don't use a template seems to be an additional advantage of our method, but not the main selling point.
+So I think the impossibility of detection in sufficiently low SNR must be emphasized earlier.}
+
+\begin{figure}[h!]
 	\centering
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each micrograph contain the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
-In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known.
-By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
+RR	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
+Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
 \end{figure}
 
-%\paragraph{Autocorrelation analysis.}
-%We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
-%In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-%In a nutshell, the method consists of two stages.
+\paragraph{Autocorrelation analysis.}
+We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
+In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
+The method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
@@
 There is no need to detect individual occurrences.
-%In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
-%This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
-
-%\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-%In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-%In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
-%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
-With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
-Crucially, the more noisy images we use, the more severe the model bias towards the template.
-%In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-%This true in general to any method which is based on template matching.
-%\TODO{Do we have a nice experiment to exemplify the phenomenon?}
-
-\section{Results} \label{sec:results}
-
-%\TODO{Results: What answer was found to the research question; what did the study find? Was the tested hypothesis true?}
-
-%To support the claim that it may be possible to bypass particle picking in SPR from micrographs, as a proof of concept,
-We conducted two experiments in the simplified image formation model described in the introduction:
-\begin{enumerate}
-	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
-This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
-	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
-\end{enumerate}
-As outlined below, we find that it is indeed possible to recover good estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
-Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
-The methods section provides additional details.
-In the discussion section, we outline how the general approach could be extended to full 3D SPR.
-
-%In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
-A micrograph contains, on average, 700 occurrences of the target image at random locations.
-The latter are chosen so that two occurrences are always separated by at least 49 pixels.
-Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
-This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
-In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.
-
-We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra).
-This is a particularly simple computation.
-In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself.
-Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{bauschke2004rrr,elser2017rrr}.
-RRR is initialized with a picture of the physicist Isaac Newton and iterates to produce the estimate, up to a reflection ambiguity.\footnote{\TODO{Initializing with a face is debatable: it might help the algorithm.
-On the other hand, I agree that it supports the notion that we don't get trapped too easily.}}
-
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs.
-(A movie is available in \TODO{supplementary material}.) Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-
-%defined as 
-%\begin{equation}
-%\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
-%\end{equation} 
-%where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
-%\TODO{We have a movie in the supplementary material.}
-
-%%%% This is about bias, and it's imprecise; let's leave it out?
-%As an initial guess, we picked an image of the physicist Issac Newton.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
+In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
+This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
+As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendices~\ref{sec:related_literature} and~\ref{sec:theory}  for more details).
+
+\section{Results}
+
+In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
+
+In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ ($\SNR=1/20$).
+An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
+Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of at least $49$ pixels between the images in each direction.
+From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
+Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix}.
+
+As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similar to the ``Einstein from noise'' effect.
+However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
+
+Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of recorded micrographs.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
+To measure the error, we use the root mean square error (RMSE) defined as 
+\begin{equation}
+\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
+\end{equation} 
+where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
+As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
+\TODO{TB: Few comments: 1.
+We have a movie in the supplementary material.
+2.
+Does the error also have the right slope?
+We'll know once we'll gather enough micrographs 3.
+Need to improve the micrograph's generation code  }
 
@@
 	\centering
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1_cropped}
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{Newton}
+		\caption{\label{fig:newton}Newton  (model)}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{reconstruction1}
 		\caption{\small $P = 512$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction10_cropped}
-		\caption{\small $P = 512\times 10$}
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{reconstruction10}
+		\caption{$P = 512\times 10$}
 	\end{subfigure}%
 
-		\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction100_cropped}
-		\caption{ \small $P = 512\times 10^2$ }
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{reconstruction100}
+		\caption{$P = 512\times 100$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1000_cropped}
-		\caption{\small $P = 512\times 10^3$}
+	\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.35]{reconstruction200}
+	\caption{$P = 512\times 200$}
 	\end{subfigure}%
-
-%	\begin{subfigure}[h]{0.33\textwidth}
-%		\centering
-%		\includegraphics[scale=0.33]{Einstein_progress_cropped}
-%		\caption{\label{fig:err_curve}\small Error curve}
-%	\end{subfigure}%
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Newton}
-%		\caption{\label{fig:newton}Newton  (model)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction2}
-%		\caption{\small $P =1024$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction20}
-%		\caption{$P = 1024\times 10$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction200}
-%		\caption{$P = 1024\times 100$}
-%	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.---\TODO{Will add image with $P=512\times 10^4$ and image of Newton.}
-		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
+	\begin{subfigure}[h]{0.3\textwidth}
+	\centering
+	\includegraphics[scale=0.35]{reconstruction840}
+	\caption{$P = 512\times 840$}
+	\end{subfigure}%
+
+	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
+The RRR algorithm is initialized with the image of the physicist Issac Newton in the upper-left panel.
+We show estimations of Einstein using $P$ number of micrographs, each containing $700$ image occurrences on average with an $\SNR$ of $1/20$.
+The signal's estimation RMSE is  $0.5874, 0.3731, 0.2517, 0.2137, 0.1534$.
+The power spectrum estimation RMSE is $0.0381, 0.012, 0.0038, 0.0027, 0.0013$.
 }
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
 \end{figure}
@@
 
-In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy.
-Any two occurrences are separated by at least 20 entries.
-The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion.
-The micrograph is then contaminated with additive white Gaussian noise.
-This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
-Neither the number of occurrences nor the noise level $\sigma$ are known.
-
-In the methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
-The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
-
-Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the signal occurrences, the individual signals can be estimated accurately given enough data.
-Furthermore, the propensity of each signal can also be estimated.
-
-%In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-%As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
-%The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-
+Results from a similar experiment with three ($K=3$) one-dimensional signals are presented in Figure~\ref{fig:1Dheterosignals}.
+ We define the ratio of the space occupied by the $i$th signal as 
+\begin{equation}
+\gamma_i = \frac{M_i L}{N},
+\end{equation}
+where $M_i$ is the number of times signal $x_i$  occurs, $L$ is the length of each signal and $N$ is the micrograph length.
+These ratios $\gamma_i$ represent the {density} of the the signals in the data.
+In the 1-D experiment, we do not assume knowledge of either the ratios $\gamma_i$ or the noise level $\sigma$.
+
+In order to estimate the signals, we compute the first three autocorrelation functions of the data and then estimate the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
+As can be seen, given enough signal occurrences, we can estimate the signals accurately. 
+The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
+\TODO{TB: 1.
+Figure~\ref{fig:1Dheterosignals} will be replaced  with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
+2.
+We may want to replace the triangle signal}
 %We do not assume the knowledge of the noise level. 
 %Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.7]{Einstein_progress}
+\caption{\label{fig:error_per_micro} The left panel shows the RMSE of estimating the power spectrum of the signal from the data as a function of the number of  collected micrographs.
+As expected, the curve is linear with slope $-1/2$ in logarithmic scale.
+The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
+\TODO{TB: The program continues running so these figures will be extended to the right (more micrographs).}}
+\end{figure}
+
 %
@@
 	\centering
-	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations.) The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
-Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
-With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
-%		
-%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
+	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
+	\caption{An experiment for estimating three one-dimensional signals simultaneously with noise level $\sigma=3$.
 Red signals are the ground truth (targets) and the blue signals are our estimations.
@@
 The $\SNR$ is $1/12$.
-\TODO{1.
-to replace with a ``progress'' plot 2.
-replace the triangle signal 3.
-add error progress figure}
-	}
+\TODO{TB: 1.
+We will replace the figure with ``progress'' plots 2.
+Need to replace the triangle signal 3.
+Need to add error curves}}
 	\label{fig:1Dheterosignals}
@@
 
-\clearpage
 \section{Discussion}
 
-%\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
-
-%All current algorithmic pipelines for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-%Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
+All current algorithmic pipelines for SPR using cryo--EM start with a particle picking stage to detect the 2-D tomographic projections of the samples in the micrograph.
+The particle picking  algorithms tend to be prone to model bias and cannot work reliably on small particles in low $\SNR$ environment. 
+Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge about the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
 Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
 
-In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
-Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
-
-The same general approach can, in principle, be applied directly to SPR from cryo-EM.
-Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) under unknown viewing directions.
-The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
-Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients.
-Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients.
-Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
-
-We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume at resolution comparable to that of the particle projections.
-This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
-Additional parameters in these equations could encode an unknown non-uniform viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
-Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
-As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
-Concerns for model bias would also greatly be reduced.
-
-%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here.
-In a future research, we hope to bridge this gap.
-
-Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
-
-One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
-Still, large amounts of data also imply large amounts of computations.
-On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in streaming mode, as only one look at each micrograph is necessary.
-The output of this data processing stage is a succinct summary in the form of autocorrelation estimates.
-Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an all important question then is whether the equations can be solved meaningfully in practice.
-The proof-of-concept experiments above suggest they might.
-
-%Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
-The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
-At the time, such approaches also seemed challenging.
-
-%\TODO{Do we want to say something about the number of images that we need?
-Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
-(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
-
-Beyond data acquisition and computational challenges, there are modeling issues to consider.
-As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
-First, we assume an additive white noise model, while in practice the noise may be structured or signal dependent.
-To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly.
-Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals.
-Perhaps this separation could be induced by careful experimental design \TODO{?}.
-Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
-Here as well, relations between autocorrelation functions of the data and of the signals can be derived.
-%Each variation leads to a different inverse problem. No sufficient conditions for them to be solvable are currently known.
-
-\TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION?
-Do we also want to stress that models have been refined over decades?
-Both points are rather defensive in nature.	}
-
-\TODO{Should we discuss CTF? Where, and to what extent?}
-
-\TODO{Where and how do we cite Kam? Fred?}
+In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
+While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems. As an alternative, we propose to use an autocorrelation analysis technique. 
+Methods based on autocorrelation analysis require only one pass over the data and therefore are usually computationally efficient. \TODO{TB: Do we want to mention Kam's method?}
+%This property has been exploit before  for  ab inito modeling assuming ideal particle picking~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
+That being said, the SPR model is far more complicated than the model presented here. In future research, we hope to bridge this gap.
+
+Our results rely on two core assumptions that are not necessarily met by an SPR experiment.  
+First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
+Second, we assumed that the signal occurrences are all separated by the length of the signal; see~\eqref{eq:spacing}. 
+This separation can be induced by careful experimental design \TODO{TB: ???}. 
+If the signals are not separated, one can introduce additional parameters that model the distribution of the spacing  between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
+It is yet to be studied under what conditions on this distribution one can estimate the signals.
 
@@
 
-We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
-For ease of exposition, we do so in the 1-D case.
-Extension to the 2-D case is straightforward.
-We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple shorter micrographs concatenated into one.)
-The forward model (or ``image'' formation model) is as follows.
-For each target signal $x_k$, an unknown binary signal $s_k \in \{0, 1\}^{N-L+1}$ indicates (with 1's) the starting positions of all occurrences of $x_k$ in $y$, so that, with additive white Gaussian noise:
-\begin{align}
-	y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
-	\label{eq:model}
-\end{align}
-where $\ast$ denotes (zero-padded) convolution. The binary signals obey the following property:
-\begin{align}
-	\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k, j), \textrm{ then } |i - j| \geq 2L-1.
-	\label{eq:spacing}
-\end{align}
-In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-
-From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
-In contrast, particle picking is the task of estimating the binary signal $s = s_1 + \cdots + s_K$, while clustering is the task of separating $s$ into its components $s_1, \ldots, s_K$.
-Neither of the latter can be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
-
-%We denote the set of these nonzero values by 
-% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
+\paragraph{Mathematical model.}
+
+Let $x_1,\ldots,x_K\in\RL$ be the target signals and let $y\in\RN$ be the observed data. 
+The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
+\begin{equation} \label{eq:model}
+y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
+\end{equation}
+%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
+The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of $x_i$'s occurrences. 
+We denote the set of these nonzero values by 
+ $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
+By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
 %Neither the $M_i$'s nor $M$ are assumed to be known.
-
-Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
-Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
-
-%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
-%\begin{align}
-%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
-%  \label{eq:spacing}
-%\end{align}
-%The goal is to estimate $x_1,\ldots,x_K$ from $y$.
+ Literature survey on blind deconvolution and related problems is given in Appendix~\ref{sec:related_literature}.
+
+In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
+\begin{equation} \label{eq:spacing}
+  \vert i-j \vert\geq L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
+\end{equation}
+The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.
 
@@
 
-\paragraph{Aperiodic autocorrelation functions}
+\paragraph{Aperiodic autocorrelation functions.}
 %\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
-
-In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+For  
+$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
 \begin{align}
-	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+	a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
 	\label{eq:ac_general}
 \end{align}
-where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
-Explicitly, the first-, second- and third-order autocorrelations are given by
+where the values of $z$ outside the indices $0, \ldots, L-1$ are taken to be zero.
+Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
 \begin{align} 
-	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+	a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
+	a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+	a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
 \end{align}
-The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-\begin{align*}
-	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-\end{align*}
-%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
+Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and also $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].$$
+%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
 
@@
 
-For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
+We first consider the problem of estimating the autocorrelations of a single signal from the data. 
+The main principles carry through for $K>1$, as will be shown next.
+
+%In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
+For the purpose of the analysis, we consider  the asymptotic regime where $M$ grows proportionally to $N$. 
+Specifically, we define the ratio of the measurement occupied by  the signal as
+\begin{equation}
+\gamma = \frac{M L}{N}.
+\end{equation}
+\TODO{WL: $\gamma$ should really be the limit of this ratio as $N$ grows to infinity; for any finite value of $N$ this ratio may be different.
+TB: The accurate definition is given in~\eqref{eq:gamma_limit}.
+We may want to leave it as is here.}
+Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+The main pillar of this work is the following simple observation.
+If the support signal $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
+to a scaled, biased, version of the signal's autocorrelation:
 \begin{align} 
-	\gamma & = \frac{M L}{N}
+\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
 \end{align}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$.
-Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$.
-The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
-\begin{align*}
-	\E\{ a_y^1 \} & = \gamma a_x^1.
-\end{align*}
-We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
-\begin{align*}
-	\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
-\end{align*}
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
-
-The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations.
-Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
-As a result,
-\begin{align*}
-	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
-\end{align*}
-for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
-The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
-Along the same lines, one can establish a relation for third-order autocorrelations:
+for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
+%These relations are proven in Appendix~\ref{sec:autocorrelation_computation}.
+
+\paragraph{Estimating the autocorrelation function of a multiple signals.}
+
+As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K$ grow proportional to $N$ and define
 \begin{align}
-	\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
-	\label{eq:data_ac_k1}
+	\gamma_k = \frac{M_k L}{N}, \quad \gamma = \sum_{k=1}^K\gamma_k.
 \end{align}
-for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
-Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
-
-\paragraph{Estimating the autocorrelation function of multiple signals.}
-
-Returning to the general case $K \geq 1$, let $M_1, \ldots, M_K$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
-\begin{align}
-	\gamma_k & = \frac{M_k L}{N}, & \gamma & = \sum_{k=1}^K\gamma_k.
-\end{align}
-As above, we consider the asymptotic regime where $M_1,\ldots,M_K,N\to\infty$ while preserving the ratios $\gamma_k$ constant.
-% 
-Still under the spacing constraint~\eqref{eq:spacing}, similarly to the developments above, one can estimate a mixture of the autocorrelations of the $K$ target signals from the autocorrelations of the micrograph:
+If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then  similarly to~\eqref{eq:data_ac_k1} one can estimate the mixture of the $K$ signals'  autocorrelations:
 \begin{align}
@@
 \end{align}
-where $\ell, \ell_1, \ell_2 = 0, \ldots, L-1$.
-The left hand side is straightforward to estimate from data: it provides a succinct summary of it.
-The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$.
-The task is to solve these polynomial equations in a robust way.
-
-%\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}
-
-\paragraph{Numerical experiment with three 1-D signals.}
-
-For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately) $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+This relation is proven in  Appendix~\ref{sec:autocorrelation_computation}.
+
+\paragraph{Numerical experiments details.}
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated $P$ micrographs of size $4096\times 4096$ pixels. 
+In each micrograph, we placed Einstein's image of size $50\times 50$  in random locations, while keeping the separation condition~\eqref{eq:spacing}.  
+This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
+an accept/reject rule based on the separation constraint and locations picked so far. On average, $700$ images were placed in each micrograph.   
+Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added, inducing an $\SNR$ of approximately $1/20$.
+A piece of one such micrograph is presented in the right panel of Figure~\ref{fig:micro_example}.
+%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+In this experiment, we assume the knowledge of the number of Einstein's occurrences and the noise level. 
+In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines   the image  almost surely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
+Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, at the cost of one  FFT per micrograph.
+To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by~\cite{elser2017matrix}
+\begin{equation}
+z \rightarrow z + P_2(2P_1(z) - z) - P_1(z).
+\end{equation}
+The RRR algorithm estimates a $2L\times 2L$ image and the exact solution contains Einstein's image in the upper-left corner and zero elsewhere.
+The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
+The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
+In order to compare the performance across multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
+While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{TB: Note the last two sentences!}.
+
+For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
+The only difference is that here, for each
+placement, one of the three signals is picked at random proportionally to the desired number
+of occurrences of each.
+In this experiment, we computed the first three autocorrelation functions. 
+We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the terms depending on $\sigma$ (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$. 
+%In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
+
+To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their number of occurrences simultaneously:
+\begin{multline}
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2  \\ +w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
+\label{eq:optim1D}
+\end{multline}
+where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
+
+ Setting $W = L$  is problematic because the above optimization problems appears to have numerous poor local optimizers.
+%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest to the measured ones in the sense of~\eqref{eq:optim1D}.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows enforcement of the positivity constraints \TODO{reference} on the coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to evaluate it and its derivatives.
+
+%For the 1D experiment, we fix $K = 3$ signals of length $L = 21$, as depicted in Figure~\TODO{ref}.
+Following the data model described in Section~\TODO{ref}, we generate an observation $y$ of length $24.6 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately) $300 \cdot 10^6$, $200 \cdot 10^6$ and $100 \cdot 10^6$ times in $y$, such that at least $L-1$ zeros separate two occurrences of any signals.
+%This is done by randomly selecting $600 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random proportionally to the desired number of occurrences of each.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting $\SNR$ of $y$
+The SNR of $y$
 % sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/9.
-
-This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+%is about 1/12.
+
+%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at random locations, uninformative of the actual locations of the signal occurrences.
 Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
@@
 %
-Given the observation $y$, we proceed to compute the autocorrelations.
-The first-order autocorrelation is straightforward.
-For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
-We have
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-coefficients in total.
-Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-\begin{align*}
-K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-\end{align*}
-Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$.
-
-In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+%Given the observation $y$, we proceed to compute the moments.
+The first-order moment is straightforward.
+For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments.
+Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ remaining moments.
+As a result, it is unnecessary to estimate $\sigma$.
+We have \TODO{TB: We may want to put this calculation is the last paragraph of Section 3.1 }
+%\begin{align*}
+%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+%\end{align*}
+%moments in total.
+In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
 Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 If multiple GPUs are available, segments can of course be handled in parallel.
-
-Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+%
+%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
 We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-\begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
-
+%\begin{multline}
+%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
+%\label{eq:optim1D}
+%\end{multline}
+%where $W \geq L$ is the length of the sought signals and \TODO{explain $w_i$'s: currently they are $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$.
+Issue is: this is not very smart..}.
 Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
+%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
+%Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ (with cyclic indexing \TODO{we should understand / explain this}) that has largest $\ell_2$-norm.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{I might need a reference for this} on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
@@
 
-%\TODO{separation}
-%
-%For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
-%The only difference is that here, for each
-%placement, one of the three signals is picked at random proportionally to the desired number
-%of occurrences of each.
-%In this experiment, we computed the first three autocorrelation functions. 
-%We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-%\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
-
-%To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
-%\begin{multline}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-%\label{eq:optim1D}
-%\end{multline}
-%where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
-
-%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
-%This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-
-\paragraph{Numerical experiment with 2-D image.}
-
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
-This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far.
-On average, $700$ images are placed in each micrograph.   
-Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
-%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-
-In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
-In start contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.\footnote{\TODO{Should we cite \cite{bendory2017fourier} here?
-I'm not against citing it somewhere, but for the specific claim being supported here, it seems the older reference should be enough.}} This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
-Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
-These can be computed highly efficiently and in parallel.
-
-To recover the target image from the estimated power spectrum, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
-\begin{align*}
-	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
-\end{align*}
-on an image $z$ of size $2L\times 2L$.
-We set the parameter $\beta$ to 1.
-The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, \TODO{possibly reflected}, and zeros elsewhere.
-The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
-The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-
-In order to compare the performance in multiple cases and at different noise levels, the algorithm is stopped after a fixed number of iterations (1000) and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
-While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
-\TODO{Note the last two sentences!}
-
 \bibliographystyle{plain}
@@
 %
-\begin{equation}
+\begin{equation} \label{eq:gamma_limit}
 \gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
@@
 The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
 
@@
 \paragraph{The impossibility of detection in low $\SNR$.}
-If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+If $x$ is known and $K=1$, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
 However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
@@
 Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
-
-\TODO{NB: This is an important point for us.
-As stated, it is imprecise.
-I like the reduction idea to $M$ windows, but then two things: (1) if we cite Aguerrebere, we need to be specific what theorem we reference and we need to check the assumptions, and (b) in any case, we need to be precise regarding what "impossible" means -- I'm guessing the result is a bit more subtle, saying something like: the probability of type I / type II error is at least this much.
-Also, someone might oppose that we don't need to get them \emph{all} right, and we don't need to get them \emph{exactly} right..
-To address such concerns, we need to be specific.
-After reading the Aguerberre paper quite carefully, one of the important points in there is that they assume a continuous model, so that shifts are continuous (that's why they can do CRBs -- CRBs are not defined for discrete problems; of course, you could define them with some work (I assume), but that's not what they did, so just referencing them doesn't cut it.}
-
-\TODO{NB: Here is a suggestion: we could further simplify the problem by having the oracle also state, for each window, that the shift is either of two possibly shifts (with 50/50 prior.) Then, knowing all of this and also knowing $x$, deciding which shift it is is a matter of deciding which Gaussian a vector came from, where both Gaussians have $\sigma^2 I$ variance and known mean.
-So, the distance test (which is equivalent to the likelihood ratio test) is optimal (that ought to be a Neyman-Pearson result).
-The probability of mistake is then at least $\frac{1}{2}\operatorname{erfc}\left(\frac{\|x_{shift 1} - x_{shift 2}\|}{2\sigma}\right)$, where $x_{shift 1}$ is a signal of the length of the given window with $x$ placed at a certain position, and zeros elsewhere.
-We can then argue that (if there is a positive lower bound on the norms up there), there always exists a sigma such that the probability of mistake is this incredibly simpler problem is still arbitrarily close to 1/2 (random chance.) having said all of that, we can then also reference Aguereberre (carefully) and make the point that, in their specific setup, they show getting a lot of images indeed helps, but not beyond a certain error level which has to do with sigma, so that for large sigma, however much data we get, we can't estimate shifts (in their setting) accurately.}
 
@@
 In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
-In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
+In~\cite{weinthesis}, this result is shown theoretically for a different, and much less efficient, algorithm.
 In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
@@
 
-\section{Stuff}
-
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
-
-\section{The autocorrelation functions in cryo--EM} \label{sec:cryoem}
-
-The 3-D Fourier transform of an L-bandlimited 3-D volume (e.g., particle) can be expanded by  spherical harmonics:
-\begin{equation} \label{eq:volume}
-\hat{V}(k,\theta,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)Y_\ell^{m}(\theta,\phi),
-\end{equation}
-where $(\theta,\phi)$ are two angles on the sphere, $k$ is the radial coordinate, $Y_{\ell}^m(\theta,\phi)$ is the spherical harmonic of degree $\ell$ and order $m$ and  $A_{\ell,m}(k)$ are the associated spherical harmonics coefficients, to be estimated.
-A rotation of the volume by $\omega\in SO(3)$ can be described using the Wigner D-function $D_{m,m'}^{\ell}$:
-\begin{equation}
-\begin{split}
-(R_\omega \hat{V})(k,\theta,\phi)  &= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)(R_\omega Y_\ell^{m})(\theta,\phi) \\
-&= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\theta,\phi).
-\end{split}
-\end{equation}
-
-By the Fourier slice theorem, each cryo--EM measurement (projection) is equivalent (through 2-D Fourier transform) to the slice of $\hat{V}$, associated with $\theta= \pi/2$, after $\hat{V}$ was rotated by $\omega\in SO(3)$.
-Explicitly, the Fourier transform of a projection from the viewing direction $\omega$ is related to the spherical harmonic coefficients of the object through:
-\begin{equation} \label{eq:P}
-\begin{split}
-P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
-\end{split}
-\end{equation}
-
-Next, we want to relate the projections $P_\omega$ with the autocorrelation functions computed from the micrograph.
-We assume the projections are sufficiently separated so that the $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is proportional to:
-\begin{equation}
-	M_2(\Delta_x, \Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y) + \textrm{bias},
-\end{equation}
-where $P_n$ denotes the $n$th projection.
-The assumption here is that $(\Delta_x, \Delta_y)$ are small enough so that, in computing the auto-correlation, points $(x, y)$ and $(x+\Delta_x, y+\Delta_y)$ do not touch distinct particles.
-By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get
-\begin{equation}
-M_2(\Delta_x,\Delta_y)\propto\sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x,y+\Delta_y)d\omega.
-\end{equation}
-In the same way and under the same conditions, the third moment is given by 
-\begin{equation} 
-M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega + \textrm{bias}.
-\end{equation}
-
-In order to determine the particle, by~\eqref{eq:volume} one needs to estimate on the order of $L^3$ spherical harmonics coefficients.
-If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides on the order of $L^4$ equations involving triple products of $P_\omega$.
-Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^4$ cubic equations in the $\sim L^3$ sought parameters.
-Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking stage.
-
 \end{document}

### 2018-07-26 TEX/draft3.tex
כובל ופ רקבםהקרט

@@
 \usepackage{subcaption}
-\usepackage{caption}
 \usepackage{mathtools} 
@@
 \paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure into several subroutines. 
-The first step in the pipeline is  known as \emph{particle picking}, in which one identifies the locations of the 2-D tomographic projections of the samples embedded within the noisy micrograph.
-The output of an ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
+All contemporary methods in the field split the reconstruction procedure to several subroutines. 
+The first step in the pipeline is the so-called \emph{particle picking}, in which one aims to detect the 2-D tomographic projections of the samples from the noisy micrograph.
+The output of ideal particle picker is a series of 2-D images, each containing one centered tomographic projection associated with an unknown viewing direction and an in-plane rotation.
 This series of images
@@
 Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it is also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
-
-The significance of  model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-In this experiment, the image of Einstein is correlated with multiple images of pure white noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-In~\cite{shatsky2009method}, it was shown that with merely  1000 such noisy images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
+Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+
+The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
+In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
+In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
 %In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
@@
 In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-This is true in general for any method which is based on template matching.
-\TODO{TB: Do we have a nice experiment to exemplify the phenomenon?}
+This true in general to any method which is based on template matching.
+\TODO{Do we have a nice experiment to exemplify the phenomenon?}
 
@@
 
-\paragraph{Simplified model for SPR.} In this paper, we present a preliminary study that aims to show that estimating a particle 
+\paragraph{Simplified model for SPR} In this paper, we present a preliminary study that aims to show that estimating a particle 
 directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
@@
 The left panel shows the data without noise.
-In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added.
-At this noise level, Einstein's locations are still easily identified.
+In the middle panel,  i.i.d.\ Gaussian noise with standard deviation $\sigma=0.5$  was added, however,  Einstein is still easily identified.
 In this scenario it is likely that standard detection algorithms can locate the copies of the signal within the micrograph.
@@
 This phenomenon is explained in detail in Appendix~\ref{sec:theory}.
-\TODO{WL: I think this example should go in the previous section on particle picking.
-The main issue we're trying to overcome is when detection is impossible; the fact that we don't use a template seems to be an additional advantage of our method, but not the main selling point.
-So I think the impossibility of detection in sufficiently low SNR must be emphasized earlier.}
 
@@
 	\end{subfigure}
-RR	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
+	\caption{\label{fig:micro_example} Example of data sequences (micrographs) of size $250\times 250$ with additive i.i.d.\ Gaussian noise with variance $\sigma^2$.
 Each micrograph contains four occurrences of a $50 \times 50$ image of Einstein.}
@@
 In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-The method consists of two stages.
+In a nutshell, the method consists of two stages.
 First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
@@
 This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendices~\ref{sec:related_literature} and~\ref{sec:theory}  for more details).
+As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
 
@@
 An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
-Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of at least $49$ pixels between the images in each direction.
+Each micrograph contains multiple occurrences of Einstein's image  in random locations, while keeping a separation of  $49$ pixels between the images in each direction.
 From the micrographs, we estimated the signal's power spectrum, which is equivalent to the second-order autocorrelation.
-Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix}.
+Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR).
 
 As an initial guess, we picked an image of the physicist Issac Newton; see Figure~\ref{fig:newton}.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similar to the ``Einstein from noise'' effect.
+If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect of Figure~\ref{fig:EinsteinFromNoise}.
 However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
@@
 As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
-\TODO{TB: Few comments: 1.
+\TODO{Few comments: 1.
 We have a movie in the supplementary material.
@@
 Does the error also have the right slope?
-We'll know once we'll gather enough micrographs 3.
+3.
+We can put more images to exemplify the progress 4.
 Need to improve the micrograph's generation code  }
@@
 	\centering
-	\begin{subfigure}[h]{0.3\textwidth}
+	\begin{subfigure}[h]{0.25\textwidth}
 		\centering
-		\includegraphics[scale=0.35]{Newton}
+		\includegraphics[scale=0.3]{Newton}
 		\caption{\label{fig:newton}Newton  (model)}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
+	\begin{subfigure}[h]{0.25\textwidth}
 		\centering
-		\includegraphics[scale=0.35]{reconstruction1}
-		\caption{\small $P = 512$}
+		\includegraphics[scale=0.3]{reconstruction2}
+		\caption{\small $P =1024$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
+	\begin{subfigure}[h]{0.25\textwidth}
 		\centering
-		\includegraphics[scale=0.35]{reconstruction10}
-		\caption{$P = 512\times 10$}
+		\includegraphics[scale=0.3]{reconstruction20}
+		\caption{$P = 1024\times 10$}
 	\end{subfigure}%
-
-	\begin{subfigure}[h]{0.3\textwidth}
+	\begin{subfigure}[h]{0.25\textwidth}
 		\centering
-		\includegraphics[scale=0.35]{reconstruction100}
-		\caption{$P = 512\times 100$}
+		\includegraphics[scale=0.3]{reconstruction200}
+		\caption{$P = 1024\times 100$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.35]{reconstruction200}
-	\caption{$P = 512\times 200$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.3\textwidth}
-	\centering
-	\includegraphics[scale=0.35]{reconstruction840}
-	\caption{$P = 512\times 840$}
-	\end{subfigure}%
-
 	\caption{\label{fig:Einst_example} Recovery of Einstein's image.
-The RRR algorithm is initialized with the image of the physicist Issac Newton in the upper-left panel.
-We show estimations of Einstein using $P$ number of micrographs, each containing $700$ image occurrences on average with an $\SNR$ of $1/20$.
-The signal's estimation RMSE is  $0.5874, 0.3731, 0.2517, 0.2137, 0.1534$.
-The power spectrum estimation RMSE is $0.0381, 0.012, 0.0038, 0.0027, 0.0013$.
-}
+The RRR algorithm is initialized with the image of the physicist Issac Newton in the left panel.
+We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $700$ image occurrences on average and the $\SNR$ is $1/20$.
+The signal's estimation RMSE is $0.5514$, $0.3494$ and $0.2112$, respectively.
+The power spectrum estimation RMSE is, respectively, $0.0269 $, $0.0083$ and $0.0027$.
+\TODO{Can add more images to exemplify the progress}}
 \end{figure}
@@
 \end{equation}
-where $M_i$ is the number of times signal $x_i$  occurs, $L$ is the length of each signal and $N$ is the micrograph length.
-These ratios $\gamma_i$ represent the {density} of the the signals in the data.
-In the 1-D experiment, we do not assume knowledge of either the ratios $\gamma_i$ or the noise level $\sigma$.
-
-In order to estimate the signals, we compute the first three autocorrelation functions of the data and then estimate the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-As can be seen, given enough signal occurrences, we can estimate the signals accurately. 
+where $M_i$ is the number of signal's  occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
+These ratios present the {density} of the the signals in the data.
+In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
+
+In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
+As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
 The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-\TODO{TB: 1.
-Figure~\ref{fig:1Dheterosignals} will be replaced  with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
+\TODO{1.
+We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error for all three signals.
 2.
@@
 The right panel shows the RMSE  (in logarithmic scale) of recovering Einstein's image.
-\TODO{TB: The program continues running so these figures will be extended to the right (more micrographs).}}
+\TODO{The program still runs so these figures will be extended to the right (more micrographs).}}
 \end{figure}
@@
 	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
-	\caption{An experiment for estimating three one-dimensional signals simultaneously with noise level $\sigma=3$.
+	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
 Red signals are the ground truth (targets) and the blue signals are our estimations.
@@
 The $\SNR$ is $1/12$.
-\TODO{TB: 1.
-We will replace the figure with ``progress'' plots 2.
-Need to replace the triangle signal 3.
-Need to add error curves}}
+\TODO{1.
+to replace with a ``progress'' plot 2.
+replace the triangle signal 3.
+add error progress figure}}
 	\label{fig:1Dheterosignals}
@@
 
-All current algorithmic pipelines for SPR using cryo--EM start with a particle picking stage to detect the 2-D tomographic projections of the samples in the micrograph.
-The particle picking  algorithms tend to be prone to model bias and cannot work reliably on small particles in low $\SNR$ environment. 
-Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge about the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
+All current algorithmic pipeline for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
+Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
 Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
@@
 In this paper, we examined a simplified model that, we believe, captures important features of the SPR problem. 
-While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems. As an alternative, we propose to use an autocorrelation analysis technique. 
-Methods based on autocorrelation analysis require only one pass over the data and therefore are usually computationally efficient. \TODO{TB: Do we want to mention Kam's method?}
-%This property has been exploit before  for  ab inito modeling assuming ideal particle picking~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}. 
-That being said, the SPR model is far more complicated than the model presented here. In future research, we hope to bridge this gap.
+While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
+As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab inito modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
+That being said, the SPR model is far more complicated than the model presented here. In a future research, we hope to bridge this gap.
 
@@
 First, we modeled the background information as i.i.d.\ additive noise. In practice, the background information may be structured or signal dependent. 
-Second, we assumed that the signal occurrences are all separated by the length of the signal; see~\eqref{eq:spacing}. 
-This separation can be induced by careful experimental design \TODO{TB: ???}. 
-If the signals are not separated, one can introduce additional parameters that model the distribution of the spacing  between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
+Second, we assumed that the signal occurrences are all separated by the length of the signal, see~\eqref{eq:spacing}. 
+This separation can be induced by careful experimental design \TODO{???}. 
+If the signals are not separated, one can introduce a new variable that represents the distribution of the spacing between signal occurrences and then compute explicitly the relation between the autocorrelation functions of the data and the signals.
 It is yet to be studied under what conditions on this distribution one can estimate the signals.
@@
 
-Let $x_1,\ldots,x_K\in\RL$ be the target signals and let $y\in\RN$ be the observed data. 
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
 The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
@@
 
-\paragraph{Aperiodic autocorrelation functions.}
+\paragraph{Aperiodic autocorrelation functions}
 %\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
@@
 \end{align}
-where the values of $z$ outside the indices $0, \ldots, L-1$ are taken to be zero.
+where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
 Explicitly, the mean (which can be thought of as a first-order autocorrelation) and the second and third autocorrelations are given by
@@
 We first consider the problem of estimating the autocorrelations of a single signal from the data. 
-The main principles carry through for $K>1$, as will be shown next.
+The main principles carry through for $K>1$ as will be shown next.
 
 %In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
-For the purpose of the analysis, we consider  the asymptotic regime where $M$ grows proportionally to $N$. 
+For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
 Specifically, we define the ratio of the measurement occupied by  the signal as
@@
 \end{equation}
-\TODO{WL: $\gamma$ should really be the limit of this ratio as $N$ grows to infinity; for any finite value of $N$ this ratio may be different.
-TB: The accurate definition is given in~\eqref{eq:gamma_limit}.
-We may want to leave it as is here.}
 Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
@@
 
-As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K$ grow proportional to $N$ and define
+As before, we consider  the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$, while preserving fixed ratios
 \begin{align}
@@
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far. On average, $700$ images were placed in each micrograph.   
-Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added, inducing an $\SNR$ of approximately $1/20$.
-A piece of one such micrograph is presented in the right panel of Figure~\ref{fig:micro_example}.
+an accept/reject rule based on the separation constraint and locations picked so far. In average, $700$ images were placed in each micrograph.   
+Then, an i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ was added inducing $\SNR$ of approximately $1/20$.
+An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
 %Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
@@
 
-In this experiment, we assume the knowledge of the number of Einstein's occurrences and the noise level. 
-In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines   the image  almost surely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
-Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, at the cost of one  FFT per micrograph.
-To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by~\cite{elser2017matrix}
+In this experiment, we assume to know the number of Einstein's occurrences and the noise level. 
+In this situation, the second-order autocorrelation (or, equivalently, the Fourier magnitudes of the signal) determines  almost all images  uniquely up to reflection through the origin~\cite{hayes1982reconstruction,bendory2017fourier}.
+Therefore, we estimate the signal's Fourier magnitude from the Fourier magnitude of the micrographs, in the cost of one  FFT per micrograph.
+To estimate the signal, we use a phase retrieval algorithm called relaxed-reflect-reflect (RRR) that iterates by
 \begin{equation}
-z \rightarrow z + P_2(2P_1(z) - z) - P_1(z).
-\end{equation}
-The RRR algorithm estimates a $2L\times 2L$ image and the exact solution contains Einstein's image in the upper-left corner and zero elsewhere.
+z \rightarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
+\end{equation}
+where we set $\beta=1$.
+RRR estimates a $2L\times 2L$ image.
+Exact solution contains Einstein's image in the upper-left corner and zero else where.
 The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the Fourier magnitudes of the signal  (estimated from the data).
 The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-In order to compare the performance across multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
-While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{TB: Note the last two sentences!}.
+In order to compare the performance in multiple cases and different noise levels, the algorithm stopped after a fixed number of 1000 iterations and the iteration with the smallest error compared to the ground truth (also taking into account the reflection ambiguity) was chosen as the solution.
+While this cannot be done in practice since we do not have access to the ground truth, this procedure enables us to compare a large number of instances in different noisy environments \TODO{Note the last two sentences!}.
 
@@
 In this experiment, we computed the first three autocorrelation functions. 
-We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the terms depending on $\sigma$ (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$. 
-%In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
-
-To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their number of occurrences simultaneously:
+We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
+In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions.
+
+To estimate the signal, we employ an optimization algorithm on the following nonlinear least-squares problem that estimate the signals and their number of occurrences simultaneously:
 \begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2  \\ +w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
 \label{eq:optim1D}
@@
 
- Setting $W = L$  is problematic because the above optimization problems appears to have numerous poor local optimizers.
+ Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
 %Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
@@
 This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest to the measured ones in the sense of~\eqref{eq:optim1D}.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are the closest the measured ones in the sense of~\eqref{eq:optim1D}.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows enforcement of the positivity constraints \TODO{reference} on the coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to evaluate it and its derivatives.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
 
@@
 %
-\begin{equation} \label{eq:gamma_limit}
+\begin{equation}
 \gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
@@
 In~\cite{boumal2017heterogeneous}, we empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
-In~\cite{weinthesis}, this result is shown theoretically for a different, and much less efficient, algorithm.
+In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
 In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.

### 2018-07-26 TEX/draft4.tex
כובל ופ רקבםהקרט

--- 2018-07-11 TEX/draft4.tex
@@
 \TODO{Frank: Working with Owen Saxton, I was able to show that alignment via cross-correlation would be accurate enough for the purpose of aligning noisy images of single molecules if the dose exceeded a certain level, which depended on the molecule?s size and contrast against the background.[19a] Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ x Resolution (as length) X Critical Electron Dose] A detailed examination of this dependency was later to be undertaken by Richard Henderson.[19b].
-From Joachim Frank?s Nobel Lecture.
-Amit's email from July 10.}
+From Joachim Frank's Nobel Lecture.
+Amit's email from July 10.
+Btw, it is also on slide 16 of his lecture}
+
 In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.

### 2018-07-26 TEX/draft_biology.tex
כובל ופ רקבםהקרט

@@
 \newcommand{\mb}{\mathbf}
+\newcommand{\mk}{\mathfrak}
 
@@
 \newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
 
@@
 where $\ast$ denotes linear convolution. Let $\textbf{i}:=(i_1,i_2)$ and similarly for \textbf{j}.
-The binary signals obey the following property:
+The binary signals obey the following property: \TODO{Rewrite in terms of $\delta$ functions for consistency with 3D}
 \begin{align}
@@
  \begin{align}
- \gamma & = \frac{M L}{N},
+ \gamma & = \frac{M L^2}{N^2},
  \end{align}
@@
 \subsection{3-D experiment}
-
-We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
-\[ \widehat V(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\]
-for $k\leq 1$ and zero otherwise, where $c$ is the assumed bandlimit, $Y_{\ell,m}$ may be taken to be either real or complex, and $j_{\ell,s}(r)$ is some radial basis function (in practice, either spherical bessel or the radial part of the 3D PSWFs as in [Lederman]).
-We work here with the complex spherical harmonics, given by
-\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
-where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase.
-
-\TODO{To write down the definition of the $j$ --- the spherical bessel (to copy from the ISBI)}
-
-In this experiment, the micrograph is related to the projections by 
-\begin{equation}
-\mathcal{I}(\rr) = \sum_{i=1}^{N} I_{\omega_i}(\rr-\rr_i)+ \varepsilon, \quad \varepsilon~\sim\mathcal{N}(0,\sigma^2 I),
+\TODO{Add similarities to 2-D}
+
+\TODO{Proposal: Use W for size of projection, M for size of micrograph}
+
+Let $\phi$ be the Coulomb potential representing the molecule we wish to recover, and denote it 3-D Fourier transform by $\widehat \phi$.
+In this paper, we assume that $\widehat\phi$ is given as a finite expansion of the form
+\be\label{eq:volume_expansion} 
+\widehat \phi(k, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}a_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),
+\ee
+where $Y_{\ell}^m$ are complex spherical harmonics and $j_{\ell,s}$ are normalized spherical Bessel functions, see Appendix TKTK for definitions.
+\TODO{Mention somewhere that since $\phi$ is real-valued, we recover only coefficients with $m\geq 0$.} Given $\omega\in\text{SO}(3)$, denote by $I_{\omega}$ the projection obtained from viewing direction $\omega$, and denote by $\widehat I_{\omega}$ its 2-D Fourier transform.
+By the Fourier projection-slice theorem~\cite[p.
+11]{natterer1986mathematics}, the 2D Fourier transform of $I_{\omega}$ is given by \TODO{Move to appendix?}
+\be\label{eq:projection_model}
+\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}a_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),\ee
+where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix rotating spherical harmonics.
+
+Let $\II\in\RR^{M\times M}$ denote a micrograph. For this paper, we assume that the micrograph consists of shifted copies of projections and perturbed by additive white Gaussian noise:
+\begin{equation}\label{eq:micrograph_model}
+\II = \sum_{j=1}^{N} I_{\omega_j}\ast\delta_{\mb s_j}+ \varepsilon, \quad \varepsilon~\sim\mathcal{N}(0,\sigma^2 I),
 \end{equation}
-where $\rr$ is a vector in $\mathbb{R}^2$. \TODO{To write down the definition of projection}
-
-In this paper, we need the first three autocorrelations. In particular, it can be shown that 
+where the viewing directions $\omega_j$ are uniformly distributed over $\text{SO}(3)$, $\mb s_j$ denotes the location of the center of the $j$th projection in the micrograph, and we impose a separation condition similarly to Eq.~\TODO{2D}:
+\be\label{eq:sep_cond} ||\mb s_j - \mb s_i||_{\infty} \geq 2L. \ee
+\TODO{Say something about nonuniformity in practice? Remember that biologists will jump at this...}
+Define the $k$th autocorrelation of $\II$ as
+\be\label{eq:Kth_autocorrelation} 
+m_k[\II](\Delta \mb i_1,\ldots, \Delta \mb i_{k-1}) = \frac{1}{M^2}\sum_{i,j = 1}^M\II(\mb i)\II(\mb i+\Delta\mb i_1)\cdots \II(\mb i+\Delta \mb i_{k-1}),
+\ee
+where $\mb i = (i,j)$, $\Delta \mb i = (\Delta i, \Delta j)$, we require $||\Delta\mb i||_{\infty}\leq 2L-1$, and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$.
+In our procedure, we compute the first three autocorrelations, called the mean, power spectrum, and bispectrum, of the micrographs.
+\TODO{This definition and terminology should come earlier}.
+Because of the separation condition Eq.~(\ref{eq:sep_cond}), the autocorrelations of the micrograph are related to those of the projections by
 \begin{align}
-m_k[\II]  \to \gamma\langle m_k[I_\omega]\rangle_{\omega}, 
+m_k[\II]  \to \gamma\langle m_k[I_\omega]\rangle_{\omega} + b_k, 
 \end{align}
-where $\langle\cdot\rangle$ denotes averaging. \TODO{Do we want to define a general moment?}
-
-In a standard SPR experiment, we expect the distribution of in-plane rotations to be uniform because .... 
-Therefore, based on~\cite{landa2017steerable}, we expand the each autocorrelation functions in Prolates .... as discussed in Appendix TKTK.
-
-The next stage is to connect the Prolates coefficients of the moments with those of the volume.
-In Appendix TKTK we show that the volume is related to autocorrelations of the micrograph through
-
-\begin{align}
-\langle m_1[I_\omega]\rangle_\omega  &= \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0) \\ 
-\mathfrak{m}_2(q) &= \frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
-\int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk \\
-\mathfrak{m}_3(k,q_1,q_2) &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}
+where $\langle\cdot\rangle$ denotes averaging, $b_k$ is a bias term, and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$.
+The mean is unbiased so $b_1 = 0$, the power spectrum has bias $b_2$ depending only on $\sigma^2$, the variance of the noise, and the bias of the bispectrum $b_3$ depends additionally on the mean of $\phi$, which can be accurately estimated from the mean of the micrograph.
+We can therefore estimate the quantities $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ directly from the micrograph.
+
+Since we assume that the viewing directions $\omega_j$ are uniformly distributed over $\text{SO}(3)$, we would like to average over all in-plane rotations of the projections in the computation of the autocorrelations.
+To do so, we follow~\cite{landa2017steerable,zhao2016fast} and expand the second and third autocorrelations of the micrograph in Prolate Spheroidal Wave Functions (PSWFs).
+It can then be shown that the expansion coefficients $\mathfrak{m}_k$ of the autocorrelations in PSWFs are related to the expansion coefficients of the volume by
+
+\begin{align}\label{eq:coeffs_to_moms}
+&\mathfrak{m}_1\{a_{\ell,m,s}\} = \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0) \\ 
+&\mathfrak{m}_2\{a_{\ell,m,s}\}(q) = \frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}C_2^{(q)}(\ell,s_1,s_2)a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
+ \\
+&\mathfrak{m}_3\{a_{\ell,m,s}\}(k,q_1,q_2) = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C_3^{(k,q_1,q_2)}(\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3)a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}},
 \end{align}
-where
-\begin{align*}
-C&:= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},
-\end{align*}
-and 
-\begin{align*}
-\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.
-\end{align*}
-
-From the data we can estimate (see Appendix TKTK) 
-\begin{align*}
-\widetilde{\mathfrak{m}}_2(q) &= \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0) \\
-\widetilde{\mathfrak{m}}_3(k,q_1,q_2) &= \mathfrak{m}_3(k,q_1,q_2) +
-\sigma^2m_1[\II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
-\end{align*}
+see Appendix TKTK for the definitions of $C_2,C_3$.
+
+To recover the expansion coefficients $\{a_{\ell,m,s}\}$ from the autocorrelation coefficients estimated from the micrograph $\mk m_k[\II]$, we minimize the weighted least-squares problem
+\be\label{eq:min_problem_cryo} \min_{\{a_{\ell,m,s}\}} \sum_{k=1}^3\frac{\Big|\Big|\mk m_k\{a_{\ell,m,s}\} - \mk m_k[\II]\Big|\Big|_F^2}{||\mk m_k[\II]||_F^2}.\ee
 
@@
 \TODO{To rewrite for the discrete case}
-We consider the moments of $\II$ in the limit $N\to\infty$.
-To take this limit, we shall assume that $N=\Omega(M^2)$ (so by the above argument, in fact $N=\Theta(M^2)$), so $\gamma = \lim_{N\to\infty}\frac{N}{M^2}\in(0,1)$.
-We also assume that the orientations of the projections in $\II$ are uniformly distributed over the sphere.
-For the first moment,
-\[ m_1[\II] =
-\frac{NL^2}{M^2}\cdot\frac{1}{N}\sum_{i=1}^N\frac{1}{L^2}\int_{\RR^2}I_{\omega_i}(\rr)\,
-d\rr \to \gamma\int_{\text{SO}(3)} L^2m_1[I_{\omega}]\, d\omega =
-\gamma L m_1[V],\]
-since $\int_{\RR^2} I_{\omega}(x,y)\, dx\, dy = \widehat I_{\omega}(\mathbf{0})=\widehat V(\mathbf{0})$ as the Fourier transform of any projection corresponds to a 2D slice of the Fourier transform of the volume passing through the origin.
-
-For the second and third moments, note that if $\rr\in S_i$ for some $i$, then $\rr+\Delta\rr\in S_i\cup Z$ whenever $||\Delta\rr||\leq 2L$ by the separation assumption $d> 2L$.
+
+We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{N}{M^2}\in(0,1)$ is a constant. 
+Because of the separation condition Eq.~(\ref{eq:sep_cond}), if $\mb i$ is in the support of the $j$th projection, then $\mb i + \Delta\mb i$ is either in the support of the same projection or outside the support of any projection.
+Formally, $\mb i$ is in the support of the $j$th projection if and only if $\mb 0\leq \mb i - \mb s_j < (L,L)^T$ where the inequalities apply to each coordinate.
+Then because of the separation condition,
+
+note that if $\rr\in S_i$ for some $i$, then $\rr+\Delta\rr\in S_i\cup Z$ whenever $||\Delta\rr||\leq 2L$ by the separation assumption $d> 2L$.
 Since $\RR^2=Z\sqcup\bigsqcup_{i=1}^NS_i$, and $\II(\rr)=0$ if $\rr\in Z$, we have for $||\Delta\rr||\leq 2L$
@@
 \[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
-where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase.
+where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase, and $j_{\ell,s}$ are normalized spherical Bessel functions given by
+\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
+where $j_{\ell}$ is the spherical Bessel function of order $\ell$, $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$, and the radius satisfies $k\in[0,1/2]$ in Fourier space since $1/2$ is the Nyquist frequency [ISBI].
 
@@
 \[ m_1[V] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]
+
+\begin{align*}
+&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
+&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},
+\end{align*}
+and 
+\begin{align*}
+\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.
+\end{align*}
 

### 2018-07-26 Cryo_EM/PSWF_2D_full_cart_OLD.m

@@ -1,0 +1,14 @@
+function psi_Nn = PSWF_2D_full_cart_OLD(maxN, n_list, L)
+
+[x,y] = meshgrid(-L:L-1, -L:L-1);
+[phi,r] = cart2pol(x,y);
+r = r./L;
+
+psi_Nn = cell(2*maxN+1, 1);
+for N = -maxN:maxN
+    psi_Nn{N+maxN+1} = zeros((2*L)^2, n_list(abs(N)+1));
+    R_Nn = PSWF_radial_2D(abs(N), n_list(abs(N)+1)-1, pi*L, r(r<=1)); % generate 2D radial prolates
+    psi_Nn{N+maxN+1}(r<=1,:) = bsxfun(@times, R_Nn, exp(1i*N*phi(r<=1))./sqrt(2*pi));
+end
+    
+    

### 2018-07-26 Cryo_EM/PSWF_radial_2D.m

@@ -1,0 +1,94 @@
+function [R_Nn, alpha_Nn] = PSWF_radial_2D(N, n, c, radial_eval_pts)
+%% Generate points for numerical integration
+% persistent x;
+% persistent w;
+phi_approx_err = 1e-16;
+% if (isempty(x))
+    [x,w]=lgwt(20*n,0,1);    % Legendre-Gauss nodes for numerical integration   
+    x = flipud(x);
+    w = flipud(w);    
+% end
+
+%% Calculate approx_len
+% - Definition for the approximation function of the d's decay
+d_decay_approx_fun = @(N,n,c,j) c^2./(16*(j.^2 + j*(2*n+N+1)) - c^2);
+
+% - Finding the first point of the decay according to the approximation
+first_idx_for_decrease = ceil((((2*n+N+1)^2+c^2/2)^0.5 - (2*n+N+1))/2);     % Analytic solution for d_decay_approx_fun<1 for every j>first_idx_for_decrease
+
+% - Finding the number of points needed to achieve the chosen error
+d_approx = d_decay_approx_fun(N,n,c,first_idx_for_decrease);
+d_decay_idx_counter = first_idx_for_decrease;
+
+while(d_approx>phi_approx_err)
+    d_decay_idx_counter = d_decay_idx_counter + 1;
+    d_approx = d_approx * d_decay_approx_fun(N,n,c,d_decay_idx_counter);
+end
+
+approx_len = n + 1 + d_decay_idx_counter;
+
+%% Funcion defenitions
+Pn = @(n,alpha,beta,x) j_polynomial(length(x),n,alpha,beta,x);
+
+%% Generate Matrix for calculation of d_k coefficients
+B_N = Generate_BN_mat(N,c,approx_len);
+[d_vec, xi] = eig(B_N);
+
+%% Sort eigenvalues by descending order
+[xiVec,idx] = sort(diag(xi),'descend');
+d_vec = d_vec(:,idx);
+for i=1:approx_len
+    xi(i,i) = xiVec(i);
+end
+
+%% Compare true decay of d's with approximation function
+% d_decay_compare = [abs(d_vec((n+2):end,n+1)./d_vec((n+1):(end-1),n+1)),d_decay_approx_fun(N,n,c,0:(approx_len-2-n)).'];
[…]

### 2018-07-26 Cryo_EM/analytic_WignerD_fixedJ.m

@@ -1,0 +1,18 @@
+function D_j = analytic_WignerD_fixedJ(j, eu_angles)
+eu_angles = sym(eu_angles);
+j = sym(j);
+D_j = zeros(double(2*j+1), double(2*j+1), 'sym');
+for m = -j:j
+    for k = -j:j
+        n_min = max(0, k-m);
+        n_max = min(j-m, j+k);
+        for n = n_min:n_max
+            w_jmkn = sqrt(factorial(sym(j+m))*factorial(sym(j-m))*factorial(sym(j+k))*factorial(sym(j-k)));
+            w_jmkn = w_jmkn./(factorial(sym(j-m-n))*factorial(sym(j+k-n))*factorial(sym(n+m-k))*factorial(sym(n)));
+            D_j(m+j+1,k+j+1) = D_j(m+j+1,k+j+1) + (-1)^n*w_jmkn*cos(eu_angles(2)/2)^(2*j+k-m-2*n)*(-sin(eu_angles(2)/2))^(m-k+2*n);
+        end
+        D_j(m+j+1, k+j+1) = exp(-1i*m*eu_angles(1))*D_j(m+j+1, k+j+1)*exp(-1i*k*eu_angles(3));
+    end
+end
+
+% D = cellfun(@(x) double(x), D, 'UniformOutput', 0);

### 2018-07-26 Cryo_EM/batch_micrograph_patches.m

@@ -1,0 +1,27 @@
+function micro_batch = batch_micrograph_patches(I, L, batch_size)
+% Splits micrograph into batches of patches, one batch per column
+
+micro_batch = cell(ceil(size(I,1)*size(I,2)/batch_size), 1);
+pixels_per_img = size(I,1)*size(I,2);
+num_micros = size(I,3);
+
+I = padarray(I, [L-1, L-1]);
+idx_micro = cart2inds(size(I), L:size(I,1)-L+1, L:size(I,2)-L+1); % linear indices of original micrograph
+sz_img = [size(I,1), size(I,2)];
+
+batch_num = ceil(pixels_per_img/batch_size);
+for batch = 1:batch_num
+    idx_vals = idx_micro(batch_size*(batch-1) + 1 : min(batch_size*batch, pixels_per_img));
+    row_vals = rem(idx_vals-1, sz_img(1)) + 1;
+    col_vals = (idx_vals - row_vals)/sz_img(1) + 1;
+    batch_size_actual = length(idx_vals);
+    batch_curr = zeros(2*L-1, 2*L-1, batch_size_actual*num_micros, 'double');
+    for ii = 1:batch_size_actual
+        row = row_vals(ii); col = col_vals(ii);
+        inds_row = row + (-(L-1):(L-1));
+        inds_col = col + (-(L-1):(L-1));
+        batch_curr(:, :, (ii-1)*num_micros+1:ii*num_micros)...
+            = I(inds_row, inds_col, :);
+    end
+    micro_batch{batch} = batch_curr;
+end

### 2018-07-26 Cryo_EM/bispectrum_from_harmonics.m

@@ -1,0 +1,53 @@
+function M = bispectrum_from_harmonics(a_lms, L, B, W)
+
+maxL = length(a_lms)-1;
+maxS = size(a_lms{1},1);
+
+if ~exist('W', 'var') || isempty(W)
+    W = precomp_wigner_weights(maxL);
+end
+
+if ~exist('B','var') || isempty(B)
+    B = precomp_bispectrum_coeffs(maxL, maxS, L, W);
+end
+
+M = cell(length(B{1}{1}), 1);
+M = cellfun(@(x) 0, M, 'UniformOutput', 0);
+for ii = 1:(maxL+1)^2
+    [L1, L2] = ind2sub([maxL+1, maxL+1], ii);
+    L1 = L1-1; L2 = L2-1;
+    
+    L3_vals = abs(L1-L2):min(L1+L2, maxL);
+    for jj = 1:length(L3_vals)
+        L3 = L3_vals(jj);
+        
+        for k = 0:length(B{ii}{jj})-1
+            sz_B = size(B{ii}{jj}{k+1}); % q1 x q2 x s1 x s2 x s3
+            % Perform summation over s1, s2, s3:
+            sz = size(a_lms{L3+1});
+            tmp = reshape(B{ii}{jj}{k+1}(:,:,:,:,1:sz(1)), [], sz(1))*conj(a_lms{L3+1}); % (q1, q2, s1, s2) x m3
+            tmp = reshape(tmp.', [sz(2), sz_B(1:4)]); % m3 x q1 x q2 x s1 x s2
+            
+            sz_B = size(tmp);
+            sz = size(a_lms{L2+1});
+            tmp = reshape(tmp(:,:,:,:,1:sz(1)), [], sz(1))*a_lms{L2+1}; % m3 x q1 x q2 x s1 x m2
+            tmp = reshape(tmp.', [sz(2), sz_B(1:4)]); % m2 x m3 x q1 x q2 x s1
+            
+            sz_B = size(tmp);
+            sz = size(a_lms{L1+1});
+            tmp = reshape(tmp(:,:,:,:,1:sz(1)), [], sz(1))*a_lms{L1+1}; % (m2, m3, q1, q2) x m1
+            tmp = reshape(tmp.', [sz(2), sz_B(1:4)]); % m1 x m2 x m3 x q1 x q2
+            
+            % Perform summation over m2, m3:
+            for m1 = -L1:L1
+                for m2 = -L2:L2
+                    m3 = m1+m2;
[…]

### 2018-07-26 Cryo_EM/bispectrum_from_harmonics_naive.m

@@ -1,0 +1,43 @@
+function M = bispectrum_from_harmonics_naive(a_lms, L)
+
+maxL = length(a_lms)-1;
+maxn = size(a_lms{1},1);
+maxI = maxn;
+% beta = radial_PSWFs_3D_to_2D_factors(maxL, maxn, L); % l x N x s x n
+beta = sph_Bessel_to_2D_PSWF_factors(maxL, maxn, maxI, L); % l x N x s x n
+T = generate_radial_triple_prods(L, maxL, maxn); % k x n1 x n2 x n3 x q1 x q2)
+
+M = cell(maxL+1, 1);
+for k = 0:maxL
+    M{k+1} = 0;
+    for L2 = k:maxL
+        for L3 = k:maxL
+            L1_vals = abs(L2-L3):min(L2+L3, maxL);
+            for jj = 1:length(L1_vals)
+                L1 = L1_vals(jj);
+                for m2 = -L2:L2
+                    for m3 = -L3:L3
+                        m1 = m2+m3;
+                        if abs(m1) > L1, continue; end
+                        for s1 = 1:maxI
+                            for s2 = 1:maxI
+                                for s3 = 1:maxI
+                                    for n1 = 0:maxn
+                                        for n2 = 0:maxn
+                                            for n3 = 0:maxn
+                                                M{k+1} = M{k+1} + conj(a_lms{L1+1}(s1, m1+L1+1))*a_lms{L2+1}(s2, m2+L2+1)*a_lms{L3+1}(s3, m3+L3+1)*...
+                                                    sqrt(2*pi)*(-1)^(m1)*double(w3j(L2, L3, L1, k, -k, 0))*double(w3j(L2, L3, L1, m2, m3, -m1))*...
+                                                    conj(beta{L1+1}{1}(s1,n1+1))*beta{L2+1}{k+1}(s2,n2+1)*beta{L3+1}{k+1}(s3,n3+1)*...
+                                                    squeeze(T{k+1}(n1+1,n2+1,n3+1,:,:));
+                                            end
+                                        end
+                                    end
+                                end
+                            end
+                        end
+                    end
+                end
+            end
+        end
+    end
+end

### 2018-07-26 Cryo_EM/bispectrum_from_harmonics_noprecomp.m

@@ -1,0 +1,71 @@
+function M = bispectrum_from_harmonics_noprecomp(a_lms, L, W)
+
+Lr = floor(L/2);
+maxL = length(a_lms)-1;
+maxS = size(a_lms{1},1);
+
+[PSWF_Kq_p, PSWF_quad_int_Kq] = precomp_pswf_t(L, 1, 1e-1, 1);
+
+n_list = precomp_Nn_list(Lr);
+psi_Nn = PSWF_2D_full_cart(maxL, n_list, Lr);
+beta = sph_Bessel_to_2D_PSWF_factors(maxL, n_list, maxS, Lr); % l x N x s x n
+
+b_LmNn = cell(maxL+1);
+for l = 0:maxL
+    b_LmNn{l+1} = cell(2*l+1, 1);
+    for N = 0:l
+        b_LmNn{l+1}{N+l+1} = beta{l+1}{N+1}(1:size(a_lms{l+1},1),:).'*a_lms{l+1}; % n x m
+    end
+    for N = -l:-1
+        b_LmNn{l+1}{N+l+1} = conj(b_LmNn{l+1}{abs(N)+l+1});
+    end
+end
+
+psi_lNm = cell(size(psi_Nn));
+for l = 0:maxL
+    psi_lNm{l+1} = cell(2*l+1, 1); % N
+    for N = -l:l
+        psi_lNm{l+1}{N+l+1} = reshape(psi_Nn{N+maxL+1}*b_LmNn{l+1}{N+l+1}, 2*Lr, 2*Lr, []); % r x m
+    end
+end
+
+blk_id = [];
+for ii = 1:max(PSWF_Kq_p.ang_freq)+1
+    num_freqs = length(find(PSWF_Kq_p.ang_freq == ii-1));
+    blk_id = [blk_id; ii*ones(num_freqs^2, 1)];
+end
+
+M = 0;
+parfor ii = 1:L^2*(maxL+1)^2
+    [row, col, L1, L2] = ind2sub([L, L, maxL+1, maxL+1], ii);
+    L1 = L1-1; L2 = L2-1;
+    
+    for L3 = abs(L1-L2):min(L1+L2, maxL)
+        
+        for jj = 1:(2*L1+1)^2*(2*L2+1)^2
+            [m1, N1, m2, N2] = ind2sub([2*L1+1, 2*L1+1, 2*L2+1, 2*L2+1], jj);
[…]

### 2018-07-26 Cryo_EM/bispectrum_grad_from_harmonics_par.m

@@ -1,0 +1,71 @@
+function [G1, G2, G3] = bispectrum_grad_from_harmonics_par(a_lms, L, B, W, L1_list, L2_list, L3_list, L_list, m_list, s_lens)
+
+
+if ~exist('W', 'var') || isempty(W)
+    W = precomp_wigner_weights(length(a_lms)-1);
+end
+
+if ~exist('B','var') || isempty(B)
+    B = precomp_bispectrum_coeffs(length(a_lms)-1, size(a_lms{1},1), L, W);
+    [B, L1_list, L2_list, L3_list] = form_B_cell(B);
+end
+
+maxK = length(B)-1;
+G1 = cellfun(@(y) zeros(length(L_list), size(y{1},1), size(y{1},1)), B, 'UniformOutput', 0);
+G2 = G1; G3 = G1;
+for k = 0:maxK
+    B_k = B{k+1};
+    q_k = size(B_k{1},1);
+    G1_acc = 0; G2_acc = 0; G3_acc = 0;
+    parfor ii = 1:length(B_k)
+        L1 = L1_list(ii); s1_curr = s_lens(L1+1); 
+        L2 = L2_list(ii); s2_curr = s_lens(L2+1);
+        jj_3 = L3_list(ii); L3 = abs(L1-L2) + jj_3 - 1; s3_curr = s_lens(L3+1);
+        
+        B_k_curr = B_k{ii}(:,:, 1:s1_curr, 1:s2_curr, 1:s3_curr);
+        % Perform summation over s1, s2, s3:
+        tmp_1 = conj(reshape(B_k_curr, q_k^2*s1_curr*s2_curr, s3_curr))*a_lms{L3+1}; % (q1, q2, s1, s2) x m3
+        tmp_1 = reshape(tmp_1.', [2*L3+1, q_k, q_k, s1_curr, s2_curr]); % m3 x q1 x q2 x s1 x s2
+        tmp_2 = permute(tmp_1, [1,5,2,3,4]); % m3 x s2 x q1 x q2 x s1
+        
+        tmp_3 = permute(B_k_curr, [5,1,2,3,4]); % s3 x q1 x q2 x s1 x s2
+        
+        tmp_1 = reshape(tmp_1, (2*L3+1)*q_k^2*s1_curr, s2_curr)*conj(a_lms{L2+1}); % (m3 x q1 x q2 x s1) x m2
[…]

### 2018-07-26 Cryo_EM/cost_micro_moments_withHess.m

@@ -1,0 +1,42 @@
+function [f, store] = cost_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, store)
+
+a_lms = vec_to_cell_vol_coeffs(a_lms(1:length(a_lms)/2) + 1i*a_lms(length(a_lms)/2+1:end), x_lists.L(x_lists.p));
+a_lms_vec = cellfun(@(x)x(:), a_lms, 'UniformOutput', 0);
+a_lms_vec = vertcat(a_lms_vec{:});
+
+if ~isfield(store, 'F')
+    [H1, H2, H3] = bispectrum_hess_from_harmonics(a_lms, L, B, W, B_lists.L1, B_lists.L2, B_lists.L3, x_lists.L, x_lists.m, x_lists.s, B_lists.blk_id);
+
+    [m2_harms, G_m2, H_m2] = power_spectrum_from_harmonics(a_lms_vec, M2_quants.j_l, M2_quants.R_0n, M2_quants.w, L);
+    
+    G1 = cellfun(@(x) x.'*a_lms_vec, H3, 'UniformOutput', 0);
+    G1 = cat(2, G1{:});
+    
+    G2 = cellfun(@(x) x*a_lms_vec, H3, 'UniformOutput', 0);
+    G2 = cat(2, G2{:});
+    
+    G3 = cellfun(@(x) x*a_lms_vec, H1, 'UniformOutput', 0);
+    G3 = cat(2, G3{:});
+    
+    m3_harms = G1.'*a_lms_vec;
+
+    dm3 = m3_harms - (1/gamma)*m3_micro;
+    dm2 = m2_harms - (1/gamma)*m2_micro;
+    F = [real(dm3); lambda*real(dm2)];
+    
+    f = norm(F)^2;
+    
+    store.H1 = H1;
+    store.H2 = H2;
+    store.H3 = H3;
+    store.H_m2 = H_m2;
+    store.G1 = G1;
+    store.G2 = G2;
+    store.G3 = G3;
+    store.G_m2 = G_m2;
+    store.F = F;
+else
+    f = norm(store.F)^2;
+end
+
+

### 2018-07-26 Cryo_EM/debias_moments_steerable.m

@@ -1,0 +1,10 @@
+function [m2, m3] = debias_moments_steerable(m1, m2, m3, sigma, L)
+
+[R_0q, alpha_0q] = PSWF_radial_2D(0, size(m3{1},1)-1, pi*(L-1), 0);
+R = (R_0q(:)/sqrt(2*pi))*(4*R_0q./(sqrt(2*pi)*alpha_0q.'));
+R = R + R.';
+
+m3 = cellfun(@(x) x - sigma^2*m1*eye(size(x)), m3, 'UniformOutput', 0);
+m3{1} = m3{1} - sigma^2*m1*R;
+
+m2 =  m2 - sigma^2*R_0q(:)/sqrt(2*pi);

### 2018-07-26 Cryo_EM/extract_patch.m

@@ -1,0 +1,7 @@
+function img = extract_patch(I, row, col, L)
+
+img = zeros(2*L+1, 2*L+1, size(I,3), 'double');
+    inds_row = max(row-L, 1):min(row+L, size(I,1));
+    inds_col = max(col-L, 1):min(col+L, size(I,2));
+    img(inds_row - row + L+1, inds_col - col + L+1, :)...
+        = I(inds_row, inds_col, :);

### 2018-07-26 Cryo_EM/form_B_cell.m

@@ -1,0 +1,25 @@
+function [B_n, L1_list, L2_list, L3_list] = form_B_cell(B)
+
+maxL = size(B,1)-1;
+maxK = length(B{1}{1})-1;
+
+B_n = cell(maxK+1, 1);
+L1_list = []; L2_list = []; L3_list = [];
+for ii = 1:(maxL+1)^2
+    [L1, L2] = ind2sub([maxL+1, maxL+1], ii);
+    L1 = L1-1; L2 = L2-1;
+    
+    L3_vals = abs(L1-L2):min(L1+L2, maxL);
+    for jj = 1:length(L3_vals)
+        L1_list = [L1_list;  L1];
+        L2_list = [L2_list;  L2];
+        L3_list = [L3_list;  jj];
+    end
+end
+
+for k = 0:maxK
+    B_n{k+1} = cell(length(L3_list), 1);
+    for ii = 1:length(L3_list)
+        B_n{k+1}{ii} = B{L1_list(ii)+1, L2_list(ii)+1}{L3_list(ii)}{k+1};
+    end
+end

### 2018-07-26 Cryo_EM/gen_rand_proj.m

@@ -1,0 +1,10 @@
+function[I, R] = gen_rand_proj(a_lms, Psilms_2D, jball_2D, L)
+
+Rot = randR(3);
+if det(Rot) < 0, Rot(:, [1,2]) = Rot(:, [2,1]); end
+R = RN2RL( getSHrotMtx( Rot, length(a_lms)-1, 'complex' ) );
+a_lms_rot = cellfun(@mtimes, a_lms, R, 'UniformOutput', 0);
+a_lms_rot = cellfun(@(x) x(:,1:2:end), a_lms_rot, 'UniformOutput', 0);
+
+I = recover_from_ALM_v4_given_Psilms_2D(a_lms_rot, floor(L/2), jball_2D, Psilms_2D, length(a_lms)-1, L);
+I = real(icfftn(I));

### 2018-07-26 Cryo_EM/gen_triple_prod.m

@@ -1,0 +1,27 @@
+function T = gen_triple_prod(I1, I2, I3, PSWF_Kq_p, PSWF_quad_int_Kq, blk_id, q_list)
+
+L = size(I1,1);
+T = 0;
+n1_len = size(I1,3);
+n2_len = size(I2,3);
+n3_len = size(I3,3);
+beta_PSWF = 1; Trunc = 1e-1; realFlag = 0;
+vec = @(x)x(:);
+parfor ii = 1:L^2
+    [row, col] = ind2sub([L, L], ii);
+    patch = extract_patch(I2, row, col, L-1);
+    patch(:,:,end+1:end+n3_len) = extract_patch(I3, row, col, L-1);
+    
+    coeffs  = pswf_t_f_fast(patch, L-1, beta_PSWF, Trunc, realFlag, PSWF_Kq_p, PSWF_quad_int_Kq, '../nfft');
+    coeffs = PSWF_coeff_convert(coeffs, PSWF_Kq_p.ang_freq);
+    
+    coeffs = cellfun(@(x) vec(x(:,1:n2_len))*vec(x(:,n2_len+1:end))', coeffs, 'UniformOutput', 0); % (q1, n2) x (q2, n3)
+    coeffs = cellfun(@(x) vec(I1(row,col,:))*vec(x).', coeffs, 'UniformOutput', 0); % n1 x (q1, n2, q2, n3)
+    coeffs = cellfun(vec, coeffs, 'UniformOutput', 0);
+    
+    T = T + vertcat(coeffs{:})./L^2;
+end
+
+T = accumarray(blk_id, T, [], @(x) {x});
+T = cellfun(@(x,y) reshape(x, n1_len, y, n2_len, y, n3_len), T, q_list, 'UniformOutput', 0); 
+T = cellfun(@(x) permute(x, [1,3,5,2,4]), T, 'UniformOutput', 0); % n1 x n2 x n3 x q1 x q2

### 2018-07-26 Cryo_EM/generate_hybrid_PSWFs.m

@@ -1,0 +1,38 @@
+function [Psi_lms, pts_in_ball, Psi_lms_2D, pts_in_disc_2D] = generate_hybrid_PSWFs(L, maxL)
+
+c=pi*L;   % band limit
+
+R = floor(L/2);
+if mod(L,2) == 0
+    [x,y,z] = meshgrid(-R:R-1, -R:R-1, -R:R-1);
+else
+    [x,y,z] = meshgrid(-R:R, -R:R, -R:R);
+end
+[phi,elev,r] = cart2sph(x,y,z);
+r = r/R;
+theta = pi/2-elev;
+pts_in_ball = find(r <= 1);
+pts_in_disc_2D = find(r(z==0) <= 1);
+
+Psi_lms = cell(maxL+1, 1);
+Psi_lms_2D = cell(maxL+1, 1);
+Y_l = YN2YL(getSH(maxL, [phi(pts_in_ball), theta(pts_in_ball)], 'complex'));
+n = L+1; T = 1e-1;
+for l = 0:maxL
+    [Phi_ls, alpha] = PSWF_radial_2D(l, n, c, r(pts_in_ball));
+    lambda = (c/(2*pi))^2 * abs(alpha).^2;
+    gamma = sqrt(abs(lambda./(1-lambda))); 
+
+    n_end = find(gamma<=T,1,'first');
+    
+    if (~isempty(n_end))
+        n = n_end;
+    else
+        % The case where the initial n isn't large enough -> Try again.        
+        n = 2*n;
+    end
+    Psi_lms{l+1} = bsxfun(@times, Phi_ls, permute(Y_l{l+1},[2,3,1]));
+    Psi_lms_2D{l+1} = Psi_lms{l+1}(z(pts_in_ball) == 0, :, 1:2:end); % restrict to xy-plane and take only m = l (mod 2)
+end
+
+end

### 2018-07-26 Cryo_EM/generate_radial_triple_prods.m

@@ -1,0 +1,56 @@
+function T = generate_radial_triple_prods(c, maxN, maxK, n_list, q_list)
+
+% Generate grid for r integral:
+[r_quad,w_r] = lgwt(1e2, 0, 1);
+w_r = w_r.*r_quad;
+phi_quad = linspace(-pi, pi, 1e2); 
+w_phi = 2*pi/length(phi_quad)*ones(length(phi_quad),1);
+[R,P] = ndgrid(r_quad, phi_quad);
+w_q = kron(w_phi, w_r);
+[X_q, Y_q] = pol2cart(P(:), R(:));
+
+% Generate grid for dr integral:
+[xx, w_x] = lgwt(1e2, -1,1);
+[X,Y] = ndgrid(xx, xx);
+[P_dr, R_dr] = cart2pol(X(:), Y(:));
+w_dr = kron(w_x, w_x);
+
+X_sum = bsxfun(@plus, X_q(:), X(:).'); % (x) x (dx)
+Y_sum = bsxfun(@plus, Y_q(:), Y(:).'); % (y) x (dy)
+[P_sum, R_sum] = cart2pol(X_sum, Y_sum);
+
+rho_kN = cell(maxK+1, 2*maxN+1);
+parfor ii = 1:(2*maxN+1)*(maxK+1)
+    [k, N] = ind2sub([maxK+1, 2*maxN+1], ii);
+    k = k-1; N = N-maxN-1;
+    
+    psi_Nn = PSWF_2D_N(N, n_list(abs(N)+1), c, R_sum(:), P_sum(:));
+    [psi_Kq, alpha_Kq] = PSWF_2D_N(k, q_list(k+1), 2*c, R_dr(:), P_dr(:)); % dr x q
+    psi_Kq = bsxfun(@times, psi_Kq, (2./alpha_Kq.').^2);
+    
+    psi_Nn = reshape(psi_Nn, numel(X_q), numel(X), []); % r x dr x n
+    psi_Nn = permute(psi_Nn, [2,1,3]); % dr x r x n
+    psi_Nn = reshape(psi_Nn, numel(X), []); % dr x (r, n)
+    
+    % dr integral:
+    rho_kN{ii} = psi_Nn.'*diag(w_dr)*psi_Kq; % (r, n) x q
+    rho_kN{ii} = reshape(rho_kN{ii}, numel(X_q), []); % r x (n, q)
+end
+
[…]

### 2018-07-26 Cryo_EM/generate_radial_triple_prods_given_N.m

@@ -1,0 +1,52 @@
+function T = generate_radial_triple_prods_given_N(Lr, N1, N2, N3, n_list, r, phi, PSWF_Nn_p, PSWF_quad_int)
+
+L = 2*Lr+1;
+c = Lr*pi;
+n1_len = n_list(abs(N1)+1);
+n2_len = n_list(abs(N2)+1);
+n3_len = n_list(abs(N3)+1);
+
+psi_N1 = PSWF_2D_N(N1, n1_len-1, c, r(:), phi(:));
+psi_N1 = reshape(psi_N1, size(r,1), size(r,2), []);
+psi_N2 = PSWF_2D_N(N2, n2_len-1, c, r(:), phi(:));
+psi_N2 = reshape(psi_N2, size(r,1), size(r,2), []);
+psi_N3 = PSWF_2D_N(N3, n3_len-1, c, r(:), phi(:));
+psi_N3 = reshape(psi_N3, size(r,1), size(r,2), []);
+
+% Create a dr1 x dr2 image:
+sz_img = size(r);
+maxK = max(PSWF_Nn_p.ang_freq);
+q_list = zeros(maxK+1);
+for k = 0:maxK, q_list(k+1) = length(find(PSWF_Nn_p.ang_freq == k)); end
+blk_id = [];
+for k = 0:maxK
+    blk_id = [blk_id; k*ones(q_list(k+1)^2*n1_len*n2_len*n3_len, 1)];
+end
+
+acc_vec = 0;
+parfor ii = 1:prod(sz_img)
+    [row, col] = ind2sub(sz_img, ii);
+    img = zeros(2*L+1, 2*L+1, n2_len+n3_len);
+    inds_row = max(row-L, 1):min(row+L, sz_img(1));
+    inds_col = max(col-L, 1):min(col+L, sz_img(2));
+    img(inds_row - row + L+1, inds_col - col + L+1, 1:n2_len)...
+        = psi_N2(inds_row, inds_col, :);
+    img(inds_row - row + L+1, inds_col - col + L+1, n2_len+1:end)...
+        = psi_N3(inds_row, inds_col, :);
+    
+    T_N = pswf_t_f_fast(img, L, 1, 1e-1, 1, PSWF_Nn_p, PSWF_quad_int, '../nfft');
+    T_N = PSWF_coeff_convert(T_N, PSWF_Nn_p.ang_freq);
[…]

### 2018-07-26 Cryo_EM/generate_spherical_bessel_basis.m

@@ -1,0 +1,19 @@
+function j_l = generate_spherical_bessel_basis(maxL, I_list, k_max, k_grid)
+
+k_grid = k_grid(:);
+j_l = cell(maxL+1,1);
+for l = 0:maxL
+    r_li = zerobess('J', l+1/2, I_list(l+1)); % fast zeroes of bessel functions
+    j_lf = @(x,l) sqrt(pi./(2*x)).*besselj(l+1/2, x);
+    X = k_grid*r_li.'/k_max;
+    Y = ones(size(k_grid))*r_li.';
+    J_vals = j_lf(X, l);
+    if l > 0
+        J_vals(isnan(J_vals)) = 0;
+    else
+        J_vals(isnan(J_vals)) = 1;
+    end
+    J_vals(k_grid > k_max) = 0; % enforce support
+    j_l{l+1} = J_vals.*sqrt(2)./(k_max^(3/2)*abs( j_lf(Y, l+1) ));
+    
+end

### 2018-07-26 Cryo_EM/grad_micro_moments_withHess.m

@@ -1,0 +1,29 @@
+function [g, store] = grad_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, store)
+
+if ~isfield(store, 'F')
+    [~, store] = cost_micro_moments_withHess(a_lms, x_lists, L, B, W, B_lists, M2_quants, m3_micro, m2_micro, gamma, lambda, store);
+else
+    G1 = store.G1;
+    G2 = store.G2;
+    G3 = store.G3;
+    G_m2 = store.G_m2;
+    F = store.F;
+end
+
+if ~isfield(store, 'J')
+    sign_factor = (-1).^(x_lists.L(x_lists.n)+x_lists.m(x_lists.n));
+    
+    J = G1 + G2; 
+    J = bsxfun(@times, J(x_lists.n,:), sign_factor) + G3(x_lists.p, :);
+    J = [J, 2*lambda*G_m2(x_lists.p,:)];
+    J(x_lists.m(x_lists.p) > 0,:) = 2*J(x_lists.m(x_lists.p) > 0, :);
+    
+    J = [real(J); imag(J)].';
+    
+    store.J = J;
+    store.signs = sign_factor;
+else
+    J = store.J;
+end
+
+g = 2*J.'*F;

### 2018-07-26 Cryo_EM/hess_pwr_spectrum.m

@@ -1,0 +1,59 @@
+function [Hu, store] = hess_pwr_spectrum(a_lms, x_lists, L, M2_quants, m2_micro, gamma, u, store)
+
+a_lms = a_lms(1:length(a_lms)/2) + 1i*a_lms(length(a_lms)/2+1:end);
+a_lms = vec_to_cell_vol_coeffs(a_lms, x_lists.L(x_lists.p));
+a_vec = cellfun(@(x)x(:), a_lms, 'UniformOutput', 0);
+a_vec = vertcat(a_vec{:});
+
+if ~isfield(store, 'dm2')
+    [m2_harms, G_m2, H_m2] = power_spectrum_from_harmonics(a_vec, M2_quants.j_l, M2_quants.R_0n, M2_quants.w, L);
+    dm2 = real(m2_harms - m2_micro./gamma);
+    store.dm2 = dm2;
+    store.G_m2 = G_m2;
+    store.H_m2 = H_m2;
+else
+    dm2 = store.dm2;
+    G_m2 = store.H_m2;
+    H_m2 = store.H_m2;
+end
+
+if ~isfield(store, 'J')
+    J = 2*G_m2(x_lists.p,:);
+    J(x_lists.m(x_lists.p) > 0,:) = 2*J(x_lists.m(x_lists.p) > 0, :);
+    
+    J = [real(J); imag(J)].';
+    store.J = J;
+else
+    J = store.J;
+end
+
+if ~isfield(store, 'H')
+    H_m2 = cellfun(@(x) x(x_lists.p, x_lists.p), H_m2, 'UniformOutput', 0);
+    for ii = 1:length(H_m2)
+        H_m2{ii}(:, x_lists.m(x_lists.p) > 0) = 2*H_m2{ii}(:, x_lists.m(x_lists.p) > 0);
+    end
+    m_zero_inds = x_lists.m(x_lists.p)==0;
+    sign_factor = (-1).^(x_lists.L(x_lists.p) + x_lists.m(x_lists.p));
+    H_m2_real = H_m2; H_m2_imag = H_m2;
+    for ii = 1:length(H_m2)
+        H_m2_real{ii}(m_zero_inds, m_zero_inds) = (H_m2_real{ii}(m_zero_inds, m_zero_inds) + ...
+            bsxfun(@times, H_m2_real{ii}(m_zero_inds, m_zero_inds), sign_factor(m_zero_inds)))/2;
[…]

### 2018-07-26 Cryo_EM/moments_from_micrograph.m

@@ -1,0 +1,29 @@
+function [m1, m2, m3] = moments_from_micrograph(I, L)
+
+m1 = mean(I(:))/L;
+
+m2 = zeros(2*L-1, 2*L-1);
+parfor ii = 1:(2*L-1)^2
+    [di, dj] = ind2sub([2*L-1, 2*L-1], ii);
+    di = di - L; dj = dj - L;
+    I_prod = I .* aperiodic_shift(I, [di, dj]);
+    m2(ii) = sum(I_prod(:))./numel(I);
+end
+
+m3 = zeros(2*L-1, 2*L-1, 2*L-1, 2*L-1);
+parfor ii = 1:(2*L-1)^4
+    [di1, dj1, di2, dj2] = ind2sub([2*L-1, 2*L-1, 2*L-1, 2*L-1], ii);
+    di1 = di1 - L; dj1 = dj1 - L; di2 = di2 - L; dj2 = dj2 - L;
+    I_prod = I .* aperiodic_shift(I, [di1, dj1]) .* aperiodic_shift(I, [di2, dj2]);
+    m3(ii) = sum(I_prod(:))./numel(I);
+end
+    
+% m2 = zeros(2*L-1, 2*L-1); m3 = m2;
+% I_spec = aperiodic_shift(I, [1, 1]);
+% parfor ii = 1:(2*L-1)^2
+%     [di, dj] = ind2sub([2*L-1, 2*L-1], ii);
+%     di = di - L; dj = dj - L;
+%     I_prod = I .* aperiodic_shift(I, [di, dj]);
+%     m2(ii) = sum(I_prod(:))./numel(I);
+%     m3(ii) = sum(sum(sum(I_prod.*I_spec)))./numel(I);
+% end

### 2018-07-26 Cryo_EM/moments_from_micrograph_steerable.m

@@ -1,0 +1,49 @@
+function [m1, m2, m3, PSWF_quad_int, points_inside_the_circle, plan] = moments_from_micrograph_steerable(I, L, PSWF_quad_int, points_inside_the_circle, plan)
+% L is size of single projection
+m1 = mean(I(:));
+
+L = L-1;        % Conform to PSWF convention where images are 2*L+1
+beta = 1;       % Bandlimit ratio (between 0 and 1) - smaller values stand for greater oversampling
+c = beta*pi*L;  % Bandlimit 
+T = 1e-1;       % Truncation parameter
+realFlag = 1;   % Flag indicating whether the data is assumed to be real-valued
+
+if ~exist('PSWF_quad_int', 'var') || isempty(PSWF_quad_int) || ~exist('points_inside_the_circle','var') || isempty(points_inside_the_circle)
+    [~, PSWF_quad_int, points_inside_the_circle, plan] = precomp_pswf_t(L, beta, T, realFlag);
+end
+
+ang_freq = PSWF_quad_int.ang_freq;
+ang_freq_u = unique(ang_freq);
+
+m2 = zeros(length(find(ang_freq == 0)), 1);
+
+blk_id = []; q_list = [];
+for ii = 1:length(ang_freq_u)
+    num_freqs = sum(ang_freq == ang_freq_u(ii));
+    q_list(end+1) = num_freqs;
+    blk_id(end+1:end+num_freqs^2, 1) = ii*ones(num_freqs^2, 1);
+end
+m3 = zeros(size(blk_id));
+
+sz_img = size(I(:,:,1));
+for col = 1:sz_img(2)
+    for row = 1:sz_img(1)
+%       form image to be expanded:
+        img = extract_patch(I, row, col, L);
+    
+%       Expand in PSWFs:
+        coeff = pswf_t_short(img, L, beta, realFlag, PSWF_quad_int, points_inside_the_circle, plan);
+        coeff = mat2cell(coeff, q_list, 1);
+    
+%       Compute contribution to moments:
+        m2 = m2 + coeff{1}*reshape(img(L+1,L+1,:), [], 1);
+        m3_add = cellfun(@(x) x*diag( reshape(img(L+1,L+1,:), [], 1) )*x', coeff, 'UniformOutput', 0);
+        m3_add = cellfun(@(x) real(x(:)), m3_add, 'UniformOutput', 0);
[…]

### 2018-07-26 Cryo_EM/moments_from_micrograph_steerable_batchMicro.m

@@ -1,0 +1,87 @@
+function [m1, m2, m3] = moments_from_micrograph_steerable_batchMicro(I, L, batch_size)
+% L is size of single projection
+m1 = mean(I(:))/L;
+
+micro_batch = batch_micrograph_patches(I, L, batch_size);
+num_pixels = numel(I);
+clear I
+disp('Done batching')
+
+if isempty(gcp('nocreate')), parpool('local', maxNumCompThreads); end
+
+beta = 1;       % Bandlimit ratio (between 0 and 1) - smaller values stand for greater oversampling
+T = 1e-1;       % Truncation parameter
+realFlag = 1;   % Flag indicating whether the data is assumed to be real-valued
+
+[~, PSWF_quad_int, points_inside_the_circle] = precomp_pswf_t(L-1, beta, T, realFlag);
+plan_par = WorkerObjWrapper(@precomp_nfft_par, {PSWF_quad_int, L-1, beta}, @nfft_finalize);
+disp('Done precomputing')
+
+ang_freq = PSWF_quad_int.ang_freq;
+q_list = PSWF_quad_int.n_list;
+
+m2 = zeros(length(find(ang_freq == 0)), 1);
+
+blk_id = [];
+for ii = 0:max(ang_freq)
+    blk_id(end+1:end+q_list(ii+1)^2, 1) = ii+1;
+end
+m3 = zeros(size(blk_id));
+
+sz_img = [size(I,1), size(I,2)];
+pixels_per_img = prod(sz_img);
+num_micros = size(I,3);
+batch_num = ceil(pixels_per_img/batch_size);
+for batch = 1:batch_num
+    idx_vals = (batch_size*(batch-1) + 1) : min(batch_size*batch, pixels_per_img);
+    row_vals = rem(idx_vals-1, sz_img(1)) + 1;
+    col_vals = (idx_vals - row_vals)/sz_img(1) + 1;
+    batch_size_actual = length(idx_vals);
+    batch_curr = zeros(2*L-1, 2*L-1, batch_size_actual*num_micros, 'double');
+    for ii = 1:batch_size_actual
+        row = row_vals(ii); col = col_vals(ii);
+        inds_row = max(row-L+1, 1):min(row+L-1, sz_img(1));
+        inds_col = max(col-L+1, 1):min(col+L-1, sz_img(2));
[…]

### 2018-07-26 Cryo_EM/moments_from_micrograph_steerable_parMicro.m

@@ -1,0 +1,74 @@
+function [m1, m2, m3] = moments_from_micrograph_steerable_parMicro(I, L, batch_size)
+% L is size of single projection
+m1 = mean(I(:))/L;
+
+beta = 1;       % Bandlimit ratio (between 0 and 1) - smaller values stand for greater oversampling
+T = 1e-1;       % Truncation parameter
+
+[Mt, ang_freq] = precomp_pswf_t_mat(L-1, beta, T);
+maxN = max(ang_freq);
+q_list = zeros(maxN+1, 1);
+for ii = 0:maxN, q_list(ii+1) = sum(ang_freq == ii); end
+q_cumsum = cumsum([0; q_list(:)]);
+q_sq_cumsum = cumsum([0; q_list(:).^2]);
+
+m2 = zeros(sum(ang_freq == 0), 1);
+
+blk_id = [];
+for ii = 0:maxN
+    blk_id(end+1:end+q_list(ii+1)^2, 1) = ii+1;
+end
+m3 = zeros(size(blk_id));
+
+[x,y] = meshgrid(-L+1:L-1, -L+1:L-1); pts_notin_disc = sqrt(x.^2 + y.^2) > L-1;
+cntr_idx = sub2ind([2*L-1, 2*L-1], L, L); % linear index of center of patch
+
+pixels_per_img = size(I,1)*size(I,2); % pixels per micrograph
+num_micros = size(I,3);
+batch_num = ceil(pixels_per_img/batch_size); % number of batches per micrograph
+
+I = padarray(I, [L-1, L-1]);
+idx_micro = cart2inds(size(I), L:size(I,1)-L+1, L:size(I,2)-L+1); % linear indices of original micrograph
+sz_img = size(I(:,:,1));
+
+if isempty(gcp('nocreate')), parpool('local', maxNumCompThreads); end
+parfor t = 1:num_micros
+    I_curr = I(:,:,t);
+    
+    for batch = 1:batch_num
+        idx_vals = idx_micro(batch_size*(batch-1) + 1 : min(batch_size*batch, pixels_per_img)); % linear indices of current batch
+        row_vals = rem(idx_vals-1, sz_img(1)) + 1; % row indices
+        col_vals = (idx_vals - row_vals)/sz_img(1) + 1; % col indices
+        batch_size_actual = length(idx_vals); % size of current batch
+        
+        batch_curr = zeros(2*L-1, 2*L-1, batch_size_actual, 'double');
[…]

### 2018-07-26 Cryo_EM/moments_grad_from_micrograph_steerable.m

@@ -1,0 +1,50 @@
+function [m1, m2, m3, m3_g] = moments_grad_from_micrograph_steerable(I, L, L_list, PSWF_Nn_p, PSWF_quad_int)
+% L is size of single projection
+m1 = mean(I(:));
+
+L = L-1;        % Conform to PSWF convention where images are 2*L+1
+beta = 1;       % Bandlimit ratio (between 0 and 1) - smaller values stand for greater oversampling
+T = 1e-1;       % Truncation parameter
+realFlag = 1;   % Flag indicating whether the data is assumed to be real-valued
+
+if ~exist('PSWF_quad_int', 'var') || isempty(PSWF_quad_int) || ~exist('points_inside_the_circle', 'var') || isempty(points_inside_the_circle)
+    [PSWF_Nn_p, PSWF_quad_int, ~] = precomp_pswf_t(L, beta, T, realFlag);
+end
+
+m2 = zeros(length(find(ang_freq == 0)), 1);
+
+blk_id = [];
+for ii = 1:length(ang_freq_u)
+    num_freqs = length(find(ang_freq == ang_freq_u(ii)));
+    blk_id = [blk_id; ii*ones(num_freqs^2, 1)];
+end
+m3 = zeros(size(blk_id));
+
+sz_img = size(I(:,:,1));
+for ii = 1:numel(I(:,:,1))
+    [row, col] = ind2sub(sz_img, ii);
+%     form image to be expanded:
+    img = extract_patch(I, row, col, L);
+    
+%     Expand in PSWFs:
+    coeff = pswf_t_f_fast(img, L, beta, T, realFlag, PSWF_Nn_p, PSWF_quad_int, '../nfft');
+    
+%     Compute contribution to moments:
+    m2 = m2 + coeff{1}*squeeze(img(L+1,L+1,:));
+    m3_add = cellfun(@(x) real(x*diag(squeeze(img(L+1,L+1,:)))*x'), coeff, 'UniformOutput', 0);
+    m3_add = cellfun(@(x) x(:), m3_add, 'UniformOutput', 0);
+    m3 = m3 + vertcat(m3_add{:});
+    
+    img_lms = extract_patch(I_lms, row, col, L);
+    coeff_lms = pswf_t_f_fast(img_lms, L, beta, T, realFlag, PSWF_Nn_p, PSWF_quad_int, '../nfft');
[…]

### 2018-07-26 Cryo_EM/nfftmtx.m

@@ -1,0 +1,13 @@
+function F = nfftmtx(N, x)
+% NFFT matrix for an N x N image with nodes x. 
+
+if mod(N,2) == 0
+    k = -N/2:N/2-1;
+else
+    k = -(N-1)/2:(N-1)/2;
+end
+[K1,K2]=meshgrid(k,k);
+K1=K1(:);
+K2=K2(:);
+
+F = exp(-1i*2*pi*(x(:,1)*K1' + x(:, 2)*K2'));

### 2018-07-26 Cryo_EM/power_spectrum_from_harmonics.m

@@ -1,0 +1,19 @@
+function [M, G, H] = power_spectrum_from_harmonics(a_vec, j_l, R_0n, w, L)
+
+maxL = length(j_l)-1;
+H = cell(size(R_0n,2),1);
+H = cellfun(@(x) cell(maxL+1,1), H, 'UniformOutput', 0);
+for ll = 0:maxL
+    JJ = bsxfun(@times, j_l{ll+1}, permute(j_l{ll+1}, [1,3,2])); % r x s1 x s2
+    JJ = reshape(JJ, size(JJ,1), []); % r x (s1, s2)
+    JJ = sqrt(pi/2)/(4*pi*L^2)*JJ.'*diag(w)*R_0n; % (s1, s2) x n
+    for n = 1:size(JJ,2)
+        H{n}{ll+1} = kron(eye(2*ll+1), reshape(JJ(:, n), size(j_l{ll+1},2), size(j_l{ll+1},2)));
+    end
+end
+H = cellfun(@(x) blkdiag(x{:}), H, 'UniformOutput', 0);
+
+G = cellfun(@(x) x*a_vec, H, 'UniformOutput', 0);
+M = cell2mat(cellfun(@(x) a_vec'*x, G, 'UniformOutput', 0));
+
+G = cat(2,G{:});

### 2018-07-26 Cryo_EM/precomp_B_factors_script.m

@@ -1,0 +1,16 @@
+addpath('../kam_cryo')
+addpath('../SHT')
+addpath(genpath('../pswf_t_mod'))
+addpath(genpath('../easyspin-5.2.18'))
+addpath('../aspire')
+initpath
+addpath('../nfft')
+
+maxL = 5; L = 31; r_cut = 1/2; r_select_ratio = 1;
+
+s_list = gen_s_list(maxL, r_cut, r_select_ratio, floor(L/2));
+W = precomp_wigner_weights(maxL);
+parpool('local', maxNumCompThreads)
+[B, L1_list, L2_list, L3_list, blk_id] = precomp_bispectrum_coeffs_matMult(maxL, s_list, L, W);
+
+save('/scratch/network/eitanl/B_factors_bispect_maxL5_L31', '-v7.3')

### 2018-07-26 Cryo_EM/precomp_nfft_par.m

@@ -1,0 +1,17 @@
+function plan = precomp_nfft_par(PSWF_quad_int, L, beta)
+
+%% Precompute NFFT plan:
+c = beta*pi*L;
+sizeX = 2*L;
+quadRulePtsX = PSWF_quad_int.quadRulePtsX; quadRulePtsY = PSWF_quad_int.quadRulePtsY;
+
+usFftPts = c/L*[quadRulePtsX.' quadRulePtsY.'];
+M=size(usFftPts,1);
+x = usFftPts.'/pi/2;
+
+plan = nfft_init_guru(2, sizeX, sizeX, M, 2*sizeX, 2*sizeX, 6, bitor(PRE_PHI_HUT,PRE_PSI), []);
+nfft_set_x(plan,x);
+nfft_precompute_psi(plan);
+
+end
+

### 2018-07-26 Cryo_EM/test_micrograph_moments.m

@@ -1,0 +1,44 @@
+clear all; close all;
+addpath('~/Documents/kam_cryo')
+addpath('../SHT')
+addpath('../aspire')
+initpath
+addpath('~/EMDB_maps')
+addpath(genpath('../pswf_t_mod'))
+% addpath(genpath('../manopt'))
+
+info.mol = '1qlq_crop';
+vol = double(ReadMRC([info.mol '.mrc'])); %read volume
+L = length(vol);
+M = 7420; % size of a micrograph
+num_micros = 1000; % number of micrographs
+projs_per_micrograph = ceil(0.15*(M/L)^2); % upper bound on # of projection per micrograph
+
+I = zeros(M, M, num_micros, 'double'); % micrographs
+gamma = zeros(num_micros, 1, 'double'); % occupancy factors
+
+if isempty(gcp('nocreate')), parpool('local', maxNumCompThreads); end
+
+parfor t = 1:num_micros % for each micrograph
+    % Generate projections for current micrograph:
+    projs_curr = cryo_project(vol, rand_rots(projs_per_micrograph));
+
+    num_projs = 0; % counter for projections
+    inds_possible = cart2inds([M,M], 1:M-L+1, 1:M-L+1); % possible indices for upper-left corner
+    curr_micro = zeros(M,M,'double');
+    while ~isempty(inds_possible)
+        % Put projection at random possible index, increment counter:
+        [off_1, off_2] = ind2sub([M,M],inds_possible(randi(length(inds_possible))));
+        curr_micro(off_1:off_1+L-1, off_2:off_2+L-1) = projs_curr(:,:,num_projs+1);        
+        num_projs = num_projs + 1;
+        
+        % Delete indices near current projection from possible indices:
+        inds_to_del = cart2inds([M,M], ...
+            off_1-2*(L-1):off_1+2*(L-1), off_2-2*(L-1):off_2+2*(L-1));
+        inds_possible = setdiff(inds_possible, inds_to_del);
+    end
+    I(:,:,t) = curr_micro;
+    gamma(t) = num_projs*L^2/M^2;
+end
+
+save(['/scratch/network/eitanl/' info.mol '_micros_' num2str(num_micros) '_M_' num2str(M) '.mat'], '-v7.3')

### 2018-07-26 TEX/draft_biology.tex
morning session at home

@@
 To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the $\SNR$ is a function of the molecule size.
+On the other hand, the $\SNR$ is a function of the molecule \TODO{size/weight}.
 The smaller the molecules, the fewer detected electrons carry information about them.
@@
 The first stage consists in extracting the various particle projections from the micrographs.
-This is called \emph{particle picking}.
+This stage is called \emph{particle picking}.
 Later stages aim to construct a 3-D model of the molecule from these projections.
@@
 
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$.
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$; see for instance~\cite{bendory2018estimation}\TODO{To verify the title}.
 This fact has been recognized early on by the cryo-EM community.
@@
 In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-The same was mentioned by Joachim Frank in his Nobel prize lecture ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size}''~\cite{frank2018single}.
-As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, as the particles themselves cannot be picked from the micrographs.
-This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-
+Joachim Frank voices a similar observation in his Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2\times $  Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
+\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
+
+The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+%
 Despite this progress, detecting small molecules in the micrographs remains a challenge.
@@
 
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
+In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
 Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
@@
 
-As a proof of concept, we study two simplified models.
-In first model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image.
-The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
-This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-We study it in more details in a companion paper~\cite{bendory2018estimation}.
-An extension to multiple planted images is analyzed in~\cite{bendory2018estimation}.
-In the second model, we consider the 3-D reconstruction problem as it appears in cryo-EM, while neglecting important aspects as discussed in detail in TKTK.
-\TODO{Here we need to elaborate a bit.} This is the main result of this paper.
-\TODO{We probably need to switch the order of this paragraph.}
-
-%A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
-Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
-We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the projections are well separated and we acquire enough of them.
+As a proof of concept, we study a simplified model for 3-D reconstruction directly from the micrograph on a simulated data. 
+In order to recover the 3-D volume, we use autocorrelation analysis.
+In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume \TODO{To mention the expansions?}.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and are the latter are separated in the micrograph.
 Importantly, there is no need to detect the projections.
@@
 To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares.
-We use similar technique for the simpler model of planted image as illustrated in Figure~\ref{fig:Einst_example}.
+In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details.
 As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details.
+\TODO{Do we want to stress that we get only low-resolution of the volume?}
 
@@
 \TODO{To add reference to our example.}
+
+% while neglecting important aspects as discussed in detail in TKTK.
+
+%In first model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+%The goal is to estimate the planted image.
+The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
+This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+We study it in more details in a companion paper~\cite{bendory2018estimation}.
+An extension to multiple planted images is analyzed in~\cite{bendory2018estimation}.
+%
+%In the second model, we consider the 3-D reconstruction problem as it appears in cryo-EM, \TODO{Here we need to elaborate a bit.} This is the main result of this paper.
+\TODO{We probably need to switch the order of this paragraph.}
+
+%A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
+%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
+Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
+We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+%In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume.
+%For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the projections are well separated and we acquire enough of them.
+Importantly, there is no need to detect the projections.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+These directly yield estimates for the autocorrelations of the volume.
+To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares.
+%We use similar technique for the simpler model of planted image as illustrated in Figure~\ref{fig:Einst_example}.
+
+To illustrate the possibility to estimate a signal without detecting its locations, we first discuss a toy model for which it is easier to convey the mathematical principles. 
+In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~TKTK for an illustration.
+The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably. 
+This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+We study it in more details, including an extension to multiple planted images, in a companion paper~\cite{bendory2018estimation}.
+
+%
 
@@
 Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-		\TODO{To add: redo the figures according to Amit's comments}
+		\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
 		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.

### 2018-07-26 TEX/draft_biology.tex
afternoon session

@@
 %
-
-%\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
-
-%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion
-
-%\clearpage
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein}
-%		\caption{\label{fig:Einstein}Einstein image (template)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
-%		\caption{$n = 10$}
-%	\end{subfigure}
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
-%		\caption{$n = 10^2$}
-%	\end{subfigure}
-
-%	\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
-%	\caption{$n = 10^3$}
-%\end{subfigure}%
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
-%	\caption{$n = 10^4$}
-%\end{subfigure}
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
-%	\caption{$n = 10^5$}
-%\end{subfigure}
-
-%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
-As a template, we used Einstein's image of size $50\times 50$ pixels.
-We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image.
-Each noise image was aligned with respect to the template by the maximal value of their cross correlation.
-After the alignment, all the images were averaged.
-As can be seen, the more pure noise images we use, the closer the averaged image to the template.
-}
-%\end{figure}
-
-%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-%As a result, the projections in the 2-D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
-%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
-
-%\paragraph{Simplified model for SPR}
-
-%In this paper, we present a preliminary study that aims to show that estimating a particle 
-%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
-
-%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
-Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
-We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
@@
 
-%\paragraph{Autocorrelation analysis.}
-%We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
-%In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-%In a nutshell, the method consists of two stages.
-First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data.
-There is no need to detect individual occurrences.
-%In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
-%This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
-
-%\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-%In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-%In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
-%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
-With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
-Crucially, the more noisy images we use, the more severe the model bias towards the template.
-%In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-%This true in general to any method which is based on template matching.
-%\TODO{Do we have a nice experiment to exemplify the phenomenon?}
-
 \section{Results} \label{sec:results}
 
-We start this section by considering the simplified model of planted image.
-This experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
-This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries.
-As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
-Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
-Then, we  show that the same holds true for the 3-D reconstruction setup.
- The Methods section provides additional details. 
-%We conducted two experiments in the simplified image formation model described in the introduction:
-%\begin{enumerate}
-%	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
-This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
-%	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
-%\end{enumerate}
-%As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
-Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
-The Methods section provides additional details.
-%In the discussion section, we outline how the general approach could be extended to full 3-D SPR.
-
-%In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+The techniques we advocate allow to recover a signal hidden in noisy micrographs without (even implicitly) detecting the location of signal repetitions in these micrographs.
+To illustrate the underlying principles of the method, we start with a toy model where the target signal is an unknown 2-D image.
+The latter appears several times in noisy micrographs, at unknown locations.
+Toward recovery, we first compute the second-order autocorrelation of the micrographs.
+We then establish that the autocorrelation of the target image can be recovered from the autocorrelation of the micrographs in a straightforward manner.
+The more micrographs we collect, the more accurate the estimate of the image's autocorrelation.
+The target image is then estimated from its autocorrelation using a standard inversion algorithm (up to elementary symmetries).
+The same principles carry over to the more challenging task of 3-D reconstruction from micrographs.
+The Methods Section provides additional details.
+
+In the  experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
 A micrograph contains, on average, 700 occurrences of the target image at random locations.
-The latter are chosen so that two occurrences are always separated by at least 49 pixels in each direction.
-\TODO{it is not clear at this point why the separation is needed.
-Maybe comment about this, or at least mention that the separation condition is discussed later on.} Thus, about 10\% of each micrograph contains signal.
+Thus, about 10\% of each micrograph contains signal.
 The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
-This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
-In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.\TODO{Need to mention that in the 3-D reconstruction we do not make these assumptions.}
-
-We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra).
-This is a particularly simple computation.
-In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself.
-Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
-% bauschke2004rrr,
-RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
+This high noise level is illustrated in TKTK.
+%In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.\TODO{Need to mention that in the 3-D reconstruction we do not make these assumptions.}
+To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction.
+The separation restriction is discussed in more details in the Methods Section.
+
+We compute the average second-order autocorrelation of the micrographs.
+This is a particularly simple computation which can be efficiently executed with a fast Fourier transform on GPUs.
+In the Methods Section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the autocorrelation of the unknown image itself.
+Mathematically, it can be shown that for any noise level, the quality of this estimate improves steadily as the amount of data grows~\cite{bendory2018estimation}.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+
+%RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
 
@@
 Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-
+\TODO{Tamir: I will rewrite it with the new experiment.}
 \TODO{Here the cryo-EM setup shows up}

### 2018-07-27 TEX/draft_biology.tex
morning session

@@
 \newcommand{\rr}{\textbf{r}}
+\newcommand{\ii}{\textbf{i}}
+\newcommand{\jj}{\textbf{j}}
+
 \newcommand{\II}{\mathcal{I}}
@@
 \newcommand{\mk}{\mathfrak}
+\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
 
@@
 \newcommand{\RL}{\mathbb{R}^L}
+\newcommand{\tamir}{x}
 \newcommand{\CL}{\mathbb{C}^L}
@@
 \newcommand{\RNN}{\mathbb{R}^{N\times N}}
+\newcommand{\RPP}{\mathbb{R}^{P\times P}}
 \newcommand{\CNN}{\mathbb{C}^{N\times N}}
@@
 The techniques we advocate allow to recover a signal hidden in noisy micrographs without (even implicitly) detecting the location of signal repetitions in these micrographs.
-To illustrate the underlying principles of the method, we start with a toy model where the target signal is an unknown 2-D image.
+To illustrate the underlying principles of the method, it is instructive to start with a toy model where the target signal is an unknown 2-D image.
 The latter appears several times in noisy micrographs, at unknown locations.
@@
 We compute the average second-order autocorrelation of the micrographs.
-This is a particularly simple computation which can be efficiently executed with a fast Fourier transform on GPUs.
+This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) on GPUs.
 In the Methods Section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the autocorrelation of the unknown image itself.
@@
 
-\subsection{2-D experiment (we need a name)}
-To explain the method, we begin by deriving the algebraic relation between the autocorrelation functions of the micrographs and the autocorrelation functions of the planted image.
-%We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
-For ease of exposition, we do so in the 1-D case.
-Extension to the 2-D case is straightforward.
-We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
-
-Let $x$ be the sought image and let $y\in\RNN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple smaller micrographs concatenated into one.)
-The forward model (or ``image'' formation model) is as follows.
-An unknown binary signal  indicates (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+\subsection{Toy 2-D experiment}
+
+Let $x\in\RPP$ be the target image and let $y\in\RNN$ be  one of  $K$ observed micrographs. 
+%If more than one micrograph is available, then it is sufficient to average the autocorrelations we compute below over the micrographs.
+Independently for each micrograph, the image formation model is as follows.
+An unknown binary signal $s\in\{0,1\}^{(N-P)\times(N-P)}$ indicates the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise, we observe:
 \begin{align}
-	y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+	y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2I),
 	\label{eq:model}
 \end{align}
-where $\ast$ denotes linear convolution. Let $\textbf{i}:=(i_1,i_2)$ and similarly for \textbf{j}.
-The binary signals obey the following property: \TODO{Rewrite in terms of $\delta$ functions for consistency with 3D}
+where $\ast$ denotes linear convolution, $\ii:=(i_1,i_2)$ identifies one location in the image and $\ii=(0,0)$ indicates the  upper left corner.
+We define the images to be zero outside their support.
+The binary signals $s$ obey the following separation property: 
 \begin{align}
-	\textrm{If } s[\textbf{i}] = 1 \textrm{ then } s[\textbf{j}] = 0 \textrm{ for all}  \|\textbf{i}-\textbf{j}\|_\infty\leq 2L-1.
+	\textrm{If } s[\ii] = 1 \textrm{, then } s[\jj] = 0  \textrm{   for all $\jj=(j_1,j_2)$ such that   }  \max\{\vert i_1-j_1\vert, \vert i_2-j_2\vert\}\leq 2P-1.
 	\label{eq:spacing}
 \end{align}
-In words: the starting positions of any two occurrences must be separated by at least $2L-1$ positions in each direction, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-
-From $y$, we aim to recover $x$.
-In this simplified model, we assume to know the number of  occurrences of the signal.
-In contrast, particle picking is the task of estimating the binary signal $s $, which cannot  be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
-
-%We denote the set of these nonzero values by 
-% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-%Neither the $M_i$'s nor $M$ are assumed to be known.
-
-%
-%Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
-Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
-
-%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
-%\begin{align}
-%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
-%  \label{eq:spacing}
-%\end{align}
-%The goal is to estimate $x_1,\ldots,x_K$ from $y$.
+In words: the upper left corners of any two occurrences of the target image $x$ in a micrograph must be separated by at least $2P-1$ pixels in each direction.
+Hence, each image is separated by a signal-free area that will ease the interpretation of the autocorrelation analysis. 
+From the micrographs, we aim to  recover $x$ only. In this simplified model, we assume  the total number of  occurrences of the signal across micrographs is known. 
+In the 3-D experiment we do not assume knowledge of the number of projections in the micrographs.
+%In contrast, particle picking is the task of estimating the binary signal $s $, which cannot  be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
 
@@
 
-\paragraph{Aperiodic autocorrelation functions}
-%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
-%
-%In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-%\begin{align}
-%	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
-%	\label{eq:ac_general}
-%\end{align}
-%where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-%For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
-For the purpose of this experiment, we need only the mean of the signal and its second-order autocorrelation defined for an arbitrary signal $z\in\mathbb{R}^{m\times m}$ by \TODO{to verify}
+\paragraph{Aperiodic autocorrelation functions.}
+The second-order autocorrelation of  an arbitrary image $z\in\mathbb{R}^{m\times m}$ is defined by
   \begin{align} 
- a_z^2[\ell_1,\ell_2] & = \frac{1}{m^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[i_1,i_2]z[i_1+\ell_1,i_2+\ell_2]. 
+ a_z^2[\Bell] & = \frac{1}{m^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[\ii]z[\ii+\Bell]. 
  \end{align}
- It can be shown that in the limit of $N\to\infty$,  the mean of the microgaph is equal to the mean of the signal $x$, scaled by the scalar 
+ Below, the image $z$ might be either a target image $x$ or the micrograph $y$. 
+ It can be shown that in the limit of infinitely many micrographs $K\to\infty$,  the mean pixel value of the micrographs is equal to the mean pixel value of the signal $x$, scaled by  
  \begin{align}
- \gamma & = \frac{M L^2}{N^2},
+ \gamma & = \frac{M P^2}{N^2},
  \end{align}
- which denotes the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
- Similarly, the second-order autocorrelations are related through 
- \begin{align*}
-	\lim_{N\to\infty} a_y^2[\ell_1,\ell_2] & = \gamma a_{x}^2[\ell_1,\ell_2] + \sigma^2\delta[\ell_1,\ell_2].
- \end{align*}
- These relations, and their extension to multiple planted images, are proven and discussed in~\cite{bendory2018estimation}.
-
-% 
-%Explicitly, the first-, second- and third-order autocorrelations are given by
-%\begin{align} 
-%	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-%	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-%	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-%\end{align}
-%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-%\begin{align*}
-%	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-%\end{align*}
-%%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
-%
-%\paragraph{Estimating the autocorrelation function of a single signal.}
-%
-%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
-%\begin{align}
-%	\gamma & = \frac{M L}{N}
-%%\end{align}
-%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-%
-%One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$.
-Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$.
-The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
-%\begin{align*}
-%	\E\{ a_y^1 \} & = \gamma a_x^1.
-%\end{align*}
-%We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
-%\begin{align*}
-%	\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
-%\end{align*}
-%Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
-%
-%The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations.
-Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
-As a result,
-%\begin{align*}
-%	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
-%\end{align*}
-%for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
-The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
-%Along the same lines, one can establish a relation for third-order autocorrelations:
-%\begin{align}
-%	\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
-%	\label{eq:data_ac_k1}
-%\end{align}
-%for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
-%Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
-%%
-%\paragraph{Estimating the autocorrelation function of multiple signals.}
-%
-%Returning to the general case $K \geq 1$, let $M_1, \ldots, M_K$ denote the number of occurrences of signals $x_1, \ldots, x_K$ respectively, and define
-%\begin{align}
-%	\gamma_k & = \frac{M_k L}{N}, & \gamma & = \sum_{k=1}^K\gamma_k.
-%\end{align}
-%As above, we consider the asymptotic regime where $M_1,\ldots,M_K,N\to\infty$ while preserving the ratios $\gamma_k$ constant.
-%% 
-%Still under the spacing constraint~\eqref{eq:spacing}, similarly to the developments above, one can estimate a mixture of the autocorrelations of the $K$ target signals from the autocorrelations of the micrograph:
-%\begin{align}
-%\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
-%\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
-%\end{align}
-%where $\ell, \ell_1, \ell_2 = 0, \ldots, L-1$.
-The left hand side is straightforward to estimate from data: it provides a succinct summary of it.
-The right hand side involves polynomial functions of unknowns $\gamma_1, \ldots, \gamma_K, x_1, \ldots, x_K$, and possibly $\sigma^2$.
-The task is to solve these polynomial equations in a robust way.
-
-%\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}
-
-%
-%\paragraph{Numerical experiment with three 1-D signals.}
-%
-%
-%For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
-%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting $\SNR$ of $y$
-%% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-%is about 1/9.
-%
-%
-%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-%
-%%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-%%
-%Given the observation $y$, we proceed to compute the autocorrelations.
-The first-order autocorrelation is straightforward.
-For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
-We have
-%\begin{align*}
-%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-%\end{align*}
-%coefficients in total.
-Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-%\begin{align*}
-%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-%\end{align*}
-%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$. \TODO{We may want to cite MRA literature here.}
-%
-%In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-%
-%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-%\begin{multline}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
-%\label{eq:optim1D}
-%\end{multline}
-%where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
-%
-%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-%%\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
-Not sure it's worth the effort.
--- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
-%%\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
-%%
-%%
-%
-%%\TODO{separation}
-%%
-%%For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
-%%The only difference is that here, for each
-%%placement, one of the three signals is picked at random proportionally to the desired number
-%%of occurrences of each.
-%%In this experiment, we computed the first three autocorrelation functions. 
-%%We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-%%\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
-%
-%%To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
-%%\begin{multline}
-%%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-%%\label{eq:optim1D}
-%%\end{multline}
-%%where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
-%
-%
-%%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
-%%This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-%
-%
-%
-%
-
-\paragraph{Numerical experiment with 2-D image.}
-
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
+ where $M$ is the number of occurrences of $x$ across micrographs. 
+ This  is the fraction of entries of all micrographs occupied by occurrences of $x$, that is, the  density of the signal. 
+  The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{P}{2P-1}\approx 1/2$.
+
+ % Similarly, as $K\to\infty$ the second-order autocorrelations are related through 
+ Similarly, numbering micrographs as $y_1, \ldots, y_K$, the empirical average of the second-order autocorrelations of the micrographs converges as follows:
+ \begin{align} \label{eq:a2}
+	\lim_{K \to \infty} \frac{1}{K} \sum_{k=1}^{K} a_{y_k}^2 & = \gamma a_{x}^2 + \sigma^2\delta,
+ \end{align}
+ where $\delta[\Bell]=1$ for $\Bell=(0,0)$ and zero otherwise.
+ Thus, for any noise level and without the need to even implicitly locate the images $x$ in the micrographs, given sufficiently many micrographs we are able to compute the second-order autocorrelation of $x$ itself.
+Recovering $x$ from $a_x^2$ can be done up to symmetries, as detailed below.
+ Equation~\eqref{eq:a2} is proven and its extension to higher-order autocorrelations and multiple distinct planted images is discussed in~\cite{bendory2018estimation}.
+
+\paragraph{Numerical experiment with a 2-D image.}
+
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $K$ micrographs of size $4096\times 4096$ pixels. 
 In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
@@
 Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
+An example of a micrograph's excerpt is presented in the right panel of Figure~TKTK.
 %Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
@@
 
-In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
-In stark contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction} (see also~\cite{bendory2017fourier} for a review).
-This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
-Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
+In this experiment, we assume $\gamma$ and the noise level $\sigma$ are known.
+In this setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction}.
+The second-order autocorrelation can be computed at the cost of one 2-D FFT per micrograph.
 These can be computed highly efficiently and in parallel.
-
-To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
-\begin{align*}
-	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
-\end{align*}
-on an image $z$ of size $2L\times 2L$.
-We set the parameter $\beta$ to 1.
-The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere.
+To recover the image $x$ itself, we use a standard algorithm used for phase retrieval called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
+
+%
+%To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
+%\begin{align*}
+%	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
+%\end{align*}
+%on an image $z$ of size $2L\times 2L$.
+%We set the parameter $\beta$ to 1.
+%The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere.
 The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
@@
 
-In order to compare the performance in multiple cases and at different noise levels, the algorithm is stopped after a fixed number of iterations (1000) and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
+In order to compare the performance in multiple cases and at different noise levels, the RRR is stopped after a fixed number of iterations (1000)\TODO{check} and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
 While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
 \TODO{Note the last two sentences!}
+\TODO{Let's try with the last iterate and see}
 
@@
 
-Let $\phi$ be the Coulomb potential representing the molecule we wish to recover, and denote it 3-D Fourier transform by $\widehat \phi$.
-In this paper, we assume that $\widehat\phi$ is given as a finite expansion of the form
+Let $\phi$ be the Coulomb potential representing the molecule we aim to recover. 
+We assume that molecule is real-valued and smooth. In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form
 \be\label{eq:volume_expansion} 
-\widehat \phi(k, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}a_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),
+\widehat \phi(k, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),
 \ee
-where $Y_{\ell}^m$ are complex spherical harmonics and $j_{\ell,s}$ are normalized spherical Bessel functions, see Appendix TKTK for definitions.
-\TODO{Mention somewhere that since $\phi$ is real-valued, we recover only coefficients with $m\geq 0$.} Given $\omega\in\text{SO}(3)$, denote by $I_{\omega}$ the projection obtained from viewing direction $\omega$, and denote by $\widehat I_{\omega}$ its 2-D Fourier transform.
-By the Fourier projection-slice theorem~\cite[p.
-11]{natterer1986mathematics}, the 2D Fourier transform of $I_{\omega}$ is given by \TODO{Move to appendix?}
+where $Y_{\ell}^m$ are complex spherical harmonics and $j_{\ell,s}$ are normalized spherical Bessel functions; see Appendix TKTK for further definitions.
+Let $I_{\omega}$ denote the tomographic projection obtained from viewing direction $\omega\in SO(3)$.
+By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}:
 \be\label{eq:projection_model}
-\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}a_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),\ee
-where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix rotating spherical harmonics.
-
-Let $\II\in\RR^{M\times M}$ denote a micrograph. For this paper, we assume that the micrograph consists of shifted copies of projections and perturbed by additive white Gaussian noise:
+\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),\ee
+where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix.
+
+Let $\II\in\RNN$ denote a micrograph. We assume that the micrograph consists of shifted copies of projections contaminated by additive white Gaussian noise:
 \begin{equation}\label{eq:micrograph_model}
-\II = \sum_{j=1}^{N} I_{\omega_j}\ast\delta_{\mb s_j}+ \varepsilon, \quad \varepsilon~\sim\mathcal{N}(0,\sigma^2 I),
+\II = \sum_{t=1}^{M} I_{\omega_t}\ast\delta_{\mb s_t}+ \varepsilon, \quad \varepsilon~\sim\mathcal{N}(0,\sigma^2 I),
 \end{equation}
-where the viewing directions $\omega_j$ are uniformly distributed over $\text{SO}(3)$, $\mb s_j$ denotes the location of the center of the $j$th projection in the micrograph, and we impose a separation condition similarly to Eq.~\TODO{2D}:
-\be\label{eq:sep_cond} ||\mb s_j - \mb s_i||_{\infty} \geq 2L. \ee
-\TODO{Say something about nonuniformity in practice? Remember that biologists will jump at this...}
-Define the $k$th autocorrelation of $\II$ as
-\be\label{eq:Kth_autocorrelation} 
-m_k[\II](\Delta \mb i_1,\ldots, \Delta \mb i_{k-1}) = \frac{1}{M^2}\sum_{i,j = 1}^M\II(\mb i)\II(\mb i+\Delta\mb i_1)\cdots \II(\mb i+\Delta \mb i_{k-1}),
-\ee
-where $\mb i = (i,j)$, $\Delta \mb i = (\Delta i, \Delta j)$, we require $||\Delta\mb i||_{\infty}\leq 2L-1$, and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$.
-In our procedure, we compute the first three autocorrelations, called the mean, power spectrum, and bispectrum, of the micrographs.
-\TODO{This definition and terminology should come earlier}.
-Because of the separation condition Eq.~(\ref{eq:sep_cond}), the autocorrelations of the micrograph are related to those of the projections by
+where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$, $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
+Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2L-1$ \TODO{2L?} pixels in each direction.
+%similarly to~\eqref{eq:spacing}:
+%\be\label{eq:sep_cond} \ ||\mb s_j - \mb s_i||_{\infty} \geq 2L. \ee
+Note that~\eqref{eq:model} can be also written as a sum of Delta functions as in~\eqref{eq:micrograph_model} 
+%\TODO{Say something about nonuniformity in practice? Remember that biologists will jump at this...}
+
+Define the $p$th autocorrelation of $\II$ as
+\begin{equation*} \label{eq:Kth_autocorrelation}
+a^p_\II(\Bell_1,\ldots, \Delta \Bell_{p-1}) = \frac{1}{N^2}\sum_{i,j = 1}^M\II(\mb i)\II(\mb i+\Bell_1)\cdots \II(\mb i+\Bell_{p-1}),
+\end{equation*}
+where $\mb i = (i,j)$. %, $\Delta \mb i = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
+%In our procedure, we compute the first three autocorrelations. %, called the mean, power spectrum, and bispectrum, of the micrographs. \TODO{This definition and terminology should come earlier}. 
+Under the specified condition, we show in Appendix TKTK that the first three autocorrelations  of the micrograph are related to those of the projections by 
 \begin{align} 
-m_k[\II]  \to \gamma\langle m_k[I_\omega]\rangle_{\omega} + b_k, 
+\lim_{M\to\infty}a^p_\II  = \gamma\langle a^k_{I_\omega}\rangle_{\omega} + b_p, \quad p=1,2,3,
 \end{align}
-where $\langle\cdot\rangle$ denotes averaging, $b_k$ is a bias term, and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$.
-The mean is unbiased so $b_1 = 0$, the power spectrum has bias $b_2$ depending only on $\sigma^2$, the variance of the noise, and the bias of the bispectrum $b_3$ depends additionally on the mean of $\phi$, which can be accurately estimated from the mean of the micrograph.
-We can therefore estimate the quantities $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ directly from the micrograph.
+where $\langle\cdot\rangle$ denotes averaging and $b_k$ is a bias term. %and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$. 
+More precisely,  $b_1 = 0$ and therefore the mean is unbiased.
+The bias term of the second-order autocorrelation  $b_2$ depending only on $\sigma^2$, the variance of the noise.
+Hence, if the noise level can be accurately estimated from the micrograph, this bias can be removed.
+The bias term of the third-order autocorrelation $b_3$ depends on the mean of the micrograph and $\sigma^2$.
+Therefore, given enough projections, we can accurately estimate the quantities $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ directly from the micrograph.
 

### 2018-07-27 TEX/draft_biology.tex
method section

@@
 
-\paragraph{Aperiodic autocorrelation functions.}
+%\paragraph{Aperiodic autocorrelation functions.}
 The second-order autocorrelation of  an arbitrary image $z\in\mathbb{R}^{m\times m}$ is defined by
@@
  \begin{align} \label{eq:a2}
-	\lim_{K \to \infty} \frac{1}{K} \sum_{k=1}^{K} a_{y_k}^2 & = \gamma a_{x}^2 + \sigma^2\delta,
+	\lim_{K \to \infty} \frac{1}{K} \sum_{k=1}^{K} a_{y_k}^2[\Bell] & = \gamma a_{x}^2[\Bell] + \sigma^2\delta_{(0,0)}[\Bell], \quad \Bell\in[0,P-1]^2,
  \end{align}
- where $\delta[\Bell]=1$ for $\Bell=(0,0)$ and zero otherwise.
+ where $\delta_{(i,j)}[\Bell]=1$ for $\Bell=(i,j)$ and zero otherwise.
  Thus, for any noise level and without the need to even implicitly locate the images $x$ in the micrographs, given sufficiently many micrographs we are able to compute the second-order autocorrelation of $x$ itself.
@@
 
-\paragraph{Numerical experiment with a 2-D image.}
+%\paragraph{Numerical experiment with a 2-D image.}
 
@@
 \subsection{3-D experiment}
-\TODO{Add similarities to 2-D}
-
-\TODO{Proposal: Use W for size of projection, M for size of micrograph}
 
@@
 
-Let $\II\in\RNN$ denote a micrograph. We assume that the micrograph consists of shifted copies of projections contaminated by additive white Gaussian noise:
+Let $\II\in\RNN$ denote a micrograph. We assume it consists of shifted copies of projections contaminated by additive white Gaussian noise:
 \begin{equation}\label{eq:micrograph_model}
@@
 \end{equation}
-where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$, $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
+where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$ and $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
 Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2L-1$ \TODO{2L?} pixels in each direction.
@@
 %\be\label{eq:sep_cond} \ ||\mb s_j - \mb s_i||_{\infty} \geq 2L. \ee
-Note that~\eqref{eq:model} can be also written as a sum of Delta functions as in~\eqref{eq:micrograph_model} 
+Note that~\eqref{eq:model} can be also written as a sum of $\delta$ functions as in~\eqref{eq:micrograph_model}. 
 %\TODO{Say something about nonuniformity in practice? Remember that biologists will jump at this...}
@@
 \begin{equation*} \label{eq:Kth_autocorrelation}
-a^p_\II(\Bell_1,\ldots, \Delta \Bell_{p-1}) = \frac{1}{N^2}\sum_{i,j = 1}^M\II(\mb i)\II(\mb i+\Bell_1)\cdots \II(\mb i+\Bell_{p-1}),
+a^p_\II(\Bell_1,\ldots, \Bell_{p-1}) = \frac{1}{N^2}\sum_{\mb i}\II(\mb i)\II(\mb i+\Bell_1)\cdots \II(\mb i+\Bell_{p-1}),
 \end{equation*}
-where $\mb i = (i,j)$. %, $\Delta \mb i = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
+where the summation is for $\mb i $ ranging over the $N^2$  pixels of the micrograph. %, $\Delta \mb i = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
 %In our procedure, we compute the first three autocorrelations. %, called the mean, power spectrum, and bispectrum, of the micrographs. \TODO{This definition and terminology should come earlier}. 
-Under the specified condition, we show in Appendix TKTK that the first three autocorrelations  of the micrograph are related to those of the projections by 
-\begin{align} 
-\lim_{M\to\infty}a^p_\II  = \gamma\langle a^k_{I_\omega}\rangle_{\omega} + b_p, \quad p=1,2,3,
+Let $\II_1,\ldots\II_K$ denote a set of $K$ micrographs. 
+Under the specified conditions, we show in Appendix TKTK that the first three autocorrelations  of the micrographs are related to those of the projections by \TODO{To fix}
+\begin{align} \label{eq:ac_micrographs}
+\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[0,P-1]^2, \nonumber
 \end{align}
-where $\langle\cdot\rangle$ denotes averaging and $b_k$ is a bias term. %and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$. 
-More precisely,  $b_1 = 0$ and therefore the mean is unbiased.
-The bias term of the second-order autocorrelation  $b_2$ depending only on $\sigma^2$, the variance of the noise.
-Hence, if the noise level can be accurately estimated from the micrograph, this bias can be removed.
-The bias term of the third-order autocorrelation $b_3$ depends on the mean of the micrograph and $\sigma^2$.
-Therefore, given enough projections, we can accurately estimate the quantities $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ directly from the micrograph.
+where $\langle\cdot\rangle_\omega$ denotes averaging over all possible viewing directions $\omega$ and $b_p$ is a bias term.
+%and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$.
+Specifically,  $b_1 = 0$ and therefore the mean is unbiased.
+The bias term of the second-order autocorrelation  $b_2$ depends only on $\sigma^2$, the variance of the noise.
+Hence, if the noise level can be accurately estimated from the micrographs, this bias can be removed.
+Finally, the bias term of the third-order autocorrelation $b_3$ depends on the mean of the micrograph and $\sigma^2$.
+Therefore, given sufficiently many projections, we can accurately estimate the quantities $\gamma\langle a^p_{I_{\omega}}\rangle_{\omega}$ directly from the micrographs.
+These quantities are functions of the unknown coefficients $\tamir_{l,m,s}$ and we could proceed to invert their relation, as we did in the 2-D toy example.
 
-Since we assume that the viewing directions $\omega_j$ are uniformly distributed over $\text{SO}(3)$, we would like to average over all in-plane rotations of the projections in the computation of the autocorrelations.
-To do so, we follow~\cite{landa2017steerable,zhao2016fast} and expand the second and third autocorrelations of the micrograph in Prolate Spheroidal Wave Functions (PSWFs).
-It can then be shown that the expansion coefficients $\mathfrak{m}_k$ of the autocorrelations in PSWFs are related to the expansion coefficients of the volume by
+In practice, we want to leverage one more feature of the 3-D reconstruction problem.
+Since all in-plane rotations of the micrographs are equally likely observations, 
+it is desirable in~\eqref{eq:ac_micrographs} to average over all in-plane rotations as well.
+This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs). 
+The details are in the appendix.
 
-\begin{align}\label{eq:coeffs_to_moms}
-&\mathfrak{m}_1\{a_{\ell,m,s}\} = \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0) \\ 
-&\mathfrak{m}_2\{a_{\ell,m,s}\}(q) = \frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}C_2^{(q)}(\ell,s_1,s_2)a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
- \\
-&\mathfrak{m}_3\{a_{\ell,m,s}\}(k,q_1,q_2) = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C_3^{(k,q_1,q_2)}(\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3)a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}},
-\end{align}
-see Appendix TKTK for the definitions of $C_2,C_3$.
-
-To recover the expansion coefficients $\{a_{\ell,m,s}\}$ from the autocorrelation coefficients estimated from the micrograph $\mk m_k[\II]$, we minimize the weighted least-squares problem
-\be\label{eq:min_problem_cryo} \min_{\{a_{\ell,m,s}\}} \sum_{k=1}^3\frac{\Big|\Big|\mk m_k\{a_{\ell,m,s}\} - \mk m_k[\II]\Big|\Big|_F^2}{||\mk m_k[\II]||_F^2}.\ee
+% as follows. We scan the micrographs with a $P\times P$ window. We expand each window in Prolate Spheroidal Wave Functions (PSWFs) 
+%and compute the  second and third autocorrelations in that basis.
+In PSWFs, it is straightforward to average over all in-plane rotations~\cite{landa2017steerable,zhao2016fast}.
+We further average over all windows, resulting in autocorrelation in the PSWF coefficients.
+%It can be shown that the PSWF coefficients of the data $\mathfrak{a}^p$  are related to the expansion coefficients of the volume~\eqref{eq:volume_expansion} by
+%\begin{align}\label{eq:coeffs_to_moms}
+%&\mathfrak{a}^1_x = \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0), \\ 
+%&\mathfrak{a}^2_x(q) = \frac{1}{2\sqrt{2\pi}}\sum_{\substack{\ell,m\\s_1,s_2}}C_2^{(q)}(\ell,s_1,s_2)a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}},
+% \\
+%&\mathfrak{a}^3_x(k,q_1,q_2) = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C_3^{(k,q_1,q_2)}(\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3)a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}.
+%\end{align}
+%The definitions of $C_2$ and $C_3$ are provided in Appendix TKTK.
+%
+%To recover the expansion coefficients $\{a_{\ell,m,s}\}$ from the autocorrelation coefficients estimated from the micrograph $\mk m_k[\II]$, we minimize the weighted least-squares problem
+%\be\label{eq:min_problem_cryo} \min_{\{a_{\ell,m,s}\}} \sum_{k=1}^3\frac{\Big|\Big|\mk m_k\{a_{\ell,m,s}\} - \mk m_k[\II]\Big|\Big|_F^2}{||\mk m_k[\II]||_F^2}.\ee
 

### 2018-07-27 TEX/draft_biology.tex
afternoon session

@@
 \section{Discussion}
-\TODO{I suggest starting the Discussion section with a summary statement highlighting the significance of the work. Something along the lines (this is not polished, just to give you a rough idea): 
-	"In this paper we illustrated that it is possible to determine the 3-D molecular structure in single particle cryo-EM directly from the micrographs without performing particle picking.
-Our work implies that it is possible to reconstruct arbitrarily small molecules, in particular, molecules that are too small to being detected and located in micrographs.
-Ultimately, this work significantly increases the range of molecules to which cryo-EM can be successfully applied."
-
+
+In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
+Our strategy is to compute autocorrelation functions of the micrographs and to relate these statistics to the unknown volume's parameters.
+Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
+Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
+Concerns for model bias are also greatly reduced since no template matching is involved.
+
+Looking towards applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, in particular, molecules that are too small to be detected in micrographs.
+In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
+We recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
+
+%As a result, it may not be limited to large molecules in the same way that particle picking approaches are. 
+%In this paper, we illustrated that it is possible to determine the 3-D molecular structure in single particle cryo-EM directly from the micrographs without performing particle picking, at least in controlled experiments.
+
+\TODO{
 	We should also incorporate Alberto's comment that our technique also allows to use much lower defocus values.
@@
 }
-%\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
 
@@
 %
-
-In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
-Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
-As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
-Concerns for model bias would also greatly be reduced.
 
@@
 
-Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
-
 One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
 Still, large amounts of data also imply large amounts of computations.
-On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs.
+On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
 It can even be done in streaming mode, as only one look at each micrograph is necessary.
@@
 First, we assume an additive white noise model, while in practice the noise may be correlated or signal dependent.
-To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly.
-\TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc..
-}
-Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals.
+To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods.
+% and to extend the autocorrelation analysis accordingly.
+ Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
 Perhaps this separation could be induced by careful experimental design \TODO{?}.
 Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
-Here as well, relations between autocorrelation functions of the data and of the signals can be derived.
-
-We also admit several aspects of SPR experiments that were neglected in this paper, including power spectrum estimation, Contrast Transfer Function (CTF) correction and the non-uniformity of the viewing directions.
-All this aspects must be taken into account so the method could be applied on real data.
-We hope to take care of this issues in a future research, as well extending this method for the possibility to estimate several volumes simultaneously.
+Here as well, relations between autocorrelations of the micrographs and of the volume could be derived.
+
+We also note several aspects of SPR experiments that were neglected in this paper, including Contrast Transfer Function (CTF) correction and the non-uniformity of the viewing directions.
+All these aspects must be taken into account so the method could be applied on real data.
+We hope to take care of these issues in future research, as well to extend the proposed method to conformational heterogeneity.
+\TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
 %
@@
 Let $\II_1,\ldots\II_K$ denote a set of $K$ micrographs. 
-Under the specified conditions, we show in Appendix TKTK that the first three autocorrelations  of the micrographs are related to those of the projections by \TODO{To fix}
-\begin{align} \label{eq:ac_micrographs}
+Under the specified conditions, we show in Appendix TKTK that the first three autocorrelations  of the micrographs are related to those of the projections by \begin{align} \label{eq:ac_micrographs}
 \lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[0,P-1]^2, \nonumber
@@
 it is desirable in~\eqref{eq:ac_micrographs} to average over all in-plane rotations as well.
-This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs). 
+This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs).  We use autocorrelations up to and including the  third order since this is necessary to  determine the volume.
 The details are in the appendix.

### 2018-07-30 TEX/draft_biology.tex
Small changes

@@
 As a proof of concept, we study a simplified model for 3-D reconstruction directly from the micrograph on a simulated data. 
-In order to recover the 3-D volume, we use autocorrelation analysis.
-In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume \TODO{To mention the expansions?}.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and are the latter are separated in the micrograph.
+In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the volume.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and the latter are separated in the micrograph.
 Importantly, there is no need to detect the projections.
@@
 Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
+In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
 In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.

### 2018-07-30 TEX/draft_biology.tex
Rewrote part of the appendix

--- 2018-07-27 TEX/draft_biology.tex
@@
 \newcommand{\mk}{\mathfrak}
+\newcommand{\mc}{\mathcal}
+
 \newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
@@
 
-\TODO{To rewrite for the discrete case}
-
-We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{N}{M^2}\in(0,1)$ is a constant. 
+We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is a constant. 
 Because of the separation condition Eq.~(\ref{eq:sep_cond}), if $\mb i$ is in the support of the $j$th projection, then $\mb i + \Delta\mb i$ is either in the support of the same projection or outside the support of any projection.
-Formally, $\mb i$ is in the support of the $j$th projection if and only if $\mb 0\leq \mb i - \mb s_j < (L,L)^T$ where the inequalities apply to each coordinate.
-Then because of the separation condition,
-
-note that if $\rr\in S_i$ for some $i$, then $\rr+\Delta\rr\in S_i\cup Z$ whenever $||\Delta\rr||\leq 2L$ by the separation assumption $d> 2L$.
-Since $\RR^2=Z\sqcup\bigsqcup_{i=1}^NS_i$, and $\II(\rr)=0$ if $\rr\in Z$, we have for $||\Delta\rr||\leq 2L$
-\[\begin{aligned} m_2[\II](\Delta \rr)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
-&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr)\, d\rr\\ 
-&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr)\, d\rr\\ 
-&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_2[I_{\omega_i}](\Delta\rr)\\
-&\to \gamma\int_{\text{SO}(3)}L^2m_2[I_{\omega}](\Delta\rr)\, d\omega.\end{aligned}\]
-If we set $m_2(\Delta \rr) = 0$ for $||\Delta\rr||>2L$, the above equality holds for all $\Delta\rr$, and taking its Fourier transform (with respect to $\Delta\rr$) and interchanging the Fourier integral with the integral over SO(3) (which can \emph{always} be done), we get
-\[ \widehat{m_2[\II]}(\kk) \to \gamma\int_{\text{SO}(3)}L^2\widehat{m_2[I_{\omega}]}(\kk)\, d\omega = \gamma\langle|\widehat I_{\omega}(\kk)|^2\rangle_{\omega},\]
-where $\langle\cdot\rangle_{\omega}$ denotes average over the orientations, so over SO(3).
-
-Similarly, for the third moment if $\rr\in S_i$ for some $i$ then $\rr+\Delta\rr_1,\rr+\Delta\rr_2\in S_i\cup Z$, and hence we again get for $||\Delta\rr_1||\leq 2L$ and $||\Delta\rr_2||\leq 2L$ that
-\[\begin{aligned} m_3[\II](\Delta \rr_1,\Delta\rr_2)  &= \frac{1}{M^2}\int_{\RR^2}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
-&= \frac{1}{M^2}\int_Z\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr + \frac{1}{M^2}\sum_{i=1}^N\int_{S_i}\II(\rr)\II(\rr+\Delta\rr_1)\II(\rr+\Delta\rr_2)\, d\rr\\ 
-&= \frac{1}{M^2}\sum_{i=1}^N\int_{\RR^2}I_{\omega_i}(\rr)I_{\omega_i}(\rr+\Delta\rr_1)I_{\omega_i}(\rr+\Delta\rr_2)\, d\rr\\ 
-&= \frac{N}{M^2}\cdot\frac{1}{N}\sum_{i=1}^NL^2m_3[I_{\omega_i}](\Delta\rr_1,\Delta\rr_2)\\
-&\to \gamma\int_{\text{SO}(3)}L^2m_3[I_{\omega}](\Delta\rr_1,\Delta\rr_2)\, d\omega.\end{aligned}\]
-Again, setting $m_3(\Delta\rr_1,\Delta\rr_2)=0$ if either $||\Delta\rr_1||>2L$ or $||\Delta\rr_2||>2L$, we also get
-\[ \widehat{m_3[\II]}(\kk_1,\kk_2) = \gamma\langle\widehat I_{\omega}(\kk_1)\widehat I_{\omega}(\kk_2)\overline{\widehat I_{\omega}(\kk_1+\kk_2)}\rangle_{\omega}.\]
+Formally, $\mb i$ is in the support of the $j$th projection if and only if $0\leq \mb i - \mb s_j < L$ where the inequalities apply to each coordinate.
+Then for $||\Delta\mb i||_{\infty}\leq L-1$ we have
+\[-(L-1) \leq \mb i+\Delta\mb i-\mb s_j< 2L-1,\]
+and because of the separation condition, given $\mb s_k$ we must either have $\mb s_k-\mb s_i\geq 2L-1$ in which case 
+\[ \mb i + \Delta\mb i- \mb s_k \leq \mb i + \Delta\mb i- \mb s_j - (2L-1) < 0,\]
+or $\mb s_k - \mb s_i \leq -(2L-1)$, in which case
+\[ \mb i + \Delta\mb i - \mb s_k \geq -(L-1) + 2L-1 = L.\]
+In either case, $\mb i+\Delta\mb i$ is not in the support of the $k$th particle.
+
+Denote by $\mc S_j$ the support of the $j$th particle and by $Z=\{1,\ldots, M\}-\sqcup_j \mc S_j$ all the points outside the support of the particle.
+The clean micrograp $\widetilde \II = \II-\xi$ then satisfies $\widetilde \II(\mb i) = 0$ if $\mb i\in Z$, so we have
+\be\begin{aligned} 
+m_k[\widetilde\II](\Delta\mb i_1,\ldots, \Delta\mb i_{k-1}) &= \frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1})\\
+&= \frac{1}{M^2}\sum_{j=1}^N\sum_{\mb i\in\mc S_i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1}) + \frac{1}{M^2}\sum_{\mb i\in Z}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1})\\
+&= \frac{NL^2}{M^2}\cdot\frac{1}{N}\sum_{j=1}^N\frac{1}{L^2}\sum_{i,j=1}^L I_{\omega_j}(\mb i)I_{\omega_j}(\mb i+\Delta\mb i_1)\cdots I_{\omega_j}(\mb i + \Delta \mb i_{k-1})\\
+&= \frac{NL^2}{M^2}\frac{1}{N}\sum_{j=1}^Nm_k[I_{\omega_j}]\\
+&\to \gamma\langle m_k[I_{\omega_j}]\rangle_{\omega}. \end{aligned}\ee
+
+In the precence of noise, we get an additional bias term, which we proceed to derive. The mean is unbiased, since the noise is assumed to have zero mean. For the power spectrum, we have
+\[\begin{aligned}
+&m_2[\II](\Delta \mb i) =
+\frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\II(\mb
+i+\Delta \mb i)\\
+&= \frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\widetilde\II(\mb i+\Delta \mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i)\\ &+ \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\xi(\mb i + \Delta\mb i).
+\end{aligned}\]
+Considering the terms one-by-one, the first term is independent of the
+noise, and as shown above converges to $\gamma \langle
+m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
+satisfies
+\[\begin{aligned} 
+\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i) &=
+\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
+i)\xi_{\omega_j}(\mb i + \Delta\mb i)\\
+&\to \gamma\mathbb{E}_{\omega,\xi}[I_{\omega}\xi]\\ 
+&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\xi}[\xi] = 0, \end{aligned}\]
+where $\xi_{\omega_j}(\mb i) = \xi(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\xi$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$.
+A similar argument applied to the third term shows that it
+also vanishes as $N\to\infty$. 
+For the fourth term,
+if $\Delta\mb i \neq \mb{0}$ then since the noise is zero mean and
+i.i.d. this term vanishes. If $\Delta\mb i = \mb0$ then
+\[ \frac{1}{m^2}\sum_{i,j=1}^m\xi(\mb i)^2 \to \sigma^2.\]
+Thus, we conclude
+\[ m_2[\II](\Delta\mb i) \to \gamma\langle m_2[I_{\omega}](\Delta\mb i)\rangle_{\omega} + \sigma^2\delta(\Delta\mb i).\]
+Note that the bias term $b_2 = \sigma^2\delta(\Delta\mb i)$ depends only on the variance of the noise $\sigma^2$.
+
+For the third moments, we get 8 terms:
+\[\begin{aligned} 
+&m_3[\II](\Delta\mb i_1, \Delta\mb i_2) =
+\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i+\Delta\mb
+	i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(1)} +
+\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i+\Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(2)}\\ 
+&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(3)} +
+\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(4)}\\
+&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(5)} +
+\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(6)}\\
+&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(7)} +
+\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(8)}.
+\end{aligned}\]
+We address these terms one by one:
+\begin{itemize}
+	\item Term (1) is $m_3[\widetilde\II]$, shown above to converge to
+	$\gamma\langle m_3[I_{\omega}]\rangle_{\omega}$.
+	\item Term (2) is $m_3[\xi]$, the bispectrum of pure noise, which
+	vanishes \TODO{Either cite a signal processing paper, or show ourselves}
+	\item Terms (3)-(5) depend linearly on the noise and hence
+	converge to zero.
+	\item For term (6), if $\Delta\mb i_1\neq \Delta\mb i_2$ the term
+	vanishes as then $\xi(\mb i + \Delta\mb i_1)$ and $\xi(\mb i +
+	\Delta\mb i_2)$ are independent. If $\Delta\mb i_1 = \Delta\mb
+	i_2$ the term becomes
+	\[ \begin{aligned}
+        \frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)^2
+      &= \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb
+		i}I_{\omega_j}(\mb i)\xi_{\omega_j}(\mb i + \Delta\mb i)^2\\ 
+      &\to \gamma\mathbb{E}_{\omega, \xi}[\xi^2I_{\omega}]\\
+      &= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
+      &= \gamma\sigma^2Lm_1[\phi],
+    \end{aligned}\]
+	where $m_1[\phi]$ is the mean of the volume.
+That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
+	\item For term (7), if $\Delta\mb i_1 \neq \mb 0$ then once again
+	this term vanishes, whereas if $\Delta\mb i_2 = \mb 0$ then it becomes
+	\[ \frac{1}{M^2}\sum_{\mb i}\xi(\mb i)^2\widetilde\II(\mb i + \Delta\mb
+	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
+		i}\xi_{\omega}(\mb i)^2I_{\omega}(\mb i + \Delta\mb i_2) \to
+	\gamma\sigma^2Lm_1[\phi].\]
+	Similarly, term (8) vanishes if $\Delta\mb i_2\neq \mb 0$ and
+	converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
+\end{itemize}
+Thus, we conclude that
+\[ m_3[\II](\Delta\mb i_1, \Delta\mb i_2) \to \gamma\langle
+m_3[I_{\omega}](\Delta\mb i_1, \Delta\mb i_2)\rangle_{\omega} +
+\gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
+\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big).\]
+Note that in practice, we have $m_1[\II] \approx m_1[\widetilde\II] \approx \gamma
+Lm_1[\phi]$ since the mean converges relatively fast to its expectation (at a rate of $1/M$), so we do not need prior knowledge of $\gamma$ to effectively
+debias the bispectrum.
 
 \section{Steering}\label{sec:steering}
-The first two moments are cheap to compute and store - $m_1$ is a scalar and $m_2$ is radially symmetric (in the limit $N\to\infty$), so it suffices to compute a single ray of it.
-The third moment however is infeasible to store - it has $(2L-1)^4$ entries, and in modern microscopes we can easily have $L\geq 300$.
-In addition, the above scheme does not average over in-plane rotations, which can improve estimation in the precense of noise (and accelerate convergence to the population moments without noise).
-We therefore propose the following steering procedure:
-
-The third moment $m_3[\II](\Delta \rr_1,\Delta \rr_2)$ as defined above is compactly supported (at least numerically) with respect to each of its variables in both real and Fourier space, with support radii $2L$ and $1/2$ in real and Fourier space, respectively (see above formulas for $m_3$ in real and Fourier space).
-Therefore, we can expand it in a suitable product basis that is compactly supported in both real and Fourier space, e.g.
-Prolate Spheroidal Wave Functions (PSWFs) or Fourier-Bessel (FB):
-\[ m_3[\II](\Delta \rr_1, \Delta \rr_2) = \sum_{k_1,k_2=-\infty}^{\infty}\sum_{q_1,q_2=1}^{\infty}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\rr_1)\overline{\psi_{k_2,q_2}(\Delta\rr_2)},\]
-where we conjugate the second set of basis functions for convenience, that will become apparent below (of course, the set of conjugates is also a basis, as $\overline{\psi_{k,q}}=\psi_{-k,q}$ for PSWFs and $\overline{\psi_{k,q}}=(-1)^k\psi_{-k,q}$ for FB).
-We shall assume that the basis $\{\psi_{k,q}(\rr)\}$ is orthonormal, so $\int_{\RR^2}\psi_{k_1,q_1}(\rr)\overline{\psi_{k_2,q_2}}(\rr) = \delta_{k_1,k_2}\delta_{q_1,q_2}$, valid for both PSWFs and FB.
-Then, the coefficients are given by
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{||\Delta\rr_1||,||\Delta\rr_2||\leq 2L}m_3[\II](\Delta\rr_1,\Delta\rr_2)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\psi_{k_2,q_2}(\Delta\rr_2)\\
-&= \int_{\rr}\II(\rr)\left(\int_{||\Delta\rr_1||\leq 2L}\II(\rr+\Delta\rr_1)\overline{\psi_{k_1,q_1}}(\Delta\rr_1)\right)\left(\int_{||\Delta\rr_2||\leq 2L}\II(\rr+\Delta\rr_2)\psi_{k_2,q_2}(\Delta\rr_2)\right).\end{aligned}\]
-Note that if we expand $\II(\rr+\Delta\rr)$ in $\{\psi_{k,q}(\Delta\rr)\}$ for fixed $\rr$ and $||\Delta\rr||\leq 2L$, so
-\[ \II(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}(\rr)\psi_{k,q}(\Delta\rr),\quad a_{k,q}(\rr)=\int_{||\Delta\rr||\leq 2L}\II(\rr+\Delta\rr)\overline{\psi_{k,q}}(\Delta\rr),\]
-and use the fact that $\II$ is real, our expression becomes
-\[ \mathfrak{m}_3(k_1,q_1;k_2,q_2) = \int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr).\]
-
-We further assume that all in-plane rotations of the micrograph and its reflection, or equivalently, all in-plane rotations of each such disc of radius $2L$ and its reflection, are present in our dataset.
-Noting that rotations and reflections commute with the Fourier transform and using the derivation of [Zhao, Landa], the expansion of the disc about $\rr$ by an angle $\alpha$ is given by
-\[ \II^{\alpha,+}(\rr+\Delta\rr) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
-and the expansion of the reflection of that disc rotated by an angle $\alpha$ by
-\[ \II^{\alpha,-}(\rr+\Delta\rr) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\rr),\]
-where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. We thus have
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr) + \overline{a_{k_1,q_1}}(\rr)a_{k_2,q_2}(\rr)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
-&= \delta_{k_1,k_2}\int_{\rr}\II(\rr)\Re\{a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\}\\
-&= \Re\left\{\delta_{k_1,k_2}\int_{\rr}\II(\rr)a_{k_1,q_1}(\rr)\overline{a_{k_2,q_2}}(\rr)\right\},\end{aligned}\]
-Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
-
-Similarly, the power spectrum is compactly supported in space (with
-support $2L-1$) and bandlimited as in Fourier space it is the average
-squared magnitude of the Fourier transform of the projections, each
-of which is supposedly bandlimited. Therefore, we may expand it as
-\[ m_2[\II](\Delta\rr) =
-\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\rr),\]
-and obtain the expansion coefficients as
+The clean autocorrelations $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ which we estimate from the micrograph are given by an average over the particule orientations.
+In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
+For this paper, we represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see \cite{landa2017steerable}.
+The PSWFs are eigenfunctions of the truncated Fourier trasnform and satisfy
+\be\label{eq:PSWF_defn_eq}
+\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi i (\mb i-\mb 1)\cdot(\mb k - \mb 1)}
+\ee
+given in polar coordinates by
+\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{ik\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
+and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}
+
+The mean is a scalar and is already invariant under in-plane rotations of the projections in the dataset, since all projections have the same mean $Lm_1[\phi]$, as explained above.
+For the power spectrum, we expand it as
+\[ m_2[\II](\Delta\mb i) =
+\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
+where the expansion is truncated according to the rule in \cite{landa2017steerable}, and obtain the expansion coefficients as
 \[\begin{aligned} 
 \mathfrak{m}_2(k,q) &=
-\int_{\Delta\rr}m_2[\II](\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
+\sum_{\Delta\mb i}m_2[\II](\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
 &=
-\int_{\rr}\II(\rr)\int_{\Delta\rr}\II(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}\\
-&= \int_{\rr}\II(\rr)a_{k,q}(\rr). \end{aligned}\]
-Taking all rotations of $\II$ and its reflection, we get
+\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i}\II(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{k,q}(\mb i), \end{aligned}\]
+where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II(\mb i)$ in PSWFs as
+\[ \II(\mb i + \Delta\mb i) = \sum_{k,q}a_{k,q}(\mb i)\psi_{k,q}(\Delta\mb i),\quad ||\Delta\mb i||_{\infty}\leq L-1,\]
+the expansion coefficients are given by the inner product
+\[ a_{k,q}(\mb i) = \sum_{\Delta\mb i}\II(\mb i + \Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
+As shown in \cite{landa2017steerable, zhao2016fast}, the rotation of the above patch by an angle $\alpha$ is given by
+\[ \II^{\alpha,+}(\mb i+\Delta\mb i) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
+and the reflection of that disc rotated by an angle $\alpha$ by
+\[ \II^{\alpha,-}(\mb i+\Delta\mb i) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
+where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
+Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
 \[\begin{aligned} 
-\mathfrak{m}_2(k,q) &= \int_{\rr}\II(\rr)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\rr) +
-\overline{a_{k,q}}(\rr)]e^{-ik\alpha}\, d\alpha\right)\\ 
-&= \delta_{k,0} \int_{\rr}\II(\rr)a_{0,q}(\rr), \end{aligned}\]
+\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\mb i) +
+\overline{a_{k,q}}(\mb i)]e^{-ik\alpha}\, d\alpha\right)\\ 
+&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{0,q}(\mb i), \end{aligned}\]
 where in the last equality we dropped the real part since both
-$\II(\rr)$ and $\psi_{0,q}$ are real valued, and hence $a_{0,q}(\rr)=\int_{\Delta\rr}\II(\rr+\Delta\rr)\psi_{0,q}(\Delta\rr)$
-is real as well.
-Thus, the average power spectrum is effectively a vector.
-
+$\II$ and $\psi_{0,q}$ are real valued.
+Thus, the average power spectrum is effectively a vector. To estimate the clean power spectrum coefficients, we also expand the bias term in PSWFs. Writing
+\[ b_2(\Delta\mb i) = \sigma^2\delta(\Delta\mb i) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
+the coefficients are given by
+\[\begin{aligned} 
+\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Delta\mb i}\delta(\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
+&= \sigma^2\overline{\psi_{k,q}(\mb 0)}\\
+&= \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
+We then estimate the expansion coefficients of the clean power spectrum as
+\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]
+
+We expand the bispectrum as
+\[ m_3[\II](\Delta \mb i_1, \Delta \mb i_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
+The expansion coefficients are then given by
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Delta\mb i_1, \Delta\mb i_2}m_3[\II](\Delta\mb i_1,\Delta\mb i_2)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\psi_{k_2,q_2}(\Delta\mb i_2)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i_1}\II(\mb i+\Delta\mb i_1)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\right)\left(\sum_{\Delta\mb i_2}\II(\mb i+\Delta\mb i_2)\psi_{k_2,q_2}(\Delta\mb i_2)\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i) a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}.
+\end{aligned}\]
+Averaging over all rotations of $\II$ and its reflection, we obtain
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)} + \overline{a_{k_1,q_1}(\mb i)}a_{k_2,q_2}(\mb i)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
+&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\Re\{a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}\}.\end{aligned}\]
+Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
+Similarly to the power spectrum, we also expand the bias term in PSWFs as
+\[ b_3(\Delta\mb i_1, \Delta\mb i_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
+\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
+b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
+where the coefficients are given by
+\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2 m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
 \section{Connection to volume}
@@
 We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
-\[ \widehat V(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\]
-for $k\leq 1$ and zero otherwise, where $c$ is the assumed bandlimit, $Y_{\ell,m}$ may be taken to be either real or complex, and $j_{\ell,s}(r)$ is some radial basis function (in practice, either spherical bessel or the radial part of the 3D PSWFs as in [Lederman]).
-We work here with the complex spherical harmonics, given by
+\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
+where $k=||\kk||_2$, $c$ is the assumed bandlimit, $Y_{\ell}^m$ is the complex spherical harmonics
 \[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
+
 where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase, and $j_{\ell,s}$ are normalized spherical Bessel functions given by
@@
 \[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}a_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta},\]
-whenever $k\leq 1$. Express this in 2D PSWFs so
+whenever $k\leq 1$. Express this in 2D PSWFs so \TODO{Eitan: I stopped here}
 \[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
@@
 We then consider the product
-\[\begin{aligned} m_3(\Delta\rr_1,\Delta\rr_2) &= \int_{\rr}\langle I_{\omega}(\rr)I_{\omega}(\rr+\Delta\rr_1)\overline{I_{\omega}(\rr+\Delta\rr_2)}\rangle_{\omega},\\
-&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\int_{\rr}\psi_{N_1,n_1}(\rr)\psi_{N_2,n_2}(\rr+\Delta\rr_1)\overline{\psi_{N_3,n_3}(\rr+\Delta\rr_2)}.\end{aligned}\]
+\[\begin{aligned} m_3(\Delta\mb i_1,\Delta\mb i_2) &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}(\mb i)I_{\omega}(\mb i+\Delta\mb i_1)\overline{I_{\omega}(\mb i+\Delta\mb i_2)}\rangle_{\omega},\\
+&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}(\mb i)\psi_{N_2,n_2}(\mb i+\Delta\mb i_1)\overline{\psi_{N_3,n_3}(\mb i+\Delta\mb i_2)}.\end{aligned}\]
 Now,
@@
 Finally, we expand
-\[ m_3(\Delta\rr_1,\Delta\rr_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Delta\rr_1)\overline{\psi_{k,q_2}(\Delta\rr_2)},\]
+\[ m_3(\Delta\mb i_1,\Delta\mb i_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Delta\mb i_1)\overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
 where we only include the block-diagonal terms in the expansion. Defining
-\[ \Psi_{\ell,N,s}(\rr) = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}(\rr),\]
+\[ \Psi_{\ell,N,s}(\mb i) = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}(\mb i),\]
 the final formula reads
@@
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)}, \end{aligned}\]
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)}, \end{aligned}\]
 where
-\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.\]
-In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\rr$ and over $\Delta\rr$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
+\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Delta\mb i}\Psi_{\ell,N,s}(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
+In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\mb i$ and over $\Delta\mb i$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
 
@@
 $Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude that
-\[ m_1[V] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]
+\[ m_1[\phi] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]
 
@@
 &C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)},
 \end{align*}
@@
 \begin{align*}
-\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\rr}\Psi_{\ell,N,s}(\rr+\Delta\rr)\overline{\psi_{k,q}(\Delta\rr)}.
+\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\mb i}\Psi_{\ell,N,s}(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.
 \end{align*}
@@
 and
-\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\int_{\rr}\Psi_{\ell_1,N_1,s_1}(\rr)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\rr)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\rr)},\]
+\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)},\]
 so in each iteration of the optimization we compute
@@
 
-For the power spectrum:
-\[\begin{aligned}
-&m_2[\II + \xi](\Delta \mb i) =
-\frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\widetilde\II(\mb
-i+\Delta \mb i)\\
-&= \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\II(\mb i+\Delta \mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\xi(\mb i + \Delta\mb i)\\ &+ \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\II(\mb i + \Delta\mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\xi(\mb i + \Delta\mb i).
-\end{aligned}\]
-Considering the terms one-by-one, the first term is independent of the
-noise, and as shown above converges to $\gamma \langle
-m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. Denoting the center
-of the instance of $I_{\omega}$ in $\II$ by $\mb s_{\omega}$, the second term
-satisfies
-\[\begin{aligned} 
-\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i) &=
-\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb i}I_{\omega}(\mb
-i)\xi_{\omega}(\mb i + \Delta\mb i)\\
-&\to \gamma \mathbb{E}[\xi]\mathbb{E}[I_{\omega}] = 0, \end{aligned}\]
-where $\xi_{\omega}(\mb i) = \xi(\mb i + \mb s_{\omega})$ and
-$\mathbb{E}[I_{\omega}]$ is proportional to the mean of the
-volume. A similar argument applied to the third term shows that it
-also vanishes as $N\to\infty$. 
-For the fourth term,
-if $\Delta\mb i \neq \mb{0}$ then since the noise is zero mean and
-i.i.d. this term vanishes. If $\Delta\mb i = \mb0$ then
-\[ \frac{1}{m^2}\sum_{i,j=1}^m\xi(\mb i)^2 \to \sigma^2.\]
-Thus, we conclude
-\[ m_2[\II+\xi](\Delta\mb i) \to \gamma\langle m_2[I_{\omega}](\Delta\mb i)\rangle_{\omega} + \sigma^2\delta(\Delta\mb i).\]
-
-For the third moments, we get 8 terms:
-\[\begin{aligned} 
-&m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) =
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i+\Delta\mb
-	i_1)\II(\mb i + \Delta\mb i_2)}_{(1)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i+\Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(2)}\\ 
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(3)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(4)}\\
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(5)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(6)}\\
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i + \Delta\mb i_1)\II(\mb i + \Delta\mb i_2)}_{(7)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(8)}.
-\end{aligned}\]
-We address these terms one by one:
-\begin{itemize}
-	\item Term (1) is $m_3[\II]$, shown above to converge to
-	$\gamma\langle m_3[I_{\omega}]\rangle_{\omega}$.
-	\item Term (2) is $m_3[\xi]$, the bispectrum of pure noise, which
-	vanishes as shown above.
-	\item Terms (3)-(5) depend linearly on the noise and hence
-	converge to zero.
-	\item For term (6), if $\Delta\mb i_1\neq \Delta\mb i_2$ the term
-	vanishes as then $\xi(\mb i + \Delta\mb i_1)$ and $\xi(\mb i +
-	\Delta\mb i_2)$ are independent. If $\Delta\mb i_1 = \Delta\mb
-	i_2$ the term becomes
-	\[ \frac{1}{M^2}\sum_{\mb i}\II(\mb i)\xi(\mb i + \Delta\mb i_1)^2
-	= \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega, \mb
-		i}I_{\omega}(\mb i)\xi_{\omega}(\mb i + \Delta\mb i)^2 \to
-	\gamma\sigma^2\mathbb{E}[I_{\omega}] =
-	\gamma\sigma^2Lm_1[V],\]
-	where $m_1[V]$ is the mean of the volume (and hence also the
-	mean of each projection $I_{\omega}$).
-	\item For term (7), if $\Delta\mb i_1 \neq \mb 0$ then once again
-	this term vanishes, whereas if $\Delta\mb i_2 = \mb 0$ then it becomes
-	\[ \frac{1}{M^2}\sum_{\mb i}\xi(\mb i)^2\II(\mb i + \Delta\mb
-	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
-		i}\xi_{\omega}(\mb i)^2I_{\omega}(\mb i + \Delta\mb i_2) \to
-	\gamma\sigma^2Lm_1[V].\]
-	Similarly, term (8) vanishes if $\Delta\mb i_2\neq \mb 0$ and
-	converges to $\gamma\sigma^2Lm_1[V]$ otherwise.
-\end{itemize}
-Thus, we conclude that
-\[ m_3[\II+\xi](\Delta\mb i_1, \Delta\mb i_2) \to \gamma\langle
-m_3[I_{\omega}](\Delta\mb i_1, \Delta\mb i_2)\rangle_{\omega} +
-\gamma\sigma^2Lm_1[V]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
-\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big).\]
-Note that in practice, we have $m_1[\II+\xi] \to m_1[\II] \approx \gamma
-Lm_1[V]$ since the noise has zero mean, so we do not need prior knowledge of $\gamma$ to effectively
-debias the bispectrum.
-
 \subsection{Expansion in PSWFs}
@@
 To this end, writing (in the continuous case again)
-\[ \delta(\Delta\rr_1 - \Delta\rr_2) =
-\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Delta\rr_1)
-\overline{\psi_{k,q_2}(\Delta\rr_2)},\]
+\[ \delta(\Delta\mb i_1 - \Delta\mb i_2) =
+\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Delta\mb i_1)
+\overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
 we get
 \[\begin{aligned}
-\mathfrak{d}(k,q_1,q_2) &= \int_{\Delta\rr_1,
-	\Delta\rr_2}\delta(\Delta\rr_1-\Delta\rr_2)\overline{\psi_{k,q_1}(\Delta\rr_1)}\psi_{k,q_2}(\Delta\rr_2)\\
+\mathfrak{d}(k,q_1,q_2) &= \int_{\Delta\mb i_1,
+	\Delta\mb i_2}\delta(\Delta\mb i_1-\Delta\mb i_2)\overline{\psi_{k,q_1}(\Delta\mb i_1)}\psi_{k,q_2}(\Delta\mb i_2)\\
 &=
-\int_{\Delta\rr_2}\overline{\psi_{k,q_1}(\Delta\rr_2)}\psi_{k,q_2}(\Delta\rr_2)\\
+\int_{\Delta\mb i_2}\overline{\psi_{k,q_1}(\Delta\mb i_2)}\psi_{k,q_2}(\Delta\mb i_2)\\
 &= \delta_{q_1,q_2}.
@@
 Similarly, writing
-\[ \delta(\Delta\rr_1) =
+\[ \delta(\Delta\mb i_1) =
 \sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
-\psi_{k,q_1}(\Delta\rr_1) \overline{\psi_{k,q_2}(\Delta\rr_2)},\]
+\psi_{k,q_1}(\Delta\mb i_1) \overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
 we get
 \[\begin{aligned} 
-\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Delta\rr_1,
-	\Delta\rr_2}\delta(\Delta\rr_1)\overline{\psi_{k,q_1}(\Delta\rr_1)}
-\psi_{k,q_2}(\Delta\rr_2)\\
+\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Delta\mb i_1,
+	\Delta\mb i_2}\delta(\Delta\mb i_1)\overline{\psi_{k,q_1}(\Delta\mb i_1)}
+\psi_{k,q_2}(\Delta\mb i_2)\\
 &= \overline{\psi_{k,q_1}(\mb 0)}
-\int_{\Delta\rr_2}\psi_{k,q_2}(\Delta\rr_2)\\
+\int_{\Delta\mb i_2}\psi_{k,q_2}(\Delta\mb i_2)\\
 &= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
@@
 $J_0(0)=1$. 
-A similar derivation applies to $\delta(\Delta\rr_2)$.
+A similar derivation applies to $\delta(\Delta\mb i_2)$.
 

### 2018-07-30 TEX/draft_biology.tex
morning session

@@
 \usepackage[margin=1.2in]{geometry}
+\usepackage{showlabels}
 
@@
   \begin{align} 
- a_z^2[\Bell] & = \frac{1}{m^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[\ii]z[\ii+\Bell]. 
+ a_z^2[\Bell] & = \frac{1}{N^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[\ii]z[\ii+\Bell]. 
  \end{align}
@@
  It can be shown that in the limit of infinitely many micrographs $K\to\infty$,  the mean pixel value of the micrographs is equal to the mean pixel value of the signal $x$, scaled by  
- \begin{align}
+ \begin{align} \label{eq:gamma}
  \gamma & = \frac{M P^2}{N^2},
@@
 \begin{equation*} \label{eq:Kth_autocorrelation}
-a^p_\II(\Bell_1,\ldots, \Bell_{p-1}) = \frac{1}{N^2}\sum_{\mb i}\II(\mb i)\II(\mb i+\Bell_1)\cdots \II(\mb i+\Bell_{p-1}),
+a^p_\II(\Bell_1,\ldots, \Bell_{p-1}) = \frac{1}{N^2}\sum_{\mb i}\II[\Bell]\II([\mb i+\Bell]_1)\cdots \II([\mb i+\Bell]_{p-1}),
 \end{equation*}
-where the summation is for $\mb i $ ranging over the $N^2$  pixels of the micrograph. %, $\Delta \mb i = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
+where the summation is for $\mb i $ ranging over the $N^2$  pixels of the micrograph. %, $\Bell = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
 %In our procedure, we compute the first three autocorrelations. %, called the mean, power spectrum, and bispectrum, of the micrographs. \TODO{This definition and terminology should come earlier}. 
 Let $\II_1,\ldots\II_K$ denote a set of $K$ micrographs. 
-Under the specified conditions, we show in Appendix TKTK that the first three autocorrelations  of the micrographs are related to those of the projections by \begin{align} \label{eq:ac_micrographs}
+Under the specified conditions, we show in Appendix~\ref{sec:moment_derivation} that the first three autocorrelations  of the micrographs are related to those of the projections by \begin{align} \label{eq:ac_micrographs}
 \lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[0,P-1]^2, \nonumber
@@
 
-\section{Moments derivation}
-
-We consider the moments of $\II$ in the limit $N\to\infty$. To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is a constant. 
-Because of the separation condition Eq.~(\ref{eq:sep_cond}), if $\mb i$ is in the support of the $j$th projection, then $\mb i + \Delta\mb i$ is either in the support of the same projection or outside the support of any projection.
-Formally, $\mb i$ is in the support of the $j$th projection if and only if $0\leq \mb i - \mb s_j < L$ where the inequalities apply to each coordinate.
-Then for $||\Delta\mb i||_{\infty}\leq L-1$ we have
-\[-(L-1) \leq \mb i+\Delta\mb i-\mb s_j< 2L-1,\]
-and because of the separation condition, given $\mb s_k$ we must either have $\mb s_k-\mb s_i\geq 2L-1$ in which case 
-\[ \mb i + \Delta\mb i- \mb s_k \leq \mb i + \Delta\mb i- \mb s_j - (2L-1) < 0,\]
-or $\mb s_k - \mb s_i \leq -(2L-1)$, in which case
-\[ \mb i + \Delta\mb i - \mb s_k \geq -(L-1) + 2L-1 = L.\]
-In either case, $\mb i+\Delta\mb i$ is not in the support of the $k$th particle.
-
-Denote by $\mc S_j$ the support of the $j$th particle and by $Z=\{1,\ldots, M\}-\sqcup_j \mc S_j$ all the points outside the support of the particle.
-The clean micrograp $\widetilde \II = \II-\xi$ then satisfies $\widetilde \II(\mb i) = 0$ if $\mb i\in Z$, so we have
-\be\begin{aligned} 
-m_k[\widetilde\II](\Delta\mb i_1,\ldots, \Delta\mb i_{k-1}) &= \frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1})\\
-&= \frac{1}{M^2}\sum_{j=1}^N\sum_{\mb i\in\mc S_i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1}) + \frac{1}{M^2}\sum_{\mb i\in Z}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\cdots \widetilde\II(\mb i + \Delta\mb i_{k-1})\\
-&= \frac{NL^2}{M^2}\cdot\frac{1}{N}\sum_{j=1}^N\frac{1}{L^2}\sum_{i,j=1}^L I_{\omega_j}(\mb i)I_{\omega_j}(\mb i+\Delta\mb i_1)\cdots I_{\omega_j}(\mb i + \Delta \mb i_{k-1})\\
-&= \frac{NL^2}{M^2}\frac{1}{N}\sum_{j=1}^Nm_k[I_{\omega_j}]\\
-&\to \gamma\langle m_k[I_{\omega_j}]\rangle_{\omega}. \end{aligned}\ee
-
-In the precence of noise, we get an additional bias term, which we proceed to derive. The mean is unbiased, since the noise is assumed to have zero mean. For the power spectrum, we have
+\section{Moments derivation} \label{sec:moment_derivation}
+In this section we prove relation~\eqref{eq:ac_micrographs}.
+We note that mathematically taking infinitely many micrographs is equivalent to take one infinitely large micrograph with fixed density $\gamma$~\eqref{eq:gamma}.
+Hence, we consider the moments of one micrograph $\II$ in the limit $N\to\infty$ and  $\gamma = \lim_{N\to\infty}\frac{MP^2}{N^2}\in(0,1)$.
+%To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is a constant.
+The separation condition guarantees that if $\mb i=(i,j)$ is in the support of some projection, then $\mb i + \mb \Bell$ for $\Bell\in[0,P-1]^2$ is either in the support of the same projection or outside the support of any projection.
+%Formally, $\mb i$ is in the support of the $j$th projection if and only if $0\leq \mb i - \mb s_j < L$ where the inequalities apply to each coordinate.
+Then for $||\Bell||_{\infty}\leq L-1$ we have
+%\[-(L-1) \leq [\mb i+\Bell]-\mb s_j< 2L-1,\]
+%and because of the separation condition, given $\mb s_k$ we must either have $\mb s_k-\mb s_i\geq 2L-1$ in which case 
+%\[ \mb i + \Bell- \mb s_k \leq \mb i + \Bell- \mb s_j - (2L-1) < 0,\]
+%or $\mb s_k - \mb s_i \leq -(2L-1)$, in which case
+%\[ \mb i + \Bell - \mb s_k \geq -(L-1) + 2L-1 = L.\]
+%In either case, $[\mb i+\Bell]$ is not in the support of the $k$th particle.
+
+We begin by calculating the relation between the $p$th autocorrelation of the clean micrograph and the  averaged autocorrelation of the projections.
+Let us denote the clean micrograph by $\widetilde \II = \II-\varepsilon$, where $\II$ and $\varepsilon$ are given in~\eqref{eq:micrograph_model}.     
+Denote by $\mc S_t$ the support of the $t$th particle.
+% and by $Z=\{1,\ldots, M\}-\sqcup_j \mc S_j$ all the points outside the support of the particle.
+%The clean  micrograph  then satisfies $\widetilde \II[\Bell] = 0$ if $\mb i\in Z$, so we have
+ Then, we have
+\be\begin{aligned} \label{eq:general_moment}
+a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}] &= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\\
+&= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
+&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[[\mb i+\Bell]_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\\
+&= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\\
+&\to \gamma\langle a^p_{I_{\omega}}[\Bell_1,\ldots, \Bell_{p-1}]\rangle_{\omega}, \end{aligned}\ee
+where the average is taken over $\omega$ with respect to the distribution of viewing directions. Here, we assume it to be uniform.
+
+In the presence of noise, we get additional bias terms denoted by $b_p$ in~\eqref{eq:ac_micrographs}.
+The mean ($p=1$) is unbiased  since the noise is assumed to have zero mean.
+For the second-order autocorrelation ($p=2$), we have
 \[\begin{aligned} 
-&m_2[\II](\Delta \mb i) =
-\frac{1}{M^2}\sum_{i,j=1}^M\II(\mb i)\II(\mb
-i+\Delta \mb i)\\
-&= \frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\widetilde\II(\mb i+\Delta \mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i)\\ &+ \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i) + \frac{1}{M^2}\sum_{i,j=1}^M\xi(\mb i)\xi(\mb i + \Delta\mb i).
+a^2_\II[\Bell] &=
+\frac{1}{N^2}\sum_{\mb i }\II[\mb i]\II[\mb
+i+\Bell]\\
+&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[[\mb i+\Bell]] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell].
 \end{aligned}\]
-Considering the terms one-by-one, the first term is independent of the
-noise, and as shown above converges to $\gamma \langle
-m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
-satisfies
-\[\begin{aligned} 
-\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i) &=
-\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
-i)\xi_{\omega_j}(\mb i + \Delta\mb i)\\
-&\to \gamma\mathbb{E}_{\omega,\xi}[I_{\omega}\xi]\\ 
-&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\xi}[\xi] = 0, \end{aligned}\]
-where $\xi_{\omega_j}(\mb i) = \xi(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\xi$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$.
+The first term is given by~\eqref{eq:general_moment} for $p=2$. 
+The cross terms vanish in the limit. 
+%Considering the terms one-by-one, the first term is independent of the
+%noise, and as shown above converges to $\gamma \langle
+%m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
+%satisfies
+%\[\begin{aligned} 
+%\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\Bell]\varepsilon[\mb i + \Bell] &=
+%\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
+%i)\varepsilon_{\omega_j}[\mb i + \Bell]\\
+%&\to \gamma\mathbb{E}_{\omega,\varepsilon}[I_{\omega}\varepsilon]\\ 
+%&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\varepsilon}[\varepsilon] = 0, \end{aligned}\]
+%where $\varepsilon_{\omega_j}[\Bell] = \varepsilon(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\varepsilon$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$.
 A similar argument applied to the third term shows that it
-also vanishes as $N\to\infty$. 
-For the fourth term,
-if $\Delta\mb i \neq \mb{0}$ then since the noise is zero mean and
-i.i.d. this term vanishes. If $\Delta\mb i = \mb0$ then
-\[ \frac{1}{m^2}\sum_{i,j=1}^m\xi(\mb i)^2 \to \sigma^2.\]
+%also vanishes as $N\to\infty$. 
+The fourth term is zero unless $\Bell=0$, in which case it converges to $\sigma^2$.
+% $\Bell \neq \mb{0}$ %then since the noise is zero mean and
+%i.i.d. this term vanishes. If $\Bell = \mb0$ then
+%\[ \frac{1}{N^2}\sum_{i,j=1}^m\varepsilon[\Bell]^2 \to \sigma^2.\]
 Thus, we conclude
-\[ m_2[\II](\Delta\mb i) \to \gamma\langle m_2[I_{\omega}](\Delta\mb i)\rangle_{\omega} + \sigma^2\delta(\Delta\mb i).\]
-Note that the bias term $b_2 = \sigma^2\delta(\Delta\mb i)$ depends only on the variance of the noise $\sigma^2$.
+\[ a^2_\II[\Bell] \to \gamma\langle a^2_{I_{\omega}}[\Bell]\rangle_{\omega} + \sigma^2\delta[\Bell],\]
+where the  bias term $b_2[\Bell] = \sigma^2\delta[\Bell]$   depends only on the variance of the noise $\sigma^2$.
 
@@
 \[\begin{aligned} 
-&m_3[\II](\Delta\mb i_1, \Delta\mb i_2) =
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i+\Delta\mb
-	i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(1)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i+\Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(2)}\\ 
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(3)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(4)}\\
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(5)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(6)}\\
-&+ \underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\xi(\mb i + \Delta\mb i_1)\widetilde\II(\mb i + \Delta\mb i_2)}_{(7)} +
-\underbrace{\frac{1}{M^2}\sum_{\mb i}\xi(\mb i)\widetilde\II(\mb i + \Delta\mb i_1)\xi(\mb i + \Delta\mb i_2)}_{(8)}.
+&a^3_\II[\Bell_1, \Bell_2] =
+\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
+\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
+&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(3)} +
+\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(4)}\\
+&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(5)} +
+\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(6)}\\
+&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(7)} +
+\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(8)}.
 \end{aligned}\]
@@
 \begin{itemize}
-	\item Term (1) is $m_3[\widetilde\II]$, shown above to converge to
-	$\gamma\langle m_3[I_{\omega}]\rangle_{\omega}$.
-	\item Term (2) is $m_3[\xi]$, the bispectrum of pure noise, which
-	vanishes \TODO{Either cite a signal processing paper, or show ourselves}
+	\item  Term (1) is treated by~\eqref{eq:general_moment} for $p=3$;
+	\item Term (2) is the third-order autocorrelation of  pure noise  which vanishes in the limit; 
 	\item Terms (3)-(5) depend linearly on the noise and hence
-	converge to zero.
-	\item For term (6), if $\Delta\mb i_1\neq \Delta\mb i_2$ the term
-	vanishes as then $\xi(\mb i + \Delta\mb i_1)$ and $\xi(\mb i +
-	\Delta\mb i_2)$ are independent. If $\Delta\mb i_1 = \Delta\mb
-	i_2$ the term becomes
+	vanish in the limit;
+	\item For term (6), if $\Bell_1\neq \Bell_2$ the term
+	vanishes in the limit. If $\Bell_1 = \Bell_2$ then
 	\[ \begin{aligned}
-        \frac{1}{M^2}\sum_{\mb i}\widetilde\II(\mb i)\xi(\mb i + \Delta\mb i_1)^2
-      &= \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb
-		i}I_{\omega_j}(\mb i)\xi_{\omega_j}(\mb i + \Delta\mb i)^2\\ 
-      &\to \gamma\mathbb{E}_{\omega, \xi}[\xi^2I_{\omega}]\\
-      &= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
-      &= \gamma\sigma^2Lm_1[\phi],
+        \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
+      &= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
+      \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
+      %&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
+      %&= \gamma\sigma^2Lm_1[\phi],
     \end{aligned}\]
-	where $m_1[\phi]$ is the mean of the volume.
-That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
-	\item For term (7), if $\Delta\mb i_1 \neq \mb 0$ then once again
-	this term vanishes, whereas if $\Delta\mb i_2 = \mb 0$ then it becomes
-	\[ \frac{1}{M^2}\sum_{\mb i}\xi(\mb i)^2\widetilde\II(\mb i + \Delta\mb
-	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
-		i}\xi_{\omega}(\mb i)^2I_{\omega}(\mb i + \Delta\mb i_2) \to
-	\gamma\sigma^2Lm_1[\phi].\]
-	Similarly, term (8) vanishes if $\Delta\mb i_2\neq \mb 0$ and
-	converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
+	where $\langle a^1_{I_{\omega}}\rangle_{\omega}$ is the mean of the volume. 
+	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
+	%That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
+%	\item For term (7), if $\Bell \neq \mb 0$ then once again
+%	this term vanishes, whereas if $\Bell_2 = \mb 0$ then it becomes
+%	\[ \frac{1}{N^2}\sum_{\mb i}\varepsilon[\Bell]^2\widetilde\II(\mb i + \Delta\mb
+%	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
+%		i}\varepsilon_{\omega}[\Bell]^2I_{\omega}(\mb i + \Bell_2) \to
+%	\gamma\sigma^2Lm_1[\phi].\]
+	%Similarly, terms (7) (8) vanishes if $\Bell_2\neq \mb 0$ and
+	%converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
 \end{itemize}
+%Similarly, terms (7) (8) contributes $\delta$ functions similar to (6).
 Thus, we conclude that
-\[ m_3[\II](\Delta\mb i_1, \Delta\mb i_2) \to \gamma\langle
-m_3[I_{\omega}](\Delta\mb i_1, \Delta\mb i_2)\rangle_{\omega} +
-\gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
-\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big).\]
-Note that in practice, we have $m_1[\II] \approx m_1[\widetilde\II] \approx \gamma
-Lm_1[\phi]$ since the mean converges relatively fast to its expectation (at a rate of $1/M$), so we do not need prior knowledge of $\gamma$ to effectively
-debias the bispectrum.
-
-\section{Steering}\label{sec:steering}
-The clean autocorrelations $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ which we estimate from the micrograph are given by an average over the particule orientations.
-In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
+\[ a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
+a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
+\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
+\delta[\Bell_1] + \delta[\Bell_2]\Big),\]
+where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
+Note that $\gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$ is approximately the mean of the micrograph since  $a^1_\II \approx a^1_{\tilde\II} \approx \gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$.
+Therefore, we do not need prior knowledge of $\gamma$ to effectively
+debias the third-order autocorrelation.
+
+\section{Accounting for all in-plane rotations} \label{sec:steering}
+
+The micrograph autocorrelations are given by an average over the particle orientations.
+Since the specific in-plane rotation of each projection is equally likely to appear, we would like to   consider all possible in-plane rotations. 
+This can be done efficiently using steerable bases , a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients;  \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
+
+%In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
 For this paper, we represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see \cite{landa2017steerable}.
@@
 \be\label{eq:PSWF_defn_eq}
-\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi i (\mb i-\mb 1)\cdot(\mb k - \mb 1)}
+\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}[\Bell]e^{-2\pi i (\mb i-\mb 1)\cdot(\mb k - \mb 1)}
 \ee
@@
 For the power spectrum, we expand it as
-\[ m_2[\II](\Delta\mb i) =
-\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
+\[ m_2[\II](\Bell) =
+\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Bell),\]
 where the expansion is truncated according to the rule in \cite{landa2017steerable}, and obtain the expansion coefficients as
@@
 \mathfrak{m}_2(k,q) &=
-\sum_{\Delta\mb i}m_2[\II](\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
+\sum_{\Bell}m_2[\II](\Bell)\overline{\psi_{k,q}(\Bell)}\\
 &=
-\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i}\II(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{k,q}(\mb i), \end{aligned}\]
-where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II(\mb i)$ in PSWFs as
-\[ \II(\mb i + \Delta\mb i) = \sum_{k,q}a_{k,q}(\mb i)\psi_{k,q}(\Delta\mb i),\quad ||\Delta\mb i||_{\infty}\leq L-1,\]
+\frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}(\Bell)}\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]a_{k,q}[\Bell], \end{aligned}\]
+where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II[\Bell]$ in PSWFs as
+\[ \II[\mb i + \Bell] = \sum_{k,q}a_{k,q}[\Bell]\psi_{k,q}(\Bell),\quad ||\Bell||_{\infty}\leq L-1,\]
 the expansion coefficients are given by the inner product
-\[ a_{k,q}(\mb i) = \sum_{\Delta\mb i}\II(\mb i + \Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
+\[ a_{k,q}[\Bell] = \sum_{\Bell}\II[\mb i + \Bell]\overline{\psi_{k,q}(\Bell)}.\]
 As shown in \cite{landa2017steerable, zhao2016fast}, the rotation of the above patch by an angle $\alpha$ is given by
-\[ \II^{\alpha,+}(\mb i+\Delta\mb i) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
+\[ \II^{\alpha,+}[\mb i+\Bell] = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Bell),\]
 and the reflection of that disc rotated by an angle $\alpha$ by
-\[ \II^{\alpha,-}(\mb i+\Delta\mb i) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
-where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
-Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
+\[ \II^{\alpha,-}[\mb i+\Bell] = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Bell),\]
+where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. Averaging over all rotations of the patch $\II[\mb i + \Bell]$ and its reflection we get
 \[\begin{aligned} 
-\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\mb i) +
-\overline{a_{k,q}}(\mb i)]e^{-ik\alpha}\, d\alpha\right)\\ 
-&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{0,q}(\mb i), \end{aligned}\]
+\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}[\Bell] +
+\overline{a_{k,q}}[\Bell]]e^{-ik\alpha}\, d\alpha\right)\\ 
+&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II[\Bell]a_{0,q}[\Bell], \end{aligned}\]
 where in the last equality we dropped the real part since both
@@
 Thus, the average power spectrum is effectively a vector. To estimate the clean power spectrum coefficients, we also expand the bias term in PSWFs. Writing
-\[ b_2(\Delta\mb i) = \sigma^2\delta(\Delta\mb i) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
+\[ b_2(\Bell) = \sigma^2\delta(\Bell) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Bell),\]
 the coefficients are given by
 \[\begin{aligned} 
-\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Delta\mb i}\delta(\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
+\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Bell}\delta(\Bell)\overline{\psi_{k,q}(\Bell)}\\
 &= \sigma^2\overline{\psi_{k,q}(\mb 0)}\\
@@
 We expand the bispectrum as
-\[ m_3[\II](\Delta \mb i_1, \Delta \mb i_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
+\[ m_3[\II](\Bell_1, \Bell_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Bell)\overline{\psi_{k_2,q_2}(\Bell_2)},\]
 The expansion coefficients are then given by
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Delta\mb i_1, \Delta\mb i_2}m_3[\II](\Delta\mb i_1,\Delta\mb i_2)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\psi_{k_2,q_2}(\Delta\mb i_2)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i_1}\II(\mb i+\Delta\mb i_1)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\right)\left(\sum_{\Delta\mb i_2}\II(\mb i+\Delta\mb i_2)\psi_{k_2,q_2}(\Delta\mb i_2)\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i) a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}.
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Bell, \Bell_2}m_3[\II](\Bell,\Bell_2)\overline{\psi_{k_1,q_1}(\Bell)}\psi_{k_2,q_2}(\Bell_2)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k_1,q_1}(\Bell)}\right)\left(\sum_{\Bell_2}\II([\mb i+\Bell]_2)\psi_{k_2,q_2}(\Bell_2)\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell] a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]}.
 \end{aligned}\]
 Averaging over all rotations of $\II$ and its reflection, we obtain
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)} + \overline{a_{k_1,q_1}(\mb i)}a_{k_2,q_2}(\mb i)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
-&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\Re\{a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}\}.\end{aligned}\]
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]} + \overline{a_{k_1,q_1}[\Bell]}a_{k_2,q_2}[\Bell]\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
+&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II[\Bell]\Re\{a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]}\}.\end{aligned}\]
 Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
 Similarly to the power spectrum, we also expand the bias term in PSWFs as
-\[ b_3(\Delta\mb i_1, \Delta\mb i_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
-\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
-b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
+\[ b_3(\Bell, \Bell_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Bell - \Bell_2) +
+\delta(\Bell) + \delta(\Bell_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
+b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Bell)\overline{\psi_{k_2,q_2}(\Bell_2)},\]
 where the coefficients are given by
@@
 We then consider the product
-\[\begin{aligned} m_3(\Delta\mb i_1,\Delta\mb i_2) &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}(\mb i)I_{\omega}(\mb i+\Delta\mb i_1)\overline{I_{\omega}(\mb i+\Delta\mb i_2)}\rangle_{\omega},\\
-&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}(\mb i)\psi_{N_2,n_2}(\mb i+\Delta\mb i_1)\overline{\psi_{N_3,n_3}(\mb i+\Delta\mb i_2)}.\end{aligned}\]
+\[\begin{aligned} m_3(\Bell,\Bell_2) &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\Bell]I_{\omega}[\mb i+\Bell]\overline{I_{\omega}([\mb i+\Bell]_2)}\rangle_{\omega},\\
+&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\Bell]\psi_{N_2,n_2}[\mb i+\Bell]\overline{\psi_{N_3,n_3}([\mb i+\Bell]_2)}.\end{aligned}\]
 Now,
@@
 Finally, we expand
-\[ m_3(\Delta\mb i_1,\Delta\mb i_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Delta\mb i_1)\overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
+\[ m_3(\Bell,\Bell_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Bell)\overline{\psi_{k,q_2}(\Bell_2)},\]
 where we only include the block-diagonal terms in the expansion. Defining
-\[ \Psi_{\ell,N,s}(\mb i) = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}(\mb i),\]
+\[ \Psi_{\ell,N,s}[\Bell] = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}[\Bell],\]
 the final formula reads
@@
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)}, \end{aligned}\]
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]}, \end{aligned}\]
 where
-\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Delta\mb i}\Psi_{\ell,N,s}(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
-In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\mb i$ and over $\Delta\mb i$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
+\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.\]
+In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
 
@@
 &C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)},
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
 \end{align*}
@@
 \begin{align*}
-\rho_{\ell,N,s}^{(k,q)}&=\int_{\Delta\mb i}\Psi_{\ell,N,s}(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.
+\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
 \end{align*}
@@
 and
-\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}(\mb i)\rho_{\ell_2,N_2,s_2}^{(k,q_1)}(\mb i)\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}(\mb i)},\]
+\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},\]
 so in each iteration of the optimization we compute
@@
 We now suppose that the micrograph is perturbed by additive white
-Gaussian noise, so we observe $\widetilde \II = \II + \xi$ where
-$\xi\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
+Gaussian noise, so we observe $\widetilde \II = \II + \varepsilon$ where
+$\varepsilon\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
 to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
@@
 To this end, writing (in the continuous case again)
-\[ \delta(\Delta\mb i_1 - \Delta\mb i_2) =
-\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Delta\mb i_1)
-\overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
+\[ \delta(\Bell - \Bell_2) =
+\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Bell)
+\overline{\psi_{k,q_2}(\Bell_2)},\]
 we get
 \[\begin{aligned}
-\mathfrak{d}(k,q_1,q_2) &= \int_{\Delta\mb i_1,
-	\Delta\mb i_2}\delta(\Delta\mb i_1-\Delta\mb i_2)\overline{\psi_{k,q_1}(\Delta\mb i_1)}\psi_{k,q_2}(\Delta\mb i_2)\\
+\mathfrak{d}(k,q_1,q_2) &= \int_{\Bell,
+	\Bell_2}\delta(\Bell-\Bell_2)\overline{\psi_{k,q_1}(\Bell_1)}\psi_{k,q_2}(\Bell_2)\\
 &=
-\int_{\Delta\mb i_2}\overline{\psi_{k,q_1}(\Delta\mb i_2)}\psi_{k,q_2}(\Delta\mb i_2)\\
+\int_{\Bell_2}\overline{\psi_{k,q_1}(\Bell_2)}\psi_{k,q_2}(\Bell_2)\\
 &= \delta_{q_1,q_2}.
@@
 Similarly, writing
-\[ \delta(\Delta\mb i_1) =
+\[ \delta(\Bell_1) =
 \sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
-\psi_{k,q_1}(\Delta\mb i_1) \overline{\psi_{k,q_2}(\Delta\mb i_2)},\]
+\psi_{k,q_1}(\Bell_1) \overline{\psi_{k,q_2}(\Bell_2)},\]
 we get
 \[\begin{aligned} 
-\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Delta\mb i_1,
-	\Delta\mb i_2}\delta(\Delta\mb i_1)\overline{\psi_{k,q_1}(\Delta\mb i_1)}
-\psi_{k,q_2}(\Delta\mb i_2)\\
+\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Bell_1,
+	\Bell_2}\delta(\Bell_1)\overline{\psi_{k,q_1}(\Bell_1)}
+\psi_{k,q_2}(\Bell_2)\\
 &= \overline{\psi_{k,q_1}(\mb 0)}
-\int_{\Delta\mb i_2}\psi_{k,q_2}(\Delta\mb i_2)\\
+\int_{\Bell_2}\psi_{k,q_2}(\Bell_2)\\
 &= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
@@
 $J_0(0)=1$. 
-A similar derivation applies to $\delta(\Delta\mb i_2)$.
+A similar derivation applies to $\delta(\Bell_2)$.
 

### 2018-07-30 TEX/draft_biology_eitanl_30-07-2018.tex
Added current version of draft on Eitan's PC

--- 2018-07-30 TEX/draft_biology.tex
@@
 where the coefficients are given by
-\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2 m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
+\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2L m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
 \section{Connection to volume}
@@
 \[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
-
 where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase, and $j_{\ell,s}$ are normalized spherical Bessel functions given by
@@
 \[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
-where in papers the 2D PSWFs are defined as
-\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
-but in Boris' code the expansion is actually performed with respect to
-\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
-where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below.
-
-We then get
+where
 \[\begin{aligned} b_{N,n} &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-iN\theta}k\, dk\, d\theta,\\

### 2018-07-30 TEX/draft_biology.tex
afternoon section

@@
 where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$ and $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
-Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2L-1$ \TODO{2L?} pixels in each direction.
+Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction.
 %similarly to~\eqref{eq:spacing}:
@@
 Under the specified conditions, we show in Appendix~\ref{sec:moment_derivation} that the first three autocorrelations  of the micrographs are related to those of the projections by \begin{align} \label{eq:ac_micrographs}
-\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[0,P-1]^2, \nonumber
+\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[-(P-1),P-1]^2, \nonumber
 \end{align}
@@
 %To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is a constant.
-The separation condition guarantees that if $\mb i=(i,j)$ is in the support of some projection, then $\mb i + \mb \Bell$ for $\Bell\in[0,P-1]^2$ is either in the support of the same projection or outside the support of any projection.
+The separation condition guarantees that if $\mb i=(i,j)$ is in the support of some projection, then $\mb i + \mb \Bell$ for $\Bell\in[-(P-1),P-1]^2$ is either in the support of the same projection or outside the support of any projection.
 %Formally, $\mb i$ is in the support of the $j$th projection if and only if $0\leq \mb i - \mb s_j < L$ where the inequalities apply to each coordinate.
@@
 &= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
-&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[[\mb i+\Bell]_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\\
+&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[\mb i+\Bell_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\\
 &= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\\
@@
 i+\Bell]\\
-&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[[\mb i+\Bell]] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell].
+&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell].
 \end{aligned}\]
@@
 
+We represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$ where $k \geq 0, q \geq 1$ are integers~\cite{landa2017steerable}.
+As we demonstrate below, this makes it easier to account for the fact that all in-plane rotations of the micrographs are equally likely observations.
+This is only a concern for the second and third order autocorrelations.
+Below, we start with $p=2$.
+The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by
+\begin{align}
+	\psi_{k,q}(r,\varphi) & = \left\{\begin{array}{ll} \frac{1}{\sqrt{8\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \label{eq:prolatesdef}
+\end{align}
+where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are \TODO{real?} scaling factors which will be defined in the next section.
+The PSWFs are orthonormal on the unit disk.
+
+For $\Bell \in [-(P-1), P-1]^2$, let us define 
+\[\begin{aligned} 
+\mathfrak{a}^2[k, q] & =
+\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
+where $\psi_{k,q}[\Bell] \triangleq \psi_{k,q}(\Bell/P)$ \TODO{?} is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
+Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
+\begin{align}
+ a^2_\II[\mb i] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
+ \label{eq:approxprolatesdiscrete}
+\end{align}
+We now proceed to show that the coefficients $\mathfrak{a}^2[k, q]$ can be computed from the micrographs directly.
+
+By definition,
+\begin{align}
+\mathfrak{a}^2[k,q] & =\sum_{\Bell} a^2_\II[\Bell] \overline{\psi_{k,q}[\Bell]} \nonumber\\
+	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}\right) \nonumber \\
+	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k,q}[\mb i], \label{eq:frakatwo}
+\end{align}
+where we defined
+\begin{align*}
+	a_{k,q}[\mb i] & = \sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}.
+\end{align*}
+These coefficients can be computed efficiently.
+Indeed, consider a patch of the micrograph $\II$ centered around pixel $\mb i$ and of size $(2P-1) \times (2P-1)$.
+This is exactly the patch indexed in the sum above.
+Hence, using the same approximation as we did in~\eqref{eq:approxprolatesdiscrete}, a direct expansion of that patch in the discretized PSWFs yields the sought coefficients:
+\begin{align}
+	\II[\mb i+\Bell] & \approx \sum_{k,q} a_{k,q}[\mb i] \psi_{k,q}[\Bell]. \label{eq:itamar}
+\end{align}
+%Considering equation~\eqref{eq:frakatwo}, our main task is to compute the coefficients $a_{k,q}$, which from the equation above can be done as follows: 
+Thus, we proceed as follows:
+for each position $\mb i$ in the micrograph $\II$, we extract the corresponding patch of size $2P-1$, expand it in the discretized PSWFs as in~\eqref{eq:itamar}, and collect the $a_{k,q}$ as per~\eqref{eq:frakatwo} to constitute the second-order autocorrelation of the micrograph.
+
+Crucially, following this formalism, it is now straightforward to account for all in-plane rotations (and reflections) of the micrograph.
+Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation.
+By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
+\[ \II^{\alpha,+}[\mb i+\Bell] = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}[\Bell],\]
+and the reflection followed by a rotation by angle $\alpha$:
+\[ \II^{\alpha,-}[\mb i+\Bell] = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}[\Bell].\]
+%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
+Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
+\[\begin{aligned} 
+\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}[\mb i] +
+\overline{a_{k,q}}[\mb i]]e^{-ik\alpha}\, d\alpha\right)\\ 
+&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
+where in the last equality we used that both $\II$ and $\psi_{0,q}$ are real valued.
+Thus, the second-order autocorrelation, though two-dimensional, effectively only provides one-dimensional information.
+
+We now follow a similar approach to estimate the bias term $b_2$.
+Introduce the coefficients $\mathfrak{b}_2$ as: \TODO{We're using that $R$ functions are zero at the origin for $k\neq 0$, right? We didn't introduce that fact so far.}
+\[\begin{aligned} 
+\mathfrak{b}_2[k,q] & = \sigma^2\sum_{\Bell}\delta[\Bell]\overline{\psi_{k,q}}[\Bell]\\
+&= \sigma^2\overline{\psi_{k,q}}[\mb 0]\\
+&= \delta[k] \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
+With this definition, we have the usual approximation:
+\[ b_2[\Bell] = \sigma^2\delta[\Bell] \approx \sum_{k,q}\mathfrak{b}_2[k,q]\psi_{k,q}[\Bell].\]
+
+We then estimate the expansion coefficients of the clean power spectrum as
+\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]
+
+\TODO{---------------------------------------------}
+
+, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see . 
+The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy 
+\be\label{eq:PSWF_defn_eq}
+\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
+\ee
+given in polar coordinates by
+\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
+and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}
+
 The micrograph autocorrelations are given by an average over the particle orientations.
@@
 
-%In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
+The clean autocorrelations $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ which we estimate from the micrograph are given by an average over the particule orientations.
+In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
 For this paper, we represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see \cite{landa2017steerable}.
-The PSWFs are eigenfunctions of the truncated Fourier trasnform and satisfy
+
+The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy \TODO{approximate} \TODO{generate the Gram matrix of the discrete approximation}
 \be\label{eq:PSWF_defn_eq}
-\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}[\Bell]e^{-2\pi i (\mb i-\mb 1)\cdot(\mb k - \mb 1)}
+\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
 \ee
 given in polar coordinates by
-\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{ik\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
+\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
 and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}
@@
 For the power spectrum, we expand it as
-\[ m_2[\II](\Bell) =
-\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Bell),\]
-where the expansion is truncated according to the rule in \cite{landa2017steerable}, and obtain the expansion coefficients as
+\[ m_2[\II](\Delta\mb i) =
+\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
+where the expansion is truncated according to the rule in~\cite{landa2017steerable}, and obtain the expansion coefficients as
 \[\begin{aligned} 
 \mathfrak{m}_2(k,q) &=
-\sum_{\Bell}m_2[\II](\Bell)\overline{\psi_{k,q}(\Bell)}\\
+\sum_{\Delta\mb i}m_2[\II](\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
 &=
-\frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}(\Bell)}\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]a_{k,q}[\Bell], \end{aligned}\]
-where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II[\Bell]$ in PSWFs as
-\[ \II[\mb i + \Bell] = \sum_{k,q}a_{k,q}[\Bell]\psi_{k,q}(\Bell),\quad ||\Bell||_{\infty}\leq L-1,\]
+\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i}\II(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{k,q}(\mb i), \end{aligned}\]
+where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II(\mb i)$ in PSWFs as
+\[ \II(\mb i + \Delta\mb i) = \sum_{k,q}a_{k,q}(\mb i)\psi_{k,q}(\Delta\mb i),\quad ||\Delta\mb i||_{\infty}\leq L-1,\]
 the expansion coefficients are given by the inner product
-\[ a_{k,q}[\Bell] = \sum_{\Bell}\II[\mb i + \Bell]\overline{\psi_{k,q}(\Bell)}.\]
+\[ a_{k,q}(\mb i) = \sum_{\Delta\mb i}\II(\mb i + \Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
 As shown in \cite{landa2017steerable, zhao2016fast}, the rotation of the above patch by an angle $\alpha$ is given by
-\[ \II^{\alpha,+}[\mb i+\Bell] = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Bell),\]
+\[ \II^{\alpha,+}(\mb i+\Delta\mb i) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
 and the reflection of that disc rotated by an angle $\alpha$ by
-\[ \II^{\alpha,-}[\mb i+\Bell] = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Bell),\]
-where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. Averaging over all rotations of the patch $\II[\mb i + \Bell]$ and its reflection we get
+\[ \II^{\alpha,-}(\mb i+\Delta\mb i) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
+where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
+Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
 \[\begin{aligned} 
-\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}[\Bell] +
-\overline{a_{k,q}}[\Bell]]e^{-ik\alpha}\, d\alpha\right)\\ 
-&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II[\Bell]a_{0,q}[\Bell], \end{aligned}\]
+\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\mb i) +
+\overline{a_{k,q}}(\mb i)]e^{-ik\alpha}\, d\alpha\right)\\ 
+&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{0,q}(\mb i), \end{aligned}\]
 where in the last equality we dropped the real part since both
@@
 Thus, the average power spectrum is effectively a vector. To estimate the clean power spectrum coefficients, we also expand the bias term in PSWFs. Writing
-\[ b_2(\Bell) = \sigma^2\delta(\Bell) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Bell),\]
+\[ b_2(\Delta\mb i) = \sigma^2\delta(\Delta\mb i) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
 the coefficients are given by
 \[\begin{aligned} 
-\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Bell}\delta(\Bell)\overline{\psi_{k,q}(\Bell)}\\
+\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Delta\mb i}\delta(\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
 &= \sigma^2\overline{\psi_{k,q}(\mb 0)}\\
@@
 We expand the bispectrum as
-\[ m_3[\II](\Bell_1, \Bell_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Bell)\overline{\psi_{k_2,q_2}(\Bell_2)},\]
+\[ m_3[\II](\Delta \mb i_1, \Delta \mb i_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
 The expansion coefficients are then given by
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Bell, \Bell_2}m_3[\II](\Bell,\Bell_2)\overline{\psi_{k_1,q_1}(\Bell)}\psi_{k_2,q_2}(\Bell_2)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k_1,q_1}(\Bell)}\right)\left(\sum_{\Bell_2}\II([\mb i+\Bell]_2)\psi_{k_2,q_2}(\Bell_2)\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II[\Bell] a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]}.
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Delta\mb i_1, \Delta\mb i_2}m_3[\II](\Delta\mb i_1,\Delta\mb i_2)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\psi_{k_2,q_2}(\Delta\mb i_2)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i_1}\II(\mb i+\Delta\mb i_1)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\right)\left(\sum_{\Delta\mb i_2}\II(\mb i+\Delta\mb i_2)\psi_{k_2,q_2}(\Delta\mb i_2)\right)\\
+&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i) a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}.
 \end{aligned}\]
 Averaging over all rotations of $\II$ and its reflection, we obtain
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II[\Bell]\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]} + \overline{a_{k_1,q_1}[\Bell]}a_{k_2,q_2}[\Bell]\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
-&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II[\Bell]\Re\{a_{k_1,q_1}[\Bell]\overline{a_{k_2,q_2}[\Bell]}\}.\end{aligned}\]
+\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)} + \overline{a_{k_1,q_1}(\mb i)}a_{k_2,q_2}(\mb i)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
+&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\Re\{a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}\}.\end{aligned}\]
 Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
 Similarly to the power spectrum, we also expand the bias term in PSWFs as
-\[ b_3(\Bell, \Bell_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Bell - \Bell_2) +
-\delta(\Bell) + \delta(\Bell_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
-b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Bell)\overline{\psi_{k_2,q_2}(\Bell_2)},\]
+\[ b_3(\Delta\mb i_1, \Delta\mb i_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
+\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
+b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
 where the coefficients are given by
-\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2 m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
+\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2L m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
+
 \section{Connection to volume}

### 2018-07-31 TEX/draft_biology.tex
morning session

@@
 
-We represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$ where $k \geq 0, q \geq 1$ are integers~\cite{landa2017steerable}.
+We represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$ where $k \geq 0, q \geq 1$ are integers~\cite{slepian1964pswfIV}.
 As we demonstrate below, this makes it easier to account for the fact that all in-plane rotations of the micrographs are equally likely observations.
@@
 where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are \TODO{real?} scaling factors which will be defined in the next section.
-The PSWFs are orthonormal on the unit disk.
+The PSWFs are orthonormal \TODO{orthogonal?} on the unit disk.
 
@@
 \sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
-where $\psi_{k,q}[\Bell] \triangleq \psi_{k,q}(\Bell/P)$ \TODO{?} is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
+where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
 Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
 \begin{align}
- a^2_\II[\mb i] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
+ a^2_\II[\Bell] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
  \label{eq:approxprolatesdiscrete}
 \end{align}
+This holds because the continuous PSWFs form an orthogonal basis, and their discretized counterparts are (empirically) almost orthogonal.
+As a result, for our purposes, the pair of equations above provides a basis expansion for the autocorrelations.
+
 We now proceed to show that the coefficients $\mathfrak{a}^2[k, q]$ can be computed from the micrographs directly.
-
 By definition,
@@
 where we defined
-\begin{align*}
+\begin{align}
 	a_{k,q}[\mb i] & = \sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}.
-\end{align*}
+	\label{eq:patchcoefficients}
+\end{align}
 These coefficients can be computed efficiently.
@@
 
-Crucially, following this formalism, it is now straightforward to account for all in-plane rotations (and reflections) of the micrograph.
-Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation.
+Crucially, following this formalism, it is now straightforward to account for all in-plane rotations and reflections of the micrograph.
+Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation: this is why this the PSWF basis is called \emph{steerable}~\cite{landa2017steerable,zhao2016fast}.
 By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
-\[ \II^{\alpha,+}[\mb i+\Bell] = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}[\Bell],\]
+\[ \II^{\alpha,+}[\mb i+\Bell] \approx \sum_{k,q}a_{k,q}e^{-\iota k\alpha}\psi_{k,q}[\Bell],\]
 and the reflection followed by a rotation by angle $\alpha$:
-\[ \II^{\alpha,-}[\mb i+\Bell] = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}[\Bell].\]
+\[ \II^{\alpha,-}[\mb i+\Bell] \approx \sum_{k,q}\overline{a_{k,q}}e^{-\iota k\alpha}\psi_{k,q}[\Bell].\]
 %where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
@@
 \[\begin{aligned} 
-\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}[\mb i] +
-\overline{a_{k,q}}[\mb i]]e^{-ik\alpha}\, d\alpha\right)\\ 
+\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k,q}[\mb i] +
+\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\\ 
 &= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
-where in the last equality we used that both $\II$ and $\psi_{0,q}$ are real valued.
-Thus, the second-order autocorrelation, though two-dimensional, effectively only provides one-dimensional information.
+where in the last equality we used that $a_{0,q}[\mb i]$ is real since both $\II$ and $\psi_{0,q}$ are real valued (more generally, $a_{-k,q}=\overline{a_{k,q}}$).
+Thus, the second-order autocorrelation, though two-dimensional, effectively only provides radial information.
 
 We now follow a similar approach to estimate the bias term $b_2$.
-Introduce the coefficients $\mathfrak{b}_2$ as: \TODO{We're using that $R$ functions are zero at the origin for $k\neq 0$, right? We didn't introduce that fact so far.}
+Introduce the coefficients $\mathfrak{b}_2$ as:
 \[\begin{aligned} 
@@
 &= \sigma^2\overline{\psi_{k,q}}[\mb 0]\\
-&= \delta[k] \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
+&= \delta[k] \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0), \end{aligned}\]
+where we used the fact that the functions $R_{k,q}$ are zero at the origin for $k\neq 0$.
 With this definition, we have the usual approximation:
@@
 
-We then estimate the expansion coefficients of the clean power spectrum as
-\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]
-
-\TODO{---------------------------------------------}
-
-, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see . 
-The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy 
+We now turn out attention to the third order autocorrelation. Following the same lines, we define the coefficients:
+\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
+&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
+&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
+\end{aligned}\]
+where the patch expansion coefficients $a_{k,q}$ are as defined in~\eqref{eq:patchcoefficients}.
+The coefficients $\mathfrak{a}^3[k_1,q_1;k_2,q_2]$ are related to the third-order autocorrelation via the approximate identity:
+\[ a^3_\II[\Bell_1, \Bell_2] \approx \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{a}^3[k_1,q_1;k_2,q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.\]
+Averaging over all rotations of $\II$ and its reflection, we obtain
+\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right),\\
+&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}.\end{aligned}\]
+Thus, similarly to the second-order autocorrelation, averaging over all in-plane rotations reveals that the 4-D third-order autocorrelation truly only carries information along three dimensions.
+
+Finally, we treat the bias terms, using approximate orthonormality \TODO{!} of the discretized PSFWs:
+\[ \mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
+\]
+Thus,
+\begin{align*}
+	b_3[\Bell_1, \Bell_2] & = \gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
+	\delta[\Bell_1] + \delta[\Bell_2]\Big) \\
+	& \approx \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
+	b_3[k_1,q_1; k_2, q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.
+\end{align*}
+
+\section{Connection to volume}
+
+\TODO{===}
+
 \be\label{eq:PSWF_defn_eq}
@@
 \ee
-given in polar coordinates by
-\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
-and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}
-
-The micrograph autocorrelations are given by an average over the particle orientations.
-Since the specific in-plane rotation of each projection is equally likely to appear, we would like to   consider all possible in-plane rotations. 
-This can be done efficiently using steerable bases , a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients;  \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
-
-The clean autocorrelations $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ which we estimate from the micrograph are given by an average over the particule orientations.
-In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.
-For this paper, we represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see \cite{landa2017steerable}.
-
-The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy \TODO{approximate} \TODO{generate the Gram matrix of the discrete approximation}
-\be\label{eq:PSWF_defn_eq}
-\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
-\ee
-given in polar coordinates by
-\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
-and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}
-
-The mean is a scalar and is already invariant under in-plane rotations of the projections in the dataset, since all projections have the same mean $Lm_1[\phi]$, as explained above.
-For the power spectrum, we expand it as
-\[ m_2[\II](\Delta\mb i) =
-\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
-where the expansion is truncated according to the rule in~\cite{landa2017steerable}, and obtain the expansion coefficients as
-\[\begin{aligned} 
-\mathfrak{m}_2(k,q) &=
-\sum_{\Delta\mb i}m_2[\II](\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
-&=
-\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i}\II(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{k,q}(\mb i), \end{aligned}\]
-where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II(\mb i)$ in PSWFs as
-\[ \II(\mb i + \Delta\mb i) = \sum_{k,q}a_{k,q}(\mb i)\psi_{k,q}(\Delta\mb i),\quad ||\Delta\mb i||_{\infty}\leq L-1,\]
-the expansion coefficients are given by the inner product
-\[ a_{k,q}(\mb i) = \sum_{\Delta\mb i}\II(\mb i + \Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
-As shown in \cite{landa2017steerable, zhao2016fast}, the rotation of the above patch by an angle $\alpha$ is given by
-\[ \II^{\alpha,+}(\mb i+\Delta\mb i) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
-and the reflection of that disc rotated by an angle $\alpha$ by
-\[ \II^{\alpha,-}(\mb i+\Delta\mb i) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
-where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
-Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
-\[\begin{aligned} 
-\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\mb i) +
-\overline{a_{k,q}}(\mb i)]e^{-ik\alpha}\, d\alpha\right)\\ 
-&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{0,q}(\mb i), \end{aligned}\]
-where in the last equality we dropped the real part since both
-$\II$ and $\psi_{0,q}$ are real valued.
-Thus, the average power spectrum is effectively a vector. To estimate the clean power spectrum coefficients, we also expand the bias term in PSWFs. Writing
-\[ b_2(\Delta\mb i) = \sigma^2\delta(\Delta\mb i) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
-the coefficients are given by
-\[\begin{aligned} 
-\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Delta\mb i}\delta(\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
-&= \sigma^2\overline{\psi_{k,q}(\mb 0)}\\
-&= \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
-We then estimate the expansion coefficients of the clean power spectrum as
-\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]
-
-We expand the bispectrum as
-\[ m_3[\II](\Delta \mb i_1, \Delta \mb i_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
-The expansion coefficients are then given by
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Delta\mb i_1, \Delta\mb i_2}m_3[\II](\Delta\mb i_1,\Delta\mb i_2)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\psi_{k_2,q_2}(\Delta\mb i_2)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i_1}\II(\mb i+\Delta\mb i_1)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\right)\left(\sum_{\Delta\mb i_2}\II(\mb i+\Delta\mb i_2)\psi_{k_2,q_2}(\Delta\mb i_2)\right)\\
-&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i) a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}.
-\end{aligned}\]
-Averaging over all rotations of $\II$ and its reflection, we obtain
-\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)} + \overline{a_{k_1,q_1}(\mb i)}a_{k_2,q_2}(\mb i)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
-&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\Re\{a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}\}.\end{aligned}\]
-Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
-Similarly to the power spectrum, we also expand the bias term in PSWFs as
-\[ b_3(\Delta\mb i_1, \Delta\mb i_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
-\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
-b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
-where the coefficients are given by
-\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2L m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
-
-\section{Connection to volume}
+
+\TODO{===}
 

### 2018-08-02 TEX/draft_biology.tex
removed false statement on EM

@@
 In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details.
-As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details.
+%As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details. 
 \TODO{Do we want to stress that we get only low-resolution of the volume?}
@@
 \end{align}
-where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are \TODO{real?} scaling factors which will be defined in the next section.
-The PSWFs are orthonormal \TODO{orthogonal?} on the unit disk.
+\TODO{Ref eq. 8 in Boris' paper}
+where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are  scaling factors which will be defined in the next section.
+The PSWFs are orthogonal on the unit disk.
 

### 2018-08-03 TEX/inverse_problem_draft.tex
outline of inverse problem paper

--- 2018-07-11 TEX/draft4.tex
@@
 
-\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}
+\title{Estimation below the detection limit with application to cryo-em}
 
@@
 \section{Introduction}
-
-\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
-%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
-%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
-% 
-In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
-The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
-Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
-The goal is to construct 3-D models of the molecules from the micrographs.
-
-The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors.
-On the one hand, the $\SNR$ is a function of the electron dose.
-To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the $\SNR$ is a function of the molecule size.
-The smaller the molecules, the fewer detected electrons carry information about them.
-
-%\paragraph{Particle picking.}
-All contemporary methods in the field split the reconstruction procedure into several stages.
-The first stage consists in extracting the various particle projections from the micrographs.
-This is called \emph{particle picking}.
-Later stages aim to construct a 3-D model of the molecule from these projections.
-The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.
-
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{quote}
-	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-\end{quote}
-
-\TODO{Frank: Working with Owen Saxton, I was able to show that alignment via cross-correlation would be accurate enough for the purpose of aligning noisy images of single molecules if the dose exceeded a certain level, which depended on the molecule?s size and contrast against the background.[19a] Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ x Resolution (as length) X Critical Electron Dose] A detailed examination of this dependency was later to be undertaken by Richard Henderson.[19b].
-From Joachim Frank?s Nobel Lecture.
-Amit's email from July 10.}
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight.
-%This has often been understood as meaning that particle reconstruction itself is impossible for such molecules~\cite{khoshouei2017cryo,liu2018nearatomic,liang2017phase}.
-\TODO{This list may be unfair, as some of these papers (in particular, \cite{liang2017phase}) just state that small molecules are very challenging, which is true.}
-As a result, it is impossible to reconstruct such small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, as the particles themselves cannot be picked from the micrographs.
-%
-%\TODO{either here, or in a close neighborhood of this paragraph you should mention the advances that the field has made in recent years towards reconstruction of small size molecules: mention Volta phase plate and the scaffolding cage (and cite the papers I sent you).}
-This has motivated recent technical advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%
-%
-Despite this progress, detecting small molecules in the micrographs (below $\sim$50 kDa) remains a challenge.
-We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
-Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
-\TODO{Need a ref for this claim.}
-
-In this paper, we argue that there is a gap between the two questions in the quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-%This can be understood from a statistical point of view by counting the number of parameters that one aims to estimate.
-\TODO{For a given target resolution, the number of parameters required to describe the 3-D model of the molecule is fixed: it does not depend on the amount of data collected.
-In contrast, particle picking involves estimation of several so-called nuisance parameters for each projection present in the micrographs, such as their locations for example.
-To overcome low $\SNR$s, the ratio of data to parameters must increase.
-This is impossible if the number of parameters grows with the amount of data collected, but not so if the number of parameters remains fixed.
-Simply put, the key is to bypass the particle picking stage.}
-%%Thus, acquiring more data does not necessarily allow to improve the particle picking stage, whereas it should in principle allow to improve the molecule reconstruction.
-%%Indeed, the signal itself (the many different views of the molecule) is still present in the micrograph: 
-%Indeed, in principle at least, the micrograph does contain the necessary information (several views of the molecule(s) of interest).
-While we may not be able to locate these views, we may still be able to extract the relevant information through other means.
-Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.
-
-%\TODO{Paragraph about the simplified model}
-As a proof of concept, we study a simplified model where an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
-%Figure~\ref{fig:Einst_example} displays the results of our method, detailed in Section~\ref{sec:results}.
-A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
-To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
-Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
-We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In order to recover the planted image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the planted image.
-%To do so, we assume the image occurrences are well separated.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided individual occurrences of the image are well separated and the image appears sufficiently many times in the micrographs.
-Importantly, there is no need to detect individual occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the image.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares or a phase retrieval algorithm; see Figure~\ref{fig:Einst_example} for an illustration and Section~\ref{sec:methods} for details.
-As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see Appendix~\ref{sec:theory} for a discussion.
-
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using cross-correlation and then averaged.
-In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
-This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates are required, thus significantly reducing concerns about model bias.
-
-%\TODO{Paragraph about bias; can also mention computational aspects (single pass, etc.)}
-
-%\TODO{Already mention challenges? I think it's a good place.} -- no, not here: in conclusion
-
-%\clearpage
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein}
-%		\caption{\label{fig:Einstein}Einstein image (template)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n10}
-%		\caption{$n = 10$}
-%	\end{subfigure}
-%	\begin{subfigure}[h]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Einstein_from_noise_n100}
-%		\caption{$n = 10^2$}
-%	\end{subfigure}
-
-%	\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n1000}
-%	\caption{$n = 10^3$}
-%\end{subfigure}%
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n10000}
-%	\caption{$n = 10^4$}
-%\end{subfigure}
-%\begin{subfigure}[h]{0.3\textwidth}
-%	\centering
-%	\includegraphics[scale=0.3]{Einstein_from_noise_n100000}
-%	\caption{$n = 10^5$}
-%\end{subfigure}
-
-%\caption{\label{fig:EinsteinFromNoise} Einstein from noise experiment.
-As a template, we used Einstein's image of size $50\times 50$ pixels.
-We drawn $n$ images of the same size whose entries are composed of i.i.d.\ Gaussian entries with the same mean and variance as Einstein's image.
-Each noise image was aligned with respect to the template by the maximal value of their cross correlation.
-After the alignment, all the images were averaged.
-As can be seen, the more pure noise images we use, the closer the averaged image to the template.
-}
-%\end{figure}
-
-%Besides the model bias, particle pickers have several limitations due to the high noise level, in particular for small particles and in low contrast. 
-%As a result, the projections in the 2-D images are typically not centered; including the correct centers as parameters dramatically increases the complexity of reconstruction algorithms.
-%In addition, the information from particles that are too close to each other is usually neglected. Hence, valuable information that can be harnessed is omitted.
-
-%\paragraph{Simplified model for SPR}
-
-%In this paper, we present a preliminary study that aims to show that estimating a particle 
-%directly from the micrograph, without identifying the location of individual particle images in the micrograph, might be possible.
-
-%In particular, we consider the toy problem of estimating a set of signals $x_1,\ldots,x_K$ from their multiple occurrences in unknown  locations in a noisy data sequence $y$.
-Here, $y$ plays the role of the micrograph and the $K$ signals can be thought of as $K$ different viewing directions of the particle, each of which  appears multiple times in the micrograph.
-%A precise mathematical formulation of the model and the estimation problem is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure; instead, we solve a simpler problem that we believe captures key elements of the true SPR problem.
-We also mention in passing that similar models emerge in different scientific fields, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
@@
 
-%\paragraph{Autocorrelation analysis.}
-%We now return to the general problem of estimating $x_1,\dots,x_K$ from the noisy observation $y$.
-%In order to recover the signals $x_1,\dots,x_K$ from the data, we use autocorrelation analysis.
-%In a nutshell, the method consists of two stages.
-First, we estimate a mixture (i.e., linear combination) of the low--order autocorrelation functions of the signals from the data.
-These quantities can be estimated, to any desired accuracy, if individual occurrences are separated by the maximum signal size and each signal appears sufficiently many times in the data.
-There is no need to detect individual occurrences.
-%In the second stage, the signals are estimated from the mixed autocorrelations using a nonconvex least-squares (LS) algorithm or a phase retrieval algorithm; see Section~\ref{sec:methods} for details.
-%This method requires only one pass over the data and can recover the signals in any $\SNR$, if the signals appear enough times in the data.
-As a side note, we mention that expectation-maximization---a popular framework in SPR---is intractable for this problem (see Appendix~\ref{sec:theory}  for more details).
-
-%\paragraph{Model bias.} The significance of the model bias in cryo--EM was stressed in~\cite{shatsky2009method,henderson2013avoiding} and demonstrated by the ``Einstein from noise'' example.
-%In this experiment, the image of Einstein is correlated with multiple images of pure noise. The noisy images are aligned to Einstein's image using cross-correlation and then averaged. 
-%In~\cite{shatsky2009method}, it was shown that with merely  1000 noise images, the averaged image is remarkably similar to the template image of Einstein rather than to pure noise.
-%In Figure~\ref{fig:EinsteinFromNoise} we conducted this experiment with different number of noise images.
-With merely 1000 noise images, Einstein's face is clearly observed in the averaged image.
-With $10,000$  image, the output is remarkably similar to the template image of Einstein rather than to pure noise.
-Crucially, the more noisy images we use, the more severe the model bias towards the template.
-%In the context of cryo--EM, this example demonstrates how our prior assumptions about the particle may influence the reconstructed structure.
-%This true in general to any method which is based on template matching.
-%\TODO{Do we have a nice experiment to exemplify the phenomenon?}
-
-\section{Results} \label{sec:results}
-
-%\TODO{Results: What answer was found to the research question; what did the study find? Was the tested hypothesis true?}
-
-%To support the claim that it may be possible to bypass particle picking in SPR from micrographs, as a proof of concept,
-We conducted two experiments in the simplified image formation model described in the introduction:
-\begin{enumerate}
-	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
-This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
-	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
-\end{enumerate}
-As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
-Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
-The Methods section provides additional details.
-In the discussion section, we outline how the general approach could be extended to full 3-D SPR.
-
-%In this section we describe  some numerical experiments and show results. The experimental details and the algorithms are discussed at length in Section~\ref{sec:methods}.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
-A micrograph contains, on average, 700 occurrences of the target image at random locations.
-The latter are chosen so that two occurrences are always separated by at least 49 pixels.
-Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
-This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
-In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.
-
-We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra).
-This is a particularly simple computation.
-In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself.
-Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
-% bauschke2004rrr,
-RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
-
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available in \TODO{supplementary material}.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-
-%defined as 
-%\begin{equation}
-%\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
-%\end{equation} 
-%where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
-%\TODO{We have a movie in the supplementary material.}
-
-%%%% This is about bias, and it's imprecise; let's leave it out?
-%As an initial guess, we picked an image of the physicist Issac Newton.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1_cropped}
-		\caption{\small $P = 512$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction10_cropped}
-		\caption{\small $P = 512\times 10$}
-	\end{subfigure}%
-
-		\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction100_cropped}
-		\caption{ \small $P = 512\times 10^2$ }
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1000_cropped}
-		\caption{\small $P = 512\times 10^3$}
-	\end{subfigure}%
-
-%	\begin{subfigure}[h]{0.33\textwidth}
-%		\centering
-%		\includegraphics[scale=0.33]{Einstein_progress_cropped}
-%		\caption{\label{fig:err_curve}\small Error curve}
-%	\end{subfigure}%
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Newton}
-%		\caption{\label{fig:newton}Newton  (model)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction2}
-%		\caption{\small $P =1024$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction20}
-%		\caption{$P = 1024\times 10$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction200}
-%		\caption{$P = 1024\times 100$}
-%	\end{subfigure}%
-	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-		\TODO{To add: initialization figure}
-		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
-	}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
-\end{figure}
-
-%
-%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
-%\begin{equation}
-%\gamma_i = \frac{M_i L}{N},
-%\end{equation}
-%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-As can be seen, given enough signals occurrences, we can estimate accurately the signals.
-he estimation quality
-%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
-
-In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy.
-Any two occurrences are separated by at least 20 entries.
-The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion.
-The micrograph is then contaminated with additive white Gaussian noise.
-This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
-Neither the number of occurrences nor the noise level $\sigma$ are known to the algorithm.
-
-In the Methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
-The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
-
-Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the individual signal occurrences, the signals can be estimated accurately given enough data.
-Furthermore, the \TODO{propensity\footnote{Might not be the right word; 'density' is not good because it might refer to the density of the particle for example, whereas here we mean to say the 'fraction of occurrences that come from a particular class'}} of each signal can also be estimated.
-
-%In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-%As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
-%The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-
-%We do not assume the knowledge of the noise level. 
-%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[scale=0.45]{progressive_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1Dhomosignals}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1DhomoRMSE}
-%\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations).
-The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
-Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
-With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
-%		
-%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
-Red signals are the ground truth (targets) and the blue signals are our estimations.
-Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$.
-The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$.
-The $\SNR$ is $1/12$.
-\TODO{1.
-to replace with a ``progress'' plot 2.
-replace the triangle signal 3.
-add error progress figure}
-	}
-	\label{fig:1Dheterosignals}
-\end{figure}
-
-\clearpage
-\section{Discussion}
-
-%\TODO{Discussion: What might the answer imply and why does it matter? How does it fit in with what other researchers have found? What are the perspectives for future research?}
-
-%All current algorithmic pipelines for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-%Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
-Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
-
-In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
-Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
-
-The same general approach can, in principle, be applied directly to SPR from cryo-EM.
-Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken from unknown viewing directions.
-The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
-Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients.
-Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients.
-Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
-
-We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume \TODO{at resolution comparable to that of the particle projections---remove?}.
-This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
-Additional parameters in these equations could encode an unknown viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
-Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
-As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
-Concerns for model bias would also greatly be reduced.
-
-%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here.
-In a future research, we hope to bridge this gap.
-
-Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
-
-One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
-Still, large amounts of data also imply large amounts of computations.
-On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in streaming mode, as only one look at each micrograph is necessary.
-The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
-Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an important question then is whether the equations can be solved meaningfully in practice.
-The proof-of-concept experiments above suggest they might.
-
-%Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
-The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
-At the time, such approaches also seemed challenging.
-
-%\TODO{Do we want to say something about the number of images that we need?
-Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
-(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
-
-Beyond data acquisition and computational challenges, there are modeling issues to consider.
-As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
-First, we assume an additive white noise model, while in practice the noise may be structured or signal dependent.
-To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly.
-Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals.
-Perhaps this separation could be induced by careful experimental design \TODO{?}.
-Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
-Here as well, relations between autocorrelation functions of the data and of the signals can be derived.
-%Each variation leads to a different inverse problem. No sufficient conditions for them to be solvable are currently known.
-
-\TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION?
-Do we also want to stress that models have been refined over decades?
-Both points are rather defensive in nature.	}
-
-\TODO{Should we discuss CTF? Where, and to what extent?}
-
-\TODO{Where and how do we cite Kam? Fred?}
-
-%The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
-Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
-%An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
-
-\section{Methods} \label{sec:methods}
+\subsection{Related work} \label{sec:related_literature}
+
+\paragraph{System identification.}
+
+For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+%
+\begin{math}
+%
+y = x\ast w + \varepsilon,  
+%
+\end{math} 
+%
+where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
+%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our model in the  case of a single signal ($K = 1$).
+The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+%\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
+
+%%%To make the problem well-posed, we must  assume some prior knowledge or  structure.
+In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}.
+Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi 016guaranteed} where the focus is on high $\SNR$ regimes.
+Importantly, in the system identification problem, the goal is only to recover $x$, not the sequence $w$, or in our case, the signal locations $s_i$.
+We refer to the $s_i$'s as \emph{nuisance parameters}.
+
+%%%An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
+The  $s_i$'s  are referred to as \emph{nuisance  variables}.
+Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
+For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the primary goal is only to sharpen the image.
+
+\paragraph{Likelihood-based methods.}
+
+Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
+For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
+If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
+
+Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
+One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
+Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
+Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
+
+In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
+The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
+However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
+%
+%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
+This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
+%
+Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
+In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
+
+Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+
+\TODO{The following was copied from the appendix of the old draft}
+
+Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
+However, most of these procedures are prone to \emph{model bias}.
+For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
+Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
+Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+
+\section{Model} \label{sec:model}
 
@@
 %In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
+
+\section{Autocorrelation analysis}
 
@@
 
-%\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}
+\section{Theory} \label{sec:theory}
+
+\paragraph{The impossibility of detection in low $\SNR$.}
+If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
+To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
+Suppose too that the oracle provides us with $x$ itself.
+That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
+This is an easier problem than detecting the support of $s$.
+Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
+
+\TODO{Here we should give the Will's proposition for the impossibility of detection}
+
+\paragraph{Estimating a signal from its third-order autocorrelation.}
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
+%
+\begin{align} \label{eq-uniqueness}
+%
+z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+%
+\end{align}
+
+In particular, we have proven the following proposition:
+
+\begin{proposition} \label{prop:uniqueness}
+	%
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\end{proposition}
+
+Some remarks are in order.
+First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+
+Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
+%%%and therefore the assumption that the first and last entries are nonzero is met.
+In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+
+\begin{comment}
+
+%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+, this uniqueness result holds for signals of any dimension. Third
+
+Furthermore,
+as proven in the following simple proposition.
+%
+\begin{proposition} \label{prop:uniqueness}
+%
+Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
+Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
+Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
+
+\end{proposition}
+
+\begin{proof}
+%
+By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
+Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
+%
+\begin{equation*}
+%
+a_z^3[k,L-1] = z[0]z[k]z[L-1].
+%
+\end{equation*}
+%
+In addition, 
+%
+\begin{equation*}
+%
+\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+%
+\end{equation*} 
+%
+\end{proof}
+
+A few remarks are in order. 
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+\end{comment}
+
+Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
+Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
+
+\paragraph{Identifiability of parameters from the moments of $y$.}
+
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
+We will show, however, that $x$ is still identifiable from the observed moments of $y$.
+In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
+
+First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
+%
+\begin{proposition} \label{prop:gamma}
+	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
+	%
+	\begin{equation*}
+	%
+	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
+	%
+	\end{equation*}
+	%
+\end{proposition}
+\begin{proof}
+	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
+\end{proof}
+
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
+
+\begin{proposition} \label{prop:gamma_sigma}
+	%
+	Let $K=1$, and $\sigma > 0$ be fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
+\begin{corollary}
+	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
+	\begin{itemize}
+		\item Either the signal $x$ is generic; or
+		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
+	\end{itemize}
+\end{corollary}
+
+\section{Expectation-maximization}
+
+Should we devote a whole section for EM or merge it with the next one?
+
+\section{Results} \label{sec:results}
+
+We conducted two experiments in the simplified image formation model described in the introduction:
+\begin{enumerate}
+	\item The first experiment aims to recover a 2-D image from an increasing number of micrographs with high noise, similar to the rightmost panel of Figure~\ref{fig:micro_example}.
+This is done using moments of second order, as these are sufficient to recover a 2-D image up to elementary symmetries;
+	\item The second experiment aims to recover three distinct 1-D signals from an increasing number of 1-D micrographs with high noise. For this task, it is necessary to use moments up to third order.
+\end{enumerate}
+As outlined below, we find that it is indeed possible to recover accurate estimates of the ground truth signals from the highly corrupted micrographs, without particle picking.
+Furthermore, we find that the quality of estimation increases with the amount of data collected, despite the fact that particle picking remains challenging.
+The Methods section provides additional details.
+In the discussion section, we outline how the general approach could be extended to full 3-D SPR.
+
+In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+A micrograph contains, on average, 700 occurrences of the target image at random locations.
+The latter are chosen so that two occurrences are always separated by at least 49 pixels.
+Thus, about 10\% of each micrograph contains signal.
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
+This high noise level is illustrated in the right panel of Figure~\ref{fig:micro_example}.
+In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.
+
+We compute the average autocorrelation of the micrographs (equivalently, the average of their power spectra).
+This is a particularly simple computation.
+In the methods section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the power spectrum of the unknown image itself.
+Mathematically, it is easy to show that the quality of this estimate improves steadily as the amount of data grows, regardless of noise level.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
+% bauschke2004rrr,
+RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available in \TODO{supplementary material}.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[scale=0.45]{reconstruction1_cropped}
+		\caption{\small $P = 512$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[scale=0.45]{reconstruction10_cropped}
+		\caption{\small $P = 512\times 10$}
+	\end{subfigure}%
+
+		\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[scale=0.45]{reconstruction100_cropped}
+		\caption{ \small $P = 512\times 10^2$ }
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[scale=0.45]{reconstruction1000_cropped}
+		\caption{\small $P = 512\times 10^3$}
+	\end{subfigure}%
+
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.7]{Einstein_progress}
+\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
+\end{figure}
+
+In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy.
+Any two occurrences are separated by at least 20 entries.
+The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion.
+The micrograph is then contaminated with additive white Gaussian noise.
+This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
+Neither the number of occurrences nor the noise level $\sigma$ are known to the algorithm.
+
+In the Methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
+The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
+
+Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the individual signal occurrences, the signals can be estimated accurately given enough data.
+Furthermore, the \TODO{propensity\footnote{Might not be the right word; 'density' is not good because it might refer to the density of the particle for example, whereas here we mean to say the 'fraction of occurrences that come from a particular class'}} of each signal can also be estimated.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
+	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations).
+The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
+Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
+With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
+	}
+	\label{fig:1Dheterosignals}
+\end{figure}
+
+\TODO{The following was copying from the Methods section}
 
@@
 Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
 Thus, we first run the optimization with $W = 2L-1$.
@@
 To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-%\TODO{Should we do variable projection for the gammas, that is, exploit the fact the problem is a regular least squares in the gammas (up to the positivity constraints) to substitute the explicit optimum for them?
-Not sure it's worth the effort.
--- Ok, it's probably not a good idea, because even with fixed gammas to the correct value, optimization takes a while.}
-%\TODO{Do we still need to stress at this point that the optimization part has complexity independent of length of observation? Should be pretty clear at this point already.}
-%
-%
-
-%\TODO{separation}
-%
-%For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
-%The only difference is that here, for each
-%placement, one of the three signals is picked at random proportionally to the desired number
-%of occurrences of each.
-%In this experiment, we computed the first three autocorrelation functions. 
-%We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
-%\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
-
-%To estimate the signal, we use an optimization algorithm on the following nonlinear least-squares problem that estimates the signals and their density of occurrences simultaneously:
-%\begin{multline}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2.
-%\label{eq:optim1D}
-%\end{multline}
-%where $W \geq L$ is the length of the sought signals and $w_1 = \frac{1}{2}, w_2 =\frac{1}{2}(L-1), w_3 = \frac{1}{(L-1)(L-2)}$; see~\cite{boumal2017heterogeneous} see for discussion on how to choose the weights properly.
-
-%Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-%Since we can only initialize randomly at first, this approach would often fail in practice. Alternatively,
-%Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have fewer poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ whose autocorrelation functions are closest to the measured ones in the sense of~\eqref{eq:optim1D}.
-%This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints \TODO{reference} on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
@@
 \TODO{Note the last two sentences!}
+
+\section{Application to cryo-EM}
+\TODO{should be concise; the details are in the Nature paper}
+
+\section{Discussion}
+
+In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
+Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
+Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
+Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
+
+The same general approach can, in principle, be applied directly to SPR from cryo-EM.
+Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken from unknown viewing directions.
+The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
+Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients.
+Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients.
+Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
+
+We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume \TODO{at resolution comparable to that of the particle projections---remove?}.
+This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
+Additional parameters in these equations could encode an unknown viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
+Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
+As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
+Concerns for model bias would also greatly be reduced.
+
+%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
+As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
+That being said, the SPR model is far more complicated than the model presented here.
+In a future research, we hope to bridge this gap.
+
+Of course, we recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
+
+One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
+Still, large amounts of data also imply large amounts of computations.
+On this front, we note that computing autocorrelations of low orders can be done efficiently on CPUs and GPUs, and in parallel across micrographs.
+It can even be done in streaming mode, as only one look at each micrograph is necessary.
+The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
+Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
+Of course, an important question then is whether the equations can be solved meaningfully in practice.
+The proof-of-concept experiments above suggest they might.
+
+Beyond data acquisition and computational challenges, there are modeling issues to consider.
+As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
+First, we assume an additive white noise model, while in practice the noise may be structured or signal dependent.
+To address this point, it may be necessary to investigate better noise models and to extend the autocorrelation analysis accordingly.
+Second, we assume that any two signal occurrences are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the target signals.
+Perhaps this separation could be induced by careful experimental design \TODO{?}.
+Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
+Here as well, relations between autocorrelation functions of the data and of the signals can be derived.
+
+\TODO{Should we discuss CTF? Where, and to what extent?}
+
+\TODO{Where and how do we cite Kam? Fred?}
+
+\paragraph{Open theoretical questions.}
+
+Our method of estimating $x$ uses the third-order moments of the observations.
+These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
+Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error in the low $\SNR$ regime.
+In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
+
+Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
+In~\cite{boumal2017heterogeneous}, it was empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
+In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
+In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
+
+%%%That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
+
+%The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on.
+Using this auxiliary variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}.
+%An interesting question is  under what conditions on $p$ and the signals, one can estimate the signals from the data.
 
@@
 
-\begin{comment}
-Writing explicitly in terms of signal and noise, the sum can be broken into eight terms.
-The first contains only signal terms (does not see noise) and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-Three other terms contain the product of two signal entries and one noise term.
-Since the noise is independent of the signal and has zero mean, these terms go to zero almost surely.
-
-We next analyze the contribution of the term composed of triple products of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
-\begin{equation*}
-\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
-\end{equation*}
-For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely.
-For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each one is a triple product of Gaussian variables with zero mean and therefore has zero expectation.
-
-To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry.
-Most of these terms converge to zero almost surely because of independency between the noise entries.
-For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$; c.f.~\cite{boumal2017heterogeneous}.
-
-\end{comment}
-
-\section{Related work} \label{sec:related_literature}
-
-\paragraph{System identification.}
-
-For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
-%
-\begin{math}
-%
-y = x\ast w + \varepsilon,  
-%
-\end{math} 
-%
-where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our model in the  case of a single signal ($K = 1$).
-The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-%\TODO{ref this by Giannakis: \cite{giannakis1989identification}}
-
-%%%To make the problem well-posed, we must  assume some prior knowledge or  structure.
-In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}.
-Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi 016guaranteed} where the focus is on high $\SNR$ regimes.
-Importantly, in the system identification problem, the goal is only to recover $x$, not the sequence $w$, or in our case, the signal locations $s_i$.
-We refer to the $s_i$'s as \emph{nuisance parameters}.
-
-%%%An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s.
-The  $s_i$'s  are referred to as \emph{nuisance  variables}.
-Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals.
-For instance, in image deblurring, both the blurring kernel and the high-resolution image are unknown, but the primary goal is only to sharpen the image.
-
-\paragraph{Likelihood-based methods.}
-
-Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
-For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
-If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
-
-Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
-One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
-Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
-
-In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
-The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
-However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
-%
-%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-%
-Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
-
-Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-
-%
-
-\section{Theory} \label{sec:theory}
-
-\paragraph{The impossibility of detection in low $\SNR$.}
-If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
-Suppose too that the oracle provides us with $x$ itself.
-That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
-This is an easier problem than detecting the support of $s$.
-Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
-
-\TODO{NB: This is an important point for us.
-As stated, it is imprecise.
-I like the reduction idea to $M$ windows, but then two things: (1) if we cite Aguerrebere, we need to be specific what theorem we reference and we need to check the assumptions, and (b) in any case, we need to be precise regarding what "impossible" means -- I'm guessing the result is a bit more subtle, saying something like: the probability of type I / type II error is at least this much.
-Also, someone might oppose that we don't need to get them \emph{all} right, and we don't need to get them \emph{exactly} right..
-To address such concerns, we need to be specific.
-After reading the Aguerberre paper quite carefully, one of the important points in there is that they assume a continuous model, so that shifts are continuous (that's why they can do CRBs -- CRBs are not defined for discrete problems; of course, you could define them with some work (I assume), but that's not what they did, so just referencing them doesn't cut it.}
-
-\TODO{NB: Here is a suggestion: we could further simplify the problem by having the oracle also state, for each window, that the shift is either of two possibly shifts (with 50/50 prior.) Then, knowing all of this and also knowing $x$, deciding which shift it is is a matter of deciding which Gaussian a vector came from, where both Gaussians have $\sigma^2 I$ variance and known mean.
-So, the distance test (which is equivalent to the likelihood ratio test) is optimal (that ought to be a Neyman-Pearson result).
-The probability of mistake is then at least $\frac{1}{2}\operatorname{erfc}\left(\frac{\|x_{shift 1} - x_{shift 2}\|}{2\sigma}\right)$, where $x_{shift 1}$ is a signal of the length of the given window with $x$ placed at a certain position, and zeros elsewhere.
-We can then argue that (if there is a positive lower bound on the norms up there), there always exists a sigma such that the probability of mistake is this incredibly simpler problem is still arbitrarily close to 1/2 (random chance.) having said all of that, we can then also reference Aguereberre (carefully) and make the point that, in their specific setup, they show getting a lot of images indeed helps, but not beyond a certain error level which has to do with sigma, so that for large sigma, however much data we get, we can't estimate shifts (in their setting) accurately.}
-
-%%%As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.
-
-%
-
-\paragraph{Estimating a signal from its third-order autocorrelation.}
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
-%
-\begin{align} \label{eq-uniqueness}
-%
-z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
-%
-\end{align}
-
-In particular, we have proven the following proposition:
-
-\begin{proposition} \label{prop:uniqueness}
-	%
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-\end{proposition}
-
-Some remarks are in order.
-First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-
-Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
-%%%and therefore the assumption that the first and last entries are nonzero is met.
-In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-
-\begin{comment}
-
-%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-, this uniqueness result holds for signals of any dimension. Third
-
-Furthermore,
-as proven in the following simple proposition.
-%
-\begin{proposition} \label{prop:uniqueness}
-%
-Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
-Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
-
-\end{proposition}
-
-\begin{proof}
-%
-By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
-Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
-%
-\begin{equation*}
-%
-a_z^3[k,L-1] = z[0]z[k]z[L-1].
-%
-\end{equation*}
-%
-In addition, 
-%
-\begin{equation*}
-%
-\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
-%
-\end{equation*} 
-%
-\end{proof}
-
-A few remarks are in order. 
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-\end{comment}
-
-Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
-Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-
-\paragraph{Identifiability of parameters from the moments of $y$.}
-
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
-We will show, however, that $x$ is still identifiable from the observed moments of $y$.
-In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
-
-First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
-%
-\begin{proposition} \label{prop:gamma}
-	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
-	%
-	\begin{equation*}
-	%
-	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
-	%
-	\end{equation*}
-	%
-\end{proposition}
-\begin{proof}
-	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
-\end{proof}
-
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
-
-\begin{proposition} \label{prop:gamma_sigma}
-	%
-	Let $K=1$, and $\sigma > 0$ be fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
-\begin{corollary}
-	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
-	\begin{itemize}
-		\item Either the signal $x$ is generic; or
-		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
-	\end{itemize}
-\end{corollary}
-
-\paragraph{Open theoretical questions.}
-
-Our method of estimating $x$ uses the third-order moments of the observations.
-These empirical moments are used to obtain consistent estimators of population parameters related to the the mean and second- and third-order autocorrelations of $x$, to which we fit the signal $x$.
-Consequently, the number of signal occurrences $M$ should grow at least as fast as $1/\SNR^3$ to achieve a constant estimation error in the low $\SNR$ regime.
-In the related problem of multireference alignment~\cite{perry2017sample,abbe2017multireference}, this is optimal in the low $\SNR$ regime; we conjecture that the same is true for our problem.
-
-Another interesting question is how many signals $x_1,\dots,x_K$ can be demixed from their mixed autocorrelation functions.
-In~\cite{boumal2017heterogeneous}, it was empirically observed that $K \sim \sqrt{L}$ signals can be estimated simultaneously from their mixed second- and third-order autocorrelations, using the least-squares procedure.
-In~\cite{weinthesis} [TKTK: add reference to Alex Wein's thesis, or put personal correspondence], this result is shown theoretically for a different, and much less efficient, algorithm.
-In our current setting, the additional parameters $\gamma$ and $\sigma$ make the problem more challenging; however, we conjecture that the number of estimable signals still grows like $\sqrt{L}$.
-
-%%%That being said, we conjecture that the number of signals that can be demixed by an efficient algorithm is significantly smaller, and scales like $\sqrt{L}$; see~\cite{boumal2017heterogeneous,weinthesis} [TKTK: reference for missing Wein's thesis].
-
 %%% We conjecture that similarly to the
@@
 
-\section{Stuff}
-
-\TODO{Might go to related work section}
-
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
-
-\section{The autocorrelation functions in cryo--EM} \label{sec:cryoem}
-
-\TODO{The most up to date version is the one from the patent -- to update here too.}
-
-The 3-D Fourier transform of an L-bandlimited 3-D volume (e.g., particle) can be expanded by  spherical harmonics:
-\begin{equation} \label{eq:volume}
-\hat{V}(k,\theta,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)Y_\ell^{m}(\theta,\phi),
-\end{equation}
-where $(\theta,\phi)$ are two angles on the sphere, $k$ is the radial coordinate, $Y_{\ell}^m(\theta,\phi)$ is the spherical harmonic of degree $\ell$ and order $m$ and  $A_{\ell,m}(k)$ are the associated spherical harmonics coefficients, to be estimated.
-A rotation of the volume by $\omega\in SO(3)$ can be described using the Wigner D-function $D_{m,m'}^{\ell}$:
-\begin{equation}
-\begin{split}
-(R_\omega \hat{V})(k,\theta,\phi)  &= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k)(R_\omega Y_\ell^{m})(\theta,\phi) \\
-&= \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\theta,\phi).
-\end{split}
-\end{equation}
-
-By the Fourier slice theorem, each cryo--EM measurement (projection) is equivalent (through 2-D Fourier transform) to the slice of $\hat{V}$, associated with $\theta= \pi/2$, after $\hat{V}$ was rotated by $\omega\in SO(3)$.
-Explicitly, the Fourier transform of a projection from the viewing direction $\omega$ is related to the spherical harmonic coefficients of the object through:
-\begin{equation} \label{eq:P}
-\begin{split}
-P_\omega(k,\phi)  = \sum_{\ell=0}^{L} \sum_{m=-\ell}^{\ell} A_{\ell,m}(k) 
-\sum_{m'=-\ell}^{m=\ell}{D_{m,m'}^{\ell}(\omega)}Y_\ell^{m'}(\pi/2,\phi).
-\end{split}
-\end{equation}
-
-Next, we want to relate the projections $P_\omega$ with the autocorrelation functions computed from the micrograph.
-We assume the projections are sufficiently separated so that the $(\Delta_x,\Delta_y)$ entry of the second-order autocorrelation of the micrograph is proportional to:
-\begin{equation}
-	M_2(\Delta_x, \Delta_y) \propto \sum_{n=1}^N \sum_{x,y}P_n(x,y)P_n(x+\Delta_x,y+\Delta_y) + \textrm{bias},
-\end{equation}
-where $P_n$ denotes the $n$th projection.
-The assumption here is that $(\Delta_x, \Delta_y)$ are small enough so that, in computing the auto-correlation, points $(x, y)$ and $(x+\Delta_x, y+\Delta_y)$ do not touch distinct particles.
-By taking $n\to\infty$ and assuming uniform distribution of viewing directions, we get
-\begin{equation}
-M_2(\Delta_x,\Delta_y)\propto\sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x,y+\Delta_y)d\omega.
-\end{equation}
-In the same way and under the same conditions, the third moment is given by 
-\begin{equation} 
-M_3(\Delta_x^1,\Delta_y^1;\Delta_x^2,\Delta_y^2) \propto \sum_{x,y}\int_{\omega} P_\omega(x,y)P_\omega(x+\Delta_x^1,y+\Delta_y^1)P_\omega(x+\Delta_x^2,y+\Delta_y^2)d\omega + \textrm{bias}.
-\end{equation}
-
-In order to determine the particle, by~\eqref{eq:volume} one needs to estimate on the order of $L^3$ spherical harmonics coefficients.
-If the pixel size is proportional to $1/L$ (to match the volume's resolution), then $M_3$ provides on the order of $L^4$ equations involving triple products of $P_\omega$.
-Since $P_\omega$ depends (after coordinate transformation) linearly in the spherical harmonic coefficients through~\eqref{eq:P}, this means we have a system of $\sim L^4$ cubic equations in the $\sim L^3$ sought parameters.
-Importantly, the coefficients of these equations can be estimated from the micrographs directly, without particle picking stage.
-
 \end{document}

### 2018-08-06 TEX/draft_biology.tex
updated figures for the 2-D example (no tex editing for now)

@@
 By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.
-\TODO{Do we want to replace with a cryo-EM figure?}}
+\TODO{Do we want to replace with a cryo-EM figure?
+This figure will be positioned with the rest of the figures about Einstein's example}}
 \end{figure}
@@
 
+%\begin{figure}[h!]
+%	\centering
+%	\begin{subfigure}[h]{0.45\textwidth}
+%		\centering
+%		\includegraphics[scale=0.45]{reconstruction1_cropped}
+%		\caption{\small $P = 512$}
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.45\textwidth}
+%		\centering
+%		\includegraphics[scale=0.45]{reconstruction10_cropped}
+%		\caption{\small $P = 512\times 10$}
+%	\end{subfigure}%
+%
+%		\begin{subfigure}[h]{0.45\textwidth}
+%		\centering
+%		\includegraphics[scale=0.45]{reconstruction100_cropped}
+%		\caption{ \small $P = 512\times 10^2$ }
+%	\end{subfigure}%
+%	\begin{subfigure}[h]{0.45\textwidth}
+%		\centering
+%		\includegraphics[scale=0.45]{reconstruction1000_cropped}
+%		\caption{\small $P = 512\times 10^3$}
+%	\end{subfigure}%
+%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
+This does not require particle picking.
+A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
+Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
+%		\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
+%		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
+%	}
+%\end{figure}
+%
+
 \begin{figure}[h!]
 	\centering
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1_cropped}
-		\caption{\small $P = 512$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction10_cropped}
-		\caption{\small $P = 512\times 10$}
-	\end{subfigure}%
-
-		\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction100_cropped}
-		\caption{ \small $P = 512\times 10^2$ }
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.45\textwidth}
-		\centering
-		\includegraphics[scale=0.45]{reconstruction1000_cropped}
-		\caption{\small $P = 512\times 10^3$}
-	\end{subfigure}%
-
-%	\begin{subfigure}[h]{0.33\textwidth}
-%		\centering
-%		\includegraphics[scale=0.33]{Einstein_progress_cropped}
-%		\caption{\label{fig:err_curve}\small Error curve}
-%	\end{subfigure}%
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{Newton}
-%		\caption{\label{fig:newton}Newton  (model)}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction2}
-%		\caption{\small $P =1024$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction20}
-%		\caption{$P = 1024\times 10$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.25\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{reconstruction200}
-%		\caption{$P = 1024\times 100$}
-%	\end{subfigure}%
+\includegraphics[scale=0.8]{Einstien_progress_examples}
 \caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
@@
 Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-		\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
+		%\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
 		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
@@
 \centering
-\includegraphics[scale=.7]{Einstein_progress}
-\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
+\includegraphics[scale=1]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
+%\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
 \end{figure}

### 2018-08-07 TEX/inverse_problem_draft.tex
updated figures for the 2-D example (no tex editing for now)
outline of the inverse problems draft

@@
 
+We consider the problem of estimating a signal from its multiple occurrences in a measurement.
+In the high SNR regime, the problem is easy.
+In the low SNR, it becomes interesting and that is the focus of this paper.
+
+The problem can be posed as blind deconvolution between the signal and a sparse binary signal.
+We can also consider the extension for multiple signals.
+
 \begin{figure}[t]
@@
 
-\subsection{Related work} \label{sec:related_literature}
+\subsection{Model}
 
-\paragraph{System identification.}
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple shorter micrographs concatenated into one.)
+The forward model (or ``image'' formation model) is as follows.
+For each target signal $x_k$, an unknown binary signal $s_k \in \{0, 1\}^{N-L+1}$ indicates (with 1's) the starting positions of all occurrences of $x_k$ in $y$, so that, with additive white Gaussian noise:
+\begin{align}
+y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{align}
+where $\ast$ denotes linear convolution. The binary signals obey the following property:
+\begin{align}
+\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{align}
+In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+
+From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
+In contrast, particle picking is the task of estimating the binary signal $s = s_1 + \cdots + s_K$, while clustering is the task of separating $s$ into its components $s_1, \ldots, s_K$.
+Neither of the latter can be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
+
+%We denote the set of these nonzero values by 
+% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
+%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
+%Neither the $M_i$'s nor $M$ are assumed to be known.
+
+Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
+Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
+
+We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
+For ease of exposition, we do so in the 1-D case.
+Extension to the 2-D case is straightforward.
+We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
+
+\subsection{Related work}
 
@@
 
-\paragraph{Likelihood-based methods.}
-
 Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
@@
 However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
-%
-%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem.
-This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
-%
+
 Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
@@
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+
+\subsection{Main motivation: The cryo-EM problem}
 
@@
 
-\section{Model} \label{sec:model}
-
-We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
-For ease of exposition, we do so in the 1-D case.
-Extension to the 2-D case is straightforward.
-We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple shorter micrographs concatenated into one.)
-The forward model (or ``image'' formation model) is as follows.
-For each target signal $x_k$, an unknown binary signal $s_k \in \{0, 1\}^{N-L+1}$ indicates (with 1's) the starting positions of all occurrences of $x_k$ in $y$, so that, with additive white Gaussian noise:
-\begin{align}
-y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
-\label{eq:model}
-\end{align}
-where $\ast$ denotes linear convolution. The binary signals obey the following property:
-\begin{align}
-\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
-\label{eq:spacing}
-\end{align}
-In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-
-From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
-In contrast, particle picking is the task of estimating the binary signal $s = s_1 + \cdots + s_K$, while clustering is the task of separating $s$ into its components $s_1, \ldots, s_K$.
-Neither of the latter can be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
-
-%We denote the set of these nonzero values by 
-% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-%Neither the $M_i$'s nor $M$ are assumed to be known.
-
-Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
-Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
-
-%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
-%\begin{align}
-%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
-%  \label{eq:spacing}
-%\end{align}
-%The goal is to estimate $x_1,\ldots,x_K$ from $y$.
-
-%
-%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
-%
-%Our method for estimating the signals is composed of two stages. 
-%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
-Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
-
 \section{Autocorrelation analysis}
-
-\paragraph{Aperiodic autocorrelation functions}
-%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}
-
-%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}
 
@@
 
-\paragraph{Estimating the autocorrelation function of a single signal.}
+\subsection{The single signal case}
 
@@
 
-\paragraph{Estimating the autocorrelation function of multiple signals.}
+\subsection{The single signal case}
 
@@
 
+\subsection{Poisson model (rename)}
+
 \section{Theory} \label{sec:theory}
 
-\paragraph{The impossibility of detection in low $\SNR$.}
 If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
@@
 \TODO{Here we should give the Will's proposition for the impossibility of detection}
-
-\paragraph{Estimating a signal from its third-order autocorrelation.}
 
@@
 However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-
-\paragraph{Identifiability of parameters from the moments of $y$.}
 

### 2018-08-08 TEX/inverse_problem_draft.tex
inverse draft

@@
 
-\author{Tamir Bendory, Nicolas Boumal, William Leeb and Amit Singer}
+\author{Tamir Bendory, Nicolas Boumal, William Leeb, Eitan Levin and Amit Singer}
 \maketitle
@@
 In the low SNR, it becomes interesting and that is the focus of this paper.
-
 The problem can be posed as blind deconvolution between the signal and a sparse binary signal.
 We can also consider the extension for multiple signals.
+
+The main motivation for this paper arises from single particle reconstruction using cryo-electron microscopy (cryo-EM). In cryo-EM, multiple samples .....
+
+in low SNR detection is impossible.
+This led to the belief in the cryo-EM community is reconstruction of small molecules is impossible.
+We claim that this argument is wrong.
+While this paper focused on the mathematical toy model, Section TKTK discusses the application to cryo-EM.
+A companion paper focused on this application and provides all the details~\cite{bendory2018toward}.
 
@@
 In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+It can be also extended to Poison model; see Section TKTK.
 
@@
 Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
-Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
+%Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
 
@@
 However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
-To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
+We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
+%
+%To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
 Suppose too that the oracle provides us with $x$ itself.
@@
 
-\TODO{Here we should give the Will's proposition for the impossibility of detection}
+%\TODO{Here we should give the Will's proposition for the impossibility of detection}
+
+Therefor, we need to consider a different approach.
+In this paper, we consider autocorrelation analysis.
+In what follows, we present several results on properties of autocorrelations.
+For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.
 

### 2018-08-08 TEX/notes_will/notes_will_poisson.tex
updates inverse problems draft

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{url} 
\usepackage[authoryear]{natbib}
%%%\usepackage{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{framed}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%%%\usepackage{custom_tex}
\usepackage{grffile}
\usepackage{multirow}
\usepackage{xcolor}
%\usepackage{setspace}
\usepackage{comment}
\usepackage{xr}

\newtheorem{thm}{Theorem}[section]
\newtheorem{definition}[thm]{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{example}[thm]{Example}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{thm}
\newtheorem{conj}{Conjecture}
\theoremstyle{definition}
\newtheorem{rmk}{Remark}

\renewcommand{\AA}{\mathcal{A}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\FF}{\mathcal{F}}

\newcommand{\R}{\mathbb{R}}

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\Poisson}{\text{Poisson}}
\newcommand{\M}{\mathcal{M}}

\newcommand{\mean}[2]{\frac{1}{#1}\sum_{#2=1}^{#1}}

\renewcommand{\P}{\mathbb{P}}
\renewcommand{\L}{\mathcal{L}}

%
%
%
%

\begin{document}
\title{Notes on Poisson Model for Big MRA}
\author{William Leeb}
\date{}
\maketitle

\section{Setup}

We consider the following observation model. $X = (X[0],\dots,X[L-1])$ is a random vector of length $L$, drawn from some fixed distribution. For fixed $n$, we observe a random vector $Y$ of length $n+L$, generated as follows. Points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$. For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poission process $M_i$'s are iid and $M_i \sim \Poisson(\gamma)$. Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.

With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
%
\begin{align}
%
Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
%
\end{align}

We will denote by $\M_l$ the moments of $X$:
%
\begin{align}
%
\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
%
\end{align}
%
\begin{align}
%
\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
%
\end{align}
%
and
%
\begin{align}
%
\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
%
\end{align}

We will also denote by $\L_l$ the autocorrelations of $X$:
%
\begin{align}
%
\L_1 = \sum_{i=0}^{L-1} \M_1[i],
%
\end{align}
%
\begin{align}
%
\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta],
%
\end{align}
%
and
%
\begin{align}
%
\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2].
%
\end{align}

Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.

%

In this notation, we will show that the first moment of the data is $\gamma \L_1$, the second moment vector is $(\gamma \L_1)^2 + \gamma \L_2(\Delta)$, and the third moment matrix is $(\gamma \L_1)^3 + \gamma \L_1  \cdot ( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)) + \gamma \L_3(\Delta_1,\Delta_2) $. In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''. So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.

%

\section{The first moment of $Y$}

To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_n)$, and then average over $M$. We have:
%
\begin{align}
%
\E[Y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \M_1[j]
= M_{i-j} \sum_{j=0}^{L-1} \M_1[j].
%
\end{align}
%
Now taking expectations over $M$ we see:
%
\begin{align}
%
\E Y[i] = \gamma \sum_{j=0}^{L-1} \M_1[j] = \gamma \L_1.
%
\end{align}

%

\section{The second moment of $Y$}

Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
%
\begin{align}
%
Y_{i_1} Y_{i_2} 
    &= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
        \sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
            X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
%
\end{align}

We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$. In the first case, all the terms are independent, and so the expectation factors. In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not. This gives (all expectations are conditional on $M$):
%
\begin{align}
%
\E Y_{i_1} Y_{i_2}
=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
    \sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
        \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
    \nonumber \\
=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
    \sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
        \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
        \E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
    \nonumber \\
=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
%
\end{align}
%
Now take expectations over the Poisson random variables, using this fact:
%
\begin{lem} \label{lem-choose}
If $M \sim \Poisson(\gamma)$, then 
\begin{align}
%
\E {M\choose k} = \frac{\gamma^k}{k!}.
%
\end{align}
\end{lem}

We get (now the expectation is over $M$ and $X$):
%
\begin{align}
%
\E Y_{i_1} Y_{i_2} 
=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
    \nonumber \\
=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
    + \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
    \nonumber \\
    & + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
    \nonumber \\
=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
    + \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
    \nonumber \\
=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
%
\end{align}

But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.

%

\section{The third moment of $Y$}

For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
%
\begin{align}
%
&Y_{i_1} Y_{i_2} Y_{i_3}
    \nonumber \\
&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
    \sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
        X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
\end{align}
%
We will break up the outer three sums into disjoint sums with the following ranges of indices:
%
\begin{enumerate}

\item \label{case1}
$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.

\item \label{case2}
$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.

\item \label{case3}
$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.

\item \label{case4}
$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.

\item \label{case5}
$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.

\end{enumerate}

For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
%
\begin{align}
%
&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
    \nonumber \\
=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
        }_{\text{(a)}}
    \nonumber \\
&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
        }_{\text{(b)}}
    \nonumber \\
&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
        }_{\text{(c)}}
    \nonumber \\
&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
        }_{\text{(d)}}
    \nonumber \\
&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
    X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
        }_{\text{(e)}}.
%
\end{align}

For term (a), the expectation conditional on $M$ is:
%
\begin{align}
%
\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
%
\end{align}
%
Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
%
\begin{align} \label{aaaa}
%
\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
%
\end{align}

For term (b), the expectation conditional on $M$ is:
%
\begin{align}
%
\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
%
\end{align}
%
and then again using Lemma \ref{lem-choose} we get the expected value:
%
\begin{align} \label{bbbb}
%
\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
%
\end{align}

Similarly, the expected values of terms (c) and (d) are:
%
\begin{align} \label{cccc}
%
\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
%
\end{align}
%
and
%
\begin{align} \label{dddd}
%
\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
%
\end{align}

Finally, the expected value of term (e) is easily shown to be:
%
\begin{align} \label{eeee}
%
\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
%
\end{align}
%
This concludes the computation for Case \ref{case1}.

Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
%
\begin{align}
%
& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
    \sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
        X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
    \nonumber \\
=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
    \Bigg\{
    \sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
        X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
    \nonumber \\
&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
            X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
%
\end{align}
%
Taking expectations conditional on $M$, we then get:
%
\begin{align}
%
& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
    \Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
    \nonumber \\
&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
%
\end{align}

Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
%
\begin{align}
%
& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
        \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
    \label{ffff} \\
& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
        \M_2[j_1,j_1+\Delta_1] \M_1[j_3].
    \label{gggg}
%
\end{align}

Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
%
\begin{align}
%
& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
        \M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
    \label{hhhh} \\
& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
        \M_2[j_1,j_1+\Delta_2] \M_1[j_2]
    \label{iiii}
%
\end{align}
%
and
%
\begin{align}
%
& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
        \M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
    \label{jjjj}\\
& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
        \M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
    \label{kkkk}
%
\end{align}

Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct. Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
%
\begin{align}
%
\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
%
\end{align}
%
since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
%
\begin{align} \label{llll}
%
\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
%
\end{align}

Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
%
\begin{align}
%
(\gamma \L_1)^3.
%
\end{align}

Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
%
\begin{align}
%
\gamma \L_1  \cdot 
    ( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
%
\end{align}
%
Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
%
\begin{align}
%
\gamma \L_3(\Delta_1,\Delta_2)
%
\end{align}
%
which is the usual third-order auto-correlation.

%

\section{Signal plus noise}

The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case. The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.

\end{document}

### 2018-08-08 TEX/inverse_problem_draft.tex

@@
 \newcommand{\1}{\mathbf{1}}
+\newcommand{\M}{\mathcal{M}}
+\newcommand{\Poisson}{\text{Poisson}}
+%\renewcommand{\P}{\mathbb{P}}
+%\renewcommand{\L}{\mathcal{L}}
 
@@
 
-\newcommand{\reals}{\mathbb{R}}
+\newcommand{\R}{\mathbb{R}}
+
 \newcommand{\RL}{\mathbb{R}^L}
@@
 \end{align}
-where $\ast$ denotes linear convolution. The binary signals obey the following property:
+where $\ast$ denotes linear convolution. 
+We consider two models for the generative process of the sparse signal:
+
+\paragraph{The well separated support model.}
+The binary signals obey the following property:
 \begin{align}
@@
 In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-It can be also extended to Poison model; see Section TKTK.
+
+\paragraph{Poisson process model.} In this model, points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$.
+For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+
+If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poission process $M_i$'s are i.i.d.\
+ and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+
+With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
+%
+\begin{align}
+%
+Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+%
+\end{align}
 
@@
 
-\subsection{Poisson model (rename)}
+\subsection{Autocorrelations of the Poisson process model}
+
+From the first three autocorrelations of the Poisson model one can compute the first three autocorrelations of the well-separated model.
+
+\begin{proposition} \label{prop:poisson_model}
+Under the Poisson process model, the first autocorrelation  is $\gamma \LL_1$, the second moment vector is $(\gamma \LL_1)^2 + \gamma \LL_2(\Delta)$, and the third moment matrix is $(\gamma \LL_1)^3 + \gamma \LL_1  \cdot ( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)) + \gamma \LL_3(\Delta_1,\Delta_2) $.
+In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''.
+So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.
+\end{proposition}
 
@@
 \begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \reals^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \R^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
 \label{eq:optim1D}
@@
 
+\section{Proof of Proposition~\ref{prop:poisson_model}}
+
+%\section{Setup}
+%
+%We consider the following observation model.
+$X = (X[0],\dots,X[L-1])$ is a random vector of length $L$, drawn from some fixed distribution.
+For fixed $n$, we observe a random vector $Y$ of length $n+L$, generated as follows.
+Points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$.
+For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+%
+%If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poission process $M_i$'s are iid and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+%
+%With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
+%%
+%\begin{align}
+%%
+%Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+%%
+%\end{align}
+
+We will denote by $\M_l$ the moments of $X$:
+%
+\begin{align}
+%
+\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+We will also denote by $\L_l$ the autocorrelations of $X$:
+%
+\begin{align}
+%
+\LL_1 = \sum_{i=0}^{L-1} \M_1[i],
+%
+\end{align}
+%
+\begin{align}
+%
+\LL_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta],
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+\LL_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2].
+%
+\end{align}
+
+Note that in the strongly-separated model, the first three observed moments are, respectively, $\LL_1$, $\LL_2(\Delta)$, and $\LL_3(\Delta_1,\Delta_2)$.
+
+%
+
+In this notation, we will show that the first moment of the data is $\gamma \LL_1$, the second moment vector is $(\gamma \LL_1)^2 + \gamma \LL_2(\Delta)$, and the third moment matrix is $(\gamma \LL_1)^3 + \gamma \LL_1  \cdot ( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)) + \gamma \LL_3(\Delta_1,\Delta_2) $.
+In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''.
+So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.
+
+%
+
+\section{The first moment of $Y$}
+
+To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_n)$, and then average over $M$. We have:
+%
+\begin{align}
+%
+\E[Y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
+= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \M_1[j]
+= M_{i-j} \sum_{j=0}^{L-1} \M_1[j].
+%
+\end{align}
+%
+Now taking expectations over $M$ we see:
+%
+\begin{align}
+%
+\E Y[i] = \gamma \sum_{j=0}^{L-1} \M_1[j] = \gamma \LL_1.
+%
+\end{align}
+
+%
+
+\section{The second moment of $Y$}
+
+Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%
+\begin{align}
+%
+Y_{i_1} Y_{i_2} 
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
+%
+\end{align}
+
+We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+In the first case, all the terms are independent, and so the expectation factors.
+In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
+This gives (all expectations are conditional on $M$):
+
+\begin{align}
+%
+\E Y_{i_1} Y_{i_2}
+=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+%
+\end{align}
+%
+Now take expectations over the Poisson random variables, using this fact:
+%
+\begin{lem} \label{lem-choose}
+	If $M \sim \Poisson(\gamma)$, then 
+	\begin{align}
+	%
+	\E {M\choose k} = \frac{\gamma^k}{k!}.
+	%
+	\end{align}
+\end{lem}
+
+We get (now the expectation is over $M$ and $X$):
+%
+\begin{align}
+%
+\E Y_{i_1} Y_{i_2} 
+=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
++ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
+\nonumber \\
+=&  (\gamma \LL_1)^2 + \gamma \LL_2(\Delta).
+%
+\end{align}
+
+But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \LL_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+
+%
+
+\section{The third moment of $Y$}
+
+For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%
+\begin{align}
+%
+&Y_{i_1} Y_{i_2} Y_{i_3}
+\nonumber \\
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
+\end{align}
+%
+We will break up the outer three sums into disjoint sums with the following ranges of indices:
+%
+\begin{enumerate}
+
+	\item \label{case1}
+	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case2}
+	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case3}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+
+	\item \label{case4}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case5}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+\end{enumerate}
+
+For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%
+\begin{align}
+%
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
+X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+\nonumber \\
+=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(a)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(b)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(c)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(d)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(e)}}.
+%
+\end{align}
+
+For term (a), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+%
+\end{align}
+%
+Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
+%
+\begin{align} \label{aaaa}
+%
+\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+For term (b), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+%
+\end{align}
+%
+and then again using Lemma \ref{lem-choose} we get the expected value:
+%
+\begin{align} \label{bbbb}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+Similarly, the expected values of terms (c) and (d) are:
+%
+\begin{align} \label{cccc}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+%
+\end{align}
+%
+and
+%
+\begin{align} \label{dddd}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+%
+\end{align}
+
+Finally, the expected value of term (e) is easily shown to be:
+%
+\begin{align} \label{eeee}
+%
+\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+%
+\end{align}
+%
+This concludes the computation for Case \ref{case1}.
+
+Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+\Bigg\{
+\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
+\nonumber \\
+&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
+%
+\end{align}
+%
+Taking expectations conditional on $M$, we then get:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\nonumber \\
+&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\label{ffff} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
+\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+\label{gggg}
+%
+\end{align}
+
+Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
+\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+\label{hhhh} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
+\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+\label{iiii}
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
+\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+\label{jjjj}\\
+& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
+\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+\label{kkkk}
+%
+\end{align}
+
+Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
+Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%
+\end{align}
+%
+since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
+%
+\begin{align} \label{llll}
+%
+\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+%
+\end{align}
+
+Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
+%
+\begin{align}
+%
+(\gamma \LL_1)^3.
+%
+\end{align}
+
+Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
+%
+\begin{align}
+%
+\gamma \LL_1  \cdot 
+( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)).
+%
+\end{align}
+%
+Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
+%
+\begin{align}
+%
+\gamma \LL_3(\Delta_1,\Delta_2)
+%
+\end{align}
+%
+which is the usual third-order auto-correlation.
+
+%
+
+\section{Signal plus noise}
+
+The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
+The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.
+
 \end{document}

### 2018-08-13 TEX/inverse_problem_draft.tex
inverse problem draft

@@
 
-\title{Estimation below the detection limit with application to cryo-em}
+\title{Estimation below the detection limit with application to cryo-EM}
 
@@
 
-We consider the problem of estimating a signal from its multiple occurrences in a measurement.
-In the high SNR regime, the problem is easy.
-In the low SNR, it becomes interesting and that is the focus of this paper.
-The problem can be posed as blind deconvolution between the signal and a sparse binary signal.
-We can also consider the extension for multiple signals.
-
-The main motivation for this paper arises from single particle reconstruction using cryo-electron microscopy (cryo-EM). In cryo-EM, multiple samples .....
-
-in low SNR detection is impossible.
-This led to the belief in the cryo-EM community is reconstruction of small molecules is impossible.
-We claim that this argument is wrong.
-While this paper focused on the mathematical toy model, Section TKTK discusses the application to cryo-EM.
-A companion paper focused on this application and provides all the details~\cite{bendory2018toward}.
+\subsection{Model}
+
+%
+%We consider the problem of estimating a signal from its multiple occurrences in a noisy measurement.
+If the signal-to-noise ratio (SNR) in the measurement is high, then one can try to detect the signal's occurrences and average.
+However, in a low SNR, detecting the individual occurrences becomes challenging.
+In this paper, we propose a method to estimate the signal, or even multiple signals, in a low SNR environment using autocorrelation analysis.
+We show that under two models specified below, the signal can be estimated to any desired accuracy, if it appears sufficiently many times.
+%We can also consider the extension for multiple signals.
+
+Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data.
+Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+\begin{align}
+y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{align}
+where $\ast$ denotes linear convolution. 
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
+The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
+As will be shown next, in the low signal-to-noise ratio (SNR) environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.
+
+The model can be extended to multiple signals. In this setup,  $x_1,\ldots,x_K\in\RL$ are the sought signals and the data is give by
+\begin{align}
+y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model_heterogeneity}
+\end{align}
+where  $s_k \in \{0, 1\}^{N-L+1}$. 
+From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
+Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals.
+
+The generative model of the support signals play a crucial role in the ability to estimate the signals in low SNR. In this paper, we consider two models: one deterministic and one probabilistic.
+
+\paragraph{Deterministic well separated support.}
+The binary signals obey the following property:
+\begin{align}
+\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{align}
+In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+
+\paragraph{Probabilistic Poisson  model.} In this model, points are chosen in $\{1,\dots,N\}$ according to a Poisson process with parameter $\gamma n$.
+For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+The single signal case fits a Delta distribution, while the heterogeneous case with $K>1$ implies a sum of Delta distribution on $X$.
+
+If $M_i$ denotes the number of hits at location $i$, $1 \le i \le M$, then by definition of the Poisson process $M_i$'s are i.i.d.\
+ and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+
+With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
+%
+\begin{align}
+%
+Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+%
+\end{align}
+
+We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
+For ease of exposition, we do so in the 1-D case.
+Extension to the 2-D case is straightforward.
+We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
 
@@
 
-\subsection{Model}
-
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed micrograph (notice that it is equivalent to think of the data as being one long micrograph or multiple shorter micrographs concatenated into one.)
-The forward model (or ``image'' formation model) is as follows.
-For each target signal $x_k$, an unknown binary signal $s_k \in \{0, 1\}^{N-L+1}$ indicates (with 1's) the starting positions of all occurrences of $x_k$ in $y$, so that, with additive white Gaussian noise:
-\begin{align}
-y & = \sum_{k=1}^K x_k \ast s_k + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
-\label{eq:model}
-\end{align}
-where $\ast$ denotes linear convolution. 
-We consider two models for the generative process of the sparse signal:
-
-\paragraph{The well separated support model.}
-The binary signals obey the following property:
-\begin{align}
-\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
-\label{eq:spacing}
-\end{align}
-In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-
-\paragraph{Poisson process model.} In this model, points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$.
-For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
-
-If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poission process $M_i$'s are i.i.d.\
- and $M_i \sim \Poisson(\gamma)$.
-Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
-
-With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
-%
-\begin{align}
-%
-Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
-%
-\end{align}
-
-From $y$, we aim to recover $x_1, \ldots x_K$, and possibly also the number of occurrences of each.
-In contrast, particle picking is the task of estimating the binary signal $s = s_1 + \cdots + s_K$, while clustering is the task of separating $s$ into its components $s_1, \ldots, s_K$.
-Neither of the latter can be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
-
-%We denote the set of these nonzero values by 
-% $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
-%By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.
-%Neither the $M_i$'s nor $M$ are assumed to be known.
-
-Considering~\eqref{eq:model}, one can think of this inverse problem as a mixture of blind deconvolution problems between binary signals and the target signals.
-%Related literature is briefly surveyed in Appendix~\ref{sec:related_literature}.
-
-We derive algebraic relations between the autocorrelation functions of the micrographs and the autocorrelation functions of the target signals.
-For ease of exposition, we do so in the 1-D case.
-Extension to the 2-D case is straightforward.
-We also give additional technical details regarding the two experiments presented in Section~\ref{sec:results}.
-
 \subsection{Related work}
@@
 The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our model in the  case of a single signal ($K = 1$).
+In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$).
 The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
@@
 
-In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
+In special cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
 The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
 However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
-
-Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
-In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
+Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
+Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
+However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
+
+\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
 
@@
 
-\TODO{The following was copied from the appendix of the old draft}
-
+The main motivation for this paper arises from single particle reconstruction using cryo-electron microscopy (cryo-EM).
+In a cryo-EM experiment, multiple samples of a molecule are frozen in a thin layer of ice.
+The microscope is then generates a tomographic image of the ice layer (with the molecules) called micrograph.
+The goal is to reconstruct the 3-D structure of the molecule from the several micrographs.
+Importantly, the electron dosage transmitted by the microscope must kept low to avoid destruction of the molecules' structure. This, in turn, induces high noise level on the micrograph.
+
+The standard algorithmic pipeline in cryo-EM begins by detecting the projections of the samples in the micrograph.
+This procedure is called \emph{particle picking}.
+Then, the 3-D structure of the molecule is constructed from the projections, usually using different variations of expectation-maximization (EM).
 Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-However, most of these procedures are prone to \emph{model bias}.
+
+If the molecule to be reconstructed is small, then the SNR might be very low. 
+As been recognized by cryo-EM scientists, particle picking is impossible in low SNR and thus for small particles. 
+This led to the belief in the cryo-EM community is reconstruction of small molecules is impossible.
+We claim that this argument is wrong.
+While this paper focused on a mathematical toy model, Section TKTK discusses the application to cryo-EM.
+A companion paper focused on this application and provides all the details~\cite{bendory2018toward}.
+
+In addition, most of the particle picking procedures are prone to \emph{model bias}.
 For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
@@
 \begin{align*}
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell]
 \end{align*}
-for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
+for $\ell = 0, \ldots, L-1$, where $\ell$ denotes the Kronecker delta function.
 The last part captures the autocorrelation of the noise.
@@
 \begin{align}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\ell[\ell_1,0]+\ell[0,\ell_2]+\ell[\ell_1,\ell_2]\big),
 \label{eq:data_ac_k1}
@@
 \lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
-\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
+\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\ell[\ell],  \label{eq:data_ac}\\
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\ell[\ell_1,0]+\ell[0,\ell_2]+\ell[\ell_1,\ell_2]), \nonumber
 \end{align}
@@
 \begin{proposition} \label{prop:poisson_model}
-Under the Poisson process model, the first autocorrelation  is $\gamma \LL_1$, the second moment vector is $(\gamma \LL_1)^2 + \gamma \LL_2(\Delta)$, and the third moment matrix is $(\gamma \LL_1)^3 + \gamma \LL_1  \cdot ( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)) + \gamma \LL_3(\Delta_1,\Delta_2) $.
+Under the Poisson process model, the first autocorrelation  is $\gamma a_y^1$, the second moment vector is $(\gamma a_y^1)^2 + \gamma a_y^2[\ell]$, and the third moment matrix is $(\gamma a_y^1)^3 + \gamma a_y^1  \cdot ( \gamma a_y^2[\ell_1] + \gamma a_y^2[\ell_2] + \gamma a_y^2[\ell_2-\ell_1]) + \gamma a_y^3(\ell_1,\ell_2) $.
 In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''.
@@
 Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \delta>0$.
-Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\delta}$.
+More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \ell>0$.
+Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\ell}$.
 
@@
 %
-\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\delta}.
+\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\ell}.
 %
@@
 \end{align*}
-Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$. \TODO{We may want to cite MRA literature here.}
-
+Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). 
 In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
@@
 
-\TODO{Should we discuss CTF? Where, and to what extent?}
-
 \TODO{Where and how do we cite Kam? Fred?}
-
-\paragraph{Open theoretical questions.}
 
@@
 %
-\LL_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta],
+\LL_2(\ell) = \sum_{i=0}^{L-1} \M_2[i,i+\ell],
 %
@@
 %
-\LL_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2].
-%
-\end{align}
-
-Note that in the strongly-separated model, the first three observed moments are, respectively, $\LL_1$, $\LL_2(\Delta)$, and $\LL_3(\Delta_1,\Delta_2)$.
-
-%
-
-In this notation, we will show that the first moment of the data is $\gamma \LL_1$, the second moment vector is $(\gamma \LL_1)^2 + \gamma \LL_2(\Delta)$, and the third moment matrix is $(\gamma \LL_1)^3 + \gamma \LL_1  \cdot ( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)) + \gamma \LL_3(\Delta_1,\Delta_2) $.
-In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''.
-So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.
-
-%
-
-\section{The first moment of $Y$}
+\LL_3(\ell_1,\ell_2) = \sum_{i=0}^{L-1} \M_3[i,i+\ell_1,i+\ell_2].
+%
+\end{align}
+
+%
+%Note that in the strongly-separated model, the first three observed moments are, respectively, $\LL_1$, $\LL_2(\ell)$, and $\LL_3(\ell_1,\ell_2)$.
+
+%
+
+In this notation, we will show that the first moment of the data is $\gamma \LL_1$, the second moment vector is $(\gamma \LL_1)^2 + \gamma \LL_2(\ell)$, and the third moment matrix is $(\gamma \LL_1)^3 + \gamma \LL_1  \cdot ( \gamma\LL_2(\ell_1) + \gamma\LL_2(\ell_2) + \gamma\LL_2(\ell_2-\ell_1)) + \gamma \LL_3(\ell_1,\ell_2) $.
+In particular, from the first three moments of the Poisson process model, once can recover the first three moments from the well-separated model, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''.
+So if recovery is possible for the well-separated model, it is also possible for the Poisson process model.
+
+%
+
+\paragraph{The first moment of $Y$.}
 
@@
 
-\section{The second moment of $Y$}
-
-Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+\paragraph{The second moment of $Y$}
+
+Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
 %
@@
 
-We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \ell$, and one where $j_2 = j_1 + \ell$ or equivalently $i_1-j_1 = i_2-j_2$.
 In the first case, all the terms are independent, and so the expectation factors.
@@
 \nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+=& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
 \sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
@@
 & + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\ell]
 \nonumber \\
 & + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \ell] 
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \ell} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \ell] .
 %
@@
 \E Y_{i_1} Y_{i_2} 
-=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
-+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+=& \sum_{j_1 - j_2 \ne \ell} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \ell]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \ell} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \ell]
 \nonumber \\
 =&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
-\nonumber \\
-=&  (\gamma \LL_1)^2 + \gamma \LL_2(\Delta).
-%
-\end{align}
-
-But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \LL_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
-
-%
-
-\section{The third moment of $Y$}
-
-For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
++ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \ell]
+\nonumber \\
+=&  (\gamma \LL_1)^2 + \gamma \LL_2(\ell).
+%
+\end{align}
+
+But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \LL_2(\ell)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+
+%
+
+\paragraph{The third moment of $Y$}
+
+For three distinct $i_1$, $i_2$ and $i_3$, we let $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$. We have:
 %
@@
 	\item \label{case1}
-	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+	$j_2 = j_1 + \ell_1$ and $j_3 = j_2 + \ell_2 - \ell_1$.
 
 	\item \label{case2}
-	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+	$j_2 = j_1 + \ell_1$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
 
 	\item \label{case3}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+	$j_2 \ne j_1 + \ell_1$ and $j_3 = j_1 + \ell_2$.
 
 	\item \label{case4}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 = j_2 + \ell_2 - \ell_1$.
 
 	\item \label{case5}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
 
@@
 &\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
-X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 \nonumber \\
 =& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 }_{\text{(a)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 }_{\text{(b)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 }_{\text{(c)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 }_{\text{(d)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 }_{\text{(e)}}.
@@
 %
-\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\ell_1] \M[j+\ell_2].
 %
@@
 %
-\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\ell_1] \M_1[j+\ell_2].
 %
@@
 %
-\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\ell_1] \M_1[j + \ell_2]
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_1] \M_1[j+\ell_2].
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_2] \M_1[j+\ell_1].
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\ell_1,j+\ell_2] \M_1[j].
 %
@@
 %
-\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+\gamma \sum_{j=0}^{L-1} \M_3[j,j+\ell_1,j+\ell_2].
 %
@@
 %
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
 \sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
-\nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{M_{\ell_2}}
 \Bigg\{
 \sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
-\nonumber \\
-&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]
+\nonumber \\
+&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \ell_1] 
 X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
@@
 %
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-\nonumber \\
-&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
+\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
+\nonumber \\
+&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\ell_1] \M_1[j_3] \Bigg).
 %
@@
 %
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
+\M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
 \label{ffff} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
-\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}  
+\M_2[j_1,j_1+\ell_1] \M_1[j_3].
 \label{gggg}
@@
 %
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
-\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1} 
+\M_1[j_1] \M_1[j_1 + \ell_2] \M_1[j_2]
 \label{hhhh} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
-\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1}  
+\M_2[j_1,j_1+\ell_2] \M_1[j_2]
 \label{iiii}
@@
 & \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+\M_1[j_1] \M_1[j_2 + \ell_1] \M_1[j_2 + \ell_2]
 \label{jjjj}\\
 & + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+\M_2[j_2+\ell_1,j_2+\ell_2] \M_1[j_1].
 \label{kkkk}
@@
 \gamma \LL_1  \cdot 
-( \gamma\LL_2(\Delta_1) + \gamma\LL_2(\Delta_2) + \gamma\LL_2(\Delta_2-\Delta_1)).
+( \gamma\LL_2(\ell_1) + \gamma\LL_2(\ell_2) + \gamma\LL_2(\ell_2-\ell_1)).
 %
@@
 %
-\gamma \LL_3(\Delta_1,\Delta_2)
+\gamma \LL_3(\ell_1,\ell_2)
 %
@@
 %
-
-\section{Signal plus noise}
+%
+%\paragraph{Signal plus noise.}
 

### 2018-08-13 2D_PR5/RRR_with_err.m

@@ -41,7 +41,7 @@ for k = 1:max_iter
     err2(k) = norm(rot90(X1(1:L,1:L),2) - X_true,'fro')/norm(X_true(:));
     err(k) = min(err1(k),err2(k));
  %   if and(err(k) < min(err(1:k-1)),k > 1) 
-        X_out = X1(1:L,1:L); 
+ %       X_out = X1(1:L,1:L); 
  %   end
     X2 = real(ifft2(P2(fft2(2*X1 - X)))); % Fourier magnitude projection
     discrepancy = X2 - X1;
@@ -57,13 +57,22 @@ for k = 1:max_iter
 end
 
 X = P1(X);
-X(X<-1) = 1;
+X(X<-1) = -1;
 X(X>1) = 1;
 err1(k) = norm(X(1:L,1:L) - X_true,'fro')/norm(X_true(:));
 err2(k) = norm(rot90(X(1:L,1:L),2) - X_true,'fro')/norm(X_true(:));
 err(k) = min(err1(k),err2(k));
+
+X_out = zeros(W);
+
+if err(k) == err1(k)
+X_out = X;
+else
+X_out(1:L,1:L) = rot90(X(1:L,1:L),2);
+end
+
 %if err(k) < min(err(1:k-1)) 
-       X_out = X(1:L,1:L); 
+%       X_out = X(1:L,1:L); 
 %end
 
 %if k == max_iter

### 2018-08-13 2D_PR5/example.m

@@ -2,100 +2,123 @@ clear;
 close all;
 clc;
 
-seed_rng = rng('shuffle');
-
+seed_rng = rng(57489754);
 if isempty(gcp('nocreate'))
     parpool(72,'IdleTimeout', 240);
 end
 
 %% Defining the problem
 
+L = 50;
+W = 2*L-1;
+sigma = 1;
+m_want = 1000; % Desired number of occurrences of the signal X in each micrograph
+micrograph_batch = 500;% # micrographs in each iterations
+epocs = 1000/5;
+N = 4096; % Each micrograph is square of size NxN
+th = 0; % threshold for the RRR
+max_iter = 2000; % max iterations for the RRR
+
 % Load a grayscale image of size LxL, removing the mean and scale between -1 and 1.
 X = double(rgb2gray(imread('Einstein5_small.jpg')));
 X = X - mean(X(:));
 X = X/max(abs(X(:)));
-
-L = 50;
-W = 2*L-1;
 X = imresize(X, [L, L]);
 X_zp = [X zeros(L, W-L) ; zeros(W-L, W)];
 PSX = abs(fft2(X_zp)).^2;
-
-% Pick a noise level
-sigma = 3;
-% Desired number of occurrences of the signal X in each micrograph
-m_want = 1000;
-%
-micrograph_batch = 100; %512;
-% Number of epocs
-epocs = 1000;
-% Number of micrographs to generate
-n_micrographs = epocs*micrograph_batch;
-% Each micrograph is square of size NxN
-N = 4096;
-
 err_PS = zeros(epocs,1);
-err_rrr = zeros(epocs,1);
-
-%% parameters for the RRR
-
-th = 0.01;
-%X_N = double(rgb2gray(imread('newton.jpg')));
-%X_N = X_N/max(X_N(:));
-%X_N = imresize(X_N, [L, L]);
-%X_N = X_N - mean(X_N(:));
-X_init = zeros(W);
-%X_init(1:L,1:L) = X_N;
+err_rrr = zeros(epocs,max_iter);
+n_micrographs = epocs*micrograph_batch; % Number of micrographs to generate
 r = randn(L);
 r = r - mean(r(:));
+X_init = zeros(W);
 X_init(1:L,1:L) = r;
 
 %% Generate the micrographs and collect their moments
 
-%m_eff = zeros(n_micrographs, 1);
[…]

### 2018-08-15 TEX/draft_biology.tex
Revised Appendix C. Several open questions remained

@@
 \newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
+\newcommand{\be}
+{\begin{equation}}
+\newcommand{\ee}
+{\end{equation}}
 
@@
 Thus, we conclude
-\[ a^2_\II[\Bell] \to \gamma\langle a^2_{I_{\omega}}[\Bell]\rangle_{\omega} + \sigma^2\delta[\Bell],\]
+\begin{equation} \label{eq:second_order_ac_volume_data}
+a^2_\II[\Bell] \to \gamma\langle a^2_{I_{\omega}}[\Bell]\rangle_{\omega} + \sigma^2\delta[\Bell],
+\end{equation}
 where the  bias term $b_2[\Bell] = \sigma^2\delta[\Bell]$   depends only on the variance of the noise $\sigma^2$.
@@
 Thus, we conclude that
-\[ a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
+\begin{equation} \label{eq:third_order_ac_micro_volume}
+a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
 a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
 \gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
-\delta[\Bell_1] + \delta[\Bell_2]\Big),\]
+\delta[\Bell_1] + \delta[\Bell_2]\Big),
+\end{equation}
 where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
@@
 For $\Bell \in [-(P-1), P-1]^2$, let us define 
-\[\begin{aligned} 
-\mathfrak{a}^2[k, q] & =
-\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
+\begin{equation} \label{eq:PSWF_expansion}
+\mathfrak{a}^2[k, q]  =
+\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{equation}
 where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
@@
 Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
-\[\begin{aligned} 
+\begin{align} \label{eq:second_order_ac_pswf}
 \mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k,q}[\mb i] +
-\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\\ 
-&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
+\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\nonumber\\ 
+&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], 
+\end{align}
 where in the last equality we used that $a_{0,q}[\mb i]$ is real since both $\II$ and $\psi_{0,q}$ are real valued (more generally, $a_{-k,q}=\overline{a_{k,q}}$).
@@
 Averaging over all rotations of $\II$ and its reflection, we obtain
-\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right),\\
-&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}.\end{aligned}\]
+\begin{align} \label{eq:third_order_ac_pswf}
+\mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
+&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. 
+\end{align}
 Thus, similarly to the second-order autocorrelation, averaging over all in-plane rotations reveals that the 4-D third-order autocorrelation truly only carries information along three dimensions.
@@
 
-\TODO{===}
-
-\be\label{eq:PSWF_defn_eq}
-\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
-\ee
-
-\TODO{===}
-
-We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
-\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
-where $k=||\kk||_2$, $c$ is the assumed bandlimit, $Y_{\ell}^m$ is the complex spherical harmonics
-\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
-
-where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase, and $j_{\ell,s}$ are normalized spherical Bessel functions given by
+Until now, we have established  simple relations between the autocorrelations of the micrographs and the autocorrelations of the volume.
+Now, we complete the picture by deriving the connection with the volume itself.
+
+We start by some preliminary computations. Let us  expand the Fourier transform of the volume as
+\begin{equation} \label{eq:volume_expansion_app} 
+\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
+\end{equation}
+%\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
+%where $k=||\kk||_2$, 
+\TODO{How do we choose $S(\ell)$?}where $c$ is the bandlimit, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
 \[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
-where $j_{\ell}$ is the spherical Bessel function of order $\ell$, $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$, and the radius satisfies $k\in[0,1/2]$ in Fourier space since $1/2$ is the Nyquist frequency [ISBI].
-
-Then
-\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}a_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta},\]
-whenever $k\leq 1$. Express this in 2D PSWFs so \TODO{Eitan: I stopped here}
-\[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
-where in papers the 2D PSWFs are defined as
-\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
-but in Boris' code the expansion is actually performed with respect to
-\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
-where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below.
-
-We then get
-\[\begin{aligned} b_{N,n} &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-iN\theta}k\, dk\, d\theta,\\
-&= \sum_{\ell,m,m',s}a_{\ell,m,s}[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)]D_{m',m}^{\ell}(\omega)\left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{i(m'-N)\theta}\, d\theta\right),\\
-&= \sum_{\ell\geq |N|}\sum_{m,s}a_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
+$j_{\ell}$ is the spherical Bessel function of order $\ell$ and  $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$. We use 
+the complex spherical harmonics $Y_{\ell}^m$ defined by  
+\[ Y_{\ell,m}(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
+where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
+Sampling at the Nyquist-rate dictates $k\in[0,1/2]$~\cite{levin20173d}. \TODO{Didn't we say that $k\leq 1$?} With this notation, 
+the Fourier transform of a  projection taken from the viewing direction $\omega\in SO(3)$ can be written as 
+\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta}.\]
+%whenever $k\leq 1$. 
+%where $D_{m',m}^{\ell}$ is the Wigner D-matrix.
+
+Recall that the PSWFs are the solution of the integral equation \TODO{To mention the range of $\mb r$?} 
+\begin{equation}
+\label{eq:PSWF_defn_eq}
+\alpha_{N,n}\psi_{N,n}(\mb k) = \int_{\mb r} \psi_{N,n}(\mb r)e^{\iota c(\mb r\cdot\mb k)}d\mb r,
+\end{equation}
+%\begin{equation}
+%\label{eq:PSWF_defn_eq}
+%\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
+%\end{equation}
+and are given explicitly by \TODO{Do we use this normalization?}
+\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{\iota N\theta},\]
+where $R_{N,n}(k)$ is a solution to another integral equation~\cite{landa2017steerable}. 
+Let us assume that $I_{\omega}$ has bandlimit $c$ and is concentrated in the unit ball in real space. 
+Using the 2-D PSWFs, we can express each projection as 
+%Express this in 2D PSWFs so %\TODO{Eitan: I stopped here}
+\[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}(\omega)\psi_{N,n}(k,\theta),\]
+%where in papers the 2D PSWFs are defined as
+%\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
+%%but in Boris' code the expansion is actually performed with respect to
+%\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
+%where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below. 
+%
+%We then get
 where
-\[ \beta_{\ell,s;N,n} = \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|,\\ 0, & \ell<|N|\end{array}\right.,\]
+\[\begin{aligned} b_{N,n}(\omega) &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
+&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
+&= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
+where the coefficients
+\begin{equation} \label{eq:beta}
+\beta_{\ell,s;N,n} := \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|\\ 0, & \ell<|N|\end{array}\right.,
+\end{equation}
 can be precomputed.
-
-Then, back in real space,
-\[\begin{aligned} I_{\omega}(r,\varphi) &= \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}\psi_{N,n}(r,\varphi),\\
-&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}a_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi).
+Since the PSWFs are eigenfunctions of the truncated Fourier operator~\eqref{eq:PSWF_defn_eq}, we can now express the projection in real space as
+\begin{align} \label{eq:proj_expansion}
+I_{\omega}(r,\varphi) &= \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}(\omega)\psi_{N,n}(r,\varphi)\nonumber \\
+&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}\tamir_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi)
+\end{align}
+\TODO{How do we choose $n_{max}$?}where $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$.
+
+\paragraph{Third-order autocorrelation.}
+In~\eqref{eq:third_order_ac_micro_volume} and~\eqref{eq:third_order_ac_pswf} we have shown how the third-order autocorrelations of the micrographs and the volume are related, and how we can present them in PSWFs.
+Now, we relate these expressions to the expansion coefficients of the volume itself.
+
+The third-order autocorrelation of the volume can be expressed in terms of~\eqref{eq:proj_expansion}:\TODO{What about the $\hat\alpha$ coefficients?}
+\begin{align} \label{eq:third_order_ac_volume}
+\langle
+a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\mb i]I_{\omega}[\mb i+\Bell_1]\overline{I_{\omega}([\mb i+\Bell_2])}\rangle_{\omega},\\
+&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
+where the approximation is due to discretization. 
+Now,
+\[\begin{aligned} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
+&\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
+where the latter coefficients are given explicitly in~\eqref{eq:beta}. Using standard properties of D-Wigner functions, we obtain  
+\[ \left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
+\]
+where  $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right)$ are called Wigner 3-j symbols. 
+Notably, these terms are zero unless $m_1+m_2+m_3=0$ and $|\ell_1-\ell_2|\leq \ell_3\leq \ell_1+\ell_2$. Thus,  we conclude that 
+\begin{align} \label{eq:b_average}
+\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \delta_{N_3,N_1+N_2}\sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
+&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+&\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}. \nonumber
+\end{align}
+Combining~\eqref{eq:b_average} with~\eqref{eq:third_order_ac_volume} provides the explicit relation between the third-order autocorrelation and the volume.
+
+Recall that we obtain the autocorrelations of the volume in PSWFs coefficients; see~\eqref{eq:third_order_ac_pswf}. Hence, to conclude the derivation we expand
+\[ \langle a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega}= \sum_{k,q_1,q_2}\mathfrak{a}^3[k,q_1,q_2]\psi_{k,q_1}[\Bell_1]\overline{\psi_{k,q_2}[\Bell_2]},\]
+where we only include the block-diagonal terms in the expansion; the rest are equal to zero. Let
+\begin{align*}
+\Psi_{\ell,N,s}[\Bell] &:= \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}[\Bell],\\ 
+\rho_{\ell,N,s}^{(k,q)}&:=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
+\end{align*}
+Then, 
+the final formula reads
+\[\begin{aligned} \mathfrak{a}^3[k,q_1,q_2] &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
+&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
 \end{aligned}\]
-where $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$.
-In this notation, we assumed $I_{\omega}$ has bandlimit $c$ and is concentrated in the unit ball in real space.
-We then consider the product
-\[\begin{aligned} m_3(\Bell,\Bell_2) &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\Bell]I_{\omega}[\mb i+\Bell]\overline{I_{\omega}([\mb i+\Bell]_2)}\rangle_{\omega},\\
-&= \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\Bell]\psi_{N_2,n_2}[\mb i+\Bell]\overline{\psi_{N_3,n_3}([\mb i+\Bell]_2)}.\end{aligned}\]
-Now,
-\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_3,s_3}}\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega}\\
-&\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned}\]
-and [Tamir's note on Kam's bispectrum]
-\[ \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\rangle_{\omega} = (-1)^{N_3+m_3}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
-\]
-and since $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right) = 0$ unless $m_1+m_2+m_3=0$ and $|\ell_1-\ell_2|\leq \ell_3\leq \ell_1+\ell_2$, we conclude that 
-\[\begin{aligned} \langle b_{N_1,n_1}b_{N_2,n_2}\overline{b_{N_3,n_3}}\rangle_{\omega} &= \delta_{N_3,N_1+N_2}\sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m2,s_3}}\\
-&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}.\end{aligned}\]
-
-Finally, we expand
-\[ m_3(\Bell,\Bell_2) = \sum_{k,q_1,q_2}\mathfrak{m}_3(k,q_1,q_2)\psi_{k,q_1}(\Bell)\overline{\psi_{k,q_2}(\Bell_2)},\]
-where we only include the block-diagonal terms in the expansion. Defining
-\[ \Psi_{\ell,N,s}[\Bell] = \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}[\Bell],\]
-the final formula reads
-\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}\\
-&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]}, \end{aligned}\]
-where
-\[ \rho_{\ell,N,s}^{(k,q)}=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.\]
-In practice, the last line of the above expression for $\mathfrak{m}_3(k,q_1,q_2)$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
-
-\subsection{The power spectrum}
-The power spectrum is easier to derive directly in Fourier space, to
-avoid integration of shifted prolates against centered ones. The
-average power spectrum in Fourier space can be derived from Kam's
-original formula [Kam, 1980; Eq. 10] by setting $\mb k_1 = \mb k_2$ to
+In practice, the last two lines of the above expression for $\mathfrak{a}^3[k,q_1,q_2]$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
+
+%\subsection{The power spectrum}
+\paragraph{Second-order autocorrelation.}
+The second-order autocorrelation is easier to derive directly in Fourier space, to avoid integration of shifted PSWFs against centered ones. 
+The relation between the second-order autocorrelation of the micrographs and the volume is given in~\eqref{eq:second_order_ac_volume_data} and~\eqref{eq:second_order_ac_pswf}. 
+The connection with the expansion coefficients of the volume can be derived in  Fourier space directly from Kam's
+original formula~\cite{kam1980reconstruction} by setting $\mb k_1 = \mb k_2$ to
 obtain
-\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
+\[ \left\langle a^2_{\hat{I}_{\omega}}(k,\theta)\right\rangle_{\omega} =
 \frac{1}{4\pi}\sum_{\ell,
-	m}\left|\sum_sa_{\ell,m,s}j_{\ell,s}(k)\right|^2 =
-\frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),\]
+	m}\left|\sum_s\tamir_{\ell,m,s}j_{\ell,s}(k)\right|^2 =
+\frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}\tamir_{\ell,m,s_1}\overline{\tamir_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),\]
 where we used the fact that the normalized spherical Bessel functions
-$j_{\ell,s}$ are real. To expand the above in 2D PSWFs, we write
-\[ \langle |\widehat I_{\omega}(k,\theta)|^2\rangle_{\omega} =
-\sum_{q}\mathfrak{m}_2(q)\psi_{0,q}(k),\]
+$j_{\ell,s}$ are real.
+
+As before, we want to derive the relation with respect to the PSWF coefficients of the autocorrelation. Hence,  we expand the above in 2-D PSWFs by
+\[\left\langle a^2_{\hat{I}_{\omega}}(k,\theta)\right\rangle_{\omega} =
+\sum_{q}\mathfrak{a}_2(q)\psi_{0,q}(k),\]
 and conclude that
-\[ \mathfrak{m}_2(q) =
-\frac{\sqrt{2\pi}}{4\pi}\sum_{\substack{\ell,m\\s_1,s_2}}a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}}
+\[ \mathfrak{a}^2[q] =
+\frac{1}{\sqrt{8\pi}}\sum_{\substack{\ell,m\\s_1,s_2}}\tamir_{\ell,m,s_1}\overline{\tamir_{\ell,m,s_2}}
 \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk.\]
-
-\subsection{The mean}
-
-Since the Fourier transformed volume is given by
-\[ \widehat V(k,\theta,\varphi) =
-\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell,m}(\theta,\varphi)j_{\ell,s}(k),\]
-since $j_{\ell,s}(0)=0$ unless $\ell=0$, and since
-$Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude that
-\[ m_1[\phi] = \widehat V(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0).\]
-
+The integral on $k$ is precomputed.
+
+\paragraph{The mean.}
+
+%Since the Fourier transformed volume is given by
+%\[ \widehat V(k,\theta,\varphi) =
+%\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell,m}(\theta,\varphi)j_{\ell,s}(k),\]
+Since $j_{\ell,s}(0) = 0$ unless $\ell=0$, and since
+$Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude from~\eqref{eq:volume_expansion_app} that
+\[ \langle
+a^1_{I_{\omega}}\rangle_{\omega} = \widehat \phi(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_s\tamir_{0,0,s}j_{0,s}(0).\]
+
+\TODO{=========== Tamir: Stopped here ===============}
+
+\TODO{=========== NOT SURE WHAT IS THAT ===============}
 \begin{align*}

### 2018-08-15 TEX/inverse_problem_draft.tex
Revised Appendix C. Several open questions remained

@@
 
+\subsection{Main motivation: The cryo-EM problem}
+
+The main motivation for this paper arises from single particle reconstruction using cryo-electron microscopy (cryo-EM).
+In a cryo-EM experiment, multiple samples of a molecule are frozen in a thin layer of ice.
+The microscope is then generates a tomographic image of the ice layer (with the molecules) called micrograph.
+The goal is to reconstruct the 3-D structure of the molecule from the several micrographs.
+Importantly, the electron dosage transmitted by the microscope must kept low to avoid destruction of the molecules' structure. This, in turn, induces high noise level on the micrograph.
+
+The standard algorithmic pipeline in cryo-EM begins by detecting the projections of the samples in the micrograph.
+This procedure is called \emph{particle picking}.
+Then, the 3-D structure of the molecule is constructed from the projections, usually using different variations of expectation-maximization (EM).
+Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
+
+If the molecule to be reconstructed is small, then the SNR might be very low. 
+As been recognized by cryo-EM scientists, particle picking is impossible in low SNR and thus for small particles. 
+This led to the belief in the cryo-EM community is reconstruction of small molecules is impossible.
+We claim that this argument is wrong.
+While this paper focused on a mathematical toy model, Section TKTK discusses the application to cryo-EM.
+A companion paper focused on this application and provides all the details~\cite{bendory2018toward}.
+
+In addition, most of the particle picking procedures are prone to \emph{model bias}.
+For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
+Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
+Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
+Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
+
 \subsection{Related work}
 
-For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+For $K=1$, our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
 %
@@
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-
-\subsection{Main motivation: The cryo-EM problem}
-
-The main motivation for this paper arises from single particle reconstruction using cryo-electron microscopy (cryo-EM).
-In a cryo-EM experiment, multiple samples of a molecule are frozen in a thin layer of ice.
-The microscope is then generates a tomographic image of the ice layer (with the molecules) called micrograph.
-The goal is to reconstruct the 3-D structure of the molecule from the several micrographs.
-Importantly, the electron dosage transmitted by the microscope must kept low to avoid destruction of the molecules' structure. This, in turn, induces high noise level on the micrograph.
-
-The standard algorithmic pipeline in cryo-EM begins by detecting the projections of the samples in the micrograph.
-This procedure is called \emph{particle picking}.
-Then, the 3-D structure of the molecule is constructed from the projections, usually using different variations of expectation-maximization (EM).
-Many automatic and semi-automatic methods for particle picking have been proposed, based on edge detection, template matching and deep learning; see for instance~\cite{harauz1989automatic,ogura2004automatic,zhu2016deep,frank1983automatic,scheres2015semi,heimowitz2018apple}.
-
-If the molecule to be reconstructed is small, then the SNR might be very low. 
-As been recognized by cryo-EM scientists, particle picking is impossible in low SNR and thus for small particles. 
-This led to the belief in the cryo-EM community is reconstruction of small molecules is impossible.
-We claim that this argument is wrong.
-While this paper focused on a mathematical toy model, Section TKTK discusses the application to cryo-EM.
-A companion paper focused on this application and provides all the details~\cite{bendory2018toward}.
-
-In addition, most of the particle picking procedures are prone to \emph{model bias}.
-For instance, in the popular framework of RELION~\cite{scheres2015semi}, the user manually marks hundreds of spots on the micrograph, believed to contain projections.
-Therefore, the algorithm's performance depends on the prior assumptions of the users about the particle's structure; the same holds true for deep learning based approaches which require constructing labeled sets of data.
-Other methods use disks or differences of Gaussians as templates~\cite{langlois2014automated,voss2009dog}.
-Nowadays, it also still popular to pick particles manually. This method, while it exploits the researcher's experience, is both tedious and subject to model bias.
 
@@
 
-\subsection{The single signal case}
+\subsection{The multiple signals case}
 
@@
 
-Should we devote a whole section for EM or merge it with the next one?
+Suppose we extract a set of windows $y_1,\ldots,y_q$ windows of $y$. If the signal's occurrences are sufficiently separated, then we can model each window as 
+\begin{equation} \label{eq:EM}
+y_i = PR_{r_i}Zx + \varepsilon,
+\end{equation}
+where $Zx = (0,\ldots 0,x[0],\ldots,x[L-1])\in\mathbb{R}^{2L}$, $R_r$ shifts a signal cyclically by $r$ entries  and $P$ restricts a signal to its first $L$ entries.
+We assume the distribution of $R_r$ to be of the form $\rho = (\alpha,\frac{1-\alpha}{2L-1},\ldots,\frac{1-\alpha}{2L-1})\in\Delta^{2L}$.
+Namely, the probability to see no signal (only noise) is $\alpha$, whereas there is equal probability to observe each one of the possible signal fractions.
+
+If each window was drawn independently from this model, then it is straight-forward to derive the EM formulation, similarly to~\cite{bendory2017bispectrum,abbe2017multireference}. In particular, ....
+
+Indeed, the formulation~\eqref{eq:EM} does not follow the EM recipe since, in order to keep the separation constraint, the random shifts $R_r$ are correlated across windows.
+Nonetheless, numerically it seems that the EM method works well; see Section TKTK for numerical demonstrations.
 
@@
 \end{figure}
-
-\TODO{The following was copying from the Methods section}
 

### 2018-08-24 pnas/Towards.tex
initial files for pnas

--- 2018-08-15 TEX/draft_biology.tex
@@
-\documentclass[english,11pt]{article}
-
-\pdfoutput=1
-
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{verbatim}
-\usepackage{float}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-%\usepackage{multirow}
-\usepackage{color}
-\usepackage{url}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{mathtools} 
-\usepackage[margin=1.2in]{geometry}
-\usepackage{showlabels}
-
-\newcommand{\LL}{\mathcal{L}}
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\I}{\mathcal{I}}
-\newcommand{\ep}{\varepsilon}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\GCD}{\mathbf{GCD}}
-\newcommand{\XX}{\mathcal{X}}
-\newcommand{\SUM}{\text{sum}}
-\newcommand{\1}{\mathbf{1}}
-\newcommand{\rr}{\textbf{r}}
-\newcommand{\ii}{\textbf{i}}
-\newcommand{\jj}{\textbf{j}}
-
-\newcommand{\II}{\mathcal{I}}
-\newcommand{\kk}{\textbf{k}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\mb}{\mathbf}
-\newcommand{\mk}{\mathfrak}
-\newcommand{\mc}{\mathcal}
-
-\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
-
-\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
-
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\numberwithin{equation}{section}
-%\numberwithin{figure}{section}
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}[section]
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{\protect\definitionname}
-\theoremstyle{remark}
-\newtheorem{claim}[thm]{\protect\claimname}
-\theoremstyle{plain}
-\newtheorem{lem}[thm]{\protect\lemmaname}
-
-\newtheorem*{lem*}{Lemma}
-
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{\protect\remarkname}
-\theoremstyle{plain}
-\newtheorem{corollary}[thm]{\protect\corollaryname}
-\theoremstyle{plain}
-\newtheorem{proposition}[thm]{\protect\propositionname}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-%\usepackage{slashbox}
-
-\usepackage{babel}
-\providecommand{\claimname}{Claim}
-\providecommand{\definitionname}{Definition}
-\providecommand{\lemmaname}{Lemma}
-\providecommand{\remarkname}{Remark}
-\providecommand{\theoremname}{Theorem}
-\providecommand{\corollaryname}{Corollary}
-\providecommand{\propositionname}{Proposition}
-
-\newcommand{\reals}{\mathbb{R}}
-\newcommand{\RL}{\mathbb{R}^L}
-\newcommand{\tamir}{x}
-\newcommand{\CL}{\mathbb{C}^L}
-\newcommand{\RN}{\mathbb{R}^N}
-\newcommand{\RNN}{\mathbb{R}^{N\times N}}
-\newcommand{\RPP}{\mathbb{R}^{P\times P}}
-\newcommand{\CNN}{\mathbb{C}^{N\times N}}
-\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\hx}{\hat{x}} 
-\newcommand{\one}{\mathbf{1}} 
-\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
-\newcommand{\be}
-{\begin{equation}}
-\newcommand{\ee}
-{\end{equation}}
+\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
+
+\templatetype{pnasresearcharticle} % Choose template 
+% {pnasresearcharticle} = Template for a two-column research article
+% {pnasmathematics} %= Template for a one-column mathematics article
+% {pnasinvited} %= Template for a PNAS invited submission
+
+\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}
+
+% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[a]{Tamir Bendory}
+\author[b]{Nicolas Boumal} 
+\author[c]{William Leeb}
+\author[a]{Eitan Levin}
+\author[a,b]{Amit Singer}
+
+\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
+\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
+\affil[c]{School of Mathematics, University of
+	Minnesota, Minneapolis, MN, USA }
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Bendory}
+
+% Please add here a significance statement to explain the relevance of your work
+\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
+The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
+The Significance Statement appears in the paper itself and is required for all research papers.}
+
+% Please include corresponding author, author contribution and author declaration information
+\authorcontributions{Please provide details of author contributions here.}
+\authordeclaration{Please declare any conflict of interest here.}
+%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
+\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}
+
+% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
+\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
+
+\begin{abstract}
+Please provide an abstract of no more than 250 words in a single paragraph.
+Abstracts should explain to the general reader the major contributions of the article.
+References in the abstract must be cited in full within the abstract itself and cited in the text.
+\end{abstract}
+
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
 
@@
 
-\title{Toward single particle reconstruction without particle picking: Breaking the detection limit}
-
-\author{Tamir Bendory, Nicolas Boumal, William Leeb, Eitan Levin and Amit Singer}
 \maketitle
-
-\begin{abstract}
-	Here comes the abstract
-\end{abstract}
-
-\section{Introduction}
-
-\TODO{Revise--Cryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules.} 
-%In recent years, structures of many molecules, previously regarded as insurmountable, are now being reconstructed to near-atomic resolution
-%; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152,smith2014beyond}.
-%This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}. 
-% 
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+\dropcap{C}ryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise}
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
@@
 
-%\paragraph{Particle picking.}
 All contemporary methods in the field split the reconstruction procedure into several stages.
@@
 The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%
 Despite this progress, detecting small molecules in the micrographs remains a challenge.
@@
 In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details.
-%As a side note, we mention that expectation-maximization (EM)---a popular framework in SPR---is intractable for this problem; see~\cite{bendory2018estimation} for the details. 
 \TODO{Do we want to stress that we get only low-resolution of the volume?}
@@
 This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates are required, thus significantly reducing concerns about model bias.
+In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
 \TODO{To add reference to our example.}
-
-% while neglecting important aspects as discussed in detail in TKTK.
-
-%In first model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-%The goal is to estimate the planted image.
-The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably.
-This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-We study it in more details in a companion paper~\cite{bendory2018estimation}.
-An extension to multiple planted images is analyzed in~\cite{bendory2018estimation}.
-%
-%In the second model, we consider the 3-D reconstruction problem as it appears in cryo-EM, \TODO{Here we need to elaborate a bit.} This is the main result of this paper.
-\TODO{We probably need to switch the order of this paragraph.}
-
-%A precise mathematical formulation of the model, including an extension where more than one planted images are to be recovered, is provided in Section~\ref{sec:methods}.
-%To be clear, we do not consider here many prominent features of real SPR experiments and do not aim to reconstruct any 3-D structure.
-Instead, we solve a simpler problem that we believe captures key elements of the SPR problem.
-We note that similar models emerge in spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-%In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelation functions of the micrographs to the autocorrelation functions of the volume.
-%For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the projections are well separated and we acquire enough of them.
-Importantly, there is no need to detect the projections.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the volume.
-To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares.
-%We use similar technique for the simpler model of planted image as illustrated in Figure~\ref{fig:Einst_example}.
 
@@
 
-%
-
-\begin{figure}[t]
+\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
+%
+
+\begin{figure*}[h]
 	\centering
@@
 This figure will be positioned with the rest of the figures about Einstein's example}}
-\end{figure}
-
-\section{Results} \label{sec:results}
+\end{figure*}
+
+\section{Proof of concept: A mathematical toy model}
+
+Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data.
+Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+\begin{align}
+y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{align}
+where $\ast$ denotes linear convolution. 
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
+The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
+As will be shown next, in the low signal-to-noise ratio (SNR) environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.
+
+The binary signals obey the following property:
+\begin{align}
+\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{align}
+In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+
+\subsection{Related work}
+
+For $K=1$, our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+%
+\begin{math}
+%
+y = x\ast w + \varepsilon,  
+%
+\end{math} 
+%
+where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
+%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$).
+The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+
+Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
+For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
+If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
+
+Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
+One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
+Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
+Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
+
+In special cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
+The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
+However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
+Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
+Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
+However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
+
+\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
+
+Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+
+\section{Autocorrelation analysis}
+
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\begin{align}
+a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
+Explicitly, the first-, second- and third-order autocorrelations are given by
+\begin{align} 
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+\begin{align*}
+a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+\end{align*}
+%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
+
+For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
+\begin{align}
+\gamma & = \frac{M L}{N}
+\end{align}
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$.
+Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$.
+The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
+\begin{align*}
+\E\{ a_y^1 \} & = \gamma a_x^1.
+\end{align*}
+We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
+\begin{align*}
+\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
+\end{align*}
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+
+The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations.
+Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
+As a result,
+\begin{align*}
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell]
+\end{align*}
+for $\ell = 0, \ldots, L-1$, where $\ell$ denotes the Kronecker delta function.
+The last part captures the autocorrelation of the noise.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
+Along the same lines, one can establish a relation for third-order autocorrelations:
+\begin{align}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\ell[\ell_1,0]+\ell[0,\ell_2]+\ell[\ell_1,\ell_2]\big),
+\label{eq:data_ac_k1}
+\end{align}
+for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
+Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
+
+\section{Theory} \label{sec:theory}
+
+If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
+We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
+%
+%To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
+Suppose too that the oracle provides us with $x$ itself.
+That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
+This is an easier problem than detecting the support of $s$.
+Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
+Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
+
+%\TODO{Here we should give the Will's proposition for the impossibility of detection}
+
+Therefor, we need to consider a different approach.
+In this paper, we consider autocorrelation analysis.
+In what follows, we present several results on properties of autocorrelations.
+For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
+%
+\begin{align} \label{eq-uniqueness}
+%
+z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+%
+\end{align}
+
+In particular, we have proven the following proposition:
+
+\begin{proposition} \label{prop:uniqueness}
+	%
+	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\end{proposition}
+
+Some remarks are in order.
+First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+
+Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
+%%%and therefore the assumption that the first and last entries are nonzero is met.
+In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+
+\begin{comment}
+
+%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+, this uniqueness result holds for signals of any dimension. Third
+
+Furthermore,
+as proven in the following simple proposition.
+%
+\begin{proposition} \label{prop:uniqueness}
+%
+Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
+Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \ell>0$.
+Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\ell}$.
+
+\end{proposition}
+
+\begin{proof}
+%
+By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
+Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
+%
+\begin{equation*}
+%
+a_z^3[k,L-1] = z[0]z[k]z[L-1].
+%
+\end{equation*}
+%
+In addition, 
+%
+\begin{equation*}
+%
+\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\ell}.
+%
+\end{equation*} 
+%
+\end{proof}
+
+A few remarks are in order. 
+First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
+In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
+Second, these results carry through to signals of any dimension.
+Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
+therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
+
+\end{comment}
+
+Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
+Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
+
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
+We will show, however, that $x$ is still identifiable from the observed moments of $y$.
+In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
+
+First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
+%
+\begin{proposition} \label{prop:gamma}
+	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
+	%
+	\begin{equation*}
+	%
+	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
+	%
+	\end{equation*}
+	%
+\end{proposition}
+\begin{proof}
+	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
+\end{proof}
+
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
+
+\begin{proposition} \label{prop:gamma_sigma}
+	%
+	Let $K=1$, and $\sigma > 0$ be fixed.
+Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
+\begin{corollary}
+	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
+	\begin{itemize}
+		\item Either the signal $x$ is generic; or
+		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
+	\end{itemize}
+\end{corollary}
 
@@
 
-%defined as 
-%\begin{equation}
-%\text{RMSE}  := \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
-%\end{equation} 
-%where $x$ and $\hat{x}$ are, respectively, the underlying and estimated image, and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm.  
-%\TODO{We have a movie in the supplementary material.}
-
-%%%% This is about bias, and it's imprecise; let's leave it out?
-%As an initial guess, we picked an image of the physicist Issac Newton.
-If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise.'' However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
-
-%\begin{figure}[h!]
-%	\centering
-%	\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[scale=0.45]{reconstruction1_cropped}
-%		\caption{\small $P = 512$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[scale=0.45]{reconstruction10_cropped}
-%		\caption{\small $P = 512\times 10$}
-%	\end{subfigure}%
-%
-%		\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[scale=0.45]{reconstruction100_cropped}
-%		\caption{ \small $P = 512\times 10^2$ }
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[scale=0.45]{reconstruction1000_cropped}
-%		\caption{\small $P = 512\times 10^3$}
-%	\end{subfigure}%
-%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-%		\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
-%		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
-%	}
-%\end{figure}
-%
-
-\begin{figure}[h!]
+\begin{figure*}[h!]
 	\centering
-\includegraphics[scale=0.8]{Einstien_progress_examples}
+	\includegraphics[scale=0.7]{Einstein_progress_examples}
 	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
@@
 	}
-\end{figure}
+\end{figure*}
 
@@
 	\centering
-\includegraphics[scale=1]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
+	\includegraphics[scale=.68]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
 	%\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
@@
 
-%
-%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
-%\begin{equation}
-%\gamma_i = \frac{M_i L}{N},
-%\end{equation}
-%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
-In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$.
-As can be seen, given enough signals occurrences, we can estimate accurately the signals.
-he estimation quality
-%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
-
-%
-%In the second experiment, three 1-D signals, each of length $L = 21$, appear at random locations in one long 1-D signal, which we call a micrograph by analogy.
-Any two occurrences are separated by at least 20 entries.
-The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion.
-The micrograph is then contaminated with additive white Gaussian noise.
-This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal.
-Neither the number of occurrences nor the noise level $\sigma$ are known to the algorithm.
-%
-%In the Methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals.
-The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.
-%
-%Figure~\ref{fig:1Dheterosignals} shows how the estimates improve as we see a larger and larger fraction of the micrograph (that is, as more and more data becomes available.) As is clear from the picture, despite the high noise level which would make it very challenging to locate the individual signal occurrences, the signals can be estimated accurately given enough data.
-Furthermore, the \TODO{propensity\footnote{Might not be the right word; 'density' is not good because it might refer to the density of the particle for example, whereas here we mean to say the 'fraction of occurrences that come from a particular class'}} of each signal can also be estimated.
-
-%In order to estimate the signals, we computed the first three autocorrelation functions of the data and then estimated the signals and their corresponding $\gamma_i$ using a nonconvex least-squares. 
-%As can be seen, given enough signal occurrences, we can estimate accurately the signals. 
-%The estimation quality of the triangle signal is poorer than the other two signals, a phenomenon that is explained using Proposition~\ref{prop:uniqueness}.
-
-%We do not assume the knowledge of the noise level. 
-%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[scale=0.45]{progressive_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1Dhomosignals}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
-%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
-%	\label{fig:1DhomoRMSE}
-%\end{figure}
-
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
-%	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations).
-The last column depicts evolution of the relative root mean square error in estimating each individual target signal.
-Signals 1 to 3 appear respectively about 30.0, 20.0 and 10.0 million times.
-With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
-%%		
-%%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$.
-Red signals are the ground truth (targets) and the blue signals are our estimations.
-Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$.
-The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$.
-The $\SNR$ is $1/12$.
-\TODO{1.
-to replace with a ``progress'' plot 2.
-replace the triangle signal 3.
-add error progress figure}
-%	}
-%	\label{fig:1Dheterosignals}
-%\end{figure}
-
-\clearpage
 \section{Discussion}
@@
 \TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
-%
-%\TODO{Do we want to note here that EM used to be perceived as computationally out of reach back when it was proposed [cite Fred], yet is now the de facto standard method as exemplified by RELION?
-Do we also want to stress that models have been refined over decades?
-Both points are rather defensive in nature.	}
 
@@
 
-\section{Methods} \label{sec:methods}
-
-\subsection{Toy 2-D experiment}
-
-Let $x\in\RPP$ be the target image and let $y\in\RNN$ be  one of  $K$ observed micrographs. 
-%If more than one micrograph is available, then it is sufficient to average the autocorrelations we compute below over the micrographs.
-Independently for each micrograph, the image formation model is as follows.
-An unknown binary signal $s\in\{0,1\}^{(N-P)\times(N-P)}$ indicates the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise, we observe:
-\begin{align}
-	y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2I),
-	\label{eq:model}
-\end{align}
-where $\ast$ denotes linear convolution, $\ii:=(i_1,i_2)$ identifies one location in the image and $\ii=(0,0)$ indicates the  upper left corner.
-We define the images to be zero outside their support.
-The binary signals $s$ obey the following separation property: 
-\begin{align}
-	\textrm{If } s[\ii] = 1 \textrm{, then } s[\jj] = 0  \textrm{   for all $\jj=(j_1,j_2)$ such that   }  \max\{\vert i_1-j_1\vert, \vert i_2-j_2\vert\}\leq 2P-1.
-	\label{eq:spacing}
-\end{align}
-In words: the upper left corners of any two occurrences of the target image $x$ in a micrograph must be separated by at least $2P-1$ pixels in each direction.
-Hence, each image is separated by a signal-free area that will ease the interpretation of the autocorrelation analysis. 
-From the micrographs, we aim to  recover $x$ only. In this simplified model, we assume  the total number of  occurrences of the signal across micrographs is known. 
-In the 3-D experiment we do not assume knowledge of the number of projections in the micrographs.
-%In contrast, particle picking is the task of estimating the binary signal $s $, which cannot  be performed reliably if $\sigma$ is large (that is, at low $\SNR$.)
-
-%
-%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
-%
-%Our method for estimating the signals is composed of two stages. 
-%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations.
-The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met.
-Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations.
-%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.
-
-%\paragraph{Aperiodic autocorrelation functions.}
-The second-order autocorrelation of  an arbitrary image $z\in\mathbb{R}^{m\times m}$ is defined by
-  \begin{align} 
- a_z^2[\Bell] & = \frac{1}{N^2} \sum_{i_1 = \max\{0, -\ell_1\}}^{m-1 + \min\{0, -\ell_1\}} \sum_{i_2 = \max\{0, -\ell_2\}}^{m-1 + \min\{0, -\ell_2\}}z[\ii]z[\ii+\Bell]. 
- \end{align}
- Below, the image $z$ might be either a target image $x$ or the micrograph $y$. 
- It can be shown that in the limit of infinitely many micrographs $K\to\infty$,  the mean pixel value of the micrographs is equal to the mean pixel value of the signal $x$, scaled by  
- \begin{align} \label{eq:gamma}
- \gamma & = \frac{M P^2}{N^2},
- \end{align}
- where $M$ is the number of occurrences of $x$ across micrographs. 
- This  is the fraction of entries of all micrographs occupied by occurrences of $x$, that is, the  density of the signal. 
-  The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{P}{2P-1}\approx 1/2$.
-
- % Similarly, as $K\to\infty$ the second-order autocorrelations are related through 
- Similarly, numbering micrographs as $y_1, \ldots, y_K$, the empirical average of the second-order autocorrelations of the micrographs converges as follows:
- \begin{align} \label{eq:a2}
-	\lim_{K \to \infty} \frac{1}{K} \sum_{k=1}^{K} a_{y_k}^2[\Bell] & = \gamma a_{x}^2[\Bell] + \sigma^2\delta_{(0,0)}[\Bell], \quad \Bell\in[0,P-1]^2,
- \end{align}
- where $\delta_{(i,j)}[\Bell]=1$ for $\Bell=(i,j)$ and zero otherwise.
- Thus, for any noise level and without the need to even implicitly locate the images $x$ in the micrographs, given sufficiently many micrographs we are able to compute the second-order autocorrelation of $x$ itself.
-Recovering $x$ from $a_x^2$ can be done up to symmetries, as detailed below.
- Equation~\eqref{eq:a2} is proven and its extension to higher-order autocorrelations and multiple distinct planted images is discussed in~\cite{bendory2018estimation}.
-
-%\paragraph{Numerical experiment with a 2-D image.}
-
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $K$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
-This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far.
-On average, $700$ images are placed in each micrograph.   
-Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an $\SNR$ of approximately $1/20$.
-An example of a micrograph's excerpt is presented in the right panel of Figure~TKTK.
-%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-
-In this experiment, we assume $\gamma$ and the noise level $\sigma$ are known.
-In this setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin~\cite{hayes1982reconstruction}.
-The second-order autocorrelation can be computed at the cost of one 2-D FFT per micrograph.
-These can be computed highly efficiently and in parallel.
-To recover the image $x$ itself, we use a standard algorithm used for phase retrieval called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}.
-
-%
-%To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
-%\begin{align*}
-%	z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
-%\end{align*}
-%on an image $z$ of size $2L\times 2L$.
-%We set the parameter $\beta$ to 1.
-%The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere.
-The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
-The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
-
-In order to compare the performance in multiple cases and at different noise levels, the RRR is stopped after a fixed number of iterations (1000)\TODO{check} and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
-While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
-\TODO{Note the last two sentences!}
-\TODO{Let's try with the last iterate and see}
-
-\subsection{3-D experiment}
+% Bibliography
+\bibliography{ref}
+
+\appendix
+
+\section{Numerical experimets details}
+
+\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}
+
+Throughout the proof, we consider the case of one signal $K=1$.
+The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
+
+We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this. We assume $M_N$ grows proportionally with $N$, and define:
+%
+\begin{equation}
+\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
+\end{equation}
+%
+We will assume that $M_N=\Omega(N)$, so that $\gamma>0$. In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
+
+We start by considering the mean of the data:
+%
+\begin{equation}
+a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
+\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
+\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
+\xrightarrow{a.s.}\gamma a_x^1,
+\end{equation}
+%
+where the noise term converges to zero almost surely (a.s.) by the strong law of large numbers.
+
+We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+%
+\begin{align*}
+%
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
+\nonumber \\
+& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
+\\ & + \underbrace{\frac{\TODO{1,2?}}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}. 
+%
+\end{align*}
+
+The cross-terms are linear in the noise, and are easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
+As for the signal term, we break it into $M$ different sums, each containing one copy of the signal.
+This gives:
+%
+\begin{equation} \label{eq:2nd_moment_signal_term}
+%
+\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
+%
+\end{equation}
+%
+
+We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
+%
+\begin{equation}
+%
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+%
+\end{equation}
+%
+Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
+If $\ell=0$, then we have:
+%
+\begin{equation}
+%
+\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
+%
+\end{equation}
+
+We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
+%
+\begin{align}
+%
+&a_y^3[\ell_1,\ell_2] 
+= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+\nonumber \\
+%
+=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
+\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
+\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
+\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+\nonumber \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
+\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%
+\end{align}
+%
+Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
+Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
+
+{\bf Case 1:} $0 < \ell_2 < \ell_1$.
+Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
+Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
+
+{\bf Case 2:} $0=\ell_2 < \ell_1$.
+Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
+The same argument as for Case 1 shows that (3) and (5) also converge to 0.
+For term (4), we write:
+%
+\begin{align}
+%
+&\frac{1}{N}\sum_{j=1}^{M} 
+\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
+\nonumber \\
+&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
+\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
+%
+\end{align}
+
+{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
+
+{\bf Case 4:} $0=\ell_2 = \ell_1$.
+The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
+Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
+
+This completes the proof of \eqref{eq:data_ac}.
+
+\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+
+We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
+For convenience, we will work with $\beta = \gamma / L$ rather than $\gamma$ itself.
+We will construct two quadratic equations satisfied by $\beta$ from observed quantities, independent of $\sigma$.
+Then, we will show that these equations are independent, and hence that $\beta$ is uniquely defined.
+Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
+
+Throughout the proof, it is important to distinguish between observed and unobserved values. 
+We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
+
+Recall that $a_y^1 = \beta(\one^Tx)$ and  
+and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ stands for vector of ones. Taking the product:
+\begin{equation}\label{eq:E1}
+\begin{split}
+E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
+& = \sigma^2a_y^1 + \beta^2F_1,
+\end{split}
+\end{equation}
+where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
+The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account:
+\begin{equation} \label{eq:E2}
+E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
+\end{equation}
+Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
+\begin{equation} \label{eq:E12}
+E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
+\end{equation}
+Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
+\begin{equation} \label{eq:sigma2}
+\sigma^2 = a_y^2 - (a^1_y)^2/(\beta L). 
+\end{equation} 
+Plugging into~\eqref{eq:E12} and rearranging we get 
+\begin{equation} \label{eq:quad1}
+\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
+\end{equation}
+where 
+\begin{align*}
+\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
+\mathcal{B} &= -E_1 + \frac{2L+1}{L}(a_y^1)^3 + a_y^1a_y^2  , \\
+\mathcal{C} &= -(a_y^1)^3/L.
+\end{align*}
+Importantly, these coefficients are observable quantities.
+
+We are now proceeding to derive the second quadratic equation. We notice that 
+\begin{equation} \label{eq:E3}
+E_3  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \frac{1}{L}\beta^3 F_2,
+\end{equation}
+where 
+\begin{equation*}
+F_2 =  a_x^3[0,0] + 3\sum_{j=1}^{L-1}a_x^3[j,j] + 3\sum_{j=1}^{L-1}a_x^3[0,j] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+\end{equation*}
+On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
+\begin{equation} \label{eq:E4}
+E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
+\end{equation}
+Taking the ratio:
+\begin{equation*} 
+\frac{E_4}{E_3} = \frac{L}{\beta^2} + \frac{(6L-3)L\sigma^2a_y^1}{E_3}, 
+\end{equation*}
+we conclude:
+\begin{equation*}
+\sigma^2 = \frac{E_4}{a_y^1L(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
+\end{equation*}
+Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
+\begin{equation} \label{eq:quad2}
+\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
+\end{equation}
+where
+\begin{align*}
+\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
+\mathcal{E} &= -(a_y^1)^2/L, \\
+\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
+\end{align*}
+
+To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
+To this end, it is enough to show that the ratio between the coefficients is not the same.
+From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
+\begin{equation*}
+\begin{split}
+\frac{\mathcal{B}}{\mathcal{C}} &= \frac{LE_1 - (2L+1)(a_y^1)^3 - La_y^1a_y^2}{(a_y^1)^3} \\&= \frac{La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2}{(a_y^1)^2}.
+\end{split}
+\end{equation*}
+In addition, using~\eqref{eq:E3}
+\begin{equation*}
+\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_3} = 3 - 6L . 
+\end{equation*}
+
+Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
+\begin{equation*}
+La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
+\end{equation*}
+Rearranging the equation and writing in terms of $x$ we get 
+\begin{equation} \label{eq:cond}
+4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
+\end{equation}	
+For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
+More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
+\begin{equation*}
+\beta \geq \frac{1}{4(L-1)},
+\end{equation*}
+the condition~\eqref{eq:cond} cannot be satisfied for any signal.
+
+\section{Autocorrelations of the cryo-EM problem}
+
+\subsection{Model and autocorrelation functions}
 
@@
 Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction.
-%similarly to~\eqref{eq:spacing}:
-%\be\label{eq:sep_cond} \ ||\mb s_j - \mb s_i||_{\infty} \geq 2L. \ee
 Note that~\eqref{eq:model} can be also written as a sum of $\delta$ functions as in~\eqref{eq:micrograph_model}.
-%\TODO{Say something about nonuniformity in practice? Remember that biologists will jump at this...}
 
@@
 Let $\II_1,\ldots\II_K$ denote a set of $K$ micrographs. 
-Under the specified conditions, we show in Appendix~\ref{sec:moment_derivation} that the first three autocorrelations  of the micrographs are related to those of the projections by \begin{align} \label{eq:ac_micrographs}
-\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3,& \quad \Bell_1,\ldots,\Bell_{p-1}\in[-(P-1),P-1]^2, \nonumber
+Under the specified conditions, we show in Appendix~\ref{sec:moment_derivation} that the first three autocorrelations  of the micrographs are related to those of the projections by 
+\begin{align} \label{eq:ac_micrographs}
+\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} \\&+ b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3, \quad \Bell_1,\ldots,\Bell_{p-1}&\in[-(P-1),P-1]^2, \nonumber
 \end{align}
 where $\langle\cdot\rangle_\omega$ denotes averaging over all possible viewing directions $\omega$ and $b_p$ is a bias term. 
-%and we take the limit as the number of projections $N$, and hence the dimensions of the micrograph $M$, tend to $\infty$.
 Specifically,  $b_1 = 0$ and therefore the mean is unbiased.
@@
 
-% as follows. We scan the micrographs with a $P\times P$ window. We expand each window in Prolate Spheroidal Wave Functions (PSWFs) 
-%and compute the  second and third autocorrelations in that basis.
-In PSWFs, it is straightforward to average over all in-plane rotations~\cite{landa2017steerable,zhao2016fast}.
-We further average over all windows, resulting in autocorrelation in the PSWF coefficients.
-%It can be shown that the PSWF coefficients of the data $\mathfrak{a}^p$  are related to the expansion coefficients of the volume~\eqref{eq:volume_expansion} by
-%\begin{align}\label{eq:coeffs_to_moms}
-%&\mathfrak{a}^1_x = \frac{L}{\sqrt{4\pi}}\sum_sa_{0,0,s}j_{0,s}(0), \\ 
-%&\mathfrak{a}^2_x(q) = \frac{1}{2\sqrt{2\pi}}\sum_{\substack{\ell,m\\s_1,s_2}}C_2^{(q)}(\ell,s_1,s_2)a_{\ell,m,s_1}\overline{a_{\ell,m,s_2}},
-% \\
-%&\mathfrak{a}^3_x(k,q_1,q_2) = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}C_3^{(k,q_1,q_2)}(\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3)a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}}.
-%\end{align}
-%The definitions of $C_2$ and $C_3$ are provided in Appendix TKTK.
-%
-%To recover the expansion coefficients $\{a_{\ell,m,s}\}$ from the autocorrelation coefficients estimated from the micrograph $\mk m_k[\II]$, we minimize the weighted least-squares problem
-%\be\label{eq:min_problem_cryo} \min_{\{a_{\ell,m,s}\}} \sum_{k=1}^3\frac{\Big|\Big|\mk m_k\{a_{\ell,m,s}\} - \mk m_k[\II]\Big|\Big|_F^2}{||\mk m_k[\II]||_F^2}.\ee
-
-\section*{Acknowledgment}
-Let's thank them all
-
-\bibliographystyle{plain}
-\bibliography{ref}
-
-\appendix
-
-\section{Moments derivation} \label{sec:moment_derivation}
+\subsection{Moments derivation} \label{sec:moment_derivation}
+
 In this section we prove relation~\eqref{eq:ac_micrographs}.
@@
 Hence, we consider the moments of one micrograph $\II$ in the limit $N\to\infty$ and  $\gamma = \lim_{N\to\infty}\frac{MP^2}{N^2}\in(0,1)$.
-%To take this limit, we shall assume that $N=\Omega(M^2)$, and that $\gamma = \lim_{N\to\infty}\frac{NL^2}{M^2}\in(0,1)$ is a constant.
 The separation condition guarantees that if $\mb i=(i,j)$ is in the support of some projection, then $\mb i + \mb \Bell$ for $\Bell\in[-(P-1),P-1]^2$ is either in the support of the same projection or outside the support of any projection.
-%Formally, $\mb i$ is in the support of the $j$th projection if and only if $0\leq \mb i - \mb s_j < L$ where the inequalities apply to each coordinate.
-Then for $||\Bell||_{\infty}\leq L-1$ we have
-%\[-(L-1) \leq [\mb i+\Bell]-\mb s_j< 2L-1,\]
-%and because of the separation condition, given $\mb s_k$ we must either have $\mb s_k-\mb s_i\geq 2L-1$ in which case 
-%\[ \mb i + \Bell- \mb s_k \leq \mb i + \Bell- \mb s_j - (2L-1) < 0,\]
-%or $\mb s_k - \mb s_i \leq -(2L-1)$, in which case
-%\[ \mb i + \Bell - \mb s_k \geq -(L-1) + 2L-1 = L.\]
-%In either case, $[\mb i+\Bell]$ is not in the support of the $k$th particle.
 
@@
 Denote by $\mc S_t$ the support of the $t$th particle. 
-% and by $Z=\{1,\ldots, M\}-\sqcup_j \mc S_j$ all the points outside the support of the particle.
-%The clean  micrograph  then satisfies $\widetilde \II[\Bell] = 0$ if $\mb i\in Z$, so we have
 Then, we have
@@
 The cross terms vanish in the limit.  
-%Considering the terms one-by-one, the first term is independent of the
-%noise, and as shown above converges to $\gamma \langle
-%m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
-%satisfies
-%\[\begin{aligned} 
-%\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\Bell]\varepsilon[\mb i + \Bell] &=
-%\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
-%i)\varepsilon_{\omega_j}[\mb i + \Bell]\\
-%&\to \gamma\mathbb{E}_{\omega,\varepsilon}[I_{\omega}\varepsilon]\\ 
-%&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\varepsilon}[\varepsilon] = 0, \end{aligned}\]
-%where $\varepsilon_{\omega_j}[\Bell] = \varepsilon(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\varepsilon$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$.
-A similar argument applied to the third term shows that it
-%also vanishes as $N\to\infty$. 
 The fourth term is zero unless $\Bell=0$, in which case it converges to $\sigma^2$.
-% $\Bell \neq \mb{0}$ %then since the noise is zero mean and
-%i.i.d. this term vanishes. If $\Bell = \mb0$ then
-%\[ \frac{1}{N^2}\sum_{i,j=1}^m\varepsilon[\Bell]^2 \to \sigma^2.\]
 Thus, we conclude
@@
 	&= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
-      \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
+	\\& \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
 	%&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
@@
 	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
-	%That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
-%	\item For term (7), if $\Bell \neq \mb 0$ then once again
-%	this term vanishes, whereas if $\Bell_2 = \mb 0$ then it becomes
-%	\[ \frac{1}{N^2}\sum_{\mb i}\varepsilon[\Bell]^2\widetilde\II(\mb i + \Delta\mb
-%	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
-%		i}\varepsilon_{\omega}[\Bell]^2I_{\omega}(\mb i + \Bell_2) \to
-%	\gamma\sigma^2Lm_1[\phi].\]
-	%Similarly, terms (7) (8) vanishes if $\Bell_2\neq \mb 0$ and
-	%converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
 \end{itemize}
-%Similarly, terms (7) (8) contributes $\delta$ functions similar to (6).
 Thus, we conclude that
@@
 
-\section{Accounting for all in-plane rotations} \label{sec:steering}
+\subsection{Accounting for all in-plane rotations} \label{sec:steering}
 
@@
 \[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
-&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
+&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\\&\times \left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
 &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
@@
 \begin{align} \label{eq:third_order_ac_pswf}
-\mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
+&\mathfrak{a}^3[k_1,q_1;k_2,q_2] \\&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
 &= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. 
@@
 Finally, we treat the bias terms, using approximate orthonormality \TODO{!} of the discretized PSFWs:
-\[ \mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
-\]
+\begin{align*}
+&\mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\\&\times \left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
+\end{align*}
+%
 Thus,
@@
 \[\begin{aligned} b_{N,n}(\omega) &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
-&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
+&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
 &= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
@@
 a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\mb i]I_{\omega}[\mb i+\Bell_1]\overline{I_{\omega}([\mb i+\Bell_2])}\rangle_{\omega},\\
-&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
+&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\\&\times \frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
 where the approximation is due to discretization. 
 Now,
-\[\begin{aligned} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
+\[\begin{aligned} \langle &b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} \\&= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\\&\times \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
 &\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
 where the latter coefficients are given explicitly in~\eqref{eq:beta}. Using standard properties of D-Wigner functions, we obtain  
-\[ \left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
-\]
+\begin{align}
+&\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
+\end{align}
 where  $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right)$ are called Wigner 3-j symbols. 
@@
 \begin{align} \label{eq:b_average}
-\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \delta_{N_3,N_1+N_2}\sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
-&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+&\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} = \delta_{N_3,N_1+N_2}\\&\times \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
+&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
 &\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}. \nonumber
@@
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\\&\times\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
 \end{aligned}\]
@@
 obtain
-\[ \left\langle a^2_{\hat{I}_{\omega}}(k,\theta)\right\rangle_{\omega} =
+\begin{align*}
+\left\langle a^2_{\hat{I}_{\omega}}(k,\theta)\right\rangle_{\omega} &=
 \frac{1}{4\pi}\sum_{\ell,
-	m}\left|\sum_s\tamir_{\ell,m,s}j_{\ell,s}(k)\right|^2 =
-\frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}\tamir_{\ell,m,s_1}\overline{\tamir_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),\]
+	m}\left|\sum_s\tamir_{\ell,m,s}j_{\ell,s}(k)\right|^2 \\&=
+\frac{1}{4\pi}\sum_{\substack{\ell,m\\s_1,s2}}\tamir_{\ell,m,s_1}\overline{\tamir_{\ell,m,s_2}}j_{\ell,s_1}(k)j_{\ell,s_2}(k),
+\end{align*}
 where we used the fact that the normalized spherical Bessel functions

### 2018-08-24 pnas/Towards.tex
introduction pnas

@@
 
-\dropcap{C}ryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise}
-In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
-Within the ice, the molecules are randomly oriented and positioned.
+\dropcap{C}ryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise first sentence}
+In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. %Within the ice, the molecules are randomly oriented and positioned.
  The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
@@
 
-The signal to noise ratio ($\SNR$) of the projections in the micrographs is a function of two dominating factors.
-On the one hand, the $\SNR$ is a function of the electron dose.
+The signal to noise ratio (SNR) of the projections in the micrographs is a function of two dominating factors.
+On the one hand, the SNR is a function of the electron dose.
 To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the $\SNR$ is a function of the molecule \TODO{size/weight}.
+On the other hand, the SNR is a function of the molecule \TODO{size/weight}.
 The smaller the molecules, the fewer detected electrons carry information about them.
@@
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the $\SNR$ degrades.
-
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical $\SNR$; see for instance~\cite{bendory2018estimation}\TODO{To verify the title}.
+Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the SNR degrades.
+
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR \TODO{the impossibility result should be in the theory section}.
 This fact has been recognized early on by the cryo-EM community.
@@
 
-As a proof of concept, we study a simplified model for 3-D reconstruction directly from the micrograph on a simulated data. 
-In order to recover the 3-D volume, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the volume.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided the we get to observe sufficiently many particle projections and the latter are separated in the micrograph.
-Importantly, there is no need to detect the projections.
+As a proof of concept, we study a toy model for which it is easier to convey the mathematical principles. 
+In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
+This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+In order to recover the image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we get to observe sufficiently many image occurrences and the latter are separated in the micrograph.
+Importantly, there is no need to detect individual image occurrences.
 The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the volume.
-To estimate the volume itself from its estimated autocorrelations, we solve a nonlinear inverse problem via least-squares.
-In this controlled experiment, we make several simplified assumptions; see the Discussion Section for details.
-\TODO{Do we want to stress that we get only low-resolution of the volume?}
+These directly yield estimates for the autocorrelations of the image.
+To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
+
+Later, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions. We show a few numerical examples
+ and draw the future developments required to make this method applicable on real data. \TODO{This paragraph would be changed according to the final results we will show}
 
@@
 In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
-\TODO{To add reference to our example.}
-
-To illustrate the possibility to estimate a signal without detecting its locations, we first discuss a toy model for which it is easier to convey the mathematical principles. 
-In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~TKTK for an illustration.
-The goal is to estimate the planted image. The task is interesting in particular when the $\SNR$ is low enough that particle picking cannot be done reliably. 
-This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+%
+%To illustrate the possibility to estimate a signal without detecting its locations, we first discuss a toy model for which it is easier to convey the mathematical principles. 
+%In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~TKTK for an illustration.
+%The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
+%This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 We study it in more details, including an extension to multiple planted images, in a companion paper~\cite{bendory2018estimation}.
@@
 In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
-In fact, it can be shown that at low $\SNR$, reliable detection of individual image occurrences is impossible, even if the true image is known.
-By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.
-\TODO{Do we want to replace with a cryo-EM figure?
-This figure will be positioned with the rest of the figures about Einstein's example}}
+In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
+By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
 \end{figure*}
@@
 
-If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible.
+If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low SNR regime, estimating the binary sparse signal $s$ is impossible.
 We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
-%
-%To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$.
-Suppose too that the oracle provides us with $x$ itself.
-That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations.
-This is an easier problem than detecting the support of $s$.
-Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}.
-Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.
-
-%\TODO{Here we should give the Will's proposition for the impossibility of detection}
 
@@
 
-%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low SNR regime.
 Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
@@
 therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low $\SNR$ regime.
+Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low SNR regime.
 Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
@@
 Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to $\SNR=1/20$).
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$=1/20$).
 This high noise level is illustrated in TKTK.
@@
 		%\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
-		% At a noise level of $\sigma = 3$, this amounts to an $\SNR$ of $1/20$.
+		% At a noise level of $\sigma = 3$, this amounts to an SNR of $1/20$.
 	}
@@
 \end{figure}
+
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[scale=0.7]{1D_example}
+	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ occurances in $N = 410*M$. he true value of $gamma$ is $0.0512$.
+		  The first three panels show reconstruction with different $M$ values compared to the ground truth signal (in blue).
+The relative error of $\gamma$ for the three panels is: $27.1\%,4\%,1.2\%$.
+The right panel shows the relative error as a function of $M$.)
+	}
+\end{figure*}
 
@@
 
-One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable $\SNR$ is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
+One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
 Still, large amounts of data also imply large amounts of computations.

### 2018-08-24 pnas/Towards.tex
Starting section 2

@@
 
+In this section, we present a toy model which is studied in the next sections. 
+The role of this model is to introduce the mathematical principles enabling to estimate a signal in a low SNR regime, although its detection might be impossible.
+Later, we discuss how these principles can be carried through for the SPR problem.
+The model is formulated for 1-D signals to ease exposition.
+
 Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data.
@@
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
-As will be shown next, in the low signal-to-noise ratio (SNR) environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.
+As will be shown next, in the low SNR environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.
 
@@
 \begin{align}
-\textrm{If } s_k[i] = 1 \textrm{ and } s_{k'}[j] = 1 \textrm{ but } (k, i) \neq (k', j), \textrm{ then } |i - j| \geq 2L-1.
+\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
 \label{eq:spacing}
 \end{align}
-In words: the starting positions of any two occurrences (be it of the same signal or of two different signals) must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
 

### 2018-08-25 pnas/Towards.tex
Section 2 updated

@@
 
-\subsection{Related work}
-
-For $K=1$, our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
 %
@@
 where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
-%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
 The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$).
-The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+In the special case where $w$, satisfying the condition of~\eqref{eq:spacing}, we obtain our model.
+The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
 
 Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.
-For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
+%For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
 If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
-
 Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
 One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
+%Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
 Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
-
-In special cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
+In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
 The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
 However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
-Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
+%Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
 Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
 However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
-
-\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
-
 Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
@@
 \end{corollary}
+
+\section{Numerical experiments}
+
+\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
 

### 2018-08-26 pnas/Towards.tex
Sections: proof of concept + ac analysis

@@
 However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
-Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
+%
+%Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
 
-\section{Autocorrelation analysis}
+Because likelihood methods are computationally expensive, methods based on recovery from moments have also been previously used for system identification.
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+Following this approach, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and analyze it in Section~\ref{sec:theory}.
+
+\section{Autocorrelation analysis} \label{sec:AC_analysis}
 
@@
 where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
+For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
 Explicitly, the first-, second- and third-order autocorrelations are given by
@@
 The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-\begin{align*}
-a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-\end{align*}
+$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$
+%\begin{align*}
+%a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+%\end{align*}
 %Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
-
-For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
+%
+%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
+%\begin{align}
+%\gamma & = \frac{M L}{N}
+%\end{align}
+%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+Under the space constraint~\eqref{eq:spacing}, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple.
 It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
@@
 Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+\TODO{TB: I think that this paragraph can be much shorter and it is sufficient to show only the second equation and remove footnote. Nicolas thinks otherwise. Need to be decided. }
 
@@
 \begin{align*}
-\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell]
+\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
 \end{align*}
-for $\ell = 0, \ldots, L-1$, where $\ell$ denotes the Kronecker delta function.
+for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
 The last part captures the autocorrelation of the noise.
@@
 Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{align}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \cdot \big(\ell[\ell_1,0]+\ell[0,\ell_2]+\ell[\ell_1,\ell_2]\big),
-\label{eq:data_ac_k1}
+\begin{align} \label{eq:data_ac_k1}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), 
+ \nonumber
 \end{align}
@@
 
-\section{Proof of \eqref{eq:data_ac}} \label{sec:autocorrelation_computation}
+\section{Derivation of identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
 

### 2018-08-27 pnas/Towards.tex
Theory section is updated

@@
 We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
-\begin{align*}
+\begin{align} \label{eq:mean_micrograph}
 \lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
-\end{align*}
+\end{align}
 Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
@@
 As a result,
-\begin{align*}
+\begin{align} \label{eq:ac2_micrograph}
 \lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
-\end{align*}
+\end{align}
 for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
@@
 Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{align} \label{eq:data_ac_k1}
+\begin{align} \label{eq:ac3_micrograph}
 \lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), 
@@
 
-If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
-However, in the low SNR regime, estimating the binary sparse signal $s$ is impossible.
-We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
-
-Therefor, we need to consider a different approach.
-In this paper, we consider autocorrelation analysis.
-In what follows, we present several results on properties of autocorrelations.
-For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are non-zero by definition, we have the formula:
+If $x$ is known, then the support signal $s$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible.
+\TODO{Here we need to provide Will's argument as a proposition}
+
+%We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
+
+Accordingly, we must consider methods that aim to estimate the signal directly, without estimating the nuisance variables as an intermediate step. 
+ %we need to consider a different approach. In this paper, we consider autocorrelation analysis.
+  In what follows, we present several results on properties of autocorrelations. For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are nonzero by definition, we have the formula:
 %
@@
 \end{align}
-
 In particular, we have proven the following proposition:
-
 \begin{proposition} \label{prop:uniqueness}
@@
 Some remarks are in order.
-First, formula \eqref{eq-uniqueness} is not numerically stable if $z[0]$ and/or $z[L-1]$ are close to 0.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have seen similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-
+First, \eqref{eq-uniqueness} is not numerically stable if $z[0]$ or $z[L-1]$ are close to 0.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
@@
 In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-
-\begin{comment}
-
-%%%Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low SNR regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low SNR regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-, this uniqueness result holds for signals of any dimension. Third
-
-Furthermore,
-as proven in the following simple proposition.
-%
-\begin{proposition} \label{prop:uniqueness}
-%
-Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero.
-Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-More precisely, suppose we can measure $\tilde{a}_z^3[k,L-1] = a_z^3[k,L-1]+\upsilon$ and that $\vert z[0]z[L-1]\vert \geq \ell>0$.
-Then,  $\hat{z}[k] =\frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} $ satisfies $\vert \hat{z}[k] - z[k]\vert\leq \frac{\vert \upsilon\vert }{\ell}$.
-
-\end{proposition}
-
-\begin{proof}
-%
-By assumption $a_z^2[L-1] = z[0]z[L-1]\neq 0$.
-Then, the uniqueness results, for all $k=0,\ldots L-1$,  follows from:
-%
-\begin{equation*}
-%
-a_z^3[k,L-1] = z[0]z[k]z[L-1].
-%
-\end{equation*}
-%
-In addition, 
-%
-\begin{equation*}
-%
-\hat{z}[k] = \frac{\tilde{a}_z^3[k,L-1]}{a_z^2[L-1]} = z[k]+\frac{\upsilon}{a_z^2[L-1]} \quad \Rightarrow \quad \vert \hat{z}[k] - {z}[k]\vert \leq \frac{\vert\upsilon\vert}{\ell}.
-%
-\end{equation*} 
-%
-\end{proof}
-
-A few remarks are in order. 
-First, the second result of Proposition~\ref{prop:uniqueness} shows that there exists a very simple estimator that has finite sensitivity.
-In the next numerical experiments we use an estimator based on nonconvex LS that shows empirical robustness to additive noise, in accordance with related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous}.
-Second, these results carry through to signals of any dimension.
-Third, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations and 
-therefore the assumption that the first and last entries are nonzero is met. In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
-Finally, computing the $d$th autocorrelation amplifies the variance of the noise by a factor $d$ in the low SNR regime.
-Therefore, if we can estimate $a_z^3$ up to small perturbation, it implies that we can estimate $a_z^2$ accurately as the proposition assumes.
-
-\end{comment}
-
-Note too that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-%%%Considering the third-order autocorrelation is also a necessary condition to determine a signal from its autocorrelations.
-Indeed, the second-order autocorrelation of a one-dimensional signal does not determine a signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible}.
+Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case).
+%~\cite{hayes1982reconstruction,hayes1982reducible}.
 The sign ambiguity can be resolved by the mean of the signal if it is not zero.
@@
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by formula~\eqref{eq:data_ac_k1}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
 We will show, however, that $x$ is still identifiable from the observed moments of $y$.
@@
 
-First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector $y$.
+First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector.
 %
 \begin{proposition} \label{prop:gamma}
-	Let $K=1$ and $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
+	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
 	%
@@
 \begin{proof}
-	The proof follows from plugging the explicit expressions of~\eqref{eq:data_ac_k1} into the right hand side of the equality.
+	The proof follows from plugging the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
 \end{proof}
@@
 Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
-
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
+lies in the vanishing locus of a nonzero polynomial\footnote{Given a  nonzero polynomial $f$ in $T$ variables (real or complex), the vanishing locus of $f$ is the set 
+	$V(f) = \{(x_1, \ldots, x_T) \in \mathbb{R}^T (\text{resp.
+} \mathbb{C}^T) \vert f(x_1,\ldots x_T)=0\}$.
+By a general result in algebraic geometry $\dim V(f) < T$.
+As a consequence the complement of $V(f)$ in $\mathbb{R}^T$ (resp.
+$\mathbb{C}^T$) is dense.}.
+In particular, this means that we can recover
+almost all signals with the given measurements.
+%
+%we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
+%
 \begin{proposition} \label{prop:gamma_sigma}
 	%
-	Let $K=1$, and $\sigma > 0$ be fixed.
-Then, $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma\geq\frac{1}{4L(L-1)}$, then this holds for any signal $x$ with nonzero mean.
+	%Let $\sigma > 0$ be fixed. 
+	The observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma\geq\frac{L}{4(L-1)}\approx \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
 	\begin{proof}
@@
 \begin{corollary}
-	Let $K=1$ and $\sigma > 0$ be fixed. Then the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
+	%Let $K=1$ and $\sigma > 0$ be fixed.
+	 The signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
 	\begin{itemize}
 		\item Either the signal $x$ is generic; or
-		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{1}{4L(L-1)}$.
+		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{L}{4(L-1)}$.
 	\end{itemize}
@@
 
-\section{Derivation of identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
+\section{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
 

### 2018-08-27 pnas/Towards.tex
Section 4 and 5

@@
 To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the SNR is a function of the molecule \TODO{size/weight}.
+On the other hand, the SNR is a function of the molecule size.
 The smaller the molecules, the fewer detected electrons carry information about them.
@@
 
-Later, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions. We show a few numerical examples
- and draw the future developments required to make this method applicable on real data. \TODO{This paragraph would be changed according to the final results we will show}
+Autocorrelation analysis for 3-D reconstruction, under the assumption of perfect particle picking,  was first proposed by Zvi Kam~\cite{kam1980reconstruction}. 
+In this work, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions.
+We show a few numerical examples and draw the future developments required to make this method applicable on real data.
+\TODO{This paragraph would be changed according to the final results we will show}
 
@@
 If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
+Methods based on such formulations are popular nowadays in cryo-EM; see for instance~\cite{sigworth1998maximum,scheres2012relion}. 
 Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
@@
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-Following this approach, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and analyze it in Section~\ref{sec:theory}.
+Following this approach, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and study it in Section~\ref{sec:theory}.
 
@@
 First, \eqref{eq-uniqueness} is not numerically stable if $z[0]$ or $z[L-1]$ are close to 0.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedures, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedures, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
@@
 
-\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
-
-The techniques we advocate allow to recover a signal hidden in noisy micrographs without (even implicitly) detecting the location of signal repetitions in these micrographs.
-To illustrate the underlying principles of the method, it is instructive to start with a toy model where the target signal is an unknown 2-D image.
+The technique we advocate allow to recover a signal hidden in noisy micrographs without (even implicitly) detecting the location of signal repetitions in these micrographs.
+To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for a simulated cryo-EM data.
+Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
+
+%it is instructive to start with a toy model where the target signal is an unknown 2-D image.
 The latter appears several times in noisy micrographs, at unknown locations.
@@
 The more micrographs we collect, the more accurate the estimate of the image's autocorrelation.
-The target image is then estimated from its autocorrelation using a standard inversion algorithm (up to elementary symmetries).
-The same principles carry over to the more challenging task of 3-D reconstruction from micrographs.
-The Methods Section provides additional details.
-
-In the  experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+%The target image is then estimated from its autocorrelation using a standard inversion algorithm (up to elementary symmetries).
+%The same principles carry over to the more challenging task of 3-D reconstruction from micrographs.
+%The Methods Section provides additional details.
+
+In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
 A micrograph contains, on average, 700 occurrences of the target image at random locations.
 Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$=1/20$).
-This high noise level is illustrated in TKTK.
-%In this first experiment, we assume knowledge of $\sigma$ and of the total number of signal occurrences across all micrographs.\TODO{Need to mention that in the 3-D reconstruction we do not make these assumptions.}
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$\approx ?$).
+This high noise level is illustrated in Figure~\ref{fig:micro_example}.
 To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction.
-The separation restriction is discussed in more details in the Methods Section.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with~\eqref{eq:spacing}.
+%The separation restriction is discussed in more details in the Methods Section.
 
@@
 This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) on GPUs.
-In the Methods Section, we show how, owing to separation of the occurrences, a determined portion of the averaged autocorrelation allows to estimate the autocorrelation of the unknown image itself.
-Mathematically, it can be shown that for any noise level, the quality of this estimate improves steadily as the amount of data grows~\cite{bendory2018estimation}.
+Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
 Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
-
-%RRR is initialized far away from the ground truth, and it iterates to produce the estimate, up to a reflection ambiguity.
 
@@
 Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities.) This is computed after fixing elementary symmetries (see Methods.) As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-\TODO{Tamir: I will rewrite it with the new experiment.}
+Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities).
+This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
+As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+\TODO{Tamir: the experiment is currently running; should be ready tomorrow  (Aug 28).}
+
+In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
+Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
+The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}.
+ Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
+Crucially, the LS does not require the knowledge of $\sigma$.
+
 \TODO{Here the cryo-EM setup shows up}
@@
 	\includegraphics[scale=0.7]{1D_example}
-	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ occurances in $N = 410*M$. he true value of $gamma$ is $0.0512$.
-		  The first three panels show reconstruction with different $M$ values compared to the ground truth signal (in blue).
-The relative error of $\gamma$ for the three panels is: $27.1\%,4\%,1.2\%$.
-The right panel shows the relative error as a function of $M$.)
+	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
+The length of the micrograph was set to be $N = 410*M$.
+The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
+		The true value of $\gamma$ is $0.0512$.
+		   The relative errors of $\gamma$ for the three panels are: $27.1\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$.
 	}
@@
 
-In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
-Our strategy is to compute autocorrelation functions of the micrographs and to relate these statistics to the unknown volume's parameters.
+%In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
+In the simplified mathematical model we examined, we showed it is possible to estimate a signal without detecting its appearances.  
+Our strategy is to compute autocorrelation functions of the micrographs and to relate these statistics to the unknown signal's parameters.
 Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
+
+We also showed how this technique can be, in principle, applied to cryo-EM.
 Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
 Concerns for model bias are also greatly reduced since no template matching is involved.
+Additionally,  our technique also allows to use much lower defocus values.
+Lower defocus means lower contrast, but will maintain  higher frequency information.
+From that perspective, we may be able to get high resolution reconstructions from fewer micrographs.
+%, just because we would be using lower defocus.
 
@@
 
+\TODO{First and foremost, we need to mention the sensitivity of the third moment and whether the fourth moment is enough}
 %As a result, it may not be limited to large molecules in the same way that particle picking approaches are. 
@@
 
-\TODO{
-	We should also incorporate Alberto's comment that our technique also allows to use much lower defocus values.
+%
+%\TODO{
+%	We should also incorporate Alberto's comment that our technique also allows to use much lower defocus values.
 Lower defocus means lower contrast, but will maintain higher frequency information.
@@
 The proof-of-concept experiments above suggest they might.
+\TODO{Is it?}
 
@@
 Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
-Perhaps this separation could be induced by careful experimental design \TODO{?}.
-Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
+We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph. 
+Such a condition can be met in practice by careful experimental design.
+
+%Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
 Here as well, relations between autocorrelations of the micrographs and of the volume could be derived.
 
-We also note several aspects of SPR experiments that were neglected in this paper, including Contrast Transfer Function (CTF) correction and the non-uniformity of the viewing directions.
+We also note several aspects of SPR experiments that were neglected in this paper, including Contrast Transfer Function (CTF) correction, non-uniformity of the viewing directions and other contaminants in the micrographs, such as ice crystals.
  All these aspects must be taken into account so the method could be applied on real data.
 We hope to take care of these issues in future research, as well to extend the proposed method to conformational heterogeneity.
-\TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
-
-\TODO{Where and how do we cite Kam? Fred?}
+%\TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
+
+%\TODO{Where and how do we cite Kam? Fred?}
 
@@
 
-\section{Numerical experimets details}
+\section{Numerical experiments details} \label{sec:numeric_details}
+
+\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
 

### 2018-08-27 pnas/Towards.tex
experimental details

@@
 Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$\approx ?$).
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$\approx1/375$).
 This high noise level is illustrated in Figure~\ref{fig:micro_example}.
@@
 	\includegraphics[scale=.68]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
-	%\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
+	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
 \end{figure}
@@
 
-\TODO{Need to refer to this paper https://arxiv.org/abs/1806.00338}
+\paragraph{2-D experiment.}
+
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
+In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
+This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
+an accept/reject rule based on the separation constraint and locations picked so far.
+On average, $700$ images are placed in each micrograph.   
+Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an SNR of approximately $1/375$.
+An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
+%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
+In stark contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin.
+This is because the second-order autocorrelations correspond to the Fourier magnitudes of the signal through the 2-D Fourier transform.
+Therefore, we estimate the signal's Fourier magnitudes (or power spectrum) from the Fourier magnitudes of the micrographs, at the cost of one 2-D fast Fourier transform (FFT) per micrograph.
+These can be computed highly efficiently and in parallel.
+
+To recover the target image from the estimated power spectrum, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR). This algorithm iterates the map
+\begin{align*}
+z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
+\end{align*}
+on an image $z$ of size $2L\times 2L$.
+We set the parameter $\beta$ to 1.
+The map is designed so that, if the estimated power spectrum is exact, then fixed points contain Einstein's image in the upper-left corner of size $L \times L$, possibly reflected through its origin, and zeros elsewhere.
+The operator $P_2(z)$ combines the Fourier phases of  the current estimation $z$ with the estimated Fourier magnitudes.
+The operator $P_1(z)$ zeros out all entries of $z$ outside the $L\times L$ upper-left corner.
+In all experiments, the algorithm halted after a fixed number of 2000 iterations.
+%
+%In order to compare the performance in multiple cases and at different noise levels,  and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
+While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
+\TODO{Note the last two sentences!}
+
+\paragraph{1-D experiment.}
+For the 1-D experiment depicted in Figure~\ref{fig:1D_example}, we used a signal of length $L=21$ and generated an observation $y$ of length $N = 10(2L-1)M$, where $M$ is the number of repetitions. 
+The observation was generated by randomly selecting placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far until reaching the desried number of signal occurences.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+The resulting SNR of $y$ is about $1/175$.
+%	 fix $K = 3$ signals of length $L = 21$.
+Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+The resulting SNR of $y$
+%% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
+%is about 1/9.
+
+%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
+
+%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
+%
+Given the observation $y$, we proceed to compute the autocorrelations. %The first-order autocorrelation is straightforward. 
+We excluded biased elements of the autocorrelations; that is $a_y^2[\ell_1]$ and $a_y^3[\ell_1, \ell_2]$ such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero. 
+This has the  practical effect that we need not know $\sigma$. 
+%For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
+Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---
+By also taking symmetries into account, the third-order autocorrelation contains $\frac{(L-1)(L-2)}{2}$ remaining entries. Thus, in total we have
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+coefficients. 
+This redundancy suggests that it might be possible to estimate several signals simultaneously (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}).
+%Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
+%\begin{align*}
+%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
+%\end{align*}
+%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). 
+In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ (if the length of the measurement is larger than that) and added up, without correction for the junction points.
+Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
+Having computed the moments of interest, we now estimate the signal $x$ and coefficient $\gamma$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear LS problem:
+%\begin{align}
+%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \mathbb{R}^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}}& w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 \\ & + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2  \nonumber \\&+ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2, \nonumber
+%\label{eq:optim1D}
+%\end{align}
+\begin{align}
+\min_{\substack{\hat x\in \mathbb{R}^{W} \\ \hat \gamma > 0}}& w_1 \left( a_y^1 - \hat \gamma a_{\hat x}^1 \right)^2  + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \hat \gamma a_{\hat x}^2[\ell] \right)^2  \nonumber \\&+ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] -  \hat \gamma a_{\hat x}^3[\ell_1,\ell_2] \right)^2,
+\label{eq:optim1D}
+\end{align}
+where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
+
+Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+Similar phenomenon was recently observed in a related problem~\cite{zhang2018structured}.
+Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+\paragraph{3-D experiments.}
 

### 2018-08-28 pnas/Towards.tex
Early noon session

@@
 
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR \TODO{the impossibility result should be in the theory section}.
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
 This fact has been recognized early on by the cryo-EM community.
@@
 Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.
+Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
 
 As a proof of concept, we study a toy model for which it is easier to convey the mathematical principles. 
-In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
+In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+The goal is to estimate the planted image.
+The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
 This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
-In order to recover the image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we get to observe sufficiently many image occurrences and the latter are separated in the micrograph.
+In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
 Importantly, there is no need to detect individual image occurrences.
 The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the image.
+These directly yield estimates for the autocorrelations of the image \TODO{Will: This is not quite true, because of the gamma parameter}.
 To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
@@
 In this work, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions.
-We show a few numerical examples and draw the future developments required to make this method applicable on real data.
+We show a few numerical examples and outline the future developments required to make this method applicable on real data.
 \TODO{This paragraph would be changed according to the final results we will show}
@@
 %
-%To illustrate the possibility to estimate a signal without detecting its locations, we first discuss a toy model for which it is easier to convey the mathematical principles. 
-%In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~TKTK for an illustration.
-%The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
-%This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-We study it in more details, including an extension to multiple planted images, in a companion paper~\cite{bendory2018estimation}.
 
@@
 For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-Explicitly, the first-, second- and third-order autocorrelations are given by
+Explicitly, the first-, second- and third-order autocorrelations are given by \TODO{we may want to remove these explicit formulas}
 \begin{align} 
@@
 Crucially, the LS does not require the knowledge of $\sigma$.
-
-\TODO{Here the cryo-EM setup shows up}
 
@@
 	\centering
-	\includegraphics[scale=.68]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
+	\includegraphics[scale=.55]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
 	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
@@
 	}
+\end{figure*}
+
+The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
+The derivation of the first three autocorrelations of the micrographs and their relations to the volume itself are provided in Appendix~\ref{sec:ac_cryo}.
+In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume.
+Figure~TKTK shows recovery of the 3-D volume from the clean autocorrelations.
+The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
+Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing recovery from noisy data. 
+In the next section, we outline how we suggest to overcome the ill-conditioning in future work.
+
+While we cannot provide a 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics (e.g.,~\cite{donoho2004higher}) and debates in the cryo-EM community~\cite{henderson2013avoiding}.
+This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
+Figure~\ref{fig:cryo_detection} presents excerpts \TODO{sections?} of two noisy micrographs, only one of which contains projections.
+In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
+On the hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
+%
+%Under the experimental parameters (see Section~\ref{sec:numeric_details}), such values of $\gamma$ predict  in the informative micrograph and less than one projection in the pure noise scenario.
+
+\begin{figure*}[h]
+	\centering
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.eps}
+		\caption{An excerpt of the pure noise micrograph}
+	\end{subfigure} \hspace{2pt}
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{noisy_micrograph_cutout.eps}
+		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
+	\end{subfigure} \hspace{2pt}
+	\begin{subfigure}[h]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{clean_micrograph_cutout.eps}
+		\caption{An excerpt of the clean micrograph}
+	\end{subfigure}
+	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from a volume of size $31^3$.
+The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
+		The noise realization is identical in both micrographs. }	
 \end{figure*}
@@
 \paragraph{3-D experiments.}
+For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK.
 
@@
 &= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
-\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
+\\& \xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
 %
@@
 
-This completes the proof of \eqref{eq:data_ac}.
+This completes the proof.
 
@@
 \begin{equation*}
-La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
+La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L).
 \end{equation*}
@@
 
-\section{Autocorrelations of the cryo-EM problem}
+\section{Autocorrelations of the cryo-EM problem} \label{sec:ac_cryo}
 
@@
 \[\begin{aligned} 
-&a^3_\II[\Bell_1, \Bell_2] =
-\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
+&a^3_\II[\Bell_1, \Bell_2]  \\&
+ = \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
 \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
@@
 a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\mb i]I_{\omega}[\mb i+\Bell_1]\overline{I_{\omega}([\mb i+\Bell_2])}\rangle_{\omega},\\
-&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\\&\times \frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
+&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\nonumber\\&\times \frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
 where the approximation is due to discretization. 
@@
 \begin{align}
-&\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\
+&\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\nonumber
 \end{align}
@@
 &\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} = \delta_{N_3,N_1+N_2}\\&\times \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
-&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\nonumber\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\nonumber\\
 &\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}. \nonumber
@@
 the final formula reads
-\[\begin{aligned} \mathfrak{a}^3[k,q_1,q_2] &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
+\[\begin{aligned} &\mathfrak{a}^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
@@
 
-\TODO{=========== Tamir: Stopped here ===============}
-
-\TODO{=========== NOT SURE WHAT IS THAT ===============}
-\begin{align*}
-&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
-&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
-\end{align*}
-and 
-\begin{align*}
-\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
-\end{align*}
-
-\subsection{Implementation details}
-To implement the above formula, we precompute the quantities
-\[ W(\ell_1,\ell_2,\ell_3,m_1,m_2) = (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right),\]
-and
-\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},\]
-so in each iteration of the optimization we compute
-\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) = \sum_{\substack{\ell_1,\ell_2,\ell_3\\m_1,m_2\\s_1,s_2,s_3}}& W(\ell_1,\ell_2,\ell_3,m_1,m_2)B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3)\times\\ &a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}} .\end{aligned}\]
-
-The Wigner 3$j$ symbols are computed from the Racah formula
-\[\begin{aligned} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right) &= \delta_{m_3,m_1+m_2}(-1)^{\ell_1-\ell_2+m_3}\sqrt{\Delta(\ell_1,\ell_2,\ell_3)}\\ &\times \prod_{i=1}^3\sqrt{(\ell_i-m_i)!(\ell_i+m_i)!}\times \sum_{t}\frac{(-1)^t}{x(t)},\end{aligned}\]
-where
-\[ x(t) = t!(\ell_3-\ell_2+t+m_1)!(\ell_3-\ell_1+t-m_2)!(\ell_1+\ell_2-\ell_3+t)!(\ell_1-t-m_1)!(\ell_2-t+m_2)!,\]
-the sum is over all integer $t$ for which the arguments in the factorials in $x(t)$ are all nonnegative, and 
-\[ \Delta(\ell_1,\ell_2,\ell_3) = \frac{(\ell_1+\ell_2-\ell_3)!(\ell_1-\ell_2+\ell_3)!(-\ell_1+\ell_2+\ell_3)!}{(\ell_1+\ell_2+\ell_3+1)!}.\]
-
-\section{Noisy micrograph moments}
-We now suppose that the micrograph is perturbed by additive white
-Gaussian noise, so we observe $\widetilde \II = \II + \varepsilon$ where
-$\varepsilon\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
-to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
-m_3[\widetilde\II]$. For simplicity of notation,
-we shall use vectorized indices $\mb i = (i,j)$.
-
-\subsection{Expansion in PSWFs}
-In practice, we compute the moments of our noisy micrograph in a
-product basis of 2D prolates, so we need to derive the expansion
-coefficients of the above bias terms in these functions for debiasing.
-
-To this end, writing (in the continuous case again)
-\[ \delta(\Bell - \Bell_2) =
-\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Bell)
-\overline{\psi_{k,q_2}(\Bell_2)},\]
-we get
-\[\begin{aligned}
-\mathfrak{d}(k,q_1,q_2) &= \int_{\Bell,
-	\Bell_2}\delta(\Bell-\Bell_2)\overline{\psi_{k,q_1}(\Bell_1)}\psi_{k,q_2}(\Bell_2)\\
-&=
-\int_{\Bell_2}\overline{\psi_{k,q_1}(\Bell_2)}\psi_{k,q_2}(\Bell_2)\\
-&= \delta_{q_1,q_2}.
-\end{aligned}\]
-
-Similarly, writing
-\[ \delta(\Bell_1) =
-\sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
-\psi_{k,q_1}(\Bell_1) \overline{\psi_{k,q_2}(\Bell_2)},\]
-we get
-\[\begin{aligned} 
-\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Bell_1,
-	\Bell_2}\delta(\Bell_1)\overline{\psi_{k,q_1}(\Bell_1)}
-\psi_{k,q_2}(\Bell_2)\\
-&= \overline{\psi_{k,q_1}(\mb 0)}
-\int_{\Bell_2}\psi_{k,q_2}(\Bell_2)\\
-&= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
-&= \delta_{k,0} \frac{\alpha_{0,q_2}}{2\pi}R_{0,q_1}(0)R_{0,q_2}(0),
-\end{aligned}\]
-where we used the fact that $R_{0,q}$ satisfies
-\[ \frac{\alpha_{0,q}}{2\pi}R_{0,q}(r) =
-\int_0^1R_{0,q}(\rho)J_{0}(cr\rho)\rho\, d\rho,\]
-where $J_k$ is the Bessel function of the first kind, and that
-$J_0(0)=1$. 
-A similar derivation applies to $\delta(\Bell_2)$.
-
-Thus, in terms of the prolate expansion coefficients, our bias
-formulas become
-\[ \widetilde{\mathfrak{m}}_3(k,q_1,q_2) = \mathfrak{m}_3(k,q_1,q_2) +
-\sigma^2m_1[\widetilde \II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].\]
-
-Similarly, for the power spectrum we get
-\[ \widetilde{\mathfrak{m}}_2(q) = \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0).\]
+%\TODO{=========== Tamir: Stopped here ===============}
+
+%\TODO{=========== NOT SURE WHAT IS THAT ===============}
+%\begin{align*}
+%&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
+%&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+%&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
+%\end{align*}
+%and 
+%\begin{align*}
+%\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
+%\end{align*}
+
+%\subsection{Implementation details}
+%To implement the above formula, we precompute the quantities
+%\[ W(\ell_1,\ell_2,\ell_3,m_1,m_2) = (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right),\]
+%and
+%\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},\]
+%so in each iteration of the optimization we compute
+%\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) = \sum_{\substack{\ell_1,\ell_2,\ell_3\\m_1,m_2\\s_1,s_2,s_3}}& W(\ell_1,\ell_2,\ell_3,m_1,m_2)B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3)\times\\ &a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}} .\end{aligned}\]
+%
+%The Wigner 3$j$ symbols are computed from the Racah formula
+%\[\begin{aligned} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right) &= \delta_{m_3,m_1+m_2}(-1)^{\ell_1-\ell_2+m_3}\sqrt{\Delta(\ell_1,\ell_2,\ell_3)}\\ &\times \prod_{i=1}^3\sqrt{(\ell_i-m_i)!(\ell_i+m_i)!}\times \sum_{t}\frac{(-1)^t}{x(t)},\end{aligned}\]
+%where
+%\[ x(t) = t!(\ell_3-\ell_2+t+m_1)!(\ell_3-\ell_1+t-m_2)!(\ell_1+\ell_2-\ell_3+t)!(\ell_1-t-m_1)!(\ell_2-t+m_2)!,\]
+%the sum is over all integer $t$ for which the arguments in the factorials in $x(t)$ are all nonnegative, and 
+%\[ \Delta(\ell_1,\ell_2,\ell_3) = \frac{(\ell_1+\ell_2-\ell_3)!(\ell_1-\ell_2+\ell_3)!(-\ell_1+\ell_2+\ell_3)!}{(\ell_1+\ell_2+\ell_3+1)!}.\]
+%
+
+%\section{Noisy micrograph moments}
+%We now suppose that the micrograph is perturbed by additive white
+%Gaussian noise, so we observe $\widetilde \II = \II + \varepsilon$ where
+%$\varepsilon\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
+%to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
+%m_3[\widetilde\II]$. For simplicity of notation,
+%we shall use vectorized indices $\mb i = (i,j)$.
+%
+%
+%\subsection{Expansion in PSWFs}
+%In practice, we compute the moments of our noisy micrograph in a
+%product basis of 2D prolates, so we need to derive the expansion
+%coefficients of the above bias terms in these functions for debiasing.
+%
+%To this end, writing (in the continuous case again)
+%\[ \delta(\Bell - \Bell_2) =
+%\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Bell)
+%\overline{\psi_{k,q_2}(\Bell_2)},\]
+%we get
+%\[\begin{aligned}
+%\mathfrak{d}(k,q_1,q_2) &= \int_{\Bell,
+%	\Bell_2}\delta(\Bell-\Bell_2)\overline{\psi_{k,q_1}(\Bell_1)}\psi_{k,q_2}(\Bell_2)\\
+%&=
+%\int_{\Bell_2}\overline{\psi_{k,q_1}(\Bell_2)}\psi_{k,q_2}(\Bell_2)\\
+%&= \delta_{q_1,q_2}.
+%\end{aligned}\]
+%
+%Similarly, writing
+%\[ \delta(\Bell_1) =
+%\sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
+%\psi_{k,q_1}(\Bell_1) \overline{\psi_{k,q_2}(\Bell_2)},\]
+%we get
+%\[\begin{aligned} 
+%\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Bell_1,
+%	\Bell_2}\delta(\Bell_1)\overline{\psi_{k,q_1}(\Bell_1)}
+%\psi_{k,q_2}(\Bell_2)\\
+%&= \overline{\psi_{k,q_1}(\mb 0)}
+%\int_{\Bell_2}\psi_{k,q_2}(\Bell_2)\\
+%&= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
+%&= \delta_{k,0} \frac{\alpha_{0,q_2}}{2\pi}R_{0,q_1}(0)R_{0,q_2}(0),
+%\end{aligned}\]
+%where we used the fact that $R_{0,q}$ satisfies
+%\[ \frac{\alpha_{0,q}}{2\pi}R_{0,q}(r) =
+%\int_0^1R_{0,q}(\rho)J_{0}(cr\rho)\rho\, d\rho,\]
+%where $J_k$ is the Bessel function of the first kind, and that
+%$J_0(0)=1$. 
+%A similar derivation applies to $\delta(\Bell_2)$. 
+%
+%Thus, in terms of the prolate expansion coefficients, our bias
+%formulas become
+%\[ \widetilde{\mathfrak{m}}_3(k,q_1,q_2) = \mathfrak{m}_3(k,q_1,q_2) +
+%\sigma^2m_1[\widetilde \II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].\]
+%
+%Similarly, for the power spectrum we get
+%\[ \widetilde{\mathfrak{m}}_2(q) = \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0).\]
 

### 2018-08-28 pnas/Towards.tex
no message

@@
 In this section, we present a toy model which is studied in the next sections. 
-The role of this model is to introduce the mathematical principles enabling to estimate a signal in a low SNR regime, although its detection might be impossible.
+The role of this model is to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
 Later, we discuss how these principles can be carried through for the SPR problem.
@@
 
-Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data.
+Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where $N \gg L$.
 Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
@@
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
-As will be shown next, in the low SNR environment, estimating $s$ is impossible, where estimating $x$ is tractable under some conditions on $s$.
-
-The binary signals obey the following property:
-\begin{align} 
-\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
-\label{eq:spacing}
-\end{align}
+As will be shown next, in the low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
+
+We assume that the binary signals $s$ obey the following \emph{separation condition}: If $s[i] = 1$ and $s[j] = 1$  for  $i \neq j$, then $\vert i - j\vert \geq 2L-1$.
+%\begin{align} 
+%\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
+%\label{eq:spacing}
+%\end{align}
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
@@
 The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w$, satisfying the condition of~\eqref{eq:spacing}, we obtain our model.
+In the special case where $w$, satisfying the separation condition, we obtain our model.
 The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
@@
 
-Under the space constraint~\eqref{eq:spacing}, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
+Under the spacing constraint, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
 \begin{align}
@@
 \end{align}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-One simple observation is that the first-order autocorrelation of $y$ (its mean) is independent of the locations of $x$.
-Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\footnote{We did not fully specify a random generating model for the location vector $s$.
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint%~\eqref{eq:spacing} 
+imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+One simple observation is that the first-order\TODO{Will: I suggest making this statement about all the autocorrelations here, instead of singling out the mean first.
+I understand that the mean can be estimated without the separation condition, but this distinction is not very critical to highlight, and it's a little confusing to have this sentence (upon first reading, it might be interpreted to mean that the other autocorrelations do depend on s).
+I'd say something like: Under the separation condition on $s$, the autocorrelation functions of $y$ can be shown to depend only on the corresponding autocorrelations of $x$ and the parameter $gamma$, defined by...
+Then go into the details.} autocorrelation of $y$ (its mean) is independent of the locations of $x$.
+Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\TODO{Will: Instead of the footnote, just specify here that the randomness is over the Gaussian noise.
+s can be deterministic.
+The only thing we assume about s is that the associated parameter gamma is constant (you might also note that this can be relaxed, so long as the sequence of $\gamma_N$'s converges to gamma, but this point is not critical).}\footnote{We did not fully specify a random generating model for the location vector $s$.
 The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
@@
 \end{align*}
-We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers gives meaning to the following statement:
+We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers can be used to show the following statement:
 \begin{align} \label{eq:mean_micrograph}
@@
 
-The spacing constraint~\eqref{eq:spacing} gives rise to more powerful observations.
+The spacing condition gives rise to more powerful observations.
 Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
@@
 In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedures, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-Second, if the spacing condition~\eqref{eq:spacing} holds, then the length of the signal can be determined from the autocorrelations.
+Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
 %%%and therefore the assumption that the first and last entries are nonzero is met.
-In particular, if~\eqref{eq:spacing} holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+In particular, if the separation condition holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
 Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
@@
 To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with~\eqref{eq:spacing}.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition.
+%~\eqref{eq:spacing}.
 %The separation restriction is discussed in more details in the Methods Section.
@@
 Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
-The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}.
+The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition.% of~\eqref{eq:spacing}.
  Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
@@
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
+In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition.%~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 For the 1-D experiment depicted in Figure~\ref{fig:1D_example}, we used a signal of length $L=21$ and generated an observation $y$ of length $N = 10(2L-1)M$, where $M$ is the number of repetitions. 
-The observation was generated by randomly selecting placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far until reaching the desried number of signal occurences.
+The observation was generated by randomly selecting placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far until reaching the desired number of signal occurrences.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
@@
 \paragraph{3-D experiments.}
-For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK.
+
+For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK. To estimate the coefficients of the volume itself, we solve the LS problem
+\begin{equation} \label{eq:LS_cryo}
+\min_{\hat{x},\hat{\gamma}} w_1 \vert \mathfrak{a}_x^1 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^1 \vert^2 + w_2\| \mathfrak{a}_x^2 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^2 \|_2^2 + w_3\| \mathfrak{a}_x^3 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^3 \|_F^2,
+\end{equation}  
+where the explicit expressions of $\mathfrak{a}_x^1$, $\mathfrak{a}_x^2$ and $\mathfrak{a}_x^3$ are given in~\eqref{eq:ac_1_prolates},~\eqref{eq:ac_2_prolates} and~\eqref{eq:ac_3_prolates}, respectively.
+In the experiments, we set $w_1=w_2=w_3=1$.
+
+The LS was solved by TKTK. The expected $\hat \gamma$ is one.
+
+In the first experiment, we used \TODO{Bla bla bla, real valued volume}
+
+The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows \TODO{separation, etc.
+}.
+Then, the LS~\eqref{eq:LS_cryo} was solved with $L=0$ (low-resolution estimate).
 
@@
 where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$ and $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
-Similarly to~\eqref{eq:spacing}, we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction.
+%Similarly to~\eqref{eq:spacing},
+Again, we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction.
 Note that~\eqref{eq:model} can be also written as a sum of $\delta$ functions as in~\eqref{eq:micrograph_model}.
@@
 Recall that we obtain the autocorrelations of the volume in PSWFs coefficients; see~\eqref{eq:third_order_ac_pswf}. Hence, to conclude the derivation we expand
-\[ \langle a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega}= \sum_{k,q_1,q_2}\mathfrak{a}^3[k,q_1,q_2]\psi_{k,q_1}[\Bell_1]\overline{\psi_{k,q_2}[\Bell_2]},\]
+\[ \langle a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega}= \sum_{k,q_1,q_2}\mathfrak{a}_x^3[k,q_1,q_2]\psi_{k,q_1}[\Bell_1]\overline{\psi_{k,q_2}[\Bell_2]},\]
 where we only include the block-diagonal terms in the expansion; the rest are equal to zero. Let
@@
 the final formula reads
-\[\begin{aligned} &\mathfrak{a}^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
+\begin{align} \label{eq:ac_3_prolates}
+ &\mathfrak{a}_x^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\nonumber \\ \ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\\&\times\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
+&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\nonumber\\ N_1 & N_2 & -N_1-N2\end{array}\right)\nonumber\\&\times\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
+\nonumber
+\end{align}
+%
+%\[\begin{aligned} \label{eq:ac_3_prolates} &\mathfrak{a}_x^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
+%&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
+%&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\\&\times\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
 \end{aligned}\]
-In practice, the last two lines of the above expression for $\mathfrak{a}^3[k,q_1,q_2]$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
+In practice, the last two lines of the above expression for $\mathfrak{a}_x^3[k,q_1,q_2]$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
 
@@
 \[\left\langle a^2_{\hat{I}_{\omega}}(k,\theta)\right\rangle_{\omega} =
-\sum_{q}\mathfrak{a}_2(q)\psi_{0,q}(k),\]
+\sum_{q}\mathfrak{a}_x^2(q)\psi_{0,q}(k),\]
 and conclude that 
-\[ \mathfrak{a}^2[q] =
+\begin{equation} \label{eq:ac_2_prolates}
+\mathfrak{a}_x^2[q] =
 \frac{1}{\sqrt{8\pi}}\sum_{\substack{\ell,m\\s_1,s_2}}\tamir_{\ell,m,s_1}\overline{\tamir_{\ell,m,s_2}}
-\int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk.\]
+\int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk.
+\end{equation}
 The integral on $k$ is precomputed.
@@
 $Y_{0,0}(\theta,\varphi) = \frac{1}{\sqrt{4\pi}}$, we conclude from~\eqref{eq:volume_expansion_app} that
-\[ \langle
-a^1_{I_{\omega}}\rangle_{\omega} = \widehat \phi(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_s\tamir_{0,0,s}j_{0,s}(0).\]
+\begin{equation} \label{eq:ac_1_prolates}
+\mathfrak{a}_x^1 = \langle
+a^1_{I_{\omega}}\rangle_{\omega}  = \widehat  \phi(\mb 0) = \frac{1}{\sqrt{4\pi}}\sum_s\tamir_{0,0,s}j_{0,s}(0).
+\end{equation}
 

### 2018-08-28 pnas/Towards.tex
Including Will's comments

@@
 Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
-\TODO{TB: I think that this paragraph can be much shorter and it is sufficient to show only the second equation and remove footnote. Nicolas thinks otherwise. Need to be decided. }
+\TODO{TB: I think that this paragraph can be much shorter and it is sufficient to show only the second equation and remove footnote.
+Nicolas thinks otherwise.
+Need to be decided.
+Will: I agree the footnote is unnecessary and actually confusing, since s need not be random.}
 
@@
 
-If $x$ is known, then the support signal $s$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}.
+If $x$ is known, then the support signal $s$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}.
 However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible.
@@
 	%
-	Let $z\in\RL$ and suppose that $z[0]$ and $z[L-1]$ are nonzero. Then $z$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+	 A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
 \end{proposition}
@@
 First, \eqref{eq-uniqueness} is not numerically stable if $z[0]$ or $z[L-1]$ are close to 0.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedures, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
@@
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, where $M=M_N$ grows with $N$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, \TODO{Will: Earlier, you defined gamma in the finite sample case; now it's the limit.
+These should be made consistent.} where $M=M_N$ grows with $N$.
 We will show, however, that $x$ is still identifiable from the observed moments of $y$.
@@
 For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-lies in the vanishing locus of a nonzero polynomial\footnote{Given a  nonzero polynomial $f$ in $T$ variables (real or complex), the vanishing locus of $f$ is the set 
-	$V(f) = \{(x_1, \ldots, x_T) \in \mathbb{R}^T (\text{resp.
+lies in a set with Lebesgue measure zero. 
+%in the vanishing locus of a nonzero polynomial\footnote{Given a  nonzero polynomial $f$ in $T$ variables (real or complex), the vanishing locus of $f$ is the set 
+%	$V(f) = \{(x_1, \ldots, x_T) \in \mathbb{R}^T (\text{resp.
 } \mathbb{C}^T) \vert f(x_1,\ldots x_T)=0\}$.
@@
 almost all signals with the given measurements.
-%
+%%
 %we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
@@
 		\item Either the signal $x$ is generic; or
-		\item  Both $x[0]$  and $x[L-1]$ are nonzero, $x$ has nonzero mean, and $\gamma\geq\frac{L}{4(L-1)}$.
+		\item   $x$ has nonzero mean  and $\gamma\geq\frac{L}{4(L-1)}$.
 	\end{itemize}
@@
 
-The technique we advocate allow to recover a signal hidden in noisy micrographs without (even implicitly) detecting the location of signal repetitions in these micrographs.
-To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for a simulated cryo-EM data.
+The technique we advocate allows recovery of a signal hidden in noisy micrographs without (even implicitly) \TODO{Will: What does this mean?} detecting the location  of the signals embedded in these micrographs.
+To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.
 Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
 
-%it is instructive to start with a toy model where the target signal is an unknown 2-D image.
-The latter appears several times in noisy micrographs, at unknown locations.
-Toward recovery, we first compute the second-order autocorrelation of the micrographs.
-We then establish that the autocorrelation of the target image can be recovered from the autocorrelation of the micrographs in a straightforward manner.
-The more micrographs we collect, the more accurate the estimate of the image's autocorrelation.
-%The target image is then estimated from its autocorrelation using a standard inversion algorithm (up to elementary symmetries).
-%The same principles carry over to the more challenging task of 3-D reconstruction from micrographs.
-%The Methods Section provides additional details.
-
-In the first experiment, we estimated Einstein's image of size $50\times 50$ and mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
-A micrograph contains, on average, 700 occurrences of the target image at random locations.
+In the first experiment, we estimated 
+an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+Each micrograph contains, on average, 700 occurrences of the target image at random locations.
 Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$ (this corresponds to SNR$\approx1/375$).
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
 This high noise level is illustrated in Figure~\ref{fig:micro_example}.
@@
 
-We also showed how this technique can be, in principle, applied to cryo-EM.
+We also showed how this technique can, in principle, be applied to cryo-EM.
 Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
 Concerns for model bias are also greatly reduced since no template matching is involved.
-Additionally,  our technique also allows to use much lower defocus values.
+Additionally,  our technique also allows the use of much lower defocus values.
 Lower defocus means lower contrast, but will maintain  higher frequency information.
-From that perspective, we may be able to get high resolution reconstructions from fewer micrographs.
-%, just because we would be using lower defocus.
-
-Looking towards applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, in particular, molecules that are too small to be detected in micrographs.
+Consequently, we may be able to get high resolution reconstructions from fewer micrographs.
+
+Looking towards applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
 In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
@@
 
-One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR is an interesting research question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
-Still, large amounts of data also imply large amounts of computations.
+One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
+Still, large amounts of data also require large amounts of computation.
 On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in streaming mode, as only one look at each micrograph is necessary.
+It can even be done in streaming mode, as only one pass through each micrograph is necessary.
 The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
@@
 \TODO{Is it?}
-
-%Insofar as the computational challenges are concerned, we note that expectation-maximization algorithms (EM) have, over time, become the norm in the cryo-EM community, as exemplified by the popular RELION package.
-The idea of using EM for cryo-EM can be traced back at least to~\TODO{Sigworth}.
-At the time, such approaches also seemed challenging.
-
-%\TODO{Do we want to say something about the number of images that we need?
-Specifically, do we want to address the fact that the numerical experiments suggest we may need a gigantic number of them for cryo, and mention trends in cryo technology that are encouraging in that regard?
-(Of course, we can't compare to RELION etc.\ in SNRs so low that one can't particle pick; that's not the point here.)}
 
@@
 Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
-We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph. 
+We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.\TODO{Will: Is this really enough?
+I think the main issue is what happens when particles can collide (or maybe even overlap), since this introduces additional cross-terms for the moment-fitting problem.}
 Such a condition can be met in practice by careful experimental design.
 
-%Alternatively, if the signals are not well separated, one can introduce new parameters which encode the distribution of the spacing between occurrences.
-Here as well, relations between autocorrelations of the micrographs and of the volume could be derived.
-
-We also note several aspects of SPR experiments that were neglected in this paper, including Contrast Transfer Function (CTF) correction, non-uniformity of the viewing directions and other contaminants in the micrographs, such as ice crystals.
+We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformity of the viewing directions \TODO{We never talk about viewing directions at all, so it's strange to mention that non-uniformity is an issue.
+I think this is confusing.
+I'd say something like: "relating the observed autocorrelations to the autocorrelations of the 3-D volume" or something like that.} and other contaminants in the micrographs, such as ice crystals.
  All these aspects must be taken into account so the method could be applied on real data.

### 2018-08-28 pnas/Towards.tex
Afternoon session

@@
 Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
 
@@
 Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-Error is measured as the ratio of the root mean square error (RMSE) to the norm of the ground truth (square root of the sum of squared pixel intensities).
 This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
@@
 
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[scale=0.7]{Einstein_progress_examples}
+\begin{figure*}[h]
+	\centering
+	\begin{subfigure}[h]{0.24\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{Einstien_progress_1}
+		\caption{$5\times 10^2$ micrographs}
+	\end{subfigure} 
+	\begin{subfigure}[h]{0.24\textwidth}
+	\centering
+	\includegraphics[scale=0.35]{Einstien_progress_10}
+	\caption{$5\times 10^3$ micrographs}
+\end{subfigure} 
+	\begin{subfigure}[h]{0.24\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{Einstien_progress_100}
+		\caption{$5\times 10^4$ micrographs}
+	\end{subfigure} 
+	\begin{subfigure}[h]{0.24\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{Einstien_progress_246}
+		\caption{$500\times 246$ micrographs}
+	\end{subfigure}
 	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
+This does not require particle picking.
+A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
+Estimates are obtained from $5\times 10^2,5\times 10^3,5\times 10^4$ micrographs (growing across panels), each containing $700$ image occurrences on average.
+\TODO{XP is still running}}
+\end{figure*}
+
+%\begin{figure*}[h!]
+%	\centering
+%	\includegraphics[scale=0.7]{Einstein_progress_examples}
+%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
 Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
@@
 Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-		%\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
-		% At a noise level of $\sigma = 3$, this amounts to an SNR of $1/20$.
-	}
-\end{figure*}
+%		%\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
+%		% At a noise level of $\sigma = 3$, this amounts to an SNR of $1/20$.
+%	}
+%\end{figure*}
 
@@
 	\centering
-	\includegraphics[scale=.55]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
-	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
+\begin{subfigure}[h]{0.23\textwidth}
+	\centering
+	\includegraphics[scale=0.33]{Einstein_ps_error}
+	\caption{relative power spectrum estimation error}
+\end{subfigure} 
+\begin{subfigure}[h]{0.23\textwidth}
+	\centering
+	\includegraphics[scale=0.33]{Einstein_recovery_error}
+	\caption{relative recovery error}
+\end{subfigure} 
+	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example} \TODO{XP is still running}}
 \end{figure}
+
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[scale=.55]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
+%	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
+%\end{figure}
 
@@
 We hope to take care of these issues in future research, as well to extend the proposed method to conformational heterogeneity.
-%\TODO{another issue is that micrographs also contain contaminants such as carbon, ice crystals, etc.. }
-
-%\TODO{Where and how do we cite Kam? Fred?}
 

### 2018-08-29 pnas/Towards.tex
some edits to introduction

@@
 
-\dropcap{C}ryo--electron microscopy (cryo--EM) is an innovative technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise first sentence}
+\dropcap{C}ryo--electron microscopy (cryo--EM) is an leading technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise first sentence}
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. %Within the ice, the molecules are randomly oriented and positioned.
@@
 The smaller the molecules, the fewer detected electrons carry information about them.
+\TODO{This isn't quite accurate: it's about the density of particles in the image; but we want to make a point about size; how do we reconcile this?}
 
@@
 This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
+In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
 \begin{quote}
@@
 In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-Joachim Frank voices a similar observation in his Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2\times $  Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
+Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
 \TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
@@
 
-As a proof of concept, we study a toy model for which it is easier to convey the mathematical principles. 
+As a proof of concept, we study
+\TODO{This sentence beginning makes it sound like what follows is our main point; should the main point be the 3D recovery, even if low-res?}
+a toy model for which it is easier to convey the mathematical principles. 
 In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
@@
 The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
-This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+This problem is interesting of its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
@@
 The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-These directly yield estimates for the autocorrelations of the image \TODO{Will: This is not quite true, because of the gamma parameter}.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
 To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
 
-Autocorrelation analysis for 3-D reconstruction, under the assumption of perfect particle picking,  was first proposed by Zvi Kam~\cite{kam1980reconstruction}. 
-In this work, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions.
+Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
+Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked particles.
+In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
 We show a few numerical examples and outline the future developments required to make this method applicable on real data.
-\TODO{This paragraph would be changed according to the final results we will show}
+\TODO{This paragraph will be changed according to the final results we will show}
 
@@
 
-In this section, we present a toy model which is studied in the next sections. 
-The role of this model is to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
-Later, we discuss how these principles can be carried through for the SPR problem.
-The model is formulated for 1-D signals to ease exposition.
+In this section, we present a toy model in order to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
+Later, we discuss how these principles carry through for the SPR problem.
+We here formulate the model for 1-D signals to ease exposition.
 

### 2018-08-29 pnas/Towards.tex
Two Gaussians proof

@@
 $
-%\begin{align*}
-%a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-%\end{align*}
-%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
-%
-%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
-%\begin{align}
-%\gamma & = \frac{M L}{N}
-%\end{align}
-%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
 
@@
 However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible. 
-\TODO{Here we need to provide Will's argument as a proposition}
-
-%We have few evidences for that\cite{aguerrebere2016fundamental}, but we will provide Will's argument here.
-
-Accordingly, we must consider methods that aim to estimate the signal directly, without estimating the nuisance variables as an intermediate step. 
+To prove this argument, we consider an even easier problem, in which someone hands us intervals of length $L$ that either contain the full signal plus noise, or contain just noise, and we are asked to determine which intervals contain signal.
+Let us assume too that we know the signal $x$, that we know the probability $q$ that one of the intervals contains a signal, and that we know the noise variance $\sigma^2$.
+Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.
+
+Let us abstract this problem.
+We have two known vectors $\theta_0$ and $\theta_1$ in $\mathbb{R}^L$.
+There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
+We observe a random vector $X \in \mathbb{R}^L$ with the following distribution: $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words, if $\eta = 0$, then $X \sim N(\theta_0,\sigma^2)$, and if $\varepsilon  = 1$, then $X \sim N(\theta_1,\sigma^2)$.
+If $\theta_1=0$, then the latter corresponds to pure noise interval.
+
+We observe $X$, and our task is to predict $\eta$.
+How well can we do it?
+First, let us assume without loss of generality that $q \ge 1/2$.
+Then, if we make the constant prediction $\hat{\eta } \equiv 0$, we will be correct with probability $q$.
+So the question is, can we do better than this?
+We will prove that as $\sigma \to \infty$, the answer is no.
+More precisely:
+\begin{proposition} \label{prop:two_gauss}
+	Let $\hat{\eta }$ be any predictor of $\eta$.
+	%
+	\begin{align*}
+	%
+	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] \le q.
+	%
+	\end{align*}
+\end{proposition}
+\noindent The result is proved in Appendix~\ref{sec:proof_two_gauss}.
+
+Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal in low SNR  we must consider methods that aim to estimate the signal directly, without estimating the nuisance variables as an intermediate step.
  %we need to consider a different approach. In this paper, we consider autocorrelation analysis.
@@
 Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
-%%%and therefore the assumption that the first and last entries are nonzero is met.
 In particular, if the separation condition holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
@@
 lies in a set with Lebesgue measure zero. 
-%in the vanishing locus of a nonzero polynomial\footnote{Given a  nonzero polynomial $f$ in $T$ variables (real or complex), the vanishing locus of $f$ is the set 
-%	$V(f) = \{(x_1, \ldots, x_T) \in \mathbb{R}^T (\text{resp.
-} \mathbb{C}^T) \vert f(x_1,\ldots x_T)=0\}$.
-By a general result in algebraic geometry $\dim V(f) < T$.
-As a consequence the complement of $V(f)$ in $\mathbb{R}^T$ (resp.
-$\mathbb{C}^T$) is dense.}.
 In particular, this means that we can recover
 almost all signals with the given measurements.
-%%
-%we mean that it holds for all $x$ inside a set $\Omega \subset \RL$, whose complement $\RL \setminus \Omega$ has Lebesgue measure zero.
-%
+
 \begin{proposition} \label{prop:gamma_sigma}
@@
 This completes the proof.
+
+\section{Proof of Proposition~\ref{prop:two_gauss}} \label{sec:proof_two_gauss}
+
+The proof is based on  a variant of the Neyman-Pearson Lemma to derive the best (deterministic) predictor $\hat{\eta}$.
+We take any predictor $\hat{\eta}$, and we let $S$ be the set of $X$'s where $\hat{\eta} = 1$.
+Then the probability that $\hat{\eta}$ fails is:
+%
+\begin{align}
+\label{eq:neyman-pearson}
+%
+\P[\hat{\eta} \ne \eta] 
+&= q \P_0[\hat{\eta} = 1 ] + (1-q) \P_1[\hat{\eta} = 0]
+\nonumber \\
+&= q \P_0[\hat{\eta} = 1] + (1-q) (1 - \P_1[\hat{\eta} = 1])
+\nonumber \\
+&= q \P_0[\hat{\eta} = 1] + (1-q) - (1-q) \P_1[\hat{\eta} = 1]
+\nonumber \\
+&= (1-q)  + \int_S (q f_0(x) - (1-q) f_1(x))dx,
+%
+\end{align}
+%
+where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$, and the notation $\P_i$ means probability conditional on the event $\eta = \theta_i$; that is, $\P_i[A] = \P[A | \eta=i]$.
+Let $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$,
+The best predictor of $\eta$ based on $X$ will minimize the integral~\eqref{eq:neyman-pearson} and thus \TODO{Tamir: Are we sure this is the best?}
+%
+% is minimized by taking $S$ to be the set:
+%%
+%\begin{align}
+%%
+%S = \left\{x : \frac{f_0(x)}{f_1(x)} \le \frac{1-q}{q} \right\}.
+%%
+%\end{align}
+%%
+%In other words, if $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, then the best predictor of $\eta$ based on $X$ is:
+%
+\begin{align}
+%
+\eta = 
+\begin{cases}
+1,  \text{ if } \Lambda(x) \le b \\
+0,  \text{ if } \Lambda(x) \ge b
+\end{cases}.
+%
+\end{align}
+
+Taking logarithms, the set $S$ can be rewritten as the set of $x$ where:
+\begin{align*}
+%
+-\| x - \theta_0\|^2 \le - \|x - \theta_1\|^2 + 2 \sigma^2 \log(b),
+%
+\end{align*}
+%
+or equivalently
+%
+\begin{align*}
+%
+\langle x , \theta_1 - \theta_0 \rangle 
+\ge \frac{\|\theta_1\|^2 - \|\theta_0\|^2}{2} - \sigma^2 \log(b).
+%
+\end{align*}
+%
+
+Now let us compute the probability of failure conditional on the event $\eta = 0$.
+In this case, failure occurs when $X \in S$.
+Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,1)$.
+Consequently,
+%
+\begin{align*}
+%
+\langle X , \theta_1 - \theta_0 \rangle 
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
++ \langle \theta_0,\theta_1 - \theta_0 \rangle
+\nonumber \\
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
++ \langle \theta_0,\theta_1 \rangle - \|\theta_0\|^2,
+%
+\end{align*}
+%
+and failure occurs when 
+%
+\begin{align}
+%
+\sigma\langle Z, \theta_1 - \theta_0 \rangle 
+&\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
+- \sigma^2 \log(b)
+\nonumber \\
+&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b)
+%
+\end{align}
+%
+or equivalently
+%
+\begin{align*}
+%
+Y \ge \frac{c}{\sigma} - \sigma^2 \log(b)
+%
+\end{align*}
+%
+where $c = \|\theta_1 - \theta_0\|^2 / 2$ and $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$. 
+Just for simplicity let us assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$. So:
+%
+\begin{align*}
+%
+\P_0[\hat{\eta} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right],
+\quad Y \sim N(0,1).
+%
+\end{align*}
+%
+Similarly,
+%
+\begin{align*}
+%
+\P_1[\hat{\eta} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right],
+\quad Y \sim N(0,1).
+%
+\end{align*}
+%
+So the overall probability of failure is:
+%
+\begin{align*}
+%
+\P[\hat{\eta} \ne \eta]
+&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
+\\&+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right].
+%
+\end{align*}
+%
+Now, if $q = 1/2$, then $\log(b) = 0$. Hence the probability of failure is simply:
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} \right] \longrightarrow \frac{1}{2} = q
+\quad \text{as} \quad \sigma \to \infty.
+%
+\end{align}
+
+On the other hand, if $q > 1-q$, then $\log(b) < 0$. Then 
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right] \longrightarrow 0
+%
+\end{align}
+%
+while
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right] \longrightarrow 1
+%
+\end{align}
+%
+as $\sigma \to \infty$. Consequently,
+%
+\begin{align}
+%
+\P[\hat{\eta} \ne \eta]
+&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
++ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
+\nonumber\\
+& \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
+%
+\end{align}
+%
+That is, the probability of success converges to $q$, which completes the proof.
 
@@
 
-\section{Connection to volume}
+\subsection{Connection to volume}
 

### 2018-08-29 pnas/Towards.tex
Edits to section 1

--- 2018-08-29 pnas/Towards.tex
@@
 Later, we discuss how these principles carry through for the SPR problem.
-We here formulate the model for 1-D signals to ease exposition.
-
-Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where $N \gg L$.
+We first formulate the model for 1-D signals to ease exposition.
+
+Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where $N$ is assumed far larger than $L$.
 Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
@@
 where $\ast$ denotes linear convolution. 
-While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$ (this is a key difference with other works on sparse blind deconvolution, e.g.~\cite{zhang2018structured}).
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
-As will be shown next, in the low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
+As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
 
@@
 
-Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
+Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
+%system identification
+forward model takes the form
 %
@@
 %
-where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
+where $x$ is the unknown signal (the system's impulse response), $w$ is an unknown (often random) input sequence, and $\varepsilon$ is an additive noise.
 The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w$, satisfying the separation condition, we obtain our model.
+In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
 The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
@@
 In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
-The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
-However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.
+The EM method for discrete $w$ is based on a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
+However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets.
 %Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
@@
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-Following this approach, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and study it in Section~\ref{sec:theory}.
+Building on such ideas, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and study it in Section~\ref{sec:theory}.
 

### 2018-08-29 pnas/Towards.tex
Just before implementing Will's suggestions in Section 2

@@
 Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
-However, exploiting the separation constraint on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
+However, exploiting the separation condition on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
 %
@@
 
-In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-\begin{align}
-a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\begin{align}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
 \label{eq:ac_general}
@@
 
-Under the spacing constraint, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple.
+Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
 It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
@@
 \end{align}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint%~\eqref{eq:spacing} 
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
 imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
@@
 
-The spacing condition gives rise to more powerful observations.
+The separation condition gives rise to more powerful observations.
 Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
@@
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
-an accept/reject rule based on the separation constraint and locations picked so far.
+an accept/reject rule based on the separation condition and locations picked so far.
 On average, $700$ images are placed in each micrograph.   
@@
 For the 1-D experiment depicted in Figure~\ref{fig:1D_example}, we used a signal of length $L=21$ and generated an observation $y$ of length $N = 10(2L-1)M$, where $M$ is the number of repetitions. 
-The observation was generated by randomly selecting placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far until reaching the desired number of signal occurrences.
+The observation was generated by randomly selecting placements in $y$, one at a time with an accept/reject rule based on the separation condition and locations picked so far until reaching the desired number of signal occurrences.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
@@
 Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
-%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation condition and locations picked so far.
 For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.

### 2018-08-29 pnas/Towards.tex
Edits to Section 2

@@
 
-One simple observation is that the first-order\TODO{Will: I suggest making this statement about all the autocorrelations here, instead of singling out the mean first.
-I understand that the mean can be estimated without the separation condition, but this distinction is not very critical to highlight, and it's a little confusing to have this sentence (upon first reading, it might be interpreted to mean that the other autocorrelations do depend on s).
-I'd say something like: Under the separation condition on $s$, the autocorrelation functions of $y$ can be shown to depend only on the corresponding autocorrelations of $x$ and the parameter $gamma$, defined by...
-Then go into the details.} autocorrelation of $y$ (its mean) is independent of the locations of $x$.
-Since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:\TODO{Will: Instead of the footnote, just specify here that the randomness is over the Gaussian noise.
-s can be deterministic.
-The only thing we assume about s is that the associated parameter gamma is constant (you might also note that this can be relaxed, so long as the sequence of $\gamma_N$'s converges to gamma, but this point is not critical).}\footnote{We did not fully specify a random generating model for the location vector $s$.
-The expectation is still well defined specifically because the quantity under consideration is independent of $s$ under the assumptions.}
+Under the separation condition on $s$,  for shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend only on the corresponding autocorrelations of $x$ and the parameter $\gamma$.
+In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
 \begin{align*}
@@
 \end{align*}
+(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
 We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers can be used to show the following statement:
@@
 \end{align}
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
-\TODO{TB: I think that this paragraph can be much shorter and it is sufficient to show only the second equation and remove footnote.
-Nicolas thinks otherwise.
-Need to be decided.
-Will: I agree the footnote is unnecessary and actually confusing, since s need not be random.}
-
-The separation condition gives rise to more powerful observations.
-Consider the second-order autocorrelation in particular: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$.
+(We show later how to estimate $\gamma$ as well.) We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
 Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
 As a result,
-\begin{align} \label{eq:ac2_micrograph}
+\begin{align}
 	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
+	\label{eq:ac2_micrograph}
 \end{align}
@@
 Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{align} \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), 
+\begin{align}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph}\\ & \quad + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
  \nonumber
@@
 Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
+
+\TODO{Nico: At this point in the paper, the reader will want to here about recovering $x$ from its moments.
+That's not what happens: the next section is called theory (a bit too vague); it discusses two things: one is the impossibility of getting $s$, another is whether we can get $x$, $\gamma$, $\sigma$.
+I propose to split that section in two, and to lead with the recovery part (which is interesting to more people, I expect.)}
 

### 2018-08-29 pnas/Towards.tex
Edits to Section 3 and mostly to Appendix C (impossibility of estimating s)

@@
 \keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
+
+\renewcommand{\P}{\mathrm{Prob}}
 
@@
 However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible. 
-To prove this argument, we consider an even easier problem, in which someone hands us intervals of length $L$ that either contain the full signal plus noise, or contain just noise, and we are asked to determine which intervals contain signal.
-Let us assume too that we know the signal $x$, that we know the probability $q$ that one of the intervals contains a signal, and that we know the noise variance $\sigma^2$.
-Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.
-
-Let us abstract this problem.
-We have two known vectors $\theta_0$ and $\theta_1$ in $\mathbb{R}^L$.
+To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us intervals of length $L$ in the micrograph that either contain a full signal occurrence (plus noise), or contain just noise.
+Our task is to determine which intervals contain signal, that is, to determine whether the corresponding entries of $s$ are 0 or 1.
+The oracle further provides the signal $x$, the probability $q$ that one of the intervals contains signal, and the noise variance $\sigma^2$.
+\TODO{Nico: I don't see how the next sentence is relevant for the task of estimating $s$---Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.---I would just write this: Since the intervals are independent of each other, it is sufficient to consider a single interval.}
+
+The decision problem for a single interval can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
 There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
-We observe a random vector $X \in \mathbb{R}^L$ with the following distribution: $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words, if $\eta = 0$, then $X \sim N(\theta_0,\sigma^2)$, and if $\varepsilon  = 1$, then $X \sim N(\theta_1,\sigma^2)$.
-If $\theta_1=0$, then the latter corresponds to pure noise interval.
-
-We observe $X$, and our task is to predict $\eta$.
-How well can we do it?
-First, let us assume without loss of generality that $q \ge 1/2$.
-Then, if we make the constant prediction $\hat{\eta } \equiv 0$, we will be correct with probability $q$.
-So the question is, can we do better than this?
-We will prove that as $\sigma \to \infty$, the answer is no.
-More precisely:
+We observe a random vector $X \in \mathbb{R}^L$ (an interval) with the following distribution:
+% $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words,
+if $\eta = 0$, then $X \sim N(\theta_0,\sigma^2)$ (that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$), and if $\eta = 1$, then $X \sim N(\theta_1,\sigma^2)$.
+%If $\theta_1=0$, then the latter corresponds to pure noise interval.
+
+We observe $X$, and our task is to estimate $\eta$.
+How reliably can this be done?
+If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise for $\hat{\eta} = 1$ if $q \leq 1/2$, correct with probability $1-q$.
+The question is, can we do better than this?
+We prove that, as $\sigma \to \infty$, the answer is no.
 \begin{proposition} \label{prop:two_gauss}
-	Let $\hat{\eta }$ be any predictor of $\eta$.
-	%
-	\begin{align*}
-	%
-	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] \le q.
-	%
+	Let $\hat{\eta }$ be any estimator of $\eta$; then:
+	\begin{align*}
+		\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q).
 	\end{align*}
@@
 
-The proof is based on  a variant of the Neyman-Pearson Lemma to derive the best (deterministic) predictor $\hat{\eta}$.
-We take any predictor $\hat{\eta}$, and we let $S$ be the set of $X$'s where $\hat{\eta} = 1$.
-Then the probability that $\hat{\eta}$ fails is:
+The proof is based on  a variant of the Neyman--Pearson Lemma to derive the best (deterministic) estimator $\hat{\eta}$.
+We take any estimator $\hat{\eta}$, and we let $S$ be the set of $X$'s where $\hat{\eta} = 1$.
+We write $\P_i$ to mean the probability conditional on the event $\eta = i$; that is, $\P_i[A] = \P[A | \eta = i]$.
+Then, the probability that $\hat{\eta}$ fails is:
 %
@@
 %
-where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$, and the notation $\P_i$ means probability conditional on the event $\eta = \theta_i$; that is, $\P_i[A] = \P[A | \eta=i]$.
-Let $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$,
-The best predictor of $\eta$ based on $X$ will minimize the integral~\eqref{eq:neyman-pearson} and thus \TODO{Tamir: Are we sure this is the best?}
-%
-% is minimized by taking $S$ to be the set:
-%%
-%\begin{align}
-%%
-%S = \left\{x : \frac{f_0(x)}{f_1(x)} \le \frac{1-q}{q} \right\}.
-%%
-%\end{align}
-%%
-%In other words, if $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, then the best predictor of $\eta$ based on $X$ is:
-%
-\begin{align}
-%
-\eta = 
+where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$. 
+The best estimator of $\eta$ based on $X$ minimizes the failure probability; hence, it minimizes the integral in~\eqref{eq:neyman-pearson} through an appropriate choice of the set $S$.
+This is achieved as follows:
+\begin{align}
+%
+%S & = \left\{x : \frac{f_0(x)}{f_1(x)} \leq \frac{1-q}{q} \right\}.
+S & = \left\{x : qf_0(x) \leq (1-q)f_1(x) \right\}.
+%
+\end{align}
+%
+%In other words, if $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, then the best estimator of $\eta$ based on $X$ is:
+%
+With $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, the corresponding estimator is:
+\begin{align}
+%
+\hat{\eta} = 
 \begin{cases}
-1,  \text{ if } \Lambda(x) \le b \\
-0,  \text{ if } \Lambda(x) \ge b
-\end{cases}.
-%
-\end{align}
-
-Taking logarithms, the set $S$ can be rewritten as the set of $x$ where:
+1  \text{ if } \Lambda(x) \leq b, \\
+0  \text{ if } \Lambda(x) > b.
+\end{cases}
+%
+\end{align}
+Taking logarithms, the set $S$ can be rewritten as the set of $x$'s where:
 \begin{align*}
@@
 %
-
 Now let us compute the probability of failure conditional on the event $\eta = 0$.
@@
 Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,1)$.
-Consequently,
+On that condition,
 %
@@
 \nonumber \\
-&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b)
-%
-\end{align}
-%
-or equivalently
-%
-\begin{align*}
-%
-Y \ge \frac{c}{\sigma} - \sigma^2 \log(b)
-%
-\end{align*}
-%
-where $c = \|\theta_1 - \theta_0\|^2 / 2$ and $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$. 
-Just for simplicity let us assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$. So:
-%
-\begin{align*}
-%
-\P_0[\hat{\eta} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right],
+&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b).
+%
+\end{align}
+%
+Define $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$ and divide through by $\sigma$. The above event is equivalent to:
+%
+\begin{align*}
+%
+Y \ge \frac{c}{\sigma} - \sigma \log(b),
+%
+\end{align*}
+%
+where $c = \|\theta_1 - \theta_0\|^2 / 2$. 
+For simplicity, let us assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$. Then, 
+%
+\begin{align*}
+%
+\P_0[\hat{\eta} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right],
 \quad Y \sim N(0,1).
@@
 %
-\P_1[\hat{\eta} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right],
+\P_1[\hat{\eta} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right],
 \quad Y \sim N(0,1).
@@
 %
-So the overall probability of failure is:
-%
-\begin{align*}
-%
-\P[\hat{\eta} \ne \eta]
-&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
-\\&+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right].
-%
-\end{align*}
+Thus, the overall probability of failure is:
+%
+\begin{multline*}
+%
+\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \\
+  + (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
+%
+\end{multline*}
 %
@@
 \end{align}
-
-On the other hand, if $q > 1-q$, then $\log(b) < 0$. Then 
-%
-\begin{align}
-%
-\P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right] \longrightarrow 0
+If $q > 1/2$, then $q > 1-q$ and $\log(b) < 0$. Consequently, 
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \longrightarrow 0
 %
@@
 %
-\P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right] \longrightarrow 1
-%
-\end{align}
-%
-as $\sigma \to \infty$. Consequently,
+\P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right] \longrightarrow 1
+%
+\end{align}
+%
+as $\sigma \to \infty$. Hence,
 %
@@
 \P[\hat{\eta} \ne \eta]
-&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
-+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
-\nonumber\\
+%&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
+%+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
+%\nonumber\\
 & \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
@@
 \end{align}
-%
-That is, the probability of success converges to $q$, which completes the proof.
+That is, the probability of success converges to $q$.
+Finally, if $q < 1/2$, then $\log(b) > 0$ and a similar reasoning shows the probability of success converges to $1-q$.
+In all cases, the probability of success of the best possible deterministic estimator converges to $\max(q, 1-q)$.
 

### 2018-08-29 pnas/Towards.tex
few more edits to Section 3

@@
 The question is, can we do better than this?
-We prove that, as $\sigma \to \infty$, the answer is no.
+We prove that, as $\sigma \to \infty$, the answer is no:
 \begin{proposition} \label{prop:two_gauss}
-	Let $\hat{\eta }$ be any estimator of $\eta$; then:
-	\begin{align*}
-		\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q).
-	\end{align*}
+	For any deterministic estimator $\hat{\eta }$ of $\eta$,
+	\begin{align*}
+		\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q),
+	\end{align*}
+	that is: the probability of success is no better than random chance in the limit of infinitely poor SNR.
 \end{proposition}
@@
  %we need to consider a different approach. In this paper, we consider autocorrelation analysis.
-  In what follows, we present several results on properties of autocorrelations. For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.
+  In what follows, we present several results on properties of autocorrelations.
+\TODO{For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
 

### 2018-08-29 pnas/Towards.tex

@@
 
-We assume that the binary signals $s$ obey the following \emph{separation condition}: If $s[i] = 1$ and $s[j] = 1$  for  $i \neq j$, then $\vert i - j\vert \geq 2L-1$.
-%\begin{align} 
-%\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
-%\label{eq:spacing}
-%\end{align}
+We assume the binary signal $s$ obeys a \emph{separation condition}:
+%% Nicolas: this is too important: it must stand out
+% If $s[i] = 1$ and $s[j] = 1$  for  $i \neq j$, then $\vert i - j\vert \geq 2L-1$.
+\begin{align} 
+\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{align}
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
@@
 Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-Building on such ideas, in the next section we present an autocorrelation analysis for~\eqref{eq:model} and study it in Section~\ref{sec:theory}.
-
-\section{Autocorrelation analysis} \label{sec:AC_analysis}
-
-In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-\begin{align}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
-\label{eq:ac_general}
-\end{align}
-where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-Explicitly, the first-, second- and third-order autocorrelations are given by \TODO{we may want to remove these explicit formulas}
-\begin{align} 
-a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-$
-
-Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
-\begin{align}
-\gamma & = \frac{M L}{N}
-\end{align}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
-imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-Under the separation condition on $s$,  for shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend only on the corresponding autocorrelations of $x$ and the parameter $\gamma$.
-In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
-\begin{align*}
-\E\{ a_y^1 \} & = \gamma a_x^1.
-\end{align*}
-(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
-We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers can be used to show the following statement:
-\begin{align} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
-\end{align}
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$.
-(We show later how to estimate $\gamma$ as well.) We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
-As a result,
-\begin{align}
-	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
-	\label{eq:ac2_micrograph}
-\end{align}
-for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
-The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
-Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{align}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph}\\ & \quad + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
- \nonumber
-\end{align}
-for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
-Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
-
-\TODO{Nico: At this point in the paper, the reader will want to here about recovering $x$ from its moments.
-That's not what happens: the next section is called theory (a bit too vague); it discusses two things: one is the impossibility of getting $s$, another is whether we can get $x$, $\gamma$, $\sigma$.
-I propose to split that section in two, and to lead with the recovery part (which is interesting to more people, I expect.)}
-
-\section{Theory} \label{sec:theory}
-
-If $x$ is known, then the support signal $s$ can be estimated via linear programming  in the high SNR regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
-However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible. 
+Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.
+% and study it in Section~\ref{sec:recovery}.
+
+\section{The detection limit} \label{sec:detectionlimit}
+
+At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
+However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
+
 To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us intervals of length $L$ in the micrograph that either contain a full signal occurrence (plus noise), or contain just noise.
@@
 There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
-We observe a random vector $X \in \mathbb{R}^L$ (an interval) with the following distribution:
+We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution:
 % $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words,
@@
 	\begin{align*}
-		\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q),
-	\end{align*}
-	that is: the probability of success is no better than random chance in the limit of infinitely poor SNR.
+	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q);
+	\end{align*}
+	that is: as the SNR deteriorates, the probability of success is no better than random chance.
 \end{proposition}
@@
 
-Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal in low SNR  we must consider methods that aim to estimate the signal directly, without estimating the nuisance variables as an intermediate step.
- %we need to consider a different approach. In this paper, we consider autocorrelation analysis.
-  In what follows, we present several results on properties of autocorrelations.
-\TODO{For simplicity, we consider one-dimensional signals, but the results carry through for higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, since $z[0]$ and $z[L-1]$ are nonzero by definition, we have the formula:
-%
-\begin{align} \label{eq-uniqueness}
-%
-z[k] = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
-%
-\end{align}
-In particular, we have proven the following proposition:
+Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
+%we need to consider a different approach.
+In the next sections, % Nicolas: sections is plural on purpose
+we consider autocorrelation analysis for that purpose.
+%In what follows, we present several results on properties of autocorrelations.
+
+\section{Autocorrelation analysis} \label{sec:AC_analysis}
+
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\begin{align}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
+Explicitly, the first-, second- and third-order autocorrelations are given by: \TODO{we may want to remove these explicit formulas}
+\begin{align} 
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$
+
+Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
+\begin{align}
+	\gamma & = \frac{M L}{N}
+	\label{eq:gamma}
+\end{align}
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
+imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+Under the separation condition on $s$,  for shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend only on the corresponding autocorrelations of $x$, the density $\gamma$ and the noise level $\sigma$.
+In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
+\begin{align*}
+\E\{ a_y^1 \} & = \gamma a_x^1.
+\end{align*}
+(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
+
+We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers can be used to show the following statement:
+\begin{align} \label{eq:mean_micrograph}
+\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
+\end{align}
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+
+We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
+As a result,
+\begin{align}
+	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
+	\label{eq:ac2_micrograph}
+\end{align}
+for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
+The last part captures the autocorrelation of the noise.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
+
+Along the same lines, one can establish a relation for third-order autocorrelations:
+\begin{multline}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] = \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
+\end{multline}
+for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
+Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
+
+Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
+
+\section{Recovering a signal from autocorrelations} \label{sec:recovery}
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
+Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
+%
+\begin{align}
+%
+z[k] & = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+\label{eq-uniqueness}
+%
+\end{align}
+This proves the following useful fact:
 \begin{proposition} \label{prop:uniqueness}
@@
 Some remarks are in order.
-First, \eqref{eq-uniqueness} is not numerically stable if $z[0]$ or $z[L-1]$ are close to 0.
+First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
 In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
-In particular, if the separation condition holds for some spacing $W\geq L$, then $a_z^2[i]=0$ for all $i>L-1$.
+In particular, if the separation condition holds \TODO{for some spacing $W\geq L$---Nico: what is this?}, then $a_z^2[i] = 0$ for all $i > L-1$.
 Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (phase for the complex signals) and reflection through the origin (with conjugation in the complex case).
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case).
 %~\cite{hayes1982reconstruction,hayes1982reducible}.
@@
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately give the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma = \lim_{N\to\infty}ML/N$, \TODO{Will: Earlier, you defined gamma in the finite sample case; now it's the limit.
-These should be made consistent.} where $M=M_N$ grows with $N$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
 We will show, however, that $x$ is still identifiable from the observed moments of $y$.
@@
 
-First, we observe that if the noise level $\sigma$ is known, one can estimate $\gamma$ from the first two moments of the observed vector.
+First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
 %
 \begin{proposition} \label{prop:gamma}
-	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
-	%
-	\begin{equation*}
-	%
-	\gamma = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2} \quad \text{a.s.}
-	%
-	\end{equation*}
+	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then  \TODO{Where does the `almost surely' come from?}
+	%
+	\begin{align*}
+	%
+	\gamma & = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{\ell = 0}^{L-1}a_y^2[\ell]-\sigma^2}, \quad \text{almost surely.}
+	%
+	\end{align*}
+	\TODO{Nico: I do not get the same formula when I plug things in.}
 	%
@@
 \begin{proof}
-	The proof follows from plugging the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
+	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
 \end{proof}
@@
 For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-lies in a set with Lebesgue measure zero. 
+lies in a set \TODO{with Lebesgue measure zero.---Nico: I don't think we should use such words in a PNAS paper.}
 In particular, this means that we can recover
@@
 \end{corollary}
+
+\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
 
@@
 		The true value of $\gamma$ is $0.0512$.
-		   The relative errors of $\gamma$ for the three panels are: $27.1\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$.
+		   The relative errors of $\gamma$ for the three panels are: $27.1\%,4\%,1.2\%$.
+The right panel shows the relative error as a function of $M$.
+\TODO{Nico: relative error should be logscale?
+Also, let's pick other colors; if we're running this again anyway, let's also aim for M being powers of 10 in all displayed cases?}
 	}
@@
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs. }	
+		The noise realization is identical in both micrographs. \TODO{The excerpts should be squares: use `axis equal;' -- also, what's going on with the diagonal line on the right panel?}}
 \end{figure*}
@@
 
-We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this. We assume $M_N$ grows proportionally with $N$, and define:
+We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this.
+We assume $M_N$ grows proportionally with $N$, and define: \TODO{---Nico: the paper now no longer references $M_N$ and defines $\gamma$ 'as is' for given $M$ and $N$; may want to adapt things here as a result.
+It wouldn't make sense to make $M_N$ appear in the paper I think, as it just makes things more complicated.
+In a sense, much of this beginning of appendix is just repeating things we already said cleanly in the paper: let's just follow up from that.}
 %
@@
 In this section we prove relation~\eqref{eq:ac_micrographs}.
-We note that mathematically taking infinitely many micrographs is equivalent to take one infinitely large micrograph with fixed density $\gamma$~\eqref{eq:gamma}.
+We note that mathematically taking infinitely many micrographs is equivalent to taking one infinitely large micrograph with fixed density $\gamma$~\eqref{eq:gamma}.
 Hence, we consider the moments of one micrograph $\II$ in the limit $N\to\infty$ and  $\gamma = \lim_{N\to\infty}\frac{MP^2}{N^2}\in(0,1)$.

### 2018-08-30 pnas/Towards.tex
Updated 3-D experiments and cryo derivations

@@
 
-For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK. To estimate the coefficients of the volume itself, we solve the LS problem
+\TODO{Fill in refs to eqns.} For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK.
+To estimate the coefficients of the volume itself, we solve the LS problem
 \begin{equation} \label{eq:LS_cryo}
@@
 
-The LS was solved by TKTK. The expected $\hat \gamma$ is one.
-
-In the first experiment, we used \TODO{Bla bla bla, real valued volume}
-
-The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows \TODO{separation, etc.
-}.
-Then, the LS~\eqref{eq:LS_cryo} was solved with $L=0$ (low-resolution estimate).
+The LS problem was solved using Matlab's \texttt{lsqnonlin} solver for nonlinear least-squares problems. The expected $\hat \gamma$ in this experiment is one.
+
+The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB)~\cite{pdb} as 1QLQ.
+We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
+
+The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows.
+We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in QR, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE \cite{aspire}.
+We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension.
+We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
+Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
 
@@
 We assume that molecule is real-valued and smooth. In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form 
-\be\label{eq:volume_expansion} 
-\widehat \phi(k, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),
-\ee
-where $Y_{\ell}^m$ are complex spherical harmonics and $j_{\ell,s}$ are normalized spherical Bessel functions; see Appendix TKTK for further definitions.
+\begin{equation} \label{eq:volume_expansion_app} 
+\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
+\end{equation}
+%\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell}^m(\kk/k),\quad k\leq 1,\]
+%where $k=||\kk||_2$, 
+where $c$ is the bandlimit, $\{S_l\}$ are determined using the Nyquist criterion as descirbed in \cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
+\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
+$j_{\ell}$ is the spherical Bessel function of order $\ell$ and  $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$. We use 
+the complex spherical harmonics $Y_{\ell}^m$ defined by  
+\[ Y_{\ell}^m(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
+where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
+Sampling at the Nyquist-rate dictates $c=1/2$~\cite{levin20173d}. 
+Because $\phi$ is real-valued, so $\widehat \phi$ is conjugate-symmetric, the expansion coefficients satisfy $\tamir_{\ell, -m, s} = (-1)^{\ell+m}\overline{\tamir_{\ell,m,s}}$, and hence we only need to recover coefficients $\tamir_{\ell, m, s}$ with $m\geq 0$.
 Let $I_{\omega}$ denote the tomographic projection obtained from viewing direction $\omega\in SO(3)$.
@@
 \widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),\ee
-where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix.
+where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix. This implies that the projections are also $c$-bandlimited.
 
@@
 \begin{equation*} \label{eq:Kth_autocorrelation}
-a^p_\II(\Bell_1,\ldots, \Bell_{p-1}) = \frac{1}{N^2}\sum_{\mb i}\II[\Bell]\II([\mb i+\Bell]_1)\cdots \II([\mb i+\Bell]_{p-1}),
+a^p_\II[\Bell_1,\ldots, \Bell_{p-1}] = \frac{1}{N^2}\sum_{\mb i}\II[\Bell]\II[\mb i+\Bell_1]\cdots \II[\mb i+\Bell_{p-1}],
 \end{equation*}
@@
 In this section we prove relation~\eqref{eq:ac_micrographs}.
-We note that mathematically taking infinitely many micrographs is equivalent to taking one infinitely large micrograph with fixed density $\gamma$~\eqref{eq:gamma}.
+We note that mathematically taking infinitely many micrographs is equivalent to take one infinitely large micrograph with fixed density $\gamma$.
 Hence, we consider the moments of one micrograph $\II$ in the limit $N\to\infty$ and  $\gamma = \lim_{N\to\infty}\frac{MP^2}{N^2}\in(0,1)$.
@@
 Below, we start with $p=2$.
-The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by
+The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by \footnote{A different normalization is used in \cite{landa2017steerable}.}
 \begin{align}
@@
 \end{align}
-\TODO{Ref eq. 8 in Boris' paper}
-where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are  scaling factors which will be defined in the next section.
+
+where the range of $k,q$ is determined by Eq.~(8) in \cite{landa2017steerable}, the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are  scaling factors which will be defined in the next section.
 The PSWFs are orthogonal on the unit disk.
@@
 \sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{equation}
-where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
+where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. 
 Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
@@
 
-Finally, we treat the bias terms, using approximate orthonormality \TODO{!} of the discretized PSFWs:
+Finally, we treat the bias terms:
 \begin{align*}
@@
 
-\subsection{Connection to volume}
+\section{Connection to volume}
 
@@
 
-We start by some preliminary computations. Let us  expand the Fourier transform of the volume as
-\begin{equation} \label{eq:volume_expansion_app} 
-\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
-\end{equation}
-%\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
-%where $k=||\kk||_2$, 
-\TODO{How do we choose $S(\ell)$?}where $c$ is the bandlimit, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
-\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
-$j_{\ell}$ is the spherical Bessel function of order $\ell$ and  $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$. We use 
-the complex spherical harmonics $Y_{\ell}^m$ defined by  
-\[ Y_{\ell,m}(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
-where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
-Sampling at the Nyquist-rate dictates $k\in[0,1/2]$~\cite{levin20173d}. \TODO{Didn't we say that $k\leq 1$?} With this notation, 
-the Fourier transform of a  projection taken from the viewing direction $\omega\in SO(3)$ can be written as 
-\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta}.\]
-%whenever $k\leq 1$. 
-%where $D_{m',m}^{\ell}$ is the Wigner D-matrix.
-
-Recall that the PSWFs are the solution of the integral equation \TODO{To mention the range of $\mb r$?} 
-\begin{equation}
-\label{eq:PSWF_defn_eq}
-\alpha_{N,n}\psi_{N,n}(\mb k) = \int_{\mb r} \psi_{N,n}(\mb r)e^{\iota c(\mb r\cdot\mb k)}d\mb r,
-\end{equation}
-%\begin{equation}
-%\label{eq:PSWF_defn_eq}
-%\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
-%\end{equation}
-and are given explicitly by \TODO{Do we use this normalization?}
-\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{\iota N\theta},\]
-where $R_{N,n}(k)$ is a solution to another integral equation~\cite{landa2017steerable}. 
-Let us assume that $I_{\omega}$ has bandlimit $c$ and is concentrated in the unit ball in real space. 
 Using the 2-D PSWFs, we can express each projection as 
-%Express this in 2D PSWFs so %\TODO{Eitan: I stopped here}
 \[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}(\omega)\psi_{N,n}(k,\theta),\]
-%where in papers the 2D PSWFs are defined as
-%\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
-%%but in Boris' code the expansion is actually performed with respect to
-%\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
-%where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below. 
-%
-%We then get
 where
-\[\begin{aligned} b_{N,n}(\omega) &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
-&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
+\[\begin{aligned} b_{N,n}(\omega) &= \frac{4}{\sqrt{2\pi}|\alpha_{N,n}|^2}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
+&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{2\sqrt{2\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
 &= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
@@
 \begin{equation} \label{eq:beta}
-\beta_{\ell,s;N,n} := \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|\\ 0, & \ell<|N|\end{array}\right.,
+\beta_{\ell,s;N,n} := \left\{\begin{array}{ll} \frac{2\sqrt{2\pi}}{\alpha_{N,n}}Y_{\ell}^{N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|\\ 0, & \ell<|N|\end{array}\right.,
 \end{equation}
 can be precomputed.
-Since the PSWFs are eigenfunctions of the truncated Fourier operator~\eqref{eq:PSWF_defn_eq}, we can now express the projection in real space as
+Since the PSWFs are eigenfunctions of the truncated Fourier transform~\cite{landa2017steerable} and hence satisfy 
+\begin{equation}
+\label{eq:PSWF_defn_eq}
+\alpha_{N,n}\psi_{N,n}(\mb k) = \int\limits_{||\mb r||_2\leq 1} \psi_{N,n}(\mb r)e^{\iota c(\mb r\cdot\mb k)}d\mb r,
+\end{equation} 
+we can now express the projection in real space as
 \begin{align} \label{eq:proj_expansion}
@@
 \end{align}
-\TODO{How do we choose $n_{max}$?}where $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$.
+where $n_{max}(N)$ is chosen according to Eq.~(8) in \cite{landa2017steerable}, $\alpha_{N,n}$ is the eigenvalue corresponding to the $(N,n)$th PSWF, $\widehat{\alpha}_{N,n} = (c/2\pi)^2\alpha_{N,n}$, and $\widehat\beta_{\ell,s;N,n}=\widehat\alpha_{N,n}\beta_{\ell,s;N,n}$.
 
@@
 
-The third-order autocorrelation of the volume can be expressed in terms of~\eqref{eq:proj_expansion}:\TODO{What about the $\hat\alpha$ coefficients?}
+The third-order autocorrelation of the volume can be expressed in terms of~\eqref{eq:proj_expansion}:
 \begin{align} \label{eq:third_order_ac_volume}
@@
 \[\begin{aligned} \langle &b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} \\&= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\\&\times \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
-&\times \beta_{\ell_1,s_1;N_1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
+&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
 where the latter coefficients are given explicitly in~\eqref{eq:beta}. Using standard properties of D-Wigner functions, we obtain  
@@
 &\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\nonumber\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\nonumber\\
-&\times \beta_{\ell_1,s_1;N1,n_1}\beta_{\ell_2,s_2;N_2,n_2}\overline{\beta_{\ell_3,s_3;N_1+N2,n_3}}. \nonumber
+&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_1+N_2,n_3}}. \nonumber
 \end{align}
@@
 \begin{align*}
-\Psi_{\ell,N,s}[\Bell] &:= \sum_{n=0}^{n_{\text{max}}(N)}\beta_{\ell,s;N,n}\psi_{N,n}[\Bell],\\ 
+\Psi_{\ell,N,s}[\Bell] &:= \sum_{n=0}^{n_{\text{max}}(N)}\widehat\beta_{\ell,s;N,n}\psi_{N,n}[\Bell],\\ 
 \rho_{\ell,N,s}^{(k,q)}&:=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
@@
 %\[ \widehat V(k,\theta,\varphi) =
-%\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell,m}(\theta,\varphi)j_{\ell,s}(k),\]
+%\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),\]
 Since $j_{\ell,s}(0) = 0$ unless $\ell=0$, and since

### 2018-08-30 pnas/Towards.tex
New figures and small modifications

@@
 		\includegraphics[scale=0.35]{Einstien_progress_1}
-		\caption{$5\times 10^2$ micrographs}
+		\caption{$500$ micrographs}
 	\end{subfigure} 
@@
 	\centering
-	\includegraphics[scale=0.35]{Einstien_progress_10}
-	\caption{$5\times 10^3$ micrographs}
+	\includegraphics[scale=0.35]{Einstien_progress_4}
+	\caption{$2\times 10^3$ micrographs}
 \end{subfigure} 
@@
 		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_100}
-		\caption{$5\times 10^4$ micrographs}
+		\includegraphics[scale=0.35]{Einstien_progress_40}
+		\caption{$2\times 10^4$ micrographs}
 	\end{subfigure} 
@@
 		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_246}
-		\caption{$500\times 246$ micrographs}
+		\includegraphics[scale=0.35]{Einstien_progress_400}
+		\caption{$2\times 10^5$ micrographs}
 	\end{subfigure}
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $5\times 10^2,5\times 10^3,5\times 10^4$ micrographs (growing across panels), each containing $700$ image occurrences on average.
+Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.
 \TODO{XP is still running}}
@@
 	\centering
-\begin{subfigure}[h]{0.23\textwidth}
-	\centering
-	\includegraphics[scale=0.33]{Einstein_ps_error}
-	\caption{relative power spectrum estimation error}
-\end{subfigure} 
-\begin{subfigure}[h]{0.23\textwidth}
-	\centering
-	\includegraphics[scale=0.33]{Einstein_recovery_error}
-	\caption{relative recovery error}
-\end{subfigure} 
-	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example} \TODO{XP is still running}}
+	\includegraphics[scale=0.28]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
 \end{figure}
+
+%\begin{figure}[h]
+%	\centering
+%\begin{subfigure}[h]{0.25\textwidth}
+%	\centering
+%	\includegraphics[scale=0.33]{Einstein_ps_error}
+%	\caption{relative power spectrum estimation error}
+%\end{subfigure} 
+%\begin{subfigure}[h]{0.25\textwidth}
+%	\centering
+%	\includegraphics[scale=0.33]{Einstein_recovery_error}
+%	\caption{relative recovery error}
+%\end{subfigure} 
+%	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example}}
+%\end{figure}
 
@@
 %
-\begin{align}
+\begin{align*}
 %
@@
 %
-\end{align}
+\end{align*}
 %
@@
   + (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
-%
+%\
 \end{multline*}

### 2018-08-30 pnas/Towards.tex
no message

@@
 Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the SNR degrades.
-
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{quote}
-	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-\end{quote}
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
-\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
-
-The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-Despite this progress, detecting small molecules in the micrographs remains a challenge.
-We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
-Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
-\TODO{Need a ref for this claim.}
-
-In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-
-As a proof of concept, we study
-\TODO{This sentence beginning makes it sound like what follows is our main point; should the main point be the 3D recovery, even if low-res?}
-a toy model for which it is easier to convey the mathematical principles. 
-In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image.
-The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
-This problem is interesting of its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
-Importantly, there is no need to detect individual image occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
-
-Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
-Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked particles.
-In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
-We show a few numerical examples and outline the future developments required to make this method applicable on real data.
-\TODO{This paragraph will be changed according to the final results we will show}
-
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
-In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
-This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
-%
-
-\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
-%
 
@@
 \end{figure*}
+
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
+This fact has been recognized early on by the cryo-EM community.
+In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
+\begin{myquote}{0.15in}
+	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
+Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
+\end{myquote}
+%\begin{quote}
+%	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
+Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
+%\end{quote}
+In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
+Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
+\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
+
+The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+Despite this progress, detecting small molecules in the micrographs remains a challenge.
+We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
+Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
+\TODO{Need a ref for this claim.}
+
+In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
+Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
+Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
+Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+
+As a proof of concept, we study
+\TODO{This sentence beginning makes it sound like what follows is our main point; should the main point be the 3D recovery, even if low-res?}
+a toy model for which it is easier to convey the mathematical principles. 
+In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+The goal is to estimate the planted image.
+The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
+This problem is interesting of its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
+Importantly, there is no need to detect individual image occurrences.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
+To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
+
+Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
+Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
+In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
+We show a few numerical examples and outline the future developments required to make this method applicable on real data.
+
+Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
+In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
+In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
+This model bias is common to all particle picking methods based on template matching.
+In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
+%
+
+\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
+%
 

### 2018-08-30 pnas/Towards.tex
Added results for TRPV1

@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[angle=270, width=0.3\textwidth]{TRPV1_rec.eps}
+    \caption{Reconstruction of the TRPV1 molecule from its clean first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
+    \label{fig:TRPV1_recon}
+\end{figure*}
+
 \section{Discussion}
@@
 We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
+We also present a reconstruction of TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB)~\cite{emdb} as EMD-8117.
+The original map has size $192^3$, and we downsample it to size $20^3$.
+To generate the ground truth for our reconstructions, we expanded both volumes as in \eqref{eq:volume_expansion_app} with cutoff $L = 5$.
+For the TRPV1 reconstruction, the optimizer converged to a point giving relative $\ell_2$ error of $10^{-6}$ in the first three autocorrelations and an error of $10^{-1}$ in the expansion coefficients of the volume.
+Similarly, \TODO{Fill details for BPTI}.
+This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.
 

### 2018-08-30 pnas/Towards.tex
no message

--- 2018-08-30 pnas/Towards.tex
@@
 where $\ast$ denotes linear convolution. 
-While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$ (this is a key difference with other works on sparse blind deconvolution, e.g.~\cite{zhang2018structured}).
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
+This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
@@
 In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
-The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+%The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
 

### 2018-08-30 pnas/Towards.tex
no message

@@
 % $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words,
-if $\eta = 0$, then $X \sim N(\theta_0,\sigma^2)$ (that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$), and if $\eta = 1$, then $X \sim N(\theta_1,\sigma^2)$.
+if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2)$ (that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$), and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2)$.
+\TODO{Tamir: to remove parenthesis}
 %If $\theta_1=0$, then the latter corresponds to pure noise interval.
@@
 The question is, can we do better than this?
-We prove that, as $\sigma \to \infty$, the answer is no:
+\TODO{to rephrase} We prove that, as $\sigma \to \infty$, the answer is no:
 \begin{proposition} \label{prop:two_gauss}

### 2018-08-30 pnas/Towards.tex
no message

--- 2018-08-30 pnas/Towards.tex
@@
 The smaller the molecules, the fewer detected electrons carry information about them.
-\TODO{This isn't quite accurate: it's about the density of particles in the image; but we want to make a point about size; how do we reconcile this?}
+\TODO{This isn't quite accurate.
+Amit: do you agree with the last sentence?
+maybe we should say it is a function of the contrast?}
 
@@
 
-As a proof of concept, we study
-\TODO{This sentence beginning makes it sound like what follows is our main point; should the main point be the 3D recovery, even if low-res?}
-a toy model for which it is easier to convey the mathematical principles. 
+As a proof of concept, we first study a toy model \TODO{Amit: do you want to keep ``toy model'' or replace with ``mathematical toy model'', ``simplified model'' etc.} for which it is easier to convey the mathematical principles.
 In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
@@
 
-To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us intervals of length $L$ in the micrograph that either contain a full signal occurrence (plus noise), or contain just noise.
-Our task is to determine which intervals contain signal, that is, to determine whether the corresponding entries of $s$ are 0 or 1.
-The oracle further provides the signal $x$, the probability $q$ that one of the intervals contains signal, and the noise variance $\sigma^2$.
-\TODO{Nico: I don't see how the next sentence is relevant for the task of estimating $s$---Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.---I would just write this: Since the intervals are independent of each other, it is sufficient to consider a single interval.}
-
-The decision problem for a single interval can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
+To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise.
+Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
+The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.
+%\TODO{Nico: I don't see how the next sentence is relevant for the task of estimating $s$---Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.---I would just write this: Since the intervals are independent of each other, it is sufficient to consider a single interval.}
+
+This decision problem can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
 There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
@@
 % $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words,
-if $\eta = 0$, then $X \sim N(\theta_0,\sigma^2)$ (that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$), and if $\eta = 1$, then $X \sim N(\theta_1,\sigma^2)$.
+if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2)$ %(that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$),
+ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2)$. %\TODO{Tamir: to remove parenthesis}
 %If $\theta_1=0$, then the latter corresponds to pure noise interval.
@@
 How reliably can this be done?
-If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise for $\hat{\eta} = 1$ if $q \leq 1/2$, correct with probability $1-q$.
+If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise, if $q \leq 1/2$, the constant estimator $\hat{\eta} = 1$ is correct with probability $1-q$.
 The question is, can we do better than this?
@@
 
-Under the separation condition on $s$,  for shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend only on the corresponding autocorrelations of $x$, the density $\gamma$ and the noise level $\sigma$.
-In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
-\begin{align*}
-\E\{ a_y^1 \} & = \gamma a_x^1.
-\end{align*}
-(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
-
-We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density.) In that regime, the law of large numbers can be used to show the following statement:
+For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
+Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
+%In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
+%\begin{align*}
+%\E\{ a_y^1 \} & = \gamma a_x^1.
+%\end{align*}
+%(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
+We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density).
+In that regime, the law of large numbers can be used to show the following statement:
 \begin{align} \label{eq:mean_micrograph}
@@
 \end{align}
+The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
 Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
@@
 We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$), and never with another occurrence.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$)\TODO{Tamir: remove parenthesis}, and never with another occurrence.
 As a result,
 \begin{align}
-	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell]
+	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
 	\label{eq:ac2_micrograph}
@@
 
-\begin{figure*}
+\begin{figure}
     \centering
-    \includegraphics[angle=270, width=0.3\textwidth]{TRPV1_rec.eps}
+    \includegraphics[angle=270, width=0.4\textwidth]{TRPV1_rec.eps}
     \caption{Reconstruction of the TRPV1 molecule from its clean first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
     \label{fig:TRPV1_recon}
-\end{figure*}
+\end{figure}
 

### 2018-08-31 pnas/Towards.tex
Updated 2D figure

@@
 \begin{align} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1.
-\end{align}
+\lim_{N\to\infty} a_y^1 & \aseq \gamma a_{x}^1,
+\end{align}
+where equality holds almost surely (a.s.), meaning it holds with probability one.
 The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
@@
 We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself (with the same shift $\ell$)\TODO{Tamir: remove parenthesis}, and never with another occurrence.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
 As a result,
 \begin{align}
-	\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
+	\lim_{N\to\infty} a_y^2[\ell] & \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
 	\label{eq:ac2_micrograph}
@@
 \begin{multline}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] = \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
 \end{multline}
@@
 Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
-In particular, if the separation condition holds \TODO{for some spacing $W\geq L$---Nico: what is this?}, then $a_z^2[i] = 0$ for all $i > L-1$.
+In particular, if  $a_y^2[L-i] = 0$ for $i=1,\ldots,T$,
+then the support of $x$ has length $L-T$ rather than $L$. 
+%the separation condition holds 
+%\TODO{for some spacing $W\geq L$---Nico: what is this?}, then $a_z^2[i] = 0$ for all $i > L-1$.
 Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
@@
 \begin{proposition} \label{prop:gamma}
-	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then  \TODO{Where does the `almost surely' come from?}
-	%
-	\begin{align*}
-	%
-	\gamma & = \lim_{N \to \infty}\frac{(a^1_y)^2}{\sum_{\ell = 0}^{L-1}a_y^2[\ell]-\sigma^2}, \quad \text{almost surely.}
-	%
-	\end{align*}
-	\TODO{Nico: I do not get the same formula when I plug things in.}
+	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
+	%
+	\begin{align*}
+	%
+	\gamma & \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	%
+	\end{align*}
 	%
@@
 \begin{proof}
-	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
+In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}x[i]x[j]$.
+Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
+The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
+%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
 \end{proof}
@@
 For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-lies in a set \TODO{with Lebesgue measure zero.---Nico: I don't think we should use such words in a PNAS paper.}
+lies in a set with Lebesgue measure zero. 
 In particular, this means that we can recover
@@
 
-\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
+%
+%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
 
@@
 
-The technique we advocate allows recovery of a signal hidden in noisy micrographs without (even implicitly) \TODO{Will: What does this mean?} detecting the location  of the signals embedded in these micrographs.
+The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
 To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.
@@
 To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition.
-%~\eqref{eq:spacing}.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
 %The separation restriction is discussed in more details in the Methods Section.
@@
 As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-\TODO{Tamir: the experiment is currently running; should be ready tomorrow  (Aug 28).}
 
@@
 Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
-The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition.% of~\eqref{eq:spacing}.
+The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}. 
 Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
-Crucially, the LS does not require the knowledge of $\sigma$.
+Crucially, the LS does not require  knowledge of $\sigma$.
 
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-\TODO{XP is still running}}
+Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}
 \end{figure*}
@@
 \TODO{Nico: relative error should be logscale?
-Also, let's pick other colors; if we're running this again anyway, let's also aim for M being powers of 10 in all displayed cases?}
+Also, let's pick other colors; if we're running this again anyway, let's also aim for M being powers of 10 in all displayed cases?
+To run with logspace(3,7,9).
+We can remove the x-axis}
 	}
@@
 In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume.
-Figure~TKTK shows recovery of the 3-D volume from the clean autocorrelations.
+Figure~\ref{fig:cryo_detection} shows recovery of the 3-D volume from the clean autocorrelations.
 The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
@@
 This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
-Figure~\ref{fig:cryo_detection} presents excerpts \TODO{sections?} of two noisy micrographs, only one of which contains projections.
+Figure~\ref{fig:cryo_detection} presents excerpts  of two noisy micrographs, only one of which contains projections.
 In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
-On the hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
+On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
 %
@@
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs. \TODO{The excerpts should be squares: use `axis equal;' -- also, what's going on with the diagonal line on the right panel?}}
+		The noise realization is identical in both micrographs. \TODO{The excerpts should be squares: use `axis equal;' -- also, what's going on with the diagonal line on the right panel?} To start }
 \end{figure*}
@@
 
-\TODO{First and foremost, we need to mention the sensitivity of the third moment and whether the fourth moment is enough}
-%As a result, it may not be limited to large molecules in the same way that particle picking approaches are. 
-%In this paper, we illustrated that it is possible to determine the 3-D molecular structure in single particle cryo-EM directly from the micrographs without performing particle picking, at least in controlled experiments.
-
-%
-%\TODO{
-%	We should also incorporate Alberto's comment that our technique also allows to use much lower defocus values.
-Lower defocus means lower contrast, but will maintain higher frequency information.
-From that perspective, we may be able to get high resolution reconstructions from fewer micrographs, just because we would be using lower defocus.
-}
-
-%All current algorithmic pipelines for SPR using cryo--EM start with a particle picking algorithm which is prone to model bias. 
-%Bypassing the particle picking stage and constructing a 3-D model directly from the data---without assuming prior knowledge on the particle to be estimated---can be used to reconstruct ab initio models to initialize a refinement algorithm.
-Alternatively, it can be applied to generate templates for a particle picker which does not suffer from model bias.
-
-%In the simplified model we examined, the aim is to estimate one, or possibly several, images from micrographs.
-Our strategy is to compute autocorrelation functions of the data and to relate these statistics to the unknown parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
-%
-
-%Depending on the scenario, we did so using either a phase retrieval algorithm or a nonlinear least-squares algorithm.
-
-%
-%The same general approach can, in principle, be applied directly to SPR from cryo-EM.
-Here, the micrographs contain numerous tomographic projections of molecules (possibly in different conformations) taken from unknown viewing directions.
-The aim is to estimate the 3-D volumes of the different conformations directly from micrographs.
-Each volume can be expanded linearly in a basis, so that the volume is characterized by its expansion coefficients.
-Since tomographic projection is a linear operation, autocorrelations of the micrographs (which can be estimated easily) are polynomial functions of the sought coefficients.
-Thus, autocorrelations of the micrographs provide a system of polynomial equations in the volume parameters, and the question becomes: are these equations sufficient to uniquely identify the volumes, and can we solve the system?
-%
-%We show in Appendix~\ref{sec:cryoem} that the number of polynomial equations provided by the third-order autocorrelations is of the same order as the number of coefficients required to describe one volume \TODO{at resolution comparable to that of the particle projections---remove?}.
-This hints that it may be possible to reconstruct one or even several distinct volumes from these equations directly.
-Additional parameters in these equations could encode an unknown viewing direction distribution and an unknown conformation distribution, which could then also be estimated.
-Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation or conformation clustering.
-As a result, it may not be limited to large molecules in the same way that particle picking approaches are.
-Concerns for model bias would also greatly be reduced.
-
-%While the field is currently dominated by Bayesian methods such as EM, they are intractable for such problems.
-As an alternative, we propose to use autocorrelation analysis technique that shares some common lines (did you get the wordplay?)  with Kam's method for ab initio modeling~\cite{kam1980reconstruction,levin20173d,singer2018mathematics}.
-That being said, the SPR model is far more complicated than the model presented here.
-In a future research, we hope to bridge this gap.
-
-One possible concern is that the numerical experiments conducted here suggest a large amount of data may be necessary.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.} Recent trends in high-throughput cryo-EM technology \TODO{?} give hope that this may be a lesser concern in the long term.
+The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
+This suggests that fourth-order autocorrelation may be necessary.
+This in turn would imply that the procedure might require a large amount of data.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.} Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
 Still, large amounts of data also require large amounts of computation.
@@
 It can even be done in streaming mode, as only one pass through each micrograph is necessary.
-The output of this data processing stage is a succinct summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
+The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
 Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
 Of course, an important question then is whether the equations can be solved meaningfully in practice.
-The proof-of-concept experiments above suggest they might.
+%The proof-of-concept experiments above suggest they might.
 \TODO{Is it?}
@@
 
-We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformity of the viewing directions \TODO{We never talk about viewing directions at all, so it's strange to mention that non-uniformity is an issue.
-I think this is confusing.
-I'd say something like: "relating the observed autocorrelations to the autocorrelations of the 3-D volume" or something like that.} and other contaminants in the micrographs, such as ice crystals.
+We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformly distributed viewing directions and other contaminants in the micrographs, such as ice crystals.
  All these aspects must be taken into account so the method could be applied on real data.
-We hope to take care of these issues in future research, as well to extend the proposed method to conformational heterogeneity.
+We hope to take care of these issues in future research, as well as to extend the proposed method to conformational heterogeneity.
 

### 2018-08-31 pnas/Towards.tex
no message

@@
 
-For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generate $P$ micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we place Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition.%~\eqref{eq:spacing}.  
+For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated micrographs of size $4096\times 4096$ pixels. 
+In each micrograph, we placed Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition.%~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 On average, $700$ images are placed in each micrograph.   
-Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an SNR of approximately $1/375$.
+Then, i.i.d.\ Gaussian noise with standard deviation $\sigma=3$ is added, inducing an SNR of approximately $1/370$.
 An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
@@
 
-In this experiment, we assume we know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
+In this experiment, we assume to know the noise level $\sigma$ and the total number of occurrences of the target image across all micrographs.
 In stark contrast with the 1-D setup, the second-order autocorrelation determines almost any target image uniquely, up to reflection through the origin.
@@
 \begin{align*}
-z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z))
+z & \leftarrow z + \beta (P_2(2P_1(z) - z) - P_1(z)),
 \end{align*}
@@
 \end{align}
-where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
+where $W \geq L$ is the length of the sought signal and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
 

### 2018-08-31 pnas/Towards.tex
updated Appendix A

@@
 
-\TODO{Fill in refs to eqns.} For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK.
+For the experiment in Figure~\ref{fig:TRPV1_recon}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
+\TODO{Add more ref to figures, if exist}
 To estimate the coefficients of the volume itself, we solve the LS problem
@@
 In the experiments, we set $w_1=w_2=w_3=1$. 
-
-The LS problem was solved using Matlab's \texttt{lsqnonlin} solver for nonlinear least-squares problems. The expected $\hat \gamma$ in this experiment is one.
+The LS problem was solved using Matlab's \texttt{lsqnonlin} solver for nonlinear LS problems. The expected $\hat \gamma$ in this experiment is one.
 
@@
 This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.
+\TODO{Tamir: This entire paragraph will be changed a bit once we will have the final figures}
 
 The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows.
-We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in QR, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE \cite{aspire}.
+We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE \cite{aspire}.
 We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension.

### 2018-08-31 pnas/Towards.tex
Updated Appendix B

@@
 
-Throughout the proof, we consider the case of one signal $K=1$.
+%Throughout the proof, we consider the case of one signal $K=1$.
 The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
-
-We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this.
-We assume $M_N$ grows proportionally with $N$, and define: \TODO{---Nico: the paper now no longer references $M_N$ and defines $\gamma$ 'as is' for given $M$ and $N$; may want to adapt things here as a result.
+%We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this.
+We consider the asymptotic regime $N,M\to\infty$ and assume that $M=\Omega(N)$, so that
+% We assume $M_N$ grows proportionally with $N$, and recall that
+% define: %\TODO{---Nico: the paper now no longer references $M_N$ and defines $\gamma$ 'as is' for given $M$ and $N$; may want to adapt things here as a result.
 It wouldn't make sense to make $M_N$ appear in the paper I think, as it just makes things more complicated.
@@
 %
-\begin{equation}
-\gamma = \lim_{N\to\infty} \frac{M_NL}{N}<1.
-\end{equation}
-%
-We will assume that $M_N=\Omega(N)$, so that $\gamma>0$. In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
-
+\begin{equation*}
+\gamma := \frac{ML}{N}>0.
+\end{equation*}
+%
+%We will consider the regime $N,M\to\infty$ and assume that $M_N=\Omega(N)$, so that $\gamma>0$. %In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
 We start by considering the mean of the data:
@@
 & = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
-\\ & + \underbrace{\frac{\TODO{1,2?}}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}. 
+\\ & + \underbrace{\frac{2}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}. 
 %
@@
 %
-\begin{equation} \label{eq:2nd_moment_signal_term}
-%
-\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
-%
-\end{equation}
+\begin{align} \label{eq:2nd_moment_signal_term}
+%
+\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] & = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\nonumber\\&\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
+%
+\end{align}
 %
@@
 %
-\begin{equation}
+\begin{equation*}
 %
@@
 %
-\end{equation}
+\end{equation*}
 

### 2018-08-31 pnas/Towards.tex
Update Appendix D
Update appendices

@@
 \TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
-%
 
@@
 We assume the binary signal $s$ obeys a \emph{separation condition}:
-%% Nicolas: this is too important: it must stand out
-% If $s[i] = 1$ and $s[j] = 1$  for  $i \neq j$, then $\vert i - j\vert \geq 2L-1$.
 \begin{align} 
@@
 Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
-%system identification
 forward model takes the form
@@
 In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
-%The same observation model is used for \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
 
 Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.  
-%For example, $f$ may be the likelihood itself, or a related function with a similar form (leading to the class of ``quasi-likelihood'' methods).
 If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
@@
 One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-%Another paper considers parameterized models for multiple distinct signals, as in our framework ($K>1$)~\cite{andrieu2001bayesian}.
-Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.
 In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
@@
 However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets.
-%Indeed, for a general support signal $s$, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$---$O(N^M)$ such combinations in total.
-Hence, the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.
-However, exploiting the separation condition on the support~\eqref{eq:spacing}, we devise in Section TKTK an approximate EM procedure for  our model.
-%
-%Because likelihood methods are computationally expensive, methods based on recovery from moments, which are akin to our method, have also been previously used for system identification.
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
 
@@
 The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.
-%\TODO{Nico: I don't see how the next sentence is relevant for the task of estimating $s$---Since we have the full generative model, we can always generate more data as needed; therefore it is enough to consider the hardness of deciding whether a single interval contains signal or not.---I would just write this: Since the intervals are independent of each other, it is sufficient to consider a single interval.}
 
@@
 There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
-We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution:
-% $X | (\eta  = i) \sim N(\theta_i,\sigma^2)$; in other words,
-if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2)$ %(that is, $X$ follows a normal distribution around $\theta_0$ with variance $\sigma^2$),
- and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2)$. %\TODO{Tamir: to remove parenthesis}
-%If $\theta_1=0$, then the latter corresponds to pure noise interval.
+We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution: if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2)$ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2)$.
 
@@
 Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
-%we need to consider a different approach.
-In the next sections, % Nicolas: sections is plural on purpose
-we consider autocorrelation analysis for that purpose.
-%In what follows, we present several results on properties of autocorrelations.
+In the next sections, we consider autocorrelation analysis for that purpose.
 
@@
 Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-%In particular, for the first-order autocorrelation (that is, the mean), since the noise is independent of the signal, the mathematical expectation of $a_y^1$ is easily seen to be:
-%\begin{align*}
-%\E\{ a_y^1 \} & = \gamma a_x^1.
-%\end{align*}
-%(The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic: under the conditions, the quantity under consideration depends on $s$ only through $\gamma$.)
 We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density).
@@
 then the support of $x$ has length $L-T$ rather than $L$. 
-%the separation condition holds 
-%\TODO{for some spacing $W\geq L$---Nico: what is this?}, then $a_z^2[i] = 0$ for all $i > L-1$.
 Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
@@
 \end{corollary}
-
 %
@@
 Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
-%The separation restriction is discussed in more details in the Methods Section.
 
@@
 
-%\begin{figure*}[h!]
-%	\centering
-%	\includegraphics[scale=0.7]{Einstein_progress_examples}
-%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized with an image of the physicist Isaac Newton.
-Estimates are obtained from $P$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-%		%\TODO{To add: redo the figures according to Amit's comments and the figures of noisy Einstein's micrographs}
-%		% At a noise level of $\sigma = 3$, this amounts to an SNR of $1/20$.
-%	}
-%\end{figure*}
-
 \begin{figure}[h]
@@
 \end{figure}
-
-%\begin{figure}[h]
-%	\centering
-%\begin{subfigure}[h]{0.25\textwidth}
-%	\centering
-%	\includegraphics[scale=0.33]{Einstein_ps_error}
-%	\caption{relative power spectrum estimation error}
-%\end{subfigure} 
-%\begin{subfigure}[h]{0.25\textwidth}
-%	\centering
-%	\includegraphics[scale=0.33]{Einstein_recovery_error}
-%	\caption{relative recovery error}
-%\end{subfigure} 
-%	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example}}
-%\end{figure}
-
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[scale=.55]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
-%	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
-%\end{figure}
 
@@
 On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
-%
-%Under the experimental parameters (see Section~\ref{sec:numeric_details}), such values of $\gamma$ predict  in the informative micrograph and less than one projection in the pure noise scenario.
 
@@
 
-%In the simplified model for cryo-EM we examined, we showed it is possible to estimate the 3-D structure of small volumes. 
 In the simplified mathematical model we examined, we showed it is possible to estimate a signal without detecting its appearances.  
@@
 Of course, an important question then is whether the equations can be solved meaningfully in practice.
-%The proof-of-concept experiments above suggest they might.
-\TODO{Is it?}
 
@@
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition.%~\eqref{eq:spacing}.  
+In each micrograph, we placed Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition ~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 An example of a micrograph's excerpt is presented in the right panel of Figure~\ref{fig:micro_example}.
-%Different micrographs are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
 
@@
 In all experiments, the algorithm halted after a fixed number of 2000 iterations.
-%
-%In order to compare the performance in multiple cases and at different noise levels,  and the iterate with the smallest error compared to the ground truth (up to the reflection ambiguity) is chosen as the solution.
-While this cannot be done in practice (since we do not have access to the ground truth to determine which iterate is best), this procedure enables us to compare a large number of instances in different noise environments.
-\TODO{Note the last two sentences!}
 
@@
 The resulting SNR of $y$ is about $1/175$.
-%	 fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
-%This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation condition and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting SNR of $y$
-%% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-%is about 1/9.
-
-%This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-%
+
 Given the observation $y$, we proceed to compute the autocorrelations. %The first-order autocorrelation is straightforward. 
@@
 This has the  practical effect that we need not know $\sigma$. 
-%For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---
 By also taking symmetries into account, the third-order autocorrelation contains $\frac{(L-1)(L-2)}{2}$ remaining entries. Thus, in total we have
@@
 This redundancy suggests that it might be possible to estimate several signals simultaneously (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}).
-%Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-%\begin{align*}
-%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-%\end{align*}
-%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). 
 In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ (if the length of the measurement is larger than that) and added up, without correction for the junction points.
@@
 
-%Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
 Having computed the moments of interest, we now estimate the signal $x$ and coefficient $\gamma$ which agree with the data.
@@
 
-The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB)~\cite{pdb} as 1QLQ.
+The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
+as 1QLQ\footnote{\url{https://www.rcsb.org}}.
 We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
-We also present a reconstruction of TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB)~\cite{emdb} as EMD-8117.
+We also present a reconstruction of TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB) %~\cite{emdb}
+as EMD-8117\footnote{\url{http://www.ebi.ac.uk/pdbe/emdb}}.
 The original map has size $192^3$, and we downsample it to size $20^3$.
@@
 The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows.
-We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE \cite{aspire}.
+We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}.
+%\cite{aspire}.
  We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension.
@@
 \end{equation*}
-%
-%We will consider the regime $N,M\to\infty$ and assume that $M_N=\Omega(N)$, so that $\gamma>0$. %In the sequel, we will suppress the explicit dependence of $M$ on $N$ for notational convenience.
+
 We start by considering the mean of the data:
-%
-\begin{equation}
+\begin{equation*}
 a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
@@
 \xrightarrow{a.s.}\gamma a_x^1,
-\end{equation}
+\end{equation*}
 %
@@
 %
-\end{align}
+\end{align*}
 
@@
 This is achieved as follows:
-\begin{align}
-%
-%S & = \left\{x : \frac{f_0(x)}{f_1(x)} \leq \frac{1-q}{q} \right\}.
+\begin{align*}
+%
 S & = \left\{x : qf_0(x) \leq (1-q)f_1(x) \right\}.
 %
-\end{align}
-%
-%In other words, if $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, then the best estimator of $\eta$ based on $X$ is:
+\end{align*}
 %
 With $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, the corresponding estimator is:
-\begin{align}
+\begin{align*}
 %
@@
 %
-\end{align}
+\end{align*}
 Taking logarithms, the set $S$ can be rewritten as the set of $x$'s where:
@@
 %
-\end{align}
+\end{align*}
 If $q > 1/2$, then $q > 1-q$ and $\log(b) < 0$. Consequently, 
 %
-\begin{align}
-%
-\P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \longrightarrow 0
-%
-\end{align}
+\begin{align*}
+%
+\P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \longrightarrow 0,
+%
+\end{align*}
 %
@@
 %
-\begin{align}
-%
-\P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right] \longrightarrow 1
-%
-\end{align}
+\begin{align*}
+%
+\P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right] \longrightarrow 1,
+%
+\end{align*}
 %
@@
 %
-\end{align}
+\end{align*}
 That is, the probability of success converges to $q$.
@@
 \end{equation}
-Let $a_y^2:=\sum_{j=0}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
+Let $a_y^2:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
 \begin{equation} \label{eq:sigma2}
-\sigma^2 = a_y^2 - (a^1_y)^2/(\beta L). 
+\sigma^2 = a_y^2 - (a^1_y)^2/\beta. 
 \end{equation} 
@@
 \mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
-\mathcal{B} &= -E_1 + \frac{2L+1}{L}(a_y^1)^3 + a_y^1a_y^2  , \\
-\mathcal{C} &= -(a_y^1)^3/L.
+\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1a_y^2  , \\
+\mathcal{C} &= -(a_y^1)^3.
 \end{align*}
@@
 On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
-\begin{equation} \label{eq:E4}
+\begin{equation*} \label{eq:E4}
 E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
-\end{equation}
+\end{equation*}
 Taking the ratio:
@@
 \mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
-\mathcal{E} &= -(a_y^1)^2/L, \\
+\mathcal{E} &= -(a_y^1)^2, \\
 \mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
@@
 \end{equation}
-%\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell}^m(\kk/k),\quad k\leq 1,\]
-%where $k=||\kk||_2$, 
-where $c$ is the bandlimit, $\{S_l\}$ are determined using the Nyquist criterion as descirbed in \cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
+where $c$ is the bandlimit, $\{S_l\}$ are determined using the Nyquist criterion as described in~\cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
 \[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
@@
 where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
-Sampling at the Nyquist-rate dictates $c=1/2$~\cite{levin20173d}. 
-Because $\phi$ is real-valued, so $\widehat \phi$ is conjugate-symmetric, the expansion coefficients satisfy $\tamir_{\ell, -m, s} = (-1)^{\ell+m}\overline{\tamir_{\ell,m,s}}$, and hence we only need to recover coefficients $\tamir_{\ell, m, s}$ with $m\geq 0$.
+Sampling at the Nyquist rate dictates $c=1/2$~\cite{levin20173d}. 
+Because $\phi$ is real-valued,  $\widehat \phi$ is conjugate-symmetric and thus the expansion coefficients satisfy $\tamir_{\ell, -m, s} = (-1)^{\ell+m}\overline{\tamir_{\ell,m,s}}$.
+Therefore, we only need to recover coefficients $\tamir_{\ell, m, s}$ with $m\geq 0$.
+
 Let $I_{\omega}$ denote the tomographic projection obtained from viewing direction $\omega\in SO(3)$.
 By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}:
-\be\label{eq:projection_model}
-\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),\ee
+\begin{equation*}\label{eq:projection_model}
+\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),
+\end{equation*}
 where $D_{m',m}^{\ell}(\omega)$ is a Wigner-D matrix. This implies that the projections are also $c$-bandlimited.
@@
 where the viewing directions $\omega_t$ are assumed to be drawn from the uniform distribution over $\text{SO}(3)$ and $\mb s_t$ denotes the location of the center of the $t$th projection in the micrograph.
-%Similarly to~\eqref{eq:spacing},
-Again, we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction.
+We assume the projection is discretized on a Cartesian grid  of size $P\times P$ and we impose a separation condition so that any two projections are separated by at least $2P-1$ pixels between their upper left corners  in each direction, similarly to~\eqref{eq:spacing}.
 Note that~\eqref{eq:model} can be also written as a sum of $\delta$ functions as in~\eqref{eq:micrograph_model}.
@@
 \begin{equation*} \label{eq:Kth_autocorrelation}
-a^p_\II[\Bell_1,\ldots, \Bell_{p-1}] = \frac{1}{N^2}\sum_{\mb i}\II[\Bell]\II[\mb i+\Bell_1]\cdots \II[\mb i+\Bell_{p-1}],
+a^p_\II[\Bell_1,\ldots, \Bell_{p-1}] := \frac{1}{N^2}\sum_{\mb i}\II[\Bell]\II[\mb i+\Bell_1]\cdots \II[\mb i+\Bell_{p-1}],
 \end{equation*}
-where the summation is for $\mb i $ ranging over the $N^2$  pixels of the micrograph. %, $\Bell = (\Delta i, \Delta j)$.% and we set $\II(i,j)=0$ if either $i,j\notin\{1,\ldots, M\}$. 
-%In our procedure, we compute the first three autocorrelations. %, called the mean, power spectrum, and bispectrum, of the micrographs. \TODO{This definition and terminology should come earlier}. 
+where the summation is for $\mb i $ ranging over the $N^2$  pixels of the micrograph. 
 Let $\II_1,\ldots\II_K$ denote a set of $K$ micrographs. 
-Under the specified conditions, we show in Appendix~\ref{sec:moment_derivation} that the first three autocorrelations  of the micrographs are related to those of the projections by 
+Under the specified conditions, we show in the next section that the first three autocorrelations  of the micrographs are related to those of the projections by 
 \begin{align} \label{eq:ac_micrographs}
-\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} \\&+ b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3, \quad \Bell_1,\ldots,\Bell_{p-1}&\in[-(P-1),P-1]^2, \nonumber
+\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} \\&+ b_p[\Bell_1,\ldots,\Bell_{p-1}], \nonumber \\ p=1,2,3, \quad \Bell_1,\ldots,\Bell_{p-1}&\in[-(P-1),P-1]^2, \nonumber
 \end{align}
@@
 Therefore, given sufficiently many projections, we can accurately estimate the quantities $\gamma\langle a^p_{I_{\omega}}\rangle_{\omega}$ directly from the micrographs.
-These quantities are functions of the unknown coefficients $\tamir_{l,m,s}$ and we could proceed to invert their relation, as we did in the 2-D toy example.
+These quantities are functions of the unknown coefficients $\tamir_{l,m,s}$ and we could proceed to invert their relation, as we did in the  toy examples.
 
@@
 This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs).  We use autocorrelations up to and including the  third order since this is necessary to  determine the volume.
-The details are in the appendix.
-
-\subsection{Moments derivation} \label{sec:moment_derivation}
+
+\subsection{Autocorrelation derivation} \label{sec:moment_derivation}
 
@@
 Then, we have
-\be\begin{aligned} \label{eq:general_moment}
+\begin{equation} \label{eq:general_moment}
+\begin{split}
 	a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}] &= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\\
@@
 &= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\\
-	&\to \gamma\langle a^p_{I_{\omega}}[\Bell_1,\ldots, \Bell_{p-1}]\rangle_{\omega}, \end{aligned}\ee
+&\to \gamma\langle a^p_{I_{\omega}}[\Bell_1,\ldots, \Bell_{p-1}]\rangle_{\omega},
+\end{split}
+\end{equation}
 where the average is taken over $\omega$ with respect to the distribution of viewing directions. Here, we assume it to be uniform.
@@
 \end{align}
-
 where the range of $k,q$ is determined by Eq.~(8) in \cite{landa2017steerable}, the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are  scaling factors which will be defined in the next section.
@@
 \mathfrak{a}^2[k, q]  =
-\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{equation}
+\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, 
+\end{equation}
 where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. 
@@
 \end{align}
-%Considering equation~\eqref{eq:frakatwo}, our main task is to compute the coefficients $a_{k,q}$, which from the equation above can be done as follows: 
 Thus, we proceed as follows:
-for each position $\mb i$ in the micrograph $\II$, we extract the corresponding patch of size $2P-1$, expand it in the discretized PSWFs as in~\eqref{eq:itamar}, and collect the $a_{k,q}$ as per~\eqref{eq:frakatwo} to constitute the second-order autocorrelation of the micrograph.
+for each position $\mb i$ in the micrograph $\II$, we extract the corresponding patch of size $(2P-1) \times (2P-1)$, expand it in the discretized PSWFs as in~\eqref{eq:itamar}, and collect the $a_{k,q}$ as per~\eqref{eq:frakatwo} to constitute the second-order autocorrelation of the micrograph.
 
@@
 \begin{align} \label{eq:third_order_ac_pswf}
-&\mathfrak{a}^3[k_1,q_1;k_2,q_2] \\&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
-&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. 
+&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
+&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. \nonumber 
 \end{align}
@@
 \[\begin{aligned} b_{N,n}(\omega) &= \frac{4}{\sqrt{2\pi}|\alpha_{N,n}|^2}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
-&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{2\sqrt{2\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
+&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{\sqrt{8\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
 &= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
@@
 \begin{equation} \label{eq:beta}
-\beta_{\ell,s;N,n} := \left\{\begin{array}{ll} \frac{2\sqrt{2\pi}}{\alpha_{N,n}}Y_{\ell}^{N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|\\ 0, & \ell<|N|\end{array}\right.,
+\beta_{\ell,s;N,n} := \left\{\begin{array}{ll} \frac{\sqrt{8\pi}}{\alpha_{N,n}}Y_{\ell}^{N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|\\ 0, & \ell<|N|\end{array}\right.,
 \end{equation}
@@
 \begin{align} \label{eq:proj_expansion}
-I_{\omega}(r,\varphi) &= \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}(\omega)\psi_{N,n}(r,\varphi)\nonumber \\
-&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}\tamir_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi)
+&I_{\omega}(r,\varphi) = \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}(\omega)\psi_{N,n}(r,\varphi)\\
+&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}\tamir_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi), \nonumber 
 \end{align}
@@
 where the latter coefficients are given explicitly in~\eqref{eq:beta}. Using standard properties of D-Wigner functions, we obtain  
-\begin{align}
+\begin{align*}
 &\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\nonumber
-\end{align}
+\end{align*}
 where  $\left(\begin{array}{ccc} \ell_1 & \ell_2 & \ell_3\\ m_1 & m_2 & m_3\end{array}\right)$ are called Wigner 3-j symbols. 

### 2018-09-01 pnas/Towards.tex
Add BPTI results, make micrographs square

@@
 In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume.
-Figure~\ref{fig:cryo_detection} shows recovery of the 3-D volume from the clean autocorrelations.
+Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations.
 The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
@@
 
-\begin{figure*}[h]
-	\centering
-	\begin{subfigure}[h]{0.3\textwidth}
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[t]{0.3\textwidth}
 		\centering
@@
 	\end{subfigure} \hspace{2pt}
-	\begin{subfigure}[h]{0.3\textwidth}
+	\begin{subfigure}[t]{0.3\textwidth}
 		\centering
@@
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs. \TODO{The excerpts should be squares: use `axis equal;' -- also, what's going on with the diagonal line on the right panel?} To start }
+		The noise realization is identical in both micrographs. \TODO{Diagonal line}}
 \end{figure*}
 
-\begin{figure}
-    \centering
-    \includegraphics[angle=270, width=0.4\textwidth]{TRPV1_rec.eps}
-    \caption{Reconstruction of the TRPV1 molecule from its clean first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
-    \label{fig:TRPV1_recon}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
+		\caption{TPRV1}\label{fig:TRPV1_recon}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[h]{0.45\textwidth}
+		\centering
+		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
+		\caption{BPTI}\label{fig:BPTI_recon}
+	\end{subfigure} 
+	\caption{\label{fig:cryo_recon} Reconstructions from the first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
 \end{figure}
@@
 
-For the experiment in Figure~\ref{fig:TRPV1_recon}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
-\TODO{Add more ref to figures, if exist}
+For the experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
 To estimate the coefficients of the volume itself, we solve the LS problem
@@
 
-The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
+The true volume used in the experiments in Figures~\ref{fig:cryo_detection} and \ref{fig:BPTI_recon} was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
 as 1QLQ\footnote{\url{https://www.rcsb.org}}.
 We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
-We also present a reconstruction of TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB) %~\cite{emdb}
+For the experiment in Figure~\ref{fig:BPTI_recon}, the volume was downsampled to size $20^3$.
+For the experiment in Figure~\ref{fig:TRPV1_recon}, we used the TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB) %~\cite{emdb}
 as EMD-8117\footnote{\url{http://www.ebi.ac.uk/pdbe/emdb}}.
-The original map has size $192^3$, and we downsample it to size $20^3$.
-To generate the ground truth for our reconstructions, we expanded both volumes as in \eqref{eq:volume_expansion_app} with cutoff $L = 5$.
+The original map has size $192^3$, and was downsampled to size $20^3$.
+To generate the ground truth for our reconstructions, we expanded both volumes as in \eqref{eq:volume_expansion_app} with cutoff $L = 5$ for TRPV1 and $L = 2$ for BPTI \TODO{Do we need to explain why?}.
 For the TRPV1 reconstruction, the optimizer converged to a point giving relative $\ell_2$ error of $10^{-6}$ in the first three autocorrelations and an error of $10^{-1}$ in the expansion coefficients of the volume.
-Similarly, \TODO{Fill details for BPTI}.
+For the BPTI reconstruction, the errors in the autocorrelations were $10^{-6}$, $10^{-7}$ and $10^{-8}$ for the third, second and first autocorrelations, respectively, while the error in the expansion coefficients of the volume was $5\times 10^{-2}$.
 This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.

### 2018-09-02 pnas/Towards.tex
Files sent to Amit

@@
 		The true value of $\gamma$ is $0.0512$.
-		   The relative errors of $\gamma$ for the three panels are: $27.1\%,4\%,1.2\%$.
-The right panel shows the relative error as a function of $M$.
-\TODO{Nico: relative error should be logscale?
-Also, let's pick other colors; if we're running this again anyway, let's also aim for M being powers of 10 in all displayed cases?
-To run with logspace(3,7,9).
-We can remove the x-axis}
+		   The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
 	}
@@
 		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
-		\caption{TPRV1}\label{fig:TRPV1_recon}
+		\caption{TPRV1 with cutoff $L=5$}\label{fig:TRPV1_recon}
 	\end{subfigure}
@@
 		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
-		\caption{BPTI}\label{fig:BPTI_recon}
+		\caption{BPTI with cutoff $L=2$}\label{fig:BPTI_recon}
 	\end{subfigure} 
-	\caption{\label{fig:cryo_recon} Reconstructions from the first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
+	\caption{\label{fig:cryo_recon} Reconstructions from the first 3 autocorrelations.
+		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L$.
+		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
 \end{figure}
@@
 
-The true volume used in the experiments in Figures~\ref{fig:cryo_detection} and \ref{fig:BPTI_recon} was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
+The true volume used in the experiments in Figures~\ref{fig:cryo_detection} and~\ref{fig:BPTI_recon} was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
 as 1QLQ\footnote{\url{https://www.rcsb.org}}.
-We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
+We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5~\AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.
 For the experiment in Figure~\ref{fig:BPTI_recon}, the volume was downsampled to size $20^3$.
@@
 The original map has size $192^3$, and was downsampled to size $20^3$.
-To generate the ground truth for our reconstructions, we expanded both volumes as in \eqref{eq:volume_expansion_app} with cutoff $L = 5$ for TRPV1 and $L = 2$ for BPTI \TODO{Do we need to explain why?}.
+To generate the ground truth for our reconstructions, we expanded both volumes as in~\eqref{eq:volume_expansion_app} with cutoff $L = 5$ for TRPV1 and $L = 2$ for BPTI.
 For the TRPV1 reconstruction, the optimizer converged to a point giving relative $\ell_2$ error of $10^{-6}$ in the first three autocorrelations and an error of $10^{-1}$ in the expansion coefficients of the volume.
@@
 This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.
-\TODO{Tamir: This entire paragraph will be changed a bit once we will have the final figures}
 
@@
 \section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-
+\TODO{Need to check the details of the proof one more time}
 We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.

### 2018-09-03 pnas/Towards.tex
Update appendices B-D

@@
 	The observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma\geq\frac{L}{4(L-1)}\approx \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
+If $\gamma\geq \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
 	\begin{proof}
@@
 		\item Either the signal $x$ is generic; or
-		\item   $x$ has nonzero mean  and $\gamma\geq\frac{L}{4(L-1)}$.
+		\item   $x$ has nonzero mean  and $\gamma\geq\frac{1}{4}$.
 	\end{itemize}
@@
 \end{equation*}
+%
+Any vectors with indices out of range are given value 0.
 
@@
 & = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
-\\ & + \underbrace{\frac{2}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] \varepsilon[s_j + i + \ell]}_{\text{cross-term}}. 
-%
-\end{align*}
-
-The cross-terms are linear in the noise, and are easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
-As for the signal term, we break it into $M$ different sums, each containing one copy of the signal.
+\\ & + \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] (\varepsilon[s_j + i + \ell] + \varepsilon[s_j + i - \ell])}_{\text{cross-term}}. 
+%
+\end{align*}
+
+The cross-term is linear in the noise, and is easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
+We break the signal term into $M$ different sums, each containing one copy of the signal.
 This gives:
@@
 %
-\begin{equation}
-%
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-%
-\end{equation}
-%
-Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and thus converges to zero almost surely as $N\to\infty$.
+\begin{equation*}
+%
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+%
+\end{equation*}
+%
+Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, hence converges to zero almost surely as $N\to\infty$.
 If $\ell=0$, then we have:
@@
 \\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
 \nonumber \\
 &+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
+	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
 \\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
@@
 &= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
-\\& \xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
+\\& \xrightarrow{a.s.} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
 %
@@
 In this case, failure occurs when $X \in S$.
-Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,1)$.
+Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,I)$.
 On that condition,
@@
 \section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-\TODO{Need to check the details of the proof one more time}
 We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
@@
 E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
-& = \sigma^2a_y^1 + \beta^2F_1,
+& = \sigma^2a_y^1 + L\beta^2F_1,
 \end{split}
@@
 \begin{equation} \label{eq:E2}
-E_2:= \beta F_1 + (2L+1)\sigma^2a_y^1.
+E_2:= L\beta F_1 + (2L+1)\sigma^2a_y^1.
 \end{equation}
@@
 \end{equation}
-Let $a_y^2:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
+Let $E_3:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
 \begin{equation} \label{eq:sigma2}
-\sigma^2 = a_y^2 - (a^1_y)^2/\beta. 
+\sigma^2 = E_3 - (a^1_y)^2/\beta. 
 \end{equation} 
@@
 \begin{align*}
-\mathcal{A} &= E_2 - (2L+1)a_y^1a_y^2, \\ 
-\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1a_y^2  , \\
+\mathcal{A} &= E_2 - (2L+1)a_y^1E_3, \\ 
+\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1E_3  , \\
 \mathcal{C} &= -(a_y^1)^3.
@@
 
-We are now proceeding to derive the second quadratic equation. We notice that 
+Next, we derive the second quadratic equation for $\beta$. We notice that 
 \begin{equation} \label{eq:E3}
-E_3  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \frac{1}{L}\beta^3 F_2,
+E_4  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
 \end{equation}
@@
 \begin{equation*} \label{eq:E4}
-E_4 = \beta F_2 + (6L-3)\sigma^2a_y^1.
+E_5 = L \beta F_2 + (6L-3)\sigma^2a_y^1.
 \end{equation*}
@@
 \begin{equation*} 
-\frac{E_4}{E_3} = \frac{L}{\beta^2} + \frac{(6L-3)L\sigma^2a_y^1}{E_3}, 
+\frac{E_5}{E_4} = \frac{L}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_4}, 
 \end{equation*}
@@
 \begin{equation*}
-\sigma^2 = \frac{E_4}{a_y^1L(6L-3)}  - \frac{E_3}{\beta^2a_y^1(6L-3)}.
+\sigma^2 = \frac{E_5}{a_y^1(6L-3)}  - \frac{LE_4}{\beta^2a_y^1(6L-3)}.
 \end{equation*}
@@
 \begin{align*}
-\mathcal{D} &= a_y^2 - \frac{E_4}{a_y^1L(6L-3)}, \\ 
+\mathcal{D} &= E_3 - \frac{E_5}{a_y^1(6L-3)}, \\ 
 \mathcal{E} &= -(a_y^1)^2, \\
-\mathcal{F} &= \frac{E_3}{a_y^1(6L-3)}.
+\mathcal{F} &= \frac{LE_4}{a_y^1(6L-3)}.
 \end{align*}
@@
 \begin{split}
-\frac{\mathcal{B}}{\mathcal{C}} &= \frac{LE_1 - (2L+1)(a_y^1)^3 - La_y^1a_y^2}{(a_y^1)^3} \\&= \frac{La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2}{(a_y^1)^2}.
+\frac{\mathcal{B}}{\mathcal{C}} &= \frac{E_1 - (2L+1)(a_y^1)^3 - a_y^1E_3}{(a_y^1)^3} \\&= \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - E_3}{(a_y^1)^2}.
 \end{split}
@@
 \begin{equation*}
-\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_3} = 3 - 6L . 
+\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_4} = 3 - 6L . 
 \end{equation*}
@@
 \begin{equation*}
-La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L).
+a_y^2[0] - (2L+1)(a_y^1)^2 - E_3 = (a_y^1)^2(3-6L).
 \end{equation*}
@@
 \begin{equation} \label{eq:cond}
-4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
-\end{equation}	
-For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
-More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
+4(L-1)\beta (\1^\top x)^2  - (\1^\top x)^2 + \|x\|^2 = 0.
+\end{equation}	
+For generic $x$,  this polynomial equation is not satisfied and the equations are independent. 
+Furthermore, from the inequality $L\|x\|^2 \ge (\1^\top x)^2$ it follows immediately that the equations must be independent so long as
 \begin{equation*}
-\beta \geq \frac{1}{4(L-1)},
+\beta \geq \frac{1}{4L}.
 \end{equation*}
-the condition~\eqref{eq:cond} cannot be satisfied for any signal.
 

### 2018-09-04 pnas/Towards.tex
still working on appendix D

@@
 In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}x[i]x[j]$.
-Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
+\TODO{In the previous equation, index $j$ is unaccounted for} Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
 The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
@@
 \section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+
+\TODO{Nicolas: I'm pretty sure this proof assumes $L \geq 3$: let's add it as an assumption in the prop.}
+
 We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
 For convenience, we will work with $\beta = \gamma / L$ rather than $\gamma$ itself.
-We will construct two quadratic equations satisfied by $\beta$ from observed quantities, independent of $\sigma$.
+We will construct two quadratic equations satisfied by $\beta$ from observed quantities, \TODO{independent of $\sigma$---they're not independent of $\sigma$; did you mean `independently'?}.
 Then, we will show that these equations are independent, and hence that $\beta$ is uniquely defined.
@@
 
-Recall that $a_y^1 = \beta(\one^Tx)$ and  
-and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ stands for vector of ones. Taking the product:
+Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, \TODO{the latter statements are only true in expectation, or almost surely in the limit though; should revise whole proof accordingly} where $\one\in\RL$ is the vector of all-ones.
+Taking the product:
 \begin{equation}\label{eq:E1}
@@
 where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
-The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account:
-\begin{equation} \label{eq:E2}
-E_2:= L\beta F_1 + (2L+1)\sigma^2a_y^1.
-\end{equation}
+% Nicolas: the expression for F_1 is correct, see identifiability_of_gamma_and_sigma_Sep4_2018.m and notes Sep 4, 2018
+The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable:
+\begin{align} 
+E_2 & := a_y^3[0,0] + \sum_{j=1}^{L-1}(a_y^3[j,j] + a_y^3[0,j]) \nonumber\\
+	& = L\beta F_1 + (2L+1)\sigma^2a_y^1. \label{eq:E2}
+\end{align}
+% Nicolas: checked this one too.
 Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
@@
 \end{equation} 
-Plugging into~\eqref{eq:E12} and rearranging we get 
+Plugging into~\eqref{eq:E12} and rearranging we get a first quadratic equation in $\beta$,
 \begin{equation} \label{eq:quad1}
@@
 Importantly, these coefficients are observable quantities. 
+% Nicolas, Sep 4 2018: everything checked and correct until here.
 
@@
 \begin{equation} \label{eq:E3}
-E_4  = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
+E_4 := \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
 \end{equation}
@@
 \begin{equation*} \label{eq:E4}
-E_5 = L \beta F_2 + (6L-3)\sigma^2a_y^1.
+E_5 := L \beta F_2 + (6L-3)\sigma^2a_y^1.
 \end{equation*}

### 2018-09-04 pnas/Towards.tex
Done checking Appendix D.

@@
 \begin{proof}
-In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}x[i]x[j]$.
-\TODO{In the previous equation, index $j$ is unaccounted for} Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
+In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
+Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
 The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
@@
 	%Let $\sigma > 0$ be fixed. 
+	Assume $L \geq 3$. % Added by Nicolas, Sep 4, 2018: I checked all identities for L >= 3, with some computer code; I didn't write code to verify the corner cases L = 1 and L = 2.
 	The observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma\geq \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
+If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
 	\begin{proof}
@@
 		\item Either the signal $x$ is generic; or
-		\item   $x$ has nonzero mean  and $\gamma\geq\frac{1}{4}$.
+		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
 	\end{itemize}
@@
 
-\TODO{Nicolas: I'm pretty sure this proof assumes $L \geq 3$: let's add it as an assumption in the prop.}
-
-We will prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
-For convenience, we will work with $\beta = \gamma / L$ rather than $\gamma$ itself.
-We will construct two quadratic equations satisfied by $\beta$ from observed quantities, \TODO{independent of $\sigma$---they're not independent of $\sigma$; did you mean `independently'?}.
-Then, we will show that these equations are independent, and hence that $\beta$ is uniquely defined.
+%\TODO{Nicolas: I'm pretty sure this proof assumes $L \geq 3$: let's add it as an assumption in the prop.
+It also very clearly requires nonzero mean because of division by $E_4$, but we say that already.}
+
+We prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
+For convenience, we work with $\beta = \gamma / L$ rather than $\gamma$ itself.
+To this end, we construct two quadratic equations satisfied by $\beta$ and whose coefficients can be computed from observable quantities (in the limit).
+Then, we show that these equations are independent, and hence that $\beta$ is uniquely defined.
 Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
@@
 Throughout the proof, it is important to distinguish between observed and unobserved values.
-We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$, while using $F_i$ for functions of the signal's autocorrelations.
-
-Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, \TODO{the latter statements are only true in expectation, or almost surely in the limit though; should revise whole proof accordingly} where $\one\in\RL$ is the vector of all-ones.
-Taking the product:
+We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$. We use $F_i$ to denote functions of the signal's autocorrelations (which are not directly observable).
+
+In the limit $N \to \infty$, almost surely, $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones.
+(In this whole section, for clarity, we now omit to specify that identities hold almost surely in the limit.) Consider the product:
 \begin{equation}\label{eq:E1}
@@
 % Nicolas: the expression for F_1 is correct, see identifiability_of_gamma_and_sigma_Sep4_2018.m and notes Sep 4, 2018
-The terms of $F_1$ can be also estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable:
+The terms of $F_1$ can also be estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable:
 \begin{align} 
@@
 % Nicolas: checked this one too.
-Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get
+Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get:
 \begin{equation} \label{eq:E12}
@@
 \end{equation}
-Let $E_3:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$ and recall from Proposition~\ref{prop:gamma}:
+Let $E_3:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$; recall from Proposition~\ref{prop:gamma}:
 \begin{equation} \label{eq:sigma2}
@@
 \end{equation} 
-Plugging into~\eqref{eq:E12} and rearranging we get a first quadratic equation in $\beta$,
+Plugging into~\eqref{eq:E12} and rearranging, we get a first quadratic equation in $\beta$,
 \begin{equation} \label{eq:quad1}
@@
 \end{align*}
-Importantly, these coefficients are observable quantities. 
-% Nicolas, Sep 4 2018: everything checked and correct until here.
+Importantly, these coefficients are observable quantities. As we assume throughout this proof that $x$ has nonzero mean, $a_y^1 \neq 0$ and we conclude that this equation is non-trivial.
 
@@
 \end{equation}
-where 
+where $F_2 = \frac{1}{L}(\one ^Tx)^3$, and we can work out that:
 \begin{equation*}
-F_2 =  a_x^3[0,0] + 3\sum_{j=1}^{L-1}a_x^3[j,j] + 3\sum_{j=1}^{L-1}a_x^3[0,j] + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+F_2 = a_x^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_x^3[j,j] + a_x^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+% Nicolas: checked this formula with the matlab code on Sep 4, 2018: it's correct
 \end{equation*}
-On the other hand, from $a_y^3$ we can directly estimate $F_2$ up to scale and bias
-\begin{equation*} \label{eq:E4}
-E_5 := L \beta F_2 + (6L-3)\sigma^2a_y^1.
+Once again, $F_2$ can be estimated from $a_y^3$, taking bias and scaling into account:
+\begin{align}
+	E_5 & := a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j] \nonumber \\
+		& = L \beta F_2 + (6L-3)\sigma^2a_y^1.
+\end{align}
+Consider the following ratio:
+\begin{equation*} 
+\frac{E_5}{E_4} = \frac{L}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_4}.
 \end{equation*}
-Taking the ratio:
-\begin{equation*} 
-\frac{E_5}{E_4} = \frac{L}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_4}, 
-\end{equation*}
-we conclude:
+From the latter, we deduce:
 \begin{equation*}
@@
 \end{equation*}
-Using~\eqref{eq:sigma2} and rearranging we get the second quadratic:
+Using~\eqref{eq:sigma2} and rearranging, we get the second quadratic:
 \begin{equation} \label{eq:quad2}
@@
 \end{align*}
+It is also non-trivial since $E_4 \neq 0$.
 
 To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
-To this end, it is enough to show that the ratio between the coefficients is not the same.
-From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have 
+To this end, it is enough to show that the ratios between coefficients differ.
+From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have:
 \begin{equation*}
@@
 \end{equation*}
-In addition, using~\eqref{eq:E3}
+In addition, using~\eqref{eq:E3},
 \begin{equation*}
@@
 \end{equation*}
-
-Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
+For contradiction, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, that is, 	
 \begin{equation*}
@@
 \end{equation*}
-Rearranging the equation and writing in terms of $x$ we get 
+Rewriting the identity in terms of $x$ and dividing by $\beta$ we get:
 \begin{equation} \label{eq:cond}
@@
 \end{equation}	
-For generic $x$,  this polynomial equation is not satisfied and the equations are independent. 
+% Nicolas, Sep 4 2018: everything checked and correct until here.
+For generic $x$,  this polynomial equation is not satisfied so that the quadratic equations are independent. 
 Furthermore, from the inequality $L\|x\|^2 \ge (\1^\top x)^2$ it follows immediately that the equations must be independent so long as
 \begin{equation*}
-\beta \geq \frac{1}{4L}.
+\beta > \frac{1}{4L}.
 \end{equation*}

### 2018-09-04 TEX/identifiability_of_gamma_and_sigma_Sep4_2018.m

@@ -1,6 +1,6 @@
 function identifiability_of_gamma_and_sigma_Sep4_2018()
 % See notes Sep 4, 2018, NB36
-L = 10;
+L = 3;
 labels = zeros(L^3, 3);
 counter = 0;
 for k1 = 0 : L-1
@@ -41,7 +41,7 @@ for k1 = 0 : L-1
         counter = counter + 1;
         % Setup linear combination corresponding to a_x^3[k1, k2]
         for j = max([0, -k1, -k2]) : (L-1+min([0, -k1, -k2]))
-            A(linear_index(j, j+k1, j+k2), counter) = 1;
+            A(linear_index(j, j+k1, j+k2), counter) = 1/L;
         end
     end
 end
@@ -51,7 +51,15 @@ end
 b = zeros(nlabels, 1);
 for k1 = 0 : L-1
     for k2 = 0 : L-1
-        b(linear_index(k1, k1, k2)) = L;
+        
+        % To check F1, activate this line
+        % b(linear_index(k1, k1, k2)) = b(linear_index(k1, k1, k2)) + 1;
+        
+        % To check F2, activate these three lines
+        for k3 = 0 : L-1
+            b(linear_index(k1, k2, k3)) = b(linear_index(k1, k2, k3)) + 1/L;
+        end
+        
     end
 end
 
@@ -67,6 +75,6 @@ for k1 = 0 : L-1
     end
 end
 
-
+imagesc(0:L-1, 0:L-1, reshape(x, L, L)); colorbar;
 
 end

### 2018-09-06 pnas/Towards.tex
small changes

@@
 The smaller the molecules, the fewer detected electrons carry information about them.
-\TODO{This isn't quite accurate.
-Amit: do you agree with the last sentence?
+\TODO{Amit: do you agree with the last sentence?
 maybe we should say it is a function of the contrast?}
@@
 Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-Similar phenomenon was recently observed in a related problem~\cite{zhang2018structured}.
+A similar phenomenon was recently observed in a related problem~\cite{zhang2018structured}.
 Thus, we first run the optimization with $W = 2L-1$.
@@
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
+\TODO{Nico: is this really how the procedure works?
+Or is it just that after a few failed attempts, we abandon?
+Also, the text doesn't say if the projections are placed at random, but I'm assuming they are ?} Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
 
@@
 %
-where the noise term converges to zero almost surely (a.s.) by the strong law of large numbers.
+where the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
 
@@
 \end{align*}
-
 The cross-term is linear in the noise, and is easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
@@
 %
-
 We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
@@
 The proof is based on  a variant of the Neyman--Pearson Lemma to derive the best (deterministic) estimator $\hat{\eta}$.
-We take any estimator $\hat{\eta}$, and we let $S$ be the set of $X$'s where $\hat{\eta} = 1$.
+Take any estimator $\hat{\eta}$; it is characterized by $S$: the set of $X$'s where $\hat{\eta} = 1$, where $X$ is a random vector as defined above Proposition~\ref{prop:two_gauss}.
 We write $\P_i$ to mean the probability conditional on the event $\eta = i$; that is, $\P_i[A] = \P[A | \eta = i]$.
@@
 The best estimator of $\eta$ based on $X$ minimizes the failure probability; hence, it minimizes the integral in~\eqref{eq:neyman-pearson} through an appropriate choice of the set $S$.
-This is achieved as follows:
-\begin{align*}
-%
-S & = \left\{x : qf_0(x) \leq (1-q)f_1(x) \right\}.
+This is achieved by picking all $x$'s such that the integrand is nonpositive:
+\begin{align*}
+%
+S & = \left\{x : qf_0(x) - (1-q)f_1(x) \leq 0 \right\}.
 %
@@
 \end{equation}	
-% Nicolas, Sep 4 2018: everything checked and correct until here.
 For generic $x$,  this polynomial equation is not satisfied so that the quadratic equations are independent. 
@@
 \end{equation*}
+% Nicolas, Sep 4 2018: everything checked and correct until here.
 
@@
 Then, we have
-\begin{equation} \label{eq:general_moment}
-\begin{split}
-	a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}] &= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\\
-&= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
-&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[\mb i+\Bell_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\\
-&= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\\
+\begin{align}
+	& a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}]  \nonumber\\
+	&= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\nonumber\\
+&= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \nonumber\\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
+&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[\mb i+\Bell_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\nonumber\\
+&= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\nonumber\\
 &\to \gamma\langle a^p_{I_{\omega}}[\Bell_1,\ldots, \Bell_{p-1}]\rangle_{\omega},
-\end{split}
-\end{equation}
+\label{eq:general_moment}
+\end{align}
 where the average is taken over $\omega$ with respect to the distribution of viewing directions. Here, we assume it to be uniform.
@@
 Thus, we conclude that
-\begin{equation} \label{eq:third_order_ac_micro_volume}
+\begin{multline} \label{eq:third_order_ac_micro_volume}
 a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
-a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
+a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} \\ +
 \gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
 \delta[\Bell_1] + \delta[\Bell_2]\Big),
-\end{equation}
+\end{multline}
 where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
@@
 Below, we start with $p=2$.
-The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by \footnote{A different normalization is used in \cite{landa2017steerable}.}
+The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by\footnote{A different normalization is used in \cite{landa2017steerable}.}
 \begin{align}
@@
 \begin{align} \label{eq:third_order_ac_pswf}
-&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
+&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right) \nonumber\\
 &= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. \nonumber 

### 2018-09-07 pnas/Towards.tex
Responding to Amit's comments

@@
 \author[c]{William Leeb}
-\author[a]{Eitan Levin}
+\author[a,b]{Eitan Levin}
 \author[a,b]{Amit Singer}
@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Please provide details of author contributions here.}
-\authordeclaration{Please declare any conflict of interest here.}
+\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
+\authordeclaration{The authors declare no conflicts of interest.}
 %\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
@@
 
-\dropcap{C}ryo--electron microscopy (cryo--EM) is an leading technology for single particle reconstruction (SPR) of macromolecules. \TODO{revise first sentence}
+\dropcap{C}ryo--electron microscopy (cryo--EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. %Within the ice, the molecules are randomly oriented and positioned.
@@
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
-The goal is to construct 3-D models of the molecules from the micrographs.
+The goal is to construct 3-D models of the molecular structure from the micrographs.
 
@@
 The smaller the molecules, the fewer detected electrons carry information about them.
-\TODO{Amit: do you agree with the last sentence?
-maybe we should say it is a function of the contrast?}
-
-All contemporary methods in the field split the reconstruction procedure into several stages.
+
+All contemporary methods in the field split the reconstruction procedure into two main  stages.
 The first stage consists in extracting the various particle projections from the micrographs.
 This stage is called \emph{particle picking}.
-Later stages aim to construct a 3-D model of the molecule from these projections.
+The second stage aims to construct a 3-D model of the molecular structure from these projections.
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
@@
 
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0.15in}
-	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-\end{myquote}
-%\begin{quote}
-%	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-%\end{quote}
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
-\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
-
-The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-Despite this progress, detecting small molecules in the micrographs remains a challenge.
-We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
-Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
-\TODO{Need a ref for this claim.}
-
-In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-
-As a proof of concept, we first study a toy model \TODO{Amit: do you want to keep ``toy model'' or replace with ``mathematical toy model'', ``simplified model'' etc.} for which it is easier to convey the mathematical principles.
-In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-The goal is to estimate the planted image.
-The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
-This problem is interesting of its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
-Importantly, there is no need to detect individual image occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.
-
-Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
-Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
-In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
-We show a few numerical examples and outline the future developments required to make this method applicable on real data.
-
-Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
-In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
-This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
-%
-
-\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
-
-\section{Proof of concept: A mathematical toy model}
-
-In this section, we present a toy model in order to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
-Later, we discuss how these principles carry through for the SPR problem.
-We first formulate the model for 1-D signals to ease exposition.
-
-Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where $N$ is assumed far larger than $L$.
-Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
-\begin{align}
-y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
-\label{eq:model}
-\end{align}
-where $\ast$ denotes linear convolution. 
-While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
-This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
-As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
-
-We assume the binary signal $s$ obeys a \emph{separation condition}:
-\begin{align} 
-\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
-\label{eq:spacing}
-\end{align}
-In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-
-Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
-forward model takes the form
-%
-\begin{math}
-%
-y = x\ast w + \varepsilon,  
-%
-\end{math} 
-%
-where $x$ is the unknown signal (the system's impulse response), $w$ is an unknown (often random) input sequence, and $\varepsilon$ is an additive noise.
-The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
-
-Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.  
-If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
-Methods based on such formulations are popular nowadays in cryo-EM; see for instance~\cite{sigworth1998maximum,scheres2012relion}. 
-Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
-One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
-The EM method for discrete $w$ is based on a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
-However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets.
-
-Because likelihood methods are computationally expensive, methods based on recovery from moments have also been previously used for system identification.
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.
-% and study it in Section~\ref{sec:recovery}.
-
-\section{The detection limit} \label{sec:detectionlimit}
-
-At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
-However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
-
-To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise.
-Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
-The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.
-
-This decision problem can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
-There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
-We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution: if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2)$ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2)$.
-
-We observe $X$, and our task is to estimate $\eta$.
-How reliably can this be done?
-If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise, if $q \leq 1/2$, the constant estimator $\hat{\eta} = 1$ is correct with probability $1-q$.
-The question is, can we do better than this?
-We prove that, as $\sigma \to \infty$, the answer is no:
-\begin{proposition} \label{prop:two_gauss}
-	For any deterministic estimator $\hat{\eta }$ of $\eta$,
-	\begin{align*}
-	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q);
-	\end{align*}
-	that is: as the SNR deteriorates, the probability of success is no better than random chance.
-\end{proposition}
-\noindent The result is proved in Appendix~\ref{sec:proof_two_gauss}.
-
-Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
-In the next sections, we consider autocorrelation analysis for that purpose.
-
-\section{Autocorrelation analysis} \label{sec:AC_analysis}
-
-In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-\begin{align}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
-\label{eq:ac_general}
-\end{align}
-where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-Explicitly, the first-, second- and third-order autocorrelations are given by: \TODO{we may want to remove these explicit formulas}
-\begin{align} 
-a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-$
-
-Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
-\begin{align}
-	\gamma & = \frac{M L}{N}
-	\label{eq:gamma}
-\end{align}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
-imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-
-For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
-Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-We consider the asymptotic regime where $M, N\to\infty$, while $\gamma$ remains constant (we see an increasingly large micrograph, containing increasingly many signal occurrences, with constant signal density).
-In that regime, the law of large numbers can be used to show the following statement:
-\begin{align} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1 & \aseq \gamma a_{x}^1,
-\end{align}
-where equality holds almost surely (a.s.), meaning it holds with probability one.
-The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
-
-We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
-As a result,
-\begin{align}
-	\lim_{N\to\infty} a_y^2[\ell] & \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
-	\label{eq:ac2_micrograph}
-\end{align}
-for $\ell = 0, \ldots, L-1$, where $\delta$ denotes the Kronecker delta function.
-The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
-
-Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{multline}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
-\end{multline}
-for $\ell_1,\ell_2 = 0, \ldots, L-1$. Here too, few entries are affected by $\sigma$ in the limit.
-Detailed derivations for identities in this and the next part are given in Appendix~\ref{sec:autocorrelation_computation}.
-
-Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
-
-\section{Recovering a signal from autocorrelations} \label{sec:recovery}
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
-Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
-%
-\begin{align}
-%
-z[k] & = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
-\label{eq-uniqueness}
-%
-\end{align}
-This proves the following useful fact:
-\begin{proposition} \label{prop:uniqueness}
-	%
-	 A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-\end{proposition}
-
-Some remarks are in order.
-First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-Second, if the separation condition holds, then the length of the signal can be determined from the autocorrelations.
-In particular, if  $a_y^2[L-i] = 0$ for $i=1,\ldots,T$,
-then the support of $x$ has length $L-T$ rather than $L$. 
-Third, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case).
-%~\cite{hayes1982reconstruction,hayes1982reducible}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
-We will show, however, that $x$ is still identifiable from the observed moments of $y$.
-In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
-
-First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
-%
-\begin{proposition} \label{prop:gamma}
-	Let $\sigma > 0$ be fixed. If the mean of $x$ is nonzero, then 
-	%
-	\begin{align*}
-	%
-	\gamma & \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
-	%
-	\end{align*}
-	%
-\end{proposition}
-\begin{proof}
-In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
-Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
-The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
-%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
-\end{proof}
-
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are identifiable.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-lies in a set with Lebesgue measure zero. 
-In particular, this means that we can recover
-almost all signals with the given measurements.
-
-\begin{proposition} \label{prop:gamma_sigma}
-	%
-	%Let $\sigma > 0$ be fixed. 
-	Assume $L \geq 3$. % Added by Nicolas, Sep 4, 2018: I checked all identities for L >= 3, with some computer code; I didn't write code to verify the corner cases L = 1 and L = 2.
-	The observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we can directly deduce the following:
-\begin{corollary}
-	%Let $K=1$ and $\sigma > 0$ be fixed.
-	 The signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are identifiable from the first three autocorrelation functions of $y$ if:
-	\begin{itemize}
-		\item Either the signal $x$ is generic; or
-		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-	\end{itemize}
-\end{corollary}
-%
-%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
-
-\section{Numerical experiments}
-
-The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
-To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.
-Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
-
-In the first experiment, we estimated 
-an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
-Each micrograph contains, on average, 700 occurrences of the target image at random locations.
-Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
-This high noise level is illustrated in Figure~\ref{fig:micro_example}.
-To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
-
-We compute the average second-order autocorrelation of the micrographs.
-This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) on GPUs.
-Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
-Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
-
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available in \TODO{supplementary material}.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
-As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-
-In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
-Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
-The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}. 
-Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
-Crucially, the LS does not require  knowledge of $\sigma$.
-
 \begin{figure*}[h]
@@
 		\includegraphics[scale=0.35]{Einstien_progress_1}
-		\caption{$500$ micrographs}
+		\caption{$500$ micrographs \TODO{Tamir: I am redo the exp}}
 	\end{subfigure} 
@@
 
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
+This fact has been recognized early on by the cryo-EM community.
+In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
+\begin{myquote}{0.15in}
+	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
+Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
+\end{myquote}
+In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
+Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
+As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
+Yet, imaging such molecules is important for a number of applications~\cite{scapin2018cryo}
+
+The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+Despite this progress, detecting small molecules in the micrographs remains a challenge.
+We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
+Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
+
+In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
+Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
+Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
+Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+
+As a proof of concept, we first study a toy model  for which it is easier to convey the mathematical principles. 
+In this model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
+The goal is to estimate the planted image.
+The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
+This problem is interesting on its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+
+In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
+Importantly, there is no need to detect individual image occurrences.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
+To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem; see for instance Figure~\ref{fig:Einst_example}.
+
+Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
+Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
+In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
+We show a few numerical examples and outline the future developments required to make this method applicable to experimental  data.
+
+Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
+In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
+In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
+This model bias is common to all particle picking methods based on template matching.
+In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
+%
+
+%\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
+
+\section{Proof of concept: A mathematical toy model}
+
+In this section, we present a toy model in order to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
+Later, we discuss how these principles carry through for the SPR problem.
+We first formulate the model for 1-D signals to ease exposition.
+
+Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
+Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+\begin{align}
+y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{align}
+where $\ast$ denotes linear convolution. 
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
+This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
+As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
+
+We assume the binary signal $s$ obeys a \emph{separation condition}:
+\begin{align} 
+\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{align}
+In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
+
+Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
+forward model takes the form
+%
+\begin{math}
+%
+y = x\ast w + \varepsilon,  
+%
+\end{math} 
+%
+where $x$ is the unknown signal (the system's impulse response), $w$ is an unknown (often random) input sequence, and $\varepsilon$ is an additive noise.
+The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
+In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
+
+Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.  
+If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
+Methods based on such formulations are popular nowadays in cryo-EM; see for instance~\cite{sigworth1998maximum,scheres2012relion}. 
+Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
+One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
+In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
+The EM method for discrete $w$ is based on a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
+However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets.
+
+Because likelihood methods are computationally expensive, methods based on recovery from moments have also been previously used for system identification.
+Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
+Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.
+% and study it in Section~\ref{sec:recovery}.
+
+\section{The detection limit} \label{sec:detectionlimit}
+
+At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
+However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
+
+To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise.
+Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
+The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.
+
+This decision problem can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
+There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
+We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution: if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2I_L)$ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2I_L)$.
+
+We observe $X$, and our task is to estimate $\eta$.
+How reliably can this be done?
+If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise, if $q \leq 1/2$, the constant estimator $\hat{\eta} = 1$ is correct with probability $1-q$.
+The question is, can we do better than this?
+We prove that, as $\sigma \to \infty$, the answer is no:
+\begin{proposition} \label{prop:two_gauss}
+	For any deterministic estimator $\hat{\eta }$ of $\eta$,
+	\begin{align*}
+	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q);
+	\end{align*}
+	that is: as the SNR deteriorates, the probability of success is no better than random chance.
+\end{proposition}
+\noindent The result is proved in Appendix~\ref{sec:proof_two_gauss}.
+
+Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
+In the next sections, we consider autocorrelation analysis for that purpose.
+
+\section{Autocorrelation analysis} \label{sec:AC_analysis}
+
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\begin{align}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+\label{eq:ac_general}
+\end{align}
+where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
+Explicitly, the first-, second- and third-order autocorrelations are given by: %\TODO{we may want to remove these explicit formulas}
+\begin{align} 
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$
+
+Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
+\begin{align}
+	\gamma & = \frac{M L}{N}
+	\label{eq:gamma}
+\end{align}
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
+imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
+Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
+We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large micrograph, it contains increasingly many signal occurrences, with constant signal density).
+In that regime, the law of large numbers can be used to show the following statement:
+\begin{align} \label{eq:mean_micrograph}
+\lim_{N\to\infty} a_y^1 & \aseq \gamma a_{x}^1,
+\end{align}
+where equality holds almost surely (a.s.), meaning it holds with probability one.
+The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+
+We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
+As a result,
+\begin{align}
+	\lim_{N\to\infty} a_y^2[\ell] & \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
+	\label{eq:ac2_micrograph}
+\end{align}
+for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
+The last part captures the autocorrelation of the noise.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
+
+Along the same lines, one can establish a relation for third-order autocorrelations:
+\begin{multline}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
+\end{multline}
+for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
+Here too, few entries are affected by $\sigma$ in the limit.
+See Appendix~\ref{sec:autocorrelation_computation}.
+
+Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
+
+\section{Recovering a signal from autocorrelations} \label{sec:recovery}
+
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
+Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
+%
+\begin{align}
+%
+z[k] & = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+\label{eq-uniqueness}
+%
+\end{align}
+This proves the following useful fact:
+\begin{proposition} \label{prop:uniqueness}
+	%
+	 A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\end{proposition}
+
+A couple of remarks are in order.
+First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
+However, for dimensions greater than one, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+%,hayes1982reducible}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
+
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
+We will show, however, that $x$ is still determined by the observed moments of $y$.
+%
+%identifiable from the observed moments of $y$. In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
+
+First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
+%
+\begin{proposition} \label{prop:gamma}
+	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
+	%
+	\begin{align*}
+	%
+	\gamma & \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	%
+	\end{align*}
+	%
+\end{proposition}
+\begin{proof}
+In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
+Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
+The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
+%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
+\end{proof}
+
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined.
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
+has Lebesgue measure zero. 
+In particular, this means that we can recover
+almost all signals with the given measurements.
+
+\begin{proposition} \label{prop:gamma_sigma}
+	%
+	%Let $\sigma > 0$ be fixed. 
+	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds.
+% Added by Nicolas, Sep 4, 2018: I checked all identities for L >= 3, with some computer code; I didn't write code to verify the corner cases L = 1 and L = 2.
+	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
+	\begin{proof}
+		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+	\end{proof}
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
+\begin{corollary}
+	%Let $K=1$ and $\sigma > 0$ be fixed.
+	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
+	\begin{itemize}
+		\item Either the signal $x$ is generic; or
+		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+	\end{itemize}
+\end{corollary}
+%
+%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
+
+As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
+%In particular, if  $a_y^2[L-i] = 0$ for $i=1,\ldots,T$,
+%then the support of $x$ has length $L-T$ rather than $L$.
+
+\section{Numerical experiments}
+
+The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
+To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.
+Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
+
+\subsection{Toy model}
+In the first experiment, we estimated 
+an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+Each micrograph contains, on average, 700 occurrences of the target image at random locations.
+Thus, about 10\% of each micrograph contains signal.
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
+This high noise level is illustrated in Figure~\ref{fig:micro_example}.
+To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
+
+We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
+ Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available as supplementary material.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
+As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
+Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
+The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}. 
+Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
+Crucially, the LS does not require  knowledge of $\sigma$.
+
 \begin{figure}[h]
@@
 
-The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
+\subsection{Cryo-EM} The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
 The derivation of the first three autocorrelations of the micrographs and their relations to the volume itself are provided in Appendix~\ref{sec:ac_cryo}.
@@
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs. \TODO{Diagonal line}}
+		The noise realization is identical in both micrographs.
+\TODO{Diagonal line} \TODO{Amit: need to specify which molecule is projected to create micrographs shown in (b) and (c).
+This is not mentioned in the text either.
+}}
 \end{figure*}
@@
 	\end{subfigure} 
-	\caption{\label{fig:cryo_recon} Reconstructions from the first 3 autocorrelations.
+	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L$.
-		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
+		The reconstruction is shown in gray while the (smoothed) ground truth in yellow.
+\TODO{Amit: I suggest calling the spherical harmonics cutoff $l_max$ rather than L.
+Previously, L is used for the size of the signal or for the size of images LxL.
+So, it is quite confusing to use L in a completely different context.
+You would need to make changes in many other places as well (e.g., eq.(23) and the labels (a) and (b) in this figure, are just two examples), in order to avoid this notation overload.
+	}}
 \end{figure}
@@
 Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an important question then is whether the equations can be solved meaningfully in practice.
+Of course, an important question then is whether the equations can be solved accurately and efficiently in practice.
 
@@
 Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
-We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.\TODO{Will: Is this really enough?
-I think the main issue is what happens when particles can collide (or maybe even overlap), since this introduces additional cross-terms for the moment-fitting problem.}
-Such a condition can be met in practice by careful experimental design.
+We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
+%Such a condition can be met in practice by careful experimental design.
 
@@
 
+\section*{Acknowledgment}
+The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, and Fred Sigworth for supplying us with the dataset of the BPTI molecule.
+The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
+\revised{Amit: to verify.} NB is partially supported by NSF award DMS-1719558.
+\TODO{Correct bib}
+
 % Bibliography
@@
 \section{Numerical experiments details} \label{sec:numeric_details}
+
+We run the toy model experiments on a shared computer with 144 logical CPUs of type Intel(R) Xeon(R) CPU E7-8880 v3 @ 2.30GHz and 792 Gb of RAM; we use at most 72 of these CPUs.
 
@@
 These can be computed highly efficiently and in parallel.
+Computing the power spectrum of 200 micrographs took less than 23 seconds.
 
@@
 In all experiments, the algorithm halted after a fixed number of 2000 iterations.
+Running the RRR took about 3 seconds.
+
+The computational complexity scales as $O(N^2L^2 + F(L))$, where $F$ is the complexity of the RRR algorithm and $N^2$ stands for the total number of pixels across micrographs.
 
@@
 If multiple GPUs are available, segments can of course be handled in parallel.
+\TODO{Do we use GPUs? Running times}
 
@@
 
+The computational complexity scales as $O(NL^2 + F(L))$, where $F$ is the complexity of the solving the LS.
+
 \paragraph{3-D experiments.}
-
+\TODO{We need to add running times}
 For the experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
@@
 The LS problem was solved using Matlab's \texttt{lsqnonlin} solver for nonlinear LS problems. The expected $\hat \gamma$ in this experiment is one.
+
+The computational complexity scales as $O(N^2L^6+ F(L))$, where $F$ is the complexity of the solving the LS and $N^2$ is the total number of pixels across micrographs.
+The factor of $L^6$ comes from \TODO{to continue}
 
@@
 
-\section{Autocorrelations of the cryo-EM problem} \label{sec:ac_cryo}
+\section{Autocorrelations for the cryo-EM problem} \label{sec:ac_cryo}
 
@@
 \end{equation}
-where $c$ is the bandlimit, $\{S_l\}$ are determined using the Nyquist criterion as described in~\cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
+where $c$ is the bandlimit, $\{S(\ell)\}$ \TODO{to check consistency of $S_l$} are determined using the Nyquist criterion as described in~\cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by \TODO{Amit: why 2?
+}
 \[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
@@
 the complex spherical harmonics $Y_{\ell}^m$ defined by  
-\[ Y_{\ell}^m(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
+\[ Y_{\ell}^m(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{\iota m\varphi},\]
 where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
@@
 Let $I_{\omega}$ denote the tomographic projection obtained from viewing direction $\omega\in SO(3)$.
-By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}:
+By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}: \TODO{Amit: why c is missing here?
+(it appears in [23])}
 \begin{equation*}\label{eq:projection_model}
@@
 it is desirable in~\eqref{eq:ac_micrographs} to average over all in-plane rotations as well.
-This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs).  We use autocorrelations up to and including the  third order since this is necessary to  determine the volume.
+This can be done efficiently using Prolate Spheroidal Wave Functions (PSWFs).
+We use autocorrelations up to and including the  third order.
+Indeed, second-order autocorrelations are not enough, as was observed already in~\cite{kam1980reconstruction} for a simpler problem where the input is not micrographs but rather picked, perfectly centered particles.
+
+this is necessary to  determine the volume.
 

### 2018-09-07 pnas/Towards.tex
no message

@@
 % Please add here a significance statement to explain the relevance of your work
-\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
-The Significance Statement appears in the paper itself and is required for all research papers.}
+\significancestatement{A common states that small molecules cannot be reconstructed using cryo-EM. In this paper, we show that this argument is flaw and show }
 
@@
 \begin{abstract}
+
 Please provide an abstract of no more than 250 words in a single paragraph.
@@
 Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
+\revised{The code to generate all figures is publicly available in TKTK.}
 
@@
 \section*{Acknowledgment}
-The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, and Fred Sigworth for supplying us with the dataset of the BPTI molecule.
+The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, Fred Sigworth for supplying us with the dataset of the BPTI molecule,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
  The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
@@
 Indeed, second-order autocorrelations are not enough, as was observed already in~\cite{kam1980reconstruction} for a simpler problem where the input is not micrographs but rather picked, perfectly centered particles.
-
-this is necessary to  determine the volume.
 

### 2018-09-07 pnas/Towards.tex
Before ;erging of finql pqper concerns in the discussion

@@
 % Please add here a significance statement to explain the relevance of your work
-\significancestatement{A common states that small molecules cannot be reconstructed using cryo-EM. In this paper, we show that this argument is flaw and show }
+\significancestatement{It is commonly believed that cryo-EM cannot be used to image the 3-D structure of small molecules (below ~50kDa).
+The classical argument is that, due to the high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs.
+Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure reconstruction.
+Our reconstruction method is based on autocorrelation analysis.
+It requires only one pass over the data, so that it should, in principle, be appropriate for high-throughput experiments.
+This autocorrelation approach could also apply to other applications where the goal is estimation rather than detection.
+}
 
@@
 %\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
-\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}
+\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu}
 
@@
 As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
-First, we assume an additive white noise model, while in practice the noise may be correlated or signal dependent.
-To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods.
-% and to extend the autocorrelation analysis accordingly.
+First, we assume an additive white noise model, while in practice the noise may be colored.
+In that case, the general strategy would remain the same: establish a forward model expressing the expected autocorrelations of the micrographs in terms of the target volume, its density in the micrograph and the noise statistics (which would now involve more than the single parameter $\sigma^2$).
+%To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
 Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
@@
 We hope to take care of these issues in future research, as well as to extend the proposed method to conformational heterogeneity.
+
+\
+% Bibliography
+\bibliography{ref}
 
@@
 \TODO{Correct bib}
-
-% Bibliography
-\bibliography{ref}
 

### 2018-09-07 pnas/Towards.tex
Revised the discussion to list aspects of cryo data we did not handle; removed discussion of ice crystals

@@
 Beyond data acquisition and computational challenges, there are modeling issues to consider.
-As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
-First, we assume an additive white noise model, while in practice the noise may be colored.
-In that case, the general strategy would remain the same: establish a forward model expressing the expected autocorrelations of the micrographs in terms of the target volume, its density in the micrograph and the noise statistics (which would now involve more than the single parameter $\sigma^2$).
+In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; their may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
+All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects.
+For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$.
+The separation condition could be relaxed by assuming a Poisson process of particle distribution in the micrograph, in which case the forward model will involve the Poisson parameter.
 %To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
-Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
-We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
+%Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
+%We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
 %Such a condition can be met in practice by careful experimental design. 
-
-We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformly distributed viewing directions and other contaminants in the micrographs, such as ice crystals.
- All these aspects must be taken into account so the method could be applied on real data.
-We hope to take care of these issues in future research, as well as to extend the proposed method to conformational heterogeneity.
-
-\
+%
+%We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformly distributed viewing directions and other contaminants in the micrographs, such as ice crystals.
+All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
+
 % Bibliography

### 2018-09-07 pnas/Towards.tex
no message

@@
 % Please add here a significance statement to explain the relevance of your work
-\significancestatement{It is commonly believed that cryo-EM cannot be used to image the 3-D structure of small molecules (below ~50kDa).
-The classical argument is that, due to the high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs.
+\significancestatement{It is commonly believed that cryo-EM cannot be used to image the 3-D structure of small molecules (below $\sim$50kDa).
+The classical argument is that, due to high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs.
 Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure reconstruction.
@@
 Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available as supplementary material.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+Figure~\ref{fig:error_per_micro} (see appendix) presents the normalized recovery error as a function of the amount of data available.
 This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
@@
 Crucially, the LS does not require  knowledge of $\sigma$.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.28]{Einstein_recovery_error_combined}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
-
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[scale=0.7]{1D_example}
-	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
-The length of the micrograph was set to be $N = 410*M$.
-The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
-		The true value of $\gamma$ is $0.0512$.
-		   The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
-	}
-\end{figure*}
 
@@
 This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
-Figure~\ref{fig:cryo_detection} presents excerpts  of two noisy micrographs, only one of which contains projections.
+Figure~\ref{fig:cryo_detection} (see appendix) presents excerpts  of two noisy micrographs, only one of which contains projections.
 In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[scale=0.28]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+\end{figure}
+
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated micrographs of size $4096\times 4096$ pixels. 
@@
 \paragraph{1-D experiment.}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\linewidth]{1D_example}
+	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
+The length of the micrograph was set to be $N = 410*M$.
+The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
+		The true value of $\gamma$ is $0.0512$.
+		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
+	}
+\end{figure*}
+
 For the 1-D experiment depicted in Figure~\ref{fig:1D_example}, we used a signal of length $L=21$ and generated an observation $y$ of length $N = 10(2L-1)M$, where $M$ is the number of repetitions. 
@@
 \paragraph{3-D experiments.}
-\TODO{We need to add running times}
+\TODO{We need to add description of computer + running times}
 For the experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.

### 2018-09-07 pnas/Towards.tex
updated ref and beginning of Sec 2

@@
 		\includegraphics[scale=0.35]{Einstien_progress_1}
-		\caption{$500$ micrographs \TODO{Tamir: I am redo the exp}}
+		\caption{$500$ micrographs \TODO{Tamir: I am redoing the exp}}
 	\end{subfigure} 
@@
 \section{The detection limit} \label{sec:detectionlimit}
-
-At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
-However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
-
+% Can be added to an arxiv version
+%At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
+%However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
+In the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
 To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise.

### 2018-09-07 pnas/Towards.tex
additional editings

@@
 		\includegraphics[scale=0.35]{Einstien_progress_1}
-		\caption{$500$ micrographs \TODO{Tamir: I am redoing the exp}}
+		\caption{$500$ micrographs}
 	\end{subfigure} 
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}
+Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.
+\TODO{Tamir: I am redoing the exp}}
 \end{figure*}
@@
 For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-Explicitly, the first-, second- and third-order autocorrelations are given by: %\TODO{we may want to remove these explicit formulas}
-\begin{align} 
-a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-\end{align}
-The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-$
+%This part can be added to an arxiv version of the manuscript
+%Explicitly, the first-, second- and third-order autocorrelations are given by: %\TODO{we may want to remove these explicit formulas}
+%\begin{align} 
+%a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+%a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
+%a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
+%\end{align}
+%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+%$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+%$
 
@@
 First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
+The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
 %
@@
 \end{proposition}
-\begin{proof}
-In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
+%\begin{proof}
+%In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
 Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
 The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
-%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
-\end{proof}
+%%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
+%\end{proof}
 
@@
 In particular, this means that we can recover
-almost all signals with the given measurements.
+almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
 
@@
 If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
-	\begin{proof}
-		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-	\end{proof}
+%	\begin{proof}
+%		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
+%	\end{proof}
 \end{proposition}
@@
 	%Let $K=1$ and $\sigma > 0$ be fixed.
-	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
-	\begin{itemize}
-		\item Either the signal $x$ is generic; or
-		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-	\end{itemize}
+	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
 \end{corollary}
+
+%This can be added to an arxiv version of the paper	
+%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
+%\begin{corollary}
+%	%Let $K=1$ and $\sigma > 0$ be fixed.
+%	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
+%	\begin{itemize}
+%		\item Either the signal $x$ is generic; or
+%		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+%	\end{itemize}
+%\end{corollary}
 %
@@
 Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
-\revised{The code to generate all figures is publicly available in TKTK.}
+The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
 
@@
 On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
-
-\begin{figure*}[t!]
-	\centering
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.eps}
-		\caption{An excerpt of the pure noise micrograph}
-	\end{subfigure} \hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{noisy_micrograph_cutout.eps}
-		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
-	\end{subfigure} \hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{clean_micrograph_cutout.eps}
-		\caption{An excerpt of the clean micrograph}
-	\end{subfigure}
-	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from a volume of size $31^3$.
-The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs.
-\TODO{Diagonal line} \TODO{Amit: need to specify which molecule is projected to create micrographs shown in (b) and (c).
-This is not mentioned in the text either.
-}}
-\end{figure*}
 
@@
 \end{figure}
+
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.eps}
+		\caption{An excerpt of the pure noise micrograph}
+	\end{subfigure} \hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{noisy_micrograph_cutout.eps}
+		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
+	\end{subfigure} \hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{clean_micrograph_cutout.eps}
+		\caption{An excerpt of the clean micrograph}
+	\end{subfigure}
+	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from a volume of size $31^3$.
+The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
+		The noise realization is identical in both micrographs.
+\TODO{Diagonal line} \TODO{Amit: need to specify which molecule is projected to create micrographs shown in (b) and (c).
+This is not mentioned in the text either.
+}}
+\end{figure*}
 
@@
 In all cases, the probability of success of the best possible deterministic estimator converges to $\max(q, 1-q)$.
+
+\section{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
+
+In the limit, 
+\begin{equation*}
+(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j].
+\end{equation*}
+ Similarly,  
+ \begin{equation*}
+\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell],
+ \end{equation*}
+and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$. The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$. 
+%%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
 

### 2018-09-07 pnas/Towards.tex
Wrote an abstract

@@
 %\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
-\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu}
+\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu \TODO{Should this be Amit's address?}}
 
 % Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}
+\keywords{Cryo-EM $|$ autocorrelation analysis $|$ detection limit}
 
@@
 \begin{abstract}
-
-Please provide an abstract of no more than 250 words in a single paragraph.
+{C}ryo--electron microscopy (cryo--EM) is used in structural biology to determine the 3-D structure of molecules.
+In a cryo-EM experiment, the microscope produces images called micrographs.
+Projections of the molecule of interest are embedded in the micrographs at unknown locations, and under unknown viewing directions.
+Standard imaging techniques first locate these projections (detection), then reconstruct the 3-D structure from them.
+Unfortunately, high noise levels hinder detection.
+When reliable detection is rendered impossible, the standard techniques fail.
+This is a problem especially for small molecules, which can be particularly hard to detect.
+In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection and independently of the noise level (provided sufficiently many micrographs are acquired).
+As a result, even small molecules should be within reach for cryo-EM.
+To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation-based techniques allow to go directly from the micrographs to the sought signals.
+This involves only one pass over the micrographs, which is desirable for large experiments.
+Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via pattern matching.
+We detail elementary theory for a 1-D version of the simplified model and show how to extend it to 2-D and to single particle reconstruction from synthetic cryo-EM data.
+We show numerical results, then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
+%Please provide an abstract of no more than 250 words in a single paragraph.
 Abstracts should explain to the general reader the major contributions of the article.

### 2018-09-08 pnas/Towards.tex
Added cluster details, running times, complexity, fixed cryo notations, edited micrograph figures

@@
 		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
-		\caption{TPRV1 with cutoff $L=5$}\label{fig:TRPV1_recon}
+		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
 	\end{subfigure}
@@
 		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
-		\caption{BPTI with cutoff $L=2$}\label{fig:BPTI_recon}
+		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
 	\end{subfigure} 
 	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
-		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L$.
-		The reconstruction is shown in gray while the (smoothed) ground truth in yellow.
-\TODO{Amit: I suggest calling the spherical harmonics cutoff $l_max$ rather than L.
-Previously, L is used for the size of the signal or for the size of images LxL.
-So, it is quite confusing to use L in a completely different context.
-You would need to make changes in many other places as well (e.g., eq.(23) and the labels (a) and (b) in this figure, are just two examples), in order to avoid this notation overload.
-	}}
+		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
+		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
 \end{figure}
 
+% -------------- Vertical subfigures: -------------------------------
+
+% \begin{figure}[t!]
+% 	\centering
+% 	\begin{subfigure}{0.3\textwidth}
+% 		\centering
+% 		\includegraphics[scale=0.3]{pure_noise_micrograph_cutout.png}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.3\textwidth}
+% 		\centering
+% 		\includegraphics[scale=0.3]{noisy_micrograph_cutout.png}
+% 	\end{subfigure} 
+% 	\begin{subfigure}{0.3\textwidth}
+% 		\centering
+% 		\includegraphics[scale=0.3]{clean_micrograph_cutout.png}
+% 	\end{subfigure}
+% 	\caption{\label{fig:cryo_detection} (a) An excerpt of the pure noise micrograph ; (b) An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.; (c) An excerpt of the clean micrograph.
+All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule, having size $31^3$.
+The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
+The noise realization is identical in both micrographs.}
+% \end{figure}
+
 \begin{figure*}[t!]
@@
 		\centering
-		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.eps}
+		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
 		\caption{An excerpt of the pure noise micrograph}
@@
 		\centering
-		\includegraphics[scale=0.4]{noisy_micrograph_cutout.eps}
+		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
 		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
@@
 		\centering
-		\includegraphics[scale=0.4]{clean_micrograph_cutout.eps}
+		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
 		\caption{An excerpt of the clean micrograph}
 	\end{subfigure}
-	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from a volume of size $31^3$.
+	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs.
-\TODO{Diagonal line} \TODO{Amit: need to specify which molecule is projected to create micrographs shown in (b) and (c).
-This is not mentioned in the text either.
-}}
+		The noise realization is identical in both micrographs.} 
 \end{figure*}
@@
 \paragraph{3-D experiments.}
-\TODO{We need to add description of computer + running times}
+The experiments in Figure~\ref{fig:cryo_recon}, and the recoveries of $\gamma$ for the experiment in Figure~\ref{fig:cryo_detection}, were performed on a machine with 40 cores of Intel Xeon E5-2698 v4 @ 2.20GHz with 100 GB of RAM, and took ~2 hours per reconstruction.
+The computation of the moments from each micrograph in Figure~\ref{fig:cryo_detection} was performed on a machine with 4 nVidia P100 GPUs with 16 GB of memory each and with 100 GB of RAM.
+It took 3 minutes per micrograph to compute the first three autocorrelations.
+
 For the experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
@@
 
-The computational complexity scales as $O(N^2L^6+ F(L))$, where $F$ is the complexity of the solving the LS and $N^2$ is the total number of pixels across micrographs.
-The factor of $L^6$ comes from \TODO{to continue}
+The computational complexity for the computation of the moments from the micrograph is $O(N^2P^6)$, since we have $N^2$ patches that we extract from the micrograph, and for each patch we perform an expansion in PSWFs with complexity $O(P^3)$ \cite{landa2017steerable}, and then compute the autocorrelations dominated by computation of the bispectrum as in \eqref{eq:third_order_ac_pswf} costing $O(P^6)$.
+The complexity of evaluating the bispecturm using \eqref{eq:ac_3_prolates} after the precomputation takes $O(BP^6)$, where $B$ is the number of entries in the bispectrum.
+Since $B=O(P^3)$ \TODO{It's not directly stated in Boris' paper, but I checked this numerically and makes sense if $k,q=O(P)$}, the total complexity for evaluating the bispectrum is $O(P^9)$.
+That is because, if the number of volume expansion coefficients is $V = O(P^3)$, the dominant step can be written as a matrix-vector multiplication with a matrix of size $BV\times V$ and a vector $V\times 1$, so the cost is $BV^2=O(P^9)$.
+Thus, the complexity of solving the LS problem \eqref{eq:LS_cryo} is $O(KP^9)$ where $K$ is the number of iterations required for the optimizer to converge, since the bispectrum evaluation dominates the cost of each iteration.
 
@@
 The original map has size $192^3$, and was downsampled to size $20^3$.
-To generate the ground truth for our reconstructions, we expanded both volumes as in~\eqref{eq:volume_expansion_app} with cutoff $L = 5$ for TRPV1 and $L = 2$ for BPTI.
+To generate the ground truth for our reconstructions, we expanded both volumes as in~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI.
 For the TRPV1 reconstruction, the optimizer converged to a point giving relative $\ell_2$ error of $10^{-6}$ in the first three autocorrelations and an error of $10^{-1}$ in the expansion coefficients of the volume.
@@
 We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension.
+The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices.
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-\TODO{Nico: is this really how the procedure works?
-Or is it just that after a few failed attempts, we abandon?
-Also, the text doesn't say if the projections are placed at random, but I'm assuming they are ?} Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
+Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
 
@@
 Let $\phi$ be the Coulomb potential representing the molecule we aim to recover. 
-We assume that molecule is real-valued and smooth. In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form 
+We assume that molecule is real-valued and smooth.
+In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form  \TODO{Is it a problem that both our Fourier coordinates and angular frequencies for prolates are called $k$?}
 \begin{equation} \label{eq:volume_expansion_app} 
-\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
+\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^{L_{\text{max}}}\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
 \end{equation}
-where $c$ is the bandlimit, $\{S(\ell)\}$ \TODO{to check consistency of $S_l$} are determined using the Nyquist criterion as described in~\cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by \TODO{Amit: why 2?
-}
-\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
+where $c$ is the bandlimit, $\{S(\ell)\}$ are determined using the Nyquist criterion as described in~\cite{bhamre2017anisotropic}, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
+\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(u_{\ell,s} k),\]
 $j_{\ell}$ is the spherical Bessel function of order $\ell$ and  $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$. We use 
@@
 Let $I_{\omega}$ denote the tomographic projection obtained from viewing direction $\omega\in SO(3)$.
-By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}: \TODO{Amit: why c is missing here?
-(it appears in [23])}
+By the Fourier projection-slice theorem, its 2-D Fourier transform  is given by~\cite{natterer1986mathematics}:
 \begin{equation*}\label{eq:projection_model}
-\widehat I_{\omega}(k,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),
+\widehat I_{\omega}(ck,\varphi) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}D_{m',m}^{\ell}(\omega)Y_{\ell}^{m'}\left(\frac{\pi}{2},\varphi\right)j_{\ell,s}(k),
 \end{equation*}
@@
 \begin{align} \label{eq:third_order_ac_pswf}
-&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right) \nonumber\\
+&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha \nonumber\\
 &= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. \nonumber 
@@
 &I_{\omega}(r,\varphi) = \sum_{N,n}\widehat{\alpha}_{N,n}b_{N,n}(\omega)\psi_{N,n}(r,\varphi)\\
-&= \sum_{\ell=0}^L\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}\tamir_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi), \nonumber 
+&= \sum_{\ell=0}^{L_{\text{max}}}\sum_{N,m=-\ell}^{\ell}\sum_{n=0}^{n_{\text{max}}(N)}\sum_{s=1}^{S(\ell)}\tamir_{\ell,m,s}\widehat\beta_{\ell,s;N,n}D_{N,m}^{\ell}(\omega)\psi_{N,n}(r,\varphi), \nonumber
 \end{align}

### 2018-09-09 pnas/Towards.tex
Editing work + abstract's modification

@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
+\authorcontributions{Please provide details of author contributions here.}
 \authordeclaration{The authors declare no conflicts of interest.}
 %\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
-\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu \TODO{Should this be Amit's address?}}
+\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu %\TODO{Should this be Amit's address?}
+}
 
@@
 \keywords{Cryo-EM $|$ autocorrelation analysis $|$ detection limit}
-
-\renewcommand{\P}{\mathrm{Prob}}
 
@@
 Projections of the molecule of interest are embedded in the micrographs at unknown locations, and under unknown viewing directions.
-Standard imaging techniques first locate these projections (detection), then reconstruct the 3-D structure from them.
+Standard imaging techniques first locate these projections (detection) and then reconstruct the 3-D structure from them.
 Unfortunately, high noise levels hinder detection.
@@
 This is a problem especially for small molecules, which can be particularly hard to detect.
-In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection and independently of the noise level (provided sufficiently many micrographs are acquired).
+In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection.
+% and independently of the noise level (provided sufficiently many micrographs are acquired).
 As a result, even small molecules should be within reach for cryo-EM.
@@
 This involves only one pass over the micrographs, which is desirable for large experiments.
-Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via pattern matching.
-We detail elementary theory for a 1-D version of the simplified model and show how to extend it to 2-D and to single particle reconstruction from synthetic cryo-EM data.
+Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via template matching.
+%We detail elementary theory for a 1-D version of the simplified model and show how to extend it to 2-D and to single particle reconstruction from synthetic cryo-EM data.
 We show numerical results, then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
-%Please provide an abstract of no more than 250 words in a single paragraph.
-Abstracts should explain to the general reader the major contributions of the article.
-References in the abstract must be cited in full within the abstract itself and cited in the text.
+We detail elementary theory for the simplified model and show how to extend it to single particle reconstruction from synthetic cryo-EM data.
+We show numerical results and then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
 \end{abstract}
@@
 By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
+	 \vspace{-14pt} 	
 \end{figure*}
@@
 \TODO{Tamir: I am redoing the exp}}
+ \vspace{-14pt} 
 \end{figure*}
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0.15in}
+\begin{myquote}{0in}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
-Figure~\ref{fig:1D_example} shows recovery of a 1-D signal from the first three autocorrelations of the data.
+Figure~\ref{fig:1D_example} (see appendix) shows recovery of a 1-D signal from the first three autocorrelations of the data.
 The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}. 
@@
 		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
+		 \vspace{-20pt} 	
 \end{figure}
-
 % -------------- Vertical subfigures: -------------------------------
@@
 
-\begin{figure*}[t!]
-	\centering
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
-		\caption{An excerpt of the pure noise micrograph}
-	\end{subfigure} \hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
-		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
-	\end{subfigure} \hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
-		\caption{An excerpt of the clean micrograph}
-	\end{subfigure}
-	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
+%\begin{figure*}[t!]
+%	\centering
+%	\begin{subfigure}[t]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
+%		\caption{An excerpt of the pure noise micrograph}
+%	\end{subfigure} \hspace{2pt}
+%	\begin{subfigure}[t]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
+%		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
+%	\end{subfigure} \hspace{2pt}
+%	\begin{subfigure}[t]{0.3\textwidth}
+%		\centering
+%		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
+%		\caption{An excerpt of the clean micrograph}
+%	\end{subfigure}
+%	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs.} 
-\end{figure*}
+%		The noise realization is identical in both micrographs.} 
+%	 \vspace{-14pt} 	
+%\end{figure*}
 
@@
 The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
-\revised{Amit: to verify.} NB is partially supported by NSF award DMS-1719558.
-\TODO{Correct bib}
+NB is partially supported by NSF award DMS-1719558.
 
@@
 In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ (if the length of the measurement is larger than that) and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+%Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
 If multiple GPUs are available, segments can of course be handled in parallel.
-\TODO{Do we use GPUs? Running times}
 
@@
 The computational complexity scales as $O(NL^2 + F(L))$, where $F$ is the complexity of the solving the LS.
+For example, computing the moments for the experiment in the left panel of Figure~\ref{fig:1D_example} took 38 seconds, while the optimization took 5.5 seconds in total.
 
 \paragraph{3-D experiments.}
+
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
+		\caption{An excerpt of the pure noise micrograph}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
+		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
+		\caption{An excerpt of the clean micrograph}
+	\end{subfigure}
+	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
+The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
+		The noise realization is identical in both micrographs.} 
+\end{figure*}
+
 The experiments in Figure~\ref{fig:cryo_recon}, and the recoveries of $\gamma$ for the experiment in Figure~\ref{fig:cryo_detection}, were performed on a machine with 40 cores of Intel Xeon E5-2698 v4 @ 2.20GHz with 100 GB of RAM, and took ~2 hours per reconstruction.
@@
 
-The computational complexity for the computation of the moments from the micrograph is $O(N^2P^6)$, since we have $N^2$ patches that we extract from the micrograph, and for each patch we perform an expansion in PSWFs with complexity $O(P^3)$ \cite{landa2017steerable}, and then compute the autocorrelations dominated by computation of the bispectrum as in \eqref{eq:third_order_ac_pswf} costing $O(P^6)$.
+The computational complexity for the computation of the moments from the micrograph is $O(N^2P^6)$, since we have $N^2$ patches that we extract from the micrograph.
+For each patch we perform an expansion in PSWFs with complexity $O(P^3)$ \cite{landa2017steerable}, and then compute the autocorrelations dominated by computation of the bispectrum as in \eqref{eq:third_order_ac_pswf} costing $O(P^6)$.
 The complexity of evaluating the bispecturm using \eqref{eq:ac_3_prolates} after the precomputation takes $O(BP^6)$, where $B$ is the number of entries in the bispectrum.
-Since $B=O(P^3)$ \TODO{It's not directly stated in Boris' paper, but I checked this numerically and makes sense if $k,q=O(P)$}, the total complexity for evaluating the bispectrum is $O(P^9)$.
+Since $B=O(P^3)$, the total complexity for evaluating the bispectrum is $O(P^9)$.
 That is because, if the number of volume expansion coefficients is $V = O(P^3)$, the dominant step can be written as a matrix-vector multiplication with a matrix of size $BV\times V$ and a vector $V\times 1$, so the cost is $BV^2=O(P^9)$.
@@
 Let $\phi$ be the Coulomb potential representing the molecule we aim to recover. 
-We assume that molecule is real-valued and smooth.
-In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form  \TODO{Is it a problem that both our Fourier coordinates and angular frequencies for prolates are called $k$?}
+We assume that molecule is real-valued and smooth. In spherical coordinates, its 3-D Fourier transform $\widehat\phi$ admits a finite expansion of the form
 \begin{equation} \label{eq:volume_expansion_app} 

### 2018-09-10 pnas/Towards.tex
Revised files. Will be sent to Amit for a second round (and maybe to Fred)

@@
 	\centering
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_clean}
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_clean}
 		\caption{$\sigma = 0$}
 	\end{subfigure}%
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_s05}
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s05}
 		\caption{$\sigma = 0.5$}
 	\end{subfigure}
-	\begin{subfigure}[h]{0.33\textwidth}
-		\centering
-		\includegraphics[scale=0.5]{micrograph_Einstein_example_s3}
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s3}
 		\caption{$\sigma = 3$}
@@
 By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
-	 \vspace{-14pt} 	
+	\vspace{-12pt} 	
 \end{figure*}
@@
 	\centering
-	\begin{subfigure}[h]{0.24\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_1}
-		\caption{$500$ micrographs}
-	\end{subfigure} 
-	\begin{subfigure}[h]{0.24\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_4}
+	\begin{subfigure}[h]{0.24\linewidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Einstien_progress_1}
+		\caption{$2\times 10^2$ micrographs}
+	\end{subfigure} \hfill
+	\begin{subfigure}[h]{0.24\linewidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Einstien_progress_4}
 		\caption{$2\times 10^3$ micrographs}
-	\end{subfigure} 
-	\begin{subfigure}[h]{0.24\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_40}
+	\end{subfigure} \hfill
+	\begin{subfigure}[h]{0.24\linewidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Einstien_progress_40}
 		\caption{$2\times 10^4$ micrographs}
-	\end{subfigure} 
-	\begin{subfigure}[h]{0.24\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{Einstien_progress_400}
+	\end{subfigure} \hfill
+	\begin{subfigure}[h]{0.24\linewidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Einstien_progress_400}
 		\caption{$2\times 10^5$ micrographs}
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.
-\TODO{Tamir: I am redoing the exp}}
- \vspace{-14pt} 
+Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}
+	\vspace{-12pt} 
 \end{figure*}
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0in}
+\begin{myquote}{0.1in}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 The question is, can we do better than this?
-We prove that, as $\sigma \to \infty$, the answer is no:
+We prove that, as $\sigma \to \infty$, the answer is no.
+The result is proved in Appendix~\ref{sec:proof_two_gauss}.
 \begin{proposition} \label{prop:two_gauss}
@@
 \end{proposition}
-\noindent The result is proved in Appendix~\ref{sec:proof_two_gauss}.
 
@@
 
+%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
+%\begin{corollary}
+%	%Let $K=1$ and $\sigma > 0$ be fixed.
+%	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+%\end{corollary}
+
+%This can be added to an arxiv version of the paper	
 From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
@@
 	%Let $K=1$ and $\sigma > 0$ be fixed.
-	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
+	\begin{itemize}
+		\item Either the signal $x$ is generic; or
+		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+	\end{itemize}
 \end{corollary}
-
-%This can be added to an arxiv version of the paper	
-%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
-%\begin{corollary}
-%	%Let $K=1$ and $\sigma > 0$ be fixed.
-%	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
-%	\begin{itemize}
-%		\item Either the signal $x$ is generic; or
-%		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-%	\end{itemize}
-%\end{corollary}
 %
@@
 	\centering
-	\includegraphics[scale=0.28]{Einstein_recovery_error_combined}
+	\includegraphics[width=\linewidth]{Einstein_recovery_error_combined}
 	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
@@
 Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
+
+\section{Proof of Proposition~\ref{prop:two_gauss}} \label{sec:proof_two_gauss}
+
+The proof is based on  a variant of the Neyman--Pearson Lemma to derive the best (deterministic) estimator $\hat{\eta}$.
+Take any estimator $\hat{\eta}$; it is characterized by $S$: the set of $X$'s where $\hat{\eta} = 1$, where $X$ is a random vector as defined above Proposition~\ref{prop:two_gauss}.
+We write $\P_i$ to mean the probability conditional on the event $\eta = i$; that is, $\P_i[A] = \P[A | \eta = i]$.
+Then, the probability that $\hat{\eta}$ fails is:
+%
+\begin{align}
+\label{eq:neyman-pearson}
+%
+\P[\hat{\eta} \ne \eta] 
+&= q \P_0[\hat{\eta} = 1 ] + (1-q) \P_1[\hat{\eta} = 0]
+\nonumber \\
+&= q \P_0[\hat{\eta} = 1] + (1-q) (1 - \P_1[\hat{\eta} = 1])
+\nonumber \\
+&= q \P_0[\hat{\eta} = 1] + (1-q) - (1-q) \P_1[\hat{\eta} = 1]
+\nonumber \\
+&= (1-q)  + \int_S (q f_0(x) - (1-q) f_1(x))dx,
+%
+\end{align}
+%
+where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$. 
+The best estimator of $\eta$ based on $X$ minimizes the failure probability; hence, it minimizes the integral in~\eqref{eq:neyman-pearson} through an appropriate choice of the set $S$.
+This is achieved by picking all $x$'s such that the integrand is nonpositive:
+\begin{align*}
+%
+S & = \left\{x : qf_0(x) - (1-q)f_1(x) \leq 0 \right\}.
+%
+\end{align*}
+%
+With $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, the corresponding estimator is:
+\begin{align*}
+%
+\hat{\eta} = 
+\begin{cases}
+1  \text{ if } \Lambda(x) \leq b, \\
+0  \text{ if } \Lambda(x) > b.
+\end{cases}
+%
+\end{align*}
+Taking logarithms, the set $S$ can be rewritten as the set of $x$'s where:
+\begin{align*}
+%
+-\| x - \theta_0\|^2 \le - \|x - \theta_1\|^2 + 2 \sigma^2 \log(b),
+%
+\end{align*}
+%
+or equivalently
+%
+\begin{align*}
+%
+\langle x , \theta_1 - \theta_0 \rangle 
+\ge \frac{\|\theta_1\|^2 - \|\theta_0\|^2}{2} - \sigma^2 \log(b).
+%
+\end{align*}
+%
+Now let us compute the probability of failure conditional on the event $\eta = 0$.
+In this case, failure occurs when $X \in S$.
+Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,I)$.
+On that condition,
+%
+\begin{align*}
+%
+\langle X , \theta_1 - \theta_0 \rangle 
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
++ \langle \theta_0,\theta_1 - \theta_0 \rangle
+\nonumber \\
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
++ \langle \theta_0,\theta_1 \rangle - \|\theta_0\|^2,
+%
+\end{align*}
+%
+and failure occurs when 
+%
+\begin{align*}
+%
+\sigma\langle Z, \theta_1 - \theta_0 \rangle 
+&\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
+- \sigma^2 \log(b)
+\nonumber \\
+&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b).
+%
+\end{align*}
+%
+Define $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$ and divide through by $\sigma$. The above event is equivalent to:
+%
+\begin{align*}
+%
+Y \ge \frac{c}{\sigma} - \sigma \log(b),
+%
+\end{align*}
+%
+where $c = \|\theta_1 - \theta_0\|^2 / 2$. 
+For simplicity, let us assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$. Then, 
+%
+\begin{align*}
+%
+\P_0[\hat{\eta} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right],
+\quad Y \sim N(0,1).
+%
+\end{align*}
+%
+Similarly,
+%
+\begin{align*}
+%
+\P_1[\hat{\eta} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right],
+\quad Y \sim N(0,1).
+%
+\end{align*}
+%
+Thus, the overall probability of failure is:
+%
+\begin{multline*}
+%
+\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \\
++ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
+%\
+\end{multline*}
+%
+Now, if $q = 1/2$, then $\log(b) = 0$. Hence the probability of failure is simply:
+%
+\begin{align*}
+%
+\P\left[Y \ge \frac{c}{\sigma} \right] \longrightarrow \frac{1}{2} = q
+\quad \text{as} \quad \sigma \to \infty.
+%
+\end{align*}
+If $q > 1/2$, then $q > 1-q$ and $\log(b) < 0$. Consequently, 
+%
+\begin{align*}
+%
+\P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \longrightarrow 0,
+%
+\end{align*}
+%
+while
+%
+\begin{align*}
+%
+\P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right] \longrightarrow 1,
+%
+\end{align*}
+%
+as $\sigma \to \infty$. Hence,
+%
+\begin{align*}
+%
+\P[\hat{\eta} \ne \eta]
+%&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
+%+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
+%\nonumber\\
+& \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
+%
+\end{align*}
+That is, the probability of success converges to $q$.
+Finally, if $q < 1/2$, then $\log(b) > 0$ and a similar reasoning shows the probability of success converges to $1-q$.
+In all cases, the probability of success of the best possible deterministic estimator converges to $\max(q, 1-q)$.
 
@@
 Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
-
 This completes the proof.
-
-\section{Proof of Proposition~\ref{prop:two_gauss}} \label{sec:proof_two_gauss}
-
-The proof is based on  a variant of the Neyman--Pearson Lemma to derive the best (deterministic) estimator $\hat{\eta}$.
-Take any estimator $\hat{\eta}$; it is characterized by $S$: the set of $X$'s where $\hat{\eta} = 1$, where $X$ is a random vector as defined above Proposition~\ref{prop:two_gauss}.
-We write $\P_i$ to mean the probability conditional on the event $\eta = i$; that is, $\P_i[A] = \P[A | \eta = i]$.
-Then, the probability that $\hat{\eta}$ fails is:
-%
-\begin{align}
-\label{eq:neyman-pearson}
-%
-\P[\hat{\eta} \ne \eta] 
-&= q \P_0[\hat{\eta} = 1 ] + (1-q) \P_1[\hat{\eta} = 0]
-\nonumber \\
-&= q \P_0[\hat{\eta} = 1] + (1-q) (1 - \P_1[\hat{\eta} = 1])
-\nonumber \\
-&= q \P_0[\hat{\eta} = 1] + (1-q) - (1-q) \P_1[\hat{\eta} = 1]
-\nonumber \\
-&= (1-q)  + \int_S (q f_0(x) - (1-q) f_1(x))dx,
-%
-\end{align}
-%
-where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$. 
-The best estimator of $\eta$ based on $X$ minimizes the failure probability; hence, it minimizes the integral in~\eqref{eq:neyman-pearson} through an appropriate choice of the set $S$.
-This is achieved by picking all $x$'s such that the integrand is nonpositive:
-\begin{align*}
-%
-S & = \left\{x : qf_0(x) - (1-q)f_1(x) \leq 0 \right\}.
-%
-\end{align*}
-%
-With $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, the corresponding estimator is:
-\begin{align*}
-%
-\hat{\eta} = 
-\begin{cases}
-1  \text{ if } \Lambda(x) \leq b, \\
-0  \text{ if } \Lambda(x) > b.
-\end{cases}
-%
-\end{align*}
-Taking logarithms, the set $S$ can be rewritten as the set of $x$'s where:
-\begin{align*}
-%
--\| x - \theta_0\|^2 \le - \|x - \theta_1\|^2 + 2 \sigma^2 \log(b),
-%
-\end{align*}
-%
-or equivalently
-%
-\begin{align*}
-%
-\langle x , \theta_1 - \theta_0 \rangle 
-\ge \frac{\|\theta_1\|^2 - \|\theta_0\|^2}{2} - \sigma^2 \log(b).
-%
-\end{align*}
-%
-Now let us compute the probability of failure conditional on the event $\eta = 0$.
-In this case, failure occurs when $X \in S$.
-Since $X|(\eta=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\eta=0) = \sigma Z + \theta_0$, where $Z \sim N(0,I)$.
-On that condition,
-%
-\begin{align*}
-%
-\langle X , \theta_1 - \theta_0 \rangle 
-&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
-+ \langle \theta_0,\theta_1 - \theta_0 \rangle
-\nonumber \\
-&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
-+ \langle \theta_0,\theta_1 \rangle - \|\theta_0\|^2,
-%
-\end{align*}
-%
-and failure occurs when 
-%
-\begin{align*}
-%
-\sigma\langle Z, \theta_1 - \theta_0 \rangle 
-&\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
-- \sigma^2 \log(b)
-\nonumber \\
-&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b).
-%
-\end{align*}
-%
-Define $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$ and divide through by $\sigma$. The above event is equivalent to:
-%
-\begin{align*}
-%
-Y \ge \frac{c}{\sigma} - \sigma \log(b),
-%
-\end{align*}
-%
-where $c = \|\theta_1 - \theta_0\|^2 / 2$. 
-For simplicity, let us assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$. Then, 
-%
-\begin{align*}
-%
-\P_0[\hat{\eta} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right],
-\quad Y \sim N(0,1).
-%
-\end{align*}
-%
-Similarly,
-%
-\begin{align*}
-%
-\P_1[\hat{\eta} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right],
-\quad Y \sim N(0,1).
-%
-\end{align*}
-%
-Thus, the overall probability of failure is:
-%
-\begin{multline*}
-%
-\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \\
-+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
-%\
-\end{multline*}
-%
-Now, if $q = 1/2$, then $\log(b) = 0$. Hence the probability of failure is simply:
-%
-\begin{align*}
-%
-\P\left[Y \ge \frac{c}{\sigma} \right] \longrightarrow \frac{1}{2} = q
-\quad \text{as} \quad \sigma \to \infty.
-%
-\end{align*}
-If $q > 1/2$, then $q > 1-q$ and $\log(b) < 0$. Consequently, 
-%
-\begin{align*}
-%
-\P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \longrightarrow 0,
-%
-\end{align*}
-%
-while
-%
-\begin{align*}
-%
-\P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right] \longrightarrow 1,
-%
-\end{align*}
-%
-as $\sigma \to \infty$. Hence,
-%
-\begin{align*}
-%
-\P[\hat{\eta} \ne \eta]
-%&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
-%+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
-%\nonumber\\
-& \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
-%
-\end{align*}
-That is, the probability of success converges to $q$.
-Finally, if $q < 1/2$, then $\log(b) > 0$ and a similar reasoning shows the probability of success converges to $1-q$.
-In all cases, the probability of success of the best possible deterministic estimator converges to $\max(q, 1-q)$.
 

### 2018-09-10 pnas/Towards.tex
small update of the acknowledgment

@@
 \section*{Acknowledgment}
-The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, Fred Sigworth for supplying us with the dataset of the BPTI molecule,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
+The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
 The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.

### 2018-09-10 pnas/Towards.tex
Added third column to Fig. 3 with original molecules

@@
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-		The reconstruction is shown in gray while the (smoothed) ground truth in yellow. }
+		The reconstruction is shown in gray, the (smoothed) ground truth in yellow, and the original molecules are shown in blue to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
+}
 		 \vspace{-20pt} 	

### 2018-09-10 pnas/Towards.tex
no message

@@
 
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
+\begin{corollary}
+	%Let $K=1$ and $\sigma > 0$ be fixed.
+	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+\end{corollary}
+%
+%%This can be added to an arxiv version of the paper	
 %From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
@@
 %	%Let $K=1$ and $\sigma > 0$ be fixed.
-%	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+%	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
+%	\begin{itemize}
+%		\item Either the signal $x$ is generic; or
+%		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+%	\end{itemize}
 %\end{corollary}
-
-%This can be added to an arxiv version of the paper	
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
-\begin{corollary}
-	%Let $K=1$ and $\sigma > 0$ be fixed.
-	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
-	\begin{itemize}
-		\item Either the signal $x$ is generic; or
-		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-	\end{itemize}
-\end{corollary}
 %
@@
 
-% Bibliography
-\bibliography{ref}
-
 \section*{Acknowledgment}
@@
 NB is partially supported by NSF award DMS-1719558.
+
+% Bibliography
+\bibliography{ref}
 

### 2018-09-10 pnas/Towards.tex
small editing

@@
 \ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+\setlength{\abovedisplayskip}{2pt}
+\setlength{\belowdisplayskip}{2pt}
 
@@
 	\centering
-	\begin{subfigure}[h]{0.24\linewidth}
-		\centering
-		\includegraphics[width=1.1\linewidth]{Einstien_progress_1}
-		\caption{$2\times 10^2$ micrographs}
-	\end{subfigure} \hfill
-	\begin{subfigure}[h]{0.24\linewidth}
-		\centering
-		\includegraphics[width=1.1\linewidth]{Einstien_progress_4}
-		\caption{$2\times 10^3$ micrographs}
-	\end{subfigure} \hfill
-	\begin{subfigure}[h]{0.24\linewidth}
-		\centering
-		\includegraphics[width=1.1\linewidth]{Einstien_progress_40}
-		\caption{$2\times 10^4$ micrographs}
-	\end{subfigure} \hfill
-	\begin{subfigure}[h]{0.24\linewidth}
-		\centering
-		\includegraphics[width=1.1\linewidth]{Einstien_progress_400}
-		\caption{$2\times 10^5$ micrographs}
-	\end{subfigure}
+	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
 	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}
+Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right), each containing $700$ image occurrences on average.}
 	\vspace{-12pt} 
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0.1in}
+\begin{myquote}{0in}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
-This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}
+, just to name a few. 
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.

### 2018-09-12 Notes/notes_Will.tex
Editing

--- 2018-05-14 TEX/notes_will/notes_moments/notes.tex
@@
 
+\newcommand{\R}{\mathbb{R}}
+
 \newcommand{\LL}{\mathcal{L}}
@@
 \newcommand{\mean}[2]{\frac{1}{#1}\sum_{#2=1}^{#1}}
+
+\renewcommand{\P}{\mathbb{P}}
 
@@
 
+\section{Impossibility of detection}
+
+Let's consider an even easier problem, in which someone hands us intervals of length $L$ that either contain the full signal plus noise, or contain just noise, and we are asked to determine which intervals contain signal.
+Let's assume too that we know the signal $x$, that we know the probability $q$ that one of the intervals contains a signal, and that we know the noise variance $\sigma$.
+Since we have the full generative model, we can always generate more data as needed; therefore it's enough to consider the hardness of deciding whether a single interval contains signal or not.
+
+Let's abstract this problem.
+We have two known vectors $\theta_0$ and $\theta_1$ in $\R^L$.
+There is a random variable $\ep$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
+We observe a random vector $X \in \R^L$ with the following distribution: $X | (\ep = i) \sim N(\theta_i,\sigma^2)$; in other words, if $\ep = 0$, then $X \sim N(\theta_0,\sigma^2)$, and if $\ep = 1$, then $X \sim N(\theta_1,\sigma^2)$.
+
+We observe $X$, and our task is to predict $\ep$.
+How well can we do it?
+First, let's assume without loss of generality that $q \ge 1-q$.
+Then if we make the constant prediction $\hat{\ep} \equiv 0$, we will be correct with probability $q$.
+So the question is, can we do better than this?
+We will prove that as $\sigma \to \infty$, the answer is no.
+More precisely:
+
+\begin{prop}
+Let $\hat{\ep}$ be any predictor of $\ep$. Then 
+%
+\begin{align}
+%
+\lim_{\sigma \to \infty} \P[ \hat{\ep} = \ep ] \le q.
+%
+\end{align}
+
+\end{prop}
+
+To begin the proof, we use a variant of the Neyman-Pearson Lemma to derive the best (deterministic) predictor $\hat{\ep}$.
+We take any predictor $\hat{\ep}$, and we let $S$ be the set of $X$'s where $\hat{\ep} = 1$.
+Then the probability that $\hat{\ep}$ fails is:
+%
+\begin{align}
+\label{eq:neyman-pearson}
+%
+\P[\hat{\ep} \ne \ep] 
+&= q \P_0[\hat{\ep} = 1 ] + (1-q) \P_1[\hat{\ep} = 0]
+    \nonumber \\
+&= q \P_0[\hat{\ep} = 1] + (1-q) (1 - \P_1[\hat{\ep} = 1])
+    \nonumber \\
+&= q \P_0[\hat{\ep} = 1] + (1-q) - (1-q) \P_1[\hat{\ep} = 1]
+    \nonumber \\
+&= (1-q)  + \int_S (q f_0(x) - (1-q) f_1(x))dx,
+%
+\end{align}
+%
+where $f_i(x)$ is the normal density with mean $\theta_i$ and variance $\sigma^2$, and the notation $\P_i$ means probability conditional on the event $\ep = \theta_i$; that is, $\P_i[A] = \P[A | \ep=i]$.
+The integral \eqref{eq:neyman-pearson} is minimized by taking $S$ to be the set:
+%
+\begin{align}
+%
+S = \left\{x : \frac{f_0(x)}{f_1(x)} \le \frac{1-q}{q} \right\}.
+%
+\end{align}
+%
+In other words, if $\Lambda(x) = f_0(x) / f_1(x)$ and $b = (1-q) / q$, then the best predictor of $\ep$ based on $X$ is:
+%
+\begin{align}
+%
+\ep = 
+\begin{cases}
+1,  \text{ if } \Lambda(x) \le b \\
+0,  \text{ if } \Lambda(x) \ge b
+\end{cases}.
+%
+\end{align}
+
+Taking logarithms, the set $S$ can be rewritten as the set of $x$ where:
+\begin{align}
+%
+-\| x - \theta_0\|^2 \le - \|x - \theta_1\|^2 + 2 \sigma^2 \log(b),
+%
+\end{align}
+%
+or equivalently
+%
+\begin{align}
+%
+\langle x , \theta_1 - \theta_0 \rangle 
+    \ge \frac{\|\theta_1\|^2 - \|\theta_0\|^2}{2} - \sigma^2 \log(b).
+%
+\end{align}
+%
+
+Now let's compute the probability of failure conditional on the event $\ep = 0$.
+In this case, failure occurs when $X \in S$.
+Since $X|(\ep=0) \sim N(\theta_0,\sigma^2)$, we can write $X | (\ep=0) = \sigma Z + \theta_0$, where $Z \sim N(0,1)$.
+Consequently,
+%
+\begin{align}
+%
+\langle X , \theta_1 - \theta_0 \rangle 
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
+    + \langle \theta_0,\theta_1 - \theta_0 \rangle
+    \nonumber \\
+&= \sigma \langle Z , \theta_1 - \theta_0 \rangle 
+            + \langle \theta_0,\theta_1 \rangle - \|\theta_0\|^2
+%
+\end{align}
+%
+and failure occurs when 
+%
+\begin{align}
+%
+\sigma\langle Z, \theta_1 - \theta_0 \rangle 
+&\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
+    - \sigma^2 \log(b)
+    \nonumber \\
+&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b)
+%
+\end{align}
+%
+or equivalently
+%
+\begin{align}
+%
+Y \ge \frac{c}{\sigma} - \sigma \log(b)
+%
+\end{align}
+%
+where $c = \|\theta_1 - \theta_0\|^2 / 2$ and $Y = \langle Z , \theta_1 - \theta_0 \rangle \sim N(0,\|\theta_1 - \theta_0\|^2)$.
+Just for simplicity let's assume $\| \theta_1 - \theta_0\| = 1$, so that $Y \sim N(0,1)$.
+So:
+%
+\begin{align}
+%
+\P_0[\hat{\ep} = 1] = \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right],
+    \quad Y \sim N(0,1).
+%
+\end{align}
+%
+Similarly,
+%
+\begin{align}
+%
+\P_1[\hat{\ep} = 0] = \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right],
+    \quad Y \sim N(0,1).
+%
+\end{align}
+%
+So the overall probability of failure is:
+%
+\begin{align}
+%
+\P[\hat{\ep} \ne \ep]
+= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
+    + (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right].
+%
+\end{align}
+%
+Now, if $q = 1/2$, the $b = 1$ and $\log(b) = 0$. Then the probability of failure is simply:
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} \right] \longrightarrow \frac{1}{2} = q
+    \quad \text{as} \quad \sigma \to \infty.
+%
+\end{align}
+
+On the other hand, if $q > 1-q$, then $\log(b) < 0$. Then 
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right] \longrightarrow 0
+%
+\end{align}
+%
+while
+%
+\begin{align}
+%
+\P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right] \longrightarrow 1
+%
+\end{align}
+%
+as $\sigma \to \infty$. Consequently,
+%
+\begin{align}
+%
+\P[\hat{\ep} \ne \ep]
+&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
+    + (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
+    \nonumber\\
+& \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
+%
+\end{align}
+%
+That is, the probability of success converges to $q$, which completes the proof.
+
 \bibliographystyle{plain}

### 2018-09-12 pnas/Towards.tex
Editing

--- 2018-09-10 pnas/Towards.tex
@@
 The classical argument is that, due to high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs.
-Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure reconstruction.
+Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure determination.
 Our reconstruction method is based on autocorrelation analysis.
@@
 % Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Please provide details of author contributions here.}
+\authorcontributions{Author contributions: T.B., N.B., W.L., E.L., and A.S., designed research, performed research and wrote the paper; E.L.
+wrote the  computer code for the cryo-EM experiments;  N.B.
+and T.B.
+wrote the computer code for the 1-D and 2-D numerical experiments.
+Authors are listed alphabetically.
+}
 \authordeclaration{The authors declare no conflicts of interest.}
@@
 \begin{abstract}
-{C}ryo--electron microscopy (cryo--EM) is used in structural biology to determine the 3-D structure of molecules.
+%{C}ryo--electron microscopy (cryo--EM) is used in structural biology to determine the 3-D structure of molecules. 
+Single-particle cryo-electron microscopy (cryo-EM) has recently joined X-ray crystallography
+and NMR spectroscopy as a high-resolution structural method for biological macromolecules.
 In a cryo-EM experiment, the microscope produces images called micrographs.
@@
 As a result, even small molecules should be within reach for cryo-EM.
-To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation-based techniques allow to go directly from the micrographs to the sought signals.
+To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation analysis technique allows to go directly from the micrographs to the sought signals.
 This involves only one pass over the micrographs, which is desirable for large experiments.
-Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via template matching.
-%We detail elementary theory for a 1-D version of the simplified model and show how to extend it to 2-D and to single particle reconstruction from synthetic cryo-EM data.
-We show numerical results, then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
-We detail elementary theory for the simplified model and show how to extend it to single particle reconstruction from synthetic cryo-EM data.
-We show numerical results and then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
+%Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via template matching. 
+%We detail elementary theory for the simplified model and show how to extend it to single particle reconstruction from synthetic cryo-EM data.
+We show numerical results and  discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
 \end{abstract}
@@
 
-\dropcap{C}ryo--electron microscopy (cryo--EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
+%\setlength{\abovedisplayskip}{2pt}
+%\setlength{\belowdisplayskip}{2pt}
+
+\begin{bibunit}
+
+\dropcap{C}ryo-electron microscopy (cryo-EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. %Within the ice, the molecules are randomly oriented and positioned.
@@
 By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
-	\vspace{-12pt} 	
+	%\vspace{-8pt} 	
 \end{figure*}
@@
 A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}
-	\vspace{-12pt} 
+Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
+%	\vspace{-8pt} 
 \end{figure*}
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0.1in}
+\begin{myquote}{.2in}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
-Yet, imaging such molecules is important for a number of applications~\cite{scapin2018cryo}
+Yet, imaging such molecules is important for structure-guided drug design and other applications~\cite{scapin2018cryo}.
 
@@
 Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
-\begin{align}
-y & =  x \ast s + \varepsilon, & \varepsilon & \sim \mathcal{N}(0,\sigma^2 I_N),
+\begin{equation}
+y  =  x \ast s + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
 \label{eq:model}
-\end{align}
+\end{equation}
 where $\ast$ denotes linear convolution. 
@@
 We assume the binary signal $s$ obeys a \emph{separation condition}:
-\begin{align} 
+\begin{equation}
 \textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
 \label{eq:spacing}
-\end{align}
+\end{equation}
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
@@
 The result is proved in Appendix~\ref{sec:proof_two_gauss}.
+
 \begin{proposition} \label{prop:two_gauss}
 	For any deterministic estimator $\hat{\eta }$ of $\eta$,
-	\begin{align*}
-	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] & \leq \max(q, 1-q);
-	\end{align*}
+	\begin{equation}
+	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] \leq \max(q, 1-q);
+	\end{equation}
 	that is: as the SNR deteriorates, the probability of success is no better than random chance.
@@
 In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-\begin{align}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+\begin{equation}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
 \label{eq:ac_general}
-\end{align}
+\end{equation}
 where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
@@
 It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
-\begin{align}
-	\gamma & = \frac{M L}{N}
+\begin{equation}
+	\gamma  = \frac{M L}{N}
 \label{eq:gamma}
-\end{align}
+\end{equation}
 denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
@@
 In that regime, the law of large numbers can be used to show the following statement:
-\begin{align} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1 & \aseq \gamma a_{x}^1,
-\end{align}
+\begin{equation} \label{eq:mean_micrograph}
+\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
+\end{equation}
 where equality holds almost surely (a.s.), meaning it holds with probability one.
@@
 As a result,
-\begin{align}
-	\lim_{N\to\infty} a_y^2[\ell] & \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
+\begin{equation}
+	\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
 	\label{eq:ac2_micrograph}
-\end{align}
+\end{equation}
 for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
@@
 Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{multline}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2] \label{eq:ac3_micrograph} \\ + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big),
-\end{multline}
+\begin{equation}
+\begin{split} \label{eq:ac3_micrograph}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &\aseq \gamma a_{x}^3[\ell_1,\ell_2]  \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]
++\delta[\ell_1,\ell_2]\big),
+\end{split}
+\end{equation}
 for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
@@
 %
-\begin{align}
-%
-z[k] & = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+\begin{equation}
+%
+z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
 \label{eq-uniqueness}
 %
-\end{align}
+\end{equation}
 This proves the following useful fact:
@@
 Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
-However, for dimensions greater than one, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
 %,hayes1982reducible}.
@@
 The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
-%
+
 \begin{proposition} \label{prop:gamma}
 	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
-	%
-	\begin{align*}
-	%
-	\gamma & \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
-	%
-	\end{align*}
-	%
+	\begin{equation}
+\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	\end{equation}
 \end{proposition}
+
 %\begin{proof}
@@
 }
-		 \vspace{-20pt} 	
+%		 \vspace{-20pt} 	
 \end{figure}
@@
 This suggests that fourth-order autocorrelation may be necessary.
-This in turn would imply that the procedure might require a large amount of data.\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.} Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
+This in turn would imply that the procedure might require a large amount of data.
+%\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.}
+Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
 Still, large amounts of data also require large amounts of computation.
 On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in streaming mode, as only one pass through each micrograph is necessary.
+It can even be done in a  streaming mode, as only one pass through each micrograph is necessary.
 The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
@@
 Beyond data acquisition and computational challenges, there are modeling issues to consider.
-In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; their may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
+In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
 All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects.
@@
 
+\putbib
+
+\end{bibunit}
+
+%\bibliographystyle{main}{plain}
+%\bibliography{main}{literature}{References}
 % Bibliography
-\bibliography{ref}
+%\bibliography{ref}
+
+\newpage
+
+\begin{bibunit}
 
@@
 
+\putbib
+
+\end{bibunit}
+
 \end{document}

### 2018-09-20 pnas/Towards.tex
Added note about references in RELION 3 paper to cite

@@
 \begin{bibunit}
+
+\TODO{In RELION 3 paper, see these references, relevant for our claims about streaming mode: ``Other programs tackled individual steps in the single-particle workflow, like [...] on-the-fly processing of images while they are being acquired at the microscope [de la Rosa-Trevin et al., 2016, Biyani et al., 2017].''}
 

### 2018-09-21 pnas/Towards.tex
modified discussion  + 1-D figure in the App

--- 2018-09-12 pnas/Towards.tex
@@
 \begin{bibunit}
+%
+%\TODO{In RELION 3 paper, see these references, relevant for our claims about streaming mode: ``Other programs tackled individual steps in the single-particle workflow, like [...] on-the-fly processing of images while they are being acquired at the microscope [de la Rosa-Trevin et al., 2016, Biyani et al., 2017].''}
 
@@
 
-In the simplified mathematical model we examined, we showed it is possible to estimate a signal without detecting its appearances.  
-Our strategy is to compute autocorrelation functions of the micrographs and to relate these statistics to the unknown signal's parameters.
+In the simplified mathematical model above, we showed it is possible to estimate a signal without detecting its appearances.  
+Our strategy is to compute autocorrelations of the micrographs and to relate these statistics to the unknown signal's parameters.
 Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
@@
 
-Looking towards applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
+Looking toward applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
 In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
-We recognize that significant challenges lay ahead for the implementation of the proposed approach to 3-D reconstruction directly from the micrographs. We discuss a few now.
+We recognize that significant challenges lay ahead for the implementation of the proposed approach to \revised{high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
 
@@
 
-Beyond data acquisition and computational challenges, there are modeling issues to consider.
+\revised{To reach high-resolution reconstruction,} beyond data acquisition and computational challenges, there are modeling issues  to consider.
 In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
@@
 For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
-The separation condition could be relaxed by assuming a Poisson process of particle distribution in the micrograph, in which case the forward model will involve the Poisson parameter.
+\revised{Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
+Such a function models the distribution of distances between neighboring projections.
+The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
+}
+%The separation condition could be relaxed by assuming a Poisson process of particle distribution in the micrograph, in which case the forward model will involve the Poisson parameter.
 %To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.7\linewidth]{example_obs_1D}
+	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
+	}
+\end{figure}
+
 For the 1-D experiment depicted in Figure~\ref{fig:1D_example}, we used a signal of length $L=21$ and generated an observation $y$ of length $N = 10(2L-1)M$, where $M$ is the number of repetitions. 
@@
 The resulting SNR of $y$ is about $1/175$.
+\revised{Figure~\ref{fig:1D_obs_example} shows an example of the observed data.}
 

### 2018-09-25 pnas/Towards.tex
Removing highlighted text

@@
 In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
-We recognize that significant challenges lay ahead for the implementation of the proposed approach to \revised{high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
+We recognize that significant challenges lay ahead for the implementation of the proposed approach to {high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
 
@@
 
-\revised{To reach high-resolution reconstruction,} beyond data acquisition and computational challenges, there are modeling issues  to consider.
+{To reach high-resolution reconstruction,} beyond data acquisition and computational challenges, there are modeling issues  to consider.
 In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
@@
 For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
-\revised{Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
+{Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
 Such a function models the distribution of distances between neighboring projections.
@@
 The resulting SNR of $y$ is about $1/175$.
-\revised{Figure~\ref{fig:1D_obs_example} shows an example of the observed data.}
+{Figure~\ref{fig:1D_obs_example} shows an example of the observed data.}
 

### 2018-09-27 pnas/Towards.tex
Added noisy cryo experiments

@@
 		\centering
-		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec.eps}
+		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec_incl_noisy.eps}
 		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
@@
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-		The reconstruction is shown in gray, the (smoothed) ground truth in yellow, and the original molecules are shown in blue to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
-}
+		\revised{The reconstructions from autocorrelations estimated from noisy data are shown in gray, the reconstructions from clean autocorrelations in yellow, the (smoothed) ground truths in blue, and the original molecules are shown in purple} to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
+\revised{For the noisy experiment, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI - we present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}}
 %		 \vspace{-20pt} 	
@@
 
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{TRPV1_clean_micro.png}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{TRPV1_noisy_micro_SNR_16.png}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{clean_micro_BPTI.png}
+		\caption{}
+	\end{subfigure} \hfill
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{noisy_micro_BPTI_SNR_64.png}
+		\caption{}
+	\end{subfigure}
+	\caption{\label{fig:cryo_noisy_micros_for_rec} \revised{Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
+(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph, with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
+\end{figure*}
+
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[t]{0.4\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{TRPV1_trunc_FSC.eps}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.4\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{BPTI_FSC.eps}
+		\caption{}
+	\end{subfigure} 
+	\caption{\label{fig:cryo_FSC} \revised{Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (low-resolution) ground truth.
+(a) FSC for the TRPV1 reconstruction, giving resolution of $24 \AA$; (b) FSC for the BPTI reconstruction, giving resolution of $13 \AA$.}}
+\end{figure*}
+
 The experiments in Figure~\ref{fig:cryo_recon}, and the recoveries of $\gamma$ for the experiment in Figure~\ref{fig:cryo_detection}, were performed on a machine with 40 cores of Intel Xeon E5-2698 v4 @ 2.20GHz with 100 GB of RAM, and took ~2 hours per reconstruction.
@@
 
-For the experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
+For the \revised{clean} experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
 To estimate the coefficients of the volume itself, we solve the LS problem
@@
 
-The micrographs for the experiment presented in Figure~\ref{fig:cryo_detection} were generated as follows.
+The micrographs for the experiment presented in Figures~\ref{fig:cryo_detection} \revised{and~\ref{fig:cryo_noisy_micros_for_rec}} were generated as follows.
 We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}.
@@
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-Then, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
+\revised{The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.
+We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.}
+
+\revised{For the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}, the LS problem~\eqref{eq:LS_cryo} was solved assuming spherical harmonic cutoffs of $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI, same as for the ground truth.}
+For the experiment in Figure~\ref{fig:cryo_detection}, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
 

### 2018-09-28 pnas/Towards.tex
small changes

@@
 Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
-%	\vspace{-8pt} 
+	\vspace{-8pt} 
 \end{figure*}
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{.2in}
+\begin{myquote}{0in}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-		\revised{The reconstructions from autocorrelations estimated from noisy data are shown in gray, the reconstructions from clean autocorrelations in yellow, the (smoothed) ground truths in blue, and the original molecules are shown in purple} to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
-\revised{For the noisy experiment, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI - we present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}}
-%		 \vspace{-20pt} 	
+		\revised{The original molecules are shown in purple
+				and the (smoothed) ground truths in blue to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
+			The reconstructions  from clean autocorrelations are shown in yellow, and 	recovery from autocorrelations estimated from noisy data in gray.
+For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI.
+We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}.}
+		 \vspace{-20pt} 	
 \end{figure}
@@
 	\caption{\label{fig:cryo_noisy_micros_for_rec} \revised{Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
-(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph, with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
+(a) Excerpt of the clean TRPV1 micrograph.
+(b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$.
+(c) Excerpt from the clean BPTI micrograph.
+(d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
 \end{figure*}
@@
 	\end{subfigure} 
-	\caption{\label{fig:cryo_FSC} \revised{Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (low-resolution) ground truth.
+	\caption{\label{fig:cryo_FSC} \revised{Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
 (a) FSC for the TRPV1 reconstruction, giving resolution of $24 \AA$; (b) FSC for the BPTI reconstruction, giving resolution of $13 \AA$.}}
@@
 \begin{equation} \label{eq:LS_cryo}
-\min_{\hat{x},\hat{\gamma}} w_1 \vert \mathfrak{a}_x^1 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^1 \vert^2 + w_2\| \mathfrak{a}_x^2 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^2 \|_2^2 + w_3\| \mathfrak{a}_x^3 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^3 \|_F^2,
+\min_{\hat{x},\hat{\gamma}} w_1 \vert \mathfrak{a}_x^1 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^1 \vert^2 + w_2\| \mathfrak{a}_x^2 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^2 \|_2^2 + w_3\| \mathfrak{a}_x^3 - \hat{\gamma}\mathfrak{a}_{\hat{x}}^3 \|_\text{F}^2,
 \end{equation}  

### 2018-09-28 pnas/Towards.tex
Added cryo SNR definition, small corrections

--- 2018-09-27 pnas/Towards.tex
@@
 
-For the \revised{clean} experiments in Figure~\ref{fig:cryo_detection}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
+For the \revised{clean} experiments in Figure~\ref{fig:cryo_recon}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
 To estimate the coefficients of the volume itself, we solve the LS problem
@@
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-\revised{The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.
+\revised{For the noise, we define signal-to-noise ratio slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
+The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.
 We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.}

### 2018-09-28 pnas/Towards.tex
small modifications

@@
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-		\revised{The reconstructions from autocorrelations estimated from noisy data are shown in gray, the reconstructions from clean autocorrelations in yellow, the (smoothed) ground truths in blue, and the original molecules are shown in purple} to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
-\revised{For the noisy experiment, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI - we present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}}
-%		 \vspace{-20pt} 	
+		\revised{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
+		The reconstructions  from clean autocorrelations are shown in yellow and recovery from 
+		autocorrelations estimated from noisy data in gray.
+For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI.
+We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}.}
+		 \vspace{-20pt} 	
 \end{figure}

### 2018-09-28 pnas/Towards.tex
small modifications

@@
 		\revised{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
-		The reconstructions  from clean autocorrelations are shown in yellow and recovery from 
+		The reconstructions  from clean autocorrelations are shown in yellow and recoveries from 
 		autocorrelations estimated from noisy data in gray.
@@
 	\caption{\label{fig:cryo_noisy_micros_for_rec} \revised{Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
-(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph, with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
+(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
 \end{figure*}
@@
 For the BPTI reconstruction, the errors in the autocorrelations were $10^{-6}$, $10^{-7}$ and $10^{-8}$ for the third, second and first autocorrelations, respectively, while the error in the expansion coefficients of the volume was $5\times 10^{-2}$.
-This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.
+This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining \revised{high-resolution} results from noisy data.
 

### 2018-09-28 pnas/Towards.tex
Finished modifications in the appendix

@@
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-\revised{For the noise, we define signal-to-noise ratio slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
+\revised{In the experiments, we define SNR slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
 The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.

### 2018-09-28 pnas/Towards.tex
modifications on the body of the text

@@
 In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. 
-Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations.
+Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations\revised{ and from noisy micrographs.
+Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.}
 The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
-Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing recovery from noisy data. 
 In the next section, we outline how we suggest to overcome the ill-conditioning in future work.
 
-While we cannot provide a 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics (e.g.,~\cite{donoho2004higher}) and debates in the cryo-EM community~\cite{henderson2013avoiding}.
+While we cannot provide a \revised{high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
+and cryo-EM~\cite{henderson2013avoiding}.
 This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
@@
 For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI.
-We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec}}.}
+We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec} (see appendix)}.}
 		 \vspace{-20pt} 	
@@
 %\cite{aspire}.
-We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension.
-The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices.
+We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least \revised{$L-1$ pixels in each dimension, where  the projections are contained in a box of size $L\times L$.}  The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices.
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-\revised{In the experiments, we define SNR slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
+\revised{In the experiments, we define SNR slightly differently than in the toy model, namely, as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
 The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.

### 2018-09-28 pnas/Towards.tex
remove highlighted comments and very small modification in the appendix

@@
 
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs, and a movie is available as supplementary material.
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. %, and a movie is available as supplementary material.
 Figure~\ref{fig:error_per_micro} (see appendix) presents the normalized recovery error as a function of the amount of data available.
@@
 In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. 
-Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations\revised{ and from noisy micrographs.
+Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations {and from noisy micrographs.
 Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.}
@@
 
-While we cannot provide a \revised{high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
+While we cannot provide a {high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
 and cryo-EM~\cite{henderson2013avoiding}.
@@
 		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-		\revised{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
+		{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
 		The reconstructions  from clean autocorrelations are shown in yellow and recoveries from 
@@
 	\end{subfigure}
-	\caption{\label{fig:cryo_noisy_micros_for_rec} \revised{Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
+	\caption{\label{fig:cryo_noisy_micros_for_rec}  {Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
 (a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
@@
 	\end{subfigure} 
-	\caption{\label{fig:cryo_FSC} \revised{Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
+	\caption{\label{fig:cryo_FSC}  {Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
 (a) FSC for the TRPV1 reconstruction, giving resolution of $24 \AA$; (b) FSC for the BPTI reconstruction, giving resolution of $13 \AA$.}}
@@
 
-For the \revised{clean} experiments in Figure~\ref{fig:cryo_recon}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
+For the {clean} experiments in Figure~\ref{fig:cryo_recon}, we computed the analytical first three autocorrelations of the volume as explained in Appendix~\ref{sec:ac_cryo}.
 To estimate the coefficients of the volume itself, we solve the LS problem
@@
 For the BPTI reconstruction, the errors in the autocorrelations were $10^{-6}$, $10^{-7}$ and $10^{-8}$ for the third, second and first autocorrelations, respectively, while the error in the expansion coefficients of the volume was $5\times 10^{-2}$.
-This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining \revised{high-resolution} results from noisy data.
-
-The micrographs for the experiment presented in Figures~\ref{fig:cryo_detection} \revised{and~\ref{fig:cryo_noisy_micros_for_rec}} were generated as follows.
+This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining {high-resolution} results from noisy data.
+
+The micrographs for the experiments presented in Figures~\ref{fig:cryo_detection}  {and~\ref{fig:cryo_noisy_micros_for_rec}} were generated as follows. 
 We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}.
 %\cite{aspire}.
-We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least \revised{$L-1$ pixels in each dimension, where  the projections are contained in a box of size $L\times L$.}  The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices.
+The projections for the experiments in Figure~\ref{fig:cryo_noisy_micros_for_rec} were obtained from the smoothed volumes, not the original ones. 
+We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least {$L-1$ pixels in each dimension, where  the projections are contained in a box of size $L\times L$.}  The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices.
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-\revised{In the experiments, we define SNR slightly differently than in the toy model, namely, as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
+{In the experiments, we define SNR slightly differently than in the toy model, namely, as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
 The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.
@@
 
-\revised{For the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}, the LS problem~\eqref{eq:LS_cryo} was solved assuming spherical harmonic cutoffs of $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI, same as for the ground truth.}
+{For the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}, the LS problem~\eqref{eq:LS_cryo} was solved assuming spherical harmonic cutoffs of $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI, same as for the ground truth.}
 For the experiment in Figure~\ref{fig:cryo_detection}, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.

### 2018-09-29 arxiv/towards_arxiv.tex
Arxiv version

--- 2018-09-28 pnas/Towards.tex
@@
-\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
-
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
+\documentclass[12pt]{article}
+%\pdfoutput=1
+
+\usepackage[T1]{fontenc}
+%\usepackage[latin9]{inputenc}
+\usepackage{verbatim}
+\usepackage{float}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+%\usepackage{multirow}
+\usepackage{color}
+\usepackage{url}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{mathtools} 
+\usepackage{stackrel} 
+%\usepackage[skip=1pt]{caption} % example skip set to 2pt
+
+\newcommand{\LL}{\mathcal{L}}
+\newcommand{\E}{\mathbb{E}}
+\newcommand{\I}{\mathcal{I}}
+\newcommand{\ep}{\varepsilon}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\GCD}{\mathbf{GCD}}
+\newcommand{\XX}{\mathcal{X}}
+\newcommand{\SUM}{\text{sum}}
+\newcommand{\1}{\mathbf{1}}
+\newcommand{\rr}{\textbf{r}}
+\newcommand{\ii}{\textbf{i}}
+\newcommand{\jj}{\textbf{j}}
+
+\newcommand{\II}{\mathcal{I}}
+\newcommand{\kk}{\textbf{k}}
+\newcommand{\RR}{\mathbb{R}}
+\newcommand{\mb}{\mathbf}
+\newcommand{\mk}{\mathfrak}
+\newcommand{\mc}{\mathcal}
+\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
+\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
+\newcommand{\revised}[1]{{\color{blue}{#1}}}
+
+%\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
+\makeatletter
+
+\newcommand{\reals}{\mathbb{R}}
+\newcommand{\RL}{\mathbb{R}^L}
+\newcommand{\tamir}{x}
+\newcommand{\CL}{\mathbb{C}^L}
+\newcommand{\RN}{\mathbb{R}^N}
+\newcommand{\RNN}{\mathbb{R}^{N\times N}}
+\newcommand{\RPP}{\mathbb{R}^{P\times P}}
+\newcommand{\CNN}{\mathbb{C}^{N\times N}}
+\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
+\newcommand{\hx}{\hat{x}} 
+\newcommand{\one}{\mathbf{1}} 
+\newcommand{\be}
+{\begin{equation}}
+\newcommand{\ee}
+{\end{equation}}
+%\renewcommand{\P}{\mathbb{P}}
+\newcommand{\aseq}{\stackrel{a.s.}{=}}
+\renewcommand{\P}{\mathrm{Prob}}
+
+\theoremstyle{plain}
+\newtheorem{thm}{\protect\theoremname}[section]
+\theoremstyle{definition}
+\newtheorem{defn}[thm]{\protect\definitionname}
+\theoremstyle{remark}
+\newtheorem{claim}[thm]{\protect\claimname}
+\theoremstyle{plain}
+\newtheorem{lem}[thm]{\protect\lemmaname}
+\newtheorem*{lem*}{Lemma}
+\theoremstyle{remark}
+\newtheorem{rem}[thm]{\protect\remarkname}
+\theoremstyle{plain}
+\newtheorem{corollary}[thm]{\protect\corollaryname}
+\theoremstyle{plain}
+\newtheorem{proposition}[thm]{\protect\propositionname}
+\providecommand{\claimname}{Claim}
+\providecommand{\definitionname}{Definition}
+\providecommand{\lemmaname}{Lemma}
+\providecommand{\remarkname}{Remark}
+\providecommand{\theoremname}{Theorem}
+\providecommand{\corollaryname}{Corollary}
+\providecommand{\propositionname}{Proposition}
+
+\usepackage{authblk}
+\renewcommand*{\Affilfont}{\normalsize}
+\setlength{\affilsep}{2em}   % set the space between author and affiliation
+
+\usepackage[margin=.6in]{geometry}
+
+\newenvironment{myquote}[1]%
+{\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
+{\endlist}
+
+\allowdisplaybreaks
+
+\begin{document}
+
+%\begin{frontmatter}
 
@@
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
 \author[a]{Tamir Bendory}
@@
 
-% Please give the surname of the lead author for the running footer
-\leadauthor{Bendory}
-
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{It is commonly believed that cryo-EM cannot be used to image the 3-D structure of small molecules (below $\sim$50kDa).
-The classical argument is that, due to high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs.
-Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure determination.
-Our reconstruction method is based on autocorrelation analysis.
-It requires only one pass over the data, so that it should, in principle, be appropriate for high-throughput experiments.
-This autocorrelation approach could also apply to other applications where the goal is estimation rather than detection.
-}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Author contributions: T.B., N.B., W.L., E.L., and A.S., designed research, performed research and wrote the paper; E.L.
-wrote the  computer code for the cryo-EM experiments;  N.B.
-and T.B.
-wrote the computer code for the 1-D and 2-D numerical experiments.
-Authors are listed alphabetically.
-}
-\authordeclaration{The authors declare no conflicts of interest.}
-%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
-\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu %\TODO{Should this be Amit's address?}
-}
-
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Cryo-EM $|$ autocorrelation analysis $|$ detection limit}
+%\date{}
+\maketitle
 
 \begin{abstract}
-%{C}ryo--electron microscopy (cryo--EM) is used in structural biology to determine the 3-D structure of molecules. 
 Single-particle cryo-electron microscopy (cryo-EM) has recently joined X-ray crystallography
@@
 In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection.
-% and independently of the noise level (provided sufficiently many micrographs are acquired).
 As a result, even small molecules should be within reach for cryo-EM.
@@
 This involves only one pass over the micrographs, which is desirable for large experiments.
-%Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via template matching. 
-%We detail elementary theory for the simplified model and show how to extend it to single particle reconstruction from synthetic cryo-EM data.
 We show numerical results and  discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
@@
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-%\setlength{\abovedisplayskip}{2pt}
-%\setlength{\belowdisplayskip}{2pt}
-
-\begin{bibunit}
-%
-%\TODO{In RELION 3 paper, see these references, relevant for our claims about streaming mode: ``Other programs tackled individual steps in the single-particle workflow, like [...] on-the-fly processing of images while they are being acquired at the microscope [de la Rosa-Trevin et al., 2016, Biyani et al., 2017].''}
-
-\dropcap{C}ryo-electron microscopy (cryo-EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
+\section{Introduction}
+
+Cryo-electron microscopy (cryo-EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice. %Within the ice, the molecules are randomly oriented and positioned.
@@
 
-\begin{figure*}[h]
+\begin{figure}[t]
 	\centering
@@
 	%\vspace{-8pt} 	
-\end{figure*}
-
-\begin{figure*}[h]
+\end{figure}
+
+\begin{figure}[t]
 	\centering
@@
 Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
-	\vspace{-8pt} 
-\end{figure*}
+%	\vspace{-8pt} 
+\end{figure}
 
@@
 In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-\begin{myquote}{0in}
+\begin{myquote}{10pt}
 	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
@@
 %
-
-%\TODO{Need to cite \cite{scapin2018cryo}. Discusses cryo-em for drug discovery and mentions small molecule}
 
@@
 Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.
-% and study it in Section~\ref{sec:recovery}.
 
 \section{The detection limit} \label{sec:detectionlimit}
-% Can be added to an arxiv version
-%At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
-%However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
+
 In the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
@@
 where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+Explicitly, the first-, second- and third-order autocorrelations are given by: 
+\begin{align} 
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$
 For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-%This part can be added to an arxiv version of the manuscript
-%Explicitly, the first-, second- and third-order autocorrelations are given by: %\TODO{we may want to remove these explicit formulas}
-%\begin{align} 
-%a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-%a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
-%a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
-%\end{align}
-%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-%$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-%$
 
@@
 \begin{equation}
-\begin{split} \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &\aseq \gamma a_{x}^3[\ell_1,\ell_2]  \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]
+ \label{eq:ac3_micrograph}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
 +\delta[\ell_1,\ell_2]\big),
-\end{split}
-\end{equation}
+\end{equation}
+%\begin{equation}
+%\begin{split} \label{eq:ac3_micrograph}
+%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &\aseq \gamma a_{x}^3[\ell_1,\ell_2]  \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]
+%+\delta[\ell_1,\ell_2]\big),
+%\end{split}
+%\end{equation}
 for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
@@
 However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-%,hayes1982reducible}.
 The sign ambiguity can be resolved by the mean of the signal if it is not zero.
@@
 We will show, however, that $x$ is still determined by the observed moments of $y$.
-%
-%identifiable from the observed moments of $y$. In general, we say a parameter is ``identifiable'' if its value is uniquely determined in the limit $N \to \infty$.
 
@@
 \end{proposition}
-
-%\begin{proof}
-%In the limit, $(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j]$.
-Similarly,  $\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell]$ and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$.
-The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
-%%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
-%\end{proof}
 
@@
 \begin{proposition} \label{prop:gamma_sigma}
-	%
-	%Let $\sigma > 0$ be fixed. 
 	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
-% Added by Nicolas, Sep 4, 2018: I checked all identities for L >= 3, with some computer code; I didn't write code to verify the corner cases L = 1 and L = 2.
 	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
 If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
-%	\begin{proof}
-%		See Appendix~\ref{sec:proof_prop_gamma_sigma}.
-%	\end{proof}
 \end{proposition}
@@
 \begin{corollary}
-	%Let $K=1$ and $\sigma > 0$ be fixed.
 	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
 \end{corollary}
-%
-%%This can be added to an arxiv version of the paper	
-%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
-%\begin{corollary}
-%	%Let $K=1$ and $\sigma > 0$ be fixed.
-%	 In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if:
-%	\begin{itemize}
-%		\item Either the signal $x$ is generic; or
-%		\item   $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-%	\end{itemize}
-%\end{corollary}
-%
-%\TODO{Similar results hold for signals in higher dimensions.---need to keep this sentence in red until the very end to make sure it's correct.}
 
 As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
-%In particular, if  $a_y^2[L-i] = 0$ for $i=1,\ldots,T$,
-%then the support of $x$ has length $L-T$ rather than $L$.
 
@@
 Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. %, and a movie is available as supplementary material.
-Figure~\ref{fig:error_per_micro} (see appendix) presents the normalized recovery error as a function of the amount of data available.
+Figure~\ref{fig:error_per_micro} %(see appendix)
+presents the normalized recovery error as a function of the amount of data available.
 This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+\end{figure}
+
 In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
-Figure~\ref{fig:1D_example} (see appendix) shows recovery of a 1-D signal from the first three autocorrelations of the data.
-The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}. 
+Figure~\ref{fig:1D_example} %(see appendix) 
+shows recovery of a 1-D signal from the first three autocorrelations of the data.
+The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}; see Figure~\ref{fig:1D_obs_example}.  
 Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
 Crucially, the LS does not require  knowledge of $\sigma$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{1D_example}
+	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
+The length of the micrograph was set to be $N = 410*M$.
+The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
+		The true value of $\gamma$ is $0.0512$.
+		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
+	}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\linewidth]{example_obs_1D}
+	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
+	}
+\end{figure}
 
@@
 In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. 
-Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations {and from noisy micrographs.
-Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.}
+Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations and from noisy micrographs. 
+Excerpts from the noisy micrographs are shown in Figure~\ref{fig:cryo_noisy_micros_for_rec}.
+Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.
 The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
@@
 
-While we cannot provide a {high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
-and cryo-EM~\cite{henderson2013avoiding}.
-This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
-Figure~\ref{fig:cryo_detection} (see appendix) presents excerpts  of two noisy micrographs, only one of which contains projections.
-In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
-On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
-
 \begin{figure}[h]
@@
 		\centering
-		\includegraphics[angle=270, width=.7\textwidth]{TRPV1_rec_incl_noisy.eps}
+		\includegraphics[angle=270, width=1\textwidth]{TRPV1_rec_incl_noisy_resize.eps}
 		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
@@
 		\centering
-		\includegraphics[angle=270, width=.7\textwidth]{BPTI_maxL2_L20.eps}
+		\includegraphics[angle=270, width=1\textwidth]{BPTI_maxL2_L20_resize.eps}
 		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
@@
 We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec} (see appendix)}.}
-		 \vspace{-20pt} 	
+	%	\vspace{-20pt} 	
 \end{figure}
-% -------------- Vertical subfigures: -------------------------------
-
-% \begin{figure}[t!]
-% 	\centering
-% 	\begin{subfigure}{0.3\textwidth}
-% 		\centering
-% 		\includegraphics[scale=0.3]{pure_noise_micrograph_cutout.png}
-% 	\end{subfigure}
-% 	\begin{subfigure}{0.3\textwidth}
-% 		\centering
-% 		\includegraphics[scale=0.3]{noisy_micrograph_cutout.png}
-% 	\end{subfigure} 
-% 	\begin{subfigure}{0.3\textwidth}
-% 		\centering
-% 		\includegraphics[scale=0.3]{clean_micrograph_cutout.png}
-% 	\end{subfigure}
-% 	\caption{\label{fig:cryo_detection} (a) An excerpt of the pure noise micrograph ; (b) An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.; (c) An excerpt of the clean micrograph.
-All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule, having size $31^3$.
+
+\begin{figure}[t!]
+	\centering
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{TRPV1_clean_micro.png}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{TRPV1_noisy_micro_SNR_16.png}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{clean_micro_BPTI.png}
+		\caption{}
+	\end{subfigure} \hfill
+	\begin{subfigure}[t]{0.245\textwidth}
+		\centering
+		\includegraphics[scale=0.3]{noisy_micro_BPTI_SNR_64.png}
+		\caption{}
+	\end{subfigure}
+	\caption{\label{fig:cryo_noisy_micros_for_rec}  {Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
+(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
+\end{figure}
+
+\begin{figure}[t!]
+	\centering
+	\begin{subfigure}[t]{0.4\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{TRPV1_trunc_FSC.eps}
+		\caption{}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.4\textwidth}
+		\centering
+		\includegraphics[scale=0.35]{BPTI_FSC.eps}
+		\caption{}
+	\end{subfigure} 
+	\caption{\label{fig:cryo_FSC}  {Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
+(a) FSC for the TRPV1 reconstruction, giving resolution of $24$\AA; (b) FSC for the BPTI reconstruction, giving resolution of $13$\AA.}}
+\end{figure}
+
+While we cannot provide a {high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
+and cryo-EM~\cite{henderson2013avoiding}.
+This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
+Figure~\ref{fig:cryo_detection} %(see appendix) 
+presents excerpts  of two noisy micrographs, only one of which contains projections.
+In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
+On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
+		\caption{An excerpt of the pure noise micrograph}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
+		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
+	\end{subfigure} \hfill %\hspace{2pt}
+	\begin{subfigure}[t]{0.3\textwidth}
+		\centering
+		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
+		\caption{An excerpt of the clean micrograph}
+	\end{subfigure}
+	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
 The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
 		The noise realization is identical in both micrographs.} 
-% \end{figure}
-
-%\begin{figure*}[t!]
-%	\centering
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
-%		\caption{An excerpt of the pure noise micrograph}
-%	\end{subfigure} \hspace{2pt}
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
-%		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
-%	\end{subfigure} \hspace{2pt}
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
-%		\caption{An excerpt of the clean micrograph}
-%	\end{subfigure}
-%	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
-The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-%		The noise realization is identical in both micrographs.} 
-%	 \vspace{-14pt} 	
-%\end{figure*}
+\end{figure}
 
@@
 The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
-This suggests that fourth-order autocorrelation may be necessary.
-This in turn would imply that the procedure might require a large amount of data.
-%\footnote{Whether or not this large amount of data would be necessary for any method to succeed given the unfavorable SNR remains an open question.}
+This suggests that fourth-order autocorrelation may be necessary. This in turn would imply that the procedure might require a large amount of data. 
 Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
@@
 
-{To reach high-resolution reconstruction,} beyond data acquisition and computational challenges, there are modeling issues  to consider.
+To reach high-resolution reconstruction, beyond data acquisition and computational challenges, there are modeling issues  to consider.
 In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
@@
 For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
-{Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
+Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
 Such a function models the distribution of distances between neighboring projections.
 The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
-}
-%The separation condition could be relaxed by assuming a Poisson process of particle distribution in the micrograph, in which case the forward model will involve the Poisson parameter.
-%To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
-%Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume.
-%We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
-%Such a condition can be met in practice by careful experimental design. 
-%
-%We also note several aspects of SPR experiments that were neglected in this paper, including contrast transfer function (CTF), non-uniformly distributed viewing directions and other contaminants in the micrographs, such as ice crystals.
 All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
@@
 
-\putbib
-
-\end{bibunit}
-
-%\bibliographystyle{main}{plain}
-%\bibliography{main}{literature}{References}
-% Bibliography
-%\bibliography{ref}
-
-\newpage
-
-\begin{bibunit}
+\bibliographystyle{plain}
+\bibliography{ref}
 
@@
 \paragraph{2-D experiment.}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{Einstein_recovery_error_combined}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=\linewidth]{Einstein_recovery_error_combined}
+%	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+%\end{figure}
 
 For the 2-D experiment shown in Figures~\ref{fig:Einst_example} and~\ref{fig:error_per_micro}, we generated micrographs of size $4096\times 4096$ pixels. 
-In each micrograph, we placed Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition ~\eqref{eq:spacing}.  
+In each micrograph, we placed Einstein's image (of zero mean) of size $50\times 50$  in random locations, while preserving the separation condition~\eqref{eq:spacing}.  
 This is done by randomly selecting $4000$ placements in the micrograph, one at a time with
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\linewidth]{1D_example}
-	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
+%
+%\begin{figure*}[t]
+%	\centering
+%	\includegraphics[width=\linewidth]{1D_example}
+%	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
 The length of the micrograph was set to be $N = 410*M$.
 The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
-		The true value of $\gamma$ is $0.0512$.
-		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
-	}
-\end{figure*}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.7\linewidth]{example_obs_1D}
-	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
-	}
-\end{figure}
+%		The true value of $\gamma$ is $0.0512$.
+%		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
+%	}
+%\end{figure*}
+
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{example_obs_1D}
+%	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
+%	}
+%\end{figure}
 
@@
 The resulting SNR of $y$ is about $1/175$.
-{Figure~\ref{fig:1D_obs_example} shows an example of the observed data.}
-
-Given the observation $y$, we proceed to compute the autocorrelations. %The first-order autocorrelation is straightforward. 
+Figure~\ref{fig:1D_obs_example} shows an example of the observed data.
+
+Given the observation $y$, we proceed to compute the autocorrelations.
 We excluded biased elements of the autocorrelations; that is $a_y^2[\ell_1]$ and $a_y^3[\ell_1, \ell_2]$ such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero. 
@@
 In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ (if the length of the measurement is larger than that) and added up, without correction for the junction points.
-%Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
 
@@
 %\begin{align}
-%\min_{\substack{\hat x_1, \ldots, \hat x_K \in \mathbb{R}^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}}& w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 \\ & + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2  \nonumber \\&+ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2, \nonumber
+%\min_{\substack{\hat x\in \mathbb{R}^{W} \\ \hat \gamma > 0}}& w_1 \left( a_y^1 - \hat \gamma a_{\hat x}^1 \right)^2  + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \hat \gamma a_{\hat x}^2[\ell] \right)^2  \nonumber \\&+ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] -  \hat \gamma a_{\hat x}^3[\ell_1,\ell_2] \right)^2,
 %\label{eq:optim1D}
@@
 \begin{align} 
-\min_{\substack{\hat x\in \mathbb{R}^{W} \\ \hat \gamma > 0}}& w_1 \left( a_y^1 - \hat \gamma a_{\hat x}^1 \right)^2  + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \hat \gamma a_{\hat x}^2[\ell] \right)^2  \nonumber \\&+ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] -  \hat \gamma a_{\hat x}^3[\ell_1,\ell_2] \right)^2,
+\min_{\substack{\hat x\in \mathbb{R}^{W} \\ \hat \gamma > 0}} w_1 \left( a_y^1 - \hat \gamma a_{\hat x}^1 \right)^2  + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \hat \gamma a_{\hat x}^2[\ell] \right)^2  + w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] -  \hat \gamma a_{\hat x}^3[\ell_1,\ell_2] \right)^2,
 \label{eq:optim1D}
@@
 
-\begin{figure*}[t!]
-	\centering
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
-		\caption{An excerpt of the pure noise micrograph}
-	\end{subfigure} \hfill %\hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
-		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
-	\end{subfigure} \hfill %\hspace{2pt}
-	\begin{subfigure}[t]{0.3\textwidth}
-		\centering
-		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
-		\caption{An excerpt of the clean micrograph}
-	\end{subfigure}
-	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
-The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-		The noise realization is identical in both micrographs.} 
-\end{figure*}
-
-\begin{figure*}[t!]
-	\centering
-	\begin{subfigure}[t]{0.245\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{TRPV1_clean_micro.png}
-		\caption{}
-	\end{subfigure} \hfill %\hspace{2pt}
-	\begin{subfigure}[t]{0.245\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{TRPV1_noisy_micro_SNR_16.png}
-		\caption{}
-	\end{subfigure} \hfill %\hspace{2pt}
-	\begin{subfigure}[t]{0.245\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{clean_micro_BPTI.png}
-		\caption{}
-	\end{subfigure} \hfill
-	\begin{subfigure}[t]{0.245\textwidth}
-		\centering
-		\includegraphics[scale=0.3]{noisy_micro_BPTI_SNR_64.png}
-		\caption{}
-	\end{subfigure}
-	\caption{\label{fig:cryo_noisy_micros_for_rec}  {Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
-(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
-\end{figure*}
-
-\begin{figure*}[t!]
-	\centering
-	\begin{subfigure}[t]{0.4\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{TRPV1_trunc_FSC.eps}
-		\caption{}
-	\end{subfigure} \hfill %\hspace{2pt}
-	\begin{subfigure}[t]{0.4\textwidth}
-		\centering
-		\includegraphics[scale=0.35]{BPTI_FSC.eps}
-		\caption{}
-	\end{subfigure} 
-	\caption{\label{fig:cryo_FSC}  {Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
-(a) FSC for the TRPV1 reconstruction, giving resolution of $24 \AA$; (b) FSC for the BPTI reconstruction, giving resolution of $13 \AA$.}}
-\end{figure*}
-
 The experiments in Figure~\ref{fig:cryo_recon}, and the recoveries of $\gamma$ for the experiment in Figure~\ref{fig:cryo_detection}, were performed on a machine with 40 cores of Intel Xeon E5-2698 v4 @ 2.20GHz with 100 GB of RAM, and took ~2 hours per reconstruction.
@@
 
-The true volume used in the experiments in Figures~\ref{fig:cryo_detection} and~\ref{fig:BPTI_recon} was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB) %~\cite{pdb}
+The true volume used in the experiments in Figures~\ref{fig:cryo_detection} and~\ref{fig:BPTI_recon} was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB)
 as 1QLQ\footnote{\url{https://www.rcsb.org}}.
@@
 For the experiment in Figure~\ref{fig:BPTI_recon}, the volume was downsampled to size $20^3$.
-For the experiment in Figure~\ref{fig:TRPV1_recon}, we used the TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB) %~\cite{emdb}
+For the experiment in Figure~\ref{fig:TRPV1_recon}, we used the TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB)
 as EMD-8117\footnote{\url{http://www.ebi.ac.uk/pdbe/emdb}}.
@@
 We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}.
-%\cite{aspire}.
 The projections for the experiments in Figure~\ref{fig:cryo_noisy_micros_for_rec} were obtained from the smoothed volumes, not the original ones.
@@
 We continue adding projections to the micrograph until no more projections can be added without violating the separation condition.
-{In the experiments, we define SNR slightly differently than in the toy model, namely, as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
+In the experiments, we define SNR slightly differently than in the toy model, namely, as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise.
 The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs.
-We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.}
-
-{For the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}, the LS problem~\eqref{eq:LS_cryo} was solved assuming spherical harmonic cutoffs of $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI, same as for the ground truth.}
+We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.
+
+For the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}, the LS problem~\eqref{eq:LS_cryo} was solved assuming spherical harmonic cutoffs of $L_{\text{max}} = 5$ for TRPV1 and $L_{\text{max}} = 2$ for BPTI, same as for the ground truth.
 For the experiment in Figure~\ref{fig:cryo_detection}, the LS problem~\eqref{eq:LS_cryo} was solved assuming the spherical harmonic cutoff for the volume is $L_{\text{max}}=0$, which is sufficient to recover a significant $\widehat\gamma$ in the presence of projections in the micrograph.
@@
 \sigma\langle Z, \theta_1 - \theta_0 \rangle 
-&\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
+\ge \frac{\|\theta_1\|^2 + \|\theta_0\|^2}{2} - \langle \theta_0,\theta_1 \rangle
 - \sigma^2 \log(b)
-\nonumber \\
-&= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b).
+= \frac{1}{2} \|\theta_1 - \theta_0\|^2 - \sigma^2 \log(b).
 %
@@
 %
-\begin{multline*}
-%
-\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \\
+%\begin{multline*}
+%%
+%\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] \\
+%+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
+%\end{multline*}
+\begin{equation*}
+%
+\P[\hat{\eta} \ne \eta] = q \P\left[Y \ge \frac{c}{\sigma} - \sigma \log(b) \right] 
 + (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma \log(b) \right].
-%\
-\end{multline*}
+\end{equation*}
 %
@@
 \P[\hat{\eta} \ne \eta]
-%&= q \P\left[Y \ge \frac{c}{\sigma} - \sigma^2 \log(b) \right]
-%+ (1-q) \P\left[Y \ge \frac{c}{\sigma} + \sigma^2 \log(b) \right]
-%\nonumber\\
 & \longrightarrow 1-q  \quad \text{as} \quad  \sigma \to \infty.
@@
 
-%Throughout the proof, we consider the case of one signal $K=1$.
-The extension to $K>1$ is straightforward by averaging the contributions of all signal with  appropriate weights; see~\cite{boumal2017heterogeneous}.
-%We will let the number of instances of the signal $M$ grow with $N$, and write $M=M_N$ to emphasize this.
 We consider the asymptotic regime $N,M\to\infty$ and assume that $M=\Omega(N)$, so that
-% We assume $M_N$ grows proportionally with $N$, and recall that
-% define: %\TODO{---Nico: the paper now no longer references $M_N$ and defines $\gamma$ 'as is' for given $M$ and $N$; may want to adapt things here as a result.
-It wouldn't make sense to make $M_N$ appear in the paper I think, as it just makes things more complicated.
-In a sense, much of this beginning of appendix is just repeating things we already said cleanly in the paper: let's just follow up from that.}
-%
 \begin{equation*}
@@
 \begin{equation*}
-%
 \frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
-%
 \end{equation*}
@@
 %
-\begin{align*}
-%
-&a_y^3[\ell_1,\ell_2] 
-= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
-\nonumber \\
+%\begin{align*}
+%%
+%&a_y^3[\ell_1,\ell_2] 
+%= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+%\nonumber \\
+%%
+%=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
+%\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
+%\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
+%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
+%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%%
+%\end{align*}
+%
+\begin{align*}
+%
+a_y^3[\ell_1,\ell_2] 
+=& \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+\\
 %
@@
 	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
-\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
-\nonumber \\
+ + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\ \\
 &+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
-\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+ + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
-\nonumber \\
+ \\
 &+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
-\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+ + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
-\nonumber \\
+\\
 &+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
-\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+ + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
 	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
@@
 \end{align*}
-%
 Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
@@
 and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$. The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
-%%	Plug in the explicit expressions of~\eqref{eq:mean_micrograph} and~\eqref{eq:ac2_micrograph} into the right hand side of the equality.
 
 \section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-
-%\TODO{Nicolas: I'm pretty sure this proof assumes $L \geq 3$: let's add it as an assumption in the prop.
-It also very clearly requires nonzero mean because of division by $E_4$, but we say that already.}
 
@@
 \begin{split}
-E_1 &:= a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2) \\
-& = \sigma^2a_y^1 + L\beta^2F_1,
+E_1 := a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2)  = \sigma^2a_y^1 + L\beta^2F_1,
 \end{split}
@@
 F_2 = a_x^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_x^3[j,j] + a_x^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
-% Nicolas: checked this formula with the matlab code on Sep 4, 2018: it's correct
 \end{equation*}
@@
 \begin{align}
-	E_5 & := a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j] \nonumber \\
-		& = L \beta F_2 + (6L-3)\sigma^2a_y^1.
+E_5 & := a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j]  = L \beta F_2 + (6L-3)\sigma^2a_y^1.
 \end{align}
@@
 \begin{split}
-\frac{\mathcal{B}}{\mathcal{C}} &= \frac{E_1 - (2L+1)(a_y^1)^3 - a_y^1E_3}{(a_y^1)^3} \\&= \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - E_3}{(a_y^1)^2}.
+\frac{\mathcal{B}}{\mathcal{C}} = \frac{E_1 - (2L+1)(a_y^1)^3 - a_y^1E_3}{(a_y^1)^3} = \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - E_3}{(a_y^1)^2}.
 \end{split}
@@
 \end{equation*}
-% Nicolas, Sep 4 2018: everything checked and correct until here.
 
@@
 \begin{align} \label{eq:ac_micrographs}
-\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} \\&+ b_p[\Bell_1,\ldots,\Bell_{p-1}], \nonumber \\ p=1,2,3, \quad \Bell_1,\ldots,\Bell_{p-1}&\in[-(P-1),P-1]^2, \nonumber
+\lim_{K\to\infty}\frac{1}{K}\sum_{i=1}^Ka^p_{\II_i}[\Bell_1,\ldots,\Bell_{p-1}]  &= \gamma\left\langle a^p_{I_\omega}[\Bell_1,\ldots,\Bell_{p-1}]\right\rangle_{\omega} + b_p[\Bell_1,\ldots,\Bell_{p-1}], \\ p=1,2,3, \quad & \Bell_1,\ldots,\Bell_{p-1}\in[-(P-1),P-1]^2, \nonumber
 \end{align}
@@
 Then, we have
+%\begin{align}
+%& a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}]  \nonumber\\
+%&= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\nonumber\\
+%&= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \nonumber\\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
+%&= \frac{MP^2}{N^2}\cdot\frac{1}{M}\sum_{t=1}^M\frac{1}{P^2}\sum_{i,j=0}^{P-1} I_{\omega_t}[\mb i]I_{\omega_t}[\mb i+\Bell_1]\cdots I_{\omega_t}[\mb i + \Bell_{p-1}]\nonumber\\
+%&= \frac{MP^2}{N^2}\frac{1}{M}\sum_{t=1}^Ma^p_{I_{\omega_t}}[\Bell_1,\ldots, \Bell_{p-1}]\nonumber\\
+%&\to \gamma\langle a^p_{I_{\omega}}[\Bell_1,\ldots, \Bell_{p-1}]\rangle_{\omega},
+%\label{eq:general_moment}
+%\end{align}
 \begin{align}
-	& a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}]  \nonumber\\
-	&= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\nonumber\\
+ a^p_{\widetilde\II}[\Bell_1,\ldots, \Bell_{p-1}]  &= \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}]\nonumber\\
 &= \frac{1}{N^2}\sum_{t=1}^M\sum_{\mb i\in\mc S_t}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\cdots \widetilde\II[\mb i + \Bell_{p-1}] \nonumber\\ %+ \frac{1}{N^2}\sum_{\mb i\in Z}\widetilde\II[\Bell]\widetilde\II[\mb i + \Bell]\cdots \widetilde\II(\mb i + \Bell_{p-1})\\
@@
 i+\Bell]\\
-&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell].
+&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell].
 \end{aligned}\]
@@
 \[\begin{aligned} 
-&a^3_\II[\Bell_1, \Bell_2]  \\&
+a^3_\II[\Bell_1, \Bell_2]  &
 = \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
@@
 	\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
-	&= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
-	\\& \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
-	%&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
-	%&= \gamma\sigma^2Lm_1[\phi],
+	= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
+	 \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, 
 	\end{aligned}\]
@@
 Thus, we conclude that
-\begin{multline} \label{eq:third_order_ac_micro_volume}
+%\begin{multline} \label{eq:third_order_ac_micro_volume}
+%a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
+%a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} \\ +
+%\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
+%\delta[\Bell_1] + \delta[\Bell_2]\Big),
+%\end{multline}
+\begin{equation} \label{eq:third_order_ac_micro_volume}
 a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
-a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} \\ +
+a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega}  +
 \gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
 \delta[\Bell_1] + \delta[\Bell_2]\Big),
-\end{multline}
+\end{equation}
 where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
@@
 \[ \II^{\alpha,-}[\mb i+\Bell] \approx \sum_{k,q}\overline{a_{k,q}}e^{-\iota k\alpha}\psi_{k,q}[\Bell].\]
-%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
 Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
@@
 We now turn out attention to the third order autocorrelation. Following the same lines, we define the coefficients:
+%\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
+%&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\\&\times \left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
+%&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
+%\end{aligned}\]
 \[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
-&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\\&\times \left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
+&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right) \left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
 &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
@@
 Averaging over all rotations of $\II$ and its reflection, we obtain
+%\begin{align} \label{eq:third_order_ac_pswf}
+%&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha \nonumber\\
+%&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. \nonumber 
+%\end{align}
 \begin{align} \label{eq:third_order_ac_pswf}
-&\mathfrak{a}^3[k_1,q_1;k_2,q_2] = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\\&\times \frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha \nonumber\\
-&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. \nonumber 
+\mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] \frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha \nonumber\\
+&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. 
 \end{align}
@@
 Finally, we treat the bias terms:
-\begin{align*}
-&\mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\\&\times \left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
+%\begin{align*}
+%&\mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\\&\times \left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
+%\end{align*}
+\begin{align*}
+\mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].
 \end{align*}
@@
 where
-\[\begin{aligned} b_{N,n}(\omega) &= \frac{4}{\sqrt{2\pi}|\alpha_{N,n}|^2}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
-&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{\sqrt{8\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
-&= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
+%\[\begin{aligned} b_{N,n}(\omega) &= \frac{4}{\sqrt{2\pi}|\alpha_{N,n}|^2}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
+%&= \sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{\sqrt{8\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega)\\&\times \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right),\\
+%&= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
+\begin{align*}
+ b_{N,n}(\omega) &= \frac{4}{\sqrt{2\pi}|\alpha_{N,n}|^2}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-\iota N\theta}k\, dk\, d\theta,\\
+&=\sum_{\ell,m,m',s}\tamir_{\ell,m,s}\left[\frac{\sqrt{8\pi}}{\alpha_{N,n}}Y_{\ell}^{m'}(\pi/2,0)\right]D_{m',m}^{\ell}(\omega) \left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{\iota(m'-N)\theta}\, d\theta\right)\\
+&= \sum_{\vert N\vert\leq \ell}\sum_{m,s}\tamir_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},
+\end{align*}
+
 where the coefficients
@@
 The third-order autocorrelation of the volume can be expressed in terms of~\eqref{eq:proj_expansion}:
+%\begin{align} \label{eq:third_order_ac_volume}
+%\langle
+%a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\mb i]I_{\omega}[\mb i+\Bell_1]\overline{I_{\omega}([\mb i+\Bell_2])}\rangle_{\omega},\\
+%&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\nonumber\\&\times \frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
 \begin{align} \label{eq:third_order_ac_volume}
@@
 a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} &= \frac{1}{L^2}\sum_{\mb i}\langle I_{\omega}[\mb i]I_{\omega}[\mb i+\Bell_1]\overline{I_{\omega}([\mb i+\Bell_2])}\rangle_{\omega},\\
-&\approx \sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega}\nonumber\\&\times \frac{1}{L^2}\sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber\end{align}
+&\approx \frac{1}{L^2}\sum_{\substack{N_1,n_1\\N_2,n_2\\N_3,n_3}} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} \sum_{\mb i}\psi_{N_1,n_1}[\mb i]\psi_{N_2,n_2}[\mb i+\Bell_1]\overline{\psi_{N_3,n_3}([\mb i+\Bell_2])},\nonumber
+\end{align}
 where the approximation is due to discretization. 
 Now,
-\[\begin{aligned} \langle &b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} \\&= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\\&\times \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
-&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
+%\[\begin{aligned} \langle &b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} \\&= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\\&\times \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega}\\
+%&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
+\[\begin{aligned} \langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\\ell_3,m_3,s_3}}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_3,s_3}}\\&\times \langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}(\omega)\overline{D_{N_3,m_3}^{\ell_3}}(\omega)\rangle_{\omega} \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_3,n_3}},\end{aligned},\]
 where the latter coefficients are given explicitly in~\eqref{eq:beta}. Using standard properties of D-Wigner functions, we obtain  
-\begin{align*}
-&\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\nonumber
+%\begin{align*}
+%&\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3}\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),\nonumber
+%\end{align*}
+\begin{align*}
+\left\langle D_{N_1,m_1}^{\ell_1}(\omega)D_{N_2,m_2}^{\ell_2}\overline{D_{N_3,m_3}^{\ell_3}}\right\rangle_{\omega} = (-1)^{N_3+m_3} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_3\end{array}\right)\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right),
 \end{align*}
@@
 Notably, these terms are zero unless $m_1+m_2+m_3=0$ and $|\ell_1-\ell_2|\leq \ell_3\leq \ell_1+\ell_2$. Thus,  we conclude that 
+%\begin{align} \label{eq:b_average}
+%&\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} = \delta_{N_3,N_1+N_2}\\&\times \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
+%&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\nonumber\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\nonumber\\
+%&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_1+N_2,n_3}}. \nonumber
+%\end{align}
 \begin{align} \label{eq:b_average}
-&\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} = \delta_{N_3,N_1+N_2}\\&\times \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\nonumber\\
-&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\nonumber\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\nonumber\\
-&\times \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_1+N_2,n_3}}. \nonumber
+\langle b_{N_1,n_1}(\omega)b_{N_2,n_2}(\omega)\overline{b_{N_3,n_3}}(\omega)\rangle_{\omega} &= \delta_{N_3,N_1+N_2} \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m2,s_3}}\\
+&\times (-1)^{N_1+N_2+m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N_2\end{array}\right)\nonumber\\&\times \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right) \widehat\beta_{\ell_1,s_1;N_1,n_1}\widehat\beta_{\ell_2,s_2;N_2,n_2}\overline{\widehat\beta_{\ell_3,s_3;N_1+N_2,n_3}}.
+\nonumber
 \end{align}
@@
 \begin{align} \label{eq:ac_3_prolates}
- &\mathfrak{a}_x^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\nonumber \\ \ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
+\mathfrak{a}_x^3[k,q_1,q_2] &= \sum_{\substack{\ell_1,m_1,s_1\nonumber \\ \ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
 &\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
@@
 \end{align}
-%
-%\[\begin{aligned} \label{eq:ac_3_prolates} &\mathfrak{a}_x^3[k,q_1,q_2] = \sum_{\substack{\ell_1,m_1,s_1\\\ell_2,m_2,s_2\\s_3}}\sum_{\ell_3=|\ell_1-\ell_2|}^{\min(L,\ell_1+\ell_2)}\tamir_{\ell_1,m_1,s_1}\tamir_{\ell_2,m_2,s_2}\overline{\tamir_{\ell_3,m_1+m_2,s_3}}\\
-%&\times (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-%&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\\&\times\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\mb i]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\mb i]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\mb i]}.
-\end{aligned}\]
 In practice, the last two lines of the above expression for $\mathfrak{a}_x^3[k,q_1,q_2]$ is precomputed, and both the integration over $\mb i$ and over $\Bell$ is performed on the grid of the images in the dataset, to match the integration performed on the actual images.
 
-%\subsection{The power spectrum}
 \paragraph{Second-order autocorrelation.}
@@
 
-%Since the Fourier transformed volume is given by
-%\[ \widehat V(k,\theta,\varphi) =
-%\sum_{\ell,m,s}a_{\ell,m,s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k),\]
 Since $j_{\ell,s}(0) = 0$ unless $\ell=0$, and since
@@
 
-%\TODO{=========== Tamir: Stopped here ===============}
-
-%\TODO{=========== NOT SURE WHAT IS THAT ===============}
-%\begin{align*}
-%&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
-%&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
-%&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
-%\end{align*}
-%and 
-%\begin{align*}
-%\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
-%\end{align*}
-
-%\subsection{Implementation details}
-%To implement the above formula, we precompute the quantities
-%\[ W(\ell_1,\ell_2,\ell_3,m_1,m_2) = (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right),\]
-%and
-%\[ B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3) = \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}W(\ell_1,\ell_2,\ell_3,N_1,N_2)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},\]
-%so in each iteration of the optimization we compute
-%\[\begin{aligned} \mathfrak{m}_3(k,q_1,q_2) = \sum_{\substack{\ell_1,\ell_2,\ell_3\\m_1,m_2\\s_1,s_2,s_3}}& W(\ell_1,\ell_2,\ell_3,m_1,m_2)B^{(k,q_1,q_2)}(\ell_1,\ell_2,\ell_3,s_1,s_2,s_3)\times\\ &a_{\ell_1,m_1,s_1}a_{\ell_2,m_2,s_2}\overline{a_{\ell_3,m_1+m_2,s_3}} .\end{aligned}\]
-%
-%The Wigner 3$j$ symbols are computed from the Racah formula
-%\[\begin{aligned} \left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_3\end{array}\right) &= \delta_{m_3,m_1+m_2}(-1)^{\ell_1-\ell_2+m_3}\sqrt{\Delta(\ell_1,\ell_2,\ell_3)}\\ &\times \prod_{i=1}^3\sqrt{(\ell_i-m_i)!(\ell_i+m_i)!}\times \sum_{t}\frac{(-1)^t}{x(t)},\end{aligned}\]
-%where
-%\[ x(t) = t!(\ell_3-\ell_2+t+m_1)!(\ell_3-\ell_1+t-m_2)!(\ell_1+\ell_2-\ell_3+t)!(\ell_1-t-m_1)!(\ell_2-t+m_2)!,\]
-%the sum is over all integer $t$ for which the arguments in the factorials in $x(t)$ are all nonnegative, and 
-%\[ \Delta(\ell_1,\ell_2,\ell_3) = \frac{(\ell_1+\ell_2-\ell_3)!(\ell_1-\ell_2+\ell_3)!(-\ell_1+\ell_2+\ell_3)!}{(\ell_1+\ell_2+\ell_3+1)!}.\]
-%
-
-%\section{Noisy micrograph moments}
-%We now suppose that the micrograph is perturbed by additive white
-%Gaussian noise, so we observe $\widetilde \II = \II + \varepsilon$ where
-%$\varepsilon\overset{\text{iid}}{\sim}\mathcal{N}(0, \sigma^2I)$. We proceed
-%to derive $\lim_{N\to\infty}m_2[\widetilde \II],\
-%m_3[\widetilde\II]$. For simplicity of notation,
-%we shall use vectorized indices $\mb i = (i,j)$.
-%
-%
-%\subsection{Expansion in PSWFs}
-%In practice, we compute the moments of our noisy micrograph in a
-%product basis of 2D prolates, so we need to derive the expansion
-%coefficients of the above bias terms in these functions for debiasing.
-%
-%To this end, writing (in the continuous case again)
-%\[ \delta(\Bell - \Bell_2) =
-%\sum_{k,q_1,q_2}\mathfrak{d}(k,q_1,q_2) \psi_{k,q_1}(\Bell)
-%\overline{\psi_{k,q_2}(\Bell_2)},\]
-%we get
-%\[\begin{aligned}
-%\mathfrak{d}(k,q_1,q_2) &= \int_{\Bell,
-%	\Bell_2}\delta(\Bell-\Bell_2)\overline{\psi_{k,q_1}(\Bell_1)}\psi_{k,q_2}(\Bell_2)\\
-%&=
-%\int_{\Bell_2}\overline{\psi_{k,q_1}(\Bell_2)}\psi_{k,q_2}(\Bell_2)\\
-%&= \delta_{q_1,q_2}.
-%\end{aligned}\]
-%
-%Similarly, writing
-%\[ \delta(\Bell_1) =
-%\sum_{k,q_1,q_2}\mathfrak{d}^{(1)}(k,q_1,q_2)
-%\psi_{k,q_1}(\Bell_1) \overline{\psi_{k,q_2}(\Bell_2)},\]
-%we get
-%\[\begin{aligned} 
-%\mathfrak{d}^{(1)}(k,q_1,q_2) &= \int_{\Bell_1,
-%	\Bell_2}\delta(\Bell_1)\overline{\psi_{k,q_1}(\Bell_1)}
-%\psi_{k,q_2}(\Bell_2)\\
-%&= \overline{\psi_{k,q_1}(\mb 0)}
-%\int_{\Bell_2}\psi_{k,q_2}(\Bell_2)\\
-%&= \delta_{k,0} R_{0,q_1}(0) \int_0^1R_{0,q_2}(r)r\, dr\\
-%&= \delta_{k,0} \frac{\alpha_{0,q_2}}{2\pi}R_{0,q_1}(0)R_{0,q_2}(0),
-%\end{aligned}\]
-%where we used the fact that $R_{0,q}$ satisfies
-%\[ \frac{\alpha_{0,q}}{2\pi}R_{0,q}(r) =
-%\int_0^1R_{0,q}(\rho)J_{0}(cr\rho)\rho\, d\rho,\]
-%where $J_k$ is the Bessel function of the first kind, and that
-%$J_0(0)=1$. 
-%A similar derivation applies to $\delta(\Bell_2)$. 
-%
-%Thus, in terms of the prolate expansion coefficients, our bias
-%formulas become
-%\[ \widetilde{\mathfrak{m}}_3(k,q_1,q_2) = \mathfrak{m}_3(k,q_1,q_2) +
-%\sigma^2m_1[\widetilde \II]\left[\delta_{q_1,q_2} + \delta_{k,0}\frac{1}{2\pi}(\alpha_{0,q_1}+\alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right].\]
-%
-%Similarly, for the power spectrum we get
-%\[ \widetilde{\mathfrak{m}}_2(q) = \mathfrak{m}_2(q) + \sigma^2\frac{1}{\sqrt{2\pi}}R_{0,q}(0).\]
-
-\putbib
-
-\end{bibunit}
-
 \end{document}

### 2019-01-30 inverse_problems/inverse_problems.tex
initial draft for inverse problem

\documentclass[12pt]{article}
\pdfoutput=1

\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{multirow}
\usepackage{color}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools} 
\usepackage{stackrel} 
%\usepackage[skip=1pt]{caption} % example skip set to 2pt

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ii}{\textbf{i}}
\newcommand{\jj}{\textbf{j}}

\newcommand{\II}{\mathcal{I}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\mb}{\mathbf}
\newcommand{\mk}{\mathfrak}
\newcommand{\mc}{\mathcal}
\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
\newcommand{\TODO}[1]{{\color{red}{[#1]}}}
\newcommand{\revised}[1]{{\color{blue}{#1}}}

%\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
\makeatletter

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\tamir}{x}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\RPP}{\mathbb{R}^{P\times P}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\hx}{\hat{x}} 
\newcommand{\one}{\mathbf{1}} 
\newcommand{\be}
{\begin{equation}}
\newcommand{\ee}
{\end{equation}}
%\renewcommand{\P}{\mathbb{P}}
\newcommand{\aseq}{\stackrel{a.s.}{=}}
\renewcommand{\P}{\mathrm{Prob}}

\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{claim}[thm]{\protect\claimname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}
\newtheorem*{lem*}{Lemma}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{plain}
\newtheorem{corollary}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{proposition}[thm]{\protect\propositionname}
\providecommand{\claimname}{Claim}
\providecommand{\definitionname}{Definition}
\providecommand{\lemmaname}{Lemma}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\corollaryname}{Corollary}
\providecommand{\propositionname}{Proposition}

\usepackage{authblk}
\renewcommand*{\Affilfont}{\normalsize}
\setlength{\affilsep}{2em}   % set the space between author and affiliation

\usepackage[margin=.6in]{geometry}

\newenvironment{myquote}[1]%
{\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
{\endlist}

\allowdisplaybreaks

\begin{document}

%\begin{frontmatter}

\title{TBD}
%
%\author[a]{Tamir Bendory}
%\author[b]{Nicolas Boumal} 
%\author[c]{William Leeb}
%\author[a,b]{Eitan Levin}
%\author[a,b]{Amit Singer}
%
%\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
%\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
%\affil[c]{School of Mathematics, University of
%	Minnesota, Minneapolis, MN, USA }

%\date{}
\maketitle

\begin{abstract}
abstract
%Single-particle cryo-electron microscopy (cryo-EM) has recently joined X-ray crystallography
%and NMR spectroscopy as a high-resolution structural method for biological macromolecules.
%In a cryo-EM experiment, the microscope produces images called micrographs. Projections of the molecule of interest are embedded in the micrographs at unknown locations, and under unknown viewing directions. Standard imaging techniques first locate these projections (detection) and then reconstruct the 3-D structure from them. Unfortunately, high noise levels hinder detection. When reliable detection is rendered impossible, the standard techniques fail. This is a problem especially for small molecules, which can be particularly hard to detect. In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection. 
%As a result, even small molecules should be within reach for cryo-EM. To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation analysis technique allows to go directly from the micrographs to the sought signals. This involves only one pass over the micrographs, which is desirable for large experiments. 
%We show numerical results and  discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
\end{abstract}

\section{Introduction}

Posing the problem: first the homogeneous case and then the heterogeneity. Later, motivating the model as an abstraction of cryo-EM, discuss the MRA-Kam's method relations, and maybe related topics.

%
%Cryo-electron microscopy (cryo-EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
%In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
%The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}. Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions. The goal is to construct 3-D models of the molecular structure from the micrographs.
%
%The signal to noise ratio (SNR) of the projections in the micrographs is a function of two dominating factors. On the one hand, the SNR is a function of the electron dose. To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels. On the other hand, the SNR is a function of the molecule size. The smaller the molecules, the fewer detected electrons carry information about them.
%
%All contemporary methods in the field split the reconstruction procedure into two main  stages.
%The first stage consists in extracting the various particle projections from the micrographs. This stage is called \emph{particle picking}. The second stage aims to construct a 3-D model of the molecular structure from these projections. The quality of the reconstruction eventually hinges on the quality of the particle picking stage. Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the SNR degrades.
%
%\begin{figure}[t]
%	\centering
%	\begin{subfigure}[h]{0.33\linewidth}
%		\centering
%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_clean}
%		\caption{$\sigma = 0$}
%	\end{subfigure}%
%	\begin{subfigure}[h]{0.33\linewidth}
%		\centering
%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s05}
%		\caption{$\sigma = 0.5$}
%	\end{subfigure}
%	\begin{subfigure}[h]{0.33\linewidth}
%		\centering
%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s3}
%		\caption{$\sigma = 3$}
%	\end{subfigure}
%	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$. Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein. In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image. In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known. By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
%	%\vspace{-8pt} 	
%\end{figure}

%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}	
%%	\vspace{-8pt} 
%\end{figure}
%
%Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR. This fact has been recognized early on by the cryo-EM community. In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
%\begin{myquote}{10pt}
%	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy? Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
%\end{myquote}
%In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
%Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}. 
%As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs. Yet, imaging such molecules is important for structure-guided drug design and other applications~\cite{scapin2018cryo}.
%
%The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
%Despite this progress, detecting small molecules in the micrographs remains a challenge.
%We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules. Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.  
%
%In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
%Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
%Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done. Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
%
%As a proof of concept, we first study a toy model  for which it is easier to convey the mathematical principles. 
%In this model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
%The goal is to estimate the planted image. The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably. 
%This problem is interesting on its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
%
%In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
%For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph. Importantly, there is no need to detect individual image occurrences. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself. To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem; see for instance Figure~\ref{fig:Einst_example}.
%
%Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well. Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles. In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
%We show a few numerical examples and outline the future developments required to make this method applicable to experimental  data. 
%
%Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}. In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged. In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template. In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure. This model bias is common to all particle picking methods based on template matching. In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias. %

%
%\section{Proof of concept: A mathematical toy model}
%
%In this section, we present a toy model in order to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible. Later, we discuss how these principles carry through for the SPR problem. We first formulate the model for 1-D signals to ease exposition.
%
%Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
%\begin{equation}
%y  =  x \ast s + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
%\label{eq:model}
%\end{equation}
%where $\ast$ denotes linear convolution. 
%While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
%This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. 
%The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem. As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$. 
%
%We assume the binary signal $s$ obeys a \emph{separation condition}:
%\begin{equation}
%\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
%\label{eq:spacing}
%\end{equation}
%In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
%
%Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
%forward model takes the form
%%
%\begin{math}
%%
%y = x\ast w + \varepsilon,  
%%
%\end{math} 
%%
%where $x$ is the unknown signal (the system's impulse response), $w$ is an unknown (often random) input sequence, and $\varepsilon$ is an additive noise.
%The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}. In the special case where $w$ is binary and satisfies our separation condition, we recover our model. 
%
%Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.  
%If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
%Methods based on such formulations are popular nowadays in cryo-EM; see for instance~\cite{sigworth1998maximum,scheres2012relion}. 
%Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}. 
%In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}. The EM method for discrete $w$ is based on a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}. However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets. 
%
%Because likelihood methods are computationally expensive, methods based on recovery from moments have also been previously used for system identification. Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}. Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.

%
%\section{The detection limit} \label{sec:detectionlimit}
%
%In the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
%To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise. Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
%The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$. 
%
%This decision problem can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$. There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively. We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution: if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2I_L)$ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2I_L)$. 
%
%We observe $X$, and our task is to estimate $\eta$. How reliably can this be done? If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise, if $q \leq 1/2$, the constant estimator $\hat{\eta} = 1$ is correct with probability $1-q$. The question is, can we do better than this?  We prove that, as $\sigma \to \infty$, the answer is no. The result is proved in Appendix~\ref{sec:proof_two_gauss}.
%
%\begin{proposition} \label{prop:two_gauss}
%	For any deterministic estimator $\hat{\eta }$ of $\eta$,
%	\begin{equation}
%	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] \leq \max(q, 1-q);
%	\end{equation}
%	that is: as the SNR deteriorates, the probability of success is no better than random chance.
%\end{proposition}
%
%Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
%In the next sections, we consider autocorrelation analysis for that purpose.

\section{The method of moments/ autocorrelation analysis} \label{sec:AC_analysis}

Presenting autocorrelations

%In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
%\begin{equation}
%a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
%\label{eq:ac_general}
%\end{equation}
%where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
%Explicitly, the first-, second- and third-order autocorrelations are given by: 
%\begin{align} 
%a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
%a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
%a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
%\end{align}
%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
%$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
%$
%For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
%
%Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show. It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
%\begin{equation}
%\gamma  = \frac{M L}{N}
%\label{eq:gamma}
%\end{equation}
%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
%imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
%
%For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$. Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
%We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large micrograph, it contains increasingly many signal occurrences, with constant signal density). In that regime, the law of large numbers can be used to show the following statement:
%\begin{equation} \label{eq:mean_micrograph}
%\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
%\end{equation}
%where equality holds almost surely (a.s.), meaning it holds with probability one.
%The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
%Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.) 
%
%We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries. Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence. As a result,
%\begin{equation}
%\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
%\label{eq:ac2_micrograph}
%\end{equation}
%for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise. The last part captures the autocorrelation of the noise. Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
%
%Along the same lines, one can establish a relation for third-order autocorrelations:
%\begin{equation}
% \label{eq:ac3_micrograph}
%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
%+\delta[\ell_1,\ell_2]\big),
%\end{equation}
%%\begin{equation}
%%\begin{split} \label{eq:ac3_micrograph}
%%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &\aseq \gamma a_{x}^3[\ell_1,\ell_2]  \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]
%%+\delta[\ell_1,\ell_2]\big),
%%\end{split}
%%\end{equation}
%for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
%Here too, few entries are affected by $\sigma$ in the limit.
%See Appendix~\ref{sec:autocorrelation_computation}.
%
%Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
%

\section{Theory}

\subsection{Theory for the 1-D homogeneous case}

\subsection{Equivalence between the spacing condition and the Poisson process}

\subsection{Theory for the 2-D case (relation with PR)}

\subsection{The heterogeneous case}

%\section{Recovering a signal from autocorrelations} \label{sec:recovery}
%
%A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations. Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
%%
%\begin{equation}
%%
%z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
%\label{eq-uniqueness}
%%
%\end{equation}
%This proves the following useful fact:
%\begin{proposition} \label{prop:uniqueness}
%	%
%	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
%\end{proposition}
%
%A couple of remarks are in order. First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations. In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
%Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
%However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}. 
%The sign ambiguity can be resolved by the mean of the signal if it is not zero. However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
%
%The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$. We will show, however, that $x$ is still determined by the observed moments of $y$.
%
%First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph. The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
%
%\begin{proposition} \label{prop:gamma}
%	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
%	\begin{equation}
%	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
%	\end{equation}
%\end{proposition}
%
%Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined. For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
%has Lebesgue measure zero. 
%In particular, this means that we can recover
%almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
%
%\begin{proposition} \label{prop:gamma_sigma}
%	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
%	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$. If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean. 
%\end{proposition}
%
%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
%\begin{corollary}
%	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
%\end{corollary}
%
%As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
%

\section{Algorithms and numerical experiments}

2-D homogeneous example, 1-D heterogeneous example, K-L figure for noiseless heterogeneous case

%
%The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs. To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.  Appendix~\ref{sec:numeric_details} provides additional details on the experiments. 
%The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
%
%\subsection{Toy model}
%In the first experiment, we estimated 
%an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels. Each micrograph contains, on average, 700 occurrences of the target image at random locations. 
%Thus, about 10\% of each micrograph contains signal. The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$. This high noise level is illustrated in Figure~\ref{fig:micro_example}. 
%To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known. Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}. 
%
%We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
%Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.  Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
%Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
%
%Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. %, and a movie is available as supplementary material.
%Figure~\ref{fig:error_per_micro} %(see appendix)
%presents the normalized recovery error as a function of the amount of data available.  This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}). As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
%
%
%\begin{figure}[h]
%	\centering
%	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
%	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
%\end{figure}
%
%
%In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
%Figure~\ref{fig:1D_example} %(see appendix) 
%shows recovery of a 1-D signal from the first three autocorrelations of the data.
%The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}; see Figure~\ref{fig:1D_obs_example}.  
%Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}. Crucially, the LS does not require  knowledge of $\sigma$. 
%
%
%\begin{figure}[h]
%	\centering
%	\includegraphics[width=\linewidth]{1D_example}
%	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions. The length of the micrograph was set to be $N = 410*M$. The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
%		The true value of $\gamma$ is $0.0512$.
%		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
%	}
%\end{figure}
%
%
%\begin{figure}[h]
%	\centering
%	\includegraphics[width=0.6\linewidth]{example_obs_1D}
%	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
%	}
%\end{figure}
%
%
%\subsection{Cryo-EM} The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
%The derivation of the first three autocorrelations of the micrographs and their relations to the volume itself are provided in Appendix~\ref{sec:ac_cryo}.
%In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. 
%Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations and from noisy micrographs. 
%Excerpts from the noisy micrographs are shown in Figure~\ref{fig:cryo_noisy_micros_for_rec}.
%Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.
%The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
%In the next section, we outline how we suggest to overcome the ill-conditioning in future work. 
%
%\begin{figure}[h]
%	\centering
%	\begin{subfigure}[h]{0.45\textwidth}
%		\centering
%		\includegraphics[angle=270, width=1\textwidth]{TRPV1_rec_incl_noisy_resize.eps}
%		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[h]{0.45\textwidth}
%		\centering
%		\includegraphics[angle=270, width=1\textwidth]{BPTI_maxL2_L20_resize.eps}
%		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
%	\end{subfigure} 
%	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
%		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
%		{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
%			The reconstructions  from clean autocorrelations are shown in yellow and recoveries from 
%			autocorrelations estimated from noisy data in gray. For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI. We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec} (see appendix)}.}
%	%	\vspace{-20pt} 	
%\end{figure}
%
%\begin{figure}[t!]
%	\centering
%	\begin{subfigure}[t]{0.245\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{TRPV1_clean_micro.png}
%		\caption{}
%	\end{subfigure} \hfill %\hspace{2pt}
%	\begin{subfigure}[t]{0.245\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{TRPV1_noisy_micro_SNR_16.png}
%		\caption{}
%	\end{subfigure} \hfill %\hspace{2pt}
%	\begin{subfigure}[t]{0.245\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{clean_micro_BPTI.png}
%		\caption{}
%	\end{subfigure} \hfill
%	\begin{subfigure}[t]{0.245\textwidth}
%		\centering
%		\includegraphics[scale=0.3]{noisy_micro_BPTI_SNR_64.png}
%		\caption{}
%	\end{subfigure}
%	\caption{\label{fig:cryo_noisy_micros_for_rec}  {Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts. (a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}} 
%\end{figure}
%
%\begin{figure}[t!]
%	\centering
%	\begin{subfigure}[t]{0.4\textwidth}
%		\centering
%		\includegraphics[scale=0.35]{TRPV1_trunc_FSC.eps}
%		\caption{}
%	\end{subfigure} \hfill %\hspace{2pt}
%	\begin{subfigure}[t]{0.4\textwidth}
%		\centering
%		\includegraphics[scale=0.35]{BPTI_FSC.eps}
%		\caption{}
%	\end{subfigure} 
%	\caption{\label{fig:cryo_FSC}  {Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth. (a) FSC for the TRPV1 reconstruction, giving resolution of $24$\AA; (b) FSC for the BPTI reconstruction, giving resolution of $13$\AA.}} 
%\end{figure}
%
%
%While we cannot provide a {high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
%and cryo-EM~\cite{henderson2013avoiding}.
%This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
%Figure~\ref{fig:cryo_detection} %(see appendix) 
%presents excerpts  of two noisy micrographs, only one of which contains projections.
%In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
%On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
%
%
%\begin{figure}[h]
%	\centering
%	\begin{subfigure}[t]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
%		\caption{An excerpt of the pure noise micrograph}
%	\end{subfigure} \hfill %\hspace{2pt}
%	\begin{subfigure}[t]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
%		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
%	\end{subfigure} \hfill %\hspace{2pt}
%	\begin{subfigure}[t]{0.3\textwidth}
%		\centering
%		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
%		\caption{An excerpt of the clean micrograph}
%	\end{subfigure}
%	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$. The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.  
%		The noise realization is identical in both micrographs.} 
%\end{figure}

\section{Relation with cryo-EM + experiments?}
%
%In the simplified mathematical model above, we showed it is possible to estimate a signal without detecting its appearances.  
%Our strategy is to compute autocorrelations of the micrographs and to relate these statistics to the unknown signal's parameters. Recovering the parameters from the statistics reduces to solving a set of polynomial equations. 
%
%We also showed how this technique can, in principle, be applied to cryo-EM.
%Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation. Concerns for model bias are also greatly reduced since no template matching is involved.
%Additionally,  our technique also allows the use of much lower defocus values. Lower defocus means lower contrast, but will maintain  higher frequency information. Consequently, we may be able to get high resolution reconstructions from fewer micrographs.
%
%Looking toward applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs. 
%In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
%We recognize that significant challenges lay ahead for the implementation of the proposed approach to {high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
%
%The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
%This suggests that fourth-order autocorrelation may be necessary. This in turn would imply that the procedure might require a large amount of data. 
%Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term. Still, large amounts of data also require large amounts of computation. On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs. It can even be done in a  streaming mode, as only one pass through each micrograph is necessary. The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs. Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary. Of course, an important question then is whether the equations can be solved accurately and efficiently in practice. 
%
%To reach high-resolution reconstruction, beyond data acquisition and computational challenges, there are modeling issues  to consider.
%In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted. All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects. 
%For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
%Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function. Such a function models the distribution of distances between neighboring projections. The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
%All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research. 
%
%\section*{Acknowledgment}
%The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
%The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
%NB is partially supported by NSF award DMS-1719558.

\bibliographystyle{plain}
\bibliography{ref}

\end{document}

### 2019-01-30 inverse_problems/inverse_problems.tex
update of the inverse problem draft (building the structure)

@@
 
-Posing the problem: first the homogeneous case and then the heterogeneity. Later, motivating the model as an abstraction of cryo-EM, discuss the MRA-Kam's method relations, and maybe related topics.
+\subsection{Model}
 
+In this paper, we consider the problem of recovering signals that appear 
+multiple times at unknown locations in a noisy measurement. This problem can be conveniently posed as  \emph{blind deconvolution}.
+Let $x\in\RL$ be the sought signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
+Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+\begin{equation} 
+y  =  x \ast s + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{equation}
+where $\ast$ denotes linear convolution. 
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. 
+We refer to~\eqref{eq:model} as the \emph{homogeneous model}.
+This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
+As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
+This model appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}
+
+We also consider a natural generalization, called the \emph{heterogeneous model}, in which one aims to estimate a set of $K$ signals $x_1,\ldots,x_K\in\RL$ from their mixed blind deconvolution
+\begin{equation} 
+y  =  \sum_{i=1}^Kx_i \ast s_i + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+\label{eq:model}
+\end{equation}
+where again $s_i$ denotes a binary signal.
+
+The signals $s_i$ indicate the support of the occurrences of $x$ in the data. We will consider two generative models for $s$: well-spaced deterministic model, and a stochastic Possion model.
+
+\paragraph{Well-separated support model:} In this model, 
+we assume the binary signal $s$ obeys \TODO{This is not accurate}
+\begin{equation}
+\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
+\label{eq:spacing}
+\end{equation}
+In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
 %
-%Cryo-electron microscopy (cryo-EM) is an imaging technique in structural biology used for single particle reconstruction (SPR) of macromolecules.
-%In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
-%The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
+\paragraph{Poisson support model:}
+
+The relation between the two models is formulated in Section~\ref{sec:support}.
+
+In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
+For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
+Importantly, there is no need to detect individual image occurrences.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
+To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem
+
+\subsection{Main motivation: single-particle reconstruction using cryo-electron microscopy}
+This work is motivated by the problem of single-particle reconstruction using cryo-electron microscopy (cryo-EM).  Cryo-EM is revolutionizing the field of structural biology, enabling XXX.
+
+In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
+The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
 The goal is to construct 3-D models of the molecular structure from the micrographs.
-%
-%The signal to noise ratio (SNR) of the projections in the micrographs is a function of two dominating factors.
+
+The signal to noise ratio (SNR) of the projections in the micrographs is a function of two dominating factors.
 On the one hand, the SNR is a function of the electron dose.
@@
 The smaller the molecules, the fewer detected electrons carry information about them.
-%
-%All contemporary methods in the field split the reconstruction procedure into two main  stages.
-%The first stage consists in extracting the various particle projections from the micrographs.
+
+All contemporary methods in the field split the reconstruction procedure into two main  stages.
+The first stage consists in extracting the various particle projections from the micrographs.
 This stage is called \emph{particle picking}.
@@
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Figure~\ref{fig:micro_example} illustrates how particle picking becomes increasingly challenging as the SNR degrades.
-%
-%\begin{figure}[t]
-%	\centering
-%	\begin{subfigure}[h]{0.33\linewidth}
-%		\centering
-%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_clean}
-%		\caption{$\sigma = 0$}
-%	\end{subfigure}%
-%	\begin{subfigure}[h]{0.33\linewidth}
-%		\centering
-%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s05}
-%		\caption{$\sigma = 0.5$}
-%	\end{subfigure}
-%	\begin{subfigure}[h]{0.33\linewidth}
-%		\centering
-%		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s3}
-%		\caption{$\sigma = 3$}
-%	\end{subfigure}
-%	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
-In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
-By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
-%	%\vspace{-8pt} 	
-%\end{figure}
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
+This fact has been recognized early on by the cryo-EM community.
+In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following
+In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa).
 
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
-%	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
-%%	\vspace{-8pt} 
-%\end{figure}
-%
-%Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following questions:
-%\begin{myquote}{10pt}
-%	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy?
-Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
-%\end{myquote}
-%In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-%Joachim Frank voices a similar observation in his 2017 Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2$ $\times$ Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}.
-%As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
+As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
 Yet, imaging such molecules is important for structure-guided drug design and other applications~\cite{scapin2018cryo}.
-%
-%The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%Despite this progress, detecting small molecules in the micrographs remains a challenge.
-%We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
+
+The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+Despite this progress, detecting small molecules in the micrographs remains a challenge.
+We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
 Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
-%
-%In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
-%Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
-%Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done.
-Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-%
-%As a proof of concept, we first study a toy model  for which it is easier to convey the mathematical principles. 
-%In this model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
-%The goal is to estimate the planted image.
-The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably.
-%This problem is interesting on its own as it appears in other scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-%
-%In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
-%For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
-Importantly, there is no need to detect individual image occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem; see for instance Figure~\ref{fig:Einst_example}.
+
+In a recent paper~\cite{bendory2018toward} by the authors, it was suggested to bypass the particle picking stage and the reconstruct the 3-D structure directly from the micrograph.
+In that paper, we have shown that, at least in principle, the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+The principle mathematical tool is the method of moments, or autocorrelation analysis, described in Section~\ref{sec:AC_analysis}.
+
+This goal of  this paper is to provide a theoretical and numerical justification for the method proposed in~\cite{bendory2018toward}.  
+In particular, the homogeneous  model serves as an abstraction of the cryo-EM problem.
+While in cryo-EM the 2-D images are tomographic projections of a 3-D structure, taken from unknown viewing directions, in the homogeneous model we observe the same 2-D image again and again.
+The heterogeneous case generalizes to multiple signals.
+
+To talk about the MRA-Kam's method relations. Also, model bias 
+\TODO{Where do we discuss the limits of detection?}
 %
@@
 
-%
-%\section{Proof of concept: A mathematical toy model}
-%
-%In this section, we present a toy model in order to introduce the mathematical principles enabling estimation of a signal in a low SNR regime, even when detection is impossible.
-Later, we discuss how these principles carry through for the SPR problem.
-We first formulate the model for 1-D signals to ease exposition.
-%
-%Let $x\in\RL$ be the target signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
-Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
-%\begin{equation}
-%y  =  x \ast s + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
-%\label{eq:model}
-%\end{equation}
-%where $\ast$ denotes linear convolution. 
-%While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$.
-%This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-%The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem.
-As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
-%
-%We assume the binary signal $s$ obeys a \emph{separation condition}:
-%\begin{equation}
-%\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
-%\label{eq:spacing}
-%\end{equation}
-%In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the micrograph.
-%
 %Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
@@
 \section{The method of moments/ autocorrelation analysis} \label{sec:AC_analysis}
+\TODO{copied from PNAS's paper}
+In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\begin{equation}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+\label{eq:ac_general}
+\end{equation}
+where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+Explicitly, the first-, second- and third-order autocorrelations are given by: 
+\begin{align} 
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
+$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$
+For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
 
-Presenting autocorrelations
+Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
+\begin{equation}
+\gamma  = \frac{M L}{N}
+\label{eq:gamma}
+\end{equation}
+denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
+imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
 
-%In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-%\begin{equation}
-%a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
-%\label{eq:ac_general}
-%\end{equation}
-%where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
-%Explicitly, the first-, second- and third-order autocorrelations are given by: 
-%\begin{align} 
-%a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-%a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
-%a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
-%\end{align}
-%The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-%$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-%$
-%For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
-%
-%Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
-%\begin{equation}
-%\gamma  = \frac{M L}{N}
-%\label{eq:gamma}
-%\end{equation}
-%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
-%imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-%
-%For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
+For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
 Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-%We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large micrograph, it contains increasingly many signal occurrences, with constant signal density).
+We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large micrograph, it contains increasingly many signal occurrences, with constant signal density).
 In that regime, the law of large numbers can be used to show the following statement:
-%\begin{equation} \label{eq:mean_micrograph}
-%\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
-%\end{equation}
-%where equality holds almost surely (a.s.), meaning it holds with probability one.
-%The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-%Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.) 
-%
-%We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
+\begin{equation} \label{eq:mean_micrograph}
+\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
+\end{equation}
+where equality holds almost surely (a.s.), meaning it holds with probability one.
+The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+
+We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
 Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
 As a result,
-%\begin{equation}
-%\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
-%\label{eq:ac2_micrograph}
-%\end{equation}
-%for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
+\begin{equation}
+\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
+\label{eq:ac2_micrograph}
+\end{equation}
+for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
 The last part captures the autocorrelation of the noise.
 Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
-%
-%Along the same lines, one can establish a relation for third-order autocorrelations:
-%\begin{equation}
-% \label{eq:ac3_micrograph}
-%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
-%+\delta[\ell_1,\ell_2]\big),
-%\end{equation}
-%%\begin{equation}
-%%\begin{split} \label{eq:ac3_micrograph}
-%%\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &\aseq \gamma a_{x}^3[\ell_1,\ell_2]  \\& + \sigma^2\gamma a_{x}^1 \cdot \big(\delta[\ell_1,0]+\delta[0,\ell_2]
-%%+\delta[\ell_1,\ell_2]\big),
-%%\end{split}
-%%\end{equation}
-%for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
-%Here too, few entries are affected by $\sigma$ in the limit.
-%See Appendix~\ref{sec:autocorrelation_computation}.
-%
-%Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
-%
+
+Along the same lines, one can establish a relation for third-order autocorrelations:
+\begin{equation}
+ \label{eq:ac3_micrograph}
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
++\delta[\ell_1,\ell_2]\big),
+\end{equation}
+for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
+Here too, few entries are affected by $\sigma$ in the limit.
+
+Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
 
@@
 
-\subsection{Equivalence between the spacing condition and the Poisson process}
+A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
+Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
+%
+\begin{equation}
+%
+z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+\label{eq-uniqueness}
+%
+\end{equation}
+This proves the following useful fact:
+\begin{proposition} \label{prop:uniqueness}
+	%
+	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+\end{proposition}
+
+A couple of remarks are in order.
+First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+%Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
+
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
+We will show, however, that $x$ is still determined by the observed moments of $y$.
+
+First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
+The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
+
+\begin{proposition} \label{prop:gamma}
+	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
+	\begin{equation}
+	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	\end{equation}
+\end{proposition}
+
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined.
+For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
+has Lebesgue measure zero. 
+In particular, this means that we can recover
+almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
+
+\begin{proposition} \label{prop:gamma_sigma}
+	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
+	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
+\end{proposition}
+
+From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
+\begin{corollary}
+	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+\end{corollary}
+
+As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
+
+\subsection{Equivalence between the spacing condition and the Poisson process} \label{sec:support}
 
 \subsection{Theory for the 2-D case (relation with PR)}
+
+However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
 
@@
 %
-%A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
-Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
-%%
-%\begin{equation}
-%%
-%z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
-%\label{eq-uniqueness}
-%%
-%\end{equation}
-%This proves the following useful fact:
-%\begin{proposition} \label{prop:uniqueness}
-%	%
-%	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
-%\end{proposition}
-%
-%A couple of remarks are in order.
-First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-%Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
-%However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-%The sign ambiguity can be resolved by the mean of the signal if it is not zero.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-%
-%The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
-We will show, however, that $x$ is still determined by the observed moments of $y$.
-%
-%First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
-The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
-%
-%\begin{proposition} \label{prop:gamma}
-%	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
-%	\begin{equation}
-%	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
-%	\end{equation}
-%\end{proposition}
-%
-%Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-%has Lebesgue measure zero. 
-%In particular, this means that we can recover
-%almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
-%
-%\begin{proposition} \label{prop:gamma_sigma}
-%	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
-%	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
-%\end{proposition}
-%
-%From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
-%\begin{corollary}
-%	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-%\end{corollary}
-%
-%As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
 %
@@
 
+\appendix
+
+\section{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
+
+In the limit, 
+\begin{equation*}
+(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j].
+\end{equation*}
+Similarly,  
+\begin{equation*}
+\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell],
+\end{equation*}
+and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$. The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
+
+\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+
+We prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
+For convenience, we work with $\beta = \gamma / L$ rather than $\gamma$ itself.
+To this end, we construct two quadratic equations satisfied by $\beta$ and whose coefficients can be computed from observable quantities (in the limit).
+Then, we show that these equations are independent, and hence that $\beta$ is uniquely defined.
+Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
+
+Throughout the proof, it is important to distinguish between observed and unobserved values.
+We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$. We use $F_i$ to denote functions of the signal's autocorrelations (which are not directly observable).
+
+In the limit $N \to \infty$, almost surely, $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones.
+(In this whole section, for clarity, we now omit to specify that identities hold almost surely in the limit.) Consider the product:
+\begin{equation}\label{eq:E1}
+\begin{split}
+E_1 := a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2)  = \sigma^2a_y^1 + L\beta^2F_1,
+\end{split}
+\end{equation}
+where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
+% Nicolas: the expression for F_1 is correct, see identifiability_of_gamma_and_sigma_Sep4_2018.m and notes Sep 4, 2018
+The terms of $F_1$ can also be estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable:
+\begin{align} 
+E_2 & := a_y^3[0,0] + \sum_{j=1}^{L-1}(a_y^3[j,j] + a_y^3[0,j]) \nonumber\\
+& = L\beta F_1 + (2L+1)\sigma^2a_y^1. \label{eq:E2}
+\end{align}
+% Nicolas: checked this one too.
+Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get:
+\begin{equation} \label{eq:E12}
+E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
+\end{equation}
+Let $E_3:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$; recall from Proposition~\ref{prop:gamma}:
+\begin{equation} \label{eq:sigma2}
+\sigma^2 = E_3 - (a^1_y)^2/\beta. 
+\end{equation} 
+Plugging into~\eqref{eq:E12} and rearranging, we get a first quadratic equation in $\beta$,
+\begin{equation} \label{eq:quad1}
+\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
+\end{equation}
+where 
+\begin{align*}
+\mathcal{A} &= E_2 - (2L+1)a_y^1E_3, \\ 
+\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1E_3  , \\
+\mathcal{C} &= -(a_y^1)^3.
+\end{align*}
+Importantly, these coefficients are observable quantities. As we assume throughout this proof that $x$ has nonzero mean, $a_y^1 \neq 0$ and we conclude that this equation is non-trivial.
+
+Next, we derive the second quadratic equation for $\beta$. We notice that 
+\begin{equation} \label{eq:E3}
+E_4 := \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
+\end{equation}
+where $F_2 = \frac{1}{L}(\one ^Tx)^3$, and we can work out that:
+\begin{equation*}
+F_2 = a_x^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_x^3[j,j] + a_x^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
+\end{equation*}
+Once again, $F_2$ can be estimated from $a_y^3$, taking bias and scaling into account:
+\begin{align}
+E_5 & := a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j]  = L \beta F_2 + (6L-3)\sigma^2a_y^1.
+\end{align}
+Consider the following ratio:
+\begin{equation*} 
+\frac{E_5}{E_4} = \frac{L}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_4}.
+\end{equation*}
+From the latter, we deduce:
+\begin{equation*}
+\sigma^2 = \frac{E_5}{a_y^1(6L-3)}  - \frac{LE_4}{\beta^2a_y^1(6L-3)}.
+\end{equation*}
+Using~\eqref{eq:sigma2} and rearranging, we get the second quadratic:
+\begin{equation} \label{eq:quad2}
+\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
+\end{equation}
+where
+\begin{align*}
+\mathcal{D} &= E_3 - \frac{E_5}{a_y^1(6L-3)}, \\ 
+\mathcal{E} &= -(a_y^1)^2, \\
+\mathcal{F} &= \frac{LE_4}{a_y^1(6L-3)}.
+\end{align*}
+It is also non-trivial since $E_4 \neq 0$.
+
+To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
+To this end, it is enough to show that the ratios between coefficients differ.
+From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have:
+\begin{equation*}
+\begin{split}
+\frac{\mathcal{B}}{\mathcal{C}} = \frac{E_1 - (2L+1)(a_y^1)^3 - a_y^1E_3}{(a_y^1)^3} = \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - E_3}{(a_y^1)^2}.
+\end{split}
+\end{equation*}
+In addition, using~\eqref{eq:E3},
+\begin{equation*}
+\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_4} = 3 - 6L . 
+\end{equation*}
+For contradiction, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, that is, 	
+\begin{equation*}
+a_y^2[0] - (2L+1)(a_y^1)^2 - E_3 = (a_y^1)^2(3-6L).
+\end{equation*}
+Rewriting the identity in terms of $x$ and dividing by $\beta$ we get:
+\begin{equation} \label{eq:cond}
+4(L-1)\beta (\1^\top x)^2  - (\1^\top x)^2 + \|x\|^2 = 0.
+\end{equation}	
+For generic $x$,  this polynomial equation is not satisfied so that the quadratic equations are independent. 
+Furthermore, from the inequality $L\|x\|^2 \ge (\1^\top x)^2$ it follows immediately that the equations must be independent so long as
+\begin{equation*}
+\beta > \frac{1}{4L}.
+\end{equation*}
+
 \end{document}

### 2019-01-30 inverse_problems/inverse_problems.tex
update

@@
 
-2-D homogeneous example, 1-D heterogeneous example, K-L figure for noiseless heterogeneous case
+The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
+To illustrate the underlying principles of the method, we present several numerical examples.
+The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
 
-%
-%The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
-To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.
-Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
-%The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
-%
-%\subsection{Toy model}
-%In the first experiment, we estimated 
-%an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+In the first experiment, we estimated 
+an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
 Each micrograph contains, on average, 700 occurrences of the target image at random locations.
-%Thus, about 10\% of each micrograph contains signal.
+Thus, about 10\% of each micrograph contains signal.
 The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
 This high noise level is illustrated in Figure~\ref{fig:micro_example}.
-%To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
+To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
 Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
-%
-%We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
-%Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
+
+We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
+Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
 Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
-%Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
-%
-%Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. %, and a movie is available as supplementary material.
-%Figure~\ref{fig:error_per_micro} %(see appendix)
-%presents the normalized recovery error as a function of the amount of data available.
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. 
+Figure~\ref{fig:error_per_micro} %(see appendix)
+presents the normalized recovery error as a function of the amount of data available.
 This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
 As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-%
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
-%	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-%\end{figure}
-%
-%
-%In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$.
-%Figure~\ref{fig:1D_example} %(see appendix) 
-%shows recovery of a 1-D signal from the first three autocorrelations of the data.
-%The autocorrelations are computed from noisy micrographs with $\sigma=3$ that obey the separation condition of~\eqref{eq:spacing}; see Figure~\ref{fig:1D_obs_example}.  
-%Both the signal  and $\gamma$ are estimated simultaneously from the observed autocorrelations by LS fitting; more details are given in Appendix~\ref{sec:numeric_details}.
-Crucially, the LS does not require  knowledge of $\sigma$.
-%
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=\linewidth]{1D_example}
-%	\caption{\label{fig:1D_example} Recovery of a 1-D signal of length $L=21$ at noise level $\sigma = 3$ from $M$ repetitions.
-The length of the micrograph was set to be $N = 410*M$.
-The first three panels (left to right) show reconstruction with different $M$ values compared to the ground truth signal (in blue).
-%		The true value of $\gamma$ is $0.0512$.
-%		The relative errors of $\gamma$ for the three panels are: $4.8\%,4\%,1.2\%$. The right panel shows the relative error as a function of $M$. 
-%	}
-%\end{figure}
-%
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.6\linewidth]{example_obs_1D}
-%	\caption{\label{fig:1D_obs_example} An example for a 1-D noisy measurement for the experiment in Figure~\ref{fig:1D_example}. The signal occurrences appear in blue, and the noisy data in green.
-%	}
-%\end{figure}
-%
-%
-%\subsection{Cryo-EM} The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
-%The derivation of the first three autocorrelations of the micrographs and their relations to the volume itself are provided in Appendix~\ref{sec:ac_cryo}.
-%In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. 
-%Figure~\ref{fig:cryo_recon} shows recovery of the 3-D volume from the clean autocorrelations and from noisy micrographs. 
-%Excerpts from the noisy micrographs are shown in Figure~\ref{fig:cryo_noisy_micros_for_rec}.
-%Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing high-resolution recovery from noisy data.
-%The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
-%In the next section, we outline how we suggest to overcome the ill-conditioning in future work. 
-%
-%\begin{figure}[h]
-%	\centering
-%	\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[angle=270, width=1\textwidth]{TRPV1_rec_incl_noisy_resize.eps}
-%		\caption{TPRV1 with cutoff $L_{\text{max}}=5$}\label{fig:TRPV1_recon}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[h]{0.45\textwidth}
-%		\centering
-%		\includegraphics[angle=270, width=1\textwidth]{BPTI_maxL2_L20_resize.eps}
-%		\caption{BPTI with cutoff $L_{\text{max}}=2$}\label{fig:BPTI_recon}
-%	\end{subfigure} 
-%	\caption{\label{fig:cryo_recon} Reconstructions from the first, second and third order autocorrelations.
-%		The ground truth volumes were expanded according to~\eqref{eq:volume_expansion_app} with cutoff $L_{\text{max}}$.
-%		{The original molecules are shown in purple and the (smoothed) ground truths in blue  to illustrate the smoothing effect of our downsampling and truncation of the spherical harmonics expansion.
-%			The reconstructions  from clean autocorrelations are shown in yellow and recoveries from 
-%			autocorrelations estimated from noisy data in gray.
-For the noisy experiments, we used 300 micrographs with SNRs of 1/16 for TRPV1 and 1/64 for BPTI.
-We present excerpts from noisy micrographs side-by-side with the corresponding clean ones in Figure~\ref{fig:cryo_noisy_micros_for_rec} (see appendix)}.}
-%	%	\vspace{-20pt} 	
-%\end{figure}
-%
-%\begin{figure}[t!]
-%	\centering
-%	\begin{subfigure}[t]{0.245\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{TRPV1_clean_micro.png}
-%		\caption{}
-%	\end{subfigure} \hfill %\hspace{2pt}
-%	\begin{subfigure}[t]{0.245\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{TRPV1_noisy_micro_SNR_16.png}
-%		\caption{}
-%	\end{subfigure} \hfill %\hspace{2pt}
-%	\begin{subfigure}[t]{0.245\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{clean_micro_BPTI.png}
-%		\caption{}
-%	\end{subfigure} \hfill
-%	\begin{subfigure}[t]{0.245\textwidth}
-%		\centering
-%		\includegraphics[scale=0.3]{noisy_micro_BPTI_SNR_64.png}
-%		\caption{}
-%	\end{subfigure}
-%	\caption{\label{fig:cryo_noisy_micros_for_rec}  {Excerpts from the noisy micrographs used for the reconstructions in Figure~\ref{fig:cryo_recon} and the corresponding clean excerpts.
-(a) Excerpt of the clean TRPV1 micrograph; (b) Excerpt of the noisy TRPV1 micrograph with SNR $= 1/16$; (c) Excerpt from the clean BPTI micrograph; (d) Excerpt from the noisy BPTI micrograph with SNR $= 1/64$.}}
-%\end{figure}
-%
-%\begin{figure}[t!]
-%	\centering
-%	\begin{subfigure}[t]{0.4\textwidth}
-%		\centering
-%		\includegraphics[scale=0.35]{TRPV1_trunc_FSC.eps}
-%		\caption{}
-%	\end{subfigure} \hfill %\hspace{2pt}
-%	\begin{subfigure}[t]{0.4\textwidth}
-%		\centering
-%		\includegraphics[scale=0.35]{BPTI_FSC.eps}
-%		\caption{}
-%	\end{subfigure} 
-%	\caption{\label{fig:cryo_FSC}  {Fourier Shell Correlations (FSCs) for the noisy reconstructions presented in Figure~\ref{fig:cryo_recon} using the $0.5$ criterion, compared to the (smoothed) ground truth.
-(a) FSC for the TRPV1 reconstruction, giving resolution of $24$\AA; (b) FSC for the BPTI reconstruction, giving resolution of $13$\AA.}}
-%\end{figure}
-%
-%
-%While we cannot provide a {high-resolution} 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics~\cite{donoho2004higher} %and debates in the cryo-EM community~\cite{henderson2013avoiding}.
-%and cryo-EM~\cite{henderson2013avoiding}.
-%This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
-%Figure~\ref{fig:cryo_detection} %(see appendix) 
-%presents excerpts  of two noisy micrographs, only one of which contains projections.
-%In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
-%On the other hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
-%
-%
-%\begin{figure}[h]
-%	\centering
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.png}
-%		\caption{An excerpt of the pure noise micrograph}
-%	\end{subfigure} \hfill %\hspace{2pt}
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{noisy_micrograph_cutout.png}
-%		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
-%	\end{subfigure} \hfill %\hspace{2pt}
-%	\begin{subfigure}[t]{0.3\textwidth}
-%		\centering
-%		\includegraphics[scale=0.4]{clean_micrograph_cutout.png}
-%		\caption{An excerpt of the clean micrograph}
-%	\end{subfigure}
-%	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from the BPTI molecule of size $31^3$.
-The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.
-%		The noise realization is identical in both micrographs.} 
-%\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_clean}
+		\caption{$\sigma = 0$}
+	\end{subfigure}%
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s05}
+		\caption{$\sigma = 0.5$}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.33\linewidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s3}
+		\caption{$\sigma = 3$}
+	\end{subfigure}
+	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
+Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein.
+In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
+In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
+By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
+	%\vspace{-8pt} 	
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
+	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
+This does not require particle picking.
+A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
+Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
+	%	\vspace{-8pt} 
+\end{figure}
+
+ Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+\end{figure}
+
+In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$
+\TODO{heterogeneous example}
+
+\TODO{K-L figure }
 
@@
 %All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
+
 %
@@
 \appendix
+
+\section{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
+
+We consider the asymptotic regime $N,M\to\infty$ and assume that $M=\Omega(N)$, so that
+\begin{equation*}
+\gamma := \frac{ML}{N}>0.
+\end{equation*}
+%
+Any vectors with indices out of range are given value 0.
+
+We start by considering the mean of the data:
+\begin{equation*}
+a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
+\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
+\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
+\xrightarrow{a.s.}\gamma a_x^1,
+\end{equation*}
+%
+where the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
+
+We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+%
+\begin{align*}
+%
+a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
+\nonumber \\
+& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
+\\ & + \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] (\varepsilon[s_j + i + \ell] + \varepsilon[s_j + i - \ell])}_{\text{cross-term}}. 
+%
+\end{align*}
+The cross-term is linear in the noise, and is easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
+We break the signal term into $M$ different sums, each containing one copy of the signal.
+This gives:
+%
+\begin{align} \label{eq:2nd_moment_signal_term}
+%
+\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] & = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\nonumber\\&\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
+%
+\end{align}
+%
+We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
+%
+\begin{equation*}
+%
+\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
+%
+\end{equation*}
+%
+Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, hence converges to zero almost surely as $N\to\infty$.
+If $\ell=0$, then we have:
+%
+\begin{equation*}
+\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
+\end{equation*}
+
+We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
+%
+%\begin{align*}
+%%
+%&a_y^3[\ell_1,\ell_2] 
+%= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+%\nonumber \\
+%%
+%=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
+%\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
+%\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
+%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+%\nonumber \\
+%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
+%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+%	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%%
+%\end{align*}
+%
+\begin{align*}
+%
+a_y^3[\ell_1,\ell_2] 
+=& \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+\\
+%
+=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
+	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
++ \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\ \\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+\\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+\\
+&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
++ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
+	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+%
+\end{align*}
+Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
+Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
+To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
+
+{\bf Case 1:} $0 < \ell_2 < \ell_1$.
+Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
+Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
+
+{\bf Case 2:} $0=\ell_2 < \ell_1$.
+Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
+The same argument as for Case 1 shows that (3) and (5) also converge to 0.
+For term (4), we write:
+%
+\begin{align*}
+%
+&\frac{1}{N}\sum_{j=1}^{M} 
+\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
+\nonumber \\
+&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
+\\& \xrightarrow{a.s.} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
+%
+\end{align*}
+
+{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
+
+{\bf Case 4:} $0=\ell_2 = \ell_1$.
+The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
+Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
+This completes the proof.
 

### 2019-01-31 inverse_problems/inverse_problems.tex
updated inverse problem draft

@@
 \newcommand{\revised}[1]{{\color{blue}{#1}}}
+\newcommand{\R}{\mathbb{R}}
 
@@
 \theoremstyle{plain}
+\newtheorem{conjecture}[thm]{\protect\conjecturename}
+\theoremstyle{plain}
 \newtheorem{proposition}[thm]{\protect\propositionname}
@@
 \providecommand{\propositionname}{Proposition}
+\providecommand{\conjecturename}{Conjecture}
 
@@
 
-\allowdisplaybreaks
+%\allowdisplaybreaks
+\numberwithin{equation}{section}
 
@@
 
-\subsection{Model}
+\subsection{Problem formulation} \label{sec:problem_formulation}
 
 In this paper, we consider the problem of recovering signals that appear 
-multiple times at unknown locations in a noisy measurement. This problem can be conveniently posed as  \emph{blind deconvolution}.
+multiple times at unknown locations in a noisy measurement. 
+In particular, we consider three/four models.
+
+\paragraph{The homogeneous well-separated model.}
+%This problem can be conveniently posed as  \emph{blind deconvolution}.
 Let $x\in\RL$ be the sought signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
@@
 While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. 
-We refer to~\eqref{eq:model} as the \emph{homogeneous model}.
 This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+Different variants of the blind deconvolution problem have been subject recently to a through  analysis, focusing on low noise regimes~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
 The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem. 
-As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas estimating $x$ is tractable under some conditions on $s$.
-This model appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}
+The model~\eqref{eq:model} appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
-We also consider a natural generalization, called the \emph{heterogeneous model}, in which one aims to estimate a set of $K$ signals $x_1,\ldots,x_K\in\RL$ from their mixed blind deconvolution
-\begin{equation} 
-y  =  \sum_{i=1}^Kx_i \ast s_i + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
-\label{eq:model}
-\end{equation}
-where again $s_i$ denotes a binary signal.
-
-The signals $s_i$ indicate the support of the occurrences of $x$ in the data. We will consider two generative models for $s$: well-spaced deterministic model, and a stochastic Possion model.
-
-\paragraph{Well-separated support model:} In this model, 
-we assume the binary signal $s$ obeys \TODO{This is not accurate}
+In the low noise regime, one can estimate $s$ and then estimate $x$ by standard deconvolution techniques.
+However, in the high noise regime, estimating $s$ is impossible---that is, detection is impossible~\cite{bendory2018toward}.
+To guarantee recovery in any noise regime, we require in this model a separation between adjacent signal's occurrences, that is,
 \begin{equation}
@@
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
-%
-\paragraph{Poisson support model:}
+As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
 
-The relation between the two models is formulated in Section~\ref{sec:support}.
+\paragraph{The homogeneous Poisson model.}
+In this model, we assume that the support signal $s$ is generated by a Poisson process.
+Bla bla bla.
+While this model is very different from the well-separated model, in Section~\ref{sec:support} we show that TKTK
 
-In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
-For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph.
-Importantly, there is no need to detect individual image occurrences.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the autocorrelations of the target image itself.
-To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem
+\paragraph{The heterogeneous well-separated model.}
 
-\subsection{Main motivation: single-particle reconstruction using cryo-electron microscopy}
-This work is motivated by the problem of single-particle reconstruction using cryo-electron microscopy (cryo-EM).  Cryo-EM is revolutionizing the field of structural biology, enabling XXX.
+The homogeneous well-separated model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$ from their mixed blind deconvolution
+\begin{equation} 
+y  =  \sum_{i=1}^Kx_i \ast s_i + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+\end{equation}
+where again $s_i$ denotes a binary signal indicating the support of the occurrences of $x_i$ in the data. We say that the separation condition is met \TODO{to verify}
+\begin{eqnarray}
+\text{If } s:=\bigcup\limits_{i=1}^Ks_i \text{ satisfies}~\eqref{eq:spacing} \text{ and for any } i\neq j, \thinspace s_i\cap s_j=\emptyset.
+\end{eqnarray}
+
+An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
+
+\paragraph{The heterogeneous Poisson model?.}
+
+\subsection{Motivation: single-particle reconstruction using cryo-electron microscopy}
+Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
+In contrast X-ray and NMR which exaggerate information from an ensembles of
+particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple energy landscapes associated with different structures.
+In addition, it does not require the formation of crystalline arrays of macromolecules.
 
@@
 The goal is to construct 3-D models of the molecular structure from the micrographs.
-
-The signal to noise ratio (SNR) of the projections in the micrographs is a function of two dominating factors.
-On the one hand, the SNR is a function of the electron dose.
-To keep radiation damage within acceptable bounds, the dose must be kept low, which leads to high noise levels.
-On the other hand, the SNR is a function of the molecule size.
-The smaller the molecules, the fewer detected electrons carry information about them.
+Importantly, to keep radiation damage within acceptable bounds, the dose must be kept low, leading to high noise levels.
 
@@
 The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR.
-This fact has been recognized early on by the cryo-EM community.
-In particular, in an influential paper from 1995, Richard Henderson~\cite{henderson1995limitations} investigates the following
-In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa).
-
-As these two leaders of the cryo-EM community point out, it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.
-Yet, imaging such molecules is important for structure-guided drug design and other applications~\cite{scapin2018cryo}.
-
+Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR. This fact has been recognized early on by the cryo-EM community. 
+In~\cite{henderson1995limitations,glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
 The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
 Despite this progress, detecting small molecules in the micrographs remains a challenge.
-We note that nuclear magnetic resonance (NMR) spectroscopy and X-ray crystallography are well suited to reconstruct small molecules.
-Yet, cryo--EM has a lot to offer even for molecules with already known structures obtained via NMR spectroscopy or X-ray crystallography, because these methods have limited ability to distinguish conformational variability.
 
-In a recent paper~\cite{bendory2018toward} by the authors, it was suggested to bypass the particle picking stage and the reconstruct the 3-D structure directly from the micrograph.
-In that paper, we have shown that, at least in principle, the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-The principle mathematical tool is the method of moments, or autocorrelation analysis, described in Section~\ref{sec:AC_analysis}.
-
-This goal of  this paper is to provide a theoretical and numerical justification for the method proposed in~\cite{bendory2018toward}.  
-In particular, the homogeneous  model serves as an abstraction of the cryo-EM problem.
-While in cryo-EM the 2-D images are tomographic projections of a 3-D structure, taken from unknown viewing directions, in the homogeneous model we observe the same 2-D image again and again.
-The heterogeneous case generalizes to multiple signals.
-
-To talk about the MRA-Kam's method relations. Also, model bias 
-\TODO{Where do we discuss the limits of detection?}
-%
-%Beyond this 2-D proof of concept, we look toward \mbox{3-D} reconstruction as well.
-Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
-In contrast, we derive the mathematical relation between the autocorrelations of the micrographs as a whole and the \mbox{3-D} volume, under some simplifying conditions.
-%We show a few numerical examples and outline the future developments required to make this method applicable to experimental  data. 
-%
-%Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+Another potential pitfall of particle picking pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
@@
 This model bias is common to all particle picking methods based on template matching.
-In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
+%In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
 %
+
+In a recent paper~\cite{bendory2018toward} by the authors, it was suggested to bypass the particle picking stage and the reconstruct the 3-D structure directly from the micrograph.
+In that paper, we have shown that, at least in principle, the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+The principle mathematical tool is  autocorrelation analysis, described in detail in Section~\ref{sec:AC_analysis}.
+This goal of  the current paper is to provide a theoretical and numerical support  for the method proposed in~\cite{bendory2018toward}.  
+In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the multiple tomographic projections of the 3-D structure (taken from unknown viewing directions) are replaced by one (or multiple) repeated signals.
+A similar abstraction has been proven itself to be useful in a similar context as described in the next section.
+
+\subsection{Principle mathematical tool: autocorrelation analysis.}
+
+In order to recover the image, we employ autocorrelation analysis.
+The underlying principle is to relate the autocorrelations of the micrographs to the autocorrelations of the image, without trying to detect individual signal occurrences (i.e., the signal $s$).
+In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy.
+The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the mixed autocorrelations of the signals.
+To estimate the signals them from their estimated autocorrelations, we solve a nonlinear inverse problem
+
+Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
+His method has been extended and employed by in X-ray free electron lasers and cryo-EM; see for instance~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
+In order to investigate the computational and statistical properties Kam's method, a series of papers have studied the  multi-reference alignment problem as an abstraction~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
+We follows the same line of research by considering the models of Section~\ref{sec:problem_formulation} as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
 
@@
 
-\section{The method of moments/ autocorrelation analysis} \label{sec:AC_analysis}
-\TODO{copied from PNAS's paper}
-In general, for a signal $z$ of length $m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+\section{Autocorrelation analysis} \label{sec:AC_analysis}
+
+For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
 \label{eq:ac_general}
@@
 \end{align}
-The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
-$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-$
+The autocorrelation functions have symmetries. Specifically, $$a_z^2[\ell] = a_z^2[-\ell],$$ and
+$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+$$
 For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
 
+\TODO{Start directly with heterogeneous model, but first need to verify that the Poisson equivalence is true holds also for this case.}
 Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
@@
 
-\subsection{Theory for the 2-D case (relation with PR)}
+\subsection{Autocorrelations in higher dimensions} \label{sec:high_dimensions}
 
-However, for dimensions greater than one \footnote{Autocorrelation in $d$ dimensions is defined similarly to~\eqref{eq:ac_general}, where $ i, \ell_1, \ldots, \ell_{q-1}$ take on values in $\mathbb{Z}^d$ and the summation in $i$ is over all of $\mathbb{Z}^d$.}, almost all signals are determined uniquely up to sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-The sign ambiguity can be resolved by the mean of the signal if it is not zero.
+Autocorrelations in $d$ dimensions is defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
+\begin{equation}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}].
+\label{eq:ac_d_dimension}
+\end{equation}
+Interestingly, for dimensions greater than one almost all signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+This is not true for 1-D signals: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating the symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
+
+In the literature, the phase and reflection symmetries are usually called trivial ambiguities.
+If the mean of signal is available and non-zero, the sign symmetry can be resolved.
 However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
 
-\subsection{The heterogeneous case}
+This uniqueness result for multi-dimensional signals (especially for 2-D images) is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
+illuminated with a coherent wave, and the far field diffraction
+intensity pattern  is measured, corresponding object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
+If the support of the object is known and less than half of the support of the measured signal, then the data is equivalent to the second-order autocorrelation.
+The computational problem of recovering the signal is usually referred to as \emph{phase retrieval} or \emph{phase problem}.
+Albeit the uniqueness result, recently it has been shown that, at least for 2-D images, the problem is  ill-conditioned~\cite{barnett2018geometry}.
+That is, there exist different images whose second-order autocorrelation agree up to machine precision.
 
-%\section{Recovering a signal from autocorrelations} \label{sec:recovery}
-%
-%
+\subsection{How many signals can be recovered in the heterogeneous model?}
+\label{sec:heterogeneity}
 
-\section{Algorithms and numerical experiments}
+In the heterogeneous models, the autocorrelation of $K$ signals are mixed together.
+To this end, we count how many equations the first three autocorrelations provide, after omitting symmetries.
+While we do not provide a rigorous proof, it was shown in similar problems that number of equations captures exactly how many signals can be decomposed for a mix of their autocorrelations~\cite{bandeira2017estimation}.
+
+Clearly, the first-order autocorrelation provides us one equation.
+For second-order autocorrelations, notice  that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
+Thus if $\sigma$ is known we obtain $L$ equations, while if not we omit $\ell = 0$.
+This has the practical effect that we need not know $\sigma$ to make sense of the computed quantities, while loosing one one equation.
+Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries): $\frac{(L+1)(L+2)}{2}-2$ in total.
+If we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. 
+Hence, if $\sigma$ is know we have 
+\begin{align*}
+1 + L + \frac{(L+1)(L+2)}{2}-2 = \frac{1}{2} L (L+5)
+\end{align*}
+and if it unknown
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+coefficients in total. Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$  is
+\begin{equation}
+K\leq \frac{L(L+5)}{2(L+1)},
+\end{equation}
+\begin{align*}
+K \leq \frac{ L (L-1) + 1}{2(L+1)}.
+\end{align*}
+Thus, we conjecture that approximately $L/2$ signals can be decomposed from  the first three mixed autocorrelations.
+
+\section{Algorithms and numerical experiments} \label{sec:numerics}
 
@@
 In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$
-\TODO{heterogeneous example}
 
-\TODO{K-L figure }
+\paragraph{Numerical experiment with three 1-D signals.}
+
+For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
+Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+The resulting SNR of $y$
+% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
+is about 1/9.
+
+This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
+
+%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
+%
+Given the observation $y$, we proceed to compute the autocorrelations.
+The first-order autocorrelation is straightforward.
+For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
+Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
+We have
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+coefficients in total.
+Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
+\begin{align*}
+K(L+1) \leq \frac{1}{2} L (L-1) + 1.
+\end{align*}
+Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). \TODO{The last paragraph can be removed}
+In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
+\begin{multline}
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \R^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
+\label{eq:optim1D}
+\end{multline}
+where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
+
+Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+\paragraph{K-L figure}
 

### 2019-02-06 inverse_problems/inverse_problems.tex
updates on the Poisson process

@@
 \newcommand{\jj}{\textbf{j}}
-
+\newcommand{\Poisson}{\text{Poisson}}
 \newcommand{\II}{\mathcal{I}}
@@
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\M}{\mathcal{M}}
+\renewcommand{\P}{\mathbb{P}}
+\renewcommand{\L}{\mathcal{L}}
 
@@
 multiple times at unknown locations in a noisy measurement.
-In particular, we consider three/four models.
-
-\paragraph{The homogeneous well-separated model.}
-%This problem can be conveniently posed as  \emph{blind deconvolution}.
 Let $x\in\RL$ be the sought signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
@@
 
-\paragraph{The homogeneous Poisson model.}
-In this model, we assume that the support signal $s$ is generated by a Poisson process.
-Bla bla bla.
-While this model is very different from the well-separated model, in Section~\ref{sec:support} we show that TKTK
+\subsection{Extensions}
 
 \paragraph{The heterogeneous well-separated model.}
-
 The homogeneous well-separated model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$ from their mixed blind deconvolution
@@
 
-\paragraph{The heterogeneous Poisson model?.}
+\paragraph{Poisson model.}
+
+Until now we have presented models assuming that the signals' occurrences are well separated. This condition can be alleviated by assuming a Poisson distribution on $s$.
+
+Let $X\in\RL$ be a random vector drawn from some fixed distribution. 
+We observe a random vector $Y\in\R^N$ generated as follows. Points are chosen in $\{0,\dots,N-L\}$ according to a Poisson process with parameter $\gamma N$. 
+The parameter $\gamma$ plays the role of the density of the signal in the measurement. 
+For each point $i$ that is chosen from $1$ to $N-L$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+If the distribution of $X$ is a single Dirac function, then we observe multiple repetition of the same signals, like in the homogeneous case.
+If the distribution consists of $K$ Diracs, then it is a heterogeneous model.
+
+If $M_i$ denotes the number of hits at location $i$, $1 \le i \le N$, then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_N)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+With this notation,  we can write each entry as:
+%
+\begin{align}
+%
+Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+%
+\end{align}
 
@@
 \section{Autocorrelation analysis} \label{sec:AC_analysis}
-
+\TODO{Maybe we should re-write this section for a random signal and then particularized to the homogeneous and heterogeneous cases}
 For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
@@
 
-\TODO{Start directly with heterogeneous model, but first need to verify that the Poisson equivalence is true holds also for this case.}
 Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
@@
 \subsection{Equivalence between the spacing condition and the Poisson process} \label{sec:support}
+
+In this section we omit the effect of the noise as it remains identical to the well-separated model.
+
+The moments of $Y$ are defined by
+%
+\begin{align}
+%
+m^1_Y[i] = \E Y[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+m^2_Y[i,j] = \E Y[i] Y[j], \quad 0 \le i,j \le L-1,
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+m^3_Y[i,j,k] = \E Y[i] Y[j] Y[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+%We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
+%%
+%\begin{align}
+%%
+%\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
+%%
+%\end{align}
+%%
+%\begin{align}
+%%
+%\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
+%%
+%\end{align}
+%%
+%and
+%%
+%\begin{align}
+%%
+%\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
+%%
+%\end{align}
+%
+%Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$. \TODO{I think we can remove it}
+%%
+%
+We now prove that the first three autocorrelations of the well-separated model can be recovered from the moments of the Poisson process.
+
+\begin{proposition} \label{prop:poisson}
+Let $a_X^1, a_X^2$ and $a_X^3$ be the first three autocorrelation function of the well-separated model \TODO{This is a bit unclear now, but if I get it right it holds true for any distribution over $X$}.
+Then, for any   $0\leq i\leq L-1$ we have
+\begin{align}
+m_Y^1[i] &= \gamma a_X^1,  \nonumber \\
+m_Y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell], \quad \ell\in[0,L-1], \\
+m_Y^3[i,i+\ell_1,i+\ell_2] &= 
+(\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a^2_X[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2], \quad \quad \ell_1,\ell_2\in[0,L-1]. \nonumber
+\end{align}
+\end{proposition}
+
+\begin{corollary}
+	From the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model.
+\end{corollary}
+
+%%%, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''. So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.
+
+%
+%
+%\begin{rem}
+%	
+%	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
+The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.
+%	
+%	
+%\end{rem}
+%
 
@@
 
+\section{Proof of Proposition~\ref{prop:poisson}} \label{sec:proof_prop_poisson}
+
+\subsection{The first moment of $Y$}
+
+To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_n)$, and then average over $M$. We have:
+%
+\begin{align}
+%
+\E[Y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
+= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \M_1[j]
+= \sum_{j=0}^{L-1} M_{i-j} \M_1[j].
+%
+\end{align}
+%
+Now taking expectations over $M$ we see:
+%
+\begin{align}
+%
+\E Y[i] = \gamma \sum_{j=0}^{L-1} \M_1[j] = \gamma \L_1.
+%
+\end{align}
+
+%
+
+\subsection{The second moment of $Y$}
+
+Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%
+\begin{align}
+%
+Y_{i_1} Y_{i_2} 
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
+%
+\end{align}
+
+We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+In the first case, all the terms are independent, and so the expectation factors.
+In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
+This gives (all expectations are conditional on $M$):
+%
+\begin{align} \label{moment2-condm}
+%
+\E Y_{i_1} Y_{i_2}
+=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+%
+\end{align}
+%
+Now take expectations over the Poisson random variables, using this fact:
+%
+\begin{lem} \label{lem-choose}
+	If $M \sim \Poisson(\gamma)$, then 
+	\begin{align}
+	%
+	\E {M\choose k} = \frac{\gamma^k}{k!}.
+	%
+	\end{align}
+\end{lem}
+
+We get (now the expectation is over $M$ and $X$):
+%
+\begin{align}
+%
+\E Y_{i_1} Y_{i_2} 
+=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
++ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
+\nonumber \\
+=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
+%
+\end{align}
+
+But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+
+%
+
+\subsection{The third moment of $Y$}
+
+For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%
+\begin{align}
+%
+&Y_{i_1} Y_{i_2} Y_{i_3}
+\nonumber \\
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
+\end{align}
+%
+We will break up the outer three sums into disjoint sums with the following ranges of indices:
+%
+\begin{enumerate}
+
+	\item \label{case1}
+	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case2}
+	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case3}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+
+	\item \label{case4}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case5}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+\end{enumerate}
+
+For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%
+\begin{align}
+%
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
+X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+\nonumber \\
+=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(a)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(b)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(c)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(d)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(e)}}.
+%
+\end{align}
+
+For term (a), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+%
+\end{align}
+%
+Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
+%
+\begin{align} \label{aaaa}
+%
+\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+For term (b), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+%
+\end{align}
+%
+and then again using Lemma \ref{lem-choose} we get the expected value:
+%
+\begin{align} \label{bbbb}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+Similarly, the expected values of terms (c) and (d) are:
+%
+\begin{align} \label{cccc}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+%
+\end{align}
+%
+and
+%
+\begin{align} \label{dddd}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+%
+\end{align}
+
+Finally, the expected value of term (e) is easily shown to be:
+%
+\begin{align} \label{eeee}
+%
+\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+%
+\end{align}
+%
+This concludes the computation for Case \ref{case1}.
+
+Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+\Bigg\{
+\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
+\nonumber \\
+&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
+%
+\end{align}
+%
+Taking expectations conditional on $M$, we then get:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\nonumber \\
+&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\label{ffff} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
+\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+\label{gggg}
+%
+\end{align}
+
+Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
+\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+\label{hhhh} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
+\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+\label{iiii}
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
+\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+\label{jjjj}\\
+& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
+\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+\label{kkkk}
+%
+\end{align}
+
+Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
+Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%
+\end{align}
+%
+since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
+%
+\begin{align} \label{llll}
+%
+\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+%
+\end{align}
+
+Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
+%
+\begin{align}
+%
+(\gamma \L_1)^3.
+%
+\end{align}
+
+Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
+%
+\begin{align}
+%
+\gamma \L_1  \cdot 
+( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
+%
+\end{align}
+%
+Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
+%
+\begin{align}
+%
+\gamma \L_3(\Delta_1,\Delta_2)
+%
+\end{align}
+%
+which is the usual third-order auto-correlation.
+
 \end{document}

### 2019-02-06 inverse_problems/inverse_problems.tex
Revert "updates on the Poisson process"
This reverts commit 81fde221912c2f7f1333bc0ca20606ddec02e8df.

@@
 
-Until now we have presented models assuming that the signals' occurrences are well separated. This condition can be alleviated by assuming a Poisson distribution on $s$.
-
-Let $X\in\RL$ be a random vector drawn from some fixed distribution. 
-We observe a random vector $Y\in\R^N$ generated as follows. Points are chosen in $\{0,\dots,N-L\}$ according to a Poisson process with parameter $\gamma N$. 
-The parameter $\gamma$ plays the role of the density of the signal in the measurement. 
-For each point $i$ that is chosen from $1$ to $N-L$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
-If the distribution of $X$ is a single Dirac function, then we observe multiple repetition of the same signals, like in the homogeneous case.
-If the distribution consists of $K$ Diracs, then it is a heterogeneous model.
-
-If $M_i$ denotes the number of hits at location $i$, $1 \le i \le N$, then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
-Conditional on the value of $M = (M_1,\dots,M_N)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
-With this notation,  we can write each entry as:
+We consider the following observation model.
+$X = (X[0],\dots,X[L-1])$ is a random vector of length $L$, drawn from some fixed distribution.
+For fixed $n$, we observe a random vector $Y$ of length $n+L$, generated as follows.
+Points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$.
+For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+
+If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poisson process $M_i$'s are iid and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+
+With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
 %
@@
 \section{Autocorrelation analysis} \label{sec:AC_analysis}
-\TODO{Maybe we should re-write this section for a random signal and then particularized to the homogeneous and heterogeneous cases}
+
 For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
@@
 
+\TODO{Start directly with heterogeneous model, but first need to verify that the Poisson equivalence is true holds also for this case.}
 Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
@@
 
-In this section we omit the effect of the noise as it remains identical to the well-separated model.
-
-The moments of $Y$ are defined by
-%
-\begin{align}
-%
-m^1_Y[i] = \E Y[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-m^2_Y[i,j] = \E Y[i] Y[j], \quad 0 \le i,j \le L-1,
+We will denote by $\M_l$ the moments of $X$:
+%
+\begin{align}
+%
+\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
 %
@@
 %
-m^3_Y[i,j,k] = \E Y[i] Y[j] Y[k], \quad 0 \le i,j,k \le L-1.
-%
-\end{align}
-
-%We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
-%%
-%\begin{align}
-%%
-%\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
-%%
-%\end{align}
-%%
-%\begin{align}
-%%
-%\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
-%%
-%\end{align}
-%%
-%and
-%%
-%\begin{align}
-%%
-%\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
-%%
-%\end{align}
-%
-%Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$. \TODO{I think we can remove it}
-%%
-%
-We now prove that the first three autocorrelations of the well-separated model can be recovered from the moments of the Poisson process.
+\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
+%
+\begin{align}
+%
+\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
+%
+\end{align}
+%
+\begin{align}
+%
+\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
+%
+\end{align}
+
+Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.
+
+%
+
+We will prove the following result:
 
 \begin{proposition} \label{prop:poisson}
-Let $a_X^1, a_X^2$ and $a_X^3$ be the first three autocorrelation function of the well-separated model \TODO{This is a bit unclear now, but if I get it right it holds true for any distribution over $X$}.
-Then, for any   $0\leq i\leq L-1$ we have
-\begin{align}
-m_Y^1[i] &= \gamma a_X^1,  \nonumber \\
-m_Y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell], \quad \ell\in[0,L-1], \\
-m_Y^3[i,i+\ell_1,i+\ell_2] &= 
-(\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a^2_X[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2], \quad \quad \ell_1,\ell_2\in[0,L-1]. \nonumber
-\end{align}
+	The first moment of the Poisson process is equal to:
+	%
+	\begin{align}
+	\gamma \L_1.
+	\end{align}
+	%
+	The second moment vector of the Poisson process has entries
+	%
+	\begin{align}
+	(\gamma \L_1)^2 + \gamma \L_2(\Delta),
+	\end{align}
+	%
+	for $0 \le \Delta < L$.
+
+	The third moment matrix of the Poisson process has entries
+	\begin{align}
+	(\gamma \L_1)^3 + \gamma \L_1  \cdot ( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)) + \gamma \L_3(\Delta_1,\Delta_2) ,
+	\end{align}
+	for $0 \le \Delta_1,\Delta_2 < L$.
 \end{proposition}
@@
 %
-%
-%\begin{rem}
-%	
-%	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
+
+\begin{rem}
+
+	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
 The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.
-%	
-%	
-%\end{rem}
-%
+
+\end{rem}
 

### 2019-02-06 inverse_problems/inverse_problems.tex
update of Poisson section

@@
 
-\paragraph{Poisson model.}
-
+\paragraph{Poisson model with a stochastic signal.}
+
+The models we described so far assume a well-separated support and a deterministic signal.
+This models can be extended to stochastic signals and the separation condition can be alleviated by assuming a Poisson process.
 We consider the following observation model.
-$X = (X[0],\dots,X[L-1])$ is a random vector of length $L$, drawn from some fixed distribution.
-For fixed $n$, we observe a random vector $Y$ of length $n+L$, generated as follows.
-Points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$.
-For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
+Let $X =\RL$ be a random vector drawn from some fixed distribution.
+We observe a random vector $Y\in\R^{N-L+1}$ generated as follows.
+Points are chosen in $\{1,\dots,N-L=1\}$ according to a Poisson process with parameter $\gamma N$.
+The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
+For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
 
@@
 \section{Autocorrelation analysis} \label{sec:AC_analysis}
-
+\TODO{Could be written for a random signal and then particularized to the homogeneous and heterogeneous cases.}
 For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by

### 2019-02-06 inverse_problems/inverse_problems.tex
no message

@@
 
-If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poisson process $M_i$'s are iid and $M_i \sim \Poisson(\gamma)$.
+If $M_i$ denotes the number of hits at location $i$, $1 \le i \le N-L+1$, then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
 Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
-
-With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
+With this notation, we can write each entry as:
 %
@@
 \end{align}
+\TODO{The well separated model can be also written for a random signal X}
 
@@
 
-We will denote by $\M_l$ the moments of $X$:
-%
-\begin{align}
-%
-\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
+In this section we omit the affect of the noise as it remains the same for the well-separated model.
+
+Let us denote by $m_Y^q$ the moments of $Y$:
+%
+\begin{align}
+%
+m_Y^1[i] = \E X[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+m_Y^2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
 %
@@
 %
-\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
-%
-\end{align}
-
-We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
-%
-\begin{align}
-%
-\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
-%
-\end{align}
-%
-\begin{align}
-%
-\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
-%
-\end{align}
-
-Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.
-
-%
-
-We will prove the following result:
+m_Y^3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+%We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
+%%
+%\begin{align}
+%%
+%\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
+%%
+%\end{align}
+%%
+%\begin{align}
+%%
+%\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
+%%
+%\end{align}
+%%
+%and
+%%
+%\begin{align}
+%%
+%\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
+%%
+%\end{align}
+%
+%
+%Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.
+%
+%%
+
+In the following,  we show that the moments of the Poisson process can be written in terms of the autocorrelations of the well-separated model.
 
@@
 
-	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
+%	
+%	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
 The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.

### 2019-02-06 inverse_problems/inverse_problems.tex
no message

--- 2019-02-06 inverse_problems/inverse_problems.tex
@@
 
+\paragraph{The well-separated model with a random signal}
+In this model, we let the signal $x\in\RL$ to be a random vector drawn from some fixed distribution.
+We observe a random vector $Y\in\R^{N-L+1}$.
+The difference from the previous models is that here in each non-zero element of $s$  a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$.
+This model generalize the homogeneous and heterogeneous models; if the distribution is a Delta function that it coincides with the homogeneous model, and if it is a sum of Diracs then it is the heterogeneous model.
+\TODO{We need to write the  separation condition clearly}.
+
 \paragraph{Poisson model with a stochastic signal.}
 
-The models we described so far assume a well-separated support and a deterministic signal.
-This models can be extended to stochastic signals and the separation condition can be alleviated by assuming a Poisson process.
-We consider the following observation model.
-Let $X =\RL$ be a random vector drawn from some fixed distribution.
-We observe a random vector $Y\in\R^{N-L+1}$ generated as follows.
-Points are chosen in $\{1,\dots,N-L=1\}$ according to a Poisson process with parameter $\gamma N$.
-The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
+The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
+We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution.
+In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
 For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

### 2019-02-06 inverse_problems/inverse_problems.tex
updates

@@
 The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
-We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution.
+We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
 In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
@@
 \begin{proposition} \label{prop:poisson}
-	The first moment of the Poisson process is equal to:
-	%
-	\begin{align}
-	\gamma \L_1.
-	\end{align}
-	%
-	The second moment vector of the Poisson process has entries
-	%
-	\begin{align}
-	(\gamma \L_1)^2 + \gamma \L_2(\Delta),
-	\end{align}
-	%
-	for $0 \le \Delta < L$.
-
-	The third moment matrix of the Poisson process has entries
-	\begin{align}
-	(\gamma \L_1)^3 + \gamma \L_1  \cdot ( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)) + \gamma \L_3(\Delta_1,\Delta_2) ,
-	\end{align}
-	for $0 \le \Delta_1,\Delta_2 < L$.
+    For each $i=0,\ldots,L-1$,  the moments of the Poisson process are equal to 
+    \begin{align}
+    m_Y^1[i] &= \gamma a_X^1 \nonumber \\
+    m_Y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
+    m_Y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
+    \end{align}
 \end{proposition}

### 2019-02-09 inverse_problems/inverse_problems.tex
adding a glorious title
considering a model with a general, random, signal

@@
 
-\title{TBD}
+\title{Multi-target detection with application to cryo-electron microscopy}
 %
@@
 \paragraph{The heterogeneous well-separated model.}
-The homogeneous well-separated model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$ from their mixed blind deconvolution
+The homogeneous well-separated model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
+Let $s$ be a binary signal satisfying the separation condition~\eqref{eq:spacing}.
+Let $s[i]$ be one of the non-zero values of $s$.
+A random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$.
+Then $x_i$ is placed in $y$
+with element $0$ at location $i$.
+
+ This model can be written as  a mix of blind deconvolution problems
 \begin{equation} 
@@
 \end{equation}
-where again $s_i$ denotes a binary signal indicating the support of the occurrences of $x_i$ in the data. We say that the separation condition is met \TODO{to verify}
-\begin{eqnarray}
-\text{If } s:=\bigcup\limits_{i=1}^Ks_i \text{ satisfies}~\eqref{eq:spacing} \text{ and for any } i\neq j, \thinspace s_i\cap s_j=\emptyset.
-\end{eqnarray}
-
+where again $s_i$ is a binary signal, which is non-zero values 
+are the subset of the non-zero values of $s$ associated with $x_i$.
 An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
@@
 \paragraph{The well-separated model with a random signal}
-In this model, we let the signal $x\in\RL$ to be a random vector drawn from some fixed distribution.
+This model generalize the homogeneous and heterogeneous models. 
+We let the signal $x\in\RL$ to be a random vector drawn from some fixed distribution.
 We observe a random vector $Y\in\R^{N-L+1}$.
-The difference from the previous models is that here in each non-zero element of $s$  a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$.
-This model generalize the homogeneous and heterogeneous models; if the distribution is a Delta function that it coincides with the homogeneous model, and if it is a sum of Diracs then it is the heterogeneous model.
-\TODO{We need to write the  separation condition clearly}.
+For each non-zero element of $s$,  a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$.
+If the distribution is a Delta function that it coincides with the homogeneous model; if it is a sum of Diracs then it is the heterogeneous model.
 
@@
 \end{align}
-\TODO{The well separated model can be also written for a random signal X}
 
@@
 
-\subsection{Principle mathematical tool: autocorrelation analysis.}
-
-In order to recover the image, we employ autocorrelation analysis.
-The underlying principle is to relate the autocorrelations of the micrographs to the autocorrelations of the image, without trying to detect individual signal occurrences (i.e., the signal $s$).
-In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy.
-The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the mixed autocorrelations of the signals.
-To estimate the signals them from their estimated autocorrelations, we solve a nonlinear inverse problem
-
+We mention that~\cite{bendory2018toward} was not the first paper to employ autocorrelation analysis to cryo-EM. 
 Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
@@
 We follows the same line of research by considering the models of Section~\ref{sec:problem_formulation} as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
+
+%\subsection{Principle mathematical tool: autocorrelation analysis.}
 
@@
 \section{Autocorrelation analysis} \label{sec:AC_analysis}
-\TODO{Could be written for a random signal and then particularized to the homogeneous and heterogeneous cases.}
-For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+
+In order to recover the signal, we employ autocorrelation analysis.
+The underlying principle is to relate the autocorrelations of the observation to the autocorrelations of the signal without trying to detect individual signal occurrences (i.e., the signal $s$).
+In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy.
+The autocorrelations of the observation are straightforward to compute and require only one pass over the data.
+After estimation of the density of particles in the micrographs, these directly yield estimates for the mixed autocorrelations of the signals.
+To estimate the signals them from their estimated autocorrelations, we solve a nonlinear inverse problem as explained in Section~\ref{sec:numerics}.
+\TODO{to re-write}
+
+Let $Z\in \R^m$ be a random signal drawn from some fixed distribution.  The autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
+a_Z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m} \sum_{i=-\infty}^{\infty} Z[i]Z[i+\ell_1]\cdots Z[i+\ell_{q-1}]\right\},
 \label{eq:ac_general}
 \end{equation}
-where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+where the expectation is taken with respect to the distribution of $Z$ and
+the indexing of $Z$ out of the range $0, \ldots, m-1$ is zero-padded.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
 \begin{align} 
-a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
-a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
-a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
-\end{align}
-The autocorrelation functions have symmetries. Specifically, $$a_z^2[\ell] = a_z^2[-\ell],$$ and
-$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
+a_Z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
+Z[i]\right\}, \nonumber\\
+a_Z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{Z[i]Z[i+\ell]\right\},\\
+a_Z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{Z[i]Z[i+\ell_1]Z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
+\end{align}
+The autocorrelation functions have symmetries. Specifically, $$\E\left\{a_Z^2[\ell]\right\} = \E\left\{a_Z^2[-\ell]\right\},$$ and \TODO{to verify}
+$$\E\left\{a_Z^3[\ell_1,\ell_2]\right\} = \E\left\{a_Z^3[\ell_2,\ell_1]\right\}=\E\left\{a_Z^3[-\ell_1,\ell_2-\ell_1]\right\}.
 $$
@@
 
-\TODO{Start directly with heterogeneous model, but first need to verify that the Poisson equivalence is true holds also for this case.}
-Under the separation condition, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$ (that is, the number of 1's in $s$), and let
+Under the separation condition, the relation between autocorrelations of the micrograph and those of $X$ is particularly simple, as we now show.
+It is useful to introduce some notation: let $M$ denote the number of occurrences of $X$ in $y$ (that is, the number of 1's in $s$), and let
 \begin{equation}
@@
 \end{equation}
-denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The separation condition %~\eqref{eq:spacing} 
-imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+denote the density of $X$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $X$.) The separation condition imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
 
@@
 \begin{equation} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
+\lim_{N\to\infty} a_y^1  \aseq \gamma \E\left\{a_{X}^1\right\},
 \end{equation}
@@
 The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_x^1$ from $y$. (We show later how to estimate $\gamma$ as well.)
+Thus, given enough data, if $\gamma$ is known, we can estimate $\E\left\{a_{X}^1\right\}$ from $y$. (We show later how to estimate $\gamma$ as well.)
 
@@
 \begin{equation}
-\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell],
+\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma \E\left\{a_{X}^2[\ell]\right\} + \sigma^2\delta[\ell],
 \label{eq:ac2_micrograph}
@@
 The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_x^2$.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $\E\left\{a_{X}^2[\ell]\right\}$.
 
@@
  \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma \E\left\{a_{x}^3[\ell_1,\ell_2]\right\}  + \sigma^2\gamma \E\left\{a_{x}^1\right\}  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
 +\delta[\ell_1,\ell_2]\big),
@@
 
-%%%, with the Poisson rate $\gamma$ playing the role of the ``occupancy factor''. So if recovery is possible for the strongly-separated model, it is also possible for the Poisson process model.
-
-%
-
-\begin{rem}
-
-%	
-%	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case.
-The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.
-
-\end{rem}
-
 \subsection{Autocorrelations in higher dimensions} \label{sec:high_dimensions}
@@
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}].
+a_Z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
 \label{eq:ac_d_dimension}
 \end{equation}
-Interestingly, for dimensions greater than one almost all signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $Z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
 This is not true for 1-D signals: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating the symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
@@
 Any vectors with indices out of range are given value 0.
+We focus here on the homogeneous model~\eqref{eq:model}. The extension to random signal $X$ is straight-forward by taking the expectation with respect to the distribution of $X$.
 

### 2019-02-11 inverse_problems/inverse_problems.tex
updated Sections 1&2

@@
 
-\title{Multi-target detection with application to cryo-electron microscopy}
-%
-%\author[a]{Tamir Bendory}
-%\author[b]{Nicolas Boumal} 
-%\author[c]{William Leeb}
-%\author[a,b]{Eitan Levin}
-%\author[a,b]{Amit Singer}
-%
-%\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
-%\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
-%\affil[c]{School of Mathematics, University of
-%	Minnesota, Minneapolis, MN, USA }
+\title{Multi-target detection and clustering with application to cryo-electron microscopy}
+
+\author[a]{Tamir Bendory}
+\author[b]{Nicolas Boumal} 
+\author[c]{William Leeb}
+\author[a,b]{Eitan Levin}
+\author[a,b]{Amit Singer}
+
+\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
+\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
+\affil[c]{School of Mathematics, University of
+	Minnesota, Minneapolis, MN, USA }
 
@@
 
-In this paper, we consider the problem of recovering signals that appear 
+In this paper, we consider the problem of recovering a signal that appear 
 multiple times at unknown locations in a noisy measurement.
 Let $x\in\RL$ be the sought signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
-Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with 1's) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise:
+Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with ones) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise the measurement model reads:
 \begin{equation} 
@@
 where $\ast$ denotes linear convolution. 
-While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. 
-This is a key difference with other works on  \emph{blind deconvolution}, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-Different variants of the blind deconvolution problem have been subject recently to a through  analysis, focusing on low noise regimes~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
-The parameters of the signal $s$ (the locations of its nonzero values) are the \emph{nuisance variables} of the problem. 
-The model~\eqref{eq:model} appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
+While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. We name this problem \emph{multi-target detection}.
+
+The multi-target detection problem  is an instance of  
+\emph{blind deconvolution}---a longstanding problem arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
+Different variants of the blind deconvolution problem have been subject recently to a thorough  analysis, focusing on low noise regimes~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
+A key difference  is that in multi-target detection the parameters of the signal $s$ (the locations of its nonzero values) are  \emph{nuisance variables}---that is, we aim only at estimating only $x$.
+Multi-target detection appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
 
 In the low noise regime, one can estimate $s$ and then estimate $x$ by standard deconvolution techniques.
-However, in the high noise regime, estimating $s$ is impossible---that is, detection is impossible~\cite{bendory2018toward}.
-To guarantee recovery in any noise regime, we require in this model a separation between adjacent signal's occurrences, that is,
+However, in the high noise regime, estimating $s$ is impossible---that is, detection is impossible~\cite{bendory2018toward,aguerrebere2016fundamental}.
+To guarantee recovery in any noise regime, we require a separation between adjacent signal's occurrences, that is,
 \begin{equation}
@@
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
-As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
-
-\subsection{Extensions}
-
-\paragraph{The heterogeneous well-separated model.}
-The homogeneous well-separated model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
+%Under the separation condition~\eqref{eq:spacing}, we refer to this model as the \emph{homogeneous well-separated model}. 
+In then next section we present a model that alleviates this condition.
+%As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
+
+\subsection{Extensions} \label{sec:extensions}
+
+The basic model~\eqref{eq:model} can be extended in various ways, some discussed below.
+
+\paragraph{Multi-target detection and clustering with separation.}
+The multi-target detection model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
 Let $s$ be a binary signal satisfying the separation condition~\eqref{eq:spacing}.
-Let $s[i]$ be one of the non-zero values of $s$.
-A random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$.
-Then $x_i$ is placed in $y$
+For each $s[i]=1$, a random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$. Then, $x_{v_i}$ is placed in $y$
 with element $0$ at location $i$. 
+We refer to this model as \emph{multi-target detection and clustering}.
 
@@
 \end{equation}
-where again $s_i$ is a binary signal, which is non-zero values 
+where again $s_i$ is a binary signal, which its non-zero values 
 are the subset of the non-zero values of $s$ associated with $x_i$.
-An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
+Generally, we refer to this problem as \emph{multi-target detection and clustering with separation.} 
+%An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
 
 \paragraph{The well-separated model with a random signal}
-This model generalize the homogeneous and heterogeneous models. 
-We let the signal $x\in\RL$ to be a random vector drawn from some fixed distribution.
-We observe a random vector $Y\in\R^{N-L+1}$.
-For each non-zero element of $s$,  a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$.
-If the distribution is a Delta function that it coincides with the homogeneous model; if it is a sum of Diracs then it is the heterogeneous model.
-
-\paragraph{Poisson model with a stochastic signal.}
+The homogeneous and heterogeneous models can be generalized as follows. 
+We let the signal $X\in\RL$ to be a random vector drawn from some fixed distribution. %We observe a random vector $Y\in\R^{N-L+1}$.
+For each non-zero element of $s$,  a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$.
+If the distribution is a Delta function that this model coincides with the multi-target detection model; if it is a sum of Diracs then it reduces to multi-target detection and clustering.
+
+\paragraph{Poisson model for the support signal.}
 
@@
 We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
-In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
-For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.
-
-If $M_i$ denotes the number of hits at location $i$, $1 \le i \le N-L+1$, then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
+Points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma (N-L)$. %The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
+For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$, with overlapping vectors being added together.
+
+If $M_i$ denotes the number of hits at location $i$,  then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
 Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
@@
 \subsection{Motivation: single-particle reconstruction using cryo-electron microscopy}
-Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
-In contrast X-ray and NMR which exaggerate information from an ensembles of
-particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple energy landscapes associated with different structures.
+Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules; see for instance~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
+In contrast X-ray and NMR which aggregate information from an ensembles of
+particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures.
 In addition, it does not require the formation of crystalline arrays of macromolecules.
@@
 All contemporary methods in the field split the reconstruction procedure into two main  stages.
-The first stage consists in extracting the various particle projections from the micrographs.
+The first stage consists in extracting the  particle projections from the micrographs.
 This stage is called \emph{particle picking}.
@@
 Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR. This fact has been recognized early on by the cryo-EM community. 
-In~\cite{henderson1995limitations,glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
-The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-Despite this progress, detecting small molecules in the micrographs remains a challenge.
-
-Another potential pitfall of particle picking pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
+%The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
+%Despite this progress, detecting small molecules in the micrographs remains a challenge.
+
+Another potential pitfall of particle picking pertains to \emph{model bias}, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
@@
 
-In a recent paper~\cite{bendory2018toward} by the authors, it was suggested to bypass the particle picking stage and the reconstruct the 3-D structure directly from the micrograph.
-In that paper, we have shown that, at least in principle, the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-The principle mathematical tool is  autocorrelation analysis, described in detail in Section~\ref{sec:AC_analysis}.
-This goal of  the current paper is to provide a theoretical and numerical support  for the method proposed in~\cite{bendory2018toward}.  
-In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the multiple tomographic projections of the 3-D structure (taken from unknown viewing directions) are replaced by one (or multiple) repeated signals.
-A similar abstraction has been proven itself to be useful in a similar context as described in the next section.
+A recent work of the authors suggests to bypass the particle picking stage and  reconstruct the 3-D structure directly from the micrograph~\cite{bendory2018toward}.
+In that paper, it was shown that---at least in principle---the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+The principle mathematical tool is  \emph{autocorrelation analysis}, described in detail in Section~\ref{sec:AC_analysis}.
+This goal of  the current paper is to provide a theoretical justification and numerical support  for the method proposed in~\cite{bendory2018toward}.  
+In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the random signal $X$ discussed in Section~\ref{sec:extensions} can be thought of as 2-D random tomographic projections of the 3-D structure
+taken according to some unknown distribution of the particles within the ice.
+
+% A similar abstraction has been proven itself to be useful in a similar context as described in the next section.
 
@@
 His method has been extended and employed by in X-ray free electron lasers and cryo-EM; see for instance~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
-In order to investigate the computational and statistical properties Kam's method, a series of papers have studied the  multi-reference alignment problem as an abstraction~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
-We follows the same line of research by considering the models of Section~\ref{sec:problem_formulation} as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
+In order to investigate the computational and statistical properties of Kam's method, a series of papers have studied a simplified model, 
+called   \emph{multi-reference alignment}~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
+We follows the same line of research by considering the multi-target detection and clustering  as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
 
@@
 The underlying principle is to relate the autocorrelations of the observation to the autocorrelations of the signal without trying to detect individual signal occurrences (i.e., the signal $s$).
-In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy.
+In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy in the limit of $N\to\infty$. 
 The autocorrelations of the observation are straightforward to compute and require only one pass over the data.
@@
 To estimate the signals them from their estimated autocorrelations, we solve a nonlinear inverse problem as explained in Section~\ref{sec:numerics}.
-\TODO{to re-write}
 
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $Z$ and
-the indexing of $Z$ out of the range $0, \ldots, m-1$ is zero-padded.
+where the expectation is taken with respect to the distribution of $Z$. The indexing of $Z$ out of the range $0, \ldots, m-1$ is zero-padded.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
@@
 \end{equation}
-denote the density of $X$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $X$.) The separation condition imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+denote the density of $X$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $X$.) 
+In this section, we assume the separation condition~\eqref{eq:spacing} that  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+In Section~\ref{sec:poisson} we show that the autocorrelations in the Poisson model are equivalent to  those presented in this section.
 
@@
 Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large micrograph, it contains increasingly many signal occurrences, with constant signal density).
+We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large observation, it contains increasingly many signal occurrences, with constant signal density).
 In that regime, the law of large numbers can be used to show the following statement:
 \begin{equation} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1  \aseq \gamma \E\left\{a_{X}^1\right\},
-\end{equation}
-where equality holds almost surely (a.s.), meaning it holds with probability one.
+\lim_{N\to\infty} a_y^1  \aseq \gamma a_{X}^1,
+\end{equation}
+\TODO{ should is be $\E\left\{a_{X}^1\right\}$?} where equality holds almost surely (a.s.), meaning it holds with probability one.
 The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-Thus, given enough data, if $\gamma$ is known, we can estimate $\E\left\{a_{X}^1\right\}$ from $y$. (We show later how to estimate $\gamma$ as well.)
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_{X}^1$ from $y$. We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ as well in the homogeneous model.
 
@@
 \begin{equation}
-\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma \E\left\{a_{X}^2[\ell]\right\} + \sigma^2\delta[\ell],
+\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{X}^2[\ell] + \sigma^2\delta[\ell],
 \label{eq:ac2_micrograph}
 \end{equation}
+%\begin{equation}
+%\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma \E\left\{a_{X}^2[\ell]\right\} + \sigma^2\delta[\ell],
+%\label{eq:ac2_micrograph}
+%\end{equation}
 for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
 The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $\E\left\{a_{X}^2[\ell]\right\}$.
+Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_{X}^2[\ell]$.
 
@@
  \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma \E\left\{a_{x}^3[\ell_1,\ell_2]\right\}  + \sigma^2\gamma \E\left\{a_{x}^1\right\}  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{X}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
 +\delta[\ell_1,\ell_2]\big),
@@
 
-Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
+%
+%Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
 
@@
 
-\subsection{Theory for the 1-D homogeneous case}
+\subsection{Theory for the homogeneous case} \label{sec:theory_homogeneous}
 
@@
 
-\subsection{Equivalence between the spacing condition and the Poisson process} \label{sec:support}
+\subsection{Equivalence between the spacing condition and the Poisson process} \label{sec:poisson}
 

### 2019-02-11 inverse_problems/inverse_problems.tex
no message

@@
 If $M_i$ denotes the number of hits at location $i$,  then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
-Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+Conditional on the value of $M = (M_1,\dots,M_{N-L+1})$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
 With this notation, we can write each entry as:
@@
 \subsection{Theory for the homogeneous case} \label{sec:theory_homogeneous}
-
-A one-dimensional signal is determined uniquely by its second- and third-order autocorrelations.
+In this section, we derive some theoretical results for the homogeneous case. \TODO{Note: I am using terms interchangeably}
+
+A signal is determined uniquely by its second- and third-order autocorrelations.
 Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
@@
 %
-m_Y^1[i] = \E X[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-m_Y^2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
+m_y^1[i] = \E X[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+m_y^2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
 %
@@
 %
-m_Y^3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+m_y^3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
 %
@@
 
-In the following,  we show that the moments of the Poisson process can be written in terms of the autocorrelations of the well-separated model.
+In the following,  we show that the moments of the observed data under the Poisson process can be written in terms of the autocorrelations of the well-separated model.
 
 \begin{proposition} \label{prop:poisson}
-    For each $i=0,\ldots,L-1$,  the moments of the Poisson process are equal to 
-    \begin{align}
-    m_Y^1[i] &= \gamma a_X^1 \nonumber \\
-    m_Y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
-    m_Y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
+    For each $i$,  the moments of the Poisson process are equal to 
+    \begin{align}
+    m_y^1[i] &= \gamma a_X^1 \nonumber \\
+    m_y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
+    m_y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
     \end{align}
@@
 
-\begin{corollary}
-	From the first three moments of the Poisson process model, once can recover the first three moments from the strongly-separated model.
+\begin{corollary} \TODO{re-write}
+	From the first three moments of the Poisson process model, one can recover the first three moments from the strongly-separated model.
 \end{corollary}
@@
 
-To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_n)$, and then average over $M$. We have:
+To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
 %
@@
 \E[Y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
-= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \M_1[j]
-= \sum_{j=0}^{L-1} M_{i-j} \M_1[j].
+= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
+= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
 %
@@
 %
-\E Y[i] = \gamma \sum_{j=0}^{L-1} \M_1[j] = \gamma \L_1.
+\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma a_x^1.
 %

### 2019-02-11 inverse_problems/inverse_problems.tex
no message

@@
 %
-Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
 %
@@
 
-\subsection{Equivalence between the spacing condition and the Poisson process} \label{sec:poisson}
-
-In this section we omit the affect of the noise as it remains the same for the well-separated model.
+\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process} \label{sec:poisson}
+
+In this section we omit the affect of the noise as it remains the same for the well-separated model. We aim to show that the moments of
 
@@
 %
-m_y^1[i] = \E X[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-m_y^2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-m_y^3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
-%
-\end{align}
-
-%We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
-%%
-%\begin{align}
-%%
-%\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
-%%
-%\end{align}
-%%
-%\begin{align}
-%%
-%\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
-%%
-%\end{align}
-%%
-%and
-%%
-%\begin{align}
-%%
-%\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
-%%
-%\end{align}
-%
-%
-%Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.
-%
-%%
+m_X^1[i] &= \E X[i], \quad 0 \le i \le L-1,   \nonumber\\ 
+m_X^2[i,j] &= \E X[i] X[j], \quad 0 \le i,j \le L-1, \\ 
+m_X^3[i,j,k] &= \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1. \nonumber
+\end{align}
+%
+Note that 
+\begin{align}
+a_X^1 &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^1[i], \nonumber \\
+a_X^2[\ell] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^2[i,i+\ell], \\
+a_X^3[\ell_1,\ell_2] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^3[i,i+\ell_1,i+\ell_2]. \nonumber
+\end{align}
 
@@
 \begin{proposition} \label{prop:poisson}
-    For each $i$,  the moments of the Poisson process are equal to 
-    \begin{align}
-    m_y^1[i] &= \gamma a_X^1 \nonumber \\
+    For any $i$,  the moments under the Poisson process are equal to 
+    \begin{align}
+    m_y^1[i] &= \gamma L a_X^1 \nonumber \\
     m_y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
@@
 Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $Z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-This is not true for 1-D signals: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating the symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
-
-In the literature, the phase and reflection symmetries are usually called trivial ambiguities.
 If the mean of signal is available and non-zero, the sign symmetry can be resolved.
 However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
+The case of 1-D signals is essentially different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
 
@@
 
+\TODO{Probably should be re-written}
 Clearly, the first-order autocorrelation provides us one equation.
@@
 
-\subsection{The first moment of $Y$}
-
-To compute the first moment of $Y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
-%
-\begin{align}
-%
-\E[Y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
+\subsection{First moment}
+
+To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
+%
+\begin{align}
+%
+\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
 = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
@@
 %
-\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma a_x^1.
-%
-\end{align}
-
-%
-
-\subsection{The second moment of $Y$}
+\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
+%
+\end{align}
+
+%
+
+\subsection{Second moment}
 
@@
 
-\subsection{The third moment of $Y$}
+\subsection{Third moment}
 

### 2019-02-14 inverse_problems/inverse_problems.tex
Added red dots to figure KL-XP and included in the paper with caption.

@@
 
-\usepackage[margin=.6in]{geometry}
+\usepackage[margin=3cm]{geometry}
 
@@
 
-\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process} \label{sec:poisson}
+\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process \TODO{?}} \label{sec:poisson}
 
@@
 If we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. 
-Hence, if $\sigma$ is know we have 
+Hence, if $\sigma$ is known we have 
 \begin{align*}
@@
 \paragraph{K-L figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=.7\linewidth]{KLXP/XP1}
+	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
+CPU time in seconds.
+Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments.
+Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
+	\label{fig:KLXP}
+\end{figure}
 

### 2019-02-14 inverse_problems/inverse_problems.tex
revising first section

@@
 
-\newenvironment{myquote}[1]%
-{\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
-{\endlist}
-
 %\allowdisplaybreaks
@@
 
-\title{Multi-target detection and clustering with application to cryo-electron microscopy}
+\title{Multi-target detection with application to cryo-electron microscopy}
 
@@
 
-In this paper, we consider the problem of recovering a signal that appear 
+We consider the problem of recovering a set of $K$ signals that appear 
 multiple times at unknown locations in a noisy measurement.
-Let $x\in\RL$ be the sought signal and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$.
-Let  $s \in \{0, 1\}^{N-L+1}$ be a binary signal indicating (with ones) the starting positions of all occurrences of $x$ in $y$, so that, with additive white Gaussian noise the measurement model reads:
+Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
+Let  $s \in \mathbb{N}^{N-L+1}$.
+In the $i$th entry of $s$, $s[i]$ signals are positioned in $y$ with element $0$ at location $i$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$.
+If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
+With additive white Gaussian noise, the measurement model can be written as a mix of blind deconvolution problems 
 \begin{equation} 
-y  =  x \ast s + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+y  =  \sum_{k=1}^K x_k \ast s_k + \varepsilon, \qquad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
 \label{eq:model}
 \end{equation}
-where $\ast$ denotes linear convolution. 
-While both $x$ and $s$ are unknown, the goal is only to estimate $x$ from $y$. We name this problem \emph{multi-target detection}.
+where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of starting positions of $x_k$ in $y[i]$ so that $s =  s_1+\cdots+s_K$. 
+The goal is  to estimate $x_1,\ldots,x_K$ from $y$. % while $s$ is the \emph{nuisance variable} of the problem.
+We name this problem \emph{multi-target detection}.
+This idealized setup appears in several scientific applications, including structural biology~\cite{bendory2018toward} (as we detail below), spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive}, and system identification~\cite{ljung1998system}.
+
+In the low noise regime, a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve a standard deconvolution problem.
+Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
+This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper. In this setting, we consider  $s_1,\ldots,s_K$  as \emph{nuisance variables}.
+
+In order to recover the signals in the high noise regime, we use autocorrelation analysis.
+For any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for large enough $N$. 
+This computation is straightforward and requires only one pass over the data.
+The underlying principle is to relate the autocorrelations of the observation $y$ to the autocorrelations of $x_1,\ldots,x_K$.
+Below we describe two generative models for $s$.  
+In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depend on $s_1,\ldots,s_K$ only through their sums, that is, the total number of occurrences of each signal.
+To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares (LS) problem as explained in Section~\ref{sec:numerics}.
 
@@
 \emph{blind deconvolution}---a longstanding problem arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-Different variants of the blind deconvolution problem have been subject recently to a thorough  analysis, focusing on low noise regimes~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
-A key difference  is that in multi-target detection the parameters of the signal $s$ (the locations of its nonzero values) are  \emph{nuisance variables}---that is, we aim only at estimating only $x$.
-Multi-target detection appears in several scientific applications, including spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.
-
-In the low noise regime, one can estimate $s$ and then estimate $x$ by standard deconvolution techniques.
+Different variants of the blind deconvolution problem have been subject recently to a thorough  analysis~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
+In clear contrast to multi-target detection, these works focus on the low noise regime and aim at estimating both unknown signals.
+
+%In the low noise regime, one can estimate $s$ and then estimate $x$ by standard deconvolution techniques.
 However, in the high noise regime, estimating $s$ is impossible---that is, detection is impossible~\cite{bendory2018toward,aguerrebere2016fundamental}.
+
+\subsection{Generative models}
+
+\paragraph{The well-separated model.}
 To guarantee recovery in any noise regime, we require a separation between adjacent signal's occurrences, that is,
@@
 
+\paragraph{The Poisson model.}
+
+\TODO{For the heterogeneous case.}
+
+The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
+We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
+Points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma (N-L)$. %The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
+For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$, with overlapping vectors being added together.
+
+If $M_i$ denotes the number of hits at location $i$,  then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
+Conditional on the value of $M = (M_1,\dots,M_{N-L+1})$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
+With this notation, we can write each entry as:
+%
+\begin{align}
+%
+y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
+%
+\end{align}
+
 \subsection{Extensions} \label{sec:extensions}
 
+\TODO{multi-dimensions}
+
 The basic model~\eqref{eq:model} can be extended in various ways, some discussed below.
-
-\paragraph{Multi-target detection and clustering with separation.}
-The multi-target detection model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
+%
+%\paragraph{Multi-target detection and clustering with separation.}
+%The multi-target detection model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
 Let $s$ be a binary signal satisfying the separation condition~\eqref{eq:spacing}.
-For each $s[i]=1$, a random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$. Then, $x_{v_i}$ is placed in $y$
-with element $0$ at location $i$. 
-We refer to this model as \emph{multi-target detection and clustering}.
-
- This model can be written as a mix of blind deconvolution problems
-\begin{equation} 
-y  =  \sum_{i=1}^Kx_i \ast s_i + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
-\end{equation}
-where again $s_i$ is a binary signal, which its non-zero values 
-are the subset of the non-zero values of $s$ associated with $x_i$.
-Generally, we refer to this problem as \emph{multi-target detection and clustering with separation.} 
+%For each $s[i]=1$, a random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$. Then, $x_{v_i}$ is placed in $y$
+%with element $0$ at location $i$. 
+%We refer to this model as \emph{multi-target detection and clustering}.
+%
+% This model can be written as a mix of blind deconvolution problems
+%\begin{equation} 
+%y  =  \sum_{k=1}^Kx_k \ast s_k + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+%\end{equation}
+%where again $s_i$ is a binary signal, which its non-zero values 
+%are the subset of the non-zero values of $s$ associated with $x_i$.
+%Generally, we refer to this problem as \emph{multi-target detection and clustering with separation.} 
 %An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
@@
 
-\paragraph{Poisson model for the support signal.}
-
-The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
-We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
-Points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma (N-L)$. %The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
-For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$, with overlapping vectors being added together.
-
-If $M_i$ denotes the number of hits at location $i$,  then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
-Conditional on the value of $M = (M_1,\dots,M_{N-L+1})$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
-With this notation, we can write each entry as:
-%
-\begin{align}
-%
-y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
-%
-\end{align}
-
-\subsection{Motivation: single-particle reconstruction using cryo-electron microscopy}
+\section{Motivation: single-particle reconstruction using cryo-electron microscopy}
 Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules; see for instance~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
@@
 
-In order to recover the signal, we employ autocorrelation analysis.
+%
+%In order to recover the signal, we employ autocorrelation analysis.
 The underlying principle is to relate the autocorrelations of the observation to the autocorrelations of the signal without trying to detect individual signal occurrences (i.e., the signal $s$).
-In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy in the limit of $N\to\infty$. 
-The autocorrelations of the observation are straightforward to compute and require only one pass over the data.
+%In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy in the limit of $N\to\infty$. 
+%The autocorrelations of the observation are straightforward to compute and require only one pass over the data.
 After estimation of the density of particles in the micrographs, these directly yield estimates for the mixed autocorrelations of the signals.

### 2019-02-14 inverse_problems/inverse_problems.tex
revised first paragraph

@@
 
-We consider the problem of recovering a set of $K$ signals that appear 
+We consider the \emph{multi-target detection} problem of recovering a set of $K$ signals that appear 
 multiple times at unknown locations in a noisy measurement.
 Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
-Let  $s \in \mathbb{N}^{N-L+1}$.
-In the $i$th entry of $s$, $s[i]$ signals are positioned in $y$ with element $0$ at location $i$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$.
+Let  $s[i]$ counts the number of signals whose first element is positioned in $y[i]$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
 If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
-With additive white Gaussian noise, the measurement model can be written as a mix of blind deconvolution problems 
+With additive white Gaussian noise, the measurement model can be written as 
 \begin{equation} 
@@
 The goal is  to estimate $x_1,\ldots,x_K$ from $y$. % while $s$ is the \emph{nuisance variable} of the problem.
-We name this problem \emph{multi-target detection}.
+%We name this problem \emph{multi-target detection}.
 This idealized setup appears in several scientific applications, including structural biology~\cite{bendory2018toward} (as we detail below), spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive}, and system identification~\cite{ljung1998system}.

### 2019-02-14 inverse_problems/inverse_problems.tex
model section

@@
 Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
-Let  $s[i]$ counts the number of signals whose first element is positioned in $y[i]$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
+Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
 If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
@@
 \begin{equation} 
-y  =  \sum_{k=1}^K x_k \ast s_k + \varepsilon, \qquad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+y  =  \sum_{k=1}^K s_k \ast x_k + \varepsilon, \qquad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
 \label{eq:model}
@@
 where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of starting positions of $x_k$ in $y[i]$ so that $s =  s_1+\cdots+s_K$.
+Explicitly, with zero-based indexing, % and zero-padding out of bounds,
+\begin{align*}
+	y[i] & = \sum_{k=1}^{K} \sum_{j = 0}^{L-1} s_k[i-j] x_k[j] + \varepsilon[i].
+\end{align*}
 The goal is  to estimate $x_1,\ldots,x_K$ from $y$. % while $s$ is the \emph{nuisance variable} of the problem.
@@
 
-%In the low noise regime, one can estimate $s$ and then estimate $x$ by standard deconvolution techniques.
-However, in the high noise regime, estimating $s$ is impossible---that is, detection is impossible~\cite{bendory2018toward,aguerrebere2016fundamental}.
-
-\subsection{Generative models}
+\subsection{Models for target distribution}
+
+We consider two  models for the signal $s$: the first one is .......
 
 \paragraph{The well-separated model.}
-To guarantee recovery in any noise regime, we require a separation between adjacent signal's occurrences, that is,
+
+%Our approach is based on considering the first few entries of the observation's autocorrelations. These entries correspond to products of $y$ with its shifted version, for some small shifts.
+%If $s$ would be too clustered, then
+
+As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
 \begin{equation}
@@
 %Under the separation condition~\eqref{eq:spacing}, we refer to this model as the \emph{homogeneous well-separated model}. 
-In then next section we present a model that alleviates this condition.
+%In the next section we present a model that alleviates this condition.
 %As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
+This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
+As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.
 
@@
 
-\TODO{For the heterogeneous case.}
-
-The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
-We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
-Points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma (N-L)$. %The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
-For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$, with overlapping vectors being added together.
-
-If $M_i$ denotes the number of hits at location $i$,  then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$.
-Conditional on the value of $M = (M_1,\dots,M_{N-L+1})$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
-With this notation, we can write each entry as:
-%
-\begin{align}
-%
-y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
-%
-\end{align}
+If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we consider a Poisson model.
+
+%The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
+%We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
+
+Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
+For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$.
+Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$.
+By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$.
+In particular, this model allows for (additive) signal overlap.
+In Section~\TODO{ref}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
 

### 2019-02-15 inverse_problems/inverse_problems.tex
Intro done

@@
 
-\subsection{Problem formulation} \label{sec:problem_formulation}
+%\subsection{Problem formulation} \label{sec:problem_formulation}
 
@@
 multiple times at unknown locations in a noisy measurement.
-Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
-Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$, each of those  is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
+Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
+Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$.
+Each of those $s[i]$ is chosen according to some (possibly unknown) distribution $\pi$ \TODO{Add notation for the distribution} over $\{1,\ldots,K\}$.
 If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
@@
 
-\subsection{Models for target distribution}
-
-We consider two  models for the signal $s$: the first one is .......
+\subsection*{Models for target distribution}
+
+We consider two  models for the distribution of signal occurrences in the observation, that is, for $s_1, \ldots, s_K$.
 
@@
 This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
+Once $s$ is determined, for each position $i$ such that $s[i] = 1$, one of the signals $x_k$ is selected independently at random, and accordingly we set $s_k[i] = 1$.
 As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.
@@
 In particular, this model allows for (additive) signal overlap.
-In Section~\TODO{ref}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
-
-\subsection{Extensions} \label{sec:extensions}
-
-\TODO{multi-dimensions}
-
-The basic model~\eqref{eq:model} can be extended in various ways, some discussed below.
-%
-%\paragraph{Multi-target detection and clustering with separation.}
-%The multi-target detection model can be naturally generalized to the problem of estimating a set of $K$ signals $x_1,\ldots,x_K\in\RL$.
-Let $s$ be a binary signal satisfying the separation condition~\eqref{eq:spacing}.
-%For each $s[i]=1$, a random variable $v_i$ is drawn from some (possibly unknown) distribution over $\{1,\ldots,K\}$. Then, $x_{v_i}$ is placed in $y$
-%with element $0$ at location $i$. 
-%We refer to this model as \emph{multi-target detection and clustering}.
-%
-% This model can be written as a mix of blind deconvolution problems
-%\begin{equation} 
-%y  =  \sum_{k=1}^Kx_k \ast s_k + \varepsilon, \quad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
-%\end{equation}
-%where again $s_i$ is a binary signal, which its non-zero values 
-%are the subset of the non-zero values of $s$ associated with $x_i$.
-%Generally, we refer to this problem as \emph{multi-target detection and clustering with separation.} 
-%An key question in this model is how many signals can be recovered simultaneously. We derive a bound in Section~\ref{sec:heterogeneity} and show a numerical experiment in Section~\ref{sec:numerics}.
-
-\paragraph{The well-separated model with a random signal}
-The homogeneous and heterogeneous models can be generalized as follows. 
-We let the signal $X\in\RL$ to be a random vector drawn from some fixed distribution. %We observe a random vector $Y\in\R^{N-L+1}$.
-For each non-zero element of $s$,  a random vector $X$ from the distribution is then placed in $y$, with element $0$ at location $i$.
-If the distribution is a Delta function that this model coincides with the multi-target detection model; if it is a sum of Diracs then it reduces to multi-target detection and clustering.
+In Section~\ref{sec:poisson}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
+
+\subsection*{Extensions} \label{sec:extensions}
+
+Extending the problem setup and autocorrelation analysis to signals in more than one dimension is straightforward: see discussion in Section~\ref{sec:high_dimensions} and numerical experiments in Section~\ref{sec:numerics}.
+
+Likewise, it is easy to extend the model to situations where the signal occurrences are sampled from a general distribution rather than from a finite set of choices $x_1, \ldots, x_K$.
+In this setup, the goal is to estimate the distribution (possibly defined by a finite set of parameters).
+In particular, this allows for continuous distributions of targets.
+We adopt this perspective when deriving the autocorrelations in Section~\ref{sec:AC_analysis}.
+
+In the next section, we show how this flexibility allows us to model an important imaging problem in structural biology.
 

### 2019-02-15 inverse_problems/inverse_problems.tex
no message

@@
 
-Let $Z\in \R^m$ be a random signal drawn from some fixed distribution.  The autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+In what follows, we consider autocorrelations of both the observation $y$ and of the signal occurrences in $y$.
+As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$, or from a more general distribution.
+Accordingly, we define autocorrelations for a random signal $z$ of length $m$ \TODO{change $m$ to something upper case, maybe $U$}.
+For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
+
+For a random signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
 \begin{equation}
-a_Z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m} \sum_{i=-\infty}^{\infty} Z[i]Z[i+\ell_1]\cdots Z[i+\ell_{q-1}]\right\},
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} \E\left\{z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\},
 \label{eq:ac_general}
 \end{equation}
-where the expectation is taken with respect to the distribution of $Z$. The indexing of $Z$ out of the range $0, \ldots, m-1$ is zero-padded.
+where the expectation is taken with respect to the distribution of $z$. Indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
 \begin{align} 
-a_Z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
-Z[i]\right\}, \nonumber\\
-a_Z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{Z[i]Z[i+\ell]\right\},\\
-a_Z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{Z[i]Z[i+\ell_1]Z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
-\end{align}
-The autocorrelation functions have symmetries. Specifically, $$\E\left\{a_Z^2[\ell]\right\} = \E\left\{a_Z^2[-\ell]\right\},$$ and \TODO{to verify}
-$$\E\left\{a_Z^3[\ell_1,\ell_2]\right\} = \E\left\{a_Z^3[\ell_2,\ell_1]\right\}=\E\left\{a_Z^3[-\ell_1,\ell_2-\ell_1]\right\}.
+a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
+z[i]\right\}, \nonumber\\
+a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{z[i]z[i+\ell]\right\},\\
+a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{z[i]z[i+\ell_1]z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
+\end{align}
+Since  autocorrelations depend only on the differences between indices, the obey the following symmetries: $$a_z^2[\ell] = a_z^2[-\ell],$$ and
+$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
 $$
-For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
 
@@
  \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{X}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
+\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{X}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{X}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
 +\delta[\ell_1,\ell_2]\big),
@@
 Here too, few entries are affected by $\sigma$ in the limit.
+
+In particular, for $X$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, the autocorrelations are given in explicit form as:
+\begin{align} 
+a_X^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
+X[i]\right\}, \nonumber\\
+a_X^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{X[i]X[i+\ell]\right\},\\
+a_X^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{X[i]X[i+\ell_1]X[i+\ell_2]\right\}.  \nonumber
+\end{align}
+\TODO{ABOVE: replace expectations with sums.}
 
@@
 \begin{equation}
-a_Z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
 \label{eq:ac_d_dimension}
 \end{equation}
-Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $Z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
 If the mean of signal is available and non-zero, the sign symmetry can be resolved.

### 2019-02-15 inverse_problems/inverse_problems.tex
in the middle of Section 2 (skipped section 2)

@@
 Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
-Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$.
-Each of those $s[i]$ is chosen according to some (possibly unknown) distribution $\pi$ \TODO{Add notation for the distribution} over $\{1,\ldots,K\}$.
+Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$. Each of those $s[i]$ is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
 If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
@@
 %As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
+Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free (but still noisy) entries.
+% This last sentence is required for the proof of the identity of the third-order autocorrelation in Section 3.
 This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
@@
 As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$, or from a more general distribution.
-Accordingly, we define autocorrelations for a random signal $z$ of length $m$ \TODO{change $m$ to something upper case, maybe $U$}.
+Accordingly, we define autocorrelations for a random signal $z$ of length $M$ .
 For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
 
-For a random signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
+For a random signal $z\in \R^M$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} \E\left\{z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\},
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E_z\left\{\frac{1}{M} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\},
 \label{eq:ac_general}
 \end{equation}
-where the expectation is taken with respect to the distribution of $z$. Indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
+where the expectation is taken with respect to the distribution of $z$. Indexing of $z$ out of the range $0, \ldots, M-1$ is zero-padded.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
 \begin{align} 
-a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
+a_z^1 & = \E_z\left\{\frac{1}{M} \sum_{i=0}^{M-1} 
 z[i]\right\}, \nonumber\\
-a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{z[i]z[i+\ell]\right\},\\
-a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{z[i]z[i+\ell_1]z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
+a_z^2[\ell] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell\}}^{M-1 + \min\{0, -\ell\}} z[i]z[i+\ell]\right\},\\
+a_z^3[\ell_1,\ell_2] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{M-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
 \end{align}
@@
 
-Under the separation condition, the relation between autocorrelations of the micrograph and those of $X$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $M$ denote the number of occurrences of $X$ in $y$ (that is, the number of 1's in $s$), and let
+Let $x$ be the random variable corresponding to signal occurrences in $y$. In particular, for the model~\eqref{eq:model}, $x=x_k$ with probability $\pi_k$.
+Under the separation condition~\eqref{eq:spacing}, the relation between autocorrelations of the observation $y$ and those of $x$ is particularly simple, as we now show.
+It is useful to introduce some notation: let $\vert s\vert = \sum_i s[i]$ denote the number of signal occurrences in $y$, and let
 \begin{equation}
-\gamma  = \frac{M L}{N}
+\gamma  = \frac{|s| L}{N}.
 \label{eq:gamma}
 \end{equation}
-denote the density of $X$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $X$.) 
-In this section, we assume the separation condition~\eqref{eq:spacing} that  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
-In Section~\ref{sec:poisson} we show that the autocorrelations in the Poisson model are equivalent to  those presented in this section.
-
-For shifts in $0, \ldots, L-1$, the autocorrelation functions of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$.
-Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $M$ also goes to infinity at the same rate (in other words, as we see an increasingly large observation, it contains increasingly many signal occurrences, with constant signal density).
-In that regime, the law of large numbers can be used to show the following statement:
+In the well-separated model, $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it   
+ the signal density. The separation condition~\eqref{eq:spacing}  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$. 
+ In Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model are equivalent to those presented in this section.
+
+For shifts in $0, \ldots, L-1$, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$. 
+%Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
+We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $|s|$ also goes to infinity at the same rate.
+%(in other words, as we see an increasingly large observation, it contains increasingly many signal occurrences, with constant signal density).
+In that regime, the law of large numbers implies
 \begin{equation} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1  \aseq \gamma a_{X}^1,
-\end{equation}
-\TODO{ should is be $\E\left\{a_{X}^1\right\}$?} where equality holds almost surely (a.s.), meaning it holds with probability one.
-The randomness is over the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_{X}^1$ from $y$. We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ as well in the homogeneous model.
+\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
+\end{equation}
+where equality holds almost surely (a.s.), meaning it holds with probability one.
+The randomness is over $x$ and the Gaussian noise $\varepsilon$; $s$ may be deterministic.
+Thus, given enough data, if $\gamma$ is known, we can estimate $a_{x}^1$ from $y$. We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ as well in a particular case.
 
@@
 
-In particular, for $X$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, the autocorrelations are given in explicit form as:
-\begin{align} 
-a_X^1 & = \frac{1}{m} \sum_{i=0}^{m-1} \E\left\{
-X[i]\right\}, \nonumber\\
-a_X^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{X[i]X[i+\ell]\right\},\\
-a_X^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{X[i]X[i+\ell_1]X[i+\ell_2]\right\}.  \nonumber
-\end{align}
-\TODO{ABOVE: replace expectations with sums.}
+In particular, for $x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, the autocorrelations are given in explicit form as:
+\begin{equation}
+a_x^q  =  \sum_{i=1}^{K} \pi_ka_{x_i}^1.
+\end{equation}
+%\begin{align} 
+%a_X^1 & = \frac{1}{K} \sum_{i=1}^{K} \pi_ka_{x_i}, \nonumber\\
+%a_X^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{X[i]X[i+\ell]\right\},\\
+%a_X^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{X[i]X[i+\ell_1]X[i+\ell_2]\right\}.  \nonumber
+%\end{align}
+%\TODO{ABOVE: replace expectations with sums.}
 
@@
 \section{Relation with cryo-EM + experiments?}
-%
-%In the simplified mathematical model above, we showed it is possible to estimate a signal without detecting its appearances.  
-%Our strategy is to compute autocorrelations of the micrographs and to relate these statistics to the unknown signal's parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-%
-%We also showed how this technique can, in principle, be applied to cryo-EM.
-%Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
-Concerns for model bias are also greatly reduced since no template matching is involved.
-%Additionally,  our technique also allows the use of much lower defocus values.
-Lower defocus means lower contrast, but will maintain  higher frequency information.
-Consequently, we may be able to get high resolution reconstructions from fewer micrographs.
-%
-%Looking toward applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
-%In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
-%We recognize that significant challenges lay ahead for the implementation of the proposed approach to {high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
-%
-%The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
-%This suggests that fourth-order autocorrelation may be necessary. This in turn would imply that the procedure might require a large amount of data. 
-%Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
-Still, large amounts of data also require large amounts of computation.
-On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in a  streaming mode, as only one pass through each micrograph is necessary.
-The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
-Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an important question then is whether the equations can be solved accurately and efficiently in practice.
-%
-%To reach high-resolution reconstruction, beyond data acquisition and computational challenges, there are modeling issues  to consider.
-%In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
-All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects.
-%For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
-%Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
-Such a function models the distribution of distances between neighboring projections.
-The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
-%All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
-
-%
-%\section*{Acknowledgment}
-%The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
-%The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
-%NB is partially supported by NSF award DMS-1719558.
-
-\bibliographystyle{plain}
-\bibliography{ref}
-
-\appendix
-
-\section{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
-
-We consider the asymptotic regime $N,M\to\infty$ and assume that $M=\Omega(N)$, so that
+
+\section{Proof}
+
+\subsection{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
+Let us define
 \begin{equation*}
-\gamma := \frac{ML}{N}>0.
+\gamma = \frac{|s|L}{N}>0.
 \end{equation*}
-%
-Any vectors with indices out of range are given value 0.
-We focus here on the homogeneous model~\eqref{eq:model}. The extension to random signal $X$ is straight-forward by taking the expectation with respect to the distribution of $X$.
-
-We start by considering the mean of the data:
+Then the first order autocorrelation of the observation is given by 
 \begin{equation*}
-a_y^1 = \frac{1}{N}\sum_{i=0}^{N-1} y[i] =
-\frac{1}{N/L}\sum_{j=0}^{M-1}\frac{1}{L}\sum_{i=0}^{L-1}x[i] +    
-\underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]}_{\text{noise term}}
-\xrightarrow{a.s.}\gamma a_x^1,
+a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
+\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
+\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
+=\gamma a_x^1,
 \end{equation*}
-%
-where the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
-
-We proceed with the (second-order) autocorrelation for fixed $\ell\in[0,\ldots,L-1]$. We can compute:
+where $\E_z$ means expectation with respect to the distribution of $z$.
+%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
+
+We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
 %
@@
 %
-a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]
-\nonumber \\
-& = \underbrace{\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}}
-\\ & + \underbrace{\frac{1}{N} \sum_{j=1}^{M} \sum_{i=0}^{L-1} x[i] (\varepsilon[s_j + i + \ell] + \varepsilon[s_j + i - \ell])}_{\text{cross-term}}. 
+a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
+\nonumber \\
+& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
 %
 \end{align*}
-The cross-term is linear in the noise, and is easily shown to vanish almost surely in the limit $N\to\infty$, by the strong law of large numbers.
-We break the signal term into $M$ different sums, each containing one copy of the signal.
-This gives:
-%
+where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
+Hence, 
 \begin{align} \label{eq:2nd_moment_signal_term}
 %
-\frac{1}{N}\sum_{j=1}^{M}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] & = \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\nonumber\\&\xrightarrow{N\to\infty}\gamma a_x^2[\ell].
-%
-\end{align}
-%
-We next analyze the pure noise term. When $\ell\neq 0$, we can break the noise term into a sum of independent terms:
-%
-\begin{equation*}
-%
-\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
-%
-\end{equation*}
-%
-Each sum $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -2} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, hence converges to zero almost surely as $N\to\infty$.
-If $\ell=0$, then we have:
-%
-\begin{equation*}
-\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon^2[i] \xrightarrow{a.s.} \sigma^2.
-\end{equation*}
-
-We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
-%
-%\begin{align*}
-%%
-%&a_y^3[\ell_1,\ell_2] 
-%= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
-%\nonumber \\
-%%
-%=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
-%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
-%\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
-%\nonumber \\
-%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
-%\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
-%\nonumber \\
-%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
-%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
-%\nonumber \\
-%&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
-%\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-%	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
-%%
-%\end{align*}
-%
+a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\delta[\ell],
+\end{align}
+where $\delta[0]=1$ and zero otherwise.
+
+We now analyze the third-order autocorrelation. 
+Let $x_{(j)}$ denote the $j$th
+realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
+Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
 \begin{align*}
@@
 a_y^3[\ell_1,\ell_2] 
-=& \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
+=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
 \\
 %
-=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
-	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
-+ \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
+\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
+	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
+\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
 \ \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
+\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
+\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
 \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i-\ell_2]x[i+\ell_1-\ell_2]x[i]}_{(6)}
+\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
+\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
 \\
-&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[i+\ell_2]}_{(7)}
-+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
-	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
+\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
+\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
 %
 \end{align*}
-Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously.
-Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}.
-To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
-
-{\bf Case 1:} $0 < \ell_2 < \ell_1$.
-Here, all summands with elements of $\ep$ involve products of distinct entries, which have expected value 0.
-Consequently, the usual argument shows that terms (2)--(5) all converge to 0 almost surely as $N \to \infty$.
-
-{\bf Case 2:} $0=\ell_2 < \ell_1$.
-Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely.
-The same argument as for Case 1 shows that (3) and (5) also converge to 0.
-For term (4), we write:
-%
-\begin{align*}
-%
-&\frac{1}{N}\sum_{j=1}^{M} 
-\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
-\nonumber \\
-&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
-\\& \xrightarrow{a.s.} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
-%
-\end{align*}
-
-{\bf Case 3:} $0<\ell_2 = \ell_1$. An argument nearly identical to that for Case 2 shows that terms (2), (4) and (5) converge to 0, while term (3) converges to $\gamma a_x^1 \sigma^2$.
-
-{\bf Case 4:} $0=\ell_2 = \ell_1$.
-The same argument as for term (4) in Case 2 shows that terms (3), (4) and (5) all converge to $\gamma a_x^1 \sigma^2$.
-Term (2) is an average of $\ep[i]^3$, which is mean zero; consequently, it converges to 0.
-This completes the proof.
-
-\section{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
+Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
+Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
+Term (2) is always zero by properties of Gaussian variables. 
+To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
+
+Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
+$\gamma\sigma^2 a_x^1 \delta[\ell_1-\ell_2]$.
+The same goes for Terms (4) and (5), which are equal, respectively, to
+$\gamma\sigma^2 a_x^1 \delta[\ell_2]$ 
+and $\gamma\sigma^2 a_x^1 \delta[\ell_1]$.
+
+\subsection{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
 
@@
 
-\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+\subsection{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
 
@@
 
-\section{Proof of Proposition~\ref{prop:poisson}} \label{sec:proof_prop_poisson}
-
-\subsection{First moment}
+\subsection{Proof of Proposition~\ref{prop:poisson}} \label{sec:proof_prop_poisson}
+
+\subsubsection{First moment}
 
@@
 
-\subsection{Second moment}
+\subsubsection{Second moment}
 
@@
 
-\subsection{Third moment}
+\subsubsection{Third moment}
 
@@
 
+%
+%In the simplified mathematical model above, we showed it is possible to estimate a signal without detecting its appearances.  
+%Our strategy is to compute autocorrelations of the micrographs and to relate these statistics to the unknown signal's parameters.
+Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
+%
+%We also showed how this technique can, in principle, be applied to cryo-EM.
+%Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
+Concerns for model bias are also greatly reduced since no template matching is involved.
+%Additionally,  our technique also allows the use of much lower defocus values.
+Lower defocus means lower contrast, but will maintain  higher frequency information.
+Consequently, we may be able to get high resolution reconstructions from fewer micrographs.
+%
+%Looking toward applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
+%In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
+%We recognize that significant challenges lay ahead for the implementation of the proposed approach to {high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
+%
+%The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
+%This suggests that fourth-order autocorrelation may be necessary. This in turn would imply that the procedure might require a large amount of data. 
+%Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
+Still, large amounts of data also require large amounts of computation.
+On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
+It can even be done in a  streaming mode, as only one pass through each micrograph is necessary.
+The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
+Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
+Of course, an important question then is whether the equations can be solved accurately and efficiently in practice.
+%
+%To reach high-resolution reconstruction, beyond data acquisition and computational challenges, there are modeling issues  to consider.
+%In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
+All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects.
+%For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
+%Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
+Such a function models the distribution of distances between neighboring projections.
+The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
+%All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
+
+%
+%\section*{Acknowledgment}
+%The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
+%The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
+%NB is partially supported by NSF award DMS-1719558.
+
+\bibliographystyle{plain}
+\bibliography{ref}
+
 \end{document}

### 2019-02-15 inverse_problems/Formalism autocorrelations relation/formalism_autocorrelations.tex

%\documentclass{siamart1116}
\documentclass[12pt]{article}

\usepackage[hyphens]{url}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

\input{preamble}

\newcommand{\minimize}{\operatorname{minimize}}

\newcommand{\st}{\textrm{ subject to }}

\newcommand{\E}{\mathbb{E}}

\title{Formalism for autocorrelation derivations}

%\author{
%Nicolas Boumal\thanks{Princeton University, Mathematics Department and PACM, \texttt{nboumal@math.princeton.edu}}  \and Vladislav Voroninski\thanks{Helm.ai} \and Afonso S.\ Bandeira\thanks{Department of Mathematics and Center for Data Science, Courant Institute of Mathematical Sciences, New York University, \texttt{bandeira@cims.nyu.edu}}
%}
\author{(T,N)B}
\date{February 15, 2019}

\begin{document}

\maketitle

Let $x_{(1)}, \ldots, x_{(|s|)}$ denote the (independent) realizations of the random signal $x$ in the observation $y$, starting at (deterministic) positions $s_{(1)}, \ldots, s_{(|s|)}$. Let $I_{ij}$ be the indicator variable for whether position $i$ is in the support of occurrence $j$, that is, it is one if $i$ is in $\{s_{(j)}, \ldots, s_{(j)}+L-1\}$, and zero otherwise. Then,
\begin{align*}
	y[i] & = \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i].
\end{align*}
This gives a simple expression for the first autocorrelation of $y$:
\begin{align}
	a_y^1 & = \E_y\left\{ \frac{1}{N} \sum_{i = 0}^{N-1} y[i] \right\} \\
		  & = \frac{1}{N} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \sum_{i = 0}^{N-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right\}.
\end{align}
Now switch the sums over $i$ and $j$, and observe that $I_{ij}$ is zero unless $i = s_{(j)} + t$ for $t$ in the range $0, \ldots, L-1$. Hence,
\begin{align}
	a_y^1 & = \frac{1}{N} \sum_{j = 1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-1} x_{(j)}[t]\right\} + \frac{1}{N} \E_\varepsilon\left\{ \sum_{i=0}^{N-1} \varepsilon[i]\right\}.
\end{align}
Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are independent and all distributed as $x$, we further find:
\begin{align}
	a_y^1 & = \frac{|s|}{N} L a_x^1 = \gamma a_x^1.
\end{align}

To address the second-order moments, we resort to the separation conditions. Indeed, consider this expression:
\begin{align}
	a_y^2[\ell] & = \E_y\left\{ \frac{1}{N} \sum_{i = 0}^{N-1} y[i] y[i+\ell] \right\} \\
				& = \frac{1}{N} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right) \right\}.
\end{align}

\end{document}

### 2019-02-15 inverse_problems/Formalism autocorrelations relation/formalism_autocorrelations.tex
Finished writing up formal derivation of moments

@@
 Then,
-\begin{align*}
+\begin{align}
 	y[i] & = \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i].
-\end{align*}
+	\label{eq:explicityiindicators}
+\end{align}
 This gives a simple expression for the first autocorrelation of $y$:
@@
 \begin{align}
-	a_y^1 & = \frac{|s|}{N} L a_x^1 = \gamma a_x^1.
+	a_y^1 & = \frac{|s|L}{N} a_x^1 = \gamma a_x^1.
 \end{align}
@@
 \begin{align}
-	a_y^2[\ell] & = \E_y\left\{ \frac{1}{N} \sum_{i = 0}^{N-1} y[i] y[i+\ell] \right\} \\
-				& = \frac{1}{N} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right) \right\}.
+	N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-1} y[i] y[i+\ell] \right\} \\
+				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \right\} \\
+				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Big\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
+					& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
+					& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
+					& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Big\}
+\end{align}
+The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences.
+The last term vanishes in expectation unless $\ell = 0$ since distinct entries of $\varepsilon$ are independent.
+For $\ell = 0$, $\E\{\varepsilon[i]^2\} = \sigma^2$.
+Finally, using the separation property, observe that if $I_{ij}  I_{i+\ell,j'}$ is nonzero, then it is equal to one, $j = j'$ and $i = s_{(j)} + t$ for some $t$ in $0, \ldots, L-\ell-1$.
+Then, switch the order of summations to get
+\begin{align}
+	N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + N\sigma^2 \delta[\ell],
+\end{align}
+where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
+\begin{align}
+	a_y^2[\ell] & = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
 \end{align}
 
+We now turn to the third-order autocorrelations. These involve the sum
+\begin{align}
+	\sum_{i=0}^{N-1} y[i] y[i+\ell_1] y[i+\ell_2].
+\end{align}
+Using~\eqref{eq:explicityiindicators}, we find that this quantity can be expressed as a sum eight terms:
+% \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i]
+\begin{enumerate}
+	\item $\sum_{i=0}^{N-1} \sum_{j,j',j'' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_{i=0}^{N-1} \sum_{j,j' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
+	\item $\sum_{i=0}^{N-1} \sum_{j,j'' = 1}^{|s|} I_{ij} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_{i=0}^{N-1} \sum_{j',j'' = 1}^{|s|} I_{i+\ell_1, j'} I_{i+\ell_2,j''} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_{i=0}^{N-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
+	\item $\sum_{i=0}^{N-1} \sum_{j' = 1}^{|s|} I_{i+\ell_1, j'} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
+	\item $\sum_{i=0}^{N-1} \sum_{j'' = 1}^{|s|} I_{i+\ell_2,j''} \varepsilon[i] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_{i=0}^{N-1} \varepsilon[i] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
+\end{enumerate}
+Terms 2--4 and 8 vanish in expectation since odd moments of centered Gaussian variables are zero. For the first term, we use the fact that the separation condition implies
+\begin{multline}
+	I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} = 1 \iff \\ j=j'=j'' \textrm{ and } i = s_{(j)} + t \textrm{ with } t \in \{ 0, \ldots L-\max(\ell_1, \ell_2)-1 \}.
+\end{multline}
+(Otherwise, the product of indicators is zero.) This allows to reduce the summations over $j,j',j''$ to a single sum over $j$.
+Then, witching the order of summation with $i$, we get that the first term is equal to
+\begin{align}
+	\sum_{j=1}^{|s|} \sum_{t=0}^{L-\max(\ell_1, \ell_2)-1} x_{(j)}[t] x_{(j)}[t+\ell_1] x_{(j)}[t+\ell_2].
+\end{align}
+In expectation over the realizations $x_{(j)}$, using again that they are i.i.d.\ with the same distribution as $x$, this first term yields $|s|L a_x^3[\ell_1, \ell_2]$.
+Now consider the fifth term.
+Taking expectation against $\varepsilon$ yields
+\begin{align}
+	\sum_{i=0}^{N-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \delta[\ell_1 - \ell_2].
+\end{align}
+Switch the order of summation over $i$ and $j$ again to get
+\begin{align}
+	\sigma^2 \delta[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
+\end{align}
+Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \delta[\ell_1 - \ell_2]$.
+A similar reasoning for terms 6 and 7 yields this final formula for the third-order autocorrelations of $y$:
+\begin{align}
+	a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \delta[\ell_1] + \delta[\ell_2] + \delta[\ell_1 - \ell_2] \right).
+\end{align}
 \end{document}

### 2019-02-17 inverse_problems/Formalism autocorrelations relation/formalism_autocorrelations.tex
Small touch-ups

@@
 \end{align}
-This gives a simple expression for the first autocorrelation of $y$:
+This gives a simple expression for the first autocorrelation of $y$. Indeed,
 \begin{align}
@@
 To address the second-order moments, we resort to the separation conditions. Indeed, consider this expression:
-\begin{align}
+\begin{align*}
 	N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-1} y[i] y[i+\ell] \right\} \\
-				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \right\} \\
-				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Big\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
+				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\Bigg\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \cdot \\
+				& \qquad \qquad \qquad \qquad \qquad  \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \Bigg\} \\
+				& = \sum_{i = 0}^{N-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Bigg\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
 					& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
 					& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
-					& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Big\}
-\end{align}
+					& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Bigg\}.
+\end{align*}
 The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences.
@@
 \end{align}
-Using~\eqref{eq:explicityiindicators}, we find that this quantity can be expressed as a sum eight terms:
+Using~\eqref{eq:explicityiindicators}, we find that this quantity can be expressed as a sum of eight terms:
 % \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i]

### 2019-02-18 inverse_problems/inverse_problems.tex
update of section 3

@@
 \end{align}
-Since  autocorrelations depend only on the differences between indices, the obey the following symmetries: $$a_z^2[\ell] = a_z^2[-\ell],$$ and
+Since  autocorrelations depend only on the differences between indices, they obey the following symmetries: $$a_z^2[\ell] = a_z^2[-\ell],$$ and
 $$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
@@
 \end{equation}
-In the well-separated model, $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it   
- the signal density. The separation condition~\eqref{eq:spacing}  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$. 
- In Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model are equivalent to those presented in this section.
-
-For shifts in $0, \ldots, L-1$, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the support signal $s$. 
-%Importantly, under the separation condition~\eqref{eq:spacing}, the dependency on $s$ is only through the density $\gamma$.
-We consider the asymptotic regime where $\gamma$ remains constant; that is, as $N$ goes to infinity, $|s|$ also goes to infinity at the same rate.
-%(in other words, as we see an increasingly large observation, it contains increasingly many signal occurrences, with constant signal density).
-In that regime, the law of large numbers implies
-\begin{equation} \label{eq:mean_micrograph}
-\lim_{N\to\infty} a_y^1  \aseq \gamma a_{x}^1,
-\end{equation}
-where equality holds almost surely (a.s.), meaning it holds with probability one.
-The randomness is over $x$ and the Gaussian noise $\varepsilon$; $s$ may be deterministic.
-Thus, given enough data, if $\gamma$ is known, we can estimate $a_{x}^1$ from $y$. We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ as well in a particular case.
-
-We have a similar observation for the second-order autocorrelation: $a_y^2[\ell]$ computes the correlation between $y$ and a copy of $y$ shifted by $\ell$ entries.
-Considering $\ell$ only in the range $0, \ldots, L-1$, one can see that any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
-As a result,
-\begin{equation}
-\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma a_{X}^2[\ell] + \sigma^2\delta[\ell],
-\label{eq:ac2_micrograph}
-\end{equation}
-%\begin{equation}
-%\lim_{N\to\infty} a_y^2[\ell]  \aseq \gamma \E\left\{a_{X}^2[\ell]\right\} + \sigma^2\delta[\ell],
-%\label{eq:ac2_micrograph}
-%\end{equation}
-for $\ell = 0, \ldots, L-1$, where $\delta[\ell]$ equals one for $\ell=0$ and zero otherwise.
-The last part captures the autocorrelation of the noise.
-Notice that, even if $\sigma$ is unknown, entries $\ell = 1, \ldots, L-1$ still provide useful information about $a_{X}^2[\ell]$.
-
-Along the same lines, one can establish a relation for third-order autocorrelations:
-\begin{equation}
- \label{eq:ac3_micrograph}
-\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] \aseq \gamma a_{X}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{X}^1  \big(\delta[\ell_1,0]+\delta[0,\ell_2]
-+\delta[\ell_1,\ell_2]\big),
-\end{equation}
-for $\ell_1,\ell_2 = 0, \ldots, L-1$, where $\delta[\ell_1,\ell_2]:=\delta[\ell_1-\ell_2]$.
-Here too, few entries are affected by $\sigma$ in the limit.
+In the well-separated model, $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it the signal density.
+The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
+
+Owing to the separation condition, when correlating $y$ with shifted versions of itself for shifts in $0, \ldots, L-1$, any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
+As a result, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the density $\gamma$ (which is a weak dependence on the support signal $s$).
+Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
+\begin{align}
+	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
+	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \label{eq:ac2_micrograph} \\
+	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
+	+\delta[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
+\end{align}
+where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
+Terms proportional to $\sigma^2$ are due to the noise.
+If $\sigma$ is known, they can be handled easily.
+If $\sigma$ is unknown, one can either estimate it form the data, or one can ignore the few entries of the autocorrelations that are affected by $\sigma$---one in $a_y^2$ and $3L-2$ in $a_y^3$, a relatively small number in both cases.
+
+In our problem setup, we are given one observation (one realization) of $y$.
+Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual autocorrelations of $y$, that is, % (ergodicity)
+\begin{align}
+	\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] = a_y^q[\ell_1, \ldots, \ell_{q-1}].
+\end{align}
+This provides a concrete means of estimating the quantities $a_y^ q$.
 
@@
 \begin{equation}
-a_x^q  =  \sum_{i=1}^{K} \pi_ka_{x_i}^1.
-\end{equation}
-%\begin{align} 
-%a_X^1 & = \frac{1}{K} \sum_{i=1}^{K} \pi_ka_{x_i}, \nonumber\\
-%a_X^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} \E\left\{X[i]X[i+\ell]\right\},\\
-%a_X^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} \E\left\{X[i]X[i+\ell_1]X[i+\ell_2]\right\}.  \nonumber
-%\end{align}
-%\TODO{ABOVE: replace expectations with sums.}
-
-%
-%Computing the autocorrelations of the micrograph is straightforward. The natural question, treated next, is whether one can recover $x$ from them.
+a_x^q  =  \sum_{k=1}^{K} \pi_ka_{x_k}^q.
+\end{equation}
+We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ from observations for the particular case where $K = 1$ (all signal occurrences are the same).
+Furthermore, in Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model provide the same information about $x$ as those presented in this section.
 
@@
 \subsection{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
-Let us define
-\begin{equation*}
-\gamma = \frac{|s|L}{N}>0.
-\end{equation*}
-Then the first order autocorrelation of the observation is given by 
-\begin{equation*}
-a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
-\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
-\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
-=\gamma a_x^1,
-\end{equation*}
-where $\E_z$ means expectation with respect to the distribution of $z$.
-%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
-
-We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
-%
+
+%Let us define
+%\begin{equation*}
+%\gamma = \frac{|s|L}{N}>0.
+%\end{equation*}
+%Then the first order autocorrelation of the observation is given by 
+%\begin{equation*}
+%a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
+%\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
+%\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
+%=\gamma a_x^1,
+%\end{equation*}
+%where $\E_z$ means expectation with respect to the distribution of $z$.
+%%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
+%
+%We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
+%%
+%\begin{align*}
+%%
+%a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
+%\nonumber \\
+%& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
+%%
+%\end{align*}
+%where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
+%Hence, 
+%\begin{align} \label{eq:2nd_moment_signal_term}
+%%
+%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\delta[\ell],
+%\end{align}
+%where $\delta[0]=1$ and zero otherwise. 
+%
+%We now analyze the third-order autocorrelation. 
+%Let $x_{(j)}$ denote the $j$th
+%realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
+%Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
+%\begin{align*}
+%%
+%a_y^3[\ell_1,\ell_2] 
+%=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
+%\\
+%%
+%\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
+%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
+%\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
+%\ \\
+%\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
+%\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
+%\\
+%\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
+%\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
+%\\
+%\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
+%\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
+%	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
+%%
+%\end{align*}
+%Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
+%Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
+%Term (2) is always zero by properties of Gaussian variables. 
+%To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
+%
+%Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
+%$\gamma\sigma^2 a_x^1 \delta[\ell_1-\ell_2]$.
+%The same goes for Terms (4) and (5), which are equal, respectively, to
+%$\gamma\sigma^2 a_x^1 \delta[\ell_2]$ 
+%and $\gamma\sigma^2 a_x^1 \delta[\ell_1]$.
+
+Let $x_{(1)}, \ldots, x_{(|s|)}$ denote the (independent) realizations of the random signal $x$ in the observation $y$, starting at (deterministic) positions $s_{(1)}, \ldots, s_{(|s|)}$.
+Let $I_{ij}$ be the indicator variable for whether position $i$ is in the support of occurrence $j$, that is, it is one if $i$ is in $\{s_{(j)}, \ldots, s_{(j)}+L-1\}$, and zero otherwise.
+Then,
+\begin{align}
+y[i] & = \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i].
+\label{eq:explicityiindicators}
+\end{align}
+This gives a simple expression for the first autocorrelation of $y$. Indeed,
+\begin{align}
+a_y^1 & = \E_y\left\{ \frac{1}{N} \sum_{i = 0}^{N-1} y[i] \right\} \\
+& = \frac{1}{N} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \sum_{i = 0}^{N-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right\}.
+\end{align}
+Now switch the sums over $i$ and $j$, and observe that $I_{ij}$ is zero unless $i = s_{(j)} + t$ for $t$ in the range $0, \ldots, L-1$. Hence,
+\begin{align}
+a_y^1 & = \frac{1}{N} \sum_{j = 1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-1} x_{(j)}[t]\right\} + \frac{1}{N} \E_\varepsilon\left\{ \sum_{i=0}^{N-1} \varepsilon[i]\right\}.
+\end{align}
+Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are independent and all distributed as $x$, we further find:
+\begin{align}
+a_y^1 & = \frac{|s|L}{N} a_x^1 = \gamma a_x^1.
+\end{align}
+
+To address the second-order moments, we resort to the separation conditions. First, consider this expression:
 \begin{align*}
-%
-a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
-\nonumber \\
-& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
-%
+N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-\ell-1} y[i] y[i+\ell] \right\} \\
+& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\Bigg\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \cdot \\
+& \qquad \qquad \qquad \qquad \qquad  \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \Bigg\} \\
+& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Bigg\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
+& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
+& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
+& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Bigg\}.
 \end{align*}
-where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
-Hence, 
-\begin{align} \label{eq:2nd_moment_signal_term}
-%
-a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\delta[\ell],
-\end{align}
-where $\delta[0]=1$ and zero otherwise.
-
-We now analyze the third-order autocorrelation. 
-Let $x_{(j)}$ denote the $j$th
-realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
-Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
-\begin{align*}
-%
-a_y^3[\ell_1,\ell_2] 
-=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
-\\
-%
-\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
-	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
-\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
-\ \\
-\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
-\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
-\\
-\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
-\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
-\\
-\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
-\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
-%
-\end{align*}
-Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
-Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
-Term (2) is always zero by properties of Gaussian variables. 
-To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
-
-Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
-$\gamma\sigma^2 a_x^1 \delta[\ell_1-\ell_2]$.
-The same goes for Terms (4) and (5), which are equal, respectively, to
-$\gamma\sigma^2 a_x^1 \delta[\ell_2]$ 
-and $\gamma\sigma^2 a_x^1 \delta[\ell_1]$.
+The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences.
+The last term vanishes in expectation unless $\ell = 0$ since distinct entries of $\varepsilon$ are independent.
+For $\ell = 0$, $\E\{\varepsilon[i]^2\} = \sigma^2$.
+Finally, using the separation property, observe that if $I_{ij}  I_{i+\ell,j'}$ is nonzero, then it is equal to one, $j = j'$ and $i = s_{(j)} + t$ for some $t$ in $0, \ldots, L-\ell-1$.
+Then, switch the order of summations to get
+\begin{align}
+N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \delta[\ell],
+\end{align}
+where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
+\begin{align}
+a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \delta[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
+\end{align}
+
+We now turn to the third-order autocorrelations. These involve the sum
+\begin{align}
+\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} y[i] y[i+\ell_1] y[i+\ell_2].
+\end{align}
+Using~\eqref{eq:explicityiindicators}, we find that this quantity can be expressed as a sum of eight terms:
+% \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i]
+\begin{enumerate}
+	\item $\sum_i \sum_{j,j',j'' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_i \sum_{j,j' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
+	\item $\sum_i \sum_{j,j'' = 1}^{|s|} I_{ij} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_i \sum_{j',j'' = 1}^{|s|} I_{i+\ell_1, j'} I_{i+\ell_2,j''} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_i \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
+	\item $\sum_i \sum_{j' = 1}^{|s|} I_{i+\ell_1, j'} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
+	\item $\sum_i \sum_{j'' = 1}^{|s|} I_{i+\ell_2,j''} \varepsilon[i] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
+	\item $\sum_i \varepsilon[i] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
+\end{enumerate}
+Terms 2--4 and 8 vanish in expectation since odd moments of centered Gaussian variables are zero. For the first term, we use the fact that the separation condition implies
+\begin{multline}
+I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} = 1 \iff \\ j=j'=j'' \textrm{ and } i = s_{(j)} + t \textrm{ with } t \in \{ 0, \ldots L-\max(\ell_1, \ell_2)-1 \}.
+\end{multline}
+(Otherwise, the product of indicators is zero.) This allows to reduce the summations over $j,j',j''$ to a single sum over $j$.
+Then, witching the order of summation with $i$, we get that the first term is equal to
+\begin{align}
+\sum_{j=1}^{|s|} \sum_{t=0}^{L-\max(\ell_1, \ell_2)-1} x_{(j)}[t] x_{(j)}[t+\ell_1] x_{(j)}[t+\ell_2].
+\end{align}
+In expectation over the realizations $x_{(j)}$, using again that they are i.i.d.\ with the same distribution as $x$, this first term yields $|s|L a_x^3[\ell_1, \ell_2]$.
+Now consider the fifth term.
+Taking expectation against $\varepsilon$ yields
+\begin{align}
+\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \delta[\ell_1 - \ell_2].
+\end{align}
+Switch the order of summation over $i$ and $j$ again to get
+\begin{align}
+\sigma^2 \delta[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
+\end{align}
+Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \delta[\ell_1 - \ell_2]$.
+A similar reasoning for terms 6 and 7 yields this final formula for the third-order autocorrelations of $y$:
+\begin{align}
+a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \delta[\ell_1] + \delta[\ell_2] + \delta[\ell_1 - \ell_2] \right).
+\end{align}
 

### 2019-02-19 inverse_problems/inverse_problems.tex
Fine 607 session: rearranged a lot of sections 3 and 4

@@
 
-Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
+\TODO{Careful that $\gamma$ changed by a factor of $L$: need to modify here too.} Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
 For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$.
@@
 
-Let $x$ be the random variable corresponding to signal occurrences in $y$. In particular, for the model~\eqref{eq:model}, $x=x_k$ with probability $\pi_k$.
+In what follows, $x$ is the random variable corresponding to signal occurrences in $y$. In particular, for the model~\eqref{eq:model}, 
+%$x=x_k$ with probability $\pi_k$.
+%In particular, for
+$x$ is sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, so that its autocorrelations are given in explicit form as:
+\begin{equation}
+	a_x^q  = \sum_{k=1}^{K} \pi_ka_{x_k}^q.
+\end{equation}
+We are given one observation (one realization) of $y$.
+Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual autocorrelations of $y$, that is, % (ergodicity)
+\begin{align}
+\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] = a_y^q[\ell_1, \ldots, \ell_{q-1}].
+\end{align}
+This provides a concrete means of estimating the quantities $a_y^ q$.
+In the remainder of this section, we relate the observables $a_y^q$  to the unknowns $a_x^q$, first under the well-separated model, then under the Poisson model.
+
+\subsection{Autocorrelations under the well-separated model}
+
 Under the separation condition~\eqref{eq:spacing}, the relation between autocorrelations of the observation $y$ and those of $x$ is particularly simple, as we now show.
@@
 \end{equation}
-In the well-separated model, $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it the signal density.
+This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it the signal density.
 The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
@@
 
-In our problem setup, we are given one observation (one realization) of $y$.
-Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual autocorrelations of $y$, that is, % (ergodicity)
-\begin{align}
-	\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] = a_y^q[\ell_1, \ldots, \ell_{q-1}].
-\end{align}
-This provides a concrete means of estimating the quantities $a_y^ q$.
-
-In particular, for $x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, the autocorrelations are given in explicit form as:
-\begin{equation}
-a_x^q  =  \sum_{k=1}^{K} \pi_ka_{x_k}^q.
-\end{equation}
-We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ from observations for the particular case where $K = 1$ (all signal occurrences are the same).
-Furthermore, in Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model provide the same information about $x$ as those presented in this section.
+\TODO{We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ from observations for the particular case where $K = 1$ (all signal occurrences are the same).}
+
+%Furthermore, in Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model provide the same information about $x$ as those presented in this section.
+
+\subsection{Autocorrelations under the Poisson model}
+
+\begin{comment}
+In this section we omit the affect of the noise as it remains the same for the well-separated model. We aim to show that the moments of
+
+Let us denote by $m_Y^q$ the moments of $Y$:
+%
+\begin{align}
+%
+m_X^1[i] &= \E X[i], \quad 0 \le i \le L-1,   \nonumber\\ 
+m_X^2[i,j] &= \E X[i] X[j], \quad 0 \le i,j \le L-1, \\ 
+m_X^3[i,j,k] &= \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1. \nonumber
+\end{align}
+%
+Note that 
+\begin{align}
+a_X^1 &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^1[i], \nonumber \\
+a_X^2[\ell] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^2[i,i+\ell], \\
+a_X^3[\ell_1,\ell_2] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^3[i,i+\ell_1,i+\ell_2]. \nonumber
+\end{align}
+
+In the following,  we show that the moments of the observed data under the Poisson process can be written in terms of the autocorrelations of the well-separated model.
+
+\begin{proposition} \label{prop:poisson}
+	For any $i$,  the moments under the Poisson process are equal to 
+	\begin{align}
+	m_y^1[i] &= \gamma L a_X^1 \nonumber \\
+	m_y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
+	m_y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
+	\end{align}
+\end{proposition}
+
+\begin{corollary} \TODO{re-write}
+	From the first three moments of the Poisson process model, one can recover the first three moments from the strongly-separated model.
+\end{corollary}
+\end{comment}
+
+\TODO{What we want to have in this section}
+\begin{enumerate}
+	\item Recall the Poisson model (it's already described at the end of intro, so keep it short).
+	\item Define a proper notion of $\gamma$ (careful with scaling $L$).
+	\item State formulas for $a_y^q$ with $q = 1, 2, 3$ (ideally, including noise terms) to parallel what we did in the well-separated section.
+It would be better to do everything with autocorrelations rather than moments to keep the story uniform.
+	\item (optional) Claim: under some assumptions (knowing $\gamma$?
+Others?), the autocorrelations of $y$ of order $q = 1, 2, 3$ under the Poisson model provide the same information about $x$ as the corresponding autocorrelations under the well-separated model.
+Could also be in Section 4.1.
+\end{enumerate}
 
@@
 
-\subsection{Theory for the homogeneous case} \label{sec:theory_homogeneous}
+\TODO{Explain difference between homogeneous and heterogeneous}
+
+\subsection{Guarantees for the homogeneous case} \label{sec:theory_homogeneous}
 In this section, we derive some theoretical results for the homogeneous case. \TODO{Note: I am using terms interchangeably}
@@
 	%
-	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$.
+	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. \TODO{Definitely only clear for the homogeneous case}
 \end{proposition}
@@
 \begin{proposition} \label{prop:gamma}
+	\TODO{Can we do this simultaneously for Poisson? or do we only need to do it for well-separated and invoke the equivalence claim? Not if that claim requires knowledge of $\gamma, \sigma$.}
 	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
@@
 
-\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process \TODO{?}} \label{sec:poisson}
-
-In this section we omit the affect of the noise as it remains the same for the well-separated model. We aim to show that the moments of
-
-Let us denote by $m_Y^q$ the moments of $Y$:
-%
-\begin{align}
-%
-m_X^1[i] &= \E X[i], \quad 0 \le i \le L-1,   \nonumber\\ 
-m_X^2[i,j] &= \E X[i] X[j], \quad 0 \le i,j \le L-1, \\ 
-m_X^3[i,j,k] &= \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1. \nonumber
-\end{align}
-%
-Note that 
-\begin{align}
-a_X^1 &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^1[i], \nonumber \\
-a_X^2[\ell] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^2[i,i+\ell], \\
-a_X^3[\ell_1,\ell_2] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^3[i,i+\ell_1,i+\ell_2]. \nonumber
-\end{align}
-
-In the following,  we show that the moments of the observed data under the Poisson process can be written in terms of the autocorrelations of the well-separated model.
-
-\begin{proposition} \label{prop:poisson}
-    For any $i$,  the moments under the Poisson process are equal to 
-    \begin{align}
-    m_y^1[i] &= \gamma L a_X^1 \nonumber \\
-    m_y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
-    m_y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
-    \end{align}
-\end{proposition}
-
-\begin{corollary} \TODO{re-write}
-	From the first three moments of the Poisson process model, one can recover the first three moments from the strongly-separated model.
-\end{corollary}
-
-\subsection{Autocorrelations in higher dimensions} \label{sec:high_dimensions}
-
-Autocorrelations in $d$ dimensions is defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
-\begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
-\label{eq:ac_d_dimension}
-\end{equation}
-Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-If the mean of signal is available and non-zero, the sign symmetry can be resolved.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-The case of 1-D signals is essentially different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
-
-This uniqueness result for multi-dimensional signals (especially for 2-D images) is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
-illuminated with a coherent wave, and the far field diffraction
-intensity pattern  is measured, corresponding object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
-If the support of the object is known and less than half of the support of the measured signal, then the data is equivalent to the second-order autocorrelation.
-The computational problem of recovering the signal is usually referred to as \emph{phase retrieval} or \emph{phase problem}.
-Albeit the uniqueness result, recently it has been shown that, at least for 2-D images, the problem is  ill-conditioned~\cite{barnett2018geometry}.
-That is, there exist different images whose second-order autocorrelation agree up to machine precision.
-
-\subsection{How many signals can be recovered in the heterogeneous model?}
+\subsection{Elemetary limitations of the heterogeneous case}
 \label{sec:heterogeneity}
+
+\TODO{Check and specify if this holds for both models}
 
@@
 Thus, we conjecture that approximately $L/2$ signals can be decomposed from  the first three mixed autocorrelations.
+
+\subsection{Autocorrelations in higher dimensions} \label{sec:high_dimensions}
+
+\TODO{Debate this later}
+
+Autocorrelations in $d$ dimensions is defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
+\begin{equation}
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
+\label{eq:ac_d_dimension}
+\end{equation}
+Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+If the mean of signal is available and non-zero, the sign symmetry can be resolved.
+However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
+The case of 1-D signals is essentially different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
+
+This uniqueness result for multi-dimensional signals (especially for 2-D images) is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
+illuminated with a coherent wave, and the far field diffraction
+intensity pattern  is measured, corresponding object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
+If the support of the object is known and less than half of the support of the measured signal, then the data is equivalent to the second-order autocorrelation.
+The computational problem of recovering the signal is usually referred to as \emph{phase retrieval} or \emph{phase problem}.
+Despite the uniqueness result, recently it has been shown that, at least for 2-D images, the problem is  ill-conditioned~\cite{barnett2018geometry}.
+That is, there exist different images whose second-order autocorrelation agree up to machine precision.
 

### 2019-02-26 inverse_problems/inverse_problems.tex
no message

@@
 In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
-The microscope produces a 2-D tomographic image of the samples embedded in the ice, called a \emph{micrograph}.
+The microscope produces 2-D tomographic images of the samples embedded in the ice, called \emph{micrographs}.
 Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
-The goal is to construct 3-D models of the molecular structure from the micrographs.
+The goal is to construct 3-D models of the molecular structures from the micrographs.
 Importantly, to keep radiation damage within acceptable bounds, the dose must be kept low, leading to high noise levels.
 
+A 2-D micrograph $y$ can be in terms of~\eqref{eq:model} where the discrete signals $x_1,\ldots,x_K$ are replaced by a random signal drawn from the a general distribution.
+In particular, in each position $s[i]$, a 2-D tomographic projection of the 3-D structure is placed, taken from a random viewing direction according to (possibly unknown) fixed distribution.
+
 All contemporary methods in the field split the reconstruction procedure into two main  stages.
-The first stage consists in extracting the  particle projections from the micrographs.
+The first stage consists of estimating the signal $s$---that is, extracting the particle projections from the micrographs.
 This stage is called \emph{particle picking}.
-The second stage aims to construct a 3-D model of the molecular structure from these projections.
-The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR. This fact has been recognized early on by the cryo-EM community. 
+Given the projections, the second stage aims to construct a 3-D model of the molecular structure.
+%The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
+Crucially, reliable detection of individual particles is impossible in a highly noisy environment. This fact has been recognized early on by the cryo-EM community. 
 Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
@@
 In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure.
+In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles biases the reconstructed structure.
 This model bias is common to all particle picking methods based on template matching.
@@
 This goal of  the current paper is to provide a theoretical justification and numerical support  for the method proposed in~\cite{bendory2018toward}.  
-In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the random signal $X$ discussed in Section~\ref{sec:extensions} can be thought of as 2-D random tomographic projections of the 3-D structure
+%In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the random signal $X$ discussed in Section~\ref{sec:extensions} can be thought of as 2-D random tomographic projections of the 3-D structure
 taken according to some unknown distribution of the particles within the ice.
@@
 Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
-His method has been extended and employed by in X-ray free electron lasers and cryo-EM; see for instance~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
+Kam's method has been extended and employed by in X-ray free electron lasers and cryo-EM; see for instance~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
 In order to investigate the computational and statistical properties of Kam's method, a series of papers have studied a simplified model, 
 called   \emph{multi-reference alignment}~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
-We follows the same line of research by considering the multi-target detection and clustering  as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
-
-%\subsection{Principle mathematical tool: autocorrelation analysis.}
-
-%Our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the
-%forward model takes the form
-%%
-%\begin{math}
-%%
-%y = x\ast w + \varepsilon,  
-%%
-%\end{math} 
-%%
-%where $x$ is the unknown signal (the system's impulse response), $w$ is an unknown (often random) input sequence, and $\varepsilon$ is an additive noise.
-%The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
-In the special case where $w$ is binary and satisfies our separation condition, we recover our model.
-%
-%Likelihood-based methods estimate $x$ as the maximizer of some function $f(x | y)$, where $f$ is derived from the likelihood function of $x$ given the observed signal $y$.  
-%If some prior is assumed on $x$, then $f(x|y)$ can be taken to be the posterior distribution of $x$ given the data; this is the simplest form of Bayesian inference.
-%Methods based on such formulations are popular nowadays in cryo-EM; see for instance~\cite{sigworth1998maximum,scheres2012relion}. 
-%Optimizing the function $f(x|y)$ exactly is often intractable, and thus heuristic methods are used instead.
-One proposed technique is to use Markov Chain Monte Carlo (MCMC)~\cite{cappe1999simulation}.
-%In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}.
-The EM method for discrete $w$ is based on a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}.
-However, the complexity of this procedure is superlinear in $N$, and therefore its usage is limited for big data sets.
-%
-%Because likelihood methods are computationally expensive, methods based on recovery from moments have also been previously used for system identification.
-Methods based on the third- and fourth-order moments are described and analyzed in~\cite{lii1982deconvolution,giannakis1989identification,tugnait1984identification}.
-Building on such ideas, we focus on an autocorrelation analysis for~\eqref{eq:model}.
-
-%
-%\section{The detection limit} \label{sec:detectionlimit}
-%
-%In the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
-%To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise.
-Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
-%The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$. 
-%
-%This decision problem can be abstracted as follows: We have two known vectors $\theta_0 = x$ and $\theta_1 = 0$ in $\mathbb{R}^L$.
-There is a random variable $\eta$ taking values 0 or 1 with probabilities $q$ and $1-q$, respectively.
-We observe a random vector $X \in \mathbb{R}^L$ (an extract of the micrograph) with the following distribution: if $\eta = 0$, then $X \sim \mathcal N(\theta_0,\sigma^2I_L)$ and if $\eta = 1$, then $X \sim \mathcal N(\theta_1,\sigma^2I_L)$.
-%
-%We observe $X$, and our task is to estimate $\eta$.
-How reliably can this be done?
-If $q \geq 1/2$, the constant estimator $\hat{\eta} = 0$ is correct with probability $q$; likewise, if $q \leq 1/2$, the constant estimator $\hat{\eta} = 1$ is correct with probability $1-q$.
-The question is, can we do better than this?
-We prove that, as $\sigma \to \infty$, the answer is no.
-The result is proved in Appendix~\ref{sec:proof_two_gauss}.
-%
-%\begin{proposition} \label{prop:two_gauss}
-%	For any deterministic estimator $\hat{\eta }$ of $\eta$,
-%	\begin{equation}
-%	\lim_{\sigma \to \infty} \P[ \hat{\eta} = \eta  ] \leq \max(q, 1-q);
-%	\end{equation}
-%	that is: as the SNR deteriorates, the probability of success is no better than random chance.
-%\end{proposition}
-%
-%Proposition~\ref{prop:two_gauss} implies that in order to estimate the signal at low SNR we must consider methods that aim to estimate the signal $x$ directly, without estimating the nuisance variable $s$ as an intermediate step.
-%In the next sections, we consider autocorrelation analysis for that purpose.
+We follows the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
 
 \section{Autocorrelation analysis} \label{sec:AC_analysis}
-
-%
-%In order to recover the signal, we employ autocorrelation analysis.
-The underlying principle is to relate the autocorrelations of the observation to the autocorrelations of the signal without trying to detect individual signal occurrences (i.e., the signal $s$).
-%In the models described above, for any noise level, these autocorrelations can be estimated to any desired accuracy in the limit of $N\to\infty$. 
-%The autocorrelations of the observation are straightforward to compute and require only one pass over the data.
-After estimation of the density of particles in the micrographs, these directly yield estimates for the mixed autocorrelations of the signals.
-To estimate the signals them from their estimated autocorrelations, we solve a nonlinear inverse problem as explained in Section~\ref{sec:numerics}.
 
@@
 In the remainder of this section, we relate the observables $a_y^q$  to the unknowns $a_x^q$, first under the well-separated model, then under the Poisson model.
+\TODO{Explicit expressions of the autocorrelations for cryo-EM are given in~\cite{bendory2018toward}}
 
@@
 \subsection{Guarantees for the homogeneous case} \label{sec:theory_homogeneous}
-In this section, we derive some theoretical results for the homogeneous case. \TODO{Note: I am using terms interchangeably}
+%In this section, we derive some theoretical results for the homogeneous case. \TODO{Note: I am using terms interchangeably}
 
@@
 
-\section{Relation with cryo-EM + experiments?}
+%\section{Relation with cryo-EM + experiments?}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Changes to §4.2

--- 2019-02-19 inverse_problems/inverse_problems.tex
@@
 %We name this problem \emph{multi-target detection}.
+In parts of the paper, we focus on the case $K = 1$, called the \emph{homogeneous} case; the case $K > 2$ is called \emph{heterogeneous}.
 This idealized setup appears in several scientific applications, including structural biology~\cite{bendory2018toward} (as we detail below), spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive}, and system identification~\cite{ljung1998system}.
@@
 z[i]\right\}, \nonumber\\
-a_z^2[\ell] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell\}}^{M-1 + \min\{0, -\ell\}} z[i]z[i+\ell]\right\},\\
-a_z^3[\ell_1,\ell_2] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{M-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]\right\}.  \nonumber \label{eq:ac_special}
+a_z^2[\ell] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell\}}^{M-1 + \min\{0, -\ell\}} z[i]z[i+\ell]\right\}, \label{eq:ac_special} \\
+a_z^3[\ell_1,\ell_2] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{M-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]\right\}. \nonumber
 \end{align}
@@
 $x$ is sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, so that its autocorrelations are given in explicit form as:
-\begin{equation}
-	a_x^q  = \sum_{k=1}^{K} \pi_ka_{x_k}^q.
-\end{equation}
+\begin{align}
+	a_x^q  & = \sum_{k=1}^{K} \pi_ka_{x_k}^q.
+	\label{eq:mixedautocorr}
+\end{align}
 We are given one observation (one realization) of $y$.
@@
 \TODO{Check and specify if this holds for both models}
-
-In the heterogeneous models, the autocorrelation of $K$ signals are mixed together.
-To this end, we count how many equations the first three autocorrelations provide, after omitting symmetries.
-While we do not provide a rigorous proof, it was shown in similar problems that number of equations captures exactly how many signals can be decomposed for a mix of their autocorrelations~\cite{bandeira2017estimation}.
-
-\TODO{Probably should be re-written}
-Clearly, the first-order autocorrelation provides us one equation.
-For second-order autocorrelations, notice  that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus if $\sigma$ is known we obtain $L$ equations, while if not we omit $\ell = 0$.
-This has the practical effect that we need not know $\sigma$ to make sense of the computed quantities, while loosing one one equation.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries): $\frac{(L+1)(L+2)}{2}-2$ in total.
-If we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. 
-Hence, if $\sigma$ is known we have 
+\TODO{Did we define densities $\gamma_k$?}
+
+In the heterogeneous model~\eqref{eq:model}, the unknowns are $K$ signals of length $L$, together with their densities $\gamma_1, \ldots, \gamma_K$ (equivalently: the distribution $\pi$ and overall density $\gamma$) and possibly the noise level $\sigma$.
+To estimate these parameters, we must collect at least as many independent equations.
+Within our framework, polynomial equations are provided by the observable autocorrelations, which correspond to mixed autocorrelations of the unknowns as per~\eqref{eq:mixedautocorr}.
+In this section, following~\cite{boumal2017heterogeneous}, we count how many equations the first three autocorrelations may provide in the best case (discounting symmetries).
+This leads to a straightforward information-theoretic upper bound on the number $K$ of signals which can be estimated, as a function of $L$.
+This is only an upper bound, though a bound of the same type was shown to be tight in a similar setting~\cite{bandeira2017estimation}.
+
+The first-order autocorrelation $a_y^1$~\eqref{eq:mean_micrograph} provides one equation.
+For second-order autocorrelations $a_y^2[\ell]$~\eqref{eq:ac2_micrograph}, if $\sigma$ is known we obtain $L$ equations with $\ell$ ranging from 0 to $L-1$.
+If $\sigma$ is unknown, we may disregard $a_y^2[0]$ (then only entry affected by $\sigma$) and still collect $L-1$ equations.
+Similarly, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$~\eqref{eq:ac3_micrograph} with $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), providing $\frac{(L+1)(L+2)}{2}-2$ equations in total.
+If we further exclude any entries such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$, there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
+
+Hence, if $\sigma$ is known we collect
 \begin{align*}
@@
 \end{align*}
-and if it unknown
+equations, while if it unknown and we choose not to estimate it, then we collect
 \begin{align*}
@@
 \end{align*}
-coefficients in total. Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$  is
+equations in total. Of course, there may be redundancy in these equations: we aim only to provide a bound, under the assumption that these equations are independent.
+
+Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$ plus $K$ parameters for the densities $\gamma_k$ (or the distribution $\pi$ and overall density $\gamma$), there are $K(L+1)$ unknowns.
+As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
 \begin{equation}
-K\leq \frac{L(L+5)}{2(L+1)},
-\end{equation}
+	K \leq \frac{L(L+5)}{2(L+1)},
+\end{equation}
+for the case of $\sigma$ known, and
 \begin{align*}
-K \leq \frac{ L (L-1) + 1}{2(L+1)}.
+	K \leq \frac{ L (L-1) + 1}{2(L+1)}
 \end{align*}
-Thus, we conjecture that approximately $L/2$ signals can be decomposed from  the first three mixed autocorrelations.
+for the case of $\sigma$ unknown and not estimated.
+Overall, this indicates that, at best, approximately $L/2$ signals and their densities can be recovered from the first three mixed autocorrelations.
+Based on related results in~\cite{bandeira2017estimation}, we expect that as many as $L/2$ signals can indeed be estimated, though possibly not with computationally tractable estimators.
 

### 2019-02-26 inverse_problems/inverse_problems.tex
unnumber equation
unnumber
.

@@
 As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
-\begin{equation}
+\begin{align*}
 	K \leq \frac{L(L+5)}{2(L+1)},
-\end{equation}
+\end{align*}
 for the case of $\sigma$ known, and
@@
 
-The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs.
+%The technique we advocate allows recovery of signals hidden in noisy observations without detecting the location  of the signals embedded in the observation.
 To illustrate the underlying principles of the method, we present several numerical examples.
 The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
+
+%\paragraph{Numerical experiment with three 1-D signals.}
+
+In this section, we present three numerical experiments: \TODO{menu}.
+
+\subsection{Experiment 1}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_466300}
+	\caption{ds}
+	\label{fig:1D_example}
+\end{figure}
+
+For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
+Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
+The resulting SNR of $y$
+% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
+is about 1/9.
+
+This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
+
+Given the observation $y$, we proceed to compute the autocorrelations.
+The first-order autocorrelation is straightforward.
+For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
+Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
+Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
+We have
+\begin{align*}
+1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+\end{align*}
+coefficients in total.
+Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
+\begin{align*}
+K(L+1) \leq \frac{1}{2} L (L-1) + 1.
+\end{align*}
+Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). \TODO{The last paragraph can be removed}
+In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
+Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
+If multiple GPUs are available, segments can of course be handled in parallel.
+
+Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
+\begin{multline}
+\min_{\substack{\hat x_1, \ldots, \hat x_K \in \R^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
+\label{eq:optim1D}
+\end{multline}
+where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
+
+Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+Thus, we first run the optimization with $W = 2L-1$.
+This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
+Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
+This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
+We find that this procedure is reliable for a wide range of experimental parameters.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+\subsection{Experiment 2}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=.7\linewidth]{KLXP/XP1}
+	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
+CPU time in seconds.
+Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments.
+Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
+	\label{fig:KLXP}
+\end{figure}
+
+\subsection{Experiment 3}
 
@@
 As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+\end{figure}
 
@@
 \end{figure}
-
- Appendix~\ref{sec:numeric_details} provides additional details on the experiments.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
-
-In practice, we do not expect to know $\gamma$ and maybe not even $\sigma$
-
-\paragraph{Numerical experiment with three 1-D signals.}
-
-For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting SNR of $y$
-% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/9.
-
-This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-%\TODO{TB: I would place the equation counting argument in the theory section in the paragraph of open questions (I marked th place)}
-%
-Given the observation $y$, we proceed to compute the autocorrelations.
-The first-order autocorrelation is straightforward.
-For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
-We have
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-coefficients in total.
-Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-\begin{align*}
-K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-\end{align*}
-Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). \TODO{The last paragraph can be removed}
-In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
-
-Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-\begin{multline}
-\min_{\substack{\hat x_1, \ldots, \hat x_K \in \R^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
-\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
-
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
-Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-
-\paragraph{K-L figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=.7\linewidth]{KLXP/XP1}
-	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
-CPU time in seconds.
-Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments.
-Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
-	\label{fig:KLXP}
-\end{figure}
-
-%\section{Relation with cryo-EM + experiments?}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Menu sentence

@@
 In particular, this model allows for (additive) signal overlap.
-In Section~\ref{sec:poisson}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
+In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
 
@@
 
-In this section, we present three numerical experiments: \TODO{menu}.
+In this section, we present three numerical experiments.
+In the first two experiments, we consider the heterogeneous model~\eqref{eq:model}.
+First, with a fixed noise level, we show how the estimation quality improves as the length of the observation grows.
+Second, we explore how many signals can be recovered in an infinite data regime, where effects of the noise have been averaged out.
+In the last experiment, we extend our model to 2D signals.
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Worked on caption XP1

@@
 First, with a fixed noise level, we show how the estimation quality improves as the length of the observation grows.
-Second, we explore how many signals can be recovered in an infinite data regime, where effects of the noise have been averaged out.
+Second, we explore how many signals can be recovered as a function of their length, in an infinite data regime where effects of the noise have been averaged out.
 In the last experiment, we extend our model to 2D signals.
 
-\subsection{Experiment 1}
+\subsection{Experiment 1} \label{sec:XP1}
 
@@
 	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{ds}
-	\label{fig:1D_example}
+	\caption{Experiment described in Section~\ref{sec:XP1}.
+For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed density and occurrence probabilities.
+Each rows corresponds to one of the signals.
+The last column shows evolution of the relative root mean squared error in estimating each signal, as a longer and longer subset of $y$ is observed.
+Red dots mark the three snapshots that are illustrated in columns 1--3: red signals are the ground truth and blue signals are the estimators.}
+	\label{fig:1Dheterosignals}
 \end{figure}

### 2019-02-26 inverse_problems/inverse_problems.tex
no message

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 
-In the first experiment, we estimated 
-an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
-Each micrograph contains, on average, 700 occurrences of the target image at random locations.
+Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimated 
+an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations.
+Each observation is  of size $4096\times 4096$ pixels and contains on average, 700 occurrences  at random locations, while keeping the separation condition~\eqref{eq:spacing}.
 Thus, about 10\% of each micrograph contains signal.

### 2019-02-26 inverse_problems/inverse_problems.tex
no message

@@
 Each observation is  of size $4096\times 4096$ pixels and contains on average, 700 occurrences  at random locations, while keeping the separation condition~\eqref{eq:spacing}.
-Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$.
 This high noise level is illustrated in Figure~\ref{fig:micro_example}.
-To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
+As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
+Hence, to use this property and keep things simple, we assume the number of signal occurrences and the noise standard deviation are known so that we can estimate the second-order autocorrelation of the image from thos the observation directly.
+%Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
+%	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+%\end{figure}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
XP 1 explained

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 
-For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+For the experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$: see the three red signals in the first column.
+Following~\eqref{eq:model}, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals (well separated).
 This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+For each placement, one of the three signals is picked at random according to the proportions $\pi = (1/2, 1/3, 1/6)$.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting SNR of $y$
+The resulting signal-to-noise ratio of $y$
 % sqrt((m_want*sum(X.^2)')/(sigma^2*n))
@@
 
-This is enough noise to make cross-correlations of $y$ even with the true signals display peaks at essentially random locations, uninformative of the actual locations of the signal occurrences.
+Visually, the noise dominates the signal to the point that it is challenging to detect occurrences.
+More precisely, the cross-correlations of $y$ even with the true signals presents peaks at essentially random locations, apparently uninformative of the actual locations of the signal occurrences.
 Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
 
-Given the observation $y$, we proceed to compute the autocorrelations.
+%Given the observation $y$, we proceed to compute the autocorrelations.
 The first-order autocorrelation is straightforward.
@@
 We have
-\begin{align*}
-1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-coefficients in total.
+%\begin{align*}
+%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
+%\end{align*}
+%coefficients in total.
 Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-\begin{align*}
-K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-\end{align*}
-Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}). \TODO{The last paragraph can be removed}
+%\begin{align*}
+%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
+%\end{align*}
+%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}).
+
+Our aim is to investigate how accurately we can estimate the signals as a function of the observation length.
+To this end, we consider a growing part of the observation $y$.
+For each length, we compute autocorrelations on that part, then we go on to estimate the signals from these ``mixed'' quantities.
 In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
@@
 
-Having computed the moments of interest, we now estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
+Having computed the autocorrelations of interest, we estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
 We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
@@
 This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
+Since we hope the signals estimated this way correspond to the true signals zero-padded on either side to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
 This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
@@
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly preempts location and classification.
+We also note that the amount of data required to produce these good estimations is large.
+Furthermore, as illustrated here and as we have observed in numerous experiments, signals with more variations (such as the third signal in this experiment which was generated once from a Gaussian distribution) are easier to estimate accurately than more regular signals (in this case, despite the fact that the third signal occurs less frequently than the others).
 

### 2019-02-26 inverse_problems/inverse_problems.tex
.

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations.
-Each observation is  of size $4096\times 4096$ pixels and contains on average, 700 occurrences  at random locations, while keeping the separation condition~\eqref{eq:spacing}.
-Thus, about 10\% of each micrograph contains signal.
-The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
-This high noise level is illustrated in Figure~\ref{fig:micro_example}.
-To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
-Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
-
-We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
-Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
-Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
-Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
-
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. 
-Figure~\ref{fig:error_per_micro} %(see appendix)
-presents the normalized recovery error as a function of the amount of data available.
-This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
-As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
+Each observation is  of size $4096\times 4096$ pixels and contains 700 occurrences on average  at random locations, while maintaining the separation condition~\eqref{eq:spacing}.
+The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$, illustrated in Figure~\ref{fig:micro_example}. 
+ % corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$. 
+%As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
+%Hence, to use this property and keep things simple, we assume the number of signal occurrences and the noise standard deviation are known so that we can estimate the second-order autocorrelation of the image from thos the observation directly.
+%Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
+
+We compute the average second-order autocorrelation of the observations. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
+To  keep things simple, we assume the number of signal occurrences and the noise standard deviation are known. 
+Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.  
+As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
+Then, to estimate the target image, we employed a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
 
@@
 	%\vspace{-8pt} 	
+\end{figure}
+
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities). \TODO{The probably appeared before}
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of observations. 
+Figure~\ref{fig:error_per_micro} 
+presents the normalized recovery error as a function of the amount of data available.  This is computed after fixing the reflection symmetries (see Section~\ref{sec:high_dimensions}).
+
+% As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
 \end{figure}

### 2019-02-26 inverse_problems/inverse_problems.tex
.

@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
-In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
-By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
+	\caption{\label{fig:micro_example} Example of observations for the 2-D experiment (of size $250\times 250$) with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
+Each observation contains the same four occurrences of a $50 \times 50$ image of Einstein.
+In panel (c), the noise level is such that it is very challenging to detect  the planted image.} %In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
+}
+\end{figure}
+%By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
 %\vspace{-8pt}
-\end{figure}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Exp 3

@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
+	\caption{\label{fig:Einst_example} Recovery of Einstein from observations at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the data allow to estimate the power spectrum of the target image.
+This does not require particle picking.
+The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ observations (growing across panels from left to right).}
+	%	\vspace{-8pt} 
+\end{figure}
+
 \begin{figure}[h]
@@
 	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
-	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
-	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
-Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
-	%	\vspace{-8pt} 
+	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}.}
 \end{figure}

### 2019-02-26 inverse_problems/inverse_problems.tex

@@
 
-In this section, we present three numerical experiments: \TODO{menu}.
-
-\subsection{Experiment 1}
+In this section, we present three numerical experiments.
+In the first two experiments, we consider the heterogeneous model~\eqref{eq:model}.
+First, with a fixed noise level, we show how the estimation quality improves as the length of the observation grows.
+Second, we explore how many signals can be recovered as a function of their length, in an infinite data regime where effects of the noise have been averaged out.
+In the last experiment, we extend our model to 2D signals.
+
+\subsection{Experiment 1} \label{sec:XP1}
 
@@
 	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{ds}
-	\label{fig:1D_example}
+	\caption{Experiment described in Section~\ref{sec:XP1}.
+For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed density and occurrence probabilities.
+Each rows corresponds to one of the signals.
+The last column shows evolution of the relative root mean squared error in estimating each signal, as a longer and longer subset of $y$ is observed.
+Red dots mark the three snapshots that are illustrated in columns 1--3: red signals are the ground truth and blue signals are the estimators.}
+	\label{fig:1Dheterosignals}
 \end{figure}
 
-For the 1-D experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$.
-Following the forward model described at the beginning of this section, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals.
+For the experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$: see the three red signals in the first column.
+Following~\eqref{eq:model}, we generate an observation $y$ of length $12.3 \cdot 10^9$.
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals (well separated).
 This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $1/2, 1/3, 1/6$.
+For each placement, one of the three signals is picked at random according to the proportions $\pi = (1/2, 1/3, 1/6)$.
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting SNR of $y$
+The resulting signal-to-noise ratio of $y$
 % sqrt((m_want*sum(X.^2)')/(sigma^2*n))

### 2019-02-26 inverse_problems/inverse_problems.tex
XP 2 beginning of description

@@
 
+In this second experiment, presented in Figure~\ref{fig:KLXP}, we investigate how many distinct signals $x_1, \ldots, x_K$ can be estimated from mixed autocorrelations~\eqref{eq:mixedautocorr}.
+In order to do so, we consider a setup where the mixed autocorrelations are known perfectly.
+This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$, and known $\sigma$ which would allow to remove noise bias.
+Furthermore, we assume uniform occurrence distribution $\pi$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
+
+To produce Figure~\ref{fig:KLXP}, we consider each pair $(K, L)$ in turn, with $K = 1, 2, 3, \ldots, 10$ and $L = 5, 10, 15, \ldots, 100$.
+For each pair, we generate $K$ random normal signals of length $L$, once.
+The perfect mixed autocorrelations are computed.
+They are then provided to the algorithm described in Section~\ref{sec:XP1}, together with the knowledge that signals occur with equal probability, as well as the correct density $\gamma$.
+The algorithm is initialized 50 times with an independent random initial guess, also following a normal distribution.
+For each run, we record three metrics:
+\begin{enumerate}
+	\item Whether the optimization algorithm managed to produce a solution with cost function value below $10^{-16}$: this assesses whether optimization succeeded.
+	\item The relative root mean squared error between the estimated signals and the ground truth (up to permutation of the $K$ signals.)
+	\item The computation time in seconds (keeping in mind that the 50 runs are done in parallel on the same, shared computer, so that this is more of a qualitative assessment.)
+\end{enumerate}
+
+Figure~\ref{fig:KLXP} has three panels. \TODO{todo todo tk tk}
+
 \subsection{Experiment 3}
 
-Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimated 
-an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations.
-Each observation is  of size $4096\times 4096$ pixels and contains 700 occurrences on average  at random locations, while maintaining the separation condition~\eqref{eq:spacing}.
-The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$, illustrated in Figure~\ref{fig:micro_example}. 
- % corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$. 
-%As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
-%Hence, to use this property and keep things simple, we assume the number of signal occurrences and the noise standard deviation are known so that we can estimate the second-order autocorrelation of the image from thos the observation directly.
-%Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
-
-We compute the average second-order autocorrelation of the observations. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
-To  keep things simple, we assume the number of signal occurrences and the noise standard deviation are known. 
-Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.  
-As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
-Then, to estimate the target image, we employed a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+In the first experiment, we estimated 
+an 50-by-50 pixel image of Einstein with mean zero from a growing number of micrographs, each of size $4096\times 4096$ pixels.
+Each micrograph contains, on average, 700 occurrences of the target image at random locations.
+Thus, about 10\% of each micrograph contains signal.
+The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$.
+This high noise level is illustrated in Figure~\ref{fig:micro_example}.
+To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known.
+Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
+
+We compute the average second-order autocorrelation of the micrographs. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
+Given the noise level and number of image repetitions, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
+Then, to estimate the target image, we resort to a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
+
+Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of micrographs. 
+Figure~\ref{fig:error_per_micro} %(see appendix)
+presents the normalized recovery error as a function of the amount of data available.
+This is computed after fixing the reflection symmetries (see Section~\ref{sec:AC_analysis}).
+As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
+	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
+\end{figure}
 
@@
 	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of observations for the 2-D experiment (of size $250\times 250$) with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each observation contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is very challenging to detect  the planted image.} %In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
-}
+	\caption{\label{fig:micro_example} Example of micrographs of size $250\times 250$ with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
+Each micrograph contains the same four occurrences of a $50 \times 50$ image of Einstein.
+In panel (c), the noise level is such that it is very challenging to locate the occurrences of the planted image.
+In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
+By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
+	%\vspace{-8pt} 	
 \end{figure}
-%By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
-%\vspace{-8pt}
-
-Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities). \TODO{The probably appeared before}
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of observations. 
-Figure~\ref{fig:error_per_micro} 
-presents the normalized recovery error as a function of the amount of data available.  This is computed after fixing the reflection symmetries (see Section~\ref{sec:high_dimensions}).
-
-% As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
 
@@
 	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
-	\caption{\label{fig:Einst_example} Recovery of Einstein from observations at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the data allow to estimate the power spectrum of the target image.
+	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
+Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image.
 This does not require particle picking.
-The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ observations (growing across panels from left to right).}
+A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly.
+Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}
 	%	\vspace{-8pt} 
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
-	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}.}
 \end{figure}

### 2019-02-26 inverse_problems/inverse_problems.tex

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 \end{figure}
+
+In this second experiment, presented in Figure~\ref{fig:KLXP}, we investigate how many distinct signals $x_1, \ldots, x_K$ can be estimated from mixed autocorrelations~\eqref{eq:mixedautocorr}.
+In order to do so, we consider a setup where the mixed autocorrelations are known perfectly.
+This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$, and known $\sigma$ which would allow to remove noise bias.
+Furthermore, we assume uniform occurrence distribution $\pi$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
+
+To produce Figure~\ref{fig:KLXP}, we consider each pair $(K, L)$ in turn, with $K = 1, 2, 3, \ldots, 10$ and $L = 5, 10, 15, \ldots, 100$.
+For each pair, we generate $K$ random normal signals of length $L$, once.
+The perfect mixed autocorrelations are computed.
+They are then provided to the algorithm described in Section~\ref{sec:XP1}, together with the knowledge that signals occur with equal probability, as well as the correct density $\gamma$.
+The algorithm is initialized 50 times with an independent random initial guess, also following a normal distribution.
+For each run, we record three metrics:
+\begin{enumerate}
+	\item Whether the optimization algorithm managed to produce a solution with cost function value below $10^{-16}$: this assesses whether optimization succeeded.
+	\item The relative root mean squared error between the estimated signals and the ground truth (up to permutation of the $K$ signals.)
+	\item The computation time in seconds (keeping in mind that the 50 runs are done in parallel on the same, shared computer, so that this is more of a qualitative assessment.)
+\end{enumerate}
+
+Figure~\ref{fig:KLXP} has three panels. \TODO{todo todo tk tk}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
2D

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 
-\TODO{Debate this later}
-
 Autocorrelations in $d$ dimensions is defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
@@
 \end{equation}
-Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) \TODO{Do we call it the homogeneous case?} signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
 If the mean of signal is available and non-zero, the sign symmetry can be resolved.
@@
 
-This uniqueness result for multi-dimensional signals (especially for 2-D images) is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
-illuminated with a coherent wave, and the far field diffraction
-intensity pattern  is measured, corresponding object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
-If the support of the object is known and less than half of the support of the measured signal, then the data is equivalent to the second-order autocorrelation.
-The computational problem of recovering the signal is usually referred to as \emph{phase retrieval} or \emph{phase problem}.
-Despite the uniqueness result, recently it has been shown that, at least for 2-D images, the problem is  ill-conditioned~\cite{barnett2018geometry}.
-That is, there exist different images whose second-order autocorrelation agree up to machine precision.
+This uniqueness result for two and three-dimensional signals is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
+illuminated with a coherent wave, and the far field diffraction pattern  is measured, corresponding to the object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
+If the diffraction pattern is over-sampled by at least  twice the Nyquist frequency,  the data is equivalent to the signal's second-order autocorrelation.
+In this context, the computational problem of recovering the signal from its second-order autocorrelation is usually referred to as \emph{phase retrieval} or the \emph{phase problem}.
+Despite the uniqueness result, recently it has been shown that, the problem is  ill-conditioned, at least for 2-D images~\cite{barnett2018geometry}.
+That is, there exist different images whose second-order autocorrelations agree up to machine precision.
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Finished good draft of explanation XP 2

--- 2019-02-26 inverse_problems/inverse_problems.tex
@@
 In order to do so, we consider a setup where the mixed autocorrelations are known perfectly.
-This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$, and known $\sigma$ which would allow to remove noise bias.
+This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$.
+The value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
 Furthermore, we assume uniform occurrence distribution $\pi$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
@@
 The perfect mixed autocorrelations are computed.
-They are then provided to the algorithm described in Section~\ref{sec:XP1}, together with the knowledge that signals occur with equal probability, as well as the correct density $\gamma$.
+They are then provided to the inversion algorithm described in Section~\ref{sec:XP1}, together with the knowledge that signals occur with equal probability, as well as the correct density $\gamma$.
 The algorithm is initialized 50 times with an independent random initial guess, also following a normal distribution.
@@
 \end{enumerate}
-
-Figure~\ref{fig:KLXP} has three panels. \TODO{todo todo tk tk}
+These metrics are summarized and presented in Figure~\ref{fig:KLXP} as three panels.
+\begin{enumerate}
+	\item Panel 1 shows for each pair $(K, L)$ which fraction of the 50 runs reached optimality (between 0 and 1).
+	\item For each pair $(K, L)$, any estimator produced by the optimization algorithm such that the cost function value is close to zero must be considered a valid estimator, since it agrees almost perfectly with the data.
+For all of those, we compute the error compared to the ground truth.
+Panel 2 shows the largest such error, on a log scale in base 10.
+(If optimization never succeeded for that pair, we report a relative error of 1.) A large value means that, among all near global optima of the optimization problem (if any), at least one was a poor estimator.
+A small value indicates all computed near global optima were good estimators.
+	\item Median $\log_{10}$ computation time (where the median is computed after taking the log of the CPU times, in base 10.)
+\end{enumerate}
+
+Following~\cite{boumal2017heterogeneous}, overlaid on the panels we trace the red curve $K = \sqrt{L}$ as well as red dots which are computed from the considerations in Section~\ref{sec:heterogeneity} (adapted to the fact that $\pi$ and $\gamma$ are known).
+We observe that strictly above the red dots the optimization problem appears to be easy to solve (despite non-convexity), yet, as predicted, the corresponding estimators are not informative since there is not enough information in the computed quantities compared to the number of parameters.
+On the other hand, below the (empirical) red curve, the optimization problem is sometimes solved to optimality (although it may take more than one random initialization to get one successful run), and the corresponding estimators are accurate.
+In between the red curve and the red dots, the optimization problem appears to be particularly challenging: we essentially never produce a global optimum, hence we also do not have an estimator.
+This experiment suggests a possible computational-statistical gap in the area between the red curve and the red dots, where it is possible that the signals could be estimated, but perhaps not with a computationally efficient procedure.
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Some edits to XP3 + startign to edit Section 6 (proofs)

@@
 
-Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimated 
-an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations.
-Each observation is  of size $4096\times 4096$ pixels and contains 700 occurrences on average  at random locations, while maintaining the separation condition~\eqref{eq:spacing}.
-The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$, illustrated in Figure~\ref{fig:micro_example}. 
+Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimate 
+a 50-by-50 pixel grayscale picture of Einstein with mean zero from a growing number of observations $y$.
+Each observation is of size $4096\times 4096$ pixels and contains 700 occurrences on average at random locations, while maintaining the separation condition adapted in the obvious way to 2D signals.
+The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma = 3$, illustrated in Figure~\ref{fig:micro_example}. 
  % corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$. 
@@
 
-We compute the average second-order autocorrelation of the observations. This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT) in parallel.  
-To  keep things simple, we assume the number of signal occurrences and the noise standard deviation are known. 
+We compute the average second-order autocorrelation of the observations.
+This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT), in parallel over the numerous observations.
+To  keep things simple, we assume the number of signal occurrences (akin to the density $\gamma$) and the standard deviation of the noise, $\sigma$, are known.
 Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
-As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
-Then, to estimate the target image, we employed a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
+\TODO{As explained in Section~\ref{sec:high_dimensions}---careful if we decide to edit}, an image is determined uniquely form its second-order autocorrelations.
+Then, to estimate the target image, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
 
@@
 Each observation contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is very challenging to detect  the planted image.} %In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
+In panel (c), the noise level is such that it is challenging to detect  the planted images.} %In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
 }
@@
 
-Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities). \TODO{The probably appeared before}
+Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
 Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of observations.
-Figure~\ref{fig:error_per_micro} 
-presents the normalized recovery error as a function of the amount of data available.  This is computed after fixing the reflection symmetries (see Section~\ref{sec:high_dimensions}).
-
-% As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many micrographs, without particle picking.
+Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
+This is computed after fixing the reflection symmetries (see Section~\ref{sec:high_dimensions}).
+
+As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many observations, without the need to locate the signal occurrences.
 
@@
 Averaged autocorrelations of the data allow to estimate the power spectrum of the target image.
-This does not require particle picking.
-The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ observations (growing across panels from left to right).}
+This does not require locating the signal occurrences.
+The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4$ and $2\times 10^5$ observations (growing across panels from left to right).}
 	%	\vspace{-8pt} 
@@
 	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
-	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}.}
+	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}. Each observation contains about 700 image occurrences at unknown locations.}
 \end{figure}
 
-\section{Proof}
-
-\subsection{Derivation of the identities in Section~\ref{sec:AC_analysis}} \label{sec:autocorrelation_computation}
+\section{Proofs}
+
+Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.
+
+\subsection{Autocorrelations in the well-separated model} \label{sec:autocorrelation_computation}
 

### 2019-02-26 inverse_problems/inverse_problems.tex
Re-arranged Section 6, in particular some titles

@@
 
+\subsection{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
+
+\TODO{Needs a complete rewrite to match the paper, in particular the modified notation and the fact we only work with autocorrelations now (not models).}
+
+\subsubsection{First moment}
+
+To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
+%
+\begin{align}
+%
+\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
+= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
+= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
+%
+\end{align}
+%
+Now taking expectations over $M$ we see:
+%
+\begin{align}
+%
+\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
+%
+\end{align}
+
+%
+
+\subsubsection{Second moment}
+
+Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%
+\begin{align}
+%
+Y_{i_1} Y_{i_2} 
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
+%
+\end{align}
+
+We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+In the first case, all the terms are independent, and so the expectation factors.
+In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
+This gives (all expectations are conditional on $M$):
+%
+\begin{align} \label{moment2-condm}
+%
+\E Y_{i_1} Y_{i_2}
+=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
+\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+%
+\end{align}
+%
+Now take expectations over the Poisson random variables, using this fact:
+%
+\begin{lem} \label{lem-choose}
+	If $M \sim \Poisson(\gamma)$, then 
+	\begin{align}
+	%
+	\E {M\choose k} = \frac{\gamma^k}{k!}.
+	%
+	\end{align}
+\end{lem}
+
+We get (now the expectation is over $M$ and $X$):
+%
+\begin{align}
+%
+\E Y_{i_1} Y_{i_2} 
+=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
++ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
+\nonumber \\
+=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
+%
+\end{align}
+
+But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+
+%
+
+\subsubsection{Third moment}
+
+For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%
+\begin{align}
+%
+&Y_{i_1} Y_{i_2} Y_{i_3}
+\nonumber \\
+&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
+\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
+X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
+\end{align}
+%
+We will break up the outer three sums into disjoint sums with the following ranges of indices:
+%
+\begin{enumerate}
+
+	\item \label{case1}
+	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case2}
+	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case3}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+
+	\item \label{case4}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+
+	\item \label{case5}
+	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+
+\end{enumerate}
+
+For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%
+\begin{align}
+%
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
+X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+\nonumber \\
+=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(a)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(b)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(c)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(d)}}
+\nonumber \\
+&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
+	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+}_{\text{(e)}}.
+%
+\end{align}
+
+For term (a), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+%
+\end{align}
+%
+Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
+%
+\begin{align} \label{aaaa}
+%
+\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+For term (b), the expectation conditional on $M$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+%
+\end{align}
+%
+and then again using Lemma \ref{lem-choose} we get the expected value:
+%
+\begin{align} \label{bbbb}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+Similarly, the expected values of terms (c) and (d) are:
+%
+\begin{align} \label{cccc}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+%
+\end{align}
+%
+and
+%
+\begin{align} \label{dddd}
+%
+\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+%
+\end{align}
+
+Finally, the expected value of term (e) is easily shown to be:
+%
+\begin{align} \label{eeee}
+%
+\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+%
+\end{align}
+%
+This concludes the computation for Case \ref{case1}.
+
+Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+\Bigg\{
+\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
+X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
+\nonumber \\
+&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
+%
+\end{align}
+%
+Taking expectations conditional on $M$, we then get:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\nonumber \\
+&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\label{ffff} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
+\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+\label{gggg}
+%
+\end{align}
+
+Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
+\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+\label{hhhh} \\
+& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
+\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+\label{iiii}
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
+\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+\label{jjjj}\\
+& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
+\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+\label{kkkk}
+%
+\end{align}
+
+Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
+Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%
+\end{align}
+%
+since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
+%
+\begin{align} \label{llll}
+%
+\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+%
+\end{align}
+
+Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
+%
+\begin{align}
+%
+(\gamma \L_1)^3.
+%
+\end{align}
+
+Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
+%
+\begin{align}
+%
+\gamma \L_1  \cdot 
+( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
+%
+\end{align}
+%
+Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
+%
+\begin{align}
+%
+\gamma \L_3(\Delta_1,\Delta_2)
+%
+\end{align}
+%
+which is the usual third-order auto-correlation.
+
 \subsection{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
@@
 
-\subsection{Proof of Proposition~\ref{prop:poisson}} \label{sec:proof_prop_poisson}
-
-\subsubsection{First moment}
-
-To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
-%
-\begin{align}
-%
-\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
-= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
-= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
-%
-\end{align}
-%
-Now taking expectations over $M$ we see:
-%
-\begin{align}
-%
-\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
-%
-\end{align}
-
-%
-
-\subsubsection{Second moment}
-
-Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
-%
-\begin{align}
-%
-Y_{i_1} Y_{i_2} 
-&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
-X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
-%
-\end{align}
-
-We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
-In the first case, all the terms are independent, and so the expectation factors.
-In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
-This gives (all expectations are conditional on $M$):
-%
-\begin{align} \label{moment2-condm}
-%
-\E Y_{i_1} Y_{i_2}
-=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
-\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
-%
-\end{align}
-%
-Now take expectations over the Poisson random variables, using this fact:
-%
-\begin{lem} \label{lem-choose}
-	If $M \sim \Poisson(\gamma)$, then 
-	\begin{align}
-	%
-	\E {M\choose k} = \frac{\gamma^k}{k!}.
-	%
-	\end{align}
-\end{lem}
-
-We get (now the expectation is over $M$ and $X$):
-%
-\begin{align}
-%
-\E Y_{i_1} Y_{i_2} 
-=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
-+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
-\nonumber \\
-=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
-%
-\end{align}
-
-But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
-
-%
-
-\subsubsection{Third moment}
-
-For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
-%
-\begin{align}
-%
-&Y_{i_1} Y_{i_2} Y_{i_3}
-\nonumber \\
-&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
-X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
-\end{align}
-%
-We will break up the outer three sums into disjoint sums with the following ranges of indices:
-%
-\begin{enumerate}
-
-	\item \label{case1}
-	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
-
-	\item \label{case2}
-	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
-
-	\item \label{case3}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
-
-	\item \label{case4}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
-
-	\item \label{case5}
-	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
-
-\end{enumerate}
-
-For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
-%
-\begin{align}
-%
-&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
-X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-\nonumber \\
-=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-}_{\text{(a)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-}_{\text{(b)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-}_{\text{(c)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-}_{\text{(d)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
-}_{\text{(e)}}.
-%
-\end{align}
-
-For term (a), the expectation conditional on $M$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
-%
-\end{align}
-%
-Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
-%
-\begin{align} \label{aaaa}
-%
-\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
-%
-\end{align}
-
-For term (b), the expectation conditional on $M$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
-%
-\end{align}
-%
-and then again using Lemma \ref{lem-choose} we get the expected value:
-%
-\begin{align} \label{bbbb}
-%
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
-%
-\end{align}
-
-Similarly, the expected values of terms (c) and (d) are:
-%
-\begin{align} \label{cccc}
-%
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
-%
-\end{align}
-%
-and
-%
-\begin{align} \label{dddd}
-%
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
-%
-\end{align}
-
-Finally, the expected value of term (e) is easily shown to be:
-%
-\begin{align} \label{eeee}
-%
-\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
-%
-\end{align}
-%
-This concludes the computation for Case \ref{case1}.
-
-Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
-%
-\begin{align}
-%
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
-\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
-\nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
-\Bigg\{
-\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
-\nonumber \\
-&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
-X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
-%
-\end{align}
-%
-Taking expectations conditional on $M$, we then get:
-%
-\begin{align}
-%
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-\nonumber \\
-&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
-%
-\end{align}
-
-Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
-%
-\begin{align}
-%
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-\label{ffff} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
-\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
-\label{gggg}
-%
-\end{align}
-
-Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
-%
-\begin{align}
-%
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
-\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
-\label{hhhh} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
-\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
-\label{iiii}
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
-\label{jjjj}\\
-& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
-\label{kkkk}
-%
-\end{align}
-
-Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
-Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
-%
-\begin{align}
-%
-\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
-%
-\end{align}
-%
-since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
-%
-\begin{align} \label{llll}
-%
-\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
-%
-\end{align}
-
-Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
-%
-\begin{align}
-%
-(\gamma \L_1)^3.
-%
-\end{align}
-
-Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
-%
-\begin{align}
-%
-\gamma \L_1  \cdot 
-( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
-%
-\end{align}
-%
-Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
-%
-\begin{align}
-%
-\gamma \L_3(\Delta_1,\Delta_2)
-%
-\end{align}
-%
-which is the usual third-order auto-correlation.
-
 %

### 2019-02-27 inverse_problems/inverse_problems.tex
section 1 - minor revision

@@
 Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
-This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper. In this setting, we consider  $s_1,\ldots,s_K$  as \emph{nuisance variables}.
+This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper. In this setting, we refer to  $s_1,\ldots,s_K$  as \emph{nuisance variables}.
 
 In order to recover the signals in the high noise regime, we use autocorrelation analysis.
-For any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for large enough $N$. 
+In any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for large enough $N$. 
 This computation is straightforward and requires only one pass over the data.

### 2019-02-27 inverse_problems/inverse_problems.tex
section 2  - part 1

@@
 \section{Motivation: single-particle reconstruction using cryo-electron microscopy}
-Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules; see for instance~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
+Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
 In contrast X-ray and NMR which aggregate information from an ensembles of
-particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures.
-In addition, it does not require the formation of crystalline arrays of macromolecules.
-
-In a cryo--EM experiment, biological samples are rapidly frozen in a thin layer of vitreous ice.
+particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures simultaneously.
+%In addition, it does not require the formation of crystalline arrays of macromolecules.
+
+In a cryo--EM experiment, biological samples (e.g., macromolecules, viruses) are rapidly frozen in a thin layer of vitreous ice.
 The microscope produces 2-D tomographic images of the samples embedded in the ice, called \emph{micrographs}.
-Each micrograph contains tomographic projections of the samples at unknown locations and under unknown viewing directions.
+Each micrograph contains multiple tomographic projections of the samples at unknown locations and under unknown viewing directions.
+Importantly, the electron dose must be kept low to mitigate  radiation damage, leading to high noise levels.
 The goal is to construct 3-D models of the molecular structures from the micrographs.
-Importantly, to keep radiation damage within acceptable bounds, the dose must be kept low, leading to high noise levels.
 

### 2019-02-27 inverse_problems/inverse_problems.tex
cryo-EM model

@@
 
-\section{Introduction}
-
-%\subsection{Problem formulation} \label{sec:problem_formulation}
+\section{Introduction} \label{sec:intro}
 
@@
 
-A 2-D micrograph $y$ can be in terms of~\eqref{eq:model} where the discrete signals $x_1,\ldots,x_K$ are replaced by a random signal drawn from the a general distribution.
-In particular, in each position $s[i]$, a 2-D tomographic projection of the 3-D structure is placed, taken from a random viewing direction according to (possibly unknown) fixed distribution.
+A 2-D micrograph $y$ can be written in terms 
+of the models described in Section~\ref{sec:intro} as
+\begin{equation}  \label{eq:model_cryo}
+y  =   s \ast x + \varepsilon,
+\end{equation}
+where tomographic projections are placed according to the signal $s$.
+In this model, the signal $x$ represents the 2-D tomographic projections of the 3-D structure taken from  random viewing directions according to (possibly unknown) distribution.
+In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation drawn from some unknown distribution and $P$ a tomographic projection, we have
+\begin{equation}
+x= P(R_\omega V).
+\end{equation}
+By allowing $V$ to be a random signal as well, this model can encode a mixture of structures  
+(which might be continuous as well).
 

### 2019-02-27 inverse_problems/inverse_problems.tex
section 2

@@
 All contemporary methods in the field split the reconstruction procedure into two main  stages.
-The first stage consists of estimating the signal $s$---that is, extracting the particle projections from the micrographs.
-This stage is called \emph{particle picking}.
-Given the projections, the second stage aims to construct a 3-D model of the molecular structure.
+The first stage, called \emph{particle picking},  extracts the particle projections from the micrographs.
+Given the projections, the second stage aims to construct a 3-D model of the molecular structure, usually using a  expectation-maximization algorithm~\cite{scheres2012relion}.
 %The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
@@
 
-Another potential pitfall of particle picking pertains to \emph{model bias}, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+Another potential pitfall of particle picking is related  to \emph{model bias}, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
-In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
+It was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template~\cite{shatsky2009method}.
 In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles biases the reconstructed structure.
-This model bias is common to all particle picking methods based on template matching.
+%This model bias is common to all particle picking methods based on template matching.
 %In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
@@
 A recent work of the authors suggests to bypass the particle picking stage and  reconstruct the 3-D structure directly from the micrograph~\cite{bendory2018toward}.
-In that paper, it was shown that---at least in principle---the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-The principle mathematical tool is  \emph{autocorrelation analysis}, described in detail in Section~\ref{sec:AC_analysis}.
+Based on autocorrelation analysis it was shown that---at least in principle---the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
+%The principle mathematical tool is  \emph{autocorrelation analysis}, described in detail in Section~\ref{sec:AC_analysis}.
 This goal of  the current paper is to provide a theoretical justification and numerical support  for the method proposed in~\cite{bendory2018toward}.  
 %In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the random signal $X$ discussed in Section~\ref{sec:extensions} can be thought of as 2-D random tomographic projections of the 3-D structure
-taken according to some unknown distribution of the particles within the ice.
+%taken according to some unknown distribution of the particles within the ice.
 
@@
 
-We mention that~\cite{bendory2018toward} was not the first paper to employ autocorrelation analysis to cryo-EM. 
-Zvi Kam~\cite{kam1980reconstruction} first proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of perfect particle picking: his method used autocorrelations of the picked, perfectly centered, particles.
-Kam's method has been extended and employed by in X-ray free electron lasers and cryo-EM; see for instance~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
+%We mention that~\cite{bendory2018toward} was not the first paper to employ autocorrelation analysis to cryo-EM. 
+Autocorrelation analysis for cryo-EM traces back to the seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
+This paper proposed autocorrelation analysis for {3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
+Kam's method has been extended and employed in X-ray free electron lasers and cryo-EM~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
 In order to investigate the computational and statistical properties of Kam's method, a series of papers have studied a simplified model, 
@@
 We follows the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
+\TODO{Not sure about the location of the last paragraph.}
 

### 2019-02-27 inverse_problems/inverse_problems.tex
abstract

@@
 \begin{abstract}
-abstract
-%Single-particle cryo-electron microscopy (cryo-EM) has recently joined X-ray crystallography
-%and NMR spectroscopy as a high-resolution structural method for biological macromolecules.
-%In a cryo-EM experiment, the microscope produces images called micrographs.
-Projections of the molecule of interest are embedded in the micrographs at unknown locations, and under unknown viewing directions.
-Standard imaging techniques first locate these projections (detection) and then reconstruct the 3-D structure from them.
-Unfortunately, high noise levels hinder detection.
-When reliable detection is rendered impossible, the standard techniques fail.
-This is a problem especially for small molecules, which can be particularly hard to detect.
-In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection.
-%As a result, even small molecules should be within reach for cryo-EM.
-To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation analysis technique allows to go directly from the micrographs to the sought signals.
-This involves only one pass over the micrographs, which is desirable for large experiments.
-%We show numerical results and  discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
+
+We consider the multi-target detection problem of recovering a set of signals that appear 
+multiple times at unknown locations in a noisy measurement.
+We derive simple relations between the autocorrelations of the observations and those of the signals.
+These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement.
+To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
+This is of particular importance in high noise regimes in which detecting individual signal appearance is impossible.
+We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.
+
+The main goal of this work is to supply theoretical and numerical support for the possibility of estimating the 3-D structure of single particles using cryo-electron microscopy without detection~\cite{bendory2018toward}.
+
 \end{abstract}

### 2019-02-27 inverse_problems/inverse_problems.tex
edits on section 5

@@
 
-%The technique we advocate allows recovery of signals hidden in noisy observations without detecting the location  of the signals embedded in the observation.
-To illustrate the underlying principles of the method, we present several numerical examples.
-The code to generate all figures is publicly available in \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
-
-%\paragraph{Numerical experiment with three 1-D signals.}
-
 In this section, we present three numerical experiments.
@@
 Second, we explore how many signals can be recovered as a function of their length, in an infinite data regime where effects of the noise have been averaged out.
-In the last experiment, we extend our model to 2D signals.
-
-\subsection{Experiment 1} \label{sec:XP1}
+In the last experiment, we extend our model to 2-D signals.
+
+\subsection{Experiment 1} 
+\label{sec:XP1}
 
@@
 Following~\eqref{eq:model}, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals (well separated).
+Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals according to~\eqref{eq:spacing}.
 This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
@@
 Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can of course be handled in parallel.
+If multiple GPUs are available, segments can  be handled in parallel.
 
@@
 \end{multline}
-where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of moments used: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
+where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of coefficients used for each autocorrelation order: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
 
@@
 Furthermore, as illustrated here and as we have observed in numerous experiments, signals with more variations (such as the third signal in this experiment which was generated once from a Gaussian distribution) are easier to estimate accurately than more regular signals (in this case, despite the fact that the third signal occurs less frequently than the others).
+This phenomenon has been also observed in multi-reference alignment~\cite[Section 3.2]{perry2017sample}.
 
@@
 
-In this second experiment, presented in Figure~\ref{fig:KLXP}, we investigate how many distinct signals $x_1, \ldots, x_K$ can be estimated from mixed autocorrelations~\eqref{eq:mixedautocorr}.
+In this second experiment, presented in Figure~\ref{fig:KLXP}, we investigate how many distinct signals ${x_1, \ldots, x_K}$ can be estimated from mixed autocorrelations~\eqref{eq:mixedautocorr}.
 In order to do so, we consider a setup where the mixed autocorrelations are known perfectly.
-This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$.
-The value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
+This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$ and fixed noise level (that may be arbitrarily high).
+The specific value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
 Furthermore, we assume uniform occurrence distribution $\pi$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
@@
 This experiment suggests a possible computational-statistical gap in the area between the red curve and the red dots, where it is possible that the signals could be estimated, but perhaps not with a computationally efficient procedure.
+Similar results were observed for the multi-reference problem~\cite{boumal2017heterogeneous,weinthesis,bandeira2017estimation}.
 
@@
 a 50-by-50 pixel grayscale picture of Einstein with mean zero from a growing number of observations $y$.
-Each observation is of size $4096\times 4096$ pixels and contains 700 occurrences on average at random locations, while maintaining the separation condition adapted in the obvious way to 2D signals.
+Each observation is of size $4096\times 4096$ pixels and contains 700 occurrences on average at random locations, while maintaining the separation condition~\eqref{eq:spacing} in each axis separately.
 The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma = 3$, illustrated in Figure~\ref{fig:micro_example}. 

### 2019-02-27 inverse_problems/inverse_problems.tex
no message

@@
 	%
-	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. \TODO{Definitely only clear for the homogeneous case}
+	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. 
 \end{proposition}
@@
 	\includegraphics[width=.7\linewidth]{KLXP/XP1}
-	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
+	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
 CPU time in seconds.

### 2019-02-28 inverse_problems/inverse_problems.tex
Section 3.2 (Will)

@@
 \subsection{Autocorrelations under the Poisson model}
+
+In this section, we give the expressions for the autocorrelations of the observed signal $y$ under the Poisson model.
+In this model, each location $k$, $1 \le k \le N-L+1$, contains a Poisson-distributed number of random signals.
+More precisely, lettin $M_k$ be the number of signals starting at location $k$, $M_k \overset{iid}{\sim} \Poisson(\gamma / L)$.
+Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
+%
+\begin{align}
+\frac{N - L + 1}{N} \cdot L \cdot \frac{\gamma  }{L} 
+\quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
+\end{align}
+%
+Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model.
+
+We will show the following expressions for the autocorrelations of $y$, expressed in terms of the autocorrelations of $x$ and the parameters $\gamma$ and $\sigma$:
+%
+\begin{align}
+a_y^1  = & \gamma a_{x}^1, 
+\label{eq:mean_micrograph2} \\
+a_y^2[\ell] = & (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
+\label{eq:ac2_micrograph2} \\
+a_y^3[\ell_1,\ell_2] = & (\gamma a_x^1)^3 + \gamma a_x^1  
+\cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2]
++ \gamma a_x^2[\ell_2-\ell_1]) + \gamma a_x^3[\ell_1,\ell_2] 
+\nonumber \\
+& + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
+\label{eq:ac3_micrograph2}
+\end{align}
+
+From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+%
+\begin{align}
+\gamma a_x^3[\ell_1,\ell_2]
+= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
+- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
++ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
+\end{align}
+
+It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
+%
+\begin{align}
+(\gamma a_x^1) (\gamma a_x^2[1])
+&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
+\left(\sum_{j=0}^{L-1} x[j]x[j+1] \right)
+\nonumber \\
+&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
+\nonumber \\
+&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
++ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
+\end{align}
+%
+Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$:
+%
+\begin{align}
+\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
+{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
+	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
+\end{align}
+%
+With $\gamma$ in hand, we can estimate $\sigma^2$:
+%
+\begin{align}
+\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+- (2 L - 1) (a_y^1)^2.
+\end{align}
 

### 2019-02-28 inverse_problems/inverse_problems.tex
./

@@
 In this section, we give the expressions for the autocorrelations of the observed signal $y$ under the Poisson model.
-In this model, each location $k$, $1 \le k \le N-L+1$, contains a Poisson-distributed number of random signals.
-More precisely, lettin $M_k$ be the number of signals starting at location $k$, $M_k \overset{iid}{\sim} \Poisson(\gamma / L)$.
+In this model, each location $k$, $1 \le k \le N-L+1$ is the starting point of a Poisson-distributed number of random signals.
+More precisely, letting $s[k]$ be the number of signals starting at location $k$, $s[k] \overset{iid}{\sim} \Poisson(\gamma / L)$.
 Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
@@
 \begin{align}
-a_y^1  = & \gamma a_{x}^1, 
+a_y^1  &=  \gamma a_{x}^1, 
 \label{eq:mean_micrograph2} \\
-a_y^2[\ell] = & (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
+a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
 \label{eq:ac2_micrograph2} \\
-a_y^3[\ell_1,\ell_2] = & (\gamma a_x^1)^3 + \gamma a_x^1  
+a_y^3[\ell_1,\ell_2]  & = (\gamma a_x^1)^3 + \gamma a_x^1  
 \cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2]
@@
 
+\TODO{Does the equivalence hold for $\ell\neq 0$?}
+\begin{corollary}
+	The autocorrelations are equivalent...
+\end{corollary}
+
 It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
@@
 &=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
-\left(\sum_{j=0}^{L-1} x[j]x[j+1] \right)
-\nonumber \\
-&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
+\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
+\nonumber \\
+&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
 \nonumber \\
@@
 %
-Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$:
-%
+Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$:
+
 \begin{align}
@@
 \end{align}
-%
-With $\gamma$ in hand, we can estimate $\sigma^2$:
+%With $\gamma$ in hand, we can estimate $\sigma^2$:
 %
@@
 \end{comment}
-
-\TODO{What we want to have in this section}
-\begin{enumerate}
-	\item Recall the Poisson model (it's already described at the end of intro, so keep it short).
-	\item Define a proper notion of $\gamma$ (careful with scaling $L$).
-	\item State formulas for $a_y^q$ with $q = 1, 2, 3$ (ideally, including noise terms) to parallel what we did in the well-separated section.
+%
+%\TODO{What we want to have in this section}
+%\begin{enumerate}
+%	\item Recall the Poisson model (it's already described at the end of intro, so keep it short).
+%	\item Define a proper notion of $\gamma$ (careful with scaling $L$).
+%	\item State formulas for $a_y^q$ with $q = 1, 2, 3$ (ideally, including noise terms) to parallel what we did in the well-separated section.
 It would be better to do everything with autocorrelations rather than moments to keep the story uniform.
-	\item (optional) Claim: under some assumptions (knowing $\gamma$?
+%	\item (optional) Claim: under some assumptions (knowing $\gamma$?
 Others?), the autocorrelations of $y$ of order $q = 1, 2, 3$ under the Poisson model provide the same information about $x$ as the corresponding autocorrelations under the well-separated model.
 Could also be in Section 4.1.
-\end{enumerate}
+%\end{enumerate}
+%
 

### 2019-02-28 inverse_problems/inverse_problems.tex
.

@@
 
-%Our approach is based on considering the first few entries of the observation's autocorrelations. These entries correspond to products of $y$ with its shifted version, for some small shifts.
-%If $s$ would be too clustered, then
-
+\TODO{The models are not equivalent but related through Corollary~\ref{cor:ac_equivalence}.}
 As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
@@
 
-\TODO{Does the equivalence hold for $\ell\neq 0$?}
-\begin{corollary}
-	The autocorrelations are equivalent...
+\begin{corollary}[informal for now] \label{cor:ac_equivalence}
+The first and the second autocorrelations  in the well-separated and the Poisson models are equivalent. 
+If $\sigma$ is known, then it is also true for the third-order autocorrelation. If $\sigma$ is unknown, the it is true whenever $\ell_1\neq 0$, $\ell_2\neq 0$ and $\ell_1\neq \ell_2$. 
 \end{corollary}
@@
 	\TODO{Can we do this simultaneously for Poisson? or do we only need to do it for well-separated and invoke the equivalence claim? Not if that claim requires knowledge of $\gamma, \sigma$.}
-	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
+	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  \TODO{Should remove the limit}
 	\begin{equation}

### 2019-03-01 inverse_problems/inverse_problems.tex
./

--- 2019-02-28 inverse_problems/inverse_problems.tex
@@
 
-%Our approach is based on considering the first few entries of the observation's autocorrelations. These entries correspond to products of $y$ with its shifted version, for some small shifts.
-%If $s$ would be too clustered, then
-
 As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
@@
 In particular, this model allows for (additive) signal overlap.
-In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
+%In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
 
@@
 In the remainder of this section, we relate the observables $a_y^q$  to the unknowns $a_x^q$, first under the well-separated model, then under the Poisson model.
-\TODO{Explicit expressions of the autocorrelations for cryo-EM are given in~\cite{bendory2018toward}}
+\TODO{Explicit expressions of the autocorrelations for cryo-EM are given in~\cite{bendory2018toward}.}
 
@@
 \nonumber \\
-& + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
+& \qquad + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
 \label{eq:ac3_micrograph2}
@@
 
-From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+%
+%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
 Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
-%
-\begin{align}
-\gamma a_x^3[\ell_1,\ell_2]
-= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
-- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
-+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
-\end{align}
-
-\TODO{Does the equivalence hold for $\ell\neq 0$?}
-\begin{corollary}
-	The autocorrelations are equivalent...
-\end{corollary}
-
-It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
-%
-\begin{align}
-(\gamma a_x^1) (\gamma a_x^2[1])
-&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
-\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
-\nonumber \\
-&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
-\nonumber \\
-&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
-+ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
-\end{align}
-%
-Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$:
-
-\begin{align}
-\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
-{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
-	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
-\end{align}
-%With $\gamma$ in hand, we can estimate $\sigma^2$:
-%
-\begin{align}
-\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-- (2 L - 1) (a_y^1)^2.
-\end{align}
-
+%%
+%\begin{align}
+%\gamma a_x^3[\ell_1,\ell_2]
+%= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
+%- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
+%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
+%\end{align}
+
+%\begin{corollary}[informal for now] \label{cor:ac_equivalence}
+%The first and the second autocorrelations  in the well-separated and the Poisson models are equivalent. 
+%If $\sigma$ is known, then it is also true for the third-order autocorrelation. If $\sigma$ is unknown, the it is true whenever $\ell_1\neq 0$, $\ell_2\neq 0$ and $\ell_1\neq \ell_2$. 
+%\end{corollary}
+%
+%It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
+%%
+%\begin{align}
+%(\gamma a_x^1) (\gamma a_x^2[1])
+%&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
+%\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
+%\nonumber \\
+%&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
+%\nonumber \\
+%&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
+%+ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
+%\end{align}
+%%
+%Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$: 
+%
+%\begin{align}
+%\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
+%{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
+%	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
+%\end{align}
+%%With $\gamma$ in hand, we can estimate $\sigma^2$:
+%%
+%\begin{align}
+%\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+%- (2 L - 1) (a_y^1)^2.
+%\end{align}
+%
 \begin{comment}
@@
 \begin{proposition} \label{prop:gamma}
-	\TODO{Can we do this simultaneously for Poisson? or do we only need to do it for well-separated and invoke the equivalence claim? Not if that claim requires knowledge of $\gamma, \sigma$.}
-	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then 
+	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  \TODO{Should remove the limit}
 	\begin{equation}
@@
 
+For the Poisson model: 
+From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+%
+\begin{align}
+\gamma a_x^3[\ell_1,\ell_2]
+= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
+- a_y^1 \cdot \big(a_y^2[\ell_1]  
++ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
+\end{align}
+
+\begin{proposition}
+	Poisson result 
+\end{proposition}
+\begin{proof}
+It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
+%
+\begin{align}
+(\gamma a_x^1) (\gamma a_x^2[1])
+&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
+\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
+\nonumber \\
+&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
+\nonumber \\
+&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
++ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
+\end{align}
+%
+Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$:
+
+\begin{align}
+\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
+{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
+	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
+\end{align}
+%With $\gamma$ in hand, we can estimate $\sigma^2$:
+%
+\begin{align}
+\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+- (2 L - 1) (a_y^1)^2.
+\end{align}
+
+\end{proof}
+
 \subsection{Elemetary limitations of the heterogeneous case}
@@
 \TODO{Did we define densities $\gamma_k$?}
+\TODO{We write the section for the Poisson model, but it would be the same for the Poisson model}
 
@@
 \end{equation}
-Interestingly, for dimensions greater than one almost all deterministic (that is, the distribution of $z$ is a Delta function) \TODO{Do we call it the homogeneous case?} signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
+Interestingly, for the homogeneous case ($K=1$) in dimensions greater than one, almost all  signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
 If the mean of signal is available and non-zero, the sign symmetry can be resolved.

### 2019-03-01 inverse_problems/inverse_problems.tex
edits section 1

@@
 
-%The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
-%We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
-
-\TODO{Careful that $\gamma$ changed by a factor of $L$: need to modify here too.} Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
+Specifically, 
+ letting $s[i]$ be the number of signals starting at location $i$, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$  for some parameter $\gamma > 0$. 
+ Then, each of those $s[i]$ is chosen independently at random from a fixed distribution over $\{1,\ldots,K,\}$ and the corresponding
+signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$. 
+As in the well-separated model, the autocorrelations under this model depend only on the signals and the parameter $\gamma$.
+
+ %Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
+%
+%\begin{align}
+%\frac{N - L + 1}{N} \cdot L \cdot \frac{\gamma  }{L} 
+%\quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
+%\end{align}
+%
+%In particular, this model allows for (additive) signal overlap
+
+%Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
 For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$.
-Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$.
-By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$.
+%Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
+%By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$.
 In particular, this model allows for (additive) signal overlap.
 %In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
+
+ %More precisely,
+ %Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model.
 

### 2019-03-01 inverse_problems/inverse_problems.tex
section 3 (first part)

@@
 \end{align}
+Explicit expressions of the autocorrelations for the more involved model of  cryo-EM are given in~\cite{bendory2018toward}.
+
 We are given one observation (one realization) of $y$.
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual autocorrelations of $y$, that is, % (ergodicity)
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
 \begin{align}
@@
 \end{align}
+\TODO{Why do we need constant $\gamma$?}
 This provides a concrete means of estimating the quantities $a_y^ q$.
 In the remainder of this section, we relate the observables $a_y^q$  to the unknowns $a_x^q$, first under the well-separated model, then under the Poisson model.
-\TODO{Explicit expressions of the autocorrelations for cryo-EM are given in~\cite{bendory2018toward}.}
 

### 2019-03-01 inverse_problems/inverse_problems.tex
section 3.1

@@
 \end{equation}
-This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it the signal density.
+This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. %Henceforth, we call it the signal density.
 The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
@@
 
-\TODO{We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ from observations for the particular case where $K = 1$ (all signal occurrences are the same).}
+We show in Section~\ref{sec:theory_homogeneous} 
+that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the particular case where $K = 1$ (all signal occurrences are the same).
 

### 2019-03-01 inverse_problems/inverse_problems.tex
section 3

@@
 
-We show in Section~\ref{sec:theory_homogeneous} 
-that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the particular case where $K = 1$ (all signal occurrences are the same).
-
-%Furthermore, in Section~\ref{sec:poisson} we show that the autocorrelations under the Poisson model provide the same information about $x$ as those presented in this section.
+We show in Section~\ref{sec:theory_homogeneous_well_separated} 
+that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).
 
@@
 In this section, we give the expressions for the autocorrelations of the observed signal $y$ under the Poisson model.
-In this model, each location $k$, $1 \le k \le N-L+1$ is the starting point of a Poisson-distributed number of random signals.
-More precisely, letting $s[k]$ be the number of signals starting at location $k$, $s[k] \overset{iid}{\sim} \Poisson(\gamma / L)$.
-Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
+%In this model, each location $k$, $1 \le k \le N-L+1$ is the starting point of a Poisson-distributed number of random signals.
+%More precisely, letting $s[k]$ be the number of signals starting at location $k$, $s[k] \overset{iid}{\sim} \Poisson(\gamma / L)$.
+ We first note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
 %
@@
 
-We will show the following expressions for the autocorrelations of $y$, expressed in terms of the autocorrelations of $x$ and the parameters $\gamma$ and $\sigma$:
+In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model, expressed in terms of the autocorrelations of $x$ and the parameters $\gamma$ and $\sigma$:
 %
@@
 
+In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
 %
@@
 
-\TODO{Explain difference between homogeneous and heterogeneous}
-
-\subsection{Guarantees for the homogeneous case} \label{sec:theory_homogeneous}
-%In this section, we derive some theoretical results for the homogeneous case. \TODO{Note: I am using terms interchangeably}
-
 A signal is determined uniquely by its second- and third-order autocorrelations.
@@
 
-A couple of remarks are in order.
-First, \eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
+Note that~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
 In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-%Second, note that the second-order autocorrelation is not by itself sufficient to determine the signal uniquely. %~\cite{beinert2015ambiguities,bendory2017fourier}.
+
+\subsection{Guarantees for the homogeneous well-separated model} \label{sec:theory_homogeneous_well_separated}
 
@@
 As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
+
+\subsection{Guarantees for the homogeneous Poisson model} \label{sec:theory_homogeneous_poisson}
 

### 2019-03-01 inverse_problems/inverse_problems.tex
Section 4 (first part)

@@
 Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
-\begin{align}
-	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
-	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \label{eq:ac2_micrograph} \\
+\begin{align} \label{eq:ac_well_separated}
+	a_y^1 & = \gamma a_{x}^1, \nonumber \\
+	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \\
 	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
-	+\delta[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
+	+\delta[\ell_1-\ell_2]\big), 
 \end{align}
@@
 
-A signal is determined uniquely by its second- and third-order autocorrelations.
+A signal $z\in\RL$ is determined uniquely by its second- and third-order autocorrelations.
 Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
@@
 
-Note that~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
+Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
 In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 
+In what follows, we show that in the homogeneous case $K=1$, the signal $x$, the parameter $\gamma$ and $\sigma^2$ are identified uniquely from the first three observed autocorrelations under both the well-separated and Poisson models.
+Then, we bound the maximal number of signals that can be recovered from  those autocorrelations in the heterogeneous case, and discuss extensions to multi-dimensional signals.
+
 \subsection{Guarantees for the homogeneous well-separated model} \label{sec:theory_homogeneous_well_separated}
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ of $y$ do not immediately yield the moments of the signal $x$, as seen by~\eqref{eq:mean_micrograph},~\eqref{eq:ac2_micrograph} and~\eqref{eq:ac3_micrograph}; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model~\eqref{eq:ac_well_separated} do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
 We will show, however, that $x$ is still determined by the observed moments of $y$.
@@
 First, we observe that if the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
-The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
+The proof is provided in Section~\ref{sec:proof_prop_gamma}.
 
@@
 \begin{align}
-\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
+\gamma &= L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
 {\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
@@
 \begin{align}
-\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+\sigma^2 &= a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
 - (2 L - 1) (a_y^1)^2.

### 2019-03-03 inverse_problems/inverse_problems.tex
plugging Will's notes (no editing yet)

@@
 
-\begin{proposition}
+The proof is provided in Section~\ref{sec:proof_uniqueness_poisson}.
+\begin{proposition} \label{prop:uniqueness_poisson}
 	Poisson result 
 \end{proposition}
-\begin{proof}
-It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
-%
-\begin{align}
-(\gamma a_x^1) (\gamma a_x^2[1])
-&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
-\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
-\nonumber \\
-&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
-\nonumber \\
-&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
-+ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
-\end{align}
-%
-Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$:
-
-\begin{align}
-\gamma &= L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
-{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
-	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
-\end{align}
-%With $\gamma$ in hand, we can estimate $\sigma^2$:
-%
-\begin{align}
-\sigma^2 &= a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-- (2 L - 1) (a_y^1)^2.
-\end{align}
-
-\end{proof}
 
@@
 
-\TODO{Needs a complete rewrite to match the paper, in particular the modified notation and the fact we only work with autocorrelations now (not models).}
-
-\subsubsection{First moment}
-
-To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
-%
-\begin{align}
-%
-\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
-= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
-= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
-%
-\end{align}
-%
-Now taking expectations over $M$ we see:
-%
-\begin{align}
-%
-\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
-%
-\end{align}
-
-%
-
-\subsubsection{Second moment}
-
-Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
-%
-\begin{align}
-%
-Y_{i_1} Y_{i_2} 
+Throughout this section, we will use the capital letter $X$ to represent the random unobserved vector of length $L$, the capital letter $Y$ to represent the random observed vector of length $N$, and the capital letter $S$ to represent the unobserved vector of occurrences.
+
+We will denote by $\M_l$ the moment tensors of $X$:
+%
+\begin{align}
+%
+\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+We obtain the autocorrelations $a_x^l$ of $x$ by averaging over a slice of the moment tensors:
+%
+\begin{align}
+%
+a_x^1 = \frac{1}{L}\sum_{i=0}^{L-1} \M_1[i],
+%
+\end{align}
+%
+\begin{align}
+%
+a_x^2[\Delta] = \frac{1}{L} \sum_{i=0}^{L-1} \M_2[i,i+\Delta],
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+a_x^3[\Delta_1,\Delta_2] = \frac{1}{L}\sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2].
+%
+\end{align}
+
+We will make repeated use of the following elementary lemma:
+%
+\begin{lem} \label{lem-choose}
+	%
+	If $M \sim \Poisson(\lambda)$, then 
+	\begin{align}
+	%
+	\E {M\choose k} = \frac{\lambda^k}{k!}.
+	%
+	\end{align}
+\end{lem}
+
+%
+
+\subsubsection{Computing $a_y^1$}
+
+We will first condition on the vector $s$ of locations of the subsignals in $y$, and then average over $s$.
+We will denote by $X_1^{i},\dots,X_{S[i]}^i$ the random vectors with position 0 located at $i$.
+We have:
+%
+\begin{align}
+%
+\E[ Y[i] | S ] = \sum_{j=0}^{L-1} \sum_{k=1}^{S[i-j]} \E X_k^{i-j}[j]
+= \sum_{k=1}^{S[i-j]} L a_x^1
+= S[i-j] L a_x^1.
+%
+\end{align}
+%
+Now taking expectations over $s$ and using $\E S[i-j] = \gamma/L$ we get:
+%
+\begin{align}
+%
+\E Y[i] = \gamma a_x^1.
+%
+\end{align}
+%
+Consequently,
+%
+\begin{align}
+a_y^1 = \frac{1}{N} \sum_{i=1}^n \E Y[i] = \gamma a_x^1.
+\end{align}
+
+%
+
+\subsubsection{Computing $a_y^2$}
+
+First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%
+\begin{align}
+%
+Y[i_1] Y[i_2]
 &= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]}
 X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
@@
 In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
-This gives (all expectations are conditional on $M$):
+This gives (all expectations are conditional on $s$):
 %
@@
 %
-\E Y_{i_1} Y_{i_2}
+\E Y[i_1] Y[i_2]
 =& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]}
 \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
@@
 \nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{S[i_1-j_1]} 
 \E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
 \nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
-%
-\end{align}
-%
-Now take expectations over the Poisson random variables, using this fact:
-%
-\begin{lem} \label{lem-choose}
-	If $M \sim \Poisson(\gamma)$, then 
-	\begin{align}
-	%
-	\E {M\choose k} = \frac{\gamma^k}{k!}.
-	%
-	\end{align}
-\end{lem}
-
-We get (now the expectation is over $M$ and $X$):
-%
-\begin{align}
-%
-\E Y_{i_1} Y_{i_2} 
-=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
-+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
-\nonumber \\
-=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
-%
-\end{align}
-
-But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
-
-%
-
-\subsubsection{Third moment}
-
-For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
-%
-\begin{align}
-%
-&Y_{i_1} Y_{i_2} Y_{i_3}
-\nonumber \\
-&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
-\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
+=& \sum_{j_1 - j_2 \ne \Delta} S[i_1-j_1] S[i_2 - j_2] \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} S[i_1-j_1](S[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} S[i_1-j_1] \M_2[j_1,j_1 + \Delta] .
+%
+\end{align}
+%
+Now take expectations over the Poisson random variables, using Lemma \ref{lem-choose}:
+%
+\begin{align}
+%
+\E Y[i_1] Y[i_2]
+=& \sum_{j_1 - j_2 \ne \Delta} \E S[i_1-j_1] S[i_2 - j_2] \M_1[j_1] \M_1[j_2]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E S[i_1-j_1](S[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E S[i_1-j_1] \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
+\nonumber \\
+&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+\nonumber \\
+=&  \bigg(\frac{\gamma}{L}  \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
++ \frac{\gamma}{L} \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
+\nonumber \\
+=&  (\gamma a_x^1)^2 + \gamma a_x^2[\Delta].
+%
+\end{align}
+%
+For positive $\sigma$, we observe that any terms linear in the noise vanish in expectation. Denoting by $X^*$ the clean signal component of length $N$, so $Y = X^* + \ep$, we have:
+%
+%
+\begin{align}
+\E Y[i_1] Y[i_2] = \E X^*[i_1] X^*[i_2] + \E \ep[i_1] \ep[i_2]
+= (\gamma a_x^1)^2 + \gamma a_x^2[\Delta] + \sigma^2 \delta[i_1 - i_2].
+\end{align}
+%
+We conclude by averaging over $i_1$ and $i_2$, leaving the gap $\Delta = i_2 - i_1$ fixed.
+
+%
+
+\subsubsection{Computing $a_x^3$}
+
+We will first assume $\sigma = 0$. For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%
+\begin{align}
+%
+& Y[i_1] Y[i_2] Y[i_3]
+= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
+\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]} \sum_{k_3=1}^{S[i_3-j_3]}
 X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
@@
 %
-&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{S[\ell]} \sum_{k_2=1}^{S[\ell]} \sum_{k_3=1}^{S[\ell]} 
 X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
@@
 
-For term (a), the expectation conditional on $M$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+For term (a), the expectation conditional on $S$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} S[\ell](S[\ell]-1)(S[\ell]-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
 %
@@
 %
-\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
-%
-\end{align}
-
-For term (b), the expectation conditional on $M$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%
+\end{align}
+
+For term (b), the expectation conditional on $S$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} S[\ell] (S[\ell] - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
 %
@@
 %
-\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
 %
@@
 %
-\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+\frac{\gamma}{L} \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
 %
@@
 & \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
-\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
+\sum_{1 \le k_1,k_2 \le S[\ell_1]} \sum_{k_3=1}^{S[\ell_2]}
 X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
 \nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
-\Bigg\{
-\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{S[\ell_2]}
+\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le S[\ell_1]} 
 X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
 \nonumber \\
-&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+& + \sum_{k_1=1}^{S[\ell_1]} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
 X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
@@
 %
-Taking expectations conditional on $M$, we then get:
-%
-\begin{align}
-%
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-\nonumber \\
-&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
-%
-\end{align}
-
-Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
-%
-\begin{align}
-%
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+Taking expectations conditional on $S$, we then get:
+%
+\begin{align}
+%
+\sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+\Bigg( & S[\ell_1] (S[\ell_1]-1) S[\ell_2] \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+\nonumber \\
+&  + S[\ell_1] S[\ell_2] \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $S$ and using Lemma \ref{lem-choose} then gives:
+%
+\begin{align}
+%
+& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
 \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
 \label{ffff} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
+& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
 \M_2[j_1,j_1+\Delta_1] \M_1[j_3].
@@
 %
-& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
+& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
 \M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
 \label{hhhh} \\
-& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
+& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
 \M_2[j_1,j_1+\Delta_2] \M_1[j_2]
@@
 %
-& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
+& \frac{\gamma^3}{L^3} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
 \M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
 \label{jjjj}\\
-& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
+& + \frac{\gamma^2}{L^2} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
 \M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
@@
 Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
+Consequently, the $X$ variables are always independent, and the expectation conditional on $S$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} S[\ell_1] S[\ell_2] S[\ell_3] \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%
+\end{align}
+%
+since the $S[\ell_q]$'s are pairwise independent, $q=1,2,3$, the expectation over $S$ then yields:
+%
+\begin{align} \label{llll}
+%
+\frac{\gamma^3}{L^3} \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+%
+\end{align}
+
+Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
+%
+\begin{align}
+%
+(\gamma a_x^1)^3.
+%
+\end{align}
+
+Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
+%
+\begin{align}
+%
+\gamma a_x^1  \cdot 
+( \gamma a_x^2[\Delta_1] + \gamma a_x^2[\Delta_2] + \gamma a_x^2[\Delta_2-\Delta_1]).
+%
+\end{align}
+%
+Finally, expression \eqref{eeee} is simply:
+%
+\begin{align}
+%
+\gamma a_x^3[\Delta_1,\Delta_2].
+%
+\end{align}
+%
+
+Now when $\sigma > 0$, we write $Y = X^* + \ep$, and
+%
+\begin{align}
+\E Y[i_1] Y[i_2] Y[i_3] =& \E X^*[i_1] X^*[i_2] X^*[i_3] + \E X^*[i_1] \ep[i_2] \ep[i_3]
+\nonumber \\
+& + \E\ep[i_1] X^*[i_2] \ep[i_3] + \E \ep[i_1] \ep[i_2] X^*[i_3] 
++ \E \ep[i_1] \ep[i_2]\ep[i_3]
+\nonumber \\
+=& \E X^*[i_1] X^*[i_2] X^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
+\nonumber \\
+& + \gamma a_x^1 \cdot \sigma^2 \delta[i_3-i_1] 
++ \gamma a_x^1 \cdot \sigma^2 \delta[i_2-i_1] .
+\end{align}
+
+We conclude by averaging over $i_1$, $i_2$, and $i_3$ leaving the gaps $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$ fixed.
+%
+%\TODO{Needs a complete rewrite to match the paper, in particular the modified notation and the fact we only work with autocorrelations now (not models).}
+%
+%\subsubsection{First moment}
+%
+%To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
+%%
+%\begin{align}
+%%
+%\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
+%= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
+%= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
+%%
+%\end{align}
+%%
+%Now taking expectations over $M$ we see:
+%%
+%\begin{align}
+%%
+%\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
+%%
+%\end{align}
+%
+%
+%%
+%
+%
+%\subsubsection{Second moment}
+%
+%Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%%
+%\begin{align}
+%%
+%Y_{i_1} Y_{i_2} 
+%&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+%X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
+%%
+%\end{align}
+%
+%We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+In the first case, all the terms are independent, and so the expectation factors.
+In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
+This gives (all expectations are conditional on $M$):
+%%
+%\begin{align} \label{moment2-condm}
+%%
+%\E Y_{i_1} Y_{i_2}
+%=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
+%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
+%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+%\nonumber \\
+%=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+%\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
+%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
+%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
+%\nonumber \\
+%=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+%%
+%\end{align}
+%%
+%Now take expectations over the Poisson random variables, using this fact:
+%%
+%\begin{lem} \label{lem-choose}
+%	If $M \sim \Poisson(\gamma)$, then 
+%	\begin{align}
+%	%
+%	\E {M\choose k} = \frac{\gamma^k}{k!}.
+%	%
+%	\end{align}
+%\end{lem}
+%
+%
+%We get (now the expectation is over $M$ and $X$):
+%%
+%\begin{align}
+%%
+%\E Y_{i_1} Y_{i_2} 
+%=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
+%\nonumber \\
+%=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
+%+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+%\nonumber \\
+%=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
+%+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
+%\nonumber \\
+%=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
+%%
+%\end{align}
+%
+%But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+%
+%
+%%
+%
+%
+%\subsubsection{Third moment}
+%
+%For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%%
+%\begin{align}
+%%
+%&Y_{i_1} Y_{i_2} Y_{i_3}
+%\nonumber \\
+%&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
+%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
+%X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
+%\end{align}
+%%
+%We will break up the outer three sums into disjoint sums with the following ranges of indices:
+%%
+%\begin{enumerate}
+%	
+%	\item \label{case1}
+%	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+%	
+%	\item \label{case2}
+%	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+%	
+%	\item \label{case3}
+%	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+%	
+%	\item \label{case4}
+%	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+%	
+%	\item \label{case5}
+%	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+%	
+%\end{enumerate}
+%
+%
+%For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%%
+%\begin{align}
+%%
+%&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
+%X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%\nonumber \\
+%=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%}_{\text{(a)}}
+%\nonumber \\
+%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%}_{\text{(b)}}
+%\nonumber \\
+%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%}_{\text{(c)}}
+%\nonumber \\
+%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%}_{\text{(d)}}
+%\nonumber \\
+%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%}_{\text{(e)}}.
+%%
+%\end{align}
+%
+%For term (a), the expectation conditional on $M$ is:
+%%
+%\begin{align}
+%%
+%\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+%%
+%\end{align}
+%%
+%Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
+%%
+%\begin{align} \label{aaaa}
+%%
+%\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%%
+%\end{align}
+%
+%
+%For term (b), the expectation conditional on $M$ is:
+%%
+%\begin{align}
+%%
+%\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+%%
+%\end{align}
+%%
+%and then again using Lemma \ref{lem-choose} we get the expected value:
+%%
+%\begin{align} \label{bbbb}
+%%
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+%%
+%\end{align}
+%
+%Similarly, the expected values of terms (c) and (d) are:
+%%
+%\begin{align} \label{cccc}
+%%
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+%%
+%\end{align}
+%%
+%and
+%%
+%\begin{align} \label{dddd}
+%%
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+%%
+%\end{align}
+%
+%Finally, the expected value of term (e) is easily shown to be:
+%%
+%\begin{align} \label{eeee}
+%%
+%\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+%%
+%\end{align}
+%%
+%This concludes the computation for Case \ref{case1}.
+%
+%Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
+%%
+%\begin{align}
+%%
+%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+%\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
+%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
+%\nonumber \\
+%=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+%\Bigg\{
+%\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
+%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
+%\nonumber \\
+%&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
+%X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
+%%
+%\end{align}
+%%
+%Taking expectations conditional on $M$, we then get:
+%%
+%\begin{align}
+%%
+%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+%\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+%\nonumber \\
+%&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
+%%
+%\end{align}
+%
+%Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
+%%
+%\begin{align}
+%%
+%& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
+%\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+%\label{ffff} \\
+%& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
+%\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+%\label{gggg}
+%%
+%\end{align}
+%
+%
+%Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
+%%
+%\begin{align}
+%%
+%& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
+%\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+%\label{hhhh} \\
+%& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
+%\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+%\label{iiii}
+%%
+%\end{align}
+%%
+%and
+%%
+%\begin{align}
+%%
+%& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
+%\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+%\label{jjjj}\\
+%& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
+%\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+%\label{kkkk}
+%%
+%\end{align}
+%
+%Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
 Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
-%
-\begin{align}
-%
-\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
-%
-\end{align}
-%
-since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
-%
-\begin{align} \label{llll}
-%
-\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
-%
-\end{align}
-
-Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
-%
-\begin{align}
-%
-(\gamma \L_1)^3.
-%
-\end{align}
-
-Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
-%
-\begin{align}
-%
-\gamma \L_1  \cdot 
-( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
-%
-\end{align}
-%
-Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
-%
-\begin{align}
-%
-\gamma \L_3(\Delta_1,\Delta_2)
-%
-\end{align}
-%
-which is the usual third-order auto-correlation.
+%%
+%\begin{align}
+%%
+%\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%%
+%\end{align}
+%%
+%since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
+%%
+%\begin{align} \label{llll}
+%%
+%\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+%%
+%\end{align}
+%
+%Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
+%%
+%\begin{align}
+%%
+%(\gamma \L_1)^3.
+%%
+%\end{align}
+%
+%Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
+%%
+%\begin{align}
+%%
+%\gamma \L_1  \cdot 
+%( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
+%%
+%\end{align}
+%%
+%Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
+%%
+%\begin{align}
+%%
+%\gamma \L_3(\Delta_1,\Delta_2)
+%%
+%\end{align}
+%%
+%which is the usual third-order auto-correlation.
+%%
 
@@
 
-%
-%In the simplified mathematical model above, we showed it is possible to estimate a signal without detecting its appearances.  
-%Our strategy is to compute autocorrelations of the micrographs and to relate these statistics to the unknown signal's parameters.
-Recovering the parameters from the statistics reduces to solving a set of polynomial equations.
-%
-%We also showed how this technique can, in principle, be applied to cryo-EM.
-%Crucially, the outlined approach involves no particle picking, hence a fortiori no viewing direction estimation.
-Concerns for model bias are also greatly reduced since no template matching is involved.
-%Additionally,  our technique also allows the use of much lower defocus values.
-Lower defocus means lower contrast, but will maintain  higher frequency information.
-Consequently, we may be able to get high resolution reconstructions from fewer micrographs.
-%
-%Looking toward applying the framework to encompass all important features of real cryo-EM experiments, our work implies that it might be possible to reconstruct small molecules, particularly, molecules that are too small to be detected in micrographs.
-%In pursuing this research direction, our goal is to significantly increase the range of molecules to which cryo-EM can be successfully applied.
-%We recognize that significant challenges lay ahead for the implementation of the proposed approach to {high-resolution} 3-D reconstruction directly from the micrographs. We discuss a few now.
-%
-%The numerical experiments we have performed reveal that the third-order autocorrelation may not be enough for 3-D reconstruction in practice, due to high sensitivity.
-%This suggests that fourth-order autocorrelation may be necessary. This in turn would imply that the procedure might require a large amount of data. 
-%Recent trends in high-throughput cryo-EM technology   give hope that this may be a lesser concern in the long term.
-Still, large amounts of data also require large amounts of computation.
-On this front, we note that computing autocorrelations can be executed efficiently on CPUs and GPUs, and in parallel across micrographs.
-It can even be done in a  streaming mode, as only one pass through each micrograph is necessary.
-The output of this data processing stage is a summary in the form of autocorrelation estimates: its size is a function of the resolution, not a function of the number of observed micrographs.
-Subsequent steps, which involve solving the system of polynomial equations, scale only in the size of that summary.
-Of course, an important question then is whether the equations can be solved accurately and efficiently in practice.
-%
-%To reach high-resolution reconstruction, beyond data acquisition and computational challenges, there are modeling issues  to consider.
-%In contrast to the simplifying assumptions we have made above, the noise might be colored; the viewing directions of the particles may be distributed non-uniformly; there may be conformational heterogeneity; particles generally do not satisfy our separation condition; and micrographs undergo a contrast transfer function which we have omitted.
-All of these aspects can be handled with the same general strategy: establish a forward model relating the expected autocorrelations of the micrographs to the target volume(s) and all parameters necessary to model the above effects.
-%For instance, for colored noise, the forward model may involve multiple parameters to capture the power spectrum of the noise instead of the single parameter $\sigma^2$. 
-%Similarly, instead of the separation condition, we can model the spacing between the projections using a parameterized pair-correlation function.
-Such a function models the distribution of distances between neighboring projections.
-The observed autocorrelations depend linearly on these parameters, which would be estimated as part of the inverse problem.
-%All these aspects must be taken into account so the method can be applied on experimental data. We hope to take care of these issues in future research.
-
-%
-%\section*{Acknowledgment}
-%The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
-%The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
-%NB is partially supported by NSF award DMS-1719558.
+\subsection{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
+
+	It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product (where $x[j]=0$ whenever $j < 0$ or $j > L-1$):
+	%
+	\begin{align}
+	L^2(\gamma a_x^1) (\gamma a_x^2[1])
+	&= \gamma^2\left( \sum_{i} x[i] \right) \left(\sum_{j} x[j]x[j+1] \right)
+	\nonumber \\
+	&= \gamma^2\sum_{j} \sum_{i} x[i]x[j]x[j+1]
+	\nonumber \\
+	&=  \gamma^2\sum_{j} \sum_{\ell} x[j+\ell]x[j]x[j+1]
+	\nonumber \\
+	&=  \gamma^2\sum_{\ell \ge 0} \sum_{j} x[j+\ell]x[j]x[j+1] 
+	+ \gamma^2\sum_{\ell < 0} \sum_{j} x[j+\ell]x[j]x[j+1]
+	\nonumber \\
+	&=  \gamma^2\sum_{\ell=0}^{L-1} a_x^3[1,\ell] 
+	+ \gamma^2\sum_{\ell > 0} \sum_{j} x[j-\ell]x[j]x[j+1]
+	\nonumber \\
+	&=  \gamma^2\sum_{\ell=0}^{L-1} a_x^3[1,\ell] 
+	+ \gamma^2\sum_{\ell > 0} \sum_{j} x[j]x[j+\ell]x[j+\ell+1]
+	\nonumber \\
+	&= \gamma\left\{ \sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell]
+	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]  \right\}.
+	\end{align}
+	%
+	Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$, and then $\sigma^2$:
+
+	\begin{align}
+	\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
+	{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
+		+ \sum_{\ell=2}^{L-1} \gamma a_x^3[\ell,\ell+1]},
+	\end{align}
+	%
+	\begin{align}
+	\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+	- (2 L - 1) (a_y^1)^2.
+	\end{align}
+
+\section*{Acknowledgment} \TODO{To check}
+The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Kan and Amit Moscovich  for helpful discussions..
+The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
+NB is partially supported by NSF award DMS-1719558.
 

### 2019-03-03 inverse_problems/inverse_problems.tex
changing notation in Section 6.1

@@
 \usepackage[T1]{fontenc}
-%\usepackage[latin9]{inputenc}
 \usepackage{verbatim}
@@
 \usepackage{graphicx}
-%\usepackage{multirow}
 \usepackage{color}
@@
 \usepackage{stackrel}
-%\usepackage[skip=1pt]{caption} % example skip set to 2pt
 
@@
 \newcommand{\mc}{\mathcal}
-\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
 \newcommand{\TODO}[1]{{\color{red}{[#1]}}}
@@
 \newcommand{\R}{\mathbb{R}}
-\newcommand{\M}{\mathcal{M}}
+%\newcommand{\M}{\mathcal{M}}
+\newcommand{\M}{m}
 \renewcommand{\P}{\mathbb{P}}
@@
 
-%\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
 \makeatletter
@@
 
-%\allowdisplaybreaks
+\allowdisplaybreaks
 \numberwithin{equation}{section}
@@
 multiple times at unknown locations in a noisy measurement.
-We derive simple relations between the autocorrelations of the observations and those of the signals.
+In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
+In the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
+By employing autocorrelation analysis, we show that in some cases the signals themselves can be estimated  without detecting their occurrences. 
+To estimate the signals, we derive simple relations between the autocorrelations of the observations and those of the signals.
 These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement.
 To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
-This is of particular importance in high noise regimes in which detecting individual signal appearance is impossible.
 We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.
 
-The main goal of this work is to supply theoretical and numerical support for the possibility of estimating the 3-D structure of single particles using cryo-electron microscopy without detection~\cite{bendory2018toward}.
+The main goal of this work is to supply theoretical and numerical support for a recent suggestion to  estimate the 3-D structure of single particles using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.
 
@@
 Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
-\begin{align} \label{eq:ac_well_separated}
-	a_y^1 & = \gamma a_{x}^1, \nonumber \\
-	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \\
-	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
-	+\delta[\ell_1-\ell_2]\big), 
-\end{align}
-where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
+\begin{align} 
+	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
+	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell], \label{eq:ac2_micrograph}\\
+	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\ell[\ell_1]+\ell[\ell_2]
+	+\ell[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
+\end{align}
+where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
 Terms proportional to $\sigma^2$ are due to the noise.
@@
 We show in Section~\ref{sec:theory_homogeneous_well_separated} 
-that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).
+that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).
 
@@
 
-In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model, expressed in terms of the autocorrelations of $x$ and the parameters $\gamma$ and $\sigma$:
+In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
+As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on $x$ itself, and the parameters $\gamma$ and $\sigma$:
 %
@@
 \label{eq:mean_micrograph2} \\
-a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
+a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \ell[\ell], 
 \label{eq:ac2_micrograph2} \\
@@
 \nonumber \\
-& \qquad + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
+& \qquad + \gamma a_x^1 \sigma^2 \big(\ell[\ell_1]+\ell[\ell_2] +\ell[\ell_1-\ell_2] \big).
 \label{eq:ac3_micrograph2}
@@
 
-In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
-%
-%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
-Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
+%
+%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
 %%
@@
 For the Poisson model: 
-From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
-Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
 %
@@
 
-Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.
+%Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.
 
@@
 %%
-%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\delta[\ell],
-%\end{align}
-%where $\delta[0]=1$ and zero otherwise. 
+%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\ell[\ell],
+%\end{align}
+%where $\ell[0]=1$ and zero otherwise. 
 %
@@
 %Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
-%$\gamma\sigma^2 a_x^1 \delta[\ell_1-\ell_2]$.
+%$\gamma\sigma^2 a_x^1 \ell[\ell_1-\ell_2]$.
 %The same goes for Terms (4) and (5), which are equal, respectively, to
-%$\gamma\sigma^2 a_x^1 \delta[\ell_2]$ 
-%and $\gamma\sigma^2 a_x^1 \delta[\ell_1]$.
+%$\gamma\sigma^2 a_x^1 \ell[\ell_2]$ 
+%and $\gamma\sigma^2 a_x^1 \ell[\ell_1]$.
 
@@
 \begin{align}
-N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \delta[\ell],
-\end{align}
-where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
-\begin{align}
-a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \delta[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
+N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \ell[\ell],
+\end{align}
+where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
+\begin{align}
+a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \ell[\ell] = \gamma a_x^2[\ell] + \sigma^2 \ell[\ell].
 \end{align}
@@
 (Otherwise, the product of indicators is zero.) This allows to reduce the summations over $j,j',j''$ to a single sum over $j$.
-Then, witching the order of summation with $i$, we get that the first term is equal to
+Then, switching the order of summation with $i$, we get that the first term is equal to
 \begin{align}
@@
 \begin{align}
-\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \delta[\ell_1 - \ell_2].
+\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \ell[\ell_1 - \ell_2].
 \end{align}
@@
 \begin{align}
-\sigma^2 \delta[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
-\end{align}
-Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \delta[\ell_1 - \ell_2]$.
+\sigma^2 \ell[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
+\end{align}
+Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \ell[\ell_1 - \ell_2]$.
 A similar reasoning for terms 6 and 7 yields this final formula for the third-order autocorrelations of $y$:
 \begin{align}
-a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \delta[\ell_1] + \delta[\ell_2] + \delta[\ell_1 - \ell_2] \right).
+a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \ell[\ell_1] + \ell[\ell_2] + \ell[\ell_1 - \ell_2] \right).
 \end{align}
@@
 
-Throughout this section, we will use the capital letter $X$ to represent the random unobserved vector of length $L$, the capital letter $Y$ to represent the random observed vector of length $N$, and the capital letter $S$ to represent the unobserved vector of occurrences.
-
-We will denote by $\M_l$ the moment tensors of $X$:
-%
-\begin{align}
-%
-\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
+%Throughout this section, we will use the capital letter $X$ to represent the random unobserved vector of length $L$, the capital letter $Y$ to represent the random observed vector of length $N$, and the capital letter $S$ to represent the unobserved vector of occurrences.
+
+We will denote by $\M_l$ the moment tensors of $x$:
+%
+\begin{align}
+%
+\M_1[i] = \E x[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_2[i,j] = \E x[i] x[j], \quad 0 \le i,j \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+\M_3[i,j,k] = \E x[i] x[j] x[k], \quad 0 \le i,j,k \le L-1.
 %
@@
 %
-a_x^2[\Delta] = \frac{1}{L} \sum_{i=0}^{L-1} \M_2[i,i+\Delta],
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-a_x^3[\Delta_1,\Delta_2] = \frac{1}{L}\sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2].
+a_x^2[\ell] = \frac{1}{L} \sum_{i=0}^{L-1} \M_2[i,i+\ell],
+%
+\end{align}
+%
+and \TODO{Compare with~\eqref{eq:ac_special}: the limits on the sum should be modified}
+%
+\begin{align}
+%
+a_x^3[\ell_1,\ell_2] = \frac{1}{L}\sum_{i=0}^{L-1} \M_3[i,i+\ell_1,i+\ell_2].
 %
@@
 	%
-	If $M \sim \Poisson(\lambda)$, then 
-	\begin{align}
-	%
-	\E {M\choose k} = \frac{\lambda^k}{k!}.
+	If $z \sim \Poisson(\lambda)$, then 
+	\begin{align}
+	%
+	\E {z\choose k} = \frac{\lambda^k}{k!}.
 	%
@@
 We will first condition on the vector $s$ of locations of the subsignals in $y$, and then average over $s$.
-We will denote by $X_1^{i},\dots,X_{S[i]}^i$ the random vectors with position 0 located at $i$.
+We will denote by $x_{(1)}^i,\dots,x_{(s[i])}^i$ the random vectors with position 0 located at $i$.
 We have:
@@
 %
-\E[ Y[i] | S ] = \sum_{j=0}^{L-1} \sum_{k=1}^{S[i-j]} \E X_k^{i-j}[j]
-= \sum_{k=1}^{S[i-j]} L a_x^1
-= S[i-j] L a_x^1.
-%
-\end{align}
-%
-Now taking expectations over $s$ and using $\E S[i-j] = \gamma/L$ we get:
-%
-\begin{align}
-%
-\E Y[i] = \gamma a_x^1.
+\E[ y[i] | s ] = \sum_{j=0}^{L-1} \sum_{k=1}^{s[i-j]} \E x_{(k)}^{i-j}[j]
+= \sum_{k=1}^{s[i-j]} L a_x^1
+= s[i-j] L a_x^1.
+%
+\end{align}
+%
+Now taking expectations over $s$ and using $\E s[i-j] = \gamma/L$ we get:
+%
+\begin{align}
+%
+\E y[i] = \gamma a_x^1.
 %
@@
 \begin{align}
-a_y^1 = \frac{1}{N} \sum_{i=1}^n \E Y[i] = \gamma a_x^1.
+a_y^1 = \frac{1}{N} \sum_{i=1}^N \E y[i] = \gamma a_x^1.
 \end{align}
@@
 
-First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
-%
-\begin{align}
-%
-Y[i_1] Y[i_2]
+First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
+%
+\begin{align}
+%
+y[i_1] y[i_2]
 &= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]}
-X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
-%
-\end{align}
-
-We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]}
+x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2].
+%
+\end{align}
+
+We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \ell$, and one where $j_2 = j_1 + \ell$ or equivalently $i_1-j_1 = i_2-j_2$.
 In the first case, all the terms are independent, and so the expectation factors.
@@
 %
-\E Y[i_1] Y[i_2]
+\E y[i_1] y[i_2]
 =& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]}
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
-\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
+\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]}
+\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2]
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
+\sum_{k_2} \E x_{(k_1)}^{i_1-j_1}[j_1] x_{k_2}^{i_2 - j_2}[j_2]
 \nonumber \\
 & + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{S[i_1-j_1]} 
-\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \Delta} S[i_1-j_1] S[i_2 - j_2] \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} S[i_1-j_1](S[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} S[i_1-j_1] \M_2[j_1,j_1 + \Delta] .
+\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_1 - j_1}[j_1+\ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{s[i_1-j_1]} 
+\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_1)}^{i_1-j_1}[j_1 + \ell] 
+\nonumber \\
+=& \sum_{j_1 - j_2 \ne \ell} s[i_1-j_1] s[i_2 - j_2] \M_1[j_1] \M_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1](s[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1] \M_2[j_1,j_1 + \ell] .
 %
@@
 %
-\E Y[i_1] Y[i_2]
-=& \sum_{j_1 - j_2 \ne \Delta} \E S[i_1-j_1] S[i_2 - j_2] \M_1[j_1] \M_1[j_2]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E S[i_1-j_1](S[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E S[i_1-j_1] \M_2[j_1,j_1 + \Delta]
-\nonumber \\
-=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
-+ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
-\nonumber \\
-&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+\E y[i_1] y[i_2]
+=& \sum_{j_1 - j_2 \ne \ell} \E s[i_1-j_1] s[i_2 - j_2] \M_1[j_1] \M_1[j_2]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1](s[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1] \M_2[j_1,j_1 + \ell]
+\nonumber \\
+=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \ell} \gamma^2 \M_1[j_1] \M_1[j_2]
++ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \ell]
+\nonumber \\
+&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \ell]
 \nonumber \\
 =&  \bigg(\frac{\gamma}{L}  \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-+ \frac{\gamma}{L} \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
-\nonumber \\
-=&  (\gamma a_x^1)^2 + \gamma a_x^2[\Delta].
-%
-\end{align}
-%
-For positive $\sigma$, we observe that any terms linear in the noise vanish in expectation. Denoting by $X^*$ the clean signal component of length $N$, so $Y = X^* + \ep$, we have:
-%
-%
-\begin{align}
-\E Y[i_1] Y[i_2] = \E X^*[i_1] X^*[i_2] + \E \ep[i_1] \ep[i_2]
-= (\gamma a_x^1)^2 + \gamma a_x^2[\Delta] + \sigma^2 \delta[i_1 - i_2].
-\end{align}
-%
-We conclude by averaging over $i_1$ and $i_2$, leaving the gap $\Delta = i_2 - i_1$ fixed.
++ \frac{\gamma}{L} \sum_{j = 0}^{L-1} \M_2[j,j + \ell]
+\nonumber \\
+=&  (\gamma a_x^1)^2 + \gamma a_x^2[\ell].
+%
+\end{align}
+%
+For positive $\sigma$, we observe that any terms linear in the noise vanish in expectation. Denoting by $x^*$ the clean signal component of length $N$, so $y = x^* + \ep$, we have:
+%
+%
+\begin{align}
+\E y[i_1] y[i_2] = \E x^*[i_1] x^*[i_2] + \E \ep[i_1] \ep[i_2]
+= (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[i_1 - i_2].
+\end{align}
+%
+We conclude by averaging over $i_1$ and $i_2$, leaving the gap $\ell = i_2 - i_1$ fixed.
 
@@
 
-We will first assume $\sigma = 0$. For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
-%
-\begin{align}
-%
-& Y[i_1] Y[i_2] Y[i_3]
+We will first assume $\sigma = 0$. For three distinct $i_1$, $i_2$ and $i_3$, we let $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$. We have:
+%
+\begin{align}
+%
+& y[i_1] y[i_2] y[i_3]
 = \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
-\sum_{k_1=1}^{S[i_1-j_1]}\sum_{k_2=1}^{S[i_2-j_2]} \sum_{k_3=1}^{S[i_3-j_3]}
-X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
+\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]} \sum_{k_3=1}^{s[i_3-j_3]}
+x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2] x_{(k_3)}^{i_3 - j_3}[j_3].
 \end{align}
@@
 
-For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
-%
-\begin{align}
-%
-&\sum_{j=0}^{L-1} \sum_{k_1=1}^{S[\ell]} \sum_{k_2=1}^{S[\ell]} \sum_{k_3=1}^{S[\ell]} 
-X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+For Case \ref{case1}, we have $q \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%
+\begin{align}
+%
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{s[q]} \sum_{k_2=1}^{s[q]} \sum_{k_3=1}^{s[q]} 
+x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 \nonumber \\
 =& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 }_{\text{(a)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 }_{\text{(b)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 }_{\text{(c)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 }_{\text{(d)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
 }_{\text{(e)}}.
@@
 
-For term (a), the expectation conditional on $S$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} S[\ell](S[\ell]-1)(S[\ell]-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+For term (a), the expectation conditional on $s$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} s[q](s[q]-1)(s[q]-2)\M[j] \M[j+\ell_1] \M[j+\ell_2].
 %
@@
 %
-\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\ell_1] \M_1[j+\ell_2].
 %
@@
 %
-\sum_{j=0}^{L-1} S[\ell] (S[\ell] - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
-%
-\end{align}
-%
-and then again using Lemma \ref{lem-choose} we get the expected value:
+\sum_{j=0}^{L-1} s[q] (s[q] - 1) \M_2[j,j+\ell_1] \M_1[j + \ell_2]
+%
+\end{align}
+%
+and then again using Lemma~\ref{lem-choose} we get the expected value:
 %
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\ell_1] \M_1[j+\ell_2].
 %
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\ell_2] \M_1[j+\ell_1].
 %
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j+\ell_1,j+\ell_2] \M_1[j].
 %
@@
 %
-\frac{\gamma}{L} \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+\frac{\gamma}{L} \sum_{j=0}^{L-1} \M_3[j,j+\ell_1,j+\ell_2].
 %
@@
 
-Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
-%
-\begin{align}
-%
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
-\sum_{1 \le k_1,k_2 \le S[\ell_1]} \sum_{k_3=1}^{S[\ell_2]}
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
-\nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{S[\ell_2]}
-\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le S[\ell_1]} 
-X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
-\nonumber \\
-& + \sum_{k_1=1}^{S[\ell_1]} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
-X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
-%
-\end{align}
-%
-Taking expectations conditional on $S$, we then get:
-%
-\begin{align}
-%
-\sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\Bigg( & S[\ell_1] (S[\ell_1]-1) S[\ell_2] \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-\nonumber \\
-&  + S[\ell_1] S[\ell_2] \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
-%
-\end{align}
-
-Taking expectations over $S$ and using Lemma \ref{lem-choose} then gives:
-%
-\begin{align}
-%
-& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
+Moving onto Case~\ref{case2}, we have $q_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $q_2 \equiv i_3 - j_3$. By definition, $q_1 \ne q_2$. The sum is:
+%
+\begin{align}
+%
+& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
+\sum_{1 \le k_1,k_2 \le S[q_1]} \sum_{k_3=1}^{s[q_2]}
+x_{(k_1)}^{q_1}[j_1] x_{(k_2)}^{q_1}[j_1 + \ell_1] x_{(k_3)}^{q_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{s[q_2]}
+\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le s[q_1]} 
+x_{(k_1)}^{q_1}[j_1] x_{(k_2)}^{q_1}[j_1 + \ell_1] x_{(k_3)}^{q_2}[j_3]
+\nonumber \\
+& + \sum_{k_1=1}^{s[q_1]} x_{(k_1)}^{q_1}[j_1] x_{(k_1)}^{q_1}[j_1 + \ell_1] 
+x_{(k_3)}^{q_2}[j_3]  \Bigg\}.
+%
+\end{align}
+%
+Taking expectations conditional on $s$, we then get:
+%
+\begin{align}
+%
+\sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
+\Bigg( & s[q_1] (s[q_1]-1) s[q_2] \M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
+ + s[q_1] s[q_2] \M_2[j_1,j_1+\ell_1] \M_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $s$ and using Lemma~\ref{lem-choose} then gives:
+%
+\begin{align}
+%
+& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
+\M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
 \label{ffff} \\
-& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
-\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
+& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}  
+\M_2[j_1,j_1+\ell_1] \M_1[j_3].
 \label{gggg}
@@
 %
-& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
-\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
+& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1} 
+\M_1[j_1] \M_1[j_1 + \ell_2] \M_1[j_2]
 \label{hhhh} \\
-& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
-\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
+& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1}  
+\M_2[j_1,j_1+\ell_2] \M_1[j_2]
 \label{iiii}
@@
 & \frac{\gamma^3}{L^3} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
+\M_1[j_1] \M_1[j_2 + \ell_1] \M_1[j_2 + \ell_2]
 \label{jjjj}\\
 & + \frac{\gamma^2}{L^2} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
+\M_2[j_2+\ell_1,j_2+\ell_2] \M_1[j_1].
 \label{kkkk}
@@
 Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
-Consequently, the $X$ variables are always independent, and the expectation conditional on $S$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
-%
-\begin{align}
-%
-\sum_{j_1,j_2,j_3} S[\ell_1] S[\ell_2] S[\ell_3] \M_1[j_1] \M_1[j_2] \M_1[j_3];
-%
-\end{align}
-%
-since the $S[\ell_q]$'s are pairwise independent, $q=1,2,3$, the expectation over $S$ then yields:
+Consequently, the $x$ variables are always independent, and the expectation conditional on $s$ (letting $q_\ell = i_\ell - j_\ell$, $\ell=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} s[q_1] s[q_2] s[q_3] \M_1[j_1] \M_1[j_2] \M_1[j_3];
+%
+\end{align}
+%
+since the $s[q_\ell]$'s are pairwise independent, $\ell=1,2,3$, the expectation over $s$ then yields:
 %
@@
 \gamma a_x^1  \cdot 
-( \gamma a_x^2[\Delta_1] + \gamma a_x^2[\Delta_2] + \gamma a_x^2[\Delta_2-\Delta_1]).
+( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2] + \gamma a_x^2[\ell_2-\ell_1]).
 %
@@
 %
-\gamma a_x^3[\Delta_1,\Delta_2].
-%
-\end{align}
-%
-
-Now when $\sigma > 0$, we write $Y = X^* + \ep$, and
-%
-\begin{align}
-\E Y[i_1] Y[i_2] Y[i_3] =& \E X^*[i_1] X^*[i_2] X^*[i_3] + \E X^*[i_1] \ep[i_2] \ep[i_3]
-\nonumber \\
-& + \E\ep[i_1] X^*[i_2] \ep[i_3] + \E \ep[i_1] \ep[i_2] X^*[i_3] 
+\gamma a_x^3[\ell_1,\ell_2].
+%
+\end{align}
+%
+
+Now when $\sigma > 0$, we write $y = x^* + \ep$, and
+%
+\begin{align}
+\E y[i_1] y[i_2] y[i_3] =& \E x^*[i_1] x^*[i_2] x^*[i_3] + \E x^*[i_1] \ep[i_2] \ep[i_3]
+\nonumber \\
+& + \E\ep[i_1] x^*[i_2] \ep[i_3] + \E \ep[i_1] \ep[i_2] x^*[i_3] 
 + \E \ep[i_1] \ep[i_2]\ep[i_3]
 \nonumber \\
-=& \E X^*[i_1] X^*[i_2] X^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
+=& \E x^*[i_1] x^*[i_2] x^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
 \nonumber \\
@@
 
-We conclude by averaging over $i_1$, $i_2$, and $i_3$ leaving the gaps $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$ fixed.
+We conclude by averaging over $i_1$, $i_2$, and $i_3$ leaving the gaps $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$ fixed.
 %
@@
 %
-%Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\Delta = i_2 - i_1$. Then:
+%Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
 %%
@@
 %
-%We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \Delta$, and one where $j_2 = j_1 + \Delta$ or equivalently $i_1-j_1 = i_2-j_2$.
+%We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \ell$, and one where $j_2 = j_1 + \ell$ or equivalently $i_1-j_1 = i_2-j_2$.
 In the first case, all the terms are independent, and so the expectation factors.
@@
 %\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \Delta} \sum_{k_1} 
+%=& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
 %\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
@@
 %& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\Delta]
+%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\ell]
 %\nonumber \\
 %& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
-%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \Delta] 
-%\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \Delta} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \Delta] .
+%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \ell] 
+%\nonumber \\
+%=& \sum_{j_1 - j_2 \ne \ell} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \ell] .
 %%
@@
 %\E Y_{i_1} Y_{i_2} 
-%=& \sum_{j_1 - j_2 \ne \Delta} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \Delta]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \Delta]
-%\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \Delta} \gamma^2 \M_1[j_1] \M_1[j_2]
-%+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \Delta]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \Delta]
+%=& \sum_{j_1 - j_2 \ne \ell} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \ell]
+%\nonumber \\
+%=& \sum_{j_1 - j_2 \ne \ell} \gamma^2 \M_1[j_1] \M_1[j_2]
+%+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \ell]
+%\nonumber \\
+%& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \ell]
 %\nonumber \\
 %=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-%+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \Delta]
-%\nonumber \\
-%=&  (\gamma \L_1)^2 + \gamma \L_2(\Delta).
-%%
-%\end{align}
-%
-%But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\Delta)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
+%+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \ell]
+%\nonumber \\
+%=&  (\gamma \L_1)^2 + \gamma \L_2(\ell).
+%%
+%\end{align}
+%
+%But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\ell)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
 %
@@
 %
-%For three distinct $i_1$, $i_2$ and $i_3$, we let $\Delta_1 = i_2 - i_1$ and $\Delta_2 = i_3 - i_1$. We have:
+%For three distinct $i_1$, $i_2$ and $i_3$, we let $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$. We have:
 %%
@@
 %	\item \label{case1}
-%	$j_2 = j_1 + \Delta_1$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+%	$j_2 = j_1 + \ell_1$ and $j_3 = j_2 + \ell_2 - \ell_1$.
 %	
 %	\item \label{case2}
-%	$j_2 = j_1 + \Delta_1$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+%	$j_2 = j_1 + \ell_1$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
 %	
 %	\item \label{case3}
-%	$j_2 \ne j_1 + \Delta_1$ and $j_3 = j_1 + \Delta_2$.
+%	$j_2 \ne j_1 + \ell_1$ and $j_3 = j_1 + \ell_2$.
 %	
 %	\item \label{case4}
-%	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 = j_2 + \Delta_2 - \Delta_1$.
+%	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 = j_2 + \ell_2 - \ell_1$.
 %	
 %	\item \label{case5}
-%	$j_2 \ne j_1 + \Delta_1$ and $j_3 \ne j_1 + \Delta_2$ and $j_3 \ne j_2 + \Delta_2 - \Delta_1$.
+%	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
 %	
@@
 %&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
-%X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %\nonumber \\
 %=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %}_{\text{(a)}}
@@
 %&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %}_{\text{(b)}}
@@
 %&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %}_{\text{(c)}}
@@
 %&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %}_{\text{(d)}}
@@
 %&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \Delta_1] X_{k_3}^{\ell}[j + \Delta_2]
+%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
 %}_{\text{(e)}}.
@@
 %%
-%\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\Delta_1] \M[j+\Delta_2].
+%\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\ell_1] \M[j+\ell_2].
 %%
@@
 %%
-%\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\Delta_1] \M_1[j+\Delta_2].
+%\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\ell_1] \M_1[j+\ell_2].
 %%
@@
 %%
-%\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\Delta_1] \M_1[j + \Delta_2]
+%\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\ell_1] \M_1[j + \ell_2]
 %%
@@
 %%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_1] \M_1[j+\Delta_2].
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_1] \M_1[j+\ell_2].
 %%
@@
 %%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\Delta_2] \M_1[j+\Delta_1].
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_2] \M_1[j+\ell_1].
 %%
@@
 %%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\Delta_1,j+\Delta_2] \M_1[j].
+%\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\ell_1,j+\ell_2] \M_1[j].
 %%
@@
 %%
-%\gamma \sum_{j=0}^{L-1} \M_3[j,j+\Delta_1,j+\Delta_2].
+%\gamma \sum_{j=0}^{L-1} \M_3[j,j+\ell_1,j+\ell_2].
 %%
@@
 %%
-%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}
+%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
 %\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
-%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]   
-%\nonumber \\
-%=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} \sum_{k_3=1}^{M_{\ell_2}}
+%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]   
+%\nonumber \\
+%=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{M_{\ell_2}}
 %\Bigg\{
 %\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
-%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \Delta_1] X_{k_3}^{\ell_2}[j_3]
+%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]
 %\nonumber \\

### 2019-03-04 inverse_problems/inverse_problems.tex
correcting section 4.1 to match the new definition of autocorrelation

@@
 
-A signal $z\in\RL$ is determined uniquely by its second- and third-order autocorrelations.
+We begin this section by showing that in the homogeneous case ($K=1$) ,under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the signal $x$, $\gamma$ and $\sigma^2$.
+Then, we bound the maximal number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.
+
+Before that, we start by showing that in the homogeneous case a signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
  Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
@@
 Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares (LS) procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-
-In what follows, we show that in the homogeneous case $K=1$, the signal $x$, the parameter $\gamma$ and $\sigma^2$ are identified uniquely from the first three observed autocorrelations under both the well-separated and Poisson models.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+%
+%In what follows, we show that in the homogeneous case $K=1$, the signal $x$, the parameter $\gamma$ and $\sigma^2$ are identified uniquely from the first three observed autocorrelations under both the well-separated and Poisson models.
 Then, we bound the maximal number of signals that can be recovered from  those autocorrelations in the heterogeneous case, and discuss extensions to multi-dimensional signals.
@@
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model~\eqref{eq:ac_well_separated} do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
-We will show, however, that $x$ is still determined by the observed moments of $y$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
+We will show, however, that all parameters---$x, \gamma$ and $\sigma^2$---are still determined by the observed moments of $y$.
 
@@
 \begin{proposition} \label{prop:gamma}
-	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  \TODO{Should remove the limit}
+	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  
 	\begin{equation}
-	\gamma  \aseq \lim_{N \to \infty}\frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	\gamma  = \frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
 	\end{equation}
@@
 	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
-	In the limit of $N\to \infty$, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
+	Then, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
 If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
@@
 \begin{corollary}
-	In the limit of $N\to \infty$ and under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+	Under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
 \end{corollary}
-
-As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
+%
+%As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
 
@@
 \subsection{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
-
-In the limit, 
+First,  note that 
 \begin{equation*}
@@
 For convenience, we work with $\beta = \gamma / L$ rather than $\gamma$ itself.
-To this end, we construct two quadratic equations satisfied by $\beta$ and whose coefficients can be computed from observable quantities (in the limit).
+To this end, we construct two quadratic equations satisfied by $\beta$ and whose coefficients can be computed from observable quantities.
 Then, we show that these equations are independent, and hence that $\beta$ is uniquely defined.
@@
 
-In the limit $N \to \infty$, almost surely, $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones.
-(In this whole section, for clarity, we now omit to specify that identities hold almost surely in the limit.) Consider the product:
+Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones.  Consider the product:
 \begin{equation}\label{eq:E1}

### 2019-03-04 inverse_problems/inverse_problems.tex
section 4.2 + proof

@@
 
-For the Poisson model: 
-From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
+Similarly to the homogeneous well-separated model, the observed autocorrelations under the Poisson model identify $x,\gamma$ and $\sigma^2$ uniquely.
+Furthermore, these quantities can be computed explicitly.
+
+We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
  Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
@@
 \end{align}
-
-The proof is provided in Section~\ref{sec:proof_uniqueness_poisson}.
+Using these expressions, we prove the following in Section~\ref{sec:proof_uniqueness_poisson}.
 \begin{proposition} \label{prop:uniqueness_poisson}
-	Poisson result 
+Under the homogeneous Poisson model, the signal $x$, and the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
+In particular, 
+	\begin{align}
+\gamma &= L \frac{(\gamma a_y^1) (\gamma a_x^2[1])}
+{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
+	+ \sum_{\ell=2}^{L-1} \gamma a_x^3[\ell,\ell+1]}, \\
+\sigma^2 &= a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
+- (2 L - 1) (a_y^1)^2.
+\end{align}
 \end{proposition}
@@
 \TODO{Did we define densities $\gamma_k$?}
-\TODO{We write the section for the Poisson model, but it would be the same for the Poisson model}
+\TODO{We write the section for the well-separated model, but it would be the same for the Poisson model}
 
@@
 \subsection{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
-
-	It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product (where $x[j]=0$ whenever $j < 0$ or $j > L-1$):
+	Let us assume that $x$ is generic. Indeed, we observe the product:
 	%
@@
 	\end{align}
+Once $\gamma$ and $\sigma$ were computed, one can recover $x$ from $a_x^2$ and $a_x^3$  by Proposition~\ref{prop:uniqueness}.
 
 \section*{Acknowledgment} \TODO{To check}
-The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Kan and Amit Moscovich  for helpful discussions..
+The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions..
 The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.

### 2019-03-04 inverse_problems/inverse_problems.tex
abstract

@@
 In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
-In the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
-By employing autocorrelation analysis, we show that in some cases the signals themselves can be estimated  without detecting their occurrences. 
-To estimate the signals, we derive simple relations between the autocorrelations of the observations and those of the signals.
-These autocorrelations can be estimate accurately in any noise level given sufficiently long measurement.
+However, in the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
+By employing autocorrelation analysis, we show that the impossibility to detect and cluster signals' occurrences in high noise levels does not necessarily impose limitations on signal estimation.
+Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals.
+These autocorrelations can be estimated accurately in any noise level given sufficiently long measurement.
 To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
-We provide rigorous analysis for the special case in which the same signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.
-
-The main goal of this work is to supply theoretical and numerical support for a recent suggestion to  estimate the 3-D structure of single particles using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.
+We provide rigorous analysis for the special case in which a single signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.
+
+The main goal of this work is to provide theoretical and numerical support for a recently proposed framework to elucidate 3-D structures of biological macromolecules using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.
 

### 2019-03-04 inverse_problems/inverse_problems.tex
sec 1

@@
 However, in the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
-By employing autocorrelation analysis, we show that the impossibility to detect and cluster signals' occurrences in high noise levels does not necessarily impose limitations on signal estimation.
+By employing autocorrelation analysis, we show that the impossibility to detect and cluster signals' occurrences in high noise levels does not necessarily preclude signal estimation.
 Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals.
@@
 
-In the low noise regime, a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve a standard deconvolution problem.
+In the low noise regime, a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve  standard deconvolution problems.
 Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
@@
 In order to recover the signals in the high noise regime, we use autocorrelation analysis.
-In any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for large enough $N$. 
+In any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for sufficiently large  $N$. 
 This computation is straightforward and requires only one pass over the data.
@@
 Below we describe two generative models for $s$.  
-In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depend on $s_1,\ldots,s_K$ only through their sums, that is, the total number of occurrences of each signal.
+In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depend on $s_1,\ldots,s_K$ only through their expected sums, that is, the expected total number of occurrences of each signal.
 To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares (LS) problem as explained in Section~\ref{sec:numerics}.
@@
 In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
-%Under the separation condition~\eqref{eq:spacing}, we refer to this model as the \emph{homogeneous well-separated model}. 
-%In the next section we present a model that alleviates this condition.
-%As will be shown next, in a low SNR environment, estimating $s$ is impossible, whereas in some cases estimating $x$ is tractable.
 Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free (but still noisy) entries.
-% This last sentence is required for the proof of the identity of the third-order autocorrelation in Section 3.
 This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
@@
 
-If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we consider a Poisson model.
-
-Specifically, 
- letting $s[i]$ be the number of signals starting at location $i$, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$  for some parameter $\gamma > 0$. 
- Then, each of those $s[i]$ is chosen independently at random from a fixed distribution over $\{1,\ldots,K,\}$ and the corresponding
+If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we consider a Poisson generative model.
+
+Specifically,  each $s[i]$ is drawn independently from a Poisson distribution with parameter $\gamma/L$, that is, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$  for some parameter $\gamma > 0$.
+ Then, each of those $s[i]$ is chosen independently at random from a fixed distribution over $\{1,\ldots,K\},$ and the corresponding
 signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$. 

### 2019-03-04 inverse_problems/inverse_problems.tex
middle of section 2 (in the model bias paragraph)

@@
 \section{Motivation: single-particle reconstruction using cryo-electron microscopy}
+
 Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
-In contrast X-ray and NMR which aggregate information from an ensembles of
-particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures simultaneously.
+%In contrast to X-ray and NMR which aggregate information from an ensembles of
+%particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures simultaneously.
 %In addition, it does not require the formation of crystalline arrays of macromolecules.
-
 In a cryo--EM experiment, biological samples (e.g., macromolecules, viruses) are rapidly frozen in a thin layer of vitreous ice.
@@
 Each micrograph contains multiple tomographic projections of the samples at unknown locations and under unknown viewing directions.
-Importantly, the electron dose must be kept low to mitigate  radiation damage, leading to high noise levels.
+Importantly, the electron dose must be kept low to mitigate  radiation damage, inducing high noise levels.
 The goal is to construct 3-D models of the molecular structures from the micrographs. 
+Since  cryo-EM produces images of individual particles, it can, in principle, elucidate multiple  structures simultaneously.
+This is in clear contrast to  X-ray and NMR, which aggregate information from an ensembles of
+particles.
 
@@
 where tomographic projections are placed according to the signal $s$.
-In this model, the signal $x$ represents the 2-D tomographic projections of the 3-D structure taken from  random viewing directions according to (possibly unknown) distribution.
-In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation drawn from some unknown distribution and $P$ a tomographic projection, we have
+In this model, the signal $x$ represents 2-D tomographic projections of the 3-D structure taken from  random viewing directions according to (possibly unknown) distribution over $SO(3)$ (the group of 3-D rotations).
+In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation for $\omega\in SO(3)$, and $P$ a tomographic projection, we have
 \begin{equation}
@@
 
-All contemporary methods in the field split the reconstruction procedure into two main  stages.
-The first stage, called \emph{particle picking},  extracts the particle projections from the micrographs.
-Given the projections, the second stage aims to construct a 3-D model of the molecular structure, usually using a  expectation-maximization algorithm~\cite{scheres2012relion}.
+All contemporary methods for single particle reconstruction using cryo-EM  split the reconstruction procedure into two main  stages.
+The first stage, called \emph{particle picking},  detects and extracts the particle projections from the micrographs.
+Given the projections, the second stage aims to construct a 3-D model of the molecular structure, usually using an expectation-maximization algorithm~\cite{scheres2012relion}.
 %The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
 Crucially, reliable detection of individual particles is impossible in a highly noisy environment. This fact has been recognized early on by the cryo-EM community. 
-Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
+Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was established that particle picking is impossible for molecules below a certain weight (below~$\sim$50 kDa). 
 %The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
@@
 
-Another potential pitfall of particle picking is related  to \emph{model bias}, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
+Even if particle picking is feasible, it may suffer from a phenomenon called \emph{model bias}.
+The main mechanism leads most particle pickers is based on correlating the micrograph with several templates; areas with high correlation are identified as areas that  are likely to contain a projection (these are the picked particles).
+Clearly, the picked particles depend heavily on the chosen templates.
+The potential pitfall of model biased
+has been recognized early by the cryo-EM community~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
 In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.

### 2019-03-04 inverse_problems/inverse_problems.tex
section 2

@@
 Even if particle picking is feasible, it may suffer from a phenomenon called \emph{model bias}.
-The main mechanism leads most particle pickers is based on correlating the micrograph with several templates; areas with high correlation are identified as areas that  are likely to contain a projection (these are the picked particles).
-Clearly, the picked particles depend heavily on the chosen templates.
-The potential pitfall of model biased
-has been recognized early by the cryo-EM community~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}.
-In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
-It was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template~\cite{shatsky2009method}.
-In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles biases the reconstructed structure.
+The main mechanism guides  most particle pickers is based on correlating the micrograph with several templates; highly correlated areas are associated with projections (these are the picked particles).
+Clearly, the picked particles depend heavily on the chosen templates: different templates may lead to different picked particles, and thus to different 3-D structures.
+This potential pitfall 
+has been recognized early by the cryo-EM community~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding} and was  exemplified using the
+``Einstein from noise'' experiment~\cite{shatsky2009method}.
+%In this experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
+It was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
+ %In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles biases the reconstructed structure.
 %This model bias is common to all particle picking methods based on template matching.
@@
 
-A recent work of the authors suggests to bypass the particle picking stage and  reconstruct the 3-D structure directly from the micrograph~\cite{bendory2018toward}.
-Based on autocorrelation analysis it was shown that---at least in principle---the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.
-%The principle mathematical tool is  \emph{autocorrelation analysis}, described in detail in Section~\ref{sec:AC_analysis}.
-This goal of  the current paper is to provide a theoretical justification and numerical support  for the method proposed in~\cite{bendory2018toward}.  
-%In this context, the  models described above serve  as  an abstraction of the cryo-EM problem: the random signal $X$ discussed in Section~\ref{sec:extensions} can be thought of as 2-D random tomographic projections of the 3-D structure
-%taken according to some unknown distribution of the particles within the ice.
-
-% A similar abstraction has been proven itself to be useful in a similar context as described in the next section.
-
-%We mention that~\cite{bendory2018toward} was not the first paper to employ autocorrelation analysis to cryo-EM. 
-Autocorrelation analysis for cryo-EM traces back to the seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
-This paper proposed autocorrelation analysis for {3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
+A recent work of the authors suggests a methodology to bypass particle picking and  reconstruct the 3-D structure directly from the micrograph~\cite{bendory2018toward}.
+Based on autocorrelation analysis, it was shown that---at least in principle---the limits high noise regimes 
+impose on particle picking  do not necessarily translate into limits on 3-D reconstruction.
+The main goal of  this paper is to provide theoretical justification and numerical support  for this method.
+
+In the next section, we introduce autocorrelation analysis in detail, focusing on the multi-target detection model. 
+We mention that similar ideas in  cryo-EM trace back to the seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
+Kam proposed autocorrelation analysis for {3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
 Kam's method has been extended and employed in X-ray free electron lasers and cryo-EM~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
@@
 called   \emph{multi-reference alignment}~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
-We follows the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph as proposed in~\cite{bendory2018toward}.
-\TODO{Not sure about the location of the last paragraph.}
+We follows the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph~\cite{bendory2018toward}.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 3.1

@@
 In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation for $\omega\in SO(3)$, and $P$ a tomographic projection, we have
-\begin{equation}
+\begin{equation} \label{eq:cryoEM}
 x= P(R_\omega V).
@@
 $$
-
-In what follows, $x$ is the random variable corresponding to signal occurrences in $y$. In particular, for the model~\eqref{eq:model}, 
+%In what follows, $x$ is the random variable corresponding to signal occurrences in $y$.
+% In particular, for the model~\eqref{eq:model}, 
 %$x=x_k$ with probability $\pi_k$.
-%In particular, for
-$x$ is sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$, so that its autocorrelations are given in explicit form as:
+In particular, for
+$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$,  the autocorrelations are given in explicit form as:
 \begin{align}
@@
 \end{align}
-Explicit expressions of the autocorrelations for the more involved model of  cryo-EM are given in~\cite{bendory2018toward}.
+Explicit expressions of the autocorrelations for the more involved model of  cryo-EM~\eqref{eq:cryoEM} are given in~\cite{bendory2018toward}.
 
@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
-\begin{align}
-\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] = a_y^q[\ell_1, \ldots, \ell_{q-1}].
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+\begin{align}
+\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
 \end{align}
@@
 	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
-	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\ell[\ell], \label{eq:ac2_micrograph}\\
-	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\ell[\ell_1]+\ell[\ell_2]
-	+\ell[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
-\end{align}
-where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
+	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \label{eq:ac2_micrograph}\\
+	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
+	+\delta[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
+\end{align}
+where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
 Terms proportional to $\sigma^2$ are due to the noise.
@@
 We show in Section~\ref{sec:theory_homogeneous_well_separated} 
-that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case where $K = 1$ (all signal occurrences are the same).
+that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case $K = 1$ (all signal occurrences are the same).
 
@@
 \end{align}
-Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are independent and all distributed as $x$, we further find:
+Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are independent, we further find:
 \begin{align}
@@
 
-To address the second-order moments, we resort to the separation conditions. First, consider this expression:
+To address the second-order moments, we resort to the separation condition~\eqref{eq:spacing}. First, consider this expression:
 \begin{align*}
@@
 \begin{align}
-a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \ell[\ell] = \gamma a_x^2[\ell] + \sigma^2 \ell[\ell].
+a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \ell[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
 \end{align}
@@
 \begin{align}
-\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \ell[\ell_1 - \ell_2].
+\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \delta[\ell_1 - \ell_2].
 \end{align}
@@
 \begin{align}
-\sigma^2 \ell[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
-\end{align}
-Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \ell[\ell_1 - \ell_2]$.
+\sigma^2 \delta[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
+\end{align}
+Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \delta[\ell_1 - \ell_2]$.
 A similar reasoning for terms 6 and 7 yields this final formula for the third-order autocorrelations of $y$:
 \begin{align}
-a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \ell[\ell_1] + \ell[\ell_2] + \ell[\ell_1 - \ell_2] \right).
+a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \delta[\ell_1] + \delta[\ell_2] + \delta[\ell_1 - \ell_2] \right).
 \end{align}

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 3.2

@@
 %
-Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model.
+Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model~\eqref{eq:gamma}.
 
@@
 \label{eq:mean_micrograph2} \\
-a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \ell[\ell], 
+a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
 \label{eq:ac2_micrograph2} \\
@@
 \nonumber \\
-& \qquad + \gamma a_x^1 \sigma^2 \big(\ell[\ell_1]+\ell[\ell_2] +\ell[\ell_1-\ell_2] \big).
+& \qquad + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
 \label{eq:ac3_micrograph2}
@@
 
-We will denote by $\M_l$ the moment tensors of $x$:
+We will denote by $\M_q$ the moment tensors of $x$:
 %
@@
 \end{align}
-
-We obtain the autocorrelations $a_x^l$ of $x$ by averaging over a slice of the moment tensors:
+We obtain the autocorrelations $a_x^q$ of $x$ by averaging over a slice of the moment tensors:
 %
@@
 
-First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
+First we will consider the noise-free case, where $\sigma = 0$. 
+Again, we will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
 %
@@
 \end{align}
-
 Similarly, the expected values of terms (c) and (d) are:
@@
 & \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
-\sum_{1 \le k_1,k_2 \le S[q_1]} \sum_{k_3=1}^{s[q_2]}
+\sum_{1 \le k_1,k_2 \le s[q_1]} \sum_{k_3=1}^{s[q_2]}
 x_{(k_1)}^{q_1}[j_1] x_{(k_2)}^{q_1}[j_1 + \ell_1] x_{(k_3)}^{q_2}[j_3]   

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4 (first paragraph)

@@
 We begin this section by showing that in the homogeneous case ($K=1$) ,under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the signal $x$, $\gamma$ and $\sigma^2$.
-Then, we bound the maximal number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.
+Then, we bound from above the number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.
 
 Before that, we start by showing that in the homogeneous case a signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
- Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
-%
+ Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly by 
 \begin{equation}
 %
-z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
+z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]},
 \label{eq-uniqueness}
@@
 \end{equation}
+for $k = 0, \ldots, L-1$.
 This proves the following useful fact:
@@
 Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-%
-%In what follows, we show that in the homogeneous case $K=1$, the signal $x$, the parameter $\gamma$ and $\sigma^2$ are identified uniquely from the first three observed autocorrelations under both the well-separated and Poisson models.
-Then, we bound the maximal number of signals that can be recovered from  those autocorrelations in the heterogeneous case, and discuss extensions to multi-dimensional signals.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
Revised abstract

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 multiple times at unknown locations in a noisy measurement.
-In the low noise regime, one can estimate the signals by first detect their occurrences and then cluster them.
-However, in the high noise regime neither detection nor  clustering can be performed reliably and thus such a strategy is destined to fail.  
-By employing autocorrelation analysis, we show that the impossibility to detect and cluster signals' occurrences in high noise levels does not necessarily preclude signal estimation.
+In the low noise regime, one can estimate the signals by first detecting occurrences, then clustering and averaging them.
+In the high noise regime however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
+Notwithstanding, using autocorrelation analysis, we show that the impossibility to detect and cluster signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
 Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals.
-These autocorrelations can be estimated accurately in any noise level given sufficiently long measurement.
-To recover the signals from their autocorrelations, we suggest to solve a nonlinear least-squares. 
-We provide rigorous analysis for the special case in which a single signal appears multiple times in the data, and demonstrate numerically the effectiveness of the method in a variety of settings.
-
-The main goal of this work is to provide theoretical and numerical support for a recently proposed framework to elucidate 3-D structures of biological macromolecules using cryo-electron microscopy in extreme noise levels~\cite{bendory2018toward}.
+These autocorrelations can be estimated accurately at any noise level given a sufficiently long measurement.
+To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
+We provide analysis regarding well-posedness of the task, and demonstrate numerically the effectiveness of the method in a variety of settings.
+
+The main goal of this work is to provide theoretical and numerical support for a recently proposed framework to image 3-D structures of biological macromolecules using cryo-electron microscopy in extreme noise levels.
+% ~\cite{bendory2018toward}.
+-- not references in the abstract, except if cited in full; but we don't want to write "arxiv" here.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4.1

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
-We will show, however, that all parameters---$x, \gamma$ and $\sigma^2$---are still determined by the observed moments of $y$.
+We will show, however, that all parameters---$x, \gamma$ and $\sigma^2$---are still identified uniquely by the observed moments of $y$.
 
 First, we observe that if  the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
+The other direction is true as well: if $\gamma>0$ is known, then one can estimate $\sigma^2$.
  The proof is provided in Section~\ref{sec:proof_prop_gamma}.
@@
 \begin{proposition} \label{prop:gamma}
-	Let $\sigma > 0$ be fixed and assume that the separation condition~\eqref{eq:spacing} holds. If the mean of $x$ is nonzero, then  
+	Assume that the separation condition~\eqref{eq:spacing} holds and $K=1$ (a single signal). If the mean of $x$ is nonzero, then  
 	\begin{equation}
@@
 
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined.
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined simultaneously.
 For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
@@
 \begin{proposition} \label{prop:gamma_sigma}
-	Assume $L \geq 3$ and assume that the separation condition~\eqref{eq:spacing} holds. 
+	Assume $L \geq 3$, $K=1$ and assume that the separation condition~\eqref{eq:spacing} holds. 
 	Then, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
@@
 \begin{corollary}
+	Assume $L \geq 3$ and $K=1$.
 	Under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.

### 2019-03-05 inverse_problems/inverse_problems.tex
Many changes to Section 1 and a few to Section 3

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+
 \begin{document}
@@
 Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
-Let  $s[i]$ count the number of signals whose first element is positioned in $y[i]$. Each of those $s[i]$ is chosen according to some (possibly unknown) distribution over $\{1,\ldots,K\}$. 
+Let  $s[i]$ count the number of signal occurrences whose first entry is positioned at $y[i]$.
+Each of those $s[i]$ signals is chosen among $x_1, \ldots, x_K$ according to some (possibly unknown) distribution over $\{1,\ldots,K\}$.
 If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
@@
 \end{equation}
-where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of starting positions of $x_k$ in $y[i]$ so that $s =  s_1+\cdots+s_K$.
+where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of occurrences of $x_k$ starting at $y[i]$, so that $s =  s_1+\cdots+s_K$.
 Explicitly, with zero-based indexing, % and zero-padding out of bounds,
@@
 \end{align*}
+%We discuss generative models for $s_1, \ldots, s_K$ below.
+%
 The goal is  to estimate $x_1,\ldots,x_K$ from $y$. % while $s$ is the \emph{nuisance variable} of the problem.
 %We name this problem \emph{multi-target detection}.
-In parts of the paper, we focus on the case $K = 1$, called the \emph{homogeneous} case; the case $K > 2$ is called \emph{heterogeneous}.
+In parts of the paper, we focus on the case $K = 1$, called the \emph{homogeneous} case; the case $K \geq 2$ is called \emph{heterogeneous}.
 This idealized setup appears in several scientific applications, including structural biology~\cite{bendory2018toward} (as we detail below), spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive}, and system identification~\cite{ljung1998system}.
 
-In the low noise regime, a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve  standard deconvolution problems.
+In the low noise regime (small $\sigma$), a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve  standard deconvolution problems.
+
 Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
-This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper. In this setting, we refer to  $s_1,\ldots,s_K$  as \emph{nuisance variables}.
+This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper.
+In this setting, we refer to  $s_1,\ldots,s_K$  as \emph{nuisance variables}: knowing them would certainly help, but we do not aim to estimate them.
 
 In order to recover the signals in the high noise regime, we use autocorrelation analysis.
-In any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for sufficiently large  $N$. 
+At any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for sufficiently large  $N$. 
 This computation is straightforward and requires only one pass over the data.
 The underlying principle is to relate the autocorrelations of the observation $y$ to the autocorrelations of $x_1,\ldots,x_K$.
+
 Below we describe two generative models for $s$.  
-In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depend on $s_1,\ldots,s_K$ only through their expected sums, that is, the expected total number of occurrences of each signal.
+In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depends on $s_1,\ldots,s_K$ only through their expected sums, that is, the expected total number of occurrences of each signal.
 To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares (LS) problem as explained in Section~\ref{sec:numerics}.
@@
 The multi-target detection problem  is an instance of  
-\emph{blind deconvolution}---a longstanding problem arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few.
-Different variants of the blind deconvolution problem have been subject recently to a thorough  analysis~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
-In clear contrast to multi-target detection, these works focus on the low noise regime and aim at estimating both unknown signals.
+\emph{blind deconvolution}---a longstanding problem arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, to name a few.
+Different variants of the blind deconvolution problem have been thoroughly analyzed recently~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
+In clear contrast to multi-target detection, these works focus on the low noise regime and aim to estimate both unknown signals (in our setting, this means estimating both $x_k$'s and $s_k$'s).
 
@@
 \end{equation}
-In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free entries in the data.
-Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free (but still noisy) entries.
+In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free (but still noisy) entries in the data.
+Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free entries.
 This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
 Once $s$ is determined, for each position $i$ such that $s[i] = 1$, one of the signals $x_k$ is selected independently at random, and accordingly we set $s_k[i] = 1$.
-As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.
+As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ (for shifts up to $L-1$) are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.
+We detail this in Section~\ref{sec:AC_analysis}.
 
@@
 
-Specifically,  each $s[i]$ is drawn independently from a Poisson distribution with parameter $\gamma/L$, that is, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$  for some parameter $\gamma > 0$.
- Then, each of those $s[i]$ is chosen independently at random from a fixed distribution over $\{1,\ldots,K\},$ and the corresponding
-signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$. 
-As in the well-separated model, the autocorrelations under this model depend only on the signals and the parameter $\gamma$.
+Specifically, for each position $i$, the number $s[i]$ of signal occurrences starting at that position is drawn independently from a Poisson distribution with parameter $\gamma/L$, that is, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$ for some parameter $\gamma > 0$.
+Then, $s[i]$ is split into $s_1[i] + \cdots + s_K[i]$ by selecting $s[i]$ signals among $x_1, \ldots, x_K$, independently at random (with replacement) following a fixed distribution over $\{1,\ldots,K\}$.
+%and the corresponding signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$.  --- No need for this, since we already explained the convolution model.
+As for the well-separated model, the autocorrelations of $y$ under this model depend weakly on $s$ and $s_1, \ldots, s_K$, essentially through the parameter $\gamma$: see Section~\ref{sec:AC_analysis}.
 
@@
 
-Extending the problem setup and autocorrelation analysis to signals in more than one dimension is straightforward: see discussion in Section~\ref{sec:high_dimensions} and numerical experiments in Section~\ref{sec:numerics}.
+Extending the problem setup and autocorrelation analysis to signals in more than one dimension is straightforward: see the discussion in Section~\ref{sec:high_dimensions} and numerical experiments in Section~\ref{sec:numerics}.
 
 Likewise, it is easy to extend the model to situations where the signal occurrences are sampled from a general distribution rather than from a finite set of choices $x_1, \ldots, x_K$.
-In this setup, the goal is to estimate the distribution (possibly defined by a finite set of parameters).
+The finite setup corresponds to the following distribution for signal occurrences:
+\begin{align}
+	x \sim \sum_{k=1}^K \pi_k \delta[x - x_k],
+	\label{eq:heterogeneousdistribution}
+\end{align}
+where $\delta[x - x_k]$ is a Dirac delta (a point mass) located at $x_k$, and $(\pi_1, \ldots, \pi_K)$ encodes the discrete distribution over $\{1, \ldots, K\}$.
+In the generalized setup, the goal is to estimate the distribution (possibly defined by a finite set of parameters).
 In particular, this allows for continuous distributions of targets.
@@
 
-\section{Motivation: single-particle reconstruction using cryo-electron microscopy}
+\section{Connection with single-particle reconstruction via cryo-electron microscopy}
 
@@
 In what follows, we consider autocorrelations of both the observation $y$ and of the signal occurrences in $y$.
-As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$, or from a more general distribution.
-Accordingly, we define autocorrelations for a random signal $z$ of length $M$ .
+As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$ (as in~\eqref{eq:heterogeneousdistribution}), or from a more general distribution.
+Accordingly, we define autocorrelations for a random signal $z$ of length $M$.
 For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
@@
 In particular, for
-$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$,  the autocorrelations are given in explicit form as:
+$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations are given in explicit form as:
 \begin{align}

### 2019-03-05 inverse_problems/inverse_problems.tex
Modifications to Section 2

@@
 The goal is to construct 3-D models of the molecular structures from the micrographs. 
-Since  cryo-EM produces images of individual particles, it can, in principle, elucidate multiple  structures simultaneously.
+Since  cryo-EM produces images of individual particles, it can elucidate multiple  structures simultaneously.
 This is in clear contrast to  X-ray and NMR, which aggregate information from an ensembles of
@@
 
-A 2-D micrograph $y$ can be written in terms 
-of the models described in Section~\ref{sec:intro} as
-\begin{equation}  \label{eq:model_cryo}
-y  =   s \ast x + \varepsilon,
-\end{equation}
-where tomographic projections are placed according to the signal $s$.
-In this model, the signal $x$ represents 2-D tomographic projections of the 3-D structure taken from  random viewing directions according to (possibly unknown) distribution over $SO(3)$ (the group of 3-D rotations).
-In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation for $\omega\in SO(3)$, and $P$ a tomographic projection, we have
-\begin{equation} \label{eq:cryoEM}
-x= P(R_\omega V).
-\end{equation}
-By allowing $V$ to be a random signal as well, this model can encode a mixture of structures  
-(which might be continuous as well).
+Considering the extensions described in the previous section, we can phrase a simplified generative model for micrographs (the observation $y$) within our framework.
+Specifically, locations are chosen in the 2-D plane of the image, corresponding to $s$: this is where the molecules are fixed in the plane of the ice layer.
+At each selected location, a 2-D tomographic projection of a molecule (a signal occurrence) is added in the observation $y$.
+This signal is drawn from a probability distribution described by a discrete number of parameters which correspond to the sought 3-D structure, as follows.
+
+The 3-D structure $V$ (the target parameter) can be expanded into a linear combination of basis functions (for example, spherical harmonics for the spherical part and Bessel functions for the radial part): the coefficients of this expansion are the unknowns.
+Then, a rotation $R_\omega$ is applied to the volume (to model viewing directions) according to a (possibly unknown) distribution of $\omega$ over $SO(3)$ (the group of 3-D rotations).
+With tomographic projection denoted by $P$, we have the following probability distribution for particles in the micrograph:
+\begin{align}
+	x & = P(R_\omega V).
+	\label{eq:cryoEM}
+\end{align}
+By further allowing $V$ itself to be a random signal as well, this model can also encode a mixture of structures in the biological sample.
+This mixture might also be continuous, corresponding to continuous conformational variability.
 
@@
 Crucially, reliable detection of individual particles is impossible in a highly noisy environment. This fact has been recognized early on by the cryo-EM community. 
-Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was established that particle picking is impossible for molecules below a certain weight (below~$\sim$50 kDa). 
+Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was reasoned that particle picking is impossible for molecules below a certain weight (below~$\sim$50 kDa). 
 %The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
@@
 
-Even if particle picking is feasible, it may suffer from a phenomenon called \emph{model bias}.
-The main mechanism guides  most particle pickers is based on correlating the micrograph with several templates; highly correlated areas are associated with projections (these are the picked particles).
-Clearly, the picked particles depend heavily on the chosen templates: different templates may lead to different picked particles, and thus to different 3-D structures.
-This potential pitfall 
-has been recognized early by the cryo-EM community~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding} and was  exemplified using the
-``Einstein from noise'' experiment~\cite{shatsky2009method}.
+Even if particle picking is feasible, procedures may be affected by \emph{model bias}.
+Particle picking algorithms are typically based on correlating the micrograph with several templates.
+Areas highly correlated with some of the templates are assumed to contain projections: these yield the picked particles.
+Clearly, the picked particles depend heavily on the chosen templates: different templates may lead to different picked particles, hence, which is more problematic, to different 3-D structure reconstructions.
+The cryo-EM community is well aware of this potential pitfall~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding}, which was notably exemplified in the ``Einstein from noise'' experiment~\cite{shatsky2009method}.
 %In this experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
@@
 impose on particle picking  do not necessarily translate into limits on 3-D reconstruction.
-The main goal of  this paper is to provide theoretical justification and numerical support  for this method.
+The main goal of  the present paper is to provide theoretical and numerical support for this approach, in a simplified setting.
 
 In the next section, we introduce autocorrelation analysis in detail, focusing on the multi-target detection model. 
-We mention that similar ideas in  cryo-EM trace back to the seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
-Kam proposed autocorrelation analysis for {3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
-Kam's method has been extended and employed in X-ray free electron lasers and cryo-EM~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
+We mention that similar ideas in  cryo-EM can be traced back to a seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
+Kam proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
+Kam's method has been extended and used in X-ray free electron lasers (XFEL) and cryo-EM~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
 In order to investigate the computational and statistical properties of Kam's method, a series of papers have studied a simplified model, 
 called   \emph{multi-reference alignment}~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
-We follows the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph~\cite{bendory2018toward}.
+We follow the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph~\cite{bendory2018toward}.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
Pointed out some issues in intro of Section 3

@@
 As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$ (as in~\eqref{eq:heterogeneousdistribution}), or from a more general distribution.
-Accordingly, we define autocorrelations for a random signal $z$ of length $M$.
+Accordingly, we define autocorrelations broadly for a random signal $z$ of length $M$.
 For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $z$. Indexing of $z$ out of the range $0, \ldots, M-1$ is zero-padded.
+where the expectation is taken with respect to the distribution of $z$. Indexing out of bounds is zero-padded, that is, $z[i] = 0$ for $i$ out of the range $0, \ldots, M-1$.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
@@
 In particular, for
-$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations are given in explicit form as:
+$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations of $x$ are given in explicit form in terms of those of the deterministic signals $x_1, \ldots, x_K$ as:
 \begin{align}
@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant \TODO{We didn't define $\gamma$ for the well-separated model at this point; we should reconsider this}, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
 \begin{align}

### 2019-03-05 inverse_problems/inverse_problems.tex
Cosmetic changes working on Section 3.1

@@
 \begin{align}
-	x \sim \sum_{k=1}^K \pi_k \delta[x - x_k],
+	x \sim \sum_{k=1}^K \pi_k \delta(x - x_k),
 	\label{eq:heterogeneousdistribution}
 \end{align}
-where $\delta[x - x_k]$ is a Dirac delta (a point mass) located at $x_k$, and $(\pi_1, \ldots, \pi_K)$ encodes the discrete distribution over $\{1, \ldots, K\}$.
+where $\delta(x - x_k)$ is a Dirac delta (a point mass) located at $x_k$, and $(\pi_1, \ldots, \pi_K)$ encodes the discrete distribution over $\{1, \ldots, K\}$.
 In the generalized setup, the goal is to estimate the distribution (possibly defined by a finite set of parameters).
@@
 where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
-Terms proportional to $\sigma^2$ are due to the noise.
+Terms proportional to $\sigma^2$ are due to noise.
 If $\sigma$ is known, they can be handled easily.

### 2019-03-05 inverse_problems/inverse_problems.tex
Further changes and notes in Sections 3.1, 3.2

@@
 that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case $K = 1$ (all signal occurrences are the same).
+\TODO{Do we also need to say "for generic $x$" here, as in Poisson?}
 
@@
 \begin{align}
-\frac{N - L + 1}{N} \cdot L \cdot \frac{\gamma  }{L} 
+\frac{N - L + 1}{N} \cdot \frac{\gamma  }{L}  \cdot L 
 \quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
@@
 %
-Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model~\eqref{eq:gamma}.
+Therefore, in the large $N$ limit, similarly to the role of $\gamma$ in the well-separated model~\eqref{eq:gamma}, $\gamma$ may be interpreted as the signal density.
 
 In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
-As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on $x$ itself, and the parameters $\gamma$ and $\sigma$:
-%
-\begin{align}
-a_y^1  &=  \gamma a_{x}^1, 
-\label{eq:mean_micrograph2} \\
-a_y^2[\ell] &=  (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[\ell], 
-\label{eq:ac2_micrograph2} \\
-a_y^3[\ell_1,\ell_2]  & = (\gamma a_x^1)^3 + \gamma a_x^1  
-\cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2]
-+ \gamma a_x^2[\ell_2-\ell_1]) + \gamma a_x^3[\ell_1,\ell_2] 
-\nonumber \\
-& \qquad + \gamma a_x^1 \sigma^2 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big).
-\label{eq:ac3_micrograph2}
-\end{align}
-
+As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$: \TODO{Do these identities hold even without taking a limit?
+I guess so, but let's be sure.}
+%
+\begin{align}
+	a_y^1  & =  \gamma a_{x}^1, \label{eq:mean_micrograph2} \\
+	a_y^2[\ell] & = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell] + (\gamma a_x^1)^2, \label{eq:ac2_micrograph2} \\
+	a_y^3[\ell_1,\ell_2]  & =  \gamma a_x^3[\ell_1,\ell_2] + \sigma^2 \gamma a_x^1 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big) \nonumber \\
+						  & \qquad + (\gamma a_x^1)^3 + \gamma a_x^1 \cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2] + \gamma a_x^2[\ell_2-\ell_1]). \label{eq:ac3_micrograph2}
+\end{align}
 In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4.2

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$ (as in~\eqref{eq:heterogeneousdistribution}), or from a more general distribution.
-Accordingly, we define autocorrelations broadly for a random signal $z$ of length $M$.
+Accordingly, we define autocorrelations for a random signal $z$ of length $M$.
 For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $z$. Indexing out of bounds is zero-padded, that is, $z[i] = 0$ for $i$ out of the range $0, \ldots, M-1$.
+where the expectation is taken with respect to the distribution of $z$. Indexing of $z$ out of the range $0, \ldots, M-1$ is zero-padded.
 Explicitly, the first-, second- and third-order autocorrelations are given by: 
@@
 In particular, for
-$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations of $x$ are given in explicit form in terms of those of the deterministic signals $x_1, \ldots, x_K$ as:
+$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations are given in explicit form as:
 \begin{align}
@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant \TODO{We didn't define $\gamma$ for the well-separated model at this point; we should reconsider this}, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
 \begin{align}
@@
 Similarly to the homogeneous well-separated model, the observed autocorrelations under the Poisson model identify $x,\gamma$ and $\sigma^2$ uniquely.
-Furthermore, these quantities can be computed explicitly.
-
-We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
- Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
-%
-\begin{align}
-\gamma a_x^3[\ell_1,\ell_2]
-= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
-- a_y^1 \cdot \big(a_y^2[\ell_1]  
-+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
-\end{align}
-Using these expressions, we prove the following in Section~\ref{sec:proof_uniqueness_poisson}.
+Opposed to Proposition~\ref{prop:gamma_sigma}, these quantities can be computed explicitly. 
+In Section~\ref{sec:proof_uniqueness_poisson} we prove the following result:
+%
+%We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
+% Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+%%
+%\begin{align}
+%\gamma a_x^3[\ell_1,\ell_2]
+%= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
+%- a_y^1 \cdot \big(a_y^2[\ell_1]  
+%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
+%\end{align}
+%Using these expressions, we prove the following in Section~\ref{sec:proof_uniqueness_poisson}.
 \begin{proposition} \label{prop:uniqueness_poisson}
-Under the homogeneous Poisson model, the signal $x$, and the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
-In particular, 
-	\begin{align}
-\gamma &= L \frac{(\gamma a_y^1) (\gamma a_x^2[1])}
+Under the homogeneous Poisson model, the signal $x$, the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
+In particular, \TODO{Shouldn't it be $L^2$ for $\gamma$?}
+	\begin{align}
+\gamma &= L \frac{(\gamma a_y^1) (a_y^2[1] - (a_y^1)^2)}
 {\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
@@
 \sigma^2 &= a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-- (2 L - 1) (a_y^1)^2.
-\end{align}
+- (2 L - 1) (a_y^1)^2,
+\end{align}
+where 
+\begin{align}
+\gamma a_x^3[\ell_1,\ell_2]
+&= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
+- a_y^1 \cdot \big(a_y^2[\ell_1]  
++ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
+\end{align}
+
 \end{proposition}
 
-\subsection{Elemetary limitations of the heterogeneous case}
+\subsection{Elementary limitations of the heterogeneous case}
 \label{sec:heterogeneity}
@@
 \subsection{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
+
+We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
+Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
+%
+\begin{align}
+\gamma a_x^3[\ell_1,\ell_2]
+= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
+- a_y^1 \cdot \big(a_y^2[\ell_1]  
++ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
+\end{align}
+
 	Let us assume that $x$ is generic. Indeed, we observe the product:
@@
 	\nonumber \\
-	&= \gamma\left\{ \sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell]
-	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]  \right\}.
-	\end{align}
-	%
-	Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$, and then $\sigma^2$:
+	&= \gamma\left( \sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell]
+	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]  \right).
+	\end{align}
+	%
+	Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$.
 
@@
 	%
+	Then, similarly to Section~\ref{sec:proof_prop_gamma}, one can solve for $\sigma^2$:
 	\begin{align}
@@
 \section*{Acknowledgment} \TODO{To check}
-The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions..
+The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
 The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4.3

@@
 The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$. 
+For the heterogeneous model~\eqref{eq:model},  one can define
+\begin{equation}
+\gamma_k  = \frac{|s_k| L}{N},
+\label{eq:gamma_k}
+\end{equation}
+where $\vert s_k\vert = \sum_i s_k[i]$ so that $\gamma=\sum_k \gamma_k$.
 
@@
 
-\subsection{Autocorrelations under the Poisson model}
+\subsection{Autocorrelations under the Poisson model} \label{sec:ac_poisson}
 
@@
 \end{align}
+Note that from those autocorrelations, it is easy to retrieve the autocorrelations of the well-separated model for all entries unaffected by $\sigma$.
+If $\sigma$ is known, then it is true for all entries.
+\TODO{addition}
+
 In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
+
 %
@@
 
-\TODO{Check and specify if this holds for both models}
-\TODO{Did we define densities $\gamma_k$?}
-\TODO{We write the section for the well-separated model, but it would be the same for the Poisson model}
-
-In the heterogeneous model~\eqref{eq:model}, the unknowns are $K$ signals of length $L$, together with their densities $\gamma_1, \ldots, \gamma_K$ (equivalently: the distribution $\pi$ and overall density $\gamma$) and possibly the noise level $\sigma$.
+\TODO{Check and specify if this holds for both models: see below}
+
+\TODO{Did we define densities $\gamma_k$? TB: yes, in section 3}
+
+In the heterogeneous model~\eqref{eq:model}, the unknowns are $K$ signals of length $L$, together with their densities $\gamma_1, \ldots, \gamma_K$~\eqref{eq:gamma_k} (equivalently: the distribution $\pi$ and overall density $\gamma$) and possibly the noise level $\sigma$.
 To estimate these parameters, we must collect at least as many independent equations.
@@
 This is only an upper bound, though a bound of the same type was shown to be tight in a similar setting~\cite{bandeira2017estimation}.
+The counting is based on the autocorrelations of the well-separated model.
+For entries independent of $\sigma$, the autocorrelations of the Poisson process are equivalent to those of the well-separated model.
+If $\sigma$ is known, it holds true for all entries; see Section~\ref{sec:ac_poisson}.
 
@@
 \end{align*}
-equations in total. Of course, there may be redundancy in these equations: we aim only to provide a bound, under the assumption that these equations are independent.
-
-Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$ plus $K$ parameters for the densities $\gamma_k$ (or the distribution $\pi$ and overall density $\gamma$), there are $K(L+1)$ unknowns.
-As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
+equations in total. Of course, there may be redundancy in these equations: we aim only to provide an upper bound. %under the assumption that these equations are independent.
+
+Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$ plus $K$ parameters for the densities $\gamma_k$, %(or the distribution $\pi$ and overall density $\gamma$)
+ there are $K(L+1)$ unknowns. As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
 \begin{align*}

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4.4

@@
 
-Autocorrelations in $d$ dimensions is defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
+Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{m^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{M^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
 \label{eq:ac_d_dimension}
@@
 In this context, the computational problem of recovering the signal from its second-order autocorrelation is usually referred to as \emph{phase retrieval} or the \emph{phase problem}.
-Despite the uniqueness result, recently it has been shown that, the problem is  ill-conditioned, at least for 2-D images~\cite{barnett2018geometry}.
-That is, there exist different images whose second-order autocorrelations agree up to machine precision.
+Despite the uniqueness result, recently it has been shown that the problem is  ill-conditioned---at least for 2-D images~\cite{barnett2018geometry}.
+That is, there exist other images whose second-order autocorrelations agree up to machine precision.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
small modifications sec 4

@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant \TODO{We didn't define $\gamma$ for the well-separated model at this point; we should reconsider this}, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
-\begin{align}
-\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
-\end{align}
-\TODO{Why do we need constant $\gamma$?}
+However, by the law of large numbers, as $N$ grows to infinity  the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+\begin{align}
+\lim_{N \to \infty} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
+\end{align}
 This provides a concrete means of estimating the quantities $a_y^ q$.
@@
 If $\sigma$ is known, then it is true for all entries.
-\TODO{addition}
 
@@
 \label{sec:heterogeneity}
-
-\TODO{Check and specify if this holds for both models: see below}
-
-\TODO{Did we define densities $\gamma_k$? TB: yes, in section 3}
 

### 2019-03-05 inverse_problems/inverse_problems.tex
section 5.1

@@
 In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depends on $s_1,\ldots,s_K$ only through their expected sums, that is, the expected total number of occurrences of each signal.
-To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares (LS) problem as explained in Section~\ref{sec:numerics}.
+To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares problem as explained in Section~\ref{sec:numerics}.
 
@@
 Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedure, which is empirically more robust to additive noise; we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 
@@
 In the last experiment, we extend our model to 2-D signals.
+The code for all experiments is available at \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}. \TODO{Need to upload the code}
 
@@
 	\caption{Experiment described in Section~\ref{sec:XP1}.
-For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed density and occurrence probabilities.
+For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed d occurrence probabilities.
 Each rows corresponds to one of the signals.
@@
 More precisely, the cross-correlations of $y$ even with the true signals presents peaks at essentially random locations, apparently uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to classify them according to which signal appears where.
-
-%Given the observation $y$, we proceed to compute the autocorrelations.
-The first-order autocorrelation is straightforward.
-For second-order autocorrelations, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$.
-Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to make sense of the computed quantities.
-Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), and we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
-We have
-%\begin{align*}
-%1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-%\end{align*}
-%coefficients in total.
-Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$ (simply to ensure we have at least as many equations as we have unknowns) is
-%\begin{align*}
-%K(L+1) \leq \frac{1}{2} L (L-1) + 1.
-%\end{align*}
-%Thus, $(L-1)/2$ (up to a small approximation) is an absolute upper limit on $K$ (compare with~\cite{boumal2017heterogeneous,bandeira2017estimation}).
+Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to cluster them according to which signal appears where.
 
@@
 
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problems appears to have numerous poor local optimizers.
+Setting $W = L$ (as is a priori desired) is problematic because the above optimization problem appears to have numerous poor local optimizers.
 Thus, we first run the optimization with $W = 2L-1$.
@@
 
-In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly preempts location and classification.
+In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly preempts location and clustering.
 We also note that the amount of data required to produce these good estimations is large.

### 2019-03-05 inverse_problems/inverse_problems.tex
section 5.2

@@
 Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals according to~\eqref{eq:spacing}.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint and locations picked so far.
+This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint~\eqref{eq:spacing} and locations picked so far.
 For each placement, one of the three signals is picked at random according to the proportions $\pi = (1/2, 1/3, 1/6)$.
@@
 	\includegraphics[width=.7\linewidth]{KLXP/XP1}
-	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
-CPU time in seconds.
-Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments.
-Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
+	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems that $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
+CPU time is in seconds.
+Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed autocorrelation; see Section~\ref{sec:heterogeneity}.
+Similarly to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
 	\label{fig:KLXP}
@@
 The specific value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
-Furthermore, we assume uniform occurrence distribution $\pi$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
+Furthermore, we assume uniform occurrence distribution $\gamma_k$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
 
@@
 
-Following~\cite{boumal2017heterogeneous}, overlaid on the panels we trace the red curve $K = \sqrt{L}$ as well as red dots which are computed from the considerations in Section~\ref{sec:heterogeneity} (adapted to the fact that $\pi$ and $\gamma$ are known).
+Following~\cite{boumal2017heterogeneous}, overlaid on the panels we trace the red curve $K = \sqrt{L}$ as well as red dots which are computed from the considerations in Section~\ref{sec:heterogeneity} (adapted to the fact that the $\gamma_k$'s are known).
 We observe that strictly above the red dots the optimization problem appears to be easy to solve (despite non-convexity), yet, as predicted, the corresponding estimators are not informative since there is not enough information in the computed quantities compared to the number of parameters.

### 2019-03-05 inverse_problems/inverse_problems.tex
section 5.3
Quick change in intro of section 4

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity  the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
-\begin{align}
-\lim_{N \to \infty} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
-\end{align}
+However, by the law of large numbers, as $N$ grows to infinity with $\gamma$ remaining constant \TODO{We didn't define $\gamma$ for the well-separated model at this point; we should reconsider this}, the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+\begin{align}
+\lim_{N \to \infty, \gamma \textrm{ constant}} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
+\end{align}
+\TODO{Why do we need constant $\gamma$?}
 This provides a concrete means of estimating the quantities $a_y^ q$.
@@
 If $\sigma$ is known, then it is true for all entries.
+\TODO{addition}
 
@@
 
-We begin this section by showing that in the homogeneous case ($K=1$) ,under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the signal $x$, $\gamma$ and $\sigma^2$.
-Then, we bound from above the number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.
+We begin this section by showing that, in the homogeneous case ($K=1$), under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the (deterministic) signal $x$, the density parameter $\gamma$, and the noise level $\sigma^2$.
+Then, for the heterogeneous case ($K \geq 2$), we bound from above the number $K$ of signals that can be recovered from those autocorrelations as a function of $L$.
+Finally, we briefly discuss multi-dimensional signals.
 
@@
 \label{sec:heterogeneity}
+
+\TODO{Check and specify if this holds for both models: see below}
+
+\TODO{Did we define densities $\gamma_k$? TB: yes, in section 3}
 

### 2019-03-05 inverse_problems/inverse_problems.tex

--- 2019-03-05 inverse_problems/inverse_problems.tex
@@
 Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
-\TODO{As explained in Section~\ref{sec:high_dimensions}---careful if we decide to edit}, an image is determined uniquely form its second-order autocorrelations.
+As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelations.
 Then, to estimate the target image, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.

### 2019-03-05 inverse_problems/inverse_problems.tex
Edits to intro of §4 and in particular for Prop. 4.1

@@
 We begin this section by showing that, in the homogeneous case ($K=1$), under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the (deterministic) signal $x$, the density parameter $\gamma$, and the noise level $\sigma^2$.
-Then, for the heterogeneous case ($K \geq 2$), we bound from above the number $K$ of signals that can be recovered from those autocorrelations as a function of $L$.
+Then, for the heterogeneous case ($K \geq 2$), we bound from above the number $K$ of signals that can be recovered from those autocorrelations as a function of the signal length $L$.
 Finally, we briefly discuss multi-dimensional signals.
 
-Before that, we start by showing that in the homogeneous case a signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
- Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly by 
+Before that, we start by showing that in the homogeneous case a deterministic signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
+ Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero, we can recover $z$ explicitly by 
 \begin{equation}
@@
 \end{equation}
-for $k = 0, \ldots, L-1$.
+for $k = 0, \ldots, L-1$. If $z[0]$ or $z[L-1]$ are equal to zero, then $a_z^2[L-1] = 0$ and we can use that indication to redefine $L$.
 This proves the following useful fact:
@@
 	%
-	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. 
+	A deterministic signal $z\in\RL$ is determined uniquely by  $a_z^2$ and $a_z^3$. 
 \end{proposition}
@@
 Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedure, which is empirically more robust to additive noise; we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
+In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedure, which is empirically robust to additive noise.
+In prior work, we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
Added details to Proof of Prop. 4.2

@@
 
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the ratio $\gamma$.
+The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the signal density $\gamma$.
 We will show, however, that all parameters---$x, \gamma$ and $\sigma^2$---are still identified uniquely by the observed moments of $y$.
@@
 \begin{proposition} \label{prop:gamma}
-	Assume that the separation condition~\eqref{eq:spacing} holds and $K=1$ (a single signal). If the mean of $x$ is nonzero, then  
+	Assume the separation condition~\eqref{eq:spacing} holds and $K=1$ (all signal occurrences in $y$ are identical, up to noise). If the mean of $x$ is nonzero, then  
 	\begin{equation}
@@
 \subsection{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
-First,  note that 
-\begin{equation*}
-(a^1_y)^2=\frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j].
-\end{equation*}
-Similarly,  
-\begin{equation*}
-\sum_{\ell = 1}^{L-1}a_y^2[\ell]=\frac{\gamma}{L}\sum_{\ell = 1}^{L-1}\sum_{i=0}^{L-1-\ell}x[i]x[i+\ell],
-\end{equation*}
-and $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x^2[i] + \sigma^2$. The proof is concluded by noting that  $a_x^2[-\ell]=a_x^2[\ell]$.
+Refer to equations \eqref{eq:mean_micrograph}--\eqref{eq:ac3_micrograph} for expressions relating the moments of $y$ and those of $x$, and the parameters $\gamma$ and $\sigma$. First,  note that 
+\begin{align*}
+	(a^1_y)^2 & = \frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j].
+\end{align*}
+Similarly, using $a_x^2[-\ell] = a_x^2[\ell]$:
+\begin{align*}
+	2\sum_{\ell = 1}^{L-1}a_y^2[\ell] & = \gamma \sum_{\ell = 1}^{L-1} a_x^2[\ell] + a_x^2[-\ell] \\
+									  & = \frac{\gamma}{L}\sum_{i=0}^{L-1}\sum_{\ell = 1}^{L-1} x[i]\left(x[i+\ell] + x[i-\ell]\right) = \frac{\gamma}{L} \sum_{i = 0}^{L-1} \sum_{j = 0, j \neq i}^{L-1} x[i] x[j],
+\end{align*}
+where the last equality is obtained by noting that, given the summation bounds, the set of pairs $(i, i\pm\ell)$ and $(i, j)$ are the same over the valid range $\{0, \ldots, L-1\}^2$.
+To conclude, notice that $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x[i]^2 + \sigma^2$ and combine.
 

### 2019-03-05 inverse_problems/inverse_problems.tex
Small changes to Section 4.1 + related proofs

@@
 	\begin{equation}
-	\gamma  = \frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2}.
+	\gamma  = \frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2},
 	\end{equation}
+	meaning $\gamma$ can be determined from $\sigma$ (and vice versa) using the observables $a_y^1, a_y^2$.
 \end{proposition}
 
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ are determined simultaneously.
+Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ can be determined simultaneously.
 For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
@@
 In particular, this means that we can recover
-almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
+almost all signals with the given measurements. The proof is provided in Section~\ref{sec:proof_prop_gamma_sigma}.
 
@@
 
-Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones.  Consider the product:
+Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones and $\|x\|=\sqrt{x[0]^2 + \cdots + x[L-1]^2}$ is the 2-norm.
+Consider the product $E_1$:
 \begin{equation}\label{eq:E1}
 \begin{split}
-E_1 := a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2)  = \sigma^2a_y^1 + L\beta^2F_1,
+E_1 = a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2)  = \sigma^2a_y^1 + L\beta^2F_1,
 \end{split}
 \end{equation}
-where $F_1 := a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
+where $F_1 = a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
 % Nicolas: the expression for F_1 is correct, see identifiability_of_gamma_and_sigma_Sep4_2018.m and notes Sep 4, 2018
-The terms of $F_1$ can also be estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable:
-\begin{align} 
-E_2 & := a_y^3[0,0] + \sum_{j=1}^{L-1}(a_y^3[j,j] + a_y^3[0,j]) \nonumber\\
-& = L\beta F_1 + (2L+1)\sigma^2a_y^1. \label{eq:E2}
+The terms of $F_1$ can also be estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable, $E_2$:
+\begin{align} 
+E_2 & = a_y^3[0,0] + \sum_{j=1}^{L-1}(a_y^3[j,j] + a_y^3[0,j]) = L\beta F_1 + (2L+1)\sigma^2a_y^1. \label{eq:E2}
 \end{align}
@@
 \end{equation}
-Let $E_3:=a_y^2[0] + 2\sum_{j = 1}^{L-1}a_y^2[j]$; recall from Proposition~\ref{prop:gamma}:
+Let $E_3 =a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]$; recall from Proposition~\ref{prop:gamma}:
 \begin{equation} \label{eq:sigma2}
@@
 \begin{equation} \label{eq:E3}
-E_4 := \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
+E_4 = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
 \end{equation}
@@
 \begin{align}
-E_5 & := a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j]  = L \beta F_2 + (6L-3)\sigma^2a_y^1.
+E_5 & = a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j]  = L \beta F_2 + (6L-3)\sigma^2a_y^1.
 \end{align}

### 2019-03-05 inverse_problems/inverse_problems.tex
Minor changes

@@
 The counting is based on the autocorrelations of the well-separated model.
-For entries independent of $\sigma$, the autocorrelations of the Poisson process are equivalent to those of the well-separated model.
-If $\sigma$ is known, it holds true for all entries; see Section~\ref{sec:ac_poisson}.
+For entries independent of $\sigma$, the autocorrelations of the Poisson process contain the same information as those of the well-separated model.
+If $\sigma$ is known, this holds true for all entries: see Section~\ref{sec:ac_poisson}.
 
@@
 For second-order autocorrelations $a_y^2[\ell]$~\eqref{eq:ac2_micrograph}, if $\sigma$ is known we obtain $L$ equations with $\ell$ ranging from 0 to $L-1$.
-If $\sigma$ is unknown, we may disregard $a_y^2[0]$ (then only entry affected by $\sigma$) and still collect $L-1$ equations.
+If $\sigma$ is unknown, we may disregard $a_y^2[0]$ (the only entry affected by $\sigma$) and still collect $L-1$ equations.
 Similarly, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$~\eqref{eq:ac3_micrograph} with $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), providing $\frac{(L+1)(L+2)}{2}-2$ equations in total.
@@
 
-Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$ plus $K$ parameters for the densities $\gamma_k$, %(or the distribution $\pi$ and overall density $\gamma$)
+Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$, plus $K$ parameters for the densities $\gamma_k$, %(or the distribution $\pi$ and overall density $\gamma$)
  there are $K(L+1)$ unknowns. As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
 \begin{align*}
-	K \leq \frac{L(L+5)}{2(L+1)},
+	K \leq \frac{L(L+5)}{2(L+1)}
 \end{align*}
@@
 
-Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
+Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as \TODO{in equation below, should M be L?}
 \begin{equation}
@@
 Interestingly, for the homogeneous case ($K=1$) in dimensions greater than one, almost all  signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-If the mean of signal is available and non-zero, the sign symmetry can be resolved.
+If the mean of the signal is available and non-zero, the sign symmetry can be resolved.
 However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-The case of 1-D signals is essentially different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
+The case of 1-D signals is fundamentally different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
 
@@
 This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT), in parallel over the numerous observations.
-To  keep things simple, we assume the number of signal occurrences (akin to the density $\gamma$) and the standard deviation of the noise, $\sigma$, are known.
+We assume the number of signal occurrences (akin to the density $\gamma$) and the standard deviation of the noise, $\sigma$, are known.
 Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.

### 2019-03-06 inverse_problems/inverse_problems.tex
minor changes

@@
 that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case $K = 1$ (all signal occurrences are the same).
-\TODO{Do we also need to say "for generic $x$" here, as in Poisson?}
+%\TODO{Do we also need to say "for generic $x$" here, as in Poisson?}
 
@@
 In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
-As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$: \TODO{Do these identities hold even without taking a limit?
+As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$: %\TODO{Do these identities hold even without taking a limit?
 I guess so, but let's be sure.}
@@
 
-Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as \TODO{in equation below, should M be L?}
+Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
 \begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{M^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
+a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{L^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
 \label{eq:ac_d_dimension}
@@
 	2\sum_{\ell = 1}^{L-1}a_y^2[\ell] & = \gamma \sum_{\ell = 1}^{L-1} a_x^2[\ell] + a_x^2[-\ell] \\
-									  & = \frac{\gamma}{L}\sum_{i=0}^{L-1}\sum_{\ell = 1}^{L-1} x[i]\left(x[i+\ell] + x[i-\ell]\right) = \frac{\gamma}{L} \sum_{i = 0}^{L-1} \sum_{j = 0, j \neq i}^{L-1} x[i] x[j],
+									  & = \frac{\gamma}{L}\sum_{i=0}^{L-1}\sum_{\ell = 1}^{L-1} x[i]\left(x[i+\ell] + x[i-\ell]\right) \\ &= \frac{\gamma}{L} \sum_{i = 0}^{L-1} \sum_{j = 0, j \neq i}^{L-1} x[i] x[j],
 \end{align*}

### 2019-03-08 inverse_problems/inverse_problems.tex
sec 1
sec 2+3

@@
 In the low noise regime (small $\sigma$), a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve  standard deconvolution problems.
-
 Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
@@
 
-If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we consider a Poisson generative model.
+If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we analyze a Poisson generative model.
 
@@
 %
-Therefore, in the large $N$ limit, similarly to the role of $\gamma$ in the well-separated model~\eqref{eq:gamma}, $\gamma$ may be interpreted as the signal density.
+Therefore, in the large $N$ limit, similarly to the role of $\gamma$ in the well-separated model~\eqref{eq:gamma}, the parameter $\gamma$ may be interpreted as the signal density.
 

### 2019-03-08 inverse_problems/inverse_problems.tex
sec 4.1

@@
 Specifically, for each position $i$, the number $s[i]$ of signal occurrences starting at that position is drawn independently from a Poisson distribution with parameter $\gamma/L$, that is, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$ for some parameter $\gamma > 0$.
-Then, $s[i]$ is split into $s_1[i] + \cdots + s_K[i]$ by selecting $s[i]$ signals among $x_1, \ldots, x_K$, independently at random (with replacement) following a fixed distribution over $\{1,\ldots,K\}$.
+Then, $s[i]$ is split into $s_1[i] + \cdots + s_K[i]$ by selecting $s[i]$ signals among $x_1, \ldots, x_K$, independently at random  following a fixed distribution over $\{1,\ldots,K\}$.
+It is possible for more than one occurrence of the same $x_k$ to start at the same position~$i$.
 %and the corresponding signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$.  --- No need for this, since we already explained the convolution model.
@@
 	Assume $L \geq 3$ and $K=1$.
-	Under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
+	Under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic, or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
 \end{corollary}

### 2019-03-08 inverse_problems/inverse_problems.tex
replying to Amit's comments

@@
 In Section~\ref{sec:proof_uniqueness_poisson} we prove the following result:
-%
-%We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
-% Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
-%%
-%\begin{align}
-%\gamma a_x^3[\ell_1,\ell_2]
-%= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
-%- a_y^1 \cdot \big(a_y^2[\ell_1]  
-%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
-%\end{align}
-%Using these expressions, we prove the following in Section~\ref{sec:proof_uniqueness_poisson}.
+
 \begin{proposition} \label{prop:uniqueness_poisson}
 Under the homogeneous Poisson model, the signal $x$, the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
-In particular, \TODO{Shouldn't it be $L^2$ for $\gamma$?}
+In particular,
 	\begin{align}
@@
 \end{align*}
-equations, while if it unknown and we choose not to estimate it, then we collect
+equations, while if it is unknown and we choose not to estimate it, then we collect
 \begin{align*}
@@
 In the last experiment, we extend our model to 2-D signals.
-The code for all experiments is available at \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}. \TODO{Need to upload the code}
+The code for all experiments is available at \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
 
@@
 	\caption{Experiment described in Section~\ref{sec:XP1}.
-For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed d occurrence probabilities.
-Each rows corresponds to one of the signals.
+For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed  occurrence probabilities.
+Each row corresponds to one of the signals.
 The last column shows evolution of the relative root mean squared error in estimating each signal, as a longer and longer subset of $y$ is observed.
@@
 CPU time is in seconds.
-Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed autocorrelation; see Section~\ref{sec:heterogeneity}.
+Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed autocorrelations; see Section~\ref{sec:heterogeneity}.
 Similarly to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
@@
 
-\section*{Acknowledgment} \TODO{To check}
+\section*{Acknowledgment} 
 The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
-The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
+The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
 NB is partially supported by NSF award DMS-1719558.

### 2019-03-08 inverse_problems/inverse_problems.tex
sketch of summary section

@@
 
- %Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
-%
-%\begin{align}
-%\frac{N - L + 1}{N} \cdot L \cdot \frac{\gamma  }{L} 
-%\quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
-%\end{align}
-%
-%In particular, this model allows for (additive) signal overlap
-
-%Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$.
-For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$.
-%Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
-%By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$.
-In particular, this model allows for (additive) signal overlap.
-%In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.
-
- %More precisely,
- %Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model.
-
 \subsection*{Extensions} \label{sec:extensions}
@@
 As a result, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the density $\gamma$ (which is a weak dependence on the support signal $s$).
-Specifically, we show the following identities in Section~\ref{sec:autocorrelation_computation}:
+Specifically, we show the following identities in Appendix~\ref{sec:autocorrelation_computation}:
 \begin{align} 
@@
 
-In Section~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
-As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$: %\TODO{Do these identities hold even without taking a limit?
-I guess so, but let's be sure.}
+In Appendix~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
+As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$:
 %
@@
 
-%
-%From these values, one may solve for the terms $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$.
-Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
-%%
-%\begin{align}
-%\gamma a_x^3[\ell_1,\ell_2]
-%= a_y^3[\ell_1,\ell_2] - (\gamma a_x^1)^3
-%- \gamma a_x^1 \cdot \big(a_y^2[\ell_1]  
-%+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(\gamma a_x^1)^2 \big).
-%\end{align}
-
-%\begin{corollary}[informal for now] \label{cor:ac_equivalence}
-%The first and the second autocorrelations  in the well-separated and the Poisson models are equivalent. 
-%If $\sigma$ is known, then it is also true for the third-order autocorrelation. If $\sigma$ is unknown, the it is true whenever $\ell_1\neq 0$, $\ell_2\neq 0$ and $\ell_1\neq \ell_2$. 
-%\end{corollary}
-%
-%It is now easy to show how to solve for both $\gamma$ and $\sigma$ from these expressions, assuming $x$ is generic. Indeed, we observe the product
-%%
-%\begin{align}
-%(\gamma a_x^1) (\gamma a_x^2[1])
-%&=  \frac{\gamma^2}{L^2} \left( \sum_{i=0}^{L-1} x[i] \right)
-%\left(\sum_{j=0}^{L-2} x[j]x[j+1] \right)
-%\nonumber \\
-%&= \frac{\gamma^2}{L^2} \sum_{j=0}^{L-2} \sum_{i=0}^{L-1} x[i]x[j]x[j+1]
-%\nonumber \\
-%&= \frac{\gamma^2}{L} \left\{ \sum_{\ell=0}^{L-1} a_x^3[1,\ell]
-%+ \sum_{\ell=1}^{L-2} a_x^3[\ell,\ell+1]  \right\}.
-%\end{align}
-%%
-%Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, \TODO{Is there a bias?} we can form the ratio and solve for $\gamma$: 
-%
-%\begin{align}
-%\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
-%{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
-%	+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]}.
-%\end{align}
-%%With $\gamma$ in hand, we can estimate $\sigma^2$:
-%%
-%\begin{align}
-%\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-%- (2 L - 1) (a_y^1)^2.
-%\end{align}
-%
-\begin{comment}
-In this section we omit the affect of the noise as it remains the same for the well-separated model. We aim to show that the moments of
-
-Let us denote by $m_Y^q$ the moments of $Y$:
-%
-\begin{align}
-%
-m_X^1[i] &= \E X[i], \quad 0 \le i \le L-1,   \nonumber\\ 
-m_X^2[i,j] &= \E X[i] X[j], \quad 0 \le i,j \le L-1, \\ 
-m_X^3[i,j,k] &= \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1. \nonumber
-\end{align}
-%
-Note that 
-\begin{align}
-a_X^1 &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^1[i], \nonumber \\
-a_X^2[\ell] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^2[i,i+\ell], \\
-a_X^3[\ell_1,\ell_2] &= \frac{1}{L}\sum_{i=0}^{L-1}m_X^3[i,i+\ell_1,i+\ell_2]. \nonumber
-\end{align}
-
-In the following,  we show that the moments of the observed data under the Poisson process can be written in terms of the autocorrelations of the well-separated model.
-
-\begin{proposition} \label{prop:poisson}
-	For any $i$,  the moments under the Poisson process are equal to 
-	\begin{align}
-	m_y^1[i] &= \gamma L a_X^1 \nonumber \\
-	m_y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
-	m_y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
-	\end{align}
-\end{proposition}
-
-\begin{corollary} \TODO{re-write}
-	From the first three moments of the Poisson process model, one can recover the first three moments from the strongly-separated model.
-\end{corollary}
-\end{comment}
-%
-%\TODO{What we want to have in this section}
-%\begin{enumerate}
-%	\item Recall the Poisson model (it's already described at the end of intro, so keep it short).
-%	\item Define a proper notion of $\gamma$ (careful with scaling $L$).
-%	\item State formulas for $a_y^q$ with $q = 1, 2, 3$ (ideally, including noise terms) to parallel what we did in the well-separated section.
-It would be better to do everything with autocorrelations rather than moments to keep the story uniform.
-%	\item (optional) Claim: under some assumptions (knowing $\gamma$?
-Others?), the autocorrelations of $y$ of order $q = 1, 2, 3$ under the Poisson model provide the same information about $x$ as the corresponding autocorrelations under the well-separated model.
-Could also be in Section 4.1.
-%\end{enumerate}
-%
-
 \section{Theory}
@@
 The other direction is true as well: if $\gamma>0$ is known, then one can estimate $\sigma^2$.
- The proof is provided in Section~\ref{sec:proof_prop_gamma}.
+ The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
 
@@
 In particular, this means that we can recover
-almost all signals with the given measurements. The proof is provided in Section~\ref{sec:proof_prop_gamma_sigma}.
+almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
 
@@
 Opposed to Proposition~\ref{prop:gamma_sigma}, these quantities can be computed explicitly. 
-In Section~\ref{sec:proof_uniqueness_poisson} we prove the following result:
+In Appendix~\ref{sec:proof_uniqueness_poisson} we prove the following result:
 
@@
 In the last experiment, we extend our model to 2-D signals.
+We run the experiments on a shared computer with 144 logical CPUs of type Intel(R) Xeon(R)
+CPU E7-8880 v3 $@$ 2.30GHz and 755Gb of RAM; we use at most 72 of these CPUs.
 The code for all experiments is available at \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
@@
 The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma = 3$, illustrated in Figure~\ref{fig:micro_example}.
- % corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$. 
-%As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
-%Hence, to use this property and keep things simple, we assume the number of signal occurrences and the noise standard deviation are known so that we can estimate the second-order autocorrelation of the image from thos the observation directly.
-%Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.
 
@@
 Each observation contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is challenging to detect  the planted images.} %In fact, it can be shown that at low SNR, reliable detection of individual image occurrences is impossible, even if the true image is known.
-}
+In panel (c), the noise level is such that it is challenging to detect  the planted images.}
 \end{figure}
-%By analogy to cryo-EM, this depicts a scenario where particle picking cannot be done.}
-%\vspace{-8pt}
 
@@
 
-\section{Proofs}
-
-%Proofs for some of the results presented in Section~\ref{sec:AC_analysis} and~\ref{sec:extensions} follow in this section.
-
-\subsection{Autocorrelations in the well-separated model} \label{sec:autocorrelation_computation}
-
-%Let us define
-%\begin{equation*}
-%\gamma = \frac{|s|L}{N}>0.
-%\end{equation*}
-%Then the first order autocorrelation of the observation is given by 
-%\begin{equation*}
-%a_y^1 = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1} y[i]\right\} =
-%\frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-1}x[i]\right\} +    
-%\E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\right\}
-%=\gamma a_x^1,
-%\end{equation*}
-%where $\E_z$ means expectation with respect to the distribution of $z$.
-%%the noise term converges to zero almost surely (a.s.)\ by the strong law of large numbers.
-%
-%We proceed with the second-order autocorrelation for  $\ell\in\{0,\ldots,L-1\}$. We can compute:
-%%
-%\begin{align*}
-%%
-%a_y^2[\ell] & = \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell]\right\}
-%\nonumber \\
-%& = \frac{|s|}{N}\E_x\left\{\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]\right\}  + \E_{\varepsilon}\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell}\varepsilon[i]\varepsilon[i+\ell] \right\},
-%%
-%\end{align*}
-%where all cross terms vanish in expectation owing to independence of $x$ of $\varepsilon$, and $\E{\varepsilon}=0$.  
-%Hence, 
-%\begin{align} \label{eq:2nd_moment_signal_term}
-%%
-%a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-1-\ell}{N}\sigma^2\ell[\ell],
-%\end{align}
-%where $\ell[0]=1$ and zero otherwise. 
-%
-%We now analyze the third-order autocorrelation. 
-%Let $x_{(j)}$ denote the $j$th
-%realization of $x$, with starting position $s_{(j)}$, for $j=1,\ldots,|s|$.
-%Let us fix $0\leq \ell_2\leq\ell_1\leq L-1$. We have:
-%\begin{align*}
-%%
-%a_y^3[\ell_1,\ell_2] 
-%=& \E_y\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]\right\}
-%\\
-%%
-%\stackrel{(1)}=& \E_{x_{(1)},\ldots,x_{(|s|)}}\left\{ \frac{|s|L}{N}\frac{1}{|s|}\sum_{j=1}^{|s|} 
-%	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x_{(j)}[i]x_{(j)}[i+\ell_1]x_{(j)}[i+\ell_2]  \right\} \\
-%\stackrel{(2)}+& \E_\varepsilon\left\{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]\right\}
-%\ \\
-%\stackrel{(3)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\} \\
-%\stackrel{(4)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_1]x_{(j)}[i]\ep[s_{(j)}+ i+\ell_2-\ell_1]\right\}
-%\\
-%\stackrel{(5)}+& \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-1} \ep[s_{(j)}+i-\ell_2]\ep[s_{(j)}+i+\ell_1-\ell_2]x_{(j)}[i]\right\}
-%\\ \stackrel{(6)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_{(j)}+i-\ell_2]x_{(j)}[i+\ell_1-\ell_2]x_{(j)}[i]\right\}
-%\\
-%\stackrel{(7)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-\ell_2-1} x_{(j)}[i]\ep[s_{(j)} + i+\ell_1]x_{(j)}[i+\ell_2]\right\}
-%\\ \stackrel{(8)}+ & \E_{x_{(1)},\ldots,x_{(|s|)},\varepsilon}\left\{\frac{1}{N}\sum_{j=1}^{|s|} 
-%	\sum_{i=0}^{L-\ell_1-1} x_{(j)}[i]x_{(j)}[i+\ell_1]\ep[s_{(j)}+ i+\ell_2]\right\}.
-%%
-%\end{align*}
-%Terms (6), (7) and (8) are linear in $\ep$ and  thus zero.
-%Term (1) is equal  to $\gamma a_x^3[\ell_1,\ell_2]$  for the same reasons as~\eqref{eq:2nd_moment_signal_term}. 
-%Term (2) is always zero by properties of Gaussian variables. 
-%To deal with terms (3)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.
-%
-%Term (3) is always zero, unless $\ell_1=\ell_2$, so that it is equal to 
-%$\gamma\sigma^2 a_x^1 \ell[\ell_1-\ell_2]$.
-%The same goes for Terms (4) and (5), which are equal, respectively, to
-%$\gamma\sigma^2 a_x^1 \ell[\ell_2]$ 
-%and $\gamma\sigma^2 a_x^1 \ell[\ell_1]$.
+\section{Summary}
+
+This paper suggests a computational framework for estimating a signal (signals) from their multiple occurrences in noisy data based on autocorrelation analysis. 
+The autocorrelations can be estimated accurately in any new level, given sufficiently long measurement. 
+Given accurate estimates of the autocorrelations, the problem reduces to estimate a signal from their autocorrelation, that is, solving a system of low-order polynomials equations.
+The crux of the method lies in the distinctions between parameters that we aim to estimate (the signal) and the nuisance variables (individual locations of signals' occurrences).
+In particular, we show that the signals can be estimated, although we cannot detect the occurrences in the data.
+
+The prime motivation for this project arises from the problem of reconstructing 3-D of macromolecules using cryo-EM.
+Currently, small molecules cannot be elucidated using cryo-EM; the signal-to-noise ratio on the micrograph is too low and thus it is impossible to detection the tomographic projections.
+However, the goal of the cryo-EM is not to detect these projections but rather to estimate the 3-D itself; the locations of the projections, as well as the viewing direction associated with each projection, are nuisance variables.
+Recently, we proposed to estimate the 3-D structure directly from the micrograph, without particle picking~\cite{bendory2018toward}.
+Currently, the reconstructed volumes are of low-resolutions.
+It is not clear whether it is possible to achieve higher resolution without considering higher autocorrelation, which in turn will increase the sample complexity of the problem.
+Application on cryo-EM data will also require incorporating additional parameters into the model: the distribution of 3-D orientation of the molecules in the ice, the noise power spectrum (usually colored noise), the contrast-transfer function, and the distribution of the projection across the   micrograph.
+These parameters will be encoded within the autocorrelations.
+Then, the goal would be to estimate these parameters, along with the 3-D structure, by solving the polynomial system of equations.
+
+\section*{Acknowledgment} 
+The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
+The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
+NB is partially supported by NSF award DMS-1719558.
+
+\bibliographystyle{plain}
+\bibliography{ref}
+
+\appendix
+
+\section{Autocorrelations in the well-separated model} \label{sec:autocorrelation_computation}
 
@@
 
-\subsection{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
-
-%Throughout this section, we will use the capital letter $X$ to represent the random unobserved vector of length $L$, the capital letter $Y$ to represent the random observed vector of length $N$, and the capital letter $S$ to represent the unobserved vector of occurrences.
+\section{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
 
@@
 
-%
-
-\subsubsection{Computing $a_y^1$}
+\subsection{Computing $a_y^1$}
 
@@
 
-%
-
-\subsubsection{Computing $a_y^2$}
+\subsection{Computing $a_y^2$}
 
@@
 
-%
-
-\subsubsection{Computing $a_x^3$}
+\subsection{Computing $a_x^3$}
 
@@
 We conclude by averaging over $i_1$, $i_2$, and $i_3$ leaving the gaps $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$ fixed.
-%
-%\TODO{Needs a complete rewrite to match the paper, in particular the modified notation and the fact we only work with autocorrelations now (not models).}
-%
-%\subsubsection{First moment}
-%
-%To compute the first moment of $y$, we will first condition on $M = (M_1,\dots,M_{N-L+1})$, and then average over $M$. We have:
-%%
-%\begin{align}
-%%
-%\E[y[i] | M] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} \E X_k^{i-j}[j]
-%= \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} m_y^1[j]
-%= \sum_{j=0}^{L-1} M_{i-j} m_y^1[j].
-%%
-%\end{align}
-%%
-%Now taking expectations over $M$ we see:
-%%
-%\begin{align}
-%%
-%\E Y[i] = \gamma \sum_{j=0}^{L-1}  m_y^1[j] = \gamma La_x^1.
-%%
-%\end{align}
-%
-%
-%%
-%
-%
-%\subsubsection{Second moment}
-%
-%Again, we will condition on $M$ first, and then take the expectation over $M$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
-%%
-%\begin{align}
-%%
-%Y_{i_1} Y_{i_2} 
-%&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
-%X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2].
-%%
-%\end{align}
-%
-%We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \ell$, and one where $j_2 = j_1 + \ell$ or equivalently $i_1-j_1 = i_2-j_2$.
-In the first case, all the terms are independent, and so the expectation factors.
-In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
-This gives (all expectations are conditional on $M$):
-%%
-%\begin{align} \label{moment2-condm}
-%%
-%\E Y_{i_1} Y_{i_2}
-%=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}}
-%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
-%\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
-%\sum_{k_2} \E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_1 - j_1}[j_1+\ell]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{M_{i_1-j_1}} 
-%\E X_{k_1}^{i_1-j_1}[j_1] X_{k_1}^{i_1-j_1}[j_1 + \ell] 
-%\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \ell} M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} M_{i_1-j_1} \M_2[j_1,j_1 + \ell] .
-%%
-%\end{align}
-%%
-%Now take expectations over the Poisson random variables, using this fact:
-%%
-%\begin{lem} \label{lem-choose}
-%	If $M \sim \Poisson(\gamma)$, then 
-%	\begin{align}
-%	%
-%	\E {M\choose k} = \frac{\gamma^k}{k!}.
-%	%
-%	\end{align}
-%\end{lem}
-%
-%
-%We get (now the expectation is over $M$ and $X$):
-%%
-%\begin{align}
-%%
-%\E Y_{i_1} Y_{i_2} 
-%=& \sum_{j_1 - j_2 \ne \ell} \E M_{i_1-j_1} M_{i_2 - j_2} \M_1[j_1] \M_1[j_2]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1}(M_{i_1-j_1} - 1) \M_1[j_1] \M_1[j_1 + \ell]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \E M_{i_1-j_1} \M_2[j_1,j_1 + \ell]
-%\nonumber \\
-%=& \sum_{j_1 - j_2 \ne \ell} \gamma^2 \M_1[j_1] \M_1[j_2]
-%+ \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \ell]
-%\nonumber \\
-%& + \sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \ell]
-%\nonumber \\
-%=&  \bigg(\gamma \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-%+ \gamma \sum_{j = 0}^{L-1} \M_2[j,j + \ell]
-%\nonumber \\
-%=&  (\gamma \L_1)^2 + \gamma \L_2(\ell).
-%%
-%\end{align}
-%
-%But the first term in the sum is just the square of the first moment of $Y$; so from the first two moments we can recover $\gamma \L_2(\ell)$, which is just the expected power spectrum of the random vector $X$, i.e.\ the usual second moment we have been working with.
-%
-%
-%%
-%
-%
-%\subsubsection{Third moment}
-%
-%For three distinct $i_1$, $i_2$ and $i_3$, we let $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$. We have:
-%%
-%\begin{align}
-%%
-%&Y_{i_1} Y_{i_2} Y_{i_3}
-%\nonumber \\
-%&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
-%\sum_{k_1=1}^{M_{i_1-j_1}}\sum_{k_2=1}^{M_{i_2-j_2}} \sum_{k_3=1}^{M_{i_3-j_3}}
-%X_{k_1}^{i_1-j_1}[j_1] X_{k_2}^{i_2 - j_2}[j_2] X_{k_3}^{i_3 - j_3}[j_3].
-%\end{align}
-%%
-%We will break up the outer three sums into disjoint sums with the following ranges of indices:
-%%
-%\begin{enumerate}
-%	
-%	\item \label{case1}
-%	$j_2 = j_1 + \ell_1$ and $j_3 = j_2 + \ell_2 - \ell_1$.
-%	
-%	\item \label{case2}
-%	$j_2 = j_1 + \ell_1$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
-%	
-%	\item \label{case3}
-%	$j_2 \ne j_1 + \ell_1$ and $j_3 = j_1 + \ell_2$.
-%	
-%	\item \label{case4}
-%	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 = j_2 + \ell_2 - \ell_1$.
-%	
-%	\item \label{case5}
-%	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
-%	
-%\end{enumerate}
-%
-%
-%For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
-%%
-%\begin{align}
-%%
-%&\sum_{j=0}^{L-1} \sum_{k_1=1}^{M_\ell} \sum_{k_2=1}^{M_\ell} \sum_{k_3=1}^{M_\ell} 
-%X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%\nonumber \\
-%=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%}_{\text{(a)}}
-%\nonumber \\
-%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%}_{\text{(b)}}
-%\nonumber \\
-%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%}_{\text{(c)}}
-%\nonumber \\
-%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%}_{\text{(d)}}
-%\nonumber \\
-%&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-%	X_{k_1}^{\ell}[j] X_{k_2}^{\ell}[j + \ell_1] X_{k_3}^{\ell}[j + \ell_2]
-%}_{\text{(e)}}.
-%%
-%\end{align}
-%
-%For term (a), the expectation conditional on $M$ is:
-%%
-%\begin{align}
-%%
-%\sum_{j=0}^{L-1} M_\ell(M_\ell-1)(M_\ell-2)\M[j] \M[j+\ell_1] \M[j+\ell_2].
-%%
-%\end{align}
-%%
-%Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
-%%
-%\begin{align} \label{aaaa}
-%%
-%\gamma^3 \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\ell_1] \M_1[j+\ell_2].
-%%
-%\end{align}
-%
-%
-%For term (b), the expectation conditional on $M$ is:
-%%
-%\begin{align}
-%%
-%\sum_{j=0}^{L-1} M_\ell (M_\ell - 1) \M_2[j,j+\ell_1] \M_1[j + \ell_2]
-%%
-%\end{align}
-%%
-%and then again using Lemma \ref{lem-choose} we get the expected value:
-%%
-%\begin{align} \label{bbbb}
-%%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_1] \M_1[j+\ell_2].
-%%
-%\end{align}
-%
-%Similarly, the expected values of terms (c) and (d) are:
-%%
-%\begin{align} \label{cccc}
-%%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j,j+\ell_2] \M_1[j+\ell_1].
-%%
-%\end{align}
-%%
-%and
-%%
-%\begin{align} \label{dddd}
-%%
-%\gamma^2 \sum_{j=0}^{L-1} \M_2[j+\ell_1,j+\ell_2] \M_1[j].
-%%
-%\end{align}
-%
-%Finally, the expected value of term (e) is easily shown to be:
-%%
-%\begin{align} \label{eeee}
-%%
-%\gamma \sum_{j=0}^{L-1} \M_3[j,j+\ell_1,j+\ell_2].
-%%
-%\end{align}
-%%
-%This concludes the computation for Case \ref{case1}.
-%
-%Moving onto Case \ref{case2}, we have $\ell_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\ell_2 \equiv i_3 - j_3$. By definition, $\ell_1 \ne \ell_2$. The sum is:
-%%
-%\begin{align}
-%%
-%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
-%\sum_{1 \le k_1,k_2 \le M_{\ell_1}} \sum_{k_3=1}^{M_{\ell_2}}
-%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]   
-%\nonumber \\
-%=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{M_{\ell_2}}
-%\Bigg\{
-%\sum_{1 \le k_1 \ne k_2 \le M_{\ell_1}} 
-%X_{k_1}^{\ell_1}[j_1] X_{k_2}^{\ell_1}[j_1 + \ell_1] X_{k_3}^{\ell_2}[j_3]
-%\nonumber \\
-%&       + \sum_{k_1=1}^{M_{\ell_1}} X_{k_1}^{\ell_1}[j_1] X_{k_1}^{\ell_1}[j_1 + \Delta_1] 
-%X_{k_3}^{\ell_2}[j_3]  \Bigg\}.
-%%
-%\end{align}
-%%
-%Taking expectations conditional on $M$, we then get:
-%%
-%\begin{align}
-%%
-%& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-%\Bigg(M_{\ell_1} (M_{\ell_1}-1) M_{\ell_2} \M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-%\nonumber \\
-%&       + M_{\ell_1} M_{\ell_2} \M_2[j_1,j_1+\Delta_1] \M_1[j_3] \Bigg).
-%%
-%\end{align}
-%
-%Taking expectations over $M$ and using Lemma \ref{lem-choose} then gives:
-%%
-%\begin{align}
-%%
-%& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2} 
-%\M_1[j_1] \M_1[j_1 + \Delta_1] \M_1[j_3]
-%\label{ffff} \\
-%& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \Delta_2}  
-%\M_2[j_1,j_1+\Delta_1] \M_1[j_3].
-%\label{gggg}
-%%
-%\end{align}
-%
-%
-%Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
-%%
-%\begin{align}
-%%
-%& \gamma^3 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1} 
-%\M_1[j_1] \M_1[j_1 + \Delta_2] \M_1[j_2]
-%\label{hhhh} \\
-%& + \gamma^2 \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \Delta_1}  
-%\M_2[j_1,j_1+\Delta_2] \M_1[j_2]
-%\label{iiii}
-%%
-%\end{align}
-%%
-%and
-%%
-%\begin{align}
-%%
-%& \gamma^3 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-%\M_1[j_1] \M_1[j_2 + \Delta_1] \M_1[j_2 + \Delta_2]
-%\label{jjjj}\\
-%& + \gamma^2 \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-%\M_2[j_2+\Delta_1,j_2+\Delta_2] \M_1[j_1].
-%\label{kkkk}
-%%
-%\end{align}
-%
-%Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
-Consequently, the $X$ variables are always independent, and the expectation conditional on $M$ (letting $\ell_q = i_q - j_q$, $q=1,2,3$),
-%%
-%\begin{align}
-%%
-%\sum_{j_1,j_2,j_3} M_{\ell_1} M_{\ell_2} M_{\ell_3} \M_1[j_1] \M_1[j_2] \M_1[j_3];
-%%
-%\end{align}
-%%
-%since the $M_{\ell_q}$'s are pairwise independent, $q=1,2,3$, the expectation over $M$ then yields:
-%%
-%\begin{align} \label{llll}
-%%
-%\gamma^3 \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
-%%
-%\end{align}
-%
-%Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
-%%
-%\begin{align}
-%%
-%(\gamma \L_1)^3.
-%%
-%\end{align}
-%
-%Note that this is obtained directly from the first moment. Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
-%%
-%\begin{align}
-%%
-%\gamma \L_1  \cdot 
-%( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)).
-%%
-%\end{align}
-%%
-%Again, note that this is obtained directly from the first two moments. Finally, expression \eqref{eeee} is simply:
-%%
-%\begin{align}
-%%
-%\gamma \L_3(\Delta_1,\Delta_2)
-%%
-%\end{align}
-%%
-%which is the usual third-order auto-correlation.
-%%
-
-\subsection{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
+
+\section{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
 Refer to equations \eqref{eq:mean_micrograph}--\eqref{eq:ac3_micrograph} for expressions relating the moments of $y$ and those of $x$, and the parameters $\gamma$ and $\sigma$. First,  note that 
@@
 
-\subsection{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
+\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
 
@@
 
-\subsection{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
+\section{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
 
@@
 %
-	Then, similarly to Section~\ref{sec:proof_prop_gamma}, one can solve for $\sigma^2$:
+Then, similarly to Appendix~\ref{sec:proof_prop_gamma}, one can solve for $\sigma^2$:
 \begin{align}
@@
 
-\section*{Acknowledgment} 
-The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
-The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
-NB is partially supported by NSF award DMS-1719558.
-
-\bibliographystyle{plain}
-\bibliography{ref}
-
 \end{document}

### 2019-03-09 inverse_problems/inverse_problems.tex
adding a summary

@@
 
-This paper suggests a computational framework for estimating a signal (signals) from their multiple occurrences in noisy data based on autocorrelation analysis. 
-The autocorrelations can be estimated accurately in any new level, given sufficiently long measurement. 
-Given accurate estimates of the autocorrelations, the problem reduces to estimate a signal from their autocorrelation, that is, solving a system of low-order polynomials equations.
-The crux of the method lies in the distinctions between parameters that we aim to estimate (the signal) and the nuisance variables (individual locations of signals' occurrences).
-In particular, we show that the signals can be estimated, although we cannot detect the occurrences in the data.
-
-The prime motivation for this project arises from the problem of reconstructing 3-D of macromolecules using cryo-EM.
-Currently, small molecules cannot be elucidated using cryo-EM; the signal-to-noise ratio on the micrograph is too low and thus it is impossible to detection the tomographic projections.
-However, the goal of the cryo-EM is not to detect these projections but rather to estimate the 3-D itself; the locations of the projections, as well as the viewing direction associated with each projection, are nuisance variables.
-Recently, we proposed to estimate the 3-D structure directly from the micrograph, without particle picking~\cite{bendory2018toward}.
-Currently, the reconstructed volumes are of low-resolutions.
-It is not clear whether it is possible to achieve higher resolution without considering higher autocorrelation, which in turn will increase the sample complexity of the problem.
-Application on cryo-EM data will also require incorporating additional parameters into the model: the distribution of 3-D orientation of the molecules in the ice, the noise power spectrum (usually colored noise), the contrast-transfer function, and the distribution of the projection across the   micrograph.
-These parameters will be encoded within the autocorrelations.
-Then, the goal would be to estimate these parameters, along with the 3-D structure, by solving the polynomial system of equations.
+This paper suggests a computational  framework for estimation in extreme noise levels. 
+The crux of the method lies in the distinction between parameters that we aim to estimate (the signals) and nuisance variables (parameters associated with signals' individual occurrences).
+In particular, we show that estimating the signals might be possible, although we cannot detect signal occurrences in the data.
+The method consists of two steps.
+First, we estimate the autocorrelations of the observation;
+these autocorrelations can be estimated to any desired accuracy 
+ given sufficiently long observation. 
+Second, the signal is recovered from the autocorrelations. 
+The recovery entails solving a system of low-order polynomial equations; the properties of the specific systems  (e.g., condition number) affects the feasibility of the estimation procedure.
+
+The prime motivation of this paper emanates from the problem of reconstructing small particles using cryo-EM.
+Small particles induce low signal-to-noise ratio on the micrograph, which  in turn implies that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
+The main message of our recent manuscript~\cite{bendory2018toward} is that  particle picking is merely an intermediate step (although frequently very useful) and the location of individual projections are nuisance variables.
+The ultimate goal is to estimate the 3-D structure.
+To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
+The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and computational complexity of the method.
+
+Autocorrelation analysis enables a flexible framework to incorporate additional parameters into the model.
+This is of particular importance for cryo-EM.
+The cryo-EM model includes, in addition to the target volume, the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored) and  the microscope contrast-transfer function.
+These parameters will be encoded within the estimated autocorrelations.
+If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations.
 

### 2019-03-10 inverse_problems/inverse_problems.tex
Will's comments

@@
 Then, $s[i]$ is split into $s_1[i] + \cdots + s_K[i]$ by selecting $s[i]$ signals among $x_1, \ldots, x_K$, independently at random  following a fixed distribution over $\{1,\ldots,K\}$.
-It is possible for more than one occurrence of the same $x_k$ to start at the same position~$i$.
+It is possible for more than one occurrence of the same $x_k$ to start at position~$i$.
 %and the corresponding signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$.  --- No need for this, since we already explained the convolution model.
@@
 
-\section{Connection with single-particle reconstruction via cryo-electron microscopy}
+\section{Connection with single-particle reconstruction via cryo-electron microscopy} \label{sec:cryoem}
 
@@
 Second, the signal is recovered from the autocorrelations. 
-The recovery entails solving a system of low-order polynomial equations; the properties of the specific systems  (e.g., condition number) affects the feasibility of the estimation procedure.
+The recovery entails solving a system of low-order polynomial equations; the properties of the specific systems  (e.g., its condition number) affects the feasibility of the estimation procedure.
 
@@
 To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
-The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and computational complexity of the method.
-
-Autocorrelation analysis enables a flexible framework to incorporate additional parameters into the model.
-This is of particular importance for cryo-EM.
-The cryo-EM model includes, in addition to the target volume, the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored) and  the microscope contrast-transfer function.
-These parameters will be encoded within the estimated autocorrelations.
-If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations.
+The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity.
+%
+%In addition, the model analyzed in~\cite{bendory2018toward} is somewhat simplified. 
+%A full cryo-EM model includes, in addition to the target volume,
+%multiple parameters:
+%the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored), and  the microscope contrast-transfer function.
+%These parameters will be encoded within the estimated autocorrelations.
+%If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations.
+Again, estimating those parameters may require high-order autocorrelations.
 
@@
 
+%\section{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
+
 \section{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
 
-We will denote by $\M_q$ the moment tensors of $x$:
-%
-\begin{align}
-%
-\M_1[i] = \E x[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-\M_2[i,j] = \E x[i] x[j], \quad 0 \le i,j \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-\M_3[i,j,k] = \E x[i] x[j] x[k], \quad 0 \le i,j,k \le L-1.
-%
-\end{align}
-We obtain the autocorrelations $a_x^q$ of $x$ by averaging over a slice of the moment tensors:
-%
-\begin{align}
-%
-a_x^1 = \frac{1}{L}\sum_{i=0}^{L-1} \M_1[i],
-%
-\end{align}
-%
-\begin{align}
-%
-a_x^2[\ell] = \frac{1}{L} \sum_{i=0}^{L-1} \M_2[i,i+\ell],
-%
-\end{align}
-%
-and \TODO{Compare with~\eqref{eq:ac_special}: the limits on the sum should be modified}
-%
-\begin{align}
-%
-a_x^3[\ell_1,\ell_2] = \frac{1}{L}\sum_{i=0}^{L-1} \M_3[i,i+\ell_1,i+\ell_2].
+We will denote by $m_l$ the moment tensors of $x$:
+%
+\begin{align}
+%
+m_1[i] = \E x[i], \quad 0 \le i \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+m_2[i,j] = \E x[i] x[j], \quad 0 \le i,j \le L-1,
+%
+\end{align}
+%
+\begin{align}
+%
+m_3[i,j,k] = \E x[i] x[j] x[k], \quad 0 \le i,j,k \le L-1.
+%
+\end{align}
+
+We obtain the autocorrelations $a_x^l$ of $x$ by averaging over a slice of the moment tensors:
+%
+\begin{align}
+%
+a_x^1 = \frac{1}{L}\sum_{i=0}^{L-1} m_1[i],
+%
+\end{align}
+%
+\begin{align}
+%
+a_x^2[\ell] = \frac{1}{L} \sum_{i=0}^{L-1} m_2[i,i+\ell],
+%
+\end{align}
+%
+and
+%
+\begin{align}
+%
+a_x^3[\ell_1,\ell_2] = \frac{1}{L}\sum_{i=0}^{L-1} m_3[i,i+\ell_1,i+\ell_2].
 %
@@
 
+%
+
 \subsection{Computing $a_y^1$}
@@
 We will first condition on the vector $s$ of locations of the subsignals in $y$, and then average over $s$.
-We will denote by $x_{(1)}^i,\dots,x_{(s[i])}^i$ the random vectors with position 0 located at $i$.
+We will denote by $x_{(1)}^{i},\dots,x_{(s[i])}^i$ the random vectors with position 0 located at $i$.
 We have:
@@
 \begin{align}
-a_y^1 = \frac{1}{N} \sum_{i=1}^N \E y[i] = \gamma a_x^1.
-\end{align}
+a_y^1 = \frac{1}{N} \sum_{i=1}^n \E y[i] = \gamma a_x^1.
+\end{align}
+
+%
 
@@
 
-First we will consider the noise-free case, where $\sigma = 0$. 
-Again, we will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
+First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
 %
@@
 =& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
-\sum_{k_2} \E x_{(k_1)}^{i_1-j_1}[j_1] x_{k_2}^{i_2 - j_2}[j_2]
+\sum_{k_2} \E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2]
 \nonumber \\
@@
 \nonumber \\
-=& \sum_{j_1 - j_2 \ne \ell} s[i_1-j_1] s[i_2 - j_2] \M_1[j_1] \M_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1](s[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \ell]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1] \M_2[j_1,j_1 + \ell] .
+=& \sum_{j_1 - j_2 \ne \ell} s[i_1-j_1] s[i_2 - j_2] m_1[j_1] m_1[j_2]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1](s[i_1-j_1] - 1) m_1[j_1] m_1[j_1 + \ell]
+\nonumber \\
+& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1] m_2[j_1,j_1 + \ell] .
 %
@@
 \E y[i_1] y[i_2]
-=& \sum_{j_1 - j_2 \ne \ell} \E s[i_1-j_1] s[i_2 - j_2] \M_1[j_1] \M_1[j_2]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1](s[i_1-j_1] - 1) \M_1[j_1] \M_1[j_1 + \ell]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1] \M_2[j_1,j_1 + \ell]
-\nonumber \\
-=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \ell} \gamma^2 \M_1[j_1] \M_1[j_2]
-+ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 \M_1[j_1] \M_1[j_1 + \ell]
-\nonumber \\
-&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma \M_2[j_1,j_1 + \ell]
-\nonumber \\
-=&  \bigg(\frac{\gamma}{L}  \sum_{j = 0}^{L-1} \M_1[j] \bigg)^2
-+ \frac{\gamma}{L} \sum_{j = 0}^{L-1} \M_2[j,j + \ell]
+=& \sum_{j_1 - j_2 \ne \ell} \E s[i_1-j_1] s[i_2 - j_2] m_1[j_1] m_1[j_2]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1](s[i_1-j_1] - 1) m_1[j_1] m_1[j_1 + \ell]
+\nonumber \\
+&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1] m_2[j_1,j_1 + \ell]
+\nonumber \\
+=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \ell} \gamma^2 m_1[j_1] m_1[j_2]
++ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 m_1[j_1] m_1[j_1 + \ell]
+\nonumber \\
+&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma m_2[j_1,j_1 + \ell]
+\nonumber \\
+=&  \bigg(\frac{\gamma}{L}  \sum_{j = 0}^{L-1} m_1[j] \bigg)^2
++ \frac{\gamma}{L} \sum_{j = 0}^{L-1} m_2[j,j + \ell]
 \nonumber \\
@@
 %
-We conclude by averaging over $i_1$ and $i_2$, leaving the gap $\ell = i_2 - i_1$ fixed.
+We conclude by averaging over $i_1$ and $i_2$ with a fixed value of $\ell = i_2 - i_1$.
+
+%
 
@@
 
-For Case \ref{case1}, we have $q \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
-%
-\begin{align}
-%
-&\sum_{j=0}^{L-1} \sum_{k_1=1}^{s[q]} \sum_{k_2=1}^{s[q]} \sum_{k_3=1}^{s[q]} 
-x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
+%
+\begin{align}
+%
+&\sum_{j=0}^{L-1} \sum_{k_1=1}^{s[\ell]} \sum_{k_2=1}^{s[\ell]} \sum_{k_3=1}^{s[\ell]} 
+x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 \nonumber \\
 =& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 }_{\text{(a)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 }_{\text{(b)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 }_{\text{(c)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 }_{\text{(d)}}
@@
 &+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-	x_{(k_1)}^{q}[j] x_{(k_2)}^{q}[j + \ell_1] x_{(k_3)}^{q}[j + \ell_2]
+	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
 }_{\text{(e)}}.
@@
 %
-\sum_{j=0}^{L-1} s[q](s[q]-1)(s[q]-2)\M[j] \M[j+\ell_1] \M[j+\ell_2].
+\sum_{j=0}^{L-1} s[\ell](s[\ell]-1)(s[\ell]-2)m_1[j] m_1[j+\ell_1] m_1[j+\ell_2].
 %
@@
 %
-\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} \M_1[j] \M_1[j+\ell_1] \M_1[j+\ell_2].
-%
-\end{align}
-
-For term (b), the expectation conditional on $S$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} s[q] (s[q] - 1) \M_2[j,j+\ell_1] \M_1[j + \ell_2]
-%
-\end{align}
-%
-and then again using Lemma~\ref{lem-choose} we get the expected value:
+\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} m_1[j] m_1[j+\ell_1] m_1[j+\ell_2].
+%
+\end{align}
+
+For term (b), the expectation conditional on $s$ is:
+%
+\begin{align}
+%
+\sum_{j=0}^{L-1} s[\ell] (s[\ell] - 1) m_2[j,j+\ell_1] m_1[j + \ell_2]
+%
+\end{align}
+%
+and then again using Lemma \ref{lem-choose} we get the expected value:
 %
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\ell_1] \M_1[j+\ell_2].
-%
-\end{align}
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j,j+\ell_1] m_1[j+\ell_2].
+%
+\end{align}
+
 Similarly, the expected values of terms (c) and (d) are:
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j,j+\ell_2] \M_1[j+\ell_1].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j,j+\ell_2] m_1[j+\ell_1].
 %
@@
 %
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} \M_2[j+\ell_1,j+\ell_2] \M_1[j].
+\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j+\ell_1,j+\ell_2] m_1[j].
 %
@@
 %
-\frac{\gamma}{L} \sum_{j=0}^{L-1} \M_3[j,j+\ell_1,j+\ell_2].
+\frac{\gamma}{L} \sum_{j=0}^{L-1} m_3[j,j+\ell_1,j+\ell_2].
 %
@@
 
-Moving onto Case~\ref{case2}, we have $q_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $q_2 \equiv i_3 - j_3$. By definition, $q_1 \ne q_2$. The sum is:
+Moving onto Case \ref{case2}, we have $\Delta_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\Delta_2 \equiv i_3 - j_3$. By definition, $\Delta_1 \ne \Delta_2$. The sum is:
 %
@@
 & \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
-\sum_{1 \le k_1,k_2 \le s[q_1]} \sum_{k_3=1}^{s[q_2]}
-x_{(k_1)}^{q_1}[j_1] x_{(k_2)}^{q_1}[j_1 + \ell_1] x_{(k_3)}^{q_2}[j_3]   
-\nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{s[q_2]}
-\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le s[q_1]} 
-x_{(k_1)}^{q_1}[j_1] x_{(k_2)}^{q_1}[j_1 + \ell_1] x_{(k_3)}^{q_2}[j_3]
-\nonumber \\
-& + \sum_{k_1=1}^{s[q_1]} x_{(k_1)}^{q_1}[j_1] x_{(k_1)}^{q_1}[j_1 + \ell_1] 
-x_{(k_3)}^{q_2}[j_3]  \Bigg\}.
+\sum_{1 \le k_1,k_2 \le s[\Delta_1]} \sum_{k_3=1}^{s[\Delta_2]}
+x_{(k_1)}^{\Delta_1}[j_1] x_{(k_2)}^{\Delta_1}[j_1 + \ell_1] x_{(k_3)}^{\Delta_2}[j_3]   
+\nonumber \\
+=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{s[\Delta_2]}
+\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le s[\Delta_1]} 
+x_{(k_1)}^{\Delta_1}[j_1] x_{(k_2)}^{\Delta_1}[j_1 + \ell_1] x_{(k_3)}^{\Delta_2}[j_3]
+\nonumber \\
+& + \sum_{k_1=1}^{s[\Delta_1]} x_{(k_1)}^{\Delta_1}[j_1] x_{(k_1)}^{\Delta_1}[j_1 + \ell_1] 
+x_{(k_3)}^{\Delta_2}[j_3]  \Bigg\}.
 %
@@
 \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
-\Bigg( & s[q_1] (s[q_1]-1) s[q_2] \M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
-+ s[q_1] s[q_2] \M_2[j_1,j_1+\ell_1] \M_1[j_3] \Bigg).
-%
-\end{align}
-
-Taking expectations over $s$ and using Lemma~\ref{lem-choose} then gives:
+\Bigg( & s[\Delta_1] (s[\Delta_1]-1) s[\Delta_2] m_1[j_1] m_1[j_1 + \ell_1] m_1[j_3]
+\nonumber \\
+&  + s[\Delta_1] s[\Delta_2] m_2[j_1,j_1+\ell_1] m_1[j_3] \Bigg).
+%
+\end{align}
+
+Taking expectations over $s$ and using Lemma \ref{lem-choose} then gives:
 %
@@
 & \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
-\M_1[j_1] \M_1[j_1 + \ell_1] \M_1[j_3]
+m_1[j_1] m_1[j_1 + \ell_1] m_1[j_3]
 \label{ffff} \\
 & + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}  
-\M_2[j_1,j_1+\ell_1] \M_1[j_3].
+m_2[j_1,j_1+\ell_1] m_1[j_3].
 \label{gggg}
@@
 & \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1} 
-\M_1[j_1] \M_1[j_1 + \ell_2] \M_1[j_2]
+m_1[j_1] m_1[j_1 + \ell_2] m_1[j_2]
 \label{hhhh} \\
 & + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1}  
-\M_2[j_1,j_1+\ell_2] \M_1[j_2]
+m_2[j_1,j_1+\ell_2] m_1[j_2]
 \label{iiii}
@@
 & \frac{\gamma^3}{L^3} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-\M_1[j_1] \M_1[j_2 + \ell_1] \M_1[j_2 + \ell_2]
+m_1[j_1] m_1[j_2 + \ell_1] m_1[j_2 + \ell_2]
 \label{jjjj}\\
 & + \frac{\gamma^2}{L^2} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-\M_2[j_2+\ell_1,j_2+\ell_2] \M_1[j_1].
+m_2[j_2+\ell_1,j_2+\ell_2] m_1[j_1].
 \label{kkkk}
@@
 Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
-Consequently, the $x$ variables are always independent, and the expectation conditional on $s$ (letting $q_\ell = i_\ell - j_\ell$, $\ell=1,2,3$),
-%
-\begin{align}
-%
-\sum_{j_1,j_2,j_3} s[q_1] s[q_2] s[q_3] \M_1[j_1] \M_1[j_2] \M_1[j_3];
-%
-\end{align}
-%
-since the $s[q_\ell]$'s are pairwise independent, $\ell=1,2,3$, the expectation over $s$ then yields:
+Consequently, the $x$ variables are always independent, and the expectation conditional on $s$ (letting $\Delta_{q} = i_q - j_q$, $q=1,2,3$),
+%
+\begin{align}
+%
+\sum_{j_1,j_2,j_3} s[\Delta_1] s[\Delta_2] s[\Delta_3] m_1[j_1] m_1[j_2] m_1[j_3];
+%
+\end{align}
+%
+since the $s[\Delta_q]$'s are pairwise independent, the expectation over $s$ then yields:
 %
@@
 %
-\frac{\gamma^3}{L^3} \sum_{j_1,j_2,j_3} \M_1[j_1] \M_1[j_2] \M_1[j_3].
+\frac{\gamma^3}{L^3} \sum_{j_1,j_2,j_3} m_1[j_1] m_1[j_2] m_1[j_3].
 %
@@
 \begin{align}
-\E y[i_1] y[i_2] y[i_3] =& \E x^*[i_1] x^*[i_2] x^*[i_3] + \E x^*[i_1] \ep[i_2] \ep[i_3]
+\E y[i_1] y[i_2] y[i_3] =\,\, & \E x^*[i_1] x^*[i_2] x^*[i_3] + \E x^*[i_1] \ep[i_2] \ep[i_3]
 \nonumber \\
@@
 \nonumber \\
-=& \E x^*[i_1] x^*[i_2] x^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
+=\,\, & \E x^*[i_1] x^*[i_2] x^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
 \nonumber \\
@@
 
-We conclude by averaging over $i_1$, $i_2$, and $i_3$ leaving the gaps $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$ fixed.
+We conclude by averaging over all $i_1$, $i_2$, and $i_3$ with fixed values of $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$.
+
+%
 

### 2019-03-10 inverse_problems/inverse_problems.tex
summary (modification)

@@
 To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
-The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity.
+In order to gain better understanding of the method, this paper focused on an abstraction of cryo-EM---the multi-target detection model. 
+Our next goal is to reconsider the full cryo-EM model, both from theoretical and algorithmic perspectives. 
+In particular, the numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity.
+
 %

### 2019-03-12 inverse_problems/inverse_problems.tex
Updates to summary + made Ackn. fit without margin overflow

--- 2019-03-10 inverse_problems/inverse_problems.tex
@@
 
-This paper suggests a computational  framework for estimation in extreme noise levels. 
-The crux of the method lies in the distinction between parameters that we aim to estimate (the signals) and nuisance variables (parameters associated with signals' individual occurrences).
-In particular, we show that estimating the signals might be possible, although we cannot detect signal occurrences in the data.
+This paper suggests a computational  framework for estimation under extreme noise levels. 
+The crux of the method lies in the distinction between parameters of interest (the signals) and nuisance variables (parameters associated with individual signal occurrences, such as location and class).
+In part through theory and in part through numerical experiments, we show that estimating the signals is possible even when they cannot be detected in the data.
 The method consists of two steps.
-First, we estimate the autocorrelations of the observation;
-these autocorrelations can be estimated to any desired accuracy 
- given sufficiently long observation. 
-Second, the signal is recovered from the autocorrelations. 
-The recovery entails solving a system of low-order polynomial equations; the properties of the specific systems  (e.g., its condition number) affects the feasibility of the estimation procedure.
-
-The prime motivation of this paper emanates from the problem of reconstructing small particles using cryo-EM.
-Small particles induce low signal-to-noise ratio on the micrograph, which  in turn implies that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
-The main message of our recent manuscript~\cite{bendory2018toward} is that  particle picking is merely an intermediate step (although frequently very useful) and the location of individual projections are nuisance variables.
-The ultimate goal is to estimate the 3-D structure.
-To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
-The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity.
+First, we estimate the autocorrelations of the observation.
+A key feature is that, for any noise level, these autocorrelations can be estimated to any desired accuracy given sufficiently rich observations.
+Second, we recover the signals from the autocorrelations.
+This recovery entails solving a system of low-order polynomial equations.
+While solving such systems is hard in general, we found that in the homogeneous case we can solve them explicitly, and in both the homogeneous and heterogeneous cases we can solve them with reasonable robustness through non-convex optimization, in a wide regime of parameters.
+%The properties of the specific systems (e.g., its condition number) affects the feasibility of the estimation procedure.
+
+The prime motivation of this paper emanates from challenges in small particle reconstruction using cryo-EM.
+Small particles induce such low signal-to-noise ratio in the micrograph that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
+The main message of our recent report~\cite{bendory2018toward} is that particle picking is merely a means to an end (although admittedly of key usefulness when it can be done): the locations and classes of individual particle projections are nuisance variables.
+The ultimate goal is only to estimate the 3-D structures.
+To this end,  we used autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
+In order to gain better understanding of the method, this paper focuses on an abstraction of cryo-EM---the multi-target detection model. 
+Our next goal is to reconsider the full cryo-EM model, both from theoretical and algorithmic perspectives. 
+In particular, the numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using autocorrelations up to third order is limited by ill-conditioning of the system of polynomial equations.
+Higher resolution may require computing higher-order autocorrelations, which would increase the sample complexity and computational complexity of the algorithm.
+Despite the challenges, we believe that this approach may ultimately offer a way to reconstruct 3-D structures that are too small for current algorithmic pipelines.
+
 %
@@
 The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
-The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
+The research is supported in parts by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
 NB is partially supported by NSF award DMS-1719558.

### 2019-03-12 inverse_problems/inverse_problems.tex
small comments (Eitan)

@@
 These autocorrelations can be estimated accurately at any noise level given a sufficiently long measurement.
-To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
+%To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
+To recover the signals from the observed autocorrelations, we  solve a set of polynomial equations through nonlinear least-squares. 
 We provide analysis regarding well-posedness of the task, and demonstrate numerically the effectiveness of the method in a variety of settings.
@@
 multiple times at unknown locations in a noisy measurement.
-Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  far larger than $L$. 
+Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  much larger than $L$. 
 Let  $s[i]$ count the number of signal occurrences whose first entry is positioned at $y[i]$.
@@
 Importantly, the electron dose must be kept low to mitigate  radiation damage, inducing high noise levels.
-The goal is to construct 3-D models of the molecular structures from the micrographs. 
+The goal is to reconstruct 3-D models of the molecular structures from the micrographs. 
 Since  cryo-EM produces images of individual particles, it can elucidate multiple  structures simultaneously.
@@
 Then, a rotation $R_\omega$ is applied to the volume (to model viewing directions) according to a (possibly unknown) distribution of $\omega$ over $SO(3)$ (the group of 3-D rotations).
-With tomographic projection denoted by $P$, we have the following probability distribution for particles in the micrograph:
+With tomographic projection denoted by $P$, $x$ is a random signal, related to the distribution of $\omega$ through:
+%we have the following probability distribution for particles in the micrograph:
 \begin{align}
@@
 The first stage, called \emph{particle picking},  detects and extracts the particle projections from the micrographs.
-Given the projections, the second stage aims to construct a 3-D model of the molecular structure, usually using an expectation-maximization algorithm~\cite{scheres2012relion}.
+Given the projections, the second stage aims to reconstruct a 3-D model of the molecular structure, usually using an expectation-maximization algorithm~\cite{scheres2012relion}.
 %The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
@@
 Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity  the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y$, that is, % (ergodicity)
+However, by the law of large numbers, as $N$ grows to infinity  the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y\in \RN$, that is, % (ergodicity)
 \begin{align}
@@
 that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case $K = 1$ (all signal occurrences are the same).
-%\TODO{Do we also need to say "for generic $x$" here, as in Poisson?}
 
@@
 \end{equation}
-for $k = 0, \ldots, L-1$. If $z[0]$ or $z[L-1]$ are equal to zero, then $a_z^2[L-1] = 0$ and we can use that indication to redefine $L$.
+for $k = 0, \ldots, L-1$. If $z[0]$ or $z[L-1]$ are equal to zero, then $a_z^2[L-1] = 0$ and we can use that indication to shrink $L$.
 This proves the following useful fact:
@@
 	\caption{Experiment described in Section~\ref{sec:XP1}.
-For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 12.3 \cdot 10^9$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed  occurrence probabilities.
+For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 1.23 \cdot 10^{10}$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed  occurrence probabilities.
 Each row corresponds to one of the signals.
@@
 Visually, the noise dominates the signal to the point that it is challenging to detect occurrences.
-More precisely, the cross-correlations of $y$ even with the true signals presents peaks at essentially random locations, apparently uninformative of the actual locations of the signal occurrences.
+More precisely, the cross-correlations of $y$ even with the true signals presents peaks at essentially random locations,  uninformative of the actual locations of the signal occurrences.
 Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to cluster them according to which signal appears where.
@@
 
-In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly preempts location and clustering.
+In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly hinders location and clustering.
 We also note that the amount of data required to produce these good estimations is large.
@@
 \end{align}
-Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are independent, we further find:
+Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are identically distributed, we further find:
 \begin{align}
@@
 \begin{align}
-N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \ell[\ell],
-\end{align}
-where $\ell[0] = 1$ and $\ell[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
-\begin{align}
-a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \ell[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
+N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \delta[\ell],
+\end{align}
+where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
+\begin{align}
+a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \delta[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
 \end{align}
@@
 We will first condition on the vector $s$ of locations of the subsignals in $y$, and then average over $s$.
-We will denote by $x_{(1)}^{i},\dots,x_{(s[i])}^i$ the random vectors with position 0 located at $i$.
+We will denote by $x_{(1)}^{i},\dots,x_{(s[i])}^i$ the random vectors starting  in $y[i]$.
 We have:
+%with position 0 located at $i$. We have:
 %
@@
 \begin{align*}
-2\sum_{\ell = 1}^{L-1}a_y^2[\ell] & = \gamma \sum_{\ell = 1}^{L-1} a_x^2[\ell] + a_x^2[-\ell] \\
+2\sum_{\ell = 1}^{L-1}a_y^2[\ell] & = \gamma \sum_{\ell = 1}^{L-1} \left(a_x^2[\ell] + a_x^2[-\ell]\right) \\
 & = \frac{\gamma}{L}\sum_{i=0}^{L-1}\sum_{\ell = 1}^{L-1} x[i]\left(x[i+\ell] + x[i-\ell]\right) \\ &= \frac{\gamma}{L} \sum_{i = 0}^{L-1} \sum_{j = 0, j \neq i}^{L-1} x[i] x[j],
@@
 Throughout the proof, it is important to distinguish between observed and unobserved values.
-We denote the observed values by $E_i$ or $a_y^1,a_y^2,a_y^3$. We use $F_i$ to denote functions of the signal's autocorrelations (which are not directly observable).
+We denote the observed values by $E_i$ and $a_y^1,a_y^2,a_y^3$. We use $F_i$ to denote functions of the signal's autocorrelations (which are not directly observable).
 

### 2019-05-24 InverseProblemsV2/inverse_problems_v2.tex
inverse problems v2

--- 2019-03-12 inverse_problems/inverse_problems.tex
@@
 \newcommand{\TODO}[1]{{\color{red}{[#1]}}}
-\newcommand{\revised}[1]{{\color{blue}{#1}}}
+\newcommand{\revised}[1]{{\color{magenta}{#1}}}
 \newcommand{\R}{\mathbb{R}}
@@
 In the low noise regime, one can estimate the signals by first detecting occurrences, then clustering and averaging them.
-In the high noise regime however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
+In the high noise regime, however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
 Notwithstanding, using autocorrelation analysis, we show that the impossibility to detect and cluster signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
@@
 With additive white Gaussian noise, the measurement model can be written as 
-\begin{equation} 
-	y  =  \sum_{k=1}^K s_k \ast x_k + \varepsilon, \qquad  \varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
+\begin{align} 
+	y  &=  \sum_{k=1}^K s_k \ast x_k + \varepsilon, &\varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
 	\label{eq:model}
-\end{equation}
+\end{align}
 where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of occurrences of $x_k$ starting at $y[i]$, so that $s =  s_1+\cdots+s_K$.
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{KLXP/XP1}
+	\includegraphics[width=.7\linewidth]{XP1}
 	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems that $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.

### 2019-05-26 InverseProblemsV2/inverse_problems_v2.tex
Add files via upload

@@
 
+%\revised{A follow-up paper~\cite{lan2019multi} extends this model by allowing an arbitrary spacing between signal occurrences, while excluding overlapping occurrences}.
+
 \paragraph{The Poisson model.}
@@
 It is possible for more than one occurrence of the same $x_k$ to start at position~$i$.
-%and the corresponding signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$.  --- No need for this, since we already explained the convolution model.
 As for the well-separated model, the autocorrelations of $y$ under this model depend weakly on $s$ and $s_1, \ldots, s_K$, essentially through the parameter $\gamma$: see Section~\ref{sec:AC_analysis}.
@@
 Clearly, the picked particles depend heavily on the chosen templates: different templates may lead to different picked particles, hence, which is more problematic, to different 3-D structure reconstructions.
-The cryo-EM community is well aware of this potential pitfall~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding}, which was notably exemplified in the ``Einstein from noise'' experiment~\cite{shatsky2009method}.
-%In this experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged.
-It was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template.
- %In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles biases the reconstructed structure.
-%This model bias is common to all particle picking methods based on template matching.
-%In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias.
-%
+The cryo-EM community is well aware of this potential pitfall~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding}, which was notably exemplified \revised{by} the ``Einstein from noise'' experiment~\cite{shatsky2009method}.
 
@@
 For entries independent of $\sigma$, the autocorrelations of the Poisson process contain the same information as those of the well-separated model.
-If $\sigma$ is known, this holds true for all entries: see Section~\ref{sec:ac_poisson}.
+If $\sigma$ is known, this holds true for all entries; see Section~\ref{sec:ac_poisson}.
 
@@
 The specific value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
-Furthermore, we assume uniform occurrence distribution $\gamma_k$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of $y$).
+Furthermore, we assume uniform occurrence distribution $\gamma_k$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of~$y$).
 

### 2019-05-29 InverseProblemsV2/inverse_problems_v2.tex
response to referees

@@
 \begin{proposition} \label{prop:uniqueness_poisson}
-Under the homogeneous Poisson model, the signal $x$, the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
+Under the homogeneous Poisson model, the signal $x$, the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely \revised{from the observed autocorrelations}. 
 In particular,
@@
 While solving such systems is hard in general, we found that in the homogeneous case we can solve them explicitly, and in both the homogeneous and heterogeneous cases we can solve them with reasonable robustness through non-convex optimization, in a wide regime of parameters.
-%The properties of the specific systems (e.g., its condition number) affects the feasibility of the estimation procedure.
+
+\revised{In addition, autocorrelation analysis provides a flexible framework to extend the multi-target detection model by  relating the expected autocorrelations
+of the data with the signals, and all parameters necessary to describe the generative model.
+For instance,  a follow-up paper relaxes the separation condition~\eqref{eq:spacing} and allows  an arbitrary spacing of targets, as long as the signal occurrences do not overlap~\cite{lan2019multi}.
+In that case, the autocorrelations of the data are functions of the signal and the unknown target distribution.
+In a similar fashion, one may include more realistic noise models, the effect of a blurring kernel (e.g., the point spread function of the microscope) and so on.}
 

### 2019-05-29 InverseProblemsV2/reponse.tex
response to referees

--- 2019-05-26 InverseProblemsV2/inverse_problems_v2.tex
@@
 
-\title{Multi-target detection with application to cryo-electron microscopy}
+\title{Response to referees: Multi-target detection with application to cryo-electron microscopy}
 
-\author[a]{Tamir Bendory}
-\author[b]{Nicolas Boumal} 
-\author[c]{William Leeb}
-\author[a,b]{Eitan Levin}
-\author[a,b]{Amit Singer}
+\author{Tamir Bendory, Nicolas Boumal, Will Leeb, Eitan Levin, and Amit Singer}
 
-\affil[a]{The Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ, USA}
-\affil[b]{Department of Mathematics, Princeton University, Princeton, NJ, USA}
-\affil[c]{School of Mathematics, University of
-	Minnesota, Minneapolis, MN, USA }
-
-%\date{}
+\date{}
 \maketitle
 
-\begin{abstract}
+We thank the editor and the referees for reading our paper. Below, we provide a detailed, one-to-one response to all comments.
 
-We consider the multi-target detection problem of recovering a set of signals that appear 
-multiple times at unknown locations in a noisy measurement.
-In the low noise regime, one can estimate the signals by first detecting occurrences, then clustering and averaging them.
-In the high noise regime, however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
-Notwithstanding, using autocorrelation analysis, we show that the impossibility to detect and cluster signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
-Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals.
-These autocorrelations can be estimated accurately at any noise level given a sufficiently long measurement.
-%To recover the signals from the observed autocorrelations, we (heuristically) solve a set of polynomial equations through nonlinear least-squares. 
-To recover the signals from the observed autocorrelations, we  solve a set of polynomial equations through nonlinear least-squares. 
-We provide analysis regarding well-posedness of the task, and demonstrate numerically the effectiveness of the method in a variety of settings.
+\section{Referee 1}
 
-The main goal of this work is to provide theoretical and numerical support for a recently proposed framework to image 3-D structures of biological macromolecules using cryo-electron microscopy in extreme noise levels.
-% ~\cite{bendory2018toward}.
--- not references in the abstract, except if cited in full; but we don't want to write "arxiv" here.
+\noindent \textbf{Comment:} The only suggestion I have is to include a brief discussion of validation - the experiments here are from simulated data with known signals.
+If this technology were ever to be adopted in experimental practice, some form of statistical validation will be essential.\\
 
-\end{abstract}
+\noindent \textbf{Response:} The question of statistical validation is of great importance in any scientific field, including single particle reconstruction using cryo-EM.
+%This question is more general that the specific method applied.
+Unfortunately,  there is  no rigorous method to validate a structure that was constituted using cryo-EM.
+In practice, researchers in the field use several useful heuristics, such as  comparing the elucidated structure with structures that were reconstructed by other imaging modalities (e.g., X-ray crystallography), or different statistical techniques (e.g., expectation-maximization).
+The validation problem is even more severe in the low SNR regime (the main interest of this paper) in which visual assessment of the data might be impossible.
+Our method does not offer insights for this question.
 
-\section{Introduction} \label{sec:intro}
+While validation is beyond the scope of this paper, autocorrelation analysis provides a flexible framework to describe reach generative models of the data.
+We added a paragraph in the summary to explain this issue.
 
-We consider the \emph{multi-target detection} problem of recovering a set of $K$ signals that appear 
-multiple times at unknown locations in a noisy measurement.
-Let ${x_1,\ldots,x_K\in\RL}$ be the sought signals and let $y\in\RN$ be the observed data, where we assume $N$ is  much larger than $L$. 
-Let  $s[i]$ count the number of signal occurrences whose first entry is positioned at $y[i]$.
-Each of those $s[i]$ signals is chosen among $x_1, \ldots, x_K$ according to some (possibly unknown) distribution over $\{1,\ldots,K\}$.
-If signal occurrences overlap, they interfere additively. %We think of those events as being rare. 
-With additive white Gaussian noise, the measurement model can be written as 
-\begin{align} 
-	y  &=  \sum_{k=1}^K s_k \ast x_k + \varepsilon, &\varepsilon   \sim \mathcal{N}(0,\sigma^2 I_N),
-	\label{eq:model}
-\end{align}
-where $\ast$ denotes linear convolution, and $s_k[i]$ indicates the number of occurrences of $x_k$ starting at $y[i]$, so that $s =  s_1+\cdots+s_K$.
-Explicitly, with zero-based indexing, % and zero-padding out of bounds,
-\begin{align*}
-	y[i] & = \sum_{k=1}^{K} \sum_{j = 0}^{L-1} s_k[i-j] x_k[j] + \varepsilon[i].
-\end{align*}
-%We discuss generative models for $s_1, \ldots, s_K$ below.
-%
-The goal is  to estimate $x_1,\ldots,x_K$ from $y$. % while $s$ is the \emph{nuisance variable} of the problem.
-%We name this problem \emph{multi-target detection}.
-In parts of the paper, we focus on the case $K = 1$, called the \emph{homogeneous} case; the case $K \geq 2$ is called \emph{heterogeneous}.
-This idealized setup appears in several scientific applications, including structural biology~\cite{bendory2018toward} (as we detail below), spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive}, and system identification~\cite{ljung1998system}.
+\section{Referee 3}
 
-In the low noise regime (small $\sigma$), a valid strategy is to first detect the signal occurrences in $y$ (that is, estimate $s$), cluster them (that is, separate $s$ into $s_1,\ldots,s_K$), and solve  standard deconvolution problems.
-Crucially, we focus on the high noise regime, where \emph{reliable detection of signal occurrences is  impossible}~\cite{bendory2018toward,aguerrebere2016fundamental}.
-This limitation does not, however, preclude estimation of the signals $x_1,\ldots,x_K$, as we show in this paper.
-In this setting, we refer to  $s_1,\ldots,s_K$  as \emph{nuisance variables}: knowing them would certainly help, but we do not aim to estimate them.
+\noindent \textbf{Comment:} An important point in practical image reconstruction, especially in modalities like phase retrieval, is that precise knowledge of the support of the image makes the reconstruction problem considerably easier.
+Beyond that, having an image with a sharply delineated, known boundary is, in fact, a huge advantage.
+Such images are used in the examples in this paper, along with an exact knowledge of their support.
+In most realistic imaging applications such information is not available, and this renders these problems inherently more difficult, regardless of the algorithm used.
+Some mention of this fact should appear in this paper.\\
 
-In order to recover the signals in the high noise regime, we use autocorrelation analysis.
-At any noise level, the autocorrelations of the observation can be estimated to any desired accuracy for sufficiently large  $N$. 
-This computation is straightforward and requires only one pass over the data.
-The underlying principle is to relate the autocorrelations of the observation $y$ to the autocorrelations of $x_1,\ldots,x_K$.
+\noindent \textbf{Response:} Section 4.4 discusses the application of our approach to 2-D images.
+In this section, we underscore the importance of the knowledge of the exact support for phase retrieval as was shown in [9].
+In our setup, if the support cannot be estimated accurately, the solution is to consider the third-order autocorrelation.
+That being said, as we mention in Section 4, the support of the signal (at least in 1-D) can be determined from the second-order autocorrelation if enough data is provided.
+\\
 
-Below we describe two generative models for $s$.  
-In these models, the relationship between the autocorrelations of $y$ and those of $x_1,\ldots,x_K$ depends on $s_1,\ldots,s_K$ only through their expected sums, that is, the expected total number of occurrences of each signal.
-To estimate the signals and occurrence counts from the computed autocorrelations, we solve a nonlinear least-squares problem as explained in Section~\ref{sec:numerics}.
+\noindent \textbf{Comment:} Though it is clarified in the proof of Prop.
+4.5 it is not immediately clear that  the right hand sides of formulae (4.3), (4.4), (4.5) are observable quantities.
+A remark, after the statement of the proposition, clarifying this  point would be useful.\\
 
-The multi-target detection problem  is an instance of  
-\emph{blind deconvolution}---a longstanding problem arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, to name a few.
-Different variants of the blind deconvolution problem have been thoroughly analyzed recently~\cite{ahmed2014blind,li2016identifiability,li2016rapid,lee2017blind,ling2017blind,kuo2019geometry}.
-In clear contrast to multi-target detection, these works focus on the low noise regime and aim to estimate both unknown signals (in our setting, this means estimating both $x_k$'s and $s_k$'s).
+\noindent \textbf{Response:} We added a remark to the proposition to make this point clear.\\
 
-\subsection*{Models for target distribution}
+\noindent \textbf{Comment:}  I found it difficult to understand what Figure 2 is demonstrating. Perhaps it is a result of the poor rendering of the grey-scale.
+\\
 
-We consider two  models for the distribution of signal occurrences in the observation, that is, for $s_1, \ldots, s_K$.
-
-\paragraph{The well-separated model.}
-
-As a first setup, we allow any generative model for $s$ which meets the following separation requirement: $s$ is binary, and
-\begin{equation}
-\textrm{If } s[i] = 1 \textrm{ and } s[j] = 1 \textrm{ for } i \neq j, \textrm{ then } |i - j| \geq 2L-1.
-\label{eq:spacing}
-\end{equation}
-In words: the starting positions of any two occurrences  must be separated by at least $2L-1$ positions, so that their end points are necessarily separated by at least $L-1$ signal-free (but still noisy) entries in the data.
-Furthermore, we require that the last signal occurrence in $y$ is also followed by at least $L-1$ signal-free entries.
-This property ensures that correlating $y$ with versions of itself shifted by at most $L-1$ entries does not involve correlating distinct signal occurrences.
-Once $s$ is determined, for each position $i$ such that $s[i] = 1$, one of the signals $x_k$ is selected independently at random, and accordingly we set $s_k[i] = 1$.
-As a result, the only properties of $s_1, \ldots, s_K$ that affect the autocorrelations of $y$ (for shifts up to $L-1$) are the total number of occurrences of the distinct signals: their individual and relative locations do not intervene.
-We detail this in Section~\ref{sec:AC_analysis}.
-
-%\revised{A follow-up paper~\cite{lan2019multi} extends this model by allowing an arbitrary spacing between signal occurrences, while excluding overlapping occurrences}.
-
-\paragraph{The Poisson model.}
-
-If the separation condition is violated, more knowledge about the location distribution is necessary to disentangle the autocorrelations of $y$. To that effect, we analyze a Poisson generative model.
-
-Specifically, for each position $i$, the number $s[i]$ of signal occurrences starting at that position is drawn independently from a Poisson distribution with parameter $\gamma/L$, that is, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$ for some parameter $\gamma > 0$.
-Then, $s[i]$ is split into $s_1[i] + \cdots + s_K[i]$ by selecting $s[i]$ signals among $x_1, \ldots, x_K$, independently at random  following a fixed distribution over $\{1,\ldots,K\}$.
-It is possible for more than one occurrence of the same $x_k$ to start at position~$i$.
-As for the well-separated model, the autocorrelations of $y$ under this model depend weakly on $s$ and $s_1, \ldots, s_K$, essentially through the parameter $\gamma$: see Section~\ref{sec:AC_analysis}.
-
-\subsection*{Extensions} \label{sec:extensions}
-
-Extending the problem setup and autocorrelation analysis to signals in more than one dimension is straightforward: see the discussion in Section~\ref{sec:high_dimensions} and numerical experiments in Section~\ref{sec:numerics}.
-
-Likewise, it is easy to extend the model to situations where the signal occurrences are sampled from a general distribution rather than from a finite set of choices $x_1, \ldots, x_K$.
-The finite setup corresponds to the following distribution for signal occurrences:
-\begin{align}
-	x \sim \sum_{k=1}^K \pi_k \delta(x - x_k),
-	\label{eq:heterogeneousdistribution}
-\end{align}
-where $\delta(x - x_k)$ is a Dirac delta (a point mass) located at $x_k$, and $(\pi_1, \ldots, \pi_K)$ encodes the discrete distribution over $\{1, \ldots, K\}$.
-In the generalized setup, the goal is to estimate the distribution (possibly defined by a finite set of parameters).
-In particular, this allows for continuous distributions of targets.
-We adopt this perspective when deriving the autocorrelations in Section~\ref{sec:AC_analysis}.
-
-In the next section, we show how this flexibility allows us to model an important imaging problem in structural biology.
-
-\section{Connection with single-particle reconstruction via cryo-electron microscopy} \label{sec:cryoem}
-
-Cryo-electron microscopy (cryo-EM)  has recently joined X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy as a high-resolution structural method for biological macromolecules~\cite{frank2006three,kuhlbrandt2014resolution,bartesaghi20152}.
-%In contrast to X-ray and NMR which aggregate information from an ensembles of
-%particles, single particle cryo-EM produces images of individual particles and thus can, in principle, elucidate multiple  structures simultaneously.
-%In addition, it does not require the formation of crystalline arrays of macromolecules.
-In a cryo--EM experiment, biological samples (e.g., macromolecules, viruses) are rapidly frozen in a thin layer of vitreous ice.
-The microscope produces 2-D tomographic images of the samples embedded in the ice, called \emph{micrographs}.
-Each micrograph contains multiple tomographic projections of the samples at unknown locations and under unknown viewing directions.
-Importantly, the electron dose must be kept low to mitigate  radiation damage, inducing high noise levels.
-The goal is to reconstruct 3-D models of the molecular structures from the micrographs. 
-Since  cryo-EM produces images of individual particles, it can elucidate multiple  structures simultaneously.
-This is in clear contrast to  X-ray and NMR, which aggregate information from an ensembles of
-particles.
-
-Considering the extensions described in the previous section, we can phrase a simplified generative model for micrographs (the observation $y$) within our framework.
-Specifically, locations are chosen in the 2-D plane of the image, corresponding to $s$: this is where the molecules are fixed in the plane of the ice layer.
-At each selected location, a 2-D tomographic projection of a molecule (a signal occurrence) is added in the observation $y$.
-This signal is drawn from a probability distribution described by a discrete number of parameters which correspond to the sought 3-D structure, as follows.
-
-The 3-D structure $V$ (the target parameter) can be expanded into a linear combination of basis functions (for example, spherical harmonics for the spherical part and Bessel functions for the radial part): the coefficients of this expansion are the unknowns.
-Then, a rotation $R_\omega$ is applied to the volume (to model viewing directions) according to a (possibly unknown) distribution of $\omega$ over $SO(3)$ (the group of 3-D rotations).
-With tomographic projection denoted by $P$, $x$ is a random signal, related to the distribution of $\omega$ through:
-%we have the following probability distribution for particles in the micrograph:
-\begin{align}
-	x & = P(R_\omega V).
-	\label{eq:cryoEM}
-\end{align}
-By further allowing $V$ itself to be a random signal as well, this model can also encode a mixture of structures in the biological sample.
-This mixture might also be continuous, corresponding to continuous conformational variability.
-
-All contemporary methods for single particle reconstruction using cryo-EM  split the reconstruction procedure into two main  stages.
-The first stage, called \emph{particle picking},  detects and extracts the particle projections from the micrographs.
-Given the projections, the second stage aims to reconstruct a 3-D model of the molecular structure, usually using an expectation-maximization algorithm~\cite{scheres2012relion}.
-%The quality of the reconstruction eventually hinges on the quality of the particle picking stage.
-Crucially, reliable detection of individual particles is impossible in a highly noisy environment. This fact has been recognized early on by the cryo-EM community. 
-Particularly, in~\cite{henderson1995limitations,glaeser1999electron}, it was reasoned that particle picking is impossible for molecules below a certain weight (below~$\sim$50 kDa). 
-%The unique issues raised by small particles have been mitigated by recent technological advances in the field, including the use of Volta phase plates~\cite{khoshouei2017cryo,liang2017phase} and scaffolding cages~\cite{liu2018nearatomic}.
-%Despite this progress, detecting small molecules in the micrographs remains a challenge.
-
-Even if particle picking is feasible, procedures may be affected by \emph{model bias}.
-Particle picking algorithms are typically based on correlating the micrograph with several templates.
-Areas highly correlated with some of the templates are assumed to contain projections: these yield the picked particles.
-Clearly, the picked particles depend heavily on the chosen templates: different templates may lead to different picked particles, hence, which is more problematic, to different 3-D structure reconstructions.
-The cryo-EM community is well aware of this potential pitfall~\cite{vanheel1992correlation,henderson2013avoiding,vanheel2013finding}, which was notably exemplified \revised{by} the ``Einstein from noise'' experiment~\cite{shatsky2009method}.
-
-A recent work of the authors suggests a methodology to bypass particle picking and  reconstruct the 3-D structure directly from the micrograph~\cite{bendory2018toward}.
-Based on autocorrelation analysis, it was shown that---at least in principle---the limits high noise regimes 
-impose on particle picking  do not necessarily translate into limits on 3-D reconstruction.
-The main goal of  the present paper is to provide theoretical and numerical support for this approach, in a simplified setting.
-
-In the next section, we introduce autocorrelation analysis in detail, focusing on the multi-target detection model. 
-We mention that similar ideas in  cryo-EM can be traced back to a seminal paper of Zvi Kam~\cite{kam1980reconstruction}.
-Kam proposed autocorrelation analysis for \mbox{3-D} reconstruction, under the assumption of picked, perfectly centered, particles.
-Kam's method has been extended and used in X-ray free electron lasers (XFEL) and cryo-EM~\cite{liu2013three,kurta2017correlations,levin20173d,von2018structure}.
-In order to investigate the computational and statistical properties of Kam's method, a series of papers have studied a simplified model, 
-called   \emph{multi-reference alignment}~\cite{bandeira2014multireference,bendory2017bispectrum,bandeira2017optimal,perry2017sample,bandeira2017estimation,abbe2017multireference}.
-We follow the same line of research by considering the multi-target detection as an abstraction to the application of reconstructing 3-D structures directly from the micrograph~\cite{bendory2018toward}.
-
-\section{Autocorrelation analysis} \label{sec:AC_analysis}
-
-In what follows, we consider autocorrelations of both the observation $y$ and of the signal occurrences in $y$.
-As per our discussion of extensions, the signal occurrences may be sampled from a discrete set $\{x_1, \ldots, x_K\}$ (as in~\eqref{eq:heterogeneousdistribution}), or from a more general distribution.
-Accordingly, we define autocorrelations broadly for a random signal $z$ of length $M$.
-For our purposes, this will be applied both to signal occurrences (of length $L$) and to $y$ (of length $N$).
-
-For a random signal $z\in \R^M$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
-\begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E_z\left\{\frac{1}{M} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\},
-\label{eq:ac_general}
-\end{equation}
-where the expectation is taken with respect to the distribution of $z$. Indexing out of bounds is zero-padded, that is, $z[i] = 0$ for $i$ out of the range $0, \ldots, M-1$.
-Explicitly, the first-, second- and third-order autocorrelations are given by: 
-\begin{align}  
-a_z^1 & = \E_z\left\{\frac{1}{M} \sum_{i=0}^{M-1} 
-z[i]\right\}, \nonumber\\
-a_z^2[\ell] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell\}}^{M-1 + \min\{0, -\ell\}} z[i]z[i+\ell]\right\}, \label{eq:ac_special} \\
-a_z^3[\ell_1,\ell_2] & = \E_z\left\{\frac{1}{M} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{M-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]\right\}. \nonumber
-\end{align}
-Since  autocorrelations depend only on the differences between indices, they obey the following symmetries: $$a_z^2[\ell] = a_z^2[-\ell],$$ and
-$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
-$$
-%In what follows, $x$ is the random variable corresponding to signal occurrences in $y$.
-% In particular, for the model~\eqref{eq:model}, 
-%$x=x_k$ with probability $\pi_k$.
-In particular, for
-$x$ sampled from $\{ x_1, \ldots, x_K \}$ with probabilities $(\pi_1, \ldots, \pi_K)$ as in~\eqref{eq:heterogeneousdistribution}, the autocorrelations of $x$ are given in explicit form in terms of those of the deterministic signals $x_1, \ldots, x_K$ as:
-\begin{align}
-	a_x^q  & = \sum_{k=1}^{K} \pi_ka_{x_k}^q.
-	\label{eq:mixedautocorr}
-\end{align}
-Explicit expressions of the autocorrelations for the more involved model of  cryo-EM~\eqref{eq:cryoEM} are given in~\cite{bendory2018toward}.
-
-We are given one observation (one realization) of $y$.
-Thus, we cannot compute the autocorrelations of $y$ exactly as they involve taking an expectation against the distribution of $y$.
-However, by the law of large numbers, as $N$ grows to infinity  the empirical autocorrelations of $y$ almost surely (a.s.) converge to the actual (population) autocorrelations of $y\in \RN$, that is, % (ergodicity)
-\begin{align}
-\lim_{N \to \infty} \frac{1}{N} \sum_{i=-\infty}^{\infty} y[i]y[i+\ell_1]\cdots y[i+\ell_{q-1}] \aseq a_y^q[\ell_1, \ldots, \ell_{q-1}].
-\end{align}
-This provides a concrete means of estimating the quantities $a_y^ q$.
-In the remainder of this section, we relate the observables $a_y^q$  to the unknowns $a_x^q$, first under the well-separated model, then under the Poisson model.
-
-\subsection{Autocorrelations under the well-separated model}
-
-Under the separation condition~\eqref{eq:spacing}, the relation between autocorrelations of the observation $y$ and those of $x$ is particularly simple, as we now show.
-It is useful to introduce some notation: let $\vert s\vert = \sum_i s[i]$ denote the number of signal occurrences in $y$, and let
-\begin{equation}
-\gamma  = \frac{|s| L}{N}.
-\label{eq:gamma}
-\end{equation}
-This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. %Henceforth, we call it the signal density.
-The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$. 
-For the heterogeneous model~\eqref{eq:model},  one can define
-\begin{equation}
-\gamma_k  = \frac{|s_k| L}{N},
-\label{eq:gamma_k}
-\end{equation}
-where $\vert s_k\vert = \sum_i s_k[i]$ so that $\gamma=\sum_k \gamma_k$.
-
-Owing to the separation condition, when correlating $y$ with shifted versions of itself for shifts in $0, \ldots, L-1$, any given occurrence of $x$ in $y$ is only ever correlated with itself, and never with another occurrence.
-As a result, the autocorrelations of $y$ depend on the corresponding autocorrelations of $x$, the noise level $\sigma$ and the density $\gamma$ (which is a weak dependence on the support signal $s$).
-Specifically, we show the following identities in Appendix~\ref{sec:autocorrelation_computation}:
-\begin{align} 
-	a_y^1 & = \gamma a_{x}^1, \label{eq:mean_micrograph} \\
-	a_y^2[\ell] & = \gamma a_{x}^2[\ell] + \sigma^2\delta[\ell], \label{eq:ac2_micrograph}\\
-	a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2]  + \sigma^2\gamma a_{x}^1  \big(\delta[\ell_1]+\delta[\ell_2]
-	+\delta[\ell_1-\ell_2]\big), \label{eq:ac3_micrograph}
-\end{align}
-where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$, and indices $\ell, \ell_1, \ell_2$ are in the range $0 \leq \ell \leq L-1$.
-Terms proportional to $\sigma^2$ are due to noise.
-If $\sigma$ is known, they can be handled easily.
-If $\sigma$ is unknown, one can either estimate it form the data, or one can ignore the few entries of the autocorrelations that are affected by $\sigma$---one in $a_y^2$ and $3L-2$ in $a_y^3$, a relatively small number in both cases.
-
-We show in Section~\ref{sec:theory_homogeneous_well_separated} 
-that $x,\gamma$ and $\sigma$ can be identified uniquely from the observed autocorrelations for the homogeneous case $K = 1$ (all signal occurrences are the same).
-
-\subsection{Autocorrelations under the Poisson model} \label{sec:ac_poisson}
-
-In this section, we give the expressions for the autocorrelations of the observed signal $y$ under the Poisson model.
-%In this model, each location $k$, $1 \le k \le N-L+1$ is the starting point of a Poisson-distributed number of random signals.
-%More precisely, letting $s[k]$ be the number of signals starting at location $k$, $s[k] \overset{iid}{\sim} \Poisson(\gamma / L)$.
- We first note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
-%
-\begin{align}
-\frac{N - L + 1}{N} \cdot \frac{\gamma  }{L}  \cdot L 
-\quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
-\end{align}
-%
-Therefore, in the large $N$ limit, similarly to the role of $\gamma$ in the well-separated model~\eqref{eq:gamma}, the parameter $\gamma$ may be interpreted as the signal density.
-
-In Appendix~\ref{sec:proof_prop_poisson}, we prove the following expressions for the autocorrelations of $y$ under the Poisson model.
-As in the well-separated model, the observed autocorrelations do not depend on individual occurrences of the signal, but only on the distribution of $x$ itself, and the parameters $\gamma$ and $\sigma$:
-%
-\begin{align}
-	a_y^1  & =  \gamma a_{x}^1, \label{eq:mean_micrograph2} \\
-	a_y^2[\ell] & = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell] + (\gamma a_x^1)^2, \label{eq:ac2_micrograph2} \\
-	a_y^3[\ell_1,\ell_2]  & =  \gamma a_x^3[\ell_1,\ell_2] + \sigma^2 \gamma a_x^1 \big(\delta[\ell_1]+\delta[\ell_2] +\delta[\ell_1-\ell_2] \big) \nonumber \\
-						  & \qquad + (\gamma a_x^1)^3 + \gamma a_x^1 \cdot ( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2] + \gamma a_x^2[\ell_2-\ell_1]). \label{eq:ac3_micrograph2}
-\end{align}
-Note that from those autocorrelations, it is easy to retrieve the autocorrelations of the well-separated model for all entries unaffected by $\sigma$.
-If $\sigma$ is known, then it is true for all entries.
-
-In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
-
-\section{Theory}
-
-We begin this section by showing that, in the homogeneous case ($K=1$), under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the (deterministic) signal $x$, the density parameter $\gamma$, and the noise level $\sigma^2$.
-Then, for the heterogeneous case ($K \geq 2$), we bound from above the number $K$ of signals that can be recovered from those autocorrelations as a function of the signal length $L$.
-Finally, we briefly discuss multi-dimensional signals.
-
-Before that, we start by showing that in the homogeneous case a deterministic signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
- Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero, we can recover $z$ explicitly by 
-\begin{equation}
-%
-z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]},
-\label{eq-uniqueness}
-%
-\end{equation}
-for $k = 0, \ldots, L-1$. If $z[0]$ or $z[L-1]$ are equal to zero, then $a_z^2[L-1] = 0$ and we can use that indication to shrink $L$.
-This proves the following useful fact:
-\begin{proposition} \label{prop:uniqueness}
-	%
-	A deterministic signal $z\in\RL$ is determined uniquely by  $a_z^2$ and $a_z^3$. 
-\end{proposition}
-
-Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations.
-In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex least-squares procedure, which is empirically robust to additive noise.
-In prior work, we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
-
-\subsection{Guarantees for the homogeneous well-separated model} \label{sec:theory_homogeneous_well_separated}
-
-The observed moments $a_y^1,a_y^2$ and $a_y^3$ under the well-separated model do not immediately yield the autocorrelations  of the signal $x$; rather, the two are related by the noise level $\sigma$ and the signal density $\gamma$.
-We will show, however, that all parameters---$x, \gamma$ and $\sigma^2$---are still identified uniquely by the observed moments of $y$.
-
-First, we observe that if  the noise level $\sigma$ is known, generally, one can estimate $\gamma$ from the first two moments of the micrograph.
-The other direction is true as well: if $\gamma>0$ is known, then one can estimate $\sigma^2$.
- The proof is provided in Appendix~\ref{sec:proof_prop_gamma}.
-
-\begin{proposition} \label{prop:gamma}
-	Assume the separation condition~\eqref{eq:spacing} holds and $K=1$ (all signal occurrences in $y$ are identical, up to noise). If the mean of $x$ is nonzero, then  
-	\begin{equation}
-	\gamma  = \frac{L (a^1_y)^2}{a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\sigma^2},
-	\end{equation}
-	meaning $\gamma$ can be determined from $\sigma$ (and vice versa) using the observables $a_y^1, a_y^2$.
-\end{proposition}
-
-Using third-order autocorrelation information of $y$, both the ratio $\gamma$ and the noise $\sigma$ can be determined simultaneously.
-For the following results, when we say that a result holds for a ``generic'' signal $x$, we mean that the set of signals which cannot be determined by these measurements
-has Lebesgue measure zero. 
-In particular, this means that we can recover
-almost all signals with the given measurements. The proof is provided in Appendix~\ref{sec:proof_prop_gamma_sigma}.
-
-\begin{proposition} \label{prop:gamma_sigma}
-	Assume $L \geq 3$, $K=1$ and assume that the separation condition~\eqref{eq:spacing} holds. 
-	Then, the observed autocorrelations $a_y^1,a_y^2$ and  $a_y^3$ determine the ratio $\gamma$ and noise level $\sigma$ uniquely for a generic signal $x$.
-If $\gamma > \frac{1}{4}$, then this holds for any signal $x$ with nonzero mean.
-\end{proposition}
-
-From Propositions~\ref{prop:uniqueness} and~\ref{prop:gamma_sigma} we   deduce the following:
-\begin{corollary}
-	Assume $L \geq 3$ and $K=1$.
-	Under the separation condition~\eqref{eq:spacing}, the signal $x$, the ratio $\gamma$, and the noise level $\sigma$ are determined from the first three autocorrelation functions of $y$ if either the signal $x$ is generic, or $x$ has nonzero mean  and $\gamma > \frac{1}{4}$.
-\end{corollary}
-%
-%As a side note, under the separation condition, the length $L$ of the signal can also be determined from the autocorrelations in the asymptotic regime, by inspection of the support of $a_y^2$.
-
-\subsection{Guarantees for the homogeneous Poisson model} \label{sec:theory_homogeneous_poisson}
-
-Similarly to the homogeneous well-separated model, the observed autocorrelations under the Poisson model identify $x,\gamma$ and $\sigma^2$ uniquely.
-Opposed to Proposition~\ref{prop:gamma_sigma}, these quantities can be computed explicitly. 
-In Appendix~\ref{sec:proof_uniqueness_poisson} we prove the following result:
-
-\begin{proposition} \label{prop:uniqueness_poisson}
-Under the homogeneous Poisson model, the signal $x$, the noise level $\sigma^2$ and the Poisson parameter $\gamma$ are identified uniquely. 
-In particular,
-	\begin{align}
-\gamma &= L \frac{(\gamma a_y^1) (a_y^2[1] - (a_y^1)^2)}
-{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
-	+ \sum_{\ell=2}^{L-1} \gamma a_x^3[\ell,\ell+1]}, \\
-\sigma^2 &= a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-- (2 L - 1) (a_y^1)^2,
-\end{align}
-where 
-\begin{align}
-\gamma a_x^3[\ell_1,\ell_2]
-&= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
-- a_y^1 \cdot \big(a_y^2[\ell_1]  
-+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
-\end{align}
-
-\end{proposition}
-
-\subsection{Elementary limitations of the heterogeneous case}
-\label{sec:heterogeneity}
-
-In the heterogeneous model~\eqref{eq:model}, the unknowns are $K$ signals of length $L$, together with their densities $\gamma_1, \ldots, \gamma_K$~\eqref{eq:gamma_k} (equivalently: the distribution $\pi$ and overall density $\gamma$) and possibly the noise level $\sigma$.
-To estimate these parameters, we must collect at least as many independent equations.
-Within our framework, polynomial equations are provided by the observable autocorrelations, which correspond to mixed autocorrelations of the unknowns as per~\eqref{eq:mixedautocorr}.
-In this section, following~\cite{boumal2017heterogeneous}, we count how many equations the first three autocorrelations may provide in the best case (discounting symmetries).
-This leads to a straightforward information-theoretic upper bound on the number $K$ of signals which can be estimated, as a function of $L$.
-This is only an upper bound, though a bound of the same type was shown to be tight in a similar setting~\cite{bandeira2017estimation}.
-The counting is based on the autocorrelations of the well-separated model.
-For entries independent of $\sigma$, the autocorrelations of the Poisson process contain the same information as those of the well-separated model.
-If $\sigma$ is known, this holds true for all entries; see Section~\ref{sec:ac_poisson}.
-
-The first-order autocorrelation $a_y^1$~\eqref{eq:mean_micrograph} provides one equation.
-For second-order autocorrelations $a_y^2[\ell]$~\eqref{eq:ac2_micrograph}, if $\sigma$ is known we obtain $L$ equations with $\ell$ ranging from 0 to $L-1$.
-If $\sigma$ is unknown, we may disregard $a_y^2[0]$ (the only entry affected by $\sigma$) and still collect $L-1$ equations.
-Similarly, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$~\eqref{eq:ac3_micrograph} with $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries), providing $\frac{(L+1)(L+2)}{2}-2$ equations in total.
-If we further exclude any entries such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$, there are $\frac{(L-1)(L-2)}{2}$ remaining entries.
-
-Hence, if $\sigma$ is known we collect
-\begin{align*}
-	1 + L + \frac{(L+1)(L+2)}{2}-2 = \frac{1}{2} L (L+5)
-\end{align*}
-equations, while if it is unknown and we choose not to estimate it, then we collect
-\begin{align*}
-	1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
-\end{align*}
-equations in total. Of course, there may be redundancy in these equations: we aim only to provide an upper bound. %under the assumption that these equations are independent.
-
-Since we aim to estimate $KL$ parameters for the $K$ signals of length $L$, plus $K$ parameters for the densities $\gamma_k$, %(or the distribution $\pi$ and overall density $\gamma$)
- there are $K(L+1)$ unknowns. As a result, an absolute upper bound on $K$ such that the estimation problem may be solvable is
-\begin{align*}
-	K \leq \frac{L(L+5)}{2(L+1)}
-\end{align*}
-for the case of $\sigma$ known, and
-\begin{align*}
-	K \leq \frac{ L (L-1) + 1}{2(L+1)}
-\end{align*}
-for the case of $\sigma$ unknown and not estimated.
-Overall, this indicates that, at best, approximately $L/2$ signals and their densities can be recovered from the first three mixed autocorrelations.
-Based on related results in~\cite{bandeira2017estimation}, we expect that as many as $L/2$ signals can indeed be estimated, though possibly not with computationally tractable estimators.
-
-\subsection{Autocorrelations in higher dimensions} \label{sec:high_dimensions}
-
-Autocorrelations in $d$ dimensions are defined for  $\ell_1,\ldots,\ell_{q-1}\in\mathbb{Z}^d$  as 
-\begin{equation}
-a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \E\left\{\frac{1}{L^d} \sum_{i\in\mathbb{Z}^d} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}]\right\}.
-\label{eq:ac_d_dimension}
-\end{equation}
-Interestingly, for the homogeneous case ($K=1$) in dimensions greater than one, almost all  signals are determined uniquely from their second-order autocorrelation, up to two symmetries: sign (or phase for complex signals) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction}.
-If the mean of the signal is available and non-zero, the sign symmetry can be resolved.
-However, determining the reflection symmetry still requires additional information, beyond the second-order autocorrelation.
-The case of 1-D signals is fundamentally different: generally there are $2^{L-2}$ signals with the same second-order autocorrelation (after eliminating  symmetries)~\cite{beinert2015ambiguities,bendory2017fourier}.
-
-This uniqueness result for two and three-dimensional signals is the basis of a popular imaging technique called coherent diffraction imaging (CDI). In CDI, an object is
-illuminated with a coherent wave, and the far field diffraction pattern  is measured, corresponding to the object's Fourier magnitude~\cite{miao1999extending,shechtman2015phase}. 
-If the diffraction pattern is over-sampled by at least  twice the Nyquist frequency,  the data is equivalent to the signal's second-order autocorrelation.
-In this context, the computational problem of recovering the signal from its second-order autocorrelation is usually referred to as \emph{phase retrieval} or the \emph{phase problem}.
-Despite the uniqueness result, recently it has been shown that the problem is  ill-conditioned---at least for 2-D images~\cite{barnett2018geometry}.
-That is, there exist other images whose second-order autocorrelations agree up to machine precision.
-
-\section{Algorithms and numerical experiments} \label{sec:numerics}
-
-In this section, we present three numerical experiments.
-In the first two experiments, we consider the heterogeneous model~\eqref{eq:model}.
-First, with a fixed noise level, we show how the estimation quality improves as the length of the observation grows.
-Second, we explore how many signals can be recovered as a function of their length, in an infinite data regime where effects of the noise have been averaged out.
-In the last experiment, we extend our model to 2-D signals.
-We run the experiments on a shared computer with 144 logical CPUs of type Intel(R) Xeon(R)
-CPU E7-8880 v3 $@$ 2.30GHz and 755Gb of RAM; we use at most 72 of these CPUs.
-The code for all experiments is available at \url{https://github.com/PrincetonUniversity/BreakingDetectionLimit}.
-
-\subsection{Experiment 1} 
-\label{sec:XP1}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_466300}
-	\caption{Experiment described in Section~\ref{sec:XP1}.
-For a fixed noise level $\sigma = 3$ and a fixed set of $K = 3$ signals of length $L = 21$, an observation $y$ of length $N = 1.23 \cdot 10^{10}$ is generated according to~\eqref{eq:model} in the well-separated model, with fixed  occurrence probabilities.
-Each row corresponds to one of the signals.
-The last column shows evolution of the relative root mean squared error in estimating each signal, as a longer and longer subset of $y$ is observed.
-Red dots mark the three snapshots that are illustrated in columns 1--3: red signals are the ground truth and blue signals are the estimators.}
-	\label{fig:1Dheterosignals}
-\end{figure}
-
-For the experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$: see the three red signals in the first column.
-Following~\eqref{eq:model}, we generate an observation $y$ of length $12.3 \cdot 10^9$.
-Each of the three signals appears, respectively (and approximately), $30.0 \cdot 10^6$, $20.0 \cdot 10^6$ and $10.0 \cdot 10^6$ times in $y$ for a total of exactly $60 \cdot 10^6$ occurrences, such that at least $L-1$ zeros separate any two occurrences of any signals according to~\eqref{eq:spacing}.
-This is done by randomly selecting $60 \cdot 10^6$ placements in $y$, one at a time with an accept/reject rule based on the separation constraint~\eqref{eq:spacing} and locations picked so far.
-For each placement, one of the three signals is picked at random according to the proportions $\pi = (1/2, 1/3, 1/6)$.
-Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting signal-to-noise ratio of $y$
-% sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/9.
-
-Visually, the noise dominates the signal to the point that it is challenging to detect occurrences.
-More precisely, the cross-correlations of $y$ even with the true signals presents peaks at essentially random locations,  uninformative of the actual locations of the signal occurrences.
-Thus, we contend that it would be difficult for any algorithm to locate the signal occurrences, let alone to cluster them according to which signal appears where.
-
-Our aim is to investigate how accurately we can estimate the signals as a function of the observation length.
-To this end, we consider a growing part of the observation $y$.
-For each length, we compute autocorrelations on that part, then we go on to estimate the signals from these ``mixed'' quantities.
-In practice, the autocorrelations are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points.
-Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
-If multiple GPUs are available, segments can  be handled in parallel.
-
-Having computed the autocorrelations of interest, we estimate signals $x_1, \ldots, x_K$ and coefficients $\gamma_1, \ldots, \gamma_K$ which agree with the data.
-We choose to do so by running an optimization algorithm on the following nonlinear least-squares problem:
-\begin{multline}
-	\min_{\substack{\hat x_1, \ldots, \hat x_K \in \R^{W} \\ \hat \gamma_1, \ldots, \hat \gamma_K > 0}} w_1 \left( a_y^1 - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^1 \right)^2 + w_2 \sum_{\ell = 1}^{L-1} \left( a_y^2[\ell] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^2[\ell] \right)^2 + \\ w_3 \sum_{\substack{2\leq\ell_1\leq L-1 \\ 1 \leq \ell_2 \leq \ell_1-1}} \left( a_y^3[\ell_1, \ell_2] - \sum_{k=1}^K \hat \gamma_k a_{\hat x_k}^3[\ell_1,\ell_2] \right)^2,
-	\label{eq:optim1D}
-\end{multline}
-where $W \geq L$ is the length of the sought signals and the weights are set to $w_1 = 1/2, w_2 = 1/2n_2, w_3 = 1/2n_3$, where $n_2, n_3$ are the number of coefficients used for each autocorrelation order: $n_2 = L-1$, $n_3 = \frac{(L-1)(L-2)}{2}$ (weights could also be set in accordance with variance estimates as in~\cite{boumal2017heterogeneous}).
-
-Setting $W = L$ (as is a priori desired) is problematic because the above optimization problem appears to have numerous poor local optimizers.
-Thus, we first run the optimization with $W = 2L-1$.
-This problem appears to have few poor local optima, perhaps because the additional degrees of freedom allow for more escape directions.
-Since we hope the signals estimated this way correspond to the true signals zero-padded on either side to length $W$, we extract from each one a subsignal of length $L$ that has largest $\ell_2$-norm.
-This estimator is then used as initial iterate for~\eqref{eq:optim1D}, this time with $W = L$.
-We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
-Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
-
-In Figure~\ref{fig:1Dheterosignals}, we find that the signals can be recovered with good accuracy despite the noise levels which seemingly hinders location and clustering.
-We also note that the amount of data required to produce these good estimations is large.
-Furthermore, as illustrated here and as we have observed in numerous experiments, signals with more variations (such as the third signal in this experiment which was generated once from a Gaussian distribution) are easier to estimate accurately than more regular signals (in this case, despite the fact that the third signal occurs less frequently than the others).
-This phenomenon has been also observed in multi-reference alignment~\cite[Section 3.2]{perry2017sample}.
-
-\subsection{Experiment 2}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=.7\linewidth]{XP1}
-	\caption{In the $N \to \infty$ regime (access to exact autocorrelations, excluding biased entries) and with known uniform densities, it seems that $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments.
-CPU time is in seconds.
-Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed autocorrelations; see Section~\ref{sec:heterogeneity}.
-Similarly to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
-	\label{fig:KLXP}
-\end{figure}
-
-In this second experiment, presented in Figure~\ref{fig:KLXP}, we investigate how many distinct signals ${x_1, \ldots, x_K}$ can be estimated from mixed autocorrelations~\eqref{eq:mixedautocorr}.
-In order to do so, we consider a setup where the mixed autocorrelations are known perfectly.
-This corresponds to the limit of an infinitely long observation $y$ with fixed density $\gamma$ and fixed noise level (that may be arbitrarily high).
-The specific value of $\sigma$ is immaterial since we only consider autocorrelations that are unaffected by noise bias.
-Furthermore, we assume uniform occurrence distribution $\gamma_k$ (known to the algorithm), and known density $\gamma$ (which is then irrelevant as it only induces a global scaling of the autocorrelations of~$y$).
-
-To produce Figure~\ref{fig:KLXP}, we consider each pair $(K, L)$ in turn, with $K = 1, 2, 3, \ldots, 10$ and $L = 5, 10, 15, \ldots, 100$.
-For each pair, we generate $K$ random normal signals of length $L$, once.
-The perfect mixed autocorrelations are computed.
-They are then provided to the inversion algorithm described in Section~\ref{sec:XP1}, together with the knowledge that signals occur with equal probability, as well as the correct density $\gamma$.
-The algorithm is initialized 50 times with an independent random initial guess, also following a normal distribution.
-For each run, we record three metrics:
-\begin{enumerate}
-	\item Whether the optimization algorithm managed to produce a solution with cost function value below $10^{-16}$: this assesses whether optimization succeeded.
-	\item The relative root mean squared error between the estimated signals and the ground truth (up to permutation of the $K$ signals.)
-	\item The computation time in seconds (keeping in mind that the 50 runs are done in parallel on the same, shared computer, so that this is more of a qualitative assessment.)
-\end{enumerate}
-These metrics are summarized and presented in Figure~\ref{fig:KLXP} as three panels.
-\begin{enumerate}
-	\item Panel 1 shows for each pair $(K, L)$ which fraction of the 50 runs reached optimality (between 0 and 1).
-	\item For each pair $(K, L)$, any estimator produced by the optimization algorithm such that the cost function value is close to zero must be considered a valid estimator, since it agrees almost perfectly with the data.
-For all of those, we compute the error compared to the ground truth.
-Panel 2 shows the largest such error, on a log scale in base 10.
-(If optimization never succeeded for that pair, we report a relative error of 1.) A large value means that, among all near global optima of the optimization problem (if any), at least one was a poor estimator.
-A small value indicates all computed near global optima were good estimators.
-	\item Median $\log_{10}$ computation time (where the median is computed after taking the log of the CPU times, in base 10.)
-\end{enumerate}
-
-Following~\cite{boumal2017heterogeneous}, overlaid on the panels we trace the red curve $K = \sqrt{L}$ as well as red dots which are computed from the considerations in Section~\ref{sec:heterogeneity} (adapted to the fact that the $\gamma_k$'s are known).
-We observe that strictly above the red dots the optimization problem appears to be easy to solve (despite non-convexity), yet, as predicted, the corresponding estimators are not informative since there is not enough information in the computed quantities compared to the number of parameters.
-On the other hand, below the (empirical) red curve, the optimization problem is sometimes solved to optimality (although it may take more than one random initialization to get one successful run), and the corresponding estimators are accurate.
-In between the red curve and the red dots, the optimization problem appears to be particularly challenging: we essentially never produce a global optimum, hence we also do not have an estimator.
-This experiment suggests a possible computational-statistical gap in the area between the red curve and the red dots, where it is possible that the signals could be estimated, but perhaps not with a computationally efficient procedure.
-Similar results were observed for the multi-reference problem~\cite{boumal2017heterogeneous,weinthesis,bandeira2017estimation}.
-
-\subsection{Experiment 3}
-
-Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimate 
-a 50-by-50 pixel grayscale picture of Einstein with mean zero from a growing number of observations $y$.
-Each observation is of size $4096\times 4096$ pixels and contains 700 occurrences on average at random locations, while maintaining the separation condition~\eqref{eq:spacing} in each axis separately.
-The observations are contaminated with additive white Gaussian noise with standard deviation $\sigma = 3$, illustrated in Figure~\ref{fig:micro_example}.
-
-We compute the average second-order autocorrelation of the observations.
-This is a particularly simple computation which can be efficiently executed with a fast Fourier transform (FFT), in parallel over the numerous observations.
-We assume the number of signal occurrences (akin to the density $\gamma$) and the standard deviation of the noise, $\sigma$, are known.
-Given those quantities, the second-order autocorrelation of the image can be easily deduced from~\eqref{eq:ac2_micrograph}.
-As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelations.
-Then, to estimate the target image, we use a standard phase retrieval algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017rrr}, initialized randomly.
-
-\begin{figure}[t]
-	\centering
-	\begin{subfigure}[h]{0.33\linewidth}
-		\centering
-		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_clean}
-		\caption{$\sigma = 0$}
-	\end{subfigure}%
-	\begin{subfigure}[h]{0.33\linewidth}
-		\centering
-		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s05}
-		\caption{$\sigma = 0.5$}
-	\end{subfigure}
-	\begin{subfigure}[h]{0.33\linewidth}
-		\centering
-		\includegraphics[width=.8\linewidth]{micrograph_Einstein_example_s3}
-		\caption{$\sigma = 3$}
-	\end{subfigure}
-	\caption{\label{fig:micro_example} Example of observations for the 2-D experiment (of size $250\times 250$) with additive white Gaussian noise of variance $\sigma^2$ for increasing values of $\sigma$.
-Each observation contains the same four occurrences of a $50 \times 50$ image of Einstein.
-In panel (c), the noise level is such that it is challenging to detect  the planted images.}
-\end{figure}
-
-Relative error is measured as the ratio of the root mean square error to the norm of the ground truth (square root of the sum of squared pixel intensities).
-Figure~\ref{fig:Einst_example} shows several estimated images for a growing number of observations.
-Figure~\ref{fig:error_per_micro} presents the normalized recovery error as a function of the amount of data available.
-This is computed after fixing the reflection symmetries (see Section~\ref{sec:high_dimensions}).
-
-As evidenced by these figures, the ground truth image can be estimated increasingly well from increasingly many observations, without the need to locate the signal occurrences.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
-	\caption{\label{fig:Einst_example} Recovery of Einstein from observations at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)).
-Averaged autocorrelations of the data allow to estimate the power spectrum of the target image.
-This does not require locating the signal occurrences.
-The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4$ and $2\times 10^5$ observations (growing across panels from left to right).}
-	%	\vspace{-8pt} 
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
-	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}. Each observation contains about 700 image occurrences at unknown locations.}
-\end{figure}
-
-\section{Summary}
-
-This paper suggests a computational  framework for estimation under extreme noise levels. 
-The crux of the method lies in the distinction between parameters of interest (the signals) and nuisance variables (parameters associated with individual signal occurrences, such as location and class).
-In part through theory and in part through numerical experiments, we show that estimating the signals is possible even when they cannot be detected in the data.
-The method consists of two steps.
-First, we estimate the autocorrelations of the observation.
-A key feature is that, for any noise level, these autocorrelations can be estimated to any desired accuracy given sufficiently rich observations.
-Second, we recover the signals from the autocorrelations.
-This recovery entails solving a system of low-order polynomial equations.
-While solving such systems is hard in general, we found that in the homogeneous case we can solve them explicitly, and in both the homogeneous and heterogeneous cases we can solve them with reasonable robustness through non-convex optimization, in a wide regime of parameters.
-%The properties of the specific systems (e.g., its condition number) affects the feasibility of the estimation procedure.
-
-The prime motivation of this paper emanates from challenges in small particle reconstruction using cryo-EM.
-Small particles induce such low signal-to-noise ratio in the micrograph that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
-The main message of our recent report~\cite{bendory2018toward} is that particle picking is merely a means to an end (although admittedly of key usefulness when it can be done): the locations and classes of individual particle projections are nuisance variables.
-The ultimate goal is only to estimate the 3-D structures.
-To this end,  we used autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
-In order to gain better understanding of the method, this paper focuses on an abstraction of cryo-EM---the multi-target detection model. 
-Our next goal is to reconsider the full cryo-EM model, both from theoretical and algorithmic perspectives. 
-In particular, the numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using autocorrelations up to third order is limited by ill-conditioning of the system of polynomial equations.
-Higher resolution may require computing higher-order autocorrelations, which would increase the sample complexity and computational complexity of the algorithm.
-Despite the challenges, we believe that this approach may ultimately offer a way to reconstruct 3-D structures that are too small for current algorithmic pipelines.
-
-%
-%In addition, the model analyzed in~\cite{bendory2018toward} is somewhat simplified. 
-%A full cryo-EM model includes, in addition to the target volume,
-%multiple parameters:
-%the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored), and  the microscope contrast-transfer function.
-%These parameters will be encoded within the estimated autocorrelations.
-%If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations.
-Again, estimating those parameters may require high-order autocorrelations.
-
-\section*{Acknowledgment} 
-The authors  thank Ayelet Heimowitz, Joe Kileel, Ti-Yen Lan and Amit Moscovich  for helpful discussions.
-The research is supported in parts by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, the Moore Foundation Data-Driven Discovery Investigator Award, and NSF BIGDATA Award IIS-1837992.
-NB is partially supported by NSF award DMS-1719558.
-
-\bibliographystyle{plain}
-\bibliography{ref}
-
-\appendix
-
-\section{Autocorrelations in the well-separated model} \label{sec:autocorrelation_computation}
-
-Let $x_{(1)}, \ldots, x_{(|s|)}$ denote the (independent) realizations of the random signal $x$ in the observation $y$, starting at (deterministic) positions $s_{(1)}, \ldots, s_{(|s|)}$.
-Let $I_{ij}$ be the indicator variable for whether position $i$ is in the support of occurrence $j$, that is, it is one if $i$ is in $\{s_{(j)}, \ldots, s_{(j)}+L-1\}$, and zero otherwise.
-Then,
-\begin{align}
-y[i] & = \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i].
-\label{eq:explicityiindicators}
-\end{align}
-This gives a simple expression for the first autocorrelation of $y$. Indeed,
-\begin{align}
-a_y^1 & = \E_y\left\{ \frac{1}{N} \sum_{i = 0}^{N-1} y[i] \right\} \\
-& = \frac{1}{N} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\left\{ \sum_{i = 0}^{N-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right\}.
-\end{align}
-Now switch the sums over $i$ and $j$, and observe that $I_{ij}$ is zero unless $i = s_{(j)} + t$ for $t$ in the range $0, \ldots, L-1$. Hence,
-\begin{align}
-a_y^1 & = \frac{1}{N} \sum_{j = 1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-1} x_{(j)}[t]\right\} + \frac{1}{N} \E_\varepsilon\left\{ \sum_{i=0}^{N-1} \varepsilon[i]\right\}.
-\end{align}
-Since the noise has zero mean and $x_{(1)}, \ldots, x_{(|s|)}$ are identically distributed, we further find:
-\begin{align}
-a_y^1 & = \frac{|s|L}{N} a_x^1 = \gamma a_x^1.
-\end{align}
-
-To address the second-order moments, we resort to the separation condition~\eqref{eq:spacing}. First, consider this expression:
-\begin{align*}
-N \cdot a_y^2[\ell] & = \E_y\left\{ \sum_{i = 0}^{N-\ell-1} y[i] y[i+\ell] \right\} \\
-& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|)}, \varepsilon}\Bigg\{ \left( \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i] \right) \cdot \\
-& \qquad \qquad \qquad \qquad \qquad  \left( \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] + \varepsilon[i+\ell] \right)  \Bigg\} \\
-& = \sum_{i = 0}^{N-\ell-1} \E_{x_{(1)}, \ldots, x_{(|s|), \varepsilon}}\Bigg\{ \sum_{j = 1}^{|s|} \sum_{j' = 1}^{|s|} I_{ij}  I_{i+\ell,j'} x_{(j)}[i-s_{(j)}]  x_{(j')}[i+\ell-s_{(j')}] \\
-& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell] \\
-& \qquad \qquad \qquad \qquad \qquad \qquad + \sum_{j' = 1}^{|s|} I_{i+\ell,j'} x_{(j')}[i+\ell-s_{(j')}] \varepsilon[i] \\
-& \qquad \qquad \qquad \qquad \qquad \qquad + \varepsilon[i] \varepsilon[i + \ell] \Bigg\}.
-\end{align*}
-The cross-terms vanish in expectation since $\varepsilon$ is zero mean and independent from the signal occurrences.
-The last term vanishes in expectation unless $\ell = 0$ since distinct entries of $\varepsilon$ are independent.
-For $\ell = 0$, $\E\{\varepsilon[i]^2\} = \sigma^2$.
-Finally, using the separation property, observe that if $I_{ij}  I_{i+\ell,j'}$ is nonzero, then it is equal to one, $j = j'$ and $i = s_{(j)} + t$ for some $t$ in $0, \ldots, L-\ell-1$.
-Then, switch the order of summations to get
-\begin{align}
-N \cdot a_y^2[\ell] & = \sum_{j=1}^{|s|} \E_{x_{(j)}}\left\{ \sum_{t = 0}^{L-\ell-1} x_{(j)}[t] x_{(j)}[t+\ell] \right\} + (N-\ell)\sigma^2 \delta[\ell],
-\end{align}
-where $\delta[0] = 1$ and $\delta[\ell \neq 0] = 0$. Since each $x_{(j)}$ is distributed as $x$, they all have the same autocorrelations as $x$ and we finally get
-\begin{align}
-a_y^2[\ell] & = \gamma a_x^2[\ell] + \frac{N-\ell}{N}\sigma^2 \delta[\ell] = \gamma a_x^2[\ell] + \sigma^2 \delta[\ell].
-\end{align}
-
-We now turn to the third-order autocorrelations. These involve the sum
-\begin{align}
-\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} y[i] y[i+\ell_1] y[i+\ell_2].
-\end{align}
-Using~\eqref{eq:explicityiindicators}, we find that this quantity can be expressed as a sum of eight terms:
-% \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] + \varepsilon[i]
-\begin{enumerate}
-	\item $\sum_i \sum_{j,j',j'' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
-	\item $\sum_i \sum_{j,j' = 1}^{|s|} I_{ij} I_{i+\ell_1, j'} x_{(j)}[i-s_{(j)}] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
-	\item $\sum_i \sum_{j,j'' = 1}^{|s|} I_{ij} I_{i+\ell_2,j''} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
-	\item $\sum_i \sum_{j',j'' = 1}^{|s|} I_{i+\ell_1, j'} I_{i+\ell_2,j''} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] x_{(j'')}[i+\ell_2-s_{(j'')}]$
-	\item $\sum_i \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
-	\item $\sum_i \sum_{j' = 1}^{|s|} I_{i+\ell_1, j'} \varepsilon[i] x_{(j')}[i+\ell_1-s_{(j')}] \varepsilon[i+\ell_2]$
-	\item $\sum_i \sum_{j'' = 1}^{|s|} I_{i+\ell_2,j''} \varepsilon[i] \varepsilon[i+\ell_1] x_{(j'')}[i+\ell_2-s_{(j'')}]$
-	\item $\sum_i \varepsilon[i] \varepsilon[i+\ell_1] \varepsilon[i+\ell_2]$
-\end{enumerate}
-Terms 2--4 and 8 vanish in expectation since odd moments of centered Gaussian variables are zero. For the first term, we use the fact that the separation condition implies
-\begin{multline}
-I_{ij} I_{i+\ell_1, j'} I_{i+\ell_2,j''} = 1 \iff \\ j=j'=j'' \textrm{ and } i = s_{(j)} + t \textrm{ with } t \in \{ 0, \ldots L-\max(\ell_1, \ell_2)-1 \}.
-\end{multline}
-(Otherwise, the product of indicators is zero.) This allows to reduce the summations over $j,j',j''$ to a single sum over $j$.
-Then, switching the order of summation with $i$, we get that the first term is equal to
-\begin{align}
-\sum_{j=1}^{|s|} \sum_{t=0}^{L-\max(\ell_1, \ell_2)-1} x_{(j)}[t] x_{(j)}[t+\ell_1] x_{(j)}[t+\ell_2].
-\end{align}
-In expectation over the realizations $x_{(j)}$, using again that they are i.i.d.\ with the same distribution as $x$, this first term yields $|s|L a_x^3[\ell_1, \ell_2]$.
-Now consider the fifth term.
-Taking expectation against $\varepsilon$ yields
-\begin{align}
-\sum_{i=0}^{N-\max(\ell_1, \ell_2)-1} \sum_{j = 1}^{|s|} I_{ij} x_{(j)}[i-s_{(j)}] \sigma^2 \delta[\ell_1 - \ell_2].
-\end{align}
-Switch the order of summation over $i$ and $j$ again to get
-\begin{align}
-\sigma^2 \delta[\ell_1 - \ell_2] \sum_{j = 1}^{|s|} \sum_{t=0}^{L-1} x_{(j)}[t].
-\end{align}
-Now taking expectation against the signal occurrences yields $|s|L \sigma^2 a_x^1 \delta[\ell_1 - \ell_2]$.
-A similar reasoning for terms 6 and 7 yields this final formula for the third-order autocorrelations of $y$:
-\begin{align}
-a_y^3[\ell_1, \ell_2] & = \gamma a_x^3[\ell_1, \ell_2] + \gamma \sigma^2 a_x^1 \left( \delta[\ell_1] + \delta[\ell_2] + \delta[\ell_1 - \ell_2] \right).
-\end{align}
-
-%\section{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
-
-\section{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}
-
-We will denote by $m_l$ the moment tensors of $x$:
-%
-\begin{align}
-%
-m_1[i] = \E x[i], \quad 0 \le i \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-m_2[i,j] = \E x[i] x[j], \quad 0 \le i,j \le L-1,
-%
-\end{align}
-%
-\begin{align}
-%
-m_3[i,j,k] = \E x[i] x[j] x[k], \quad 0 \le i,j,k \le L-1.
-%
-\end{align}
-
-We obtain the autocorrelations $a_x^l$ of $x$ by averaging over a slice of the moment tensors:
-%
-\begin{align}
-%
-a_x^1 = \frac{1}{L}\sum_{i=0}^{L-1} m_1[i],
-%
-\end{align}
-%
-\begin{align}
-%
-a_x^2[\ell] = \frac{1}{L} \sum_{i=0}^{L-1} m_2[i,i+\ell],
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-a_x^3[\ell_1,\ell_2] = \frac{1}{L}\sum_{i=0}^{L-1} m_3[i,i+\ell_1,i+\ell_2].
-%
-\end{align}
-
-We will make repeated use of the following elementary lemma:
-%
-\begin{lem} \label{lem-choose}
-	%
-	If $z \sim \Poisson(\lambda)$, then 
-	\begin{align}
-	%
-	\E {z\choose k} = \frac{\lambda^k}{k!}.
-	%
-	\end{align}
-\end{lem}
-
-%
-
-\subsection{Computing $a_y^1$}
-
-We will first condition on the vector $s$ of locations of the subsignals in $y$, and then average over $s$.
-We will denote by $x_{(1)}^{i},\dots,x_{(s[i])}^i$ the random vectors starting  in $y[i]$.
-We have:
-%with position 0 located at $i$. We have:
-%
-\begin{align}
-%
-\E[ y[i] | s ] = \sum_{j=0}^{L-1} \sum_{k=1}^{s[i-j]} \E x_{(k)}^{i-j}[j]
-= \sum_{k=1}^{s[i-j]} L a_x^1
-= s[i-j] L a_x^1.
-%
-\end{align}
-%
-Now taking expectations over $s$ and using $\E s[i-j] = \gamma/L$ we get:
-%
-\begin{align}
-%
-\E y[i] = \gamma a_x^1.
-%
-\end{align}
-%
-Consequently,
-%
-\begin{align}
-a_y^1 = \frac{1}{N} \sum_{i=1}^n \E y[i] = \gamma a_x^1.
-\end{align}
-
-%
-
-\subsection{Computing $a_y^2$}
-
-First we will consider the noise-free case, where $\sigma = 0$. We will condition on $s$ first, and then take the expectation over $s$. Fix $i_1 \ne i_2$, and let $\ell = i_2 - i_1$. Then:
-%
-\begin{align}
-%
-y[i_1] y[i_2]
-&= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]}
-x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2].
-%
-\end{align}
-
-We break up the double sum over $j_1$ and $j_2$ into two terms: one where $j_2 \ne j_1 + \ell$, and one where $j_2 = j_1 + \ell$ or equivalently $i_1-j_1 = i_2-j_2$.
-In the first case, all the terms are independent, and so the expectation factors.
-In the second case, when $k_1 \ne k_2$ we have independence, but otherwise not.
-This gives (all expectations are conditional on $s$):
-%
-\begin{align} \label{moment2-condm}
-%
-\E y[i_1] y[i_2]
-=& \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} 
-\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]}
-\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2]
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \ell} \sum_{k_1} 
-\sum_{k_2} \E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1 \ne k_2} 
-\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_1 - j_1}[j_1+\ell]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} \sum_{k_1=1}^{s[i_1-j_1]} 
-\E x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_1)}^{i_1-j_1}[j_1 + \ell] 
-\nonumber \\
-=& \sum_{j_1 - j_2 \ne \ell} s[i_1-j_1] s[i_2 - j_2] m_1[j_1] m_1[j_2]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1](s[i_1-j_1] - 1) m_1[j_1] m_1[j_1 + \ell]
-\nonumber \\
-& + \sum_{j_1 = 0}^{L-1} s[i_1-j_1] m_2[j_1,j_1 + \ell] .
-%
-\end{align}
-%
-Now take expectations over the Poisson random variables, using Lemma \ref{lem-choose}:
-%
-\begin{align}
-%
-\E y[i_1] y[i_2]
-=& \sum_{j_1 - j_2 \ne \ell} \E s[i_1-j_1] s[i_2 - j_2] m_1[j_1] m_1[j_2]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1](s[i_1-j_1] - 1) m_1[j_1] m_1[j_1 + \ell]
-\nonumber \\
-&       + \sum_{j_1 = 0}^{L-1} \E s[i_1-j_1] m_2[j_1,j_1 + \ell]
-\nonumber \\
-=& \frac{1}{L^2}\sum_{j_1 - j_2 \ne \ell} \gamma^2 m_1[j_1] m_1[j_2]
-+ \frac{1}{L^2} \sum_{j_1 = 0}^{L-1} \gamma^2 m_1[j_1] m_1[j_1 + \ell]
-\nonumber \\
-&       + \frac{1}{L}\sum_{j_1 = 0}^{L-1} \gamma m_2[j_1,j_1 + \ell]
-\nonumber \\
-=&  \bigg(\frac{\gamma}{L}  \sum_{j = 0}^{L-1} m_1[j] \bigg)^2
-+ \frac{\gamma}{L} \sum_{j = 0}^{L-1} m_2[j,j + \ell]
-\nonumber \\
-=&  (\gamma a_x^1)^2 + \gamma a_x^2[\ell].
-%
-\end{align}
-%
-For positive $\sigma$, we observe that any terms linear in the noise vanish in expectation. Denoting by $x^*$ the clean signal component of length $N$, so $y = x^* + \ep$, we have:
-%
-%
-\begin{align}
-\E y[i_1] y[i_2] = \E x^*[i_1] x^*[i_2] + \E \ep[i_1] \ep[i_2]
-= (\gamma a_x^1)^2 + \gamma a_x^2[\ell] + \sigma^2 \delta[i_1 - i_2].
-\end{align}
-%
-We conclude by averaging over $i_1$ and $i_2$ with a fixed value of $\ell = i_2 - i_1$.
-
-%
-
-\subsection{Computing $a_x^3$}
-
-We will first assume $\sigma = 0$. For three distinct $i_1$, $i_2$ and $i_3$, we let $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$. We have:
-%
-\begin{align}
-%
-& y[i_1] y[i_2] y[i_3]
-= \sum_{j_1=0}^{L-1} \sum_{j_2=0}^{L-1} \sum_{j_3=0}^{L-1} 
-\sum_{k_1=1}^{s[i_1-j_1]}\sum_{k_2=1}^{s[i_2-j_2]} \sum_{k_3=1}^{s[i_3-j_3]}
-x_{(k_1)}^{i_1-j_1}[j_1] x_{(k_2)}^{i_2 - j_2}[j_2] x_{(k_3)}^{i_3 - j_3}[j_3].
-\end{align}
-%
-We will break up the outer three sums into disjoint sums with the following ranges of indices:
-%
-\begin{enumerate}
-
-	\item \label{case1}
-	$j_2 = j_1 + \ell_1$ and $j_3 = j_2 + \ell_2 - \ell_1$.
-
-	\item \label{case2}
-	$j_2 = j_1 + \ell_1$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
-
-	\item \label{case3}
-	$j_2 \ne j_1 + \ell_1$ and $j_3 = j_1 + \ell_2$.
-
-	\item \label{case4}
-	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 = j_2 + \ell_2 - \ell_1$.
-
-	\item \label{case5}
-	$j_2 \ne j_1 + \ell_1$ and $j_3 \ne j_1 + \ell_2$ and $j_3 \ne j_2 + \ell_2 - \ell_1$.
-
-\end{enumerate}
-
-For Case \ref{case1}, we have $\ell \equiv i_1 - j_1 = i_2 - j_2 = i_3 - j_3$. We further break up the sum:
-%
-\begin{align}
-%
-&\sum_{j=0}^{L-1} \sum_{k_1=1}^{s[\ell]} \sum_{k_2=1}^{s[\ell]} \sum_{k_3=1}^{s[\ell]} 
-x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-\nonumber \\
-=& \underbrace{ \sum_{j=0}^{L-1} \sum_{k_i \text{distinct}} 
-	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-}_{\text{(a)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2\ne k_3} 
-	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-}_{\text{(b)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_3\ne k_2} 
-	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-}_{\text{(c)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_2=k_3\ne k_1} 
-	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-}_{\text{(d)}}
-\nonumber \\
-&+\underbrace{ \sum_{j=0}^{L-1} \sum_{k_1=k_2=k_3} 
-	x_{(k_1)}^{\ell}[j] x_{(k_2)}^{\ell}[j + \ell_1] x_{(k_3)}^{\ell}[j + \ell_2]
-}_{\text{(e)}}.
-%
-\end{align}
-
-For term (a), the expectation conditional on $s$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} s[\ell](s[\ell]-1)(s[\ell]-2)m_1[j] m_1[j+\ell_1] m_1[j+\ell_2].
-%
-\end{align}
-%
-Using Lemma \ref{lem-choose}, the unconditional expectation of (a) is then:
-%
-\begin{align} \label{aaaa}
-%
-\frac{\gamma^3}{L^3} \sum_{j=0}^{L-1} m_1[j] m_1[j+\ell_1] m_1[j+\ell_2].
-%
-\end{align}
-
-For term (b), the expectation conditional on $s$ is:
-%
-\begin{align}
-%
-\sum_{j=0}^{L-1} s[\ell] (s[\ell] - 1) m_2[j,j+\ell_1] m_1[j + \ell_2]
-%
-\end{align}
-%
-and then again using Lemma \ref{lem-choose} we get the expected value:
-%
-\begin{align} \label{bbbb}
-%
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j,j+\ell_1] m_1[j+\ell_2].
-%
-\end{align}
-
-Similarly, the expected values of terms (c) and (d) are:
-%
-\begin{align} \label{cccc}
-%
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j,j+\ell_2] m_1[j+\ell_1].
-%
-\end{align}
-%
-and
-%
-\begin{align} \label{dddd}
-%
-\frac{\gamma^2}{L^2} \sum_{j=0}^{L-1} m_2[j+\ell_1,j+\ell_2] m_1[j].
-%
-\end{align}
-
-Finally, the expected value of term (e) is easily shown to be:
-%
-\begin{align} \label{eeee}
-%
-\frac{\gamma}{L} \sum_{j=0}^{L-1} m_3[j,j+\ell_1,j+\ell_2].
-%
-\end{align}
-%
-This concludes the computation for Case \ref{case1}.
-
-Moving onto Case \ref{case2}, we have $\Delta_1 \equiv i_1 - j_1 = i_2 - j_2$, and also define $\Delta_2 \equiv i_3 - j_3$. By definition, $\Delta_1 \ne \Delta_2$. The sum is:
-%
-\begin{align}
-%
-& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}
-\sum_{1 \le k_1,k_2 \le s[\Delta_1]} \sum_{k_3=1}^{s[\Delta_2]}
-x_{(k_1)}^{\Delta_1}[j_1] x_{(k_2)}^{\Delta_1}[j_1 + \ell_1] x_{(k_3)}^{\Delta_2}[j_3]   
-\nonumber \\
-=& \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} \sum_{k_3=1}^{s[\Delta_2]}
-\Bigg\{  \sum_{1 \le k_1 \ne k_2 \le s[\Delta_1]} 
-x_{(k_1)}^{\Delta_1}[j_1] x_{(k_2)}^{\Delta_1}[j_1 + \ell_1] x_{(k_3)}^{\Delta_2}[j_3]
-\nonumber \\
-& + \sum_{k_1=1}^{s[\Delta_1]} x_{(k_1)}^{\Delta_1}[j_1] x_{(k_1)}^{\Delta_1}[j_1 + \ell_1] 
-x_{(k_3)}^{\Delta_2}[j_3]  \Bigg\}.
-%
-\end{align}
-%
-Taking expectations conditional on $s$, we then get:
-%
-\begin{align}
-%
-\sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
-\Bigg( & s[\Delta_1] (s[\Delta_1]-1) s[\Delta_2] m_1[j_1] m_1[j_1 + \ell_1] m_1[j_3]
-\nonumber \\
-&  + s[\Delta_1] s[\Delta_2] m_2[j_1,j_1+\ell_1] m_1[j_3] \Bigg).
-%
-\end{align}
-
-Taking expectations over $s$ and using Lemma \ref{lem-choose} then gives:
-%
-\begin{align}
-%
-& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2} 
-m_1[j_1] m_1[j_1 + \ell_1] m_1[j_3]
-\label{ffff} \\
-& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_3 \ne j_1 + \ell_2}  
-m_2[j_1,j_1+\ell_1] m_1[j_3].
-\label{gggg}
-%
-\end{align}
-
-Similarly, Cases \ref{case3} and \ref{case4} give the expressions:
-%
-\begin{align}
-%
-& \frac{\gamma^3}{L^3} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1} 
-m_1[j_1] m_1[j_1 + \ell_2] m_1[j_2]
-\label{hhhh} \\
-& + \frac{\gamma^2}{L^2} \sum_{j_1=0}^{L-1} \sum_{j_2 \ne j_1 + \ell_1}  
-m_2[j_1,j_1+\ell_2] m_1[j_2]
-\label{iiii}
-%
-\end{align}
-%
-and
-%
-\begin{align}
-%
-& \frac{\gamma^3}{L^3} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2} 
-m_1[j_1] m_1[j_2 + \ell_1] m_1[j_2 + \ell_2]
-\label{jjjj}\\
-& + \frac{\gamma^2}{L^2} \sum_{j_2=0}^{L-1} \sum_{j_1 \ne j_2}  
-m_2[j_2+\ell_1,j_2+\ell_2] m_1[j_1].
-\label{kkkk}
-%
-\end{align}
-
-Finally, in Case \ref{case5} we have $i_1 - j_1$, $i_2 - j_2$, and $i_3 - j_3$ are all pairwise distinct.
-Consequently, the $x$ variables are always independent, and the expectation conditional on $s$ (letting $\Delta_{q} = i_q - j_q$, $q=1,2,3$),
-%
-\begin{align}
-%
-\sum_{j_1,j_2,j_3} s[\Delta_1] s[\Delta_2] s[\Delta_3] m_1[j_1] m_1[j_2] m_1[j_3];
-%
-\end{align}
-%
-since the $s[\Delta_q]$'s are pairwise independent, the expectation over $s$ then yields:
-%
-\begin{align} \label{llll}
-%
-\frac{\gamma^3}{L^3} \sum_{j_1,j_2,j_3} m_1[j_1] m_1[j_2] m_1[j_3].
-%
-\end{align}
-
-Now we add all the terms from Cases \ref{case1} to \ref{case5}. Expressions \eqref{aaaa}, \eqref{ffff}, \eqref{hhhh}, \eqref{jjjj}, and \eqref{llll} sum to the expression:
-%
-\begin{align}
-%
-(\gamma a_x^1)^3.
-%
-\end{align}
-
-Expressions \eqref{bbbb}, \eqref{cccc}, \eqref{dddd}, \eqref{gggg},\eqref{iiii}, and \eqref{kkkk} sum to the expression:
-%
-\begin{align}
-%
-\gamma a_x^1  \cdot 
-( \gamma a_x^2[\ell_1] + \gamma a_x^2[\ell_2] + \gamma a_x^2[\ell_2-\ell_1]).
-%
-\end{align}
-%
-Finally, expression \eqref{eeee} is simply:
-%
-\begin{align}
-%
-\gamma a_x^3[\ell_1,\ell_2].
-%
-\end{align}
-%
-
-Now when $\sigma > 0$, we write $y = x^* + \ep$, and
-%
-\begin{align}
-\E y[i_1] y[i_2] y[i_3] =\,\, & \E x^*[i_1] x^*[i_2] x^*[i_3] + \E x^*[i_1] \ep[i_2] \ep[i_3]
-\nonumber \\
-& + \E\ep[i_1] x^*[i_2] \ep[i_3] + \E \ep[i_1] \ep[i_2] x^*[i_3] 
-+ \E \ep[i_1] \ep[i_2]\ep[i_3]
-\nonumber \\
-=\,\, & \E x^*[i_1] x^*[i_2] x^*[i_3] + \gamma  a_x^1 \cdot \sigma^2 \delta[i_2-i_3]
-\nonumber \\
-& + \gamma a_x^1 \cdot \sigma^2 \delta[i_3-i_1] 
-+ \gamma a_x^1 \cdot \sigma^2 \delta[i_2-i_1] .
-\end{align}
-
-We conclude by averaging over all $i_1$, $i_2$, and $i_3$ with fixed values of $\ell_1 = i_2 - i_1$ and $\ell_2 = i_3 - i_1$.
-
-%
-
-\section{Proof of Proposition~\ref{prop:gamma}} \label{sec:proof_prop_gamma}
-Refer to equations \eqref{eq:mean_micrograph}--\eqref{eq:ac3_micrograph} for expressions relating the moments of $y$ and those of $x$, and the parameters $\gamma$ and $\sigma$. First,  note that 
-\begin{align*}
-(a^1_y)^2 & = \frac{\gamma^2}{L^2}\sum_{i=0}^{L-1}\sum_{j=0}^{L-1}x[i]x[j].
-\end{align*}
-Similarly, using $a_x^2[-\ell] = a_x^2[\ell]$:
-\begin{align*}
-2\sum_{\ell = 1}^{L-1}a_y^2[\ell] & = \gamma \sum_{\ell = 1}^{L-1} \left(a_x^2[\ell] + a_x^2[-\ell]\right) \\
-& = \frac{\gamma}{L}\sum_{i=0}^{L-1}\sum_{\ell = 1}^{L-1} x[i]\left(x[i+\ell] + x[i-\ell]\right) \\ &= \frac{\gamma}{L} \sum_{i = 0}^{L-1} \sum_{j = 0, j \neq i}^{L-1} x[i] x[j],
-\end{align*}
-where the last equality is obtained by noting that, given the summation bounds, the set of pairs $(i, i\pm\ell)$ and $(i, j)$ are the same over the valid range $\{0, \ldots, L-1\}^2$.
-To conclude, notice that $a_y^2[0]=\frac{\gamma}{L}\sum_{i=0}^{L-1}x[i]^2 + \sigma^2$ and combine.
-
-\section{Proof of Proposition~\ref{prop:gamma_sigma}} \label{sec:proof_prop_gamma_sigma}
-
-We prove that both $\sigma$ and $\gamma$ are identifiable from the observed first three moments of $y$.
-For convenience, we work with $\beta = \gamma / L$ rather than $\gamma$ itself.
-To this end, we construct two quadratic equations satisfied by $\beta$ and whose coefficients can be computed from observable quantities.
-Then, we show that these equations are independent, and hence that $\beta$ is uniquely defined.
-Given $\beta$, we can estimate $\sigma$ using Proposition~\ref{prop:gamma}.
-
-Throughout the proof, it is important to distinguish between observed and unobserved values.
-We denote the observed values by $E_i$ and $a_y^1,a_y^2,a_y^3$. We use $F_i$ to denote functions of the signal's autocorrelations (which are not directly observable).
-
-Recall that $a_y^1 = \beta(\one^Tx)$ and $a_y^2[0] = \beta\|x\|^2+\sigma^2$, where $\one\in\RL$ is the vector of all-ones and $\|x\|=\sqrt{x[0]^2 + \cdots + x[L-1]^2}$ is the 2-norm.
-Consider the product $E_1$:
-\begin{equation}\label{eq:E1}
-\begin{split}
-E_1 = a_y^1a_y^2[0] =  (\beta(\one^Tx))(\beta\|x\|^2+\sigma^2)  = \sigma^2a_y^1 + L\beta^2F_1,
-\end{split}
-\end{equation}
-where $F_1 = a_x^3[0,0] + \sum_{j=1}^{L-1}(a_x^3[j,j] + a_x^3[0,j])$. 
-% Nicolas: the expression for F_1 is correct, see identifiability_of_gamma_and_sigma_Sep4_2018.m and notes Sep 4, 2018
-The terms of $F_1$ can also be estimated from $a_y^3$, while taking the scaling and bias terms into account. This yields another observable, $E_2$:
-\begin{align} 
-E_2 & = a_y^3[0,0] + \sum_{j=1}^{L-1}(a_y^3[j,j] + a_y^3[0,j]) = L\beta F_1 + (2L+1)\sigma^2a_y^1. \label{eq:E2}
-\end{align}
-% Nicolas: checked this one too.
-Therefore, from~\eqref{eq:E1} and~\eqref{eq:E2} we get:
-\begin{equation} \label{eq:E12}
-E_2\beta -(2L+1)\sigma^2\beta a_y^1 = E_1-\sigma^2a_y^1.
-\end{equation}
-Let $E_3 =a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]$; recall from Proposition~\ref{prop:gamma}:
-\begin{equation} \label{eq:sigma2}
-\sigma^2 = E_3 - (a^1_y)^2/\beta. 
-\end{equation} 
-Plugging into~\eqref{eq:E12} and rearranging, we get a first quadratic equation in $\beta$,
-\begin{equation} \label{eq:quad1}
-\mathcal{A}\beta^2 + \mathcal{B}\beta + \mathcal{C} = 0,
-\end{equation}
-where 
-\begin{align*}
-\mathcal{A} &= E_2 - (2L+1)a_y^1E_3, \\ 
-\mathcal{B} &= -E_1 + (2L+1)(a_y^1)^3 + a_y^1E_3  , \\
-\mathcal{C} &= -(a_y^1)^3.
-\end{align*}
-Importantly, these coefficients are observable quantities. As we assume throughout this proof that $x$ has nonzero mean, $a_y^1 \neq 0$ and we conclude that this equation is non-trivial.
-
-Next, we derive the second quadratic equation for $\beta$. We notice that 
-\begin{equation} \label{eq:E3}
-E_4 = \frac{1}{L}(a_y^1)^3 = \frac{1}{L}\beta^3 (\one ^Tx)^3   = \beta^3 F_2,
-\end{equation}
-where $F_2 = \frac{1}{L}(\one ^Tx)^3$, and we can work out that:
-\begin{equation*}
-F_2 = a_x^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_x^3[j,j] + a_x^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_x^3[i,j].
-\end{equation*}
-Once again, $F_2$ can be estimated from $a_y^3$, taking bias and scaling into account:
-\begin{align}
-E_5 & = a_y^3[0,0] + 3\sum_{j=1}^{L-1} \left(a_y^3[j,j] + a_y^3[0,j]\right) + 6\sum_{1\leq i < j\leq L-1}a_y^3[i,j]  = L \beta F_2 + (6L-3)\sigma^2a_y^1.
-\end{align}
-Consider the following ratio:
-\begin{equation*} 
-\frac{E_5}{E_4} = \frac{L}{\beta^2} + \frac{(6L-3)\sigma^2a_y^1}{E_4}.
-\end{equation*}
-From the latter, we deduce:
-\begin{equation*}
-\sigma^2 = \frac{E_5}{a_y^1(6L-3)}  - \frac{LE_4}{\beta^2a_y^1(6L-3)}.
-\end{equation*}
-Using~\eqref{eq:sigma2} and rearranging, we get the second quadratic:
-\begin{equation} \label{eq:quad2}
-\mathcal{D}\beta^2 + \mathcal{E}\beta + \mathcal{F} = 0,
-\end{equation}
-where
-\begin{align*}
-\mathcal{D} &= E_3 - \frac{E_5}{a_y^1(6L-3)}, \\ 
-\mathcal{E} &= -(a_y^1)^2, \\
-\mathcal{F} &= \frac{LE_4}{a_y^1(6L-3)}.
-\end{align*}
-It is also non-trivial since $E_4 \neq 0$.
-
-To complete the proof, we need to show that the two quadratic equations~\eqref{eq:quad1} and~\eqref{eq:quad2} are independent.
-To this end, it is enough to show that the ratios between coefficients differ.
-From~\eqref{eq:quad1} and~\eqref{eq:E1}, we have:
-\begin{equation*}
-\begin{split}
-\frac{\mathcal{B}}{\mathcal{C}} = \frac{E_1 - (2L+1)(a_y^1)^3 - a_y^1E_3}{(a_y^1)^3} = \frac{a_y^2[0] - (2L+1)(a_y^1)^2 - E_3}{(a_y^1)^2}.
-\end{split}
-\end{equation*}
-In addition, using~\eqref{eq:E3},
-\begin{equation*}
-\frac{\mathcal{E}}{\mathcal{F}} = \frac{(3-6L)(a_y^1)^3}{LE_4} = 3 - 6L . 
-\end{equation*}
-For contradiction, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, that is, 	
-\begin{equation*}
-a_y^2[0] - (2L+1)(a_y^1)^2 - E_3 = (a_y^1)^2(3-6L).
-\end{equation*}
-Rewriting the identity in terms of $x$ and dividing by $\beta$ we get:
-\begin{equation} \label{eq:cond}
-4(L-1)\beta (\1^\top x)^2  - (\1^\top x)^2 + \|x\|^2 = 0.
-\end{equation}	
-For generic $x$,  this polynomial equation is not satisfied so that the quadratic equations are independent. 
-Furthermore, from the inequality $L\|x\|^2 \ge (\1^\top x)^2$ it follows immediately that the equations must be independent so long as
-\begin{equation*}
-\beta > \frac{1}{4L}.
-\end{equation*}
-
-\section{Proof of Proposition~\ref{prop:uniqueness_poisson}} \label{sec:proof_uniqueness_poisson}
-
-We first note that $\gamma a_x^1$, $\gamma a_x^2[\ell] + \sigma^2 \delta[\ell]$, and $\gamma a_x^3[\ell_1,\ell_2]$ can be computed directly form the observed autocorrelations~\eqref{eq:mean_micrograph2},~\eqref{eq:ac2_micrograph2} and~\eqref{eq:ac3_micrograph2}.
-Indeed, recovering  $\gamma a_x^1$ and $\gamma a_x^2[\ell] + \sigma^2 \ell[\ell]$ is immediate from \eqref{eq:mean_micrograph2} and \eqref{eq:ac2_micrograph2}, and $\gamma a_x^3[\ell_1,\ell_2]$ then follows from
-%
-\begin{align}
-\gamma a_x^3[\ell_1,\ell_2]
-= a_y^3[\ell_1,\ell_2] - (a_y^1)^3
-- a_y^1 \cdot \big(a_y^2[\ell_1]  
-+ a_y^2[\ell_2] + a_y^2[\ell_1-\ell_2]- 3(a_y^1)^2 \big).
-\end{align}
-
-Let us assume that $x$ is generic. Indeed, we observe the product:
-%
-\begin{align}
-L^2(\gamma a_x^1) (\gamma a_x^2[1])
-&= \gamma^2\left( \sum_{i} x[i] \right) \left(\sum_{j} x[j]x[j+1] \right)
-\nonumber \\
-&= \gamma^2\sum_{j} \sum_{i} x[i]x[j]x[j+1]
-\nonumber \\
-&=  \gamma^2\sum_{j} \sum_{\ell} x[j+\ell]x[j]x[j+1]
-\nonumber \\
-&=  \gamma^2\sum_{\ell \ge 0} \sum_{j} x[j+\ell]x[j]x[j+1] 
-+ \gamma^2\sum_{\ell < 0} \sum_{j} x[j+\ell]x[j]x[j+1]
-\nonumber \\
-&=  \gamma^2\sum_{\ell=0}^{L-1} a_x^3[1,\ell] 
-+ \gamma^2\sum_{\ell > 0} \sum_{j} x[j-\ell]x[j]x[j+1]
-\nonumber \\
-&=  \gamma^2\sum_{\ell=0}^{L-1} a_x^3[1,\ell] 
-+ \gamma^2\sum_{\ell > 0} \sum_{j} x[j]x[j+\ell]x[j+\ell+1]
-\nonumber \\
-&= \gamma\left( \sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell]
-+ \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]  \right).
-\end{align}
-%
-Since we also observe $\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] + \sum_{\ell=1}^{L-2} \gamma a_x^3[\ell,\ell+1]$, we can form the ratio and solve for $\gamma$.
-
-\begin{align}
-\gamma = L \frac{(\gamma a_x^1) (\gamma a_x^2[1])}
-{\sum_{\ell=0}^{L-1} \gamma a_x^3[1,\ell] 
-	+ \sum_{\ell=2}^{L-1} \gamma a_x^3[\ell,\ell+1]},
-\end{align}
-%
-Then, similarly to Appendix~\ref{sec:proof_prop_gamma}, one can solve for $\sigma^2$:
-\begin{align}
-\sigma^2 = a_y^2[0] + 2\sum_{\ell = 1}^{L-1}a_y^2[\ell]-\frac{L (a^1_y)^2}{\gamma}
-- (2 L - 1) (a_y^1)^2.
-\end{align}
-Once $\gamma$ and $\sigma$ were computed, one can recover $x$ from $a_x^2$ and $a_x^3$  by Proposition~\ref{prop:uniqueness}.
+\noindent \textbf{Response:} We find this figure important to inspect (empirically) how many signals can be estimated simultaneously from a mix of their autocorrelations.
+We agree that this figure should be visualized in a colored version of the manuscript.
+We used a similar figure for the same purpose (but for a different problem) in a previous publication: Boumal, Nicolas, et al.
+``Heterogeneous multireference alignment: A single pass approach.'' \emph{2018 52nd Annual Conference on Information Sciences and Systems (CISS)}.
+IEEE, 2018.
 

### 2019-05-31 InverseProblemsV2/inverse_problems_v2.tex
revision

@@
 \end{align}
-where 
+where \revised{$\gamma a_x^3$ is indeed observable since}
 \begin{align}
@@
 In this context, the computational problem of recovering the signal from its second-order autocorrelation is usually referred to as \emph{phase retrieval} or the \emph{phase problem}.
-Despite the uniqueness result, recently it has been shown that the problem is  ill-conditioned---at least for 2-D images~\cite{barnett2018geometry}.
+\revised{However, for 2-D images it has been shown recently that the problem is  ill-conditioned unless the support of the image is known exactly~\cite{barnett2018geometry}}.
 That is, there exist other images whose second-order autocorrelations agree up to machine precision.
@@
 
+\revised{In this section, to assess the quality of our reconstruction, we compare against the ground truth.
+In a realistic setting, the ground truth is of course not available, which raises the question of how one can validate the results.
+A common technique used in cryo-EM is to split the data in two halves, produce two independent reconstructions based on these halves, then to compare the two reconstructions.
+It is clear how the same technique can be applied to our setting.}
+
 \subsection{Experiment 1} 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_466300}
+	\includegraphics[width=1\linewidth]{heterogeneous_progressive_n12300000000_143392}
 	\caption{Experiment described in Section~\ref{sec:XP1}.
@@
 For the experiment depicted in Figure~\ref{fig:1Dheterosignals}, we fix $K = 3$ signals of length $L = 21$: see the three red signals in the first column.
+\revised{The first signal's actual support has length 11 (rather than 21), which allows us to simulate the situation in which the support of the signal is overestimated.}
+
 Following~\eqref{eq:model}, we generate an observation $y$ of length $12.3 \cdot 10^9$.
@@
 Then, i.i.d.\ Gaussian noise with mean zero and standard deviation $\sigma = 3$ is added, to form the observed $y$.
-The resulting signal-to-noise ratio of $y$
+%The resulting signal-to-noise ratio of $y$
 % sqrt((m_want*sum(X.^2)')/(sigma^2*n))
-is about 1/9.
+%is about 1/9.
 
@@
 We find that this procedure is reliable for a wide range of experimental parameters.
-To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt}, which allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
+To solve~\eqref{eq:optim1D}, we run the trust-region method implemented in Manopt~\cite{manopt} \revised{from 10 different random initial guesses and keep the one with lowest cost function value.}
+\revised{Manopt} allows to treat the positivity constraints on coefficients $\hat \gamma_k$.
 Notice that the cost function is a polynomial in the variables, so that it is straightforward to compute it and its derivatives.
+
+\revised{To asses reconstruction quality, we report the relative root mean squared error between the estimated signals and the ground truth (up to permutation of the $K$ signals.) For the first signal (with the overestimated support), we also translationally aligned the estimate with the ground truth because its estimation is only possible up to shift.}
 

### 2019-05-31 InverseProblemsV2/reponse.tex
revision

@@
 
-We thank the editor and the referees for reading our paper. Below, we provide a detailed, one-to-one response to all comments.
+We thank the editor and the referees for their comments on our paper. Below, we provide a detailed, one-to-one response to all comments.
 
@@
 
-\noindent \textbf{Response:} The question of statistical validation is of great importance in any scientific field, including single particle reconstruction using cryo-EM.
+\noindent \textbf{Response:} We agree that statistical validation is important, in particular for single particle reconstruction using cryo-EM.
 %This question is more general that the specific method applied.
-Unfortunately,  there is  no rigorous method to validate a structure that was constituted using cryo-EM.
+Several heuristics are used in cryo-EM. A common one is to split the data into two halves, reconstruct two structures independently, then compare them. 
+It is easy to apply the same technique to our framework. We added a few sentences to this effect in the numerical experiments section.
+
+%Unfortunately,  there is  no rigorous method to validate a structure that was constituted using cryo-EM.
 In practice, researchers in the field use several useful heuristics, such as  comparing the elucidated structure with structures that were reconstructed by other imaging modalities (e.g., X-ray crystallography), or different statistical techniques (e.g., expectation-maximization).
@@
 
-While validation is beyond the scope of this paper, autocorrelation analysis provides a flexible framework to describe reach generative models of the data.
+%While validation is beyond the scope of this paper, autocorrelation analysis provides a flexible framework to describe reach generative models of the data.
 We added a paragraph in the summary to explain this issue.
+
+%\TODO{Split the data into to halves independently and compare; checking objective and flexible model; analysis from optimization perspective of the LS }
 
@@
 \noindent \textbf{Response:} Section 4.4 discusses the application of our approach to 2-D images.
-In this section, we underscore the importance of the knowledge of the exact support for phase retrieval as was shown in [9].
-In our setup, if the support cannot be estimated accurately, the solution is to consider the third-order autocorrelation.
-That being said, as we mention in Section 4, the support of the signal (at least in 1-D) can be determined from the second-order autocorrelation if enough data is provided.
+In this section, we underscore the importance of the knowledge of the exact support for phase retrieval (recovery from second-order autocorrelation) as was shown in [9].
+We revised a couple of sentences in this section for the sake of clarity. 
+If exact support knowledge is not available, our proposed solution is to consider the third-order autocorrelation.
+To demonstrate it, in the revised manuscript, we changed Experiment 1.
+Now, half of the first signal in Figure 1 is zero, which allows us to simulate the situation in which the support of the signal is overestimated.
+Our algorithm still recovers the signal accurately.
 \\
@@
 
-\noindent \textbf{Response:} We find this figure important to inspect (empirically) how many signals can be estimated simultaneously from a mix of their autocorrelations.
+\noindent \textbf{Response:} The number of numbers we compute (as autocorrelations) is a growing function of the signal length $L$.
+Hence, we expect that, as $L$ grows, we should be able to estimate more and more distinct signals in the heterogeneous case.
+The experiment reported in Figure 2 illustrates how $K$ (the number of signals we can estimate simultaneously) grows as a function of $L$.
+Since to do the actual recovery we need to solve a non-convex optimization problem, this experiment is setup so that we can distinguish between the effects of statistical and computational difficulties.
+
+We find this figure important to inspect (empirically) how many signals can be estimated simultaneously from a mix of their autocorrelations.
 We agree that this figure should be visualized in a colored version of the manuscript.
-We used a similar figure for the same purpose (but for a different problem) in a previous publication: Boumal, Nicolas, et al.
+We used a similar figure for the same purpose (but for a different problem) in a previous publication: Boumal, N., et al.
 ``Heterogeneous multireference alignment: A single pass approach.'' \emph{2018 52nd Annual Conference on Information Sciences and Systems (CISS)}.

### 2019-06-03 InverseProblemsV2/reponse.tex
With Amit's comments

@@
 \noindent \textbf{Response:} Section 4.4 discusses the application of our approach to 2-D images.
-In this section, we underscore the importance of the knowledge of the exact support for phase retrieval (recovery from second-order autocorrelation) as was shown in [9].
+For Einstein's image used in the manuscript, the boundary of the second-order autocorrelation  can be identified easily if the second-order autocorrelation is known precisely (that is, $N\to\infty$); see Figure~\ref{fig:XC} (in this report).
+Since the image is square, it implies the support of the image itself. 
+In Section 4.4, we underscore the importance of the knowledge of the exact support for phase retrieval (recovery from second-order autocorrelation) as was shown in [9]. 
 We revised a couple of sentences in this section for the sake of clarity.
+
 If exact support knowledge is not available, our proposed solution is to consider the third-order autocorrelation.
@@
 \\
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Xcorr}
+	\caption{	\label{fig:XC} The second-order autocorrelation of Einstein's image used in the paper (padded by zeros).}
+\end{figure}
 
@@
 
-\noindent \textbf{Response:} The number of numbers we compute (as autocorrelations) is a growing function of the signal length $L$.
+\noindent \textbf{Response:} The number of autocorrelation entries we compute increases with the signal length $L$.
 Hence, we expect that, as $L$ grows, we should be able to estimate more and more distinct signals in the heterogeneous case.

### 2019-06-03 InverseProblemsV2/inverse_problems_v2_highlighted.tex
submitted files

--- 2019-05-31 InverseProblemsV2/inverse_problems_v2.tex
@@
 
-In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$ and the noise level $\sigma$ for generic $x$.
+In the homogeneous case ($K=1$), we show in Section~\ref{sec:theory_homogeneous_poisson} that $a_y^1,a_y^2$ and $a_y^3$ identify uniquely the signal $x$, the Poisson parameter $\gamma$, and the noise level $\sigma$ for generic $x$.
 

### 2019-06-17 InverseProblemsV2/inverse_problems_v2.tex
small change to abstract (to do -> of doing)

@@
 \newcommand{\TODO}[1]{{\color{red}{[#1]}}}
-\newcommand{\revised}[1]{{\color{magenta}{#1}}}
+%\newcommand{\revised}[1]{{\color{magenta}{#1}}}
+\newcommand{\revised}[1]{{\color{black}{#1}}}
 \newcommand{\R}{\mathbb{R}}
@@
 In the high noise regime, however, neither detection nor clustering can be performed reliably, so that strategies along these lines are destined to fail.  
-Notwithstanding, using autocorrelation analysis, we show that the impossibility to detect and cluster signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
+Notwithstanding, using autocorrelation analysis, we show that the impossibility of detecting and clustering signal occurrences in the presence of high noise does not necessarily preclude signal estimation.
 Specifically, to estimate the signals, we derive simple relations between the autocorrelations of the observation and those of the signals.
@@
 \bibliographystyle{plain}
-\bibliography{ref}
+%\bibliography{ref}
+\input{inverse_problems_v2.bbl}
 
